### 2022-09-28 code/0_preprocessing/0_preprocessingCN.Rmd
started new repo for manuscript

---
title: "preprocessing"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("ggplot2")
library("tidyjson")
library("gtools")
library("dplyr")
library(lme4)
library(digest)
library(lmerTest)
```
### Getting CN data
```{r import data, warning=FALSE, eval=F}
# read in raw data files
#folder_path = "~/Triad/data_expt/data_M/"
all_files <- list.files(path=folder_path, pattern="")

split_responses <- function(responses) {
  responses <- as.character(responses)
  response_list <- unlist(strsplit(responses, ',|:'))
  response_list <- response_list[seq(2, length(response_list), 2)]
  response_list <- gsub("}", "", response_list)
  response_list <- gsub("\"", "", response_list)
  return(response_list)
}

colnames <- c("subject", "trial_index", "rt", "trial_type", "stim_type", "cue", "top_opt", "bottom_opt", "responses", "variable_type")

df <- data.frame()
#reading each file within the range and append them to create one file
for (f in all_files){
  file_path = paste(folder_path, f, sep="")
  result <- read_json(path = file_path, format = "infer")     # read the file
  temp <- data.frame()
  for (page in result[[2]][[1]]) { #iterating through each trial
    #if (page["subject"] %in% exclude_subjects) { next }
    if (page["trial_type"] == "survey-multi-choice") { #only triads

       trials <- matrix(NA, nrow = length(page["options"][[1]]), ncol = length(colnames), 
                        dimnames = list(NULL, colnames))
       trials <- as.data.frame(trials)

       trials$top_opt <- lapply(page["options"][[1]], `[[`, 1)
       trials$bottom_opt <- lapply(page["options"][[1]], `[[`, 2)
       trials$stim_type <- page["stimulus_type"][[1]]
       trials$cue <- page["prompt"][[1]]

       trials$responses <- split_responses(page["responses"])

       trials$subject <- page["subject"]
       trials$trial_index <- page["trial_index"]
       trials$rt <- page["rt"]
       trials$trial_type <- page["trial_type"]

    } else {
      trials <- as.data.frame(page)
    }
    temp <- smartbind(temp, select(trials, one_of(colnames)))
  }
  df <- smartbind(df, select(temp, one_of(colnames)))
}

anonymise <- function(data, cols_to_anon, algo = "sha256")
{
  if(!require(digest)) stop("digest package is required")
  to_anon <- subset(data, select = cols_to_anon)
  unname(apply(to_anon, 1, digest, algo = algo))
}

cols_to_anon <- c("subject")
df$subject <- anonymise(df, cols_to_anon)

#write.csv(df, "data_anon0115_full.csv")

```

```{r recoded a cue due to typo}
df_raw <- df

df <- df_raw %>%
  mutate(responses = ifelse(responses == "锤子 ", "锤子", responses)) %>%
  mutate(top_opt = ifelse(top_opt == "锤子 ", "锤子", top_opt)) %>%
  mutate(bottom_opt = ifelse(bottom_opt == "锤子 ", "锤子", bottom_opt))

write.csv(df, "data_M_0530.csv")

```

### 2022-09-28 code/0_preprocessing/0_preprocessingUS.Rmd
started new repo for manuscript

--- 2022-09-28 code/0_preprocessing/0_preprocessingCN.Rmd
@@
 ```
-### Getting CN data
+### Getting US data
 ```{r import data, warning=FALSE, eval=F}
-# read in raw data files
-#folder_path = "~/Triad/data_expt/data_M/"
+# read in all raw data files
+#folder_path = "~/Triad/data_expt/data_E/"
 all_files <- list.files(path=folder_path, pattern="")
@@
 df$subject <- anonymise(df, cols_to_anon)
-
-#write.csv(df, "data_anon0115_full.csv")
-
 ```
@@
 df <- df_raw %>%
-  mutate(responses = ifelse(responses == "锤子 ", "锤子", responses)) %>%
-  mutate(top_opt = ifelse(top_opt == "锤子 ", "锤子", top_opt)) %>%
-  mutate(bottom_opt = ifelse(bottom_opt == "锤子 ", "锤子", bottom_opt))
+  mutate(responses = ifelse(responses == "hammer ", "hammer", responses)) %>%
+  mutate(top_opt = ifelse(top_opt == "hammer ", "hammer", top_opt)) %>%
+  mutate(bottom_opt = ifelse(bottom_opt == "hammer ", "hammer", bottom_opt))
 
-write.csv(df, "data_M_0530.csv")
+write.csv(df, "data_E_0319.csv")
 

### 2022-09-28 code/0_preprocessing/0_preprocessingVN.Rmd
started new repo for manuscript

--- 2022-09-28 code/0_preprocessing/0_preprocessingUS.Rmd
@@
 ---
-title: "preprocessing"
+title: "Untitled"
 output: html_document
@@
 ```
-### Getting US data
+
+### Getting VN data
+
 ```{r import data, warning=FALSE, eval=F}
-# read in all raw data files
-#folder_path = "~/Triad/data_expt/data_E/"
+# read in raw data files
+#folder_path = "~/Triad/data_expt/data_V/"
 all_files <- list.files(path=folder_path, pattern="")
@@
 df <- df_raw %>%
-  mutate(responses = ifelse(responses == "hammer ", "hammer", responses)) %>%
-  mutate(top_opt = ifelse(top_opt == "hammer ", "hammer", top_opt)) %>%
-  mutate(bottom_opt = ifelse(bottom_opt == "hammer ", "hammer", bottom_opt))
+  mutate(responses = ifelse(responses == "búa ", "búa", responses)) %>%
+  mutate(top_opt = ifelse(top_opt == "búa ", "búa", top_opt)) %>%
+  mutate(bottom_opt = ifelse(bottom_opt == "búa ", "búa", bottom_opt))
 
-write.csv(df, "data_E_0319.csv")
-
+write.csv(df, "data_V_0530.csv")
 ```

### 2022-09-28 code/1_exclusions/1_exclusionsCN.Rmd
started new repo for manuscript

```{r setup, echo = FALSE, include = FALSE}
library("papaja")
library("knitr") # for knitting things
library("tidyverse") # for all things tidyverse
library("car")
library("lme4")
library("patchwork")
library("effsize")

# these options here change the formatting of how comments are rendered
opts_chunk$set(
  comment = "",
  results = "hold",
  fig.show = "hold")

# set the default ggplot theme 
theme_set(theme_classic())
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r loading data M, warning=FALSE, include=F}
df.resp_M <- read.csv("../../data/responding/data_CN.csv") %>%
  select(-X)

# check for participants who completed the entire experiment. Because the experiment is
# quite long, some participants decide to come back afterwards, so there are a few files
# that are recorded as incomplete. 
df.ppts_finished_M <- df.resp_M %>% 
  group_by(subject) %>%
  summarize(finished = ifelse("demo-final" %in% unique(variable_type), "yes", "no")) %>%
  filter(finished == "yes")

df.ppts_not_finished_M <- df.resp_M %>% 
  group_by(subject) %>%
  summarize(finished = ifelse("demo-final" %in% unique(variable_type), "yes", "no")) %>%
  filter(finished == "no")

df.resp_M <- df.resp_M %>%
  filter(subject %in% df.ppts_finished_M$subject)

df.ppts_att_M <- df.resp_M %>%
  filter(stim_type == "attention check") %>%
  mutate(correct_response = strsplit(cue, "选择")) %>%
  mutate(correct_response = sapply(correct_response, "[[", 2)) %>%
  mutate(correct_response = str_replace_all(correct_response, "“", "")) %>%
  mutate(correct_response = str_replace_all(correct_response, "”", "")) %>%
  mutate(pass_att_check = ifelse(responses == correct_response, 1, 0)) %>%
  group_by(subject) %>%
  summarize(pass_att_check_percent = mean(pass_att_check)) %>%
  filter(pass_att_check_percent == 1.0)

df.resp_M <- df.resp_M %>%
  filter(subject %in% df.ppts_att_M$subject) 
```

```{r exclusion M, include = F, warning = F}
#non-native speaker
split_responses_demog <- function(responses) {
  responses <- as.character(responses)
  response_list <- unlist(strsplit(responses, ',|:'))
  response_list <- response_list[seq(1, length(response_list))]
  response_list <- gsub("}", "", response_list)
  response_list <- gsub("\"", "", response_list)
  return(response_list)
}

NATIVE_LANG = 2
get_native_lang <- Vectorize(function(responses) {
  responses <- split_responses_demog(responses)
  if(responses[NATIVE_LANG-1] != "{firstlanguage") 
    {warnings("cannot find native language answer")}
  else
    {return (responses[NATIVE_LANG])}
})

df.ppts_non_native_lang_M <- df.resp_M %>%
  select(subject, responses, variable_type) %>%
  filter(variable_type == "demog_language") %>%
  mutate(native_speaker = get_native_lang(responses)) %>%
  filter(native_speaker == "不是")

ppts_non_native_lang_M = unique(df.ppts_non_native_lang_M$subject) #2
percent_dropped = length(ppts_non_native_lang_M) / length(unique(df.resp_M$subject))
percent_dropped #0.01398601

#fluent in English
SPEAKER = 2
SPEAKING = 23
UNDERSTANDING = 46

get_speaker <- Vectorize(function(responses) {
  responses <- split_responses_demog(responses)
  return (responses[SPEAKER])
})

get_fluency_speaking <- Vectorize(function(responses) {
  responses <- split_responses_demog(responses)
  return (responses[SPEAKING])
})

get_fluency_understanding <- Vectorize(function(responses) {
  responses <- split_responses_demog(responses)
  return (responses[UNDERSTANDING])
})

df.lang_en_M <- df.resp_M %>%
  select(subject, responses, variable_type) %>%
  filter(variable_type == "demog_language_en") %>%
  mutate(en_speaker = get_speaker(responses))

df.lang_en_fluency_M <- df.resp_M %>%
  select(subject, responses, variable_type) %>%
  filter(variable_type == "demog_conditional_language_en_fluency") %>%
  mutate(en_fluency_sp = as.numeric(get_fluency_speaking(responses))) %>%
  mutate(en_fluency_ud = as.numeric(get_fluency_understanding(responses)))

df.lang_en_M <- full_join(df.lang_en_M, 
                          df.lang_en_fluency_M, 
                          by = "subject") %>%
  select(subject, en_speaker, en_fluency_sp, en_fluency_ud) %>%
  filter(en_speaker == "能",
         en_fluency_sp > 4, 
         en_fluency_ud > 4)

ppts_en_speaker_M = unique(df.lang_en_M$subject) #50
percent_dropped = length(ppts_en_speaker_M) / length(unique(df.resp_M$subject))
percent_dropped #0.3496503 # will not use this criterion

df.lang_vi_M <- df.resp_M %>%
  select(subject, responses, variable_type) %>%
  filter(variable_type == "demog_language_vi") %>%
  mutate(vi_speaker = get_speaker(responses))

df.lang_vi_fluency_M <- df.resp_M %>%
  filter(variable_type == "demog_conditional_language_vi_fluency") %>%
  mutate(vi_fluency_sp = as.numeric(get_fluency_speaking(responses))) %>%
  mutate(vi_fluency_ud = as.numeric(get_fluency_understanding(responses)))

df.lang_vi_M <- full_join(df.lang_vi_M, 
                          df.lang_vi_fluency_M, 
                          by = "subject") %>%
  select(subject, vi_speaker, vi_fluency_sp, vi_fluency_ud) %>%
  filter(vi_speaker == "能",
         vi_fluency_sp > 4, 
         vi_fluency_ud > 4)

ppts_vi_speaker_M = unique(df.lang_vi_M$subject) #50
percent_dropped = length(ppts_vi_speaker_M) / length(unique(df.resp_M$subject))
percent_dropped #0

#have lived outside the sample country for more than 2 years
#have travelled extensively (more than 6 international experiences of 2 days or longer) 
YEARSABROAD = 2
OVERSEAEXP = 4

get_lived_abroad <- Vectorize(function(responses) {
  responses <- split_responses_demog(responses)
  return (responses[YEARSABROAD])
})

get_oversea_exp <- Vectorize(function(responses) {
  responses <- split_responses_demog(responses)
  return (responses[OVERSEAEXP])
})

df.abroad_M <- df.resp_M %>%
  select(subject, responses, variable_type) %>%
  filter(variable_type == "demog_oversea_experience") %>%
  mutate(lived_abroad = get_lived_abroad(responses)) %>%
  mutate(oversea_exp = get_oversea_exp(responses))

df.lived_abroad_M <- df.abroad_M %>%
  filter(lived_abroad == "是")

ppts_lived_abroad_M = unique(df.lived_abroad_M$subject) #23
percent_dropped = length(ppts_lived_abroad_M) / length(unique(df.resp_M$subject))
percent_dropped # 0.1608392

df.oversea_exp_M <- df.abroad_M %>%
  filter(oversea_exp == "六段或更多国际经历")

ppts_oversea_exp_M = unique(df.oversea_exp_M$subject) #0
percent_dropped = length(ppts_oversea_exp_M) / length(unique(df.resp_M$subject))
percent_dropped #0

df.resp_M <- df.resp_M %>%
  filter(!(subject %in% ppts_non_native_lang_M),
         !(subject %in% ppts_lived_abroad_M),
         !(subject %in% ppts_vi_speaker_M),
         !(subject %in% ppts_oversea_exp_M),)

length(unique(df.resp_M$subject)) 
```

```{r}
write.csv(df.resp_M, "../../data/dataCN_excl.csv")
```

### 2022-09-28 code/1_exclusions/1_exclusionsUS.Rmd
started new repo for manuscript

```{r setup, echo = FALSE, include = FALSE}
library("papaja")
library("knitr") # for knitting things
library("tidyverse") # for all things tidyverse
library("car")
library("lme4")
library("patchwork")
library("effsize")

# these options here change the formatting of how comments are rendered
opts_chunk$set(
  comment = "",
  results = "hold",
  fig.show = "hold")

# set the default ggplot theme 
theme_set(theme_classic())

```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r loading data E, warning=FALSE, include=F}
df.resp_E <- read.csv("../../data/responding/data_US.csv") %>%
  select(-X)

# check for participants who completed the entire experiment. Because the experiment is
# quite long, some participants decide to come back afterwards, so there are a few files
# that are recorded as incomplete. 
df.ppts_finished_E <- df.resp_E %>% 
  group_by(subject) %>%
  summarize(finished = ifelse("demo-final" %in% unique(variable_type), "yes", "no")) %>%
  filter(finished == "yes")

df.resp_E <- df.resp_E %>%
  filter(subject %in% df.ppts_finished_E$subject)

df.ppts_att_E <- df.resp_E %>%
  filter(stim_type == "attention check") %>%
  mutate(correct_response = strsplit(cue, "Choose ")) %>%
  mutate(correct_response = sapply(correct_response, "[[", 2)) %>%
  mutate(pass_att_check = ifelse(responses == correct_response, 1, 0)) %>%
  group_by(subject) %>%
  summarize(pass_att_check_percent = mean(pass_att_check)) %>%
  filter(pass_att_check_percent == 1.0)

df.resp_E <- df.resp_E %>%
  filter(subject %in% df.ppts_att_E$subject) 
```

```{r exclusion E, include = F, warning = F}
#non-native speaker
split_responses_demog <- function(responses) {
  responses <- as.character(responses)
  response_list <- unlist(strsplit(responses, ',|:'))
  response_list <- response_list[seq(1, length(response_list))]
  response_list <- gsub("}", "", response_list)
  response_list <- gsub("\"", "", response_list)
  return(response_list)
}

NATIVE_LANG = 2
get_native_lang <- Vectorize(function(responses) {
  responses <- split_responses_demog(responses)
  if(responses[NATIVE_LANG-1] != "{firstlanguage") 
    {warnings("cannot find native language answer")}
  else
    {return (responses[NATIVE_LANG])}
})

df.ppts_non_native_lang_E <- df.resp_E %>%
  select(subject, responses, variable_type) %>%
  filter(variable_type == "demog_language") %>%
  mutate(native_speaker = get_native_lang(responses)) %>%
  filter(native_speaker == "No")

ppts_non_native_lang_E = unique(df.ppts_non_native_lang_E$subject)#18
percent_dropped = length(ppts_non_native_lang_E) / length(unique(df.resp_E$subject))
percent_dropped #0.1034482775

#fluent in Vietnamese & Mandarin
SPEAKER = 2
SPEAKING = 23
UNDERSTANDING = 46

get_speaker <- Vectorize(function(responses) {
  responses <- split_responses_demog(responses)
  return (responses[SPEAKER])
})

get_fluency_speaking <- Vectorize(function(responses) {
  responses <- split_responses_demog(responses)
  return (responses[SPEAKING])
})

get_fluency_understanding <- Vectorize(function(responses) {
  responses <- split_responses_demog(responses)
  return (responses[UNDERSTANDING])
})

df.lang_vi_E <- df.resp_E %>%
  select(subject, responses, variable_type) %>%
  filter(variable_type == "demog_language_vi") %>%
  mutate(vi_speaker = get_speaker(responses))

df.lang_vi_fluency_E <- df.resp_E %>%
  select(subject, responses, variable_type) %>%
  filter(variable_type == "demog_conditional_language_vn_fluency") %>%
  mutate(vi_fluency_sp = as.numeric(get_fluency_speaking(responses))) %>%
  mutate(vi_fluency_ud = as.numeric(get_fluency_understanding(responses)))

df.lang_vi_E <- full_join(df.lang_vi_E, 
                          df.lang_vi_fluency_E, 
                          by = "subject") %>%
  select(subject, vi_speaker, vi_fluency_sp, vi_fluency_ud) %>%
  filter(vi_speaker == "Yes",
         vi_fluency_sp > 4, 
         vi_fluency_ud > 4)

ppts_vi_speaker_E = unique(df.lang_vi_E$subject) #4
percent_dropped = length(ppts_vi_speaker_E) / length(unique(df.resp_E$subject))
percent_dropped #0.02298851

df.lang_zh_E <- df.resp_E %>%
  select(subject, responses, variable_type) %>%
  filter(variable_type == "demog_language_cn") %>%
  mutate(zh_speaker = get_speaker(responses))

df.lang_zh_fluency_E <- df.resp_E %>%
  select(subject, responses, variable_type) %>%
  filter(variable_type == "demog_conditional_language_cn_fluency") %>%
  mutate(zh_fluency_sp = as.numeric(get_fluency_speaking(responses))) %>%
  mutate(zh_fluency_ud = as.numeric(get_fluency_understanding(responses)))

df.lang_zh_E <- full_join(df.lang_zh_E, 
                          df.lang_zh_fluency_E, 
                          by = "subject") %>%
  select(subject, zh_speaker, zh_fluency_sp, zh_fluency_ud) %>%
  filter(zh_speaker == "Yes",
         zh_fluency_sp > 4, 
         zh_fluency_ud > 4)

ppts_zh_speaker_E = unique(df.lang_zh_E$subject) #30
percent_dropped = length(ppts_zh_speaker_E) / length(unique(df.resp_E$subject))
percent_dropped #0.1742424

#have lived outside the sample country for more than 2 years
#have travelled extensively (more than 6 international experiences of 2 days or longer) 
YEARSABROAD = 2
OVERSEAEXP = 4

get_lived_abroad <- Vectorize(function(responses) {
  responses <- split_responses_demog(responses)
  return (responses[YEARSABROAD])
})

get_oversea_exp <- Vectorize(function(responses) {
  responses <- split_responses_demog(responses)
  return (responses[OVERSEAEXP])
})

df.abroad_E <- df.resp_E %>%
  select(subject, responses, variable_type) %>%
  filter(variable_type == "demog_oversea_experience") %>%
  mutate(lived_abroad = get_lived_abroad(responses)) %>%
  mutate(oversea_exp = get_oversea_exp(responses))

df.lived_abroad_E <- df.abroad_E %>%
  filter(lived_abroad == "Yes")

ppts_lived_abroad_E = unique(df.lived_abroad_E$subject) #29
percent_dropped = length(ppts_lived_abroad_E) / length(unique(df.resp_E$subject))
percent_dropped #0.1666667

df.oversea_exp_E <- df.abroad_E %>%
  filter(oversea_exp == "Six or more experiences")

ppts_oversea_exp_E = unique(df.oversea_exp_E$subject) #77
percent_dropped = length(ppts_oversea_exp_E) / length(unique(df.resp_E$subject))
percent_dropped #0.44 # will not use this criterion

df.resp_E <- df.resp_E %>%
  filter(!(subject %in% ppts_non_native_lang_E),
         !(subject %in% ppts_vi_speaker_E), 
         !(subject %in% ppts_zh_speaker_E),
         !(subject %in% ppts_lived_abroad_E))

length(unique(df.resp_E$subject)) #132
```

```{r}
write.csv(df.resp_E, "../../data/dataUS_excl.csv")
```

### 2022-09-28 code/1_exclusions/1_exclusionsVN.Rmd
started new repo for manuscript

```{r setup, echo = FALSE, include = FALSE}
library("papaja")
library("knitr") # for knitting things
library("tidyverse") # for all things tidyverse
library("car")
library("lme4")
library("patchwork")
library("effsize")

# these options here change the formatting of how comments are rendered
opts_chunk$set(
  comment = "",
  results = "hold",
  fig.show = "hold")

# set the default ggplot theme 
theme_set(theme_classic())
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r loading data V, include=F}
df.resp_V <- read.csv("../../data/responding/data_VN.csv") %>%
  select(-X)

# check for participants who completed the entire experiment. Because the experiment is
# quite long, some participants decide to come back afterwards, so there are a few files
# that are recorded as incomplete. 
df.ppts_finished_V <- df.resp_V %>% 
  group_by(subject) %>%
  summarize(finished = ifelse("demo-final" %in% unique(variable_type), "yes", "no")) %>%
  filter(finished == "yes")

df.resp_V <- df.resp_V %>%
  filter(subject %in% df.ppts_finished_V$subject)

df.ppts_att_V <- df.resp_V %>%
  filter(stim_type == "attention check") %>%
  mutate(correct_response = strsplit(cue, "Chọn ")) %>%
  mutate(correct_response = sapply(correct_response, "[[", 2)) %>%
  mutate(pass_att_check = ifelse(responses == correct_response, 1, 0)) %>%
  group_by(subject) %>%
  summarize(pass_att_check_percent = mean(pass_att_check)) %>%
  filter(pass_att_check_percent == 1.0)

df.resp_V <- df.resp_V %>%
  filter(subject %in% df.ppts_att_V$subject) #73
```

```{r exclusion V, include = F}
#non-native speaker
split_responses_demog <- function(responses) {
  responses <- as.character(responses)
  response_list <- unlist(strsplit(responses, ',|:'))
  response_list <- response_list[seq(1, length(response_list))]
  response_list <- gsub("}", "", response_list)
  response_list <- gsub("\"", "", response_list)
  return(response_list)
}

NATIVE_LANG = 2
get_native_lang <- Vectorize(function(responses) {
  responses <- split_responses_demog(responses)
  if(responses[NATIVE_LANG-1] != "{firstlanguage") 
    {warnings("cannot find native language answer")}
  else
    {return (responses[NATIVE_LANG])}
})

df.ppts_non_native_lang_V <- df.resp_V %>%
  select(subject, responses, variable_type) %>%
  filter(variable_type == "demog_language") %>%
  mutate(native_speaker = get_native_lang(responses)) %>%
  filter(native_speaker == "Không")

ppts_non_native_lang_V = unique(df.ppts_non_native_lang_V$subject)
percent_dropped = length(ppts_non_native_lang_V) / length(unique(df.resp_V$subject))
percent_dropped #0

#fluent in English
SPEAKER = 2
SPEAKING = 23
UNDERSTANDING = 46

get_speaker <- Vectorize(function(responses) {
  responses <- split_responses_demog(responses)
  return (responses[SPEAKER])
})

get_fluency_speaking <- Vectorize(function(responses) {
  responses <- split_responses_demog(responses)
  return (responses[SPEAKING])
})

get_fluency_understanding <- Vectorize(function(responses) {
  responses <- split_responses_demog(responses)
  return (responses[UNDERSTANDING])
})

df.lang_en_V <- df.resp_V %>%
  select(subject, responses, variable_type) %>%
  filter(variable_type == "demog_language_en") %>%
  mutate(en_speaker = get_speaker(responses))

df.lang_en_fluency_V <- df.resp_V %>%
  select(subject, responses, variable_type) %>%
  filter(variable_type == "demog_conditional_language_en_fluency") %>%
  mutate(en_fluency_sp = as.numeric(get_fluency_speaking(responses))) %>%
  mutate(en_fluency_ud = as.numeric(get_fluency_understanding(responses)))

df.lang_en_V <- full_join(df.lang_en_V, 
                          df.lang_en_fluency_V, 
                          by = "subject") %>%
  select(subject, en_speaker, en_fluency_sp, en_fluency_ud) %>%
  filter(en_speaker == "Có",
         en_fluency_sp > 4, 
         en_fluency_ud > 4)

ppts_en_speaker_V = unique(df.lang_en_V$subject) #4
percent_dropped = length(ppts_en_speaker_V) / length(unique(df.resp_V$subject))
percent_dropped #0.6986301 # do not use this criterion

df.lang_zh_V <- df.resp_V %>%
  select(subject, responses, variable_type) %>%
  filter(variable_type == "demog_language_cn") %>%
  mutate(zh_speaker = get_speaker(responses))

df.lang_zh_fluency_V <- df.resp_V %>%
  select(subject, responses, variable_type) %>%
  filter(variable_type == "demog_conditional_language_cn_fluency") %>%
  mutate(zh_fluency_sp = as.numeric(get_fluency_speaking(responses))) %>%
  mutate(zh_fluency_ud = as.numeric(get_fluency_understanding(responses)))

df.lang_zh_V <- full_join(df.lang_zh_V, 
                          df.lang_zh_fluency_V, 
                          by = "subject") %>%
  select(subject, zh_speaker, zh_fluency_sp, zh_fluency_ud) %>%
  filter(zh_speaker == "Có",
         zh_fluency_sp > 4, 
         zh_fluency_ud > 4)

ppts_zh_speaker_V = unique(df.lang_zh_V$subject) #4
percent_dropped = length(ppts_zh_speaker_V) / length(unique(df.resp_V$subject))
percent_dropped #0.06557377

#have lived outside the sample country for more than 2 years
#have travelled extensively (more than 6 international experiences of 2 days or longer) 
YEARSABROAD = 2
OVERSEAEXP = 4

get_lived_abroad <- Vectorize(function(responses) {
  responses <- split_responses_demog(responses)
  return (responses[YEARSABROAD])
})

get_oversea_exp <- Vectorize(function(responses) {
  responses <- split_responses_demog(responses)
  return (responses[OVERSEAEXP])
})

df.abroad_V <- df.resp_V %>%
  select(subject, responses, variable_type) %>%
  filter(variable_type == "demog_oversea_experience") %>%
  mutate(lived_abroad = get_lived_abroad(responses)) %>%
  mutate(oversea_exp = get_oversea_exp(responses))

df.lived_abroad_V <- df.abroad_V %>%
  filter(lived_abroad == "Có")

ppts_lived_abroad_V = unique(df.lived_abroad_V$subject)
percent_dropped = length(ppts_lived_abroad_V) / length(unique(df.resp_V$subject))
percent_dropped #0.1369863

df.oversea_exp_V <- df.abroad_V %>%
  filter(oversea_exp == "6 lần trở lên")

ppts_oversea_exp_V = unique(df.oversea_exp_V$subject) #77
percent_dropped = length(ppts_oversea_exp_V) / length(unique(df.resp_V$subject))
percent_dropped #0.1506849

df.resp_V <- df.resp_V %>%
  filter(!(subject %in% ppts_non_native_lang_V),
         !(subject %in% ppts_oversea_exp_V), 
         !(subject %in% ppts_zh_speaker_V),
         !(subject %in% ppts_lived_abroad_V))

length(unique(df.resp_V$subject)) 
```

```{r}
write.csv(df.resp_V, "../../data/dataVN_excl.csv")
```

### 2022-09-28 code/2_combine/2_combine.Rmd
started new repo for manuscript

```{r setup, echo = FALSE, include = FALSE}
library("papaja")
library("knitr") # for knitting things
library("tidyverse") # for all things tidyverse
library("car")
library("lme4")
library("patchwork")
library("effsize")

# these options here change the formatting of how comments are rendered
opts_chunk$set(
  comment = "",
  results = "hold",
  fig.show = "hold")

# set the default ggplot theme 
theme_set(theme_classic())
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r loading data E, warning=FALSE, include=F}
df.resp_E <- read.csv("../../data/dataUS_excl.csv") %>%
  select(-X)
```

```{r loading data V, include=F}
df.resp_V <- read.csv("../../data/dataVN_excl.csv") %>%
  select(-X)
```

```{r loading data M, warning=FALSE, include=F}
df.resp_M <- read.csv("../../data/dataCN_excl.csv") %>%
  select(-X)
```

```{r corpus, include = F}
df.corpus_E <- read.csv("../../data/corpus/corpusE.csv") %>%
  rename(tax_frequency_E = tax.frequency,
         theme_frequency_E = theme.frequency,
         tax_cosine_E = Tax.cosine_dist, 
         theme_cosine_E = Theme.cosine_dist,
         tax_cosine_sim_E = Tax.cosine_sim,
         theme_cosine_sim_E = Theme.cosine_sim,
         tax_match_E = Tax.match,
         theme_match_E = Theme.match, 
         cue_E = Cue)

df.corpus_V <- read.csv("../../data/corpus/corpusV.csv") %>%
  rename(tax_frequency_V = tax.frequency,
         theme_frequency_V = theme.frequency,
         tax_cosine_V = Tax.cosine_dist, 
         theme_cosine_V = Theme.cosine_dist,
         tax_cosine_sim_V = Tax.cosine_sim,
         theme_cosine_sim_V = Theme.cosine_sim,
         tax_match_V = Tax.match,
         theme_match_V = Theme.match, 
         cue_V = Cue)

df.corpus_M <- read.csv("../../data/corpus/corpusM.csv") %>%
  rename(tax_frequency_M = tax.frequency,
         theme_frequency_M = theme.frequency,
         tax_cosine_M = Tax.cosine_dist, 
         theme_cosine_M = Theme.cosine_dist,
         tax_cosine_sim_M = Tax.cosine_sim,
         theme_cosine_sim_M = Theme.cosine_sim,
         tax_match_M = Tax.match,
         theme_match_M = Theme.match, 
         cue_M = Cue)
```

```{r full corpus, correct M freqs has been swapped in, include=F}
df.corpus <- left_join(df.corpus_E, df.corpus_V, by = "Cue_renamed")
df.corpus <- left_join(df.corpus, df.corpus_M, by = "Cue_renamed")

#replacing any 0 raw counts with epsilon
df.corpus <- df.corpus %>%
  mutate(tax_frequency_E = ifelse(tax_frequency_E == 0, 
                                  .Machine$double.eps, tax_frequency_E),
         theme_frequency_E = ifelse(theme_frequency_E == 0, 
                                  .Machine$double.eps, theme_frequency_E),
         tax_frequency_V = ifelse(tax_frequency_V == 0, 
                                  .Machine$double.eps, tax_frequency_V),
         theme_frequency_V = ifelse(theme_frequency_V == 0, 
                                  .Machine$double.eps, theme_frequency_V), 
         tax_frequency_M = ifelse(tax_frequency_M == 0, 
                                  .Machine$double.eps, tax_frequency_M),
         theme_frequency_M = ifelse(theme_frequency_M == 0, 
                                  .Machine$double.eps, theme_frequency_M)
         )

```

```{r corpus - frequency, include = F}
#find triads_omit, used whenever analysis uses raw collocates 
df.corpus_E_freq <- df.corpus_E %>%
  select(Cue_renamed, cue_E, tax_match_E, theme_match_E, tax_frequency_E, theme_frequency_E)
corpus_E_omit <- df.corpus_E_freq %>%
  filter(tax_frequency_E == 0 & theme_frequency_E == 0)

df.corpus_V_freq <- df.corpus_V %>%
  select(Cue_renamed, cue_V, tax_match_V, theme_match_V, tax_frequency_V, theme_frequency_V)
corpus_V_omit <- df.corpus_V_freq %>% 
  filter(tax_frequency_V == 0 & theme_frequency_V == 0)

df.corpus_M_freq <- df.corpus_M %>%
  select(Cue_renamed, cue_M, tax_match_M, theme_match_M, tax_frequency_M, theme_frequency_M)
corpus_M_omit <- df.corpus_M_freq %>% 
  filter(tax_frequency_M == 0 & theme_frequency_M == 0)

triads_omit <- append(corpus_E_omit$Cue_renamed, 
                      corpus_V_omit$Cue_renamed)
triads_omit <- append(triads_omit,
                      corpus_M_omit$Cue_renamed)

df.corpus_freq <- left_join(df.corpus_E_freq, 
                            df.corpus_V_freq, 
                            df.corpus_M_freq,
                            by = "Cue_renamed")
```

```{r corpus - cosine, include = F}
#mainly for sanity checking and so that there is a parallel df to df.corpus_freq
df.corpus_E_cos <- df.corpus_E %>%
  select(Cue_renamed, cue_E, tax_match_E, theme_match_E, 
         tax_cosine_E, theme_cosine_E,
         tax_cosine_sim_E, theme_cosine_sim_E)

df.corpus_V_cos <- df.corpus_V %>%
  select(Cue_renamed, cue_V, tax_match_V, theme_match_V, tax_cosine_V, theme_cosine_V,
         tax_cosine_sim_V, theme_cosine_sim_V)

df.corpus_M_cos <- df.corpus_M %>%
  select(Cue_renamed, cue_M, tax_match_M, theme_match_M, tax_cosine_M, theme_cosine_M, 
         tax_cosine_sim_M, theme_cosine_sim_M)

df.corpus_cos <- left_join(df.corpus_E_cos, df.corpus_V_cos, by = "Cue_renamed")
df.corpus_cos <- left_join(df.corpus_cos, df.corpus_M_cos, by = "Cue_renamed")
```

```{r getting triads from the 3 languages, include = F}
#combine response and corpus data
df.triad_E <- df.resp_E %>%
  filter(stim_type == "triad",
         responses != "NA")
triad_cues_E <- read.csv("../../data/corpus/cue_renamed_E.csv")
df.triad_E <- left_join(df.triad_E, triad_cues_E, by = c("cue", "top_opt", "bottom_opt"))
df.triad_E <- inner_join(df.triad_E, df.corpus, by = "Cue_renamed")

df.triad_E <- df.triad_E %>%
  mutate(responses_theme = ifelse(responses == theme_match_E, 1, 0),
         language = "English",
         country = "US") %>%
  select(subject, rt, Cue_renamed, cue, top_opt, bottom_opt, 
         responses, responses_theme, country, language,
         tax_match_E, theme_match_E, tax_match_V, theme_match_V, tax_match_M, theme_match_M,
         tax_frequency_E, theme_frequency_E, tax_frequency_V, theme_frequency_V, tax_frequency_M, theme_frequency_M,
         tax_cosine_E, theme_cosine_E, tax_cosine_V, theme_cosine_V, tax_cosine_M, theme_cosine_M,
         tax_cosine_sim_E, theme_cosine_sim_E, tax_cosine_sim_V, theme_cosine_sim_V, tax_cosine_sim_M, theme_cosine_sim_M)

df.triad_V <- df.resp_V %>%
  filter(stim_type == "triad",
         responses != "NA")
triad_cues_V <- read.csv("../../data/corpus/cue_renamed_V.csv")
df.triad_V <- left_join(df.triad_V, triad_cues_V, by = c("cue", "top_opt", "bottom_opt"))
df.triad_V <- inner_join(df.triad_V, df.corpus, by = "Cue_renamed")

df.triad_V <- df.triad_V %>%
  mutate(responses_theme = ifelse(responses == theme_match_V, 1, 0),
         language = "Vietnamese", 
         country = "Vietnam") %>%
  select(subject, rt, Cue_renamed, cue, top_opt, bottom_opt, 
         responses, responses_theme, country, language,
         tax_match_E, theme_match_E, tax_match_V, theme_match_V, tax_match_M, theme_match_M,
         tax_frequency_E, theme_frequency_E, tax_frequency_V, theme_frequency_V, tax_frequency_M, theme_frequency_M,
         tax_cosine_E, theme_cosine_E, tax_cosine_V, theme_cosine_V, tax_cosine_M, theme_cosine_M,
         tax_cosine_sim_E, theme_cosine_sim_E, tax_cosine_sim_V, theme_cosine_sim_V, tax_cosine_sim_M, theme_cosine_sim_M)

df.triad_M <- df.resp_M %>%
  filter(stim_type == "triad",
         responses != "NA")
triad_cues_M <- read.csv("../../data/corpus/cue_renamed_M.csv")
df.triad_M <- left_join(df.triad_M, triad_cues_M, by = c("cue", "top_opt", "bottom_opt"))
df.triad_M <- inner_join(df.triad_M, df.corpus, by = "Cue_renamed")

df.triad_M <- df.triad_M %>%
  mutate(responses_theme = ifelse(responses == theme_match_M, 1, 0),
         language = "Mandarin", 
         country = "China") %>%
  select(subject, rt, Cue_renamed, cue, top_opt, bottom_opt, 
         responses, responses_theme, country, language,
         tax_match_E, theme_match_E, tax_match_V, theme_match_V, tax_match_M, theme_match_M,
         tax_frequency_E, theme_frequency_E, tax_frequency_V, theme_frequency_V, tax_frequency_M, theme_frequency_M,
         tax_cosine_E, theme_cosine_E, tax_cosine_V, theme_cosine_V, tax_cosine_M, theme_cosine_M,
         tax_cosine_sim_E, theme_cosine_sim_E, tax_cosine_sim_V, theme_cosine_sim_V, tax_cosine_sim_M, theme_cosine_sim_M)

#calculate proportion for raw frequencies and cosine distance
df <- rbind(df.triad_E, df.triad_V)
df <- rbind(df, df.triad_M) %>%
  mutate(theme_freq_prop_E = theme_frequency_E / (theme_frequency_E + tax_frequency_E),
         theme_freq_prop_V = theme_frequency_V / (theme_frequency_V + tax_frequency_V), 
         theme_freq_prop_M = theme_frequency_M / (theme_frequency_M + tax_frequency_M), 
         theme_cosine_prop_E = theme_cosine_E / (theme_cosine_E + tax_cosine_E),
         theme_cosine_prop_V = theme_cosine_V / (theme_cosine_V + tax_cosine_V), 
         theme_cosine_prop_M = theme_cosine_M / (theme_cosine_M + tax_cosine_M)) %>%
  rename(triad = Cue_renamed)

df_main_analysis <- df #keep a copy of df in case exploratory analysis changes it
write.csv(df_main_analysis, "../../data/data_USCNVN_ENZHVI.csv")
```

### 2022-09-28 code/3_analysis/3_analysis.Rmd
started new repo for manuscript

---
title             : "Is It Language or Is It Culture? Re-examining Cross-Cultural Similarity Judgments Using Lexical Co-Occurrence"
shorttitle        : "Re-examining Cross-Cultural Similarity Judgments Using Lexical Co-Occurrence"

author: 
  - name          : "Khuyen Le"
    affiliation   : "1,2"
    corresponding : yes    # Define only one corresponding author
    email         : "khuyenle@stanford.edu"

affiliation:
  - id            : "1"
    institution   : "Symbolic Systems Program"
  - id            : "2"
    institution   : "Stanford University"

authornote: |
    An honors thesis submitted to the program of Symbolic Systems of Stanford University in partial fulfillment of the requirements for the degree in Symbolic Systems. 
    Honors Student: Khuyen Le. Honors Advisor: Mike Frank. Second Reader: Alex Carstensen

abstract: |
  Is “cow” more closely related to “grass” or “chicken”? Speakers of different languages judge similarity in this context differently, but why? One possibility is that cultures co-varying with these languages induce variation in conceptualizations of similarity. Specifically, East Asian cultures may promote reasoning about thematic similarity, by which cow and grass are more related whereas Western cultures may bias similarity judgments toward taxonomic relations, like cow-chicken. This difference in notions of similarity is the consensus interpretation for cross-cultural variation in this paradigm. We consider, and provide evidence for, an alternative possibility, by which notions of similarity are equivalent across contexts, but the statistics of the environment vary. On this account, similarity judgments are guided by co-occurrence in experience, and observing or hearing about cows and grass or cows and chickens more often could induce preferences for the relevant grouping and account for apparent differences in notions of similarity across contexts.

  <!-- https://tinyurl.com/ybremelq -->

keywords          : "similarity, culture, language, semantics, lexical co-occurrence, variation"
wordcount         : "150"

bibliography      : ["r-references.bib", "references/references.bib"]

floatsintext      : yes
figurelist        : no
tablelist         : yes
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no
header-includes:
  - \raggedbottom

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf

---

\newpage
To the Directors of the Program on Symbolic Systems:

I certify that I have read the thesis of Khuyen Le in its final form for submission and have found it to be satisfactory for the degree of Bachelor of Science with Honors.

Signed electronically

06/04/2021

Michael C. Frank

Department of Psychology

To the Directors of the Program on Symbolic Systems:

I certify that I have read the thesis of Khuyen Le in its final form for submission and have found it to be satisfactory for the degree of Bachelor of Science with Honors.

Signed electronically

06/04/2021

Alex Carstensen

Department of Psychology

\newpage

```{r setup, echo = FALSE, include = FALSE}
library("papaja")
library("knitr") # for knitting things
library("tidyverse") # for all things tidyverse
library("car")
library("lme4")
library("patchwork")
library("effsize")

# these options here change the formatting of how comments are rendered
opts_chunk$set(
  comment = "",
  results = "hold",
  fig.show = "hold")

# set the default ggplot theme 
theme_set(theme_classic())

r_refs("r-references.bib")
r_refs("references/packages.bib")

```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

# Introduction 
By virtue of discrete words and grammatical features, language provides a categorical partition of our continuous experiences. Previous research has observed variation in the cognition of speakers of different languages corresponding to variation within semantic domains in these languages. This language-aligned variation has been observed in the domains of color [@Winawer2007], number [@Frank2008], and gender [@Boroditsky2003], among many others [@Wolff2011]. Differences in cognition between speakers of different languages have often been used to suggest, explain, or exemplify cultural differences between speakers of those languages. Findings in studies of both language and of culture provide convergent evidence suggesting that variation across languages and cultures may shape broad variation in how people think about similarity between, for instance, different colors or objects.

Looking beyond this domain-specific variation, we can also consider broader notions of similarity and relatedness between concepts across domains. The Free Association Norms [@FreeAssoc], for example, measures human judgment in semantic relatedness across domains and contexts. With the availability of large linguistic corpora, we can examine the similarity of concepts that are not circumscribed in individual domains (as color, number, and gender are), allowing us to answer more general questions about variation in cognition between speakers of different languages. By measuring the similarity between arbitrary words (as commonly done with lexical co-occurrence models), it may be possible to model the shape of similarity space in order to capture cross-linguistic and cross-cultural variation and provide a more general answer to the question of how language influences our conception of the world.

Taxonomic and thematic similarity provide a convenient entry point to broader debates about cross-linguistic and cross-cultural variation in notions of similarity. Taxonomic categorization is based on the similarity of attributes, for example, similar perceptual properties, like shared color or shape, among objects. In contrast, thematic categorization is based on causal, spatial, and temporal relationships among objects [@Markman1984]. To illustrate this point, if a participant is given the words “chicken” and “grass”, and asked which of those words are more closely related to the word “cow”, the pairing “chicken” - “cow” indicates a taxonomic match, whereas “grass” - “cow” indicates a thematic match.

@Ji2004 found that preferences for taxonomic and thematic matches differ across culture, even when controlling for testing language and fluency. Specifically, Chinese participants made more thematic matches than taxonomic, while the converse was true for European Americans. This difference held even for Chinese participants tested in English (rather than Mandarin), suggesting that culture has an effect on the categorization strategy independent of the test language. However, the study also found an effect of language within Chinese participants from mainland China (when tested both in China and in the US): their preference for thematic categorization was significantly lower when tested in English compared to Mandarin Chinese. This suggests that test language also influences categorization strategies. Ji et al. characterize these results as demonstrating that culture (independent of language) leads to different styles of reasoning about similarity, whereas language serves as a “tuning” mechanism operating within a culturally-specific style, by activating representations corresponding to the language being used.

## Cross-cultural variation in similarity
The account that culture drives differences in categorization style has been one favored by other non-linguistic studies that use taxonomic vs thematic categorization to probe similarity judgment. A similar study to the aforementioned shows that when shown pictorial triads that represent words (i.e. pictures of an ant, a bee, and honey), Chinese children (9-10 years old) scored higher on thematic categorization compared to American children of the same age range, and vice versa for taxonomic categorization [@Chiu1972]. Additionally, the cross-cultural differences in similarity judgment seem to persist even when the stimuli are more perceptual and less conceptual. @Norenzayan2002 conducted a study where participants are shown a target stimulus beneath two groups of 4 similar objects. The target shares a common feature with all the objects in one group, and only shares another one feature with each member of that group. Meanwhile, the target shares many features with 3 out of 4 members of the other group, but does not share any 1 feature in common with the entire group. The study showed that American participants judged the target to be more similar with the former group more often, and vice versa for Chinese participants. Since differences in categorization style persist with novel stimuli (as opposed to previously seen words or pictures of concepts), this suggests that participants from different cultural backgrounds are utilizing different reasoning strategies when making similarity judgments.

Most commonly, researchers account for the differences in similarity judgment described above by differences in analytic vs holistic processing and in attention between Eastern and Western cultures. According to this framework, East Asians attend more to relationships between objects and context and reason more holistically, whereas Westerners attend more to objects and their properties, and reason analytically [@Nisbett2003]. The analytic-holistic cultural difference in reasoning style has been observed in other non-linguistic tasks. For example, in a rod-and-frame test [@Witkin1954], East Asian (Taiwanese Chinese) participants are more influenced by the position of the surrounding frame than European Americans [@Ji2000], suggesting a higher level of sensitivity to context. East Asians (Koreans) have also been demonstrated to make more situational attributions for behaviors than European Americans, who make more dispositional attributions [@Choi1999], again suggesting higher sensitivity to context. When shown a complex scene with foreground and background information, Japanese participants made more statements about contextual information and relationships between objects than Americans did [@Masuda2001]. Non-linguistic tasks have also shown that participants from Eastern and Western cultures differ in where they focus their visual attention. Another study presented American and Chinese participants with photographs of an object on a complex background [@Chua2005]. They found that Chinese participants made more eye saccades to the background compared to American participants, and that American participants looked at the object more quickly. These cross-cultural differences in attention and analytic vs holistic processing are seen to map onto the cross-cultural differences in similarity judgment: because East Asian participants attend more to the context between objects and reason more holistically, it stands to reason that they would consider words that appear in the same context (i.e. thematically similar) to be more similar than taxonomically-similar words.

Studies that explain these cross-cultural differences in reasoning and similarity judgment with a cultural framework often draw on social and historical contexts as the distal cause for these differences. For example, social structure and social practice can explain why different cultures develop different reasoning habits. To demonstrate this, researchers have looked at regions that are geographically close but with different social structures. @Kitayama2006 showed that Hokkaido Japanese demonstrated greater dispositional bias in attribution of behaviors compared to non-Hokkaido Japanese. The study suggested that this difference is correlated to the fact that Hokkaido was settled quite recently (mid-19th century) by pioneers from southern Japan, and thus its social practices (e.g. daily routines, child-rearing practices, and explicit education) would be influenced by the independent, goal-oriented characteristic of pioneer life. Another study showed that Northern Italians (more independent) categorized objects in a more taxonomic manner than Southern Italians (more interdependent) [@Knight2007]. These studies, however, stopped short of providing a mechanism for the nature of the relationship between differences in social structures and differences in reasoning and similarity judgments.

Another component of the social context explanation seems to be more tenable regarding the causal connection between cross-cultural differences in social practice and those in similarity judgments: that different patterns of attention are passed on by caregivers to children. @Fernald1993 found that American mothers labeled toys and pointed out their attributes more often than do Japanese mothers, while Japanese mothers tended to use the toys to engage their infants in social routines more often than American mothers. @Tardif1997 found that English-speaking caregivers produced more nouns than verbs in child-directed speech, while Mandarin-speaking caregivers emphasized verbs over nouns.  Emphasis on labeling objects and focus on nouns over verbs might lead infants to attend to objects and their taxonomic categorizations, while emphasis on social practices and producing more verbs might direct infants' attention to the relationship between objects. Such differences in early-childhood environments could tune children’s attention to either object or context, and result in cross-cultural differences in similarity judgments (preferring either taxonomic or thematic, respectively) in adulthood.

The above view explains cross-cultural differences in similarity judgment tasks as variation in the conceptualization of similarity itself. Alternatively, these judgments could be shaped by cross-cultural differences in the statistics of the environment, and accordingly the content of everyday experiences. Perhaps when confronted with the triad task, participants from all cultures follow the same process for reasoning about similarity, but rely on language or culture-specific inputs to this process. For example, it may be that Vietnamese participants are more likely to have knowledge of farming practices than Americans, and may associate cows and grass more strongly (as grass is the typical feed for cows in the small-scale family farming contexts common in Vietnam). Americans, on the other hand, may have strong associations between cows and chickens as a result of encountering them together in children’s books or petting zoo contexts. If we observe a difference in categorization between, say Vietnamese and US participants, perhaps they use the same procedure (considering similarity that is influenced by both taxonomic and thematic relations), but the inputs to this procedure differ between cultures, with Vietnamese participants exposed to more instances of “cow” and “grass” occurring together, compared to US participants.

A study by @Miyamoto2006 lends support to this theory. The study randomly sampled scenes from different-sized cities in Japan and the US. Both subjective (judgment by American and East Asian college students) and objective (number of objects as counted by an automated program) showed that Japanese scenes were more complex and contained a larger number of objects than American scenes. This suggests that people living in Japan would more frequently encounter perceptual environments that contain more relationships between objects compared to those who live in the US. Japanese scenes therefore might encourage focus on the overall context, while American scenes might encourage focus on a few salient objects.

Differences in environmental statistics extend beyond the immediate environment to cultural artifacts. @Tsai2007 showed that best-selling storybooks in the US contain more pictures of excited states (e.g. open-mouthed smiles, wide-open eyes) compared to best-selling storybooks in Taiwan, which contain more pictures of calm states. European American preschoolers also perceived excited states as happier and more desirable compared to calm states, and vice versa for Taiwanese Chinese preschoolers. The study also showed that there is a causal link between exposure to environmental statistics and personal preference: regardless of culture, exposure to exciting (vs. calm) storybooks increased children’s preference for the  corresponding activities. Broadly, this suggests that cultural artifacts or information in language (rather than direct, first-hand lived experiences) could be crucial factors in driving cross-cultural variation.

## Language as a proxy of variation in experience
While co-occurrences in experience are difficult to measure, co-occurrence in language can provide a rough proxy--and indeed, language may afford many of the “experiences” that people have with infrequently encountered items, like cows or helicopters. In the planned analyses, we will use co-occurrence in language as a proxy of cultural experience. This is a generalizing assumption, and while no linguistic corpus can be expected to fully capture a culture, and different linguistic corpora may capture different variables of a culture, using this proxy as a model of culture provides a conservative test of the hypothesis that differences in the input, rather than the process, of reasoning produces cultural variation in this task. This means that if such a model does work -- if linguistic co-occurrence can predict cultural variation in this similarity task without building differences in the decision process into the model -- it is relatively strong evidence that language alone (perhaps as a more easily observed source of information on broader cultural and ecological variation) may account for these cross-cultural differences in reasoning.[^footnote]

Indeed, previous work suggests that using lexical co-occurrence as a proxy can be useful in thinking about similarity judgments. Natural language processing tasks have found that lexical co-occurrence is a good predictor for performance in similarity judgment tasks. @Griffiths2007 showed that a model that takes word-document co-occurrence as input can be used to predict word association and the effects of semantic association on a variety of linguistic tasks. Additionally, lexical semantic models that are constructed using lexical co-occurrence (as opposed to annotated relations) have been shown to perform well on predicting human judgments about similarity between word pairs that are either thematically or taxonomically related [@Rohde2006].

Our current study will be using 2 measures of lexical co-occurrence: 1) raw lexical co-occurrences and 2) cosined distances of fastText word vectors. fastText is a system that uses lexical co-occurrence information to generate a vector representing each word in its lexicon [@Mikolov2018]. fastText uses a continuous bag-of-words model, which takes into account a symmetric window of words surrounding the word in question and maximizes the log-likelihood of the probability of the word given its context. Calculating the cosine-similarity between word vectors from fastText gives us a score of how similar the contexts of these words are. Therefore, words that occur in the same context (high lexical co-occurrence) would have a larger cosine-similarity score.

It must be noted that fastText supplements the lexical co-occurrence information by simultaneously training weight vectors for each position relative to the word in question, as well as adding sub-word information (bag-of-character n-gram vectors for each character forming the words). The similarity judgment prediction given by fastText may be more higher than a model using purely lexical co-occurrence information. However, models that use only lexical co-occurrence information (with or without a simple position weight system that gives more weight to words that are closer to the word in question) also perform well in similarity prediction tasks. For this study, due to the lack of large cleaned corpora for Mandarin and Vietnamese, we are leveraging fastText pre-trained models on the languages we are interested in @Grave2018.

Systems like fastText and word2vec have been demonstrated to be good predictors for similarity judgments. @Liu2019 showed that fastText performed well as the data for a system matching responses in a knowledge base by how similar they are to a customer’s query. A study by @Jatnika2019 tested a word2vec model trained on the English wikipedia corpus against 353 word pairs labeled with similarity values based on human judgment. The word2vec model correlates moderately with human judgment. fastText has also been shown to be sensitive towards cultural effects on word meanings: @Thompson2020 applied fastText to language-specific Wikipedia corpus (among others) to generate a “semantic neighborhood” of 1010 meanings in different languages. The study showed that languages that are spoken by more similar cultures, more geographically proximate and/or historically related had more semantic neighborhoods that aligned. This is a proof of concept for our use of fastText in different languages with varying levels of relatedness.

## The present study
@Ji2004 showed the difference in similarity judgment between Chinese and European Americans (the former prefers thematic categorization while the latter prefers taxonomic). However, their evidence is not sufficient to conclude that it is culture that drives this difference, as their cross-cultural data is correlational. Furthermore, they have yet to rule out all mechanisms by which language could be relevant to the task. For example, their language manipulation (bilingual speakers from Mainland China making more taxonomic categorizations when tested in language) only points to an offline effect of language because it does not prevent participants from accessing linguistic representations. A stronger claim could have been made if verbal interference had been conducted, and if cross-cultural differences had remained. This would have been stronger in eliminating online effect of language as a potential cause for cross-cultural differences in similarity judgment.

Additionally, outside of language, cross-cultural differences could come from a couple different mechanisms: @Ji2004 suggested that the notion of similarity is what varies across cultural groups, but it’s quite possible that similarity is regarded in the same way and it’s actually the input to this similarity judgment that varies across culture contexts. It might be possible to gain traction on possible mechanisms by examining whether variation in similarity judgments co-varies with environmental statistics that differ across the cultural and linguistic contexts.

In this study, we ask whether variation in lexical co-occurrence can account for the cross-context (culture and language) differences observed in how people evaluate similarity. Firstly, we attempt to replicate @Ji2004 by running a study comparing English speakers in the US and Mandarin speakers in mainland China. Secondly, we evaluate whether the differences observed between English and Mandarin speakers’ similarity judgments also extend to comparisons between English and Vietnamese, by running a similar study between English speakers in the US and Vietnamese speakers in Vietnam. Vietnam is a Southeast Asian country that borders China and is historically greatly influenced by Chinese culture [@Hui2002]. Therefore, it serves as a suitable cultural context to investigate whether the claim made by @Ji2004 and previous studies, that Eastern and Western cultures have different notions of similarity, extends beyond mainland China.

We then ask to what extent similarity judgments show cross-context differences that align with co-occurrence patterns in participants’ languages. We would only see a main effect of cultural context if the notion of differing notions of similarity is driving these cross-cultural differences. Meanwhile, if we do see variation in responding trial-to-trial that tracks with lexical co-occurrence statistics (as a rough proxy combining both linguistic and cultural context), this would give traction to the view that cross-cultural notions of similarity might be similar, and it is environmental statistics that guide the differences in similarity judgments. To preview our results, we find that, while we do not see overall group differences (between the East Asian contexts and the US) in similarity, we do find language-specific co-occurrence can indeed explain cross-context differences in similarity judgments. In contrast to previous accounts, by which culture induces differing conceptions of similarity (varying between taxonomic and thematic), these findings provide an alternative, and more specific, account by which language may explain these cross-cultural differences without invoking variation in notions of similarity.

# Methods 
```{r get exclusion results from 1_exclusions.Rmd}
source("../1_exclusions/1_exclusionsCN.Rmd")
source("../1_exclusions/1_exclusionsUS.Rmd")
source("../1_exclusions/1_exclusionsVN.Rmd")
```

```{r demog_E, TODO: move outside, include = F}
demog <- c("demog-dropdown", "demog-multi-choice", "demog-free-response", "demog-multi-select")
df.demog_E <- df.resp_E %>%
  filter(trial_type %in% demog) 
#write.csv(data_demog, "data_anon_demog_0201.csv")

AGE = 97 #index for age answer
GENDER = 115 #index for gender answer
split_responses <- function(responses) {
  responses <- as.character(responses)
  response_list <- unlist(strsplit(responses, ',|:'))
  response_list <- response_list[seq(1, length(response_list))]
  response_list <- gsub("}", "", response_list)
  response_list <- gsub("\"", "", response_list)
  return(response_list)
}

get_age <- Vectorize(function(responses) {
  responses <- split_responses(responses)
  if(responses[AGE-1] != "A0") {warnings("cannot find age answer")}
  else{return (responses[AGE])}
})

get_gender <- Vectorize(function(responses) {
  responses <- split_responses(responses)
  if(responses[GENDER-1] != "A1") {warnings("cannot find gender answer")}
  else{return (responses[GENDER])}
})

df.age_gender_E <- df.demog_E %>%
  filter(variable_type == "demog_age_gender_ethnic") %>%
  select(subject, responses) %>%
  mutate(age = as.numeric(get_age(responses))) %>%
  mutate(age = as.numeric(age)) %>%
  mutate(gender = get_gender(responses))

df.age_gender_E_summ <- df.age_gender_E %>%
  summarize(mean_age = mean(age), 
            median_age = median(age), 
            sd_age = sd(age))
```

```{r demog_V, TODO: move outside, include = F}
demog <- c("demog-dropdown", "demog-multi-choice", "demog-free-response", "demog-multi-select")
df.demog_V <- df.resp_V %>%
  filter(trial_type %in% demog)

AGE = 97 #index for age answer
GENDER = 115 #index for gender answer
split_responses <- function(responses) {
  responses <- as.character(responses)
  response_list <- unlist(strsplit(responses, ',|:'))
  response_list <- response_list[seq(1, length(response_list))]
  response_list <- gsub("}", "", response_list)
  response_list <- gsub("\"", "", response_list)
  return(response_list)
}

get_age <- Vectorize(function(responses) {
  responses <- split_responses(responses)
  if(responses[AGE-1] != "A0") {warnings("cannot find age answer")}
  else{return (responses[AGE])}
})

get_gender <- Vectorize(function(responses) {
  responses <- split_responses(responses)
  if(responses[GENDER-1] != "A1") {warnings("cannot find gender answer")}
  else{return (responses[GENDER])}
})

df.age_gender_V <- df.demog_V %>%
  filter(variable_type == "demog_age_gender_ethnic") %>%
  select(subject, responses) %>%
  mutate(age = as.numeric(get_age(responses))) %>%
  mutate(age = as.numeric(age)) %>%
  mutate(gender = get_gender(responses))

df.age_gender_V_summ <- df.age_gender_V %>%
  summarize(mean_age = mean(age), 
            median_age = median(age), 
            sd_age = sd(age))
```

```{r demog_M, TODO: MOVE outside, include = F}
demog <- c("demog-dropdown", "demog-multi-choice", "demog-free-response", "demog-multi-select")
df.demog_M <- df.resp_M %>%
  filter(trial_type %in% demog) 
#write.csv(data_demog, "data_anon_demog_0201.csv")

AGE = 97 #index for age answer
GENDER = 115 #index for gender answer
split_responses <- function(responses) {
  responses <- as.character(responses)
  response_list <- unlist(strsplit(responses, ',|:'))
  response_list <- response_list[seq(1, length(response_list))]
  response_list <- gsub("}", "", response_list)
  response_list <- gsub("\"", "", response_list)
  return(response_list)
}

get_age <- Vectorize(function(responses) {
  responses <- split_responses(responses)
  if(responses[AGE-1] != "A0") {warnings("cannot find age answer")}
  else{return (responses[AGE])}
})

get_gender <- Vectorize(function(responses) {
  responses <- split_responses(responses)
  if(responses[GENDER-1] != "A1") {warnings("cannot find gender answer")}
  else{return (responses[GENDER])}
})

df.age_gender_M <- df.demog_M %>%
  filter(variable_type == "demog_age_gender_ethnic") %>%
  select(subject, responses) %>%
  mutate(age = as.numeric(get_age(responses))) %>%
  mutate(age = as.numeric(age)) %>%
  mutate(gender = get_gender(responses))

df.age_gender_M_summ <- df.age_gender_M %>%
  summarize(mean_age = mean(age), 
            median_age = median(age), 
            sd_age = sd(age))
```
## Participants
We recruited `r length(unique(df.ppts_finished_E$subject))` participants from the US, `r length(unique(df.ppts_finished_V$subject))` participants from Vietnam, and `r length(unique(df.ppts_finished_M$subject))` participants from mainland China. US participants were recruited through snowball sampling seeded with Stanford email lists, Vietnam participants were recruited through snowball sampling seeded with Vietnam-based student groups on Facebook, and mainland China participants were recruited through snowball smapling seeded with group chats on WeChat. US participants were compensated with $5 gift certificates (USD), VN participants received 50,000₫ (VND) in phone credit, and mainland China participants received 25CNY through WeChat credit transfer.

We excluded `r length(unique(df.ppts_finished_E$subject)) - length(unique(df.ppts_att_E$subject))` US participants, `r length(unique(df.ppts_finished_V$subject)) - length(unique(df.ppts_att_V$subject))` Vietnam participants, and `r length(unique(df.ppts_finished_M$subject)) - length(unique(df.ppts_att_M$subject))` China participants who did not answer all attention checks correctly. We followed 4 exclusion criteria that aim to retain only participants who are influenced by one culture: (1) non-native speakers of English and Vietnamese, respectively, (2) fluent in at least one of the other two study languages (Vietnamese for US participants, English for Vietnamese participants and Chinese participants), (3) have lived outside of the test country (US, Vietnam, or China) for more than two years, and (4) have significant international experience (more than 6 international experiences of 2 days or longer.) We did not use a particular criterion for a language if it would exclude 25% or more of any one sample. In this round of exclusion, we excluded `r length(unique(df.ppts_att_E$subject)) - length(unique(df.resp_E$subject))` US, `r length(unique(df.ppts_att_V$subject)) - length(unique(df.resp_V$subject))` Vietnam participants, and `r length(unique(df.ppts_att_M$subject)) - length(unique(df.resp_M$subject))` China participants. After these exclusions, the US sample included `r length(unique(df.resp_E$subject))` participants (`r df.age_gender_E %>% filter(gender == "Male") %>% count()`M, `r df.age_gender_E %>% filter(gender == "Female") %>% count()`F, `r df.age_gender_E %>% filter(gender == "Non-binary") %>% count()` non-binary, `r df.age_gender_E %>% filter(gender == "Decline to answer") %>% count()` other), with mean age = `r round(df.age_gender_E_summ$mean_age, 2)` (SD = `r round(df.age_gender_E_summ$sd_age, 2)`) and median age = `r df.age_gender_E_summ$median_age`. The Vietnam sample included `r length(unique(df.resp_V$subject))` participants (`r df.age_gender_V %>% filter(gender == "Nam") %>% count()`M, `r df.age_gender_V %>% filter(gender == "Nữ") %>% count()`F), with mean age = `r round(df.age_gender_V_summ$mean_age, 2)` (SD = `r round(df.age_gender_V_summ$sd_age, 2)`) and median age = `r df.age_gender_V_summ$median_age`. The China sample included `r length(unique(df.resp_M$subject))` participants (`r df.age_gender_M %>% filter(gender == "男性") %>% count()`M, `r df.age_gender_M %>% filter(gender == "女性") %>% count()`F), with mean age = `r round(df.age_gender_M_summ$mean_age, 2)` (SD = `r round(df.age_gender_M_summ$sd_age, 2)`) and median age = `r df.age_gender_M_summ$median_age`.

Notably, we lost a majority of our Vietnam participants (more than 60%) in the attention check exclusion. One reason we suspect why this might have happened is because our Vietnam participants are less familiar with research surveys and attention check questions, and thus might have thought too much about the attention check questions. We carried out an exploratory analysis where we used a less stringent attention check exclusion (covered in the final part of the Results & Analysis section). To preview our findings for this analysis, we did not find any difference in significant results when compared with the main analysis.

## Stimuli
We adapted stimuli from previous studies to create a set of test triads consisting of a cue, with one thematic and one taxonomic match option. For example, “cow,” “grass,” and “chicken,” where “cow” is the cue, “grass” is the thematic match, and “chicken” the taxonomic match. We included 105 such triads, a superset including triads pulled from supplemental information and in-text examples across the literature, and others that we adapted or created (see SI for the full list of stimuli and sources). We selected triads on the basis of cultural familiarity in the US, Vietnam, and China. The triads were originally in English; they were translated to Vietnamese and Mandarin by a fluent bilingual speaker in each language. The translations were then checked for accuracy after backtranslation to English by another fluent bilingual in each language who was naive to the original English versions.

Each participant completed all 105 triads in sets of 21 trials at a time (10 test triads, 10 filler triads, and 1 attention check per page), by selecting the match most related to the cue (“Which thing is most closely related to the bolded item?” or "Thu nào liên quan nhat voi thu đuoc in đam?"). The test triads were presented with 105 filler triads mixed in, to obscure the taxonomic-thematic two-answer forced choice structure of the test stimuli and reduce the likelihood that participants would become aware of the design. The filler triads were groups of three semantically related words, but where the match options were not distinguished by thematic vs. taxonomic similarity, e.g., cue “bird” with match options “lizard” and “toad.” Additionally, we included 10 attention check trials, which were formatted like the test and filler triads but included an instruction instead of a cue item, e.g., “Choose wife” with match options “wife” and “husband.” In total, each participant completed 210 similarity judgments and 10 attention check questions, with triads presented in randomized orders that varied between subjects.

## Corpus model 
Our general approach is to build a model of similarity that is based on collocation counts in each language.

### Raw lexical co-occurrences
To give an intuition for our model, consider the cow-grass-chicken triad: we counted how many times “cow” and “grass” co-occur within a window of text in each corpus, and compare this to how many times “cow” and “chicken” co-occur. Our similarity prediction is then proportional to the relative frequency of these pairs. For example, if the thematic cow-grass match accounts for 30% of collocations for this triad (with cow-chicken making up the other 70%), then our model predicts, correspondingly, that 30% of responses to the triad will be grass, and the other 70% chicken. We then use a mixed-effects regression to evaluate how well each corpus collocate model predicts participants’ similarity judgments, across triads and languages.

#### Collocate retrieval and coding
For our English co-occurrence metric, we used the online interface of the Corpus of Contemporary American English [@COCA] to retrieve collocation counts. We recorded the raw count of times that any cue-match pair (e.g., cow-grass or cow-chicken) co-occur in a window of 19 words, which is the maximum window size in the online interface, and closest to the sentence co-occurrence metric in our VI corpus collocation counts.

To determine Vietnamese co-occurrence, we used the raw frequency of sentence co-occurrences from a subset of the Vietnamese corpus in the Leipzig Corpora Collection [@VICorpus]; this corpus includes 70 million Vietnamese sentences, but our corpus data comes from a 1 million sentence subset for which co-occurrence counts are available for download. Vietnamese makes very frequent use of compositional morphology but the written language  uses spacing to delineate syllable boundaries rather than word boundaries. Accordingly, collocate searches returned instances of both target terms and many morphologically related, but distinct, words. We included in our counts any instances of the target term or close semantic neighbors containing the same morpheme(s) as long as they entailed a likely literal reference to the target term. For example, our search for collocates of the term “gà” (chicken) also returned “gà mái,” a distinct word for female chickens. Despite being a different word, “gà mái” both includes the morpheme for “chicken” and entails reference to a chicken. Accordingly, instances of both “gà” and “gà mái” were included in our collocate count for “chicken.” Some compounds do not meet this criteria, and were excluded from collocate counts. For example “trái cây” (tree.fruits) includes the same syllable as the word “cây” (tree), but refers to fruit that comes from trees, not the trees themselves, and was therefore excluded from our collocate counts for “tree.”

We were unable to obtain a Mandarin corpus with similar number of sentences as the aforementioned English and Vietnamese corpora, hence we did not include any analysis based on raw lexical co-occurrences with Mandarin.

#### Collocate similarity model
From the raw co-occurrence counts of each triad, we calculated the thematic co-occurrence ratio as the number of thematic co-occurrences over the sum of thematic and taxonomic co-occurrences. We did this for both the English and Vietnamese corpus co-occurrence counts. In this way, we obtained predictions for 73 of 105 triads from the Vietnamese corpus and 104 of 105 triads from English. We therefore limited all analyses reported here to the subset of triads for which our corpus-based model can make meaningful predictions, meaning triads that have at least one non-zero collocate count (either thematic or taxonomic match). We replaced any remaining zero collocate counts with $\epsilon$ to account for sparsity in the corpus data. We then tested whether these simple relative frequency models predict US and VN responding.

### Cosine distance of word vectors
To give an intuition for our model, consider again the cow-grass-chicken triad: we retrieved word vectors for "cow" and "grass", and calculate the cosine distance between these vectors. Similarly, we retrieved vectors for "cow" and "chicken" and calculate the cosine distance between them. Our similarity prediction is then inversely proportional to the cosine distance of these pairs. This is because a larger cosine distance means the word vectors are further apart, and thus the words are less similar. For example, if the cosine distance of thematic cow-grass is 0.7 and the cosine distance of taxonomic cow-chicken is 0.3, then our model predicts, correspondingly, that 30% of responses to the triad will be grass, and the other 70% chicken. We then use a mixed-effects regression to evaluate how well each corpus model predicts participants’ similarity judgments, across triads and languages.

#### Collocate retrieval
We use the fastText pre-trained models of English, Mandarin, and Vietnamese in @Grave2018. These models are trained on Common Crawl and Wikipedia using We distribute pre-trained word vectors for 157 languages, trained on Common Crawl and Wikipedia using fastText. These models were trained using a Continuous Bag of Words (CBOW) with position-weights and a window of size 5. The models use character n-grams of length 5 and 10  negative examples.From the aforementioned models, we retrieve the word vectors (dimension 300) for each word we are interested in.

#### Collocate similarity model
From the word vectors, we calculated the cosine distance between each cue-thematic match (thematic cosine distance) and cue-taxonomic match (taxonomic cosine distance), using the spatial.distance.cosine function from the SciPy package [@2020SciPy]. We then calculated the thematic cosine distance proportion as thematic cosine distance over the sum of taxonomic cosine distance and thematic cosine distance. We did this for all three corpora. We were able to obtain predictions for all triads in all languages.

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.

# Results
```{r combine corpus and behavior data, include = F}
source("../2_combine/2_combine.Rmd")
```

## Do we extend previous work reporting a preference for taxonomic matching in the US and thematic matching in Asia?

```{r warning=FALSE, include=FALSE, paged.print=TRUE}
df.country <- df %>%
  group_by(subject, country) %>%
  summarize(theme_resp_percent = mean(responses_theme, na.rm = T))

df.country_sum <- df.country %>%
  group_by(country) %>%
  summarize(mean_theme_resp_percent = mean(theme_resp_percent), 
            sd_theme_resp_percent = sd(theme_resp_percent))

fit.country = glmer(responses_theme ~ country + (1 | subject) + (country | triad), 
                    data = df, 
                    family = "binomial")
summary(fit.country) 
fit.country.anova = Anova(fit.country, type=3)

fit.country_EN_VN = glmer(responses_theme ~ country + (1 | subject) + (country | triad), 
                    data = df %>% filter(country != "China"),
                    family = "binomial")
summary(fit.country_EN_VN) 
```
The group means of proportion of thematic response in mainland China is the highest (M = `r round((df.country_sum %>% filter(country == "China"))$mean_theme_resp_percent, 2)`, SD = `r round((df.country_sum %>% filter(country == "China"))$sd_theme_resp_percent, 2)`), followed by the groups means in Vietnam (M = `r round((df.country_sum %>% filter(country == "Vietnam"))$mean_theme_resp_percent, 2)`, SD = `r round((df.country_sum %>% filter(country == "Vietnam"))$sd_theme_resp_percent, 2)`), which is slightly higher than that of the US (M = `r round((df.country_sum %>% filter(country == "US"))$mean_theme_resp_percent, 2)`, SD = `r round((df.country_sum %>% filter(country == "US"))$sd_theme_resp_percent, 2)`).

```{r echo=FALSE, warning=FALSE, fig.cap="Proportion of thematic responses by country. Only US-China responding comparison shows a siginficant difference. We could not extend this to US-Vietnam responding comparison."}

#show violin plot
ggplot(df.country,
       mapping = aes(x = factor(country, levels=c("China", "US", "Vietnam")), 
                     y = theme_resp_percent, 
                     color = factor(country, levels=c("China", "US", "Vietnam")))) +
  geom_violin() +
  geom_jitter(height = 0, 
              alpha = 0.3) +  
  stat_summary(fun.data = "mean_cl_boot", 
               geom = "pointrange") + 
  labs(y = "Proportion Thematic Chosen", 
       x = "Country", 
       color = "Country") + 
  scale_color_manual(values=c("#D63230", "#1C77C3", "#F39237"))
```

```{r correlation of country response, echo=FALSE, warning=FALSE}
#US-China, US-Vietnam, China-Vietnam
df.triad_country <- df %>%
  group_by(triad, country) %>%
  summarize(emp_theme_prop = mean(responses_theme))

df.triad_country <- pivot_wider(data = df.triad_country, 
                                names_from = country, 
                                values_from = emp_theme_prop)
plotUSCN = ggplot(data = df.triad_country,
                  mapping = aes(x = US, 
                                y = China, 
                                label = triad)) +
   geom_text() + 
   geom_smooth(method = "lm") +
   labs(x = "Proportion Thematic Chosen (US)", 
        y = "Proportion Thematic Chosen (China)") + 
   xlim(0, 1) + 
   ylim(0, 1) + 
  theme(axis.title = element_text(size=rel(0.75)))

plotUSVN = ggplot(data = df.triad_country,
                  mapping = aes(x = US, 
                                y = Vietnam, 
                                label = triad)) +
   geom_text() + 
   geom_smooth(method = "lm") +
   labs(x = "Proportion Thematic Chosen (US)", 
        y = "Proportion Thematic Chosen (Vietnam)") + 
   xlim(0, 1) + 
   ylim(0, 1)  + 
  theme(axis.title = element_text(size=rel(0.75)))

plotCNVN = ggplot(data = df.triad_country,
                  mapping = aes(x = Vietnam,
                                y = China, 
                                label = triad)) +
   geom_text() + 
   geom_smooth(method = "lm") +
   labs(x = "Proportion Thematic Chosen (Vietnam)", 
        y = "Proportion Thematic Chosen (China)") + 
   xlim(0, 1) + 
   ylim(0, 1)  + 
  theme(axis.title = element_text(size=rel(0.75)))

corr.USCN = apa_print(cor.test(df.triad_country$US, 
                  df.triad_country$China, na.rm=T))

corr.USVN = apa_print(cor.test(df.triad_country$US, 
                  df.triad_country$Vietnam, na.rm=T))

corr.CNVN = apa_print(cor.test(df.triad_country$China, 
                  df.triad_country$Vietnam, na.rm=T))
```

```{r warning = F, fig.width = 8, fig.cap="Correlation between proportion thematic chosen by US-China participants, US-Vietnam participants, and China-Vietnam participants. All three comparisons show strong correlation, suggesting a strong signal of universality across cultural contexts regarding similarity judgments"}
plotUSCN + plotUSVN + plotCNVN +
  plot_layout(ncol = 3)
```

With a Pearson correlation test, we observed high correlations between thematic responding across all three countries. The proportion of US thematic responding is strongly correlated with thematic responding in China, `r corr.USCN$full_result`. The proportion of US thematic responding is strongly correlated with thematic responding in Vietnam, `r corr.USVN$full_result`. Likewise, the proportion of China thematic response is strongly correlated with thematic responding in Vietnam, `r corr.CNVN$full_result`. This points to a strong signal of universality across cultural contexts regarding similarity judgments.

```{r USCN effect size comparison, include=FALSE}
USCN_cohen <- cohen.d(df.triad_country$China, df.triad_country$US)
```

For comparison with previous work, we also included an effect size comparison for the difference in US-China thematic response data (though this was not a planned analysis). The effect size for this analysis was d = `r USCN_cohen$estimate`, a small effect size. This is smaller than the effect size from @Ji2004, even when we are unable to make a direct comparison. Calculating the effect size from the ANOVA reported in @Ji2004 between US participants tested in English and mainland China participants tested in English (both groups tested in the US) yields a Cohen's d = 0.81. @Ji2004 reported that mean thematic response for mainland China participants tested in Mandarin Chinese is higher than for those tested in English, so the effect size for a comparison between mainland China participants tested in Mandarin Chinese and US participants tested in English (parallel to our comparison) would likely have yielded an even larger effect size than 0.814. It is possible that we failed to replicate the magnitude of effect from @Ji2004 because the previous study calculated their dependent variable as frequency of thematic responses minus frequency of taxonomic responses, whereas our dependent variable is proportion of thematic response over total number of responses.

To test for cross-context differences in similarity judgments between the countries, we ran a mixed-effects logistic regression predicting triad responding (taxonomic or thematic) with country (US, China, or Vietnam) as a fixed effect. As random effects, we included an intercept per subject and one per triad, as well as by-triad random slopes for country to account for variation in the country effect across triads. In R syntax, the model is: response ~ country + (1 | subject) + (country | triad).

Overall, there is a significant effect of country on proportion of thematic responses ($\chi^2$(`r fit.country.anova["country", "Df"]`) = `r round(fit.country.anova["country", "Chisq"], 2)`, p < .001). However, this effect is driven by the difference between US and China responding ($\beta$ = `r round(fixef(fit.country)["countryUS"], 2)`, p < .001). There is no statistical difference between the Vietnam and China responding ($\beta$ = `r round(fixef(fit.country)["countryVietnam"], 2)`, p = `r round(as.data.frame(summary(fit.country)[["coefficients"]])["countryVietnam", "Pr(>|z|)"], 2)`), and the US and Vietnam responding ($\beta$ = `r round(fixef(fit.country_EN_VN)["countryVietnam"], 2)`, p = `r round(as.data.frame(summary(fit.country_EN_VN)[["coefficients"]])["countryVietnam", "Pr(>|z|)"], 3)`).

On this analysis, we do not find support that the US-China tendencies toward taxonomic and thematic responding (respectively) extend to the US-Vietnam comparison. Accordingly, we cannot speak to overall biases toward thematic responding across Asian cultural contexts broadly, but we do replicate the differences documented by @Ji2004 between the US and China. However, in our corpus model comparison, we do find evidence for different, more fine-grained variation in similarity judgments between the US and Vietnam.

## Can the differences in similarity judgments between English, Mandarin and Vietnamese speakers be explained by variation in lexical statistics?
### Is responding in each cultural context predicted by the corresponding lexical statistics (raw co-occurrences and cosine distance)? 
```{r Pearson correlation between raw co-occurrences of corpora and responding, warning=FALSE, include=FALSE}

#raw co-occurrences
df.triad_country_freq <- df %>%
  filter(!(triad %in% triads_omit)) %>% # omit triads that do not have meaningful prediction (at least 1 non-zero prediction in both languages)
  group_by(triad, country, theme_freq_prop_E, theme_freq_prop_V, theme_freq_prop_M) %>%  # not working 
  summarize(emp_theme_prop = mean(responses_theme))
df.triad_country_freq   #sanity

df.triad_country_freq_E <- df.triad_country_freq %>%
  filter(country == "US")

#plotting English corpus against US responding data
plotE = ggplot(data = df.triad_country_freq_E,
        mapping = aes(x = emp_theme_prop,
                     y = theme_freq_prop_E,
                     label = triad)) +
   geom_text() +
   geom_smooth(method = "lm") +
   labs(x = "Proportion Thematic Chosen (US)",
        y = "Proportion Thematic Predicted (English)")
plotE

df.triad_country_freq_V <- df.triad_country_freq %>%
  filter(country == "Vietnam")

#plotting Vietnamese corpus against VN responding data
plotV = ggplot(data = df.triad_country_freq_V,
        mapping = aes(x = emp_theme_prop,
                     y = theme_freq_prop_V,
                     label = triad)) +
   geom_text() +
   geom_smooth(method = "lm") +
   labs(x = "Proportion Thematic Chosen (Vietnam)",
        y = "Proportion Thematic Predicted (Vietnamese)")
plotV

df.triad_country_freq_M <- df.triad_country_freq %>%
  filter(country == "China")

#plotting China corpus against CN responding data
plotM = ggplot(data = df.triad_country_freq_M,
        mapping = aes(x = emp_theme_prop,
                     y = theme_freq_prop_M,
                     label = triad)) +
   geom_text() +
   geom_smooth(method = "lm") +
   labs(x = "Proportion Thematic Chosen (China)",
        y = "Proportion Thematic Predicted (Chinese)")
plotM

#Pearson correlation between corpus and responding
corr.E = apa_print(cor.test(df.triad_country_freq_E$emp_theme_prop,
                  df.triad_country_freq_E$theme_freq_prop_E, na.rm=T))
corr.E

corr.V = apa_print(cor.test(df.triad_country_freq_V$emp_theme_prop,
                  df.triad_country_freq_V$theme_freq_prop_V, na.rm=T))
corr.V

corr.M = apa_print(cor.test(df.triad_country_freq_M$emp_theme_prop,
                  df.triad_country_freq_M$theme_freq_prop_M, na.rm=T))
corr.M

#Pearson correlation between EN and VI corpus
corr.EV = apa_print(cor.test(df.triad_country_freq_V$theme_freq_prop_V,
                   df.triad_country_freq_E$theme_freq_prop_E, na.rm=T))
corr.EM = apa_print(cor.test(df.triad_country_freq_M$theme_freq_prop_M,
                   df.triad_country_freq_E$theme_freq_prop_E, na.rm=T))
corr.MV = apa_print(cor.test(df.triad_country_freq_V$theme_freq_prop_V,
                   df.triad_country_freq_M$theme_freq_prop_M, na.rm=T))
```

```{r echo=FALSE, paged.print=FALSE, fig.cap ="Correlation between English corpus lexical co-occurrence and US responding, and Vietnamese corpus lexical co-occurrence and Vietnam responding."}
plotE + plotV + plotM
  plot_layout(ncol = 3)
```

We first conducted a Pearson correlation test between corresponding response data and corpus data. Looking at the raw lexical co-occurrence data, proportion of US thematic responding is moderately correlated to English corpus thematic proportion, `r corr.E$full_result`. Proportion of Vietnam thematic responding is moderately correlated to Vietnamese corpus thematic proportion, `r corr.V$full_result`. Proportion of China thematic responding is moderately correlated to Chinese corpus thematic proportion, `r corr.M$full_result`. 
There was a strong similarity signal between the thematic proportions in the English and Vietnamese corpora, `r corr.EV$full_result`, and the thematic proportions in the English and Mandarin corpora, `r corr.EM$full_result`. There was a moderate similarity signal between the proportions in the Mandarin and Vietnamese corpora, `r corr.MV$full_result.`

```{r Pearson correlation between corpus cosine distance and responding, warning=FALSE, include=FALSE}
df.triad_country_cos <- df %>%
  group_by(triad, country, theme_cosine_prop_E, theme_cosine_prop_V, theme_cosine_prop_M) %>%
  summarize(emp_theme_prop = mean(responses_theme))

df.triad_country_cos_E <- df.triad_country_cos %>%
  filter(country == "US")

plotE = ggplot(data = df.triad_country_cos_E, 
        mapping = aes(x = emp_theme_prop, 
                     y = theme_cosine_prop_E,
                     label = triad)) +
   geom_text() + 
   geom_smooth(method = "lm") +
   labs(x = "Proportion Thematic Chosen (US)", 
        y = "Proportion Thematic Predicted (English)") + 
   scale_y_reverse() + 
   xlim(0, 1) +
   ylim(0.8, 0.2) + 
  theme(axis.title = element_text(size=rel(0.75)))

df.triad_country_cos_V <- df.triad_country_cos %>%
  filter(country == "Vietnam")

plotV = ggplot(data = df.triad_country_cos_V, 
        mapping = aes(x = emp_theme_prop, 
                     y = theme_cosine_prop_V, 
                     label = triad)) +
   geom_text() + 
   geom_smooth(method = "lm") +
   labs(x = "Proportion Thematic Chosen (Vietnam)", 
        y = "Proportion Thematic Predicted (Vietnamese)") + 
   scale_y_reverse() +
   xlim(0, 1) +
   ylim(0.8, 0.2) + 
  theme(axis.title = element_text(size=rel(0.75)))

df.triad_country_cos_M <- df.triad_country_cos %>%
  filter(country == "China")

plotM = ggplot(data = df.triad_country_cos_M, 
        mapping = aes(x = emp_theme_prop, 
                     y = theme_cosine_prop_M, 
                     label = triad)) +
   geom_text() + 
   geom_smooth(method = "lm") +
   labs(x = "Proportion Thematic Chosen (China)", 
        y = "Proportion Thematic Predicted (Mandarin)") + 
   xlim(0, 1) +
   ylim(0.8, 0.2) + 
  theme(axis.title = element_text(size=rel(0.75)))

corr.E_cos = apa_print(cor.test(df.triad_country_cos_E$emp_theme_prop,
                      df.triad_country_cos_E$theme_cosine_prop_E, na.rm=T))

corr.V_cos = apa_print(cor.test(df.triad_country_cos_V$emp_theme_prop,
                      df.triad_country_cos_V$theme_cosine_prop_V, na.rm=T))

corr.M_cos = apa_print(cor.test(df.triad_country_cos_M$emp_theme_prop,
                      df.triad_country_cos_M$theme_cosine_prop_M, na.rm=T))

#correlation between corpora
corr.EV_cos = apa_print(cor.test(df.triad_country_cos_E$theme_cosine_prop_E,
                       df.triad_country_cos_V$theme_cosine_prop_V, na.rm=T))

corr.EM_cos = apa_print(cor.test(df.triad_country_cos_E$theme_cosine_prop_E,
                      df.triad_country_cos_M$theme_cosine_prop_M, na.rm=T))

corr.VM_cos = apa_print(cor.test(df.triad_country_cos_V$theme_cosine_prop_V,
                      df.triad_country_cos_M$theme_cosine_prop_M, na.rm=T))
```

```{r warning = FALSE, echo=FALSE, fig.width = 8, fig.cap="Correlation between English corpus cosine distance and US responding; Vietnamese corpus cosine distance and Vietnam responding; and Mandarin corpus cosine distance and China responding."}
#maybe we should include a note that explains why they are correlate in the opposite direction? 
#either changing the label of y-axis, or use y = 1/theme_cosine_prop_V? 
plotE + plotV + plotM +
  plot_layout(ncol = 3)
```

```{r US-Mandarin, China-English cross correlation, NOT SHOWN, eval=FALSE, warning=FALSE, include=FALSE}
plotUSZH = ggplot(data = df.triad_country_cos_E, 
        mapping = aes(x = emp_theme_prop, 
                     y = theme_cosine_prop_M,
                     label = triad)) +
   geom_text() + 
   geom_smooth(method = "lm") +
   labs(x = "Proportion Thematic Chosen (US)", 
        y = "Proportion Thematic Predicted (Mandarin)") + 
   scale_y_reverse() + 
   xlim(0, 1) +
   ylim(0.8, 0.3)

plotCNEN = ggplot(data = df.triad_country_cos_M, 
        mapping = aes(x = emp_theme_prop, 
                     y = theme_cosine_prop_E,
                     label = triad)) +
   geom_text() + 
   geom_smooth(method = "lm") +
   labs(x = "Proportion Thematic Chosen (China)", 
        y = "Proportion Thematic Predicted (English)") + 
   scale_y_reverse() + 
   xlim(0, 1) +
   ylim(0.8, 0.3)

plotUSZH + plotCNEN +
  plot_layout(ncol = 2)
```

Looking at the cosine distance data using fastText word vectors, proportion of US thematic responding is moderately correlated to English thematic cosine distance proportion, `r corr.E_cos$full_result`. There is a small correlation between proportion of Vietnam thematic responding and the Vietnamese thematic cosine distance proportion, `r corr.V_cos$full_result`. Proportion of China thematic responding is moderately correlated to Mandarin thematic match cosine distance proportion, `r corr.M_cos$full_result`. There were moderate signals of similarity between English and Mandarin (`r corr.EM_cos$full_result`). There was no significant correlation between English and Vietnamese (`r corr.EV_cos$full_result`), and between Vietnamese and Mandarin (`r corr.VM_cos$full_result`).

To test whether variation in lexical co-occurrence can explain differences in similarity judgments between US and Vietnam participants, we compare logistic mixed-effects regression models fit to the thematic responding data from each country separately. We first ask how well each corpus model (English, Vietnamese, or Mandarin) predicts similarity judgments by speakers of the corresponding language (US, Vietnam, or China). To do this, we use a mixed-effects logistic regression to predict triad responses (0=taxonomic or 1=thematic) with corpus prediction (proportion thematic co-occurrence or cosine distance) as a fixed effect and participant and triad as random effects.

#### Raw lexical co-occurrences

```{r US responding predicted by each corpus model raw co-occurrences, warning=FALSE, include=F}
# English 
fit.EN_US = glmer(responses_theme ~ theme_freq_prop_E + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "US", !(triad %in% triads_omit)), 
          family="binomial")
summary(fit.EN_US)
fit.EN_US.anova = Anova(fit.EN_US, type = 3)

#Vietnamese
fit.VI_US = glmer(responses_theme ~ theme_freq_prop_V + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "US", !(triad %in% triads_omit)), 
          family="binomial")
summary(fit.VI_US)
fit.VI_US.anova = Anova(fit.VI_US, type = 3)

#Mandarin
fit.ZH_US = glmer(responses_theme ~ theme_freq_prop_M + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "US", !(triad %in% triads_omit)), 
          family="binomial")
summary(fit.ZH_US)
fit.ZH_US.anova = Anova(fit.ZH_US, type = 3)
```

```{r VN responding predicted by each corpus model raw co-occurrences, warning=FALSE, include=F}
# English 
fit.EN_VN = glmer(responses_theme ~ theme_freq_prop_E + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "Vietnam", !(triad %in% triads_omit)), 
          family="binomial")
summary(fit.EN_VN)
fit.EN_VN.anova = Anova(fit.EN_VN, type = 3)

#Vietnamese
fit.VI_VN = glmer(responses_theme ~ theme_freq_prop_V + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "Vietnam", !(triad %in% triads_omit)), 
          family="binomial")
summary(fit.VI_VN)
fit.VI_VN.anova = Anova(fit.VI_VN, type = 3)

#Mandarin
fit.ZH_VN = glmer(responses_theme ~ theme_freq_prop_M + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "Vietnam", !(triad %in% triads_omit)), 
          family="binomial")
summary(fit.ZH_VN)
fit.ZH_VN.anova = Anova(fit.ZH_VN, type = 3)
```

```{r CN responding predicted by each corpus model raw co-occurrences, warning=FALSE, include=F}
#English
fit.EN_CN = glmer(responses_theme ~ theme_freq_prop_E + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "China", !(triad %in% triads_omit)), 
          family="binomial")
summary(fit.EN_CN)
fit.EN_CN.anova = Anova(fit.EN_CN, type = 3)

#Vietnamese
fit.VI_CN = glmer(responses_theme ~ theme_freq_prop_V + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "China", !(triad %in% triads_omit)), 
          family="binomial")
summary(fit.VI_CN)
fit.VI_CN.anova = Anova(fit.VI_CN, type = 3)

#Mandarin
fit.ZH_CN = glmer(responses_theme ~ theme_freq_prop_M + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "China", !(triad %in% triads_omit)), 
          family="binomial")
summary(fit.ZH_CN)
fit.ZH_CN.anova = Anova(fit.ZH_CN, type = 3)
```

TODO: ADD CHINA RESULTS
Both the English (EN) and Vietnamese (VI) corpus are significant predictors of US responding (EN-US model: $\beta$ = `r round(fixef(fit.EN_US)["theme_freq_prop_E"], 2)`, $\chi^2$(`r fit.EN_US.anova["theme_freq_prop_E", "Df"]`) = `r round(fit.EN_US.anova["theme_freq_prop_E", "Chisq"], 2)`, p < .001; VI-US model: $\beta$ = `r round(fixef(fit.VI_US)["theme_freq_prop_V"], 2)`, $\chi^2$(`r fit.VI_US.anova["theme_freq_prop_V", "Df"]`) = `r round(fit.VI_US.anova["theme_freq_prop_V", "Chisq"], 2)`, p < .001).

Similarly, both the English (EN) and Vietnamese (VI) corpus are significant predictors of Vietnam (VN) responding (EN-VN model: $\beta$ = `r round(fixef(fit.EN_VN)["theme_freq_prop_E"], 2)`, $\chi^2$(`r fit.EN_VN.anova["theme_freq_prop_E", "Df"]`) = `r round(fit.EN_VN.anova["theme_freq_prop_E", "Chisq"], 2)`, p < .001; VI-VN model: $\beta$ = `r round(fixef(fit.VI_VN)["theme_freq_prop_V"], 2)`, $\chi^2$(`r fit.VI_VN.anova["theme_freq_prop_V", "Df"]`) = `r round(fit.VI_VN.anova["theme_freq_prop_V", "Chisq"], 2)`, p < .001).

This suggests a strong shared similarity signal across the languages, which is also reflected in the strong correlation between the two corpus models reported above (`r corr.EV$full_result`).

#### Cosine distances of fastText word vectors
```{r US responding predicted by each corpus model cosine differences, warning=FALSE, include=F}
#English
fit.EN_US_cos = glmer(responses_theme ~ theme_cosine_prop_E + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "US"), 
          family="binomial")
summary(fit.EN_US_cos)
fit.EN_US_cos.anova = Anova(fit.EN_US_cos, type = 3)
fit.EN_US_cos.anova

#Vietnamese
fit.VI_US_cos = glmer(responses_theme ~ theme_cosine_prop_V + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "US"), 
          family="binomial")
summary(fit.VI_US_cos)
fit.VI_US_cos.anova = Anova(fit.VI_US_cos, type = 3)
fit.VI_US_cos.anova

#Mandarin
fit.ZH_US_cos = glmer(responses_theme ~ theme_cosine_prop_M + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "US"), 
          family="binomial")
summary(fit.ZH_US_cos)
fit.ZH_US_cos.anova = Anova(fit.ZH_US_cos, type = 3)
fit.ZH_US_cos.anova
```

```{r VN responding predicted by each corpus model cosine differences, warning=FALSE, include=F}
#English
fit.EN_VN_cos = glmer(responses_theme ~ theme_cosine_prop_E + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "Vietnam"), 
          family="binomial")
summary(fit.EN_VN_cos)
fit.EN_VN_cos.anova = Anova(fit.EN_VN_cos, type = 3)
fit.EN_VN_cos.anova

#Vietnamese
fit.VI_VN_cos = glmer(responses_theme ~ theme_cosine_prop_V + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "Vietnam"), 
          family="binomial")
summary(fit.VI_VN_cos)
fit.VI_VN_cos.anova = Anova(fit.VI_VN_cos, type = 3)
fit.VI_VN_cos.anova

#Mandarin
fit.ZH_VN_cos = glmer(responses_theme ~ theme_cosine_prop_M + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "Vietnam"), 
          family="binomial")
summary(fit.ZH_VN_cos)
fit.ZH_VN_cos.anova = Anova(fit.ZH_VN_cos, type = 3)
fit.ZH_VN_cos.anova
```

```{r CN responding predicted by each corpus model cosine differences, warning=FALSE, include=F}
## English
fit.EN_CN_cos = glmer(responses_theme ~ theme_cosine_prop_E + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "China"), 
          family="binomial")
summary(fit.EN_CN_cos)
fit.EN_CN_cos.anova = Anova(fit.EN_CN_cos, type = 3)
fit.EN_CN_cos.anova

#Vietnamese
fit.VI_CN_cos = glmer(responses_theme ~ theme_cosine_prop_V + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "China"), 
          family="binomial")
summary(fit.VI_CN_cos)
fit.VI_CN_cos.anova = Anova(fit.VI_CN_cos, type = 3)
fit.VI_CN_cos.anova

#Mandarin
fit.ZH_CN_cos = glmer(responses_theme ~ theme_cosine_prop_M + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "China"), 
          family="binomial")
summary(fit.ZH_CN_cos)
fit.ZH_CN_cos.anova = Anova(fit.ZH_CN_cos, type = 3)
fit.ZH_CN_cos.anova
```

Similar to the results from the analysis with raw lexical co-occurrences, we found that all corpora are significant predictors of all cultural context responding.

For US responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are significant predictors of US responding (EN-US model: $\beta$ = `r round(fixef(fit.EN_US_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.EN_US_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.EN_US_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p < .001; VI-US model: $\beta$ = `r round(fixef(fit.VI_US_cos)["theme_cosine_prop_V"], 2)`, $\chi^2$(`r fit.VI_US_cos.anova["theme_cosine_prop_V", "Df"]`) = `r round(fit.VI_US_cos.anova["theme_cosine_prop_V", "Chisq"], 2)`, p = `r round(fit.VI_US_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"], 3)`; ZH-US model: $\beta$ = `r round(fixef(fit.ZH_US_cos)["theme_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ZH_US_cos.anova["theme_cosine_prop_M", "Df"]`) = `r round(fit.ZH_US_cos.anova["theme_cosine_prop_M", "Chisq"], 2)`, p < .001).

For Vietnam (VN) responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are significant predictors of VN responding (EN-VN model: $\beta$ = `r round(fixef(fit.EN_VN_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.EN_VN_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.EN_VN_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p < .001; VI-VN model: $\beta$ = `r round(fixef(fit.VI_VN_cos)["theme_cosine_prop_V"], 2)`, $\chi^2$(`r fit.VI_VN_cos.anova["theme_cosine_prop_V", "Df"]`) = `r round(fit.VI_VN_cos.anova["theme_cosine_prop_V", "Chisq"], 2)`, p = `r round(fit.VI_VN_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"], 3)`; ZH-VN model: $\beta$ = `r round(fixef(fit.ZH_VN_cos)["theme_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ZH_VN_cos.anova["theme_cosine_prop_M", "Df"]`) = `r round(fit.ZH_VN_cos.anova["theme_cosine_prop_M", "Chisq"], 2)`, p < .001).

For China (CN) responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are significant predictors of CN responding (EN-CN model: $\beta$ = `r round(fixef(fit.EN_CN_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.EN_CN_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.EN_CN_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p < .001; VI-CN model: $\beta$ = `r round(fixef(fit.VI_CN_cos)["theme_cosine_prop_V"], 2)`, $\chi^2$(`r fit.VI_CN_cos.anova["theme_cosine_prop_V", "Df"]`) = `r round(fit.VI_CN_cos.anova["theme_cosine_prop_V", "Chisq"], 2)`, p = `r round(fit.VI_VN_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"], 3)`; ZH-CN model: $\beta$ = `r round(fixef(fit.ZH_CN_cos)["theme_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ZH_CN_cos.anova["theme_cosine_prop_M", "Df"]`) = `r round(fit.ZH_CN_cos.anova["theme_cosine_prop_M", "Chisq"], 2)`, p < .001).

### Is responding in each cultural context __best__ predicted by the corresponding corpus's lexical statistics (raw co-occurrences and cosine distance), as opposed to the other two corpora?
Next, we directly compare the corpus models by including both as fixed effects in two mixed-effect regressions (predicting US and Vietnam responding) with the same random effects as above. In R syntax, the model is: response ~ corpus_English + corpus_Vietnamese + corpus_Mandarin + (1|triad) + (1|subject).

#### Raw co-occurrences 
```{r MIGHT NEED TO REMOVEEnglish + Vietnamese raw co-occurrences predicting US and Vietnam, warning=FALSE, include=F}
## English/Vietnamese comparison
fit.ENVI_US = glmer(responses_theme ~ theme_freq_prop_E + theme_freq_prop_V + 
                      (1 | subject) + (1 | triad), 
                    data = df %>% filter(country == "US"), 
                    family="binomial")
summary(fit.ENVI_US)
fit.ENVI_US.anova = Anova(fit.ENVI_US, type = 3)
fit.ENVI_US.anova

fit.ENVI_VN = glmer(responses_theme ~ theme_freq_prop_V + theme_freq_prop_E + 
                      (1 | subject) + (1 | triad), 
                    data = df %>% filter(country == "Vietnam"), 
                    family="binomial")
summary(fit.ENVI_VN)
fit.ENVI_VN.anova = Anova(fit.ENVI_VN, type = 3)
fit.ENVI_VN.anova
```
When we included both corpora as predictors for US responding, only the English corpus has a significant effect ($\beta$ = `r round(fixef(fit.ENVI_US)["theme_freq_prop_E"], 2)`, $\chi^2$(`r fit.ENVI_US.anova["theme_freq_prop_E", "Df"]`) = `r round(fit.ENVI_US.anova["theme_freq_prop_E", "Chisq"], 2)`, p < .001). There is no effect of the Vietnamese corpus ($\beta$ = `r round(fixef(fit.ENVI_US)["theme_freq_prop_V"], 2)`, $\chi^2$(`r fit.ENVI_US.anova["theme_freq_prop_V", "Df"]`) = `r round(fit.ENVI_US.anova["theme_freq_prop_V", "Chisq"], 2)`, p = `r round(fit.ENVI_US.anova["theme_freq_prop_V", "Pr(>Chisq)"], 3)`).

However, when both corpora are included as predictors for Vietnam responding -- both corpora has a significant effect (English corpus: $\beta$ = `r round(fixef(fit.ENVI_VN)["theme_freq_prop_E"], 2)`, $\chi^2$(`r fit.ENVI_VN.anova["theme_freq_prop_E", "Df"]`) = `r round(fit.ENVI_VN.anova["theme_freq_prop_E", "Chisq"], 2)`, p = `r round(fit.ENVI_VN.anova["theme_freq_prop_E", "Pr(>Chisq)"], 3)`; Vietnamese corpus: $\beta$ = `r round(fixef(fit.ENVI_VN)["theme_freq_prop_V"], 2)`, $\chi^2$(`r fit.ENVI_VN.anova["theme_freq_prop_V", "Df"]`) = `r round(fit.ENVI_VN.anova["theme_freq_prop_V", "Chisq"], 2)`, p = `r round(fit.ENVI_VN.anova["theme_freq_prop_V", "Pr(>Chisq)"], 3)`).

```{r Eng-Vie-Mand lexical co-occ predicting US, VN, CN, warning=FALSE, include=F}
# ADDITION: adding theme_freq_prop_M
#raw co-occurrences
#linear mixed model with ALL corpora as predictors for each population.
fit.ENVIZH_US = glmer(responses_theme ~ 
                      theme_freq_prop_E + theme_freq_prop_V + theme_freq_prop_M +
                      (1 | subject) + (1 | triad), 
                    data = df %>% filter(country == "US", !(triad %in% triads_omit)),
                    family="binomial")
summary(fit.ENVIZH_US)
fit.ENVIZH_US.anova = Anova(fit.ENVIZH_US, type = 3)
fit.ENVIZH_US.anova

fit.ENVIZH_VN = glmer(responses_theme ~ 
                      theme_freq_prop_V + theme_freq_prop_E + theme_freq_prop_M +
                      (1 | subject) + (1 | triad), 
                    data = df %>% filter(country == "Vietnam", !(triad %in% triads_omit)),
                    family="binomial")
summary(fit.ENVIZH_VN)
fit.ENVIZH_VN.anova = Anova(fit.ENVIZH_VN, type = 3)
fit.ENVIZH_VN.anova

fit.ENVIZH_CN = glmer(responses_theme ~ 
                      theme_freq_prop_V + theme_freq_prop_E + theme_freq_prop_M +
                      (1 | subject) + (1 | triad), 
                    data = df %>% filter(country == "China", !(triad %in% triads_omit)),
                    family="binomial")
summary(fit.ENVIZH_CN)
fit.ENVIZH_CN.anova = Anova(fit.ENVIZH_CN, type = 3)
fit.ENVIZH_CN.anova
```
TODO: ADD WRITE-UP OF RESULTS

```{r echo=FALSE, warning = FALSE, fig.cap = "Fixed effect sizes of each corpus when included as a predictor for China, US, and Vietnam responding, respectively. The English corpus is the best predictor for US response, and the Mandarin corpus is the best predictor for China response."}
coeff_value_freq <- c(fixef(fit.ENVIZH_US)["theme_freq_prop_E"],
                 fixef(fit.ENVIZH_US)["theme_freq_prop_V"], 
                 fixef(fit.ENVIZH_US)["theme_freq_prop_M"],
                 fixef(fit.ENVIZH_VN)["theme_freq_prop_E"],
                 fixef(fit.ENVIZH_VN)["theme_freq_prop_V"],
                 fixef(fit.ENVIZH_VN)["theme_freq_prop_M"], 
                 fixef(fit.ENVIZH_CN)["theme_freq_prop_E"],
                 fixef(fit.ENVIZH_CN)["theme_freq_prop_V"], 
                 fixef(fit.ENVIZH_CN)["theme_freq_prop_M"])

se_value_freq <- c(summary(fit.ENVIZH_US)$coef["theme_freq_prop_E", "Std. Error"], 
              summary(fit.ENVIZH_US)$coef["theme_freq_prop_V", "Std. Error"],
              summary(fit.ENVIZH_US)$coef["theme_freq_prop_M", "Std. Error"], 
              summary(fit.ENVIZH_VN)$coef["theme_freq_prop_E", "Std. Error"], 
              summary(fit.ENVIZH_VN)$coef["theme_freq_prop_V", "Std. Error"],
              summary(fit.ENVIZH_VN)$coef["theme_freq_prop_M", "Std. Error"],
              summary(fit.ENVIZH_CN)$coef["theme_freq_prop_E", "Std. Error"], 
              summary(fit.ENVIZH_CN)$coef["theme_freq_prop_V", "Std. Error"],
              summary(fit.ENVIZH_CN)$coef["theme_freq_prop_M", "Std. Error"])

country_value <- c(rep("US", 3),
                   rep("VN", 3),
                   rep("CN", 3))

corpus_value <- c(rep(c("EN", "VI", "ZH"), 3))

df.USVNCN_coeffs_freq <- data.frame(country_value, corpus_value, coeff_value_freq, se_value_freq)

ggplot(data = df.USVNCN_coeffs_freq, 
       mapping = aes(x = country_value, y = coeff_value_freq, fill = corpus_value)) +
  geom_bar(position="dodge", stat="identity") +
  geom_errorbar(aes(ymin= coeff_value_freq - se_value_freq, ymax = coeff_value_freq + se_value_freq), width=.2,
                 position=position_dodge(.9)) +
  scale_y_reverse() + 
  labs(x = "Country", y = "Fixed effect size", fill = "Corpus") + 
  scale_x_discrete(labels=c("CN" = "China", "US" = "US", "VN" = "Vietnam")) + 
  scale_fill_manual(values=c("#D63230", "#1C77C3", "#F39237"))

```

```{r model comparison, include=FALSE}
fit.US_freq_compare = anova(fit.ENVIZH_US, fit.EN_US, type = 3)
fit.VN_freq_compare = anova(fit.ENVIZH_VN, fit.VI_VN, type = 3)
fit.CN_freq_compare = anova(fit.ENVIZH_CN, fit.ZH_CN, type = 3)
```

TODO: ADD WRITE-UP ON RESULTS

#### Cosine distances of fastText word vectors

```{r Eng-Vie-Mand cosine similarities predicting US, VN, CN warning=FALSE, include=FALSE}
## English/Vietnamese/Mandarin comparison
fit.ENVIZH_US_cos = glmer(responses_theme ~ theme_cosine_prop_E + theme_cosine_prop_V + theme_cosine_prop_M +
                      (1 | subject) + (1 | triad), 
                    data = df %>% filter(country == "US"), 
                    family="binomial")
summary(fit.ENVIZH_US_cos)
fit.ENVIZH_US_cos.anova = Anova(fit.ENVIZH_US_cos, type = 3)
fit.ENVIZH_US_cos.anova

fit.ENVIZH_VN_cos = glmer(responses_theme ~ theme_cosine_prop_V + theme_cosine_prop_E + theme_cosine_prop_M +
                      (1 | subject) + (1 | triad), 
                    data = df %>% filter(country == "Vietnam"), 
                    family="binomial")
summary(fit.ENVIZH_VN_cos)
fit.ENVIZH_VN_cos.anova = Anova(fit.ENVIZH_VN_cos, type = 3)
fit.ENVIZH_VN_cos.anova

fit.ENVIZH_CN_cos = glmer(responses_theme ~ theme_cosine_prop_M + theme_cosine_prop_E + theme_cosine_prop_V +
                      (1 | subject) + (1 | triad), 
                    data = df %>% filter(country == "China"), 
                    family="binomial")
summary(fit.ENVIZH_CN_cos)
fit.ENVIZH_CN_cos.anova = Anova(fit.ENVIZH_CN_cos, type = 3)
fit.ENVIZH_CN_cos.anova
```

When we included all corpora thematic cosine distance proportion as predictors, all corpora are significant in predicting all cultural context's responding.

For US responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are all significant predictors. EN corpus: $\beta$ = `r round(fixef(fit.ENVIZH_US_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.ENVIZH_US_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.ENVIZH_US_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p < .001. VI corpus: $\beta$ = `r round(fixef(fit.ENVIZH_US_cos)["theme_cosine_prop_V"], 2)`, $\chi^2$(`r fit.ENVIZH_US_cos.anova["theme_cosine_prop_V", "Df"]`) = `r round(fit.ENVIZH_US_cos.anova["theme_cosine_prop_V", "Chisq"], 2)`, p = `r round(fit.ENVIZH_US_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"], 3)`. ZH corpus: $\beta$ = `r round(fixef(fit.ENVIZH_US_cos)["theme_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ENVIZH_US_cos.anova["theme_cosine_prop_M", "Df"]`) = `r round(fit.ENVIZH_US_cos.anova["theme_cosine_prop_M", "Chisq"], 2)`, p = `r round(fit.ENVIZH_US_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"], 3)`.

For Vietnam responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are all significant predictors. EN corpus: $\beta$ = `r round(fixef(fit.ENVIZH_VN_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.ENVIZH_VN_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p = `r round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"], 3)`. VI corpus: $\beta$ = `r round(fixef(fit.ENVIZH_VN_cos)["theme_cosine_prop_V"], 2)`, $\chi^2$(`r fit.ENVIZH_VN_cos.anova["theme_cosine_prop_V", "Df"]`) = `r round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_V", "Chisq"], 2)`, p = `r round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"], 3)`. ZH corpus: $\beta$ = `r round(fixef(fit.ENVIZH_VN_cos)["theme_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ENVIZH_VN_cos.anova["theme_cosine_prop_M", "Df"]`) = `r round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_M", "Chisq"], 2)`, p = `r round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"], 3)`.

For China responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are all significant predictors. EN corpus: $\beta$ = `r round(fixef(fit.ENVIZH_CN_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.ENVIZH_CN_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.ENVIZH_CN_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p = `r round(fit.ENVIZH_CN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"], 3)`. VI corpus: $\beta$ = `r round(fixef(fit.ENVIZH_CN_cos)["theme_cosine_prop_V"], 2)`, $\chi^2$(`r fit.ENVIZH_CN_cos.anova["theme_cosine_prop_V", "Df"]`) = `r round(fit.ENVIZH_CN_cos.anova["theme_cosine_prop_V", "Chisq"], 2)`, p = `r round(fit.ENVIZH_CN_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"], 3)`. ZH corpus: $\beta$ = `r round(fixef(fit.ENVIZH_CN_cos)["theme_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ENVIZH_CN_cos.anova["theme_cosine_prop_M", "Df"]`) = `r round(fit.ENVIZH_CN_cos.anova["theme_cosine_prop_M", "Chisq"], 2)`, p = < .001.

We observed some level of language specificity from this analysis. The English corpus is the best predictor for US responding, and the Mandarin corpus is the best predictor for China response. While this is not the case with the Vietnamese corpus and the Vietnam responding, the Vietnamese corpus is still a significant predictor for the Vietnam responding.

```{r echo=FALSE, warning = FALSE, fig.cap = "Fixed effect sizes of each corpus when included as a predictor for China, US, and Vietnam responding, respectively. The English corpus is the best predictor for US response, and the Mandarin corpus is the best predictor for China response."}
coeff_value_cos <- c(fixef(fit.ENVIZH_US_cos)["theme_cosine_prop_E"],
                 fixef(fit.ENVIZH_US_cos)["theme_cosine_prop_V"], 
                 fixef(fit.ENVIZH_US_cos)["theme_cosine_prop_M"],
                 fixef(fit.ENVIZH_VN_cos)["theme_cosine_prop_E"],
                 fixef(fit.ENVIZH_VN_cos)["theme_cosine_prop_V"],
                 fixef(fit.ENVIZH_VN_cos)["theme_cosine_prop_M"], 
                 fixef(fit.ENVIZH_CN_cos)["theme_cosine_prop_E"],
                 fixef(fit.ENVIZH_CN_cos)["theme_cosine_prop_V"], 
                 fixef(fit.ENVIZH_CN_cos)["theme_cosine_prop_M"])

se_value_cos <- c(summary(fit.ENVIZH_US_cos)$coef["theme_cosine_prop_E", "Std. Error"], 
              summary(fit.ENVIZH_US_cos)$coef["theme_cosine_prop_V", "Std. Error"],
              summary(fit.ENVIZH_US_cos)$coef["theme_cosine_prop_M", "Std. Error"], 
              summary(fit.ENVIZH_VN_cos)$coef["theme_cosine_prop_E", "Std. Error"], 
              summary(fit.ENVIZH_VN_cos)$coef["theme_cosine_prop_V", "Std. Error"],
              summary(fit.ENVIZH_VN_cos)$coef["theme_cosine_prop_M", "Std. Error"],
              summary(fit.ENVIZH_CN_cos)$coef["theme_cosine_prop_E", "Std. Error"], 
              summary(fit.ENVIZH_CN_cos)$coef["theme_cosine_prop_V", "Std. Error"],
              summary(fit.ENVIZH_CN_cos)$coef["theme_cosine_prop_M", "Std. Error"])

country_value <- c(rep("US", 3),
                   rep("VN", 3),
                   rep("CN", 3))

corpus_value <- c(rep(c("EN", "VI", "ZH"), 3))

df.USVNCN_coeffs_cos <- data.frame(country_value, corpus_value, coeff_value_cos, se_value_cos)

ggplot(data = df.USVNCN_coeffs_cos, 
       mapping = aes(x = country_value, y = coeff_value_cos, fill = corpus_value)) +
  geom_bar(position="dodge", stat="identity") +
  geom_errorbar(aes(ymin= coeff_value_cos - se_value_cos, ymax = coeff_value_cos + se_value_cos), width=.2,
                 position=position_dodge(.9)) +
  scale_y_reverse() + 
  labs(x = "Country", y = "Fixed effect size", fill = "Corpus") + 
  scale_x_discrete(labels=c("CN" = "China", "US" = "US", "VN" = "Vietnam")) + 
  scale_fill_manual(values=c("#D63230", "#1C77C3", "#F39237"))

```

```{r model comparison, include=FALSE}
fit.US_cos_compare = anova(fit.ENVIZH_US_cos, fit.EN_US_cos, type = 3)
fit.VN_cos_compare = anova(fit.ENVIZH_VN_cos, fit.VI_VN_cos, type = 3)
fit.CN_cos_compare = anova(fit.ENVIZH_CN_cos, fit.ZH_CN_cos, type = 3)
```

However, we found that language specificity alone does not explain our results. We used an ANOVA to compare the model with only the corresponding corpus, and the model with all 3 corpora for each cultural context. We found that in all three cases (US, China, Vietnam), adding the other two corpora produces a significantly better fit than the identical model without the additional corpora, and only the corresponding corpus included as a predictor (US response: $\chi^2$(`r fit.US_compare["fit.ENVIZH_US_cos", "Df"]`) = `r round(fit.US_compare["fit.ENVIZH_US_cos", "Chisq"], 2)`, p = `r round(fit.US_compare["fit.ENVIZH_US_cos", "Pr(>Chisq)"], 3)`; Vietnam response: $\chi^2$(`r fit.VN_compare["fit.ENVIZH_VN_cos", "Df"]`) = `r round(fit.VN_compare["fit.ENVIZH_VN_cos", "Chisq"], 2)`, p = < .001; China response: $\chi^2$(`r fit.CN_compare["fit.ENVIZH_CN_cos", "Df"]`) = `r round(fit.CN_compare["fit.ENVIZH_CN_cos", "Chisq"], 2)`, p = `r round(fit.CN_compare["fit.ENVIZH_CN_cos", "Pr(>Chisq)"], 3)`).

```{r add linguistic model to Ji et al., include=FALSE}
fit.country = glmer(responses_theme ~ country + (1 | subject) + (1 | triad), 
                           data = df %>% filter(country != "Vietnam"), 
                           family = "binomial")

fit.country_corpus = glmer(responses_theme ~ country + theme_cosine_prop_E + theme_cosine_prop_M + (1 | subject) + (1 | triad), 
                           data = df %>% filter(country != "Vietnam"), 
                           family = "binomial")

fit.add_corpus <- anova(fit.country, fit.country_corpus, type = 3)

```

We carried out an ANOVA model comparison to compare our approach with previous studies that did not include corpus information. Because @Ji2004 only compared US and China participants, we filtered our data to only include responding data from these two countries. Our approach would be to compare a model that only includes country (US or China) as a fixed effect with one that also includes English and Chinese corpus data. Our previous model with an intercept per subject and one per triad, as well as by-triad random slopes for country to account for variation in the country effect across triads fails to converge with the more complex model, so we include a simpler random effect structure with an intercept per subject and one per triad in both the basic and more complex model. We compare this model with an identical model but including Chinese and English corpus cosine distance proportion prediction. We found that adding English and Chinese corpus data produces a significantly better fit than the identical model without English and Chinese corpus data as predictors ($\chi^2$(`r fit.add_corpus["fit.country_corpus", "Df"]`) = `r round(fit.add_corpus["fit.country_corpus", "Chisq"], 2)`, p = < .001. This suggests that including corpus data would better model the cross-cultural differences in similarity judgment in this study as well as similar studies.

## Exploratory analysis

Because our exclusion criterion for attention checks excluded over 50% Vietnam participants, we carried out exploratory analysis where we applied less stringent exclusion criteria. In the following analysis, we only exclude participants who miss more than 2 attention checks (rather than any attention checks). We kept the rest of the exclusion criteria.

TODO: CREATE .CSV FILES FOR THESE, SEPARATE OUT R SCRIPT INTO RMD.
```{r loading data E explore, warning=FALSE, include=F}
df.resp_E <- read.csv("../../data/data_E_0319.csv") %>%
  select(-X)

# check for participants who completed the entire experiment. Because the experiment is
# quite long, some participants decide to come back afterwards, so there are a few files
# that are recorded as incomplete. 
df.ppts_finished_E <- df.resp_E %>% 
  group_by(subject) %>%
  summarize(finished = ifelse("demo-final" %in% unique(variable_type), "yes", "no")) %>%
  filter(finished == "yes")

df.resp_E <- df.resp_E %>%
  filter(subject %in% df.ppts_finished_E$subject)

df.ppts_att_E <- df.resp_E %>%
  filter(stim_type == "attention check") %>%
  mutate(correct_response = strsplit(cue, "Choose ")) %>%
  mutate(correct_response = sapply(correct_response, "[[", 2)) %>%
  mutate(pass_att_check = ifelse(responses == correct_response, 1, 0)) %>%
  group_by(subject) %>%
  summarize(pass_att_check_percent = mean(pass_att_check)) %>%
  filter(pass_att_check_percent >= 0.8)

df.resp_E <- df.resp_E %>%
  filter(subject %in% df.ppts_att_E$subject) 
```

```{r exclusion E explore, include = F, warning = F}
#non-native speaker
split_responses_demog <- function(responses) {
  responses <- as.character(responses)
  response_list <- unlist(strsplit(responses, ',|:'))
  response_list <- response_list[seq(1, length(response_list))]
  response_list <- gsub("}", "", response_list)
  response_list <- gsub("\"", "", response_list)
  return(response_list)
}

NATIVE_LANG = 2
get_native_lang <- Vectorize(function(responses) {
  responses <- split_responses_demog(responses)
  if(responses[NATIVE_LANG-1] != "{firstlanguage") 
    {warnings("cannot find native language answer")}
  else
    {return (responses[NATIVE_LANG])}
})

df.ppts_non_native_lang_E <- df.resp_E %>%
  select(subject, responses, variable_type) %>%
  filter(variable_type == "demog_language") %>%
  mutate(native_speaker = get_native_lang(responses)) %>%
  filter(native_speaker == "No")

ppts_non_native_lang_E = unique(df.ppts_non_native_lang_E$subject)#18
percent_dropped = length(ppts_non_native_lang_E) / length(unique(df.resp_E$subject))
percent_dropped #0.1041667

#fluent in Vietnamese & Mandarin
SPEAKER = 2
SPEAKING = 23
UNDERSTANDING = 46

get_speaker <- Vectorize(function(responses) {
  responses <- split_responses_demog(responses)
  return (responses[SPEAKER])
})

get_fluency_speaking <- Vectorize(function(responses) {
  responses <- split_responses_demog(responses)
  return (responses[SPEAKING])
})

get_fluency_understanding <- Vectorize(function(responses) {
  responses <- split_responses_demog(responses)
  return (responses[UNDERSTANDING])
})

df.lang_vi_E <- df.resp_E %>%
  select(subject, responses, variable_type) %>%
  filter(variable_type == "demog_language_vi") %>%
  mutate(vi_speaker = get_speaker(responses))

df.lang_vi_fluency_E <- df.resp_E %>%
  select(subject, responses, variable_type) %>%
  filter(variable_type == "demog_conditional_language_vn_fluency") %>%
  mutate(vi_fluency_sp = as.numeric(get_fluency_speaking(responses))) %>%
  mutate(vi_fluency_ud = as.numeric(get_fluency_understanding(responses)))

df.lang_vi_E <- full_join(df.lang_vi_E, 
                          df.lang_vi_fluency_E, 
                          by = "subject") %>%
  select(subject, vi_speaker, vi_fluency_sp, vi_fluency_ud) %>%
  filter(vi_speaker == "Yes",
         vi_fluency_sp > 4, 
         vi_fluency_ud > 4)

ppts_vi_speaker_E = unique(df.lang_vi_E$subject) #4
percent_dropped = length(ppts_vi_speaker_E) / length(unique(df.resp_E$subject))
percent_dropped #0.02083333

df.lang_zh_E <- df.resp_E %>%
  select(subject, responses, variable_type) %>%
  filter(variable_type == "demog_language_cn") %>%
  mutate(zh_speaker = get_speaker(responses))

df.lang_zh_fluency_E <- df.resp_E %>%
  select(subject, responses, variable_type) %>%
  filter(variable_type == "demog_conditional_language_cn_fluency") %>%
  mutate(zh_fluency_sp = as.numeric(get_fluency_speaking(responses))) %>%
  mutate(zh_fluency_ud = as.numeric(get_fluency_understanding(responses)))

df.lang_zh_E <- full_join(df.lang_zh_E, 
                          df.lang_zh_fluency_E, 
                          by = "subject") %>%
  select(subject, zh_speaker, zh_fluency_sp, zh_fluency_ud) %>%
  filter(zh_speaker == "Yes",
         zh_fluency_sp > 4, 
         zh_fluency_ud > 4)

ppts_zh_speaker_E = unique(df.lang_zh_E$subject) #30
percent_dropped = length(ppts_zh_speaker_E) / length(unique(df.resp_E$subject))
percent_dropped #0.1822917

#have lived outside the sample country for more than 2 years
#have travelled extensively (more than 6 international experiences of 2 days or longer) 
YEARSABROAD = 2
OVERSEAEXP = 4

get_lived_abroad <- Vectorize(function(responses) {
  responses <- split_responses_demog(responses)
  return (responses[YEARSABROAD])
})

get_oversea_exp <- Vectorize(function(responses) {
  responses <- split_responses_demog(responses)
  return (responses[OVERSEAEXP])
})

df.abroad_E <- df.resp_E %>%
  select(subject, responses, variable_type) %>%
  filter(variable_type == "demog_oversea_experience") %>%
  mutate(lived_abroad = get_lived_abroad(responses)) %>%
  mutate(oversea_exp = get_oversea_exp(responses))

df.lived_abroad_E <- df.abroad_E %>%
  filter(lived_abroad == "Yes")

ppts_lived_abroad_E = unique(df.lived_abroad_E$subject) #29
percent_dropped = length(ppts_lived_abroad_E) / length(unique(df.resp_E$subject))
percent_dropped #0.171875

df.oversea_exp_E <- df.abroad_E %>%
  filter(oversea_exp == "Six or more experiences")

ppts_oversea_exp_E = unique(df.oversea_exp_E$subject) #77
percent_dropped = length(ppts_oversea_exp_E) / length(unique(df.resp_E$subject))
percent_dropped #0.44 # will not use this criterion

df.resp_E <- df.resp_E %>%
  filter(!(subject %in% ppts_non_native_lang_E),
         !(subject %in% ppts_vi_speaker_E), 
         !(subject %in% ppts_zh_speaker_E),
         !(subject %in% ppts_lived_abroad_E))

length(unique(df.resp_E$subject)) #132
```

```{r demog_E explore, include = F}
demog <- c("demog-dropdown", "demog-multi-choice", "demog-free-response", "demog-multi-select")
df.demog_E <- df.resp_E %>%
  filter(trial_type %in% demog)

AGE = 97 #index for age answer
GENDER = 115 #index for gender answer
split_responses <- function(responses) {
  responses <- as.character(responses)
  response_list <- unlist(strsplit(responses, ',|:'))
  response_list <- response_list[seq(1, length(response_list))]
  response_list <- gsub("}", "", response_list)
  response_list <- gsub("\"", "", response_list)
  return(response_list)
}

get_age <- Vectorize(function(responses) {
  responses <- split_responses(responses)
  if(responses[AGE-1] != "A0") {warnings("cannot find age answer")}
  else{return (responses[AGE])}
})

get_gender <- Vectorize(function(responses) {
  responses <- split_responses(responses)
  if(responses[GENDER-1] != "A1") {warnings("cannot find gender answer")}
  else{return (responses[GENDER])}
})

df.age_gender_E <- df.demog_E %>%
  filter(variable_type == "demog_age_gender_ethnic") %>%
  select(subject, responses) %>%
  mutate(age = as.numeric(get_age(responses))) %>%
  mutate(age = as.numeric(age)) %>%
  mutate(gender = get_gender(responses))

df.age_gender_E_summ <- df.age_gender_E %>%
  summarize(mean_age = mean(age), 
            median_age = median(age), 
            sd_age = sd(age))
```

```{r loading data V explore, include=F}
df.resp_V <- read.csv("../../data/data_V_0530.csv") %>%
  select(-X)

# check for participants who completed the entire experiment. Because the experiment is
# quite long, some participants decide to come back afterwards, so there are a few files
# that are recorded as incomplete. 
df.ppts_finished_V <- df.resp_V %>% 
  group_by(subject) %>%
  summarize(finished = ifelse("demo-final" %in% unique(variable_type), "yes", "no")) %>%
  filter(finished == "yes")

df.resp_V <- df.resp_V %>%
  filter(subject %in% df.ppts_finished_V$subject)

df.ppts_att_V <- df.resp_V %>%
  filter(stim_type == "attention check") %>%
  mutate(correct_response = strsplit(cue, "Chọn ")) %>%
  mutate(correct_response = sapply(correct_response, "[[", 2)) %>%
  mutate(pass_att_check = ifelse(responses == correct_response, 1, 0)) %>%
  group_by(subject) %>%
  summarize(pass_att_check_percent = mean(pass_att_check)) %>%
  filter(pass_att_check_percent >= 0.8)

df.resp_V <- df.resp_V %>%
  filter(subject %in% df.ppts_att_V$subject) #73
```

```{r exclusion V explore, include = F}
#non-native speaker
split_responses_demog <- function(responses) {
  responses <- as.character(responses)
  response_list <- unlist(strsplit(responses, ',|:'))
  response_list <- response_list[seq(1, length(response_list))]
  response_list <- gsub("}", "", response_list)
  response_list <- gsub("\"", "", response_list)
  return(response_list)
}

NATIVE_LANG = 2
get_native_lang <- Vectorize(function(responses) {
  responses <- split_responses_demog(responses)
  if(responses[NATIVE_LANG-1] != "{firstlanguage") 
    {warnings("cannot find native language answer")}
  else
    {return (responses[NATIVE_LANG])}
})

df.ppts_non_native_lang_V <- df.resp_V %>%
  select(subject, responses, variable_type) %>%
  filter(variable_type == "demog_language") %>%
  mutate(native_speaker = get_native_lang(responses)) %>%
  filter(native_speaker == "Không")

ppts_non_native_lang_V = unique(df.ppts_non_native_lang_V$subject)
percent_dropped = length(ppts_non_native_lang_V) / length(unique(df.resp_V$subject))
percent_dropped #0

#fluent in English
SPEAKER = 2
SPEAKING = 23
UNDERSTANDING = 46

get_speaker <- Vectorize(function(responses) {
  responses <- split_responses_demog(responses)
  return (responses[SPEAKER])
})

get_fluency_speaking <- Vectorize(function(responses) {
  responses <- split_responses_demog(responses)
  return (responses[SPEAKING])
})

get_fluency_understanding <- Vectorize(function(responses) {
  responses <- split_responses_demog(responses)
  return (responses[UNDERSTANDING])
})

df.lang_en_V <- df.resp_V %>%
  select(subject, responses, variable_type) %>%
  filter(variable_type == "demog_language_en") %>%
  mutate(en_speaker = get_speaker(responses))

df.lang_en_fluency_V <- df.resp_V %>%
  select(subject, responses, variable_type) %>%
  filter(variable_type == "demog_conditional_language_en_fluency") %>%
  mutate(en_fluency_sp = as.numeric(get_fluency_speaking(responses))) %>%
  mutate(en_fluency_ud = as.numeric(get_fluency_understanding(responses)))

df.lang_en_V <- full_join(df.lang_en_V, 
                          df.lang_en_fluency_V, 
                          by = "subject") %>%
  select(subject, en_speaker, en_fluency_sp, en_fluency_ud) %>%
  filter(en_speaker == "Có",
         en_fluency_sp > 4, 
         en_fluency_ud > 4)

ppts_en_speaker_V = unique(df.lang_en_V$subject) #4
percent_dropped = length(ppts_en_speaker_V) / length(unique(df.resp_V$subject))
percent_dropped #0.6861314 # do not use this criterion

df.lang_zh_V <- df.resp_V %>%
  select(subject, responses, variable_type) %>%
  filter(variable_type == "demog_language_cn") %>%
  mutate(zh_speaker = get_speaker(responses))

df.lang_zh_fluency_V <- df.resp_V %>%
  select(subject, responses, variable_type) %>%
  filter(variable_type == "demog_conditional_language_cn_fluency") %>%
  mutate(zh_fluency_sp = as.numeric(get_fluency_speaking(responses))) %>%
  mutate(zh_fluency_ud = as.numeric(get_fluency_understanding(responses)))

df.lang_zh_V <- full_join(df.lang_zh_V, 
                          df.lang_zh_fluency_V, 
                          by = "subject") %>%
  select(subject, zh_speaker, zh_fluency_sp, zh_fluency_ud) %>%
  filter(zh_speaker == "Có",
         zh_fluency_sp > 4, 
         zh_fluency_ud > 4)

ppts_zh_speaker_V = unique(df.lang_zh_V$subject) #4
percent_dropped = length(ppts_zh_speaker_V) / length(unique(df.resp_V$subject))
percent_dropped #0.05839416

#have lived outside the sample country for more than 2 years
#have travelled extensively (more than 6 international experiences of 2 days or longer) 
YEARSABROAD = 2
OVERSEAEXP = 4

get_lived_abroad <- Vectorize(function(responses) {
  responses <- split_responses_demog(responses)
  return (responses[YEARSABROAD])
})

get_oversea_exp <- Vectorize(function(responses) {
  responses <- split_responses_demog(responses)
  return (responses[OVERSEAEXP])
})

df.abroad_V <- df.resp_V %>%
  select(subject, responses, variable_type) %>%
  filter(variable_type == "demog_oversea_experience") %>%
  mutate(lived_abroad = get_lived_abroad(responses)) %>%
  mutate(oversea_exp = get_oversea_exp(responses))

df.lived_abroad_V <- df.abroad_V %>%
  filter(lived_abroad == "Có")

ppts_lived_abroad_V = unique(df.lived_abroad_V$subject)
percent_dropped = length(ppts_lived_abroad_V) / length(unique(df.resp_V$subject))
percent_dropped #0.1094891

df.oversea_exp_V <- df.abroad_V %>%
  filter(oversea_exp == "6 lần trở lên")

ppts_oversea_exp_V = unique(df.oversea_exp_V$subject) #77
percent_dropped = length(ppts_oversea_exp_V) / length(unique(df.resp_V$subject))
percent_dropped #0.1094891

df.resp_V <- df.resp_V %>%
  filter(!(subject %in% ppts_non_native_lang_V),
         !(subject %in% ppts_oversea_exp_V), 
         !(subject %in% ppts_zh_speaker_V),
         !(subject %in% ppts_lived_abroad_V))

length(unique(df.resp_V$subject))  #110
```

```{r demog_V explore, include = F}
demog <- c("demog-dropdown", "demog-multi-choice", "demog-free-response", "demog-multi-select")
df.demog_V <- df.resp_V %>%
  filter(trial_type %in% demog)

AGE = 97 #index for age answer
GENDER = 115 #index for gender answer
split_responses <- function(responses) {
  responses <- as.character(responses)
  response_list <- unlist(strsplit(responses, ',|:'))
  response_list <- response_list[seq(1, length(response_list))]
  response_list <- gsub("}", "", response_list)
  response_list <- gsub("\"", "", response_list)
  return(response_list)
}

get_age <- Vectorize(function(responses) {
  responses <- split_responses(responses)
  if(responses[AGE-1] != "A0") {warnings("cannot find age answer")}
  else{return (responses[AGE])}
})

get_gender <- Vectorize(function(responses) {
  responses <- split_responses(responses)
  if(responses[GENDER-1] != "A1") {warnings("cannot find gender answer")}
  else{return (responses[GENDER])}
})

df.age_gender_V <- df.demog_V %>%
  filter(variable_type == "demog_age_gender_ethnic") %>%
  select(subject, responses) %>%
  mutate(age = as.numeric(get_age(responses))) %>%
  mutate(age = as.numeric(age)) %>%
  mutate(gender = get_gender(responses))

df.age_gender_V_summ <- df.age_gender_V %>%
  summarize(mean_age = mean(age), 
            median_age = median(age), 
            sd_age = sd(age))
```

```{r loading data M explore, warning=FALSE, include=F}
df.resp_M <- read.csv("../../data/data_M_0530.csv") %>%
  select(-X)

# check for participants who completed the entire experiment. Because the experiment is
# quite long, some participants decide to come back afterwards, so there are a few files
# that are recorded as incomplete. 
df.ppts_finished_M <- df.resp_M %>% 
  group_by(subject) %>%
  summarize(finished = ifelse("demo-final" %in% unique(variable_type), "yes", "no")) %>%
  filter(finished == "yes")

df.resp_M <- df.resp_M %>%
  filter(subject %in% df.ppts_finished_M$subject)

df.ppts_att_M <- df.resp_M %>%
  filter(stim_type == "attention check") %>%
  mutate(correct_response = strsplit(cue, "选择")) %>%
  mutate(correct_response = sapply(correct_response, "[[", 2)) %>%
  mutate(correct_response = str_replace_all(correct_response, "“", "")) %>%
  mutate(correct_response = str_replace_all(correct_response, "”", "")) %>%
  mutate(pass_att_check = ifelse(responses == correct_response, 1, 0)) %>%
  group_by(subject) %>%
  summarize(pass_att_check_percent = mean(pass_att_check)) %>%
  filter(pass_att_check_percent >= 0.8)

df.resp_M <- df.resp_M %>%
  filter(subject %in% df.ppts_att_M$subject) 
```

```{r exclusion M explore, include = F, warning = F}
#non-native speaker
split_responses_demog <- function(responses) {
  responses <- as.character(responses)
  response_list <- unlist(strsplit(responses, ',|:'))
  response_list <- response_list[seq(1, length(response_list))]
  response_list <- gsub("}", "", response_list)
  response_list <- gsub("\"", "", response_list)
  return(response_list)
}

NATIVE_LANG = 2
get_native_lang <- Vectorize(function(responses) {
  responses <- split_responses_demog(responses)
  if(responses[NATIVE_LANG-1] != "{firstlanguage") 
    {warnings("cannot find native language answer")}
  else
    {return (responses[NATIVE_LANG])}
})

df.ppts_non_native_lang_M <- df.resp_M %>%
  select(subject, responses, variable_type) %>%
  filter(variable_type == "demog_language") %>%
  mutate(native_speaker = get_native_lang(responses)) %>%
  filter(native_speaker == "不是")

ppts_non_native_lang_M = unique(df.ppts_non_native_lang_M$subject) #2
percent_dropped = length(ppts_non_native_lang_M) / length(unique(df.resp_M$subject))
percent_dropped #0.01149425

#fluent in English
SPEAKER = 2
SPEAKING = 23
UNDERSTANDING = 46

get_speaker <- Vectorize(function(responses) {
  responses <- split_responses_demog(responses)
  return (responses[SPEAKER])
})

get_fluency_speaking <- Vectorize(function(responses) {
  responses <- split_responses_demog(responses)
  return (responses[SPEAKING])
})

get_fluency_understanding <- Vectorize(function(responses) {
  responses <- split_responses_demog(responses)
  return (responses[UNDERSTANDING])
})

df.lang_en_M <- df.resp_M %>%
  select(subject, responses, variable_type) %>%
  filter(variable_type == "demog_language_en") %>%
  mutate(en_speaker = get_speaker(responses))

df.lang_en_fluency_M <- df.resp_M %>%
  select(subject, responses, variable_type) %>%
  filter(variable_type == "demog_conditional_language_en_fluency") %>%
  mutate(en_fluency_sp = as.numeric(get_fluency_speaking(responses))) %>%
  mutate(en_fluency_ud = as.numeric(get_fluency_understanding(responses)))

df.lang_en_M <- full_join(df.lang_en_M, 
                          df.lang_en_fluency_M, 
                          by = "subject") %>%
  select(subject, en_speaker, en_fluency_sp, en_fluency_ud) %>%
  filter(en_speaker == "能",
         en_fluency_sp > 4, 
         en_fluency_ud > 4)

ppts_en_speaker_M = unique(df.lang_en_M$subject) #50
percent_dropped = length(ppts_en_speaker_M) / length(unique(df.resp_M$subject))
percent_dropped #0.3850575 # will not use this criterion

df.lang_vi_M <- df.resp_M %>%
  select(subject, responses, variable_type) %>%
  filter(variable_type == "demog_language_vi") %>%
  mutate(vi_speaker = get_speaker(responses))

df.lang_vi_fluency_M <- df.resp_M %>%
  filter(variable_type == "demog_conditional_language_vi_fluency") %>%
  mutate(vi_fluency_sp = as.numeric(get_fluency_speaking(responses))) %>%
  mutate(vi_fluency_ud = as.numeric(get_fluency_understanding(responses)))

df.lang_vi_M <- full_join(df.lang_vi_M, 
                          df.lang_vi_fluency_M, 
                          by = "subject") %>%
  select(subject, vi_speaker, vi_fluency_sp, vi_fluency_ud) %>%
  filter(vi_speaker == "能",
         vi_fluency_sp > 4, 
         vi_fluency_ud > 4)

ppts_vi_speaker_M = unique(df.lang_vi_M$subject) #50
percent_dropped = length(ppts_vi_speaker_M) / length(unique(df.resp_M$subject))
percent_dropped #0

#have lived outside the sample country for more than 2 years
#have travelled extensively (more than 6 international experiences of 2 days or longer) 
YEARSABROAD = 2
OVERSEAEXP = 4

get_lived_abroad <- Vectorize(function(responses) {
  responses <- split_responses_demog(responses)
  return (responses[YEARSABROAD])
})

get_oversea_exp <- Vectorize(function(responses) {
  responses <- split_responses_demog(responses)
  return (responses[OVERSEAEXP])
})

df.abroad_M <- df.resp_M %>%
  select(subject, responses, variable_type) %>%
  filter(variable_type == "demog_oversea_experience") %>%
  mutate(lived_abroad = get_lived_abroad(responses)) %>%
  mutate(oversea_exp = get_oversea_exp(responses))

df.lived_abroad_M <- df.abroad_M %>%
  filter(lived_abroad == "是")

ppts_lived_abroad_M = unique(df.lived_abroad_M$subject) #23
percent_dropped = length(ppts_lived_abroad_M) / length(unique(df.resp_M$subject))
percent_dropped # 0.1551724

df.oversea_exp_M <- df.abroad_M %>%
  filter(oversea_exp == "六段或更多国际经历")

ppts_oversea_exp_M = unique(df.oversea_exp_M$subject) #0
percent_dropped = length(ppts_oversea_exp_M) / length(unique(df.resp_M$subject))
percent_dropped #0.03448276

df.resp_M <- df.resp_M %>%
  filter(!(subject %in% ppts_non_native_lang_M),
         !(subject %in% ppts_lived_abroad_M),
         !(subject %in% ppts_vi_speaker_M),
         !(subject %in% ppts_oversea_exp_M),)

length(unique(df.resp_M$subject)) #143
```

```{r demog_M explore, include = F}
demog <- c("demog-dropdown", "demog-multi-choice", "demog-free-response", "demog-multi-select")
df.demog_M <- df.resp_M %>%
  filter(trial_type %in% demog) 
#write.csv(data_demog, "data_anon_demog_0201.csv")

AGE = 97 #index for age answer
GENDER = 115 #index for gender answer
split_responses <- function(responses) {
  responses <- as.character(responses)
  response_list <- unlist(strsplit(responses, ',|:'))
  response_list <- response_list[seq(1, length(response_list))]
  response_list <- gsub("}", "", response_list)
  response_list <- gsub("\"", "", response_list)
  return(response_list)
}

get_age <- Vectorize(function(responses) {
  responses <- split_responses(responses)
  if(responses[AGE-1] != "A0") {warnings("cannot find age answer")}
  else{return (responses[AGE])}
})

get_gender <- Vectorize(function(responses) {
  responses <- split_responses(responses)
  if(responses[GENDER-1] != "A1") {warnings("cannot find gender answer")}
  else{return (responses[GENDER])}
})

df.age_gender_M <- df.demog_M %>%
  filter(variable_type == "demog_age_gender_ethnic") %>%
  select(subject, responses) %>%
  mutate(age = as.numeric(get_age(responses))) %>%
  mutate(age = as.numeric(age)) %>%
  mutate(gender = get_gender(responses))

df.age_gender_M_summ <- df.age_gender_M %>%
  summarize(mean_age = mean(age), 
            median_age = median(age), 
            sd_age = sd(age))
```

With the new exclusion criteria, we excluded `r length(unique(df.ppts_finished_E$subject)) - length(unique(df.ppts_att_E$subject))` US participants, `r length(unique(df.ppts_finished_V$subject)) - length(unique(df.ppts_att_V$subject))` VN participants, and `r length(unique(df.ppts_finished_M$subject)) - length(unique(df.ppts_att_M$subject))` CN participants who did not answer more than 2 attention checks correctly. We then applied the 4 criteria that aim to retain only participants who are influenced by one culture: (1) non-native speakers of English and Vietnamese, respectively, (2) fluent in at least one of the other two study languages (Vietnamese for US participants, English for Vietnamese participants and Chinese participants), (3) have lived outside of the test country (US, Vietnam, or China) for more than two years, and (4) have significant international experience (more than 6 international experiences of 2 days or longer.) We did not use a particular criterion for a language if it would exclude 25% or more of any one sample. In this round of exclusion, we excluded `r length(unique(df.ppts_att_E$subject)) - length(unique(df.resp_E$subject))` US, `r length(unique(df.ppts_att_V$subject)) - length(unique(df.resp_V$subject))` VN participants, and `r length(unique(df.ppts_att_M$subject)) - length(unique(df.resp_M$subject))` CN participants. After these exclusions, the US sample included `r length(unique(df.resp_E$subject))` participants (`r df.age_gender_E %>% filter(gender == "Male") %>% count()`M, `r df.age_gender_E %>% filter(gender == "Female") %>% count()`F, `r df.age_gender_E %>% filter(gender == "Non-binary") %>% count()` non-binary, `r df.age_gender_E %>% filter(gender == "Decline to answer") %>% count()` other), with mean age = `r round(df.age_gender_E_summ$mean_age, 2)` (SD = `r round(df.age_gender_E_summ$sd_age, 2)`) and median age = `r df.age_gender_E_summ$median_age`. The VN sample included `r length(unique(df.resp_V$subject))` participants (`r df.age_gender_V %>% filter(gender == "Nam") %>% count()`M, `r df.age_gender_V %>% filter(gender == "Nữ") %>% count()`F), with mean age = `r round(df.age_gender_V_summ$mean_age, 2)` (SD = `r round(df.age_gender_V_summ$sd_age, 2)`) and median age = `r df.age_gender_V_summ$median_age`. The CN sample included `r length(unique(df.resp_M$subject))` participants (`r df.age_gender_M %>% filter(gender == "男性") %>% count()`M, `r df.age_gender_M %>% filter(gender == "女性") %>% count()`F), with mean age = `r round(df.age_gender_M_summ$mean_age, 2)` (SD = `r round(df.age_gender_M_summ$sd_age, 2)`) and median age = `r df.age_gender_M_summ$median_age`.

```{r corpus explore, include = F}
df.corpus_E <- read.csv("../../data/corpusE_cos.csv") %>%
  rename(tax_frequency_E = tax.frequency,
         theme_frequency_E = theme.frequency,
         tax_cosine_E = Tax.cosine_dist, 
         theme_cosine_E = Theme.cosine_dist,
         tax_cosine_sim_E = Tax.cosine_sim,
         theme_cosine_sim_E = Theme.cosine_sim,
         tax_match_E = Tax.match,
         theme_match_E = Theme.match, 
         cue_E = Cue)

df.corpus_V <- read.csv("../../data/corpusV_cos.csv") %>%
  rename(tax_frequency_V = tax.frequency,
         theme_frequency_V = theme.frequency,
         tax_cosine_V = Tax.cosine_dist, 
         theme_cosine_V = Theme.cosine_dist,
         tax_cosine_sim_V = Tax.cosine_sim,
         theme_cosine_sim_V = Theme.cosine_sim,
         tax_match_V = Tax.match,
         theme_match_V = Theme.match, 
         cue_V = Cue)

df.corpus_M <- read.csv("../../data/corpusM_cos.csv") %>%
  rename(tax_frequency_M = tax.frequency,
         theme_frequency_M = theme.frequency,
         tax_cosine_M = Tax.cosine_dist, 
         theme_cosine_M = Theme.cosine_dist,
         tax_cosine_sim_M = Tax.cosine_sim,
         theme_cosine_sim_M = Theme.cosine_sim,
         tax_match_M = Tax.match,
         theme_match_M = Theme.match, 
         cue_M = Cue)
```

```{r full corpus explore, M freqs is incorrect, include=F}
df.corpus <- left_join(df.corpus_E, df.corpus_V, by = "Cue_renamed")
df.corpus <- left_join(df.corpus, df.corpus_M, by = "Cue_renamed")

#replacing any 0 raw counts with epsilon
df.corpus <- df.corpus %>%
  mutate(tax_frequency_E = ifelse(tax_frequency_E == 0, 
                                  .Machine$double.eps, tax_frequency_E),
         theme_frequency_E = ifelse(theme_frequency_E == 0, 
                                  .Machine$double.eps, theme_frequency_E),
         tax_frequency_V = ifelse(tax_frequency_V == 0, 
                                  .Machine$double.eps, tax_frequency_V),
         theme_frequency_V = ifelse(theme_frequency_V == 0, 
                                  .Machine$double.eps, theme_frequency_V))

```

```{r corpus - frequency explore, include = F}
#find triads_omit, used whenever analysis uses raw collocates 
df.corpus_E_freq <- df.corpus_E %>%
  select(Cue_renamed, cue_E, tax_match_E, theme_match_E, tax_frequency_E, theme_frequency_E)
corpus_E_omit <- df.corpus_E_freq %>%
  filter(tax_frequency_E == 0 & theme_frequency_E == 0)

df.corpus_V_freq <- df.corpus_V %>%
  select(Cue_renamed, cue_V, tax_match_V, theme_match_V, tax_frequency_V, theme_frequency_V)
corpus_V_omit <- df.corpus_V_freq %>% 
  filter(tax_frequency_V == 0 & theme_frequency_V == 0)

triads_omit <- append(corpus_E_omit$Cue_renamed, corpus_V_omit$Cue_renamed)

df.corpus_freq <- left_join(df.corpus_E_freq, df.corpus_V_freq, by = "Cue_renamed")
```

```{r corpus - cosine explore, include = F}
#mainly for sanity checking and so that there is a parallel df to df.corpus_freq
df.corpus_E_cos <- df.corpus_E %>%
  select(Cue_renamed, cue_E, tax_match_E, theme_match_E, 
         tax_cosine_E, theme_cosine_E,
         tax_cosine_sim_E, theme_cosine_sim_E)

df.corpus_V_cos <- df.corpus_V %>%
  select(Cue_renamed, cue_V, tax_match_V, theme_match_V, tax_cosine_V, theme_cosine_V,
         tax_cosine_sim_V, theme_cosine_sim_V)

df.corpus_M_cos <- df.corpus_M %>%
  select(Cue_renamed, cue_M, tax_match_M, theme_match_M, tax_cosine_M, theme_cosine_M, 
         tax_cosine_sim_M, theme_cosine_sim_M)

df.corpus_cos <- left_join(df.corpus_E_cos, df.corpus_V_cos, by = "Cue_renamed")
df.corpus_cos <- left_join(df.corpus_cos, df.corpus_M_cos, by = "Cue_renamed")
```

```{r getting triads from the 3 languages explore, include = F}
#combine response and corpus data
df.triad_E <- df.resp_E %>%
  filter(stim_type == "triad",
         responses != "NA")
triad_cues_E <- read.csv("../../data/cue_renamed_E.csv")
df.triad_E <- left_join(df.triad_E, triad_cues_E, by = c("cue", "top_opt", "bottom_opt"))
df.triad_E <- inner_join(df.triad_E, df.corpus, by = "Cue_renamed")

df.triad_E <- df.triad_E %>%
  mutate(responses_theme = ifelse(responses == theme_match_E, 1, 0),
         language = "English",
         country = "US") %>%
  select(subject, rt, Cue_renamed, cue, top_opt, bottom_opt, 
         responses, responses_theme, country, language,
         tax_match_E, theme_match_E, tax_match_V, theme_match_V, tax_match_M, theme_match_M,
         tax_frequency_E, theme_frequency_E, tax_frequency_V, theme_frequency_V, tax_frequency_M, theme_frequency_M,
         tax_cosine_E, theme_cosine_E, tax_cosine_V, theme_cosine_V, tax_cosine_M, theme_cosine_M,
         tax_cosine_sim_E, theme_cosine_sim_E, tax_cosine_sim_V, theme_cosine_sim_V, tax_cosine_sim_M, theme_cosine_sim_M)

df.triad_V <- df.resp_V %>%
  filter(stim_type == "triad",
         responses != "NA")
triad_cues_V <- read.csv("../../data/cue_renamed_V.csv")
df.triad_V <- left_join(df.triad_V, triad_cues_V, by = c("cue", "top_opt", "bottom_opt"))
df.triad_V <- inner_join(df.triad_V, df.corpus, by = "Cue_renamed")

df.triad_V <- df.triad_V %>%
  mutate(responses_theme = ifelse(responses == theme_match_V, 1, 0),
         language = "Vietnamese", 
         country = "Vietnam") %>%
  select(subject, rt, Cue_renamed, cue, top_opt, bottom_opt, 
         responses, responses_theme, country, language,
         tax_match_E, theme_match_E, tax_match_V, theme_match_V, tax_match_M, theme_match_M,
         tax_frequency_E, theme_frequency_E, tax_frequency_V, theme_frequency_V, tax_frequency_M, theme_frequency_M,
         tax_cosine_E, theme_cosine_E, tax_cosine_V, theme_cosine_V, tax_cosine_M, theme_cosine_M,
         tax_cosine_sim_E, theme_cosine_sim_E, tax_cosine_sim_V, theme_cosine_sim_V, tax_cosine_sim_M, theme_cosine_sim_M)

df.triad_M <- df.resp_M %>%
  filter(stim_type == "triad",
         responses != "NA")
triad_cues_M <- read.csv("../../data/cue_renamed_M.csv")
df.triad_M <- left_join(df.triad_M, triad_cues_M, by = c("cue", "top_opt", "bottom_opt"))
df.triad_M <- inner_join(df.triad_M, df.corpus, by = "Cue_renamed")

df.triad_M <- df.triad_M %>%
  mutate(responses_theme = ifelse(responses == theme_match_M, 1, 0),
         language = "Mandarin", 
         country = "China") %>%
  select(subject, rt, Cue_renamed, cue, top_opt, bottom_opt, 
         responses, responses_theme, country, language,
         tax_match_E, theme_match_E, tax_match_V, theme_match_V, tax_match_M, theme_match_M,
         tax_frequency_E, theme_frequency_E, tax_frequency_V, theme_frequency_V, tax_frequency_M, theme_frequency_M,
         tax_cosine_E, theme_cosine_E, tax_cosine_V, theme_cosine_V, tax_cosine_M, theme_cosine_M,
         tax_cosine_sim_E, theme_cosine_sim_E, tax_cosine_sim_V, theme_cosine_sim_V, tax_cosine_sim_M, theme_cosine_sim_M)

#calculate proportion for raw frequencies and cosine distance
df <- rbind(df.triad_E, df.triad_V)
df <- rbind(df, df.triad_M) %>%
  mutate(theme_freq_prop_E = theme_frequency_E / (theme_frequency_E + tax_frequency_E),
         theme_freq_prop_V = theme_frequency_V / (theme_frequency_V + tax_frequency_V), 
         theme_freq_prop_M = theme_frequency_M / (theme_frequency_M + tax_frequency_M), 
         theme_cosine_prop_E = theme_cosine_E / (theme_cosine_E + tax_cosine_E),
         theme_cosine_prop_V = theme_cosine_V / (theme_cosine_V + tax_cosine_V), 
         theme_cosine_prop_M = theme_cosine_M / (theme_cosine_M + tax_cosine_M)) %>%
  rename(triad = Cue_renamed)
```

```{r country effect - explore, warning=FALSE, include=FALSE, paged.print=TRUE}
df.country <- df %>%
  group_by(subject, country) %>%
  summarize(theme_resp_percent = mean(responses_theme, na.rm = T))

df.country_sum <- df.country %>%
  group_by(country) %>%
  summarize(mean_theme_resp_percent = mean(theme_resp_percent), 
            sd_theme_resp_percent = sd(theme_resp_percent))

fit.country = glmer(responses_theme ~ country + (1 | subject) + (country | triad), 
                    data = df, 
                    family = "binomial")
summary(fit.country) 
fit.country.anova = Anova(fit.country, type=3)

fit.country_EN_VN = glmer(responses_theme ~ country + (1 | subject) + (country | triad), 
                    data = df %>% filter(country != "China"),
                    family = "binomial")
summary(fit.country_EN_VN) 
```

```{r echo=FALSE, warning=FALSE, fig.cap="Proportion of thematic responses by country, with a less stringent attention check criterion. We did not find any significant differences from the analysis reported above with a more stringent criterion."}

ggplot(df.country,
       mapping = aes(x = country, 
                     y = theme_resp_percent, 
                     color = country)) +
  geom_violin() +
  geom_jitter(height = 0, 
              alpha = 0.3) +  
  stat_summary(fun.data = "mean_cl_boot", 
               geom = "pointrange") + 
  labs(y = "Proportion Thematic Chosen", 
       x = "Country", 
       color = "Country") + 
  scale_color_manual(values=c("#D63230", "#1C77C3", "#F39237"))
```

There is no significant difference in this round of analysis compared to the one reported above (with more stringent attention check criterion). That is, we still observed a significant effect of country on proportion of thematic responses ($\chi^2$(`r fit.country.anova["country", "Df"]`) = `r round(fit.country.anova["country", "Chisq"], 2)`, p < .001), but this effect is driven by only the difference between US and China response ($\beta$ = `r round(fixef(fit.country)["countryUS"], 2)`, p < .001). There is no statistical difference between the Vietnam and China response ($\beta$ = `r round(fixef(fit.country)["countryVietnam"], 2)`, p = `r round(as.data.frame(summary(fit.country)[["coefficients"]])["countryVietnam", "Pr(>|z|)"], 3)`), and the US and Vietnam response ($\beta$ = `r round(fixef(fit.country_EN_VN)["countryVietnam"], 2)`, p = `r round(as.data.frame(summary(fit.country)[["coefficients"]])["countryVietnam", "Pr(>|z|)"], 3)`).

# Discussion
In this paper, we consider whether statistics of the language environment can account for cross-cultural differences in a classic similarity judgment paradigm, as an alternative to the view that members of different cultures vary in their conception of similarity.

We first tested the generality of a cultural account which holds that people from Western and East Asian cultures tend to conceive of similarity in more taxonomic and thematic ways, respectively, and respond accordingly in categorization tasks such as ours. While we managed to replicate the previously documented contrast between English speakers in the US and Mandarin Chinese speakers from East Asia (mainland China, Taiwan, Hong Kong, and Singapore), we do not extend this contrast to our sample of Vietnamese speakers in Vietnam and English speakers in the US. This finding suggests some limitations on the generality of this cultural account.

We did find some signatures of language specificity in our analysis, such as the large positive correlation between similarity judgments of each country and the respective corpus statistics, and how each corpus statistics are good predictors for corresponding country's similarity judgments. However, this is potentially due to the high correlation between corpus statistics of English, Vietnamese and Mandarin. We find even stronger evidence for consistency across the three groups, with substantive overlapping predictions across the corpus models, highly similar responding across the experiments, and a correspondingly high fit in cross-language comparisons between models and data.

```{r include=FALSE}
fit.country_no_triad <- glmer(responses_theme ~ country + (1 | subject), 
                              data = df_main_analysis, 
                              family = "binomial")

fit.country = glmer(responses_theme ~ country + (1 | subject) + (country | triad), 
                    data = df_main_analysis, 
                    family = "binomial")
summary(fit.country)

fit.no_triad_compare <- anova(fit.country, fit.country_no_triad, type = 3)
```

There are some suggestions that the current approach can predict triad-specific cross-cultural effects. First of all, an ANOVA model comparison showed that adding a random effect term for varying slope by country and varying intercept by triad to the model produces a significant better fit than the identical model without this random effect term included as a predictor ($\chi^2$(`r fit.no_triad_compare["fit.country", "Df"]`) = `r round(fit.no_triad_compare["fit.country", "Chisq"], 2)`, p < .001)

Anecdotally, we show below some examples of triads that show contrasting difference in the magnitude of difference in thematic responses between countries. As a review, the overall result across all triads showed that there was significant difference between US and China responding, and no significant differences between US and Vietnam or China and Vietnam responding. However, we observed that for the triad "cow-grass-chicken," there were significant differences between US and China, and US and Vietnam responding. There was no significant difference between China and Vietnam responding. For the triad "spoon-sugar-fork," there were significant difference between China and US, and China and Vietnam responding, but no significant difference between US and Vietnam. For the triad "hair-comb-beard," there were no significant differences pairwise across the three cultural contexts. This suggests that there are triad-specific cross-cultural effects in play. Beyond emphasizing the importance of including triad predictors as a random effect, this finding suggests that, firstly, future similar studies need to report triads that are used, as the triads used can affect results (for example, if a study only includes triads where China and US responding are significantly different, it would be more likely to conclude that Chinese and US cultures hold different notions of similarity). Secondly, that future studies can look more deeply into which groups of triads are driving the US-China responding difference. For example, triads belonging to different semantic neighborhoods might be influencing cross-cultural responding in different ways.

```{r include=FALSE}
df.country_item <- df_main_analysis %>%
  filter(triad == "hair")

plot.hair <- ggplot(df.country_item,
       mapping = aes(x = factor(country, levels=c("China", "US", "Vietnam")), 
                     y = responses_theme, 
                     color = factor(country, levels=c("China", "US", "Vietnam")))) +
  geom_jitter(stat = "identity", alpha  = .5) +
  labs(y = "Proportion Thematic Chosen (hair: beard / comb)",  
       x = "Country", 
       color = "Country") + 
  stat_summary(fun.data = "mean_cl_boot", 
               geom = "pointrange") + 
  scale_y_continuous(limits=c(0.0, 1.0), oob = scales::squish) + 
  scale_fill_manual(values=c("#D63230", "#1C77C3", "#F39237")) +  
  scale_color_manual(values=c("#D63230", "#1C77C3", "#F39237"))  + 
  theme(axis.title = element_text(size=rel(0.75)))
```

```{r include=FALSE}
df.country_item <- df_main_analysis %>%
  filter(triad == "spoon2")

plot.spoon2 <- ggplot(df.country_item,
       mapping = aes(x = factor(country, levels=c("China", "US", "Vietnam")), 
                     y = responses_theme, 
                     color = factor(country, levels=c("China", "US", "Vietnam")))) +
  geom_jitter(stat = "identity", alpha  = .5) +
  labs(y = "Proportion Thematic Chosen (spoon: fork / sugar)",  
       x = "Country", 
       color = "Country") + 
  stat_summary(fun.data = "mean_cl_boot", 
               geom = "pointrange") + 
  scale_y_continuous(limits=c(0.0, 1.0), oob = scales::squish) + 
  scale_fill_manual(values=c("#D63230", "#1C77C3", "#F39237")) +  
  scale_color_manual(values=c("#D63230", "#1C77C3", "#F39237")) + 
  theme(legend.position = "none") + 
  theme(axis.title = element_text(size=rel(0.75)))
```

```{r include = FALSE}
#show 1 triad

df.country_item <- df_main_analysis %>%
  filter(triad == "cow2")

df.country_item_summ <- df_main_analysis %>%
  group_by(triad, country) %>%
  summarize(theme_resp_percent = mean(responses_theme, na.rm = T)) %>%
  filter(triad == "cow2")

plot.cow2 <- ggplot(df.country_item,
       mapping = aes(x = factor(country, levels=c("China", "US", "Vietnam")), 
                     y = responses_theme, 
                     color = factor(country, levels=c("China", "US", "Vietnam")))) +
  geom_jitter(stat = "identity", alpha  = .5) +
  labs(y = "Proportion Thematic Chosen (cow: chicken / grass)",  
       x = "Country", 
       color = "Country") + 
  stat_summary(fun.data = "mean_cl_boot", 
               geom = "pointrange") + 
  scale_y_continuous(limits=c(0.0, 1.0), oob = scales::squish) + 
  scale_fill_manual(values=c("#D63230", "#1C77C3", "#F39237")) +  
  scale_color_manual(values=c("#D63230", "#1C77C3", "#F39237")) + 
  theme(legend.position = "none") + 
  theme(axis.title = element_text(size=rel(0.75)))
# 
# +  
#   geom_bar(data = df.country_item_summ, 
#            mapping = aes(x = factor(country, levels=c("China", "US", "Vietnam")), 
#                           y = theme_resp_percent, 
#                          color = factor(country, levels=c("China", "US", "Vietnam"))), 
#            stat='identity', alpha = .3, 
#            fill=c("#D63230", "#1C77C3", "#F39237"))
```

```{r echo=FALSE, warning = FALSE, fig.width=8, fig.cap="Anecdotal evidence of triad-specific effects. Cow-grass-chicken shows significant differences between US-China responding, and between US-Vietnam responding. Spoon-sugar-fork shows only a significant difference between US-China responding. Hair-comb-beard does not show any significant differences in pairwise comparisons across the three countries."}
plot.cow2 + plot.spoon2 + plot.hair + 
    plot_layout(ncol = 3)
```

We also identified some data quality / quantity issues that are an obstacle to modeling similarity in Vietnamese and Mandarin. As stated above, we were not able to find a Mandarin corpus with raw co-occurrences that contains similar magnitude of number of sentences as our English corpus (COCA). Additionally, we could only retrieve fastText word vectors for Vietnamese and Mandarin that are trained on both Common Crawl and Wikipedia. 63% of the articles on Vietnamese Wikipedia and 16% of the Chinese Wikipedia are bot translations from another language (compared to 3% of English Wikipedia). This would affect the quality of the word vectors trained on the Vietnamese and Chinese Wikipedia, potentially making them not reflecting the naturally-occurring lexical co-occurrence in the corresponding language.

Our findings raise additional questions for future work: if not differences in taxonomic vs. thematic responding, then what differences drive the relativity effects previous studies have observed? To what extent are the relativity effects driven by language, and to what extent by culture? @Ji2004 established that culture-aligned differences in this paradigm exist, even when the test language is held constant, concluding that “it is culture (independent of the testing language) that led to different grouping styles” in their study. Our data provide a cautionary note to this conclusion, suggesting that semantic representations in bilinguals (see @Francis2005 for a review) may have the potential to provide an offline account for cross-context differences in similarity judgments, independent of test language. However, there are still many open questions for this account. How do semantic associations guide categorization? Can they explain taxonomic-thematic differences of the type reported by @Ji2004 and others? Can we provide a more specific computational account than the simple frequency model tested here?

Despite these caveats, our findings here demonstrate the plausibility of an alternative perspective on cross-cultural accounts of language, thought, and similarity in the case of taxonomic and thematic reasoning: that it may be the input to similarity judgments, rather than the evaluative process or the conceptualization of similarity that produces variation in similarity reasoning across cultural and linguistic contexts. We hope this work provides a foundation for further research probing this question.

[^footnote]:While we discuss cross-cultural variability at the level of countries or larger world areas, these are not cultural monoliths. For convenience, we operationalize culture at the level of country, based on where participants were raised. It is an open question whether performance in our participant populations (of relatively young and well-educated adults) is representative of the broader country. This is especially true for societies with substantial ethnic and cultural variation such as the US. We expect that our data is likely to underestimate variation both within and between the countries we sample from.

\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup

\newpage
# Supplemental Information

hi
```{r echo=TRUE, fig.align="center", fig.cap=c("List of triads used"), fig.show="hold"}
#include_graphics(c("../../data/SI_triads/SI_triads_1.jpg"))
include_graphics(c("../../data/SI_triads/SI_triads_1.jpg",
                   "../../data/SI_triads/SI_triads_2.jpg",
                   "../../data/SI_triads/SI_triads_3.jpg",
                   "../../data/SI_triads/SI_triads_4.jpg",
                   "../../data/SI_triads/SI_triads_5.jpg"))
```

### 2022-09-28 code/3_analysis/3_analysis.Rmd
removed thesis sections

@@
   - id            : "1"
-    institution   : "Symbolic Systems Program"
+    institution   : "Psychology Department"
   - id            : "2"
-    institution   : "Stanford University"
-
-authornote: |
-    An honors thesis submitted to the program of Symbolic Systems of Stanford University in partial fulfillment of the requirements for the degree in Symbolic Systems. 
-    Honors Student: Khuyen Le. Honors Advisor: Mike Frank. Second Reader: Alex Carstensen
+    institution   : "University of California, San Diego"
 
@@
 ---
-
-\newpage
-To the Directors of the Program on Symbolic Systems:
-
-I certify that I have read the thesis of Khuyen Le in its final form for submission and have found it to be satisfactory for the degree of Bachelor of Science with Honors.
-
-Signed electronically
-
-06/04/2021
-
-Michael C. Frank
-
-Department of Psychology
-
-To the Directors of the Program on Symbolic Systems:
-
-I certify that I have read the thesis of Khuyen Le in its final form for submission and have found it to be satisfactory for the degree of Bachelor of Science with Honors.
-
-Signed electronically
-
-06/04/2021
-
-Alex Carstensen
-
-Department of Psychology
-
-\newpage
 
@@
 ```{r combine corpus and behavior data, include = F}
-source("../2_combine/2_combine.Rmd")
+#source("../2_combine/2_combine.Rmd")
+df <- read.csv("../../data/data_USCNVN_ENZHVI.csv")
 ```

### 2022-09-28 code/3_analysis/3_analysis_direction.Rmd
added new analysis on direction

--- 2022-09-28 code/3_analysis/3_analysis.Rmd
@@
----
-title             : "Is It Language or Is It Culture? Re-examining Cross-Cultural Similarity Judgments Using Lexical Co-Occurrence"
-shorttitle        : "Re-examining Cross-Cultural Similarity Judgments Using Lexical Co-Occurrence"
-
-author: 
-  - name          : "Khuyen Le"
-    affiliation   : "1,2"
-    corresponding : yes    # Define only one corresponding author
-    email         : "khuyenle@stanford.edu"
-
-affiliation:
-  - id            : "1"
-    institution   : "Psychology Department"
-  - id            : "2"
-    institution   : "University of California, San Diego"
-
-abstract: |
-  Is “cow” more closely related to “grass” or “chicken”?
-Speakers of different languages judge similarity in this context differently, but why?
-One possibility is that cultures co-varying with these languages induce variation in conceptualizations of similarity.
-Specifically, East Asian cultures may promote reasoning about thematic similarity, by which cow and grass are more related whereas Western cultures may bias similarity judgments toward taxonomic relations, like cow-chicken.
-This difference in notions of similarity is the consensus interpretation for cross-cultural variation in this paradigm.
-We consider, and provide evidence for, an alternative possibility, by which notions of similarity are equivalent across contexts, but the statistics of the environment vary.
-On this account, similarity judgments are guided by co-occurrence in experience, and observing or hearing about cows and grass or cows and chickens more often could induce preferences for the relevant grouping and account for apparent differences in notions of similarity across contexts.
-
-  <!-- https://tinyurl.com/ybremelq -->
-
-keywords          : "similarity, culture, language, semantics, lexical co-occurrence, variation"
-wordcount         : "150"
-
-bibliography      : ["r-references.bib", "references/references.bib"]
-
-floatsintext      : yes
-figurelist        : no
-tablelist         : yes
-footnotelist      : no
-linenumbers       : no
-mask              : no
-draft             : no
-header-includes:
-  - \raggedbottom
-
-documentclass     : "apa6"
-classoption       : "man"
-output            : papaja::apa6_pdf
-
----
-
 ```{r setup, echo = FALSE, include = FALSE}
@@
 
-# Introduction 
-By virtue of discrete words and grammatical features, language provides a categorical partition of our continuous experiences.
-Previous research has observed variation in the cognition of speakers of different languages corresponding to variation within semantic domains in these languages.
-This language-aligned variation has been observed in the domains of color [@Winawer2007], number [@Frank2008], and gender [@Boroditsky2003], among many others [@Wolff2011].
-Differences in cognition between speakers of different languages have often been used to suggest, explain, or exemplify cultural differences between speakers of those languages.
-Findings in studies of both language and of culture provide convergent evidence suggesting that variation across languages and cultures may shape broad variation in how people think about similarity between, for instance, different colors or objects.
-
-Looking beyond this domain-specific variation, we can also consider broader notions of similarity and relatedness between concepts across domains.
-The Free Association Norms [@FreeAssoc], for example, measures human judgment in semantic relatedness across domains and contexts.
-With the availability of large linguistic corpora, we can examine the similarity of concepts that are not circumscribed in individual domains (as color, number, and gender are), allowing us to answer more general questions about variation in cognition between speakers of different languages.
-By measuring the similarity between arbitrary words (as commonly done with lexical co-occurrence models), it may be possible to model the shape of similarity space in order to capture cross-linguistic and cross-cultural variation and provide a more general answer to the question of how language influences our conception of the world.
-
-Taxonomic and thematic similarity provide a convenient entry point to broader debates about cross-linguistic and cross-cultural variation in notions of similarity.
-Taxonomic categorization is based on the similarity of attributes, for example, similar perceptual properties, like shared color or shape, among objects.
-In contrast, thematic categorization is based on causal, spatial, and temporal relationships among objects [@Markman1984].
-To illustrate this point, if a participant is given the words “chicken” and “grass”, and asked which of those words are more closely related to the word “cow”, the pairing “chicken” - “cow” indicates a taxonomic match, whereas “grass” - “cow” indicates a thematic match.
-
-@Ji2004 found that preferences for taxonomic and thematic matches differ across culture, even when controlling for testing language and fluency.
-Specifically, Chinese participants made more thematic matches than taxonomic, while the converse was true for European Americans.
-This difference held even for Chinese participants tested in English (rather than Mandarin), suggesting that culture has an effect on the categorization strategy independent of the test language.
-However, the study also found an effect of language within Chinese participants from mainland China (when tested both in China and in the US): their preference for thematic categorization was significantly lower when tested in English compared to Mandarin Chinese.
-This suggests that test language also influences categorization strategies.
-Ji et al.
-characterize these results as demonstrating that culture (independent of language) leads to different styles of reasoning about similarity, whereas language serves as a “tuning” mechanism operating within a culturally-specific style, by activating representations corresponding to the language being used.
-
-## Cross-cultural variation in similarity
-The account that culture drives differences in categorization style has been one favored by other non-linguistic studies that use taxonomic vs thematic categorization to probe similarity judgment.
-A similar study to the aforementioned shows that when shown pictorial triads that represent words (i.e.
-pictures of an ant, a bee, and honey), Chinese children (9-10 years old) scored higher on thematic categorization compared to American children of the same age range, and vice versa for taxonomic categorization [@Chiu1972].
-Additionally, the cross-cultural differences in similarity judgment seem to persist even when the stimuli are more perceptual and less conceptual.
-@Norenzayan2002 conducted a study where participants are shown a target stimulus beneath two groups of 4 similar objects.
-The target shares a common feature with all the objects in one group, and only shares another one feature with each member of that group.
-Meanwhile, the target shares many features with 3 out of 4 members of the other group, but does not share any 1 feature in common with the entire group.
-The study showed that American participants judged the target to be more similar with the former group more often, and vice versa for Chinese participants.
-Since differences in categorization style persist with novel stimuli (as opposed to previously seen words or pictures of concepts), this suggests that participants from different cultural backgrounds are utilizing different reasoning strategies when making similarity judgments.
-
-Most commonly, researchers account for the differences in similarity judgment described above by differences in analytic vs holistic processing and in attention between Eastern and Western cultures.
-According to this framework, East Asians attend more to relationships between objects and context and reason more holistically, whereas Westerners attend more to objects and their properties, and reason analytically [@Nisbett2003].
-The analytic-holistic cultural difference in reasoning style has been observed in other non-linguistic tasks.
-For example, in a rod-and-frame test [@Witkin1954], East Asian (Taiwanese Chinese) participants are more influenced by the position of the surrounding frame than European Americans [@Ji2000], suggesting a higher level of sensitivity to context.
-East Asians (Koreans) have also been demonstrated to make more situational attributions for behaviors than European Americans, who make more dispositional attributions [@Choi1999], again suggesting higher sensitivity to context.
-When shown a complex scene with foreground and background information, Japanese participants made more statements about contextual information and relationships between objects than Americans did [@Masuda2001].
-Non-linguistic tasks have also shown that participants from Eastern and Western cultures differ in where they focus their visual attention.
-Another study presented American and Chinese participants with photographs of an object on a complex background [@Chua2005].
-They found that Chinese participants made more eye saccades to the background compared to American participants, and that American participants looked at the object more quickly.
-These cross-cultural differences in attention and analytic vs holistic processing are seen to map onto the cross-cultural differences in similarity judgment: because East Asian participants attend more to the context between objects and reason more holistically, it stands to reason that they would consider words that appear in the same context (i.e.
-thematically similar) to be more similar than taxonomically-similar words.
-
-Studies that explain these cross-cultural differences in reasoning and similarity judgment with a cultural framework often draw on social and historical contexts as the distal cause for these differences.
-For example, social structure and social practice can explain why different cultures develop different reasoning habits.
-To demonstrate this, researchers have looked at regions that are geographically close but with different social structures.
-@Kitayama2006 showed that Hokkaido Japanese demonstrated greater dispositional bias in attribution of behaviors compared to non-Hokkaido Japanese.
-The study suggested that this difference is correlated to the fact that Hokkaido was settled quite recently (mid-19th century) by pioneers from southern Japan, and thus its social practices (e.g.
-daily routines, child-rearing practices, and explicit education) would be influenced by the independent, goal-oriented characteristic of pioneer life.
-Another study showed that Northern Italians (more independent) categorized objects in a more taxonomic manner than Southern Italians (more interdependent) [@Knight2007].
-These studies, however, stopped short of providing a mechanism for the nature of the relationship between differences in social structures and differences in reasoning and similarity judgments.
-
-Another component of the social context explanation seems to be more tenable regarding the causal connection between cross-cultural differences in social practice and those in similarity judgments: that different patterns of attention are passed on by caregivers to children.
-@Fernald1993 found that American mothers labeled toys and pointed out their attributes more often than do Japanese mothers, while Japanese mothers tended to use the toys to engage their infants in social routines more often than American mothers.
-@Tardif1997 found that English-speaking caregivers produced more nouns than verbs in child-directed speech, while Mandarin-speaking caregivers emphasized verbs over nouns.
-Emphasis on labeling objects and focus on nouns over verbs might lead infants to attend to objects and their taxonomic categorizations, while emphasis on social practices and producing more verbs might direct infants' attention to the relationship between objects.
-Such differences in early-childhood environments could tune children’s attention to either object or context, and result in cross-cultural differences in similarity judgments (preferring either taxonomic or thematic, respectively) in adulthood.
-
-The above view explains cross-cultural differences in similarity judgment tasks as variation in the conceptualization of similarity itself.
-Alternatively, these judgments could be shaped by cross-cultural differences in the statistics of the environment, and accordingly the content of everyday experiences.
-Perhaps when confronted with the triad task, participants from all cultures follow the same process for reasoning about similarity, but rely on language or culture-specific inputs to this process.
-For example, it may be that Vietnamese participants are more likely to have knowledge of farming practices than Americans, and may associate cows and grass more strongly (as grass is the typical feed for cows in the small-scale family farming contexts common in Vietnam).
-Americans, on the other hand, may have strong associations between cows and chickens as a result of encountering them together in children’s books or petting zoo contexts.
-If we observe a difference in categorization between, say Vietnamese and US participants, perhaps they use the same procedure (considering similarity that is influenced by both taxonomic and thematic relations), but the inputs to this procedure differ between cultures, with Vietnamese participants exposed to more instances of “cow” and “grass” occurring together, compared to US participants.
-
-A study by @Miyamoto2006 lends support to this theory.
-The study randomly sampled scenes from different-sized cities in Japan and the US.
-Both subjective (judgment by American and East Asian college students) and objective (number of objects as counted by an automated program) showed that Japanese scenes were more complex and contained a larger number of objects than American scenes.
-This suggests that people living in Japan would more frequently encounter perceptual environments that contain more relationships between objects compared to those who live in the US.
-Japanese scenes therefore might encourage focus on the overall context, while American scenes might encourage focus on a few salient objects.
-
-Differences in environmental statistics extend beyond the immediate environment to cultural artifacts.
-@Tsai2007 showed that best-selling storybooks in the US contain more pictures of excited states (e.g.
-open-mouthed smiles, wide-open eyes) compared to best-selling storybooks in Taiwan, which contain more pictures of calm states.
-European American preschoolers also perceived excited states as happier and more desirable compared to calm states, and vice versa for Taiwanese Chinese preschoolers.
-The study also showed that there is a causal link between exposure to environmental statistics and personal preference: regardless of culture, exposure to exciting (vs.
-calm) storybooks increased children’s preference for the  corresponding activities.
-Broadly, this suggests that cultural artifacts or information in language (rather than direct, first-hand lived experiences) could be crucial factors in driving cross-cultural variation.
-
-## Language as a proxy of variation in experience
-While co-occurrences in experience are difficult to measure, co-occurrence in language can provide a rough proxy--and indeed, language may afford many of the “experiences” that people have with infrequently encountered items, like cows or helicopters.
-In the planned analyses, we will use co-occurrence in language as a proxy of cultural experience.
-This is a generalizing assumption, and while no linguistic corpus can be expected to fully capture a culture, and different linguistic corpora may capture different variables of a culture, using this proxy as a model of culture provides a conservative test of the hypothesis that differences in the input, rather than the process, of reasoning produces cultural variation in this task.
-This means that if such a model does work -- if linguistic co-occurrence can predict cultural variation in this similarity task without building differences in the decision process into the model -- it is relatively strong evidence that language alone (perhaps as a more easily observed source of information on broader cultural and ecological variation) may account for these cross-cultural differences in reasoning.[^footnote]
-
-Indeed, previous work suggests that using lexical co-occurrence as a proxy can be useful in thinking about similarity judgments.
-Natural language processing tasks have found that lexical co-occurrence is a good predictor for performance in similarity judgment tasks.
-@Griffiths2007 showed that a model that takes word-document co-occurrence as input can be used to predict word association and the effects of semantic association on a variety of linguistic tasks.
-Additionally, lexical semantic models that are constructed using lexical co-occurrence (as opposed to annotated relations) have been shown to perform well on predicting human judgments about similarity between word pairs that are either thematically or taxonomically related [@Rohde2006].
-
-Our current study will be using 2 measures of lexical co-occurrence: 1) raw lexical co-occurrences and 2) cosined distances of fastText word vectors.
-fastText is a system that uses lexical co-occurrence information to generate a vector representing each word in its lexicon [@Mikolov2018].
-fastText uses a continuous bag-of-words model, which takes into account a symmetric window of words surrounding the word in question and maximizes the log-likelihood of the probability of the word given its context.
-Calculating the cosine-similarity between word vectors from fastText gives us a score of how similar the contexts of these words are.
-Therefore, words that occur in the same context (high lexical co-occurrence) would have a larger cosine-similarity score.
-
-It must be noted that fastText supplements the lexical co-occurrence information by simultaneously training weight vectors for each position relative to the word in question, as well as adding sub-word information (bag-of-character n-gram vectors for each character forming the words).
-The similarity judgment prediction given by fastText may be more higher than a model using purely lexical co-occurrence information.
-However, models that use only lexical co-occurrence information (with or without a simple position weight system that gives more weight to words that are closer to the word in question) also perform well in similarity prediction tasks.
-For this study, due to the lack of large cleaned corpora for Mandarin and Vietnamese, we are leveraging fastText pre-trained models on the languages we are interested in @Grave2018.
-
-Systems like fastText and word2vec have been demonstrated to be good predictors for similarity judgments.
-@Liu2019 showed that fastText performed well as the data for a system matching responses in a knowledge base by how similar they are to a customer’s query.
-A study by @Jatnika2019 tested a word2vec model trained on the English wikipedia corpus against 353 word pairs labeled with similarity values based on human judgment.
-The word2vec model correlates moderately with human judgment.
-fastText has also been shown to be sensitive towards cultural effects on word meanings: @Thompson2020 applied fastText to language-specific Wikipedia corpus (among others) to generate a “semantic neighborhood” of 1010 meanings in different languages.
-The study showed that languages that are spoken by more similar cultures, more geographically proximate and/or historically related had more semantic neighborhoods that aligned.
-This is a proof of concept for our use of fastText in different languages with varying levels of relatedness.
-
-## The present study
-@Ji2004 showed the difference in similarity judgment between Chinese and European Americans (the former prefers thematic categorization while the latter prefers taxonomic).
-However, their evidence is not sufficient to conclude that it is culture that drives this difference, as their cross-cultural data is correlational.
-Furthermore, they have yet to rule out all mechanisms by which language could be relevant to the task.
-For example, their language manipulation (bilingual speakers from Mainland China making more taxonomic categorizations when tested in language) only points to an offline effect of language because it does not prevent participants from accessing linguistic representations.
-A stronger claim could have been made if verbal interference had been conducted, and if cross-cultural differences had remained.
-This would have been stronger in eliminating online effect of language as a potential cause for cross-cultural differences in similarity judgment.
-
-Additionally, outside of language, cross-cultural differences could come from a couple different mechanisms: @Ji2004 suggested that the notion of similarity is what varies across cultural groups, but it’s quite possible that similarity is regarded in the same way and it’s actually the input to this similarity judgment that varies across culture contexts.
-It might be possible to gain traction on possible mechanisms by examining whether variation in similarity judgments co-varies with environmental statistics that differ across the cultural and linguistic contexts.
-
-In this study, we ask whether variation in lexical co-occurrence can account for the cross-context (culture and language) differences observed in how people evaluate similarity.
-Firstly, we attempt to replicate @Ji2004 by running a study comparing English speakers in the US and Mandarin speakers in mainland China.
-Secondly, we evaluate whether the differences observed between English and Mandarin speakers’ similarity judgments also extend to comparisons between English and Vietnamese, by running a similar study between English speakers in the US and Vietnamese speakers in Vietnam.
-Vietnam is a Southeast Asian country that borders China and is historically greatly influenced by Chinese culture [@Hui2002].
-Therefore, it serves as a suitable cultural context to investigate whether the claim made by @Ji2004 and previous studies, that Eastern and Western cultures have different notions of similarity, extends beyond mainland China.
-
-We then ask to what extent similarity judgments show cross-context differences that align with co-occurrence patterns in participants’ languages.
-We would only see a main effect of cultural context if the notion of differing notions of similarity is driving these cross-cultural differences.
-Meanwhile, if we do see variation in responding trial-to-trial that tracks with lexical co-occurrence statistics (as a rough proxy combining both linguistic and cultural context), this would give traction to the view that cross-cultural notions of similarity might be similar, and it is environmental statistics that guide the differences in similarity judgments.
-To preview our results, we find that, while we do not see overall group differences (between the East Asian contexts and the US) in similarity, we do find language-specific co-occurrence can indeed explain cross-context differences in similarity judgments.
-In contrast to previous accounts, by which culture induces differing conceptions of similarity (varying between taxonomic and thematic), these findings provide an alternative, and more specific, account by which language may explain these cross-cultural differences without invoking variation in notions of similarity.
-
-# Methods 
-```{r get exclusion results from 1_exclusions.Rmd}
-source("../1_exclusions/1_exclusionsCN.Rmd")
-source("../1_exclusions/1_exclusionsUS.Rmd")
-source("../1_exclusions/1_exclusionsVN.Rmd")
-```
-
-```{r demog_E, TODO: move outside, include = F}
-demog <- c("demog-dropdown", "demog-multi-choice", "demog-free-response", "demog-multi-select")
-df.demog_E <- df.resp_E %>%
-  filter(trial_type %in% demog) 
-#write.csv(data_demog, "data_anon_demog_0201.csv")
-
-AGE = 97 #index for age answer
-GENDER = 115 #index for gender answer
-split_responses <- function(responses) {
-  responses <- as.character(responses)
-  response_list <- unlist(strsplit(responses, ',|:'))
-  response_list <- response_list[seq(1, length(response_list))]
-  response_list <- gsub("}", "", response_list)
-  response_list <- gsub("\"", "", response_list)
-  return(response_list)
-}
-
-get_age <- Vectorize(function(responses) {
-  responses <- split_responses(responses)
-  if(responses[AGE-1] != "A0") {warnings("cannot find age answer")}
-  else{return (responses[AGE])}
-})
-
-get_gender <- Vectorize(function(responses) {
-  responses <- split_responses(responses)
-  if(responses[GENDER-1] != "A1") {warnings("cannot find gender answer")}
-  else{return (responses[GENDER])}
-})
-
-df.age_gender_E <- df.demog_E %>%
-  filter(variable_type == "demog_age_gender_ethnic") %>%
-  select(subject, responses) %>%
-  mutate(age = as.numeric(get_age(responses))) %>%
-  mutate(age = as.numeric(age)) %>%
-  mutate(gender = get_gender(responses))
-
-df.age_gender_E_summ <- df.age_gender_E %>%
-  summarize(mean_age = mean(age), 
-            median_age = median(age), 
-            sd_age = sd(age))
-```
-
-```{r demog_V, TODO: move outside, include = F}
-demog <- c("demog-dropdown", "demog-multi-choice", "demog-free-response", "demog-multi-select")
-df.demog_V <- df.resp_V %>%
-  filter(trial_type %in% demog)
-
-AGE = 97 #index for age answer
-GENDER = 115 #index for gender answer
-split_responses <- function(responses) {
-  responses <- as.character(responses)
-  response_list <- unlist(strsplit(responses, ',|:'))
-  response_list <- response_list[seq(1, length(response_list))]
-  response_list <- gsub("}", "", response_list)
-  response_list <- gsub("\"", "", response_list)
-  return(response_list)
-}
-
-get_age <- Vectorize(function(responses) {
-  responses <- split_responses(responses)
-  if(responses[AGE-1] != "A0") {warnings("cannot find age answer")}
-  else{return (responses[AGE])}
-})
-
-get_gender <- Vectorize(function(responses) {
-  responses <- split_responses(responses)
-  if(responses[GENDER-1] != "A1") {warnings("cannot find gender answer")}
-  else{return (responses[GENDER])}
-})
-
-df.age_gender_V <- df.demog_V %>%
-  filter(variable_type == "demog_age_gender_ethnic") %>%
-  select(subject, responses) %>%
-  mutate(age = as.numeric(get_age(responses))) %>%
-  mutate(age = as.numeric(age)) %>%
-  mutate(gender = get_gender(responses))
-
-df.age_gender_V_summ <- df.age_gender_V %>%
-  summarize(mean_age = mean(age), 
-            median_age = median(age), 
-            sd_age = sd(age))
-```
-
-```{r demog_M, TODO: MOVE outside, include = F}
-demog <- c("demog-dropdown", "demog-multi-choice", "demog-free-response", "demog-multi-select")
-df.demog_M <- df.resp_M %>%
-  filter(trial_type %in% demog) 
-#write.csv(data_demog, "data_anon_demog_0201.csv")
-
-AGE = 97 #index for age answer
-GENDER = 115 #index for gender answer
-split_responses <- function(responses) {
-  responses <- as.character(responses)
-  response_list <- unlist(strsplit(responses, ',|:'))
-  response_list <- response_list[seq(1, length(response_list))]
-  response_list <- gsub("}", "", response_list)
-  response_list <- gsub("\"", "", response_list)
-  return(response_list)
-}
-
-get_age <- Vectorize(function(responses) {
-  responses <- split_responses(responses)
-  if(responses[AGE-1] != "A0") {warnings("cannot find age answer")}
-  else{return (responses[AGE])}
-})
-
-get_gender <- Vectorize(function(responses) {
-  responses <- split_responses(responses)
-  if(responses[GENDER-1] != "A1") {warnings("cannot find gender answer")}
-  else{return (responses[GENDER])}
-})
-
-df.age_gender_M <- df.demog_M %>%
-  filter(variable_type == "demog_age_gender_ethnic") %>%
-  select(subject, responses) %>%
-  mutate(age = as.numeric(get_age(responses))) %>%
-  mutate(age = as.numeric(age)) %>%
-  mutate(gender = get_gender(responses))
-
-df.age_gender_M_summ <- df.age_gender_M %>%
-  summarize(mean_age = mean(age), 
-            median_age = median(age), 
-            sd_age = sd(age))
-```
-## Participants
-We recruited `r length(unique(df.ppts_finished_E$subject))` participants from the US, `r length(unique(df.ppts_finished_V$subject))` participants from Vietnam, and `r length(unique(df.ppts_finished_M$subject))` participants from mainland China.
-US participants were recruited through snowball sampling seeded with Stanford email lists, Vietnam participants were recruited through snowball sampling seeded with Vietnam-based student groups on Facebook, and mainland China participants were recruited through snowball smapling seeded with group chats on WeChat.
-US participants were compensated with $5 gift certificates (USD), VN participants received 50,000₫ (VND) in phone credit, and mainland China participants received 25CNY through WeChat credit transfer.
-
-We excluded `r length(unique(df.ppts_finished_E$subject)) - length(unique(df.ppts_att_E$subject))` US participants, `r length(unique(df.ppts_finished_V$subject)) - length(unique(df.ppts_att_V$subject))` Vietnam participants, and `r length(unique(df.ppts_finished_M$subject)) - length(unique(df.ppts_att_M$subject))` China participants who did not answer all attention checks correctly.
-We followed 4 exclusion criteria that aim to retain only participants who are influenced by one culture: (1) non-native speakers of English and Vietnamese, respectively, (2) fluent in at least one of the other two study languages (Vietnamese for US participants, English for Vietnamese participants and Chinese participants), (3) have lived outside of the test country (US, Vietnam, or China) for more than two years, and (4) have significant international experience (more than 6 international experiences of 2 days or longer.) We did not use a particular criterion for a language if it would exclude 25% or more of any one sample.
-In this round of exclusion, we excluded `r length(unique(df.ppts_att_E$subject)) - length(unique(df.resp_E$subject))` US, `r length(unique(df.ppts_att_V$subject)) - length(unique(df.resp_V$subject))` Vietnam participants, and `r length(unique(df.ppts_att_M$subject)) - length(unique(df.resp_M$subject))` China participants.
-After these exclusions, the US sample included `r length(unique(df.resp_E$subject))` participants (`r df.age_gender_E %>% filter(gender == "Male") %>% count()`M, `r df.age_gender_E %>% filter(gender == "Female") %>% count()`F, `r df.age_gender_E %>% filter(gender == "Non-binary") %>% count()` non-binary, `r df.age_gender_E %>% filter(gender == "Decline to answer") %>% count()` other), with mean age = `r round(df.age_gender_E_summ$mean_age, 2)` (SD = `r round(df.age_gender_E_summ$sd_age, 2)`) and median age = `r df.age_gender_E_summ$median_age`.
-The Vietnam sample included `r length(unique(df.resp_V$subject))` participants (`r df.age_gender_V %>% filter(gender == "Nam") %>% count()`M, `r df.age_gender_V %>% filter(gender == "Nữ") %>% count()`F), with mean age = `r round(df.age_gender_V_summ$mean_age, 2)` (SD = `r round(df.age_gender_V_summ$sd_age, 2)`) and median age = `r df.age_gender_V_summ$median_age`.
-The China sample included `r length(unique(df.resp_M$subject))` participants (`r df.age_gender_M %>% filter(gender == "男性") %>% count()`M, `r df.age_gender_M %>% filter(gender == "女性") %>% count()`F), with mean age = `r round(df.age_gender_M_summ$mean_age, 2)` (SD = `r round(df.age_gender_M_summ$sd_age, 2)`) and median age = `r df.age_gender_M_summ$median_age`.
-
-Notably, we lost a majority of our Vietnam participants (more than 60%) in the attention check exclusion.
-One reason we suspect why this might have happened is because our Vietnam participants are less familiar with research surveys and attention check questions, and thus might have thought too much about the attention check questions.
-We carried out an exploratory analysis where we used a less stringent attention check exclusion (covered in the final part of the Results & Analysis section).
-To preview our findings for this analysis, we did not find any difference in significant results when compared with the main analysis.
-
-## Stimuli
-We adapted stimuli from previous studies to create a set of test triads consisting of a cue, with one thematic and one taxonomic match option.
-For example, “cow,” “grass,” and “chicken,” where “cow” is the cue, “grass” is the thematic match, and “chicken” the taxonomic match.
-We included 105 such triads, a superset including triads pulled from supplemental information and in-text examples across the literature, and others that we adapted or created (see SI for the full list of stimuli and sources).
-We selected triads on the basis of cultural familiarity in the US, Vietnam, and China.
-The triads were originally in English; they were translated to Vietnamese and Mandarin by a fluent bilingual speaker in each language.
-The translations were then checked for accuracy after backtranslation to English by another fluent bilingual in each language who was naive to the original English versions.
-
-Each participant completed all 105 triads in sets of 21 trials at a time (10 test triads, 10 filler triads, and 1 attention check per page), by selecting the match most related to the cue (“Which thing is most closely related to the bolded item?” or "Thu nào liên quan nhat voi thu đuoc in đam?").
-The test triads were presented with 105 filler triads mixed in, to obscure the taxonomic-thematic two-answer forced choice structure of the test stimuli and reduce the likelihood that participants would become aware of the design.
-The filler triads were groups of three semantically related words, but where the match options were not distinguished by thematic vs.
-taxonomic similarity, e.g., cue “bird” with match options “lizard” and “toad.” Additionally, we included 10 attention check trials, which were formatted like the test and filler triads but included an instruction instead of a cue item, e.g., “Choose wife” with match options “wife” and “husband.” In total, each participant completed 210 similarity judgments and 10 attention check questions, with triads presented in randomized orders that varied between subjects.
-
-## Corpus model 
-Our general approach is to build a model of similarity that is based on collocation counts in each language.
-
-### Raw lexical co-occurrences
-To give an intuition for our model, consider the cow-grass-chicken triad: we counted how many times “cow” and “grass” co-occur within a window of text in each corpus, and compare this to how many times “cow” and “chicken” co-occur.
-Our similarity prediction is then proportional to the relative frequency of these pairs.
-For example, if the thematic cow-grass match accounts for 30% of collocations for this triad (with cow-chicken making up the other 70%), then our model predicts, correspondingly, that 30% of responses to the triad will be grass, and the other 70% chicken.
-We then use a mixed-effects regression to evaluate how well each corpus collocate model predicts participants’ similarity judgments, across triads and languages.
-
-#### Collocate retrieval and coding
-For our English co-occurrence metric, we used the online interface of the Corpus of Contemporary American English [@COCA] to retrieve collocation counts.
-We recorded the raw count of times that any cue-match pair (e.g., cow-grass or cow-chicken) co-occur in a window of 19 words, which is the maximum window size in the online interface, and closest to the sentence co-occurrence metric in our VI corpus collocation counts.
-
-To determine Vietnamese co-occurrence, we used the raw frequency of sentence co-occurrences from a subset of the Vietnamese corpus in the Leipzig Corpora Collection [@VICorpus]; this corpus includes 70 million Vietnamese sentences, but our corpus data comes from a 1 million sentence subset for which co-occurrence counts are available for download.
-Vietnamese makes very frequent use of compositional morphology but the written language  uses spacing to delineate syllable boundaries rather than word boundaries.
-Accordingly, collocate searches returned instances of both target terms and many morphologically related, but distinct, words.
-We included in our counts any instances of the target term or close semantic neighbors containing the same morpheme(s) as long as they entailed a likely literal reference to the target term.
-For example, our search for collocates of the term “gà” (chicken) also returned “gà mái,” a distinct word for female chickens.
-Despite being a different word, “gà mái” both includes the morpheme for “chicken” and entails reference to a chicken.
-Accordingly, instances of both “gà” and “gà mái” were included in our collocate count for “chicken.” Some compounds do not meet this criteria, and were excluded from collocate counts.
-For example “trái cây” (tree.fruits) includes the same syllable as the word “cây” (tree), but refers to fruit that comes from trees, not the trees themselves, and was therefore excluded from our collocate counts for “tree.”
-
-We were unable to obtain a Mandarin corpus with similar number of sentences as the aforementioned English and Vietnamese corpora, hence we did not include any analysis based on raw lexical co-occurrences with Mandarin.
-
-#### Collocate similarity model
-From the raw co-occurrence counts of each triad, we calculated the thematic co-occurrence ratio as the number of thematic co-occurrences over the sum of thematic and taxonomic co-occurrences.
-We did this for both the English and Vietnamese corpus co-occurrence counts.
-In this way, we obtained predictions for 73 of 105 triads from the Vietnamese corpus and 104 of 105 triads from English.
-We therefore limited all analyses reported here to the subset of triads for which our corpus-based model can make meaningful predictions, meaning triads that have at least one non-zero collocate count (either thematic or taxonomic match).
-We replaced any remaining zero collocate counts with $\epsilon$ to account for sparsity in the corpus data.
-We then tested whether these simple relative frequency models predict US and VN responding.
-
-### Cosine distance of word vectors
-To give an intuition for our model, consider again the cow-grass-chicken triad: we retrieved word vectors for "cow" and "grass", and calculate the cosine distance between these vectors.
-Similarly, we retrieved vectors for "cow" and "chicken" and calculate the cosine distance between them.
-Our similarity prediction is then inversely proportional to the cosine distance of these pairs.
-This is because a larger cosine distance means the word vectors are further apart, and thus the words are less similar.
-For example, if the cosine distance of thematic cow-grass is 0.7 and the cosine distance of taxonomic cow-chicken is 0.3, then our model predicts, correspondingly, that 30% of responses to the triad will be grass, and the other 70% chicken.
-We then use a mixed-effects regression to evaluate how well each corpus model predicts participants’ similarity judgments, across triads and languages.
-
-#### Collocate retrieval
-We use the fastText pre-trained models of English, Mandarin, and Vietnamese in @Grave2018.
-These models are trained on Common Crawl and Wikipedia using We distribute pre-trained word vectors for 157 languages, trained on Common Crawl and Wikipedia using fastText.
-These models were trained using a Continuous Bag of Words (CBOW) with position-weights and a window of size 5.
-The models use character n-grams of length 5 and 10  negative examples.From the aforementioned models, we retrieve the word vectors (dimension 300) for each word we are interested in.
-
-#### Collocate similarity model
-From the word vectors, we calculated the cosine distance between each cue-thematic match (thematic cosine distance) and cue-taxonomic match (taxonomic cosine distance), using the spatial.distance.cosine function from the SciPy package [@2020SciPy].
-We then calculated the thematic cosine distance proportion as thematic cosine distance over the sum of taxonomic cosine distance and thematic cosine distance.
-We did this for all three corpora.
-We were able to obtain predictions for all triads in all languages.
-
-## Data analysis
-We used `r cite_r("r-references.bib")` for all our analyses.
-
-# Results
 ```{r combine corpus and behavior data, include = F}
-#source("../2_combine/2_combine.Rmd")
-df <- read.csv("../../data/data_USCNVN_ENZHVI.csv")
-```
+source("../2_combine/2_combine.R")
+df.basefreq <- read.csv("../../data/corpus/basefreq_EMV.csv")
+
+#no base frequencies for vietnamese yet
+df.basefreq <- df.basefreq %>% select(triad, 
+                                      cue_basefreq_E, tax_basefreq_E, theme_basefreq_E,
+                                      cue_basefreq_M, tax_basefreq_M, theme_basefreq_M, 
+                                      cue_basefreq_V, tax_basefreq_V, theme_basefreq_V)
+
+df <- left_join(df, df.basefreq, by = "triad")
+```
+
+## Does cue given match  predict behavior better than match given cue?
 

### 2022-09-28 code/2_combine/2_combine.R

@@ -1,0 +1,189 @@
+library("papaja")
+library("knitr") # for knitting things
+library("tidyverse") # for all things tidyverse
+library("car")
+library("lme4")
+library("patchwork")
+library("effsize")
+
+# Seed for random number generation-----
+set.seed(42)
+knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
+
+
+#loading responding data --------
+df.resp_E <- read.csv("../../data/dataUS_excl.csv") %>%
+  select(-X)
+
+df.resp_V <- read.csv("../../data/dataVN_excl.csv") %>%
+  select(-X)
+
+df.resp_M <- read.csv("../../data/dataCN_excl.csv") %>%
+  select(-X)
+
+#loading corpus data ---------
+df.corpus_E <- read.csv("../../data/corpus/corpusE.csv") %>%
+  rename(tax_frequency_E = tax.frequency,
+         theme_frequency_E = theme.frequency,
+         tax_cosine_E = Tax.cosine_dist, 
+         theme_cosine_E = Theme.cosine_dist,
+         tax_cosine_sim_E = Tax.cosine_sim,
+         theme_cosine_sim_E = Theme.cosine_sim,
+         tax_match_E = Tax.match,
+         theme_match_E = Theme.match, 
+         cue_E = Cue)
+
+df.corpus_V <- read.csv("../../data/corpus/corpusV.csv") %>%
+  rename(tax_frequency_V = tax.frequency,
+         theme_frequency_V = theme.frequency,
+         tax_cosine_V = Tax.cosine_dist, 
+         theme_cosine_V = Theme.cosine_dist,
+         tax_cosine_sim_V = Tax.cosine_sim,
+         theme_cosine_sim_V = Theme.cosine_sim,
+         tax_match_V = Tax.match,
+         theme_match_V = Theme.match, 
+         cue_V = Cue)
+
+df.corpus_M <- read.csv("../../data/corpus/corpusM.csv") %>%
+  rename(tax_frequency_M = tax.frequency,
+         theme_frequency_M = theme.frequency,
+         tax_cosine_M = Tax.cosine_dist, 
+         theme_cosine_M = Theme.cosine_dist,
+         tax_cosine_sim_M = Tax.cosine_sim,
+         theme_cosine_sim_M = Theme.cosine_sim,
+         tax_match_M = Tax.match,
+         theme_match_M = Theme.match, 
+         cue_M = Cue)
+
[…]

### 2022-11-30 code/0_demographic/0_demographic.Rmd
added a lot of analysis. prepared to move to coglink_cogsci

---
title: "Demographics"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("ggplot2")
library("tidyjson")
library("gtools")
library("dplyr")
library(lme4)
library(digest)
library(lmerTest)
```

```{r}
source("extract_demog.r")
```
### Getting raw data

```{r}
df.US <- read.csv("../../data/responding/data_US.csv") %>%
  select(-X)

df.CN <- read.csv("../../data/responding/data_CN.csv") %>%
  select(-X)

df.VN <- read.csv("../../data/responding/data_VN.csv") %>%
  select(-X)
```

```{r warning=F}
df.US_demog <- extract_demog(df.US, "US")
df.VN_demog <- extract_demog(df.VN, "VN")
df.CN_demog <- extract_demog(df.CN, "CN")
df.demog <- full_join(df.US_demog, df.VN_demog) %>%
  full_join(df.CN_demog)
write.csv(df.demog, "../../data/responding/data_demog.csv")
```

### 2022-11-30 code/2_combine/2_combine_assoc.Rmd
added a lot of analysis. prepared to move to coglink_cogsci

```{r setup, echo = FALSE, include = FALSE}
library("papaja")
library("knitr") # for knitting things
library("tidyverse") # for all things tidyverse
library("car")
library("lme4")
library("patchwork")
library("effsize")
```

```{r get association strengths and triad information}
df.assoc = read_delim("../../data/assoc_strengths.csv",delim='\t',quote = '',escape_backslash = F,escape_double = F) %>%
  select(cue, response, R123.Strength) %>%
  rename(assoc_strength = R123.Strength)
df.triad_E = read.csv("../../data/corpus/corpusE.csv") %>% 
  select(Cue_renamed, Cue, Tax.match, Theme.match) %>%
  rename(triad = Cue_renamed, 
         cue = Cue, 
         tax_match_E = Tax.match, 
         theme_match_E = Theme.match)

df.filler_E = read.csv("../../data/corpus/corpusEMV_filler.csv") %>% 
  select(Cue_renamed, Cue, Tax.match, Theme.match) %>%
  rename(triad = Cue_renamed, 
         cue = Cue, 
         tax_match_E = Tax.match, 
         theme_match_E = Theme.match)
```

```{r combine association strength and triad information}
df.triad_assoc <- left_join(df.triad_E, df.assoc,
                            by = c('cue'='cue', 'tax_match_E'='response')) %>%
  rename(tax_match_assoc_strength_E = assoc_strength)

df.triad_assoc <- left_join(df.triad_assoc, df.assoc,
                            by = c('cue'='cue', 'theme_match_E'='response')) %>%
  rename(theme_match_assoc_strength_E = assoc_strength)

#write.csv(df.triad_assoc, "../../data/corpus/corpusE_assoc_strength.csv", row.names = FALSE)
```

```{r}
triad_omit <- df.triad_assoc %>%
  filter(is.na(tax_match_assoc_strength_E) & is.na(theme_match_assoc_strength_E))
#write.csv(triad_omit$triad, "../../data/triads_omit_assoc.csv", row.names = FALSE)
```

```{r combine association strength data with responding data}
df = read.csv("../../data/data_USCNVN_ENZHVI.csv") %>%
  select(-X)

#df.triad_assoc <- read.csv("../../data/corpus/corpusE_assoc_strength.csv") %>%
#  select(-X)

df <- left_join(df, df.triad_assoc, 
                by = c("cue", "triad", "tax_match_E", "theme_match_E"))

write.csv(df, "../../data/data_USCNVN_ENZHVI_assoc_strength.csv", row.names = F)
```

### 2022-11-30 code/2_combine/2_combine_filler.Rmd
added a lot of analysis. prepared to move to coglink_cogsci

```{r setup, echo = FALSE, include = FALSE}
library("papaja")
library("knitr") # for knitting things
library("tidyverse") # for all things tidyverse
library("car")
library("lme4")
library("patchwork")
library("effsize")

# these options here change the formatting of how comments are rendered
opts_chunk$set(
  comment = "",
  results = "hold",
  fig.show = "hold")

# set the default ggplot theme 
theme_set(theme_classic())
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r loading data E, warning=FALSE, include=F}
df.resp_E <- read.csv("../../data/responding/dataUS_excl.csv") %>%
  select(-X)
```

```{r loading data V, include=F}
df.resp_V <- read.csv("../../data/responding/dataVN_excl.csv") %>%
  select(-X)
```

```{r loading data M, warning=FALSE, include=F}
df.resp_M <- read.csv("../../data/responding/dataCN_excl.csv") %>%
  select(-X)
```

```{r corpus filler just English, include = F}
df.corpus_filler <- read.csv("../../data/corpus/corpusEMV_filler.csv") %>%
  select(ends_with("_E") | ends_with("_M") | ends_with("_V")) %>%
  mutate(cue_id = cue_E)
```

```{r corpus - frequency, include = F}
#find triads_omit, used whenever analysis uses raw collocates 
corpus_E_omit <- df.corpus_filler %>% 
  filter(word1_match_frequency_E == 0 & word2_match_frequency_E == 0) # = 0 so no need to do this.
```

```{r full corpus, include=F}
#replacing any 0 raw counts with epsilon
df.corpus_filler <- df.corpus_filler %>%
    mutate(across(contains("frequency") , 
                  ~ ifelse(. == 0, .Machine$double.eps, .)))
```

```{r getting triads from the 3 languages, include = F}
#combine response and corpus data
df.filler_E <- df.resp_E %>%
  filter(stim_type == "filler",
         responses != "NA") %>%
  select(-variable_type, -trial_index, -trial_type, -stim_type) %>%
  mutate(language = "English", 
         country = "US")

df.filler_E <- left_join(df.filler_E, df.corpus_filler, 
                         by = c("cue" = "cue_E"), 
                         keep = TRUE)

df.filler_E <- df.filler_E %>%
  mutate(responses_word1 = ifelse(responses == word1_E, 1, 0))

```

```{r}
df.filler_M <- df.resp_M %>%
  filter(stim_type == "filler",
         responses != "NA") %>%
  select(-variable_type, -trial_index, -trial_type, -stim_type) %>%
  mutate(language = "Mandarin", 
         country = "China")

df.filler_M <- inner_join(df.filler_M, df.corpus_filler, 
                          by = c("cue" = "cue_M"), keep = TRUE)

df.filler_M <- df.filler_M %>%
  mutate(responses_word1 = ifelse(responses == word1_M, 1, 0))
```

```{r}
df.filler_V <- df.resp_V %>%
  filter(stim_type == "filler",
         responses != "NA") %>%
  select(-variable_type, -trial_index, -trial_type, -stim_type) %>%
  mutate(language = "Vietnamese", 
         country = "Vietnam")

df.filler_V <- inner_join(df.filler_V, df.corpus_filler, 
                          by = c("cue" = "cue_V"), keep = TRUE)

df.filler_V <- df.filler_V %>%
  mutate(responses_word1 = ifelse(responses == word1_V, 1, 0))
```

```{r}
df <- rbind(df.filler_E, df.filler_M)
df <- rbind(df, df.filler_V)

df <- df %>%
  mutate(word1_match_frequency_prop_E = 
           word1_match_frequency_E / (word1_match_frequency_E + word2_match_frequency_E),
         word1_match_frequency_prop_M = 
           word1_match_frequency_M / (word1_match_frequency_M + word2_match_frequency_M),
         word1_match_frequency_prop_V = 
           word1_match_frequency_V / (word1_match_frequency_V + word2_match_frequency_V))

write.csv(df, "../../data/data_filler_USCNVN_ENZHVI.csv")
```

### 2022-11-30 code/3_analysis/3_analysis_assoc.Rmd
added a lot of analysis. prepared to move to coglink_cogsci

```{r setup, echo = FALSE, include = FALSE}
library("papaja")
library("knitr") # for knitting things
library("tidyverse") # for all things tidyverse
library("car")
library("lme4")
library("patchwork")
library("effsize")
library("Hmisc")
library("dplyr")

# these options here change the formatting of how comments are rendered
opts_chunk$set(
  comment = "",
  results = "hold",
  fig.show = "hold")

# set the default ggplot theme 
theme_set(theme_classic())

r_refs("r-references.bib")
r_refs("references/packages.bib")

```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r read in data}
df <- read.csv("../../data/data_USCNVN_ENZHVI_assoc_strength.csv")
triads_omit_assoc <- read.csv("../../data/triads_omit_assoc.csv") %>%
  pull(x)
triads_omit_freq <- read.csv("../../data/triads_omit.csv") %>%
  pull(x)
```

```{r change NA to epsilon}
df <- df %>%
  mutate(tax_match_assoc_strength_E = ifelse(is.na(tax_match_assoc_strength_E), 
                                  .Machine$double.eps, tax_match_assoc_strength_E),
         theme_match_assoc_strength_E = ifelse(is.na(theme_match_assoc_strength_E), 
                                  .Machine$double.eps, theme_match_assoc_strength_E)) %>%
  mutate(theme_assoc_strength_prop_E = theme_match_assoc_strength_E / (theme_match_assoc_strength_E + tax_match_assoc_strength_E))
```

# Correlation between assoc strength prediction and response data
```{r}
df.cue_country_freq <- df %>%
  group_by(triad, country, theme_match_assoc_strength_E) %>%
  dplyr::summarize(emp_theme_prop = mean(responses_theme))
ggplot(data = df.cue_country_freq %>% filter(country == "US"), 
        mapping = aes(x = emp_theme_prop, 
                     y = theme_match_assoc_strength_E,
                     label = triad)) +
   geom_text() + 
   geom_smooth(method = "lm") +
   labs(x = "Proportion Thematic Chosen (US)", 
        y = "Proportion Thematic Predicted by Assoc Strength (English)") + 
  theme(axis.title = element_text(size=rel(0.75)))
```

# Does adding association improve the model?
```{r US responding predicted by each corpus model raw co-occurrences, warning=FALSE}
# English 
fit.EN_US = glmer(responses_theme ~ theme_freq_prop_E + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "US", 
                               !(triad %in% triads_omit_assoc),
                               !(triad %in% triads_omit_freq)), 
          family="binomial")
summary(fit.EN_US)
fit.EN_US.anova = Anova(fit.EN_US, type = 3)

fit.EN_US.anova

# English with association strengths
fit.EN_US_assoc = glmer(responses_theme ~ theme_freq_prop_E + theme_match_assoc_strength_E + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "US", 
                               !(triad %in% triads_omit_assoc),
                               !(triad %in% triads_omit_freq)), 
          family="binomial")
summary(fit.EN_US_assoc)
fit.EN_US_assoc.anova = Anova(fit.EN_US_assoc, type = 3)

fit.EN_US_assoc.anova

fit.EN_US_assoc_compare = anova(fit.EN_US, fit.EN_US_assoc, type = 3)
fit.EN_US_assoc_compare
```

Adding association strengths did not improve the model significantly.

# Does association strength predict response data?
```{r only association strengths}
# English 
fit.EN_US_assoc_only = glmer(responses_theme ~ theme_match_assoc_strength_E + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "US", 
                               !(triad %in% triads_omit_assoc),
                               !(triad %in% triads_omit_freq)), 
          family="binomial")
summary(fit.EN_US_assoc_only)
fit.EN_US_assoc_only.anova = Anova(fit.EN_US_assoc_only, type = 3)

fit.EN_US_assoc_only.anova

fit.EN_US_assoc_only_compare = anova(fit.EN_US, fit.EN_US_assoc_only, type = 3)
fit.EN_US_assoc_only_compare
```

Yes.

### 2022-11-30 code/3_analysis/3_analysis_compare_freq_cosine.Rmd
added a lot of analysis. prepared to move to coglink_cogsci

```{r setup, echo = FALSE, include = FALSE}
library("papaja")
library("knitr") # for knitting things
library("tidyverse") # for all things tidyverse
library("car")
library("lme4")
library("patchwork")
library("effsize")
library("Hmisc")
library("dplyr")

# these options here change the formatting of how comments are rendered
opts_chunk$set(
  comment = "",
  results = "hold",
  fig.show = "hold")

# set the default ggplot theme 
theme_set(theme_classic())

r_refs("r-references.bib")
r_refs("references/packages.bib")

```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r read in data}
df <- read.csv("../../data/data_USCNVN_ENZHVI.csv")
triads_omit_freq <- read.csv("../../data/triads_omit.csv") %>%
  pull(x)
```

# Comparing between 2 models for US repsonding
```{r US responding predicted by each corpus model raw co-occurrences, warning=FALSE}
# English 
fit.EN_US = glmer(responses_theme ~ theme_freq_prop_E + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "US", 
                               !(near(theme_frequency_E, .Machine$double.eps) & 
                                  near(tax_frequency_E, .Machine$double.eps))), 
          family="binomial")
summary(fit.EN_US)
fit.EN_US.anova = Anova(fit.EN_US, type = 3)

fit.EN_US.anova

fit.EN_US_cos = glmer(responses_theme ~ theme_cosine_prop_E + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "US", 
                               !(near(theme_match_frequency_E, .Machine$double.eps) & 
                                  near(tax_match_frequency_E, .Machine$double.eps))),

          family="binomial")
summary(fit.EN_US_cos)
fit.EN_US_cos.anova = Anova(fit.EN_US_cos, type = 3)
fit.EN_US_cos.anova

fit.EN_US_compare_freq_cos = anova(fit.EN_US, fit.EN_US_cos, type = 3)
fit.EN_US_compare_freq_cos

```

# Comparing between 2 models for VN responding
```{r US responding predicted by each corpus model raw co-occurrences, warning=FALSE}
# Vietnamese 
fit.VI_VN = glmer(responses_theme ~ theme_freq_prop_V + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "Vietnam", 
                               !(near(theme_frequency_V, .Machine$double.eps) & 
                                  near(tax_frequency_V, .Machine$double.eps))), 
          family="binomial")
summary(fit.VI_VN)
fit.VI_VN.anova = Anova(fit.EN_US, type = 3)

fit.VI_VN.anova

fit.VI_VN_cos = glmer(responses_theme ~ theme_cosine_prop_V + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "Vietnam", 
                               !(near(theme_frequency_V, .Machine$double.eps) & 
                                  near(tax_frequency_V, .Machine$double.eps))),

          family="binomial")
summary(fit.VI_VN_cos)
fit.VI_VN_cos.anova = Anova(fit.VI_VN_cos, type = 3)
fit.VI_VN_cos.anova

fit.VI_VN_compare_freq_cos = anova(fit.VI_VN, fit.VI_VN_cos, type = 3)
fit.VI_VN_compare_freq_cos

```

### 2022-11-30 code/3_analysis/3_analysis_demographics.Rmd
added a lot of analysis. prepared to move to coglink_cogsci

```{r setup, echo = FALSE, include = FALSE}
library("papaja")
library("knitr") # for knitting things
library("tidyverse") # for all things tidyverse
library("car")
library("lme4")
library("patchwork")
library("effsize")

# these options here change the formatting of how comments are rendered
opts_chunk$set(
  comment = "",
  results = "hold",
  fig.show = "hold")

# set the default ggplot theme 
theme_set(theme_classic())

r_refs("r-references.bib")
r_refs("references/packages.bib")

```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r get responses and demographics, eval=F, include = F}
df.response <- read.csv("../../data/data_USCNVN_ENZHVI.csv") %>%
  select(-X, -country)
df.demog <- read.csv("../../data/responding/data_demog.csv") %>%
  select(-X) %>%
  mutate(country = case_when(
    country == "CN" ~ "China",
    country == "VN" ~ "Vietnam", 
    country == "US" ~ "US",
    TRUE ~ country
  ))
```

```{r get cleaned demographics}
us_regions <- read_csv("../../data/us_regions.csv")
cn_regions <- read_csv("../../data/cn_regions.csv")

df.demog_cleaned <- df.demog %>%
  mutate(demog_response = case_when(
    demog_response %in% c("男性", "Nam") ~ "Male",
    demog_response %in% c("女性", "Nữ") ~ "Female",
    demog_response %in% c("非二元性别者", "Phi nhị nguyên giới / Phi nhị giới") ~ "Non-binary",
    demog_response %in% c("拒绝回答", "Từ chối trả lời ") ~ "Decline to answer",
    TRUE ~ demog_response
  )) %>% 
  mutate(demog_response = case_when(
    demog_response %in% c("是", "Đúng") ~ "Yes",
    demog_response %in% c("否", "Không") ~ "No",
    TRUE ~ demog_response
  )) %>% 
  #oversea experiences
  mutate(demog_response = case_when(
    demog_response %in% c("没有国际经历", "Chưa lần nào") ~ "No experiences",
    demog_response %in% c("一段国际经历", "1 lần") ~ "One experience",
    demog_response %in% c("两段国际经历", "2 lần") ~ "Two experiences",
    demog_response %in% c("三到五段国际经历", "3-5 lần") ~ "Three to five experiences",
    demog_response %in% c("六段或更多国际经历", "6 lần trở lên") ~ "Six or more experiences", 
    TRUE ~ demog_response
  )) %>% 
  mutate(demog_response = case_when(
    demog_response == "No experiences" ~ "0", 
    demog_response ==  "One experience" ~ "1",
    demog_response == "Two experiences" ~ "2",
    demog_response ==  "Three to five experiences" ~ "3",
    demog_response ==  "Six or more experiences" ~ "4",

    demog_response %in% c('8th grade/junior high or less', 
                          "九年级/初中及以下", 
                          "Lớp 9 / Trung học Cơ sở trở xuống") ~ "0",

    demog_response %in% c('Some high school', 
                           "上过一部分高中", 
                          "Một phần Trung học Phổ thông") ~ "1",

    demog_response %in% c('High school graduate/GED', 
                          "普通高中或职业高中毕业/高中等级学历", 
                          "Tốt nghiệp Trung học Phổ thông") ~"2",

    demog_response %in% c('One or more years of college, no degree', 
                          "一年或多年大学教育，无学位", 
                          "Một hoặc nhiều năm học Đại học, chưa tốt nghiệp") ~ "3",

    demog_response %in% c('Two-year college degree/vocational school', 
                          "大专学历") ~ "4", # not asked in vietnamese because not applicable.

    demog_response %in% c("Four-/Five-year college Bachelor's degree", 
                          "四年/五年制大学本科学位", 
                          "Tốt nghiệp Đại học") ~ "5",

     demog_response %in% c("At least some graduate school", 
                          "有过一些研究生经历", 
                          "Có kinh nghiệm học cao học") ~ "6",

    TRUE ~ demog_response
  )) 
toneless_dict <- pinyin::pydic("toneless")
df.demog_cleaned <- df.demog_cleaned %>%
  mutate(demog_response = case_when(
    country == "China" & demog_question == "state_grewup" ~ 
      as.character(pinyin::py(demog_response, toneless_dict, sep = "", other_replace = NULL)), 
    TRUE ~ demog_response
  )) %>% 
  mutate(demog_response = case_when(
    demog_response == "hena" ~ "Henan",
    demog_response == "jita" ~ "Others",
    demog_response == "haina" ~ "Hainan",
    demog_response == "huna" ~ "Hunan",
    demog_response == "andong" ~ "Guangdong",
    demog_response == "namenggu" ~ "Inner Mongolia",
    demog_response == "jinghai" ~ "Qinghai",
    demog_response == "angxi" ~ "Guangxi",
    demog_response == "anxi" ~ "Guangxi",
    demog_response == "yunna" ~ "Yunnan",
    demog_response == "山西" ~ "Shanxi",
    demog_response == "宁夏" ~ "Ningxia",
    demog_response == "陕西" ~ "Shaanxi",
    TRUE ~ str_to_title(demog_response)
  )) %>%
  pivot_wider(names_from = "demog_question", values_from = "demog_response")

df.demog_cleaned <- df.demog_cleaned %>%
  left_join(us_regions %>% 
              select(Region, Coast, State), by = c("state_grewup" = "State")
            ) %>% 
  left_join(cn_regions %>% 
              select(PercentPaddy, RiceCat, Province), 
            by = c("state_grewup" = "Province")) %>% 
    janitor::clean_names() %>% 
   mutate(rice_cat = case_when(rice_cat == 1 ~ "wheat", 
                              rice_cat == 2 ~ "rice"))
```

```{r}
df <- left_join(df.response, df.demog_cleaned, by = "subject") %>%
  mutate(age = as.numeric(as.character(age))) %>%
  mutate(objectiveses = as.numeric(as.character(objectiveses))) %>%
  mutate(subjectiveses = as.numeric(as.character(subjectiveses)))

triads_omit <- read.csv("../../data/triads_omit.csv")
```

# Age Effect
```{r age effect}
ggplot(df %>%
         group_by(subject, age, country) %>%
         summarise(responses_theme_mean = mean(responses_theme)),
       aes(x = age, y = responses_theme_mean, color = country)) +
  geom_point() + 
  facet_grid(~country)
```

### English
```{r US responding predicted by age, warning=FALSE}
# English 
fit.EN_US = glmer(responses_theme ~ theme_freq_prop_E + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "US", !(triad %in% triads_omit)), 
          family="binomial")

fit.EN_US_age = glmer(responses_theme ~ theme_freq_prop_E + age + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "US", !(triad %in% triads_omit)), 
          family="binomial")
summary(fit.EN_US_age)
fit.EN_US_age.anova = Anova(fit.EN_US_age, type = 3)
fit.EN_US_age.anova

anova(fit.EN_US, fit.EN_US_age)
```

### Mandarin
```{r CN responding predicted by age, warning=FALSE}
fit.ZH_CN = glmer(responses_theme ~ theme_freq_prop_M + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "China", !(triad %in% triads_omit)), 
          family="binomial")

fit.ZH_CN_age = glmer(responses_theme ~ theme_freq_prop_M + age + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "China", !(triad %in% triads_omit)), 
          family="binomial")
summary(fit.ZH_CN_age)
fit.ZH_CN_age.anova = Anova(fit.ZH_CN_age, type = 3)
fit.ZH_CN_age.anova

anova(fit.ZH_CN, fit.ZH_CN_age)
```

### Vietnamese
```{r VN responding predicted by age, warning=FALSE}
fit.VI_VN = glmer(responses_theme ~ theme_freq_prop_V + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "Vietnam", !(triad %in% triads_omit)), 
          family="binomial")

fit.VI_VN_age = glmer(responses_theme ~ theme_freq_prop_V + age + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "Vietnam", !(triad %in% triads_omit)), 
          family="binomial")
summary(fit.VI_VN_age)
fit.VI_VN_age.anova = Anova(fit.VI_VN_age, type = 3)
fit.VI_VN_age.anova

anova(fit.VI_VN, fit.VI_VN_age)
```
No effect of age when added to the base model of all cultures.

# Gender Effect
```{r gender effect}
ggplot(df %>%
         group_by(subject, gender, country) %>%
         summarise(responses_theme_mean = mean(responses_theme)),
       aes(x = gender, y = responses_theme_mean, fill = country)) +
  stat_summary(fun.y = mean, geom = "bar") + 
  stat_summary(fun.data = mean_se, geom = "errorbar") + 
  geom_jitter(alpha = .5) + 
  facet_grid(~country)
```

### English
```{r US responding predicted by gender, warning=FALSE}
# English 
fit.EN_US = glmer(responses_theme ~ theme_freq_prop_E + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "US", !(triad %in% triads_omit), 
                               gender != "Decline to answer"), 
          family="binomial")

fit.EN_US_gender = glmer(responses_theme ~ theme_freq_prop_E + gender + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "US", !(triad %in% triads_omit),
                               gender != "Decline to answer"), 
          family="binomial")
summary(fit.EN_US_gender)
fit.EN_US_gender.anova = Anova(fit.EN_US_gender, type = 3)
fit.EN_US_gender.anova

anova(fit.EN_US, fit.EN_US_gender)
```

### Mandarin
```{r CN responding predicted by gender, warning=FALSE}
fit.ZH_CN = glmer(responses_theme ~ theme_freq_prop_M + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "China", !(triad %in% triads_omit),
                               gender != "Decline to answer"), 
          family="binomial")

fit.ZH_CN_gender = glmer(responses_theme ~ theme_freq_prop_M + gender + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "China", !(triad %in% triads_omit),
                               gender != "Decline to answer"), 
          family="binomial")
summary(fit.ZH_CN_gender)
fit.ZH_CN_gender.anova = Anova(fit.ZH_CN_gender, type = 3)
fit.ZH_CN_gender.anova

anova(fit.ZH_CN, fit.ZH_CN_gender)
```

### Vietnamese
```{r VN responding predicted by gender, warning=FALSE}
fit.VI_VN = glmer(responses_theme ~ theme_freq_prop_V + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "Vietnam", !(triad %in% triads_omit),
                               gender != "Decline to answer"), 
          family="binomial")

fit.VI_VN_gender = glmer(responses_theme ~ theme_freq_prop_V + gender + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "Vietnam", !(triad %in% triads_omit),
                               gender != "Decline to answer"), 
          family="binomial")
summary(fit.VI_VN_gender)
fit.VI_VN_gender.anova = Anova(fit.VI_VN_gender, type = 3)
fit.VI_VN_gender.anova

anova(fit.VI_VN, fit.VI_VN_gender)
```

No effects of gender either.

# Rice / wheat areas

```{r, warning = FALSE}
ggplot(df %>%
         filter(country == "China") %>%
         group_by(subject, rice_cat) %>%
         summarise(responses_theme_mean = mean(responses_theme)),
       aes(x = rice_cat, y = responses_theme_mean, fill = rice_cat)) +
  stat_summary(fun.y = mean, geom = "bar") + 
  stat_summary(fun.data = mean_se, geom = "errorbar") + 
  geom_jitter(alpha = .5)
```
```{r CN responding predicted by rice/wheat, warning=FALSE}
fit.ZH_CN = glmer(responses_theme ~ theme_freq_prop_M + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "China", !(triad %in% triads_omit)), 
          family="binomial")

fit.ZH_CN_ricewheat = glmer(responses_theme ~ theme_freq_prop_M + rice_cat + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "China", !(triad %in% triads_omit)), 
          family="binomial")
summary(fit.ZH_CN_ricewheat)
fit.ZH_CN_ricewheat.anova = Anova(fit.ZH_CN_ricewheat, type = 3)
fit.ZH_CN_ricewheat.anova
anova(fit.ZH_CN, fit.ZH_CN_ricewheat)

fit.ZH_CN_paddy = glmer(responses_theme ~ theme_freq_prop_M + percent_paddy + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "China", !(triad %in% triads_omit)), 
          family="binomial")
summary(fit.ZH_CN_paddy)
fit.ZH_CN_paddy.anova = Anova(fit.ZH_CN_paddy, type = 3)
fit.ZH_CN_paddy.anova
anova(fit.ZH_CN, fit.ZH_CN_paddy)
```

No effect of rice/wheat, or percentage paddy.

# US Regions
```{r, warning = FALSE}
ggplot(df %>%
         filter(country == "US") %>%
         group_by(subject, region, coast) %>%
         summarise(responses_theme_mean = mean(responses_theme)),
       aes(x = region, y = responses_theme_mean, fill = region)) +
  stat_summary(fun.y = mean, geom = "bar") + 
  stat_summary(fun.data = mean_se, geom = "errorbar") + 
  geom_jitter(alpha = .5)

ggplot(df %>%
         filter(country == "US") %>%
         group_by(subject, region, coast) %>%
         summarise(responses_theme_mean = mean(responses_theme)),
       aes(x = coast, y = responses_theme_mean, fill = coast)) +
  stat_summary(fun.y = mean, geom = "bar") + 
  stat_summary(fun.data = mean_se, geom = "errorbar") + 
  geom_jitter(alpha = .5)
```

```{r US responding predicted by region, warning=FALSE}
fit.EN_US = glmer(responses_theme ~ theme_freq_prop_E + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "US", !(triad %in% triads_omit),
                               !is.na(region)), 
          family="binomial")

fit.EN_US_region = glmer(responses_theme ~ theme_freq_prop_E + region + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "US", !(triad %in% triads_omit), 
                               !is.na(region)), 
          family="binomial")
summary(fit.EN_US_region)
fit.EN_US_region.anova = Anova(fit.EN_US_region, type = 3)
fit.EN_US_region.anova

anova(fit.EN_US, fit.EN_US_region)

fit.EN_US_coast = glmer(responses_theme ~ theme_freq_prop_E + coast + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "US", !(triad %in% triads_omit), 
                               !is.na(region)), 
          family="binomial")
summary(fit.EN_US_coast)
fit.EN_US_coast.anova = Anova(fit.EN_US_coast, type = 3)
fit.EN_US_coast.anova

anova(fit.EN_US, fit.EN_US_coast)
```

No effect of region.

# SES Effect

```{r ses effect}
ggplot(df %>%
         group_by(subject, objectiveses, country) %>%
         summarise(responses_theme_mean = mean(responses_theme)),
       aes(x = objectiveses, y = responses_theme_mean, fill = objectiveses)) +
  stat_summary(fun.y = mean, geom="bar") + 
  stat_summary(fun.data = mean_se, geom = "errorbar") + 
  geom_jitter(alpha = .5) + 
  facet_grid(~country)
```
```{r}
ggplot(df %>%
         group_by(subject, subjectiveses, country) %>%
         summarise(responses_theme_mean = mean(responses_theme)),
       aes(x = subjectiveses, y = responses_theme_mean, fill = subjectiveses)) +
  stat_summary(fun.y = mean, geom="bar") + 
  stat_summary(fun.data = mean_se, geom = "errorbar") + 
  geom_jitter(alpha = .5) + 
  facet_grid(~country)
```
# English
```{r US responding predicted by ses, warning=FALSE}
# English 
fit.EN_US = glmer(responses_theme ~ theme_freq_prop_E + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "US", !(triad %in% triads_omit)), 
          family="binomial")

fit.EN_US_subjses = glmer(responses_theme ~ theme_freq_prop_E + subjectiveses + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "US", !(triad %in% triads_omit)), 
          family="binomial")
summary(fit.EN_US_subjses)
fit.EN_US_subjses.anova = Anova(fit.EN_US_subjses, type = 3)
fit.EN_US_subjses.anova

anova(fit.EN_US, fit.EN_US_subjses)

fit.EN_US_objses = glmer(responses_theme ~ theme_freq_prop_E + objectiveses + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "US", !(triad %in% triads_omit)), 
          family="binomial")
summary(fit.EN_US_objses)
fit.EN_US_objses.anova = Anova(fit.EN_US_objses, type = 3)
fit.EN_US_objses.anova

anova(fit.EN_US, fit.EN_US_objses)
```
NO effect of subjective ses, 
YES effect of objective ses! (higher objective ses --> more taxonomic)

### Mandarin
```{r CN responding predicted by ses, warning=FALSE}
fit.ZH_CN = glmer(responses_theme ~ theme_freq_prop_M + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "China", !(triad %in% triads_omit)), 
          family="binomial")

fit.ZH_CN_subjses = glmer(responses_theme ~ theme_freq_prop_M + subjectiveses + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "China", !(triad %in% triads_omit)), 
          family="binomial")
summary(fit.ZH_CN_subjses)
fit.ZH_CN_subjses.anova = Anova(fit.ZH_CN_subjses, type = 3)
fit.ZH_CN_subjses.anova
anova(fit.ZH_CN, fit.ZH_CN_subjses)

fit.ZH_CN_objses = glmer(responses_theme ~ theme_freq_prop_M + objectiveses + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "China", !(triad %in% triads_omit)), 
          family="binomial")
summary(fit.ZH_CN_objses)
fit.ZH_CN_objses.anova = Anova(fit.ZH_CN_objses, type = 3)
fit.ZH_CN_objses.anova
anova(fit.ZH_CN, fit.ZH_CN_objses)
```
No effect.

### Vietnamese
```{r VN responding predicted by ses, warning=FALSE}
fit.VI_VN = glmer(responses_theme ~ theme_freq_prop_V + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "Vietnam", !(triad %in% triads_omit)), 
          family="binomial")

fit.VI_VN_subjses = glmer(responses_theme ~ theme_freq_prop_V + subjectiveses + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "Vietnam", !(triad %in% triads_omit)), 
          family="binomial")
summary(fit.VI_VN_subjses)
fit.VI_VN_subjses.anova = Anova(fit.VI_VN_subjses, type = 3)
fit.VI_VN_subjses.anova

anova(fit.VI_VN, fit.VI_VN_subjses)

fit.VI_VN_objses = glmer(responses_theme ~ theme_freq_prop_V + objectiveses + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "Vietnam", !(triad %in% triads_omit)), 
          family="binomial")
summary(fit.VI_VN_objses)
fit.VI_VN_objses.anova = Anova(fit.VI_VN_objses, type = 3)
fit.VI_VN_objses.anova

anova(fit.VI_VN, fit.VI_VN_objses)
```
No effect.

### 2022-11-30 code/3_analysis/3_analysis_direction.Rmd
added a lot of analysis. prepared to move to coglink_cogsci

@@
 ```{r combine corpus and behavior data, include = F}
-source("../2_combine/2_combine.R")
+source("../2_combine/2_combine.R") # include triad_omits. TODO: Find a way to also save this.
+```
+
+```{r incorporate base freq, eval=F, include = F}
+df <- read.csv("../../data/data_USCNVN_ENZHVI.csv")
 df.basefreq <- read.csv("../../data/corpus/basefreq_EMV.csv")
@@
 df <- left_join(df, df.basefreq, by = "triad")
+
+#replacing any 0 raw counts with epsilon
+df <- df %>%
+  mutate(cue_basefreq_E = ifelse(cue_basefreq_E == 0, 
+                                  .Machine$double.eps, cue_basefreq_E),
+         tax_basefreq_E = ifelse(tax_basefreq_E == 0, 
+                                  .Machine$double.eps, tax_basefreq_E),
+         theme_basefreq_E = ifelse(theme_basefreq_E == 0, 
+                                  .Machine$double.eps, theme_basefreq_E),
+         cue_basefreq_M = ifelse(cue_basefreq_M == 0, 
+                                  .Machine$double.eps, cue_basefreq_M), 
+         tax_basefreq_M = ifelse(tax_basefreq_M == 0, 
+                                  .Machine$double.eps, tax_basefreq_M),
+         theme_basefreq_M = ifelse(theme_basefreq_M == 0, 
+                                  .Machine$double.eps, theme_basefreq_M),
+         cue_basefreq_V = ifelse(cue_basefreq_V == 0, 
+                                  .Machine$double.eps, cue_basefreq_V),
+         tax_basefreq_V = ifelse(tax_basefreq_V == 0, 
+                                  .Machine$double.eps, tax_basefreq_V), 
+         theme_basefreq_V = ifelse(theme_basefreq_V == 0, 
+                                  .Machine$double.eps, theme_basefreq_V)
+         )
 ```
 
-## Does cue given match  predict behavior better than match given cue?
+```{r calculate cue given match and match given cue proportions, include = F, eval = F}
+# for now, calculate specifically in terms of which one they have answered? (theme vs match)
+# but maybe do for all languages? 
+calculate_cue_given_match <- function(responses_theme, language,
+                                      tax_basefreq_E, theme_basefreq_E,
+                                      theme_frequency_E, tax_frequency_E,
+                                      tax_basefreq_M, theme_basefreq_M,
+                                      theme_frequency_M, tax_frequency_M,
+                                      tax_basefreq_V, theme_basefreq_V,
+                                      theme_frequency_V, tax_frequency_V) {
+    ifelse(language == "English",
+           ifelse(responses_theme == 1, theme_frequency_E / theme_basefreq_E, tax_frequency_E / tax_basefreq_E),
+           ifelse(language == "Mandarin",
+                  ifelse(responses_theme == 1, theme_frequency_M / theme_basefreq_M, tax_frequency_M / tax_basefreq_M),
+                  NA))
+}
 
-## Do we extend previous work reporting a preference for taxonomic matching in the US and thematic matching in Asia?
+calculate_match_given_cue <- function(responses_theme, language,
+                                      cue_basefreq_E, theme_frequency_E, tax_frequency_E,
+                                      cue_basefreq_M, theme_frequency_M, tax_frequency_M,
+                                      cue_basefreq_V, theme_frequency_V, tax_frequency_V) {
+    ifelse(language == "English",
+           ifelse(responses_theme == 1, theme_frequency_E / cue_basefreq_E, tax_frequency_E / cue_basefreq_E),
+           ifelse(language == "Mandarin",
+                  ifelse(responses_theme == 1, theme_frequency_M / cue_basefreq_M, tax_frequency_M / cue_basefreq_M),
+                  NA))
+}
 
-```{r warning=FALSE, include=FALSE, paged.print=TRUE}
-df.country <- df %>%
-  group_by(subject, country) %>%
-  summarize(theme_resp_percent = mean(responses_theme, na.rm = T))
+df <- df %>% mutate(cue_given_match = calculate_cue_given_match(
+                                          responses_theme, language,
+                                          tax_basefreq_E, theme_basefreq_E,
+                                          theme_frequency_E, tax_frequency_E,
+                                          tax_basefreq_M, theme_basefreq_M,
+                                          theme_frequency_M, tax_frequency_M,
+                                          tax_basefreq_V, theme_basefreq_V,
+                                          theme_frequency_V, tax_frequency_V),
+                    match_given_cue = calculate_match_given_cue(
+                                          responses_theme, language,
+                                          cue_basefreq_E, theme_frequency_E, tax_frequency_E,
+                                          cue_basefreq_M, theme_frequency_M, tax_frequency_M,
+                                          cue_basefreq_V, theme_frequency_V, tax_frequency_V))
 
-df.country_sum <- df.country %>%
-  group_by(country) %>%
-  summarize(mean_theme_resp_percent = mean(theme_resp_percent), 
-            sd_theme_resp_percent = sd(theme_resp_percent))
-
-fit.country = glmer(responses_theme ~ country + (1 | subject) + (country | triad), 
-                    data = df, 
-                    family = "binomial")
-summary(fit.country) 
-fit.country.anova = Anova(fit.country, type=3)
-
-fit.country_EN_VN = glmer(responses_theme ~ country + (1 | subject) + (country | triad), 
-                    data = df %>% filter(country != "China"),
-                    family = "binomial")
-summary(fit.country_EN_VN) 
-```
-The group means of proportion of thematic response in mainland China is the highest (M = `r round((df.country_sum %>% filter(country == "China"))$mean_theme_resp_percent, 2)`, SD = `r round((df.country_sum %>% filter(country == "China"))$sd_theme_resp_percent, 2)`), followed by the groups means in Vietnam (M = `r round((df.country_sum %>% filter(country == "Vietnam"))$mean_theme_resp_percent, 2)`, SD = `r round((df.country_sum %>% filter(country == "Vietnam"))$sd_theme_resp_percent, 2)`), which is slightly higher than that of the US (M = `r round((df.country_sum %>% filter(country == "US"))$mean_theme_resp_percent, 2)`, SD = `r round((df.country_sum %>% filter(country == "US"))$sd_theme_resp_percent, 2)`).
-
-```{r echo=FALSE, warning=FALSE, fig.cap="Proportion of thematic responses by country.
-Only US-China responding comparison shows a siginficant difference.
-We could not extend this to US-Vietnam responding comparison."}
-
-#show violin plot
-ggplot(df.country,
-       mapping = aes(x = factor(country, levels=c("China", "US", "Vietnam")), 
-                     y = theme_resp_percent, 
-                     color = factor(country, levels=c("China", "US", "Vietnam")))) +
-  geom_violin() +
-  geom_jitter(height = 0, 
-              alpha = 0.3) +  
-  stat_summary(fun.data = "mean_cl_boot", 
-               geom = "pointrange") + 
-  labs(y = "Proportion Thematic Chosen", 
-       x = "Country", 
-       color = "Country") + 
-  scale_color_manual(values=c("#D63230", "#1C77C3", "#F39237"))
+write.csv(df, "../../data/data_USCNVN_ENZHVI_direction.csv")
 ```
 
-```{r correlation of country response, echo=FALSE, warning=FALSE}
-#US-China, US-Vietnam, China-Vietnam
-df.triad_country <- df %>%
-  group_by(triad, country) %>%
-  summarize(emp_theme_prop = mean(responses_theme))
+## Does match given cue (intuitive) predict behavior better than cue given match (non-intuitive)?
 
-df.triad_country <- pivot_wider(data = df.triad_country, 
-                                names_from = country, 
-                                values_from = emp_theme_prop)
-plotUSCN = ggplot(data = df.triad_country,
-                  mapping = aes(x = US, 
-                                y = China, 
-                                label = triad)) +
-   geom_text() + 
-   geom_smooth(method = "lm") +
-   labs(x = "Proportion Thematic Chosen (US)", 
-        y = "Proportion Thematic Chosen (China)") + 
-   xlim(0, 1) + 
-   ylim(0, 1) + 
-  theme(axis.title = element_text(size=rel(0.75)))
-
-plotUSVN = ggplot(data = df.triad_country,
-                  mapping = aes(x = US, 
-                                y = Vietnam, 
-                                label = triad)) +
-   geom_text() + 
-   geom_smooth(method = "lm") +
-   labs(x = "Proportion Thematic Chosen (US)", 
-        y = "Proportion Thematic Chosen (Vietnam)") + 
-   xlim(0, 1) + 
-   ylim(0, 1)  + 
-  theme(axis.title = element_text(size=rel(0.75)))
-
-plotCNVN = ggplot(data = df.triad_country,
-                  mapping = aes(x = Vietnam,
-                                y = China, 
-                                label = triad)) +
-   geom_text() + 
-   geom_smooth(method = "lm") +
-   labs(x = "Proportion Thematic Chosen (Vietnam)", 
-        y = "Proportion Thematic Chosen (China)") + 
-   xlim(0, 1) + 
-   ylim(0, 1)  + 
-  theme(axis.title = element_text(size=rel(0.75)))
-
-corr.USCN = apa_print(cor.test(df.triad_country$US, 
-                  df.triad_country$China, na.rm=T))
-
-corr.USVN = apa_print(cor.test(df.triad_country$US, 
-                  df.triad_country$Vietnam, na.rm=T))
-
-corr.CNVN = apa_print(cor.test(df.triad_country$China, 
-                  df.triad_country$Vietnam, na.rm=T))
+We are trying to figure out if people's process is more well-modeled by match given cue or cue given match.
+In other words, are people looking at the cue ("cow") and then judging the matches ("chicken" or "grass")?
+Or are people looking at the matches first ("chicken") and then seeing if it matches with the cue ("cow") well enough?
+```{r loading in the csv with direction so we dont need to go through the previous section, include =F}
+df <- read.csv("../../data/data_USCNVN_ENZHVI_direction.csv")
 ```
 
-```{r warning = F, fig.width = 8, fig.cap="Correlation between proportion thematic chosen by US-China participants, US-Vietnam participants, and China-Vietnam participants.
-All three comparisons show strong correlation, suggesting a strong signal of universality across cultural contexts regarding similarity judgments"}
-plotUSCN + plotUSVN + plotCNVN +
-  plot_layout(ncol = 3)
-```
+We need to run the baseline model again (corresponding corpora predicting responding behavior). And then compare that to the new updated models.
 
-With a Pearson correlation test, we observed high correlations between thematic responding across all three countries.
-The proportion of US thematic responding is strongly correlated with thematic responding in China, `r corr.USCN$full_result`.
-The proportion of US thematic responding is strongly correlated with thematic responding in Vietnam, `r corr.USVN$full_result`.
-Likewise, the proportion of China thematic response is strongly correlated with thematic responding in Vietnam, `r corr.CNVN$full_result`.
-This points to a strong signal of universality across cultural contexts regarding similarity judgments.
-
-```{r USCN effect size comparison, include=FALSE}
-USCN_cohen <- cohen.d(df.triad_country$China, df.triad_country$US)
-```
-
-For comparison with previous work, we also included an effect size comparison for the difference in US-China thematic response data (though this was not a planned analysis).
-The effect size for this analysis was d = `r USCN_cohen$estimate`, a small effect size.
-This is smaller than the effect size from @Ji2004, even when we are unable to make a direct comparison.
-Calculating the effect size from the ANOVA reported in @Ji2004 between US participants tested in English and mainland China participants tested in English (both groups tested in the US) yields a Cohen's d = 0.81.
-@Ji2004 reported that mean thematic response for mainland China participants tested in Mandarin Chinese is higher than for those tested in English, so the effect size for a comparison between mainland China participants tested in Mandarin Chinese and US participants tested in English (parallel to our comparison) would likely have yielded an even larger effect size than 0.814.
-It is possible that we failed to replicate the magnitude of effect from @Ji2004 because the previous study calculated their dependent variable as frequency of thematic responses minus frequency of taxonomic responses, whereas our dependent variable is proportion of thematic response over total number of responses.
-
-To test for cross-context differences in similarity judgments between the countries, we ran a mixed-effects logistic regression predicting triad responding (taxonomic or thematic) with country (US, China, or Vietnam) as a fixed effect.
-As random effects, we included an intercept per subject and one per triad, as well as by-triad random slopes for country to account for variation in the country effect across triads.
-In R syntax, the model is: response ~ country + (1 | subject) + (country | triad).
-
-Overall, there is a significant effect of country on proportion of thematic responses ($\chi^2$(`r fit.country.anova["country", "Df"]`) = `r round(fit.country.anova["country", "Chisq"], 2)`, p < .001).
-However, this effect is driven by the difference between US and China responding ($\beta$ = `r round(fixef(fit.country)["countryUS"], 2)`, p < .001).
-There is no statistical difference between the Vietnam and China responding ($\beta$ = `r round(fixef(fit.country)["countryVietnam"], 2)`, p = `r round(as.data.frame(summary(fit.country)[["coefficients"]])["countryVietnam", "Pr(>|z|)"], 2)`), and the US and Vietnam responding ($\beta$ = `r round(fixef(fit.country_EN_VN)["countryVietnam"], 2)`, p = `r round(as.data.frame(summary(fit.country_EN_VN)[["coefficients"]])["countryVietnam", "Pr(>|z|)"], 3)`).
-
-On this analysis, we do not find support that the US-China tendencies toward taxonomic and thematic responding (respectively) extend to the US-Vietnam comparison.
-Accordingly, we cannot speak to overall biases toward thematic responding across Asian cultural contexts broadly, but we do replicate the differences documented by @Ji2004 between the US and China.
-However, in our corpus model comparison, we do find evidence for different, more fine-grained variation in similarity judgments between the US and Vietnam.
-
-## Can the differences in similarity judgments between English, Mandarin and Vietnamese speakers be explained by variation in lexical statistics?
-### Is responding in each cultural context predicted by the corresponding lexical statistics (raw co-occurrences and cosine distance)? 
-```{r Pearson correlation between raw co-occurrences of corpora and responding, warning=FALSE, include=FALSE}
-
-#raw co-occurrences
-df.triad_country_freq <- df %>%
-  filter(!(triad %in% triads_omit)) %>% # omit triads that do not have meaningful prediction (at least 1 non-zero prediction in both languages)
-  group_by(triad, country, theme_freq_prop_E, theme_freq_prop_V, theme_freq_prop_M) %>%  # not working 
-  summarize(emp_theme_prop = mean(responses_theme))
-df.triad_country_freq   #sanity
-
-df.triad_country_freq_E <- df.triad_country_freq %>%
-  filter(country == "US")
-
-#plotting English corpus against US responding data
-plotE = ggplot(data = df.triad_country_freq_E,
-        mapping = aes(x = emp_theme_prop,
-                     y = theme_freq_prop_E,
-                     label = triad)) +
-   geom_text() +
-   geom_smooth(method = "lm") +
-   labs(x = "Proportion Thematic Chosen (US)",
-        y = "Proportion Thematic Predicted (English)")
-plotE
-
-df.triad_country_freq_V <- df.triad_country_freq %>%
-  filter(country == "Vietnam")
-
-#plotting Vietnamese corpus against VN responding data
-plotV = ggplot(data = df.triad_country_freq_V,
-        mapping = aes(x = emp_theme_prop,
-                     y = theme_freq_prop_V,
-                     label = triad)) +
-   geom_text() +
-   geom_smooth(method = "lm") +
-   labs(x = "Proportion Thematic Chosen (Vietnam)",
-        y = "Proportion Thematic Predicted (Vietnamese)")
-plotV
-
-df.triad_country_freq_M <- df.triad_country_freq %>%
-  filter(country == "China")
-
-#plotting China corpus against CN responding data
-plotM = ggplot(data = df.triad_country_freq_M,
-        mapping = aes(x = emp_theme_prop,
-                     y = theme_freq_prop_M,
-                     label = triad)) +
-   geom_text() +
-   geom_smooth(method = "lm") +
-   labs(x = "Proportion Thematic Chosen (China)",
-        y = "Proportion Thematic Predicted (Chinese)")
-plotM
-
-#Pearson correlation between corpus and responding
-corr.E = apa_print(cor.test(df.triad_country_freq_E$emp_theme_prop,
-                  df.triad_country_freq_E$theme_freq_prop_E, na.rm=T))
-corr.E
-
-corr.V = apa_print(cor.test(df.triad_country_freq_V$emp_theme_prop,
-                  df.triad_country_freq_V$theme_freq_prop_V, na.rm=T))
-corr.V
-
-corr.M = apa_print(cor.test(df.triad_country_freq_M$emp_theme_prop,
-                  df.triad_country_freq_M$theme_freq_prop_M, na.rm=T))
-corr.M
-
-#Pearson correlation between EN and VI corpus
-corr.EV = apa_print(cor.test(df.triad_country_freq_V$theme_freq_prop_V,
-                   df.triad_country_freq_E$theme_freq_prop_E, na.rm=T))
-corr.EM = apa_print(cor.test(df.triad_country_freq_M$theme_freq_prop_M,
-                   df.triad_country_freq_E$theme_freq_prop_E, na.rm=T))
-corr.MV = apa_print(cor.test(df.triad_country_freq_V$theme_freq_prop_V,
-                   df.triad_country_freq_M$theme_freq_prop_M, na.rm=T))
-```
-
-```{r echo=FALSE, paged.print=FALSE, fig.cap ="Correlation between English corpus lexical co-occurrence and US responding, and Vietnamese corpus lexical co-occurrence and Vietnam responding."}
-plotE + plotV + plotM
-  plot_layout(ncol = 3)
-```
-
-We first conducted a Pearson correlation test between corresponding response data and corpus data.
-Looking at the raw lexical co-occurrence data, proportion of US thematic responding is moderately correlated to English corpus thematic proportion, `r corr.E$full_result`.
-Proportion of Vietnam thematic responding is moderately correlated to Vietnamese corpus thematic proportion, `r corr.V$full_result`.
-Proportion of China thematic responding is moderately correlated to Chinese corpus thematic proportion, `r corr.M$full_result`.
-There was a strong similarity signal between the thematic proportions in the English and Vietnamese corpora, `r corr.EV$full_result`, and the thematic proportions in the English and Mandarin corpora, `r corr.EM$full_result`.
-There was a moderate similarity signal between the proportions in the Mandarin and Vietnamese corpora, `r corr.MV$full_result.`
-
-```{r Pearson correlation between corpus cosine distance and responding, warning=FALSE, include=FALSE}
-df.triad_country_cos <- df %>%
-  group_by(triad, country, theme_cosine_prop_E, theme_cosine_prop_V, theme_cosine_prop_M) %>%
-  summarize(emp_theme_prop = mean(responses_theme))
-
-df.triad_country_cos_E <- df.triad_country_cos %>%
-  filter(country == "US")
-
-plotE = ggplot(data = df.triad_country_cos_E, 
-        mapping = aes(x = emp_theme_prop, 
-                     y = theme_cosine_prop_E,
-                     label = triad)) +
-   geom_text() + 
-   geom_smooth(method = "lm") +
-   labs(x = "Proportion Thematic Chosen (US)", 
-        y = "Proportion Thematic Predicted (English)") + 
-   scale_y_reverse() + 
-   xlim(0, 1) +
-   ylim(0.8, 0.2) + 
-  theme(axis.title = element_text(size=rel(0.75)))
-
-df.triad_country_cos_V <- df.triad_country_cos %>%
-  filter(country == "Vietnam")
-
-plotV = ggplot(data = df.triad_country_cos_V, 
-        mapping = aes(x = emp_theme_prop, 
-                     y = theme_cosine_prop_V, 
-                     label = triad)) +
-   geom_text() + 
-   geom_smooth(method = "lm") +
-   labs(x = "Proportion Thematic Chosen (Vietnam)", 
-        y = "Proportion Thematic Predicted (Vietnamese)") + 
-   scale_y_reverse() +
-   xlim(0, 1) +
-   ylim(0.8, 0.2) + 
-  theme(axis.title = element_text(size=rel(0.75)))
-
-df.triad_country_cos_M <- df.triad_country_cos %>%
-  filter(country == "China")
-
-plotM = ggplot(data = df.triad_country_cos_M, 
-        mapping = aes(x = emp_theme_prop, 
-                     y = theme_cosine_prop_M, 
-                     label = triad)) +
-   geom_text() + 
-   geom_smooth(method = "lm") +
-   labs(x = "Proportion Thematic Chosen (China)", 
-        y = "Proportion Thematic Predicted (Mandarin)") + 
-   xlim(0, 1) +
-   ylim(0.8, 0.2) + 
-  theme(axis.title = element_text(size=rel(0.75)))
-
-corr.E_cos = apa_print(cor.test(df.triad_country_cos_E$emp_theme_prop,
-                      df.triad_country_cos_E$theme_cosine_prop_E, na.rm=T))
-
-corr.V_cos = apa_print(cor.test(df.triad_country_cos_V$emp_theme_prop,
-                      df.triad_country_cos_V$theme_cosine_prop_V, na.rm=T))
-
-corr.M_cos = apa_print(cor.test(df.triad_country_cos_M$emp_theme_prop,
-                      df.triad_country_cos_M$theme_cosine_prop_M, na.rm=T))
-
-#correlation between corpora
-corr.EV_cos = apa_print(cor.test(df.triad_country_cos_E$theme_cosine_prop_E,
-                       df.triad_country_cos_V$theme_cosine_prop_V, na.rm=T))
-
-corr.EM_cos = apa_print(cor.test(df.triad_country_cos_E$theme_cosine_prop_E,
-                      df.triad_country_cos_M$theme_cosine_prop_M, na.rm=T))
-
-corr.VM_cos = apa_print(cor.test(df.triad_country_cos_V$theme_cosine_prop_V,
-                      df.triad_country_cos_M$theme_cosine_prop_M, na.rm=T))
-```
-
-```{r warning = FALSE, echo=FALSE, fig.width = 8, fig.cap="Correlation between English corpus cosine distance and US responding; Vietnamese corpus cosine distance and Vietnam responding; and Mandarin corpus cosine distance and China responding."}
-#maybe we should include a note that explains why they are correlate in the opposite direction? 
-#either changing the label of y-axis, or use y = 1/theme_cosine_prop_V? 
-plotE + plotV + plotM +
-  plot_layout(ncol = 3)
-```
-
-```{r US-Mandarin, China-English cross correlation, NOT SHOWN, eval=FALSE, warning=FALSE, include=FALSE}
-plotUSZH = ggplot(data = df.triad_country_cos_E, 
-        mapping = aes(x = emp_theme_prop, 
-                     y = theme_cosine_prop_M,
-                     label = triad)) +
-   geom_text() + 
-   geom_smooth(method = "lm") +
-   labs(x = "Proportion Thematic Chosen (US)", 
-        y = "Proportion Thematic Predicted (Mandarin)") + 
-   scale_y_reverse() + 
-   xlim(0, 1) +
-   ylim(0.8, 0.3)
-
-plotCNEN = ggplot(data = df.triad_country_cos_M, 
-        mapping = aes(x = emp_theme_prop, 
-                     y = theme_cosine_prop_E,
-                     label = triad)) +
-   geom_text() + 
-   geom_smooth(method = "lm") +
-   labs(x = "Proportion Thematic Chosen (China)", 
-        y = "Proportion Thematic Predicted (English)") + 
-   scale_y_reverse() + 
-   xlim(0, 1) +
-   ylim(0.8, 0.3)
-
-plotUSZH + plotCNEN +
-  plot_layout(ncol = 2)
-```
-
-Looking at the cosine distance data using fastText word vectors, proportion of US thematic responding is moderately correlated to English thematic cosine distance proportion, `r corr.E_cos$full_result`.
-There is a small correlation between proportion of Vietnam thematic responding and the Vietnamese thematic cosine distance proportion, `r corr.V_cos$full_result`.
-Proportion of China thematic responding is moderately correlated to Mandarin thematic match cosine distance proportion, `r corr.M_cos$full_result`.
-There were moderate signals of similarity between English and Mandarin (`r corr.EM_cos$full_result`).
-There was no significant correlation between English and Vietnamese (`r corr.EV_cos$full_result`), and between Vietnamese and Mandarin (`r corr.VM_cos$full_result`).
-
-To test whether variation in lexical co-occurrence can explain differences in similarity judgments between US and Vietnam participants, we compare logistic mixed-effects regression models fit to the thematic responding data from each country separately.
-We first ask how well each corpus model (English, Vietnamese, or Mandarin) predicts similarity judgments by speakers of the corresponding language (US, Vietnam, or China).
-To do this, we use a mixed-effects logistic regression to predict triad responses (0=taxonomic or 1=thematic) with corpus prediction (proportion thematic co-occurrence or cosine distance) as a fixed effect and participant and triad as random effects.
-
-#### Raw lexical co-occurrences
-
-```{r US responding predicted by each corpus model raw co-occurrences, warning=FALSE, include=F}
+### English
+Baseline model:
+```{r US responding predicted by each corpus model raw co-occurrences, warning=FALSE}
 # English 
@@
 fit.EN_US.anova = Anova(fit.EN_US, type = 3)
+```
 
-#Vietnamese
-fit.VI_US = glmer(responses_theme ~ theme_freq_prop_V + (1 | subject) + (1 | triad), 
+Intuitive model (cue first): 
+```{r}
+fit.EN_US_cue_first = glmer(responses_theme ~ theme_freq_prop_E + match_given_cue + (1 | subject) + (1 | triad), 
           data = df %>% filter(country == "US", !(triad %in% triads_omit)), 
           family="binomial")
-summary(fit.VI_US)
-fit.VI_US.anova = Anova(fit.VI_US, type = 3)
+summary(fit.EN_US_cue_first)
+```
 
-#Mandarin
-fit.ZH_US = glmer(responses_theme ~ theme_freq_prop_M + (1 | subject) + (1 | triad), 
+Comparing cue-first (intuitive) and base model: Cue-first model fits data better than base model.
+```{r}
+fit.EN_US_dir_compare_cue_first = anova(fit.EN_US, fit.EN_US_cue_first, type = 3)
+fit.EN_US_dir_compare_cue_first
+```
+
+Non-intuitive model (match first):
+```{r}
+fit.EN_US_match_first = glmer(responses_theme ~ theme_freq_prop_E + cue_given_match + (1 | subject) + (1 | triad), 
           data = df %>% filter(country == "US", !(triad %in% triads_omit)), 
           family="binomial")
-summary(fit.ZH_US)
-fit.ZH_US.anova = Anova(fit.ZH_US, type = 3)
+summary(fit.EN_US_match_first)
 ```
 
-```{r VN responding predicted by each corpus model raw co-occurrences, warning=FALSE, include=F}
+Comparing match-first (non-intuitive) and base model: Match-first model fits data better than base model.
+```{r}
+fit.EN_US_dir_compare_match_first = anova(fit.EN_US, fit.EN_US_match_first, type = 3)
+fit.EN_US_dir_compare_match_first
+```
+
+Comparing match-first (non-intuitive) and cue-first (intuitive) model: Null result?
+```{r}
+fit.EN_US_dir_compare_cue_vs_match_first = anova(fit.EN_US_cue_first, fit.EN_US_match_first, type = 3)
+fit.EN_US_dir_compare_cue_vs_match_first
+```
+
+Adding cue given match (cue+match / match) OR match given cue (cue+match / cue) both improve the model significantly over only having thematic frequency prop, even though the additional term does not wipe out the effect of thematic proportion.
+Comparing between the cue given match and match given cue model yields null result.
+
+```{r VN responding predicted by each corpus model raw co-occurrences, warning=FALSE, include=F, eval=F}
 # English 
@@
 
-```{r CN responding predicted by each corpus model raw co-occurrences, warning=FALSE, include=F}
-#English
-fit.EN_CN = glmer(responses_theme ~ theme_freq_prop_E + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "China", !(triad %in% triads_omit)), 
-          family="binomial")
-summary(fit.EN_CN)
-fit.EN_CN.anova = Anova(fit.EN_CN, type = 3)
-
-#Vietnamese
-fit.VI_CN = glmer(responses_theme ~ theme_freq_prop_V + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "China", !(triad %in% triads_omit)), 
-          family="binomial")
-summary(fit.VI_CN)
-fit.VI_CN.anova = Anova(fit.VI_CN, type = 3)
-
+### Mandarin
+Baseline model:
+```{r CN responding predicted by each corpus model raw co-occurrences, warning=FALSE}
 #Mandarin
@@
 
-TODO: ADD CHINA RESULTS
-Both the English (EN) and Vietnamese (VI) corpus are significant predictors of US responding (EN-US model: $\beta$ = `r round(fixef(fit.EN_US)["theme_freq_prop_E"], 2)`, $\chi^2$(`r fit.EN_US.anova["theme_freq_prop_E", "Df"]`) = `r round(fit.EN_US.anova["theme_freq_prop_E", "Chisq"], 2)`, p < .001; VI-US model: $\beta$ = `r round(fixef(fit.VI_US)["theme_freq_prop_V"], 2)`, $\chi^2$(`r fit.VI_US.anova["theme_freq_prop_V", "Df"]`) = `r round(fit.VI_US.anova["theme_freq_prop_V", "Chisq"], 2)`, p < .001).
-
-Similarly, both the English (EN) and Vietnamese (VI) corpus are significant predictors of Vietnam (VN) responding (EN-VN model: $\beta$ = `r round(fixef(fit.EN_VN)["theme_freq_prop_E"], 2)`, $\chi^2$(`r fit.EN_VN.anova["theme_freq_prop_E", "Df"]`) = `r round(fit.EN_VN.anova["theme_freq_prop_E", "Chisq"], 2)`, p < .001; VI-VN model: $\beta$ = `r round(fixef(fit.VI_VN)["theme_freq_prop_V"], 2)`, $\chi^2$(`r fit.VI_VN.anova["theme_freq_prop_V", "Df"]`) = `r round(fit.VI_VN.anova["theme_freq_prop_V", "Chisq"], 2)`, p < .001).
-
-This suggests a strong shared similarity signal across the languages, which is also reflected in the strong correlation between the two corpus models reported above (`r corr.EV$full_result`).
-
-#### Cosine distances of fastText word vectors
-```{r US responding predicted by each corpus model cosine differences, warning=FALSE, include=F}
-#English
-fit.EN_US_cos = glmer(responses_theme ~ theme_cosine_prop_E + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "US"), 
+Intuitive model (cue first):
+```{r}
+fit.ZH_CN_cue_first = glmer(responses_theme ~ theme_freq_prop_M + match_given_cue + (1 | subject) + (1 | triad), 
+          data = df %>% filter(country == "China", !(triad %in% triads_omit)), 
           family="binomial")
-summary(fit.EN_US_cos)
-fit.EN_US_cos.anova = Anova(fit.EN_US_cos, type = 3)
-fit.EN_US_cos.anova
-
-#Vietnamese
-fit.VI_US_cos = glmer(responses_theme ~ theme_cosine_prop_V + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "US"), 
-          family="binomial")
-summary(fit.VI_US_cos)
-fit.VI_US_cos.anova = Anova(fit.VI_US_cos, type = 3)
-fit.VI_US_cos.anova
-
-#Mandarin
-fit.ZH_US_cos = glmer(responses_theme ~ theme_cosine_prop_M + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "US"), 
-          family="binomial")
-summary(fit.ZH_US_cos)
-fit.ZH_US_cos.anova = Anova(fit.ZH_US_cos, type = 3)
-fit.ZH_US_cos.anova
+summary(fit.ZH_CN_cue_first)
 ```
 
-```{r VN responding predicted by each corpus model cosine differences, warning=FALSE, include=F}
-#English
-fit.EN_VN_cos = glmer(responses_theme ~ theme_cosine_prop_E + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "Vietnam"), 
-          family="binomial")
-summary(fit.EN_VN_cos)
-fit.EN_VN_cos.anova = Anova(fit.EN_VN_cos, type = 3)
-fit.EN_VN_cos.anova
-
-#Vietnamese
-fit.VI_VN_cos = glmer(responses_theme ~ theme_cosine_prop_V + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "Vietnam"), 
-          family="binomial")
-summary(fit.VI_VN_cos)
-fit.VI_VN_cos.anova = Anova(fit.VI_VN_cos, type = 3)
-fit.VI_VN_cos.anova
-
-#Mandarin
-fit.ZH_VN_cos = glmer(responses_theme ~ theme_cosine_prop_M + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "Vietnam"), 
-          family="binomial")
-summary(fit.ZH_VN_cos)
-fit.ZH_VN_cos.anova = Anova(fit.ZH_VN_cos, type = 3)
-fit.ZH_VN_cos.anova
+Comparing cue-first (intuitive) and base model: Cue-first model fits data better than base model.
+```{r}
+fit.ZH_CN_dir_compare_cue_first = anova(fit.ZH_CN, fit.ZH_CN_cue_first, type = 3)
+fit.ZH_CN_dir_compare_cue_first
 ```
 
-```{r CN responding predicted by each corpus model cosine differences, warning=FALSE, include=F}
-## English
-fit.EN_CN_cos = glmer(responses_theme ~ theme_cosine_prop_E + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "China"), 
+Non-intuitive model (match first):
+```{r}
+fit.ZH_CN_match_first = glmer(responses_theme ~ theme_freq_prop_M + cue_given_match + (1 | subject) + (1 | triad), 
+          data = df %>% filter(country == "China", !(triad %in% triads_omit)), 
           family="binomial")
-summary(fit.EN_CN_cos)
-fit.EN_CN_cos.anova = Anova(fit.EN_CN_cos, type = 3)
-fit.EN_CN_cos.anova
-
-#Vietnamese
-fit.VI_CN_cos = glmer(responses_theme ~ theme_cosine_prop_V + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "China"), 
-          family="binomial")
-summary(fit.VI_CN_cos)
-fit.VI_CN_cos.anova = Anova(fit.VI_CN_cos, type = 3)
-fit.VI_CN_cos.anova
-
-#Mandarin
-fit.ZH_CN_cos = glmer(responses_theme ~ theme_cosine_prop_M + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "China"), 
-          family="binomial")
-summary(fit.ZH_CN_cos)
-fit.ZH_CN_cos.anova = Anova(fit.ZH_CN_cos, type = 3)
-fit.ZH_CN_cos.anova
+summary(fit.ZH_CN_match_first)
 ```
 
-Similar to the results from the analysis with raw lexical co-occurrences, we found that all corpora are significant predictors of all cultural context responding.
+Comparing match-first (non-intuitive) and base model: Match-first model fits data better than base model.
+```{r}
+fit.ZH_CN_dir_compare_match_first = anova(fit.ZH_CN, fit.ZH_CN_match_first, type = 3)
+fit.ZH_CN_dir_compare_match_first
+```
 
-For US responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are significant predictors of US responding (EN-US model: $\beta$ = `r round(fixef(fit.EN_US_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.EN_US_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.EN_US_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p < .001; VI-US model: $\beta$ = `r round(fixef(fit.VI_US_cos)["theme_cosine_prop_V"], 2)`, $\chi^2$(`r fit.VI_US_cos.anova["theme_cosine_prop_V", "Df"]`) = `r round(fit.VI_US_cos.anova["theme_cosine_prop_V", "Chisq"], 2)`, p = `r round(fit.VI_US_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"], 3)`; ZH-US model: $\beta$ = `r round(fixef(fit.ZH_US_cos)["theme_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ZH_US_cos.anova["theme_cosine_prop_M", "Df"]`) = `r round(fit.ZH_US_cos.anova["theme_cosine_prop_M", "Chisq"], 2)`, p < .001).
-
-For Vietnam (VN) responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are significant predictors of VN responding (EN-VN model: $\beta$ = `r round(fixef(fit.EN_VN_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.EN_VN_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.EN_VN_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p < .001; VI-VN model: $\beta$ = `r round(fixef(fit.VI_VN_cos)["theme_cosine_prop_V"], 2)`, $\chi^2$(`r fit.VI_VN_cos.anova["theme_cosine_prop_V", "Df"]`) = `r round(fit.VI_VN_cos.anova["theme_cosine_prop_V", "Chisq"], 2)`, p = `r round(fit.VI_VN_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"], 3)`; ZH-VN model: $\beta$ = `r round(fixef(fit.ZH_VN_cos)["theme_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ZH_VN_cos.anova["theme_cosine_prop_M", "Df"]`) = `r round(fit.ZH_VN_cos.anova["theme_cosine_prop_M", "Chisq"], 2)`, p < .001).
-
-For China (CN) responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are significant predictors of CN responding (EN-CN model: $\beta$ = `r round(fixef(fit.EN_CN_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.EN_CN_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.EN_CN_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p < .001; VI-CN model: $\beta$ = `r round(fixef(fit.VI_CN_cos)["theme_cosine_prop_V"], 2)`, $\chi^2$(`r fit.VI_CN_cos.anova["theme_cosine_prop_V", "Df"]`) = `r round(fit.VI_CN_cos.anova["theme_cosine_prop_V", "Chisq"], 2)`, p = `r round(fit.VI_VN_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"], 3)`; ZH-CN model: $\beta$ = `r round(fixef(fit.ZH_CN_cos)["theme_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ZH_CN_cos.anova["theme_cosine_prop_M", "Df"]`) = `r round(fit.ZH_CN_cos.anova["theme_cosine_prop_M", "Chisq"], 2)`, p < .001).
-
-### Is responding in each cultural context __best__ predicted by the corresponding corpus's lexical statistics (raw co-occurrences and cosine distance), as opposed to the other two corpora?
-Next, we directly compare the corpus models by including both as fixed effects in two mixed-effect regressions (predicting US and Vietnam responding) with the same random effects as above.
-In R syntax, the model is: response ~ corpus_English + corpus_Vietnamese + corpus_Mandarin + (1|triad) + (1|subject).
-
-#### Raw co-occurrences 
-```{r MIGHT NEED TO REMOVEEnglish + Vietnamese raw co-occurrences predicting US and Vietnam, warning=FALSE, include=F}
-## English/Vietnamese comparison
-fit.ENVI_US = glmer(responses_theme ~ theme_freq_prop_E + theme_freq_prop_V + 
-                      (1 | subject) + (1 | triad), 
-                    data = df %>% filter(country == "US"), 
-                    family="binomial")
-summary(fit.ENVI_US)
-fit.ENVI_US.anova = Anova(fit.ENVI_US, type = 3)
-fit.ENVI_US.anova
-
-fit.ENVI_VN = glmer(responses_theme ~ theme_freq_prop_V + theme_freq_prop_E + 
-                      (1 | subject) + (1 | triad), 
-                    data = df %>% filter(country == "Vietnam"), 
-                    family="binomial")
-summary(fit.ENVI_VN)
-fit.ENVI_VN.anova = Anova(fit.ENVI_VN, type = 3)
-fit.ENVI_VN.anova
-```
-When we included both corpora as predictors for US responding, only the English corpus has a significant effect ($\beta$ = `r round(fixef(fit.ENVI_US)["theme_freq_prop_E"], 2)`, $\chi^2$(`r fit.ENVI_US.anova["theme_freq_prop_E", "Df"]`) = `r round(fit.ENVI_US.anova["theme_freq_prop_E", "Chisq"], 2)`, p < .001).
-There is no effect of the Vietnamese corpus ($\beta$ = `r round(fixef(fit.ENVI_US)["theme_freq_prop_V"], 2)`, $\chi^2$(`r fit.ENVI_US.anova["theme_freq_prop_V", "Df"]`) = `r round(fit.ENVI_US.anova["theme_freq_prop_V", "Chisq"], 2)`, p = `r round(fit.ENVI_US.anova["theme_freq_prop_V", "Pr(>Chisq)"], 3)`).
-
-However, when both corpora are included as predictors for Vietnam responding -- both corpora has a significant effect (English corpus: $\beta$ = `r round(fixef(fit.ENVI_VN)["theme_freq_prop_E"], 2)`, $\chi^2$(`r fit.ENVI_VN.anova["theme_freq_prop_E", "Df"]`) = `r round(fit.ENVI_VN.anova["theme_freq_prop_E", "Chisq"], 2)`, p = `r round(fit.ENVI_VN.anova["theme_freq_prop_E", "Pr(>Chisq)"], 3)`; Vietnamese corpus: $\beta$ = `r round(fixef(fit.ENVI_VN)["theme_freq_prop_V"], 2)`, $\chi^2$(`r fit.ENVI_VN.anova["theme_freq_prop_V", "Df"]`) = `r round(fit.ENVI_VN.anova["theme_freq_prop_V", "Chisq"], 2)`, p = `r round(fit.ENVI_VN.anova["theme_freq_prop_V", "Pr(>Chisq)"], 3)`).
-
-```{r Eng-Vie-Mand lexical co-occ predicting US, VN, CN, warning=FALSE, include=F}
-# ADDITION: adding theme_freq_prop_M
-#raw co-occurrences
-#linear mixed model with ALL corpora as predictors for each population.
-fit.ENVIZH_US = glmer(responses_theme ~ 
-                      theme_freq_prop_E + theme_freq_prop_V + theme_freq_prop_M +
-                      (1 | subject) + (1 | triad), 
-                    data = df %>% filter(country == "US", !(triad %in% triads_omit)),
-                    family="binomial")
-summary(fit.ENVIZH_US)
-fit.ENVIZH_US.anova = Anova(fit.ENVIZH_US, type = 3)
-fit.ENVIZH_US.anova
-
-fit.ENVIZH_VN = glmer(responses_theme ~ 
-                      theme_freq_prop_V + theme_freq_prop_E + theme_freq_prop_M +
-                      (1 | subject) + (1 | triad), 
-                    data = df %>% filter(country == "Vietnam", !(triad %in% triads_omit)),
-                    family="binomial")
-summary(fit.ENVIZH_VN)
-fit.ENVIZH_VN.anova = Anova(fit.ENVIZH_VN, type = 3)
-fit.ENVIZH_VN.anova
-
-fit.ENVIZH_CN = glmer(responses_theme ~ 
-                      theme_freq_prop_V + theme_freq_prop_E + theme_freq_prop_M +
-                      (1 | subject) + (1 | triad), 
-                    data = df %>% filter(country == "China", !(triad %in% triads_omit)),
-                    family="binomial")
-summary(fit.ENVIZH_CN)
-fit.ENVIZH_CN.anova = Anova(fit.ENVIZH_CN, type = 3)
-fit.ENVIZH_CN.anova
-```
-TODO: ADD WRITE-UP OF RESULTS
-
-```{r echo=FALSE, warning = FALSE, fig.cap = "Fixed effect sizes of each corpus when included as a predictor for China, US, and Vietnam responding, respectively.
-The English corpus is the best predictor for US response, and the Mandarin corpus is the best predictor for China response."}
-coeff_value_freq <- c(fixef(fit.ENVIZH_US)["theme_freq_prop_E"],
-                 fixef(fit.ENVIZH_US)["theme_freq_prop_V"], 
-                 fixef(fit.ENVIZH_US)["theme_freq_prop_M"],
-                 fixef(fit.ENVIZH_VN)["theme_freq_prop_E"],
-                 fixef(fit.ENVIZH_VN)["theme_freq_prop_V"],
-                 fixef(fit.ENVIZH_VN)["theme_freq_prop_M"], 
-                 fixef(fit.ENVIZH_CN)["theme_freq_prop_E"],
-                 fixef(fit.ENVIZH_CN)["theme_freq_prop_V"], 
-                 fixef(fit.ENVIZH_CN)["theme_freq_prop_M"])
-
-se_value_freq <- c(summary(fit.ENVIZH_US)$coef["theme_freq_prop_E", "Std. Error"], 
-              summary(fit.ENVIZH_US)$coef["theme_freq_prop_V", "Std. Error"],
-              summary(fit.ENVIZH_US)$coef["theme_freq_prop_M", "Std. Error"], 
-              summary(fit.ENVIZH_VN)$coef["theme_freq_prop_E", "Std. Error"], 
-              summary(fit.ENVIZH_VN)$coef["theme_freq_prop_V", "Std. Error"],
-              summary(fit.ENVIZH_VN)$coef["theme_freq_prop_M", "Std. Error"],
-              summary(fit.ENVIZH_CN)$coef["theme_freq_prop_E", "Std. Error"], 
-              summary(fit.ENVIZH_CN)$coef["theme_freq_prop_V", "Std. Error"],
-              summary(fit.ENVIZH_CN)$coef["theme_freq_prop_M", "Std. Error"])
-
-country_value <- c(rep("US", 3),
-                   rep("VN", 3),
-                   rep("CN", 3))
-
-corpus_value <- c(rep(c("EN", "VI", "ZH"), 3))
-
-df.USVNCN_coeffs_freq <- data.frame(country_value, corpus_value, coeff_value_freq, se_value_freq)
-
-ggplot(data = df.USVNCN_coeffs_freq, 
-       mapping = aes(x = country_value, y = coeff_value_freq, fill = corpus_value)) +
-  geom_bar(position="dodge", stat="identity") +
-  geom_errorbar(aes(ymin= coeff_value_freq - se_value_freq, ymax = coeff_value_freq + se_value_freq), width=.2,
-                 position=position_dodge(.9)) +
-  scale_y_reverse() + 
-  labs(x = "Country", y = "Fixed effect size", fill = "Corpus") + 
-  scale_x_discrete(labels=c("CN" = "China", "US" = "US", "VN" = "Vietnam")) + 
-  scale_fill_manual(values=c("#D63230", "#1C77C3", "#F39237"))
+Comparing match-first (non-intuitive) and cue-first (intuitive) model: Null result?
+```{r}
+fit.ZH_CN_dir_compare_cue_vs_match_first = anova(fit.ZH_CN_cue_first, fit.ZH_CN_match_first, type = 3)
+fit.ZH_CN_dir_compare_cue_vs_match_first
 
 ```
-
-```{r model comparison, include=FALSE}
-fit.US_freq_compare = anova(fit.ENVIZH_US, fit.EN_US, type = 3)
-fit.VN_freq_compare = anova(fit.ENVIZH_VN, fit.VI_VN, type = 3)
-fit.CN_freq_compare = anova(fit.ENVIZH_CN, fit.ZH_CN, type = 3)
-```
-
-TODO: ADD WRITE-UP ON RESULTS
-
-#### Cosine distances of fastText word vectors
-
-```{r Eng-Vie-Mand cosine similarities predicting US, VN, CN warning=FALSE, include=FALSE}
-## English/Vietnamese/Mandarin comparison
-fit.ENVIZH_US_cos = glmer(responses_theme ~ theme_cosine_prop_E + theme_cosine_prop_V + theme_cosine_prop_M +
-                      (1 | subject) + (1 | triad), 
-                    data = df %>% filter(country == "US"), 
-                    family="binomial")
-summary(fit.ENVIZH_US_cos)
-fit.ENVIZH_US_cos.anova = Anova(fit.ENVIZH_US_cos, type = 3)
-fit.ENVIZH_US_cos.anova
-
-fit.ENVIZH_VN_cos = glmer(responses_theme ~ theme_cosine_prop_V + theme_cosine_prop_E + theme_cosine_prop_M +
-                      (1 | subject) + (1 | triad), 
-                    data = df %>% filter(country == "Vietnam"), 
-                    family="binomial")
-summary(fit.ENVIZH_VN_cos)
-fit.ENVIZH_VN_cos.anova = Anova(fit.ENVIZH_VN_cos, type = 3)
-fit.ENVIZH_VN_cos.anova
-
-fit.ENVIZH_CN_cos = glmer(responses_theme ~ theme_cosine_prop_M + theme_cosine_prop_E + theme_cosine_prop_V +
-                      (1 | subject) + (1 | triad), 
-                    data = df %>% filter(country == "China"), 
-                    family="binomial")
-summary(fit.ENVIZH_CN_cos)
-fit.ENVIZH_CN_cos.anova = Anova(fit.ENVIZH_CN_cos, type = 3)
-fit.ENVIZH_CN_cos.anova
-```
-
-When we included all corpora thematic cosine distance proportion as predictors, all corpora are significant in predicting all cultural context's responding.
-
-For US responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are all significant predictors.
-EN corpus: $\beta$ = `r round(fixef(fit.ENVIZH_US_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.ENVIZH_US_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.ENVIZH_US_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p < .001.
-VI corpus: $\beta$ = `r round(fixef(fit.ENVIZH_US_cos)["theme_cosine_prop_V"], 2)`, $\chi^2$(`r fit.ENVIZH_US_cos.anova["theme_cosine_prop_V", "Df"]`) = `r round(fit.ENVIZH_US_cos.anova["theme_cosine_prop_V", "Chisq"], 2)`, p = `r round(fit.ENVIZH_US_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"], 3)`.
-ZH corpus: $\beta$ = `r round(fixef(fit.ENVIZH_US_cos)["theme_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ENVIZH_US_cos.anova["theme_cosine_prop_M", "Df"]`) = `r round(fit.ENVIZH_US_cos.anova["theme_cosine_prop_M", "Chisq"], 2)`, p = `r round(fit.ENVIZH_US_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"], 3)`.
-
-For Vietnam responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are all significant predictors.
-EN corpus: $\beta$ = `r round(fixef(fit.ENVIZH_VN_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.ENVIZH_VN_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p = `r round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"], 3)`.
-VI corpus: $\beta$ = `r round(fixef(fit.ENVIZH_VN_cos)["theme_cosine_prop_V"], 2)`, $\chi^2$(`r fit.ENVIZH_VN_cos.anova["theme_cosine_prop_V", "Df"]`) = `r round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_V", "Chisq"], 2)`, p = `r round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"], 3)`.
-ZH corpus: $\beta$ = `r round(fixef(fit.ENVIZH_VN_cos)["theme_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ENVIZH_VN_cos.anova["theme_cosine_prop_M", "Df"]`) = `r round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_M", "Chisq"], 2)`, p = `r round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"], 3)`.
-
-For China responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are all significant predictors.
-EN corpus: $\beta$ = `r round(fixef(fit.ENVIZH_CN_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.ENVIZH_CN_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.ENVIZH_CN_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p = `r round(fit.ENVIZH_CN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"], 3)`.
-VI corpus: $\beta$ = `r round(fixef(fit.ENVIZH_CN_cos)["theme_cosine_prop_V"], 2)`, $\chi^2$(`r fit.ENVIZH_CN_cos.anova["theme_cosine_prop_V", "Df"]`) = `r round(fit.ENVIZH_CN_cos.anova["theme_cosine_prop_V", "Chisq"], 2)`, p = `r round(fit.ENVIZH_CN_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"], 3)`.
-ZH corpus: $\beta$ = `r round(fixef(fit.ENVIZH_CN_cos)["theme_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ENVIZH_CN_cos.anova["theme_cosine_prop_M", "Df"]`) = `r round(fit.ENVIZH_CN_cos.anova["theme_cosine_prop_M", "Chisq"], 2)`, p = < .001.
-
-We observed some level of language specificity from this analysis.
-The English corpus is the best predictor for US responding, and the Mandarin corpus is the best predictor for China response.
-While this is not the case with the Vietnamese corpus and the Vietnam responding, the Vietnamese corpus is still a significant predictor for the Vietnam responding.
-
-```{r echo=FALSE, warning = FALSE, fig.cap = "Fixed effect sizes of each corpus when included as a predictor for China, US, and Vietnam responding, respectively.
-The English corpus is the best predictor for US response, and the Mandarin corpus is the best predictor for China response."}
-coeff_value_cos <- c(fixef(fit.ENVIZH_US_cos)["theme_cosine_prop_E"],
-                 fixef(fit.ENVIZH_US_cos)["theme_cosine_prop_V"], 
-                 fixef(fit.ENVIZH_US_cos)["theme_cosine_prop_M"],
-                 fixef(fit.ENVIZH_VN_cos)["theme_cosine_prop_E"],
-                 fixef(fit.ENVIZH_VN_cos)["theme_cosine_prop_V"],
-                 fixef(fit.ENVIZH_VN_cos)["theme_cosine_prop_M"], 
-                 fixef(fit.ENVIZH_CN_cos)["theme_cosine_prop_E"],
-                 fixef(fit.ENVIZH_CN_cos)["theme_cosine_prop_V"], 
-                 fixef(fit.ENVIZH_CN_cos)["theme_cosine_prop_M"])
-
-se_value_cos <- c(summary(fit.ENVIZH_US_cos)$coef["theme_cosine_prop_E", "Std. Error"], 
-              summary(fit.ENVIZH_US_cos)$coef["theme_cosine_prop_V", "Std. Error"],
-              summary(fit.ENVIZH_US_cos)$coef["theme_cosine_prop_M", "Std. Error"], 
-              summary(fit.ENVIZH_VN_cos)$coef["theme_cosine_prop_E", "Std. Error"], 
-              summary(fit.ENVIZH_VN_cos)$coef["theme_cosine_prop_V", "Std. Error"],
-              summary(fit.ENVIZH_VN_cos)$coef["theme_cosine_prop_M", "Std. Error"],
-              summary(fit.ENVIZH_CN_cos)$coef["theme_cosine_prop_E", "Std. Error"], 
-              summary(fit.ENVIZH_CN_cos)$coef["theme_cosine_prop_V", "Std. Error"],
-              summary(fit.ENVIZH_CN_cos)$coef["theme_cosine_prop_M", "Std. Error"])
-
-country_value <- c(rep("US", 3),
-                   rep("VN", 3),
-                   rep("CN", 3))
-
-corpus_value <- c(rep(c("EN", "VI", "ZH"), 3))
-
-df.USVNCN_coeffs_cos <- data.frame(country_value, corpus_value, coeff_value_cos, se_value_cos)
-
-ggplot(data = df.USVNCN_coeffs_cos, 
-       mapping = aes(x = country_value, y = coeff_value_cos, fill = corpus_value)) +
-  geom_bar(position="dodge", stat="identity") +
-  geom_errorbar(aes(ymin= coeff_value_cos - se_value_cos, ymax = coeff_value_cos + se_value_cos), width=.2,
-                 position=position_dodge(.9)) +
-  scale_y_reverse() + 
-  labs(x = "Country", y = "Fixed effect size", fill = "Corpus") + 
-  scale_x_discrete(labels=c("CN" = "China", "US" = "US", "VN" = "Vietnam")) + 
-  scale_fill_manual(values=c("#D63230", "#1C77C3", "#F39237"))
-
-```
-
-```{r model comparison, include=FALSE}
-fit.US_cos_compare = anova(fit.ENVIZH_US_cos, fit.EN_US_cos, type = 3)
-fit.VN_cos_compare = anova(fit.ENVIZH_VN_cos, fit.VI_VN_cos, type = 3)
-fit.CN_cos_compare = anova(fit.ENVIZH_CN_cos, fit.ZH_CN_cos, type = 3)
-```
-
-However, we found that language specificity alone does not explain our results.
-We used an ANOVA to compare the model with only the corresponding corpus, and the model with all 3 corpora for each cultural context.
-We found that in all three cases (US, China, Vietnam), adding the other two corpora produces a significantly better fit than the identical model without the additional corpora, and only the corresponding corpus included as a predictor (US response: $\chi^2$(`r fit.US_compare["fit.ENVIZH_US_cos", "Df"]`) = `r round(fit.US_compare["fit.ENVIZH_US_cos", "Chisq"], 2)`, p = `r round(fit.US_compare["fit.ENVIZH_US_cos", "Pr(>Chisq)"], 3)`; Vietnam response: $\chi^2$(`r fit.VN_compare["fit.ENVIZH_VN_cos", "Df"]`) = `r round(fit.VN_compare["fit.ENVIZH_VN_cos", "Chisq"], 2)`, p = < .001; China response: $\chi^2$(`r fit.CN_compare["fit.ENVIZH_CN_cos", "Df"]`) = `r round(fit.CN_compare["fit.ENVIZH_CN_cos", "Chisq"], 2)`, p = `r round(fit.CN_compare["fit.ENVIZH_CN_cos", "Pr(>Chisq)"], 3)`).
-
-```{r add linguistic model to Ji et al., include=FALSE}
-fit.country = glmer(responses_theme ~ country + (1 | subject) + (1 | triad), 
-                           data = df %>% filter(country != "Vietnam"), 
-                           family = "binomial")
-
-fit.country_corpus = glmer(responses_theme ~ country + theme_cosine_prop_E + theme_cosine_prop_M + (1 | subject) + (1 | triad), 
-                           data = df %>% filter(country != "Vietnam"), 
-                           family = "binomial")
-
-fit.add_corpus <- anova(fit.country, fit.country_corpus, type = 3)
-
-```
-
-We carried out an ANOVA model comparison to compare our approach with previous studies that did not include corpus information.
-Because @Ji2004 only compared US and China participants, we filtered our data to only include responding data from these two countries.
-Our approach would be to compare a model that only includes country (US or China) as a fixed effect with one that also includes English and Chinese corpus data.
-Our previous model with an intercept per subject and one per triad, as well as by-triad random slopes for country to account for variation in the country effect across triads fails to converge with the more complex model, so we include a simpler random effect structure with an intercept per subject and one per triad in both the basic and more complex model.
-We compare this model with an identical model but including Chinese and English corpus cosine distance proportion prediction.
-We found that adding English and Chinese corpus data produces a significantly better fit than the identical model without English and Chinese corpus data as predictors ($\chi^2$(`r fit.add_corpus["fit.country_corpus", "Df"]`) = `r round(fit.add_corpus["fit.country_corpus", "Chisq"], 2)`, p = < .001.
-This suggests that including corpus data would better model the cross-cultural differences in similarity judgment in this study as well as similar studies.
-
-## Exploratory analysis
-
-Because our exclusion criterion for attention checks excluded over 50% Vietnam participants, we carried out exploratory analysis where we applied less stringent exclusion criteria.
-In the following analysis, we only exclude participants who miss more than 2 attention checks (rather than any attention checks).
-We kept the rest of the exclusion criteria.
-
-TODO: CREATE .CSV FILES FOR THESE, SEPARATE OUT R SCRIPT INTO RMD.
-```{r loading data E explore, warning=FALSE, include=F}
-df.resp_E <- read.csv("../../data/data_E_0319.csv") %>%
-  select(-X)
-
-# check for participants who completed the entire experiment. Because the experiment is
-# quite long, some participants decide to come back afterwards, so there are a few files
-# that are recorded as incomplete. 
-df.ppts_finished_E <- df.resp_E %>% 
-  group_by(subject) %>%
-  summarize(finished = ifelse("demo-final" %in% unique(variable_type), "yes", "no")) %>%
-  filter(finished == "yes")
-
-df.resp_E <- df.resp_E %>%
-  filter(subject %in% df.ppts_finished_E$subject)
-
-df.ppts_att_E <- df.resp_E %>%
-  filter(stim_type == "attention check") %>%
-  mutate(correct_response = strsplit(cue, "Choose ")) %>%
-  mutate(correct_response = sapply(correct_response, "[[", 2)) %>%
-  mutate(pass_att_check = ifelse(responses == correct_response, 1, 0)) %>%
-  group_by(subject) %>%
-  summarize(pass_att_check_percent = mean(pass_att_check)) %>%
-  filter(pass_att_check_percent >= 0.8)
-
-df.resp_E <- df.resp_E %>%
-  filter(subject %in% df.ppts_att_E$subject) 
-```
-
-```{r exclusion E explore, include = F, warning = F}
-#non-native speaker
-split_responses_demog <- function(responses) {
-  responses <- as.character(responses)
-  response_list <- unlist(strsplit(responses, ',|:'))
-  response_list <- response_list[seq(1, length(response_list))]
-  response_list <- gsub("}", "", response_list)
-  response_list <- gsub("\"", "", response_list)
-  return(response_list)
-}
-
-NATIVE_LANG = 2
-get_native_lang <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  if(responses[NATIVE_LANG-1] != "{firstlanguage") 
-    {warnings("cannot find native language answer")}
-  else
-    {return (responses[NATIVE_LANG])}
-})
-
-df.ppts_non_native_lang_E <- df.resp_E %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_language") %>%
-  mutate(native_speaker = get_native_lang(responses)) %>%
-  filter(native_speaker == "No")
-
-ppts_non_native_lang_E = unique(df.ppts_non_native_lang_E$subject)#18
-percent_dropped = length(ppts_non_native_lang_E) / length(unique(df.resp_E$subject))
-percent_dropped #0.1041667
-
-#fluent in Vietnamese & Mandarin
-SPEAKER = 2
-SPEAKING = 23
-UNDERSTANDING = 46
-
-get_speaker <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[SPEAKER])
-})
-
-get_fluency_speaking <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[SPEAKING])
-})
-
-get_fluency_understanding <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[UNDERSTANDING])
-})
-
-df.lang_vi_E <- df.resp_E %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_language_vi") %>%
-  mutate(vi_speaker = get_speaker(responses))
-
-df.lang_vi_fluency_E <- df.resp_E %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_conditional_language_vn_fluency") %>%
-  mutate(vi_fluency_sp = as.numeric(get_fluency_speaking(responses))) %>%
-  mutate(vi_fluency_ud = as.numeric(get_fluency_understanding(responses)))
-
-df.lang_vi_E <- full_join(df.lang_vi_E, 
-                          df.lang_vi_fluency_E, 
-                          by = "subject") %>%
-  select(subject, vi_speaker, vi_fluency_sp, vi_fluency_ud) %>%
-  filter(vi_speaker == "Yes",
-         vi_fluency_sp > 4, 
-         vi_fluency_ud > 4)
-
-ppts_vi_speaker_E = unique(df.lang_vi_E$subject) #4
-percent_dropped = length(ppts_vi_speaker_E) / length(unique(df.resp_E$subject))
-percent_dropped #0.02083333
-
-df.lang_zh_E <- df.resp_E %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_language_cn") %>%
-  mutate(zh_speaker = get_speaker(responses))
-
-df.lang_zh_fluency_E <- df.resp_E %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_conditional_language_cn_fluency") %>%
-  mutate(zh_fluency_sp = as.numeric(get_fluency_speaking(responses))) %>%
-  mutate(zh_fluency_ud = as.numeric(get_fluency_understanding(responses)))
-
-df.lang_zh_E <- full_join(df.lang_zh_E, 
-                          df.lang_zh_fluency_E, 
-                          by = "subject") %>%
-  select(subject, zh_speaker, zh_fluency_sp, zh_fluency_ud) %>%
-  filter(zh_speaker == "Yes",
-         zh_fluency_sp > 4, 
-         zh_fluency_ud > 4)
-
-ppts_zh_speaker_E = unique(df.lang_zh_E$subject) #30
-percent_dropped = length(ppts_zh_speaker_E) / length(unique(df.resp_E$subject))
-percent_dropped #0.1822917
-
-#have lived outside the sample country for more than 2 years
-#have travelled extensively (more than 6 international experiences of 2 days or longer) 
-YEARSABROAD = 2
-OVERSEAEXP = 4
-
-get_lived_abroad <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[YEARSABROAD])
-})
-
-get_oversea_exp <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[OVERSEAEXP])
-})
-
-df.abroad_E <- df.resp_E %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_oversea_experience") %>%
-  mutate(lived_abroad = get_lived_abroad(responses)) %>%
-  mutate(oversea_exp = get_oversea_exp(responses))
-
-df.lived_abroad_E <- df.abroad_E %>%
-  filter(lived_abroad == "Yes")
-
-ppts_lived_abroad_E = unique(df.lived_abroad_E$subject) #29
-percent_dropped = length(ppts_lived_abroad_E) / length(unique(df.resp_E$subject))
-percent_dropped #0.171875
-
-df.oversea_exp_E <- df.abroad_E %>%
-  filter(oversea_exp == "Six or more experiences")
-
-ppts_oversea_exp_E = unique(df.oversea_exp_E$subject) #77
-percent_dropped = length(ppts_oversea_exp_E) / length(unique(df.resp_E$subject))
-percent_dropped #0.44 # will not use this criterion
-
-df.resp_E <- df.resp_E %>%
-  filter(!(subject %in% ppts_non_native_lang_E),
-         !(subject %in% ppts_vi_speaker_E), 
-         !(subject %in% ppts_zh_speaker_E),
-         !(subject %in% ppts_lived_abroad_E))
-
-length(unique(df.resp_E$subject)) #132
-```
-
-```{r demog_E explore, include = F}
-demog <- c("demog-dropdown", "demog-multi-choice", "demog-free-response", "demog-multi-select")
-df.demog_E <- df.resp_E %>%
-  filter(trial_type %in% demog)
-
-AGE = 97 #index for age answer
-GENDER = 115 #index for gender answer
-split_responses <- function(responses) {
-  responses <- as.character(responses)
-  response_list <- unlist(strsplit(responses, ',|:'))
-  response_list <- response_list[seq(1, length(response_list))]
-  response_list <- gsub("}", "", response_list)
-  response_list <- gsub("\"", "", response_list)
-  return(response_list)
-}
-
-get_age <- Vectorize(function(responses) {
-  responses <- split_responses(responses)
-  if(responses[AGE-1] != "A0") {warnings("cannot find age answer")}
-  else{return (responses[AGE])}
-})
-
-get_gender <- Vectorize(function(responses) {
-  responses <- split_responses(responses)
-  if(responses[GENDER-1] != "A1") {warnings("cannot find gender answer")}
-  else{return (responses[GENDER])}
-})
-
-df.age_gender_E <- df.demog_E %>%
-  filter(variable_type == "demog_age_gender_ethnic") %>%
-  select(subject, responses) %>%
-  mutate(age = as.numeric(get_age(responses))) %>%
-  mutate(age = as.numeric(age)) %>%
-  mutate(gender = get_gender(responses))
-
-df.age_gender_E_summ <- df.age_gender_E %>%
-  summarize(mean_age = mean(age), 
-            median_age = median(age), 
-            sd_age = sd(age))
-```
-
-```{r loading data V explore, include=F}
-df.resp_V <- read.csv("../../data/data_V_0530.csv") %>%
-  select(-X)
-
-# check for participants who completed the entire experiment. Because the experiment is
-# quite long, some participants decide to come back afterwards, so there are a few files
-# that are recorded as incomplete. 
-df.ppts_finished_V <- df.resp_V %>% 
-  group_by(subject) %>%
-  summarize(finished = ifelse("demo-final" %in% unique(variable_type), "yes", "no")) %>%
-  filter(finished == "yes")
-
-df.resp_V <- df.resp_V %>%
-  filter(subject %in% df.ppts_finished_V$subject)
-
-df.ppts_att_V <- df.resp_V %>%
-  filter(stim_type == "attention check") %>%
-  mutate(correct_response = strsplit(cue, "Chọn ")) %>%
-  mutate(correct_response = sapply(correct_response, "[[", 2)) %>%
-  mutate(pass_att_check = ifelse(responses == correct_response, 1, 0)) %>%
-  group_by(subject) %>%
-  summarize(pass_att_check_percent = mean(pass_att_check)) %>%
-  filter(pass_att_check_percent >= 0.8)
-
-df.resp_V <- df.resp_V %>%
-  filter(subject %in% df.ppts_att_V$subject) #73
-```
-
-```{r exclusion V explore, include = F}
-#non-native speaker
-split_responses_demog <- function(responses) {
-  responses <- as.character(responses)
-  response_list <- unlist(strsplit(responses, ',|:'))
-  response_list <- response_list[seq(1, length(response_list))]
-  response_list <- gsub("}", "", response_list)
-  response_list <- gsub("\"", "", response_list)
-  return(response_list)
-}
-
-NATIVE_LANG = 2
-get_native_lang <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  if(responses[NATIVE_LANG-1] != "{firstlanguage") 
-    {warnings("cannot find native language answer")}
-  else
-    {return (responses[NATIVE_LANG])}
-})
-
-df.ppts_non_native_lang_V <- df.resp_V %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_language") %>%
-  mutate(native_speaker = get_native_lang(responses)) %>%
-  filter(native_speaker == "Không")
-
-ppts_non_native_lang_V = unique(df.ppts_non_native_lang_V$subject)
-percent_dropped = length(ppts_non_native_lang_V) / length(unique(df.resp_V$subject))
-percent_dropped #0
-
-#fluent in English
-SPEAKER = 2
-SPEAKING = 23
-UNDERSTANDING = 46
-
-get_speaker <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[SPEAKER])
-})
-
-get_fluency_speaking <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[SPEAKING])
-})
-
-get_fluency_understanding <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[UNDERSTANDING])
-})
-
-df.lang_en_V <- df.resp_V %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_language_en") %>%
-  mutate(en_speaker = get_speaker(responses))
-
-df.lang_en_fluency_V <- df.resp_V %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_conditional_language_en_fluency") %>%
-  mutate(en_fluency_sp = as.numeric(get_fluency_speaking(responses))) %>%
-  mutate(en_fluency_ud = as.numeric(get_fluency_understanding(responses)))
-
-df.lang_en_V <- full_join(df.lang_en_V, 
-                          df.lang_en_fluency_V, 
-                          by = "subject") %>%
-  select(subject, en_speaker, en_fluency_sp, en_fluency_ud) %>%
-  filter(en_speaker == "Có",
-         en_fluency_sp > 4, 
-         en_fluency_ud > 4)
-
-ppts_en_speaker_V = unique(df.lang_en_V$subject) #4
-percent_dropped = length(ppts_en_speaker_V) / length(unique(df.resp_V$subject))
-percent_dropped #0.6861314 # do not use this criterion
-
-df.lang_zh_V <- df.resp_V %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_language_cn") %>%
-  mutate(zh_speaker = get_speaker(responses))
-
-df.lang_zh_fluency_V <- df.resp_V %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_conditional_language_cn_fluency") %>%
-  mutate(zh_fluency_sp = as.numeric(get_fluency_speaking(responses))) %>%
-  mutate(zh_fluency_ud = as.numeric(get_fluency_understanding(responses)))
-
-df.lang_zh_V <- full_join(df.lang_zh_V, 
-                          df.lang_zh_fluency_V, 
-                          by = "subject") %>%
-  select(subject, zh_speaker, zh_fluency_sp, zh_fluency_ud) %>%
-  filter(zh_speaker == "Có",
-         zh_fluency_sp > 4, 
-         zh_fluency_ud > 4)
-
-ppts_zh_speaker_V = unique(df.lang_zh_V$subject) #4
-percent_dropped = length(ppts_zh_speaker_V) / length(unique(df.resp_V$subject))
-percent_dropped #0.05839416
-
-#have lived outside the sample country for more than 2 years
-#have travelled extensively (more than 6 international experiences of 2 days or longer) 
-YEARSABROAD = 2
-OVERSEAEXP = 4
-
-get_lived_abroad <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[YEARSABROAD])
-})
-
-get_oversea_exp <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[OVERSEAEXP])
-})
-
-df.abroad_V <- df.resp_V %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_oversea_experience") %>%
-  mutate(lived_abroad = get_lived_abroad(responses)) %>%
-  mutate(oversea_exp = get_oversea_exp(responses))
-
-df.lived_abroad_V <- df.abroad_V %>%
-  filter(lived_abroad == "Có")
-
-ppts_lived_abroad_V = unique(df.lived_abroad_V$subject)
-percent_dropped = length(ppts_lived_abroad_V) / length(unique(df.resp_V$subject))
-percent_dropped #0.1094891
-
-df.oversea_exp_V <- df.abroad_V %>%
-  filter(oversea_exp == "6 lần trở lên")
-
-ppts_oversea_exp_V = unique(df.oversea_exp_V$subject) #77
-percent_dropped = length(ppts_oversea_exp_V) / length(unique(df.resp_V$subject))
-percent_dropped #0.1094891
-
-df.resp_V <- df.resp_V %>%
-  filter(!(subject %in% ppts_non_native_lang_V),
-         !(subject %in% ppts_oversea_exp_V), 
-         !(subject %in% ppts_zh_speaker_V),
-         !(subject %in% ppts_lived_abroad_V))
-
-length(unique(df.resp_V$subject))  #110
-```
-
-```{r demog_V explore, include = F}
-demog <- c("demog-dropdown", "demog-multi-choice", "demog-free-response", "demog-multi-select")
-df.demog_V <- df.resp_V %>%
-  filter(trial_type %in% demog)
-
-AGE = 97 #index for age answer
-GENDER = 115 #index for gender answer
-split_responses <- function(responses) {
-  responses <- as.character(responses)
-  response_list <- unlist(strsplit(responses, ',|:'))
-  response_list <- response_list[seq(1, length(response_list))]
-  response_list <- gsub("}", "", response_list)
-  response_list <- gsub("\"", "", response_list)
-  return(response_list)
-}
-
-get_age <- Vectorize(function(responses) {
-  responses <- split_responses(responses)
-  if(responses[AGE-1] != "A0") {warnings("cannot find age answer")}
-  else{return (responses[AGE])}
-})
-
-get_gender <- Vectorize(function(responses) {
-  responses <- split_responses(responses)
-  if(responses[GENDER-1] != "A1") {warnings("cannot find gender answer")}
-  else{return (responses[GENDER])}
-})
-
-df.age_gender_V <- df.demog_V %>%
-  filter(variable_type == "demog_age_gender_ethnic") %>%
-  select(subject, responses) %>%
-  mutate(age = as.numeric(get_age(responses))) %>%
-  mutate(age = as.numeric(age)) %>%
-  mutate(gender = get_gender(responses))
-
-df.age_gender_V_summ <- df.age_gender_V %>%
-  summarize(mean_age = mean(age), 
-            median_age = median(age), 
-            sd_age = sd(age))
-```
-
-```{r loading data M explore, warning=FALSE, include=F}
-df.resp_M <- read.csv("../../data/data_M_0530.csv") %>%
-  select(-X)
-
-# check for participants who completed the entire experiment. Because the experiment is
-# quite long, some participants decide to come back afterwards, so there are a few files
-# that are recorded as incomplete. 
-df.ppts_finished_M <- df.resp_M %>% 
-  group_by(subject) %>%
-  summarize(finished = ifelse("demo-final" %in% unique(variable_type), "yes", "no")) %>%
-  filter(finished == "yes")
-
-df.resp_M <- df.resp_M %>%
-  filter(subject %in% df.ppts_finished_M$subject)
-
-df.ppts_att_M <- df.resp_M %>%
-  filter(stim_type == "attention check") %>%
-  mutate(correct_response = strsplit(cue, "选择")) %>%
-  mutate(correct_response = sapply(correct_response, "[[", 2)) %>%
-  mutate(correct_response = str_replace_all(correct_response, "“", "")) %>%
-  mutate(correct_response = str_replace_all(correct_response, "”", "")) %>%
-  mutate(pass_att_check = ifelse(responses == correct_response, 1, 0)) %>%
-  group_by(subject) %>%
-  summarize(pass_att_check_percent = mean(pass_att_check)) %>%
-  filter(pass_att_check_percent >= 0.8)
-
-df.resp_M <- df.resp_M %>%
-  filter(subject %in% df.ppts_att_M$subject) 
-```
-
-```{r exclusion M explore, include = F, warning = F}
-#non-native speaker
-split_responses_demog <- function(responses) {
-  responses <- as.character(responses)
-  response_list <- unlist(strsplit(responses, ',|:'))
-  response_list <- response_list[seq(1, length(response_list))]
-  response_list <- gsub("}", "", response_list)
-  response_list <- gsub("\"", "", response_list)
-  return(response_list)
-}
-
-NATIVE_LANG = 2
-get_native_lang <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  if(responses[NATIVE_LANG-1] != "{firstlanguage") 
-    {warnings("cannot find native language answer")}
-  else
-    {return (responses[NATIVE_LANG])}
-})
-
-df.ppts_non_native_lang_M <- df.resp_M %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_language") %>%
-  mutate(native_speaker = get_native_lang(responses)) %>%
-  filter(native_speaker == "不是")
-
-ppts_non_native_lang_M = unique(df.ppts_non_native_lang_M$subject) #2
-percent_dropped = length(ppts_non_native_lang_M) / length(unique(df.resp_M$subject))
-percent_dropped #0.01149425
-
-#fluent in English
-SPEAKER = 2
-SPEAKING = 23
-UNDERSTANDING = 46
-
-get_speaker <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[SPEAKER])
-})
-
-get_fluency_speaking <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[SPEAKING])
-})
-
-get_fluency_understanding <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[UNDERSTANDING])
-})
-
-df.lang_en_M <- df.resp_M %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_language_en") %>%
-  mutate(en_speaker = get_speaker(responses))
-
-df.lang_en_fluency_M <- df.resp_M %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_conditional_language_en_fluency") %>%
-  mutate(en_fluency_sp = as.numeric(get_fluency_speaking(responses))) %>%
-  mutate(en_fluency_ud = as.numeric(get_fluency_understanding(responses)))
-
-df.lang_en_M <- full_join(df.lang_en_M, 
-                          df.lang_en_fluency_M, 
-                          by = "subject") %>%
-  select(subject, en_speaker, en_fluency_sp, en_fluency_ud) %>%
-  filter(en_speaker == "能",
-         en_fluency_sp > 4, 
-         en_fluency_ud > 4)
-
-ppts_en_speaker_M = unique(df.lang_en_M$subject) #50
-percent_dropped = length(ppts_en_speaker_M) / length(unique(df.resp_M$subject))
-percent_dropped #0.3850575 # will not use this criterion
-
-df.lang_vi_M <- df.resp_M %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_language_vi") %>%
-  mutate(vi_speaker = get_speaker(responses))
-
-df.lang_vi_fluency_M <- df.resp_M %>%
-  filter(variable_type == "demog_conditional_language_vi_fluency") %>%
-  mutate(vi_fluency_sp = as.numeric(get_fluency_speaking(responses))) %>%
-  mutate(vi_fluency_ud = as.numeric(get_fluency_understanding(responses)))
-
-df.lang_vi_M <- full_join(df.lang_vi_M, 
-                          df.lang_vi_fluency_M, 
-                          by = "subject") %>%
-  select(subject, vi_speaker, vi_fluency_sp, vi_fluency_ud) %>%
-  filter(vi_speaker == "能",
-         vi_fluency_sp > 4, 
-         vi_fluency_ud > 4)
-
-ppts_vi_speaker_M = unique(df.lang_vi_M$subject) #50
-percent_dropped = length(ppts_vi_speaker_M) / length(unique(df.resp_M$subject))
-percent_dropped #0
-
-#have lived outside the sample country for more than 2 years
-#have travelled extensively (more than 6 international experiences of 2 days or longer) 
-YEARSABROAD = 2
-OVERSEAEXP = 4
-
-get_lived_abroad <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[YEARSABROAD])
-})
-
-get_oversea_exp <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[OVERSEAEXP])
-})
-
-df.abroad_M <- df.resp_M %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_oversea_experience") %>%
-  mutate(lived_abroad = get_lived_abroad(responses)) %>%
-  mutate(oversea_exp = get_oversea_exp(responses))
-
-df.lived_abroad_M <- df.abroad_M %>%
-  filter(lived_abroad == "是")
-
-ppts_lived_abroad_M = unique(df.lived_abroad_M$subject) #23
-percent_dropped = length(ppts_lived_abroad_M) / length(unique(df.resp_M$subject))
-percent_dropped # 0.1551724
-
-df.oversea_exp_M <- df.abroad_M %>%
-  filter(oversea_exp == "六段或更多国际经历")
-
-ppts_oversea_exp_M = unique(df.oversea_exp_M$subject) #0
-percent_dropped = length(ppts_oversea_exp_M) / length(unique(df.resp_M$subject))
-percent_dropped #0.03448276
-
-df.resp_M <- df.resp_M %>%
-  filter(!(subject %in% ppts_non_native_lang_M),
-         !(subject %in% ppts_lived_abroad_M),
-         !(subject %in% ppts_vi_speaker_M),
-         !(subject %in% ppts_oversea_exp_M),)
-
-length(unique(df.resp_M$subject)) #143
-```
-
-```{r demog_M explore, include = F}
-demog <- c("demog-dropdown", "demog-multi-choice", "demog-free-response", "demog-multi-select")
-df.demog_M <- df.resp_M %>%
-  filter(trial_type %in% demog) 
-#write.csv(data_demog, "data_anon_demog_0201.csv")
-
-AGE = 97 #index for age answer
-GENDER = 115 #index for gender answer
-split_responses <- function(responses) {
-  responses <- as.character(responses)
-  response_list <- unlist(strsplit(responses, ',|:'))
-  response_list <- response_list[seq(1, length(response_list))]
-  response_list <- gsub("}", "", response_list)
-  response_list <- gsub("\"", "", response_list)
-  return(response_list)
-}
-
-get_age <- Vectorize(function(responses) {
-  responses <- split_responses(responses)
-  if(responses[AGE-1] != "A0") {warnings("cannot find age answer")}
-  else{return (responses[AGE])}
-})
-
-get_gender <- Vectorize(function(responses) {
-  responses <- split_responses(responses)
-  if(responses[GENDER-1] != "A1") {warnings("cannot find gender answer")}
-  else{return (responses[GENDER])}
-})
-
-df.age_gender_M <- df.demog_M %>%
-  filter(variable_type == "demog_age_gender_ethnic") %>%
-  select(subject, responses) %>%
-  mutate(age = as.numeric(get_age(responses))) %>%
-  mutate(age = as.numeric(age)) %>%
-  mutate(gender = get_gender(responses))
-
-df.age_gender_M_summ <- df.age_gender_M %>%
-  summarize(mean_age = mean(age), 
-            median_age = median(age), 
-            sd_age = sd(age))
-```
-
-With the new exclusion criteria, we excluded `r length(unique(df.ppts_finished_E$subject)) - length(unique(df.ppts_att_E$subject))` US participants, `r length(unique(df.ppts_finished_V$subject)) - length(unique(df.ppts_att_V$subject))` VN participants, and `r length(unique(df.ppts_finished_M$subject)) - length(unique(df.ppts_att_M$subject))` CN participants who did not answer more than 2 attention checks correctly.
-We then applied the 4 criteria that aim to retain only participants who are influenced by one culture: (1) non-native speakers of English and Vietnamese, respectively, (2) fluent in at least one of the other two study languages (Vietnamese for US participants, English for Vietnamese participants and Chinese participants), (3) have lived outside of the test country (US, Vietnam, or China) for more than two years, and (4) have significant international experience (more than 6 international experiences of 2 days or longer.) We did not use a particular criterion for a language if it would exclude 25% or more of any one sample.
-In this round of exclusion, we excluded `r length(unique(df.ppts_att_E$subject)) - length(unique(df.resp_E$subject))` US, `r length(unique(df.ppts_att_V$subject)) - length(unique(df.resp_V$subject))` VN participants, and `r length(unique(df.ppts_att_M$subject)) - length(unique(df.resp_M$subject))` CN participants.
-After these exclusions, the US sample included `r length(unique(df.resp_E$subject))` participants (`r df.age_gender_E %>% filter(gender == "Male") %>% count()`M, `r df.age_gender_E %>% filter(gender == "Female") %>% count()`F, `r df.age_gender_E %>% filter(gender == "Non-binary") %>% count()` non-binary, `r df.age_gender_E %>% filter(gender == "Decline to answer") %>% count()` other), with mean age = `r round(df.age_gender_E_summ$mean_age, 2)` (SD = `r round(df.age_gender_E_summ$sd_age, 2)`) and median age = `r df.age_gender_E_summ$median_age`.
-The VN sample included `r length(unique(df.resp_V$subject))` participants (`r df.age_gender_V %>% filter(gender == "Nam") %>% count()`M, `r df.age_gender_V %>% filter(gender == "Nữ") %>% count()`F), with mean age = `r round(df.age_gender_V_summ$mean_age, 2)` (SD = `r round(df.age_gender_V_summ$sd_age, 2)`) and median age = `r df.age_gender_V_summ$median_age`.
-The CN sample included `r length(unique(df.resp_M$subject))` participants (`r df.age_gender_M %>% filter(gender == "男性") %>% count()`M, `r df.age_gender_M %>% filter(gender == "女性") %>% count()`F), with mean age = `r round(df.age_gender_M_summ$mean_age, 2)` (SD = `r round(df.age_gender_M_summ$sd_age, 2)`) and median age = `r df.age_gender_M_summ$median_age`.
-
-```{r corpus explore, include = F}
-df.corpus_E <- read.csv("../../data/corpusE_cos.csv") %>%
-  rename(tax_frequency_E = tax.frequency,
-         theme_frequency_E = theme.frequency,
-         tax_cosine_E = Tax.cosine_dist, 
-         theme_cosine_E = Theme.cosine_dist,
-         tax_cosine_sim_E = Tax.cosine_sim,
-         theme_cosine_sim_E = Theme.cosine_sim,
-         tax_match_E = Tax.match,
-         theme_match_E = Theme.match, 
-         cue_E = Cue)
-
-df.corpus_V <- read.csv("../../data/corpusV_cos.csv") %>%
-  rename(tax_frequency_V = tax.frequency,
-         theme_frequency_V = theme.frequency,
-         tax_cosine_V = Tax.cosine_dist, 
-         theme_cosine_V = Theme.cosine_dist,
-         tax_cosine_sim_V = Tax.cosine_sim,
-         theme_cosine_sim_V = Theme.cosine_sim,
-         tax_match_V = Tax.match,
-         theme_match_V = Theme.match, 
-         cue_V = Cue)
-
-df.corpus_M <- read.csv("../../data/corpusM_cos.csv") %>%
-  rename(tax_frequency_M = tax.frequency,
-         theme_frequency_M = theme.frequency,
-         tax_cosine_M = Tax.cosine_dist, 
-         theme_cosine_M = Theme.cosine_dist,
-         tax_cosine_sim_M = Tax.cosine_sim,
-         theme_cosine_sim_M = Theme.cosine_sim,
-         tax_match_M = Tax.match,
-         theme_match_M = Theme.match, 
-         cue_M = Cue)
-```
-
-```{r full corpus explore, M freqs is incorrect, include=F}
-df.corpus <- left_join(df.corpus_E, df.corpus_V, by = "Cue_renamed")
-df.corpus <- left_join(df.corpus, df.corpus_M, by = "Cue_renamed")
-
-#replacing any 0 raw counts with epsilon
-df.corpus <- df.corpus %>%
-  mutate(tax_frequency_E = ifelse(tax_frequency_E == 0, 
-                                  .Machine$double.eps, tax_frequency_E),
-         theme_frequency_E = ifelse(theme_frequency_E == 0, 
-                                  .Machine$double.eps, theme_frequency_E),
-         tax_frequency_V = ifelse(tax_frequency_V == 0, 
-                                  .Machine$double.eps, tax_frequency_V),
-         theme_frequency_V = ifelse(theme_frequency_V == 0, 
-                                  .Machine$double.eps, theme_frequency_V))
-
-```
-
-```{r corpus - frequency explore, include = F}
-#find triads_omit, used whenever analysis uses raw collocates 
-df.corpus_E_freq <- df.corpus_E %>%
-  select(Cue_renamed, cue_E, tax_match_E, theme_match_E, tax_frequency_E, theme_frequency_E)
-corpus_E_omit <- df.corpus_E_freq %>%
-  filter(tax_frequency_E == 0 & theme_frequency_E == 0)
-
-df.corpus_V_freq <- df.corpus_V %>%
-  select(Cue_renamed, cue_V, tax_match_V, theme_match_V, tax_frequency_V, theme_frequency_V)
-corpus_V_omit <- df.corpus_V_freq %>% 
-  filter(tax_frequency_V == 0 & theme_frequency_V == 0)
-
-triads_omit <- append(corpus_E_omit$Cue_renamed, corpus_V_omit$Cue_renamed)
-
-df.corpus_freq <- left_join(df.corpus_E_freq, df.corpus_V_freq, by = "Cue_renamed")
-```
-
-```{r corpus - cosine explore, include = F}
-#mainly for sanity checking and so that there is a parallel df to df.corpus_freq
-df.corpus_E_cos <- df.corpus_E %>%
-  select(Cue_renamed, cue_E, tax_match_E, theme_match_E, 
-         tax_cosine_E, theme_cosine_E,
-         tax_cosine_sim_E, theme_cosine_sim_E)
-
-df.corpus_V_cos <- df.corpus_V %>%
-  select(Cue_renamed, cue_V, tax_match_V, theme_match_V, tax_cosine_V, theme_cosine_V,
-         tax_cosine_sim_V, theme_cosine_sim_V)
-
-df.corpus_M_cos <- df.corpus_M %>%
-  select(Cue_renamed, cue_M, tax_match_M, theme_match_M, tax_cosine_M, theme_cosine_M, 
-         tax_cosine_sim_M, theme_cosine_sim_M)
-
-df.corpus_cos <- left_join(df.corpus_E_cos, df.corpus_V_cos, by = "Cue_renamed")
-df.corpus_cos <- left_join(df.corpus_cos, df.corpus_M_cos, by = "Cue_renamed")
-```
-
-```{r getting triads from the 3 languages explore, include = F}
-#combine response and corpus data
-df.triad_E <- df.resp_E %>%
-  filter(stim_type == "triad",
-         responses != "NA")
-triad_cues_E <- read.csv("../../data/cue_renamed_E.csv")
-df.triad_E <- left_join(df.triad_E, triad_cues_E, by = c("cue", "top_opt", "bottom_opt"))
-df.triad_E <- inner_join(df.triad_E, df.corpus, by = "Cue_renamed")
-
-df.triad_E <- df.triad_E %>%
-  mutate(responses_theme = ifelse(responses == theme_match_E, 1, 0),
-         language = "English",
-         country = "US") %>%
-  select(subject, rt, Cue_renamed, cue, top_opt, bottom_opt, 
-         responses, responses_theme, country, language,
-         tax_match_E, theme_match_E, tax_match_V, theme_match_V, tax_match_M, theme_match_M,
-         tax_frequency_E, theme_frequency_E, tax_frequency_V, theme_frequency_V, tax_frequency_M, theme_frequency_M,
-         tax_cosine_E, theme_cosine_E, tax_cosine_V, theme_cosine_V, tax_cosine_M, theme_cosine_M,
-         tax_cosine_sim_E, theme_cosine_sim_E, tax_cosine_sim_V, theme_cosine_sim_V, tax_cosine_sim_M, theme_cosine_sim_M)
-
-df.triad_V <- df.resp_V %>%
-  filter(stim_type == "triad",
-         responses != "NA")
-triad_cues_V <- read.csv("../../data/cue_renamed_V.csv")
-df.triad_V <- left_join(df.triad_V, triad_cues_V, by = c("cue", "top_opt", "bottom_opt"))
-df.triad_V <- inner_join(df.triad_V, df.corpus, by = "Cue_renamed")
-
-df.triad_V <- df.triad_V %>%
-  mutate(responses_theme = ifelse(responses == theme_match_V, 1, 0),
-         language = "Vietnamese", 
-         country = "Vietnam") %>%
-  select(subject, rt, Cue_renamed, cue, top_opt, bottom_opt, 
-         responses, responses_theme, country, language,
-         tax_match_E, theme_match_E, tax_match_V, theme_match_V, tax_match_M, theme_match_M,
-         tax_frequency_E, theme_frequency_E, tax_frequency_V, theme_frequency_V, tax_frequency_M, theme_frequency_M,
-         tax_cosine_E, theme_cosine_E, tax_cosine_V, theme_cosine_V, tax_cosine_M, theme_cosine_M,
-         tax_cosine_sim_E, theme_cosine_sim_E, tax_cosine_sim_V, theme_cosine_sim_V, tax_cosine_sim_M, theme_cosine_sim_M)
-
-df.triad_M <- df.resp_M %>%
-  filter(stim_type == "triad",
-         responses != "NA")
-triad_cues_M <- read.csv("../../data/cue_renamed_M.csv")
-df.triad_M <- left_join(df.triad_M, triad_cues_M, by = c("cue", "top_opt", "bottom_opt"))
-df.triad_M <- inner_join(df.triad_M, df.corpus, by = "Cue_renamed")
-
-df.triad_M <- df.triad_M %>%
-  mutate(responses_theme = ifelse(responses == theme_match_M, 1, 0),
-         language = "Mandarin", 
-         country = "China") %>%
-  select(subject, rt, Cue_renamed, cue, top_opt, bottom_opt, 
-         responses, responses_theme, country, language,
-         tax_match_E, theme_match_E, tax_match_V, theme_match_V, tax_match_M, theme_match_M,
-         tax_frequency_E, theme_frequency_E, tax_frequency_V, theme_frequency_V, tax_frequency_M, theme_frequency_M,
-         tax_cosine_E, theme_cosine_E, tax_cosine_V, theme_cosine_V, tax_cosine_M, theme_cosine_M,
-         tax_cosine_sim_E, theme_cosine_sim_E, tax_cosine_sim_V, theme_cosine_sim_V, tax_cosine_sim_M, theme_cosine_sim_M)
-
-#calculate proportion for raw frequencies and cosine distance
-df <- rbind(df.triad_E, df.triad_V)
-df <- rbind(df, df.triad_M) %>%
-  mutate(theme_freq_prop_E = theme_frequency_E / (theme_frequency_E + tax_frequency_E),
-         theme_freq_prop_V = theme_frequency_V / (theme_frequency_V + tax_frequency_V), 
-         theme_freq_prop_M = theme_frequency_M / (theme_frequency_M + tax_frequency_M), 
-         theme_cosine_prop_E = theme_cosine_E / (theme_cosine_E + tax_cosine_E),
-         theme_cosine_prop_V = theme_cosine_V / (theme_cosine_V + tax_cosine_V), 
-         theme_cosine_prop_M = theme_cosine_M / (theme_cosine_M + tax_cosine_M)) %>%
-  rename(triad = Cue_renamed)
-```
-
-```{r country effect - explore, warning=FALSE, include=FALSE, paged.print=TRUE}
-df.country <- df %>%
-  group_by(subject, country) %>%
-  summarize(theme_resp_percent = mean(responses_theme, na.rm = T))
-
-df.country_sum <- df.country %>%
-  group_by(country) %>%
-  summarize(mean_theme_resp_percent = mean(theme_resp_percent), 
-            sd_theme_resp_percent = sd(theme_resp_percent))
-
-fit.country = glmer(responses_theme ~ country + (1 | subject) + (country | triad), 
-                    data = df, 
-                    family = "binomial")
-summary(fit.country) 
-fit.country.anova = Anova(fit.country, type=3)
-
-fit.country_EN_VN = glmer(responses_theme ~ country + (1 | subject) + (country | triad), 
-                    data = df %>% filter(country != "China"),
-                    family = "binomial")
-summary(fit.country_EN_VN) 
-```
-
-```{r echo=FALSE, warning=FALSE, fig.cap="Proportion of thematic responses by country, with a less stringent attention check criterion.
-We did not find any significant differences from the analysis reported above with a more stringent criterion."}
-
-ggplot(df.country,
-       mapping = aes(x = country, 
-                     y = theme_resp_percent, 
-                     color = country)) +
-  geom_violin() +
-  geom_jitter(height = 0, 
-              alpha = 0.3) +  
-  stat_summary(fun.data = "mean_cl_boot", 
-               geom = "pointrange") + 
-  labs(y = "Proportion Thematic Chosen", 
-       x = "Country", 
-       color = "Country") + 
-  scale_color_manual(values=c("#D63230", "#1C77C3", "#F39237"))
-```
-
-There is no significant difference in this round of analysis compared to the one reported above (with more stringent attention check criterion).
-That is, we still observed a significant effect of country on proportion of thematic responses ($\chi^2$(`r fit.country.anova["country", "Df"]`) = `r round(fit.country.anova["country", "Chisq"], 2)`, p < .001), but this effect is driven by only the difference between US and China response ($\beta$ = `r round(fixef(fit.country)["countryUS"], 2)`, p < .001).
-There is no statistical difference between the Vietnam and China response ($\beta$ = `r round(fixef(fit.country)["countryVietnam"], 2)`, p = `r round(as.data.frame(summary(fit.country)[["coefficients"]])["countryVietnam", "Pr(>|z|)"], 3)`), and the US and Vietnam response ($\beta$ = `r round(fixef(fit.country_EN_VN)["countryVietnam"], 2)`, p = `r round(as.data.frame(summary(fit.country)[["coefficients"]])["countryVietnam", "Pr(>|z|)"], 3)`).
-
-# Discussion
-In this paper, we consider whether statistics of the language environment can account for cross-cultural differences in a classic similarity judgment paradigm, as an alternative to the view that members of different cultures vary in their conception of similarity.
-
-We first tested the generality of a cultural account which holds that people from Western and East Asian cultures tend to conceive of similarity in more taxonomic and thematic ways, respectively, and respond accordingly in categorization tasks such as ours.
-While we managed to replicate the previously documented contrast between English speakers in the US and Mandarin Chinese speakers from East Asia (mainland China, Taiwan, Hong Kong, and Singapore), we do not extend this contrast to our sample of Vietnamese speakers in Vietnam and English speakers in the US.
-This finding suggests some limitations on the generality of this cultural account.
-
-We did find some signatures of language specificity in our analysis, such as the large positive correlation between similarity judgments of each country and the respective corpus statistics, and how each corpus statistics are good predictors for corresponding country's similarity judgments.
-However, this is potentially due to the high correlation between corpus statistics of English, Vietnamese and Mandarin.
-We find even stronger evidence for consistency across the three groups, with substantive overlapping predictions across the corpus models, highly similar responding across the experiments, and a correspondingly high fit in cross-language comparisons between models and data.
-
-```{r include=FALSE}
-fit.country_no_triad <- glmer(responses_theme ~ country + (1 | subject), 
-                              data = df_main_analysis, 
-                              family = "binomial")
-
-fit.country = glmer(responses_theme ~ country + (1 | subject) + (country | triad), 
-                    data = df_main_analysis, 
-                    family = "binomial")
-summary(fit.country)
-
-fit.no_triad_compare <- anova(fit.country, fit.country_no_triad, type = 3)
-```
-
-There are some suggestions that the current approach can predict triad-specific cross-cultural effects.
-First of all, an ANOVA model comparison showed that adding a random effect term for varying slope by country and varying intercept by triad to the model produces a significant better fit than the identical model without this random effect term included as a predictor ($\chi^2$(`r fit.no_triad_compare["fit.country", "Df"]`) = `r round(fit.no_triad_compare["fit.country", "Chisq"], 2)`, p < .001)
-
-Anecdotally, we show below some examples of triads that show contrasting difference in the magnitude of difference in thematic responses between countries.
-As a review, the overall result across all triads showed that there was significant difference between US and China responding, and no significant differences between US and Vietnam or China and Vietnam responding.
-However, we observed that for the triad "cow-grass-chicken," there were significant differences between US and China, and US and Vietnam responding.
-There was no significant difference between China and Vietnam responding.
-For the triad "spoon-sugar-fork," there were significant difference between China and US, and China and Vietnam responding, but no significant difference between US and Vietnam.
-For the triad "hair-comb-beard," there were no significant differences pairwise across the three cultural contexts.
-This suggests that there are triad-specific cross-cultural effects in play.
-Beyond emphasizing the importance of including triad predictors as a random effect, this finding suggests that, firstly, future similar studies need to report triads that are used, as the triads used can affect results (for example, if a study only includes triads where China and US responding are significantly different, it would be more likely to conclude that Chinese and US cultures hold different notions of similarity).
-Secondly, that future studies can look more deeply into which groups of triads are driving the US-China responding difference.
-For example, triads belonging to different semantic neighborhoods might be influencing cross-cultural responding in different ways.
-
-```{r include=FALSE}
-df.country_item <- df_main_analysis %>%
-  filter(triad == "hair")
-
-plot.hair <- ggplot(df.country_item,
-       mapping = aes(x = factor(country, levels=c("China", "US", "Vietnam")), 
-                     y = responses_theme, 
-                     color = factor(country, levels=c("China", "US", "Vietnam")))) +
-  geom_jitter(stat = "identity", alpha  = .5) +
-  labs(y = "Proportion Thematic Chosen (hair: beard / comb)",  
-       x = "Country", 
-       color = "Country") + 
-  stat_summary(fun.data = "mean_cl_boot", 
-               geom = "pointrange") + 
-  scale_y_continuous(limits=c(0.0, 1.0), oob = scales::squish) + 
-  scale_fill_manual(values=c("#D63230", "#1C77C3", "#F39237")) +  
-  scale_color_manual(values=c("#D63230", "#1C77C3", "#F39237"))  + 
-  theme(axis.title = element_text(size=rel(0.75)))
-```
-
-```{r include=FALSE}
-df.country_item <- df_main_analysis %>%
-  filter(triad == "spoon2")
-
-plot.spoon2 <- ggplot(df.country_item,
-       mapping = aes(x = factor(country, levels=c("China", "US", "Vietnam")), 
-                     y = responses_theme, 
-                     color = factor(country, levels=c("China", "US", "Vietnam")))) +
-  geom_jitter(stat = "identity", alpha  = .5) +
-  labs(y = "Proportion Thematic Chosen (spoon: fork / sugar)",  
-       x = "Country", 
-       color = "Country") + 
-  stat_summary(fun.data = "mean_cl_boot", 
-               geom = "pointrange") + 
-  scale_y_continuous(limits=c(0.0, 1.0), oob = scales::squish) + 
-  scale_fill_manual(values=c("#D63230", "#1C77C3", "#F39237")) +  
-  scale_color_manual(values=c("#D63230", "#1C77C3", "#F39237")) + 
-  theme(legend.position = "none") + 
-  theme(axis.title = element_text(size=rel(0.75)))
-```
-
-```{r include = FALSE}
-#show 1 triad
-
-df.country_item <- df_main_analysis %>%
-  filter(triad == "cow2")
-
-df.country_item_summ <- df_main_analysis %>%
-  group_by(triad, country) %>%
-  summarize(theme_resp_percent = mean(responses_theme, na.rm = T)) %>%
-  filter(triad == "cow2")
-
-plot.cow2 <- ggplot(df.country_item,
-       mapping = aes(x = factor(country, levels=c("China", "US", "Vietnam")), 
-                     y = responses_theme, 
-                     color = factor(country, levels=c("China", "US", "Vietnam")))) +
-  geom_jitter(stat = "identity", alpha  = .5) +
-  labs(y = "Proportion Thematic Chosen (cow: chicken / grass)",  
-       x = "Country", 
-       color = "Country") + 
-  stat_summary(fun.data = "mean_cl_boot", 
-               geom = "pointrange") + 
-  scale_y_continuous(limits=c(0.0, 1.0), oob = scales::squish) + 
-  scale_fill_manual(values=c("#D63230", "#1C77C3", "#F39237")) +  
-  scale_color_manual(values=c("#D63230", "#1C77C3", "#F39237")) + 
-  theme(legend.position = "none") + 
-  theme(axis.title = element_text(size=rel(0.75)))
-# 
-# +  
-#   geom_bar(data = df.country_item_summ, 
-#            mapping = aes(x = factor(country, levels=c("China", "US", "Vietnam")), 
-#                           y = theme_resp_percent, 
-#                          color = factor(country, levels=c("China", "US", "Vietnam"))), 
-#            stat='identity', alpha = .3, 
-#            fill=c("#D63230", "#1C77C3", "#F39237"))
-```
-
-```{r echo=FALSE, warning = FALSE, fig.width=8, fig.cap="Anecdotal evidence of triad-specific effects.
-Cow-grass-chicken shows significant differences between US-China responding, and between US-Vietnam responding.
-Spoon-sugar-fork shows only a significant difference between US-China responding.
-Hair-comb-beard does not show any significant differences in pairwise comparisons across the three countries."}
-plot.cow2 + plot.spoon2 + plot.hair + 
-    plot_layout(ncol = 3)
-```
-
-We also identified some data quality / quantity issues that are an obstacle to modeling similarity in Vietnamese and Mandarin.
-As stated above, we were not able to find a Mandarin corpus with raw co-occurrences that contains similar magnitude of number of sentences as our English corpus (COCA).
-Additionally, we could only retrieve fastText word vectors for Vietnamese and Mandarin that are trained on both Common Crawl and Wikipedia.
-63% of the articles on Vietnamese Wikipedia and 16% of the Chinese Wikipedia are bot translations from another language (compared to 3% of English Wikipedia).
-This would affect the quality of the word vectors trained on the Vietnamese and Chinese Wikipedia, potentially making them not reflecting the naturally-occurring lexical co-occurrence in the corresponding language.
-
-Our findings raise additional questions for future work: if not differences in taxonomic vs.
-thematic responding, then what differences drive the relativity effects previous studies have observed?
-To what extent are the relativity effects driven by language, and to what extent by culture?
-@Ji2004 established that culture-aligned differences in this paradigm exist, even when the test language is held constant, concluding that “it is culture (independent of the testing language) that led to different grouping styles” in their study.
-Our data provide a cautionary note to this conclusion, suggesting that semantic representations in bilinguals (see @Francis2005 for a review) may have the potential to provide an offline account for cross-context differences in similarity judgments, independent of test language.
-However, there are still many open questions for this account.
-How do semantic associations guide categorization?
-Can they explain taxonomic-thematic differences of the type reported by @Ji2004 and others?
-Can we provide a more specific computational account than the simple frequency model tested here?
-
-Despite these caveats, our findings here demonstrate the plausibility of an alternative perspective on cross-cultural accounts of language, thought, and similarity in the case of taxonomic and thematic reasoning: that it may be the input to similarity judgments, rather than the evaluative process or the conceptualization of similarity that produces variation in similarity reasoning across cultural and linguistic contexts.
-We hope this work provides a foundation for further research probing this question.
-
-[^footnote]:While we discuss cross-cultural variability at the level of countries or larger world areas, these are not cultural monoliths.
-For convenience, we operationalize culture at the level of country, based on where participants were raised.
-It is an open question whether performance in our participant populations (of relatively young and well-educated adults) is representative of the broader country.
-This is especially true for societies with substantial ethnic and cultural variation such as the US.
-We expect that our data is likely to underestimate variation both within and between the countries we sample from.
-
-\newpage
-
-# References
-
-\begingroup
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
-
-<div id="refs" custom-style="Bibliography"></div>
-\endgroup
-
-\newpage
-# Supplemental Information
-
-hi
-```{r echo=TRUE, fig.align="center", fig.cap=c("List of triads used"), fig.show="hold"}
-#include_graphics(c("../../data/SI_triads/SI_triads_1.jpg"))
-include_graphics(c("../../data/SI_triads/SI_triads_1.jpg",
-                   "../../data/SI_triads/SI_triads_2.jpg",
-                   "../../data/SI_triads/SI_triads_3.jpg",
-                   "../../data/SI_triads/SI_triads_4.jpg",
-                   "../../data/SI_triads/SI_triads_5.jpg"))
-```
+Adding cue given match (cue+match / match) OR match given cue (cue+match / cue) both improve the model significantly over only having thematic frequency prop, even though the additional term does not wipe out the effect of thematic proportion.
+Comparing between the cue given match and match given cue model yields null result.

### 2022-11-30 code/3_analysis/3_analysis_filler.Rmd
added a lot of analysis. prepared to move to coglink_cogsci

```{r setup, echo = FALSE, include = FALSE}
library("papaja")
library("knitr") # for knitting things
library("tidyverse") # for all things tidyverse
library("car")
library("lme4")
library("patchwork")
library("effsize")
library("dplyr")

# these options here change the formatting of how comments are rendered
opts_chunk$set(
  comment = "",
  results = "hold",
  fig.show = "hold")

# set the default ggplot theme 
theme_set(theme_classic())

r_refs("r-references.bib")
r_refs("references/packages.bib")

```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r incorporate base freq}
df <- read.csv("../../data/data_filler_USCNVN_ENZHVI.csv")
```

```{r correlation across China and US}
df.resp_by_country <- df %>%
  group_by(cue_id, country) %>%
  summarize(emp_theme_prop = mean(responses_word1))

df.resp_by_country <- pivot_wider(data = df.resp_by_country, 
                                  names_from = country, 
                                  values_from = emp_theme_prop)
plotUSCN = ggplot(data = df.resp_by_country,
                  mapping = aes(x = US, 
                                y = China, 
                                label = cue_id)) +
   geom_text() + 
   geom_smooth(method = "lm") +
   labs(x = "Proportion Word1 Chosen (US)", 
        y = "Proportion Word1 Chosen (China)") + 
   xlim(0, 1) + 
   ylim(0, 1) + 
  theme(axis.title = element_text(size=rel(0.75)))

plotUSVN = ggplot(data = df.resp_by_country,
                  mapping = aes(x = US, 
                                y = Vietnam, 
                                label = cue_id)) +
   geom_text() + 
   geom_smooth(method = "lm") +
   labs(x = "Proportion Word1 Chosen (US)", 
        y = "Proportion Word1 Chosen (Vietnam)") + 
   xlim(0, 1) + 
   ylim(0, 1)  + 
  theme(axis.title = element_text(size=rel(0.75)))

plotCNVN = ggplot(data = df.resp_by_country,
                  mapping = aes(x = Vietnam,
                                y = China, 
                                label = cue_id)) +
   geom_text() + 
   geom_smooth(method = "lm") +
   labs(x = "Proportion Word1 Chosen (Vietnam)", 
        y = "Proportion Word1 Chosen (China)") + 
   xlim(0, 1) + 
   ylim(0, 1)  + 
  theme(axis.title = element_text(size=rel(0.75)))

corr.USCN = apa_print(cor.test(df.resp_by_country$US, 
                  df.resp_by_country$China, na.rm=T))

corr.USVN = apa_print(cor.test(df.resp_by_country$US, 
                  df.resp_by_country$Vietnam, na.rm=T))

corr.CNVN = apa_print(cor.test(df.resp_by_country$China, 
                  df.resp_by_country$Vietnam, na.rm=T))
```

```{r warning = F, fig.width = 8, fig.cap="Correlation between proportion thematic chosen by US-China participants, US-Vietnam participants, and China-Vietnam participants. All three comparisons show strong correlation, suggesting a strong signal of universality across cultural contexts regarding similarity judgments"}
plotUSCN + plotUSVN + plotCNVN +
  plot_layout(ncol = 3)
```

```{r}
df.cue_country_freq <- df %>%
  group_by(cue_id, country, word1_match_frequency_prop_E, word1_match_frequency_prop_M, word1_match_frequency_prop_V) %>%
  summarize(emp_word1_prop = mean(responses_word1))
ggplot(data = df.cue_country_freq %>% filter(country == "US"), 
        mapping = aes(x = emp_word1_prop, 
                     y = word1_match_frequency_prop_E,
                     label = cue_id)) +
   geom_text() + 
   geom_smooth(method = "lm") +
   labs(x = "Proportion Word1 Chosen (US)", 
        y = "Proportion Word1 Predicted (English)") + 
  theme(axis.title = element_text(size=rel(0.75)))

ggplot(data = df.cue_country_freq %>% filter(country == "Vietnam"), 
        mapping = aes(x = emp_word1_prop, 
                     y = word1_match_frequency_prop_V,
                     label = cue_id)) +
   geom_text() + 
   geom_smooth(method = "lm") +
   labs(x = "Proportion Word1 Chosen (VN)", 
        y = "Proportion Word1 Predicted (Vietnamese)") + 
  theme(axis.title = element_text(size=rel(0.75)))
```
# Does lexical co-occurrences for fillers in English predict US responding? 
```{r US responding predicted by each corpus model raw co-occurrences, warning=FALSE}
# English 
fit.EN_US = glmer(responses_word1 ~ word1_match_frequency_prop_E + (1 | subject) + (1 | cue), 
          data = df %>% filter(country == "US", 
                               !(near(word1_match_frequency_E, .Machine$double.eps) & 
                                  near(word2_match_frequency_E, .Machine$double.eps))), 
          family="binomial")
summary(fit.EN_US)
fit.EN_US.anova = Anova(fit.EN_US, type = 3)

fit.EN_US.anova
```
# Does lexical co-occurrences for fillers in Vietnamese predict VN responding? 
```{r VN responding predicted by each corpus model raw co-occurrences, warning=FALSE}
# Vietnamese
fit.VI_VN = glmer(responses_word1 ~ word1_match_frequency_prop_V + (1 | subject) + (1 | cue), 
          data = df %>% filter(country == "Vietnam", 
                               !(near(word1_match_frequency_V, .Machine$double.eps) & 
                                  near(word2_match_frequency_V, .Machine$double.eps))), 
          family="binomial")
summary(fit.VI_VN)
fit.VI_VN.anova = Anova(fit.VI_VN, type = 3)

fit.VI_VN.anova
```

### 2022-11-30 code/3_analysis/3_analysis_semcoding.Rmd
added a lot of analysis. prepared to move to coglink_cogsci

```{r setup, echo = FALSE, include = FALSE}
library("papaja")
library("knitr") # for knitting things
library("tidyverse") # for all things tidyverse
library("car")
library("lme4")
library("patchwork")
library("effsize")
library("emmeans")

# these options here change the formatting of how comments are rendered
opts_chunk$set(
  comment = "",
  results = "hold",
  fig.show = "hold")

# set the default ggplot theme 
theme_set(theme_classic())

r_refs("r-references.bib")
r_refs("references/packages.bib")

```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r combine corpus and behavior data, include = F}
source("../2_combine/2_combine.R") # include triad_omits. TODO: Find a way to also save this.
```

```{r loading in the csv with direction so we dont need to go through the previous section, include =F}
df <- read.csv("../../data/data_USCNVN_ENZHVI_direction.csv")
```

```{r loading in the csv with semantic coding, include =F}
df.sem_code <- read.csv("../../data/corpus/corpus_sem_coding.csv")

df <- df %>%
  left_join(df.sem_code, by = "triad")
```

## Do people make more thematic matches for certain semantic groups of cue?

Plotting mean response theme by country, by type of triad
```{r plotting thematic responses by cue_genre}

ggplot(data = df) + 
   geom_bar(stat = "summary", 
            fun.data = "mean_cl_boot",
            alpha = .5, 
            mapping = aes(x = cue_genre, 
                          y = responses_theme)) +
  geom_pointrange(stat = "summary", 
            fun.data = "mean_cl_boot",
            alpha = .5, 
            mapping = aes(x = cue_genre, 
                          y = responses_theme))

```

```{r plotting thematic response by cue_genre and country}
ggplot(data = df,
       mapping = aes(x = cue_genre, 
                     y = responses_theme,
                     color = country, 
                     fill = country)) + 
   stat_summary(fun.data = "mean_cl_boot", 
               geom = "pointrange") 
#color code by cue genre, spatial sep by country, plotting all triads (mean response)

```

```{r plotting thematic response by cue_genre, country and triad}
ggplot(data = df, 
       mapping = aes(x = country, 
                     y = responses_theme, 
                     label = triad, 
                     group = triad,
                     color = cue_genre)) + 
  stat_summary(fun.data = "mean_cl_boot", 
               geom = "point", 
               alpha = .5, 
               position = position_dodge(width = .2)) + 
  stat_summary(fun.data = "mean_cl_boot", 
               geom = "text", 
               position = position_dodge(width = .2), size = 2)
```

There seems to be a clear preference for more thematic matches in the 'living things' cues in comparison to the 'moveable artifacts' cue. (need to omit cue_genre = "other")

Comparing some models:
Q: SHOULD we look at a model where responses theme is predicted by genre?

### English
Base line model:

```{r US responding predicted by corpus co-occurrences, warning=FALSE}
# English 
fit.EN_US = glmer(responses_theme ~ theme_freq_prop_E + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "US", 
                               !(triad %in% triads_omit),
                               !(cue_genre == "other")), 
          family="binomial")
summary(fit.EN_US)
fit.EN_US.anova = Anova(fit.EN_US, type = 3)
```

Adding cue genre: significant

```{r US responding, co-occurrence and cue_genre}
fit.EN_US_cue_genre = glmer(responses_theme ~ theme_freq_prop_E + cue_genre + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "US", 
                               !(triad %in% triads_omit),
                               !(cue_genre == "other")), 
          family="binomial")

summary(fit.EN_US_cue_genre)
Anova(fit.EN_US_cue_genre, type = 3)
```

Anova comparison: including cue genre is a better model
```{r US anova comparison, cue_genre}
fit.EN_US_cue_genre_compare = anova(fit.EN_US, fit.EN_US_cue_genre, type = 3)
fit.EN_US_cue_genre_compare
```
### Vietnamese

```{r VN responding predicted by VN corpus model, warning=FALSE}

#Vietnamese
fit.VI_VN = glmer(responses_theme ~ theme_freq_prop_V + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "Vietnam", 
                               !(triad %in% triads_omit), 
                               !(cue_genre == "other")), 
          family="binomial")
summary(fit.VI_VN)
fit.VI_VN.anova = Anova(fit.VI_VN, type = 3)
```

Adding cue genre: NOT significant

```{r VN responding, co-occurrence + cue_genre}
fit.VI_VN_cue_genre = glmer(responses_theme ~ theme_freq_prop_V + cue_genre + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "Vietnam", 
                               !(triad %in% triads_omit), 
                               !(cue_genre == "other")), 
          family="binomial")

summary(fit.VI_VN_cue_genre)
Anova(fit.VI_VN_cue_genre, type = 3)
```

Anova comparison (also not significant)
```{r VN anova comparison, cue_genre}
fit.VI_VN_cue_genre_compare = anova(fit.VI_VN, fit.VI_VN_cue_genre, type = 3)
fit.VI_VN_cue_genre_compare
```

### Mandarin
```{r CN responding predicted by co-occurrences, warning=FALSE}
#Mandarin
fit.ZH_CN = glmer(responses_theme ~ theme_freq_prop_M + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "China", 
                               !(triad %in% triads_omit),
                               !(cue_genre == "other")), 
          family="binomial")
summary(fit.ZH_CN)
fit.ZH_CN.anova = Anova(fit.ZH_CN, type = 3)
```

Adding cue genre: significant

```{r CN responding, co-occurrences + cue_genre}
fit.ZH_CN_cue_genre = glmer(responses_theme ~ theme_freq_prop_M + cue_genre + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "China", 
                               !(triad %in% triads_omit),
                               !(cue_genre == "other")), 
          family="binomial")

summary(fit.ZH_CN_cue_genre)
Anova(fit.ZH_CN_cue_genre, type = 3)
```
Anova comparison: including cue genre is a better model
```{r CN anova comparison,cue_genre}
fit.ZH_CN_cue_genre_compare = anova(fit.ZH_CN, fit.ZH_CN_cue_genre, type = 3)
fit.ZH_CN_cue_genre_compare
```

When added to the baseline model, cue genre is a significant predictor for US and China responses. But not for Vietnam.

### More general models that predict thematic response based on cue genre
NOT significant when just predicted by cue_genre.
```{r responding predicted only on cue genre, warning=FALSE}
fit.cue_genre = glmer(responses_theme ~ cue_genre + (1 | subject) + (1 | triad),
          data = df %>% filter(!(cue_genre == "other")),  
          # no need to pull out triads_omit because we're not using the raw coocurrences
          family="binomial")
summary(fit.cue_genre)
fit.cue_genre.anova = Anova(fit.cue_genre, type = 3)
fit.cue_genre.anova
```

NOT significant when predicted by country and cue_genre (only country is significant)
```{r responding predicted on cue genre and country, warning=FALSE}
fit.cue_genre_country = glmer(responses_theme ~ country + cue_genre + (1 | subject) + (1 | triad), 
          data = df %>% filter(!(cue_genre == "other")),  
          # no need to pull out triads_omit because we're not using the raw coocurrences
          family="binomial")
summary(fit.cue_genre_country)
fit.cue_genre_country.anova = Anova(fit.cue_genre_country, type = 3)
fit.cue_genre_country.anova
```

NO interaction between country and cue genre either. 
```{r responding predicted on cue genre and country, with interaction, warning=FALSE}
fit.cue_genre_country_int = glmer(responses_theme ~ country + cue_genre + country * cue_genre + (1 | subject) + (1 | triad), 
          data = df %>% filter(!(cue_genre == "other")),  
          # no need to pull out triads_omit because we're not using the raw coocurrences
          family="binomial")
summary(fit.cue_genre_country_int)
fit.cue_genre_country_int.anova = Anova(fit.cue_genre_country_int, type = 3)
fit.cue_genre_country_int.anova
```

NOT significance even with country having random slope and intercept for cue_genre.

```{r responding predicted on cue genre and country, with random intercept and slope by country, warning=FALSE}
fit.cue_genre_country_slope = glmer(responses_theme ~ country + cue_genre + (cue_genre | country) + (1 | subject) + (1 | triad), 
          data = df %>% filter(!(cue_genre == "other")),  
          # no need to pull out triads_omit because we're not using the raw co-ocurrences
          family="binomial")
summary(fit.cue_genre_country_slope)
fit.cue_genre_country_slope.anova = Anova(fit.cue_genre_country_slope, type = 3)
fit.cue_genre_country_slope.anova
```

## Do people make more thematic matches for certain semantic groups of thematic relationships?

Plotting mean response theme by country, by type of thematic match
```{r plotting thematic responses by theme_genre}
ggplot(data = df) + 
   geom_bar(stat = "summary", 
            fun.data = "mean_cl_boot",
            alpha = .5, 
            mapping = aes(x = theme_genre, 
                          y = responses_theme)) +
  geom_pointrange(stat = "summary", 
            fun.data = "mean_cl_boot",
            alpha = .5, 
            mapping = aes(x = theme_genre, 
                          y = responses_theme)) +
  geom_hline(yintercept = 0.5)

```
```{r plotting thematic responses by theme_genre and country}
ggplot(data = df) + 
   geom_bar(stat = "summary", 
            fun.data = "mean_cl_boot",
            mapping = aes(x = theme_genre, 
                          y = responses_theme, 
                          fill = country), 
            position = position_dodge(width = .7), width = .7) +
  geom_pointrange(stat = "summary", 
            fun.data = "mean_cl_boot",
            mapping = aes(x = theme_genre, 
                          y = responses_theme,
                          group = country), 
            position = position_dodge(width = .7)) +
  geom_hline(yintercept = 0.5)
#color code by cue genre, spatial sep by country, plotting all triads (mean response)

```

```{r plotting thematic response by country, triad and theme_genre}
ggplot(data = df, 
       mapping = aes(x = country, 
                     y = responses_theme, 
                     label = triad, 
                     group = triad)) + 
  geom_point(stat = "summary", 
             fun.data = "mean_cl_boot", 
             position = position_dodge(width = .7)) +
  geom_text(stat = "summary", 
            fun.data = "mean_cl_boot", 
            color = alpha('black'),
            position = position_dodge(width = .7), size = 2) +
  geom_violin(data = df %>% 
                group_by(country, theme_genre, triad) %>%
                summarize(theme_resp_triad = mean(responses_theme, na.rm = T)), 
                mapping = aes(x = country,
                              y = theme_resp_triad, 
                              group = country,
                              fill = country,
                              color = country), 
                alpha = .5) + 
  facet_grid(~theme_genre)

# geom_point(data = df %>% filter(theme_genre == 'ecology'),
#            mapping = aes(x = country,
#                    y = responses_theme,
#                    label = triad,
#                    group = triad,
#                    color = theme_genre),
#            stat = "summary",
#            fun.data = "mean_cl_boot",
#            position = position_dodge(width =.7))

```

1. All theme match semantic categories prefer thematic, except for association.
2. China is always the most thematic in all theme match semantic categories. Only country that prefers thematic across all categories. 
3. Only US & Vietnam + association prefer taxonomic. Overall, association seems to be least thematic preferring.
4. Vietnam is not significantly different from US except for ecology. 
5. Most thematic: causal (but might be driven by strong China response) and occupation (most consistent across countries to be thematic).

### English
Base line model:

```{r US responding predicted by corpus co-occurrences re-run for theme_genre, warning=FALSE}
# English 
fit.EN_US = glmer(responses_theme ~ theme_freq_prop_E + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "US", 
                               !(triad %in% triads_omit),
                               !(cue_genre == "other")), 
          family="binomial")
summary(fit.EN_US)
fit.EN_US.anova = Anova(fit.EN_US, type = 3)
```

Adding theme genre: NOT significant (p = 0.08)

```{r US responding, co-occurrence and theme_genre}
fit.EN_US_theme_genre = glmer(responses_theme ~ theme_freq_prop_E + theme_genre + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "US", 
                               !(triad %in% triads_omit),
                               !(cue_genre == "other")), 
          family="binomial")

summary(fit.EN_US_theme_genre)
Anova(fit.EN_US_theme_genre, type = 3)
```

Anova comparison: including theme genre is NOT a better model
```{r US anova comparison, theme_genre}
fit.EN_US_theme_genre_compare = anova(fit.EN_US, fit.EN_US_theme_genre, type = 3)
fit.EN_US_theme_genre_compare
```
### Vietnamese

```{r VN responding predicted by VN corpus model re-run for theme_genre, warning=FALSE}

#Vietnamese
fit.VI_VN = glmer(responses_theme ~ theme_freq_prop_V + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "Vietnam", 
                               !(triad %in% triads_omit), 
                               !(cue_genre == "other")), 
          family="binomial")
summary(fit.VI_VN)
fit.VI_VN.anova = Anova(fit.VI_VN, type = 3)
```

Adding theme genre: significant (p < 0.05)

```{r VN responding, co-occurrence + theme_genre}
fit.VI_VN_theme_genre = glmer(responses_theme ~ theme_freq_prop_V + theme_genre + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "Vietnam", 
                               !(triad %in% triads_omit), 
                               !(cue_genre == "other")), 
          family="binomial")

summary(fit.VI_VN_theme_genre)
Anova(fit.VI_VN_theme_genre, type = 3)
```

Anova comparison: significant
```{r VN anova comparison, theme_genre}
fit.VI_VN_theme_genre_compare = anova(fit.VI_VN, fit.VI_VN_theme_genre, type = 3)
fit.VI_VN_theme_genre_compare
```

### Mandarin
```{r CN responding predicted by co-occurrences re-run for theme_genre, warning=FALSE}
#Mandarin
fit.ZH_CN = glmer(responses_theme ~ theme_freq_prop_M + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "China", 
                               !(triad %in% triads_omit),
                               !(cue_genre == "other")), 
          family="binomial")
summary(fit.ZH_CN)
fit.ZH_CN.anova = Anova(fit.ZH_CN, type = 3)
```

Adding theme genre: NOT significant (p = 0.12)

```{r CN responding, co-occurrences + theme_genre}
fit.ZH_CN_theme_genre = glmer(responses_theme ~ theme_freq_prop_M + theme_genre + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "China", 
                               !(triad %in% triads_omit),
                               !(cue_genre == "other")), 
          family="binomial")

summary(fit.ZH_CN_theme_genre)
Anova(fit.ZH_CN_theme_genre, type = 3)
```
Anova comparison: including theme genre is a better model
```{r CN anova comparison, theme_genre}
fit.ZH_CN_theme_genre_compare = anova(fit.ZH_CN, fit.ZH_CN_theme_genre, type = 3)
fit.ZH_CN_theme_genre_compare
```

When added to the baseline model, theme genre is a significant predictor for Vietnam response, but not for US and China!

```{r summary of semantic coding result}
text_tbl <- data.frame(
  Country = c("US", "China", "Vietnam"),
  Add_Cue_Genre = c(
    "significant", "significant", "not significant"
  ), 
  Add_Theme_Genre = c(
    "not significant", "not significant", "significant"
  )
)
kable(text_tbl)
```

### 2022-11-30 code/0_demographic/extract_demog.r

@@ -1,0 +1,162 @@
+
+
+library(tidyverse)
+library(here)
+library(jsonlite)
+
+#INPUT_PATH <- here("data/raw_data/anonymized_All.csv")
+#OUTPUT_PATH <- here("data/processed_data/demog_All.csv")
+
+# take raw_df 
+# take culture string "US" or "CN"
+extract_demog <- function(raw_df, culture_string){
+  demog_fields <- c("demog_country_born_current_grew_up", 
+                    "demog_oversea_experience",
+                    "demog_conditional_year_abroad_regions",
+                    "demog_language",
+                    "demog_conditional_language_target_fluency",
+                    "demog_age_gender_ethnic",
+                    "demo-objses")
+  
+  if (culture_string == "US") {
+    demog_fields <- c(demog_fields, c("demog_language_cn",
+                                      "demog_conditional_language_cn_fluency",
+                                      "demog_language_vi",
+                                      "demog_conditional_language_vn_fluency"))
+  } else if (culture_string == "CN") {
+    demog_fields <- c(demog_fields, c("demog_language_en",
+                                      "demog_conditional_language_en_fluency",
+                                      "demog_language_vi",
+                                      "demog_conditional_language_vn_fluency"))
+  } else if (culture_string == "VN") {
+    demog_fields <- c(demog_fields, c("demog_language_en",
+                                      "demog_conditional_language_en_fluency",
+                                      "demog_language_cn",
+                                      "demog_conditional_language_cn_fluency"))
+  } else {
+    stop("culture_string has to be US / CN / VN")
+  }
+
+  # non dropdown demog 
+  demog <- raw_df %>%
+    filter(variable_type %in% demog_fields) %>% 
+    select(subject, trial_type, variable_type, responses) %>%
+    filter(trial_type != "demog-dropdown") %>% 
+    group_by(subject) %>%
+    mutate(responses = map(responses, ~ fromJSON(.) %>% as.data.frame())) %>%
+    unnest(responses) %>%
+    select(-variable_type) %>%
+    group_by(subject) %>%
+    mutate_at(vars(-group_cols()), function(x) {
+      lapply((list(as.character(x))), function(x) unique(x[!is.na(x)]))
+    }) %>%
+    distinct() %>%
+    mutate_at(vars(-group_cols()), as.character) %>%
[…]

### 2022-11-30 code/2_combine/2_combine.R

@@ -5,6 +5,7 @@ library("car")
 library("lme4")
 library("patchwork")
 library("effsize")
+library("here")
 
 # Seed for random number generation-----
 set.seed(42)
@@ -12,17 +13,17 @@ knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
 
 
 #loading responding data --------
-df.resp_E <- read.csv("../../data/dataUS_excl.csv") %>%
+df.resp_E <- read.csv(paste(here(), "/data/responding/dataUS_excl.csv", sep = "")) %>%
   select(-X)
 
-df.resp_V <- read.csv("../../data/dataVN_excl.csv") %>%
+df.resp_V <- read.csv(paste(here(), "/data/responding/dataVN_excl.csv", sep = "")) %>%
   select(-X)
 
-df.resp_M <- read.csv("../../data/dataCN_excl.csv") %>%
+df.resp_M <- read.csv(paste(here(), "/data/responding/dataCN_excl.csv", sep = "")) %>%
   select(-X)
 
 #loading corpus data ---------
-df.corpus_E <- read.csv("../../data/corpus/corpusE.csv") %>%
+df.corpus_E <- read.csv(paste(here(), "/data/corpus/corpusE.csv", sep = "")) %>%
   rename(tax_frequency_E = tax.frequency,
          theme_frequency_E = theme.frequency,
          tax_cosine_E = Tax.cosine_dist, 
@@ -33,7 +34,7 @@ df.corpus_E <- read.csv("../../data/corpus/corpusE.csv") %>%
          theme_match_E = Theme.match, 
          cue_E = Cue)
 
-df.corpus_V <- read.csv("../../data/corpus/corpusV.csv") %>%
+df.corpus_V <- read.csv(paste(here(), "/data/corpus/corpusV.csv", sep = "")) %>%
   rename(tax_frequency_V = tax.frequency,
          theme_frequency_V = theme.frequency,
          tax_cosine_V = Tax.cosine_dist, 
@@ -44,7 +45,7 @@ df.corpus_V <- read.csv("../../data/corpus/corpusV.csv") %>%
          theme_match_V = Theme.match, 
          cue_V = Cue)
 
-df.corpus_M <- read.csv("../../data/corpus/corpusM.csv") %>%
+df.corpus_M <- read.csv(paste(here(), "/data/corpus/corpusM.csv", sep = "")) %>%
   rename(tax_frequency_M = tax.frequency,
[…]

### 2022-12-14 code/1_exclusions/1_exclusionsCN.Rmd
setting up cogsci paper

@@
   summarize(pass_att_check_percent = mean(pass_att_check)) %>%
-  filter(pass_att_check_percent == 1.0)
+  filter(pass_att_check_percent >= 0.8)
 
@@
   filter(subject %in% df.ppts_att_M$subject)
+
+ppts_resp_M <- unique(df.resp_M$subject)
 ```
 
-```{r exclusion M, include = F, warning = F}
+```{r}
+df.demog <- read.csv("../../data/responding/data_demog.csv") %>%
+  select(-X) %>%
+  filter(country == "CN")
+```
+
+```{r exclusion E, include = F, warning = F}
 #non-native speaker
-split_responses_demog <- function(responses) {
-  responses <- as.character(responses)
-  response_list <- unlist(strsplit(responses, ',|:'))
-  response_list <- response_list[seq(1, length(response_list))]
-  response_list <- gsub("}", "", response_list)
-  response_list <- gsub("\"", "", response_list)
-  return(response_list)
-}
+df.ppts_non_native_lang_M <- df.demog %>%
+  filter(demog_question == "firstlanguage" & demog_response == "不是")
 
-NATIVE_LANG = 2
-get_native_lang <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  if(responses[NATIVE_LANG-1] != "{firstlanguage") 
-    {warnings("cannot find native language answer")}
-  else
-    {return (responses[NATIVE_LANG])}
-})
+ppts_non_native_lang_M = unique(df.ppts_non_native_lang_M$subject) #3
+percent_dropped = length(intersect(ppts_non_native_lang_M, ppts_resp_M)) / length(ppts_resp_M)
+percent_dropped #0.01086
 
-df.ppts_non_native_lang_M <- df.resp_M %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_language") %>%
-  mutate(native_speaker = get_native_lang(responses)) %>%
-  filter(native_speaker == "不是")
+#fluent in Vietnamese & Mandarin
+df.lang_sp_vi_M <- df.demog %>%
+  filter(demog_question == "lang_sp_vi" & demog_response > 4)
 
-ppts_non_native_lang_M = unique(df.ppts_non_native_lang_M$subject) #2
-percent_dropped = length(ppts_non_native_lang_M) / length(unique(df.resp_M$subject))
-percent_dropped #0.01398601
+df.lang_ud_vi_M <- df.demog %>%
+  filter(demog_question == "lang_ud_vi" & demog_response > 4)
 
-#fluent in English
-SPEAKER = 2
-SPEAKING = 23
-UNDERSTANDING = 46
+df.lang_vi_M <- inner_join(df.lang_sp_vi_M, df.lang_ud_vi_M, by = 'subject')
 
-get_speaker <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[SPEAKER])
-})
-
-get_fluency_speaking <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[SPEAKING])
-})
-
-get_fluency_understanding <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[UNDERSTANDING])
-})
-
-df.lang_en_M <- df.resp_M %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_language_en") %>%
-  mutate(en_speaker = get_speaker(responses))
-
-df.lang_en_fluency_M <- df.resp_M %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_conditional_language_en_fluency") %>%
-  mutate(en_fluency_sp = as.numeric(get_fluency_speaking(responses))) %>%
-  mutate(en_fluency_ud = as.numeric(get_fluency_understanding(responses)))
-
-df.lang_en_M <- full_join(df.lang_en_M, 
-                          df.lang_en_fluency_M, 
-                          by = "subject") %>%
-  select(subject, en_speaker, en_fluency_sp, en_fluency_ud) %>%
-  filter(en_speaker == "能",
-         en_fluency_sp > 4, 
-         en_fluency_ud > 4)
-
-ppts_en_speaker_M = unique(df.lang_en_M$subject) #50
-percent_dropped = length(ppts_en_speaker_M) / length(unique(df.resp_M$subject))
-percent_dropped #0.3496503 # will not use this criterion
-
-df.lang_vi_M <- df.resp_M %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_language_vi") %>%
-  mutate(vi_speaker = get_speaker(responses))
-
-df.lang_vi_fluency_M <- df.resp_M %>%
-  filter(variable_type == "demog_conditional_language_vi_fluency") %>%
-  mutate(vi_fluency_sp = as.numeric(get_fluency_speaking(responses))) %>%
-  mutate(vi_fluency_ud = as.numeric(get_fluency_understanding(responses)))
-
-df.lang_vi_M <- full_join(df.lang_vi_M, 
-                          df.lang_vi_fluency_M, 
-                          by = "subject") %>%
-  select(subject, vi_speaker, vi_fluency_sp, vi_fluency_ud) %>%
-  filter(vi_speaker == "能",
-         vi_fluency_sp > 4, 
-         vi_fluency_ud > 4)
-
-ppts_vi_speaker_M = unique(df.lang_vi_M$subject) #50
-percent_dropped = length(ppts_vi_speaker_M) / length(unique(df.resp_M$subject))
+ppts_vi_speaker_M = unique(df.lang_vi_M$subject) #1
+percent_dropped = length(intersect(ppts_vi_speaker_M, ppts_resp_M)) / length(ppts_resp_M)
 percent_dropped #0
 
+df.lang_sp_en_M <- df.demog %>%
+  filter(demog_question == "lang_sp_en" & demog_response > 4)
+
+df.lang_ud_en_M <- df.demog %>%
+  filter(demog_question == "lang_ud_en" & demog_response > 4)
+
+df.lang_en_M <- inner_join(df.lang_sp_en_M, df.lang_ud_en_M, by = 'subject')
+
+ppts_en_speaker_M = unique(df.lang_en_M$subject) #74
+percent_dropped = length(intersect(ppts_en_speaker_M, ppts_resp_M)) / length(ppts_resp_M)
+percent_dropped #0.375 # do not use this criterion
+
 #have lived outside the sample country for more than 2 years
+df.lived_abroad_M <- df.demog %>%
+  filter(demog_question == "abroadexp" & demog_response == "是")
+
+ppts_lived_abroad_M = unique(df.lived_abroad_M$subject) #40
+percent_dropped = length(intersect(ppts_lived_abroad_M, ppts_resp_M)) / length(unique(df.resp_M$subject))
+percent_dropped #0.163043
+
 #have travelled extensively (more than 6 international experiences of 2 days or longer)
-YEARSABROAD = 2
-OVERSEAEXP = 4
+df.oversea_exp_M <- df.demog %>%
+  filter(demog_question == "overseaexpnum" & demog_response == "六段或更多国际经历")
 
-get_lived_abroad <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[YEARSABROAD])
-})
-
-get_oversea_exp <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[OVERSEAEXP])
-})
-
-df.abroad_M <- df.resp_M %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_oversea_experience") %>%
-  mutate(lived_abroad = get_lived_abroad(responses)) %>%
-  mutate(oversea_exp = get_oversea_exp(responses))
-
-df.lived_abroad_M <- df.abroad_M %>%
-  filter(lived_abroad == "是")
-
-ppts_lived_abroad_M = unique(df.lived_abroad_M$subject) #23
-percent_dropped = length(ppts_lived_abroad_M) / length(unique(df.resp_M$subject))
-percent_dropped # 0.1608392
-
-df.oversea_exp_M <- df.abroad_M %>%
-  filter(oversea_exp == "六段或更多国际经历")
-
-ppts_oversea_exp_M = unique(df.oversea_exp_M$subject) #0
-percent_dropped = length(ppts_oversea_exp_M) / length(unique(df.resp_M$subject))
-percent_dropped #0
+ppts_oversea_exp_M = unique(df.oversea_exp_M$subject) #12
+percent_dropped = length(intersect(ppts_oversea_exp_M, ppts_resp_M)) / length(unique(df.resp_M$subject))
+percent_dropped #0.0434782
 
@@
   filter(!(subject %in% ppts_non_native_lang_M),
+         !(subject %in% ppts_vi_speaker_M), 
          !(subject %in% ppts_lived_abroad_M), 
-         !(subject %in% ppts_vi_speaker_M),
-         !(subject %in% ppts_oversea_exp_M),)
+         !(subject %in% ppts_oversea_exp_M))
 
-length(unique(df.resp_M$subject)) 
+length(unique(df.resp_M$subject)) #149
 ```
@@
 ```{r}
-write.csv(df.resp_M, "../../data/dataCN_excl.csv")
+write.csv(df.resp_M, "../../data/responding/dataCN_excl.csv")
 ```

### 2022-12-14 code/1_exclusions/1_exclusionsUS.Rmd
setting up cogsci paper

@@
   filter(subject %in% df.ppts_att_E$subject)
+
+ppts_resp_E <- unique(df.resp_E$subject)
+```
+
+```{r}
+df.demog <- read.csv("../../data/responding/data_demog.csv") %>%
+  select(-X) %>%
+  filter(country == "US")
 ```
@@
 #non-native speaker
-split_responses_demog <- function(responses) {
-  responses <- as.character(responses)
-  response_list <- unlist(strsplit(responses, ',|:'))
-  response_list <- response_list[seq(1, length(response_list))]
-  response_list <- gsub("}", "", response_list)
-  response_list <- gsub("\"", "", response_list)
-  return(response_list)
-}
+df.ppts_non_native_lang_E <- df.demog %>%
+  filter(demog_question == "firstlanguage" & demog_response == "No")
 
-NATIVE_LANG = 2
-get_native_lang <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  if(responses[NATIVE_LANG-1] != "{firstlanguage") 
-    {warnings("cannot find native language answer")}
-  else
-    {return (responses[NATIVE_LANG])}
-})
-
-df.ppts_non_native_lang_E <- df.resp_E %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_language") %>%
-  mutate(native_speaker = get_native_lang(responses)) %>%
-  filter(native_speaker == "No")
-
-ppts_non_native_lang_E = unique(df.ppts_non_native_lang_E$subject)#18
-percent_dropped = length(ppts_non_native_lang_E) / length(unique(df.resp_E$subject))
-percent_dropped #0.1034482775
+ppts_non_native_lang_E = unique(df.ppts_non_native_lang_E$subject)#20
+percent_dropped = length(intersect(ppts_non_native_lang_E, ppts_resp_E)) / length(ppts_resp_E)
+percent_dropped #0.104166
 
 #fluent in Vietnamese & Mandarin
-SPEAKER = 2
-SPEAKING = 23
-UNDERSTANDING = 46
+df.lang_sp_vi_E <- df.demog %>%
+  filter(demog_question == "lang_sp_vi" & demog_response > 4)
 
-get_speaker <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[SPEAKER])
-})
+df.lang_ud_vi_E <- df.demog %>%
+  filter(demog_question == "lang_ud_vi" & demog_response > 4)
 
-get_fluency_speaking <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[SPEAKING])
-})
+df.lang_vi_E <- inner_join(df.lang_sp_vi_E, df.lang_ud_vi_E, by = 'subject')
 
-get_fluency_understanding <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[UNDERSTANDING])
-})
+ppts_vi_speaker_E = unique(df.lang_vi_E$subject) #2
+percent_dropped = length(intersect(ppts_vi_speaker_E, ppts_resp_E)) / length(ppts_resp_E)
+percent_dropped #0.01041666
 
-df.lang_vi_E <- df.resp_E %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_language_vi") %>%
-  mutate(vi_speaker = get_speaker(responses))
+df.lang_sp_zh_E <- df.demog %>%
+  filter(demog_question == "lang_sp_zh" & demog_response > 4)
 
-df.lang_vi_fluency_E <- df.resp_E %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_conditional_language_vn_fluency") %>%
-  mutate(vi_fluency_sp = as.numeric(get_fluency_speaking(responses))) %>%
-  mutate(vi_fluency_ud = as.numeric(get_fluency_understanding(responses)))
+df.lang_ud_zh_E <- df.demog %>%
+  filter(demog_question == "lang_ud_zh" & demog_response > 4)
 
-df.lang_vi_E <- full_join(df.lang_vi_E, 
-                          df.lang_vi_fluency_E, 
-                          by = "subject") %>%
-  select(subject, vi_speaker, vi_fluency_sp, vi_fluency_ud) %>%
-  filter(vi_speaker == "Yes",
-         vi_fluency_sp > 4, 
-         vi_fluency_ud > 4)
-
-ppts_vi_speaker_E = unique(df.lang_vi_E$subject) #4
-percent_dropped = length(ppts_vi_speaker_E) / length(unique(df.resp_E$subject))
-percent_dropped #0.02298851
-
-df.lang_zh_E <- df.resp_E %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_language_cn") %>%
-  mutate(zh_speaker = get_speaker(responses))
-
-df.lang_zh_fluency_E <- df.resp_E %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_conditional_language_cn_fluency") %>%
-  mutate(zh_fluency_sp = as.numeric(get_fluency_speaking(responses))) %>%
-  mutate(zh_fluency_ud = as.numeric(get_fluency_understanding(responses)))
-
-df.lang_zh_E <- full_join(df.lang_zh_E, 
-                          df.lang_zh_fluency_E, 
-                          by = "subject") %>%
-  select(subject, zh_speaker, zh_fluency_sp, zh_fluency_ud) %>%
-  filter(zh_speaker == "Yes",
-         zh_fluency_sp > 4, 
-         zh_fluency_ud > 4)
+df.lang_zh_E <- inner_join(df.lang_sp_zh_E, df.lang_ud_zh_E, by = 'subject')
 
 ppts_zh_speaker_E = unique(df.lang_zh_E$subject) #30
-percent_dropped = length(ppts_zh_speaker_E) / length(unique(df.resp_E$subject))
-percent_dropped #0.1742424
+percent_dropped = length(intersect(ppts_zh_speaker_E, ppts_resp_E)) / length(ppts_resp_E)
+percent_dropped #0.15104
 
 #have lived outside the sample country for more than 2 years
+df.lived_abroad_E <- df.demog %>%
+  filter(demog_question == "abroadexp" & demog_response == "Yes")
+
+ppts_lived_abroad_E = unique(df.lived_abroad_E$subject) #36
+percent_dropped = length(intersect(ppts_lived_abroad_E, ppts_resp_E)) / length(unique(df.resp_E$subject))
+percent_dropped #0.171875
+
 #have travelled extensively (more than 6 international experiences of 2 days or longer)
-YEARSABROAD = 2
-OVERSEAEXP = 4
+df.oversea_exp_E <- df.demog %>%
+  filter(demog_question == "overseaexpnum" & demog_response == "Six or more experiences")
 
-get_lived_abroad <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[YEARSABROAD])
-})
-
-get_oversea_exp <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[OVERSEAEXP])
-})
-
-df.abroad_E <- df.resp_E %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_oversea_experience") %>%
-  mutate(lived_abroad = get_lived_abroad(responses)) %>%
-  mutate(oversea_exp = get_oversea_exp(responses))
-
-df.lived_abroad_E <- df.abroad_E %>%
-  filter(lived_abroad == "Yes")
-
-ppts_lived_abroad_E = unique(df.lived_abroad_E$subject) #29
-percent_dropped = length(ppts_lived_abroad_E) / length(unique(df.resp_E$subject))
-percent_dropped #0.1666667
-
-df.oversea_exp_E <- df.abroad_E %>%
-  filter(oversea_exp == "Six or more experiences")
-
-ppts_oversea_exp_E = unique(df.oversea_exp_E$subject) #77
-percent_dropped = length(ppts_oversea_exp_E) / length(unique(df.resp_E$subject))
-percent_dropped #0.44 # will not use this criterion
+ppts_oversea_exp_E = unique(df.oversea_exp_E$subject) #95
+percent_dropped = length(intersect(ppts_oversea_exp_E, ppts_resp_E)) / length(unique(df.resp_E$subject))
+percent_dropped #0.4739 # will not use this criterion
 
@@
 
-length(unique(df.resp_E$subject)) #132
+length(unique(df.resp_E$subject)) #124
 ```
@@
 ```{r}
-write.csv(df.resp_E, "../../data/dataUS_excl.csv")
+write.csv(df.resp_E, "../../data/responding/dataUS_excl.csv")
 ```

### 2022-12-14 code/1_exclusions/1_exclusionsVN.Rmd
added a lot of analysis. prepared to move to coglink_cogsci
setting up cogsci paper

@@
   filter(subject %in% df.ppts_att_V$subject) #73
+
+ppts_resp_V <- unique(df.resp_V$subject) #137
 ```
 
-```{r exclusion V, include = F}
+```{r}
+df.demog <- read.csv("../../data/responding/data_demog.csv") %>%
+  select(-X) %>%
+  filter(country == "VN")
+```
+
+```{r exclusion E, include = F, warning = F}
 #non-native speaker
-split_responses_demog <- function(responses) {
-  responses <- as.character(responses)
-  response_list <- unlist(strsplit(responses, ',|:'))
-  response_list <- response_list[seq(1, length(response_list))]
-  response_list <- gsub("}", "", response_list)
-  response_list <- gsub("\"", "", response_list)
-  return(response_list)
-}
+df.ppts_non_native_lang_V <- df.demog %>%
+  filter(demog_question == "firstlanguage" & demog_response == "Không")
 
-NATIVE_LANG = 2
-get_native_lang <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  if(responses[NATIVE_LANG-1] != "{firstlanguage") 
-    {warnings("cannot find native language answer")}
-  else
-    {return (responses[NATIVE_LANG])}
-})
-
-df.ppts_non_native_lang_V <- df.resp_V %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_language") %>%
-  mutate(native_speaker = get_native_lang(responses)) %>%
-  filter(native_speaker == "Không")
-
-ppts_non_native_lang_V = unique(df.ppts_non_native_lang_V$subject)
-percent_dropped = length(ppts_non_native_lang_V) / length(unique(df.resp_V$subject))
+ppts_non_native_lang_V = unique(df.ppts_non_native_lang_V$subject)#2
+percent_dropped = length(intersect(ppts_non_native_lang_V, ppts_resp_V)) / length(ppts_resp_V)
 percent_dropped #0
 
-#fluent in English
-SPEAKER = 2
-SPEAKING = 23
-UNDERSTANDING = 46
+#fluent in Vietnamese & Mandarin
+df.lang_sp_en_V <- df.demog %>%
+  filter(demog_question == "lang_sp_en" & demog_response > 4)
 
-get_speaker <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[SPEAKER])
-})
+df.lang_ud_en_V <- df.demog %>%
+  filter(demog_question == "lang_ud_en" & demog_response > 4)
 
-get_fluency_speaking <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[SPEAKING])
-})
+df.lang_en_V <- inner_join(df.lang_sp_en_V, df.lang_ud_en_V, by = 'subject')
 
-get_fluency_understanding <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[UNDERSTANDING])
-})
+ppts_en_speaker_V = unique(df.lang_en_V$subject) #119
+percent_dropped = length(intersect(ppts_en_speaker_V, ppts_resp_V)) / length(ppts_resp_V)
+percent_dropped #0.6277 # do not use this criterion
 
-df.lang_en_V <- df.resp_V %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_language_en") %>%
-  mutate(en_speaker = get_speaker(responses))
+df.lang_sp_zh_V <- df.demog %>%
+  filter(demog_question == "lang_sp_zh" & demog_response > 4)
 
-df.lang_en_fluency_V <- df.resp_V %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_conditional_language_en_fluency") %>%
-  mutate(en_fluency_sp = as.numeric(get_fluency_speaking(responses))) %>%
-  mutate(en_fluency_ud = as.numeric(get_fluency_understanding(responses)))
+df.lang_ud_zh_V <- df.demog %>%
+  filter(demog_question == "lang_ud_zh" & demog_response > 4)
 
-df.lang_en_V <- full_join(df.lang_en_V, 
-                          df.lang_en_fluency_V, 
-                          by = "subject") %>%
-  select(subject, en_speaker, en_fluency_sp, en_fluency_ud) %>%
-  filter(en_speaker == "Có",
-         en_fluency_sp > 4, 
-         en_fluency_ud > 4)
+df.lang_zh_V <- inner_join(df.lang_sp_zh_V, df.lang_ud_zh_V, by = 'subject')
 
-ppts_en_speaker_V = unique(df.lang_en_V$subject) #4
-percent_dropped = length(ppts_en_speaker_V) / length(unique(df.resp_V$subject))
-percent_dropped #0.6986301 # do not use this criterion
-
-df.lang_zh_V <- df.resp_V %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_language_cn") %>%
-  mutate(zh_speaker = get_speaker(responses))
-
-df.lang_zh_fluency_V <- df.resp_V %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_conditional_language_cn_fluency") %>%
-  mutate(zh_fluency_sp = as.numeric(get_fluency_speaking(responses))) %>%
-  mutate(zh_fluency_ud = as.numeric(get_fluency_understanding(responses)))
-
-df.lang_zh_V <- full_join(df.lang_zh_V, 
-                          df.lang_zh_fluency_V, 
-                          by = "subject") %>%
-  select(subject, zh_speaker, zh_fluency_sp, zh_fluency_ud) %>%
-  filter(zh_speaker == "Có",
-         zh_fluency_sp > 4, 
-         zh_fluency_ud > 4)
-
-ppts_zh_speaker_V = unique(df.lang_zh_V$subject) #4
-percent_dropped = length(ppts_zh_speaker_V) / length(unique(df.resp_V$subject))
-percent_dropped #0.06557377
+ppts_zh_speaker_V = unique(df.lang_zh_V$subject) #9
+percent_dropped = length(intersect(ppts_zh_speaker_V, ppts_resp_V)) / length(ppts_resp_V)
+percent_dropped #0.05839416
 
 #have lived outside the sample country for more than 2 years
+df.lived_abroad_V <- df.demog %>%
+  filter(demog_question == "abroadexp" & demog_response == "Có")
+
+ppts_lived_abroad_V = unique(df.lived_abroad_V$subject) #18
+percent_dropped = length(intersect(ppts_lived_abroad_V, ppts_resp_V)) / length(unique(df.resp_V$subject))
+percent_dropped #0.05839416
+
 #have travelled extensively (more than 6 international experiences of 2 days or longer)
-YEARSABROAD = 2
-OVERSEAEXP = 4
+df.oversea_exp_V <- df.demog %>%
+  filter(demog_question == "overseaexpnum" & demog_response == "Six or more experiences")
 
-get_lived_abroad <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[YEARSABROAD])
-})
-
-get_oversea_exp <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[OVERSEAEXP])
-})
-
-df.abroad_V <- df.resp_V %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_oversea_experience") %>%
-  mutate(lived_abroad = get_lived_abroad(responses)) %>%
-  mutate(oversea_exp = get_oversea_exp(responses))
-
-df.lived_abroad_V <- df.abroad_V %>%
-  filter(lived_abroad == "Có")
-
-ppts_lived_abroad_V = unique(df.lived_abroad_V$subject)
-percent_dropped = length(ppts_lived_abroad_V) / length(unique(df.resp_V$subject))
-percent_dropped #0.1369863
-
-df.oversea_exp_V <- df.abroad_V %>%
-  filter(oversea_exp == "6 lần trở lên")
-
-ppts_oversea_exp_V = unique(df.oversea_exp_V$subject) #77
-percent_dropped = length(ppts_oversea_exp_V) / length(unique(df.resp_V$subject))
-percent_dropped #0.1506849
+ppts_oversea_exp_V = unique(df.oversea_exp_V$subject) #95
+percent_dropped = length(intersect(ppts_oversea_exp_V, ppts_resp_V)) / length(unique(df.resp_V$subject))
+percent_dropped #0.4739 # will not use this criterion
 
@@
   filter(!(subject %in% ppts_non_native_lang_V),
-         !(subject %in% ppts_oversea_exp_V), 
+         !(subject %in% ppts_vi_speaker_V), 
          !(subject %in% ppts_zh_speaker_V),
@@
 
-length(unique(df.resp_V$subject)) 
+length(unique(df.resp_V$subject)) #124
 ```
@@
 ```{r}
-write.csv(df.resp_V, "../../data/dataVN_excl.csv")
+write.csv(df.resp_V, "../../data/responding/dataVN_excl.csv")
 ```

### 2022-12-14 code/1_exclusions_old/1_exclusionsCN.Rmd
setting up cogsci paper

--- 2022-09-28 code/3_analysis/3_analysis.Rmd
@@
 theme_set(theme_classic())
-
-r_refs("r-references.bib")
-r_refs("references/packages.bib")
-
 ```
@@
 
-# Introduction 
-By virtue of discrete words and grammatical features, language provides a categorical partition of our continuous experiences.
-Previous research has observed variation in the cognition of speakers of different languages corresponding to variation within semantic domains in these languages.
-This language-aligned variation has been observed in the domains of color [@Winawer2007], number [@Frank2008], and gender [@Boroditsky2003], among many others [@Wolff2011].
-Differences in cognition between speakers of different languages have often been used to suggest, explain, or exemplify cultural differences between speakers of those languages.
-Findings in studies of both language and of culture provide convergent evidence suggesting that variation across languages and cultures may shape broad variation in how people think about similarity between, for instance, different colors or objects.
-
-Looking beyond this domain-specific variation, we can also consider broader notions of similarity and relatedness between concepts across domains.
-The Free Association Norms [@FreeAssoc], for example, measures human judgment in semantic relatedness across domains and contexts.
-With the availability of large linguistic corpora, we can examine the similarity of concepts that are not circumscribed in individual domains (as color, number, and gender are), allowing us to answer more general questions about variation in cognition between speakers of different languages.
-By measuring the similarity between arbitrary words (as commonly done with lexical co-occurrence models), it may be possible to model the shape of similarity space in order to capture cross-linguistic and cross-cultural variation and provide a more general answer to the question of how language influences our conception of the world.
-
-Taxonomic and thematic similarity provide a convenient entry point to broader debates about cross-linguistic and cross-cultural variation in notions of similarity.
-Taxonomic categorization is based on the similarity of attributes, for example, similar perceptual properties, like shared color or shape, among objects.
-In contrast, thematic categorization is based on causal, spatial, and temporal relationships among objects [@Markman1984].
-To illustrate this point, if a participant is given the words “chicken” and “grass”, and asked which of those words are more closely related to the word “cow”, the pairing “chicken” - “cow” indicates a taxonomic match, whereas “grass” - “cow” indicates a thematic match.
-
-@Ji2004 found that preferences for taxonomic and thematic matches differ across culture, even when controlling for testing language and fluency.
-Specifically, Chinese participants made more thematic matches than taxonomic, while the converse was true for European Americans.
-This difference held even for Chinese participants tested in English (rather than Mandarin), suggesting that culture has an effect on the categorization strategy independent of the test language.
-However, the study also found an effect of language within Chinese participants from mainland China (when tested both in China and in the US): their preference for thematic categorization was significantly lower when tested in English compared to Mandarin Chinese.
-This suggests that test language also influences categorization strategies.
-Ji et al.
-characterize these results as demonstrating that culture (independent of language) leads to different styles of reasoning about similarity, whereas language serves as a “tuning” mechanism operating within a culturally-specific style, by activating representations corresponding to the language being used.
-
-## Cross-cultural variation in similarity
-The account that culture drives differences in categorization style has been one favored by other non-linguistic studies that use taxonomic vs thematic categorization to probe similarity judgment.
-A similar study to the aforementioned shows that when shown pictorial triads that represent words (i.e.
-pictures of an ant, a bee, and honey), Chinese children (9-10 years old) scored higher on thematic categorization compared to American children of the same age range, and vice versa for taxonomic categorization [@Chiu1972].
-Additionally, the cross-cultural differences in similarity judgment seem to persist even when the stimuli are more perceptual and less conceptual.
-@Norenzayan2002 conducted a study where participants are shown a target stimulus beneath two groups of 4 similar objects.
-The target shares a common feature with all the objects in one group, and only shares another one feature with each member of that group.
-Meanwhile, the target shares many features with 3 out of 4 members of the other group, but does not share any 1 feature in common with the entire group.
-The study showed that American participants judged the target to be more similar with the former group more often, and vice versa for Chinese participants.
-Since differences in categorization style persist with novel stimuli (as opposed to previously seen words or pictures of concepts), this suggests that participants from different cultural backgrounds are utilizing different reasoning strategies when making similarity judgments.
-
-Most commonly, researchers account for the differences in similarity judgment described above by differences in analytic vs holistic processing and in attention between Eastern and Western cultures.
-According to this framework, East Asians attend more to relationships between objects and context and reason more holistically, whereas Westerners attend more to objects and their properties, and reason analytically [@Nisbett2003].
-The analytic-holistic cultural difference in reasoning style has been observed in other non-linguistic tasks.
-For example, in a rod-and-frame test [@Witkin1954], East Asian (Taiwanese Chinese) participants are more influenced by the position of the surrounding frame than European Americans [@Ji2000], suggesting a higher level of sensitivity to context.
-East Asians (Koreans) have also been demonstrated to make more situational attributions for behaviors than European Americans, who make more dispositional attributions [@Choi1999], again suggesting higher sensitivity to context.
-When shown a complex scene with foreground and background information, Japanese participants made more statements about contextual information and relationships between objects than Americans did [@Masuda2001].
-Non-linguistic tasks have also shown that participants from Eastern and Western cultures differ in where they focus their visual attention.
-Another study presented American and Chinese participants with photographs of an object on a complex background [@Chua2005].
-They found that Chinese participants made more eye saccades to the background compared to American participants, and that American participants looked at the object more quickly.
-These cross-cultural differences in attention and analytic vs holistic processing are seen to map onto the cross-cultural differences in similarity judgment: because East Asian participants attend more to the context between objects and reason more holistically, it stands to reason that they would consider words that appear in the same context (i.e.
-thematically similar) to be more similar than taxonomically-similar words.
-
-Studies that explain these cross-cultural differences in reasoning and similarity judgment with a cultural framework often draw on social and historical contexts as the distal cause for these differences.
-For example, social structure and social practice can explain why different cultures develop different reasoning habits.
-To demonstrate this, researchers have looked at regions that are geographically close but with different social structures.
-@Kitayama2006 showed that Hokkaido Japanese demonstrated greater dispositional bias in attribution of behaviors compared to non-Hokkaido Japanese.
-The study suggested that this difference is correlated to the fact that Hokkaido was settled quite recently (mid-19th century) by pioneers from southern Japan, and thus its social practices (e.g.
-daily routines, child-rearing practices, and explicit education) would be influenced by the independent, goal-oriented characteristic of pioneer life.
-Another study showed that Northern Italians (more independent) categorized objects in a more taxonomic manner than Southern Italians (more interdependent) [@Knight2007].
-These studies, however, stopped short of providing a mechanism for the nature of the relationship between differences in social structures and differences in reasoning and similarity judgments.
-
-Another component of the social context explanation seems to be more tenable regarding the causal connection between cross-cultural differences in social practice and those in similarity judgments: that different patterns of attention are passed on by caregivers to children.
-@Fernald1993 found that American mothers labeled toys and pointed out their attributes more often than do Japanese mothers, while Japanese mothers tended to use the toys to engage their infants in social routines more often than American mothers.
-@Tardif1997 found that English-speaking caregivers produced more nouns than verbs in child-directed speech, while Mandarin-speaking caregivers emphasized verbs over nouns.
-Emphasis on labeling objects and focus on nouns over verbs might lead infants to attend to objects and their taxonomic categorizations, while emphasis on social practices and producing more verbs might direct infants' attention to the relationship between objects.
-Such differences in early-childhood environments could tune children’s attention to either object or context, and result in cross-cultural differences in similarity judgments (preferring either taxonomic or thematic, respectively) in adulthood.
-
-The above view explains cross-cultural differences in similarity judgment tasks as variation in the conceptualization of similarity itself.
-Alternatively, these judgments could be shaped by cross-cultural differences in the statistics of the environment, and accordingly the content of everyday experiences.
-Perhaps when confronted with the triad task, participants from all cultures follow the same process for reasoning about similarity, but rely on language or culture-specific inputs to this process.
-For example, it may be that Vietnamese participants are more likely to have knowledge of farming practices than Americans, and may associate cows and grass more strongly (as grass is the typical feed for cows in the small-scale family farming contexts common in Vietnam).
-Americans, on the other hand, may have strong associations between cows and chickens as a result of encountering them together in children’s books or petting zoo contexts.
-If we observe a difference in categorization between, say Vietnamese and US participants, perhaps they use the same procedure (considering similarity that is influenced by both taxonomic and thematic relations), but the inputs to this procedure differ between cultures, with Vietnamese participants exposed to more instances of “cow” and “grass” occurring together, compared to US participants.
-
-A study by @Miyamoto2006 lends support to this theory.
-The study randomly sampled scenes from different-sized cities in Japan and the US.
-Both subjective (judgment by American and East Asian college students) and objective (number of objects as counted by an automated program) showed that Japanese scenes were more complex and contained a larger number of objects than American scenes.
-This suggests that people living in Japan would more frequently encounter perceptual environments that contain more relationships between objects compared to those who live in the US.
-Japanese scenes therefore might encourage focus on the overall context, while American scenes might encourage focus on a few salient objects.
-
-Differences in environmental statistics extend beyond the immediate environment to cultural artifacts.
-@Tsai2007 showed that best-selling storybooks in the US contain more pictures of excited states (e.g.
-open-mouthed smiles, wide-open eyes) compared to best-selling storybooks in Taiwan, which contain more pictures of calm states.
-European American preschoolers also perceived excited states as happier and more desirable compared to calm states, and vice versa for Taiwanese Chinese preschoolers.
-The study also showed that there is a causal link between exposure to environmental statistics and personal preference: regardless of culture, exposure to exciting (vs.
-calm) storybooks increased children’s preference for the  corresponding activities.
-Broadly, this suggests that cultural artifacts or information in language (rather than direct, first-hand lived experiences) could be crucial factors in driving cross-cultural variation.
-
-## Language as a proxy of variation in experience
-While co-occurrences in experience are difficult to measure, co-occurrence in language can provide a rough proxy--and indeed, language may afford many of the “experiences” that people have with infrequently encountered items, like cows or helicopters.
-In the planned analyses, we will use co-occurrence in language as a proxy of cultural experience.
-This is a generalizing assumption, and while no linguistic corpus can be expected to fully capture a culture, and different linguistic corpora may capture different variables of a culture, using this proxy as a model of culture provides a conservative test of the hypothesis that differences in the input, rather than the process, of reasoning produces cultural variation in this task.
-This means that if such a model does work -- if linguistic co-occurrence can predict cultural variation in this similarity task without building differences in the decision process into the model -- it is relatively strong evidence that language alone (perhaps as a more easily observed source of information on broader cultural and ecological variation) may account for these cross-cultural differences in reasoning.[^footnote]
-
-Indeed, previous work suggests that using lexical co-occurrence as a proxy can be useful in thinking about similarity judgments.
-Natural language processing tasks have found that lexical co-occurrence is a good predictor for performance in similarity judgment tasks.
-@Griffiths2007 showed that a model that takes word-document co-occurrence as input can be used to predict word association and the effects of semantic association on a variety of linguistic tasks.
-Additionally, lexical semantic models that are constructed using lexical co-occurrence (as opposed to annotated relations) have been shown to perform well on predicting human judgments about similarity between word pairs that are either thematically or taxonomically related [@Rohde2006].
-
-Our current study will be using 2 measures of lexical co-occurrence: 1) raw lexical co-occurrences and 2) cosined distances of fastText word vectors.
-fastText is a system that uses lexical co-occurrence information to generate a vector representing each word in its lexicon [@Mikolov2018].
-fastText uses a continuous bag-of-words model, which takes into account a symmetric window of words surrounding the word in question and maximizes the log-likelihood of the probability of the word given its context.
-Calculating the cosine-similarity between word vectors from fastText gives us a score of how similar the contexts of these words are.
-Therefore, words that occur in the same context (high lexical co-occurrence) would have a larger cosine-similarity score.
-
-It must be noted that fastText supplements the lexical co-occurrence information by simultaneously training weight vectors for each position relative to the word in question, as well as adding sub-word information (bag-of-character n-gram vectors for each character forming the words).
-The similarity judgment prediction given by fastText may be more higher than a model using purely lexical co-occurrence information.
-However, models that use only lexical co-occurrence information (with or without a simple position weight system that gives more weight to words that are closer to the word in question) also perform well in similarity prediction tasks.
-For this study, due to the lack of large cleaned corpora for Mandarin and Vietnamese, we are leveraging fastText pre-trained models on the languages we are interested in @Grave2018.
-
-Systems like fastText and word2vec have been demonstrated to be good predictors for similarity judgments.
-@Liu2019 showed that fastText performed well as the data for a system matching responses in a knowledge base by how similar they are to a customer’s query.
-A study by @Jatnika2019 tested a word2vec model trained on the English wikipedia corpus against 353 word pairs labeled with similarity values based on human judgment.
-The word2vec model correlates moderately with human judgment.
-fastText has also been shown to be sensitive towards cultural effects on word meanings: @Thompson2020 applied fastText to language-specific Wikipedia corpus (among others) to generate a “semantic neighborhood” of 1010 meanings in different languages.
-The study showed that languages that are spoken by more similar cultures, more geographically proximate and/or historically related had more semantic neighborhoods that aligned.
-This is a proof of concept for our use of fastText in different languages with varying levels of relatedness.
-
-## The present study
-@Ji2004 showed the difference in similarity judgment between Chinese and European Americans (the former prefers thematic categorization while the latter prefers taxonomic).
-However, their evidence is not sufficient to conclude that it is culture that drives this difference, as their cross-cultural data is correlational.
-Furthermore, they have yet to rule out all mechanisms by which language could be relevant to the task.
-For example, their language manipulation (bilingual speakers from Mainland China making more taxonomic categorizations when tested in language) only points to an offline effect of language because it does not prevent participants from accessing linguistic representations.
-A stronger claim could have been made if verbal interference had been conducted, and if cross-cultural differences had remained.
-This would have been stronger in eliminating online effect of language as a potential cause for cross-cultural differences in similarity judgment.
-
-Additionally, outside of language, cross-cultural differences could come from a couple different mechanisms: @Ji2004 suggested that the notion of similarity is what varies across cultural groups, but it’s quite possible that similarity is regarded in the same way and it’s actually the input to this similarity judgment that varies across culture contexts.
-It might be possible to gain traction on possible mechanisms by examining whether variation in similarity judgments co-varies with environmental statistics that differ across the cultural and linguistic contexts.
-
-In this study, we ask whether variation in lexical co-occurrence can account for the cross-context (culture and language) differences observed in how people evaluate similarity.
-Firstly, we attempt to replicate @Ji2004 by running a study comparing English speakers in the US and Mandarin speakers in mainland China.
-Secondly, we evaluate whether the differences observed between English and Mandarin speakers’ similarity judgments also extend to comparisons between English and Vietnamese, by running a similar study between English speakers in the US and Vietnamese speakers in Vietnam.
-Vietnam is a Southeast Asian country that borders China and is historically greatly influenced by Chinese culture [@Hui2002].
-Therefore, it serves as a suitable cultural context to investigate whether the claim made by @Ji2004 and previous studies, that Eastern and Western cultures have different notions of similarity, extends beyond mainland China.
-
-We then ask to what extent similarity judgments show cross-context differences that align with co-occurrence patterns in participants’ languages.
-We would only see a main effect of cultural context if the notion of differing notions of similarity is driving these cross-cultural differences.
-Meanwhile, if we do see variation in responding trial-to-trial that tracks with lexical co-occurrence statistics (as a rough proxy combining both linguistic and cultural context), this would give traction to the view that cross-cultural notions of similarity might be similar, and it is environmental statistics that guide the differences in similarity judgments.
-To preview our results, we find that, while we do not see overall group differences (between the East Asian contexts and the US) in similarity, we do find language-specific co-occurrence can indeed explain cross-context differences in similarity judgments.
-In contrast to previous accounts, by which culture induces differing conceptions of similarity (varying between taxonomic and thematic), these findings provide an alternative, and more specific, account by which language may explain these cross-cultural differences without invoking variation in notions of similarity.
-
-# Methods 
-```{r get exclusion results from 1_exclusions.Rmd}
-source("../1_exclusions/1_exclusionsCN.Rmd")
-source("../1_exclusions/1_exclusionsUS.Rmd")
-source("../1_exclusions/1_exclusionsVN.Rmd")
-```
-
-```{r demog_E, TODO: move outside, include = F}
-demog <- c("demog-dropdown", "demog-multi-choice", "demog-free-response", "demog-multi-select")
-df.demog_E <- df.resp_E %>%
-  filter(trial_type %in% demog) 
-#write.csv(data_demog, "data_anon_demog_0201.csv")
-
-AGE = 97 #index for age answer
-GENDER = 115 #index for gender answer
-split_responses <- function(responses) {
-  responses <- as.character(responses)
-  response_list <- unlist(strsplit(responses, ',|:'))
-  response_list <- response_list[seq(1, length(response_list))]
-  response_list <- gsub("}", "", response_list)
-  response_list <- gsub("\"", "", response_list)
-  return(response_list)
-}
-
-get_age <- Vectorize(function(responses) {
-  responses <- split_responses(responses)
-  if(responses[AGE-1] != "A0") {warnings("cannot find age answer")}
-  else{return (responses[AGE])}
-})
-
-get_gender <- Vectorize(function(responses) {
-  responses <- split_responses(responses)
-  if(responses[GENDER-1] != "A1") {warnings("cannot find gender answer")}
-  else{return (responses[GENDER])}
-})
-
-df.age_gender_E <- df.demog_E %>%
-  filter(variable_type == "demog_age_gender_ethnic") %>%
-  select(subject, responses) %>%
-  mutate(age = as.numeric(get_age(responses))) %>%
-  mutate(age = as.numeric(age)) %>%
-  mutate(gender = get_gender(responses))
-
-df.age_gender_E_summ <- df.age_gender_E %>%
-  summarize(mean_age = mean(age), 
-            median_age = median(age), 
-            sd_age = sd(age))
-```
-
-```{r demog_V, TODO: move outside, include = F}
-demog <- c("demog-dropdown", "demog-multi-choice", "demog-free-response", "demog-multi-select")
-df.demog_V <- df.resp_V %>%
-  filter(trial_type %in% demog)
-
-AGE = 97 #index for age answer
-GENDER = 115 #index for gender answer
-split_responses <- function(responses) {
-  responses <- as.character(responses)
-  response_list <- unlist(strsplit(responses, ',|:'))
-  response_list <- response_list[seq(1, length(response_list))]
-  response_list <- gsub("}", "", response_list)
-  response_list <- gsub("\"", "", response_list)
-  return(response_list)
-}
-
-get_age <- Vectorize(function(responses) {
-  responses <- split_responses(responses)
-  if(responses[AGE-1] != "A0") {warnings("cannot find age answer")}
-  else{return (responses[AGE])}
-})
-
-get_gender <- Vectorize(function(responses) {
-  responses <- split_responses(responses)
-  if(responses[GENDER-1] != "A1") {warnings("cannot find gender answer")}
-  else{return (responses[GENDER])}
-})
-
-df.age_gender_V <- df.demog_V %>%
-  filter(variable_type == "demog_age_gender_ethnic") %>%
-  select(subject, responses) %>%
-  mutate(age = as.numeric(get_age(responses))) %>%
-  mutate(age = as.numeric(age)) %>%
-  mutate(gender = get_gender(responses))
-
-df.age_gender_V_summ <- df.age_gender_V %>%
-  summarize(mean_age = mean(age), 
-            median_age = median(age), 
-            sd_age = sd(age))
-```
-
-```{r demog_M, TODO: MOVE outside, include = F}
-demog <- c("demog-dropdown", "demog-multi-choice", "demog-free-response", "demog-multi-select")
-df.demog_M <- df.resp_M %>%
-  filter(trial_type %in% demog) 
-#write.csv(data_demog, "data_anon_demog_0201.csv")
-
-AGE = 97 #index for age answer
-GENDER = 115 #index for gender answer
-split_responses <- function(responses) {
-  responses <- as.character(responses)
-  response_list <- unlist(strsplit(responses, ',|:'))
-  response_list <- response_list[seq(1, length(response_list))]
-  response_list <- gsub("}", "", response_list)
-  response_list <- gsub("\"", "", response_list)
-  return(response_list)
-}
-
-get_age <- Vectorize(function(responses) {
-  responses <- split_responses(responses)
-  if(responses[AGE-1] != "A0") {warnings("cannot find age answer")}
-  else{return (responses[AGE])}
-})
-
-get_gender <- Vectorize(function(responses) {
-  responses <- split_responses(responses)
-  if(responses[GENDER-1] != "A1") {warnings("cannot find gender answer")}
-  else{return (responses[GENDER])}
-})
-
-df.age_gender_M <- df.demog_M %>%
-  filter(variable_type == "demog_age_gender_ethnic") %>%
-  select(subject, responses) %>%
-  mutate(age = as.numeric(get_age(responses))) %>%
-  mutate(age = as.numeric(age)) %>%
-  mutate(gender = get_gender(responses))
-
-df.age_gender_M_summ <- df.age_gender_M %>%
-  summarize(mean_age = mean(age), 
-            median_age = median(age), 
-            sd_age = sd(age))
-```
-## Participants
-We recruited `r length(unique(df.ppts_finished_E$subject))` participants from the US, `r length(unique(df.ppts_finished_V$subject))` participants from Vietnam, and `r length(unique(df.ppts_finished_M$subject))` participants from mainland China.
-US participants were recruited through snowball sampling seeded with Stanford email lists, Vietnam participants were recruited through snowball sampling seeded with Vietnam-based student groups on Facebook, and mainland China participants were recruited through snowball smapling seeded with group chats on WeChat.
-US participants were compensated with $5 gift certificates (USD), VN participants received 50,000₫ (VND) in phone credit, and mainland China participants received 25CNY through WeChat credit transfer.
-
-We excluded `r length(unique(df.ppts_finished_E$subject)) - length(unique(df.ppts_att_E$subject))` US participants, `r length(unique(df.ppts_finished_V$subject)) - length(unique(df.ppts_att_V$subject))` Vietnam participants, and `r length(unique(df.ppts_finished_M$subject)) - length(unique(df.ppts_att_M$subject))` China participants who did not answer all attention checks correctly.
-We followed 4 exclusion criteria that aim to retain only participants who are influenced by one culture: (1) non-native speakers of English and Vietnamese, respectively, (2) fluent in at least one of the other two study languages (Vietnamese for US participants, English for Vietnamese participants and Chinese participants), (3) have lived outside of the test country (US, Vietnam, or China) for more than two years, and (4) have significant international experience (more than 6 international experiences of 2 days or longer.) We did not use a particular criterion for a language if it would exclude 25% or more of any one sample.
-In this round of exclusion, we excluded `r length(unique(df.ppts_att_E$subject)) - length(unique(df.resp_E$subject))` US, `r length(unique(df.ppts_att_V$subject)) - length(unique(df.resp_V$subject))` Vietnam participants, and `r length(unique(df.ppts_att_M$subject)) - length(unique(df.resp_M$subject))` China participants.
-After these exclusions, the US sample included `r length(unique(df.resp_E$subject))` participants (`r df.age_gender_E %>% filter(gender == "Male") %>% count()`M, `r df.age_gender_E %>% filter(gender == "Female") %>% count()`F, `r df.age_gender_E %>% filter(gender == "Non-binary") %>% count()` non-binary, `r df.age_gender_E %>% filter(gender == "Decline to answer") %>% count()` other), with mean age = `r round(df.age_gender_E_summ$mean_age, 2)` (SD = `r round(df.age_gender_E_summ$sd_age, 2)`) and median age = `r df.age_gender_E_summ$median_age`.
-The Vietnam sample included `r length(unique(df.resp_V$subject))` participants (`r df.age_gender_V %>% filter(gender == "Nam") %>% count()`M, `r df.age_gender_V %>% filter(gender == "Nữ") %>% count()`F), with mean age = `r round(df.age_gender_V_summ$mean_age, 2)` (SD = `r round(df.age_gender_V_summ$sd_age, 2)`) and median age = `r df.age_gender_V_summ$median_age`.
-The China sample included `r length(unique(df.resp_M$subject))` participants (`r df.age_gender_M %>% filter(gender == "男性") %>% count()`M, `r df.age_gender_M %>% filter(gender == "女性") %>% count()`F), with mean age = `r round(df.age_gender_M_summ$mean_age, 2)` (SD = `r round(df.age_gender_M_summ$sd_age, 2)`) and median age = `r df.age_gender_M_summ$median_age`.
-
-Notably, we lost a majority of our Vietnam participants (more than 60%) in the attention check exclusion.
-One reason we suspect why this might have happened is because our Vietnam participants are less familiar with research surveys and attention check questions, and thus might have thought too much about the attention check questions.
-We carried out an exploratory analysis where we used a less stringent attention check exclusion (covered in the final part of the Results & Analysis section).
-To preview our findings for this analysis, we did not find any difference in significant results when compared with the main analysis.
-
-## Stimuli
-We adapted stimuli from previous studies to create a set of test triads consisting of a cue, with one thematic and one taxonomic match option.
-For example, “cow,” “grass,” and “chicken,” where “cow” is the cue, “grass” is the thematic match, and “chicken” the taxonomic match.
-We included 105 such triads, a superset including triads pulled from supplemental information and in-text examples across the literature, and others that we adapted or created (see SI for the full list of stimuli and sources).
-We selected triads on the basis of cultural familiarity in the US, Vietnam, and China.
-The triads were originally in English; they were translated to Vietnamese and Mandarin by a fluent bilingual speaker in each language.
-The translations were then checked for accuracy after backtranslation to English by another fluent bilingual in each language who was naive to the original English versions.
-
-Each participant completed all 105 triads in sets of 21 trials at a time (10 test triads, 10 filler triads, and 1 attention check per page), by selecting the match most related to the cue (“Which thing is most closely related to the bolded item?” or "Thu nào liên quan nhat voi thu đuoc in đam?").
-The test triads were presented with 105 filler triads mixed in, to obscure the taxonomic-thematic two-answer forced choice structure of the test stimuli and reduce the likelihood that participants would become aware of the design.
-The filler triads were groups of three semantically related words, but where the match options were not distinguished by thematic vs.
-taxonomic similarity, e.g., cue “bird” with match options “lizard” and “toad.” Additionally, we included 10 attention check trials, which were formatted like the test and filler triads but included an instruction instead of a cue item, e.g., “Choose wife” with match options “wife” and “husband.” In total, each participant completed 210 similarity judgments and 10 attention check questions, with triads presented in randomized orders that varied between subjects.
-
-## Corpus model 
-Our general approach is to build a model of similarity that is based on collocation counts in each language.
-
-### Raw lexical co-occurrences
-To give an intuition for our model, consider the cow-grass-chicken triad: we counted how many times “cow” and “grass” co-occur within a window of text in each corpus, and compare this to how many times “cow” and “chicken” co-occur.
-Our similarity prediction is then proportional to the relative frequency of these pairs.
-For example, if the thematic cow-grass match accounts for 30% of collocations for this triad (with cow-chicken making up the other 70%), then our model predicts, correspondingly, that 30% of responses to the triad will be grass, and the other 70% chicken.
-We then use a mixed-effects regression to evaluate how well each corpus collocate model predicts participants’ similarity judgments, across triads and languages.
-
-#### Collocate retrieval and coding
-For our English co-occurrence metric, we used the online interface of the Corpus of Contemporary American English [@COCA] to retrieve collocation counts.
-We recorded the raw count of times that any cue-match pair (e.g., cow-grass or cow-chicken) co-occur in a window of 19 words, which is the maximum window size in the online interface, and closest to the sentence co-occurrence metric in our VI corpus collocation counts.
-
-To determine Vietnamese co-occurrence, we used the raw frequency of sentence co-occurrences from a subset of the Vietnamese corpus in the Leipzig Corpora Collection [@VICorpus]; this corpus includes 70 million Vietnamese sentences, but our corpus data comes from a 1 million sentence subset for which co-occurrence counts are available for download.
-Vietnamese makes very frequent use of compositional morphology but the written language  uses spacing to delineate syllable boundaries rather than word boundaries.
-Accordingly, collocate searches returned instances of both target terms and many morphologically related, but distinct, words.
-We included in our counts any instances of the target term or close semantic neighbors containing the same morpheme(s) as long as they entailed a likely literal reference to the target term.
-For example, our search for collocates of the term “gà” (chicken) also returned “gà mái,” a distinct word for female chickens.
-Despite being a different word, “gà mái” both includes the morpheme for “chicken” and entails reference to a chicken.
-Accordingly, instances of both “gà” and “gà mái” were included in our collocate count for “chicken.” Some compounds do not meet this criteria, and were excluded from collocate counts.
-For example “trái cây” (tree.fruits) includes the same syllable as the word “cây” (tree), but refers to fruit that comes from trees, not the trees themselves, and was therefore excluded from our collocate counts for “tree.”
-
-We were unable to obtain a Mandarin corpus with similar number of sentences as the aforementioned English and Vietnamese corpora, hence we did not include any analysis based on raw lexical co-occurrences with Mandarin.
-
-#### Collocate similarity model
-From the raw co-occurrence counts of each triad, we calculated the thematic co-occurrence ratio as the number of thematic co-occurrences over the sum of thematic and taxonomic co-occurrences.
-We did this for both the English and Vietnamese corpus co-occurrence counts.
-In this way, we obtained predictions for 73 of 105 triads from the Vietnamese corpus and 104 of 105 triads from English.
-We therefore limited all analyses reported here to the subset of triads for which our corpus-based model can make meaningful predictions, meaning triads that have at least one non-zero collocate count (either thematic or taxonomic match).
-We replaced any remaining zero collocate counts with $\epsilon$ to account for sparsity in the corpus data.
-We then tested whether these simple relative frequency models predict US and VN responding.
-
-### Cosine distance of word vectors
-To give an intuition for our model, consider again the cow-grass-chicken triad: we retrieved word vectors for "cow" and "grass", and calculate the cosine distance between these vectors.
-Similarly, we retrieved vectors for "cow" and "chicken" and calculate the cosine distance between them.
-Our similarity prediction is then inversely proportional to the cosine distance of these pairs.
-This is because a larger cosine distance means the word vectors are further apart, and thus the words are less similar.
-For example, if the cosine distance of thematic cow-grass is 0.7 and the cosine distance of taxonomic cow-chicken is 0.3, then our model predicts, correspondingly, that 30% of responses to the triad will be grass, and the other 70% chicken.
-We then use a mixed-effects regression to evaluate how well each corpus model predicts participants’ similarity judgments, across triads and languages.
-
-#### Collocate retrieval
-We use the fastText pre-trained models of English, Mandarin, and Vietnamese in @Grave2018.
-These models are trained on Common Crawl and Wikipedia using We distribute pre-trained word vectors for 157 languages, trained on Common Crawl and Wikipedia using fastText.
-These models were trained using a Continuous Bag of Words (CBOW) with position-weights and a window of size 5.
-The models use character n-grams of length 5 and 10  negative examples.From the aforementioned models, we retrieve the word vectors (dimension 300) for each word we are interested in.
-
-#### Collocate similarity model
-From the word vectors, we calculated the cosine distance between each cue-thematic match (thematic cosine distance) and cue-taxonomic match (taxonomic cosine distance), using the spatial.distance.cosine function from the SciPy package [@2020SciPy].
-We then calculated the thematic cosine distance proportion as thematic cosine distance over the sum of taxonomic cosine distance and thematic cosine distance.
-We did this for all three corpora.
-We were able to obtain predictions for all triads in all languages.
-
-## Data analysis
-We used `r cite_r("r-references.bib")` for all our analyses.
-
-# Results
-```{r combine corpus and behavior data, include = F}
-#source("../2_combine/2_combine.Rmd")
-df <- read.csv("../../data/data_USCNVN_ENZHVI.csv")
-```
-
-## Do we extend previous work reporting a preference for taxonomic matching in the US and thematic matching in Asia?
-
-```{r warning=FALSE, include=FALSE, paged.print=TRUE}
-df.country <- df %>%
-  group_by(subject, country) %>%
-  summarize(theme_resp_percent = mean(responses_theme, na.rm = T))
-
-df.country_sum <- df.country %>%
-  group_by(country) %>%
-  summarize(mean_theme_resp_percent = mean(theme_resp_percent), 
-            sd_theme_resp_percent = sd(theme_resp_percent))
-
-fit.country = glmer(responses_theme ~ country + (1 | subject) + (country | triad), 
-                    data = df, 
-                    family = "binomial")
-summary(fit.country) 
-fit.country.anova = Anova(fit.country, type=3)
-
-fit.country_EN_VN = glmer(responses_theme ~ country + (1 | subject) + (country | triad), 
-                    data = df %>% filter(country != "China"),
-                    family = "binomial")
-summary(fit.country_EN_VN) 
-```
-The group means of proportion of thematic response in mainland China is the highest (M = `r round((df.country_sum %>% filter(country == "China"))$mean_theme_resp_percent, 2)`, SD = `r round((df.country_sum %>% filter(country == "China"))$sd_theme_resp_percent, 2)`), followed by the groups means in Vietnam (M = `r round((df.country_sum %>% filter(country == "Vietnam"))$mean_theme_resp_percent, 2)`, SD = `r round((df.country_sum %>% filter(country == "Vietnam"))$sd_theme_resp_percent, 2)`), which is slightly higher than that of the US (M = `r round((df.country_sum %>% filter(country == "US"))$mean_theme_resp_percent, 2)`, SD = `r round((df.country_sum %>% filter(country == "US"))$sd_theme_resp_percent, 2)`).
-
-```{r echo=FALSE, warning=FALSE, fig.cap="Proportion of thematic responses by country.
-Only US-China responding comparison shows a siginficant difference.
-We could not extend this to US-Vietnam responding comparison."}
-
-#show violin plot
-ggplot(df.country,
-       mapping = aes(x = factor(country, levels=c("China", "US", "Vietnam")), 
-                     y = theme_resp_percent, 
-                     color = factor(country, levels=c("China", "US", "Vietnam")))) +
-  geom_violin() +
-  geom_jitter(height = 0, 
-              alpha = 0.3) +  
-  stat_summary(fun.data = "mean_cl_boot", 
-               geom = "pointrange") + 
-  labs(y = "Proportion Thematic Chosen", 
-       x = "Country", 
-       color = "Country") + 
-  scale_color_manual(values=c("#D63230", "#1C77C3", "#F39237"))
-```
-
-```{r correlation of country response, echo=FALSE, warning=FALSE}
-#US-China, US-Vietnam, China-Vietnam
-df.triad_country <- df %>%
-  group_by(triad, country) %>%
-  summarize(emp_theme_prop = mean(responses_theme))
-
-df.triad_country <- pivot_wider(data = df.triad_country, 
-                                names_from = country, 
-                                values_from = emp_theme_prop)
-plotUSCN = ggplot(data = df.triad_country,
-                  mapping = aes(x = US, 
-                                y = China, 
-                                label = triad)) +
-   geom_text() + 
-   geom_smooth(method = "lm") +
-   labs(x = "Proportion Thematic Chosen (US)", 
-        y = "Proportion Thematic Chosen (China)") + 
-   xlim(0, 1) + 
-   ylim(0, 1) + 
-  theme(axis.title = element_text(size=rel(0.75)))
-
-plotUSVN = ggplot(data = df.triad_country,
-                  mapping = aes(x = US, 
-                                y = Vietnam, 
-                                label = triad)) +
-   geom_text() + 
-   geom_smooth(method = "lm") +
-   labs(x = "Proportion Thematic Chosen (US)", 
-        y = "Proportion Thematic Chosen (Vietnam)") + 
-   xlim(0, 1) + 
-   ylim(0, 1)  + 
-  theme(axis.title = element_text(size=rel(0.75)))
-
-plotCNVN = ggplot(data = df.triad_country,
-                  mapping = aes(x = Vietnam,
-                                y = China, 
-                                label = triad)) +
-   geom_text() + 
-   geom_smooth(method = "lm") +
-   labs(x = "Proportion Thematic Chosen (Vietnam)", 
-        y = "Proportion Thematic Chosen (China)") + 
-   xlim(0, 1) + 
-   ylim(0, 1)  + 
-  theme(axis.title = element_text(size=rel(0.75)))
-
-corr.USCN = apa_print(cor.test(df.triad_country$US, 
-                  df.triad_country$China, na.rm=T))
-
-corr.USVN = apa_print(cor.test(df.triad_country$US, 
-                  df.triad_country$Vietnam, na.rm=T))
-
-corr.CNVN = apa_print(cor.test(df.triad_country$China, 
-                  df.triad_country$Vietnam, na.rm=T))
-```
-
-```{r warning = F, fig.width = 8, fig.cap="Correlation between proportion thematic chosen by US-China participants, US-Vietnam participants, and China-Vietnam participants.
-All three comparisons show strong correlation, suggesting a strong signal of universality across cultural contexts regarding similarity judgments"}
-plotUSCN + plotUSVN + plotCNVN +
-  plot_layout(ncol = 3)
-```
-
-With a Pearson correlation test, we observed high correlations between thematic responding across all three countries.
-The proportion of US thematic responding is strongly correlated with thematic responding in China, `r corr.USCN$full_result`.
-The proportion of US thematic responding is strongly correlated with thematic responding in Vietnam, `r corr.USVN$full_result`.
-Likewise, the proportion of China thematic response is strongly correlated with thematic responding in Vietnam, `r corr.CNVN$full_result`.
-This points to a strong signal of universality across cultural contexts regarding similarity judgments.
-
-```{r USCN effect size comparison, include=FALSE}
-USCN_cohen <- cohen.d(df.triad_country$China, df.triad_country$US)
-```
-
-For comparison with previous work, we also included an effect size comparison for the difference in US-China thematic response data (though this was not a planned analysis).
-The effect size for this analysis was d = `r USCN_cohen$estimate`, a small effect size.
-This is smaller than the effect size from @Ji2004, even when we are unable to make a direct comparison.
-Calculating the effect size from the ANOVA reported in @Ji2004 between US participants tested in English and mainland China participants tested in English (both groups tested in the US) yields a Cohen's d = 0.81.
-@Ji2004 reported that mean thematic response for mainland China participants tested in Mandarin Chinese is higher than for those tested in English, so the effect size for a comparison between mainland China participants tested in Mandarin Chinese and US participants tested in English (parallel to our comparison) would likely have yielded an even larger effect size than 0.814.
-It is possible that we failed to replicate the magnitude of effect from @Ji2004 because the previous study calculated their dependent variable as frequency of thematic responses minus frequency of taxonomic responses, whereas our dependent variable is proportion of thematic response over total number of responses.
-
-To test for cross-context differences in similarity judgments between the countries, we ran a mixed-effects logistic regression predicting triad responding (taxonomic or thematic) with country (US, China, or Vietnam) as a fixed effect.
-As random effects, we included an intercept per subject and one per triad, as well as by-triad random slopes for country to account for variation in the country effect across triads.
-In R syntax, the model is: response ~ country + (1 | subject) + (country | triad).
-
-Overall, there is a significant effect of country on proportion of thematic responses ($\chi^2$(`r fit.country.anova["country", "Df"]`) = `r round(fit.country.anova["country", "Chisq"], 2)`, p < .001).
-However, this effect is driven by the difference between US and China responding ($\beta$ = `r round(fixef(fit.country)["countryUS"], 2)`, p < .001).
-There is no statistical difference between the Vietnam and China responding ($\beta$ = `r round(fixef(fit.country)["countryVietnam"], 2)`, p = `r round(as.data.frame(summary(fit.country)[["coefficients"]])["countryVietnam", "Pr(>|z|)"], 2)`), and the US and Vietnam responding ($\beta$ = `r round(fixef(fit.country_EN_VN)["countryVietnam"], 2)`, p = `r round(as.data.frame(summary(fit.country_EN_VN)[["coefficients"]])["countryVietnam", "Pr(>|z|)"], 3)`).
-
-On this analysis, we do not find support that the US-China tendencies toward taxonomic and thematic responding (respectively) extend to the US-Vietnam comparison.
-Accordingly, we cannot speak to overall biases toward thematic responding across Asian cultural contexts broadly, but we do replicate the differences documented by @Ji2004 between the US and China.
-However, in our corpus model comparison, we do find evidence for different, more fine-grained variation in similarity judgments between the US and Vietnam.
-
-## Can the differences in similarity judgments between English, Mandarin and Vietnamese speakers be explained by variation in lexical statistics?
-### Is responding in each cultural context predicted by the corresponding lexical statistics (raw co-occurrences and cosine distance)? 
-```{r Pearson correlation between raw co-occurrences of corpora and responding, warning=FALSE, include=FALSE}
-
-#raw co-occurrences
-df.triad_country_freq <- df %>%
-  filter(!(triad %in% triads_omit)) %>% # omit triads that do not have meaningful prediction (at least 1 non-zero prediction in both languages)
-  group_by(triad, country, theme_freq_prop_E, theme_freq_prop_V, theme_freq_prop_M) %>%  # not working 
-  summarize(emp_theme_prop = mean(responses_theme))
-df.triad_country_freq   #sanity
-
-df.triad_country_freq_E <- df.triad_country_freq %>%
-  filter(country == "US")
-
-#plotting English corpus against US responding data
-plotE = ggplot(data = df.triad_country_freq_E,
-        mapping = aes(x = emp_theme_prop,
-                     y = theme_freq_prop_E,
-                     label = triad)) +
-   geom_text() +
-   geom_smooth(method = "lm") +
-   labs(x = "Proportion Thematic Chosen (US)",
-        y = "Proportion Thematic Predicted (English)")
-plotE
-
-df.triad_country_freq_V <- df.triad_country_freq %>%
-  filter(country == "Vietnam")
-
-#plotting Vietnamese corpus against VN responding data
-plotV = ggplot(data = df.triad_country_freq_V,
-        mapping = aes(x = emp_theme_prop,
-                     y = theme_freq_prop_V,
-                     label = triad)) +
-   geom_text() +
-   geom_smooth(method = "lm") +
-   labs(x = "Proportion Thematic Chosen (Vietnam)",
-        y = "Proportion Thematic Predicted (Vietnamese)")
-plotV
-
-df.triad_country_freq_M <- df.triad_country_freq %>%
-  filter(country == "China")
-
-#plotting China corpus against CN responding data
-plotM = ggplot(data = df.triad_country_freq_M,
-        mapping = aes(x = emp_theme_prop,
-                     y = theme_freq_prop_M,
-                     label = triad)) +
-   geom_text() +
-   geom_smooth(method = "lm") +
-   labs(x = "Proportion Thematic Chosen (China)",
-        y = "Proportion Thematic Predicted (Chinese)")
-plotM
-
-#Pearson correlation between corpus and responding
-corr.E = apa_print(cor.test(df.triad_country_freq_E$emp_theme_prop,
-                  df.triad_country_freq_E$theme_freq_prop_E, na.rm=T))
-corr.E
-
-corr.V = apa_print(cor.test(df.triad_country_freq_V$emp_theme_prop,
-                  df.triad_country_freq_V$theme_freq_prop_V, na.rm=T))
-corr.V
-
-corr.M = apa_print(cor.test(df.triad_country_freq_M$emp_theme_prop,
-                  df.triad_country_freq_M$theme_freq_prop_M, na.rm=T))
-corr.M
-
-#Pearson correlation between EN and VI corpus
-corr.EV = apa_print(cor.test(df.triad_country_freq_V$theme_freq_prop_V,
-                   df.triad_country_freq_E$theme_freq_prop_E, na.rm=T))
-corr.EM = apa_print(cor.test(df.triad_country_freq_M$theme_freq_prop_M,
-                   df.triad_country_freq_E$theme_freq_prop_E, na.rm=T))
-corr.MV = apa_print(cor.test(df.triad_country_freq_V$theme_freq_prop_V,
-                   df.triad_country_freq_M$theme_freq_prop_M, na.rm=T))
-```
-
-```{r echo=FALSE, paged.print=FALSE, fig.cap ="Correlation between English corpus lexical co-occurrence and US responding, and Vietnamese corpus lexical co-occurrence and Vietnam responding."}
-plotE + plotV + plotM
-  plot_layout(ncol = 3)
-```
-
-We first conducted a Pearson correlation test between corresponding response data and corpus data.
-Looking at the raw lexical co-occurrence data, proportion of US thematic responding is moderately correlated to English corpus thematic proportion, `r corr.E$full_result`.
-Proportion of Vietnam thematic responding is moderately correlated to Vietnamese corpus thematic proportion, `r corr.V$full_result`.
-Proportion of China thematic responding is moderately correlated to Chinese corpus thematic proportion, `r corr.M$full_result`.
-There was a strong similarity signal between the thematic proportions in the English and Vietnamese corpora, `r corr.EV$full_result`, and the thematic proportions in the English and Mandarin corpora, `r corr.EM$full_result`.
-There was a moderate similarity signal between the proportions in the Mandarin and Vietnamese corpora, `r corr.MV$full_result.`
-
-```{r Pearson correlation between corpus cosine distance and responding, warning=FALSE, include=FALSE}
-df.triad_country_cos <- df %>%
-  group_by(triad, country, theme_cosine_prop_E, theme_cosine_prop_V, theme_cosine_prop_M) %>%
-  summarize(emp_theme_prop = mean(responses_theme))
-
-df.triad_country_cos_E <- df.triad_country_cos %>%
-  filter(country == "US")
-
-plotE = ggplot(data = df.triad_country_cos_E, 
-        mapping = aes(x = emp_theme_prop, 
-                     y = theme_cosine_prop_E,
-                     label = triad)) +
-   geom_text() + 
-   geom_smooth(method = "lm") +
-   labs(x = "Proportion Thematic Chosen (US)", 
-        y = "Proportion Thematic Predicted (English)") + 
-   scale_y_reverse() + 
-   xlim(0, 1) +
-   ylim(0.8, 0.2) + 
-  theme(axis.title = element_text(size=rel(0.75)))
-
-df.triad_country_cos_V <- df.triad_country_cos %>%
-  filter(country == "Vietnam")
-
-plotV = ggplot(data = df.triad_country_cos_V, 
-        mapping = aes(x = emp_theme_prop, 
-                     y = theme_cosine_prop_V, 
-                     label = triad)) +
-   geom_text() + 
-   geom_smooth(method = "lm") +
-   labs(x = "Proportion Thematic Chosen (Vietnam)", 
-        y = "Proportion Thematic Predicted (Vietnamese)") + 
-   scale_y_reverse() +
-   xlim(0, 1) +
-   ylim(0.8, 0.2) + 
-  theme(axis.title = element_text(size=rel(0.75)))
-
-df.triad_country_cos_M <- df.triad_country_cos %>%
-  filter(country == "China")
-
-plotM = ggplot(data = df.triad_country_cos_M, 
-        mapping = aes(x = emp_theme_prop, 
-                     y = theme_cosine_prop_M, 
-                     label = triad)) +
-   geom_text() + 
-   geom_smooth(method = "lm") +
-   labs(x = "Proportion Thematic Chosen (China)", 
-        y = "Proportion Thematic Predicted (Mandarin)") + 
-   xlim(0, 1) +
-   ylim(0.8, 0.2) + 
-  theme(axis.title = element_text(size=rel(0.75)))
-
-corr.E_cos = apa_print(cor.test(df.triad_country_cos_E$emp_theme_prop,
-                      df.triad_country_cos_E$theme_cosine_prop_E, na.rm=T))
-
-corr.V_cos = apa_print(cor.test(df.triad_country_cos_V$emp_theme_prop,
-                      df.triad_country_cos_V$theme_cosine_prop_V, na.rm=T))
-
-corr.M_cos = apa_print(cor.test(df.triad_country_cos_M$emp_theme_prop,
-                      df.triad_country_cos_M$theme_cosine_prop_M, na.rm=T))
-
-#correlation between corpora
-corr.EV_cos = apa_print(cor.test(df.triad_country_cos_E$theme_cosine_prop_E,
-                       df.triad_country_cos_V$theme_cosine_prop_V, na.rm=T))
-
-corr.EM_cos = apa_print(cor.test(df.triad_country_cos_E$theme_cosine_prop_E,
-                      df.triad_country_cos_M$theme_cosine_prop_M, na.rm=T))
-
-corr.VM_cos = apa_print(cor.test(df.triad_country_cos_V$theme_cosine_prop_V,
-                      df.triad_country_cos_M$theme_cosine_prop_M, na.rm=T))
-```
-
-```{r warning = FALSE, echo=FALSE, fig.width = 8, fig.cap="Correlation between English corpus cosine distance and US responding; Vietnamese corpus cosine distance and Vietnam responding; and Mandarin corpus cosine distance and China responding."}
-#maybe we should include a note that explains why they are correlate in the opposite direction? 
-#either changing the label of y-axis, or use y = 1/theme_cosine_prop_V? 
-plotE + plotV + plotM +
-  plot_layout(ncol = 3)
-```
-
-```{r US-Mandarin, China-English cross correlation, NOT SHOWN, eval=FALSE, warning=FALSE, include=FALSE}
-plotUSZH = ggplot(data = df.triad_country_cos_E, 
-        mapping = aes(x = emp_theme_prop, 
-                     y = theme_cosine_prop_M,
-                     label = triad)) +
-   geom_text() + 
-   geom_smooth(method = "lm") +
-   labs(x = "Proportion Thematic Chosen (US)", 
-        y = "Proportion Thematic Predicted (Mandarin)") + 
-   scale_y_reverse() + 
-   xlim(0, 1) +
-   ylim(0.8, 0.3)
-
-plotCNEN = ggplot(data = df.triad_country_cos_M, 
-        mapping = aes(x = emp_theme_prop, 
-                     y = theme_cosine_prop_E,
-                     label = triad)) +
-   geom_text() + 
-   geom_smooth(method = "lm") +
-   labs(x = "Proportion Thematic Chosen (China)", 
-        y = "Proportion Thematic Predicted (English)") + 
-   scale_y_reverse() + 
-   xlim(0, 1) +
-   ylim(0.8, 0.3)
-
-plotUSZH + plotCNEN +
-  plot_layout(ncol = 2)
-```
-
-Looking at the cosine distance data using fastText word vectors, proportion of US thematic responding is moderately correlated to English thematic cosine distance proportion, `r corr.E_cos$full_result`.
-There is a small correlation between proportion of Vietnam thematic responding and the Vietnamese thematic cosine distance proportion, `r corr.V_cos$full_result`.
-Proportion of China thematic responding is moderately correlated to Mandarin thematic match cosine distance proportion, `r corr.M_cos$full_result`.
-There were moderate signals of similarity between English and Mandarin (`r corr.EM_cos$full_result`).
-There was no significant correlation between English and Vietnamese (`r corr.EV_cos$full_result`), and between Vietnamese and Mandarin (`r corr.VM_cos$full_result`).
-
-To test whether variation in lexical co-occurrence can explain differences in similarity judgments between US and Vietnam participants, we compare logistic mixed-effects regression models fit to the thematic responding data from each country separately.
-We first ask how well each corpus model (English, Vietnamese, or Mandarin) predicts similarity judgments by speakers of the corresponding language (US, Vietnam, or China).
-To do this, we use a mixed-effects logistic regression to predict triad responses (0=taxonomic or 1=thematic) with corpus prediction (proportion thematic co-occurrence or cosine distance) as a fixed effect and participant and triad as random effects.
-
-#### Raw lexical co-occurrences
-
-```{r US responding predicted by each corpus model raw co-occurrences, warning=FALSE, include=F}
-# English 
-fit.EN_US = glmer(responses_theme ~ theme_freq_prop_E + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "US", !(triad %in% triads_omit)), 
-          family="binomial")
-summary(fit.EN_US)
-fit.EN_US.anova = Anova(fit.EN_US, type = 3)
-
-#Vietnamese
-fit.VI_US = glmer(responses_theme ~ theme_freq_prop_V + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "US", !(triad %in% triads_omit)), 
-          family="binomial")
-summary(fit.VI_US)
-fit.VI_US.anova = Anova(fit.VI_US, type = 3)
-
-#Mandarin
-fit.ZH_US = glmer(responses_theme ~ theme_freq_prop_M + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "US", !(triad %in% triads_omit)), 
-          family="binomial")
-summary(fit.ZH_US)
-fit.ZH_US.anova = Anova(fit.ZH_US, type = 3)
-```
-
-```{r VN responding predicted by each corpus model raw co-occurrences, warning=FALSE, include=F}
-# English 
-fit.EN_VN = glmer(responses_theme ~ theme_freq_prop_E + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "Vietnam", !(triad %in% triads_omit)), 
-          family="binomial")
-summary(fit.EN_VN)
-fit.EN_VN.anova = Anova(fit.EN_VN, type = 3)
-
-#Vietnamese
-fit.VI_VN = glmer(responses_theme ~ theme_freq_prop_V + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "Vietnam", !(triad %in% triads_omit)), 
-          family="binomial")
-summary(fit.VI_VN)
-fit.VI_VN.anova = Anova(fit.VI_VN, type = 3)
-
-#Mandarin
-fit.ZH_VN = glmer(responses_theme ~ theme_freq_prop_M + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "Vietnam", !(triad %in% triads_omit)), 
-          family="binomial")
-summary(fit.ZH_VN)
-fit.ZH_VN.anova = Anova(fit.ZH_VN, type = 3)
-```
-
-```{r CN responding predicted by each corpus model raw co-occurrences, warning=FALSE, include=F}
-#English
-fit.EN_CN = glmer(responses_theme ~ theme_freq_prop_E + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "China", !(triad %in% triads_omit)), 
-          family="binomial")
-summary(fit.EN_CN)
-fit.EN_CN.anova = Anova(fit.EN_CN, type = 3)
-
-#Vietnamese
-fit.VI_CN = glmer(responses_theme ~ theme_freq_prop_V + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "China", !(triad %in% triads_omit)), 
-          family="binomial")
-summary(fit.VI_CN)
-fit.VI_CN.anova = Anova(fit.VI_CN, type = 3)
-
-#Mandarin
-fit.ZH_CN = glmer(responses_theme ~ theme_freq_prop_M + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "China", !(triad %in% triads_omit)), 
-          family="binomial")
-summary(fit.ZH_CN)
-fit.ZH_CN.anova = Anova(fit.ZH_CN, type = 3)
-```
-
-TODO: ADD CHINA RESULTS
-Both the English (EN) and Vietnamese (VI) corpus are significant predictors of US responding (EN-US model: $\beta$ = `r round(fixef(fit.EN_US)["theme_freq_prop_E"], 2)`, $\chi^2$(`r fit.EN_US.anova["theme_freq_prop_E", "Df"]`) = `r round(fit.EN_US.anova["theme_freq_prop_E", "Chisq"], 2)`, p < .001; VI-US model: $\beta$ = `r round(fixef(fit.VI_US)["theme_freq_prop_V"], 2)`, $\chi^2$(`r fit.VI_US.anova["theme_freq_prop_V", "Df"]`) = `r round(fit.VI_US.anova["theme_freq_prop_V", "Chisq"], 2)`, p < .001).
-
-Similarly, both the English (EN) and Vietnamese (VI) corpus are significant predictors of Vietnam (VN) responding (EN-VN model: $\beta$ = `r round(fixef(fit.EN_VN)["theme_freq_prop_E"], 2)`, $\chi^2$(`r fit.EN_VN.anova["theme_freq_prop_E", "Df"]`) = `r round(fit.EN_VN.anova["theme_freq_prop_E", "Chisq"], 2)`, p < .001; VI-VN model: $\beta$ = `r round(fixef(fit.VI_VN)["theme_freq_prop_V"], 2)`, $\chi^2$(`r fit.VI_VN.anova["theme_freq_prop_V", "Df"]`) = `r round(fit.VI_VN.anova["theme_freq_prop_V", "Chisq"], 2)`, p < .001).
-
-This suggests a strong shared similarity signal across the languages, which is also reflected in the strong correlation between the two corpus models reported above (`r corr.EV$full_result`).
-
-#### Cosine distances of fastText word vectors
-```{r US responding predicted by each corpus model cosine differences, warning=FALSE, include=F}
-#English
-fit.EN_US_cos = glmer(responses_theme ~ theme_cosine_prop_E + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "US"), 
-          family="binomial")
-summary(fit.EN_US_cos)
-fit.EN_US_cos.anova = Anova(fit.EN_US_cos, type = 3)
-fit.EN_US_cos.anova
-
-#Vietnamese
-fit.VI_US_cos = glmer(responses_theme ~ theme_cosine_prop_V + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "US"), 
-          family="binomial")
-summary(fit.VI_US_cos)
-fit.VI_US_cos.anova = Anova(fit.VI_US_cos, type = 3)
-fit.VI_US_cos.anova
-
-#Mandarin
-fit.ZH_US_cos = glmer(responses_theme ~ theme_cosine_prop_M + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "US"), 
-          family="binomial")
-summary(fit.ZH_US_cos)
-fit.ZH_US_cos.anova = Anova(fit.ZH_US_cos, type = 3)
-fit.ZH_US_cos.anova
-```
-
-```{r VN responding predicted by each corpus model cosine differences, warning=FALSE, include=F}
-#English
-fit.EN_VN_cos = glmer(responses_theme ~ theme_cosine_prop_E + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "Vietnam"), 
-          family="binomial")
-summary(fit.EN_VN_cos)
-fit.EN_VN_cos.anova = Anova(fit.EN_VN_cos, type = 3)
-fit.EN_VN_cos.anova
-
-#Vietnamese
-fit.VI_VN_cos = glmer(responses_theme ~ theme_cosine_prop_V + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "Vietnam"), 
-          family="binomial")
-summary(fit.VI_VN_cos)
-fit.VI_VN_cos.anova = Anova(fit.VI_VN_cos, type = 3)
-fit.VI_VN_cos.anova
-
-#Mandarin
-fit.ZH_VN_cos = glmer(responses_theme ~ theme_cosine_prop_M + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "Vietnam"), 
-          family="binomial")
-summary(fit.ZH_VN_cos)
-fit.ZH_VN_cos.anova = Anova(fit.ZH_VN_cos, type = 3)
-fit.ZH_VN_cos.anova
-```
-
-```{r CN responding predicted by each corpus model cosine differences, warning=FALSE, include=F}
-## English
-fit.EN_CN_cos = glmer(responses_theme ~ theme_cosine_prop_E + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "China"), 
-          family="binomial")
-summary(fit.EN_CN_cos)
-fit.EN_CN_cos.anova = Anova(fit.EN_CN_cos, type = 3)
-fit.EN_CN_cos.anova
-
-#Vietnamese
-fit.VI_CN_cos = glmer(responses_theme ~ theme_cosine_prop_V + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "China"), 
-          family="binomial")
-summary(fit.VI_CN_cos)
-fit.VI_CN_cos.anova = Anova(fit.VI_CN_cos, type = 3)
-fit.VI_CN_cos.anova
-
-#Mandarin
-fit.ZH_CN_cos = glmer(responses_theme ~ theme_cosine_prop_M + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "China"), 
-          family="binomial")
-summary(fit.ZH_CN_cos)
-fit.ZH_CN_cos.anova = Anova(fit.ZH_CN_cos, type = 3)
-fit.ZH_CN_cos.anova
-```
-
-Similar to the results from the analysis with raw lexical co-occurrences, we found that all corpora are significant predictors of all cultural context responding.
-
-For US responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are significant predictors of US responding (EN-US model: $\beta$ = `r round(fixef(fit.EN_US_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.EN_US_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.EN_US_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p < .001; VI-US model: $\beta$ = `r round(fixef(fit.VI_US_cos)["theme_cosine_prop_V"], 2)`, $\chi^2$(`r fit.VI_US_cos.anova["theme_cosine_prop_V", "Df"]`) = `r round(fit.VI_US_cos.anova["theme_cosine_prop_V", "Chisq"], 2)`, p = `r round(fit.VI_US_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"], 3)`; ZH-US model: $\beta$ = `r round(fixef(fit.ZH_US_cos)["theme_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ZH_US_cos.anova["theme_cosine_prop_M", "Df"]`) = `r round(fit.ZH_US_cos.anova["theme_cosine_prop_M", "Chisq"], 2)`, p < .001).
-
-For Vietnam (VN) responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are significant predictors of VN responding (EN-VN model: $\beta$ = `r round(fixef(fit.EN_VN_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.EN_VN_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.EN_VN_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p < .001; VI-VN model: $\beta$ = `r round(fixef(fit.VI_VN_cos)["theme_cosine_prop_V"], 2)`, $\chi^2$(`r fit.VI_VN_cos.anova["theme_cosine_prop_V", "Df"]`) = `r round(fit.VI_VN_cos.anova["theme_cosine_prop_V", "Chisq"], 2)`, p = `r round(fit.VI_VN_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"], 3)`; ZH-VN model: $\beta$ = `r round(fixef(fit.ZH_VN_cos)["theme_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ZH_VN_cos.anova["theme_cosine_prop_M", "Df"]`) = `r round(fit.ZH_VN_cos.anova["theme_cosine_prop_M", "Chisq"], 2)`, p < .001).
-
-For China (CN) responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are significant predictors of CN responding (EN-CN model: $\beta$ = `r round(fixef(fit.EN_CN_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.EN_CN_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.EN_CN_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p < .001; VI-CN model: $\beta$ = `r round(fixef(fit.VI_CN_cos)["theme_cosine_prop_V"], 2)`, $\chi^2$(`r fit.VI_CN_cos.anova["theme_cosine_prop_V", "Df"]`) = `r round(fit.VI_CN_cos.anova["theme_cosine_prop_V", "Chisq"], 2)`, p = `r round(fit.VI_VN_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"], 3)`; ZH-CN model: $\beta$ = `r round(fixef(fit.ZH_CN_cos)["theme_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ZH_CN_cos.anova["theme_cosine_prop_M", "Df"]`) = `r round(fit.ZH_CN_cos.anova["theme_cosine_prop_M", "Chisq"], 2)`, p < .001).
-
-### Is responding in each cultural context __best__ predicted by the corresponding corpus's lexical statistics (raw co-occurrences and cosine distance), as opposed to the other two corpora?
-Next, we directly compare the corpus models by including both as fixed effects in two mixed-effect regressions (predicting US and Vietnam responding) with the same random effects as above.
-In R syntax, the model is: response ~ corpus_English + corpus_Vietnamese + corpus_Mandarin + (1|triad) + (1|subject).
-
-#### Raw co-occurrences 
-```{r MIGHT NEED TO REMOVEEnglish + Vietnamese raw co-occurrences predicting US and Vietnam, warning=FALSE, include=F}
-## English/Vietnamese comparison
-fit.ENVI_US = glmer(responses_theme ~ theme_freq_prop_E + theme_freq_prop_V + 
-                      (1 | subject) + (1 | triad), 
-                    data = df %>% filter(country == "US"), 
-                    family="binomial")
-summary(fit.ENVI_US)
-fit.ENVI_US.anova = Anova(fit.ENVI_US, type = 3)
-fit.ENVI_US.anova
-
-fit.ENVI_VN = glmer(responses_theme ~ theme_freq_prop_V + theme_freq_prop_E + 
-                      (1 | subject) + (1 | triad), 
-                    data = df %>% filter(country == "Vietnam"), 
-                    family="binomial")
-summary(fit.ENVI_VN)
-fit.ENVI_VN.anova = Anova(fit.ENVI_VN, type = 3)
-fit.ENVI_VN.anova
-```
-When we included both corpora as predictors for US responding, only the English corpus has a significant effect ($\beta$ = `r round(fixef(fit.ENVI_US)["theme_freq_prop_E"], 2)`, $\chi^2$(`r fit.ENVI_US.anova["theme_freq_prop_E", "Df"]`) = `r round(fit.ENVI_US.anova["theme_freq_prop_E", "Chisq"], 2)`, p < .001).
-There is no effect of the Vietnamese corpus ($\beta$ = `r round(fixef(fit.ENVI_US)["theme_freq_prop_V"], 2)`, $\chi^2$(`r fit.ENVI_US.anova["theme_freq_prop_V", "Df"]`) = `r round(fit.ENVI_US.anova["theme_freq_prop_V", "Chisq"], 2)`, p = `r round(fit.ENVI_US.anova["theme_freq_prop_V", "Pr(>Chisq)"], 3)`).
-
-However, when both corpora are included as predictors for Vietnam responding -- both corpora has a significant effect (English corpus: $\beta$ = `r round(fixef(fit.ENVI_VN)["theme_freq_prop_E"], 2)`, $\chi^2$(`r fit.ENVI_VN.anova["theme_freq_prop_E", "Df"]`) = `r round(fit.ENVI_VN.anova["theme_freq_prop_E", "Chisq"], 2)`, p = `r round(fit.ENVI_VN.anova["theme_freq_prop_E", "Pr(>Chisq)"], 3)`; Vietnamese corpus: $\beta$ = `r round(fixef(fit.ENVI_VN)["theme_freq_prop_V"], 2)`, $\chi^2$(`r fit.ENVI_VN.anova["theme_freq_prop_V", "Df"]`) = `r round(fit.ENVI_VN.anova["theme_freq_prop_V", "Chisq"], 2)`, p = `r round(fit.ENVI_VN.anova["theme_freq_prop_V", "Pr(>Chisq)"], 3)`).
-
-```{r Eng-Vie-Mand lexical co-occ predicting US, VN, CN, warning=FALSE, include=F}
-# ADDITION: adding theme_freq_prop_M
-#raw co-occurrences
-#linear mixed model with ALL corpora as predictors for each population.
-fit.ENVIZH_US = glmer(responses_theme ~ 
-                      theme_freq_prop_E + theme_freq_prop_V + theme_freq_prop_M +
-                      (1 | subject) + (1 | triad), 
-                    data = df %>% filter(country == "US", !(triad %in% triads_omit)),
-                    family="binomial")
-summary(fit.ENVIZH_US)
-fit.ENVIZH_US.anova = Anova(fit.ENVIZH_US, type = 3)
-fit.ENVIZH_US.anova
-
-fit.ENVIZH_VN = glmer(responses_theme ~ 
-                      theme_freq_prop_V + theme_freq_prop_E + theme_freq_prop_M +
-                      (1 | subject) + (1 | triad), 
-                    data = df %>% filter(country == "Vietnam", !(triad %in% triads_omit)),
-                    family="binomial")
-summary(fit.ENVIZH_VN)
-fit.ENVIZH_VN.anova = Anova(fit.ENVIZH_VN, type = 3)
-fit.ENVIZH_VN.anova
-
-fit.ENVIZH_CN = glmer(responses_theme ~ 
-                      theme_freq_prop_V + theme_freq_prop_E + theme_freq_prop_M +
-                      (1 | subject) + (1 | triad), 
-                    data = df %>% filter(country == "China", !(triad %in% triads_omit)),
-                    family="binomial")
-summary(fit.ENVIZH_CN)
-fit.ENVIZH_CN.anova = Anova(fit.ENVIZH_CN, type = 3)
-fit.ENVIZH_CN.anova
-```
-TODO: ADD WRITE-UP OF RESULTS
-
-```{r echo=FALSE, warning = FALSE, fig.cap = "Fixed effect sizes of each corpus when included as a predictor for China, US, and Vietnam responding, respectively.
-The English corpus is the best predictor for US response, and the Mandarin corpus is the best predictor for China response."}
-coeff_value_freq <- c(fixef(fit.ENVIZH_US)["theme_freq_prop_E"],
-                 fixef(fit.ENVIZH_US)["theme_freq_prop_V"], 
-                 fixef(fit.ENVIZH_US)["theme_freq_prop_M"],
-                 fixef(fit.ENVIZH_VN)["theme_freq_prop_E"],
-                 fixef(fit.ENVIZH_VN)["theme_freq_prop_V"],
-                 fixef(fit.ENVIZH_VN)["theme_freq_prop_M"], 
-                 fixef(fit.ENVIZH_CN)["theme_freq_prop_E"],
-                 fixef(fit.ENVIZH_CN)["theme_freq_prop_V"], 
-                 fixef(fit.ENVIZH_CN)["theme_freq_prop_M"])
-
-se_value_freq <- c(summary(fit.ENVIZH_US)$coef["theme_freq_prop_E", "Std. Error"], 
-              summary(fit.ENVIZH_US)$coef["theme_freq_prop_V", "Std. Error"],
-              summary(fit.ENVIZH_US)$coef["theme_freq_prop_M", "Std. Error"], 
-              summary(fit.ENVIZH_VN)$coef["theme_freq_prop_E", "Std. Error"], 
-              summary(fit.ENVIZH_VN)$coef["theme_freq_prop_V", "Std. Error"],
-              summary(fit.ENVIZH_VN)$coef["theme_freq_prop_M", "Std. Error"],
-              summary(fit.ENVIZH_CN)$coef["theme_freq_prop_E", "Std. Error"], 
-              summary(fit.ENVIZH_CN)$coef["theme_freq_prop_V", "Std. Error"],
-              summary(fit.ENVIZH_CN)$coef["theme_freq_prop_M", "Std. Error"])
-
-country_value <- c(rep("US", 3),
-                   rep("VN", 3),
-                   rep("CN", 3))
-
-corpus_value <- c(rep(c("EN", "VI", "ZH"), 3))
-
-df.USVNCN_coeffs_freq <- data.frame(country_value, corpus_value, coeff_value_freq, se_value_freq)
-
-ggplot(data = df.USVNCN_coeffs_freq, 
-       mapping = aes(x = country_value, y = coeff_value_freq, fill = corpus_value)) +
-  geom_bar(position="dodge", stat="identity") +
-  geom_errorbar(aes(ymin= coeff_value_freq - se_value_freq, ymax = coeff_value_freq + se_value_freq), width=.2,
-                 position=position_dodge(.9)) +
-  scale_y_reverse() + 
-  labs(x = "Country", y = "Fixed effect size", fill = "Corpus") + 
-  scale_x_discrete(labels=c("CN" = "China", "US" = "US", "VN" = "Vietnam")) + 
-  scale_fill_manual(values=c("#D63230", "#1C77C3", "#F39237"))
-
-```
-
-```{r model comparison, include=FALSE}
-fit.US_freq_compare = anova(fit.ENVIZH_US, fit.EN_US, type = 3)
-fit.VN_freq_compare = anova(fit.ENVIZH_VN, fit.VI_VN, type = 3)
-fit.CN_freq_compare = anova(fit.ENVIZH_CN, fit.ZH_CN, type = 3)
-```
-
-TODO: ADD WRITE-UP ON RESULTS
-
-#### Cosine distances of fastText word vectors
-
-```{r Eng-Vie-Mand cosine similarities predicting US, VN, CN warning=FALSE, include=FALSE}
-## English/Vietnamese/Mandarin comparison
-fit.ENVIZH_US_cos = glmer(responses_theme ~ theme_cosine_prop_E + theme_cosine_prop_V + theme_cosine_prop_M +
-                      (1 | subject) + (1 | triad), 
-                    data = df %>% filter(country == "US"), 
-                    family="binomial")
-summary(fit.ENVIZH_US_cos)
-fit.ENVIZH_US_cos.anova = Anova(fit.ENVIZH_US_cos, type = 3)
-fit.ENVIZH_US_cos.anova
-
-fit.ENVIZH_VN_cos = glmer(responses_theme ~ theme_cosine_prop_V + theme_cosine_prop_E + theme_cosine_prop_M +
-                      (1 | subject) + (1 | triad), 
-                    data = df %>% filter(country == "Vietnam"), 
-                    family="binomial")
-summary(fit.ENVIZH_VN_cos)
-fit.ENVIZH_VN_cos.anova = Anova(fit.ENVIZH_VN_cos, type = 3)
-fit.ENVIZH_VN_cos.anova
-
-fit.ENVIZH_CN_cos = glmer(responses_theme ~ theme_cosine_prop_M + theme_cosine_prop_E + theme_cosine_prop_V +
-                      (1 | subject) + (1 | triad), 
-                    data = df %>% filter(country == "China"), 
-                    family="binomial")
-summary(fit.ENVIZH_CN_cos)
-fit.ENVIZH_CN_cos.anova = Anova(fit.ENVIZH_CN_cos, type = 3)
-fit.ENVIZH_CN_cos.anova
-```
-
-When we included all corpora thematic cosine distance proportion as predictors, all corpora are significant in predicting all cultural context's responding.
-
-For US responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are all significant predictors.
-EN corpus: $\beta$ = `r round(fixef(fit.ENVIZH_US_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.ENVIZH_US_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.ENVIZH_US_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p < .001.
-VI corpus: $\beta$ = `r round(fixef(fit.ENVIZH_US_cos)["theme_cosine_prop_V"], 2)`, $\chi^2$(`r fit.ENVIZH_US_cos.anova["theme_cosine_prop_V", "Df"]`) = `r round(fit.ENVIZH_US_cos.anova["theme_cosine_prop_V", "Chisq"], 2)`, p = `r round(fit.ENVIZH_US_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"], 3)`.
-ZH corpus: $\beta$ = `r round(fixef(fit.ENVIZH_US_cos)["theme_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ENVIZH_US_cos.anova["theme_cosine_prop_M", "Df"]`) = `r round(fit.ENVIZH_US_cos.anova["theme_cosine_prop_M", "Chisq"], 2)`, p = `r round(fit.ENVIZH_US_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"], 3)`.
-
-For Vietnam responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are all significant predictors.
-EN corpus: $\beta$ = `r round(fixef(fit.ENVIZH_VN_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.ENVIZH_VN_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p = `r round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"], 3)`.
-VI corpus: $\beta$ = `r round(fixef(fit.ENVIZH_VN_cos)["theme_cosine_prop_V"], 2)`, $\chi^2$(`r fit.ENVIZH_VN_cos.anova["theme_cosine_prop_V", "Df"]`) = `r round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_V", "Chisq"], 2)`, p = `r round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"], 3)`.
-ZH corpus: $\beta$ = `r round(fixef(fit.ENVIZH_VN_cos)["theme_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ENVIZH_VN_cos.anova["theme_cosine_prop_M", "Df"]`) = `r round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_M", "Chisq"], 2)`, p = `r round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"], 3)`.
-
-For China responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are all significant predictors.
-EN corpus: $\beta$ = `r round(fixef(fit.ENVIZH_CN_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.ENVIZH_CN_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.ENVIZH_CN_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p = `r round(fit.ENVIZH_CN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"], 3)`.
-VI corpus: $\beta$ = `r round(fixef(fit.ENVIZH_CN_cos)["theme_cosine_prop_V"], 2)`, $\chi^2$(`r fit.ENVIZH_CN_cos.anova["theme_cosine_prop_V", "Df"]`) = `r round(fit.ENVIZH_CN_cos.anova["theme_cosine_prop_V", "Chisq"], 2)`, p = `r round(fit.ENVIZH_CN_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"], 3)`.
-ZH corpus: $\beta$ = `r round(fixef(fit.ENVIZH_CN_cos)["theme_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ENVIZH_CN_cos.anova["theme_cosine_prop_M", "Df"]`) = `r round(fit.ENVIZH_CN_cos.anova["theme_cosine_prop_M", "Chisq"], 2)`, p = < .001.
-
-We observed some level of language specificity from this analysis.
-The English corpus is the best predictor for US responding, and the Mandarin corpus is the best predictor for China response.
-While this is not the case with the Vietnamese corpus and the Vietnam responding, the Vietnamese corpus is still a significant predictor for the Vietnam responding.
-
-```{r echo=FALSE, warning = FALSE, fig.cap = "Fixed effect sizes of each corpus when included as a predictor for China, US, and Vietnam responding, respectively.
-The English corpus is the best predictor for US response, and the Mandarin corpus is the best predictor for China response."}
-coeff_value_cos <- c(fixef(fit.ENVIZH_US_cos)["theme_cosine_prop_E"],
-                 fixef(fit.ENVIZH_US_cos)["theme_cosine_prop_V"], 
-                 fixef(fit.ENVIZH_US_cos)["theme_cosine_prop_M"],
-                 fixef(fit.ENVIZH_VN_cos)["theme_cosine_prop_E"],
-                 fixef(fit.ENVIZH_VN_cos)["theme_cosine_prop_V"],
-                 fixef(fit.ENVIZH_VN_cos)["theme_cosine_prop_M"], 
-                 fixef(fit.ENVIZH_CN_cos)["theme_cosine_prop_E"],
-                 fixef(fit.ENVIZH_CN_cos)["theme_cosine_prop_V"], 
-                 fixef(fit.ENVIZH_CN_cos)["theme_cosine_prop_M"])
-
-se_value_cos <- c(summary(fit.ENVIZH_US_cos)$coef["theme_cosine_prop_E", "Std. Error"], 
-              summary(fit.ENVIZH_US_cos)$coef["theme_cosine_prop_V", "Std. Error"],
-              summary(fit.ENVIZH_US_cos)$coef["theme_cosine_prop_M", "Std. Error"], 
-              summary(fit.ENVIZH_VN_cos)$coef["theme_cosine_prop_E", "Std. Error"], 
-              summary(fit.ENVIZH_VN_cos)$coef["theme_cosine_prop_V", "Std. Error"],
-              summary(fit.ENVIZH_VN_cos)$coef["theme_cosine_prop_M", "Std. Error"],
-              summary(fit.ENVIZH_CN_cos)$coef["theme_cosine_prop_E", "Std. Error"], 
-              summary(fit.ENVIZH_CN_cos)$coef["theme_cosine_prop_V", "Std. Error"],
-              summary(fit.ENVIZH_CN_cos)$coef["theme_cosine_prop_M", "Std. Error"])
-
-country_value <- c(rep("US", 3),
-                   rep("VN", 3),
-                   rep("CN", 3))
-
-corpus_value <- c(rep(c("EN", "VI", "ZH"), 3))
-
-df.USVNCN_coeffs_cos <- data.frame(country_value, corpus_value, coeff_value_cos, se_value_cos)
-
-ggplot(data = df.USVNCN_coeffs_cos, 
-       mapping = aes(x = country_value, y = coeff_value_cos, fill = corpus_value)) +
-  geom_bar(position="dodge", stat="identity") +
-  geom_errorbar(aes(ymin= coeff_value_cos - se_value_cos, ymax = coeff_value_cos + se_value_cos), width=.2,
-                 position=position_dodge(.9)) +
-  scale_y_reverse() + 
-  labs(x = "Country", y = "Fixed effect size", fill = "Corpus") + 
-  scale_x_discrete(labels=c("CN" = "China", "US" = "US", "VN" = "Vietnam")) + 
-  scale_fill_manual(values=c("#D63230", "#1C77C3", "#F39237"))
-
-```
-
-```{r model comparison, include=FALSE}
-fit.US_cos_compare = anova(fit.ENVIZH_US_cos, fit.EN_US_cos, type = 3)
-fit.VN_cos_compare = anova(fit.ENVIZH_VN_cos, fit.VI_VN_cos, type = 3)
-fit.CN_cos_compare = anova(fit.ENVIZH_CN_cos, fit.ZH_CN_cos, type = 3)
-```
-
-However, we found that language specificity alone does not explain our results.
-We used an ANOVA to compare the model with only the corresponding corpus, and the model with all 3 corpora for each cultural context.
-We found that in all three cases (US, China, Vietnam), adding the other two corpora produces a significantly better fit than the identical model without the additional corpora, and only the corresponding corpus included as a predictor (US response: $\chi^2$(`r fit.US_compare["fit.ENVIZH_US_cos", "Df"]`) = `r round(fit.US_compare["fit.ENVIZH_US_cos", "Chisq"], 2)`, p = `r round(fit.US_compare["fit.ENVIZH_US_cos", "Pr(>Chisq)"], 3)`; Vietnam response: $\chi^2$(`r fit.VN_compare["fit.ENVIZH_VN_cos", "Df"]`) = `r round(fit.VN_compare["fit.ENVIZH_VN_cos", "Chisq"], 2)`, p = < .001; China response: $\chi^2$(`r fit.CN_compare["fit.ENVIZH_CN_cos", "Df"]`) = `r round(fit.CN_compare["fit.ENVIZH_CN_cos", "Chisq"], 2)`, p = `r round(fit.CN_compare["fit.ENVIZH_CN_cos", "Pr(>Chisq)"], 3)`).
-
-```{r add linguistic model to Ji et al., include=FALSE}
-fit.country = glmer(responses_theme ~ country + (1 | subject) + (1 | triad), 
-                           data = df %>% filter(country != "Vietnam"), 
-                           family = "binomial")
-
-fit.country_corpus = glmer(responses_theme ~ country + theme_cosine_prop_E + theme_cosine_prop_M + (1 | subject) + (1 | triad), 
-                           data = df %>% filter(country != "Vietnam"), 
-                           family = "binomial")
-
-fit.add_corpus <- anova(fit.country, fit.country_corpus, type = 3)
-
-```
-
-We carried out an ANOVA model comparison to compare our approach with previous studies that did not include corpus information.
-Because @Ji2004 only compared US and China participants, we filtered our data to only include responding data from these two countries.
-Our approach would be to compare a model that only includes country (US or China) as a fixed effect with one that also includes English and Chinese corpus data.
-Our previous model with an intercept per subject and one per triad, as well as by-triad random slopes for country to account for variation in the country effect across triads fails to converge with the more complex model, so we include a simpler random effect structure with an intercept per subject and one per triad in both the basic and more complex model.
-We compare this model with an identical model but including Chinese and English corpus cosine distance proportion prediction.
-We found that adding English and Chinese corpus data produces a significantly better fit than the identical model without English and Chinese corpus data as predictors ($\chi^2$(`r fit.add_corpus["fit.country_corpus", "Df"]`) = `r round(fit.add_corpus["fit.country_corpus", "Chisq"], 2)`, p = < .001.
-This suggests that including corpus data would better model the cross-cultural differences in similarity judgment in this study as well as similar studies.
-
-## Exploratory analysis
-
-Because our exclusion criterion for attention checks excluded over 50% Vietnam participants, we carried out exploratory analysis where we applied less stringent exclusion criteria.
-In the following analysis, we only exclude participants who miss more than 2 attention checks (rather than any attention checks).
-We kept the rest of the exclusion criteria.
-
-TODO: CREATE .CSV FILES FOR THESE, SEPARATE OUT R SCRIPT INTO RMD.
-```{r loading data E explore, warning=FALSE, include=F}
-df.resp_E <- read.csv("../../data/data_E_0319.csv") %>%
-  select(-X)
-
-# check for participants who completed the entire experiment. Because the experiment is
-# quite long, some participants decide to come back afterwards, so there are a few files
-# that are recorded as incomplete. 
-df.ppts_finished_E <- df.resp_E %>% 
-  group_by(subject) %>%
-  summarize(finished = ifelse("demo-final" %in% unique(variable_type), "yes", "no")) %>%
-  filter(finished == "yes")
-
-df.resp_E <- df.resp_E %>%
-  filter(subject %in% df.ppts_finished_E$subject)
-
-df.ppts_att_E <- df.resp_E %>%
-  filter(stim_type == "attention check") %>%
-  mutate(correct_response = strsplit(cue, "Choose ")) %>%
-  mutate(correct_response = sapply(correct_response, "[[", 2)) %>%
-  mutate(pass_att_check = ifelse(responses == correct_response, 1, 0)) %>%
-  group_by(subject) %>%
-  summarize(pass_att_check_percent = mean(pass_att_check)) %>%
-  filter(pass_att_check_percent >= 0.8)
-
-df.resp_E <- df.resp_E %>%
-  filter(subject %in% df.ppts_att_E$subject) 
-```
-
-```{r exclusion E explore, include = F, warning = F}
-#non-native speaker
-split_responses_demog <- function(responses) {
-  responses <- as.character(responses)
-  response_list <- unlist(strsplit(responses, ',|:'))
-  response_list <- response_list[seq(1, length(response_list))]
-  response_list <- gsub("}", "", response_list)
-  response_list <- gsub("\"", "", response_list)
-  return(response_list)
-}
-
-NATIVE_LANG = 2
-get_native_lang <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  if(responses[NATIVE_LANG-1] != "{firstlanguage") 
-    {warnings("cannot find native language answer")}
-  else
-    {return (responses[NATIVE_LANG])}
-})
-
-df.ppts_non_native_lang_E <- df.resp_E %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_language") %>%
-  mutate(native_speaker = get_native_lang(responses)) %>%
-  filter(native_speaker == "No")
-
-ppts_non_native_lang_E = unique(df.ppts_non_native_lang_E$subject)#18
-percent_dropped = length(ppts_non_native_lang_E) / length(unique(df.resp_E$subject))
-percent_dropped #0.1041667
-
-#fluent in Vietnamese & Mandarin
-SPEAKER = 2
-SPEAKING = 23
-UNDERSTANDING = 46
-
-get_speaker <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[SPEAKER])
-})
-
-get_fluency_speaking <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[SPEAKING])
-})
-
-get_fluency_understanding <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[UNDERSTANDING])
-})
-
-df.lang_vi_E <- df.resp_E %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_language_vi") %>%
-  mutate(vi_speaker = get_speaker(responses))
-
-df.lang_vi_fluency_E <- df.resp_E %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_conditional_language_vn_fluency") %>%
-  mutate(vi_fluency_sp = as.numeric(get_fluency_speaking(responses))) %>%
-  mutate(vi_fluency_ud = as.numeric(get_fluency_understanding(responses)))
-
-df.lang_vi_E <- full_join(df.lang_vi_E, 
-                          df.lang_vi_fluency_E, 
-                          by = "subject") %>%
-  select(subject, vi_speaker, vi_fluency_sp, vi_fluency_ud) %>%
-  filter(vi_speaker == "Yes",
-         vi_fluency_sp > 4, 
-         vi_fluency_ud > 4)
-
-ppts_vi_speaker_E = unique(df.lang_vi_E$subject) #4
-percent_dropped = length(ppts_vi_speaker_E) / length(unique(df.resp_E$subject))
-percent_dropped #0.02083333
-
-df.lang_zh_E <- df.resp_E %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_language_cn") %>%
-  mutate(zh_speaker = get_speaker(responses))
-
-df.lang_zh_fluency_E <- df.resp_E %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_conditional_language_cn_fluency") %>%
-  mutate(zh_fluency_sp = as.numeric(get_fluency_speaking(responses))) %>%
-  mutate(zh_fluency_ud = as.numeric(get_fluency_understanding(responses)))
-
-df.lang_zh_E <- full_join(df.lang_zh_E, 
-                          df.lang_zh_fluency_E, 
-                          by = "subject") %>%
-  select(subject, zh_speaker, zh_fluency_sp, zh_fluency_ud) %>%
-  filter(zh_speaker == "Yes",
-         zh_fluency_sp > 4, 
-         zh_fluency_ud > 4)
-
-ppts_zh_speaker_E = unique(df.lang_zh_E$subject) #30
-percent_dropped = length(ppts_zh_speaker_E) / length(unique(df.resp_E$subject))
-percent_dropped #0.1822917
-
-#have lived outside the sample country for more than 2 years
-#have travelled extensively (more than 6 international experiences of 2 days or longer) 
-YEARSABROAD = 2
-OVERSEAEXP = 4
-
-get_lived_abroad <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[YEARSABROAD])
-})
-
-get_oversea_exp <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[OVERSEAEXP])
-})
-
-df.abroad_E <- df.resp_E %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_oversea_experience") %>%
-  mutate(lived_abroad = get_lived_abroad(responses)) %>%
-  mutate(oversea_exp = get_oversea_exp(responses))
-
-df.lived_abroad_E <- df.abroad_E %>%
-  filter(lived_abroad == "Yes")
-
-ppts_lived_abroad_E = unique(df.lived_abroad_E$subject) #29
-percent_dropped = length(ppts_lived_abroad_E) / length(unique(df.resp_E$subject))
-percent_dropped #0.171875
-
-df.oversea_exp_E <- df.abroad_E %>%
-  filter(oversea_exp == "Six or more experiences")
-
-ppts_oversea_exp_E = unique(df.oversea_exp_E$subject) #77
-percent_dropped = length(ppts_oversea_exp_E) / length(unique(df.resp_E$subject))
-percent_dropped #0.44 # will not use this criterion
-
-df.resp_E <- df.resp_E %>%
-  filter(!(subject %in% ppts_non_native_lang_E),
-         !(subject %in% ppts_vi_speaker_E), 
-         !(subject %in% ppts_zh_speaker_E),
-         !(subject %in% ppts_lived_abroad_E))
-
-length(unique(df.resp_E$subject)) #132
-```
-
-```{r demog_E explore, include = F}
-demog <- c("demog-dropdown", "demog-multi-choice", "demog-free-response", "demog-multi-select")
-df.demog_E <- df.resp_E %>%
-  filter(trial_type %in% demog)
-
-AGE = 97 #index for age answer
-GENDER = 115 #index for gender answer
-split_responses <- function(responses) {
-  responses <- as.character(responses)
-  response_list <- unlist(strsplit(responses, ',|:'))
-  response_list <- response_list[seq(1, length(response_list))]
-  response_list <- gsub("}", "", response_list)
-  response_list <- gsub("\"", "", response_list)
-  return(response_list)
-}
-
-get_age <- Vectorize(function(responses) {
-  responses <- split_responses(responses)
-  if(responses[AGE-1] != "A0") {warnings("cannot find age answer")}
-  else{return (responses[AGE])}
-})
-
-get_gender <- Vectorize(function(responses) {
-  responses <- split_responses(responses)
-  if(responses[GENDER-1] != "A1") {warnings("cannot find gender answer")}
-  else{return (responses[GENDER])}
-})
-
-df.age_gender_E <- df.demog_E %>%
-  filter(variable_type == "demog_age_gender_ethnic") %>%
-  select(subject, responses) %>%
-  mutate(age = as.numeric(get_age(responses))) %>%
-  mutate(age = as.numeric(age)) %>%
-  mutate(gender = get_gender(responses))
-
-df.age_gender_E_summ <- df.age_gender_E %>%
-  summarize(mean_age = mean(age), 
-            median_age = median(age), 
-            sd_age = sd(age))
-```
-
-```{r loading data V explore, include=F}
-df.resp_V <- read.csv("../../data/data_V_0530.csv") %>%
-  select(-X)
-
-# check for participants who completed the entire experiment. Because the experiment is
-# quite long, some participants decide to come back afterwards, so there are a few files
-# that are recorded as incomplete. 
-df.ppts_finished_V <- df.resp_V %>% 
-  group_by(subject) %>%
-  summarize(finished = ifelse("demo-final" %in% unique(variable_type), "yes", "no")) %>%
-  filter(finished == "yes")
-
-df.resp_V <- df.resp_V %>%
-  filter(subject %in% df.ppts_finished_V$subject)
-
-df.ppts_att_V <- df.resp_V %>%
-  filter(stim_type == "attention check") %>%
-  mutate(correct_response = strsplit(cue, "Chọn ")) %>%
-  mutate(correct_response = sapply(correct_response, "[[", 2)) %>%
-  mutate(pass_att_check = ifelse(responses == correct_response, 1, 0)) %>%
-  group_by(subject) %>%
-  summarize(pass_att_check_percent = mean(pass_att_check)) %>%
-  filter(pass_att_check_percent >= 0.8)
-
-df.resp_V <- df.resp_V %>%
-  filter(subject %in% df.ppts_att_V$subject) #73
-```
-
-```{r exclusion V explore, include = F}
-#non-native speaker
-split_responses_demog <- function(responses) {
-  responses <- as.character(responses)
-  response_list <- unlist(strsplit(responses, ',|:'))
-  response_list <- response_list[seq(1, length(response_list))]
-  response_list <- gsub("}", "", response_list)
-  response_list <- gsub("\"", "", response_list)
-  return(response_list)
-}
-
-NATIVE_LANG = 2
-get_native_lang <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  if(responses[NATIVE_LANG-1] != "{firstlanguage") 
-    {warnings("cannot find native language answer")}
-  else
-    {return (responses[NATIVE_LANG])}
-})
-
-df.ppts_non_native_lang_V <- df.resp_V %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_language") %>%
-  mutate(native_speaker = get_native_lang(responses)) %>%
-  filter(native_speaker == "Không")
-
-ppts_non_native_lang_V = unique(df.ppts_non_native_lang_V$subject)
-percent_dropped = length(ppts_non_native_lang_V) / length(unique(df.resp_V$subject))
-percent_dropped #0
-
-#fluent in English
-SPEAKER = 2
-SPEAKING = 23
-UNDERSTANDING = 46
-
-get_speaker <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[SPEAKER])
-})
-
-get_fluency_speaking <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[SPEAKING])
-})
-
-get_fluency_understanding <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[UNDERSTANDING])
-})
-
-df.lang_en_V <- df.resp_V %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_language_en") %>%
-  mutate(en_speaker = get_speaker(responses))
-
-df.lang_en_fluency_V <- df.resp_V %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_conditional_language_en_fluency") %>%
-  mutate(en_fluency_sp = as.numeric(get_fluency_speaking(responses))) %>%
-  mutate(en_fluency_ud = as.numeric(get_fluency_understanding(responses)))
-
-df.lang_en_V <- full_join(df.lang_en_V, 
-                          df.lang_en_fluency_V, 
-                          by = "subject") %>%
-  select(subject, en_speaker, en_fluency_sp, en_fluency_ud) %>%
-  filter(en_speaker == "Có",
-         en_fluency_sp > 4, 
-         en_fluency_ud > 4)
-
-ppts_en_speaker_V = unique(df.lang_en_V$subject) #4
-percent_dropped = length(ppts_en_speaker_V) / length(unique(df.resp_V$subject))
-percent_dropped #0.6861314 # do not use this criterion
-
-df.lang_zh_V <- df.resp_V %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_language_cn") %>%
-  mutate(zh_speaker = get_speaker(responses))
-
-df.lang_zh_fluency_V <- df.resp_V %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_conditional_language_cn_fluency") %>%
-  mutate(zh_fluency_sp = as.numeric(get_fluency_speaking(responses))) %>%
-  mutate(zh_fluency_ud = as.numeric(get_fluency_understanding(responses)))
-
-df.lang_zh_V <- full_join(df.lang_zh_V, 
-                          df.lang_zh_fluency_V, 
-                          by = "subject") %>%
-  select(subject, zh_speaker, zh_fluency_sp, zh_fluency_ud) %>%
-  filter(zh_speaker == "Có",
-         zh_fluency_sp > 4, 
-         zh_fluency_ud > 4)
-
-ppts_zh_speaker_V = unique(df.lang_zh_V$subject) #4
-percent_dropped = length(ppts_zh_speaker_V) / length(unique(df.resp_V$subject))
-percent_dropped #0.05839416
-
-#have lived outside the sample country for more than 2 years
-#have travelled extensively (more than 6 international experiences of 2 days or longer) 
-YEARSABROAD = 2
-OVERSEAEXP = 4
-
-get_lived_abroad <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[YEARSABROAD])
-})
-
-get_oversea_exp <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[OVERSEAEXP])
-})
-
-df.abroad_V <- df.resp_V %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_oversea_experience") %>%
-  mutate(lived_abroad = get_lived_abroad(responses)) %>%
-  mutate(oversea_exp = get_oversea_exp(responses))
-
-df.lived_abroad_V <- df.abroad_V %>%
-  filter(lived_abroad == "Có")
-
-ppts_lived_abroad_V = unique(df.lived_abroad_V$subject)
-percent_dropped = length(ppts_lived_abroad_V) / length(unique(df.resp_V$subject))
-percent_dropped #0.1094891
-
-df.oversea_exp_V <- df.abroad_V %>%
-  filter(oversea_exp == "6 lần trở lên")
-
-ppts_oversea_exp_V = unique(df.oversea_exp_V$subject) #77
-percent_dropped = length(ppts_oversea_exp_V) / length(unique(df.resp_V$subject))
-percent_dropped #0.1094891
-
-df.resp_V <- df.resp_V %>%
-  filter(!(subject %in% ppts_non_native_lang_V),
-         !(subject %in% ppts_oversea_exp_V), 
-         !(subject %in% ppts_zh_speaker_V),
-         !(subject %in% ppts_lived_abroad_V))
-
-length(unique(df.resp_V$subject))  #110
-```
-
-```{r demog_V explore, include = F}
-demog <- c("demog-dropdown", "demog-multi-choice", "demog-free-response", "demog-multi-select")
-df.demog_V <- df.resp_V %>%
-  filter(trial_type %in% demog)
-
-AGE = 97 #index for age answer
-GENDER = 115 #index for gender answer
-split_responses <- function(responses) {
-  responses <- as.character(responses)
-  response_list <- unlist(strsplit(responses, ',|:'))
-  response_list <- response_list[seq(1, length(response_list))]
-  response_list <- gsub("}", "", response_list)
-  response_list <- gsub("\"", "", response_list)
-  return(response_list)
-}
-
-get_age <- Vectorize(function(responses) {
-  responses <- split_responses(responses)
-  if(responses[AGE-1] != "A0") {warnings("cannot find age answer")}
-  else{return (responses[AGE])}
-})
-
-get_gender <- Vectorize(function(responses) {
-  responses <- split_responses(responses)
-  if(responses[GENDER-1] != "A1") {warnings("cannot find gender answer")}
-  else{return (responses[GENDER])}
-})
-
-df.age_gender_V <- df.demog_V %>%
-  filter(variable_type == "demog_age_gender_ethnic") %>%
-  select(subject, responses) %>%
-  mutate(age = as.numeric(get_age(responses))) %>%
-  mutate(age = as.numeric(age)) %>%
-  mutate(gender = get_gender(responses))
-
-df.age_gender_V_summ <- df.age_gender_V %>%
-  summarize(mean_age = mean(age), 
-            median_age = median(age), 
-            sd_age = sd(age))
-```
-
-```{r loading data M explore, warning=FALSE, include=F}
-df.resp_M <- read.csv("../../data/data_M_0530.csv") %>%
+```{r loading data M, warning=FALSE, include=F}
+df.resp_M <- read.csv("../../data/responding/data_CN.csv") %>%
   select(-X)
@@
   filter(finished == "yes")
+
+df.ppts_not_finished_M <- df.resp_M %>% 
+  group_by(subject) %>%
+  summarize(finished = ifelse("demo-final" %in% unique(variable_type), "yes", "no")) %>%
+  filter(finished == "no")
 
@@
   summarize(pass_att_check_percent = mean(pass_att_check)) %>%
-  filter(pass_att_check_percent >= 0.8)
+  filter(pass_att_check_percent == 1.0)
 
@@
 
-```{r exclusion M explore, include = F, warning = F}
+```{r exclusion M, include = F, warning = F}
 #non-native speaker
@@
 percent_dropped = length(ppts_non_native_lang_M) / length(unique(df.resp_M$subject))
-percent_dropped #0.01149425
+percent_dropped #0.01398601
 
@@
 percent_dropped = length(ppts_en_speaker_M) / length(unique(df.resp_M$subject))
-percent_dropped #0.3850575 # will not use this criterion
+percent_dropped #0.3496503 # will not use this criterion
 
@@
 percent_dropped = length(ppts_lived_abroad_M) / length(unique(df.resp_M$subject))
-percent_dropped # 0.1551724
+percent_dropped # 0.1608392
 
@@
 percent_dropped = length(ppts_oversea_exp_M) / length(unique(df.resp_M$subject))
-percent_dropped #0.03448276
+percent_dropped #0
 
@@
 
-length(unique(df.resp_M$subject)) #143
+length(unique(df.resp_M$subject)) 
 ```
 
-```{r demog_M explore, include = F}
-demog <- c("demog-dropdown", "demog-multi-choice", "demog-free-response", "demog-multi-select")
-df.demog_M <- df.resp_M %>%
-  filter(trial_type %in% demog) 
-#write.csv(data_demog, "data_anon_demog_0201.csv")
-
-AGE = 97 #index for age answer
-GENDER = 115 #index for gender answer
-split_responses <- function(responses) {
-  responses <- as.character(responses)
-  response_list <- unlist(strsplit(responses, ',|:'))
-  response_list <- response_list[seq(1, length(response_list))]
-  response_list <- gsub("}", "", response_list)
-  response_list <- gsub("\"", "", response_list)
-  return(response_list)
-}
-
-get_age <- Vectorize(function(responses) {
-  responses <- split_responses(responses)
-  if(responses[AGE-1] != "A0") {warnings("cannot find age answer")}
-  else{return (responses[AGE])}
-})
-
-get_gender <- Vectorize(function(responses) {
-  responses <- split_responses(responses)
-  if(responses[GENDER-1] != "A1") {warnings("cannot find gender answer")}
-  else{return (responses[GENDER])}
-})
-
-df.age_gender_M <- df.demog_M %>%
-  filter(variable_type == "demog_age_gender_ethnic") %>%
-  select(subject, responses) %>%
-  mutate(age = as.numeric(get_age(responses))) %>%
-  mutate(age = as.numeric(age)) %>%
-  mutate(gender = get_gender(responses))
-
-df.age_gender_M_summ <- df.age_gender_M %>%
-  summarize(mean_age = mean(age), 
-            median_age = median(age), 
-            sd_age = sd(age))
+```{r}
+write.csv(df.resp_M, "../../data/responding/dataCN_excl.csv")
 ```
-
-With the new exclusion criteria, we excluded `r length(unique(df.ppts_finished_E$subject)) - length(unique(df.ppts_att_E$subject))` US participants, `r length(unique(df.ppts_finished_V$subject)) - length(unique(df.ppts_att_V$subject))` VN participants, and `r length(unique(df.ppts_finished_M$subject)) - length(unique(df.ppts_att_M$subject))` CN participants who did not answer more than 2 attention checks correctly.
-We then applied the 4 criteria that aim to retain only participants who are influenced by one culture: (1) non-native speakers of English and Vietnamese, respectively, (2) fluent in at least one of the other two study languages (Vietnamese for US participants, English for Vietnamese participants and Chinese participants), (3) have lived outside of the test country (US, Vietnam, or China) for more than two years, and (4) have significant international experience (more than 6 international experiences of 2 days or longer.) We did not use a particular criterion for a language if it would exclude 25% or more of any one sample.
-In this round of exclusion, we excluded `r length(unique(df.ppts_att_E$subject)) - length(unique(df.resp_E$subject))` US, `r length(unique(df.ppts_att_V$subject)) - length(unique(df.resp_V$subject))` VN participants, and `r length(unique(df.ppts_att_M$subject)) - length(unique(df.resp_M$subject))` CN participants.
-After these exclusions, the US sample included `r length(unique(df.resp_E$subject))` participants (`r df.age_gender_E %>% filter(gender == "Male") %>% count()`M, `r df.age_gender_E %>% filter(gender == "Female") %>% count()`F, `r df.age_gender_E %>% filter(gender == "Non-binary") %>% count()` non-binary, `r df.age_gender_E %>% filter(gender == "Decline to answer") %>% count()` other), with mean age = `r round(df.age_gender_E_summ$mean_age, 2)` (SD = `r round(df.age_gender_E_summ$sd_age, 2)`) and median age = `r df.age_gender_E_summ$median_age`.
-The VN sample included `r length(unique(df.resp_V$subject))` participants (`r df.age_gender_V %>% filter(gender == "Nam") %>% count()`M, `r df.age_gender_V %>% filter(gender == "Nữ") %>% count()`F), with mean age = `r round(df.age_gender_V_summ$mean_age, 2)` (SD = `r round(df.age_gender_V_summ$sd_age, 2)`) and median age = `r df.age_gender_V_summ$median_age`.
-The CN sample included `r length(unique(df.resp_M$subject))` participants (`r df.age_gender_M %>% filter(gender == "男性") %>% count()`M, `r df.age_gender_M %>% filter(gender == "女性") %>% count()`F), with mean age = `r round(df.age_gender_M_summ$mean_age, 2)` (SD = `r round(df.age_gender_M_summ$sd_age, 2)`) and median age = `r df.age_gender_M_summ$median_age`.
-
-```{r corpus explore, include = F}
-df.corpus_E <- read.csv("../../data/corpusE_cos.csv") %>%
-  rename(tax_frequency_E = tax.frequency,
-         theme_frequency_E = theme.frequency,
-         tax_cosine_E = Tax.cosine_dist, 
-         theme_cosine_E = Theme.cosine_dist,
-         tax_cosine_sim_E = Tax.cosine_sim,
-         theme_cosine_sim_E = Theme.cosine_sim,
-         tax_match_E = Tax.match,
-         theme_match_E = Theme.match, 
-         cue_E = Cue)
-
-df.corpus_V <- read.csv("../../data/corpusV_cos.csv") %>%
-  rename(tax_frequency_V = tax.frequency,
-         theme_frequency_V = theme.frequency,
-         tax_cosine_V = Tax.cosine_dist, 
-         theme_cosine_V = Theme.cosine_dist,
-         tax_cosine_sim_V = Tax.cosine_sim,
-         theme_cosine_sim_V = Theme.cosine_sim,
-         tax_match_V = Tax.match,
-         theme_match_V = Theme.match, 
-         cue_V = Cue)
-
-df.corpus_M <- read.csv("../../data/corpusM_cos.csv") %>%
-  rename(tax_frequency_M = tax.frequency,
-         theme_frequency_M = theme.frequency,
-         tax_cosine_M = Tax.cosine_dist, 
-         theme_cosine_M = Theme.cosine_dist,
-         tax_cosine_sim_M = Tax.cosine_sim,
-         theme_cosine_sim_M = Theme.cosine_sim,
-         tax_match_M = Tax.match,
-         theme_match_M = Theme.match, 
-         cue_M = Cue)
-```
-
-```{r full corpus explore, M freqs is incorrect, include=F}
-df.corpus <- left_join(df.corpus_E, df.corpus_V, by = "Cue_renamed")
-df.corpus <- left_join(df.corpus, df.corpus_M, by = "Cue_renamed")
-
-#replacing any 0 raw counts with epsilon
-df.corpus <- df.corpus %>%
-  mutate(tax_frequency_E = ifelse(tax_frequency_E == 0, 
-                                  .Machine$double.eps, tax_frequency_E),
-         theme_frequency_E = ifelse(theme_frequency_E == 0, 
-                                  .Machine$double.eps, theme_frequency_E),
-         tax_frequency_V = ifelse(tax_frequency_V == 0, 
-                                  .Machine$double.eps, tax_frequency_V),
-         theme_frequency_V = ifelse(theme_frequency_V == 0, 
-                                  .Machine$double.eps, theme_frequency_V))
-
-```
-
-```{r corpus - frequency explore, include = F}
-#find triads_omit, used whenever analysis uses raw collocates 
-df.corpus_E_freq <- df.corpus_E %>%
-  select(Cue_renamed, cue_E, tax_match_E, theme_match_E, tax_frequency_E, theme_frequency_E)
-corpus_E_omit <- df.corpus_E_freq %>%
-  filter(tax_frequency_E == 0 & theme_frequency_E == 0)
-
-df.corpus_V_freq <- df.corpus_V %>%
-  select(Cue_renamed, cue_V, tax_match_V, theme_match_V, tax_frequency_V, theme_frequency_V)
-corpus_V_omit <- df.corpus_V_freq %>% 
-  filter(tax_frequency_V == 0 & theme_frequency_V == 0)
-
-triads_omit <- append(corpus_E_omit$Cue_renamed, corpus_V_omit$Cue_renamed)
-
-df.corpus_freq <- left_join(df.corpus_E_freq, df.corpus_V_freq, by = "Cue_renamed")
-```
-
-```{r corpus - cosine explore, include = F}
-#mainly for sanity checking and so that there is a parallel df to df.corpus_freq
-df.corpus_E_cos <- df.corpus_E %>%
-  select(Cue_renamed, cue_E, tax_match_E, theme_match_E, 
-         tax_cosine_E, theme_cosine_E,
-         tax_cosine_sim_E, theme_cosine_sim_E)
-
-df.corpus_V_cos <- df.corpus_V %>%
-  select(Cue_renamed, cue_V, tax_match_V, theme_match_V, tax_cosine_V, theme_cosine_V,
-         tax_cosine_sim_V, theme_cosine_sim_V)
-
-df.corpus_M_cos <- df.corpus_M %>%
-  select(Cue_renamed, cue_M, tax_match_M, theme_match_M, tax_cosine_M, theme_cosine_M, 
-         tax_cosine_sim_M, theme_cosine_sim_M)
-
-df.corpus_cos <- left_join(df.corpus_E_cos, df.corpus_V_cos, by = "Cue_renamed")
-df.corpus_cos <- left_join(df.corpus_cos, df.corpus_M_cos, by = "Cue_renamed")
-```
-
-```{r getting triads from the 3 languages explore, include = F}
-#combine response and corpus data
-df.triad_E <- df.resp_E %>%
-  filter(stim_type == "triad",
-         responses != "NA")
-triad_cues_E <- read.csv("../../data/cue_renamed_E.csv")
-df.triad_E <- left_join(df.triad_E, triad_cues_E, by = c("cue", "top_opt", "bottom_opt"))
-df.triad_E <- inner_join(df.triad_E, df.corpus, by = "Cue_renamed")
-
-df.triad_E <- df.triad_E %>%
-  mutate(responses_theme = ifelse(responses == theme_match_E, 1, 0),
-         language = "English",
-         country = "US") %>%
-  select(subject, rt, Cue_renamed, cue, top_opt, bottom_opt, 
-         responses, responses_theme, country, language,
-         tax_match_E, theme_match_E, tax_match_V, theme_match_V, tax_match_M, theme_match_M,
-         tax_frequency_E, theme_frequency_E, tax_frequency_V, theme_frequency_V, tax_frequency_M, theme_frequency_M,
-         tax_cosine_E, theme_cosine_E, tax_cosine_V, theme_cosine_V, tax_cosine_M, theme_cosine_M,
-         tax_cosine_sim_E, theme_cosine_sim_E, tax_cosine_sim_V, theme_cosine_sim_V, tax_cosine_sim_M, theme_cosine_sim_M)
-
-df.triad_V <- df.resp_V %>%
-  filter(stim_type == "triad",
-         responses != "NA")
-triad_cues_V <- read.csv("../../data/cue_renamed_V.csv")
-df.triad_V <- left_join(df.triad_V, triad_cues_V, by = c("cue", "top_opt", "bottom_opt"))
-df.triad_V <- inner_join(df.triad_V, df.corpus, by = "Cue_renamed")
-
-df.triad_V <- df.triad_V %>%
-  mutate(responses_theme = ifelse(responses == theme_match_V, 1, 0),
-         language = "Vietnamese", 
-         country = "Vietnam") %>%
-  select(subject, rt, Cue_renamed, cue, top_opt, bottom_opt, 
-         responses, responses_theme, country, language,
-         tax_match_E, theme_match_E, tax_match_V, theme_match_V, tax_match_M, theme_match_M,
-         tax_frequency_E, theme_frequency_E, tax_frequency_V, theme_frequency_V, tax_frequency_M, theme_frequency_M,
-         tax_cosine_E, theme_cosine_E, tax_cosine_V, theme_cosine_V, tax_cosine_M, theme_cosine_M,
-         tax_cosine_sim_E, theme_cosine_sim_E, tax_cosine_sim_V, theme_cosine_sim_V, tax_cosine_sim_M, theme_cosine_sim_M)
-
-df.triad_M <- df.resp_M %>%
-  filter(stim_type == "triad",
-         responses != "NA")
-triad_cues_M <- read.csv("../../data/cue_renamed_M.csv")
-df.triad_M <- left_join(df.triad_M, triad_cues_M, by = c("cue", "top_opt", "bottom_opt"))
-df.triad_M <- inner_join(df.triad_M, df.corpus, by = "Cue_renamed")
-
-df.triad_M <- df.triad_M %>%
-  mutate(responses_theme = ifelse(responses == theme_match_M, 1, 0),
-         language = "Mandarin", 
-         country = "China") %>%
-  select(subject, rt, Cue_renamed, cue, top_opt, bottom_opt, 
-         responses, responses_theme, country, language,
-         tax_match_E, theme_match_E, tax_match_V, theme_match_V, tax_match_M, theme_match_M,
-         tax_frequency_E, theme_frequency_E, tax_frequency_V, theme_frequency_V, tax_frequency_M, theme_frequency_M,
-         tax_cosine_E, theme_cosine_E, tax_cosine_V, theme_cosine_V, tax_cosine_M, theme_cosine_M,
-         tax_cosine_sim_E, theme_cosine_sim_E, tax_cosine_sim_V, theme_cosine_sim_V, tax_cosine_sim_M, theme_cosine_sim_M)
-
-#calculate proportion for raw frequencies and cosine distance
-df <- rbind(df.triad_E, df.triad_V)
-df <- rbind(df, df.triad_M) %>%
-  mutate(theme_freq_prop_E = theme_frequency_E / (theme_frequency_E + tax_frequency_E),
-         theme_freq_prop_V = theme_frequency_V / (theme_frequency_V + tax_frequency_V), 
-         theme_freq_prop_M = theme_frequency_M / (theme_frequency_M + tax_frequency_M), 
-         theme_cosine_prop_E = theme_cosine_E / (theme_cosine_E + tax_cosine_E),
-         theme_cosine_prop_V = theme_cosine_V / (theme_cosine_V + tax_cosine_V), 
-         theme_cosine_prop_M = theme_cosine_M / (theme_cosine_M + tax_cosine_M)) %>%
-  rename(triad = Cue_renamed)
-```
-
-```{r country effect - explore, warning=FALSE, include=FALSE, paged.print=TRUE}
-df.country <- df %>%
-  group_by(subject, country) %>%
-  summarize(theme_resp_percent = mean(responses_theme, na.rm = T))
-
-df.country_sum <- df.country %>%
-  group_by(country) %>%
-  summarize(mean_theme_resp_percent = mean(theme_resp_percent), 
-            sd_theme_resp_percent = sd(theme_resp_percent))
-
-fit.country = glmer(responses_theme ~ country + (1 | subject) + (country | triad), 
-                    data = df, 
-                    family = "binomial")
-summary(fit.country) 
-fit.country.anova = Anova(fit.country, type=3)
-
-fit.country_EN_VN = glmer(responses_theme ~ country + (1 | subject) + (country | triad), 
-                    data = df %>% filter(country != "China"),
-                    family = "binomial")
-summary(fit.country_EN_VN) 
-```
-
-```{r echo=FALSE, warning=FALSE, fig.cap="Proportion of thematic responses by country, with a less stringent attention check criterion.
-We did not find any significant differences from the analysis reported above with a more stringent criterion."}
-
-ggplot(df.country,
-       mapping = aes(x = country, 
-                     y = theme_resp_percent, 
-                     color = country)) +
-  geom_violin() +
-  geom_jitter(height = 0, 
-              alpha = 0.3) +  
-  stat_summary(fun.data = "mean_cl_boot", 
-               geom = "pointrange") + 
-  labs(y = "Proportion Thematic Chosen", 
-       x = "Country", 
-       color = "Country") + 
-  scale_color_manual(values=c("#D63230", "#1C77C3", "#F39237"))
-```
-
-There is no significant difference in this round of analysis compared to the one reported above (with more stringent attention check criterion).
-That is, we still observed a significant effect of country on proportion of thematic responses ($\chi^2$(`r fit.country.anova["country", "Df"]`) = `r round(fit.country.anova["country", "Chisq"], 2)`, p < .001), but this effect is driven by only the difference between US and China response ($\beta$ = `r round(fixef(fit.country)["countryUS"], 2)`, p < .001).
-There is no statistical difference between the Vietnam and China response ($\beta$ = `r round(fixef(fit.country)["countryVietnam"], 2)`, p = `r round(as.data.frame(summary(fit.country)[["coefficients"]])["countryVietnam", "Pr(>|z|)"], 3)`), and the US and Vietnam response ($\beta$ = `r round(fixef(fit.country_EN_VN)["countryVietnam"], 2)`, p = `r round(as.data.frame(summary(fit.country)[["coefficients"]])["countryVietnam", "Pr(>|z|)"], 3)`).
-
-# Discussion
-In this paper, we consider whether statistics of the language environment can account for cross-cultural differences in a classic similarity judgment paradigm, as an alternative to the view that members of different cultures vary in their conception of similarity.
-
-We first tested the generality of a cultural account which holds that people from Western and East Asian cultures tend to conceive of similarity in more taxonomic and thematic ways, respectively, and respond accordingly in categorization tasks such as ours.
-While we managed to replicate the previously documented contrast between English speakers in the US and Mandarin Chinese speakers from East Asia (mainland China, Taiwan, Hong Kong, and Singapore), we do not extend this contrast to our sample of Vietnamese speakers in Vietnam and English speakers in the US.
-This finding suggests some limitations on the generality of this cultural account.
-
-We did find some signatures of language specificity in our analysis, such as the large positive correlation between similarity judgments of each country and the respective corpus statistics, and how each corpus statistics are good predictors for corresponding country's similarity judgments.
-However, this is potentially due to the high correlation between corpus statistics of English, Vietnamese and Mandarin.
-We find even stronger evidence for consistency across the three groups, with substantive overlapping predictions across the corpus models, highly similar responding across the experiments, and a correspondingly high fit in cross-language comparisons between models and data.
-
-```{r include=FALSE}
-fit.country_no_triad <- glmer(responses_theme ~ country + (1 | subject), 
-                              data = df_main_analysis, 
-                              family = "binomial")
-
-fit.country = glmer(responses_theme ~ country + (1 | subject) + (country | triad), 
-                    data = df_main_analysis, 
-                    family = "binomial")
-summary(fit.country)
-
-fit.no_triad_compare <- anova(fit.country, fit.country_no_triad, type = 3)
-```
-
-There are some suggestions that the current approach can predict triad-specific cross-cultural effects.
-First of all, an ANOVA model comparison showed that adding a random effect term for varying slope by country and varying intercept by triad to the model produces a significant better fit than the identical model without this random effect term included as a predictor ($\chi^2$(`r fit.no_triad_compare["fit.country", "Df"]`) = `r round(fit.no_triad_compare["fit.country", "Chisq"], 2)`, p < .001)
-
-Anecdotally, we show below some examples of triads that show contrasting difference in the magnitude of difference in thematic responses between countries.
-As a review, the overall result across all triads showed that there was significant difference between US and China responding, and no significant differences between US and Vietnam or China and Vietnam responding.
-However, we observed that for the triad "cow-grass-chicken," there were significant differences between US and China, and US and Vietnam responding.
-There was no significant difference between China and Vietnam responding.
-For the triad "spoon-sugar-fork," there were significant difference between China and US, and China and Vietnam responding, but no significant difference between US and Vietnam.
-For the triad "hair-comb-beard," there were no significant differences pairwise across the three cultural contexts.
-This suggests that there are triad-specific cross-cultural effects in play.
-Beyond emphasizing the importance of including triad predictors as a random effect, this finding suggests that, firstly, future similar studies need to report triads that are used, as the triads used can affect results (for example, if a study only includes triads where China and US responding are significantly different, it would be more likely to conclude that Chinese and US cultures hold different notions of similarity).
-Secondly, that future studies can look more deeply into which groups of triads are driving the US-China responding difference.
-For example, triads belonging to different semantic neighborhoods might be influencing cross-cultural responding in different ways.
-
-```{r include=FALSE}
-df.country_item <- df_main_analysis %>%
-  filter(triad == "hair")
-
-plot.hair <- ggplot(df.country_item,
-       mapping = aes(x = factor(country, levels=c("China", "US", "Vietnam")), 
-                     y = responses_theme, 
-                     color = factor(country, levels=c("China", "US", "Vietnam")))) +
-  geom_jitter(stat = "identity", alpha  = .5) +
-  labs(y = "Proportion Thematic Chosen (hair: beard / comb)",  
-       x = "Country", 
-       color = "Country") + 
-  stat_summary(fun.data = "mean_cl_boot", 
-               geom = "pointrange") + 
-  scale_y_continuous(limits=c(0.0, 1.0), oob = scales::squish) + 
-  scale_fill_manual(values=c("#D63230", "#1C77C3", "#F39237")) +  
-  scale_color_manual(values=c("#D63230", "#1C77C3", "#F39237"))  + 
-  theme(axis.title = element_text(size=rel(0.75)))
-```
-
-```{r include=FALSE}
-df.country_item <- df_main_analysis %>%
-  filter(triad == "spoon2")
-
-plot.spoon2 <- ggplot(df.country_item,
-       mapping = aes(x = factor(country, levels=c("China", "US", "Vietnam")), 
-                     y = responses_theme, 
-                     color = factor(country, levels=c("China", "US", "Vietnam")))) +
-  geom_jitter(stat = "identity", alpha  = .5) +
-  labs(y = "Proportion Thematic Chosen (spoon: fork / sugar)",  
-       x = "Country", 
-       color = "Country") + 
-  stat_summary(fun.data = "mean_cl_boot", 
-               geom = "pointrange") + 
-  scale_y_continuous(limits=c(0.0, 1.0), oob = scales::squish) + 
-  scale_fill_manual(values=c("#D63230", "#1C77C3", "#F39237")) +  
-  scale_color_manual(values=c("#D63230", "#1C77C3", "#F39237")) + 
-  theme(legend.position = "none") + 
-  theme(axis.title = element_text(size=rel(0.75)))
-```
-
-```{r include = FALSE}
-#show 1 triad
-
-df.country_item <- df_main_analysis %>%
-  filter(triad == "cow2")
-
-df.country_item_summ <- df_main_analysis %>%
-  group_by(triad, country) %>%
-  summarize(theme_resp_percent = mean(responses_theme, na.rm = T)) %>%
-  filter(triad == "cow2")
-
-plot.cow2 <- ggplot(df.country_item,
-       mapping = aes(x = factor(country, levels=c("China", "US", "Vietnam")), 
-                     y = responses_theme, 
-                     color = factor(country, levels=c("China", "US", "Vietnam")))) +
-  geom_jitter(stat = "identity", alpha  = .5) +
-  labs(y = "Proportion Thematic Chosen (cow: chicken / grass)",  
-       x = "Country", 
-       color = "Country") + 
-  stat_summary(fun.data = "mean_cl_boot", 
-               geom = "pointrange") + 
-  scale_y_continuous(limits=c(0.0, 1.0), oob = scales::squish) + 
-  scale_fill_manual(values=c("#D63230", "#1C77C3", "#F39237")) +  
-  scale_color_manual(values=c("#D63230", "#1C77C3", "#F39237")) + 
-  theme(legend.position = "none") + 
-  theme(axis.title = element_text(size=rel(0.75)))
-# 
-# +  
-#   geom_bar(data = df.country_item_summ, 
-#            mapping = aes(x = factor(country, levels=c("China", "US", "Vietnam")), 
-#                           y = theme_resp_percent, 
-#                          color = factor(country, levels=c("China", "US", "Vietnam"))), 
-#            stat='identity', alpha = .3, 
-#            fill=c("#D63230", "#1C77C3", "#F39237"))
-```
-
-```{r echo=FALSE, warning = FALSE, fig.width=8, fig.cap="Anecdotal evidence of triad-specific effects.
-Cow-grass-chicken shows significant differences between US-China responding, and between US-Vietnam responding.
-Spoon-sugar-fork shows only a significant difference between US-China responding.
-Hair-comb-beard does not show any significant differences in pairwise comparisons across the three countries."}
-plot.cow2 + plot.spoon2 + plot.hair + 
-    plot_layout(ncol = 3)
-```
-
-We also identified some data quality / quantity issues that are an obstacle to modeling similarity in Vietnamese and Mandarin.
-As stated above, we were not able to find a Mandarin corpus with raw co-occurrences that contains similar magnitude of number of sentences as our English corpus (COCA).
-Additionally, we could only retrieve fastText word vectors for Vietnamese and Mandarin that are trained on both Common Crawl and Wikipedia.
-63% of the articles on Vietnamese Wikipedia and 16% of the Chinese Wikipedia are bot translations from another language (compared to 3% of English Wikipedia).
-This would affect the quality of the word vectors trained on the Vietnamese and Chinese Wikipedia, potentially making them not reflecting the naturally-occurring lexical co-occurrence in the corresponding language.
-
-Our findings raise additional questions for future work: if not differences in taxonomic vs.
-thematic responding, then what differences drive the relativity effects previous studies have observed?
-To what extent are the relativity effects driven by language, and to what extent by culture?
-@Ji2004 established that culture-aligned differences in this paradigm exist, even when the test language is held constant, concluding that “it is culture (independent of the testing language) that led to different grouping styles” in their study.
-Our data provide a cautionary note to this conclusion, suggesting that semantic representations in bilinguals (see @Francis2005 for a review) may have the potential to provide an offline account for cross-context differences in similarity judgments, independent of test language.
-However, there are still many open questions for this account.
-How do semantic associations guide categorization?
-Can they explain taxonomic-thematic differences of the type reported by @Ji2004 and others?
-Can we provide a more specific computational account than the simple frequency model tested here?
-
-Despite these caveats, our findings here demonstrate the plausibility of an alternative perspective on cross-cultural accounts of language, thought, and similarity in the case of taxonomic and thematic reasoning: that it may be the input to similarity judgments, rather than the evaluative process or the conceptualization of similarity that produces variation in similarity reasoning across cultural and linguistic contexts.
-We hope this work provides a foundation for further research probing this question.
-
-[^footnote]:While we discuss cross-cultural variability at the level of countries or larger world areas, these are not cultural monoliths.
-For convenience, we operationalize culture at the level of country, based on where participants were raised.
-It is an open question whether performance in our participant populations (of relatively young and well-educated adults) is representative of the broader country.
-This is especially true for societies with substantial ethnic and cultural variation such as the US.
-We expect that our data is likely to underestimate variation both within and between the countries we sample from.
-
-\newpage
-
-# References
-
-\begingroup
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
-
-<div id="refs" custom-style="Bibliography"></div>
-\endgroup
-
-\newpage
-# Supplemental Information
-
-hi
-```{r echo=TRUE, fig.align="center", fig.cap=c("List of triads used"), fig.show="hold"}
-#include_graphics(c("../../data/SI_triads/SI_triads_1.jpg"))
-include_graphics(c("../../data/SI_triads/SI_triads_1.jpg",
-                   "../../data/SI_triads/SI_triads_2.jpg",
-                   "../../data/SI_triads/SI_triads_3.jpg",
-                   "../../data/SI_triads/SI_triads_4.jpg",
-                   "../../data/SI_triads/SI_triads_5.jpg"))
-```

### 2022-12-14 code/1_exclusions_old/1_exclusionsUS.Rmd
setting up cogsci paper

--- 2022-09-28 code/3_analysis/3_analysis.Rmd
@@
 
-r_refs("r-references.bib")
-r_refs("references/packages.bib")
-
 ```
@@
 
-# Introduction 
-By virtue of discrete words and grammatical features, language provides a categorical partition of our continuous experiences.
-Previous research has observed variation in the cognition of speakers of different languages corresponding to variation within semantic domains in these languages.
-This language-aligned variation has been observed in the domains of color [@Winawer2007], number [@Frank2008], and gender [@Boroditsky2003], among many others [@Wolff2011].
-Differences in cognition between speakers of different languages have often been used to suggest, explain, or exemplify cultural differences between speakers of those languages.
-Findings in studies of both language and of culture provide convergent evidence suggesting that variation across languages and cultures may shape broad variation in how people think about similarity between, for instance, different colors or objects.
-
-Looking beyond this domain-specific variation, we can also consider broader notions of similarity and relatedness between concepts across domains.
-The Free Association Norms [@FreeAssoc], for example, measures human judgment in semantic relatedness across domains and contexts.
-With the availability of large linguistic corpora, we can examine the similarity of concepts that are not circumscribed in individual domains (as color, number, and gender are), allowing us to answer more general questions about variation in cognition between speakers of different languages.
-By measuring the similarity between arbitrary words (as commonly done with lexical co-occurrence models), it may be possible to model the shape of similarity space in order to capture cross-linguistic and cross-cultural variation and provide a more general answer to the question of how language influences our conception of the world.
-
-Taxonomic and thematic similarity provide a convenient entry point to broader debates about cross-linguistic and cross-cultural variation in notions of similarity.
-Taxonomic categorization is based on the similarity of attributes, for example, similar perceptual properties, like shared color or shape, among objects.
-In contrast, thematic categorization is based on causal, spatial, and temporal relationships among objects [@Markman1984].
-To illustrate this point, if a participant is given the words “chicken” and “grass”, and asked which of those words are more closely related to the word “cow”, the pairing “chicken” - “cow” indicates a taxonomic match, whereas “grass” - “cow” indicates a thematic match.
-
-@Ji2004 found that preferences for taxonomic and thematic matches differ across culture, even when controlling for testing language and fluency.
-Specifically, Chinese participants made more thematic matches than taxonomic, while the converse was true for European Americans.
-This difference held even for Chinese participants tested in English (rather than Mandarin), suggesting that culture has an effect on the categorization strategy independent of the test language.
-However, the study also found an effect of language within Chinese participants from mainland China (when tested both in China and in the US): their preference for thematic categorization was significantly lower when tested in English compared to Mandarin Chinese.
-This suggests that test language also influences categorization strategies.
-Ji et al.
-characterize these results as demonstrating that culture (independent of language) leads to different styles of reasoning about similarity, whereas language serves as a “tuning” mechanism operating within a culturally-specific style, by activating representations corresponding to the language being used.
-
-## Cross-cultural variation in similarity
-The account that culture drives differences in categorization style has been one favored by other non-linguistic studies that use taxonomic vs thematic categorization to probe similarity judgment.
-A similar study to the aforementioned shows that when shown pictorial triads that represent words (i.e.
-pictures of an ant, a bee, and honey), Chinese children (9-10 years old) scored higher on thematic categorization compared to American children of the same age range, and vice versa for taxonomic categorization [@Chiu1972].
-Additionally, the cross-cultural differences in similarity judgment seem to persist even when the stimuli are more perceptual and less conceptual.
-@Norenzayan2002 conducted a study where participants are shown a target stimulus beneath two groups of 4 similar objects.
-The target shares a common feature with all the objects in one group, and only shares another one feature with each member of that group.
-Meanwhile, the target shares many features with 3 out of 4 members of the other group, but does not share any 1 feature in common with the entire group.
-The study showed that American participants judged the target to be more similar with the former group more often, and vice versa for Chinese participants.
-Since differences in categorization style persist with novel stimuli (as opposed to previously seen words or pictures of concepts), this suggests that participants from different cultural backgrounds are utilizing different reasoning strategies when making similarity judgments.
-
-Most commonly, researchers account for the differences in similarity judgment described above by differences in analytic vs holistic processing and in attention between Eastern and Western cultures.
-According to this framework, East Asians attend more to relationships between objects and context and reason more holistically, whereas Westerners attend more to objects and their properties, and reason analytically [@Nisbett2003].
-The analytic-holistic cultural difference in reasoning style has been observed in other non-linguistic tasks.
-For example, in a rod-and-frame test [@Witkin1954], East Asian (Taiwanese Chinese) participants are more influenced by the position of the surrounding frame than European Americans [@Ji2000], suggesting a higher level of sensitivity to context.
-East Asians (Koreans) have also been demonstrated to make more situational attributions for behaviors than European Americans, who make more dispositional attributions [@Choi1999], again suggesting higher sensitivity to context.
-When shown a complex scene with foreground and background information, Japanese participants made more statements about contextual information and relationships between objects than Americans did [@Masuda2001].
-Non-linguistic tasks have also shown that participants from Eastern and Western cultures differ in where they focus their visual attention.
-Another study presented American and Chinese participants with photographs of an object on a complex background [@Chua2005].
-They found that Chinese participants made more eye saccades to the background compared to American participants, and that American participants looked at the object more quickly.
-These cross-cultural differences in attention and analytic vs holistic processing are seen to map onto the cross-cultural differences in similarity judgment: because East Asian participants attend more to the context between objects and reason more holistically, it stands to reason that they would consider words that appear in the same context (i.e.
-thematically similar) to be more similar than taxonomically-similar words.
-
-Studies that explain these cross-cultural differences in reasoning and similarity judgment with a cultural framework often draw on social and historical contexts as the distal cause for these differences.
-For example, social structure and social practice can explain why different cultures develop different reasoning habits.
-To demonstrate this, researchers have looked at regions that are geographically close but with different social structures.
-@Kitayama2006 showed that Hokkaido Japanese demonstrated greater dispositional bias in attribution of behaviors compared to non-Hokkaido Japanese.
-The study suggested that this difference is correlated to the fact that Hokkaido was settled quite recently (mid-19th century) by pioneers from southern Japan, and thus its social practices (e.g.
-daily routines, child-rearing practices, and explicit education) would be influenced by the independent, goal-oriented characteristic of pioneer life.
-Another study showed that Northern Italians (more independent) categorized objects in a more taxonomic manner than Southern Italians (more interdependent) [@Knight2007].
-These studies, however, stopped short of providing a mechanism for the nature of the relationship between differences in social structures and differences in reasoning and similarity judgments.
-
-Another component of the social context explanation seems to be more tenable regarding the causal connection between cross-cultural differences in social practice and those in similarity judgments: that different patterns of attention are passed on by caregivers to children.
-@Fernald1993 found that American mothers labeled toys and pointed out their attributes more often than do Japanese mothers, while Japanese mothers tended to use the toys to engage their infants in social routines more often than American mothers.
-@Tardif1997 found that English-speaking caregivers produced more nouns than verbs in child-directed speech, while Mandarin-speaking caregivers emphasized verbs over nouns.
-Emphasis on labeling objects and focus on nouns over verbs might lead infants to attend to objects and their taxonomic categorizations, while emphasis on social practices and producing more verbs might direct infants' attention to the relationship between objects.
-Such differences in early-childhood environments could tune children’s attention to either object or context, and result in cross-cultural differences in similarity judgments (preferring either taxonomic or thematic, respectively) in adulthood.
-
-The above view explains cross-cultural differences in similarity judgment tasks as variation in the conceptualization of similarity itself.
-Alternatively, these judgments could be shaped by cross-cultural differences in the statistics of the environment, and accordingly the content of everyday experiences.
-Perhaps when confronted with the triad task, participants from all cultures follow the same process for reasoning about similarity, but rely on language or culture-specific inputs to this process.
-For example, it may be that Vietnamese participants are more likely to have knowledge of farming practices than Americans, and may associate cows and grass more strongly (as grass is the typical feed for cows in the small-scale family farming contexts common in Vietnam).
-Americans, on the other hand, may have strong associations between cows and chickens as a result of encountering them together in children’s books or petting zoo contexts.
-If we observe a difference in categorization between, say Vietnamese and US participants, perhaps they use the same procedure (considering similarity that is influenced by both taxonomic and thematic relations), but the inputs to this procedure differ between cultures, with Vietnamese participants exposed to more instances of “cow” and “grass” occurring together, compared to US participants.
-
-A study by @Miyamoto2006 lends support to this theory.
-The study randomly sampled scenes from different-sized cities in Japan and the US.
-Both subjective (judgment by American and East Asian college students) and objective (number of objects as counted by an automated program) showed that Japanese scenes were more complex and contained a larger number of objects than American scenes.
-This suggests that people living in Japan would more frequently encounter perceptual environments that contain more relationships between objects compared to those who live in the US.
-Japanese scenes therefore might encourage focus on the overall context, while American scenes might encourage focus on a few salient objects.
-
-Differences in environmental statistics extend beyond the immediate environment to cultural artifacts.
-@Tsai2007 showed that best-selling storybooks in the US contain more pictures of excited states (e.g.
-open-mouthed smiles, wide-open eyes) compared to best-selling storybooks in Taiwan, which contain more pictures of calm states.
-European American preschoolers also perceived excited states as happier and more desirable compared to calm states, and vice versa for Taiwanese Chinese preschoolers.
-The study also showed that there is a causal link between exposure to environmental statistics and personal preference: regardless of culture, exposure to exciting (vs.
-calm) storybooks increased children’s preference for the  corresponding activities.
-Broadly, this suggests that cultural artifacts or information in language (rather than direct, first-hand lived experiences) could be crucial factors in driving cross-cultural variation.
-
-## Language as a proxy of variation in experience
-While co-occurrences in experience are difficult to measure, co-occurrence in language can provide a rough proxy--and indeed, language may afford many of the “experiences” that people have with infrequently encountered items, like cows or helicopters.
-In the planned analyses, we will use co-occurrence in language as a proxy of cultural experience.
-This is a generalizing assumption, and while no linguistic corpus can be expected to fully capture a culture, and different linguistic corpora may capture different variables of a culture, using this proxy as a model of culture provides a conservative test of the hypothesis that differences in the input, rather than the process, of reasoning produces cultural variation in this task.
-This means that if such a model does work -- if linguistic co-occurrence can predict cultural variation in this similarity task without building differences in the decision process into the model -- it is relatively strong evidence that language alone (perhaps as a more easily observed source of information on broader cultural and ecological variation) may account for these cross-cultural differences in reasoning.[^footnote]
-
-Indeed, previous work suggests that using lexical co-occurrence as a proxy can be useful in thinking about similarity judgments.
-Natural language processing tasks have found that lexical co-occurrence is a good predictor for performance in similarity judgment tasks.
-@Griffiths2007 showed that a model that takes word-document co-occurrence as input can be used to predict word association and the effects of semantic association on a variety of linguistic tasks.
-Additionally, lexical semantic models that are constructed using lexical co-occurrence (as opposed to annotated relations) have been shown to perform well on predicting human judgments about similarity between word pairs that are either thematically or taxonomically related [@Rohde2006].
-
-Our current study will be using 2 measures of lexical co-occurrence: 1) raw lexical co-occurrences and 2) cosined distances of fastText word vectors.
-fastText is a system that uses lexical co-occurrence information to generate a vector representing each word in its lexicon [@Mikolov2018].
-fastText uses a continuous bag-of-words model, which takes into account a symmetric window of words surrounding the word in question and maximizes the log-likelihood of the probability of the word given its context.
-Calculating the cosine-similarity between word vectors from fastText gives us a score of how similar the contexts of these words are.
-Therefore, words that occur in the same context (high lexical co-occurrence) would have a larger cosine-similarity score.
-
-It must be noted that fastText supplements the lexical co-occurrence information by simultaneously training weight vectors for each position relative to the word in question, as well as adding sub-word information (bag-of-character n-gram vectors for each character forming the words).
-The similarity judgment prediction given by fastText may be more higher than a model using purely lexical co-occurrence information.
-However, models that use only lexical co-occurrence information (with or without a simple position weight system that gives more weight to words that are closer to the word in question) also perform well in similarity prediction tasks.
-For this study, due to the lack of large cleaned corpora for Mandarin and Vietnamese, we are leveraging fastText pre-trained models on the languages we are interested in @Grave2018.
-
-Systems like fastText and word2vec have been demonstrated to be good predictors for similarity judgments.
-@Liu2019 showed that fastText performed well as the data for a system matching responses in a knowledge base by how similar they are to a customer’s query.
-A study by @Jatnika2019 tested a word2vec model trained on the English wikipedia corpus against 353 word pairs labeled with similarity values based on human judgment.
-The word2vec model correlates moderately with human judgment.
-fastText has also been shown to be sensitive towards cultural effects on word meanings: @Thompson2020 applied fastText to language-specific Wikipedia corpus (among others) to generate a “semantic neighborhood” of 1010 meanings in different languages.
-The study showed that languages that are spoken by more similar cultures, more geographically proximate and/or historically related had more semantic neighborhoods that aligned.
-This is a proof of concept for our use of fastText in different languages with varying levels of relatedness.
-
-## The present study
-@Ji2004 showed the difference in similarity judgment between Chinese and European Americans (the former prefers thematic categorization while the latter prefers taxonomic).
-However, their evidence is not sufficient to conclude that it is culture that drives this difference, as their cross-cultural data is correlational.
-Furthermore, they have yet to rule out all mechanisms by which language could be relevant to the task.
-For example, their language manipulation (bilingual speakers from Mainland China making more taxonomic categorizations when tested in language) only points to an offline effect of language because it does not prevent participants from accessing linguistic representations.
-A stronger claim could have been made if verbal interference had been conducted, and if cross-cultural differences had remained.
-This would have been stronger in eliminating online effect of language as a potential cause for cross-cultural differences in similarity judgment.
-
-Additionally, outside of language, cross-cultural differences could come from a couple different mechanisms: @Ji2004 suggested that the notion of similarity is what varies across cultural groups, but it’s quite possible that similarity is regarded in the same way and it’s actually the input to this similarity judgment that varies across culture contexts.
-It might be possible to gain traction on possible mechanisms by examining whether variation in similarity judgments co-varies with environmental statistics that differ across the cultural and linguistic contexts.
-
-In this study, we ask whether variation in lexical co-occurrence can account for the cross-context (culture and language) differences observed in how people evaluate similarity.
-Firstly, we attempt to replicate @Ji2004 by running a study comparing English speakers in the US and Mandarin speakers in mainland China.
-Secondly, we evaluate whether the differences observed between English and Mandarin speakers’ similarity judgments also extend to comparisons between English and Vietnamese, by running a similar study between English speakers in the US and Vietnamese speakers in Vietnam.
-Vietnam is a Southeast Asian country that borders China and is historically greatly influenced by Chinese culture [@Hui2002].
-Therefore, it serves as a suitable cultural context to investigate whether the claim made by @Ji2004 and previous studies, that Eastern and Western cultures have different notions of similarity, extends beyond mainland China.
-
-We then ask to what extent similarity judgments show cross-context differences that align with co-occurrence patterns in participants’ languages.
-We would only see a main effect of cultural context if the notion of differing notions of similarity is driving these cross-cultural differences.
-Meanwhile, if we do see variation in responding trial-to-trial that tracks with lexical co-occurrence statistics (as a rough proxy combining both linguistic and cultural context), this would give traction to the view that cross-cultural notions of similarity might be similar, and it is environmental statistics that guide the differences in similarity judgments.
-To preview our results, we find that, while we do not see overall group differences (between the East Asian contexts and the US) in similarity, we do find language-specific co-occurrence can indeed explain cross-context differences in similarity judgments.
-In contrast to previous accounts, by which culture induces differing conceptions of similarity (varying between taxonomic and thematic), these findings provide an alternative, and more specific, account by which language may explain these cross-cultural differences without invoking variation in notions of similarity.
-
-# Methods 
-```{r get exclusion results from 1_exclusions.Rmd}
-source("../1_exclusions/1_exclusionsCN.Rmd")
-source("../1_exclusions/1_exclusionsUS.Rmd")
-source("../1_exclusions/1_exclusionsVN.Rmd")
-```
-
-```{r demog_E, TODO: move outside, include = F}
-demog <- c("demog-dropdown", "demog-multi-choice", "demog-free-response", "demog-multi-select")
-df.demog_E <- df.resp_E %>%
-  filter(trial_type %in% demog) 
-#write.csv(data_demog, "data_anon_demog_0201.csv")
-
-AGE = 97 #index for age answer
-GENDER = 115 #index for gender answer
-split_responses <- function(responses) {
-  responses <- as.character(responses)
-  response_list <- unlist(strsplit(responses, ',|:'))
-  response_list <- response_list[seq(1, length(response_list))]
-  response_list <- gsub("}", "", response_list)
-  response_list <- gsub("\"", "", response_list)
-  return(response_list)
-}
-
-get_age <- Vectorize(function(responses) {
-  responses <- split_responses(responses)
-  if(responses[AGE-1] != "A0") {warnings("cannot find age answer")}
-  else{return (responses[AGE])}
-})
-
-get_gender <- Vectorize(function(responses) {
-  responses <- split_responses(responses)
-  if(responses[GENDER-1] != "A1") {warnings("cannot find gender answer")}
-  else{return (responses[GENDER])}
-})
-
-df.age_gender_E <- df.demog_E %>%
-  filter(variable_type == "demog_age_gender_ethnic") %>%
-  select(subject, responses) %>%
-  mutate(age = as.numeric(get_age(responses))) %>%
-  mutate(age = as.numeric(age)) %>%
-  mutate(gender = get_gender(responses))
-
-df.age_gender_E_summ <- df.age_gender_E %>%
-  summarize(mean_age = mean(age), 
-            median_age = median(age), 
-            sd_age = sd(age))
-```
-
-```{r demog_V, TODO: move outside, include = F}
-demog <- c("demog-dropdown", "demog-multi-choice", "demog-free-response", "demog-multi-select")
-df.demog_V <- df.resp_V %>%
-  filter(trial_type %in% demog)
-
-AGE = 97 #index for age answer
-GENDER = 115 #index for gender answer
-split_responses <- function(responses) {
-  responses <- as.character(responses)
-  response_list <- unlist(strsplit(responses, ',|:'))
-  response_list <- response_list[seq(1, length(response_list))]
-  response_list <- gsub("}", "", response_list)
-  response_list <- gsub("\"", "", response_list)
-  return(response_list)
-}
-
-get_age <- Vectorize(function(responses) {
-  responses <- split_responses(responses)
-  if(responses[AGE-1] != "A0") {warnings("cannot find age answer")}
-  else{return (responses[AGE])}
-})
-
-get_gender <- Vectorize(function(responses) {
-  responses <- split_responses(responses)
-  if(responses[GENDER-1] != "A1") {warnings("cannot find gender answer")}
-  else{return (responses[GENDER])}
-})
-
-df.age_gender_V <- df.demog_V %>%
-  filter(variable_type == "demog_age_gender_ethnic") %>%
-  select(subject, responses) %>%
-  mutate(age = as.numeric(get_age(responses))) %>%
-  mutate(age = as.numeric(age)) %>%
-  mutate(gender = get_gender(responses))
-
-df.age_gender_V_summ <- df.age_gender_V %>%
-  summarize(mean_age = mean(age), 
-            median_age = median(age), 
-            sd_age = sd(age))
-```
-
-```{r demog_M, TODO: MOVE outside, include = F}
-demog <- c("demog-dropdown", "demog-multi-choice", "demog-free-response", "demog-multi-select")
-df.demog_M <- df.resp_M %>%
-  filter(trial_type %in% demog) 
-#write.csv(data_demog, "data_anon_demog_0201.csv")
-
-AGE = 97 #index for age answer
-GENDER = 115 #index for gender answer
-split_responses <- function(responses) {
-  responses <- as.character(responses)
-  response_list <- unlist(strsplit(responses, ',|:'))
-  response_list <- response_list[seq(1, length(response_list))]
-  response_list <- gsub("}", "", response_list)
-  response_list <- gsub("\"", "", response_list)
-  return(response_list)
-}
-
-get_age <- Vectorize(function(responses) {
-  responses <- split_responses(responses)
-  if(responses[AGE-1] != "A0") {warnings("cannot find age answer")}
-  else{return (responses[AGE])}
-})
-
-get_gender <- Vectorize(function(responses) {
-  responses <- split_responses(responses)
-  if(responses[GENDER-1] != "A1") {warnings("cannot find gender answer")}
-  else{return (responses[GENDER])}
-})
-
-df.age_gender_M <- df.demog_M %>%
-  filter(variable_type == "demog_age_gender_ethnic") %>%
-  select(subject, responses) %>%
-  mutate(age = as.numeric(get_age(responses))) %>%
-  mutate(age = as.numeric(age)) %>%
-  mutate(gender = get_gender(responses))
-
-df.age_gender_M_summ <- df.age_gender_M %>%
-  summarize(mean_age = mean(age), 
-            median_age = median(age), 
-            sd_age = sd(age))
-```
-## Participants
-We recruited `r length(unique(df.ppts_finished_E$subject))` participants from the US, `r length(unique(df.ppts_finished_V$subject))` participants from Vietnam, and `r length(unique(df.ppts_finished_M$subject))` participants from mainland China.
-US participants were recruited through snowball sampling seeded with Stanford email lists, Vietnam participants were recruited through snowball sampling seeded with Vietnam-based student groups on Facebook, and mainland China participants were recruited through snowball smapling seeded with group chats on WeChat.
-US participants were compensated with $5 gift certificates (USD), VN participants received 50,000₫ (VND) in phone credit, and mainland China participants received 25CNY through WeChat credit transfer.
-
-We excluded `r length(unique(df.ppts_finished_E$subject)) - length(unique(df.ppts_att_E$subject))` US participants, `r length(unique(df.ppts_finished_V$subject)) - length(unique(df.ppts_att_V$subject))` Vietnam participants, and `r length(unique(df.ppts_finished_M$subject)) - length(unique(df.ppts_att_M$subject))` China participants who did not answer all attention checks correctly.
-We followed 4 exclusion criteria that aim to retain only participants who are influenced by one culture: (1) non-native speakers of English and Vietnamese, respectively, (2) fluent in at least one of the other two study languages (Vietnamese for US participants, English for Vietnamese participants and Chinese participants), (3) have lived outside of the test country (US, Vietnam, or China) for more than two years, and (4) have significant international experience (more than 6 international experiences of 2 days or longer.) We did not use a particular criterion for a language if it would exclude 25% or more of any one sample.
-In this round of exclusion, we excluded `r length(unique(df.ppts_att_E$subject)) - length(unique(df.resp_E$subject))` US, `r length(unique(df.ppts_att_V$subject)) - length(unique(df.resp_V$subject))` Vietnam participants, and `r length(unique(df.ppts_att_M$subject)) - length(unique(df.resp_M$subject))` China participants.
-After these exclusions, the US sample included `r length(unique(df.resp_E$subject))` participants (`r df.age_gender_E %>% filter(gender == "Male") %>% count()`M, `r df.age_gender_E %>% filter(gender == "Female") %>% count()`F, `r df.age_gender_E %>% filter(gender == "Non-binary") %>% count()` non-binary, `r df.age_gender_E %>% filter(gender == "Decline to answer") %>% count()` other), with mean age = `r round(df.age_gender_E_summ$mean_age, 2)` (SD = `r round(df.age_gender_E_summ$sd_age, 2)`) and median age = `r df.age_gender_E_summ$median_age`.
-The Vietnam sample included `r length(unique(df.resp_V$subject))` participants (`r df.age_gender_V %>% filter(gender == "Nam") %>% count()`M, `r df.age_gender_V %>% filter(gender == "Nữ") %>% count()`F), with mean age = `r round(df.age_gender_V_summ$mean_age, 2)` (SD = `r round(df.age_gender_V_summ$sd_age, 2)`) and median age = `r df.age_gender_V_summ$median_age`.
-The China sample included `r length(unique(df.resp_M$subject))` participants (`r df.age_gender_M %>% filter(gender == "男性") %>% count()`M, `r df.age_gender_M %>% filter(gender == "女性") %>% count()`F), with mean age = `r round(df.age_gender_M_summ$mean_age, 2)` (SD = `r round(df.age_gender_M_summ$sd_age, 2)`) and median age = `r df.age_gender_M_summ$median_age`.
-
-Notably, we lost a majority of our Vietnam participants (more than 60%) in the attention check exclusion.
-One reason we suspect why this might have happened is because our Vietnam participants are less familiar with research surveys and attention check questions, and thus might have thought too much about the attention check questions.
-We carried out an exploratory analysis where we used a less stringent attention check exclusion (covered in the final part of the Results & Analysis section).
-To preview our findings for this analysis, we did not find any difference in significant results when compared with the main analysis.
-
-## Stimuli
-We adapted stimuli from previous studies to create a set of test triads consisting of a cue, with one thematic and one taxonomic match option.
-For example, “cow,” “grass,” and “chicken,” where “cow” is the cue, “grass” is the thematic match, and “chicken” the taxonomic match.
-We included 105 such triads, a superset including triads pulled from supplemental information and in-text examples across the literature, and others that we adapted or created (see SI for the full list of stimuli and sources).
-We selected triads on the basis of cultural familiarity in the US, Vietnam, and China.
-The triads were originally in English; they were translated to Vietnamese and Mandarin by a fluent bilingual speaker in each language.
-The translations were then checked for accuracy after backtranslation to English by another fluent bilingual in each language who was naive to the original English versions.
-
-Each participant completed all 105 triads in sets of 21 trials at a time (10 test triads, 10 filler triads, and 1 attention check per page), by selecting the match most related to the cue (“Which thing is most closely related to the bolded item?” or "Thu nào liên quan nhat voi thu đuoc in đam?").
-The test triads were presented with 105 filler triads mixed in, to obscure the taxonomic-thematic two-answer forced choice structure of the test stimuli and reduce the likelihood that participants would become aware of the design.
-The filler triads were groups of three semantically related words, but where the match options were not distinguished by thematic vs.
-taxonomic similarity, e.g., cue “bird” with match options “lizard” and “toad.” Additionally, we included 10 attention check trials, which were formatted like the test and filler triads but included an instruction instead of a cue item, e.g., “Choose wife” with match options “wife” and “husband.” In total, each participant completed 210 similarity judgments and 10 attention check questions, with triads presented in randomized orders that varied between subjects.
-
-## Corpus model 
-Our general approach is to build a model of similarity that is based on collocation counts in each language.
-
-### Raw lexical co-occurrences
-To give an intuition for our model, consider the cow-grass-chicken triad: we counted how many times “cow” and “grass” co-occur within a window of text in each corpus, and compare this to how many times “cow” and “chicken” co-occur.
-Our similarity prediction is then proportional to the relative frequency of these pairs.
-For example, if the thematic cow-grass match accounts for 30% of collocations for this triad (with cow-chicken making up the other 70%), then our model predicts, correspondingly, that 30% of responses to the triad will be grass, and the other 70% chicken.
-We then use a mixed-effects regression to evaluate how well each corpus collocate model predicts participants’ similarity judgments, across triads and languages.
-
-#### Collocate retrieval and coding
-For our English co-occurrence metric, we used the online interface of the Corpus of Contemporary American English [@COCA] to retrieve collocation counts.
-We recorded the raw count of times that any cue-match pair (e.g., cow-grass or cow-chicken) co-occur in a window of 19 words, which is the maximum window size in the online interface, and closest to the sentence co-occurrence metric in our VI corpus collocation counts.
-
-To determine Vietnamese co-occurrence, we used the raw frequency of sentence co-occurrences from a subset of the Vietnamese corpus in the Leipzig Corpora Collection [@VICorpus]; this corpus includes 70 million Vietnamese sentences, but our corpus data comes from a 1 million sentence subset for which co-occurrence counts are available for download.
-Vietnamese makes very frequent use of compositional morphology but the written language  uses spacing to delineate syllable boundaries rather than word boundaries.
-Accordingly, collocate searches returned instances of both target terms and many morphologically related, but distinct, words.
-We included in our counts any instances of the target term or close semantic neighbors containing the same morpheme(s) as long as they entailed a likely literal reference to the target term.
-For example, our search for collocates of the term “gà” (chicken) also returned “gà mái,” a distinct word for female chickens.
-Despite being a different word, “gà mái” both includes the morpheme for “chicken” and entails reference to a chicken.
-Accordingly, instances of both “gà” and “gà mái” were included in our collocate count for “chicken.” Some compounds do not meet this criteria, and were excluded from collocate counts.
-For example “trái cây” (tree.fruits) includes the same syllable as the word “cây” (tree), but refers to fruit that comes from trees, not the trees themselves, and was therefore excluded from our collocate counts for “tree.”
-
-We were unable to obtain a Mandarin corpus with similar number of sentences as the aforementioned English and Vietnamese corpora, hence we did not include any analysis based on raw lexical co-occurrences with Mandarin.
-
-#### Collocate similarity model
-From the raw co-occurrence counts of each triad, we calculated the thematic co-occurrence ratio as the number of thematic co-occurrences over the sum of thematic and taxonomic co-occurrences.
-We did this for both the English and Vietnamese corpus co-occurrence counts.
-In this way, we obtained predictions for 73 of 105 triads from the Vietnamese corpus and 104 of 105 triads from English.
-We therefore limited all analyses reported here to the subset of triads for which our corpus-based model can make meaningful predictions, meaning triads that have at least one non-zero collocate count (either thematic or taxonomic match).
-We replaced any remaining zero collocate counts with $\epsilon$ to account for sparsity in the corpus data.
-We then tested whether these simple relative frequency models predict US and VN responding.
-
-### Cosine distance of word vectors
-To give an intuition for our model, consider again the cow-grass-chicken triad: we retrieved word vectors for "cow" and "grass", and calculate the cosine distance between these vectors.
-Similarly, we retrieved vectors for "cow" and "chicken" and calculate the cosine distance between them.
-Our similarity prediction is then inversely proportional to the cosine distance of these pairs.
-This is because a larger cosine distance means the word vectors are further apart, and thus the words are less similar.
-For example, if the cosine distance of thematic cow-grass is 0.7 and the cosine distance of taxonomic cow-chicken is 0.3, then our model predicts, correspondingly, that 30% of responses to the triad will be grass, and the other 70% chicken.
-We then use a mixed-effects regression to evaluate how well each corpus model predicts participants’ similarity judgments, across triads and languages.
-
-#### Collocate retrieval
-We use the fastText pre-trained models of English, Mandarin, and Vietnamese in @Grave2018.
-These models are trained on Common Crawl and Wikipedia using We distribute pre-trained word vectors for 157 languages, trained on Common Crawl and Wikipedia using fastText.
-These models were trained using a Continuous Bag of Words (CBOW) with position-weights and a window of size 5.
-The models use character n-grams of length 5 and 10  negative examples.From the aforementioned models, we retrieve the word vectors (dimension 300) for each word we are interested in.
-
-#### Collocate similarity model
-From the word vectors, we calculated the cosine distance between each cue-thematic match (thematic cosine distance) and cue-taxonomic match (taxonomic cosine distance), using the spatial.distance.cosine function from the SciPy package [@2020SciPy].
-We then calculated the thematic cosine distance proportion as thematic cosine distance over the sum of taxonomic cosine distance and thematic cosine distance.
-We did this for all three corpora.
-We were able to obtain predictions for all triads in all languages.
-
-## Data analysis
-We used `r cite_r("r-references.bib")` for all our analyses.
-
-# Results
-```{r combine corpus and behavior data, include = F}
-#source("../2_combine/2_combine.Rmd")
-df <- read.csv("../../data/data_USCNVN_ENZHVI.csv")
-```
-
-## Do we extend previous work reporting a preference for taxonomic matching in the US and thematic matching in Asia?
-
-```{r warning=FALSE, include=FALSE, paged.print=TRUE}
-df.country <- df %>%
-  group_by(subject, country) %>%
-  summarize(theme_resp_percent = mean(responses_theme, na.rm = T))
-
-df.country_sum <- df.country %>%
-  group_by(country) %>%
-  summarize(mean_theme_resp_percent = mean(theme_resp_percent), 
-            sd_theme_resp_percent = sd(theme_resp_percent))
-
-fit.country = glmer(responses_theme ~ country + (1 | subject) + (country | triad), 
-                    data = df, 
-                    family = "binomial")
-summary(fit.country) 
-fit.country.anova = Anova(fit.country, type=3)
-
-fit.country_EN_VN = glmer(responses_theme ~ country + (1 | subject) + (country | triad), 
-                    data = df %>% filter(country != "China"),
-                    family = "binomial")
-summary(fit.country_EN_VN) 
-```
-The group means of proportion of thematic response in mainland China is the highest (M = `r round((df.country_sum %>% filter(country == "China"))$mean_theme_resp_percent, 2)`, SD = `r round((df.country_sum %>% filter(country == "China"))$sd_theme_resp_percent, 2)`), followed by the groups means in Vietnam (M = `r round((df.country_sum %>% filter(country == "Vietnam"))$mean_theme_resp_percent, 2)`, SD = `r round((df.country_sum %>% filter(country == "Vietnam"))$sd_theme_resp_percent, 2)`), which is slightly higher than that of the US (M = `r round((df.country_sum %>% filter(country == "US"))$mean_theme_resp_percent, 2)`, SD = `r round((df.country_sum %>% filter(country == "US"))$sd_theme_resp_percent, 2)`).
-
-```{r echo=FALSE, warning=FALSE, fig.cap="Proportion of thematic responses by country.
-Only US-China responding comparison shows a siginficant difference.
-We could not extend this to US-Vietnam responding comparison."}
-
-#show violin plot
-ggplot(df.country,
-       mapping = aes(x = factor(country, levels=c("China", "US", "Vietnam")), 
-                     y = theme_resp_percent, 
-                     color = factor(country, levels=c("China", "US", "Vietnam")))) +
-  geom_violin() +
-  geom_jitter(height = 0, 
-              alpha = 0.3) +  
-  stat_summary(fun.data = "mean_cl_boot", 
-               geom = "pointrange") + 
-  labs(y = "Proportion Thematic Chosen", 
-       x = "Country", 
-       color = "Country") + 
-  scale_color_manual(values=c("#D63230", "#1C77C3", "#F39237"))
-```
-
-```{r correlation of country response, echo=FALSE, warning=FALSE}
-#US-China, US-Vietnam, China-Vietnam
-df.triad_country <- df %>%
-  group_by(triad, country) %>%
-  summarize(emp_theme_prop = mean(responses_theme))
-
-df.triad_country <- pivot_wider(data = df.triad_country, 
-                                names_from = country, 
-                                values_from = emp_theme_prop)
-plotUSCN = ggplot(data = df.triad_country,
-                  mapping = aes(x = US, 
-                                y = China, 
-                                label = triad)) +
-   geom_text() + 
-   geom_smooth(method = "lm") +
-   labs(x = "Proportion Thematic Chosen (US)", 
-        y = "Proportion Thematic Chosen (China)") + 
-   xlim(0, 1) + 
-   ylim(0, 1) + 
-  theme(axis.title = element_text(size=rel(0.75)))
-
-plotUSVN = ggplot(data = df.triad_country,
-                  mapping = aes(x = US, 
-                                y = Vietnam, 
-                                label = triad)) +
-   geom_text() + 
-   geom_smooth(method = "lm") +
-   labs(x = "Proportion Thematic Chosen (US)", 
-        y = "Proportion Thematic Chosen (Vietnam)") + 
-   xlim(0, 1) + 
-   ylim(0, 1)  + 
-  theme(axis.title = element_text(size=rel(0.75)))
-
-plotCNVN = ggplot(data = df.triad_country,
-                  mapping = aes(x = Vietnam,
-                                y = China, 
-                                label = triad)) +
-   geom_text() + 
-   geom_smooth(method = "lm") +
-   labs(x = "Proportion Thematic Chosen (Vietnam)", 
-        y = "Proportion Thematic Chosen (China)") + 
-   xlim(0, 1) + 
-   ylim(0, 1)  + 
-  theme(axis.title = element_text(size=rel(0.75)))
-
-corr.USCN = apa_print(cor.test(df.triad_country$US, 
-                  df.triad_country$China, na.rm=T))
-
-corr.USVN = apa_print(cor.test(df.triad_country$US, 
-                  df.triad_country$Vietnam, na.rm=T))
-
-corr.CNVN = apa_print(cor.test(df.triad_country$China, 
-                  df.triad_country$Vietnam, na.rm=T))
-```
-
-```{r warning = F, fig.width = 8, fig.cap="Correlation between proportion thematic chosen by US-China participants, US-Vietnam participants, and China-Vietnam participants.
-All three comparisons show strong correlation, suggesting a strong signal of universality across cultural contexts regarding similarity judgments"}
-plotUSCN + plotUSVN + plotCNVN +
-  plot_layout(ncol = 3)
-```
-
-With a Pearson correlation test, we observed high correlations between thematic responding across all three countries.
-The proportion of US thematic responding is strongly correlated with thematic responding in China, `r corr.USCN$full_result`.
-The proportion of US thematic responding is strongly correlated with thematic responding in Vietnam, `r corr.USVN$full_result`.
-Likewise, the proportion of China thematic response is strongly correlated with thematic responding in Vietnam, `r corr.CNVN$full_result`.
-This points to a strong signal of universality across cultural contexts regarding similarity judgments.
-
-```{r USCN effect size comparison, include=FALSE}
-USCN_cohen <- cohen.d(df.triad_country$China, df.triad_country$US)
-```
-
-For comparison with previous work, we also included an effect size comparison for the difference in US-China thematic response data (though this was not a planned analysis).
-The effect size for this analysis was d = `r USCN_cohen$estimate`, a small effect size.
-This is smaller than the effect size from @Ji2004, even when we are unable to make a direct comparison.
-Calculating the effect size from the ANOVA reported in @Ji2004 between US participants tested in English and mainland China participants tested in English (both groups tested in the US) yields a Cohen's d = 0.81.
-@Ji2004 reported that mean thematic response for mainland China participants tested in Mandarin Chinese is higher than for those tested in English, so the effect size for a comparison between mainland China participants tested in Mandarin Chinese and US participants tested in English (parallel to our comparison) would likely have yielded an even larger effect size than 0.814.
-It is possible that we failed to replicate the magnitude of effect from @Ji2004 because the previous study calculated their dependent variable as frequency of thematic responses minus frequency of taxonomic responses, whereas our dependent variable is proportion of thematic response over total number of responses.
-
-To test for cross-context differences in similarity judgments between the countries, we ran a mixed-effects logistic regression predicting triad responding (taxonomic or thematic) with country (US, China, or Vietnam) as a fixed effect.
-As random effects, we included an intercept per subject and one per triad, as well as by-triad random slopes for country to account for variation in the country effect across triads.
-In R syntax, the model is: response ~ country + (1 | subject) + (country | triad).
-
-Overall, there is a significant effect of country on proportion of thematic responses ($\chi^2$(`r fit.country.anova["country", "Df"]`) = `r round(fit.country.anova["country", "Chisq"], 2)`, p < .001).
-However, this effect is driven by the difference between US and China responding ($\beta$ = `r round(fixef(fit.country)["countryUS"], 2)`, p < .001).
-There is no statistical difference between the Vietnam and China responding ($\beta$ = `r round(fixef(fit.country)["countryVietnam"], 2)`, p = `r round(as.data.frame(summary(fit.country)[["coefficients"]])["countryVietnam", "Pr(>|z|)"], 2)`), and the US and Vietnam responding ($\beta$ = `r round(fixef(fit.country_EN_VN)["countryVietnam"], 2)`, p = `r round(as.data.frame(summary(fit.country_EN_VN)[["coefficients"]])["countryVietnam", "Pr(>|z|)"], 3)`).
-
-On this analysis, we do not find support that the US-China tendencies toward taxonomic and thematic responding (respectively) extend to the US-Vietnam comparison.
-Accordingly, we cannot speak to overall biases toward thematic responding across Asian cultural contexts broadly, but we do replicate the differences documented by @Ji2004 between the US and China.
-However, in our corpus model comparison, we do find evidence for different, more fine-grained variation in similarity judgments between the US and Vietnam.
-
-## Can the differences in similarity judgments between English, Mandarin and Vietnamese speakers be explained by variation in lexical statistics?
-### Is responding in each cultural context predicted by the corresponding lexical statistics (raw co-occurrences and cosine distance)? 
-```{r Pearson correlation between raw co-occurrences of corpora and responding, warning=FALSE, include=FALSE}
-
-#raw co-occurrences
-df.triad_country_freq <- df %>%
-  filter(!(triad %in% triads_omit)) %>% # omit triads that do not have meaningful prediction (at least 1 non-zero prediction in both languages)
-  group_by(triad, country, theme_freq_prop_E, theme_freq_prop_V, theme_freq_prop_M) %>%  # not working 
-  summarize(emp_theme_prop = mean(responses_theme))
-df.triad_country_freq   #sanity
-
-df.triad_country_freq_E <- df.triad_country_freq %>%
-  filter(country == "US")
-
-#plotting English corpus against US responding data
-plotE = ggplot(data = df.triad_country_freq_E,
-        mapping = aes(x = emp_theme_prop,
-                     y = theme_freq_prop_E,
-                     label = triad)) +
-   geom_text() +
-   geom_smooth(method = "lm") +
-   labs(x = "Proportion Thematic Chosen (US)",
-        y = "Proportion Thematic Predicted (English)")
-plotE
-
-df.triad_country_freq_V <- df.triad_country_freq %>%
-  filter(country == "Vietnam")
-
-#plotting Vietnamese corpus against VN responding data
-plotV = ggplot(data = df.triad_country_freq_V,
-        mapping = aes(x = emp_theme_prop,
-                     y = theme_freq_prop_V,
-                     label = triad)) +
-   geom_text() +
-   geom_smooth(method = "lm") +
-   labs(x = "Proportion Thematic Chosen (Vietnam)",
-        y = "Proportion Thematic Predicted (Vietnamese)")
-plotV
-
-df.triad_country_freq_M <- df.triad_country_freq %>%
-  filter(country == "China")
-
-#plotting China corpus against CN responding data
-plotM = ggplot(data = df.triad_country_freq_M,
-        mapping = aes(x = emp_theme_prop,
-                     y = theme_freq_prop_M,
-                     label = triad)) +
-   geom_text() +
-   geom_smooth(method = "lm") +
-   labs(x = "Proportion Thematic Chosen (China)",
-        y = "Proportion Thematic Predicted (Chinese)")
-plotM
-
-#Pearson correlation between corpus and responding
-corr.E = apa_print(cor.test(df.triad_country_freq_E$emp_theme_prop,
-                  df.triad_country_freq_E$theme_freq_prop_E, na.rm=T))
-corr.E
-
-corr.V = apa_print(cor.test(df.triad_country_freq_V$emp_theme_prop,
-                  df.triad_country_freq_V$theme_freq_prop_V, na.rm=T))
-corr.V
-
-corr.M = apa_print(cor.test(df.triad_country_freq_M$emp_theme_prop,
-                  df.triad_country_freq_M$theme_freq_prop_M, na.rm=T))
-corr.M
-
-#Pearson correlation between EN and VI corpus
-corr.EV = apa_print(cor.test(df.triad_country_freq_V$theme_freq_prop_V,
-                   df.triad_country_freq_E$theme_freq_prop_E, na.rm=T))
-corr.EM = apa_print(cor.test(df.triad_country_freq_M$theme_freq_prop_M,
-                   df.triad_country_freq_E$theme_freq_prop_E, na.rm=T))
-corr.MV = apa_print(cor.test(df.triad_country_freq_V$theme_freq_prop_V,
-                   df.triad_country_freq_M$theme_freq_prop_M, na.rm=T))
-```
-
-```{r echo=FALSE, paged.print=FALSE, fig.cap ="Correlation between English corpus lexical co-occurrence and US responding, and Vietnamese corpus lexical co-occurrence and Vietnam responding."}
-plotE + plotV + plotM
-  plot_layout(ncol = 3)
-```
-
-We first conducted a Pearson correlation test between corresponding response data and corpus data.
-Looking at the raw lexical co-occurrence data, proportion of US thematic responding is moderately correlated to English corpus thematic proportion, `r corr.E$full_result`.
-Proportion of Vietnam thematic responding is moderately correlated to Vietnamese corpus thematic proportion, `r corr.V$full_result`.
-Proportion of China thematic responding is moderately correlated to Chinese corpus thematic proportion, `r corr.M$full_result`.
-There was a strong similarity signal between the thematic proportions in the English and Vietnamese corpora, `r corr.EV$full_result`, and the thematic proportions in the English and Mandarin corpora, `r corr.EM$full_result`.
-There was a moderate similarity signal between the proportions in the Mandarin and Vietnamese corpora, `r corr.MV$full_result.`
-
-```{r Pearson correlation between corpus cosine distance and responding, warning=FALSE, include=FALSE}
-df.triad_country_cos <- df %>%
-  group_by(triad, country, theme_cosine_prop_E, theme_cosine_prop_V, theme_cosine_prop_M) %>%
-  summarize(emp_theme_prop = mean(responses_theme))
-
-df.triad_country_cos_E <- df.triad_country_cos %>%
-  filter(country == "US")
-
-plotE = ggplot(data = df.triad_country_cos_E, 
-        mapping = aes(x = emp_theme_prop, 
-                     y = theme_cosine_prop_E,
-                     label = triad)) +
-   geom_text() + 
-   geom_smooth(method = "lm") +
-   labs(x = "Proportion Thematic Chosen (US)", 
-        y = "Proportion Thematic Predicted (English)") + 
-   scale_y_reverse() + 
-   xlim(0, 1) +
-   ylim(0.8, 0.2) + 
-  theme(axis.title = element_text(size=rel(0.75)))
-
-df.triad_country_cos_V <- df.triad_country_cos %>%
-  filter(country == "Vietnam")
-
-plotV = ggplot(data = df.triad_country_cos_V, 
-        mapping = aes(x = emp_theme_prop, 
-                     y = theme_cosine_prop_V, 
-                     label = triad)) +
-   geom_text() + 
-   geom_smooth(method = "lm") +
-   labs(x = "Proportion Thematic Chosen (Vietnam)", 
-        y = "Proportion Thematic Predicted (Vietnamese)") + 
-   scale_y_reverse() +
-   xlim(0, 1) +
-   ylim(0.8, 0.2) + 
-  theme(axis.title = element_text(size=rel(0.75)))
-
-df.triad_country_cos_M <- df.triad_country_cos %>%
-  filter(country == "China")
-
-plotM = ggplot(data = df.triad_country_cos_M, 
-        mapping = aes(x = emp_theme_prop, 
-                     y = theme_cosine_prop_M, 
-                     label = triad)) +
-   geom_text() + 
-   geom_smooth(method = "lm") +
-   labs(x = "Proportion Thematic Chosen (China)", 
-        y = "Proportion Thematic Predicted (Mandarin)") + 
-   xlim(0, 1) +
-   ylim(0.8, 0.2) + 
-  theme(axis.title = element_text(size=rel(0.75)))
-
-corr.E_cos = apa_print(cor.test(df.triad_country_cos_E$emp_theme_prop,
-                      df.triad_country_cos_E$theme_cosine_prop_E, na.rm=T))
-
-corr.V_cos = apa_print(cor.test(df.triad_country_cos_V$emp_theme_prop,
-                      df.triad_country_cos_V$theme_cosine_prop_V, na.rm=T))
-
-corr.M_cos = apa_print(cor.test(df.triad_country_cos_M$emp_theme_prop,
-                      df.triad_country_cos_M$theme_cosine_prop_M, na.rm=T))
-
-#correlation between corpora
-corr.EV_cos = apa_print(cor.test(df.triad_country_cos_E$theme_cosine_prop_E,
-                       df.triad_country_cos_V$theme_cosine_prop_V, na.rm=T))
-
-corr.EM_cos = apa_print(cor.test(df.triad_country_cos_E$theme_cosine_prop_E,
-                      df.triad_country_cos_M$theme_cosine_prop_M, na.rm=T))
-
-corr.VM_cos = apa_print(cor.test(df.triad_country_cos_V$theme_cosine_prop_V,
-                      df.triad_country_cos_M$theme_cosine_prop_M, na.rm=T))
-```
-
-```{r warning = FALSE, echo=FALSE, fig.width = 8, fig.cap="Correlation between English corpus cosine distance and US responding; Vietnamese corpus cosine distance and Vietnam responding; and Mandarin corpus cosine distance and China responding."}
-#maybe we should include a note that explains why they are correlate in the opposite direction? 
-#either changing the label of y-axis, or use y = 1/theme_cosine_prop_V? 
-plotE + plotV + plotM +
-  plot_layout(ncol = 3)
-```
-
-```{r US-Mandarin, China-English cross correlation, NOT SHOWN, eval=FALSE, warning=FALSE, include=FALSE}
-plotUSZH = ggplot(data = df.triad_country_cos_E, 
-        mapping = aes(x = emp_theme_prop, 
-                     y = theme_cosine_prop_M,
-                     label = triad)) +
-   geom_text() + 
-   geom_smooth(method = "lm") +
-   labs(x = "Proportion Thematic Chosen (US)", 
-        y = "Proportion Thematic Predicted (Mandarin)") + 
-   scale_y_reverse() + 
-   xlim(0, 1) +
-   ylim(0.8, 0.3)
-
-plotCNEN = ggplot(data = df.triad_country_cos_M, 
-        mapping = aes(x = emp_theme_prop, 
-                     y = theme_cosine_prop_E,
-                     label = triad)) +
-   geom_text() + 
-   geom_smooth(method = "lm") +
-   labs(x = "Proportion Thematic Chosen (China)", 
-        y = "Proportion Thematic Predicted (English)") + 
-   scale_y_reverse() + 
-   xlim(0, 1) +
-   ylim(0.8, 0.3)
-
-plotUSZH + plotCNEN +
-  plot_layout(ncol = 2)
-```
-
-Looking at the cosine distance data using fastText word vectors, proportion of US thematic responding is moderately correlated to English thematic cosine distance proportion, `r corr.E_cos$full_result`.
-There is a small correlation between proportion of Vietnam thematic responding and the Vietnamese thematic cosine distance proportion, `r corr.V_cos$full_result`.
-Proportion of China thematic responding is moderately correlated to Mandarin thematic match cosine distance proportion, `r corr.M_cos$full_result`.
-There were moderate signals of similarity between English and Mandarin (`r corr.EM_cos$full_result`).
-There was no significant correlation between English and Vietnamese (`r corr.EV_cos$full_result`), and between Vietnamese and Mandarin (`r corr.VM_cos$full_result`).
-
-To test whether variation in lexical co-occurrence can explain differences in similarity judgments between US and Vietnam participants, we compare logistic mixed-effects regression models fit to the thematic responding data from each country separately.
-We first ask how well each corpus model (English, Vietnamese, or Mandarin) predicts similarity judgments by speakers of the corresponding language (US, Vietnam, or China).
-To do this, we use a mixed-effects logistic regression to predict triad responses (0=taxonomic or 1=thematic) with corpus prediction (proportion thematic co-occurrence or cosine distance) as a fixed effect and participant and triad as random effects.
-
-#### Raw lexical co-occurrences
-
-```{r US responding predicted by each corpus model raw co-occurrences, warning=FALSE, include=F}
-# English 
-fit.EN_US = glmer(responses_theme ~ theme_freq_prop_E + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "US", !(triad %in% triads_omit)), 
-          family="binomial")
-summary(fit.EN_US)
-fit.EN_US.anova = Anova(fit.EN_US, type = 3)
-
-#Vietnamese
-fit.VI_US = glmer(responses_theme ~ theme_freq_prop_V + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "US", !(triad %in% triads_omit)), 
-          family="binomial")
-summary(fit.VI_US)
-fit.VI_US.anova = Anova(fit.VI_US, type = 3)
-
-#Mandarin
-fit.ZH_US = glmer(responses_theme ~ theme_freq_prop_M + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "US", !(triad %in% triads_omit)), 
-          family="binomial")
-summary(fit.ZH_US)
-fit.ZH_US.anova = Anova(fit.ZH_US, type = 3)
-```
-
-```{r VN responding predicted by each corpus model raw co-occurrences, warning=FALSE, include=F}
-# English 
-fit.EN_VN = glmer(responses_theme ~ theme_freq_prop_E + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "Vietnam", !(triad %in% triads_omit)), 
-          family="binomial")
-summary(fit.EN_VN)
-fit.EN_VN.anova = Anova(fit.EN_VN, type = 3)
-
-#Vietnamese
-fit.VI_VN = glmer(responses_theme ~ theme_freq_prop_V + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "Vietnam", !(triad %in% triads_omit)), 
-          family="binomial")
-summary(fit.VI_VN)
-fit.VI_VN.anova = Anova(fit.VI_VN, type = 3)
-
-#Mandarin
-fit.ZH_VN = glmer(responses_theme ~ theme_freq_prop_M + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "Vietnam", !(triad %in% triads_omit)), 
-          family="binomial")
-summary(fit.ZH_VN)
-fit.ZH_VN.anova = Anova(fit.ZH_VN, type = 3)
-```
-
-```{r CN responding predicted by each corpus model raw co-occurrences, warning=FALSE, include=F}
-#English
-fit.EN_CN = glmer(responses_theme ~ theme_freq_prop_E + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "China", !(triad %in% triads_omit)), 
-          family="binomial")
-summary(fit.EN_CN)
-fit.EN_CN.anova = Anova(fit.EN_CN, type = 3)
-
-#Vietnamese
-fit.VI_CN = glmer(responses_theme ~ theme_freq_prop_V + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "China", !(triad %in% triads_omit)), 
-          family="binomial")
-summary(fit.VI_CN)
-fit.VI_CN.anova = Anova(fit.VI_CN, type = 3)
-
-#Mandarin
-fit.ZH_CN = glmer(responses_theme ~ theme_freq_prop_M + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "China", !(triad %in% triads_omit)), 
-          family="binomial")
-summary(fit.ZH_CN)
-fit.ZH_CN.anova = Anova(fit.ZH_CN, type = 3)
-```
-
-TODO: ADD CHINA RESULTS
-Both the English (EN) and Vietnamese (VI) corpus are significant predictors of US responding (EN-US model: $\beta$ = `r round(fixef(fit.EN_US)["theme_freq_prop_E"], 2)`, $\chi^2$(`r fit.EN_US.anova["theme_freq_prop_E", "Df"]`) = `r round(fit.EN_US.anova["theme_freq_prop_E", "Chisq"], 2)`, p < .001; VI-US model: $\beta$ = `r round(fixef(fit.VI_US)["theme_freq_prop_V"], 2)`, $\chi^2$(`r fit.VI_US.anova["theme_freq_prop_V", "Df"]`) = `r round(fit.VI_US.anova["theme_freq_prop_V", "Chisq"], 2)`, p < .001).
-
-Similarly, both the English (EN) and Vietnamese (VI) corpus are significant predictors of Vietnam (VN) responding (EN-VN model: $\beta$ = `r round(fixef(fit.EN_VN)["theme_freq_prop_E"], 2)`, $\chi^2$(`r fit.EN_VN.anova["theme_freq_prop_E", "Df"]`) = `r round(fit.EN_VN.anova["theme_freq_prop_E", "Chisq"], 2)`, p < .001; VI-VN model: $\beta$ = `r round(fixef(fit.VI_VN)["theme_freq_prop_V"], 2)`, $\chi^2$(`r fit.VI_VN.anova["theme_freq_prop_V", "Df"]`) = `r round(fit.VI_VN.anova["theme_freq_prop_V", "Chisq"], 2)`, p < .001).
-
-This suggests a strong shared similarity signal across the languages, which is also reflected in the strong correlation between the two corpus models reported above (`r corr.EV$full_result`).
-
-#### Cosine distances of fastText word vectors
-```{r US responding predicted by each corpus model cosine differences, warning=FALSE, include=F}
-#English
-fit.EN_US_cos = glmer(responses_theme ~ theme_cosine_prop_E + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "US"), 
-          family="binomial")
-summary(fit.EN_US_cos)
-fit.EN_US_cos.anova = Anova(fit.EN_US_cos, type = 3)
-fit.EN_US_cos.anova
-
-#Vietnamese
-fit.VI_US_cos = glmer(responses_theme ~ theme_cosine_prop_V + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "US"), 
-          family="binomial")
-summary(fit.VI_US_cos)
-fit.VI_US_cos.anova = Anova(fit.VI_US_cos, type = 3)
-fit.VI_US_cos.anova
-
-#Mandarin
-fit.ZH_US_cos = glmer(responses_theme ~ theme_cosine_prop_M + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "US"), 
-          family="binomial")
-summary(fit.ZH_US_cos)
-fit.ZH_US_cos.anova = Anova(fit.ZH_US_cos, type = 3)
-fit.ZH_US_cos.anova
-```
-
-```{r VN responding predicted by each corpus model cosine differences, warning=FALSE, include=F}
-#English
-fit.EN_VN_cos = glmer(responses_theme ~ theme_cosine_prop_E + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "Vietnam"), 
-          family="binomial")
-summary(fit.EN_VN_cos)
-fit.EN_VN_cos.anova = Anova(fit.EN_VN_cos, type = 3)
-fit.EN_VN_cos.anova
-
-#Vietnamese
-fit.VI_VN_cos = glmer(responses_theme ~ theme_cosine_prop_V + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "Vietnam"), 
-          family="binomial")
-summary(fit.VI_VN_cos)
-fit.VI_VN_cos.anova = Anova(fit.VI_VN_cos, type = 3)
-fit.VI_VN_cos.anova
-
-#Mandarin
-fit.ZH_VN_cos = glmer(responses_theme ~ theme_cosine_prop_M + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "Vietnam"), 
-          family="binomial")
-summary(fit.ZH_VN_cos)
-fit.ZH_VN_cos.anova = Anova(fit.ZH_VN_cos, type = 3)
-fit.ZH_VN_cos.anova
-```
-
-```{r CN responding predicted by each corpus model cosine differences, warning=FALSE, include=F}
-## English
-fit.EN_CN_cos = glmer(responses_theme ~ theme_cosine_prop_E + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "China"), 
-          family="binomial")
-summary(fit.EN_CN_cos)
-fit.EN_CN_cos.anova = Anova(fit.EN_CN_cos, type = 3)
-fit.EN_CN_cos.anova
-
-#Vietnamese
-fit.VI_CN_cos = glmer(responses_theme ~ theme_cosine_prop_V + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "China"), 
-          family="binomial")
-summary(fit.VI_CN_cos)
-fit.VI_CN_cos.anova = Anova(fit.VI_CN_cos, type = 3)
-fit.VI_CN_cos.anova
-
-#Mandarin
-fit.ZH_CN_cos = glmer(responses_theme ~ theme_cosine_prop_M + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "China"), 
-          family="binomial")
-summary(fit.ZH_CN_cos)
-fit.ZH_CN_cos.anova = Anova(fit.ZH_CN_cos, type = 3)
-fit.ZH_CN_cos.anova
-```
-
-Similar to the results from the analysis with raw lexical co-occurrences, we found that all corpora are significant predictors of all cultural context responding.
-
-For US responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are significant predictors of US responding (EN-US model: $\beta$ = `r round(fixef(fit.EN_US_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.EN_US_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.EN_US_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p < .001; VI-US model: $\beta$ = `r round(fixef(fit.VI_US_cos)["theme_cosine_prop_V"], 2)`, $\chi^2$(`r fit.VI_US_cos.anova["theme_cosine_prop_V", "Df"]`) = `r round(fit.VI_US_cos.anova["theme_cosine_prop_V", "Chisq"], 2)`, p = `r round(fit.VI_US_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"], 3)`; ZH-US model: $\beta$ = `r round(fixef(fit.ZH_US_cos)["theme_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ZH_US_cos.anova["theme_cosine_prop_M", "Df"]`) = `r round(fit.ZH_US_cos.anova["theme_cosine_prop_M", "Chisq"], 2)`, p < .001).
-
-For Vietnam (VN) responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are significant predictors of VN responding (EN-VN model: $\beta$ = `r round(fixef(fit.EN_VN_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.EN_VN_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.EN_VN_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p < .001; VI-VN model: $\beta$ = `r round(fixef(fit.VI_VN_cos)["theme_cosine_prop_V"], 2)`, $\chi^2$(`r fit.VI_VN_cos.anova["theme_cosine_prop_V", "Df"]`) = `r round(fit.VI_VN_cos.anova["theme_cosine_prop_V", "Chisq"], 2)`, p = `r round(fit.VI_VN_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"], 3)`; ZH-VN model: $\beta$ = `r round(fixef(fit.ZH_VN_cos)["theme_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ZH_VN_cos.anova["theme_cosine_prop_M", "Df"]`) = `r round(fit.ZH_VN_cos.anova["theme_cosine_prop_M", "Chisq"], 2)`, p < .001).
-
-For China (CN) responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are significant predictors of CN responding (EN-CN model: $\beta$ = `r round(fixef(fit.EN_CN_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.EN_CN_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.EN_CN_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p < .001; VI-CN model: $\beta$ = `r round(fixef(fit.VI_CN_cos)["theme_cosine_prop_V"], 2)`, $\chi^2$(`r fit.VI_CN_cos.anova["theme_cosine_prop_V", "Df"]`) = `r round(fit.VI_CN_cos.anova["theme_cosine_prop_V", "Chisq"], 2)`, p = `r round(fit.VI_VN_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"], 3)`; ZH-CN model: $\beta$ = `r round(fixef(fit.ZH_CN_cos)["theme_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ZH_CN_cos.anova["theme_cosine_prop_M", "Df"]`) = `r round(fit.ZH_CN_cos.anova["theme_cosine_prop_M", "Chisq"], 2)`, p < .001).
-
-### Is responding in each cultural context __best__ predicted by the corresponding corpus's lexical statistics (raw co-occurrences and cosine distance), as opposed to the other two corpora?
-Next, we directly compare the corpus models by including both as fixed effects in two mixed-effect regressions (predicting US and Vietnam responding) with the same random effects as above.
-In R syntax, the model is: response ~ corpus_English + corpus_Vietnamese + corpus_Mandarin + (1|triad) + (1|subject).
-
-#### Raw co-occurrences 
-```{r MIGHT NEED TO REMOVEEnglish + Vietnamese raw co-occurrences predicting US and Vietnam, warning=FALSE, include=F}
-## English/Vietnamese comparison
-fit.ENVI_US = glmer(responses_theme ~ theme_freq_prop_E + theme_freq_prop_V + 
-                      (1 | subject) + (1 | triad), 
-                    data = df %>% filter(country == "US"), 
-                    family="binomial")
-summary(fit.ENVI_US)
-fit.ENVI_US.anova = Anova(fit.ENVI_US, type = 3)
-fit.ENVI_US.anova
-
-fit.ENVI_VN = glmer(responses_theme ~ theme_freq_prop_V + theme_freq_prop_E + 
-                      (1 | subject) + (1 | triad), 
-                    data = df %>% filter(country == "Vietnam"), 
-                    family="binomial")
-summary(fit.ENVI_VN)
-fit.ENVI_VN.anova = Anova(fit.ENVI_VN, type = 3)
-fit.ENVI_VN.anova
-```
-When we included both corpora as predictors for US responding, only the English corpus has a significant effect ($\beta$ = `r round(fixef(fit.ENVI_US)["theme_freq_prop_E"], 2)`, $\chi^2$(`r fit.ENVI_US.anova["theme_freq_prop_E", "Df"]`) = `r round(fit.ENVI_US.anova["theme_freq_prop_E", "Chisq"], 2)`, p < .001).
-There is no effect of the Vietnamese corpus ($\beta$ = `r round(fixef(fit.ENVI_US)["theme_freq_prop_V"], 2)`, $\chi^2$(`r fit.ENVI_US.anova["theme_freq_prop_V", "Df"]`) = `r round(fit.ENVI_US.anova["theme_freq_prop_V", "Chisq"], 2)`, p = `r round(fit.ENVI_US.anova["theme_freq_prop_V", "Pr(>Chisq)"], 3)`).
-
-However, when both corpora are included as predictors for Vietnam responding -- both corpora has a significant effect (English corpus: $\beta$ = `r round(fixef(fit.ENVI_VN)["theme_freq_prop_E"], 2)`, $\chi^2$(`r fit.ENVI_VN.anova["theme_freq_prop_E", "Df"]`) = `r round(fit.ENVI_VN.anova["theme_freq_prop_E", "Chisq"], 2)`, p = `r round(fit.ENVI_VN.anova["theme_freq_prop_E", "Pr(>Chisq)"], 3)`; Vietnamese corpus: $\beta$ = `r round(fixef(fit.ENVI_VN)["theme_freq_prop_V"], 2)`, $\chi^2$(`r fit.ENVI_VN.anova["theme_freq_prop_V", "Df"]`) = `r round(fit.ENVI_VN.anova["theme_freq_prop_V", "Chisq"], 2)`, p = `r round(fit.ENVI_VN.anova["theme_freq_prop_V", "Pr(>Chisq)"], 3)`).
-
-```{r Eng-Vie-Mand lexical co-occ predicting US, VN, CN, warning=FALSE, include=F}
-# ADDITION: adding theme_freq_prop_M
-#raw co-occurrences
-#linear mixed model with ALL corpora as predictors for each population.
-fit.ENVIZH_US = glmer(responses_theme ~ 
-                      theme_freq_prop_E + theme_freq_prop_V + theme_freq_prop_M +
-                      (1 | subject) + (1 | triad), 
-                    data = df %>% filter(country == "US", !(triad %in% triads_omit)),
-                    family="binomial")
-summary(fit.ENVIZH_US)
-fit.ENVIZH_US.anova = Anova(fit.ENVIZH_US, type = 3)
-fit.ENVIZH_US.anova
-
-fit.ENVIZH_VN = glmer(responses_theme ~ 
-                      theme_freq_prop_V + theme_freq_prop_E + theme_freq_prop_M +
-                      (1 | subject) + (1 | triad), 
-                    data = df %>% filter(country == "Vietnam", !(triad %in% triads_omit)),
-                    family="binomial")
-summary(fit.ENVIZH_VN)
-fit.ENVIZH_VN.anova = Anova(fit.ENVIZH_VN, type = 3)
-fit.ENVIZH_VN.anova
-
-fit.ENVIZH_CN = glmer(responses_theme ~ 
-                      theme_freq_prop_V + theme_freq_prop_E + theme_freq_prop_M +
-                      (1 | subject) + (1 | triad), 
-                    data = df %>% filter(country == "China", !(triad %in% triads_omit)),
-                    family="binomial")
-summary(fit.ENVIZH_CN)
-fit.ENVIZH_CN.anova = Anova(fit.ENVIZH_CN, type = 3)
-fit.ENVIZH_CN.anova
-```
-TODO: ADD WRITE-UP OF RESULTS
-
-```{r echo=FALSE, warning = FALSE, fig.cap = "Fixed effect sizes of each corpus when included as a predictor for China, US, and Vietnam responding, respectively.
-The English corpus is the best predictor for US response, and the Mandarin corpus is the best predictor for China response."}
-coeff_value_freq <- c(fixef(fit.ENVIZH_US)["theme_freq_prop_E"],
-                 fixef(fit.ENVIZH_US)["theme_freq_prop_V"], 
-                 fixef(fit.ENVIZH_US)["theme_freq_prop_M"],
-                 fixef(fit.ENVIZH_VN)["theme_freq_prop_E"],
-                 fixef(fit.ENVIZH_VN)["theme_freq_prop_V"],
-                 fixef(fit.ENVIZH_VN)["theme_freq_prop_M"], 
-                 fixef(fit.ENVIZH_CN)["theme_freq_prop_E"],
-                 fixef(fit.ENVIZH_CN)["theme_freq_prop_V"], 
-                 fixef(fit.ENVIZH_CN)["theme_freq_prop_M"])
-
-se_value_freq <- c(summary(fit.ENVIZH_US)$coef["theme_freq_prop_E", "Std. Error"], 
-              summary(fit.ENVIZH_US)$coef["theme_freq_prop_V", "Std. Error"],
-              summary(fit.ENVIZH_US)$coef["theme_freq_prop_M", "Std. Error"], 
-              summary(fit.ENVIZH_VN)$coef["theme_freq_prop_E", "Std. Error"], 
-              summary(fit.ENVIZH_VN)$coef["theme_freq_prop_V", "Std. Error"],
-              summary(fit.ENVIZH_VN)$coef["theme_freq_prop_M", "Std. Error"],
-              summary(fit.ENVIZH_CN)$coef["theme_freq_prop_E", "Std. Error"], 
-              summary(fit.ENVIZH_CN)$coef["theme_freq_prop_V", "Std. Error"],
-              summary(fit.ENVIZH_CN)$coef["theme_freq_prop_M", "Std. Error"])
-
-country_value <- c(rep("US", 3),
-                   rep("VN", 3),
-                   rep("CN", 3))
-
-corpus_value <- c(rep(c("EN", "VI", "ZH"), 3))
-
-df.USVNCN_coeffs_freq <- data.frame(country_value, corpus_value, coeff_value_freq, se_value_freq)
-
-ggplot(data = df.USVNCN_coeffs_freq, 
-       mapping = aes(x = country_value, y = coeff_value_freq, fill = corpus_value)) +
-  geom_bar(position="dodge", stat="identity") +
-  geom_errorbar(aes(ymin= coeff_value_freq - se_value_freq, ymax = coeff_value_freq + se_value_freq), width=.2,
-                 position=position_dodge(.9)) +
-  scale_y_reverse() + 
-  labs(x = "Country", y = "Fixed effect size", fill = "Corpus") + 
-  scale_x_discrete(labels=c("CN" = "China", "US" = "US", "VN" = "Vietnam")) + 
-  scale_fill_manual(values=c("#D63230", "#1C77C3", "#F39237"))
-
-```
-
-```{r model comparison, include=FALSE}
-fit.US_freq_compare = anova(fit.ENVIZH_US, fit.EN_US, type = 3)
-fit.VN_freq_compare = anova(fit.ENVIZH_VN, fit.VI_VN, type = 3)
-fit.CN_freq_compare = anova(fit.ENVIZH_CN, fit.ZH_CN, type = 3)
-```
-
-TODO: ADD WRITE-UP ON RESULTS
-
-#### Cosine distances of fastText word vectors
-
-```{r Eng-Vie-Mand cosine similarities predicting US, VN, CN warning=FALSE, include=FALSE}
-## English/Vietnamese/Mandarin comparison
-fit.ENVIZH_US_cos = glmer(responses_theme ~ theme_cosine_prop_E + theme_cosine_prop_V + theme_cosine_prop_M +
-                      (1 | subject) + (1 | triad), 
-                    data = df %>% filter(country == "US"), 
-                    family="binomial")
-summary(fit.ENVIZH_US_cos)
-fit.ENVIZH_US_cos.anova = Anova(fit.ENVIZH_US_cos, type = 3)
-fit.ENVIZH_US_cos.anova
-
-fit.ENVIZH_VN_cos = glmer(responses_theme ~ theme_cosine_prop_V + theme_cosine_prop_E + theme_cosine_prop_M +
-                      (1 | subject) + (1 | triad), 
-                    data = df %>% filter(country == "Vietnam"), 
-                    family="binomial")
-summary(fit.ENVIZH_VN_cos)
-fit.ENVIZH_VN_cos.anova = Anova(fit.ENVIZH_VN_cos, type = 3)
-fit.ENVIZH_VN_cos.anova
-
-fit.ENVIZH_CN_cos = glmer(responses_theme ~ theme_cosine_prop_M + theme_cosine_prop_E + theme_cosine_prop_V +
-                      (1 | subject) + (1 | triad), 
-                    data = df %>% filter(country == "China"), 
-                    family="binomial")
-summary(fit.ENVIZH_CN_cos)
-fit.ENVIZH_CN_cos.anova = Anova(fit.ENVIZH_CN_cos, type = 3)
-fit.ENVIZH_CN_cos.anova
-```
-
-When we included all corpora thematic cosine distance proportion as predictors, all corpora are significant in predicting all cultural context's responding.
-
-For US responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are all significant predictors.
-EN corpus: $\beta$ = `r round(fixef(fit.ENVIZH_US_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.ENVIZH_US_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.ENVIZH_US_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p < .001.
-VI corpus: $\beta$ = `r round(fixef(fit.ENVIZH_US_cos)["theme_cosine_prop_V"], 2)`, $\chi^2$(`r fit.ENVIZH_US_cos.anova["theme_cosine_prop_V", "Df"]`) = `r round(fit.ENVIZH_US_cos.anova["theme_cosine_prop_V", "Chisq"], 2)`, p = `r round(fit.ENVIZH_US_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"], 3)`.
-ZH corpus: $\beta$ = `r round(fixef(fit.ENVIZH_US_cos)["theme_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ENVIZH_US_cos.anova["theme_cosine_prop_M", "Df"]`) = `r round(fit.ENVIZH_US_cos.anova["theme_cosine_prop_M", "Chisq"], 2)`, p = `r round(fit.ENVIZH_US_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"], 3)`.
-
-For Vietnam responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are all significant predictors.
-EN corpus: $\beta$ = `r round(fixef(fit.ENVIZH_VN_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.ENVIZH_VN_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p = `r round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"], 3)`.
-VI corpus: $\beta$ = `r round(fixef(fit.ENVIZH_VN_cos)["theme_cosine_prop_V"], 2)`, $\chi^2$(`r fit.ENVIZH_VN_cos.anova["theme_cosine_prop_V", "Df"]`) = `r round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_V", "Chisq"], 2)`, p = `r round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"], 3)`.
-ZH corpus: $\beta$ = `r round(fixef(fit.ENVIZH_VN_cos)["theme_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ENVIZH_VN_cos.anova["theme_cosine_prop_M", "Df"]`) = `r round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_M", "Chisq"], 2)`, p = `r round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"], 3)`.
-
-For China responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are all significant predictors.
-EN corpus: $\beta$ = `r round(fixef(fit.ENVIZH_CN_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.ENVIZH_CN_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.ENVIZH_CN_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p = `r round(fit.ENVIZH_CN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"], 3)`.
-VI corpus: $\beta$ = `r round(fixef(fit.ENVIZH_CN_cos)["theme_cosine_prop_V"], 2)`, $\chi^2$(`r fit.ENVIZH_CN_cos.anova["theme_cosine_prop_V", "Df"]`) = `r round(fit.ENVIZH_CN_cos.anova["theme_cosine_prop_V", "Chisq"], 2)`, p = `r round(fit.ENVIZH_CN_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"], 3)`.
-ZH corpus: $\beta$ = `r round(fixef(fit.ENVIZH_CN_cos)["theme_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ENVIZH_CN_cos.anova["theme_cosine_prop_M", "Df"]`) = `r round(fit.ENVIZH_CN_cos.anova["theme_cosine_prop_M", "Chisq"], 2)`, p = < .001.
-
-We observed some level of language specificity from this analysis.
-The English corpus is the best predictor for US responding, and the Mandarin corpus is the best predictor for China response.
-While this is not the case with the Vietnamese corpus and the Vietnam responding, the Vietnamese corpus is still a significant predictor for the Vietnam responding.
-
-```{r echo=FALSE, warning = FALSE, fig.cap = "Fixed effect sizes of each corpus when included as a predictor for China, US, and Vietnam responding, respectively.
-The English corpus is the best predictor for US response, and the Mandarin corpus is the best predictor for China response."}
-coeff_value_cos <- c(fixef(fit.ENVIZH_US_cos)["theme_cosine_prop_E"],
-                 fixef(fit.ENVIZH_US_cos)["theme_cosine_prop_V"], 
-                 fixef(fit.ENVIZH_US_cos)["theme_cosine_prop_M"],
-                 fixef(fit.ENVIZH_VN_cos)["theme_cosine_prop_E"],
-                 fixef(fit.ENVIZH_VN_cos)["theme_cosine_prop_V"],
-                 fixef(fit.ENVIZH_VN_cos)["theme_cosine_prop_M"], 
-                 fixef(fit.ENVIZH_CN_cos)["theme_cosine_prop_E"],
-                 fixef(fit.ENVIZH_CN_cos)["theme_cosine_prop_V"], 
-                 fixef(fit.ENVIZH_CN_cos)["theme_cosine_prop_M"])
-
-se_value_cos <- c(summary(fit.ENVIZH_US_cos)$coef["theme_cosine_prop_E", "Std. Error"], 
-              summary(fit.ENVIZH_US_cos)$coef["theme_cosine_prop_V", "Std. Error"],
-              summary(fit.ENVIZH_US_cos)$coef["theme_cosine_prop_M", "Std. Error"], 
-              summary(fit.ENVIZH_VN_cos)$coef["theme_cosine_prop_E", "Std. Error"], 
-              summary(fit.ENVIZH_VN_cos)$coef["theme_cosine_prop_V", "Std. Error"],
-              summary(fit.ENVIZH_VN_cos)$coef["theme_cosine_prop_M", "Std. Error"],
-              summary(fit.ENVIZH_CN_cos)$coef["theme_cosine_prop_E", "Std. Error"], 
-              summary(fit.ENVIZH_CN_cos)$coef["theme_cosine_prop_V", "Std. Error"],
-              summary(fit.ENVIZH_CN_cos)$coef["theme_cosine_prop_M", "Std. Error"])
-
-country_value <- c(rep("US", 3),
-                   rep("VN", 3),
-                   rep("CN", 3))
-
-corpus_value <- c(rep(c("EN", "VI", "ZH"), 3))
-
-df.USVNCN_coeffs_cos <- data.frame(country_value, corpus_value, coeff_value_cos, se_value_cos)
-
-ggplot(data = df.USVNCN_coeffs_cos, 
-       mapping = aes(x = country_value, y = coeff_value_cos, fill = corpus_value)) +
-  geom_bar(position="dodge", stat="identity") +
-  geom_errorbar(aes(ymin= coeff_value_cos - se_value_cos, ymax = coeff_value_cos + se_value_cos), width=.2,
-                 position=position_dodge(.9)) +
-  scale_y_reverse() + 
-  labs(x = "Country", y = "Fixed effect size", fill = "Corpus") + 
-  scale_x_discrete(labels=c("CN" = "China", "US" = "US", "VN" = "Vietnam")) + 
-  scale_fill_manual(values=c("#D63230", "#1C77C3", "#F39237"))
-
-```
-
-```{r model comparison, include=FALSE}
-fit.US_cos_compare = anova(fit.ENVIZH_US_cos, fit.EN_US_cos, type = 3)
-fit.VN_cos_compare = anova(fit.ENVIZH_VN_cos, fit.VI_VN_cos, type = 3)
-fit.CN_cos_compare = anova(fit.ENVIZH_CN_cos, fit.ZH_CN_cos, type = 3)
-```
-
-However, we found that language specificity alone does not explain our results.
-We used an ANOVA to compare the model with only the corresponding corpus, and the model with all 3 corpora for each cultural context.
-We found that in all three cases (US, China, Vietnam), adding the other two corpora produces a significantly better fit than the identical model without the additional corpora, and only the corresponding corpus included as a predictor (US response: $\chi^2$(`r fit.US_compare["fit.ENVIZH_US_cos", "Df"]`) = `r round(fit.US_compare["fit.ENVIZH_US_cos", "Chisq"], 2)`, p = `r round(fit.US_compare["fit.ENVIZH_US_cos", "Pr(>Chisq)"], 3)`; Vietnam response: $\chi^2$(`r fit.VN_compare["fit.ENVIZH_VN_cos", "Df"]`) = `r round(fit.VN_compare["fit.ENVIZH_VN_cos", "Chisq"], 2)`, p = < .001; China response: $\chi^2$(`r fit.CN_compare["fit.ENVIZH_CN_cos", "Df"]`) = `r round(fit.CN_compare["fit.ENVIZH_CN_cos", "Chisq"], 2)`, p = `r round(fit.CN_compare["fit.ENVIZH_CN_cos", "Pr(>Chisq)"], 3)`).
-
-```{r add linguistic model to Ji et al., include=FALSE}
-fit.country = glmer(responses_theme ~ country + (1 | subject) + (1 | triad), 
-                           data = df %>% filter(country != "Vietnam"), 
-                           family = "binomial")
-
-fit.country_corpus = glmer(responses_theme ~ country + theme_cosine_prop_E + theme_cosine_prop_M + (1 | subject) + (1 | triad), 
-                           data = df %>% filter(country != "Vietnam"), 
-                           family = "binomial")
-
-fit.add_corpus <- anova(fit.country, fit.country_corpus, type = 3)
-
-```
-
-We carried out an ANOVA model comparison to compare our approach with previous studies that did not include corpus information.
-Because @Ji2004 only compared US and China participants, we filtered our data to only include responding data from these two countries.
-Our approach would be to compare a model that only includes country (US or China) as a fixed effect with one that also includes English and Chinese corpus data.
-Our previous model with an intercept per subject and one per triad, as well as by-triad random slopes for country to account for variation in the country effect across triads fails to converge with the more complex model, so we include a simpler random effect structure with an intercept per subject and one per triad in both the basic and more complex model.
-We compare this model with an identical model but including Chinese and English corpus cosine distance proportion prediction.
-We found that adding English and Chinese corpus data produces a significantly better fit than the identical model without English and Chinese corpus data as predictors ($\chi^2$(`r fit.add_corpus["fit.country_corpus", "Df"]`) = `r round(fit.add_corpus["fit.country_corpus", "Chisq"], 2)`, p = < .001.
-This suggests that including corpus data would better model the cross-cultural differences in similarity judgment in this study as well as similar studies.
-
-## Exploratory analysis
-
-Because our exclusion criterion for attention checks excluded over 50% Vietnam participants, we carried out exploratory analysis where we applied less stringent exclusion criteria.
-In the following analysis, we only exclude participants who miss more than 2 attention checks (rather than any attention checks).
-We kept the rest of the exclusion criteria.
-
-TODO: CREATE .CSV FILES FOR THESE, SEPARATE OUT R SCRIPT INTO RMD.
-```{r loading data E explore, warning=FALSE, include=F}
-df.resp_E <- read.csv("../../data/data_E_0319.csv") %>%
+```{r loading data E, warning=FALSE, include=F}
+df.resp_E <- read.csv("../../data/responding/data_US.csv") %>%
   select(-X)
@@
 
-```{r exclusion E explore, include = F, warning = F}
+```{r exclusion E, include = F, warning = F}
 #non-native speaker
@@
 percent_dropped = length(ppts_non_native_lang_E) / length(unique(df.resp_E$subject))
-percent_dropped #0.1041667
+percent_dropped #0.1034482775
 
@@
 percent_dropped = length(ppts_vi_speaker_E) / length(unique(df.resp_E$subject))
-percent_dropped #0.02083333
+percent_dropped #0.02298851
 
@@
 percent_dropped = length(ppts_zh_speaker_E) / length(unique(df.resp_E$subject))
-percent_dropped #0.1822917
+percent_dropped #0.1742424
 
@@
 percent_dropped = length(ppts_lived_abroad_E) / length(unique(df.resp_E$subject))
-percent_dropped #0.171875
+percent_dropped #0.1666667
 
@@
 
-```{r demog_E explore, include = F}
-demog <- c("demog-dropdown", "demog-multi-choice", "demog-free-response", "demog-multi-select")
-df.demog_E <- df.resp_E %>%
-  filter(trial_type %in% demog)
-
-AGE = 97 #index for age answer
-GENDER = 115 #index for gender answer
-split_responses <- function(responses) {
-  responses <- as.character(responses)
-  response_list <- unlist(strsplit(responses, ',|:'))
-  response_list <- response_list[seq(1, length(response_list))]
-  response_list <- gsub("}", "", response_list)
-  response_list <- gsub("\"", "", response_list)
-  return(response_list)
-}
-
-get_age <- Vectorize(function(responses) {
-  responses <- split_responses(responses)
-  if(responses[AGE-1] != "A0") {warnings("cannot find age answer")}
-  else{return (responses[AGE])}
-})
-
-get_gender <- Vectorize(function(responses) {
-  responses <- split_responses(responses)
-  if(responses[GENDER-1] != "A1") {warnings("cannot find gender answer")}
-  else{return (responses[GENDER])}
-})
-
-df.age_gender_E <- df.demog_E %>%
-  filter(variable_type == "demog_age_gender_ethnic") %>%
-  select(subject, responses) %>%
-  mutate(age = as.numeric(get_age(responses))) %>%
-  mutate(age = as.numeric(age)) %>%
-  mutate(gender = get_gender(responses))
-
-df.age_gender_E_summ <- df.age_gender_E %>%
-  summarize(mean_age = mean(age), 
-            median_age = median(age), 
-            sd_age = sd(age))
+```{r}
+write.csv(df.resp_E, "../../data/responding/dataUS_excl.csv")
 ```
-
-```{r loading data V explore, include=F}
-df.resp_V <- read.csv("../../data/data_V_0530.csv") %>%
-  select(-X)
-
-# check for participants who completed the entire experiment. Because the experiment is
-# quite long, some participants decide to come back afterwards, so there are a few files
-# that are recorded as incomplete. 
-df.ppts_finished_V <- df.resp_V %>% 
-  group_by(subject) %>%
-  summarize(finished = ifelse("demo-final" %in% unique(variable_type), "yes", "no")) %>%
-  filter(finished == "yes")
-
-df.resp_V <- df.resp_V %>%
-  filter(subject %in% df.ppts_finished_V$subject)
-
-df.ppts_att_V <- df.resp_V %>%
-  filter(stim_type == "attention check") %>%
-  mutate(correct_response = strsplit(cue, "Chọn ")) %>%
-  mutate(correct_response = sapply(correct_response, "[[", 2)) %>%
-  mutate(pass_att_check = ifelse(responses == correct_response, 1, 0)) %>%
-  group_by(subject) %>%
-  summarize(pass_att_check_percent = mean(pass_att_check)) %>%
-  filter(pass_att_check_percent >= 0.8)
-
-df.resp_V <- df.resp_V %>%
-  filter(subject %in% df.ppts_att_V$subject) #73
-```
-
-```{r exclusion V explore, include = F}
-#non-native speaker
-split_responses_demog <- function(responses) {
-  responses <- as.character(responses)
-  response_list <- unlist(strsplit(responses, ',|:'))
-  response_list <- response_list[seq(1, length(response_list))]
-  response_list <- gsub("}", "", response_list)
-  response_list <- gsub("\"", "", response_list)
-  return(response_list)
-}
-
-NATIVE_LANG = 2
-get_native_lang <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  if(responses[NATIVE_LANG-1] != "{firstlanguage") 
-    {warnings("cannot find native language answer")}
-  else
-    {return (responses[NATIVE_LANG])}
-})
-
-df.ppts_non_native_lang_V <- df.resp_V %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_language") %>%
-  mutate(native_speaker = get_native_lang(responses)) %>%
-  filter(native_speaker == "Không")
-
-ppts_non_native_lang_V = unique(df.ppts_non_native_lang_V$subject)
-percent_dropped = length(ppts_non_native_lang_V) / length(unique(df.resp_V$subject))
-percent_dropped #0
-
-#fluent in English
-SPEAKER = 2
-SPEAKING = 23
-UNDERSTANDING = 46
-
-get_speaker <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[SPEAKER])
-})
-
-get_fluency_speaking <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[SPEAKING])
-})
-
-get_fluency_understanding <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[UNDERSTANDING])
-})
-
-df.lang_en_V <- df.resp_V %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_language_en") %>%
-  mutate(en_speaker = get_speaker(responses))
-
-df.lang_en_fluency_V <- df.resp_V %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_conditional_language_en_fluency") %>%
-  mutate(en_fluency_sp = as.numeric(get_fluency_speaking(responses))) %>%
-  mutate(en_fluency_ud = as.numeric(get_fluency_understanding(responses)))
-
-df.lang_en_V <- full_join(df.lang_en_V, 
-                          df.lang_en_fluency_V, 
-                          by = "subject") %>%
-  select(subject, en_speaker, en_fluency_sp, en_fluency_ud) %>%
-  filter(en_speaker == "Có",
-         en_fluency_sp > 4, 
-         en_fluency_ud > 4)
-
-ppts_en_speaker_V = unique(df.lang_en_V$subject) #4
-percent_dropped = length(ppts_en_speaker_V) / length(unique(df.resp_V$subject))
-percent_dropped #0.6861314 # do not use this criterion
-
-df.lang_zh_V <- df.resp_V %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_language_cn") %>%
-  mutate(zh_speaker = get_speaker(responses))
-
-df.lang_zh_fluency_V <- df.resp_V %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_conditional_language_cn_fluency") %>%
-  mutate(zh_fluency_sp = as.numeric(get_fluency_speaking(responses))) %>%
-  mutate(zh_fluency_ud = as.numeric(get_fluency_understanding(responses)))
-
-df.lang_zh_V <- full_join(df.lang_zh_V, 
-                          df.lang_zh_fluency_V, 
-                          by = "subject") %>%
-  select(subject, zh_speaker, zh_fluency_sp, zh_fluency_ud) %>%
-  filter(zh_speaker == "Có",
-         zh_fluency_sp > 4, 
-         zh_fluency_ud > 4)
-
-ppts_zh_speaker_V = unique(df.lang_zh_V$subject) #4
-percent_dropped = length(ppts_zh_speaker_V) / length(unique(df.resp_V$subject))
-percent_dropped #0.05839416
-
-#have lived outside the sample country for more than 2 years
-#have travelled extensively (more than 6 international experiences of 2 days or longer) 
-YEARSABROAD = 2
-OVERSEAEXP = 4
-
-get_lived_abroad <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[YEARSABROAD])
-})
-
-get_oversea_exp <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[OVERSEAEXP])
-})
-
-df.abroad_V <- df.resp_V %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_oversea_experience") %>%
-  mutate(lived_abroad = get_lived_abroad(responses)) %>%
-  mutate(oversea_exp = get_oversea_exp(responses))
-
-df.lived_abroad_V <- df.abroad_V %>%
-  filter(lived_abroad == "Có")
-
-ppts_lived_abroad_V = unique(df.lived_abroad_V$subject)
-percent_dropped = length(ppts_lived_abroad_V) / length(unique(df.resp_V$subject))
-percent_dropped #0.1094891
-
-df.oversea_exp_V <- df.abroad_V %>%
-  filter(oversea_exp == "6 lần trở lên")
-
-ppts_oversea_exp_V = unique(df.oversea_exp_V$subject) #77
-percent_dropped = length(ppts_oversea_exp_V) / length(unique(df.resp_V$subject))
-percent_dropped #0.1094891
-
-df.resp_V <- df.resp_V %>%
-  filter(!(subject %in% ppts_non_native_lang_V),
-         !(subject %in% ppts_oversea_exp_V), 
-         !(subject %in% ppts_zh_speaker_V),
-         !(subject %in% ppts_lived_abroad_V))
-
-length(unique(df.resp_V$subject))  #110
-```
-
-```{r demog_V explore, include = F}
-demog <- c("demog-dropdown", "demog-multi-choice", "demog-free-response", "demog-multi-select")
-df.demog_V <- df.resp_V %>%
-  filter(trial_type %in% demog)
-
-AGE = 97 #index for age answer
-GENDER = 115 #index for gender answer
-split_responses <- function(responses) {
-  responses <- as.character(responses)
-  response_list <- unlist(strsplit(responses, ',|:'))
-  response_list <- response_list[seq(1, length(response_list))]
-  response_list <- gsub("}", "", response_list)
-  response_list <- gsub("\"", "", response_list)
-  return(response_list)
-}
-
-get_age <- Vectorize(function(responses) {
-  responses <- split_responses(responses)
-  if(responses[AGE-1] != "A0") {warnings("cannot find age answer")}
-  else{return (responses[AGE])}
-})
-
-get_gender <- Vectorize(function(responses) {
-  responses <- split_responses(responses)
-  if(responses[GENDER-1] != "A1") {warnings("cannot find gender answer")}
-  else{return (responses[GENDER])}
-})
-
-df.age_gender_V <- df.demog_V %>%
-  filter(variable_type == "demog_age_gender_ethnic") %>%
-  select(subject, responses) %>%
-  mutate(age = as.numeric(get_age(responses))) %>%
-  mutate(age = as.numeric(age)) %>%
-  mutate(gender = get_gender(responses))
-
-df.age_gender_V_summ <- df.age_gender_V %>%
-  summarize(mean_age = mean(age), 
-            median_age = median(age), 
-            sd_age = sd(age))
-```
-
-```{r loading data M explore, warning=FALSE, include=F}
-df.resp_M <- read.csv("../../data/data_M_0530.csv") %>%
-  select(-X)
-
-# check for participants who completed the entire experiment. Because the experiment is
-# quite long, some participants decide to come back afterwards, so there are a few files
-# that are recorded as incomplete. 
-df.ppts_finished_M <- df.resp_M %>% 
-  group_by(subject) %>%
-  summarize(finished = ifelse("demo-final" %in% unique(variable_type), "yes", "no")) %>%
-  filter(finished == "yes")
-
-df.resp_M <- df.resp_M %>%
-  filter(subject %in% df.ppts_finished_M$subject)
-
-df.ppts_att_M <- df.resp_M %>%
-  filter(stim_type == "attention check") %>%
-  mutate(correct_response = strsplit(cue, "选择")) %>%
-  mutate(correct_response = sapply(correct_response, "[[", 2)) %>%
-  mutate(correct_response = str_replace_all(correct_response, "“", "")) %>%
-  mutate(correct_response = str_replace_all(correct_response, "”", "")) %>%
-  mutate(pass_att_check = ifelse(responses == correct_response, 1, 0)) %>%
-  group_by(subject) %>%
-  summarize(pass_att_check_percent = mean(pass_att_check)) %>%
-  filter(pass_att_check_percent >= 0.8)
-
-df.resp_M <- df.resp_M %>%
-  filter(subject %in% df.ppts_att_M$subject) 
-```
-
-```{r exclusion M explore, include = F, warning = F}
-#non-native speaker
-split_responses_demog <- function(responses) {
-  responses <- as.character(responses)
-  response_list <- unlist(strsplit(responses, ',|:'))
-  response_list <- response_list[seq(1, length(response_list))]
-  response_list <- gsub("}", "", response_list)
-  response_list <- gsub("\"", "", response_list)
-  return(response_list)
-}
-
-NATIVE_LANG = 2
-get_native_lang <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  if(responses[NATIVE_LANG-1] != "{firstlanguage") 
-    {warnings("cannot find native language answer")}
-  else
-    {return (responses[NATIVE_LANG])}
-})
-
-df.ppts_non_native_lang_M <- df.resp_M %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_language") %>%
-  mutate(native_speaker = get_native_lang(responses)) %>%
-  filter(native_speaker == "不是")
-
-ppts_non_native_lang_M = unique(df.ppts_non_native_lang_M$subject) #2
-percent_dropped = length(ppts_non_native_lang_M) / length(unique(df.resp_M$subject))
-percent_dropped #0.01149425
-
-#fluent in English
-SPEAKER = 2
-SPEAKING = 23
-UNDERSTANDING = 46
-
-get_speaker <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[SPEAKER])
-})
-
-get_fluency_speaking <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[SPEAKING])
-})
-
-get_fluency_understanding <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[UNDERSTANDING])
-})
-
-df.lang_en_M <- df.resp_M %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_language_en") %>%
-  mutate(en_speaker = get_speaker(responses))
-
-df.lang_en_fluency_M <- df.resp_M %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_conditional_language_en_fluency") %>%
-  mutate(en_fluency_sp = as.numeric(get_fluency_speaking(responses))) %>%
-  mutate(en_fluency_ud = as.numeric(get_fluency_understanding(responses)))
-
-df.lang_en_M <- full_join(df.lang_en_M, 
-                          df.lang_en_fluency_M, 
-                          by = "subject") %>%
-  select(subject, en_speaker, en_fluency_sp, en_fluency_ud) %>%
-  filter(en_speaker == "能",
-         en_fluency_sp > 4, 
-         en_fluency_ud > 4)
-
-ppts_en_speaker_M = unique(df.lang_en_M$subject) #50
-percent_dropped = length(ppts_en_speaker_M) / length(unique(df.resp_M$subject))
-percent_dropped #0.3850575 # will not use this criterion
-
-df.lang_vi_M <- df.resp_M %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_language_vi") %>%
-  mutate(vi_speaker = get_speaker(responses))
-
-df.lang_vi_fluency_M <- df.resp_M %>%
-  filter(variable_type == "demog_conditional_language_vi_fluency") %>%
-  mutate(vi_fluency_sp = as.numeric(get_fluency_speaking(responses))) %>%
-  mutate(vi_fluency_ud = as.numeric(get_fluency_understanding(responses)))
-
-df.lang_vi_M <- full_join(df.lang_vi_M, 
-                          df.lang_vi_fluency_M, 
-                          by = "subject") %>%
-  select(subject, vi_speaker, vi_fluency_sp, vi_fluency_ud) %>%
-  filter(vi_speaker == "能",
-         vi_fluency_sp > 4, 
-         vi_fluency_ud > 4)
-
-ppts_vi_speaker_M = unique(df.lang_vi_M$subject) #50
-percent_dropped = length(ppts_vi_speaker_M) / length(unique(df.resp_M$subject))
-percent_dropped #0
-
-#have lived outside the sample country for more than 2 years
-#have travelled extensively (more than 6 international experiences of 2 days or longer) 
-YEARSABROAD = 2
-OVERSEAEXP = 4
-
-get_lived_abroad <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[YEARSABROAD])
-})
-
-get_oversea_exp <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[OVERSEAEXP])
-})
-
-df.abroad_M <- df.resp_M %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_oversea_experience") %>%
-  mutate(lived_abroad = get_lived_abroad(responses)) %>%
-  mutate(oversea_exp = get_oversea_exp(responses))
-
-df.lived_abroad_M <- df.abroad_M %>%
-  filter(lived_abroad == "是")
-
-ppts_lived_abroad_M = unique(df.lived_abroad_M$subject) #23
-percent_dropped = length(ppts_lived_abroad_M) / length(unique(df.resp_M$subject))
-percent_dropped # 0.1551724
-
-df.oversea_exp_M <- df.abroad_M %>%
-  filter(oversea_exp == "六段或更多国际经历")
-
-ppts_oversea_exp_M = unique(df.oversea_exp_M$subject) #0
-percent_dropped = length(ppts_oversea_exp_M) / length(unique(df.resp_M$subject))
-percent_dropped #0.03448276
-
-df.resp_M <- df.resp_M %>%
-  filter(!(subject %in% ppts_non_native_lang_M),
-         !(subject %in% ppts_lived_abroad_M),
-         !(subject %in% ppts_vi_speaker_M),
-         !(subject %in% ppts_oversea_exp_M),)
-
-length(unique(df.resp_M$subject)) #143
-```
-
-```{r demog_M explore, include = F}
-demog <- c("demog-dropdown", "demog-multi-choice", "demog-free-response", "demog-multi-select")
-df.demog_M <- df.resp_M %>%
-  filter(trial_type %in% demog) 
-#write.csv(data_demog, "data_anon_demog_0201.csv")
-
-AGE = 97 #index for age answer
-GENDER = 115 #index for gender answer
-split_responses <- function(responses) {
-  responses <- as.character(responses)
-  response_list <- unlist(strsplit(responses, ',|:'))
-  response_list <- response_list[seq(1, length(response_list))]
-  response_list <- gsub("}", "", response_list)
-  response_list <- gsub("\"", "", response_list)
-  return(response_list)
-}
-
-get_age <- Vectorize(function(responses) {
-  responses <- split_responses(responses)
-  if(responses[AGE-1] != "A0") {warnings("cannot find age answer")}
-  else{return (responses[AGE])}
-})
-
-get_gender <- Vectorize(function(responses) {
-  responses <- split_responses(responses)
-  if(responses[GENDER-1] != "A1") {warnings("cannot find gender answer")}
-  else{return (responses[GENDER])}
-})
-
-df.age_gender_M <- df.demog_M %>%
-  filter(variable_type == "demog_age_gender_ethnic") %>%
-  select(subject, responses) %>%
-  mutate(age = as.numeric(get_age(responses))) %>%
-  mutate(age = as.numeric(age)) %>%
-  mutate(gender = get_gender(responses))
-
-df.age_gender_M_summ <- df.age_gender_M %>%
-  summarize(mean_age = mean(age), 
-            median_age = median(age), 
-            sd_age = sd(age))
-```
-
-With the new exclusion criteria, we excluded `r length(unique(df.ppts_finished_E$subject)) - length(unique(df.ppts_att_E$subject))` US participants, `r length(unique(df.ppts_finished_V$subject)) - length(unique(df.ppts_att_V$subject))` VN participants, and `r length(unique(df.ppts_finished_M$subject)) - length(unique(df.ppts_att_M$subject))` CN participants who did not answer more than 2 attention checks correctly.
-We then applied the 4 criteria that aim to retain only participants who are influenced by one culture: (1) non-native speakers of English and Vietnamese, respectively, (2) fluent in at least one of the other two study languages (Vietnamese for US participants, English for Vietnamese participants and Chinese participants), (3) have lived outside of the test country (US, Vietnam, or China) for more than two years, and (4) have significant international experience (more than 6 international experiences of 2 days or longer.) We did not use a particular criterion for a language if it would exclude 25% or more of any one sample.
-In this round of exclusion, we excluded `r length(unique(df.ppts_att_E$subject)) - length(unique(df.resp_E$subject))` US, `r length(unique(df.ppts_att_V$subject)) - length(unique(df.resp_V$subject))` VN participants, and `r length(unique(df.ppts_att_M$subject)) - length(unique(df.resp_M$subject))` CN participants.
-After these exclusions, the US sample included `r length(unique(df.resp_E$subject))` participants (`r df.age_gender_E %>% filter(gender == "Male") %>% count()`M, `r df.age_gender_E %>% filter(gender == "Female") %>% count()`F, `r df.age_gender_E %>% filter(gender == "Non-binary") %>% count()` non-binary, `r df.age_gender_E %>% filter(gender == "Decline to answer") %>% count()` other), with mean age = `r round(df.age_gender_E_summ$mean_age, 2)` (SD = `r round(df.age_gender_E_summ$sd_age, 2)`) and median age = `r df.age_gender_E_summ$median_age`.
-The VN sample included `r length(unique(df.resp_V$subject))` participants (`r df.age_gender_V %>% filter(gender == "Nam") %>% count()`M, `r df.age_gender_V %>% filter(gender == "Nữ") %>% count()`F), with mean age = `r round(df.age_gender_V_summ$mean_age, 2)` (SD = `r round(df.age_gender_V_summ$sd_age, 2)`) and median age = `r df.age_gender_V_summ$median_age`.
-The CN sample included `r length(unique(df.resp_M$subject))` participants (`r df.age_gender_M %>% filter(gender == "男性") %>% count()`M, `r df.age_gender_M %>% filter(gender == "女性") %>% count()`F), with mean age = `r round(df.age_gender_M_summ$mean_age, 2)` (SD = `r round(df.age_gender_M_summ$sd_age, 2)`) and median age = `r df.age_gender_M_summ$median_age`.
-
-```{r corpus explore, include = F}
-df.corpus_E <- read.csv("../../data/corpusE_cos.csv") %>%
-  rename(tax_frequency_E = tax.frequency,
-         theme_frequency_E = theme.frequency,
-         tax_cosine_E = Tax.cosine_dist, 
-         theme_cosine_E = Theme.cosine_dist,
-         tax_cosine_sim_E = Tax.cosine_sim,
-         theme_cosine_sim_E = Theme.cosine_sim,
-         tax_match_E = Tax.match,
-         theme_match_E = Theme.match, 
-         cue_E = Cue)
-
-df.corpus_V <- read.csv("../../data/corpusV_cos.csv") %>%
-  rename(tax_frequency_V = tax.frequency,
-         theme_frequency_V = theme.frequency,
-         tax_cosine_V = Tax.cosine_dist, 
-         theme_cosine_V = Theme.cosine_dist,
-         tax_cosine_sim_V = Tax.cosine_sim,
-         theme_cosine_sim_V = Theme.cosine_sim,
-         tax_match_V = Tax.match,
-         theme_match_V = Theme.match, 
-         cue_V = Cue)
-
-df.corpus_M <- read.csv("../../data/corpusM_cos.csv") %>%
-  rename(tax_frequency_M = tax.frequency,
-         theme_frequency_M = theme.frequency,
-         tax_cosine_M = Tax.cosine_dist, 
-         theme_cosine_M = Theme.cosine_dist,
-         tax_cosine_sim_M = Tax.cosine_sim,
-         theme_cosine_sim_M = Theme.cosine_sim,
-         tax_match_M = Tax.match,
-         theme_match_M = Theme.match, 
-         cue_M = Cue)
-```
-
-```{r full corpus explore, M freqs is incorrect, include=F}
-df.corpus <- left_join(df.corpus_E, df.corpus_V, by = "Cue_renamed")
-df.corpus <- left_join(df.corpus, df.corpus_M, by = "Cue_renamed")
-
-#replacing any 0 raw counts with epsilon
-df.corpus <- df.corpus %>%
-  mutate(tax_frequency_E = ifelse(tax_frequency_E == 0, 
-                                  .Machine$double.eps, tax_frequency_E),
-         theme_frequency_E = ifelse(theme_frequency_E == 0, 
-                                  .Machine$double.eps, theme_frequency_E),
-         tax_frequency_V = ifelse(tax_frequency_V == 0, 
-                                  .Machine$double.eps, tax_frequency_V),
-         theme_frequency_V = ifelse(theme_frequency_V == 0, 
-                                  .Machine$double.eps, theme_frequency_V))
-
-```
-
-```{r corpus - frequency explore, include = F}
-#find triads_omit, used whenever analysis uses raw collocates 
-df.corpus_E_freq <- df.corpus_E %>%
-  select(Cue_renamed, cue_E, tax_match_E, theme_match_E, tax_frequency_E, theme_frequency_E)
-corpus_E_omit <- df.corpus_E_freq %>%
-  filter(tax_frequency_E == 0 & theme_frequency_E == 0)
-
-df.corpus_V_freq <- df.corpus_V %>%
-  select(Cue_renamed, cue_V, tax_match_V, theme_match_V, tax_frequency_V, theme_frequency_V)
-corpus_V_omit <- df.corpus_V_freq %>% 
-  filter(tax_frequency_V == 0 & theme_frequency_V == 0)
-
-triads_omit <- append(corpus_E_omit$Cue_renamed, corpus_V_omit$Cue_renamed)
-
-df.corpus_freq <- left_join(df.corpus_E_freq, df.corpus_V_freq, by = "Cue_renamed")
-```
-
-```{r corpus - cosine explore, include = F}
-#mainly for sanity checking and so that there is a parallel df to df.corpus_freq
-df.corpus_E_cos <- df.corpus_E %>%
-  select(Cue_renamed, cue_E, tax_match_E, theme_match_E, 
-         tax_cosine_E, theme_cosine_E,
-         tax_cosine_sim_E, theme_cosine_sim_E)
-
-df.corpus_V_cos <- df.corpus_V %>%
-  select(Cue_renamed, cue_V, tax_match_V, theme_match_V, tax_cosine_V, theme_cosine_V,
-         tax_cosine_sim_V, theme_cosine_sim_V)
-
-df.corpus_M_cos <- df.corpus_M %>%
-  select(Cue_renamed, cue_M, tax_match_M, theme_match_M, tax_cosine_M, theme_cosine_M, 
-         tax_cosine_sim_M, theme_cosine_sim_M)
-
-df.corpus_cos <- left_join(df.corpus_E_cos, df.corpus_V_cos, by = "Cue_renamed")
-df.corpus_cos <- left_join(df.corpus_cos, df.corpus_M_cos, by = "Cue_renamed")
-```
-
-```{r getting triads from the 3 languages explore, include = F}
-#combine response and corpus data
-df.triad_E <- df.resp_E %>%
-  filter(stim_type == "triad",
-         responses != "NA")
-triad_cues_E <- read.csv("../../data/cue_renamed_E.csv")
-df.triad_E <- left_join(df.triad_E, triad_cues_E, by = c("cue", "top_opt", "bottom_opt"))
-df.triad_E <- inner_join(df.triad_E, df.corpus, by = "Cue_renamed")
-
-df.triad_E <- df.triad_E %>%
-  mutate(responses_theme = ifelse(responses == theme_match_E, 1, 0),
-         language = "English",
-         country = "US") %>%
-  select(subject, rt, Cue_renamed, cue, top_opt, bottom_opt, 
-         responses, responses_theme, country, language,
-         tax_match_E, theme_match_E, tax_match_V, theme_match_V, tax_match_M, theme_match_M,
-         tax_frequency_E, theme_frequency_E, tax_frequency_V, theme_frequency_V, tax_frequency_M, theme_frequency_M,
-         tax_cosine_E, theme_cosine_E, tax_cosine_V, theme_cosine_V, tax_cosine_M, theme_cosine_M,
-         tax_cosine_sim_E, theme_cosine_sim_E, tax_cosine_sim_V, theme_cosine_sim_V, tax_cosine_sim_M, theme_cosine_sim_M)
-
-df.triad_V <- df.resp_V %>%
-  filter(stim_type == "triad",
-         responses != "NA")
-triad_cues_V <- read.csv("../../data/cue_renamed_V.csv")
-df.triad_V <- left_join(df.triad_V, triad_cues_V, by = c("cue", "top_opt", "bottom_opt"))
-df.triad_V <- inner_join(df.triad_V, df.corpus, by = "Cue_renamed")
-
-df.triad_V <- df.triad_V %>%
-  mutate(responses_theme = ifelse(responses == theme_match_V, 1, 0),
-         language = "Vietnamese", 
-         country = "Vietnam") %>%
-  select(subject, rt, Cue_renamed, cue, top_opt, bottom_opt, 
-         responses, responses_theme, country, language,
-         tax_match_E, theme_match_E, tax_match_V, theme_match_V, tax_match_M, theme_match_M,
-         tax_frequency_E, theme_frequency_E, tax_frequency_V, theme_frequency_V, tax_frequency_M, theme_frequency_M,
-         tax_cosine_E, theme_cosine_E, tax_cosine_V, theme_cosine_V, tax_cosine_M, theme_cosine_M,
-         tax_cosine_sim_E, theme_cosine_sim_E, tax_cosine_sim_V, theme_cosine_sim_V, tax_cosine_sim_M, theme_cosine_sim_M)
-
-df.triad_M <- df.resp_M %>%
-  filter(stim_type == "triad",
-         responses != "NA")
-triad_cues_M <- read.csv("../../data/cue_renamed_M.csv")
-df.triad_M <- left_join(df.triad_M, triad_cues_M, by = c("cue", "top_opt", "bottom_opt"))
-df.triad_M <- inner_join(df.triad_M, df.corpus, by = "Cue_renamed")
-
-df.triad_M <- df.triad_M %>%
-  mutate(responses_theme = ifelse(responses == theme_match_M, 1, 0),
-         language = "Mandarin", 
-         country = "China") %>%
-  select(subject, rt, Cue_renamed, cue, top_opt, bottom_opt, 
-         responses, responses_theme, country, language,
-         tax_match_E, theme_match_E, tax_match_V, theme_match_V, tax_match_M, theme_match_M,
-         tax_frequency_E, theme_frequency_E, tax_frequency_V, theme_frequency_V, tax_frequency_M, theme_frequency_M,
-         tax_cosine_E, theme_cosine_E, tax_cosine_V, theme_cosine_V, tax_cosine_M, theme_cosine_M,
-         tax_cosine_sim_E, theme_cosine_sim_E, tax_cosine_sim_V, theme_cosine_sim_V, tax_cosine_sim_M, theme_cosine_sim_M)
-
-#calculate proportion for raw frequencies and cosine distance
-df <- rbind(df.triad_E, df.triad_V)
-df <- rbind(df, df.triad_M) %>%
-  mutate(theme_freq_prop_E = theme_frequency_E / (theme_frequency_E + tax_frequency_E),
-         theme_freq_prop_V = theme_frequency_V / (theme_frequency_V + tax_frequency_V), 
-         theme_freq_prop_M = theme_frequency_M / (theme_frequency_M + tax_frequency_M), 
-         theme_cosine_prop_E = theme_cosine_E / (theme_cosine_E + tax_cosine_E),
-         theme_cosine_prop_V = theme_cosine_V / (theme_cosine_V + tax_cosine_V), 
-         theme_cosine_prop_M = theme_cosine_M / (theme_cosine_M + tax_cosine_M)) %>%
-  rename(triad = Cue_renamed)
-```
-
-```{r country effect - explore, warning=FALSE, include=FALSE, paged.print=TRUE}
-df.country <- df %>%
-  group_by(subject, country) %>%
-  summarize(theme_resp_percent = mean(responses_theme, na.rm = T))
-
-df.country_sum <- df.country %>%
-  group_by(country) %>%
-  summarize(mean_theme_resp_percent = mean(theme_resp_percent), 
-            sd_theme_resp_percent = sd(theme_resp_percent))
-
-fit.country = glmer(responses_theme ~ country + (1 | subject) + (country | triad), 
-                    data = df, 
-                    family = "binomial")
-summary(fit.country) 
-fit.country.anova = Anova(fit.country, type=3)
-
-fit.country_EN_VN = glmer(responses_theme ~ country + (1 | subject) + (country | triad), 
-                    data = df %>% filter(country != "China"),
-                    family = "binomial")
-summary(fit.country_EN_VN) 
-```
-
-```{r echo=FALSE, warning=FALSE, fig.cap="Proportion of thematic responses by country, with a less stringent attention check criterion.
-We did not find any significant differences from the analysis reported above with a more stringent criterion."}
-
-ggplot(df.country,
-       mapping = aes(x = country, 
-                     y = theme_resp_percent, 
-                     color = country)) +
-  geom_violin() +
-  geom_jitter(height = 0, 
-              alpha = 0.3) +  
-  stat_summary(fun.data = "mean_cl_boot", 
-               geom = "pointrange") + 
-  labs(y = "Proportion Thematic Chosen", 
-       x = "Country", 
-       color = "Country") + 
-  scale_color_manual(values=c("#D63230", "#1C77C3", "#F39237"))
-```
-
-There is no significant difference in this round of analysis compared to the one reported above (with more stringent attention check criterion).
-That is, we still observed a significant effect of country on proportion of thematic responses ($\chi^2$(`r fit.country.anova["country", "Df"]`) = `r round(fit.country.anova["country", "Chisq"], 2)`, p < .001), but this effect is driven by only the difference between US and China response ($\beta$ = `r round(fixef(fit.country)["countryUS"], 2)`, p < .001).
-There is no statistical difference between the Vietnam and China response ($\beta$ = `r round(fixef(fit.country)["countryVietnam"], 2)`, p = `r round(as.data.frame(summary(fit.country)[["coefficients"]])["countryVietnam", "Pr(>|z|)"], 3)`), and the US and Vietnam response ($\beta$ = `r round(fixef(fit.country_EN_VN)["countryVietnam"], 2)`, p = `r round(as.data.frame(summary(fit.country)[["coefficients"]])["countryVietnam", "Pr(>|z|)"], 3)`).
-
-# Discussion
-In this paper, we consider whether statistics of the language environment can account for cross-cultural differences in a classic similarity judgment paradigm, as an alternative to the view that members of different cultures vary in their conception of similarity.
-
-We first tested the generality of a cultural account which holds that people from Western and East Asian cultures tend to conceive of similarity in more taxonomic and thematic ways, respectively, and respond accordingly in categorization tasks such as ours.
-While we managed to replicate the previously documented contrast between English speakers in the US and Mandarin Chinese speakers from East Asia (mainland China, Taiwan, Hong Kong, and Singapore), we do not extend this contrast to our sample of Vietnamese speakers in Vietnam and English speakers in the US.
-This finding suggests some limitations on the generality of this cultural account.
-
-We did find some signatures of language specificity in our analysis, such as the large positive correlation between similarity judgments of each country and the respective corpus statistics, and how each corpus statistics are good predictors for corresponding country's similarity judgments.
-However, this is potentially due to the high correlation between corpus statistics of English, Vietnamese and Mandarin.
-We find even stronger evidence for consistency across the three groups, with substantive overlapping predictions across the corpus models, highly similar responding across the experiments, and a correspondingly high fit in cross-language comparisons between models and data.
-
-```{r include=FALSE}
-fit.country_no_triad <- glmer(responses_theme ~ country + (1 | subject), 
-                              data = df_main_analysis, 
-                              family = "binomial")
-
-fit.country = glmer(responses_theme ~ country + (1 | subject) + (country | triad), 
-                    data = df_main_analysis, 
-                    family = "binomial")
-summary(fit.country)
-
-fit.no_triad_compare <- anova(fit.country, fit.country_no_triad, type = 3)
-```
-
-There are some suggestions that the current approach can predict triad-specific cross-cultural effects.
-First of all, an ANOVA model comparison showed that adding a random effect term for varying slope by country and varying intercept by triad to the model produces a significant better fit than the identical model without this random effect term included as a predictor ($\chi^2$(`r fit.no_triad_compare["fit.country", "Df"]`) = `r round(fit.no_triad_compare["fit.country", "Chisq"], 2)`, p < .001)
-
-Anecdotally, we show below some examples of triads that show contrasting difference in the magnitude of difference in thematic responses between countries.
-As a review, the overall result across all triads showed that there was significant difference between US and China responding, and no significant differences between US and Vietnam or China and Vietnam responding.
-However, we observed that for the triad "cow-grass-chicken," there were significant differences between US and China, and US and Vietnam responding.
-There was no significant difference between China and Vietnam responding.
-For the triad "spoon-sugar-fork," there were significant difference between China and US, and China and Vietnam responding, but no significant difference between US and Vietnam.
-For the triad "hair-comb-beard," there were no significant differences pairwise across the three cultural contexts.
-This suggests that there are triad-specific cross-cultural effects in play.
-Beyond emphasizing the importance of including triad predictors as a random effect, this finding suggests that, firstly, future similar studies need to report triads that are used, as the triads used can affect results (for example, if a study only includes triads where China and US responding are significantly different, it would be more likely to conclude that Chinese and US cultures hold different notions of similarity).
-Secondly, that future studies can look more deeply into which groups of triads are driving the US-China responding difference.
-For example, triads belonging to different semantic neighborhoods might be influencing cross-cultural responding in different ways.
-
-```{r include=FALSE}
-df.country_item <- df_main_analysis %>%
-  filter(triad == "hair")
-
-plot.hair <- ggplot(df.country_item,
-       mapping = aes(x = factor(country, levels=c("China", "US", "Vietnam")), 
-                     y = responses_theme, 
-                     color = factor(country, levels=c("China", "US", "Vietnam")))) +
-  geom_jitter(stat = "identity", alpha  = .5) +
-  labs(y = "Proportion Thematic Chosen (hair: beard / comb)",  
-       x = "Country", 
-       color = "Country") + 
-  stat_summary(fun.data = "mean_cl_boot", 
-               geom = "pointrange") + 
-  scale_y_continuous(limits=c(0.0, 1.0), oob = scales::squish) + 
-  scale_fill_manual(values=c("#D63230", "#1C77C3", "#F39237")) +  
-  scale_color_manual(values=c("#D63230", "#1C77C3", "#F39237"))  + 
-  theme(axis.title = element_text(size=rel(0.75)))
-```
-
-```{r include=FALSE}
-df.country_item <- df_main_analysis %>%
-  filter(triad == "spoon2")
-
-plot.spoon2 <- ggplot(df.country_item,
-       mapping = aes(x = factor(country, levels=c("China", "US", "Vietnam")), 
-                     y = responses_theme, 
-                     color = factor(country, levels=c("China", "US", "Vietnam")))) +
-  geom_jitter(stat = "identity", alpha  = .5) +
-  labs(y = "Proportion Thematic Chosen (spoon: fork / sugar)",  
-       x = "Country", 
-       color = "Country") + 
-  stat_summary(fun.data = "mean_cl_boot", 
-               geom = "pointrange") + 
-  scale_y_continuous(limits=c(0.0, 1.0), oob = scales::squish) + 
-  scale_fill_manual(values=c("#D63230", "#1C77C3", "#F39237")) +  
-  scale_color_manual(values=c("#D63230", "#1C77C3", "#F39237")) + 
-  theme(legend.position = "none") + 
-  theme(axis.title = element_text(size=rel(0.75)))
-```
-
-```{r include = FALSE}
-#show 1 triad
-
-df.country_item <- df_main_analysis %>%
-  filter(triad == "cow2")
-
-df.country_item_summ <- df_main_analysis %>%
-  group_by(triad, country) %>%
-  summarize(theme_resp_percent = mean(responses_theme, na.rm = T)) %>%
-  filter(triad == "cow2")
-
-plot.cow2 <- ggplot(df.country_item,
-       mapping = aes(x = factor(country, levels=c("China", "US", "Vietnam")), 
-                     y = responses_theme, 
-                     color = factor(country, levels=c("China", "US", "Vietnam")))) +
-  geom_jitter(stat = "identity", alpha  = .5) +
-  labs(y = "Proportion Thematic Chosen (cow: chicken / grass)",  
-       x = "Country", 
-       color = "Country") + 
-  stat_summary(fun.data = "mean_cl_boot", 
-               geom = "pointrange") + 
-  scale_y_continuous(limits=c(0.0, 1.0), oob = scales::squish) + 
-  scale_fill_manual(values=c("#D63230", "#1C77C3", "#F39237")) +  
-  scale_color_manual(values=c("#D63230", "#1C77C3", "#F39237")) + 
-  theme(legend.position = "none") + 
-  theme(axis.title = element_text(size=rel(0.75)))
-# 
-# +  
-#   geom_bar(data = df.country_item_summ, 
-#            mapping = aes(x = factor(country, levels=c("China", "US", "Vietnam")), 
-#                           y = theme_resp_percent, 
-#                          color = factor(country, levels=c("China", "US", "Vietnam"))), 
-#            stat='identity', alpha = .3, 
-#            fill=c("#D63230", "#1C77C3", "#F39237"))
-```
-
-```{r echo=FALSE, warning = FALSE, fig.width=8, fig.cap="Anecdotal evidence of triad-specific effects.
-Cow-grass-chicken shows significant differences between US-China responding, and between US-Vietnam responding.
-Spoon-sugar-fork shows only a significant difference between US-China responding.
-Hair-comb-beard does not show any significant differences in pairwise comparisons across the three countries."}
-plot.cow2 + plot.spoon2 + plot.hair + 
-    plot_layout(ncol = 3)
-```
-
-We also identified some data quality / quantity issues that are an obstacle to modeling similarity in Vietnamese and Mandarin.
-As stated above, we were not able to find a Mandarin corpus with raw co-occurrences that contains similar magnitude of number of sentences as our English corpus (COCA).
-Additionally, we could only retrieve fastText word vectors for Vietnamese and Mandarin that are trained on both Common Crawl and Wikipedia.
-63% of the articles on Vietnamese Wikipedia and 16% of the Chinese Wikipedia are bot translations from another language (compared to 3% of English Wikipedia).
-This would affect the quality of the word vectors trained on the Vietnamese and Chinese Wikipedia, potentially making them not reflecting the naturally-occurring lexical co-occurrence in the corresponding language.
-
-Our findings raise additional questions for future work: if not differences in taxonomic vs.
-thematic responding, then what differences drive the relativity effects previous studies have observed?
-To what extent are the relativity effects driven by language, and to what extent by culture?
-@Ji2004 established that culture-aligned differences in this paradigm exist, even when the test language is held constant, concluding that “it is culture (independent of the testing language) that led to different grouping styles” in their study.
-Our data provide a cautionary note to this conclusion, suggesting that semantic representations in bilinguals (see @Francis2005 for a review) may have the potential to provide an offline account for cross-context differences in similarity judgments, independent of test language.
-However, there are still many open questions for this account.
-How do semantic associations guide categorization?
-Can they explain taxonomic-thematic differences of the type reported by @Ji2004 and others?
-Can we provide a more specific computational account than the simple frequency model tested here?
-
-Despite these caveats, our findings here demonstrate the plausibility of an alternative perspective on cross-cultural accounts of language, thought, and similarity in the case of taxonomic and thematic reasoning: that it may be the input to similarity judgments, rather than the evaluative process or the conceptualization of similarity that produces variation in similarity reasoning across cultural and linguistic contexts.
-We hope this work provides a foundation for further research probing this question.
-
-[^footnote]:While we discuss cross-cultural variability at the level of countries or larger world areas, these are not cultural monoliths.
-For convenience, we operationalize culture at the level of country, based on where participants were raised.
-It is an open question whether performance in our participant populations (of relatively young and well-educated adults) is representative of the broader country.
-This is especially true for societies with substantial ethnic and cultural variation such as the US.
-We expect that our data is likely to underestimate variation both within and between the countries we sample from.
-
-\newpage
-
-# References
-
-\begingroup
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
-
-<div id="refs" custom-style="Bibliography"></div>
-\endgroup
-
-\newpage
-# Supplemental Information
-
-hi
-```{r echo=TRUE, fig.align="center", fig.cap=c("List of triads used"), fig.show="hold"}
-#include_graphics(c("../../data/SI_triads/SI_triads_1.jpg"))
-include_graphics(c("../../data/SI_triads/SI_triads_1.jpg",
-                   "../../data/SI_triads/SI_triads_2.jpg",
-                   "../../data/SI_triads/SI_triads_3.jpg",
-                   "../../data/SI_triads/SI_triads_4.jpg",
-                   "../../data/SI_triads/SI_triads_5.jpg"))
-```

### 2022-12-14 code/2_combine/2_combine.Rmd
setting up cogsci paper

@@
 ```{r loading data E, warning=FALSE, include=F}
-df.resp_E <- read.csv("../../data/dataUS_excl.csv") %>%
+df.resp_E <- read.csv("../../data/responding/dataUS_excl.csv") %>%
   select(-X)
@@
 ```{r loading data V, include=F}
-df.resp_V <- read.csv("../../data/dataVN_excl.csv") %>%
+df.resp_V <- read.csv("../../data/responding/dataVN_excl.csv") %>%
   select(-X)
@@
 ```{r loading data M, warning=FALSE, include=F}
-df.resp_M <- read.csv("../../data/dataCN_excl.csv") %>%
+df.resp_M <- read.csv("../../data/responding/dataCN_excl.csv") %>%
   select(-X)

### 2022-12-14 code/2_combine/2_combine_filler_assoc.Rmd
setting up cogsci paper

```{r setup, echo = FALSE, include = FALSE}
library("papaja")
library("knitr") # for knitting things
library("tidyverse") # for all things tidyverse
library("car")
library("lme4")
library("patchwork")
library("effsize")
```

```{r get association strengths and triad information}
df.assoc = read_delim("../../data/assoc_strengths.csv",delim='\t',quote = '',escape_backslash = F,escape_double = F) %>%
  select(cue, response, R123.Strength) %>%
  rename(assoc_strength = R123.Strength)

df.filler_E = read.csv("../../data/corpus/corpusEMV_filler.csv") %>% 
  select(cue_E, word1_E, word2_E, cue_M, word1_M, word2_M, cue_V, word1_V, word2_V)
```

```{r combine association strength and triad information}
df.filler_assoc <- left_join(df.filler_E, df.assoc,
                            by = c('cue_E'='cue', 'word1_E'='response')) %>%
  rename(word1_assoc_strength_E = assoc_strength)

df.filler_assoc <- left_join(df.filler_assoc, df.assoc,
                            by = c('cue_E'='cue', 'word2_E'='response')) %>%
  rename(word2_assoc_strength_E = assoc_strength)

#write.csv(df.filler_assoc, "../../data/corpus/fillers_assoc_strength.csv", row.names = FALSE)
```

```{r}
triad_omit <- df.filler_assoc %>%
  filter(is.na(word1_assoc_strength_E) & is.na(word2_assoc_strength_E))
#write.csv(triad_omit$triad, "../../data/fillers_omit_assoc.csv", row.names = FALSE)
```

```{r combine association strength data with responding data}
df = read.csv("../../data/data_filler_USCNVN_ENZHVI.csv") %>%
  select(-X)

#df.triad_assoc <- read.csv("../../data/corpus/corpusE_assoc_strength.csv") %>%
#  select(-X)

df <- left_join(df, df.filler_assoc, 
                by = c("cue_E", "word1_E", "word2_E",
                       "cue_M", "word1_M", "word2_M", 
                       "cue_V", "word1_V", "word2_V"))

write.csv(df, "../../data/data_filler_USCNVN_ENZHVI_assoc_strength.csv", row.names = F)
```

### 2022-12-14 code/3_analysis/3_analysis_compare_freq_cosine.Rmd
setting up cogsci paper

@@
 library("effsize")
-library("Hmisc")
+#library("Hmisc")
 library("dplyr")
@@
           data = df %>% filter(country == "US", 
-                               !(near(theme_match_frequency_E, .Machine$double.eps) & 
-                                  near(tax_match_frequency_E, .Machine$double.eps))),
+                               !(near(theme_frequency_E, .Machine$double.eps) & 
+                                  near(tax_frequency_E, .Machine$double.eps))),
 
@@
 ```
+
+```{r US responding predicted by each corpus model raw co-occurrences, warning=FALSE}
+# Mandarin 
+fit.ZH_CN = glmer(responses_theme ~ theme_freq_prop_M + (1 | subject) + (1 | triad), 
+          data = df %>% filter(country == "China", 
+                               !(near(theme_frequency_M, .Machine$double.eps) & 
+                                  near(tax_frequency_M, .Machine$double.eps))), 
+          family="binomial")
+summary(fit.ZH_CN)
+fit.ZH_CN.anova = Anova(fit.ZH_CN, type = 3)
+
+fit.ZH_CN.anova
+
+fit.ZH_CN_cos = glmer(responses_theme ~ theme_cosine_prop_M + (1 | subject) + (1 | triad), 
+          data = df %>% filter(country == "China", 
+                               !(near(theme_frequency_M, .Machine$double.eps) & 
+                                  near(tax_frequency_M, .Machine$double.eps))),
+
+          family="binomial")
+summary(fit.ZH_CN_cos)
+fit.ZH_CN_cos.anova = Anova(fit.ZH_CN_cos, type = 3)
+fit.ZH_CN_cos.anova
+
+fit.ZH_CN_compare_freq_cos = anova(fit.ZH_CN, fit.ZH_CN_cos, type = 3)
+fit.ZH_CN_compare_freq_cos
+
+```
+# Does adding country help with the model (compared to with just English co-occurrence)? 
+```{r}
+fit.language = glmer(responses_theme ~ theme_freq_prop_E + (1 | subject) + (1 | triad), 
+          data = df %>% filter(!(near(theme_frequency_E, .Machine$double.eps) & 
+                                  near(tax_frequency_E, .Machine$double.eps))),
+
+          family="binomial")
+summary(fit.language)
+fit.language.anova = Anova(fit.language, type = 3)
+fit.language.anova
+
+fit.country_language = glmer(responses_theme ~ theme_freq_prop_E * country + (1 | subject) + (1 | triad), 
+          data = df %>% filter(!(near(theme_frequency_E, .Machine$double.eps) & 
+                                  near(tax_frequency_E, .Machine$double.eps))),
+
+          family="binomial")
+summary(fit.country_language)
+
+fit.country_language.anova = Anova(fit.country_language, type = 3)
+fit.country_language.anova
+
+fit.country_language_compare = anova(fit.language, fit.country_language, type = 3)
+fit.country_language_compare
+```
+
+Adding country improves the model (thematic proportion of lexical co-occurrence, country, and their interaction were all significant predictors).

### 2022-12-14 code/3_analysis/3_analysis_filler_assoc.Rmd
setting up cogsci paper

```{r setup, echo = FALSE, include = FALSE}
library("papaja")
library("knitr") # for knitting things
library("tidyverse") # for all things tidyverse
library("car")
library("lme4")
library("patchwork")
library("effsize")
library("Hmisc")
library("dplyr")

# these options here change the formatting of how comments are rendered
opts_chunk$set(
  comment = "",
  results = "hold",
  fig.show = "hold")

# set the default ggplot theme 
theme_set(theme_classic())

r_refs("r-references.bib")
r_refs("references/packages.bib")

```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r read in data}
df <- read.csv("../../data/data_filler_USCNVN_ENZHVI_assoc_strength.csv")
fillers_omit_assoc <- read.csv("../../data/fillers_omit_assoc.csv") %>%
  pull(x)

#NO FILLERS NEEDED TO BE OMITTED
#triads_omit_freq <- read.csv("../../data/triads_omit.csv") %>%
#  pull(x)
```

```{r change NA to epsilon}
df <- df %>%
  mutate(word1_assoc_strength_E = ifelse(is.na(word1_assoc_strength_E), 
                                  .Machine$double.eps, word1_assoc_strength_E),
         word2_assoc_strength_E = ifelse(is.na(word2_assoc_strength_E), 
                                  .Machine$double.eps, word2_assoc_strength_E)) %>%
  mutate(word1_assoc_strength_prop_E = word1_assoc_strength_E / (word1_assoc_strength_E + word2_assoc_strength_E))
```

# Correlation between assoc strength prediction and response data
```{r}
df.cue_country_freq <- df %>%
  group_by(cue_E, country, word1_assoc_strength_prop_E) %>%
  dplyr::summarize(emp_word1_prop = mean(responses_word1))
ggplot(data = df.cue_country_freq %>% filter(country == "US"), 
        mapping = aes(x = emp_word1_prop, 
                     y = word1_assoc_strength_prop_E,
                     label = cue_E)) +
   geom_text() + 
   geom_smooth(method = "lm") +
   labs(x = "Proportion Word1 Chosen (US)", 
        y = "Proportion Word1 Predicted by Assoc Strength (English)") + 
  theme(axis.title = element_text(size=rel(0.75)))
```

# Does adding association improve the model?
```{r US responding predicted by each corpus model raw co-occurrences, warning=FALSE}
# English 
fit.EN_US = glmer(responses_word1 ~ word1_match_frequency_prop_E + (1 | subject) + (1 | cue_E), 
          data = df %>% filter(country == "US", 
                               !(cue_E %in% fillers_omit_assoc)), 
          family="binomial")
summary(fit.EN_US)
fit.EN_US.anova = Anova(fit.EN_US, type = 3)

fit.EN_US.anova

# English with association strengths
fit.EN_US_assoc = glmer(responses_word1 ~ word1_match_frequency_prop_E + word1_assoc_strength_E + (1 | subject) + (1 | cue_E), 
          data = df %>% filter(country == "US", 
                               !(cue_E %in% fillers_omit_assoc)), 
          family="binomial")
summary(fit.EN_US_assoc)
fit.EN_US_assoc.anova = Anova(fit.EN_US_assoc, type = 3)

fit.EN_US_assoc.anova

fit.EN_US_assoc_compare = anova(fit.EN_US, fit.EN_US_assoc, type = 3)
fit.EN_US_assoc_compare
```

Adding association strengths does not improve the model significantly (p = 0.07)

# Does association strength predict response data?
```{r only association strengths}
# English 
fit.EN_US_assoc_only = glmer(responses_word1 ~ word1_assoc_strength_E + (1 | subject) + (1 | cue_E), 
          data = df %>% filter(country == "US", 
                               !(cue_E %in% fillers_omit_assoc)),
          family="binomial")
summary(fit.EN_US_assoc_only)
fit.EN_US_assoc_only.anova = Anova(fit.EN_US_assoc_only, type = 3)

fit.EN_US_assoc_only.anova

fit.EN_US_assoc_only_compare = anova(fit.EN_US, fit.EN_US_assoc_only, type = 3)
fit.EN_US_assoc_only_compare
```

Having just the association strength is a significant predictor. But not significantly better than only the language co-occurrence model.

Yes.

### 2022-12-14 code/3_analysis/3_paper_cogsci.Rmd
setting up cogsci paper

--- 2022-09-28 code/3_analysis/3_analysis.Rmd
@@
 
-hi
 ```{r echo=TRUE, fig.align="center", fig.cap=c("List of triads used"), fig.show="hold"}

### 2022-12-14 code/4_paper/manuscript/manuscript.Rmd
setting up cogsci paper

--- 2022-12-14 code/3_analysis/3_paper_cogsci.Rmd
@@
 ---
-title             : "Is It Language or Is It Culture? Re-examining Cross-Cultural Similarity Judgments Using Lexical Co-Occurrence"
-shorttitle        : "Re-examining Cross-Cultural Similarity Judgments Using Lexical Co-Occurrence"
+title: "How to Make a Proceedings Paper Submission"
+bibliography: library.bib
+csl: apa6.csl
+document-params: "10pt, letterpaper"
 
-author: 
-  - name          : "Khuyen Le"
-    affiliation   : "1,2"
-    corresponding : yes    # Define only one corresponding author
-    email         : "khuyenle@stanford.edu"
+author-information: > 
+    \author{{\large \bf Morton Ann Gernsbacher (MAG@Macc.Wisc.Edu)} \\ Department of Psychology, 1202 W. Johnson Street \\ Madison, WI 53706 USA
+    \AND {\large \bf Sharon J.~Derry (SDJ@Macc.Wisc.Edu)} \\ Department of Educational Psychology, 1025 W. Johnson Street \\ Madison, WI 53706 USA}
 
-affiliation:
-  - id            : "1"
-    institution   : "Psychology Department"
-  - id            : "2"
-    institution   : "University of California, San Diego"
-
-abstract: |
+abstract: >
   Is “cow” more closely related to “grass” or “chicken”?
@@
 
-  <!-- https://tinyurl.com/ybremelq -->
+keywords: >
+    similarity; culture; language; semantics; lexical co-occurrence; variation
 
-keywords          : "similarity, culture, language, semantics, lexical co-occurrence, variation"
-wordcount         : "150"
+output: cogsci2016::cogsci_paper
+#final-submission: \cogscifinalcopy
+---
 
-bibliography      : ["r-references.bib", "references/references.bib"]
+```{r global_options, include=FALSE}
+knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, 
+                      fig.pos = "tb", fig.path='figs/',
+                      echo=F, warning=F, cache=F, 
+                      message=F, sanitize = T)
+```
 
-floatsintext      : yes
-figurelist        : no
-tablelist         : yes
-footnotelist      : no
-linenumbers       : no
-mask              : no
-draft             : no
-header-includes:
-  - \raggedbottom
-
-documentclass     : "apa6"
-classoption       : "man"
-output            : papaja::apa6_pdf
-
----
+```{r, libraries}
+library(png)
+library(grid)
+library(ggplot2)
+library(xtable)
+```
 
@@
 
-r_refs("r-references.bib")
-r_refs("references/packages.bib")
+#r_refs("r-references.bib")
+#r_refs("references/packages.bib")
 
@@
 
-# Methods 
-```{r get exclusion results from 1_exclusions.Rmd}
-source("../1_exclusions/1_exclusionsCN.Rmd")
-source("../1_exclusions/1_exclusionsUS.Rmd")
-source("../1_exclusions/1_exclusionsVN.Rmd")
+## Two-column images
+
+You can read local images using png package for example and plot 
+it like a regular plot using grid.raster from the grid package. 
+With this method you have full control of the size of your image. **Note: Image must be in .png file format for the readPNG function to work.**
+
+You might want to display a wide figure across both columns.
+To do this, you change the `fig.env` chunk option to `figure*`.
+To align the image in the center of the page, set `fig.align` option to `center`.
+To format the width of your caption text, you set the `num.cols.cap` option to `2`.
+
+```{r 2-col-image, fig.env = "figure*", fig.pos = "h", fig.width=4, fig.height=2, fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "This image spans both columns.
+And the caption text is limited to 0.8 of the width of the document."}
+img <- png::readPNG("figs/walrus.png")
+grid::grid.raster(img)
 ```
 
-```{r demog_E, TODO: move outside, include = F}
-demog <- c("demog-dropdown", "demog-multi-choice", "demog-free-response", "demog-multi-select")
-df.demog_E <- df.resp_E %>%
-  filter(trial_type %in% demog) 
-#write.csv(data_demog, "data_anon_demog_0201.csv")
+## One-column images
 
-AGE = 97 #index for age answer
-GENDER = 115 #index for gender answer
-split_responses <- function(responses) {
-  responses <- as.character(responses)
-  response_list <- unlist(strsplit(responses, ',|:'))
-  response_list <- response_list[seq(1, length(response_list))]
-  response_list <- gsub("}", "", response_list)
-  response_list <- gsub("\"", "", response_list)
-  return(response_list)
-}
+Single column is the default option, but if you want set it explicitly, set `fig.env` to `figure`. Notice that the `num.cols` option for the caption width is set to `1`.
 
-get_age <- Vectorize(function(responses) {
-  responses <- split_responses(responses)
-  if(responses[AGE-1] != "A0") {warnings("cannot find age answer")}
-  else{return (responses[AGE])}
-})
-
-get_gender <- Vectorize(function(responses) {
-  responses <- split_responses(responses)
-  if(responses[GENDER-1] != "A1") {warnings("cannot find gender answer")}
-  else{return (responses[GENDER])}
-})
-
-df.age_gender_E <- df.demog_E %>%
-  filter(variable_type == "demog_age_gender_ethnic") %>%
-  select(subject, responses) %>%
-  mutate(age = as.numeric(get_age(responses))) %>%
-  mutate(age = as.numeric(age)) %>%
-  mutate(gender = get_gender(responses))
-
-df.age_gender_E_summ <- df.age_gender_E %>%
-  summarize(mean_age = mean(age), 
-            median_age = median(age), 
-            sd_age = sd(age))
+```{r image, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=2, fig.height=2, set.cap.width=T, num.cols.cap=1, fig.cap = "One column image."}
+img <- png::readPNG("figs/lab_logo_stanford.png")
+grid::grid.raster(img)
 ```
 
-```{r demog_V, TODO: move outside, include = F}
-demog <- c("demog-dropdown", "demog-multi-choice", "demog-free-response", "demog-multi-select")
-df.demog_V <- df.resp_V %>%
-  filter(trial_type %in% demog)
+## R Plots
 
-AGE = 97 #index for age answer
-GENDER = 115 #index for gender answer
-split_responses <- function(responses) {
-  responses <- as.character(responses)
-  response_list <- unlist(strsplit(responses, ',|:'))
-  response_list <- response_list[seq(1, length(response_list))]
-  response_list <- gsub("}", "", response_list)
-  response_list <- gsub("\"", "", response_list)
-  return(response_list)
-}
+You can use R chunks directly to plot graphs. And you can use latex floats in the
+fig.pos chunk option to have more control over the location of your plot on the page.
+For more information on latex placement specifiers see **[here](https://en.wikibooks.org/wiki/LaTeX/Floats,_Figures_and_Captions)**
 
-get_age <- Vectorize(function(responses) {
-  responses <- split_responses(responses)
-  if(responses[AGE-1] != "A0") {warnings("cannot find age answer")}
-  else{return (responses[AGE])}
-})
+```{r plot, fig.env="figure", fig.pos = "H", fig.align = "center", fig.width=2, fig.height=2, fig.cap = "R plot" }
+x <- 0:100
+y <- 2 * (x + rnorm(length(x), sd = 3) + 3)
 
-get_gender <- Vectorize(function(responses) {
-  responses <- split_responses(responses)
-  if(responses[GENDER-1] != "A1") {warnings("cannot find gender answer")}
-  else{return (responses[GENDER])}
-})
-
-df.age_gender_V <- df.demog_V %>%
-  filter(variable_type == "demog_age_gender_ethnic") %>%
-  select(subject, responses) %>%
-  mutate(age = as.numeric(get_age(responses))) %>%
-  mutate(age = as.numeric(age)) %>%
-  mutate(gender = get_gender(responses))
-
-df.age_gender_V_summ <- df.age_gender_V %>%
-  summarize(mean_age = mean(age), 
-            median_age = median(age), 
-            sd_age = sd(age))
+ggplot2::ggplot(data = data.frame(x, y), 
+                aes(x = x, y = y)) + 
+  geom_point() + 
+  geom_smooth(method = "lm")
 ```
 
-```{r demog_M, TODO: MOVE outside, include = F}
-demog <- c("demog-dropdown", "demog-multi-choice", "demog-free-response", "demog-multi-select")
-df.demog_M <- df.resp_M %>%
-  filter(trial_type %in% demog) 
-#write.csv(data_demog, "data_anon_demog_0201.csv")
+## Tables
 
-AGE = 97 #index for age answer
-GENDER = 115 #index for gender answer
-split_responses <- function(responses) {
-  responses <- as.character(responses)
-  response_list <- unlist(strsplit(responses, ',|:'))
-  response_list <- response_list[seq(1, length(response_list))]
-  response_list <- gsub("}", "", response_list)
-  response_list <- gsub("\"", "", response_list)
-  return(response_list)
-}
+Number tables consecutively; place the table number and title (in
+10 point) above the table with one line space above the caption and
+one line space below it, as in Table 1. You may float
+tables to the top or bottom of a column, set wide tables across both
+columns.
 
-get_age <- Vectorize(function(responses) {
-  responses <- split_responses(responses)
-  if(responses[AGE-1] != "A0") {warnings("cannot find age answer")}
-  else{return (responses[AGE])}
-})
+You can use the xtable function in the xtable package.
 
-get_gender <- Vectorize(function(responses) {
-  responses <- split_responses(responses)
-  if(responses[GENDER-1] != "A1") {warnings("cannot find gender answer")}
-  else{return (responses[GENDER])}
-})
+```{r xtable, results="asis"}
+n <- 100
+x <- rnorm(n)
+y <- 2*x + rnorm(n)
+out <- lm(y ~ x)
 
-df.age_gender_M <- df.demog_M %>%
-  filter(variable_type == "demog_age_gender_ethnic") %>%
-  select(subject, responses) %>%
-  mutate(age = as.numeric(get_age(responses))) %>%
-  mutate(age = as.numeric(age)) %>%
-  mutate(gender = get_gender(responses))
+tab1 <- xtable::xtable(summary(out)$coef, digits=c(0, 2, 2, 1, 2), 
+                       caption = "This table prints across one column.")
 
-df.age_gender_M_summ <- df.age_gender_M %>%
-  summarize(mean_age = mean(age), 
-            median_age = median(age), 
-            sd_age = sd(age))
-```
-## Participants
-We recruited `r length(unique(df.ppts_finished_E$subject))` participants from the US, `r length(unique(df.ppts_finished_V$subject))` participants from Vietnam, and `r length(unique(df.ppts_finished_M$subject))` participants from mainland China.
-US participants were recruited through snowball sampling seeded with Stanford email lists, Vietnam participants were recruited through snowball sampling seeded with Vietnam-based student groups on Facebook, and mainland China participants were recruited through snowball smapling seeded with group chats on WeChat.
-US participants were compensated with $5 gift certificates (USD), VN participants received 50,000₫ (VND) in phone credit, and mainland China participants received 25CNY through WeChat credit transfer.
-
-We excluded `r length(unique(df.ppts_finished_E$subject)) - length(unique(df.ppts_att_E$subject))` US participants, `r length(unique(df.ppts_finished_V$subject)) - length(unique(df.ppts_att_V$subject))` Vietnam participants, and `r length(unique(df.ppts_finished_M$subject)) - length(unique(df.ppts_att_M$subject))` China participants who did not answer all attention checks correctly.
-We followed 4 exclusion criteria that aim to retain only participants who are influenced by one culture: (1) non-native speakers of English and Vietnamese, respectively, (2) fluent in at least one of the other two study languages (Vietnamese for US participants, English for Vietnamese participants and Chinese participants), (3) have lived outside of the test country (US, Vietnam, or China) for more than two years, and (4) have significant international experience (more than 6 international experiences of 2 days or longer.) We did not use a particular criterion for a language if it would exclude 25% or more of any one sample.
-In this round of exclusion, we excluded `r length(unique(df.ppts_att_E$subject)) - length(unique(df.resp_E$subject))` US, `r length(unique(df.ppts_att_V$subject)) - length(unique(df.resp_V$subject))` Vietnam participants, and `r length(unique(df.ppts_att_M$subject)) - length(unique(df.resp_M$subject))` China participants.
-After these exclusions, the US sample included `r length(unique(df.resp_E$subject))` participants (`r df.age_gender_E %>% filter(gender == "Male") %>% count()`M, `r df.age_gender_E %>% filter(gender == "Female") %>% count()`F, `r df.age_gender_E %>% filter(gender == "Non-binary") %>% count()` non-binary, `r df.age_gender_E %>% filter(gender == "Decline to answer") %>% count()` other), with mean age = `r round(df.age_gender_E_summ$mean_age, 2)` (SD = `r round(df.age_gender_E_summ$sd_age, 2)`) and median age = `r df.age_gender_E_summ$median_age`.
-The Vietnam sample included `r length(unique(df.resp_V$subject))` participants (`r df.age_gender_V %>% filter(gender == "Nam") %>% count()`M, `r df.age_gender_V %>% filter(gender == "Nữ") %>% count()`F), with mean age = `r round(df.age_gender_V_summ$mean_age, 2)` (SD = `r round(df.age_gender_V_summ$sd_age, 2)`) and median age = `r df.age_gender_V_summ$median_age`.
-The China sample included `r length(unique(df.resp_M$subject))` participants (`r df.age_gender_M %>% filter(gender == "男性") %>% count()`M, `r df.age_gender_M %>% filter(gender == "女性") %>% count()`F), with mean age = `r round(df.age_gender_M_summ$mean_age, 2)` (SD = `r round(df.age_gender_M_summ$sd_age, 2)`) and median age = `r df.age_gender_M_summ$median_age`.
-
-Notably, we lost a majority of our Vietnam participants (more than 60%) in the attention check exclusion.
-One reason we suspect why this might have happened is because our Vietnam participants are less familiar with research surveys and attention check questions, and thus might have thought too much about the attention check questions.
-We carried out an exploratory analysis where we used a less stringent attention check exclusion (covered in the final part of the Results & Analysis section).
-To preview our findings for this analysis, we did not find any difference in significant results when compared with the main analysis.
-
-## Stimuli
-We adapted stimuli from previous studies to create a set of test triads consisting of a cue, with one thematic and one taxonomic match option.
-For example, “cow,” “grass,” and “chicken,” where “cow” is the cue, “grass” is the thematic match, and “chicken” the taxonomic match.
-We included 105 such triads, a superset including triads pulled from supplemental information and in-text examples across the literature, and others that we adapted or created (see SI for the full list of stimuli and sources).
-We selected triads on the basis of cultural familiarity in the US, Vietnam, and China.
-The triads were originally in English; they were translated to Vietnamese and Mandarin by a fluent bilingual speaker in each language.
-The translations were then checked for accuracy after backtranslation to English by another fluent bilingual in each language who was naive to the original English versions.
-
-Each participant completed all 105 triads in sets of 21 trials at a time (10 test triads, 10 filler triads, and 1 attention check per page), by selecting the match most related to the cue (“Which thing is most closely related to the bolded item?” or "Thu nào liên quan nhat voi thu đuoc in đam?").
-The test triads were presented with 105 filler triads mixed in, to obscure the taxonomic-thematic two-answer forced choice structure of the test stimuli and reduce the likelihood that participants would become aware of the design.
-The filler triads were groups of three semantically related words, but where the match options were not distinguished by thematic vs.
-taxonomic similarity, e.g., cue “bird” with match options “lizard” and “toad.” Additionally, we included 10 attention check trials, which were formatted like the test and filler triads but included an instruction instead of a cue item, e.g., “Choose wife” with match options “wife” and “husband.” In total, each participant completed 210 similarity judgments and 10 attention check questions, with triads presented in randomized orders that varied between subjects.
-
-## Corpus model 
-Our general approach is to build a model of similarity that is based on collocation counts in each language.
-
-### Raw lexical co-occurrences
-To give an intuition for our model, consider the cow-grass-chicken triad: we counted how many times “cow” and “grass” co-occur within a window of text in each corpus, and compare this to how many times “cow” and “chicken” co-occur.
-Our similarity prediction is then proportional to the relative frequency of these pairs.
-For example, if the thematic cow-grass match accounts for 30% of collocations for this triad (with cow-chicken making up the other 70%), then our model predicts, correspondingly, that 30% of responses to the triad will be grass, and the other 70% chicken.
-We then use a mixed-effects regression to evaluate how well each corpus collocate model predicts participants’ similarity judgments, across triads and languages.
-
-#### Collocate retrieval and coding
-For our English co-occurrence metric, we used the online interface of the Corpus of Contemporary American English [@COCA] to retrieve collocation counts.
-We recorded the raw count of times that any cue-match pair (e.g., cow-grass or cow-chicken) co-occur in a window of 19 words, which is the maximum window size in the online interface, and closest to the sentence co-occurrence metric in our VI corpus collocation counts.
-
-To determine Vietnamese co-occurrence, we used the raw frequency of sentence co-occurrences from a subset of the Vietnamese corpus in the Leipzig Corpora Collection [@VICorpus]; this corpus includes 70 million Vietnamese sentences, but our corpus data comes from a 1 million sentence subset for which co-occurrence counts are available for download.
-Vietnamese makes very frequent use of compositional morphology but the written language  uses spacing to delineate syllable boundaries rather than word boundaries.
-Accordingly, collocate searches returned instances of both target terms and many morphologically related, but distinct, words.
-We included in our counts any instances of the target term or close semantic neighbors containing the same morpheme(s) as long as they entailed a likely literal reference to the target term.
-For example, our search for collocates of the term “gà” (chicken) also returned “gà mái,” a distinct word for female chickens.
-Despite being a different word, “gà mái” both includes the morpheme for “chicken” and entails reference to a chicken.
-Accordingly, instances of both “gà” and “gà mái” were included in our collocate count for “chicken.” Some compounds do not meet this criteria, and were excluded from collocate counts.
-For example “trái cây” (tree.fruits) includes the same syllable as the word “cây” (tree), but refers to fruit that comes from trees, not the trees themselves, and was therefore excluded from our collocate counts for “tree.”
-
-We were unable to obtain a Mandarin corpus with similar number of sentences as the aforementioned English and Vietnamese corpora, hence we did not include any analysis based on raw lexical co-occurrences with Mandarin.
-
-#### Collocate similarity model
-From the raw co-occurrence counts of each triad, we calculated the thematic co-occurrence ratio as the number of thematic co-occurrences over the sum of thematic and taxonomic co-occurrences.
-We did this for both the English and Vietnamese corpus co-occurrence counts.
-In this way, we obtained predictions for 73 of 105 triads from the Vietnamese corpus and 104 of 105 triads from English.
-We therefore limited all analyses reported here to the subset of triads for which our corpus-based model can make meaningful predictions, meaning triads that have at least one non-zero collocate count (either thematic or taxonomic match).
-We replaced any remaining zero collocate counts with $\epsilon$ to account for sparsity in the corpus data.
-We then tested whether these simple relative frequency models predict US and VN responding.
-
-### Cosine distance of word vectors
-To give an intuition for our model, consider again the cow-grass-chicken triad: we retrieved word vectors for "cow" and "grass", and calculate the cosine distance between these vectors.
-Similarly, we retrieved vectors for "cow" and "chicken" and calculate the cosine distance between them.
-Our similarity prediction is then inversely proportional to the cosine distance of these pairs.
-This is because a larger cosine distance means the word vectors are further apart, and thus the words are less similar.
-For example, if the cosine distance of thematic cow-grass is 0.7 and the cosine distance of taxonomic cow-chicken is 0.3, then our model predicts, correspondingly, that 30% of responses to the triad will be grass, and the other 70% chicken.
-We then use a mixed-effects regression to evaluate how well each corpus model predicts participants’ similarity judgments, across triads and languages.
-
-#### Collocate retrieval
-We use the fastText pre-trained models of English, Mandarin, and Vietnamese in @Grave2018.
-These models are trained on Common Crawl and Wikipedia using We distribute pre-trained word vectors for 157 languages, trained on Common Crawl and Wikipedia using fastText.
-These models were trained using a Continuous Bag of Words (CBOW) with position-weights and a window of size 5.
-The models use character n-grams of length 5 and 10  negative examples.From the aforementioned models, we retrieve the word vectors (dimension 300) for each word we are interested in.
-
-#### Collocate similarity model
-From the word vectors, we calculated the cosine distance between each cue-thematic match (thematic cosine distance) and cue-taxonomic match (taxonomic cosine distance), using the spatial.distance.cosine function from the SciPy package [@2020SciPy].
-We then calculated the thematic cosine distance proportion as thematic cosine distance over the sum of taxonomic cosine distance and thematic cosine distance.
-We did this for all three corpora.
-We were able to obtain predictions for all triads in all languages.
-
-## Data analysis
-We used `r cite_r("r-references.bib")` for all our analyses.
-
-# Results
-```{r combine corpus and behavior data, include = F}
-#source("../2_combine/2_combine.Rmd")
-df <- read.csv("../../data/data_USCNVN_ENZHVI.csv")
+print(tab1, type="latex", comment = F, table.placement = "H")
 ```
 
-## Do we extend previous work reporting a preference for taxonomic matching in the US and thematic matching in Asia?
+# Acknowledgements
 
-```{r warning=FALSE, include=FALSE, paged.print=TRUE}
-df.country <- df %>%
-  group_by(subject, country) %>%
-  summarize(theme_resp_percent = mean(responses_theme, na.rm = T))
-
-df.country_sum <- df.country %>%
-  group_by(country) %>%
-  summarize(mean_theme_resp_percent = mean(theme_resp_percent), 
-            sd_theme_resp_percent = sd(theme_resp_percent))
-
-fit.country = glmer(responses_theme ~ country + (1 | subject) + (country | triad), 
-                    data = df, 
-                    family = "binomial")
-summary(fit.country) 
-fit.country.anova = Anova(fit.country, type=3)
-
-fit.country_EN_VN = glmer(responses_theme ~ country + (1 | subject) + (country | triad), 
-                    data = df %>% filter(country != "China"),
-                    family = "binomial")
-summary(fit.country_EN_VN) 
-```
-The group means of proportion of thematic response in mainland China is the highest (M = `r round((df.country_sum %>% filter(country == "China"))$mean_theme_resp_percent, 2)`, SD = `r round((df.country_sum %>% filter(country == "China"))$sd_theme_resp_percent, 2)`), followed by the groups means in Vietnam (M = `r round((df.country_sum %>% filter(country == "Vietnam"))$mean_theme_resp_percent, 2)`, SD = `r round((df.country_sum %>% filter(country == "Vietnam"))$sd_theme_resp_percent, 2)`), which is slightly higher than that of the US (M = `r round((df.country_sum %>% filter(country == "US"))$mean_theme_resp_percent, 2)`, SD = `r round((df.country_sum %>% filter(country == "US"))$sd_theme_resp_percent, 2)`).
-
-```{r echo=FALSE, warning=FALSE, fig.cap="Proportion of thematic responses by country.
-Only US-China responding comparison shows a siginficant difference.
-We could not extend this to US-Vietnam responding comparison."}
-
-#show violin plot
-ggplot(df.country,
-       mapping = aes(x = factor(country, levels=c("China", "US", "Vietnam")), 
-                     y = theme_resp_percent, 
-                     color = factor(country, levels=c("China", "US", "Vietnam")))) +
-  geom_violin() +
-  geom_jitter(height = 0, 
-              alpha = 0.3) +  
-  stat_summary(fun.data = "mean_cl_boot", 
-               geom = "pointrange") + 
-  labs(y = "Proportion Thematic Chosen", 
-       x = "Country", 
-       color = "Country") + 
-  scale_color_manual(values=c("#D63230", "#1C77C3", "#F39237"))
-```
-
-```{r correlation of country response, echo=FALSE, warning=FALSE}
-#US-China, US-Vietnam, China-Vietnam
-df.triad_country <- df %>%
-  group_by(triad, country) %>%
-  summarize(emp_theme_prop = mean(responses_theme))
-
-df.triad_country <- pivot_wider(data = df.triad_country, 
-                                names_from = country, 
-                                values_from = emp_theme_prop)
-plotUSCN = ggplot(data = df.triad_country,
-                  mapping = aes(x = US, 
-                                y = China, 
-                                label = triad)) +
-   geom_text() + 
-   geom_smooth(method = "lm") +
-   labs(x = "Proportion Thematic Chosen (US)", 
-        y = "Proportion Thematic Chosen (China)") + 
-   xlim(0, 1) + 
-   ylim(0, 1) + 
-  theme(axis.title = element_text(size=rel(0.75)))
-
-plotUSVN = ggplot(data = df.triad_country,
-                  mapping = aes(x = US, 
-                                y = Vietnam, 
-                                label = triad)) +
-   geom_text() + 
-   geom_smooth(method = "lm") +
-   labs(x = "Proportion Thematic Chosen (US)", 
-        y = "Proportion Thematic Chosen (Vietnam)") + 
-   xlim(0, 1) + 
-   ylim(0, 1)  + 
-  theme(axis.title = element_text(size=rel(0.75)))
-
-plotCNVN = ggplot(data = df.triad_country,
-                  mapping = aes(x = Vietnam,
-                                y = China, 
-                                label = triad)) +
-   geom_text() + 
-   geom_smooth(method = "lm") +
-   labs(x = "Proportion Thematic Chosen (Vietnam)", 
-        y = "Proportion Thematic Chosen (China)") + 
-   xlim(0, 1) + 
-   ylim(0, 1)  + 
-  theme(axis.title = element_text(size=rel(0.75)))
-
-corr.USCN = apa_print(cor.test(df.triad_country$US, 
-                  df.triad_country$China, na.rm=T))
-
-corr.USVN = apa_print(cor.test(df.triad_country$US, 
-                  df.triad_country$Vietnam, na.rm=T))
-
-corr.CNVN = apa_print(cor.test(df.triad_country$China, 
-                  df.triad_country$Vietnam, na.rm=T))
-```
-
-```{r warning = F, fig.width = 8, fig.cap="Correlation between proportion thematic chosen by US-China participants, US-Vietnam participants, and China-Vietnam participants.
-All three comparisons show strong correlation, suggesting a strong signal of universality across cultural contexts regarding similarity judgments"}
-plotUSCN + plotUSVN + plotCNVN +
-  plot_layout(ncol = 3)
-```
-
-With a Pearson correlation test, we observed high correlations between thematic responding across all three countries.
-The proportion of US thematic responding is strongly correlated with thematic responding in China, `r corr.USCN$full_result`.
-The proportion of US thematic responding is strongly correlated with thematic responding in Vietnam, `r corr.USVN$full_result`.
-Likewise, the proportion of China thematic response is strongly correlated with thematic responding in Vietnam, `r corr.CNVN$full_result`.
-This points to a strong signal of universality across cultural contexts regarding similarity judgments.
-
-```{r USCN effect size comparison, include=FALSE}
-USCN_cohen <- cohen.d(df.triad_country$China, df.triad_country$US)
-```
-
-For comparison with previous work, we also included an effect size comparison for the difference in US-China thematic response data (though this was not a planned analysis).
-The effect size for this analysis was d = `r USCN_cohen$estimate`, a small effect size.
-This is smaller than the effect size from @Ji2004, even when we are unable to make a direct comparison.
-Calculating the effect size from the ANOVA reported in @Ji2004 between US participants tested in English and mainland China participants tested in English (both groups tested in the US) yields a Cohen's d = 0.81.
-@Ji2004 reported that mean thematic response for mainland China participants tested in Mandarin Chinese is higher than for those tested in English, so the effect size for a comparison between mainland China participants tested in Mandarin Chinese and US participants tested in English (parallel to our comparison) would likely have yielded an even larger effect size than 0.814.
-It is possible that we failed to replicate the magnitude of effect from @Ji2004 because the previous study calculated their dependent variable as frequency of thematic responses minus frequency of taxonomic responses, whereas our dependent variable is proportion of thematic response over total number of responses.
-
-To test for cross-context differences in similarity judgments between the countries, we ran a mixed-effects logistic regression predicting triad responding (taxonomic or thematic) with country (US, China, or Vietnam) as a fixed effect.
-As random effects, we included an intercept per subject and one per triad, as well as by-triad random slopes for country to account for variation in the country effect across triads.
-In R syntax, the model is: response ~ country + (1 | subject) + (country | triad).
-
-Overall, there is a significant effect of country on proportion of thematic responses ($\chi^2$(`r fit.country.anova["country", "Df"]`) = `r round(fit.country.anova["country", "Chisq"], 2)`, p < .001).
-However, this effect is driven by the difference between US and China responding ($\beta$ = `r round(fixef(fit.country)["countryUS"], 2)`, p < .001).
-There is no statistical difference between the Vietnam and China responding ($\beta$ = `r round(fixef(fit.country)["countryVietnam"], 2)`, p = `r round(as.data.frame(summary(fit.country)[["coefficients"]])["countryVietnam", "Pr(>|z|)"], 2)`), and the US and Vietnam responding ($\beta$ = `r round(fixef(fit.country_EN_VN)["countryVietnam"], 2)`, p = `r round(as.data.frame(summary(fit.country_EN_VN)[["coefficients"]])["countryVietnam", "Pr(>|z|)"], 3)`).
-
-On this analysis, we do not find support that the US-China tendencies toward taxonomic and thematic responding (respectively) extend to the US-Vietnam comparison.
-Accordingly, we cannot speak to overall biases toward thematic responding across Asian cultural contexts broadly, but we do replicate the differences documented by @Ji2004 between the US and China.
-However, in our corpus model comparison, we do find evidence for different, more fine-grained variation in similarity judgments between the US and Vietnam.
-
-## Can the differences in similarity judgments between English, Mandarin and Vietnamese speakers be explained by variation in lexical statistics?
-### Is responding in each cultural context predicted by the corresponding lexical statistics (raw co-occurrences and cosine distance)? 
-```{r Pearson correlation between raw co-occurrences of corpora and responding, warning=FALSE, include=FALSE}
-
-#raw co-occurrences
-df.triad_country_freq <- df %>%
-  filter(!(triad %in% triads_omit)) %>% # omit triads that do not have meaningful prediction (at least 1 non-zero prediction in both languages)
-  group_by(triad, country, theme_freq_prop_E, theme_freq_prop_V, theme_freq_prop_M) %>%  # not working 
-  summarize(emp_theme_prop = mean(responses_theme))
-df.triad_country_freq   #sanity
-
-df.triad_country_freq_E <- df.triad_country_freq %>%
-  filter(country == "US")
-
-#plotting English corpus against US responding data
-plotE = ggplot(data = df.triad_country_freq_E,
-        mapping = aes(x = emp_theme_prop,
-                     y = theme_freq_prop_E,
-                     label = triad)) +
-   geom_text() +
-   geom_smooth(method = "lm") +
-   labs(x = "Proportion Thematic Chosen (US)",
-        y = "Proportion Thematic Predicted (English)")
-plotE
-
-df.triad_country_freq_V <- df.triad_country_freq %>%
-  filter(country == "Vietnam")
-
-#plotting Vietnamese corpus against VN responding data
-plotV = ggplot(data = df.triad_country_freq_V,
-        mapping = aes(x = emp_theme_prop,
-                     y = theme_freq_prop_V,
-                     label = triad)) +
-   geom_text() +
-   geom_smooth(method = "lm") +
-   labs(x = "Proportion Thematic Chosen (Vietnam)",
-        y = "Proportion Thematic Predicted (Vietnamese)")
-plotV
-
-df.triad_country_freq_M <- df.triad_country_freq %>%
-  filter(country == "China")
-
-#plotting China corpus against CN responding data
-plotM = ggplot(data = df.triad_country_freq_M,
-        mapping = aes(x = emp_theme_prop,
-                     y = theme_freq_prop_M,
-                     label = triad)) +
-   geom_text() +
-   geom_smooth(method = "lm") +
-   labs(x = "Proportion Thematic Chosen (China)",
-        y = "Proportion Thematic Predicted (Chinese)")
-plotM
-
-#Pearson correlation between corpus and responding
-corr.E = apa_print(cor.test(df.triad_country_freq_E$emp_theme_prop,
-                  df.triad_country_freq_E$theme_freq_prop_E, na.rm=T))
-corr.E
-
-corr.V = apa_print(cor.test(df.triad_country_freq_V$emp_theme_prop,
-                  df.triad_country_freq_V$theme_freq_prop_V, na.rm=T))
-corr.V
-
-corr.M = apa_print(cor.test(df.triad_country_freq_M$emp_theme_prop,
-                  df.triad_country_freq_M$theme_freq_prop_M, na.rm=T))
-corr.M
-
-#Pearson correlation between EN and VI corpus
-corr.EV = apa_print(cor.test(df.triad_country_freq_V$theme_freq_prop_V,
-                   df.triad_country_freq_E$theme_freq_prop_E, na.rm=T))
-corr.EM = apa_print(cor.test(df.triad_country_freq_M$theme_freq_prop_M,
-                   df.triad_country_freq_E$theme_freq_prop_E, na.rm=T))
-corr.MV = apa_print(cor.test(df.triad_country_freq_V$theme_freq_prop_V,
-                   df.triad_country_freq_M$theme_freq_prop_M, na.rm=T))
-```
-
-```{r echo=FALSE, paged.print=FALSE, fig.cap ="Correlation between English corpus lexical co-occurrence and US responding, and Vietnamese corpus lexical co-occurrence and Vietnam responding."}
-plotE + plotV + plotM
-  plot_layout(ncol = 3)
-```
-
-We first conducted a Pearson correlation test between corresponding response data and corpus data.
-Looking at the raw lexical co-occurrence data, proportion of US thematic responding is moderately correlated to English corpus thematic proportion, `r corr.E$full_result`.
-Proportion of Vietnam thematic responding is moderately correlated to Vietnamese corpus thematic proportion, `r corr.V$full_result`.
-Proportion of China thematic responding is moderately correlated to Chinese corpus thematic proportion, `r corr.M$full_result`.
-There was a strong similarity signal between the thematic proportions in the English and Vietnamese corpora, `r corr.EV$full_result`, and the thematic proportions in the English and Mandarin corpora, `r corr.EM$full_result`.
-There was a moderate similarity signal between the proportions in the Mandarin and Vietnamese corpora, `r corr.MV$full_result.`
-
-```{r Pearson correlation between corpus cosine distance and responding, warning=FALSE, include=FALSE}
-df.triad_country_cos <- df %>%
-  group_by(triad, country, theme_cosine_prop_E, theme_cosine_prop_V, theme_cosine_prop_M) %>%
-  summarize(emp_theme_prop = mean(responses_theme))
-
-df.triad_country_cos_E <- df.triad_country_cos %>%
-  filter(country == "US")
-
-plotE = ggplot(data = df.triad_country_cos_E, 
-        mapping = aes(x = emp_theme_prop, 
-                     y = theme_cosine_prop_E,
-                     label = triad)) +
-   geom_text() + 
-   geom_smooth(method = "lm") +
-   labs(x = "Proportion Thematic Chosen (US)", 
-        y = "Proportion Thematic Predicted (English)") + 
-   scale_y_reverse() + 
-   xlim(0, 1) +
-   ylim(0.8, 0.2) + 
-  theme(axis.title = element_text(size=rel(0.75)))
-
-df.triad_country_cos_V <- df.triad_country_cos %>%
-  filter(country == "Vietnam")
-
-plotV = ggplot(data = df.triad_country_cos_V, 
-        mapping = aes(x = emp_theme_prop, 
-                     y = theme_cosine_prop_V, 
-                     label = triad)) +
-   geom_text() + 
-   geom_smooth(method = "lm") +
-   labs(x = "Proportion Thematic Chosen (Vietnam)", 
-        y = "Proportion Thematic Predicted (Vietnamese)") + 
-   scale_y_reverse() +
-   xlim(0, 1) +
-   ylim(0.8, 0.2) + 
-  theme(axis.title = element_text(size=rel(0.75)))
-
-df.triad_country_cos_M <- df.triad_country_cos %>%
-  filter(country == "China")
-
-plotM = ggplot(data = df.triad_country_cos_M, 
-        mapping = aes(x = emp_theme_prop, 
-                     y = theme_cosine_prop_M, 
-                     label = triad)) +
-   geom_text() + 
-   geom_smooth(method = "lm") +
-   labs(x = "Proportion Thematic Chosen (China)", 
-        y = "Proportion Thematic Predicted (Mandarin)") + 
-   xlim(0, 1) +
-   ylim(0.8, 0.2) + 
-  theme(axis.title = element_text(size=rel(0.75)))
-
-corr.E_cos = apa_print(cor.test(df.triad_country_cos_E$emp_theme_prop,
-                      df.triad_country_cos_E$theme_cosine_prop_E, na.rm=T))
-
-corr.V_cos = apa_print(cor.test(df.triad_country_cos_V$emp_theme_prop,
-                      df.triad_country_cos_V$theme_cosine_prop_V, na.rm=T))
-
-corr.M_cos = apa_print(cor.test(df.triad_country_cos_M$emp_theme_prop,
-                      df.triad_country_cos_M$theme_cosine_prop_M, na.rm=T))
-
-#correlation between corpora
-corr.EV_cos = apa_print(cor.test(df.triad_country_cos_E$theme_cosine_prop_E,
-                       df.triad_country_cos_V$theme_cosine_prop_V, na.rm=T))
-
-corr.EM_cos = apa_print(cor.test(df.triad_country_cos_E$theme_cosine_prop_E,
-                      df.triad_country_cos_M$theme_cosine_prop_M, na.rm=T))
-
-corr.VM_cos = apa_print(cor.test(df.triad_country_cos_V$theme_cosine_prop_V,
-                      df.triad_country_cos_M$theme_cosine_prop_M, na.rm=T))
-```
-
-```{r warning = FALSE, echo=FALSE, fig.width = 8, fig.cap="Correlation between English corpus cosine distance and US responding; Vietnamese corpus cosine distance and Vietnam responding; and Mandarin corpus cosine distance and China responding."}
-#maybe we should include a note that explains why they are correlate in the opposite direction? 
-#either changing the label of y-axis, or use y = 1/theme_cosine_prop_V? 
-plotE + plotV + plotM +
-  plot_layout(ncol = 3)
-```
-
-```{r US-Mandarin, China-English cross correlation, NOT SHOWN, eval=FALSE, warning=FALSE, include=FALSE}
-plotUSZH = ggplot(data = df.triad_country_cos_E, 
-        mapping = aes(x = emp_theme_prop, 
-                     y = theme_cosine_prop_M,
-                     label = triad)) +
-   geom_text() + 
-   geom_smooth(method = "lm") +
-   labs(x = "Proportion Thematic Chosen (US)", 
-        y = "Proportion Thematic Predicted (Mandarin)") + 
-   scale_y_reverse() + 
-   xlim(0, 1) +
-   ylim(0.8, 0.3)
-
-plotCNEN = ggplot(data = df.triad_country_cos_M, 
-        mapping = aes(x = emp_theme_prop, 
-                     y = theme_cosine_prop_E,
-                     label = triad)) +
-   geom_text() + 
-   geom_smooth(method = "lm") +
-   labs(x = "Proportion Thematic Chosen (China)", 
-        y = "Proportion Thematic Predicted (English)") + 
-   scale_y_reverse() + 
-   xlim(0, 1) +
-   ylim(0.8, 0.3)
-
-plotUSZH + plotCNEN +
-  plot_layout(ncol = 2)
-```
-
-Looking at the cosine distance data using fastText word vectors, proportion of US thematic responding is moderately correlated to English thematic cosine distance proportion, `r corr.E_cos$full_result`.
-There is a small correlation between proportion of Vietnam thematic responding and the Vietnamese thematic cosine distance proportion, `r corr.V_cos$full_result`.
-Proportion of China thematic responding is moderately correlated to Mandarin thematic match cosine distance proportion, `r corr.M_cos$full_result`.
-There were moderate signals of similarity between English and Mandarin (`r corr.EM_cos$full_result`).
-There was no significant correlation between English and Vietnamese (`r corr.EV_cos$full_result`), and between Vietnamese and Mandarin (`r corr.VM_cos$full_result`).
-
-To test whether variation in lexical co-occurrence can explain differences in similarity judgments between US and Vietnam participants, we compare logistic mixed-effects regression models fit to the thematic responding data from each country separately.
-We first ask how well each corpus model (English, Vietnamese, or Mandarin) predicts similarity judgments by speakers of the corresponding language (US, Vietnam, or China).
-To do this, we use a mixed-effects logistic regression to predict triad responses (0=taxonomic or 1=thematic) with corpus prediction (proportion thematic co-occurrence or cosine distance) as a fixed effect and participant and triad as random effects.
-
-#### Raw lexical co-occurrences
-
-```{r US responding predicted by each corpus model raw co-occurrences, warning=FALSE, include=F}
-# English 
-fit.EN_US = glmer(responses_theme ~ theme_freq_prop_E + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "US", !(triad %in% triads_omit)), 
-          family="binomial")
-summary(fit.EN_US)
-fit.EN_US.anova = Anova(fit.EN_US, type = 3)
-
-#Vietnamese
-fit.VI_US = glmer(responses_theme ~ theme_freq_prop_V + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "US", !(triad %in% triads_omit)), 
-          family="binomial")
-summary(fit.VI_US)
-fit.VI_US.anova = Anova(fit.VI_US, type = 3)
-
-#Mandarin
-fit.ZH_US = glmer(responses_theme ~ theme_freq_prop_M + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "US", !(triad %in% triads_omit)), 
-          family="binomial")
-summary(fit.ZH_US)
-fit.ZH_US.anova = Anova(fit.ZH_US, type = 3)
-```
-
-```{r VN responding predicted by each corpus model raw co-occurrences, warning=FALSE, include=F}
-# English 
-fit.EN_VN = glmer(responses_theme ~ theme_freq_prop_E + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "Vietnam", !(triad %in% triads_omit)), 
-          family="binomial")
-summary(fit.EN_VN)
-fit.EN_VN.anova = Anova(fit.EN_VN, type = 3)
-
-#Vietnamese
-fit.VI_VN = glmer(responses_theme ~ theme_freq_prop_V + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "Vietnam", !(triad %in% triads_omit)), 
-          family="binomial")
-summary(fit.VI_VN)
-fit.VI_VN.anova = Anova(fit.VI_VN, type = 3)
-
-#Mandarin
-fit.ZH_VN = glmer(responses_theme ~ theme_freq_prop_M + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "Vietnam", !(triad %in% triads_omit)), 
-          family="binomial")
-summary(fit.ZH_VN)
-fit.ZH_VN.anova = Anova(fit.ZH_VN, type = 3)
-```
-
-```{r CN responding predicted by each corpus model raw co-occurrences, warning=FALSE, include=F}
-#English
-fit.EN_CN = glmer(responses_theme ~ theme_freq_prop_E + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "China", !(triad %in% triads_omit)), 
-          family="binomial")
-summary(fit.EN_CN)
-fit.EN_CN.anova = Anova(fit.EN_CN, type = 3)
-
-#Vietnamese
-fit.VI_CN = glmer(responses_theme ~ theme_freq_prop_V + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "China", !(triad %in% triads_omit)), 
-          family="binomial")
-summary(fit.VI_CN)
-fit.VI_CN.anova = Anova(fit.VI_CN, type = 3)
-
-#Mandarin
-fit.ZH_CN = glmer(responses_theme ~ theme_freq_prop_M + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "China", !(triad %in% triads_omit)), 
-          family="binomial")
-summary(fit.ZH_CN)
-fit.ZH_CN.anova = Anova(fit.ZH_CN, type = 3)
-```
-
-TODO: ADD CHINA RESULTS
-Both the English (EN) and Vietnamese (VI) corpus are significant predictors of US responding (EN-US model: $\beta$ = `r round(fixef(fit.EN_US)["theme_freq_prop_E"], 2)`, $\chi^2$(`r fit.EN_US.anova["theme_freq_prop_E", "Df"]`) = `r round(fit.EN_US.anova["theme_freq_prop_E", "Chisq"], 2)`, p < .001; VI-US model: $\beta$ = `r round(fixef(fit.VI_US)["theme_freq_prop_V"], 2)`, $\chi^2$(`r fit.VI_US.anova["theme_freq_prop_V", "Df"]`) = `r round(fit.VI_US.anova["theme_freq_prop_V", "Chisq"], 2)`, p < .001).
-
-Similarly, both the English (EN) and Vietnamese (VI) corpus are significant predictors of Vietnam (VN) responding (EN-VN model: $\beta$ = `r round(fixef(fit.EN_VN)["theme_freq_prop_E"], 2)`, $\chi^2$(`r fit.EN_VN.anova["theme_freq_prop_E", "Df"]`) = `r round(fit.EN_VN.anova["theme_freq_prop_E", "Chisq"], 2)`, p < .001; VI-VN model: $\beta$ = `r round(fixef(fit.VI_VN)["theme_freq_prop_V"], 2)`, $\chi^2$(`r fit.VI_VN.anova["theme_freq_prop_V", "Df"]`) = `r round(fit.VI_VN.anova["theme_freq_prop_V", "Chisq"], 2)`, p < .001).
-
-This suggests a strong shared similarity signal across the languages, which is also reflected in the strong correlation between the two corpus models reported above (`r corr.EV$full_result`).
-
-#### Cosine distances of fastText word vectors
-```{r US responding predicted by each corpus model cosine differences, warning=FALSE, include=F}
-#English
-fit.EN_US_cos = glmer(responses_theme ~ theme_cosine_prop_E + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "US"), 
-          family="binomial")
-summary(fit.EN_US_cos)
-fit.EN_US_cos.anova = Anova(fit.EN_US_cos, type = 3)
-fit.EN_US_cos.anova
-
-#Vietnamese
-fit.VI_US_cos = glmer(responses_theme ~ theme_cosine_prop_V + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "US"), 
-          family="binomial")
-summary(fit.VI_US_cos)
-fit.VI_US_cos.anova = Anova(fit.VI_US_cos, type = 3)
-fit.VI_US_cos.anova
-
-#Mandarin
-fit.ZH_US_cos = glmer(responses_theme ~ theme_cosine_prop_M + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "US"), 
-          family="binomial")
-summary(fit.ZH_US_cos)
-fit.ZH_US_cos.anova = Anova(fit.ZH_US_cos, type = 3)
-fit.ZH_US_cos.anova
-```
-
-```{r VN responding predicted by each corpus model cosine differences, warning=FALSE, include=F}
-#English
-fit.EN_VN_cos = glmer(responses_theme ~ theme_cosine_prop_E + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "Vietnam"), 
-          family="binomial")
-summary(fit.EN_VN_cos)
-fit.EN_VN_cos.anova = Anova(fit.EN_VN_cos, type = 3)
-fit.EN_VN_cos.anova
-
-#Vietnamese
-fit.VI_VN_cos = glmer(responses_theme ~ theme_cosine_prop_V + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "Vietnam"), 
-          family="binomial")
-summary(fit.VI_VN_cos)
-fit.VI_VN_cos.anova = Anova(fit.VI_VN_cos, type = 3)
-fit.VI_VN_cos.anova
-
-#Mandarin
-fit.ZH_VN_cos = glmer(responses_theme ~ theme_cosine_prop_M + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "Vietnam"), 
-          family="binomial")
-summary(fit.ZH_VN_cos)
-fit.ZH_VN_cos.anova = Anova(fit.ZH_VN_cos, type = 3)
-fit.ZH_VN_cos.anova
-```
-
-```{r CN responding predicted by each corpus model cosine differences, warning=FALSE, include=F}
-## English
-fit.EN_CN_cos = glmer(responses_theme ~ theme_cosine_prop_E + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "China"), 
-          family="binomial")
-summary(fit.EN_CN_cos)
-fit.EN_CN_cos.anova = Anova(fit.EN_CN_cos, type = 3)
-fit.EN_CN_cos.anova
-
-#Vietnamese
-fit.VI_CN_cos = glmer(responses_theme ~ theme_cosine_prop_V + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "China"), 
-          family="binomial")
-summary(fit.VI_CN_cos)
-fit.VI_CN_cos.anova = Anova(fit.VI_CN_cos, type = 3)
-fit.VI_CN_cos.anova
-
-#Mandarin
-fit.ZH_CN_cos = glmer(responses_theme ~ theme_cosine_prop_M + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "China"), 
-          family="binomial")
-summary(fit.ZH_CN_cos)
-fit.ZH_CN_cos.anova = Anova(fit.ZH_CN_cos, type = 3)
-fit.ZH_CN_cos.anova
-```
-
-Similar to the results from the analysis with raw lexical co-occurrences, we found that all corpora are significant predictors of all cultural context responding.
-
-For US responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are significant predictors of US responding (EN-US model: $\beta$ = `r round(fixef(fit.EN_US_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.EN_US_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.EN_US_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p < .001; VI-US model: $\beta$ = `r round(fixef(fit.VI_US_cos)["theme_cosine_prop_V"], 2)`, $\chi^2$(`r fit.VI_US_cos.anova["theme_cosine_prop_V", "Df"]`) = `r round(fit.VI_US_cos.anova["theme_cosine_prop_V", "Chisq"], 2)`, p = `r round(fit.VI_US_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"], 3)`; ZH-US model: $\beta$ = `r round(fixef(fit.ZH_US_cos)["theme_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ZH_US_cos.anova["theme_cosine_prop_M", "Df"]`) = `r round(fit.ZH_US_cos.anova["theme_cosine_prop_M", "Chisq"], 2)`, p < .001).
-
-For Vietnam (VN) responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are significant predictors of VN responding (EN-VN model: $\beta$ = `r round(fixef(fit.EN_VN_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.EN_VN_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.EN_VN_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p < .001; VI-VN model: $\beta$ = `r round(fixef(fit.VI_VN_cos)["theme_cosine_prop_V"], 2)`, $\chi^2$(`r fit.VI_VN_cos.anova["theme_cosine_prop_V", "Df"]`) = `r round(fit.VI_VN_cos.anova["theme_cosine_prop_V", "Chisq"], 2)`, p = `r round(fit.VI_VN_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"], 3)`; ZH-VN model: $\beta$ = `r round(fixef(fit.ZH_VN_cos)["theme_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ZH_VN_cos.anova["theme_cosine_prop_M", "Df"]`) = `r round(fit.ZH_VN_cos.anova["theme_cosine_prop_M", "Chisq"], 2)`, p < .001).
-
-For China (CN) responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are significant predictors of CN responding (EN-CN model: $\beta$ = `r round(fixef(fit.EN_CN_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.EN_CN_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.EN_CN_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p < .001; VI-CN model: $\beta$ = `r round(fixef(fit.VI_CN_cos)["theme_cosine_prop_V"], 2)`, $\chi^2$(`r fit.VI_CN_cos.anova["theme_cosine_prop_V", "Df"]`) = `r round(fit.VI_CN_cos.anova["theme_cosine_prop_V", "Chisq"], 2)`, p = `r round(fit.VI_VN_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"], 3)`; ZH-CN model: $\beta$ = `r round(fixef(fit.ZH_CN_cos)["theme_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ZH_CN_cos.anova["theme_cosine_prop_M", "Df"]`) = `r round(fit.ZH_CN_cos.anova["theme_cosine_prop_M", "Chisq"], 2)`, p < .001).
-
-### Is responding in each cultural context __best__ predicted by the corresponding corpus's lexical statistics (raw co-occurrences and cosine distance), as opposed to the other two corpora?
-Next, we directly compare the corpus models by including both as fixed effects in two mixed-effect regressions (predicting US and Vietnam responding) with the same random effects as above.
-In R syntax, the model is: response ~ corpus_English + corpus_Vietnamese + corpus_Mandarin + (1|triad) + (1|subject).
-
-#### Raw co-occurrences 
-```{r MIGHT NEED TO REMOVEEnglish + Vietnamese raw co-occurrences predicting US and Vietnam, warning=FALSE, include=F}
-## English/Vietnamese comparison
-fit.ENVI_US = glmer(responses_theme ~ theme_freq_prop_E + theme_freq_prop_V + 
-                      (1 | subject) + (1 | triad), 
-                    data = df %>% filter(country == "US"), 
-                    family="binomial")
-summary(fit.ENVI_US)
-fit.ENVI_US.anova = Anova(fit.ENVI_US, type = 3)
-fit.ENVI_US.anova
-
-fit.ENVI_VN = glmer(responses_theme ~ theme_freq_prop_V + theme_freq_prop_E + 
-                      (1 | subject) + (1 | triad), 
-                    data = df %>% filter(country == "Vietnam"), 
-                    family="binomial")
-summary(fit.ENVI_VN)
-fit.ENVI_VN.anova = Anova(fit.ENVI_VN, type = 3)
-fit.ENVI_VN.anova
-```
-When we included both corpora as predictors for US responding, only the English corpus has a significant effect ($\beta$ = `r round(fixef(fit.ENVI_US)["theme_freq_prop_E"], 2)`, $\chi^2$(`r fit.ENVI_US.anova["theme_freq_prop_E", "Df"]`) = `r round(fit.ENVI_US.anova["theme_freq_prop_E", "Chisq"], 2)`, p < .001).
-There is no effect of the Vietnamese corpus ($\beta$ = `r round(fixef(fit.ENVI_US)["theme_freq_prop_V"], 2)`, $\chi^2$(`r fit.ENVI_US.anova["theme_freq_prop_V", "Df"]`) = `r round(fit.ENVI_US.anova["theme_freq_prop_V", "Chisq"], 2)`, p = `r round(fit.ENVI_US.anova["theme_freq_prop_V", "Pr(>Chisq)"], 3)`).
-
-However, when both corpora are included as predictors for Vietnam responding -- both corpora has a significant effect (English corpus: $\beta$ = `r round(fixef(fit.ENVI_VN)["theme_freq_prop_E"], 2)`, $\chi^2$(`r fit.ENVI_VN.anova["theme_freq_prop_E", "Df"]`) = `r round(fit.ENVI_VN.anova["theme_freq_prop_E", "Chisq"], 2)`, p = `r round(fit.ENVI_VN.anova["theme_freq_prop_E", "Pr(>Chisq)"], 3)`; Vietnamese corpus: $\beta$ = `r round(fixef(fit.ENVI_VN)["theme_freq_prop_V"], 2)`, $\chi^2$(`r fit.ENVI_VN.anova["theme_freq_prop_V", "Df"]`) = `r round(fit.ENVI_VN.anova["theme_freq_prop_V", "Chisq"], 2)`, p = `r round(fit.ENVI_VN.anova["theme_freq_prop_V", "Pr(>Chisq)"], 3)`).
-
-```{r Eng-Vie-Mand lexical co-occ predicting US, VN, CN, warning=FALSE, include=F}
-# ADDITION: adding theme_freq_prop_M
-#raw co-occurrences
-#linear mixed model with ALL corpora as predictors for each population.
-fit.ENVIZH_US = glmer(responses_theme ~ 
-                      theme_freq_prop_E + theme_freq_prop_V + theme_freq_prop_M +
-                      (1 | subject) + (1 | triad), 
-                    data = df %>% filter(country == "US", !(triad %in% triads_omit)),
-                    family="binomial")
-summary(fit.ENVIZH_US)
-fit.ENVIZH_US.anova = Anova(fit.ENVIZH_US, type = 3)
-fit.ENVIZH_US.anova
-
-fit.ENVIZH_VN = glmer(responses_theme ~ 
-                      theme_freq_prop_V + theme_freq_prop_E + theme_freq_prop_M +
-                      (1 | subject) + (1 | triad), 
-                    data = df %>% filter(country == "Vietnam", !(triad %in% triads_omit)),
-                    family="binomial")
-summary(fit.ENVIZH_VN)
-fit.ENVIZH_VN.anova = Anova(fit.ENVIZH_VN, type = 3)
-fit.ENVIZH_VN.anova
-
-fit.ENVIZH_CN = glmer(responses_theme ~ 
-                      theme_freq_prop_V + theme_freq_prop_E + theme_freq_prop_M +
-                      (1 | subject) + (1 | triad), 
-                    data = df %>% filter(country == "China", !(triad %in% triads_omit)),
-                    family="binomial")
-summary(fit.ENVIZH_CN)
-fit.ENVIZH_CN.anova = Anova(fit.ENVIZH_CN, type = 3)
-fit.ENVIZH_CN.anova
-```
-TODO: ADD WRITE-UP OF RESULTS
-
-```{r echo=FALSE, warning = FALSE, fig.cap = "Fixed effect sizes of each corpus when included as a predictor for China, US, and Vietnam responding, respectively.
-The English corpus is the best predictor for US response, and the Mandarin corpus is the best predictor for China response."}
-coeff_value_freq <- c(fixef(fit.ENVIZH_US)["theme_freq_prop_E"],
-                 fixef(fit.ENVIZH_US)["theme_freq_prop_V"], 
-                 fixef(fit.ENVIZH_US)["theme_freq_prop_M"],
-                 fixef(fit.ENVIZH_VN)["theme_freq_prop_E"],
-                 fixef(fit.ENVIZH_VN)["theme_freq_prop_V"],
-                 fixef(fit.ENVIZH_VN)["theme_freq_prop_M"], 
-                 fixef(fit.ENVIZH_CN)["theme_freq_prop_E"],
-                 fixef(fit.ENVIZH_CN)["theme_freq_prop_V"], 
-                 fixef(fit.ENVIZH_CN)["theme_freq_prop_M"])
-
-se_value_freq <- c(summary(fit.ENVIZH_US)$coef["theme_freq_prop_E", "Std. Error"], 
-              summary(fit.ENVIZH_US)$coef["theme_freq_prop_V", "Std. Error"],
-              summary(fit.ENVIZH_US)$coef["theme_freq_prop_M", "Std. Error"], 
-              summary(fit.ENVIZH_VN)$coef["theme_freq_prop_E", "Std. Error"], 
-              summary(fit.ENVIZH_VN)$coef["theme_freq_prop_V", "Std. Error"],
-              summary(fit.ENVIZH_VN)$coef["theme_freq_prop_M", "Std. Error"],
-              summary(fit.ENVIZH_CN)$coef["theme_freq_prop_E", "Std. Error"], 
-              summary(fit.ENVIZH_CN)$coef["theme_freq_prop_V", "Std. Error"],
-              summary(fit.ENVIZH_CN)$coef["theme_freq_prop_M", "Std. Error"])
-
-country_value <- c(rep("US", 3),
-                   rep("VN", 3),
-                   rep("CN", 3))
-
-corpus_value <- c(rep(c("EN", "VI", "ZH"), 3))
-
-df.USVNCN_coeffs_freq <- data.frame(country_value, corpus_value, coeff_value_freq, se_value_freq)
-
-ggplot(data = df.USVNCN_coeffs_freq, 
-       mapping = aes(x = country_value, y = coeff_value_freq, fill = corpus_value)) +
-  geom_bar(position="dodge", stat="identity") +
-  geom_errorbar(aes(ymin= coeff_value_freq - se_value_freq, ymax = coeff_value_freq + se_value_freq), width=.2,
-                 position=position_dodge(.9)) +
-  scale_y_reverse() + 
-  labs(x = "Country", y = "Fixed effect size", fill = "Corpus") + 
-  scale_x_discrete(labels=c("CN" = "China", "US" = "US", "VN" = "Vietnam")) + 
-  scale_fill_manual(values=c("#D63230", "#1C77C3", "#F39237"))
-
-```
-
-```{r model comparison, include=FALSE}
-fit.US_freq_compare = anova(fit.ENVIZH_US, fit.EN_US, type = 3)
-fit.VN_freq_compare = anova(fit.ENVIZH_VN, fit.VI_VN, type = 3)
-fit.CN_freq_compare = anova(fit.ENVIZH_CN, fit.ZH_CN, type = 3)
-```
-
-TODO: ADD WRITE-UP ON RESULTS
-
-#### Cosine distances of fastText word vectors
-
-```{r Eng-Vie-Mand cosine similarities predicting US, VN, CN warning=FALSE, include=FALSE}
-## English/Vietnamese/Mandarin comparison
-fit.ENVIZH_US_cos = glmer(responses_theme ~ theme_cosine_prop_E + theme_cosine_prop_V + theme_cosine_prop_M +
-                      (1 | subject) + (1 | triad), 
-                    data = df %>% filter(country == "US"), 
-                    family="binomial")
-summary(fit.ENVIZH_US_cos)
-fit.ENVIZH_US_cos.anova = Anova(fit.ENVIZH_US_cos, type = 3)
-fit.ENVIZH_US_cos.anova
-
-fit.ENVIZH_VN_cos = glmer(responses_theme ~ theme_cosine_prop_V + theme_cosine_prop_E + theme_cosine_prop_M +
-                      (1 | subject) + (1 | triad), 
-                    data = df %>% filter(country == "Vietnam"), 
-                    family="binomial")
-summary(fit.ENVIZH_VN_cos)
-fit.ENVIZH_VN_cos.anova = Anova(fit.ENVIZH_VN_cos, type = 3)
-fit.ENVIZH_VN_cos.anova
-
-fit.ENVIZH_CN_cos = glmer(responses_theme ~ theme_cosine_prop_M + theme_cosine_prop_E + theme_cosine_prop_V +
-                      (1 | subject) + (1 | triad), 
-                    data = df %>% filter(country == "China"), 
-                    family="binomial")
-summary(fit.ENVIZH_CN_cos)
-fit.ENVIZH_CN_cos.anova = Anova(fit.ENVIZH_CN_cos, type = 3)
-fit.ENVIZH_CN_cos.anova
-```
-
-When we included all corpora thematic cosine distance proportion as predictors, all corpora are significant in predicting all cultural context's responding.
-
-For US responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are all significant predictors.
-EN corpus: $\beta$ = `r round(fixef(fit.ENVIZH_US_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.ENVIZH_US_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.ENVIZH_US_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p < .001.
-VI corpus: $\beta$ = `r round(fixef(fit.ENVIZH_US_cos)["theme_cosine_prop_V"], 2)`, $\chi^2$(`r fit.ENVIZH_US_cos.anova["theme_cosine_prop_V", "Df"]`) = `r round(fit.ENVIZH_US_cos.anova["theme_cosine_prop_V", "Chisq"], 2)`, p = `r round(fit.ENVIZH_US_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"], 3)`.
-ZH corpus: $\beta$ = `r round(fixef(fit.ENVIZH_US_cos)["theme_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ENVIZH_US_cos.anova["theme_cosine_prop_M", "Df"]`) = `r round(fit.ENVIZH_US_cos.anova["theme_cosine_prop_M", "Chisq"], 2)`, p = `r round(fit.ENVIZH_US_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"], 3)`.
-
-For Vietnam responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are all significant predictors.
-EN corpus: $\beta$ = `r round(fixef(fit.ENVIZH_VN_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.ENVIZH_VN_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p = `r round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"], 3)`.
-VI corpus: $\beta$ = `r round(fixef(fit.ENVIZH_VN_cos)["theme_cosine_prop_V"], 2)`, $\chi^2$(`r fit.ENVIZH_VN_cos.anova["theme_cosine_prop_V", "Df"]`) = `r round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_V", "Chisq"], 2)`, p = `r round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"], 3)`.
-ZH corpus: $\beta$ = `r round(fixef(fit.ENVIZH_VN_cos)["theme_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ENVIZH_VN_cos.anova["theme_cosine_prop_M", "Df"]`) = `r round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_M", "Chisq"], 2)`, p = `r round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"], 3)`.
-
-For China responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are all significant predictors.
-EN corpus: $\beta$ = `r round(fixef(fit.ENVIZH_CN_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.ENVIZH_CN_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.ENVIZH_CN_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p = `r round(fit.ENVIZH_CN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"], 3)`.
-VI corpus: $\beta$ = `r round(fixef(fit.ENVIZH_CN_cos)["theme_cosine_prop_V"], 2)`, $\chi^2$(`r fit.ENVIZH_CN_cos.anova["theme_cosine_prop_V", "Df"]`) = `r round(fit.ENVIZH_CN_cos.anova["theme_cosine_prop_V", "Chisq"], 2)`, p = `r round(fit.ENVIZH_CN_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"], 3)`.
-ZH corpus: $\beta$ = `r round(fixef(fit.ENVIZH_CN_cos)["theme_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ENVIZH_CN_cos.anova["theme_cosine_prop_M", "Df"]`) = `r round(fit.ENVIZH_CN_cos.anova["theme_cosine_prop_M", "Chisq"], 2)`, p = < .001.
-
-We observed some level of language specificity from this analysis.
-The English corpus is the best predictor for US responding, and the Mandarin corpus is the best predictor for China response.
-While this is not the case with the Vietnamese corpus and the Vietnam responding, the Vietnamese corpus is still a significant predictor for the Vietnam responding.
-
-```{r echo=FALSE, warning = FALSE, fig.cap = "Fixed effect sizes of each corpus when included as a predictor for China, US, and Vietnam responding, respectively.
-The English corpus is the best predictor for US response, and the Mandarin corpus is the best predictor for China response."}
-coeff_value_cos <- c(fixef(fit.ENVIZH_US_cos)["theme_cosine_prop_E"],
-                 fixef(fit.ENVIZH_US_cos)["theme_cosine_prop_V"], 
-                 fixef(fit.ENVIZH_US_cos)["theme_cosine_prop_M"],
-                 fixef(fit.ENVIZH_VN_cos)["theme_cosine_prop_E"],
-                 fixef(fit.ENVIZH_VN_cos)["theme_cosine_prop_V"],
-                 fixef(fit.ENVIZH_VN_cos)["theme_cosine_prop_M"], 
-                 fixef(fit.ENVIZH_CN_cos)["theme_cosine_prop_E"],
-                 fixef(fit.ENVIZH_CN_cos)["theme_cosine_prop_V"], 
-                 fixef(fit.ENVIZH_CN_cos)["theme_cosine_prop_M"])
-
-se_value_cos <- c(summary(fit.ENVIZH_US_cos)$coef["theme_cosine_prop_E", "Std. Error"], 
-              summary(fit.ENVIZH_US_cos)$coef["theme_cosine_prop_V", "Std. Error"],
-              summary(fit.ENVIZH_US_cos)$coef["theme_cosine_prop_M", "Std. Error"], 
-              summary(fit.ENVIZH_VN_cos)$coef["theme_cosine_prop_E", "Std. Error"], 
-              summary(fit.ENVIZH_VN_cos)$coef["theme_cosine_prop_V", "Std. Error"],
-              summary(fit.ENVIZH_VN_cos)$coef["theme_cosine_prop_M", "Std. Error"],
-              summary(fit.ENVIZH_CN_cos)$coef["theme_cosine_prop_E", "Std. Error"], 
-              summary(fit.ENVIZH_CN_cos)$coef["theme_cosine_prop_V", "Std. Error"],
-              summary(fit.ENVIZH_CN_cos)$coef["theme_cosine_prop_M", "Std. Error"])
-
-country_value <- c(rep("US", 3),
-                   rep("VN", 3),
-                   rep("CN", 3))
-
-corpus_value <- c(rep(c("EN", "VI", "ZH"), 3))
-
-df.USVNCN_coeffs_cos <- data.frame(country_value, corpus_value, coeff_value_cos, se_value_cos)
-
-ggplot(data = df.USVNCN_coeffs_cos, 
-       mapping = aes(x = country_value, y = coeff_value_cos, fill = corpus_value)) +
-  geom_bar(position="dodge", stat="identity") +
-  geom_errorbar(aes(ymin= coeff_value_cos - se_value_cos, ymax = coeff_value_cos + se_value_cos), width=.2,
-                 position=position_dodge(.9)) +
-  scale_y_reverse() + 
-  labs(x = "Country", y = "Fixed effect size", fill = "Corpus") + 
-  scale_x_discrete(labels=c("CN" = "China", "US" = "US", "VN" = "Vietnam")) + 
-  scale_fill_manual(values=c("#D63230", "#1C77C3", "#F39237"))
-
-```
-
-```{r model comparison, include=FALSE}
-fit.US_cos_compare = anova(fit.ENVIZH_US_cos, fit.EN_US_cos, type = 3)
-fit.VN_cos_compare = anova(fit.ENVIZH_VN_cos, fit.VI_VN_cos, type = 3)
-fit.CN_cos_compare = anova(fit.ENVIZH_CN_cos, fit.ZH_CN_cos, type = 3)
-```
-
-However, we found that language specificity alone does not explain our results.
-We used an ANOVA to compare the model with only the corresponding corpus, and the model with all 3 corpora for each cultural context.
-We found that in all three cases (US, China, Vietnam), adding the other two corpora produces a significantly better fit than the identical model without the additional corpora, and only the corresponding corpus included as a predictor (US response: $\chi^2$(`r fit.US_compare["fit.ENVIZH_US_cos", "Df"]`) = `r round(fit.US_compare["fit.ENVIZH_US_cos", "Chisq"], 2)`, p = `r round(fit.US_compare["fit.ENVIZH_US_cos", "Pr(>Chisq)"], 3)`; Vietnam response: $\chi^2$(`r fit.VN_compare["fit.ENVIZH_VN_cos", "Df"]`) = `r round(fit.VN_compare["fit.ENVIZH_VN_cos", "Chisq"], 2)`, p = < .001; China response: $\chi^2$(`r fit.CN_compare["fit.ENVIZH_CN_cos", "Df"]`) = `r round(fit.CN_compare["fit.ENVIZH_CN_cos", "Chisq"], 2)`, p = `r round(fit.CN_compare["fit.ENVIZH_CN_cos", "Pr(>Chisq)"], 3)`).
-
-```{r add linguistic model to Ji et al., include=FALSE}
-fit.country = glmer(responses_theme ~ country + (1 | subject) + (1 | triad), 
-                           data = df %>% filter(country != "Vietnam"), 
-                           family = "binomial")
-
-fit.country_corpus = glmer(responses_theme ~ country + theme_cosine_prop_E + theme_cosine_prop_M + (1 | subject) + (1 | triad), 
-                           data = df %>% filter(country != "Vietnam"), 
-                           family = "binomial")
-
-fit.add_corpus <- anova(fit.country, fit.country_corpus, type = 3)
-
-```
-
-We carried out an ANOVA model comparison to compare our approach with previous studies that did not include corpus information.
-Because @Ji2004 only compared US and China participants, we filtered our data to only include responding data from these two countries.
-Our approach would be to compare a model that only includes country (US or China) as a fixed effect with one that also includes English and Chinese corpus data.
-Our previous model with an intercept per subject and one per triad, as well as by-triad random slopes for country to account for variation in the country effect across triads fails to converge with the more complex model, so we include a simpler random effect structure with an intercept per subject and one per triad in both the basic and more complex model.
-We compare this model with an identical model but including Chinese and English corpus cosine distance proportion prediction.
-We found that adding English and Chinese corpus data produces a significantly better fit than the identical model without English and Chinese corpus data as predictors ($\chi^2$(`r fit.add_corpus["fit.country_corpus", "Df"]`) = `r round(fit.add_corpus["fit.country_corpus", "Chisq"], 2)`, p = < .001.
-This suggests that including corpus data would better model the cross-cultural differences in similarity judgment in this study as well as similar studies.
-
-## Exploratory analysis
-
-Because our exclusion criterion for attention checks excluded over 50% Vietnam participants, we carried out exploratory analysis where we applied less stringent exclusion criteria.
-In the following analysis, we only exclude participants who miss more than 2 attention checks (rather than any attention checks).
-We kept the rest of the exclusion criteria.
-
-TODO: CREATE .CSV FILES FOR THESE, SEPARATE OUT R SCRIPT INTO RMD.
-```{r loading data E explore, warning=FALSE, include=F}
-df.resp_E <- read.csv("../../data/data_E_0319.csv") %>%
-  select(-X)
-
-# check for participants who completed the entire experiment. Because the experiment is
-# quite long, some participants decide to come back afterwards, so there are a few files
-# that are recorded as incomplete. 
-df.ppts_finished_E <- df.resp_E %>% 
-  group_by(subject) %>%
-  summarize(finished = ifelse("demo-final" %in% unique(variable_type), "yes", "no")) %>%
-  filter(finished == "yes")
-
-df.resp_E <- df.resp_E %>%
-  filter(subject %in% df.ppts_finished_E$subject)
-
-df.ppts_att_E <- df.resp_E %>%
-  filter(stim_type == "attention check") %>%
-  mutate(correct_response = strsplit(cue, "Choose ")) %>%
-  mutate(correct_response = sapply(correct_response, "[[", 2)) %>%
-  mutate(pass_att_check = ifelse(responses == correct_response, 1, 0)) %>%
-  group_by(subject) %>%
-  summarize(pass_att_check_percent = mean(pass_att_check)) %>%
-  filter(pass_att_check_percent >= 0.8)
-
-df.resp_E <- df.resp_E %>%
-  filter(subject %in% df.ppts_att_E$subject) 
-```
-
-```{r exclusion E explore, include = F, warning = F}
-#non-native speaker
-split_responses_demog <- function(responses) {
-  responses <- as.character(responses)
-  response_list <- unlist(strsplit(responses, ',|:'))
-  response_list <- response_list[seq(1, length(response_list))]
-  response_list <- gsub("}", "", response_list)
-  response_list <- gsub("\"", "", response_list)
-  return(response_list)
-}
-
-NATIVE_LANG = 2
-get_native_lang <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  if(responses[NATIVE_LANG-1] != "{firstlanguage") 
-    {warnings("cannot find native language answer")}
-  else
-    {return (responses[NATIVE_LANG])}
-})
-
-df.ppts_non_native_lang_E <- df.resp_E %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_language") %>%
-  mutate(native_speaker = get_native_lang(responses)) %>%
-  filter(native_speaker == "No")
-
-ppts_non_native_lang_E = unique(df.ppts_non_native_lang_E$subject)#18
-percent_dropped = length(ppts_non_native_lang_E) / length(unique(df.resp_E$subject))
-percent_dropped #0.1041667
-
-#fluent in Vietnamese & Mandarin
-SPEAKER = 2
-SPEAKING = 23
-UNDERSTANDING = 46
-
-get_speaker <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[SPEAKER])
-})
-
-get_fluency_speaking <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[SPEAKING])
-})
-
-get_fluency_understanding <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[UNDERSTANDING])
-})
-
-df.lang_vi_E <- df.resp_E %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_language_vi") %>%
-  mutate(vi_speaker = get_speaker(responses))
-
-df.lang_vi_fluency_E <- df.resp_E %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_conditional_language_vn_fluency") %>%
-  mutate(vi_fluency_sp = as.numeric(get_fluency_speaking(responses))) %>%
-  mutate(vi_fluency_ud = as.numeric(get_fluency_understanding(responses)))
-
-df.lang_vi_E <- full_join(df.lang_vi_E, 
-                          df.lang_vi_fluency_E, 
-                          by = "subject") %>%
-  select(subject, vi_speaker, vi_fluency_sp, vi_fluency_ud) %>%
-  filter(vi_speaker == "Yes",
-         vi_fluency_sp > 4, 
-         vi_fluency_ud > 4)
-
-ppts_vi_speaker_E = unique(df.lang_vi_E$subject) #4
-percent_dropped = length(ppts_vi_speaker_E) / length(unique(df.resp_E$subject))
-percent_dropped #0.02083333
-
-df.lang_zh_E <- df.resp_E %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_language_cn") %>%
-  mutate(zh_speaker = get_speaker(responses))
-
-df.lang_zh_fluency_E <- df.resp_E %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_conditional_language_cn_fluency") %>%
-  mutate(zh_fluency_sp = as.numeric(get_fluency_speaking(responses))) %>%
-  mutate(zh_fluency_ud = as.numeric(get_fluency_understanding(responses)))
-
-df.lang_zh_E <- full_join(df.lang_zh_E, 
-                          df.lang_zh_fluency_E, 
-                          by = "subject") %>%
-  select(subject, zh_speaker, zh_fluency_sp, zh_fluency_ud) %>%
-  filter(zh_speaker == "Yes",
-         zh_fluency_sp > 4, 
-         zh_fluency_ud > 4)
-
-ppts_zh_speaker_E = unique(df.lang_zh_E$subject) #30
-percent_dropped = length(ppts_zh_speaker_E) / length(unique(df.resp_E$subject))
-percent_dropped #0.1822917
-
-#have lived outside the sample country for more than 2 years
-#have travelled extensively (more than 6 international experiences of 2 days or longer) 
-YEARSABROAD = 2
-OVERSEAEXP = 4
-
-get_lived_abroad <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[YEARSABROAD])
-})
-
-get_oversea_exp <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[OVERSEAEXP])
-})
-
-df.abroad_E <- df.resp_E %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_oversea_experience") %>%
-  mutate(lived_abroad = get_lived_abroad(responses)) %>%
-  mutate(oversea_exp = get_oversea_exp(responses))
-
-df.lived_abroad_E <- df.abroad_E %>%
-  filter(lived_abroad == "Yes")
-
-ppts_lived_abroad_E = unique(df.lived_abroad_E$subject) #29
-percent_dropped = length(ppts_lived_abroad_E) / length(unique(df.resp_E$subject))
-percent_dropped #0.171875
-
-df.oversea_exp_E <- df.abroad_E %>%
-  filter(oversea_exp == "Six or more experiences")
-
-ppts_oversea_exp_E = unique(df.oversea_exp_E$subject) #77
-percent_dropped = length(ppts_oversea_exp_E) / length(unique(df.resp_E$subject))
-percent_dropped #0.44 # will not use this criterion
-
-df.resp_E <- df.resp_E %>%
-  filter(!(subject %in% ppts_non_native_lang_E),
-         !(subject %in% ppts_vi_speaker_E), 
-         !(subject %in% ppts_zh_speaker_E),
-         !(subject %in% ppts_lived_abroad_E))
-
-length(unique(df.resp_E$subject)) #132
-```
-
-```{r demog_E explore, include = F}
-demog <- c("demog-dropdown", "demog-multi-choice", "demog-free-response", "demog-multi-select")
-df.demog_E <- df.resp_E %>%
-  filter(trial_type %in% demog)
-
-AGE = 97 #index for age answer
-GENDER = 115 #index for gender answer
-split_responses <- function(responses) {
-  responses <- as.character(responses)
-  response_list <- unlist(strsplit(responses, ',|:'))
-  response_list <- response_list[seq(1, length(response_list))]
-  response_list <- gsub("}", "", response_list)
-  response_list <- gsub("\"", "", response_list)
-  return(response_list)
-}
-
-get_age <- Vectorize(function(responses) {
-  responses <- split_responses(responses)
-  if(responses[AGE-1] != "A0") {warnings("cannot find age answer")}
-  else{return (responses[AGE])}
-})
-
-get_gender <- Vectorize(function(responses) {
-  responses <- split_responses(responses)
-  if(responses[GENDER-1] != "A1") {warnings("cannot find gender answer")}
-  else{return (responses[GENDER])}
-})
-
-df.age_gender_E <- df.demog_E %>%
-  filter(variable_type == "demog_age_gender_ethnic") %>%
-  select(subject, responses) %>%
-  mutate(age = as.numeric(get_age(responses))) %>%
-  mutate(age = as.numeric(age)) %>%
-  mutate(gender = get_gender(responses))
-
-df.age_gender_E_summ <- df.age_gender_E %>%
-  summarize(mean_age = mean(age), 
-            median_age = median(age), 
-            sd_age = sd(age))
-```
-
-```{r loading data V explore, include=F}
-df.resp_V <- read.csv("../../data/data_V_0530.csv") %>%
-  select(-X)
-
-# check for participants who completed the entire experiment. Because the experiment is
-# quite long, some participants decide to come back afterwards, so there are a few files
-# that are recorded as incomplete. 
-df.ppts_finished_V <- df.resp_V %>% 
-  group_by(subject) %>%
-  summarize(finished = ifelse("demo-final" %in% unique(variable_type), "yes", "no")) %>%
-  filter(finished == "yes")
-
-df.resp_V <- df.resp_V %>%
-  filter(subject %in% df.ppts_finished_V$subject)
-
-df.ppts_att_V <- df.resp_V %>%
-  filter(stim_type == "attention check") %>%
-  mutate(correct_response = strsplit(cue, "Chọn ")) %>%
-  mutate(correct_response = sapply(correct_response, "[[", 2)) %>%
-  mutate(pass_att_check = ifelse(responses == correct_response, 1, 0)) %>%
-  group_by(subject) %>%
-  summarize(pass_att_check_percent = mean(pass_att_check)) %>%
-  filter(pass_att_check_percent >= 0.8)
-
-df.resp_V <- df.resp_V %>%
-  filter(subject %in% df.ppts_att_V$subject) #73
-```
-
-```{r exclusion V explore, include = F}
-#non-native speaker
-split_responses_demog <- function(responses) {
-  responses <- as.character(responses)
-  response_list <- unlist(strsplit(responses, ',|:'))
-  response_list <- response_list[seq(1, length(response_list))]
-  response_list <- gsub("}", "", response_list)
-  response_list <- gsub("\"", "", response_list)
-  return(response_list)
-}
-
-NATIVE_LANG = 2
-get_native_lang <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  if(responses[NATIVE_LANG-1] != "{firstlanguage") 
-    {warnings("cannot find native language answer")}
-  else
-    {return (responses[NATIVE_LANG])}
-})
-
-df.ppts_non_native_lang_V <- df.resp_V %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_language") %>%
-  mutate(native_speaker = get_native_lang(responses)) %>%
-  filter(native_speaker == "Không")
-
-ppts_non_native_lang_V = unique(df.ppts_non_native_lang_V$subject)
-percent_dropped = length(ppts_non_native_lang_V) / length(unique(df.resp_V$subject))
-percent_dropped #0
-
-#fluent in English
-SPEAKER = 2
-SPEAKING = 23
-UNDERSTANDING = 46
-
-get_speaker <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[SPEAKER])
-})
-
-get_fluency_speaking <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[SPEAKING])
-})
-
-get_fluency_understanding <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[UNDERSTANDING])
-})
-
-df.lang_en_V <- df.resp_V %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_language_en") %>%
-  mutate(en_speaker = get_speaker(responses))
-
-df.lang_en_fluency_V <- df.resp_V %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_conditional_language_en_fluency") %>%
-  mutate(en_fluency_sp = as.numeric(get_fluency_speaking(responses))) %>%
-  mutate(en_fluency_ud = as.numeric(get_fluency_understanding(responses)))
-
-df.lang_en_V <- full_join(df.lang_en_V, 
-                          df.lang_en_fluency_V, 
-                          by = "subject") %>%
-  select(subject, en_speaker, en_fluency_sp, en_fluency_ud) %>%
-  filter(en_speaker == "Có",
-         en_fluency_sp > 4, 
-         en_fluency_ud > 4)
-
-ppts_en_speaker_V = unique(df.lang_en_V$subject) #4
-percent_dropped = length(ppts_en_speaker_V) / length(unique(df.resp_V$subject))
-percent_dropped #0.6861314 # do not use this criterion
-
-df.lang_zh_V <- df.resp_V %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_language_cn") %>%
-  mutate(zh_speaker = get_speaker(responses))
-
-df.lang_zh_fluency_V <- df.resp_V %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_conditional_language_cn_fluency") %>%
-  mutate(zh_fluency_sp = as.numeric(get_fluency_speaking(responses))) %>%
-  mutate(zh_fluency_ud = as.numeric(get_fluency_understanding(responses)))
-
-df.lang_zh_V <- full_join(df.lang_zh_V, 
-                          df.lang_zh_fluency_V, 
-                          by = "subject") %>%
-  select(subject, zh_speaker, zh_fluency_sp, zh_fluency_ud) %>%
-  filter(zh_speaker == "Có",
-         zh_fluency_sp > 4, 
-         zh_fluency_ud > 4)
-
-ppts_zh_speaker_V = unique(df.lang_zh_V$subject) #4
-percent_dropped = length(ppts_zh_speaker_V) / length(unique(df.resp_V$subject))
-percent_dropped #0.05839416
-
-#have lived outside the sample country for more than 2 years
-#have travelled extensively (more than 6 international experiences of 2 days or longer) 
-YEARSABROAD = 2
-OVERSEAEXP = 4
-
-get_lived_abroad <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[YEARSABROAD])
-})
-
-get_oversea_exp <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[OVERSEAEXP])
-})
-
-df.abroad_V <- df.resp_V %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_oversea_experience") %>%
-  mutate(lived_abroad = get_lived_abroad(responses)) %>%
-  mutate(oversea_exp = get_oversea_exp(responses))
-
-df.lived_abroad_V <- df.abroad_V %>%
-  filter(lived_abroad == "Có")
-
-ppts_lived_abroad_V = unique(df.lived_abroad_V$subject)
-percent_dropped = length(ppts_lived_abroad_V) / length(unique(df.resp_V$subject))
-percent_dropped #0.1094891
-
-df.oversea_exp_V <- df.abroad_V %>%
-  filter(oversea_exp == "6 lần trở lên")
-
-ppts_oversea_exp_V = unique(df.oversea_exp_V$subject) #77
-percent_dropped = length(ppts_oversea_exp_V) / length(unique(df.resp_V$subject))
-percent_dropped #0.1094891
-
-df.resp_V <- df.resp_V %>%
-  filter(!(subject %in% ppts_non_native_lang_V),
-         !(subject %in% ppts_oversea_exp_V), 
-         !(subject %in% ppts_zh_speaker_V),
-         !(subject %in% ppts_lived_abroad_V))
-
-length(unique(df.resp_V$subject))  #110
-```
-
-```{r demog_V explore, include = F}
-demog <- c("demog-dropdown", "demog-multi-choice", "demog-free-response", "demog-multi-select")
-df.demog_V <- df.resp_V %>%
-  filter(trial_type %in% demog)
-
-AGE = 97 #index for age answer
-GENDER = 115 #index for gender answer
-split_responses <- function(responses) {
-  responses <- as.character(responses)
-  response_list <- unlist(strsplit(responses, ',|:'))
-  response_list <- response_list[seq(1, length(response_list))]
-  response_list <- gsub("}", "", response_list)
-  response_list <- gsub("\"", "", response_list)
-  return(response_list)
-}
-
-get_age <- Vectorize(function(responses) {
-  responses <- split_responses(responses)
-  if(responses[AGE-1] != "A0") {warnings("cannot find age answer")}
-  else{return (responses[AGE])}
-})
-
-get_gender <- Vectorize(function(responses) {
-  responses <- split_responses(responses)
-  if(responses[GENDER-1] != "A1") {warnings("cannot find gender answer")}
-  else{return (responses[GENDER])}
-})
-
-df.age_gender_V <- df.demog_V %>%
-  filter(variable_type == "demog_age_gender_ethnic") %>%
-  select(subject, responses) %>%
-  mutate(age = as.numeric(get_age(responses))) %>%
-  mutate(age = as.numeric(age)) %>%
-  mutate(gender = get_gender(responses))
-
-df.age_gender_V_summ <- df.age_gender_V %>%
-  summarize(mean_age = mean(age), 
-            median_age = median(age), 
-            sd_age = sd(age))
-```
-
-```{r loading data M explore, warning=FALSE, include=F}
-df.resp_M <- read.csv("../../data/data_M_0530.csv") %>%
-  select(-X)
-
-# check for participants who completed the entire experiment. Because the experiment is
-# quite long, some participants decide to come back afterwards, so there are a few files
-# that are recorded as incomplete. 
-df.ppts_finished_M <- df.resp_M %>% 
-  group_by(subject) %>%
-  summarize(finished = ifelse("demo-final" %in% unique(variable_type), "yes", "no")) %>%
-  filter(finished == "yes")
-
-df.resp_M <- df.resp_M %>%
-  filter(subject %in% df.ppts_finished_M$subject)
-
-df.ppts_att_M <- df.resp_M %>%
-  filter(stim_type == "attention check") %>%
-  mutate(correct_response = strsplit(cue, "选择")) %>%
-  mutate(correct_response = sapply(correct_response, "[[", 2)) %>%
-  mutate(correct_response = str_replace_all(correct_response, "“", "")) %>%
-  mutate(correct_response = str_replace_all(correct_response, "”", "")) %>%
-  mutate(pass_att_check = ifelse(responses == correct_response, 1, 0)) %>%
-  group_by(subject) %>%
-  summarize(pass_att_check_percent = mean(pass_att_check)) %>%
-  filter(pass_att_check_percent >= 0.8)
-
-df.resp_M <- df.resp_M %>%
-  filter(subject %in% df.ppts_att_M$subject) 
-```
-
-```{r exclusion M explore, include = F, warning = F}
-#non-native speaker
-split_responses_demog <- function(responses) {
-  responses <- as.character(responses)
-  response_list <- unlist(strsplit(responses, ',|:'))
-  response_list <- response_list[seq(1, length(response_list))]
-  response_list <- gsub("}", "", response_list)
-  response_list <- gsub("\"", "", response_list)
-  return(response_list)
-}
-
-NATIVE_LANG = 2
-get_native_lang <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  if(responses[NATIVE_LANG-1] != "{firstlanguage") 
-    {warnings("cannot find native language answer")}
-  else
-    {return (responses[NATIVE_LANG])}
-})
-
-df.ppts_non_native_lang_M <- df.resp_M %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_language") %>%
-  mutate(native_speaker = get_native_lang(responses)) %>%
-  filter(native_speaker == "不是")
-
-ppts_non_native_lang_M = unique(df.ppts_non_native_lang_M$subject) #2
-percent_dropped = length(ppts_non_native_lang_M) / length(unique(df.resp_M$subject))
-percent_dropped #0.01149425
-
-#fluent in English
-SPEAKER = 2
-SPEAKING = 23
-UNDERSTANDING = 46
-
-get_speaker <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[SPEAKER])
-})
-
-get_fluency_speaking <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[SPEAKING])
-})
-
-get_fluency_understanding <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[UNDERSTANDING])
-})
-
-df.lang_en_M <- df.resp_M %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_language_en") %>%
-  mutate(en_speaker = get_speaker(responses))
-
-df.lang_en_fluency_M <- df.resp_M %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_conditional_language_en_fluency") %>%
-  mutate(en_fluency_sp = as.numeric(get_fluency_speaking(responses))) %>%
-  mutate(en_fluency_ud = as.numeric(get_fluency_understanding(responses)))
-
-df.lang_en_M <- full_join(df.lang_en_M, 
-                          df.lang_en_fluency_M, 
-                          by = "subject") %>%
-  select(subject, en_speaker, en_fluency_sp, en_fluency_ud) %>%
-  filter(en_speaker == "能",
-         en_fluency_sp > 4, 
-         en_fluency_ud > 4)
-
-ppts_en_speaker_M = unique(df.lang_en_M$subject) #50
-percent_dropped = length(ppts_en_speaker_M) / length(unique(df.resp_M$subject))
-percent_dropped #0.3850575 # will not use this criterion
-
-df.lang_vi_M <- df.resp_M %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_language_vi") %>%
-  mutate(vi_speaker = get_speaker(responses))
-
-df.lang_vi_fluency_M <- df.resp_M %>%
-  filter(variable_type == "demog_conditional_language_vi_fluency") %>%
-  mutate(vi_fluency_sp = as.numeric(get_fluency_speaking(responses))) %>%
-  mutate(vi_fluency_ud = as.numeric(get_fluency_understanding(responses)))
-
-df.lang_vi_M <- full_join(df.lang_vi_M, 
-                          df.lang_vi_fluency_M, 
-                          by = "subject") %>%
-  select(subject, vi_speaker, vi_fluency_sp, vi_fluency_ud) %>%
-  filter(vi_speaker == "能",
-         vi_fluency_sp > 4, 
-         vi_fluency_ud > 4)
-
-ppts_vi_speaker_M = unique(df.lang_vi_M$subject) #50
-percent_dropped = length(ppts_vi_speaker_M) / length(unique(df.resp_M$subject))
-percent_dropped #0
-
-#have lived outside the sample country for more than 2 years
-#have travelled extensively (more than 6 international experiences of 2 days or longer) 
-YEARSABROAD = 2
-OVERSEAEXP = 4
-
-get_lived_abroad <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[YEARSABROAD])
-})
-
-get_oversea_exp <- Vectorize(function(responses) {
-  responses <- split_responses_demog(responses)
-  return (responses[OVERSEAEXP])
-})
-
-df.abroad_M <- df.resp_M %>%
-  select(subject, responses, variable_type) %>%
-  filter(variable_type == "demog_oversea_experience") %>%
-  mutate(lived_abroad = get_lived_abroad(responses)) %>%
-  mutate(oversea_exp = get_oversea_exp(responses))
-
-df.lived_abroad_M <- df.abroad_M %>%
-  filter(lived_abroad == "是")
-
-ppts_lived_abroad_M = unique(df.lived_abroad_M$subject) #23
-percent_dropped = length(ppts_lived_abroad_M) / length(unique(df.resp_M$subject))
-percent_dropped # 0.1551724
-
-df.oversea_exp_M <- df.abroad_M %>%
-  filter(oversea_exp == "六段或更多国际经历")
-
-ppts_oversea_exp_M = unique(df.oversea_exp_M$subject) #0
-percent_dropped = length(ppts_oversea_exp_M) / length(unique(df.resp_M$subject))
-percent_dropped #0.03448276
-
-df.resp_M <- df.resp_M %>%
-  filter(!(subject %in% ppts_non_native_lang_M),
-         !(subject %in% ppts_lived_abroad_M),
-         !(subject %in% ppts_vi_speaker_M),
-         !(subject %in% ppts_oversea_exp_M),)
-
-length(unique(df.resp_M$subject)) #143
-```
-
-```{r demog_M explore, include = F}
-demog <- c("demog-dropdown", "demog-multi-choice", "demog-free-response", "demog-multi-select")
-df.demog_M <- df.resp_M %>%
-  filter(trial_type %in% demog) 
-#write.csv(data_demog, "data_anon_demog_0201.csv")
-
-AGE = 97 #index for age answer
-GENDER = 115 #index for gender answer
-split_responses <- function(responses) {
-  responses <- as.character(responses)
-  response_list <- unlist(strsplit(responses, ',|:'))
-  response_list <- response_list[seq(1, length(response_list))]
-  response_list <- gsub("}", "", response_list)
-  response_list <- gsub("\"", "", response_list)
-  return(response_list)
-}
-
-get_age <- Vectorize(function(responses) {
-  responses <- split_responses(responses)
-  if(responses[AGE-1] != "A0") {warnings("cannot find age answer")}
-  else{return (responses[AGE])}
-})
-
-get_gender <- Vectorize(function(responses) {
-  responses <- split_responses(responses)
-  if(responses[GENDER-1] != "A1") {warnings("cannot find gender answer")}
-  else{return (responses[GENDER])}
-})
-
-df.age_gender_M <- df.demog_M %>%
-  filter(variable_type == "demog_age_gender_ethnic") %>%
-  select(subject, responses) %>%
-  mutate(age = as.numeric(get_age(responses))) %>%
-  mutate(age = as.numeric(age)) %>%
-  mutate(gender = get_gender(responses))
-
-df.age_gender_M_summ <- df.age_gender_M %>%
-  summarize(mean_age = mean(age), 
-            median_age = median(age), 
-            sd_age = sd(age))
-```
-
-With the new exclusion criteria, we excluded `r length(unique(df.ppts_finished_E$subject)) - length(unique(df.ppts_att_E$subject))` US participants, `r length(unique(df.ppts_finished_V$subject)) - length(unique(df.ppts_att_V$subject))` VN participants, and `r length(unique(df.ppts_finished_M$subject)) - length(unique(df.ppts_att_M$subject))` CN participants who did not answer more than 2 attention checks correctly.
-We then applied the 4 criteria that aim to retain only participants who are influenced by one culture: (1) non-native speakers of English and Vietnamese, respectively, (2) fluent in at least one of the other two study languages (Vietnamese for US participants, English for Vietnamese participants and Chinese participants), (3) have lived outside of the test country (US, Vietnam, or China) for more than two years, and (4) have significant international experience (more than 6 international experiences of 2 days or longer.) We did not use a particular criterion for a language if it would exclude 25% or more of any one sample.
-In this round of exclusion, we excluded `r length(unique(df.ppts_att_E$subject)) - length(unique(df.resp_E$subject))` US, `r length(unique(df.ppts_att_V$subject)) - length(unique(df.resp_V$subject))` VN participants, and `r length(unique(df.ppts_att_M$subject)) - length(unique(df.resp_M$subject))` CN participants.
-After these exclusions, the US sample included `r length(unique(df.resp_E$subject))` participants (`r df.age_gender_E %>% filter(gender == "Male") %>% count()`M, `r df.age_gender_E %>% filter(gender == "Female") %>% count()`F, `r df.age_gender_E %>% filter(gender == "Non-binary") %>% count()` non-binary, `r df.age_gender_E %>% filter(gender == "Decline to answer") %>% count()` other), with mean age = `r round(df.age_gender_E_summ$mean_age, 2)` (SD = `r round(df.age_gender_E_summ$sd_age, 2)`) and median age = `r df.age_gender_E_summ$median_age`.
-The VN sample included `r length(unique(df.resp_V$subject))` participants (`r df.age_gender_V %>% filter(gender == "Nam") %>% count()`M, `r df.age_gender_V %>% filter(gender == "Nữ") %>% count()`F), with mean age = `r round(df.age_gender_V_summ$mean_age, 2)` (SD = `r round(df.age_gender_V_summ$sd_age, 2)`) and median age = `r df.age_gender_V_summ$median_age`.
-The CN sample included `r length(unique(df.resp_M$subject))` participants (`r df.age_gender_M %>% filter(gender == "男性") %>% count()`M, `r df.age_gender_M %>% filter(gender == "女性") %>% count()`F), with mean age = `r round(df.age_gender_M_summ$mean_age, 2)` (SD = `r round(df.age_gender_M_summ$sd_age, 2)`) and median age = `r df.age_gender_M_summ$median_age`.
-
-```{r corpus explore, include = F}
-df.corpus_E <- read.csv("../../data/corpusE_cos.csv") %>%
-  rename(tax_frequency_E = tax.frequency,
-         theme_frequency_E = theme.frequency,
-         tax_cosine_E = Tax.cosine_dist, 
-         theme_cosine_E = Theme.cosine_dist,
-         tax_cosine_sim_E = Tax.cosine_sim,
-         theme_cosine_sim_E = Theme.cosine_sim,
-         tax_match_E = Tax.match,
-         theme_match_E = Theme.match, 
-         cue_E = Cue)
-
-df.corpus_V <- read.csv("../../data/corpusV_cos.csv") %>%
-  rename(tax_frequency_V = tax.frequency,
-         theme_frequency_V = theme.frequency,
-         tax_cosine_V = Tax.cosine_dist, 
-         theme_cosine_V = Theme.cosine_dist,
-         tax_cosine_sim_V = Tax.cosine_sim,
-         theme_cosine_sim_V = Theme.cosine_sim,
-         tax_match_V = Tax.match,
-         theme_match_V = Theme.match, 
-         cue_V = Cue)
-
-df.corpus_M <- read.csv("../../data/corpusM_cos.csv") %>%
-  rename(tax_frequency_M = tax.frequency,
-         theme_frequency_M = theme.frequency,
-         tax_cosine_M = Tax.cosine_dist, 
-         theme_cosine_M = Theme.cosine_dist,
-         tax_cosine_sim_M = Tax.cosine_sim,
-         theme_cosine_sim_M = Theme.cosine_sim,
-         tax_match_M = Tax.match,
-         theme_match_M = Theme.match, 
-         cue_M = Cue)
-```
-
-```{r full corpus explore, M freqs is incorrect, include=F}
-df.corpus <- left_join(df.corpus_E, df.corpus_V, by = "Cue_renamed")
-df.corpus <- left_join(df.corpus, df.corpus_M, by = "Cue_renamed")
-
-#replacing any 0 raw counts with epsilon
-df.corpus <- df.corpus %>%
-  mutate(tax_frequency_E = ifelse(tax_frequency_E == 0, 
-                                  .Machine$double.eps, tax_frequency_E),
-         theme_frequency_E = ifelse(theme_frequency_E == 0, 
-                                  .Machine$double.eps, theme_frequency_E),
-         tax_frequency_V = ifelse(tax_frequency_V == 0, 
-                                  .Machine$double.eps, tax_frequency_V),
-         theme_frequency_V = ifelse(theme_frequency_V == 0, 
-                                  .Machine$double.eps, theme_frequency_V))
-
-```
-
-```{r corpus - frequency explore, include = F}
-#find triads_omit, used whenever analysis uses raw collocates 
-df.corpus_E_freq <- df.corpus_E %>%
-  select(Cue_renamed, cue_E, tax_match_E, theme_match_E, tax_frequency_E, theme_frequency_E)
-corpus_E_omit <- df.corpus_E_freq %>%
-  filter(tax_frequency_E == 0 & theme_frequency_E == 0)
-
-df.corpus_V_freq <- df.corpus_V %>%
-  select(Cue_renamed, cue_V, tax_match_V, theme_match_V, tax_frequency_V, theme_frequency_V)
-corpus_V_omit <- df.corpus_V_freq %>% 
-  filter(tax_frequency_V == 0 & theme_frequency_V == 0)
-
-triads_omit <- append(corpus_E_omit$Cue_renamed, corpus_V_omit$Cue_renamed)
-
-df.corpus_freq <- left_join(df.corpus_E_freq, df.corpus_V_freq, by = "Cue_renamed")
-```
-
-```{r corpus - cosine explore, include = F}
-#mainly for sanity checking and so that there is a parallel df to df.corpus_freq
-df.corpus_E_cos <- df.corpus_E %>%
-  select(Cue_renamed, cue_E, tax_match_E, theme_match_E, 
-         tax_cosine_E, theme_cosine_E,
-         tax_cosine_sim_E, theme_cosine_sim_E)
-
-df.corpus_V_cos <- df.corpus_V %>%
-  select(Cue_renamed, cue_V, tax_match_V, theme_match_V, tax_cosine_V, theme_cosine_V,
-         tax_cosine_sim_V, theme_cosine_sim_V)
-
-df.corpus_M_cos <- df.corpus_M %>%
-  select(Cue_renamed, cue_M, tax_match_M, theme_match_M, tax_cosine_M, theme_cosine_M, 
-         tax_cosine_sim_M, theme_cosine_sim_M)
-
-df.corpus_cos <- left_join(df.corpus_E_cos, df.corpus_V_cos, by = "Cue_renamed")
-df.corpus_cos <- left_join(df.corpus_cos, df.corpus_M_cos, by = "Cue_renamed")
-```
-
-```{r getting triads from the 3 languages explore, include = F}
-#combine response and corpus data
-df.triad_E <- df.resp_E %>%
-  filter(stim_type == "triad",
-         responses != "NA")
-triad_cues_E <- read.csv("../../data/cue_renamed_E.csv")
-df.triad_E <- left_join(df.triad_E, triad_cues_E, by = c("cue", "top_opt", "bottom_opt"))
-df.triad_E <- inner_join(df.triad_E, df.corpus, by = "Cue_renamed")
-
-df.triad_E <- df.triad_E %>%
-  mutate(responses_theme = ifelse(responses == theme_match_E, 1, 0),
-         language = "English",
-         country = "US") %>%
-  select(subject, rt, Cue_renamed, cue, top_opt, bottom_opt, 
-         responses, responses_theme, country, language,
-         tax_match_E, theme_match_E, tax_match_V, theme_match_V, tax_match_M, theme_match_M,
-         tax_frequency_E, theme_frequency_E, tax_frequency_V, theme_frequency_V, tax_frequency_M, theme_frequency_M,
-         tax_cosine_E, theme_cosine_E, tax_cosine_V, theme_cosine_V, tax_cosine_M, theme_cosine_M,
-         tax_cosine_sim_E, theme_cosine_sim_E, tax_cosine_sim_V, theme_cosine_sim_V, tax_cosine_sim_M, theme_cosine_sim_M)
-
-df.triad_V <- df.resp_V %>%
-  filter(stim_type == "triad",
-         responses != "NA")
-triad_cues_V <- read.csv("../../data/cue_renamed_V.csv")
-df.triad_V <- left_join(df.triad_V, triad_cues_V, by = c("cue", "top_opt", "bottom_opt"))
-df.triad_V <- inner_join(df.triad_V, df.corpus, by = "Cue_renamed")
-
-df.triad_V <- df.triad_V %>%
-  mutate(responses_theme = ifelse(responses == theme_match_V, 1, 0),
-         language = "Vietnamese", 
-         country = "Vietnam") %>%
-  select(subject, rt, Cue_renamed, cue, top_opt, bottom_opt, 
-         responses, responses_theme, country, language,
-         tax_match_E, theme_match_E, tax_match_V, theme_match_V, tax_match_M, theme_match_M,
-         tax_frequency_E, theme_frequency_E, tax_frequency_V, theme_frequency_V, tax_frequency_M, theme_frequency_M,
-         tax_cosine_E, theme_cosine_E, tax_cosine_V, theme_cosine_V, tax_cosine_M, theme_cosine_M,
-         tax_cosine_sim_E, theme_cosine_sim_E, tax_cosine_sim_V, theme_cosine_sim_V, tax_cosine_sim_M, theme_cosine_sim_M)
-
-df.triad_M <- df.resp_M %>%
-  filter(stim_type == "triad",
-         responses != "NA")
-triad_cues_M <- read.csv("../../data/cue_renamed_M.csv")
-df.triad_M <- left_join(df.triad_M, triad_cues_M, by = c("cue", "top_opt", "bottom_opt"))
-df.triad_M <- inner_join(df.triad_M, df.corpus, by = "Cue_renamed")
-
-df.triad_M <- df.triad_M %>%
-  mutate(responses_theme = ifelse(responses == theme_match_M, 1, 0),
-         language = "Mandarin", 
-         country = "China") %>%
-  select(subject, rt, Cue_renamed, cue, top_opt, bottom_opt, 
-         responses, responses_theme, country, language,
-         tax_match_E, theme_match_E, tax_match_V, theme_match_V, tax_match_M, theme_match_M,
-         tax_frequency_E, theme_frequency_E, tax_frequency_V, theme_frequency_V, tax_frequency_M, theme_frequency_M,
-         tax_cosine_E, theme_cosine_E, tax_cosine_V, theme_cosine_V, tax_cosine_M, theme_cosine_M,
-         tax_cosine_sim_E, theme_cosine_sim_E, tax_cosine_sim_V, theme_cosine_sim_V, tax_cosine_sim_M, theme_cosine_sim_M)
-
-#calculate proportion for raw frequencies and cosine distance
-df <- rbind(df.triad_E, df.triad_V)
-df <- rbind(df, df.triad_M) %>%
-  mutate(theme_freq_prop_E = theme_frequency_E / (theme_frequency_E + tax_frequency_E),
-         theme_freq_prop_V = theme_frequency_V / (theme_frequency_V + tax_frequency_V), 
-         theme_freq_prop_M = theme_frequency_M / (theme_frequency_M + tax_frequency_M), 
-         theme_cosine_prop_E = theme_cosine_E / (theme_cosine_E + tax_cosine_E),
-         theme_cosine_prop_V = theme_cosine_V / (theme_cosine_V + tax_cosine_V), 
-         theme_cosine_prop_M = theme_cosine_M / (theme_cosine_M + tax_cosine_M)) %>%
-  rename(triad = Cue_renamed)
-```
-
-```{r country effect - explore, warning=FALSE, include=FALSE, paged.print=TRUE}
-df.country <- df %>%
-  group_by(subject, country) %>%
-  summarize(theme_resp_percent = mean(responses_theme, na.rm = T))
-
-df.country_sum <- df.country %>%
-  group_by(country) %>%
-  summarize(mean_theme_resp_percent = mean(theme_resp_percent), 
-            sd_theme_resp_percent = sd(theme_resp_percent))
-
-fit.country = glmer(responses_theme ~ country + (1 | subject) + (country | triad), 
-                    data = df, 
-                    family = "binomial")
-summary(fit.country) 
-fit.country.anova = Anova(fit.country, type=3)
-
-fit.country_EN_VN = glmer(responses_theme ~ country + (1 | subject) + (country | triad), 
-                    data = df %>% filter(country != "China"),
-                    family = "binomial")
-summary(fit.country_EN_VN) 
-```
-
-```{r echo=FALSE, warning=FALSE, fig.cap="Proportion of thematic responses by country, with a less stringent attention check criterion.
-We did not find any significant differences from the analysis reported above with a more stringent criterion."}
-
-ggplot(df.country,
-       mapping = aes(x = country, 
-                     y = theme_resp_percent, 
-                     color = country)) +
-  geom_violin() +
-  geom_jitter(height = 0, 
-              alpha = 0.3) +  
-  stat_summary(fun.data = "mean_cl_boot", 
-               geom = "pointrange") + 
-  labs(y = "Proportion Thematic Chosen", 
-       x = "Country", 
-       color = "Country") + 
-  scale_color_manual(values=c("#D63230", "#1C77C3", "#F39237"))
-```
-
-There is no significant difference in this round of analysis compared to the one reported above (with more stringent attention check criterion).
-That is, we still observed a significant effect of country on proportion of thematic responses ($\chi^2$(`r fit.country.anova["country", "Df"]`) = `r round(fit.country.anova["country", "Chisq"], 2)`, p < .001), but this effect is driven by only the difference between US and China response ($\beta$ = `r round(fixef(fit.country)["countryUS"], 2)`, p < .001).
-There is no statistical difference between the Vietnam and China response ($\beta$ = `r round(fixef(fit.country)["countryVietnam"], 2)`, p = `r round(as.data.frame(summary(fit.country)[["coefficients"]])["countryVietnam", "Pr(>|z|)"], 3)`), and the US and Vietnam response ($\beta$ = `r round(fixef(fit.country_EN_VN)["countryVietnam"], 2)`, p = `r round(as.data.frame(summary(fit.country)[["coefficients"]])["countryVietnam", "Pr(>|z|)"], 3)`).
-
-# Discussion
-In this paper, we consider whether statistics of the language environment can account for cross-cultural differences in a classic similarity judgment paradigm, as an alternative to the view that members of different cultures vary in their conception of similarity.
-
-We first tested the generality of a cultural account which holds that people from Western and East Asian cultures tend to conceive of similarity in more taxonomic and thematic ways, respectively, and respond accordingly in categorization tasks such as ours.
-While we managed to replicate the previously documented contrast between English speakers in the US and Mandarin Chinese speakers from East Asia (mainland China, Taiwan, Hong Kong, and Singapore), we do not extend this contrast to our sample of Vietnamese speakers in Vietnam and English speakers in the US.
-This finding suggests some limitations on the generality of this cultural account.
-
-We did find some signatures of language specificity in our analysis, such as the large positive correlation between similarity judgments of each country and the respective corpus statistics, and how each corpus statistics are good predictors for corresponding country's similarity judgments.
-However, this is potentially due to the high correlation between corpus statistics of English, Vietnamese and Mandarin.
-We find even stronger evidence for consistency across the three groups, with substantive overlapping predictions across the corpus models, highly similar responding across the experiments, and a correspondingly high fit in cross-language comparisons between models and data.
-
-```{r include=FALSE}
-fit.country_no_triad <- glmer(responses_theme ~ country + (1 | subject), 
-                              data = df_main_analysis, 
-                              family = "binomial")
-
-fit.country = glmer(responses_theme ~ country + (1 | subject) + (country | triad), 
-                    data = df_main_analysis, 
-                    family = "binomial")
-summary(fit.country)
-
-fit.no_triad_compare <- anova(fit.country, fit.country_no_triad, type = 3)
-```
-
-There are some suggestions that the current approach can predict triad-specific cross-cultural effects.
-First of all, an ANOVA model comparison showed that adding a random effect term for varying slope by country and varying intercept by triad to the model produces a significant better fit than the identical model without this random effect term included as a predictor ($\chi^2$(`r fit.no_triad_compare["fit.country", "Df"]`) = `r round(fit.no_triad_compare["fit.country", "Chisq"], 2)`, p < .001)
-
-Anecdotally, we show below some examples of triads that show contrasting difference in the magnitude of difference in thematic responses between countries.
-As a review, the overall result across all triads showed that there was significant difference between US and China responding, and no significant differences between US and Vietnam or China and Vietnam responding.
-However, we observed that for the triad "cow-grass-chicken," there were significant differences between US and China, and US and Vietnam responding.
-There was no significant difference between China and Vietnam responding.
-For the triad "spoon-sugar-fork," there were significant difference between China and US, and China and Vietnam responding, but no significant difference between US and Vietnam.
-For the triad "hair-comb-beard," there were no significant differences pairwise across the three cultural contexts.
-This suggests that there are triad-specific cross-cultural effects in play.
-Beyond emphasizing the importance of including triad predictors as a random effect, this finding suggests that, firstly, future similar studies need to report triads that are used, as the triads used can affect results (for example, if a study only includes triads where China and US responding are significantly different, it would be more likely to conclude that Chinese and US cultures hold different notions of similarity).
-Secondly, that future studies can look more deeply into which groups of triads are driving the US-China responding difference.
-For example, triads belonging to different semantic neighborhoods might be influencing cross-cultural responding in different ways.
-
-```{r include=FALSE}
-df.country_item <- df_main_analysis %>%
-  filter(triad == "hair")
-
-plot.hair <- ggplot(df.country_item,
-       mapping = aes(x = factor(country, levels=c("China", "US", "Vietnam")), 
-                     y = responses_theme, 
-                     color = factor(country, levels=c("China", "US", "Vietnam")))) +
-  geom_jitter(stat = "identity", alpha  = .5) +
-  labs(y = "Proportion Thematic Chosen (hair: beard / comb)",  
-       x = "Country", 
-       color = "Country") + 
-  stat_summary(fun.data = "mean_cl_boot", 
-               geom = "pointrange") + 
-  scale_y_continuous(limits=c(0.0, 1.0), oob = scales::squish) + 
-  scale_fill_manual(values=c("#D63230", "#1C77C3", "#F39237")) +  
-  scale_color_manual(values=c("#D63230", "#1C77C3", "#F39237"))  + 
-  theme(axis.title = element_text(size=rel(0.75)))
-```
-
-```{r include=FALSE}
-df.country_item <- df_main_analysis %>%
-  filter(triad == "spoon2")
-
-plot.spoon2 <- ggplot(df.country_item,
-       mapping = aes(x = factor(country, levels=c("China", "US", "Vietnam")), 
-                     y = responses_theme, 
-                     color = factor(country, levels=c("China", "US", "Vietnam")))) +
-  geom_jitter(stat = "identity", alpha  = .5) +
-  labs(y = "Proportion Thematic Chosen (spoon: fork / sugar)",  
-       x = "Country", 
-       color = "Country") + 
-  stat_summary(fun.data = "mean_cl_boot", 
-               geom = "pointrange") + 
-  scale_y_continuous(limits=c(0.0, 1.0), oob = scales::squish) + 
-  scale_fill_manual(values=c("#D63230", "#1C77C3", "#F39237")) +  
-  scale_color_manual(values=c("#D63230", "#1C77C3", "#F39237")) + 
-  theme(legend.position = "none") + 
-  theme(axis.title = element_text(size=rel(0.75)))
-```
-
-```{r include = FALSE}
-#show 1 triad
-
-df.country_item <- df_main_analysis %>%
-  filter(triad == "cow2")
-
-df.country_item_summ <- df_main_analysis %>%
-  group_by(triad, country) %>%
-  summarize(theme_resp_percent = mean(responses_theme, na.rm = T)) %>%
-  filter(triad == "cow2")
-
-plot.cow2 <- ggplot(df.country_item,
-       mapping = aes(x = factor(country, levels=c("China", "US", "Vietnam")), 
-                     y = responses_theme, 
-                     color = factor(country, levels=c("China", "US", "Vietnam")))) +
-  geom_jitter(stat = "identity", alpha  = .5) +
-  labs(y = "Proportion Thematic Chosen (cow: chicken / grass)",  
-       x = "Country", 
-       color = "Country") + 
-  stat_summary(fun.data = "mean_cl_boot", 
-               geom = "pointrange") + 
-  scale_y_continuous(limits=c(0.0, 1.0), oob = scales::squish) + 
-  scale_fill_manual(values=c("#D63230", "#1C77C3", "#F39237")) +  
-  scale_color_manual(values=c("#D63230", "#1C77C3", "#F39237")) + 
-  theme(legend.position = "none") + 
-  theme(axis.title = element_text(size=rel(0.75)))
-# 
-# +  
-#   geom_bar(data = df.country_item_summ, 
-#            mapping = aes(x = factor(country, levels=c("China", "US", "Vietnam")), 
-#                           y = theme_resp_percent, 
-#                          color = factor(country, levels=c("China", "US", "Vietnam"))), 
-#            stat='identity', alpha = .3, 
-#            fill=c("#D63230", "#1C77C3", "#F39237"))
-```
-
-```{r echo=FALSE, warning = FALSE, fig.width=8, fig.cap="Anecdotal evidence of triad-specific effects.
-Cow-grass-chicken shows significant differences between US-China responding, and between US-Vietnam responding.
-Spoon-sugar-fork shows only a significant difference between US-China responding.
-Hair-comb-beard does not show any significant differences in pairwise comparisons across the three countries."}
-plot.cow2 + plot.spoon2 + plot.hair + 
-    plot_layout(ncol = 3)
-```
-
-We also identified some data quality / quantity issues that are an obstacle to modeling similarity in Vietnamese and Mandarin.
-As stated above, we were not able to find a Mandarin corpus with raw co-occurrences that contains similar magnitude of number of sentences as our English corpus (COCA).
-Additionally, we could only retrieve fastText word vectors for Vietnamese and Mandarin that are trained on both Common Crawl and Wikipedia.
-63% of the articles on Vietnamese Wikipedia and 16% of the Chinese Wikipedia are bot translations from another language (compared to 3% of English Wikipedia).
-This would affect the quality of the word vectors trained on the Vietnamese and Chinese Wikipedia, potentially making them not reflecting the naturally-occurring lexical co-occurrence in the corresponding language.
-
-Our findings raise additional questions for future work: if not differences in taxonomic vs.
-thematic responding, then what differences drive the relativity effects previous studies have observed?
-To what extent are the relativity effects driven by language, and to what extent by culture?
-@Ji2004 established that culture-aligned differences in this paradigm exist, even when the test language is held constant, concluding that “it is culture (independent of the testing language) that led to different grouping styles” in their study.
-Our data provide a cautionary note to this conclusion, suggesting that semantic representations in bilinguals (see @Francis2005 for a review) may have the potential to provide an offline account for cross-context differences in similarity judgments, independent of test language.
-However, there are still many open questions for this account.
-How do semantic associations guide categorization?
-Can they explain taxonomic-thematic differences of the type reported by @Ji2004 and others?
-Can we provide a more specific computational account than the simple frequency model tested here?
-
-Despite these caveats, our findings here demonstrate the plausibility of an alternative perspective on cross-cultural accounts of language, thought, and similarity in the case of taxonomic and thematic reasoning: that it may be the input to similarity judgments, rather than the evaluative process or the conceptualization of similarity that produces variation in similarity reasoning across cultural and linguistic contexts.
-We hope this work provides a foundation for further research probing this question.
-
-[^footnote]:While we discuss cross-cultural variability at the level of countries or larger world areas, these are not cultural monoliths.
-For convenience, we operationalize culture at the level of country, based on where participants were raised.
-It is an open question whether performance in our participant populations (of relatively young and well-educated adults) is representative of the broader country.
-This is especially true for societies with substantial ethnic and cultural variation such as the US.
-We expect that our data is likely to underestimate variation both within and between the countries we sample from.
-
-\newpage
+Place acknowledgments (including funding information) in a section at
+the end of the paper.
 
@@
 
-\begingroup
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
+```{r}
+# References will be generated automatically by Pandoc and included here.
+# The following code is some latex to format the bibliography. Do not remove it.
+```
 
-<div id="refs" custom-style="Bibliography"></div>
-\endgroup
-
-\newpage
-# Supplemental Information
-
-```{r echo=TRUE, fig.align="center", fig.cap=c("List of triads used"), fig.show="hold"}
-#include_graphics(c("../../data/SI_triads/SI_triads_1.jpg"))
-include_graphics(c("../../data/SI_triads/SI_triads_1.jpg",
-                   "../../data/SI_triads/SI_triads_2.jpg",
-                   "../../data/SI_triads/SI_triads_3.jpg",
-                   "../../data/SI_triads/SI_triads_4.jpg",
-                   "../../data/SI_triads/SI_triads_5.jpg"))
-```
+\setlength{\parindent}{-0.1in} 
+\setlength{\leftskip}{0.125in}
+\noindent

### 2022-12-31 code/1_exclusions/1_exclusionsCN.Rmd
added analysis with cosine distance

@@
 ```{r}
+df.demog_metadata <- data.frame(ppts_finished = c(length(unique(df.ppts_finished_M$subject))),
+                      ppts_after_att_check_excl = c(length(unique(df.ppts_att_M$subject))), 
+                      ppts_after_demog_excl = c(length(unique(df.resp_M$subject))))
+```
+
+```{r}
 write.csv(df.resp_M, "../../data/responding/dataCN_excl.csv")
+write.csv(df.demog_metadata, "../../data/responding/dataCN_excl_metadata.csv")
 ```

### 2022-12-31 code/1_exclusions/1_exclusionsUS.Rmd
added analysis with cosine distance

@@
 ```{r}
+df.demog_metadata <- data.frame(ppts_finished = c(length(unique(df.ppts_finished_E$subject))),
+                      ppts_after_att_check_excl = c(length(unique(df.ppts_att_E$subject))), 
+                      ppts_after_demog_excl = c(length(unique(df.resp_E$subject))))
+```
+
+```{r}
 write.csv(df.resp_E, "../../data/responding/dataUS_excl.csv")
+write.csv(df.demog_metadata, "../../data/responding/dataUS_excl_metadata.csv")
 ```

### 2022-12-31 code/1_exclusions_exploratory/1_exclusionsVN.Rmd
added analysis with cosine distance

--- 2022-12-14 code/1_exclusions/1_exclusionsVN.Rmd
@@
 df.oversea_exp_V <- df.demog %>%
-  filter(demog_question == "overseaexpnum" & demog_response == "Six or more experiences")
+  filter(demog_question == "overseaexpnum" & demog_response == "6 lần trở lên")
 
-ppts_oversea_exp_V = unique(df.oversea_exp_V$subject) #95
+ppts_oversea_exp_V = unique(df.oversea_exp_V$subject) #20
 percent_dropped = length(intersect(ppts_oversea_exp_V, ppts_resp_V)) / length(unique(df.resp_V$subject))
-percent_dropped #0.4739 # will not use this criterion
+percent_dropped #0.109
 
@@
   filter(!(subject %in% ppts_non_native_lang_V),
-         !(subject %in% ppts_vi_speaker_V), 
          !(subject %in% ppts_zh_speaker_V),
-         !(subject %in% ppts_lived_abroad_V))
+         !(subject %in% ppts_lived_abroad_V), 
+         !(subject %in% ppts_oversea_exp_V))
 
-length(unique(df.resp_V$subject)) #124
+length(unique(df.resp_V$subject)) #110
+```
+
+```{r}
+df.demog_metadata <- data.frame(ppts_finished = c(length(unique(df.ppts_finished_V$subject))),
+                      ppts_after_att_check_excl = c(length(unique(df.ppts_att_V$subject))), 
+                      ppts_after_demog_excl = c(length(unique(df.resp_V$subject))))
 ```
@@
 write.csv(df.resp_V, "../../data/responding/dataVN_excl.csv")
+write.csv(df.demog_metadata, "../../data/responding/dataVN_excl_metadata.csv")
 ```

### 2022-12-31 code/2_combine/2_combine.Rmd
added analysis with cosine distance

@@
 df_main_analysis <- df #keep a copy of df in case exploratory analysis changes it
-write.csv(df_main_analysis, "../../data/data_USCNVN_ENZHVI.csv")
+write.csv(df_main_analysis, "../../data/data_USCNVN_ENZHVI.csv", row.names = F)
+write.csv(triads_omit, "../../data/triads_omit.csv", row.names = F)
 ```

### 2022-12-31 code/2_combine/2_combine_filler.Rmd
added analysis with cosine distance

@@
   select(ends_with("_E") | ends_with("_M") | ends_with("_V")) %>%
+  select(!(contains("cue_frequency") | contains("word1_frequency") | contains("word2_frequency"))) %>% # ignore base frequencies for now
   mutate(cue_id = cue_E)
@@
 #find triads_omit, used whenever analysis uses raw collocates 
-corpus_E_omit <- df.corpus_filler %>% 
-  filter(word1_match_frequency_E == 0 & word2_match_frequency_E == 0) # = 0 so no need to do this.
+triads_omit <- df.corpus_filler %>% 
+  filter((word1_match_frequency_E == 0 & word2_match_frequency_E == 0) |
+          #(word1_match_frequency_M == 0 & word2_match_frequency_M == 0) |
+           (word1_match_frequency_V == 0 & word2_match_frequency_V == 0)) %>%
+  pull(cue_id)
 ```
@@
 
-```{r getting triads from the 3 languages, include = F}
+```{r getting triads from the 3 languages}
 #combine response and corpus data
@@
   mutate(responses_word1 = ifelse(responses == word1_E, 1, 0))
-
 ```
@@
          word1_match_frequency_prop_V = 
-           word1_match_frequency_V / (word1_match_frequency_V + word2_match_frequency_V))
+           word1_match_frequency_V / (word1_match_frequency_V + word2_match_frequency_V), 
+         word1_match_cosine_prop_E = 
+           word1_match_cosine_E / (word1_match_cosine_E + word2_match_cosine_E),
+         word1_match_cosine_prop_M = 
+           word1_match_cosine_M / (word1_match_cosine_M + word2_match_cosine_M),
+         word1_match_cosine_prop_V = 
+           word1_match_cosine_V / (word1_match_cosine_V + word2_match_cosine_V), 
+         )
 
-write.csv(df, "../../data/data_filler_USCNVN_ENZHVI.csv")
+write.csv(df, "../../data/data_filler_USCNVN_ENZHVI.csv", row.names = F)
+write.csv(triads_omit, "../../data/fillers_omit.csv", row.names = F)
 ```

### 2022-12-31 code/3_analysis/3_analysis_compare_freq_cosine.Rmd
added analysis with cosine distance

@@
 # Comparing between 2 models for VN responding
-```{r US responding predicted by each corpus model raw co-occurrences, warning=FALSE}
+```{r VN responding predicted by each corpus model raw co-occurrences, warning=FALSE}
 # Vietnamese 
@@
 ```
-# Does adding country help with the model (compared to with just English co-occurrence)? 
+
+# Does adding country help with the model (compared to with corresponding lexcial co-occurrence)? 
 ```{r}
-fit.language = glmer(responses_theme ~ theme_freq_prop_E + (1 | subject) + (1 | triad), 
-          data = df %>% filter(!(near(theme_frequency_E, .Machine$double.eps) & 
-                                  near(tax_frequency_E, .Machine$double.eps))),
+df <- df %>%
+  mutate(theme_freq_prop_corr_lang = case_when(
+    country == "US" ~ theme_freq_prop_E,
+    country == "China" ~ theme_freq_prop_M, 
+    country == "Vietnam" ~ theme_freq_prop_V)) %>%
+  mutate(theme_frequency_corr_lang = case_when(
+    country == "US" ~ theme_frequency_E,
+    country == "China" ~ theme_frequency_M, 
+    country == "Vietnam" ~ theme_frequency_V)) %>%
+  mutate(tax_frequency_corr_lang = case_when(
+    country == "US" ~ tax_frequency_E,
+    country == "China" ~ tax_frequency_M, 
+    country == "Vietnam" ~ tax_frequency_V))
+
+fit.language = glmer(responses_theme ~ theme_freq_prop_corr_lang + (1 | subject) + (1 | triad), 
+          data = df %>% filter(!(near(theme_frequency_corr_lang, .Machine$double.eps) & 
+                                  near(tax_frequency_corr_lang, .Machine$double.eps))),
 
@@
 
-fit.country_language = glmer(responses_theme ~ theme_freq_prop_E * country + (1 | subject) + (1 | triad), 
-          data = df %>% filter(!(near(theme_frequency_E, .Machine$double.eps) & 
-                                  near(tax_frequency_E, .Machine$double.eps))),
+fit.country_language = glmer(responses_theme ~ theme_freq_prop_corr_lang * country + (1 | subject) + (1 | triad), 
+          data = df %>% filter(!(near(theme_frequency_corr_lang, .Machine$double.eps) & 
+                                  near(tax_frequency_corr_lang, .Machine$double.eps))),
 
@@
 
-Adding country improves the model (thematic proportion of lexical co-occurrence, country, and their interaction were all significant predictors).
+Adding country improves the model.
+Only country and interaction between country and corresponding corpus's lexical co-occurrence were significant predictors.
+Corresponding corpus's lexical co-occurrence is no longer a significant predictor.

### 2022-12-31 code/4_paper/manuscript/analysis_preview.Rmd
added analysis with cosine distance

---
title: "Analysis Preview"
output: html_document
date: "2022-12-17"
---

```{r, libraries}
library(png)
library(grid)
library(ggplot2)
library(xtable)
```

```{r setup, echo = FALSE, include = FALSE}
library("papaja")
library("knitr") # for knitting things
library("tidyverse") # for all things tidyverse
library("car")
library("lme4")
library("patchwork")
library("effsize")

# these options here change the formatting of how comments are rendered
opts_chunk$set(
  comment = "",
  results = "hold",
  fig.show = "hold")

# set the default ggplot theme 
theme_set(theme_classic())

opts_chunk$set(cache=TRUE)

#r_refs("r-references.bib")
#r_refs("references/packages.bib")

```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r get responding and demographic data, include = F}
df <- read.csv("../../../data/data_USCNVN_ENZHVI.csv")
df_main_analysis <- df

triads_omit <- read.csv("../../../data/triads_omit.csv")
```

# Results

## Do we extend previous work reporting a preference for taxonomic matching in the US and thematic matching in Asia?

```{r warning=FALSE, cache = TRUE, include = FALSE, paged.print=TRUE}
df.country <- df %>%
  group_by(subject, country) %>%
  summarize(theme_resp_percent = mean(responses_theme, na.rm = T))
```

```{r echo=FALSE, warning=FALSE, cache = TRUE, fig.cap="Proportion of thematic responses by country. Only US-China responding comparison shows a siginficant difference. We could not extend this to US-Vietnam responding comparison."}

#show violin plot
ggplot(df.country,
       mapping = aes(x = factor(country, levels=c("China", "US", "Vietnam")), 
                     y = theme_resp_percent, 
                     color = factor(country, levels=c("China", "US", "Vietnam")))) +
  geom_violin() +
  geom_jitter(height = 0, 
              alpha = 0.3) +  
  stat_summary(fun.data = "mean_cl_boot", 
               geom = "pointrange") + 
  labs(y = "Proportion Thematic Chosen", 
       x = "Country", 
       color = "Country") + 
  scale_color_manual(values=c("#D63230", "#1C77C3", "#F39237"))
```

```{r warning=FALSE, include = TRUE, cache = TRUE, paged.print=TRUE}
# df.country_sum <- df.country %>%
#   group_by(country) %>%
#   summarize(mean_theme_resp_percent = mean(theme_resp_percent), 
#             sd_theme_resp_percent = sd(theme_resp_percent))

fit.country = glmer(responses_theme ~ country + (1 | subject) + (country | triad),
                    data = df, 
                    family = "binomial")
summary(fit.country) 
fit.country.anova = Anova(fit.country, type=3)

fit.country_EN_VN = glmer(responses_theme ~ country + (1 | subject) + (country | triad), 
                    data = df %>% filter(country != "China"),
                    family = "binomial")
summary(fit.country_EN_VN) 
```

To test for cross-context differences in similarity judgments between the countries, we ran a mixed-effects logistic regression predicting triad responding (taxonomic or thematic) with country (US, China, or Vietnam) as a fixed effect. As random effects, we included an intercept per subject and one per triad, as well as by-triad random slopes for country to account for variation in the country effect across triads. In R syntax, the model is: response ~ country + (1 | subject) + (country | triad).

Overall, there is a significant effect of country on proportion of thematic responses ($\chi^2$(`r fit.country.anova["country", "Df"]`) = `r round(fit.country.anova["country", "Chisq"], 2)`, p `r ifelse( fit.country.anova["country", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.country.anova["country", "Pr(>Chisq)"], 3)), "< .001")`). However, this effect is driven by the difference between US and China responding ($\beta$ = `r round(fixef(fit.country)["countryUS"], 2)`, p `r ifelse(as.data.frame(summary(fit.country)[["coefficients"]])["countryUS", "Pr(>|z|)"] > 0.001, paste0("= ", round(as.data.frame(summary(fit.country)[["coefficients"]])["countryUS", "Pr(>|z|)"], 3)), "< .001")`). There is no statistical difference between the Vietnam and China responding ($\beta$ = `r round(fixef(fit.country)["countryVietnam"], 2)`, p `r ifelse(as.data.frame(summary(fit.country)[["coefficients"]])["countryVietnam", "Pr(>|z|)"] > 0.001, paste0("= ", round(as.data.frame(summary(fit.country)[["coefficients"]])["countryVietnam", "Pr(>|z|)"], 3)), "< .001")`), and the US and Vietnam responding ($\beta$ = `r round(fixef(fit.country_EN_VN)["countryVietnam"], 2)`, p `r ifelse(as.data.frame(summary(fit.country_EN_VN)[["coefficients"]])["countryVietnam", "Pr(>|z|)"] > 0.001, paste0("= ", round(as.data.frame(summary(fit.country_EN_VN)[["coefficients"]])["countryVietnam", "Pr(>|z|)"], 3)), "< .001")`).

On this analysis, we do not find support that the US-China tendencies toward taxonomic and thematic responding (respectively) extend to the US-Vietnam comparison. Accordingly, we cannot speak to overall biases toward thematic responding across Asian cultural contexts broadly, but we do replicate the differences documented by @Ji2004 between the US and China. However, in our corpus model comparison, we do find evidence for different, more fine-grained variation in similarity judgments between the US and Vietnam.

## Can the differences in similarity judgments between English, Mandarin and Vietnamese speakers be explained by variation in lexical statistics?
### Is responding in each cultural context predicted by the corresponding lexical statistics?

To test whether variation in lexical co-occurrence can explain differences in similarity judgments between US and Vietnam participants, we compare logistic mixed-effects regression models fit to the thematic responding data from each country separately. We first ask how well each corpus model (English, Vietnamese, or Mandarin) predicts similarity judgments by speakers of the corresponding language (US, Vietnam, or China). To do this, we use a mixed-effects logistic regression to predict triad responses (0=taxonomic or 1=thematic) with corpus prediction (proportion thematic co-occurrence or cosine distance) as a fixed effect and participant and triad as random effects.

We found that all corpora are significant predictors of all cultural context responding.
```{r US responding predicted by each corpus model raw co-occurrences, warning=FALSE, include=T, cache = TRUE}
# English 
fit.EN_US = glmer(responses_theme ~ theme_freq_prop_E + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "US", !(triad %in% triads_omit)), 
          family="binomial")
summary(fit.EN_US)
fit.EN_US.anova = Anova(fit.EN_US, type = 3)

#Vietnamese
fit.VI_US = glmer(responses_theme ~ theme_freq_prop_V + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "US", !(triad %in% triads_omit)), 
          family="binomial")
summary(fit.VI_US)
fit.VI_US.anova = Anova(fit.VI_US, type = 3)

#Mandarin
fit.ZH_US = glmer(responses_theme ~ theme_freq_prop_M + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "US", !(triad %in% triads_omit)), 
          family="binomial")
summary(fit.ZH_US)
fit.ZH_US.anova = Anova(fit.ZH_US, type = 3)
```
For US responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are all significant predictors. EN corpus: $\beta$ = `r round(fixef(fit.EN_US)["theme_freq_prop_E"], 2)`, $\chi^2$(`r fit.EN_US.anova["theme_freq_prop_E", "Df"]`) = `r round(fit.EN_US.anova["theme_freq_prop_E", "Chisq"], 2)`, p `r ifelse( fit.EN_US.anova["theme_freq_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.EN_US.anova["theme_freq_prop_E", "Pr(>Chisq)"], 3)), "< .001")`. VI corpus: $\beta$ = `r round(fixef(fit.VI_US)["theme_freq_prop_V"], 2)`, $\chi^2$(`r fit.VI_US.anova["theme_freq_prop_V", "Df"]`) = `r round(fit.VI_US.anova["theme_freq_prop_V", "Chisq"], 2)`, p `r ifelse( fit.VI_US.anova["theme_freq_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.VI_US.anova["theme_freq_prop_V", "Pr(>Chisq)"], 3)), "< .001")`. ZH corpus: $\beta$ = `r round(fixef(fit.ZH_US)["theme_freq_prop_M"], 2)`, $\chi^2$(`r fit.ZH_US.anova["theme_freq_prop_M", "Df"]`) = `r round(fit.ZH_US.anova["theme_freq_prop_M", "Chisq"], 2)`, p `r ifelse( fit.ZH_US.anova["theme_freq_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ZH_US.anova["theme_freq_prop_M", "Pr(>Chisq)"], 3)), "< .001")`.

```{r VN responding predicted by each corpus model raw co-occurrences, warning=FALSE, include=T, cache = TRUE}
# English 
fit.EN_VN = glmer(responses_theme ~ theme_freq_prop_E + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "Vietnam", !(triad %in% triads_omit)), 
          family="binomial")
summary(fit.EN_VN)
fit.EN_VN.anova = Anova(fit.EN_VN, type = 3)

#Vietnamese
fit.VI_VN = glmer(responses_theme ~ theme_freq_prop_V + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "Vietnam", !(triad %in% triads_omit)), 
          family="binomial")
summary(fit.VI_VN)
fit.VI_VN.anova = Anova(fit.VI_VN, type = 3)

#Mandarin
fit.ZH_VN = glmer(responses_theme ~ theme_freq_prop_M + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "Vietnam", !(triad %in% triads_omit)), 
          family="binomial")
summary(fit.ZH_VN)
fit.ZH_VN.anova = Anova(fit.ZH_VN, type = 3)
```
For Vietnam responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are all significant predictors. EN corpus: $\beta$ = `r round(fixef(fit.EN_VN)["theme_freq_prop_E"], 2)`, $\chi^2$(`r fit.EN_VN.anova["theme_freq_prop_E", "Df"]`) = `r round(fit.EN_VN.anova["theme_freq_prop_E", "Chisq"], 2)`, p `r ifelse( fit.EN_VN.anova["theme_freq_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.EN_VN.anova["theme_freq_prop_E", "Pr(>Chisq)"], 3)), "< .001")`. VI corpus: $\beta$ = `r round(fixef(fit.VI_VN)["theme_freq_prop_V"], 2)`, $\chi^2$(`r fit.VI_VN.anova["theme_freq_prop_V", "Df"]`) = `r round(fit.VI_VN.anova["theme_freq_prop_V", "Chisq"], 2)`, p `r ifelse( fit.VI_VN.anova["theme_freq_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.VI_VN.anova["theme_freq_prop_V", "Pr(>Chisq)"], 3)), "< .001")`. ZH corpus: $\beta$ = `r round(fixef(fit.ZH_VN)["theme_freq_prop_M"], 2)`, $\chi^2$(`r fit.ZH_VN.anova["theme_freq_prop_M", "Df"]`) = `r round(fit.ZH_VN.anova["theme_freq_prop_M", "Chisq"], 2)`, p `r ifelse( fit.ZH_VN.anova["theme_freq_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ZH_VN.anova["theme_freq_prop_M", "Pr(>Chisq)"], 3)), "< .001")`.

```{r CN responding predicted by each corpus model raw co-occurrences, warning=FALSE, include=T, cache = TRUE}
#English
fit.EN_CN = glmer(responses_theme ~ theme_freq_prop_E + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "China", !(triad %in% triads_omit)), 
          family="binomial")
summary(fit.EN_CN)
fit.EN_CN.anova = Anova(fit.EN_CN, type = 3)

#Vietnamese
fit.VI_CN = glmer(responses_theme ~ theme_freq_prop_V + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "China", !(triad %in% triads_omit)), 
          family="binomial")
summary(fit.VI_CN)
fit.VI_CN.anova = Anova(fit.VI_CN, type = 3)

#Mandarin
fit.ZH_CN = glmer(responses_theme ~ theme_freq_prop_M + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "China", !(triad %in% triads_omit)), 
          family="binomial")
summary(fit.ZH_CN)
fit.ZH_CN.anova = Anova(fit.ZH_CN, type = 3)
```

For China responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are all significant predictors. EN corpus: $\beta$ = `r round(fixef(fit.EN_CN)["theme_freq_prop_E"], 2)`, $\chi^2$(`r fit.EN_CN.anova["theme_freq_prop_E", "Df"]`) = `r round(fit.EN_CN.anova["theme_freq_prop_E", "Chisq"], 2)`, p `r ifelse( fit.EN_CN.anova["theme_freq_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.EN_CN.anova["theme_freq_prop_E", "Pr(>Chisq)"], 3)), "< .001")`. VI corpus: $\beta$ = `r round(fixef(fit.VI_CN)["theme_freq_prop_V"], 2)`, $\chi^2$(`r fit.VI_CN.anova["theme_freq_prop_V", "Df"]`) = `r round(fit.VI_CN.anova["theme_freq_prop_V", "Chisq"], 2)`, p `r ifelse( fit.VI_CN.anova["theme_freq_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.VI_CN.anova["theme_freq_prop_V", "Pr(>Chisq)"], 3)), "< .001")`. ZH corpus: $\beta$ = `r round(fixef(fit.ZH_US)["theme_freq_prop_M"], 2)`, $\chi^2$(`r fit.ZH_CN.anova["theme_freq_prop_M", "Df"]`) = `r round(fit.ZH_CN.anova["theme_freq_prop_M", "Chisq"], 2)`, p `r ifelse( fit.ZH_CN.anova["theme_freq_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ZH_CN.anova["theme_freq_prop_M", "Pr(>Chisq)"], 3)), "< .001")`.

This suggests a strong shared similarity signal across the languages.

### Is responding in each cultural context __best__ predicted by the corresponding corpus's lexical statistics, as opposed to the other two corpora?
Next, we directly compare the corpus models by including both as fixed effects in three mixed-effect regressions (predicting US, Vietnam and China responding) with the same random effects as above. In R syntax, the model is: response ~ corpus_English + corpus_Vietnamese + corpus_Mandarin + (1|triad) + (1|subject).

```{r Eng-Vie-Mand lexical co-occ predicting US, warning=FALSE, include=T, cache = TRUE}
#raw co-occurrences
#linear mixed model with ALL corpora as predictors for each population.
fit.ENVIZH_US = glmer(responses_theme ~ 
                      theme_freq_prop_E + theme_freq_prop_V + theme_freq_prop_M +
                      (1 | subject) + (1 | triad), 
                    data = df %>% filter(country == "US", !(triad %in% triads_omit)),
                    family="binomial")
summary(fit.ENVIZH_US)
fit.ENVIZH_US.anova = Anova(fit.ENVIZH_US, type = 3)
fit.ENVIZH_US.anova
```
For US responding: only English (EN) corpus is a significant predictor. EN corpus: $\beta$ = `r round(fixef(fit.ENVIZH_US)["theme_freq_prop_E"], 2)`, $\chi^2$(`r fit.ENVIZH_US.anova["theme_freq_prop_E", "Df"]`) = `r round(fit.ENVIZH_US.anova["theme_freq_prop_E", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_US.anova["theme_freq_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_US.anova["theme_freq_prop_E", "Pr(>Chisq)"], 3)), "< .001")`. VI corpus: $\beta$ = `r round(fixef(fit.ENVIZH_US)["theme_freq_prop_V"], 2)`, $\chi^2$(`r fit.ENVIZH_US.anova["theme_freq_prop_V", "Df"]`) = `r round(fit.ENVIZH_US.anova["theme_freq_prop_V", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_US.anova["theme_freq_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_US.anova["theme_freq_prop_V", "Pr(>Chisq)"], 3)), "< .001")`. ZH corpus: $\beta$ = `r round(fixef(fit.ENVIZH_US)["theme_freq_prop_M"], 2)`, $\chi^2$(`r fit.ENVIZH_US.anova["theme_freq_prop_M", "Df"]`) = `r round(fit.ENVIZH_US.anova["theme_freq_prop_M", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_US.anova["theme_freq_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_US.anova["theme_freq_prop_M", "Pr(>Chisq)"], 3)), "< .001")`.

```{r Eng-Vie-Mand lexical co-occ predicting VN, warning=FALSE, include=T, cache = TRUE}
fit.ENVIZH_VN = glmer(responses_theme ~ 
                      theme_freq_prop_V + theme_freq_prop_E + theme_freq_prop_M +
                      (1 | subject) + (1 | triad), 
                    data = df %>% filter(country == "Vietnam", !(triad %in% triads_omit)),
                    family="binomial")
summary(fit.ENVIZH_VN)
fit.ENVIZH_VN.anova = Anova(fit.ENVIZH_VN, type = 3)
fit.ENVIZH_VN.anova
```
For Vietnam responding: only English (EN) and Mandarin (ZH) corpora are significant predictors. EN corpus: $\beta$ = `r round(fixef(fit.ENVIZH_VN)["theme_freq_prop_E"], 2)`, $\chi^2$(`r fit.ENVIZH_VN.anova["theme_freq_prop_E", "Df"]`) = `r round(fit.ENVIZH_VN.anova["theme_freq_prop_E", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_VN.anova["theme_freq_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_VN.anova["theme_freq_prop_E", "Pr(>Chisq)"], 3)), "< .001")`. ZH corpus: $\beta$ = `r round(fixef(fit.ENVIZH_VN)["theme_freq_prop_M"], 2)`, $\chi^2$(`r fit.ENVIZH_VN.anova["theme_freq_prop_M", "Df"]`) = `r round(fit.ENVIZH_VN.anova["theme_freq_prop_M", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_VN.anova["theme_freq_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_VN.anova["theme_freq_prop_M", "Pr(>Chisq)"], 3)), "< .001")`.VI corpus: $\beta$ = `r round(fixef(fit.ENVIZH_VN)["theme_freq_prop_V"], 2)`, $\chi^2$(`r fit.ENVIZH_VN.anova["theme_freq_prop_V", "Df"]`) = `r round(fit.ENVIZH_VN.anova["theme_freq_prop_V", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_VN.anova["theme_freq_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_VN.anova["theme_freq_prop_V", "Pr(>Chisq)"], 3)), "< .001")`.

```{r Eng-Vie-Mand lexical co-occ predicting CN, warning=FALSE, include=T, cache = TRUE}
fit.ENVIZH_CN = glmer(responses_theme ~ 
                      theme_freq_prop_V + theme_freq_prop_E + theme_freq_prop_M +
                      (1 | subject) + (1 | triad), 
                    data = df %>% filter(country == "China", !(triad %in% triads_omit)),
                    family="binomial")
summary(fit.ENVIZH_CN)
fit.ENVIZH_CN.anova = Anova(fit.ENVIZH_CN, type = 3)
fit.ENVIZH_CN.anova
```
For China responding: only Mandarin (ZH) corpus is a significant predictor. ZH corpus: $\beta$ = `r round(fixef(fit.ENVIZH_CN)["theme_freq_prop_M"], 2)`, $\chi^2$(`r fit.ENVIZH_CN.anova["theme_freq_prop_M", "Df"]`) = `r round(fit.ENVIZH_CN.anova["theme_freq_prop_M", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_CN.anova["theme_freq_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_CN.anova["theme_freq_prop_M", "Pr(>Chisq)"], 3)), "< .001")`. EN corpus: $\beta$ = `r round(fixef(fit.ENVIZH_CN)["theme_freq_prop_E"], 2)`, $\chi^2$(`r fit.ENVIZH_CN.anova["theme_freq_prop_E", "Df"]`) = `r round(fit.ENVIZH_CN.anova["theme_freq_prop_E", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_CN.anova["theme_freq_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_CN.anova["theme_freq_prop_E", "Pr(>Chisq)"], 3)), "< .001")`. VI corpus: $\beta$ = `r round(fixef(fit.ENVIZH_CN)["theme_freq_prop_V"], 2)`, $\chi^2$(`r fit.ENVIZH_CN.anova["theme_freq_prop_V", "Df"]`) = `r round(fit.ENVIZH_CN.anova["theme_freq_prop_V", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_CN.anova["theme_freq_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_CN.anova["theme_freq_prop_V", "Pr(>Chisq)"], 3)), "< .001")`.

```{r echo=FALSE, warning = FALSE, cache = TRUE, fig.cap = "Fixed effect sizes of each corpus when included as a predictor for China, US, and Vietnam responding, respectively. The English corpus is the best predictor for US response, and the Mandarin corpus is the best predictor for China response."}
coeff_value_freq <- c(fixef(fit.ENVIZH_US)["theme_freq_prop_M"],
                 fixef(fit.ENVIZH_US)["theme_freq_prop_E"], 
                 fixef(fit.ENVIZH_US)["theme_freq_prop_V"],
                 fixef(fit.ENVIZH_VN)["theme_freq_prop_M"],
                 fixef(fit.ENVIZH_VN)["theme_freq_prop_E"],
                 fixef(fit.ENVIZH_VN)["theme_freq_prop_V"], 
                 fixef(fit.ENVIZH_CN)["theme_freq_prop_M"],
                 fixef(fit.ENVIZH_CN)["theme_freq_prop_E"], 
                 fixef(fit.ENVIZH_CN)["theme_freq_prop_V"])

se_value_freq <- c(summary(fit.ENVIZH_US)$coef["theme_freq_prop_M", "Std. Error"], 
              summary(fit.ENVIZH_US)$coef["theme_freq_prop_E", "Std. Error"],
              summary(fit.ENVIZH_US)$coef["theme_freq_prop_V", "Std. Error"], 
              summary(fit.ENVIZH_VN)$coef["theme_freq_prop_M", "Std. Error"], 
              summary(fit.ENVIZH_VN)$coef["theme_freq_prop_E", "Std. Error"],
              summary(fit.ENVIZH_VN)$coef["theme_freq_prop_V", "Std. Error"],
              summary(fit.ENVIZH_CN)$coef["theme_freq_prop_M", "Std. Error"], 
              summary(fit.ENVIZH_CN)$coef["theme_freq_prop_E", "Std. Error"],
              summary(fit.ENVIZH_CN)$coef["theme_freq_prop_V", "Std. Error"])

country_value <- c(rep("US", 3),
                   rep("VN", 3),
                   rep("CN", 3))

corpus_value <- c(rep(c("ZH", "EN", "VI"), 3))

df.USVNCN_coeffs_freq <- data.frame(country_value, corpus_value, coeff_value_freq, se_value_freq) %>%
  mutate(corpus_value = factor(corpus_value, levels=c("ZH", "EN", "VI")))

ggplot(data = df.USVNCN_coeffs_freq, 
       mapping = aes(x = country_value, y = coeff_value_freq, fill = corpus_value)) +
  geom_bar(position="dodge", stat="identity") +
  geom_errorbar(aes(ymin= coeff_value_freq - se_value_freq, ymax = coeff_value_freq + se_value_freq), width=.2,
                 position=position_dodge(.9)) +
  labs(x = "Country", y = "Fixed effect size", fill = "Corpus") + 
  scale_x_discrete(labels=c("CN" = "China", "US" = "US", "VN" = "Vietnam")) + 
  scale_fill_manual(values=c("#D63230", "#1C77C3", "#F39237"))

```

```{r freq model comparison, include=FALSE, cache = TRUE}
fit.US_freq_compare = anova(fit.ENVIZH_US, fit.EN_US, type = 3)
fit.US_freq_compare
fit.VN_freq_compare = anova(fit.ENVIZH_VN, fit.VI_VN, type = 3)
fit.VN_freq_compare
fit.CN_freq_compare = anova(fit.ENVIZH_CN, fit.ZH_CN, type = 3)
fit.CN_freq_compare
```

We observed some level of language specificity from this analysis. The English corpus is the best predictor for US responding, and the Mandarin corpus is the best predictor for China response.

We used an ANOVA to compare the model with only the corresponding corpus, and the model with all 3 corpora for each cultural context. For Vietnam, adding the other two corpora produces a significantly better fit than the identical model without the additional corpora, and only the corresponding corpus included as a predictor. However, for US and China, adding the other two corpora does not produce a significantly better fit.
*When this analysis was done with cosine similarity proportion (in my thesis), all prediction for all 3 cultural contexts improved with the addition of the other corpora, which we explained as an effect of linguistic universality. This different result probably stems from the Vietnamese corpus being sparse?*

<!-- While this is not the case with the Vietnamese corpus and the Vietnam responding, the Vietnamese corpus is still a significant predictor for the Vietnam responding.  -->

<!-- However, we found that language specificity alone does not explain our results. We used an ANOVA to compare the model with only the corresponding corpus, and the model with all 3 corpora for each cultural context. We found that in all three cases (US, China, Vietnam), adding the other two corpora produces a significantly better fit than the identical model without the additional corpora, and only the corresponding corpus included as a predictor (US response: $\chi^2$(`r fit.US_freq_compare["fit.ENVIZH_US", "Df"]`) = `r round(fit.US_freq_compare["fit.ENVIZH_US", "Chisq"], 2)`, p `r ifelse( fit.US_freq_compare["fit.ENVIZH_US", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.US_freq_compare["fit.ENVIZH_US", "Pr(>Chisq)"], 3)), "< .001")`; Vietnam response: $\chi^2$(`r fit.VN_freq_compare["fit.ENVIZH_VN", "Df"]`) = `r round(fit.VN_freq_compare["fit.ENVIZH_VN", "Chisq"], 2)`, p `r ifelse( fit.VN_freq_compare["fit.ENVIZH_VN", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.VN_freq_compare["fit.ENVIZH_VN", "Pr(>Chisq)"], 3)), "< .001")`; China response: $\chi^2$(`r fit.CN_freq_compare["fit.ENVIZH_CN", "Df"]`) = `r round(fit.CN_freq_compare["fit.ENVIZH_CN", "Chisq"], 2)`, p `r ifelse( fit.CN_freq_compare["fit.ENVIZH_CN", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.CN_freq_compare["fit.ENVIZH_CN", "Pr(>Chisq)"], 3)), "< .001")`).   -->

```{r add linguistic model to Ji et al., include=TRUE, cache = T}
fit.country = glmer(responses_theme ~ country + (1 | subject) + (1 | triad), 
                           data = df %>% filter(country != "Vietnam"), 
                           family = "binomial")

#changed from cosine to frequency proportion
fit.country_corpus = glmer(responses_theme ~ country + theme_freq_prop_E + theme_freq_prop_M + (1 | subject) + (1 | triad), 
                           data = df %>% filter(country != "Vietnam"), 
                           family = "binomial")

fit.add_corpus <- anova(fit.country, fit.country_corpus, type = 3)
fit.add_corpus

```
*Should this analysis be updated to be more similar to the analysis in 3 (next section)?*
We carried out an ANOVA model comparison to compare our approach with previous studies that did not include corpus information. Because @Ji2004 only compared US and China participants, we filtered our data to only include responding data from these two countries. Our approach would be to compare a model that only includes country (US or China) as a fixed effect with one that also includes English and Chinese corpus data. Our previous model with an intercept per subject and one per triad, as well as by-triad random slopes for country to account for variation in the country effect across triads fails to converge with the more complex model, so we include a simpler random effect structure with an intercept per subject and one per triad in both the basic and more complex model. We compare this model with an identical model but including Chinese and English corpus cosine distance proportion prediction. We found that adding English and Chinese corpus data produces a significantly better fit than the identical model without English and Chinese corpus data as predictors ($\chi^2$(`r fit.add_corpus["fit.country_corpus", "Df"]`) = `r round(fit.add_corpus["fit.country_corpus", "Chisq"], 2)`, p = < .001. This suggests that including corpus data would better model the cross-cultural differences in similarity judgment in this study as well as similar studies.

## Does similarity reasoning differ across cultures, only the input to it, or both?
Does adding country and interaction term with the corresponding corpus improves the model? 
```{r}
df <- df %>%
  mutate(theme_freq_prop_corr_lang = case_when(
    country == "US" ~ theme_freq_prop_E,
    country == "China" ~ theme_freq_prop_M, 
    country == "Vietnam" ~ theme_freq_prop_V))

fit.language = glmer(responses_theme ~ theme_freq_prop_corr_lang + (1 | subject) + (1 | triad), 
          data = df %>% filter(!(triad %in% triads_omit)),  
          family="binomial")
summary(fit.language)
fit.language.anova = Anova(fit.language, type = 3)
fit.language.anova

fit.country_language = glmer(responses_theme ~ theme_freq_prop_corr_lang * country + (1 | subject) + (1 | triad), 
          data = df %>% filter(!(triad %in% triads_omit)),  
          family="binomial")
summary(fit.country_language)
fit.country_language.anova = Anova(fit.country_language, type = 3)
fit.country_language.anova

fit.country_language_compare = anova(fit.language, fit.country_language, type = 3)
fit.country_language_compare
```

Adding country improves the model. Only country and interaction between country and corresponding corpus's lexical co-occurrence are significant predictors. Corresponding corpus's lexical co-occurrence is no longer a significant predictor.

## How specific are the cross-language differences in similarity judgments we observe?
```{r loading in the csv with semantic coding, include =F}
df.sem_code <- read.csv("../../../data/corpus/corpus_sem_coding.csv")

df <- df %>%
  left_join(df.sem_code, by = "triad")
```
### Do we see differential responding across cue items from different semantic domains?
Plotting mean response theme by country, by type of triad
```{r plotting thematic responses by cue_genre, cache = T}

ggplot(data = df) + 
   geom_bar(stat = "summary", 
            fun.data = "mean_cl_boot",
            alpha = .5, 
            mapping = aes(x = cue_genre, 
                          y = responses_theme)) +
  geom_pointrange(stat = "summary", 
            fun.data = "mean_cl_boot",
            alpha = .5, 
            mapping = aes(x = cue_genre, 
                          y = responses_theme))

```

```{r plotting thematic response by cue_genre and country, cache = T}
ggplot(data = df,
       mapping = aes(x = cue_genre, 
                     y = responses_theme,
                     color = country, 
                     fill = country)) + 
   stat_summary(fun.data = "mean_cl_boot", 
               geom = "pointrange") 
#color code by cue genre, spatial sep by country, plotting all triads (mean response)

```

```{r plotting thematic response by cue_genre, country and triad, cache = T}
ggplot(data = df, 
       mapping = aes(x = country, 
                     y = responses_theme, 
                     label = triad, 
                     group = triad,
                     color = cue_genre)) + 
  stat_summary(fun.data = "mean_cl_boot", 
               geom = "point", 
               alpha = .5, 
               position = position_dodge(width = .2)) + 
  stat_summary(fun.data = "mean_cl_boot", 
               geom = "text", 
               position = position_dodge(width = .2), size = 2)
```

There seems to be a preference for more thematic matches in the 'living things' cues in comparison to the 'moveable artifacts' cue.

Comparing some models (omitting cue_genre = "other") *should we omit 'other' from the analysis?*

#### English
Base line model:

```{r US responding predicted by corpus co-occurrences, warning=FALSE, cache = T}
# English 
fit.EN_US_cue_genre_base = glmer(responses_theme ~ theme_freq_prop_E + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "US", 
                               !(triad %in% triads_omit),
                               !(cue_genre == "other")), 
          family="binomial")
summary(fit.EN_US_cue_genre_base)
fit.EN_US_cue_genre_base.anova = Anova(fit.EN_US_cue_genre_base, type = 3)
```

Adding cue genre: significant

```{r US responding, co-occurrence and cue_genre, cache = T}
fit.EN_US_cue_genre = glmer(responses_theme ~ theme_freq_prop_E + cue_genre + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "US", 
                               !(triad %in% triads_omit),
                               !(cue_genre == "other")), 
          family="binomial")

summary(fit.EN_US_cue_genre)
Anova(fit.EN_US_cue_genre, type = 3)
```

Anova comparison: including cue genre is a better model
```{r US anova comparison, cue_genre, cache = T}
fit.EN_US_cue_genre_compare = anova(fit.EN_US_cue_genre_base, fit.EN_US_cue_genre, type = 3)
fit.EN_US_cue_genre_compare
```
#### Vietnamese

```{r VN responding predicted by VN corpus model, warning=FALSE, cache = T}

#Vietnamese
fit.VI_VN_cue_genre_base = glmer(responses_theme ~ theme_freq_prop_V + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "Vietnam", 
                               !(triad %in% triads_omit), 
                               !(cue_genre == "other")), 
          family="binomial")
summary(fit.VI_VN_cue_genre_base)
fit.VI_VN_cue_genre_base.anova = Anova(fit.VI_VN_cue_genre_base, type = 3)
```

Adding cue genre: NOT significant

```{r VN responding, co-occurrence + cue_genre}
fit.VI_VN_cue_genre = glmer(responses_theme ~ theme_freq_prop_V + cue_genre + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "Vietnam", 
                               !(triad %in% triads_omit), 
                               !(cue_genre == "other")), 
          family="binomial")

summary(fit.VI_VN_cue_genre)
Anova(fit.VI_VN_cue_genre, type = 3)
```

Anova comparison (also not significant)
```{r VN anova comparison, cue_genre, cach}
fit.VI_VN_cue_genre_compare = anova(fit.VI_VN_cue_genre_base, fit.VI_VN_cue_genre, type = 3)
fit.VI_VN_cue_genre_compare
```

#### Mandarin
```{r CN responding predicted by co-occurrences, warning=FALSE, cache = T}
#Mandarin
fit.ZH_CN_cue_genre_base = glmer(responses_theme ~ theme_freq_prop_M + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "China", 
                               !(triad %in% triads_omit),
                               !(cue_genre == "other")), 
          family="binomial")
summary(fit.ZH_CN_cue_genre_base)
fit.ZH_CN_cue_genre_base.anova = Anova(fit.ZH_CN_cue_genre_base, type = 3)
```

Adding cue genre: significant

```{r CN responding, co-occurrences + cue_genre, cache = T}
fit.ZH_CN_cue_genre = glmer(responses_theme ~ theme_freq_prop_M + cue_genre + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "China", 
                               !(triad %in% triads_omit),
                               !(cue_genre == "other")), 
          family="binomial")

summary(fit.ZH_CN_cue_genre)
Anova(fit.ZH_CN_cue_genre, type = 3)
```
Anova comparison: including cue genre is a better model
```{r CN anova comparison,cue_genre, cache = T}
fit.ZH_CN_cue_genre_compare = anova(fit.ZH_CN_cue_genre_base, fit.ZH_CN_cue_genre, type = 3)
fit.ZH_CN_cue_genre_compare
```

When added to the baseline model, cue genre is a significant predictor for US and China responses. But not for Vietnam.

### Do we see differential responding across distinct types of thematic relationships?
Plotting mean response theme by country, by type of thematic match
```{r plotting thematic responses by theme_genre, cache = T}
ggplot(data = df) + 
   geom_bar(stat = "summary", 
            fun.data = "mean_cl_boot",
            alpha = .5, 
            mapping = aes(x = theme_genre, 
                          y = responses_theme)) +
  geom_pointrange(stat = "summary", 
            fun.data = "mean_cl_boot",
            alpha = .5, 
            mapping = aes(x = theme_genre, 
                          y = responses_theme)) +
  geom_hline(yintercept = 0.5)

```

```{r plotting thematic responses by theme_genre and country}
ggplot(data = df) + 
   geom_bar(stat = "summary", 
            fun.data = "mean_cl_boot",
            mapping = aes(x = theme_genre, 
                          y = responses_theme, 
                          fill = country), 
            position = position_dodge(width = .7), width = .7) +
  geom_pointrange(stat = "summary", 
            fun.data = "mean_cl_boot",
            mapping = aes(x = theme_genre, 
                          y = responses_theme,
                          group = country), 
            position = position_dodge(width = .7)) +
  geom_hline(yintercept = 0.5)
#color code by cue genre, spatial sep by country, plotting all triads (mean response)

```

```{r plotting thematic response by country, triad and theme_genre}
ggplot(data = df, 
       mapping = aes(x = country, 
                     y = responses_theme, 
                     label = triad, 
                     group = triad)) + 
  geom_point(stat = "summary", 
             fun.data = "mean_cl_boot", 
             position = position_dodge(width = .7)) +
  geom_text(stat = "summary", 
            fun.data = "mean_cl_boot", 
            color = alpha('black'),
            position = position_dodge(width = .7), size = 2) +
  geom_violin(data = df %>% 
                group_by(country, theme_genre, triad) %>%
                summarize(theme_resp_triad = mean(responses_theme, na.rm = T)), 
                mapping = aes(x = country,
                              y = theme_resp_triad, 
                              group = country,
                              fill = country,
                              color = country), 
                alpha = .5) + 
  facet_grid(~theme_genre)

# geom_point(data = df %>% filter(theme_genre == 'ecology'),
#            mapping = aes(x = country,
#                    y = responses_theme,
#                    label = triad,
#                    group = triad,
#                    color = theme_genre),
#            stat = "summary",
#            fun.data = "mean_cl_boot",
#            position = position_dodge(width =.7))

```

1. All theme match semantic categories prefer thematic, except for association.
2. China is always the most thematic in all theme match semantic categories. Only country that prefers thematic across all categories. 
3. Only US & Vietnam + association prefer taxonomic. Overall, association seems to be least thematic preferring.
4. Vietnam is not significantly different from US except for ecology. 
5. Most thematic: causal (but might be driven by strong China response) and occupation (most consistent across countries to be thematic).

#### English
Base line model:

```{r US responding predicted by corpus co-occurrences re-run for theme_genre, warning=FALSE}
# English 
fit.EN_US_theme_genre_base = glmer(responses_theme ~ theme_freq_prop_E + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "US", 
                               !(triad %in% triads_omit)), 
          family="binomial")
summary(fit.EN_US_theme_genre_base)
fit.EN_US_theme_genre_base.anova = Anova(fit.EN_US_theme_genre_base, type = 3)
```

Adding theme genre: significant

```{r US responding, co-occurrence and theme_genre}
fit.EN_US_theme_genre = glmer(responses_theme ~ theme_freq_prop_E + theme_genre + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "US", 
                               !(triad %in% triads_omit)), 
          family="binomial")

summary(fit.EN_US_theme_genre)
fit.EN_US_theme_genre.anova = Anova(fit.EN_US_theme_genre, type = 3)
```

Anova comparison: including theme genre is a better model
```{r US anova comparison, theme_genre}
fit.EN_US_theme_genre_compare = anova(fit.EN_US_theme_genre_base, fit.EN_US_theme_genre, type = 3)
fit.EN_US_theme_genre_compare
```
#### Vietnamese

```{r VN responding predicted by VN corpus model re-run for theme_genre, warning=FALSE}

#Vietnamese
fit.VI_VN_theme_genre_base = glmer(responses_theme ~ theme_freq_prop_V + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "Vietnam", 
                               !(triad %in% triads_omit)), 
          family="binomial")
summary(fit.VI_VN_theme_genre_base)
fit.VI_VN_theme_genre_base.anova = Anova(fit.VI_VN_theme_genre_base, type = 3)
```

Adding theme genre: not significant

```{r VN responding, co-occurrence + theme_genre}
fit.VI_VN_theme_genre = glmer(responses_theme ~ theme_freq_prop_V + theme_genre + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "Vietnam", 
                               !(triad %in% triads_omit)), 
          family="binomial")

summary(fit.VI_VN_theme_genre)
fit.VI_VN_theme_genre.anova = Anova(fit.VI_VN_theme_genre, type = 3)
```

Anova comparison: not significant
```{r VN anova comparison, theme_genre}
fit.VI_VN_theme_genre_compare = anova(fit.VI_VN_theme_genre_base, fit.VI_VN_theme_genre, type = 3)
fit.VI_VN_theme_genre_compare
```

#### Mandarin
```{r CN responding predicted by co-occurrences re-run for theme_genre, warning=FALSE}
#Mandarin
fit.ZH_CN_theme_genre_base = glmer(responses_theme ~ theme_freq_prop_M + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "China", 
                               !(triad %in% triads_omit)), 
          family="binomial")
summary(fit.ZH_CN_theme_genre_base)
fit.ZH_CN_theme_genre_base.anova = Anova(fit.ZH_CN_theme_genre_base, type = 3)
```

Adding theme genre: NOT significant

```{r CN responding, co-occurrences + theme_genre}
fit.ZH_CN_theme_genre = glmer(responses_theme ~ theme_freq_prop_M + theme_genre + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "China", 
                               !(triad %in% triads_omit)), 
          family="binomial")

summary(fit.ZH_CN_theme_genre)
fit.ZH_CN_theme_genre.anova = Anova(fit.ZH_CN_theme_genre, type = 3)
fit.ZH_CN_theme_genre.anova
```
Anova comparison: including theme genre is not a better model
```{r CN anova comparison, theme_genre}
fit.ZH_CN_theme_genre_compare = anova(fit.ZH_CN_theme_genre_base, fit.ZH_CN_theme_genre, type = 3)
fit.ZH_CN_theme_genre_compare
```

When added to the baseline model, theme genre is a significant predictor for Vietnam response, but not for US and China!

```{r summary of semantic coding result}
text_tbl <- data.frame(
  Country = c("US", "China", "Vietnam"),
  Add_Cue_Genre = c(
    "significant", "significant", "not significant"
  ), 
  Add_Theme_Genre = c(
    "significant", "not significant", "not significant"
  )
)
kable(text_tbl)
```

## How general are the cross-language differences in similarity judgments we observe? Are they limited to taxonomic-thematic contrasts or do they extend to other cases?

```{r incorporate base freq}
df.filler <- read.csv("../../../data/data_filler_USCNVN_ENZHVI.csv")
```

```{r warning=FALSE, cache = TRUE, include = FALSE, paged.print=TRUE}
df.country_filler <- df.filler %>%
  group_by(subject, country) %>%
  summarize(word1_resp_percent = mean(responses_word1, na.rm = T))
```

```{r echo=FALSE, warning=FALSE, cache = TRUE, fig.cap="Proportion of thematic responses by country. Only US-China responding comparison shows a siginficant difference. We could not extend this to US-Vietnam responding comparison."}

#show violin plot
ggplot(df.country_filler,
       mapping = aes(x = factor(country, levels=c("China", "US", "Vietnam")), 
                     y = word1_resp_percent, 
                     color = factor(country, levels=c("China", "US", "Vietnam")))) +
  geom_violin() +
  geom_jitter(height = 0, 
              alpha = 0.3) +  
  stat_summary(fun.data = "mean_cl_boot", 
               geom = "pointrange") + 
  labs(y = "Proportion Word1 Chosen", 
       x = "Country", 
       color = "Country") + 
  scale_color_manual(values=c("#D63230", "#1C77C3", "#F39237"))
```

```{r warning=FALSE, include = TRUE, cache = TRUE, paged.print=TRUE}
# df.country_sum <- df.country %>%
#   group_by(country) %>%
#   summarize(mean_theme_resp_percent = mean(theme_resp_percent), 
#             sd_theme_resp_percent = sd(theme_resp_percent))

fit.country_filler = glmer(responses_word1 ~ country + (1 | subject) + (country | cue),
                    data = df.filler, 
                    family = "binomial")
summary(fit.country_filler) 
fit.country_filler.anova = Anova(fit.country_filler, type=3)
fit.country_filler.anova
```

No effect of country on filler responding.

### Does lexical co-occurrences for fillers predict responding in the corresponding cultural context?

```{r US responding predicted by each corpus model raw co-occurrences for fillers, warning=FALSE}
# English 
fit.EN_US_filler = glmer(responses_word1 ~ word1_match_frequency_prop_E + (1 | subject) + (1 | cue), 
          data = df.filler %>% filter(country == "US", 
                               !(near(word1_match_frequency_E, .Machine$double.eps) & 
                                  near(word2_match_frequency_E, .Machine$double.eps))), 
          family="binomial")
summary(fit.EN_US_filler)
fit.EN_US_filler.anova = Anova(fit.EN_US_filler, type = 3)

fit.EN_US_filler.anova
```

```{r VN responding predicted by each corpus model raw co-occurrences for fillers, warning=FALSE}
# Vietnamese
fit.VI_VN_filler = glmer(responses_word1 ~ word1_match_frequency_prop_V + (1 | subject) + (1 | cue), 
          data = df.filler %>% filter(country == "Vietnam", 
                               !(near(word1_match_frequency_V, .Machine$double.eps) & 
                                  near(word2_match_frequency_V, .Machine$double.eps))), 
          family="binomial")
summary(fit.VI_VN_filler)
fit.VI_VN_filler.anova = Anova(fit.VI_VN_filler, type = 3)

fit.VI_VN_filler.anova
```
Yes, corpus predicts responding for both US and Vietnamese. *need to discuss with Shan to incorporate Mandarin due to a lot of empty counts*

### 2022-12-31 code/4_paper/manuscript/manuscript.Rmd
added analysis with cosine distance

@@
 ---
-title: "How to Make a Proceedings Paper Submission"
+title: "Re-examining cross-cultural similarity judgements using lexical co-occurrence"
 bibliography: library.bib
@@
 document-params: "10pt, letterpaper"
+
+header-includes:
+  - \usepackage[utf8]{inputenc}
+  - \usepackage[T1, T5]{fontenc}
 
@@
 One possibility is that cultures co-varying with these languages induce variation in conceptualizations of similarity.
-Specifically, East Asian cultures may promote reasoning about thematic similarity, by which cow and grass are more related whereas Western cultures may bias similarity judgments toward taxonomic relations, like cow-chicken.
+Specifically, East Asian cultures may promote reasoning about thematic similarity, by which cow and grass are more related whereas Western cultures may bias similarity judgements toward taxonomic relations, like cow-chicken.
 This difference in notions of similarity is the consensus interpretation for cross-cultural variation in this paradigm.
 We consider, and provide evidence for, an alternative possibility, by which notions of similarity are equivalent across contexts, but the statistics of the environment vary.
-On this account, similarity judgments are guided by co-occurrence in experience, and observing or hearing about cows and grass or cows and chickens more often could induce preferences for the relevant grouping and account for apparent differences in notions of similarity across contexts.
+On this account, similarity judgements are guided by co-occurrence in experience, and observing or hearing about cows and grass or cows and chickens more often could induce preferences for the relevant grouping, and account for apparent differences in notions of similarity across contexts.
 
@@
                       fig.pos = "tb", fig.path='figs/',
-                      echo=F, warning=F, cache=F, 
+                      echo=F, warning=F, cache=T, 
                       message=F, sanitize = T)
@@
 
-```{r, libraries}
+```{r, libraries, cache=F}
 library(png)
@@
 
-```{r setup, echo = FALSE, include = FALSE}
+```{r setup, include = FALSE, cache=F}
 library("papaja")
@@
 
-# these options here change the formatting of how comments are rendered
-opts_chunk$set(
-  comment = "",
-  results = "hold",
-  fig.show = "hold")
+# # these options here change the formatting of how comments are rendered
+# opts_chunk$set(
+#   comment = "",
+#   results = "hold",
+#   fig.show = "hold")
 
@@
 
-```{r analysis-preferences}
+```{r analysis-preferences, cache=F}
 # Seed for random number generation
@@
 By virtue of discrete words and grammatical features, language provides a categorical partition of our continuous experiences.
-Previous research has observed variation in the cognition of speakers of different languages corresponding to variation within semantic domains in these languages.
-This language-aligned variation has been observed in the domains of color [@Winawer2007], number [@Frank2008], and gender [@Boroditsky2003], among many others [@Wolff2011].
-Differences in cognition between speakers of different languages have often been used to suggest, explain, or exemplify cultural differences between speakers of those languages.
-Findings in studies of both language and of culture provide convergent evidence suggesting that variation across languages and cultures may shape broad variation in how people think about similarity between, for instance, different colors or objects.
-
-Looking beyond this domain-specific variation, we can also consider broader notions of similarity and relatedness between concepts across domains.
-The Free Association Norms [@FreeAssoc], for example, measures human judgment in semantic relatedness across domains and contexts.
-With the availability of large linguistic corpora, we can examine the similarity of concepts that are not circumscribed in individual domains (as color, number, and gender are), allowing us to answer more general questions about variation in cognition between speakers of different languages.
-By measuring the similarity between arbitrary words (as commonly done with lexical co-occurrence models), it may be possible to model the shape of similarity space in order to capture cross-linguistic and cross-cultural variation and provide a more general answer to the question of how language influences our conception of the world.
+By measuring the similarity between words (as commonly done with lexical co-occurrence models), it may be possible to model the shape of similarity space in order to capture cross-linguistic and cross-cultural variation and provide a more general answer to the question of how language influences our conception of the world.
 
@@
 
-@Ji2004 found that preferences for taxonomic and thematic matches differ across culture, even when controlling for testing language and fluency.
+@Ji2004 found that preferences for taxonomic and thematic matches differ across cultures, even when controlling for testing language and fluency.
 Specifically, Chinese participants made more thematic matches than taxonomic, while the converse was true for European Americans.
@@
 ## Cross-cultural variation in similarity
-The account that culture drives differences in categorization style has been one favored by other non-linguistic studies that use taxonomic vs thematic categorization to probe similarity judgment.
-A similar study to the aforementioned shows that when shown pictorial triads that represent words (i.e.
+The view that culture drives differences in categorization style has been one favored by other non-linguistic studies that use taxonomic vs thematic categorization to probe similarity judgment.
+When shown pictorial triads that represent words (i.e.
 pictures of an ant, a bee, and honey), Chinese children (9-10 years old) scored higher on thematic categorization compared to American children of the same age range, and vice versa for taxonomic categorization [@Chiu1972].
-Additionally, the cross-cultural differences in similarity judgment seem to persist even when the stimuli are more perceptual and less conceptual.
-@Norenzayan2002 conducted a study where participants are shown a target stimulus beneath two groups of 4 similar objects.
-The target shares a common feature with all the objects in one group, and only shares another one feature with each member of that group.
-Meanwhile, the target shares many features with 3 out of 4 members of the other group, but does not share any 1 feature in common with the entire group.
-The study showed that American participants judged the target to be more similar with the former group more often, and vice versa for Chinese participants.
+These cross-cultural differences in similarity judgment persist in novel object categorization, with Chinese participants preferring to group by family resemblance across multiple features and Americans preferring a single-feature rule [@Norenzayan2002].
 Since differences in categorization style persist with novel stimuli (as opposed to previously seen words or pictures of concepts), this suggests that participants from different cultural backgrounds are utilizing different reasoning strategies when making similarity judgments.
-
-Most commonly, researchers account for the differences in similarity judgment described above by differences in analytic vs holistic processing and in attention between Eastern and Western cultures.
-According to this framework, East Asians attend more to relationships between objects and context and reason more holistically, whereas Westerners attend more to objects and their properties, and reason analytically [@Nisbett2003].
-The analytic-holistic cultural difference in reasoning style has been observed in other non-linguistic tasks.
-For example, in a rod-and-frame test [@Witkin1954], East Asian (Taiwanese Chinese) participants are more influenced by the position of the surrounding frame than European Americans [@Ji2000], suggesting a higher level of sensitivity to context.
-East Asians (Koreans) have also been demonstrated to make more situational attributions for behaviors than European Americans, who make more dispositional attributions [@Choi1999], again suggesting higher sensitivity to context.
-When shown a complex scene with foreground and background information, Japanese participants made more statements about contextual information and relationships between objects than Americans did [@Masuda2001].
-Non-linguistic tasks have also shown that participants from Eastern and Western cultures differ in where they focus their visual attention.
-Another study presented American and Chinese participants with photographs of an object on a complex background [@Chua2005].
-They found that Chinese participants made more eye saccades to the background compared to American participants, and that American participants looked at the object more quickly.
+The authors attribute these differences to tendencies toward analytic processing in Western cultures, which emphasizes objects and their properties and holistic processing in East Asian cultures, which emphasizes relationships between objects and their context.
+According to this framework, East Asians attend more to relationships between objects and context and reason more holistically, whereas Westerners attend more to objects and their properties, and reason analytically (ibid, see also @Nisbett2003).
+In related work, East Asian participants show a higher level of sensitivity to context than their Western counterparts when reproducing drawings from memory [@Ji2000]; visually exploring naturalistic scenes [@Chua2005]; describing scenes [@Masuda2001]; and in explaining the causes of ambiguous behaviors [@Choi1999].
 These cross-cultural differences in attention and analytic vs holistic processing are seen to map onto the cross-cultural differences in similarity judgment: because East Asian participants attend more to the context between objects and reason more holistically, it stands to reason that they would consider words that appear in the same context (i.e.
@@
 
-Studies that explain these cross-cultural differences in reasoning and similarity judgment with a cultural framework often draw on social and historical contexts as the distal cause for these differences.
-For example, social structure and social practice can explain why different cultures develop different reasoning habits.
-To demonstrate this, researchers have looked at regions that are geographically close but with different social structures.
-@Kitayama2006 showed that Hokkaido Japanese demonstrated greater dispositional bias in attribution of behaviors compared to non-Hokkaido Japanese.
-The study suggested that this difference is correlated to the fact that Hokkaido was settled quite recently (mid-19th century) by pioneers from southern Japan, and thus its social practices (e.g.
-daily routines, child-rearing practices, and explicit education) would be influenced by the independent, goal-oriented characteristic of pioneer life.
-Another study showed that Northern Italians (more independent) categorized objects in a more taxonomic manner than Southern Italians (more interdependent) [@Knight2007].
-These studies, however, stopped short of providing a mechanism for the nature of the relationship between differences in social structures and differences in reasoning and similarity judgments.
-
-Another component of the social context explanation seems to be more tenable regarding the causal connection between cross-cultural differences in social practice and those in similarity judgments: that different patterns of attention are passed on by caregivers to children.
-@Fernald1993 found that American mothers labeled toys and pointed out their attributes more often than do Japanese mothers, while Japanese mothers tended to use the toys to engage their infants in social routines more often than American mothers.
-@Tardif1997 found that English-speaking caregivers produced more nouns than verbs in child-directed speech, while Mandarin-speaking caregivers emphasized verbs over nouns.
-Emphasis on labeling objects and focus on nouns over verbs might lead infants to attend to objects and their taxonomic categorizations, while emphasis on social practices and producing more verbs might direct infants' attention to the relationship between objects.
-Such differences in early-childhood environments could tune children’s attention to either object or context, and result in cross-cultural differences in similarity judgments (preferring either taxonomic or thematic, respectively) in adulthood.
-
-The above view explains cross-cultural differences in similarity judgment tasks as variation in the conceptualization of similarity itself.
+This view ascribes cross-cultural differences in similarity judgment tasks to variation in the conceptualization of similarity itself.
 Alternatively, these judgments could be shaped by cross-cultural differences in the statistics of the environment, and accordingly the content of everyday experiences.
@@
 Americans, on the other hand, may have strong associations between cows and chickens as a result of encountering them together in children’s books or petting zoo contexts.
-If we observe a difference in categorization between, say Vietnamese and US participants, perhaps they use the same procedure (considering similarity that is influenced by both taxonomic and thematic relations), but the inputs to this procedure differ between cultures, with Vietnamese participants exposed to more instances of “cow” and “grass” occurring together, compared to US participants.
-
-A study by @Miyamoto2006 lends support to this theory.
-The study randomly sampled scenes from different-sized cities in Japan and the US.
-Both subjective (judgment by American and East Asian college students) and objective (number of objects as counted by an automated program) showed that Japanese scenes were more complex and contained a larger number of objects than American scenes.
-This suggests that people living in Japan would more frequently encounter perceptual environments that contain more relationships between objects compared to those who live in the US.
-Japanese scenes therefore might encourage focus on the overall context, while American scenes might encourage focus on a few salient objects.
-
-Differences in environmental statistics extend beyond the immediate environment to cultural artifacts.
-@Tsai2007 showed that best-selling storybooks in the US contain more pictures of excited states (e.g.
-open-mouthed smiles, wide-open eyes) compared to best-selling storybooks in Taiwan, which contain more pictures of calm states.
-European American preschoolers also perceived excited states as happier and more desirable compared to calm states, and vice versa for Taiwanese Chinese preschoolers.
-The study also showed that there is a causal link between exposure to environmental statistics and personal preference: regardless of culture, exposure to exciting (vs.
-calm) storybooks increased children’s preference for the  corresponding activities.
-Broadly, this suggests that cultural artifacts or information in language (rather than direct, first-hand lived experiences) could be crucial factors in driving cross-cultural variation.
+If we observe a difference in categorization between, say Vietnamese and US participants, it could be that members of both groups use the same procedure (considering similarity that is influenced by both taxonomic and thematic relations), but the inputs to this procedure differ between cultures, with Vietnamese participants exposed to more instances of “cow” and “grass” occurring together, compared to US participants.
 
@@
 While co-occurrences in experience are difficult to measure, co-occurrence in language can provide a rough proxy--and indeed, language may afford many of the “experiences” that people have with infrequently encountered items, like cows or helicopters.
-In the planned analyses, we will use co-occurrence in language as a proxy of cultural experience.
-This is a generalizing assumption, and while no linguistic corpus can be expected to fully capture a culture, and different linguistic corpora may capture different variables of a culture, using this proxy as a model of culture provides a conservative test of the hypothesis that differences in the input, rather than the process, of reasoning produces cultural variation in this task.
+In this study, we use co-occurrence in language as a proxy of cultural experience.
+This is a generalizing assumption, and while no linguistic corpus can be expected to fully capture a culture, using this proxy as a model of culture provides a conservative test of the hypothesis that differences in the input, rather than the process, of reasoning produces cultural variation in this task.
 This means that if such a model does work -- if linguistic co-occurrence can predict cultural variation in this similarity task without building differences in the decision process into the model -- it is relatively strong evidence that language alone (perhaps as a more easily observed source of information on broader cultural and ecological variation) may account for these cross-cultural differences in reasoning.[^footnote]
@@
 ## The present study
-@Ji2004 showed the difference in similarity judgment between Chinese and European Americans (the former prefers thematic categorization while the latter prefers taxonomic).
+<!-- @Ji2004 observed a difference in similarity judgment between Chinese and European Americans (the former preferred thematic matching the latter taxonomic).
 However, their evidence is not sufficient to conclude that it is culture that drives this difference, as their cross-cultural data is correlational.
@@
 This would have been stronger in eliminating online effect of language as a potential cause for cross-cultural differences in similarity judgment.
+-->
 
-Additionally, outside of language, cross-cultural differences could come from a couple different mechanisms: @Ji2004 suggested that the notion of similarity is what varies across cultural groups, but it’s quite possible that similarity is regarded in the same way and it’s actually the input to this similarity judgment that varies across culture contexts.
+<!-- Additionally, outside of language, cross-cultural differences could come from a couple different mechanisms:  -->
+@Ji2004 suggest that the notion of similarity is what varies across cultural groups, but it is quite possible that similarity is regarded in the same way and it is actually the input to this similarity judgment that varies across culture contexts.
 It might be possible to gain traction on possible mechanisms by examining whether variation in similarity judgments co-varies with environmental statistics that differ across the cultural and linguistic contexts.
@@
 In this study, we ask whether variation in lexical co-occurrence can account for the cross-context (culture and language) differences observed in how people evaluate similarity.
-Firstly, we attempt to replicate @Ji2004 by running a study comparing English speakers in the US and Mandarin speakers in mainland China.
-Secondly, we evaluate whether the differences observed between English and Mandarin speakers’ similarity judgments also extend to comparisons between English and Vietnamese, by running a similar study between English speakers in the US and Vietnamese speakers in Vietnam.
+First, we attempt to replicate @Ji2004 by running a study comparing English speakers in the US and Mandarin speakers in mainland China.
+Second, we evaluate whether the differences observed between English and Mandarin speakers’ similarity judgments also extend to comparisons between English and Vietnamese, by running a similar study between English speakers in the US and Vietnamese speakers in Vietnam.
 Vietnam is a Southeast Asian country that borders China and is historically greatly influenced by Chinese culture [@Hui2002].
@@
 We then ask to what extent similarity judgments show cross-context differences that align with co-occurrence patterns in participants’ languages.
-We would only see a main effect of cultural context if the notion of differing notions of similarity is driving these cross-cultural differences.
-Meanwhile, if we do see variation in responding trial-to-trial that tracks with lexical co-occurrence statistics (as a rough proxy combining both linguistic and cultural context), this would give traction to the view that cross-cultural notions of similarity might be similar, and it is environmental statistics that guide the differences in similarity judgments.
+We would only see a main effect of cultural context if differing notions of similarity drive these cross-cultural differences.
+Meanwhile, if we do see variation in responding trial-to-trial that tracks with lexical co-occurrence statistics (as a rough proxy combining both linguistic and cultural context), this suggests that cross-cultural notions of similarity might be similar, and it is environmental statistics that guide the differences in similarity judgments.
 To preview our results, we find that, while we do not see overall group differences (between the East Asian contexts and the US) in similarity, we do find language-specific co-occurrence can indeed explain cross-context differences in similarity judgments.
 In contrast to previous accounts, by which culture induces differing conceptions of similarity (varying between taxonomic and thematic), these findings provide an alternative, and more specific, account by which language may explain these cross-cultural differences without invoking variation in notions of similarity.
+
+# Methods 
+```{r get responding and demographic data, include = F}
+df <- read.csv("../../../data/data_USCNVN_ENZHVI.csv")
+
+df_main_analysis <- df
+df.demog <- read.csv("../../../data/responding/data_demog.csv") %>%
+  filter(subject %in% unique(df$subject))
+
+triads_omit <- read.csv("../../../data/triads_omit.csv") %>%
+  pull(x)
+```
+
+```{r get exclusions data, include = F, cache = T}
+df.excl_US <- read.csv("../../../data/responding/dataUS_excl_metadata.csv")
+df.excl_CN <- read.csv("../../../data/responding/dataCN_excl_metadata.csv")
+df.excl_VN <- read.csv("../../../data/responding/dataVN_excl_metadata.csv")
+```
+
+```{r demog_E, include = F, cache = T}
+df.demog_E <- df.demog %>%
+  filter(country == "US")
+
+df.age_E <- df.demog_E %>%
+  filter(demog_question == "age") %>%
+  mutate(demog_response = as.numeric(demog_response)) %>%
+  summarize(mean_age = mean(demog_response), 
+            median_age = median(demog_response), 
+            sd_age = sd(demog_response))
+
+df.gender_E <- df.demog_E %>%
+  filter(demog_question == "gender") %>%
+  group_by(demog_response) %>%
+  rename(gender = demog_response) %>%
+  summarize(n=n())
+```
+
+```{r demog_M, include = F, cache = T}
+df.demog_M <- df.demog %>%
+  filter(country == "CN")
+
+df.age_M <- df.demog_M %>%
+  filter(demog_question == "age") %>%
+  mutate(demog_response = as.numeric(demog_response)) %>%
+  summarize(mean_age = mean(demog_response), 
+            median_age = median(demog_response), 
+            sd_age = sd(demog_response))
+
+df.gender_M <- df.demog_M %>%
+  filter(demog_question == "gender") %>%
+  group_by(demog_response) %>%
+  rename(gender = demog_response) %>%
+  summarize(n=n())
+```
+
+```{r demog_V, include = F, cache = T}
+df.demog_V <- df.demog %>%
+  filter(country == "VN")
+
+df.age_V <- df.demog_V %>%
+  filter(demog_question == "age") %>%
+  mutate(demog_response = as.numeric(demog_response)) %>%
+  summarize(mean_age = mean(demog_response), 
+            median_age = median(demog_response), 
+            sd_age = sd(demog_response))
+
+df.gender_V <- df.demog_V %>%
+  filter(demog_question == "gender") %>%
+  group_by(demog_response) %>%
+  rename(gender = demog_response) %>%
+  summarize(n=n())
+```
+
+## Participants
+We recruited `r df.excl_US$ppts_finished` participants from the US, `r df.excl_VN$ppts_finished` participants from Vietnam, and `r df.excl_CN$ppts_finished` participants from mainland China.
+US participants were recruited through snowball sampling seeded with Stanford student email lists, Vietnam participants were recruited through snowball sampling seeded with Vietnam-based student groups on Facebook, and mainland China participants were recruited through snowball sampling seeded with group chats on WeChat.
+US participants were compensated with $5 gift certificates (USD), VN participants received 50,000₫ (VND) in phone credit, and mainland China participants received 25CNY through WeChat credit transfer.
+
+We excluded `r df.excl_US$ppts_finished - df.excl_US$ppts_after_att_check_excl` US participants, `r df.excl_VN$ppts_finished - df.excl_VN$ppts_after_att_check_excl` Vietnam participants, and `r df.excl_CN$ppts_finished - df.excl_CN$ppts_after_att_check_excl` China participants who did not answer all attention checks correctly.
+We followed 4 exclusion criteria that aim to retain only participants who are influenced by one culture: (1) non-native speakers of English and Vietnamese, respectively, (2) fluent in at least one of the other two study languages (Vietnamese for US participants, English for Vietnamese participants and Chinese participants), (3) have lived outside of the test country (US, Vietnam, or China) for more than two years, and (4) have significant international experience (more than 6 international experiences of 2 days or longer.) We did not use a particular criterion for a language if it would exclude 25% or more of any one sample.
+In this round of exclusion, we excluded `r df.excl_US$ppts_after_att_check_excl - df.excl_US$ppts_after_demog_excl` US, `r df.excl_VN$ppts_after_att_check_excl - df.excl_VN$ppts_after_demog_excl` Vietnam participants, and `r df.excl_CN$ppts_after_att_check_excl - df.excl_CN$ppts_after_demog_excl` China participants.
+After these exclusions, the US sample included `r df.excl_US$ppts_after_demog_excl` participants (`r df.gender_E %>% filter(gender == "Male") %>% pull(n)`M, `r df.gender_E %>% filter(gender == "Female") %>% pull(n)`F, `r df.gender_E %>% filter(gender == "Non-binary") %>% pull(n)` non-binary, `r df.gender_E %>% filter(gender == "Decline to answer") %>% pull(n)` other), with mean age = `r round(df.age_E$mean_age, 2)` (SD = `r round(df.age_E$sd_age, 2)`) and median age = `r df.age_E$median_age`.
+The Vietnam sample included `r df.excl_VN$ppts_after_demog_excl` participants (`r df.gender_V %>% filter(gender == "Nam") %>% pull(n)`M, `r df.gender_V %>% filter(gender == "Nữ") %>% pull(n)`F, `r df.gender_V %>% filter(gender == "Từ chối trả lời") %>% pull(n)` other), with mean age = `r round(df.age_V$mean_age, 2)` (SD = `r round(df.age_V$sd_age, 2)`) and median age = `r df.age_V$median_age`.
+The China sample included `r df.excl_CN$ppts_after_demog_excl` participants (`r df.gender_M %>% filter(gender == "男性") %>% pull(n)`M, `r df.gender_M %>% filter(gender == "女性") %>% pull(n)`F, `r df.gender_M %>% filter(gender == "拒绝回答") %>% pull(n)` other), with mean age = `r round(df.age_M$mean_age, 2)` (SD = `r round(df.age_M$sd_age, 2)`) and median age = `r df.age_M$median_age`.
+
+Notably, we lost a majority of our Vietnam participants (more than 60%) in the attention check exclusion.
+One reason we suspect why this might have happened is because our Vietnam participants are less familiar with research surveys and attention check questions, and thus might have thought too much about the attention check questions.
+We carried out an exploratory analysis where we used a less stringent attention check exclusion (covered in the final part of the Results & Analysis section).
+To preview our findings for this analysis, we did not find any difference in significant results when compared with the main analysis.
+
+## Stimuli
+We adapted stimuli from previous studies to create a set of test triads consisting of a cue, with one thematic and one taxonomic match option.
+For example, “cow,” “grass,” and “chicken,” where “cow” is the cue, “grass” is the thematic match, and “chicken” the taxonomic match.
+We included 105 such triads, a superset including triads pulled from supplemental information and in-text examples across the literature, and others that we adapted or created (see SI for the full list of stimuli and sources).
+We selected triads on the basis of cultural familiarity in the US, Vietnam, and China.
+The triads were originally in English; they were translated to Vietnamese and Mandarin by a fluent bilingual speaker in each language.
+The translations were then checked for accuracy after backtranslation to English by another fluent bilingual in each language who was naive to the original English versions.
+
+Each participant completed all 105 triads in sets of 21 trials at a time (10 test triads, 10 filler triads, and 1 attention check per page), by selecting the match most related to the cue (“Which thing is most closely related to the bolded item?” or "Thứ nào liên quan nhất với thứ được in đậm?").
+The test triads were presented with 105 filler triads mixed in, to obscure the taxonomic-thematic two-answer forced choice structure of the test stimuli and reduce the likelihood that participants would become aware of the design.
+The filler triads were groups of three semantically related words, but where the match options were not distinguished by thematic vs.
+taxonomic similarity, e.g., cue “bird” with match options “lizard” and “toad.” Additionally, we included 10 attention check trials, which were formatted like the test and filler triads but included an instruction instead of a cue item, e.g., “Choose wife” with match options “wife” and “husband.” In total, each participant completed 210 similarity judgments and 10 attention check questions, with triads presented in randomized orders that varied between subjects.
+
+## Corpus model 
+Our general approach is to build a model of similarity that is based on collocation counts in each language.
+
+### Raw lexical co-occurrences
+To give an intuition for our model, consider the cow-grass-chicken triad: we counted how many times “cow” and “grass” co-occur within a window of text in each corpus, and compare this to how many times “cow” and “chicken” co-occur.
+Our similarity prediction is then proportional to the relative frequency of these pairs.
+For example, if the thematic cow-grass match accounts for 30% of collocations for this triad (with cow-chicken making up the other 70%), then our model predicts, correspondingly, that 30% of responses to the triad will be grass, and the other 70% chicken.
+We then use a mixed-effects regression to evaluate how well each corpus collocate model predicts participants’ similarity judgments, across triads and languages.
+
+#### Collocate retrieval and coding
+For our English co-occurrence metric, we used the online interface of the Corpus of Contemporary American English [@COCA] to retrieve collocation counts.
+We recorded the raw count of times that any cue-match pair (e.g., cow-grass or cow-chicken) co-occur in a window of 19 words, which is the maximum window size in the online interface, and closest to the sentence co-occurrence metric in our VI corpus collocation counts.
+
+To determine Vietnamese co-occurrence, we used the raw frequency of sentence co-occurrences from a subset of the Vietnamese corpus in the Leipzig Corpora Collection [@VICorpus]; this corpus includes 70 million Vietnamese sentences, but our corpus data comes from a 1 million sentence subset for which co-occurrence counts are available for download.
+Vietnamese makes very frequent use of compositional morphology but the written language  uses spacing to delineate syllable boundaries rather than word boundaries.
+Accordingly, collocate searches returned instances of both target terms and many morphologically related, but distinct, words.
+We included in our counts any instances of the target term or close semantic neighbors containing the same morpheme(s) as long as they entailed a likely literal reference to the target term.
+For example, our search for collocates of the term “gà” (chicken) also returned “gà mái,” a distinct word for female chickens.
+Despite being a different word, “gà mái” both includes the morpheme for “chicken” and entails reference to a chicken.
+Accordingly, instances of both “gà” and “gà mái” were included in our collocate count for “chicken.” Some compounds do not meet this criteria, and were excluded from collocate counts.
+For example “trái cây” (tree.fruits) includes the same syllable as the word “cây” (tree), but refers to fruit that comes from trees, not the trees themselves, and was therefore excluded from our collocate counts for “tree.”
+
+TODO; ADD INFO ABOUT MANDARIN CORPUS
+
+#### Collocate similarity model
+From the raw co-occurrence counts of each triad, we calculated the thematic co-occurrence ratio as the number of thematic co-occurrences over the sum of thematic and taxonomic co-occurrences.
+We did this for both the English and Vietnamese corpus co-occurrence counts.
+In this way, we obtained predictions for 73 of 105 triads from the Vietnamese corpus and 104 of 105 triads from English.
+We therefore limited all analyses reported here to the subset of triads for which our corpus-based model can make meaningful predictions, meaning triads that have at least one non-zero collocate count (either thematic or taxonomic match).
+We replaced any remaining zero collocate counts with $\epsilon$ to account for sparsity in the corpus data.
+We then tested whether these simple relative frequency models predict US and VN responding.
+
+### Cosine distance of word vectors
+To give an intuition for our model, consider again the cow-grass-chicken triad: we retrieved word vectors for "cow" and "grass", and calculate the cosine distance between these vectors.
+Similarly, we retrieved vectors for "cow" and "chicken" and calculate the cosine distance between them.
+Our similarity prediction is then inversely proportional to the cosine distance of these pairs.
+This is because a larger cosine distance means the word vectors are further apart, and thus the words are less similar.
+For example, if the cosine distance of thematic cow-grass is 0.7 and the cosine distance of taxonomic cow-chicken is 0.3, then our model predicts, correspondingly, that 30% of responses to the triad will be grass, and the other 70% chicken.
+We then use a mixed-effects regression to evaluate how well each corpus model predicts participants’ similarity judgments, across triads and languages.
+
+#### Collocate retrieval
+We use the fastText pre-trained models of English, Mandarin, and Vietnamese in @Grave2018.
+These models are trained on Common Crawl and Wikipedia using We distribute pre-trained word vectors for 157 languages, trained on Common Crawl and Wikipedia using fastText.
+These models were trained using a Continuous Bag of Words (CBOW) with position-weights and a window of size 5.
+The models use character n-grams of length 5 and 10  negative examples.From the aforementioned models, we retrieve the word vectors (dimension 300) for each word we are interested in.
+
+#### Collocate similarity model
+From the word vectors, we calculated the cosine distance between each cue-thematic match (thematic cosine distance) and cue-taxonomic match (taxonomic cosine distance), using the spatial.distance.cosine function from the SciPy package [@2020SciPy].
+We then calculated the thematic cosine distance proportion as thematic cosine distance over the sum of taxonomic cosine distance and thematic cosine distance.
+We did this for all three corpora.
+We were able to obtain predictions for all triads in all languages.
+
+# Results
+
+## 1. Do we extend previous work reporting a preference for taxonomic matching in the US and thematic matching in Asia?
+
+```{r warning=FALSE, cache = TRUE, include=FALSE, paged.print=TRUE}
+df.country <- df %>%
+  group_by(subject, country) %>%
+  summarize(theme_resp_percent = mean(responses_theme, na.rm = T))
+
+df.country_sum <- df.country %>%
+  group_by(country) %>%
+  summarize(mean_theme_resp_percent = mean(theme_resp_percent), 
+            sd_theme_resp_percent = sd(theme_resp_percent))
+
+fit.country = glmer(responses_theme ~ country + (1 | subject) + (country | triad), 
+                    data = df, 
+                    family = "binomial")
+summary(fit.country) 
+fit.country.anova = Anova(fit.country, type=3)
+
+fit.country_EN_VN = glmer(responses_theme ~ country + (1 | subject) + (country | triad), 
+                    data = df %>% filter(country != "China"),
+                    family = "binomial")
+summary(fit.country_EN_VN) 
+```
+The group means of proportion of thematic response in mainland China is the highest (M = `r round((df.country_sum %>% filter(country == "China"))$mean_theme_resp_percent, 2)`, SD = `r round((df.country_sum %>% filter(country == "China"))$sd_theme_resp_percent, 2)`), followed by the groups means in Vietnam (M = `r round((df.country_sum %>% filter(country == "Vietnam"))$mean_theme_resp_percent, 2)`, SD = `r round((df.country_sum %>% filter(country == "Vietnam"))$sd_theme_resp_percent, 2)`), which is slightly higher than that of the US (M = `r round((df.country_sum %>% filter(country == "US"))$mean_theme_resp_percent, 2)`, SD = `r round((df.country_sum %>% filter(country == "US"))$sd_theme_resp_percent, 2)`).
+
+```{r echo=FALSE, warning=FALSE, cache = TRUE, fig.cap="Proportion of thematic responses by country.
+Only US-China responding comparison shows a siginficant difference.
+We could not extend this to US-Vietnam responding comparison."}
+
+#show violin plot
+ggplot(df.country,
+       mapping = aes(x = factor(country, levels=c("China", "US", "Vietnam")), 
+                     y = theme_resp_percent, 
+                     color = factor(country, levels=c("China", "US", "Vietnam")))) +
+  geom_violin() +
+  geom_jitter(height = 0, 
+              alpha = 0.3) +  
+  stat_summary(fun.data = "mean_cl_boot", 
+               geom = "pointrange") + 
+  labs(y = "Proportion Thematic Chosen", 
+       x = "Country", 
+       color = "Country") + 
+  scale_color_manual(values=c("#D63230", "#1C77C3", "#F39237"))
+```
+
+```{r correlation of country response, cache = TRUE, echo=FALSE, warning=FALSE}
+#US-China, US-Vietnam, China-Vietnam
+df.triad_country <- df %>%
+  group_by(triad, country) %>%
+  summarize(emp_theme_prop = mean(responses_theme))
+
+df.triad_country <- pivot_wider(data = df.triad_country, 
+                                names_from = country, 
+                                values_from = emp_theme_prop)
+plotUSCN = ggplot(data = df.triad_country,
+                  mapping = aes(x = US, 
+                                y = China, 
+                                label = triad)) +
+   geom_text() + 
+   geom_smooth(method = "lm") +
+   labs(x = "Proportion Thematic Chosen (US)", 
+        y = "Proportion Thematic Chosen (China)") + 
+   xlim(0, 1) + 
+   ylim(0, 1) + 
+  theme(axis.title = element_text(size=rel(0.75)))
+
+plotUSVN = ggplot(data = df.triad_country,
+                  mapping = aes(x = US, 
+                                y = Vietnam, 
+                                label = triad)) +
+   geom_text() + 
+   geom_smooth(method = "lm") +
+   labs(x = "Proportion Thematic Chosen (US)", 
+        y = "Proportion Thematic Chosen (Vietnam)") + 
+   xlim(0, 1) + 
+   ylim(0, 1)  + 
+  theme(axis.title = element_text(size=rel(0.75)))
+
+plotCNVN = ggplot(data = df.triad_country,
+                  mapping = aes(x = Vietnam,
+                                y = China, 
+                                label = triad)) +
+   geom_text() + 
+   geom_smooth(method = "lm") +
+   labs(x = "Proportion Thematic Chosen (Vietnam)", 
+        y = "Proportion Thematic Chosen (China)") + 
+   xlim(0, 1) + 
+   ylim(0, 1)  + 
+  theme(axis.title = element_text(size=rel(0.75)))
+
+corr.USCN = apa_print(cor.test(df.triad_country$US, 
+                  df.triad_country$China, na.rm=T))
+
+corr.USVN = apa_print(cor.test(df.triad_country$US, 
+                  df.triad_country$Vietnam, na.rm=T))
+
+corr.CNVN = apa_print(cor.test(df.triad_country$China, 
+                  df.triad_country$Vietnam, na.rm=T))
+```
+
+<!-- With a Pearson correlation test, we observed high correlations between thematic responding across all three countries.
+The proportion of US thematic responding is strongly correlated with thematic responding in China, `r corr.USCN$full_result`.
+The proportion of US thematic responding is strongly correlated with thematic responding in Vietnam, `r corr.USVN$full_result`.
+Likewise, the proportion of China thematic response is strongly correlated with thematic responding in Vietnam, `r corr.CNVN$full_result`.
+This points to a strong signal of universality across cultural contexts regarding similarity judgments.
+-->
+
+```{r USCN effect size comparison, cache = TRUE, include=FALSE}
+USCN_cohen <- cohen.d(df.triad_country$China, df.triad_country$US)
+```
+
+To test for cross-context differences in similarity judgments between the countries, we ran a mixed-effects logistic regression predicting triad responding (taxonomic or thematic) with country (US, China, or Vietnam) as a fixed effect.
+As random effects, we included an intercept per subject and one per triad, as well as by-triad random slopes for country to account for variation in the country effect across triads.
+In R syntax, the model is: response ~ country + (1 | subject) + (country | triad).
+
+Overall, there is a significant effect of country on proportion of thematic responses ($\chi^2$(`r fit.country.anova["country", "Df"]`) = `r round(fit.country.anova["country", "Chisq"], 2)`, p `r ifelse( fit.country.anova["country", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.country.anova["country", "Pr(>Chisq)"], 3)), "< .001")`).
+However, this effect is driven by the difference between US and China responding ($\beta$ = `r round(fixef(fit.country)["countryUS"], 2)`, p `r ifelse(as.data.frame(summary(fit.country)[["coefficients"]])["countryUS", "Pr(>|z|)"] > 0.001, paste0("= ", round(as.data.frame(summary(fit.country)[["coefficients"]])["countryUS", "Pr(>|z|)"], 3)), "< .001")`).
+There is no statistical difference between the Vietnam and China responding ($\beta$ = `r round(fixef(fit.country)["countryVietnam"], 2)`, p `r ifelse(as.data.frame(summary(fit.country)[["coefficients"]])["countryVietnam", "Pr(>|z|)"] > 0.001, paste0("= ", round(as.data.frame(summary(fit.country)[["coefficients"]])["countryVietnam", "Pr(>|z|)"], 3)), "< .001")`), and the US and Vietnam responding ($\beta$ = `r round(fixef(fit.country_EN_VN)["countryVietnam"], 2)`, p `r ifelse(as.data.frame(summary(fit.country_EN_VN)[["coefficients"]])["countryVietnam", "Pr(>|z|)"] > 0.001, paste0("= ", round(as.data.frame(summary(fit.country_EN_VN)[["coefficients"]])["countryVietnam", "Pr(>|z|)"], 3)), "< .001")`).
+
+On this analysis, we do not find support that the US-China tendencies toward taxonomic and thematic responding (respectively) extend to the US-Vietnam comparison.
+Accordingly, we cannot speak to overall biases toward thematic responding across Asian cultural contexts broadly, but we do replicate the differences documented by @Ji2004 between the US and China.
+However, in our corpus model comparison, we do find evidence for different, more fine-grained variation in similarity judgments between the US and Vietnam.
+
+## 2. Can the differences in similarity judgments between English, Mandarin and Vietnamese speakers be explained by variation in lexical statistics?
+### Is responding in each cultural context predicted by the corresponding lexical statistics (raw co-occurrences)? 
+#### Raw lexical co-occurrences
+```{r Pearson correlation between raw co-occurrences of corpora and responding, warning=FALSE, eval = F, cache = TRUE, include=FALSE}
+
+#raw co-occurrences
+df.triad_country_freq <- df %>%
+  filter(!(triad %in% triads_omit)) %>% # omit triads that do not have meaningful prediction (at least 1 non-zero prediction in both languages)
+  group_by(triad, country, theme_freq_prop_E, theme_freq_prop_V, theme_freq_prop_M) %>%  # not working 
+  summarize(emp_theme_prop = mean(responses_theme))
+df.triad_country_freq   #sanity
+
+df.triad_country_freq_E <- df.triad_country_freq %>%
+  filter(country == "US")
+
+#plotting English corpus against US responding data
+plotE = ggplot(data = df.triad_country_freq_E,
+        mapping = aes(x = emp_theme_prop,
+                     y = theme_freq_prop_E,
+                     label = triad)) +
+   geom_text() +
+   geom_smooth(method = "lm") +
+   labs(x = "Proportion Thematic Chosen (US)",
+        y = "Proportion Thematic Predicted (English)")
+plotE
+
+df.triad_country_freq_V <- df.triad_country_freq %>%
+  filter(country == "Vietnam")
+
+#plotting Vietnamese corpus against VN responding data
+plotV = ggplot(data = df.triad_country_freq_V,
+        mapping = aes(x = emp_theme_prop,
+                     y = theme_freq_prop_V,
+                     label = triad)) +
+   geom_text() +
+   geom_smooth(method = "lm") +
+   labs(x = "Proportion Thematic Chosen (Vietnam)",
+        y = "Proportion Thematic Predicted (Vietnamese)")
+plotV
+
+df.triad_country_freq_M <- df.triad_country_freq %>%
+  filter(country == "China")
+
+#plotting China corpus against CN responding data
+plotM = ggplot(data = df.triad_country_freq_M,
+        mapping = aes(x = emp_theme_prop,
+                     y = theme_freq_prop_M,
+                     label = triad)) +
+   geom_text() +
+   geom_smooth(method = "lm") +
+   labs(x = "Proportion Thematic Chosen (China)",
+        y = "Proportion Thematic Predicted (Chinese)")
+plotM
+
+#Pearson correlation between corpus and responding
+corr.E = apa_print(cor.test(df.triad_country_freq_E$emp_theme_prop,
+                  df.triad_country_freq_E$theme_freq_prop_E, na.rm=T))
+corr.E
+
+corr.V = apa_print(cor.test(df.triad_country_freq_V$emp_theme_prop,
+                  df.triad_country_freq_V$theme_freq_prop_V, na.rm=T))
+corr.V
+
+corr.M = apa_print(cor.test(df.triad_country_freq_M$emp_theme_prop,
+                  df.triad_country_freq_M$theme_freq_prop_M, na.rm=T))
+corr.M
+
+#Pearson correlation between EN and VI corpus
+corr.EV = apa_print(cor.test(df.triad_country_freq_V$theme_freq_prop_V,
+                   df.triad_country_freq_E$theme_freq_prop_E, na.rm=T))
+corr.EM = apa_print(cor.test(df.triad_country_freq_M$theme_freq_prop_M,
+                   df.triad_country_freq_E$theme_freq_prop_E, na.rm=T))
+corr.MV = apa_print(cor.test(df.triad_country_freq_V$theme_freq_prop_V,
+                   df.triad_country_freq_M$theme_freq_prop_M, na.rm=T))
+```
+
+```{r echo=FALSE, warning = F, eval = F, cache = TRUE, paged.print=FALSE, fig.cap ="Correlation between English corpus lexical co-occurrence and US responding, and Vietnamese corpus lexical co-occurrence and Vietnam responding."}
+plotE + plotV + plotM
+  plot_layout(ncol = 3)
+```
+
+To test whether variation in lexical co-occurrence can explain differences in similarity judgments between US and Vietnam participants, we compare logistic mixed-effects regression models fit to the thematic responding data from each country separately.
+We first ask how well each corpus model (English, Vietnamese, or Mandarin) predicts similarity judgments by speakers of the corresponding language (US, Vietnam, or China).
+To do this, we use a mixed-effects logistic regression to predict triad responses (0=taxonomic or 1=thematic) with corpus prediction (proportion thematic co-occurrence or cosine distance) as a fixed effect and participant and triad as random effects.
+
+We found that all corpora are significant predictors of all cultural context responding.
+```{r US responding predicted by each corpus model raw co-occurrences, warning=FALSE, include=F, cache = TRUE}
+# English 
+fit.EN_US = glmer(responses_theme ~ theme_freq_prop_E + (1 | subject) + (1 | triad), 
+          data = df %>% filter(country == "US", !(triad %in% triads_omit)), 
+          family="binomial")
+summary(fit.EN_US)
+fit.EN_US.anova = Anova(fit.EN_US, type = 3)
+
+#Vietnamese
+fit.VI_US = glmer(responses_theme ~ theme_freq_prop_V + (1 | subject) + (1 | triad), 
+          data = df %>% filter(country == "US", !(triad %in% triads_omit)), 
+          family="binomial")
+summary(fit.VI_US)
+fit.VI_US.anova = Anova(fit.VI_US, type = 3)
+
+#Mandarin
+fit.ZH_US = glmer(responses_theme ~ theme_freq_prop_M + (1 | subject) + (1 | triad), 
+          data = df %>% filter(country == "US", !(triad %in% triads_omit)), 
+          family="binomial")
+summary(fit.ZH_US)
+fit.ZH_US.anova = Anova(fit.ZH_US, type = 3)
+```
+For US responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are all significant predictors.
+EN corpus: $\beta$ = `r round(fixef(fit.EN_US)["theme_freq_prop_E"], 2)`, $\chi^2$(`r fit.EN_US.anova["theme_freq_prop_E", "Df"]`) = `r round(fit.EN_US.anova["theme_freq_prop_E", "Chisq"], 2)`, p `r ifelse( fit.EN_US.anova["theme_freq_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.EN_US.anova["theme_freq_prop_E", "Pr(>Chisq)"], 3)), "< .001")`.
+VI corpus: $\beta$ = `r round(fixef(fit.VI_US)["theme_freq_prop_V"], 2)`, $\chi^2$(`r fit.VI_US.anova["theme_freq_prop_V", "Df"]`) = `r round(fit.VI_US.anova["theme_freq_prop_V", "Chisq"], 2)`, p `r ifelse( fit.VI_US.anova["theme_freq_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.VI_US.anova["theme_freq_prop_V", "Pr(>Chisq)"], 3)), "< .001")`.
+ZH corpus: $\beta$ = `r round(fixef(fit.ZH_US)["theme_freq_prop_M"], 2)`, $\chi^2$(`r fit.ZH_US.anova["theme_freq_prop_M", "Df"]`) = `r round(fit.ZH_US.anova["theme_freq_prop_M", "Chisq"], 2)`, p `r ifelse( fit.ZH_US.anova["theme_freq_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ZH_US.anova["theme_freq_prop_M", "Pr(>Chisq)"], 3)), "< .001")`.
+
+```{r VN responding predicted by each corpus model raw co-occurrences, warning=FALSE, include=F, cache = TRUE}
+# English 
+fit.EN_VN = glmer(responses_theme ~ theme_freq_prop_E + (1 | subject) + (1 | triad), 
+          data = df %>% filter(country == "Vietnam", !(triad %in% triads_omit)), 
+          family="binomial")
+summary(fit.EN_VN)
+fit.EN_VN.anova = Anova(fit.EN_VN, type = 3)
+
+#Vietnamese
+fit.VI_VN = glmer(responses_theme ~ theme_freq_prop_V + (1 | subject) + (1 | triad), 
+          data = df %>% filter(country == "Vietnam", !(triad %in% triads_omit)), 
+          family="binomial")
+summary(fit.VI_VN)
+fit.VI_VN.anova = Anova(fit.VI_VN, type = 3)
+
+#Mandarin
+fit.ZH_VN = glmer(responses_theme ~ theme_freq_prop_M + (1 | subject) + (1 | triad), 
+          data = df %>% filter(country == "Vietnam", !(triad %in% triads_omit)), 
+          family="binomial")
+summary(fit.ZH_VN)
+fit.ZH_VN.anova = Anova(fit.ZH_VN, type = 3)
+```
+For Vietnam responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are all significant predictors.
+EN corpus: $\beta$ = `r round(fixef(fit.EN_VN)["theme_freq_prop_E"], 2)`, $\chi^2$(`r fit.EN_VN.anova["theme_freq_prop_E", "Df"]`) = `r round(fit.EN_VN.anova["theme_freq_prop_E", "Chisq"], 2)`, p `r ifelse( fit.EN_VN.anova["theme_freq_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.EN_VN.anova["theme_freq_prop_E", "Pr(>Chisq)"], 3)), "< .001")`.
+VI corpus: $\beta$ = `r round(fixef(fit.VI_VN)["theme_freq_prop_V"], 2)`, $\chi^2$(`r fit.VI_VN.anova["theme_freq_prop_V", "Df"]`) = `r round(fit.VI_VN.anova["theme_freq_prop_V", "Chisq"], 2)`, p `r ifelse( fit.VI_VN.anova["theme_freq_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.VI_VN.anova["theme_freq_prop_V", "Pr(>Chisq)"], 3)), "< .001")`.
+ZH corpus: $\beta$ = `r round(fixef(fit.ZH_VN)["theme_freq_prop_M"], 2)`, $\chi^2$(`r fit.ZH_VN.anova["theme_freq_prop_M", "Df"]`) = `r round(fit.ZH_VN.anova["theme_freq_prop_M", "Chisq"], 2)`, p `r ifelse( fit.ZH_VN.anova["theme_freq_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ZH_VN.anova["theme_freq_prop_M", "Pr(>Chisq)"], 3)), "< .001")`.
+
+```{r CN responding predicted by each corpus model raw co-occurrences, warning=FALSE, include=F, cache = TRUE}
+#English
+fit.EN_CN = glmer(responses_theme ~ theme_freq_prop_E + (1 | subject) + (1 | triad), 
+          data = df %>% filter(country == "China", !(triad %in% triads_omit)), 
+          family="binomial")
+summary(fit.EN_CN)
+fit.EN_CN.anova = Anova(fit.EN_CN, type = 3)
+
+#Vietnamese
+fit.VI_CN = glmer(responses_theme ~ theme_freq_prop_V + (1 | subject) + (1 | triad), 
+          data = df %>% filter(country == "China", !(triad %in% triads_omit)), 
+          family="binomial")
+summary(fit.VI_CN)
+fit.VI_CN.anova = Anova(fit.VI_CN, type = 3)
+
+#Mandarin
+fit.ZH_CN = glmer(responses_theme ~ theme_freq_prop_M + (1 | subject) + (1 | triad), 
+          data = df %>% filter(country == "China", !(triad %in% triads_omit)), 
+          family="binomial")
+summary(fit.ZH_CN)
+fit.ZH_CN.anova = Anova(fit.ZH_CN, type = 3)
+```
+
+For China responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are all significant predictors.
+EN corpus: $\beta$ = `r round(fixef(fit.EN_CN)["theme_freq_prop_E"], 2)`, $\chi^2$(`r fit.EN_CN.anova["theme_freq_prop_E", "Df"]`) = `r round(fit.EN_CN.anova["theme_freq_prop_E", "Chisq"], 2)`, p `r ifelse( fit.EN_CN.anova["theme_freq_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.EN_CN.anova["theme_freq_prop_E", "Pr(>Chisq)"], 3)), "< .001")`.
+VI corpus: $\beta$ = `r round(fixef(fit.VI_CN)["theme_freq_prop_V"], 2)`, $\chi^2$(`r fit.VI_CN.anova["theme_freq_prop_V", "Df"]`) = `r round(fit.VI_CN.anova["theme_freq_prop_V", "Chisq"], 2)`, p `r ifelse( fit.VI_CN.anova["theme_freq_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.VI_CN.anova["theme_freq_prop_V", "Pr(>Chisq)"], 3)), "< .001")`.
+ZH corpus: $\beta$ = `r round(fixef(fit.ZH_US)["theme_freq_prop_M"], 2)`, $\chi^2$(`r fit.ZH_CN.anova["theme_freq_prop_M", "Df"]`) = `r round(fit.ZH_CN.anova["theme_freq_prop_M", "Chisq"], 2)`, p `r ifelse( fit.ZH_CN.anova["theme_freq_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ZH_CN.anova["theme_freq_prop_M", "Pr(>Chisq)"], 3)), "< .001")`.
+
+This suggests a strong shared similarity signal across the languages.
+
+#### Cosine distances of fastText word vectors
+Similar to the results from the analysis with raw lexical co-occurrences, we found that all corpora are significant predictors of all cultural context responding.
+
+```{r US responding predicted by each corpus model cosine differences, warning=FALSE, include=F}
+#English
+fit.EN_US_cos = glmer(responses_theme ~ theme_cosine_prop_E + (1 | subject) + (1 | triad), 
+          data = df %>% filter(country == "US"), 
+          family="binomial")
+summary(fit.EN_US_cos)
+fit.EN_US_cos.anova = Anova(fit.EN_US_cos, type = 3)
+fit.EN_US_cos.anova
+
+#Vietnamese
+fit.VI_US_cos = glmer(responses_theme ~ theme_cosine_prop_V + (1 | subject) + (1 | triad), 
+          data = df %>% filter(country == "US"), 
+          family="binomial")
+summary(fit.VI_US_cos)
+fit.VI_US_cos.anova = Anova(fit.VI_US_cos, type = 3)
+fit.VI_US_cos.anova
+
+#Mandarin
+fit.ZH_US_cos = glmer(responses_theme ~ theme_cosine_prop_M + (1 | subject) + (1 | triad), 
+          data = df %>% filter(country == "US"), 
+          family="binomial")
+summary(fit.ZH_US_cos)
+fit.ZH_US_cos.anova = Anova(fit.ZH_US_cos, type = 3)
+fit.ZH_US_cos.anova
+```
+For US responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are significant predictors of US responding (EN-US model: $\beta$ = `r round(fixef(fit.EN_US_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.EN_US_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.EN_US_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p `r ifelse( fit.EN_US_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.EN_US_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"], 3)), "< .001")`; VI-US model: $\beta$ = `r round(fixef(fit.VI_US_cos)["theme_cosine_prop_V"], 2)`, $\chi^2$(`r fit.VI_US_cos.anova["theme_cosine_prop_V", "Df"]`) = `r round(fit.VI_US_cos.anova["theme_cosine_prop_V", "Chisq"], 2)`, p = `r ifelse( fit.VI_US_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.VI_US_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"], 3)), "< .001")`; ZH-US model: $\beta$ = `r round(fixef(fit.ZH_US_cos)["theme_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ZH_US_cos.anova["theme_cosine_prop_M", "Df"]`) = `r round(fit.ZH_US_cos.anova["theme_cosine_prop_M", "Chisq"], 2)`, p `r ifelse( fit.ZH_US_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ZH_US_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"], 3)), "< .001")`).
+
+```{r VN responding predicted by each corpus model cosine differences, warning=FALSE, include=F}
+#English
+fit.EN_VN_cos = glmer(responses_theme ~ theme_cosine_prop_E + (1 | subject) + (1 | triad), 
+          data = df %>% filter(country == "Vietnam"), 
+          family="binomial")
+summary(fit.EN_VN_cos)
+fit.EN_VN_cos.anova = Anova(fit.EN_VN_cos, type = 3)
+fit.EN_VN_cos.anova
+
+#Vietnamese
+fit.VI_VN_cos = glmer(responses_theme ~ theme_cosine_prop_V + (1 | subject) + (1 | triad), 
+          data = df %>% filter(country == "Vietnam"), 
+          family="binomial")
+summary(fit.VI_VN_cos)
+fit.VI_VN_cos.anova = Anova(fit.VI_VN_cos, type = 3)
+fit.VI_VN_cos.anova
+
+#Mandarin
+fit.ZH_VN_cos = glmer(responses_theme ~ theme_cosine_prop_M + (1 | subject) + (1 | triad), 
+          data = df %>% filter(country == "Vietnam"), 
+          family="binomial")
+summary(fit.ZH_VN_cos)
+fit.ZH_VN_cos.anova = Anova(fit.ZH_VN_cos, type = 3)
+fit.ZH_VN_cos.anova
+```
+
+For Vietnam (VN) responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are significant predictors of VN responding (EN-VN model: $\beta$ = `r round(fixef(fit.EN_VN_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.EN_VN_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.EN_VN_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p `r ifelse( fit.EN_VN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.EN_VN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"], 3)), "< .001")`; VI-VN model: $\beta$ = `r round(fixef(fit.VI_VN_cos)["theme_cosine_prop_V"], 2)`, $\chi^2$(`r fit.VI_VN_cos.anova["theme_cosine_prop_V", "Df"]`) = `r round(fit.VI_VN_cos.anova["theme_cosine_prop_V", "Chisq"], 2)`, p = `r ifelse( fit.VI_VN_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.VI_VN_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"], 3)), "< .001")`; ZH-VN model: $\beta$ = `r round(fixef(fit.ZH_VN_cos)["theme_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ZH_VN_cos.anova["theme_cosine_prop_M", "Df"]`) = `r round(fit.ZH_VN_cos.anova["theme_cosine_prop_M", "Chisq"], 2)`, p `r ifelse( fit.ZH_VN_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ZH_VN_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"], 3)), "< .001")`).
+
+```{r CN responding predicted by each corpus model cosine differences, warning=FALSE, include=F}
+## English
+fit.EN_CN_cos = glmer(responses_theme ~ theme_cosine_prop_E + (1 | subject) + (1 | triad), 
+          data = df %>% filter(country == "China"), 
+          family="binomial")
+summary(fit.EN_CN_cos)
+fit.EN_CN_cos.anova = Anova(fit.EN_CN_cos, type = 3)
+fit.EN_CN_cos.anova
+
+#Vietnamese
+fit.VI_CN_cos = glmer(responses_theme ~ theme_cosine_prop_V + (1 | subject) + (1 | triad), 
+          data = df %>% filter(country == "China"), 
+          family="binomial")
+summary(fit.VI_CN_cos)
+fit.VI_CN_cos.anova = Anova(fit.VI_CN_cos, type = 3)
+fit.VI_CN_cos.anova
+
+#Mandarin
+fit.ZH_CN_cos = glmer(responses_theme ~ theme_cosine_prop_M + (1 | subject) + (1 | triad), 
+          data = df %>% filter(country == "China"), 
+          family="binomial")
+summary(fit.ZH_CN_cos)
+fit.ZH_CN_cos.anova = Anova(fit.ZH_CN_cos, type = 3)
+fit.ZH_CN_cos.anova
+```
+
+For China (CN) responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are significant predictors of CN responding (EN-CN model: $\beta$ = `r round(fixef(fit.EN_CN_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.EN_CN_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.EN_CN_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p `r ifelse( fit.EN_CN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.EN_CN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"], 3)), "< .001")`; VI-CN model: $\beta$ = `r round(fixef(fit.VI_CN_cos)["theme_cosine_prop_V"], 2)`, $\chi^2$(`r fit.VI_CN_cos.anova["theme_cosine_prop_V", "Df"]`) = `r round(fit.VI_CN_cos.anova["theme_cosine_prop_V", "Chisq"], 2)`, p = `r ifelse( fit.VI_CN_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.VI_CN_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"], 3)), "< .001")`; ZH-CN model: $\beta$ = `r round(fixef(fit.ZH_CN_cos)["theme_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ZH_CN_cos.anova["theme_cosine_prop_M", "Df"]`) = `r round(fit.ZH_CN_cos.anova["theme_cosine_prop_M", "Chisq"], 2)`, p `r ifelse( fit.ZH_CN_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ZH_CN_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"], 3)), "< .001")`).
+
+### Is responding in each cultural context __best__ predicted by the corresponding corpus's lexical statistics (raw co-occurrences), as opposed to the other two corpora?
+Next, we directly compare the corpus models by including both as fixed effects in three mixed-effect regressions (predicting US, Vietnam and China responding) with the same random effects as above.
+In R syntax, the model is: response ~ corpus_English + corpus_Vietnamese + corpus_Mandarin + (1|triad) + (1|subject).
+
+#### Raw co-occurrences 
+When we included all corpora thematic cosine distance proportion as predictors, all corpora are significant in predicting all cultural context's responding.
+
+```{r Eng-Vie-Mand lexical co-occ predicting US, warning=FALSE, include=F, cache = TRUE}
+# ADDITION: adding theme_freq_prop_M, 
+#raw co-occurrences
+#linear mixed model with ALL corpora as predictors for each population.
+fit.ENVIZH_US = glmer(responses_theme ~ 
+                      theme_freq_prop_E + theme_freq_prop_V + theme_freq_prop_M +
+                      (1 | subject) + (1 | triad), 
+                    data = df %>% filter(country == "US", !(triad %in% triads_omit)),
+                    family="binomial")
+summary(fit.ENVIZH_US)
+fit.ENVIZH_US.anova = Anova(fit.ENVIZH_US, type = 3)
+fit.ENVIZH_US.anova
+```
+For US responding: only English (EN) corpus is a significant predictor.
+EN corpus: $\beta$ = `r round(fixef(fit.ENVIZH_US)["theme_freq_prop_E"], 2)`, $\chi^2$(`r fit.ENVIZH_US.anova["theme_freq_prop_E", "Df"]`) = `r round(fit.ENVIZH_US.anova["theme_freq_prop_E", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_US.anova["theme_freq_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_US.anova["theme_freq_prop_E", "Pr(>Chisq)"], 3)), "< .001")`.
+VI corpus: $\beta$ = `r round(fixef(fit.ENVIZH_US)["theme_freq_prop_V"], 2)`, $\chi^2$(`r fit.ENVIZH_US.anova["theme_freq_prop_V", "Df"]`) = `r round(fit.ENVIZH_US.anova["theme_freq_prop_V", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_US.anova["theme_freq_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_US.anova["theme_freq_prop_V", "Pr(>Chisq)"], 3)), "< .001")`.
+ZH corpus: $\beta$ = `r round(fixef(fit.ENVIZH_US)["theme_freq_prop_M"], 2)`, $\chi^2$(`r fit.ENVIZH_US.anova["theme_freq_prop_M", "Df"]`) = `r round(fit.ENVIZH_US.anova["theme_freq_prop_M", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_US.anova["theme_freq_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_US.anova["theme_freq_prop_M", "Pr(>Chisq)"], 3)), "< .001")`.
+
+```{r Eng-Vie-Mand lexical co-occ predicting VN, warning=FALSE, include=F, cache = TRUE}
+fit.ENVIZH_VN = glmer(responses_theme ~ 
+                      theme_freq_prop_V + theme_freq_prop_E + theme_freq_prop_M +
+                      (1 | subject) + (1 | triad), 
+                    data = df %>% filter(country == "Vietnam", !(triad %in% triads_omit)),
+                    family="binomial")
+summary(fit.ENVIZH_VN)
+fit.ENVIZH_VN.anova = Anova(fit.ENVIZH_VN, type = 3)
+fit.ENVIZH_VN.anova
+```
+For Vietnam responding: only English (EN) and Mandarin (ZH) corpora are significant predictors.
+EN corpus: $\beta$ = `r round(fixef(fit.ENVIZH_VN)["theme_freq_prop_E"], 2)`, $\chi^2$(`r fit.ENVIZH_VN.anova["theme_freq_prop_E", "Df"]`) = `r round(fit.ENVIZH_VN.anova["theme_freq_prop_E", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_VN.anova["theme_freq_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_VN.anova["theme_freq_prop_E", "Pr(>Chisq)"], 3)), "< .001")`.
+ZH corpus: $\beta$ = `r round(fixef(fit.ENVIZH_VN)["theme_freq_prop_M"], 2)`, $\chi^2$(`r fit.ENVIZH_VN.anova["theme_freq_prop_M", "Df"]`) = `r round(fit.ENVIZH_VN.anova["theme_freq_prop_M", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_VN.anova["theme_freq_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_VN.anova["theme_freq_prop_M", "Pr(>Chisq)"], 3)), "< .001")`.VI corpus: $\beta$ = `r round(fixef(fit.ENVIZH_VN)["theme_freq_prop_V"], 2)`, $\chi^2$(`r fit.ENVIZH_VN.anova["theme_freq_prop_V", "Df"]`) = `r round(fit.ENVIZH_VN.anova["theme_freq_prop_V", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_VN.anova["theme_freq_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_VN.anova["theme_freq_prop_V", "Pr(>Chisq)"], 3)), "< .001")`.
+
+```{r Eng-Vie-Mand lexical co-occ predicting CN, warning=FALSE, include=F, cache = TRUE}
+fit.ENVIZH_CN = glmer(responses_theme ~ 
+                      theme_freq_prop_V + theme_freq_prop_E + theme_freq_prop_M +
+                      (1 | subject) + (1 | triad), 
+                    data = df %>% filter(country == "China", !(triad %in% triads_omit)),
+                    family="binomial")
+summary(fit.ENVIZH_CN)
+fit.ENVIZH_CN.anova = Anova(fit.ENVIZH_CN, type = 3)
+fit.ENVIZH_CN.anova
+```
+For China responding: only Mandarin (ZH) corpus is a significant predictor.
+ZH corpus: $\beta$ = `r round(fixef(fit.ENVIZH_CN)["theme_freq_prop_M"], 2)`, $\chi^2$(`r fit.ENVIZH_CN.anova["theme_freq_prop_M", "Df"]`) = `r round(fit.ENVIZH_CN.anova["theme_freq_prop_M", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_CN.anova["theme_freq_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_CN.anova["theme_freq_prop_M", "Pr(>Chisq)"], 3)), "< .001")`.
+EN corpus: $\beta$ = `r round(fixef(fit.ENVIZH_CN)["theme_freq_prop_E"], 2)`, $\chi^2$(`r fit.ENVIZH_CN.anova["theme_freq_prop_E", "Df"]`) = `r round(fit.ENVIZH_CN.anova["theme_freq_prop_E", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_CN.anova["theme_freq_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_CN.anova["theme_freq_prop_E", "Pr(>Chisq)"], 3)), "< .001")`.
+VI corpus: $\beta$ = `r round(fixef(fit.ENVIZH_CN)["theme_freq_prop_V"], 2)`, $\chi^2$(`r fit.ENVIZH_CN.anova["theme_freq_prop_V", "Df"]`) = `r round(fit.ENVIZH_CN.anova["theme_freq_prop_V", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_CN.anova["theme_freq_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_CN.anova["theme_freq_prop_V", "Pr(>Chisq)"], 3)), "< .001")`.
+
+```{r echo=FALSE, warning = FALSE, cache = TRUE, fig.cap = "Fixed effect sizes of each corpus when included as a predictor for China, US, and Vietnam responding, respectively.
+The English corpus is the best predictor for US response, and the Mandarin corpus is the best predictor for China response."}
+coeff_value_freq <- c(fixef(fit.ENVIZH_US)["theme_freq_prop_M"],
+                 fixef(fit.ENVIZH_US)["theme_freq_prop_E"], 
+                 fixef(fit.ENVIZH_US)["theme_freq_prop_V"],
+                 fixef(fit.ENVIZH_VN)["theme_freq_prop_M"],
+                 fixef(fit.ENVIZH_VN)["theme_freq_prop_E"],
+                 fixef(fit.ENVIZH_VN)["theme_freq_prop_V"], 
+                 fixef(fit.ENVIZH_CN)["theme_freq_prop_M"],
+                 fixef(fit.ENVIZH_CN)["theme_freq_prop_E"], 
+                 fixef(fit.ENVIZH_CN)["theme_freq_prop_V"])
+
+se_value_freq <- c(summary(fit.ENVIZH_US)$coef["theme_freq_prop_M", "Std. Error"], 
+              summary(fit.ENVIZH_US)$coef["theme_freq_prop_E", "Std. Error"],
+              summary(fit.ENVIZH_US)$coef["theme_freq_prop_V", "Std. Error"], 
+              summary(fit.ENVIZH_VN)$coef["theme_freq_prop_M", "Std. Error"], 
+              summary(fit.ENVIZH_VN)$coef["theme_freq_prop_E", "Std. Error"],
+              summary(fit.ENVIZH_VN)$coef["theme_freq_prop_V", "Std. Error"],
+              summary(fit.ENVIZH_CN)$coef["theme_freq_prop_M", "Std. Error"], 
+              summary(fit.ENVIZH_CN)$coef["theme_freq_prop_E", "Std. Error"],
+              summary(fit.ENVIZH_CN)$coef["theme_freq_prop_V", "Std. Error"])
+
+country_value <- c(rep("US", 3),
+                   rep("VN", 3),
+                   rep("CN", 3))
+
+corpus_value <- c(rep(c("ZH", "EN", "VI"), 3))
+
+df.USVNCN_coeffs_freq <- data.frame(country_value, corpus_value, coeff_value_freq, se_value_freq) %>%
+  mutate(corpus_value = factor(corpus_value, levels=c("ZH", "EN", "VI")))
+
+ggplot(data = df.USVNCN_coeffs_freq, 
+       mapping = aes(x = country_value, y = coeff_value_freq, fill = corpus_value)) +
+  geom_bar(position="dodge", stat="identity") +
+  geom_errorbar(aes(ymin= coeff_value_freq - se_value_freq, ymax = coeff_value_freq + se_value_freq), width=.2,
+                 position=position_dodge(.9)) +
+  labs(x = "Country", y = "Fixed effect size", fill = "Corpus") + 
+  scale_x_discrete(labels=c("CN" = "China", "US" = "US", "VN" = "Vietnam")) + 
+  scale_fill_manual(values=c("#D63230", "#1C77C3", "#F39237"))
+
+```
+
+```{r freq model comparison, include=FALSE, cache = TRUE}
+fit.US_freq_compare = anova(fit.ENVIZH_US, fit.EN_US, type = 3)
+fit.VN_freq_compare = anova(fit.ENVIZH_VN, fit.VI_VN, type = 3)
+fit.CN_freq_compare = anova(fit.ENVIZH_CN, fit.ZH_CN, type = 3)
+```
+
+We observed some level of language specificity from this analysis.
+The English corpus is the best predictor for US responding, and the Mandarin corpus is the best predictor for China response.
+While this is not the case with the Vietnamese corpus and the Vietnam responding, the Vietnamese corpus is still a significant predictor for the Vietnam responding.
+
+However, we found that language specificity alone does not explain our results.
+We used an ANOVA to compare the model with only the corresponding corpus, and the model with all 3 corpora for each cultural context.
+We found that in all three cases (US, China, Vietnam), adding the other two corpora produces a significantly better fit than the identical model without the additional corpora, and only the corresponding corpus included as a predictor (US response: $\chi^2$(`r fit.US_freq_compare["fit.ENVIZH_US", "Df"]`) = `r round(fit.US_freq_compare["fit.ENVIZH_US", "Chisq"], 2)`, p `r ifelse( fit.US_freq_compare["fit.ENVIZH_US", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.US_freq_compare["fit.ENVIZH_US", "Pr(>Chisq)"], 3)), "< .001")`; Vietnam response: $\chi^2$(`r fit.VN_freq_compare["fit.ENVIZH_VN", "Df"]`) = `r round(fit.VN_freq_compare["fit.ENVIZH_VN", "Chisq"], 2)`, p `r ifelse( fit.VN_freq_compare["fit.ENVIZH_VN", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.VN_freq_compare["fit.ENVIZH_VN", "Pr(>Chisq)"], 3)), "< .001")`; China response: $\chi^2$(`r fit.CN_freq_compare["fit.ENVIZH_CN", "Df"]`) = `r round(fit.CN_freq_compare["fit.ENVIZH_CN", "Chisq"], 2)`, p `r ifelse( fit.CN_freq_compare["fit.ENVIZH_CN", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.CN_freq_compare["fit.ENVIZH_CN", "Pr(>Chisq)"], 3)), "< .001")`).
+
+```{r add cosine linguistic model to Ji et al., include=FALSE, cache = T}
+fit.country = glmer(responses_theme ~ country + (1 | subject) + (1 | triad), 
+                           data = df %>% filter(country != "Vietnam"), 
+                           family = "binomial")
+
+fit.country_corpus = glmer(responses_theme ~ country + theme_cosine_prop_E + theme_cosine_prop_M + (1 | subject) + (1 | triad), 
+                           data = df %>% filter(country != "Vietnam"), 
+                           family = "binomial")
+
+fit.add_corpus <- anova(fit.country, fit.country_corpus, type = 3)
+
+```
+_TODO: should we take this out?__
+We carried out an ANOVA model comparison to compare our approach with previous studies that did not include corpus information.
+Because @Ji2004 only compared US and China participants, we filtered our data to only include responding data from these two countries.
+Our approach would be to compare a model that only includes country (US or China) as a fixed effect with one that also includes English and Chinese corpus data.
+Our previous model with an intercept per subject and one per triad, as well as by-triad random slopes for country to account for variation in the country effect across triads fails to converge with the more complex model, so we include a simpler random effect structure with an intercept per subject and one per triad in both the basic and more complex model.
+We compare this model with an identical model but including Chinese and English corpus cosine distance proportion prediction.
+We found that adding English and Chinese corpus data produces a significantly better fit than the identical model without English and Chinese corpus data as predictors ($\chi^2$(`r fit.add_corpus["fit.country_corpus", "Df"]`) = `r round(fit.add_corpus["fit.country_corpus", "Chisq"], 2)`, p = < .001.
+This suggests that including corpus data would better model the cross-cultural differences in similarity judgment in this study as well as similar studies.
+
+#### Cosine distances of fastText word vectors
+
+```{r Eng-Vie-Mand cosine similarities predicting US-VN-CN, warning=FALSE, include=FALSE}
+## English/Vietnamese/Mandarin comparison
+fit.ENVIZH_US_cos = glmer(responses_theme ~ theme_cosine_prop_E + theme_cosine_prop_V + theme_cosine_prop_M +
+                      (1 | subject) + (1 | triad), 
+                    data = df %>% filter(country == "US"), 
+                    family="binomial")
+summary(fit.ENVIZH_US_cos)
+fit.ENVIZH_US_cos.anova = Anova(fit.ENVIZH_US_cos, type = 3)
+fit.ENVIZH_US_cos.anova
+
+fit.ENVIZH_VN_cos = glmer(responses_theme ~ theme_cosine_prop_V + theme_cosine_prop_E + theme_cosine_prop_M +
+                      (1 | subject) + (1 | triad), 
+                    data = df %>% filter(country == "Vietnam"), 
+                    family="binomial")
+summary(fit.ENVIZH_VN_cos)
+fit.ENVIZH_VN_cos.anova = Anova(fit.ENVIZH_VN_cos, type = 3)
+fit.ENVIZH_VN_cos.anova
+
+fit.ENVIZH_CN_cos = glmer(responses_theme ~ theme_cosine_prop_M + theme_cosine_prop_E + theme_cosine_prop_V +
+                      (1 | subject) + (1 | triad), 
+                    data = df %>% filter(country == "China"), 
+                    family="binomial")
+summary(fit.ENVIZH_CN_cos)
+fit.ENVIZH_CN_cos.anova = Anova(fit.ENVIZH_CN_cos, type = 3)
+fit.ENVIZH_CN_cos.anova
+```
+
+When we included all corpora thematic cosine distance proportion as predictors, all corpora are significant in predicting all cultural context's responding.
+
+For US responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are all significant predictors.
+EN corpus: $\beta$ = `r round(fixef(fit.ENVIZH_US_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.ENVIZH_US_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.ENVIZH_US_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_US_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_US_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"], 3)), "< .001")`.
+VI corpus: $\beta$ = `r round(fixef(fit.ENVIZH_US_cos)["theme_cosine_prop_V"], 2)`, $\chi^2$(`r fit.ENVIZH_US_cos.anova["theme_cosine_prop_V", "Df"]`) = `r round(fit.ENVIZH_US_cos.anova["theme_cosine_prop_V", "Chisq"], 2)`, p = `r ifelse( fit.ENVIZH_US_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_US_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"], 3)), "< .001")`.
+ZH corpus: $\beta$ = `r round(fixef(fit.ENVIZH_US_cos)["theme_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ENVIZH_US_cos.anova["theme_cosine_prop_M", "Df"]`) = `r round(fit.ENVIZH_US_cos.anova["theme_cosine_prop_M", "Chisq"], 2)`, p = `r ifelse( fit.ENVIZH_US_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_US_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"], 3)), "< .001")`.
+
+For Vietnam responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are all significant predictors.
+EN corpus: $\beta$ = `r round(fixef(fit.ENVIZH_VN_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.ENVIZH_VN_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p = `r ifelse( fit.ENVIZH_VN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"], 3)), "< .001")`.
+VI corpus: $\beta$ = `r round(fixef(fit.ENVIZH_VN_cos)["theme_cosine_prop_V"], 2)`, $\chi^2$(`r fit.ENVIZH_VN_cos.anova["theme_cosine_prop_V", "Df"]`) = `r round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_V", "Chisq"], 2)`, p = `r ifelse( fit.ENVIZH_VN_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"], 3)), "< .001")`.
+ZH corpus: $\beta$ = `r round(fixef(fit.ENVIZH_VN_cos)["theme_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ENVIZH_VN_cos.anova["theme_cosine_prop_M", "Df"]`) = `r round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_M", "Chisq"], 2)`, p = `r ifelse( fit.ENVIZH_VN_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"], 3)), "< .001")`.
+
+For China responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are all significant predictors.
+EN corpus: $\beta$ = `r round(fixef(fit.ENVIZH_CN_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.ENVIZH_CN_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.ENVIZH_CN_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p = `r ifelse( fit.ENVIZH_CN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_CN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"], 3)), "< .001")`.
+VI corpus: $\beta$ = `r round(fixef(fit.ENVIZH_CN_cos)["theme_cosine_prop_V"], 2)`, $\chi^2$(`r fit.ENVIZH_CN_cos.anova["theme_cosine_prop_V", "Df"]`) = `r round(fit.ENVIZH_CN_cos.anova["theme_cosine_prop_V", "Chisq"], 2)`, p = `r ifelse( fit.ENVIZH_CN_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_CN_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"], 3)), "< .001")`.
+ZH corpus: $\beta$ = `r round(fixef(fit.ENVIZH_CN_cos)["theme_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ENVIZH_CN_cos.anova["theme_cosine_prop_M", "Df"]`) = `r round(fit.ENVIZH_CN_cos.anova["theme_cosine_prop_M", "Chisq"], 2)`, p = `r ifelse( fit.ENVIZH_CN_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_CN_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"], 3)), "< .001")`.
+
+We observed some level of language specificity from this analysis.
+The English corpus is the best predictor for US responding, and the Mandarin corpus is the best predictor for China response.
+While this is not the case with the Vietnamese corpus and the Vietnam responding, the Vietnamese corpus is still a significant predictor for the Vietnam responding.
+
+```{r echo=FALSE, warning = FALSE, fig.cap = "Fixed effect sizes of each corpus when included as a predictor for China, US, and Vietnam responding, respectively.
+The English corpus is the best predictor for US response, and the Mandarin corpus is the best predictor for China response."}
+coeff_value_cos <- c(fixef(fit.ENVIZH_US_cos)["theme_cosine_prop_E"],
+                 fixef(fit.ENVIZH_US_cos)["theme_cosine_prop_V"], 
+                 fixef(fit.ENVIZH_US_cos)["theme_cosine_prop_M"],
+                 fixef(fit.ENVIZH_VN_cos)["theme_cosine_prop_E"],
+                 fixef(fit.ENVIZH_VN_cos)["theme_cosine_prop_V"],
+                 fixef(fit.ENVIZH_VN_cos)["theme_cosine_prop_M"], 
+                 fixef(fit.ENVIZH_CN_cos)["theme_cosine_prop_E"],
+                 fixef(fit.ENVIZH_CN_cos)["theme_cosine_prop_V"], 
+                 fixef(fit.ENVIZH_CN_cos)["theme_cosine_prop_M"])
+
+se_value_cos <- c(summary(fit.ENVIZH_US_cos)$coef["theme_cosine_prop_E", "Std. Error"], 
+              summary(fit.ENVIZH_US_cos)$coef["theme_cosine_prop_V", "Std. Error"],
+              summary(fit.ENVIZH_US_cos)$coef["theme_cosine_prop_M", "Std. Error"], 
+              summary(fit.ENVIZH_VN_cos)$coef["theme_cosine_prop_E", "Std. Error"], 
+              summary(fit.ENVIZH_VN_cos)$coef["theme_cosine_prop_V", "Std. Error"],
+              summary(fit.ENVIZH_VN_cos)$coef["theme_cosine_prop_M", "Std. Error"],
+              summary(fit.ENVIZH_CN_cos)$coef["theme_cosine_prop_E", "Std. Error"], 
+              summary(fit.ENVIZH_CN_cos)$coef["theme_cosine_prop_V", "Std. Error"],
+              summary(fit.ENVIZH_CN_cos)$coef["theme_cosine_prop_M", "Std. Error"])
+
+country_value <- c(rep("US", 3),
+                   rep("VN", 3),
+                   rep("CN", 3))
+
+corpus_value <- c(rep(c("EN", "VI", "ZH"), 3))
+
+df.USVNCN_coeffs_cos <- data.frame(country_value, corpus_value, coeff_value_freq, se_value_freq) %>%
+  mutate(corpus_value = factor(corpus_value, levels=c("ZH", "EN", "VI")))
+
+ggplot(data = df.USVNCN_coeffs_cos, 
+       mapping = aes(x = country_value, y = coeff_value_cos, fill = corpus_value)) +
+  geom_bar(position="dodge", stat="identity") +
+  geom_errorbar(aes(ymin= coeff_value_cos - se_value_cos, ymax = coeff_value_cos + se_value_cos), width=.2,
+                 position=position_dodge(.9)) +
+  scale_y_reverse() + 
+  labs(x = "Country", y = "Fixed effect size", fill = "Corpus") + 
+  scale_x_discrete(labels=c("CN" = "China", "US" = "US", "VN" = "Vietnam")) + 
+  scale_fill_manual(values=c("#D63230", "#1C77C3", "#F39237"))
+
+```
+
+```{r model comparison, include=FALSE}
+fit.US_cos_compare = anova(fit.ENVIZH_US_cos, fit.EN_US_cos, type = 3)
+fit.VN_cos_compare = anova(fit.ENVIZH_VN_cos, fit.VI_VN_cos, type = 3)
+fit.CN_cos_compare = anova(fit.ENVIZH_CN_cos, fit.ZH_CN_cos, type = 3)
+```
+
+However, we found that language specificity alone does not explain our results.
+We used an ANOVA to compare the model with only the corresponding corpus, and the model with all 3 corpora for each cultural context.
+We found that in all three cases (US, China, Vietnam), adding the other two corpora produces a significantly better fit than the identical model without the additional corpora, and only the corresponding corpus included as a predictor (US response: $\chi^2$(`r fit.US_cos_compare["fit.ENVIZH_US_cos", "Df"]`) = `r round(fit.US_cos_compare["fit.ENVIZH_US_cos", "Chisq"], 2)`, p = `r ifelse( fit.US_cos_compare["fit.ENVIZH_US_cos", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.US_cos_compare["fit.ENVIZH_US_cos", "Pr(>Chisq)"], 3)), "< .001")`; Vietnam response: $\chi^2$(`r fit.VN_cos_compare["fit.ENVIZH_VN_cos", "Df"]`) = `r round(fit.VN_cos_compare["fit.ENVIZH_VN_cos", "Chisq"], 2)`, p = `r ifelse( fit.VN_cos_compare["fit.ENVIZH_VN_cos", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.VN_cos_compare["fit.ENVIZH_VN_cos", "Pr(>Chisq)"], 3)), "< .001")`; China response: $\chi^2$(`r fit.CN_cos_compare["fit.ENVIZH_CN_cos", "Df"]`) = `r round(fit.CN_cos_compare["fit.ENVIZH_CN_cos", "Chisq"], 2)`, p = `r ifelse( fit.CN_cos_compare["fit.ENVIZH_VN_cos", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.CN_cos_compare["fit.ENVIZH_VN_cos", "Pr(>Chisq)"], 3)), "< .001")`).
+
+```{r add linguistic model to Ji et al., include=FALSE}
+fit.country = glmer(responses_theme ~ country + (1 | subject) + (1 | triad), 
+                           data = df %>% filter(country != "Vietnam"), 
+                           family = "binomial")
+
+fit.country_corpus = glmer(responses_theme ~ country + theme_cosine_prop_E + theme_cosine_prop_M + (1 | subject) + (1 | triad), 
+                           data = df %>% filter(country != "Vietnam"), 
+                           family = "binomial")
+
+fit.add_corpus <- anova(fit.country, fit.country_corpus, type = 3)
+
+```
+_TODO: should we take this out?__
+We carried out an ANOVA model comparison to compare our approach with previous studies that did not include corpus information.
+Because @Ji2004 only compared US and China participants, we filtered our data to only include responding data from these two countries.
+Our approach would be to compare a model that only includes country (US or China) as a fixed effect with one that also includes English and Chinese corpus data.
+Our previous model with an intercept per subject and one per triad, as well as by-triad random slopes for country to account for variation in the country effect across triads fails to converge with the more complex model, so we include a simpler random effect structure with an intercept per subject and one per triad in both the basic and more complex model.
+We compare this model with an identical model but including Chinese and English corpus cosine distance proportion prediction.
+We found that adding English and Chinese corpus data produces a significantly better fit than the identical model without English and Chinese corpus data as predictors ($\chi^2$(`r fit.add_corpus["fit.country_corpus", "Df"]`) = `r round(fit.add_corpus["fit.country_corpus", "Chisq"], 2)`, p = < .001.
+This suggests that including corpus data would better model the cross-cultural differences in similarity judgment in this study as well as similar studies.
+
+## 3. Does similarity reasoning differ across cultures, only the input to it, or both?
+Does adding country and interaction term with the corresponding corpus improves the model?
+
+```{r, include = F}
+df <- df %>%
+  mutate(theme_freq_prop_corr_lang = case_when(
+    country == "US" ~ theme_freq_prop_E,
+    country == "China" ~ theme_freq_prop_M, 
+    country == "Vietnam" ~ theme_freq_prop_V)) %>% 
+    mutate(theme_cosine_prop_corr_lang = case_when(
+    country == "US" ~ theme_cosine_prop_E,
+    country == "China" ~ theme_cosine_prop_M, 
+    country == "Vietnam" ~ theme_cosine_prop_V))
+```
+
+```{r country language interaction in raw co-occurrences, include = F}
+fit.language = glmer(responses_theme ~ theme_freq_prop_corr_lang + (1 | subject) + (1 | triad), 
+          data = df %>% filter(!(triad %in% triads_omit)),  
+          family="binomial")
+summary(fit.language)
+fit.language.anova = Anova(fit.language, type = 3)
+fit.language.anova
+
+fit.country_language = glmer(responses_theme ~ theme_freq_prop_corr_lang * country + (1 | subject) + (1 | triad), 
+          data = df %>% filter(!(triad %in% triads_omit)),  
+          family="binomial")
+summary(fit.country_language)
+fit.country_language.anova = Anova(fit.country_language, type = 3)
+fit.country_language.anova
+
+fit.country_language_compare = anova(fit.language, fit.country_language, type = 3)
+fit.country_language_compare
+```
+
+```{r country language interaction in cosine prop, include = F}
+fit.language_cos = glmer(responses_theme ~ theme_cosine_prop_corr_lang + (1 | subject) + (1 | triad), 
+          data = df %>% filter(!(triad %in% triads_omit)),  
+          family="binomial")
+summary(fit.language_cos)
+fit.language_cos.anova = Anova(fit.language_cos, type = 3)
+fit.language_cos.anova
+
+fit.country_language_cos= glmer(responses_theme ~ theme_cosine_prop_corr_lang * country + (1 | subject) + (1 | triad), 
+          data = df %>% filter(!(triad %in% triads_omit)),  
+          family="binomial")
+summary(fit.country_language_cos)
+fit.country_language_cos.anova = Anova(fit.country_language_cos, type = 3)
+fit.country_language_cos.anova
+
+fit.country_language_cos_compare = anova(fit.language_cos, fit.country_language_cos, type = 3)
+fit.country_language_cos_compare
+```
+
+Adding country improves the model.
+Only country and interaction between country and corresponding corpus's lexical co-occurrence are significant predictors.
+Corresponding corpus's lexical co-occurrence is no longer a significant predictor.
+
+## 5. How general are the cross-language differences in similarity judgments we observe? Are they limited to taxonomic-thematic contrasts or do they extend to other cases?
+
+```{r incorporate base freq for fillers}
+df.filler <- read.csv("../../../data/data_filler_USCNVN_ENZHVI.csv")
+fillers_omit <- read.csv("../../../data/fillers_omit.csv") %>%
+  pull(x)
+```
+
+```{r warning=FALSE, cache = TRUE, include = FALSE, paged.print=TRUE}
+df.country_filler <- df.filler %>%
+  group_by(subject, country) %>%
+  summarize(word1_resp_percent = mean(responses_word1, na.rm = T))
+```
+
+```{r echo=FALSE, warning=FALSE, cache = TRUE, fig.cap="Proportion of thematic responses by country.
+Only US-China responding comparison shows a siginficant difference.
+We could not extend this to US-Vietnam responding comparison."}
+
+#show violin plot
+ggplot(df.country_filler,
+       mapping = aes(x = factor(country, levels=c("China", "US", "Vietnam")), 
+                     y = word1_resp_percent, 
+                     color = factor(country, levels=c("China", "US", "Vietnam")))) +
+  geom_violin() +
+  geom_jitter(height = 0, 
+              alpha = 0.3) +  
+  stat_summary(fun.data = "mean_cl_boot", 
+               geom = "pointrange") + 
+  labs(y = "Proportion Word1 Chosen", 
+       x = "Country", 
+       color = "Country") + 
+  scale_color_manual(values=c("#D63230", "#1C77C3", "#F39237"))
+```
+
+```{r warning=FALSE, include = F, cache = TRUE, paged.print=TRUE}
+# df.country_sum <- df.country %>%
+#   group_by(country) %>%
+#   summarize(mean_theme_resp_percent = mean(theme_resp_percent), 
+#             sd_theme_resp_percent = sd(theme_resp_percent))
+
+fit.country_filler = glmer(responses_word1 ~ country + (1 | subject) + (country | cue),
+                    data = df.filler, 
+                    family = "binomial")
+summary(fit.country_filler) 
+fit.country_filler.anova = Anova(fit.country_filler, type=3)
+fit.country_filler.anova
+``` 
+No effect of country on filler responding.
+
+### Does lexical statistics for fillers predict responding in the corresponding cultural context?
+
+#### Raw co-occurrences
+```{r US responding predicted by each corpus model raw co-occurrences for fillers, warning=FALSE,include = F}
+# English 
+fit.EN_US_filler = glmer(responses_word1 ~ word1_match_frequency_prop_E + (1 | subject) + (1 | cue), 
+          data = df.filler %>% filter(country == "US", 
+                               !(cue_id %in% fillers_omit)), 
+          family="binomial")
+summary(fit.EN_US_filler)
+fit.EN_US_filler.anova = Anova(fit.EN_US_filler, type = 3)
+
+fit.EN_US_filler.anova
+```
+
+```{r VN responding predicted by each corpus model raw co-occurrences for fillers, warning=FALSE, include = F}
+# Vietnamese
+fit.VI_VN_filler = glmer(responses_word1 ~ word1_match_frequency_prop_V + (1 | subject) + (1 | cue), 
+          data = df.filler %>% filter(country == "Vietnam", 
+                               !(cue_id %in% fillers_omit)), 
+          family="binomial")
+summary(fit.VI_VN_filler)
+fit.VI_VN_filler.anova = Anova(fit.VI_VN_filler, type = 3)
+
+fit.VI_VN_filler.anova
+```
+Yes, corpus raw co-occurrences predicts responding for both US and Vietnamese. *need to discuss with Shan to incorporate Mandarin due to a lot of empty counts*
+
+#### Cosine distance
+```{r US responding predicted by each corpus model cosine distances for fillers, warning=FALSE, include = F}
+# English 
+fit.EN_US_filler_cos = glmer(responses_word1 ~ word1_match_cosine_prop_E + (1 | subject) + (1 | cue), 
+          data = df.filler %>% filter(country == "US"), 
+          family="binomial")
+summary(fit.EN_US_filler_cos)
+fit.EN_US_filler_cos.anova = Anova(fit.EN_US_filler_cos, type = 3)
+
+fit.EN_US_filler_cos.anova
+```
+
+```{r VN responding predicted by each corpus model cosine distances for fillers, warning=FALSE, include = F}
+# Vietnamese
+fit.VI_VN_filler_cos = glmer(responses_word1 ~ word1_match_cosine_prop_V + (1 | subject) + (1 | cue), 
+          data = df.filler %>% filter(country == "Vietnam"), 
+          family="binomial")
+summary(fit.VI_VN_filler_cos)
+fit.VI_VN_filler_cos.anova = Anova(fit.VI_VN_filler_cos, type = 3)
+
+fit.VI_VN_filler_cos.anova
+```
+
+```{r CN responding predicted by each corpus model cosine distances for fillers, warning=FALSE, include = F}
+# Vietnamese
+fit.ZH_CN_filler_cos = glmer(responses_word1 ~ word1_match_cosine_prop_M + (1 | subject) + (1 | cue), 
+          data = df.filler %>% filter(country == "China"), 
+          family="binomial")
+summary(fit.ZH_CN_filler_cos)
+fit.ZH_CN_filler_cos.anova = Anova(fit.ZH_CN_filler_cos, type = 3)
+
+fit.ZH_CN_filler_cos.anova
+```
+Corpus cosine similarities also predict responding for all cultures.
+
+# Discussion
+In this paper, we consider whether statistics of the language environment can account for cross-cultural differences in a classic similarity judgment paradigm, as an alternative to the view that members of different cultures vary in their conception of similarity.
+
+We first tested the generality of a cultural account which holds that people from Western and East Asian cultures tend to conceive of similarity in more taxonomic and thematic ways, respectively, and respond accordingly in categorization tasks such as ours.
+While we managed to replicate the previously documented contrast between English speakers in the US and Mandarin Chinese speakers from East Asia (mainland China, Taiwan, Hong Kong, and Singapore), we do not extend this contrast to our sample of Vietnamese speakers in Vietnam and English speakers in the US.
+This finding suggests some limitations on the generality of this cultural account.
+
+We did find some signatures of language specificity in our analysis, such as the large positive correlation between similarity judgments of each country and the respective corpus statistics, and how each corpus statistics are good predictors for corresponding country's similarity judgments.
+However, this is potentially due to the high correlation between corpus statistics of English, Vietnamese and Mandarin.
+We find even stronger evidence for consistency across the three groups, with substantive overlapping predictions across the corpus models, highly similar responding across the experiments, and a correspondingly high fit in cross-language comparisons between models and data.
+
+```{r include=FALSE, cache = TRUE}
+fit.country_no_triad <- glmer(responses_theme ~ country + (1 | subject), 
+                              data = df_main_analysis, 
+                              family = "binomial")
+
+fit.country = glmer(responses_theme ~ country + (1 | subject) + (country | triad), 
+                    data = df_main_analysis, 
+                    family = "binomial")
+summary(fit.country)
+
+fit.no_triad_compare <- anova(fit.country, fit.country_no_triad, type = 3)
+```
+
+There are some suggestions that the current approach can predict triad-specific cross-cultural effects.
+First of all, an ANOVA model comparison showed that adding a random effect term for varying slope by country and varying intercept by triad to the model produces a significant better fit than the identical model without this random effect term included as a predictor ($\chi^2$(`r fit.no_triad_compare["fit.country", "Df"]`) = `r round(fit.no_triad_compare["fit.country", "Chisq"], 2)`, p `r ifelse( fit.no_triad_compare["fit.country", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.no_triad_compare["fit.country", "Pr(>Chisq)"], 3)), "< .001")`)
+
+<!-- Anecdotally, we show below some examples of triads that show contrasting difference in the magnitude of difference in thematic responses between countries.
+As a review, the overall result across all triads showed that there was significant difference between US and China responding, and no significant differences between US and Vietnam or China and Vietnam responding.
+However, we observed that for the triad "cow-grass-chicken," there were significant differences between US and China, and US and Vietnam responding.
+There was no significant difference between China and Vietnam responding.
+For the triad "spoon-sugar-fork," there were significant difference between China and US, and China and Vietnam responding, but no significant difference between US and Vietnam.
+For the triad "hair-comb-beard," there were no significant differences pairwise across the three cultural contexts.
+This suggests that there are triad-specific cross-cultural effects in play.
+Beyond emphasizing the importance of including triad predictors as a random effect, this finding suggests that, firstly, future similar studies need to report triads that are used, as the triads used can affect results (for example, if a study only includes triads where China and US responding are significantly different, it would be more likely to conclude that Chinese and US cultures hold different notions of similarity).
+Secondly, that future studies can look more deeply into which groups of triads are driving the US-China responding difference.
+For example, triads belonging to different semantic neighborhoods might be influencing cross-cultural responding in different ways.
+-->
+
+```{r include=FALSE, eval = F, cache = TRUE}
+df.country_item <- df_main_analysis %>%
+  filter(triad == "hair")
+
+plot.hair <- ggplot(df.country_item,
+       mapping = aes(x = factor(country, levels=c("China", "US", "Vietnam")), 
+                     y = responses_theme, 
+                     color = factor(country, levels=c("China", "US", "Vietnam")))) +
+  geom_jitter(stat = "identity", alpha  = .5) +
+  labs(y = "Proportion Thematic Chosen (hair: beard / comb)",  
+       x = "Country", 
+       color = "Country") + 
+  stat_summary(fun.data = "mean_cl_boot", 
+               geom = "pointrange") + 
+  scale_y_continuous(limits=c(0.0, 1.0), oob = scales::squish) + 
+  scale_fill_manual(values=c("#D63230", "#1C77C3", "#F39237")) +  
+  scale_color_manual(values=c("#D63230", "#1C77C3", "#F39237"))  + 
+  theme(axis.title = element_text(size=rel(0.75)))
+```
+
+```{r include=FALSE, eval = F, cache = TRUE}
+df.country_item <- df_main_analysis %>%
+  filter(triad == "spoon2")
+
+plot.spoon2 <- ggplot(df.country_item,
+       mapping = aes(x = factor(country, levels=c("China", "US", "Vietnam")), 
+                     y = responses_theme, 
+                     color = factor(country, levels=c("China", "US", "Vietnam")))) +
+  geom_jitter(stat = "identity", alpha  = .5) +
+  labs(y = "Proportion Thematic Chosen (spoon: fork / sugar)",  
+       x = "Country", 
+       color = "Country") + 
+  stat_summary(fun.data = "mean_cl_boot", 
+               geom = "pointrange") + 
+  scale_y_continuous(limits=c(0.0, 1.0), oob = scales::squish) + 
+  scale_fill_manual(values=c("#D63230", "#1C77C3", "#F39237")) +  
+  scale_color_manual(values=c("#D63230", "#1C77C3", "#F39237")) + 
+  theme(legend.position = "none") + 
+  theme(axis.title = element_text(size=rel(0.75)))
+```
+
+```{r include = FALSE, eval = F, cache = TRUE}
+#show 1 triad
+
+df.country_item <- df_main_analysis %>%
+  filter(triad == "cow2")
+
+df.country_item_summ <- df %>%
+  group_by(triad, country) %>%
+  summarize(theme_resp_percent = mean(responses_theme, na.rm = T)) %>%
+  filter(triad == "cow2")
+
+plot.cow2 <- ggplot(df.country_item,
+       mapping = aes(x = factor(country, levels=c("China", "US", "Vietnam")), 
+                     y = responses_theme, 
+                     color = factor(country, levels=c("China", "US", "Vietnam")))) +
+  geom_jitter(stat = "identity", alpha  = .5) +
+  labs(y = "Proportion Thematic Chosen (cow: chicken / grass)",  
+       x = "Country", 
+       color = "Country") + 
+  stat_summary(fun.data = "mean_cl_boot", 
+               geom = "pointrange") + 
+  scale_y_continuous(limits=c(0.0, 1.0), oob = scales::squish) + 
+  scale_fill_manual(values=c("#D63230", "#1C77C3", "#F39237")) +  
+  scale_color_manual(values=c("#D63230", "#1C77C3", "#F39237")) + 
+  theme(legend.position = "none") + 
+  theme(axis.title = element_text(size=rel(0.75)))
+# 
+# +  
+#   geom_bar(data = df.country_item_summ, 
+#            mapping = aes(x = factor(country, levels=c("China", "US", "Vietnam")), 
+#                           y = theme_resp_percent, 
+#                          color = factor(country, levels=c("China", "US", "Vietnam"))), 
+#            stat='identity', alpha = .3, 
+#            fill=c("#D63230", "#1C77C3", "#F39237"))
+```
+
+```{r echo=FALSE, eval = F, warning = FALSE, cache = TRUE, fig.width=8, fig.cap="Anecdotal evidence of triad-specific effects.
+Cow-grass-chicken shows significant differences between US-China responding, and between US-Vietnam responding.
+Spoon-sugar-fork shows only a significant difference between US-China responding.
+Hair-comb-beard does not show any significant differences in pairwise comparisons across the three countries."}
+plot.cow2 + plot.spoon2 + plot.hair + 
+    plot_layout(ncol = 3)
+```
+
+Our findings raise additional questions for future work: if not differences in taxonomic vs.
+thematic responding, then what differences drive the relativity effects previous studies have observed?
+To what extent are the relativity effects driven by language, and to what extent by culture?
+@Ji2004 established that culture-aligned differences in this paradigm exist, even when the test language is held constant, concluding that “it is culture (independent of the testing language) that led to different grouping styles” in their study.
+Our data provide a cautionary note to this conclusion, suggesting that semantic representations in bilinguals (see @Francis2005 for a review) may have the potential to provide an offline account for cross-context differences in similarity judgments, independent of test language.
+However, there are still many open questions for this account.
+How do semantic associations guide categorization?
+Can they explain taxonomic-thematic differences of the type reported by @Ji2004 and others?
+Can we provide a more specific computational account than the simple frequency model tested here?
+
+Despite these caveats, our findings here demonstrate the plausibility of an alternative perspective on cross-cultural accounts of language, thought, and similarity in the case of taxonomic and thematic reasoning: that it may be the input to similarity judgments, rather than the evaluative process or the conceptualization of similarity that produces variation in similarity reasoning across cultural and linguistic contexts.
+We hope this work provides a foundation for further research probing this question.
+
+[^footnote]:While we discuss cross-cultural variability at the level of countries or larger world areas, these are not cultural monoliths.
+For convenience, we operationalize culture at the level of country, based on where participants were raised.
+It is an open question whether performance in our participant populations (of relatively young and well-educated adults) is representative of the broader country.
+This is especially true for societies with substantial ethnic and cultural variation such as the US.
+We expect that our data is likely to underestimate variation both within and between the countries we sample from.
+
+\newpage
 

### 2022-12-31 code/4_paper/manuscript/manuscript.tex
added analysis with cosine distance

% Template for Cogsci submission with R Markdown

% Stuff changed from original Markdown PLOS Template
\documentclass[10pt, letterpaper]{article}

\usepackage{cogsci}
\usepackage{pslatex}
\usepackage{float}
\usepackage{caption}

% amsmath package, useful for mathematical formulas
\usepackage{amsmath}

% amssymb package, useful for mathematical symbols
\usepackage{amssymb}

% hyperref package, useful for hyperlinks
\usepackage{hyperref}

% graphicx package, useful for including eps and pdf graphics
% include graphics with the command \includegraphics
\usepackage{graphicx}

% Sweave(-like)
\usepackage{fancyvrb}
\DefineVerbatimEnvironment{Sinput}{Verbatim}{fontshape=sl}
\DefineVerbatimEnvironment{Soutput}{Verbatim}{}
\DefineVerbatimEnvironment{Scode}{Verbatim}{fontshape=sl}
\newenvironment{Schunk}{}{}
\DefineVerbatimEnvironment{Code}{Verbatim}{}
\DefineVerbatimEnvironment{CodeInput}{Verbatim}{fontshape=sl}
\DefineVerbatimEnvironment{CodeOutput}{Verbatim}{}
\newenvironment{CodeChunk}{}{}

% cite package, to clean up citations in the main text. Do not remove.
\usepackage{apacite}

% KM added 1/4/18 to allow control of blind submission

\usepackage{color}

% Use doublespacing - comment out for single spacing
%\usepackage{setspace}
%\doublespacing

% % Text layout
% \topmargin 0.0cm
% \oddsidemargin 0.5cm
% \evensidemargin 0.5cm
% \textwidth 16cm
% \textheight 21cm

\title{Re-examining cross-cultural similarity judgements using lexical
co-occurrence}

\usepackage[utf8]{inputenc}
\usepackage[T1, T5]{fontenc}

\author{{\large \bf Morton Ann Gernsbacher (MAG@Macc.Wisc.Edu)} \\ Department of Psychology, 1202 W. Johnson Street \\ Madison, WI 53706 USA \AND {\large \bf Sharon J.~Derry (SDJ@Macc.Wisc.Edu)} \\ Department of Educational Psychology, 1025 W. Johnson Street \\ Madison, WI 53706 USA}

\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newenvironment{CSLReferences}%
  {}%
  {\par}

\begin{document}

\maketitle

\begin{abstract}
Is ``cow'' more closely related to ``grass'' or ``chicken''? Speakers of
different languages judge similarity in this context differently, but
why? One possibility is that cultures co-varying with these languages
induce variation in conceptualizations of similarity. Specifically, East
Asian cultures may promote reasoning about thematic similarity, by which
cow and grass are more related whereas Western cultures may bias
similarity judgements toward taxonomic relations, like cow-chicken. This
difference in notions of similarity is the consensus interpretation for
cross-cultural variation in this paradigm. We consider, and provide
evidence for, an alternative possibility, by which notions of similarity
are equivalent across contexts, but the statistics of the environment
vary. On this account, similarity judgements are guided by co-occurrence
in experience, and observing or hearing about cows and grass or cows and
chickens more often could induce preferences for the relevant grouping,
and account for apparent differences in notions of similarity across
contexts.

\textbf{Keywords:}
similarity; culture; language; semantics; lexical co-occurrence;
variation
\end{abstract}

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

By virtue of discrete words and grammatical features, language provides
a categorical partition of our continuous experiences. By measuring the
similarity between words (as commonly done with lexical co-occurrence
models), it may be possible to model the shape of similarity space in
order to capture cross-linguistic and cross-cultural variation and
provide a more general answer to the question of how language influences
our conception of the world.

Taxonomic and thematic similarity provide a convenient entry point to
broader debates about cross-linguistic and cross-cultural variation in
notions of similarity. Taxonomic categorization is based on the
similarity of attributes, for example, similar perceptual properties,
like shared color or shape, among objects. In contrast, thematic
categorization is based on causal, spatial, and temporal relationships
among objects (Markman \& Hutchinson, 1984). To illustrate this point,
if a participant is given the words ``chicken'' and ``grass'', and asked
which of those words are more closely related to the word ``cow'', the
pairing ``chicken'' - ``cow'' indicates a taxonomic match, whereas
``grass'' - ``cow'' indicates a thematic match.

Ji, Zhang, \& Nisbett (2004) found that preferences for taxonomic and
thematic matches differ across cultures, even when controlling for
testing language and fluency. Specifically, Chinese participants made
more thematic matches than taxonomic, while the converse was true for
European Americans. This difference held even for Chinese participants
tested in English (rather than Mandarin), suggesting that culture has an
effect on the categorization strategy independent of the test language.
However, the study also found an effect of language within Chinese
participants from mainland China (when tested both in China and in the
US): their preference for thematic categorization was significantly
lower when tested in English compared to Mandarin Chinese. This suggests
that test language also influences categorization strategies. Ji et
al.~characterize these results as demonstrating that culture
(independent of language) leads to different styles of reasoning about
similarity, whereas language serves as a ``tuning'' mechanism operating
within a culturally-specific style, by activating representations
corresponding to the language being used.

\hypertarget{cross-cultural-variation-in-similarity}{%
\subsection{Cross-cultural variation in
similarity}\label{cross-cultural-variation-in-similarity}}

The view that culture drives differences in categorization style has
been one favored by other non-linguistic studies that use taxonomic vs
thematic categorization to probe similarity judgment. When shown
pictorial triads that represent words (i.e.~pictures of an ant, a bee,
and honey), Chinese children (9-10 years old) scored higher on thematic
categorization compared to American children of the same age range, and
vice versa for taxonomic categorization (Chiu, 1972). These
cross-cultural differences in similarity judgment persist in novel
object categorization, with Chinese participants preferring to group by
family resemblance across multiple features and Americans preferring a
single-feature rule (Norenzayan, Smith, Kim, \& Nisbett, 2002). Since
differences in categorization style persist with novel stimuli (as
opposed to previously seen words or pictures of concepts), this suggests
that participants from different cultural backgrounds are utilizing
different reasoning strategies when making similarity judgments. The
authors attribute these differences to tendencies toward analytic
processing in Western cultures, which emphasizes objects and their
properties and holistic processing in East Asian cultures, which
emphasizes relationships between objects and their context. According to
this framework, East Asians attend more to relationships between objects
and context and reason more holistically, whereas Westerners attend more
to objects and their properties, and reason analytically (ibid, see also
Nisbett (2003)). In related work, East Asian participants show a higher
level of sensitivity to context than their Western counterparts when
reproducing drawings from memory (Ji, Peng, \& Nisbett, 2000); visually
exploring naturalistic scenes (Chua, Boland, \& Nisbett, 2005);
describing scenes (Masuda \& Nisbett, 2001); and in explaining the
causes of ambiguous behaviors (Choi, Nisbett, \& Norenzayan, 1999).
These cross-cultural differences in attention and analytic vs holistic
processing are seen to map onto the cross-cultural differences in
similarity judgment: because East Asian participants attend more to the
context between objects and reason more holistically, it stands to
reason that they would consider words that appear in the same context
(i.e.~thematically similar) to be more similar than
taxonomically-similar words.

This view ascribes cross-cultural differences in similarity judgment
tasks to variation in the conceptualization of similarity itself.
Alternatively, these judgments could be shaped by cross-cultural
differences in the statistics of the environment, and accordingly the
content of everyday experiences. Perhaps when confronted with the triad
task, participants from all cultures follow the same process for
reasoning about similarity, but rely on language or culture-specific
inputs to this process. For example, it may be that Vietnamese
participants are more likely to have knowledge of farming practices than
Americans, and may associate cows and grass more strongly (as grass is
the typical feed for cows in the small-scale family farming contexts
common in Vietnam). Americans, on the other hand, may have strong
associations between cows and chickens as a result of encountering them
together in children's books or petting zoo contexts. If we observe a
difference in categorization between, say Vietnamese and US
participants, it could be that members of both groups use the same
procedure (considering similarity that is influenced by both taxonomic
and thematic relations), but the inputs to this procedure differ between
cultures, with Vietnamese participants exposed to more instances of
``cow'' and ``grass'' occurring together, compared to US participants.

\hypertarget{language-as-a-proxy-of-variation-in-experience}{%
\subsection{Language as a proxy of variation in
experience}\label{language-as-a-proxy-of-variation-in-experience}}

While co-occurrences in experience are difficult to measure,
co-occurrence in language can provide a rough proxy--and indeed,
language may afford many of the ``experiences'' that people have with
infrequently encountered items, like cows or helicopters. In this study,
we use co-occurrence in language as a proxy of cultural experience. This
is a generalizing assumption, and while no linguistic corpus can be
expected to fully capture a culture, using this proxy as a model of
culture provides a conservative test of the hypothesis that differences
in the input, rather than the process, of reasoning produces cultural
variation in this task. This means that if such a model does work -- if
linguistic co-occurrence can predict cultural variation in this
similarity task without building differences in the decision process
into the model -- it is relatively strong evidence that language alone
(perhaps as a more easily observed source of information on broader
cultural and ecological variation) may account for these cross-cultural
differences in reasoning.\footnote{While we discuss cross-cultural
  variability at the level of countries or larger world areas, these are
  not cultural monoliths. For convenience, we operationalize culture at
  the level of country, based on where participants were raised. It is
  an open question whether performance in our participant populations
  (of relatively young and well-educated adults) is representative of
  the broader country. This is especially true for societies with
  substantial ethnic and cultural variation such as the US. We expect
  that our data is likely to underestimate variation both within and
  between the countries we sample from.}

Indeed, previous work suggests that using lexical co-occurrence as a
proxy can be useful in thinking about similarity judgments. Natural
language processing tasks have found that lexical co-occurrence is a
good predictor for performance in similarity judgment tasks. Griffiths,
Steyvers, \& Tenenbaum (2007) showed that a model that takes
word-document co-occurrence as input can be used to predict word
association and the effects of semantic association on a variety of
linguistic tasks. Additionally, lexical semantic models that are
constructed using lexical co-occurrence (as opposed to annotated
relations) have been shown to perform well on predicting human judgments
about similarity between word pairs that are either thematically or
taxonomically related (Rohde, Gonnerman, \& Plaut, 2006).

Our current study will be using 2 measures of lexical co-occurrence: 1)
raw lexical co-occurrences and 2) cosined distances of fastText word
vectors. fastText is a system that uses lexical co-occurrence
information to generate a vector representing each word in its lexicon
(Mikolov, Grave, Bojanowski, Puhrsch, \& Joulin, 2018). fastText uses a
continuous bag-of-words model, which takes into account a symmetric
window of words surrounding the word in question and maximizes the
log-likelihood of the probability of the word given its context.
Calculating the cosine-similarity between word vectors from fastText
gives us a score of how similar the contexts of these words are.
Therefore, words that occur in the same context (high lexical
co-occurrence) would have a larger cosine-similarity score.

It must be noted that fastText supplements the lexical co-occurrence
information by simultaneously training weight vectors for each position
relative to the word in question, as well as adding sub-word information
(bag-of-character n-gram vectors for each character forming the words).
The similarity judgment prediction given by fastText may be more higher
than a model using purely lexical co-occurrence information. However,
models that use only lexical co-occurrence information (with or without
a simple position weight system that gives more weight to words that are
closer to the word in question) also perform well in similarity
prediction tasks. For this study, due to the lack of large cleaned
corpora for Mandarin and Vietnamese, we are leveraging fastText
pre-trained models on the languages we are interested in Grave,
Bojanowski, Gupta, Joulin, \& Mikolov (2018).

Systems like fastText and word2vec have been demonstrated to be good
predictors for similarity judgments. Liu, Feng, Wu, Chan, \& Fulton
(2019) showed that fastText performed well as the data for a system
matching responses in a knowledge base by how similar they are to a
customer's query. A study by Jatnika, Bijaksana, \& Suryani (2019)
tested a word2vec model trained on the English wikipedia corpus against
353 word pairs labeled with similarity values based on human judgment.
The word2vec model correlates moderately with human judgment. fastText
has also been shown to be sensitive towards cultural effects on word
meanings: Thompson \& Lupyan (2020) applied fastText to
language-specific Wikipedia corpus (among others) to generate a
``semantic neighborhood'' of 1010 meanings in different languages. The
study showed that languages that are spoken by more similar cultures,
more geographically proximate and/or historically related had more
semantic neighborhoods that aligned. This is a proof of concept for our
use of fastText in different languages with varying levels of
relatedness.

\hypertarget{the-present-study}{%
\subsection{The present study}\label{the-present-study}}

Ji et al. (2004) suggest that the notion of similarity is what varies
across cultural groups, but it is quite possible that similarity is
regarded in the same way and it is actually the input to this similarity
judgment that varies across culture contexts. It might be possible to
gain traction on possible mechanisms by examining whether variation in
similarity judgments co-varies with environmental statistics that differ
across the cultural and linguistic contexts.

In this study, we ask whether variation in lexical co-occurrence can
account for the cross-context (culture and language) differences
observed in how people evaluate similarity. First, we attempt to
replicate Ji et al. (2004) by running a study comparing English speakers
in the US and Mandarin speakers in mainland China. Second, we evaluate
whether the differences observed between English and Mandarin speakers'
similarity judgments also extend to comparisons between English and
Vietnamese, by running a similar study between English speakers in the
US and Vietnamese speakers in Vietnam. Vietnam is a Southeast Asian
country that borders China and is historically greatly influenced by
Chinese culture (Hui, 2002). Therefore, it serves as a suitable cultural
context to investigate whether the claim made by Ji et al. (2004) and
previous studies, that Eastern and Western cultures have different
notions of similarity, extends beyond mainland China.

We then ask to what extent similarity judgments show cross-context
differences that align with co-occurrence patterns in participants'
languages. We would only see a main effect of cultural context if
differing notions of similarity drive these cross-cultural differences.
Meanwhile, if we do see variation in responding trial-to-trial that
tracks with lexical co-occurrence statistics (as a rough proxy combining
both linguistic and cultural context), this suggests that cross-cultural
notions of similarity might be similar, and it is environmental
statistics that guide the differences in similarity judgments. To
preview our results, we find that, while we do not see overall group
differences (between the East Asian contexts and the US) in similarity,
we do find language-specific co-occurrence can indeed explain
cross-context differences in similarity judgments. In contrast to
previous accounts, by which culture induces differing conceptions of
similarity (varying between taxonomic and thematic), these findings
provide an alternative, and more specific, account by which language may
explain these cross-cultural differences without invoking variation in
notions of similarity.

\hypertarget{methods}{%
\section{Methods}\label{methods}}

\hypertarget{participants}{%
\subsection{Participants}\label{participants}}

We recruited 200 participants from the US, 199 participants from
Vietnam, and 200 participants from mainland China. US participants were
recruited through snowball sampling seeded with Stanford student email
lists, Vietnam participants were recruited through snowball sampling
seeded with Vietnam-based student groups on Facebook, and mainland China
participants were recruited through snowball sampling seeded with group
chats on WeChat. US participants were compensated with \$5 gift
certificates (USD), VN participants received 50,000₫ (VND) in phone
credit, and mainland China participants received 25CNY through WeChat
credit transfer.

We excluded 8 US participants, 62 Vietnam participants, and 34 China
participants who did not answer all attention checks correctly. We
followed 4 exclusion criteria that aim to retain only participants who
are influenced by one culture: (1) non-native speakers of English and
Vietnamese, respectively, (2) fluent in at least one of the other two
study languages (Vietnamese for US participants, English for Vietnamese
participants and Chinese participants), (3) have lived outside of the
test country (US, Vietnam, or China) for more than two years, and (4)
have significant international experience (more than 6 international
experiences of 2 days or longer.) We did not use a particular criterion
for a language if it would exclude 25\% or more of any one sample. In
this round of exclusion, we excluded 68 US, 27 Vietnam participants, and
34 China participants. After these exclusions, the US sample included
124 participants (30M, 89F, 3 non-binary, 2 other), with mean age =
22.18 (SD = 8) and median age = 20. The Vietnam sample included 110
participants (34M, 71F, 5 other), with mean age = 22.21 (SD = 5.81) and
median age = 21. The China sample included 132 participants (51M, 81F,
other), with mean age = 23.27 (SD = 3.75) and median age = 23.

Notably, we lost a majority of our Vietnam participants (more than 60\%)
in the attention check exclusion. One reason we suspect why this might
have happened is because our Vietnam participants are less familiar with
research surveys and attention check questions, and thus might have
thought too much about the attention check questions. We carried out an
exploratory analysis where we used a less stringent attention check
exclusion (covered in the final part of the Results \& Analysis
section). To preview our findings for this analysis, we did not find any
difference in significant results when compared with the main analysis.

\hypertarget{stimuli}{%
\subsection{Stimuli}\label{stimuli}}

We adapted stimuli from previous studies to create a set of test triads
consisting of a cue, with one thematic and one taxonomic match option.
For example, ``cow,'' ``grass,'' and ``chicken,'' where ``cow'' is the
cue, ``grass'' is the thematic match, and ``chicken'' the taxonomic
match. We included 105 such triads, a superset including triads pulled
from supplemental information and in-text examples across the
literature, and others that we adapted or created (see SI for the full
list of stimuli and sources). We selected triads on the basis of
cultural familiarity in the US, Vietnam, and China. The triads were
originally in English; they were translated to Vietnamese and Mandarin
by a fluent bilingual speaker in each language. The translations were
then checked for accuracy after backtranslation to English by another
fluent bilingual in each language who was naive to the original English
versions.

Each participant completed all 105 triads in sets of 21 trials at a time
(10 test triads, 10 filler triads, and 1 attention check per page), by
selecting the match most related to the cue (``Which thing is most
closely related to the bolded item?'' or ``Thứ nào liên quan nhất với
thứ được in đậm?''). The test triads were presented with 105 filler
triads mixed in, to obscure the taxonomic-thematic two-answer forced
choice structure of the test stimuli and reduce the likelihood that
participants would become aware of the design. The filler triads were
groups of three semantically related words, but where the match options
were not distinguished by thematic vs.~taxonomic similarity, e.g., cue
``bird'' with match options ``lizard'' and ``toad.'' Additionally, we
included 10 attention check trials, which were formatted like the test
and filler triads but included an instruction instead of a cue item,
e.g., ``Choose wife'' with match options ``wife'' and ``husband.'' In
total, each participant completed 210 similarity judgments and 10
attention check questions, with triads presented in randomized orders
that varied between subjects.

\hypertarget{corpus-model}{%
\subsection{Corpus model}\label{corpus-model}}

Our general approach is to build a model of similarity that is based on
collocation counts in each language.

\hypertarget{raw-lexical-co-occurrences}{%
\subsubsection{Raw lexical
co-occurrences}\label{raw-lexical-co-occurrences}}

To give an intuition for our model, consider the cow-grass-chicken
triad: we counted how many times ``cow'' and ``grass'' co-occur within a
window of text in each corpus, and compare this to how many times
``cow'' and ``chicken'' co-occur. Our similarity prediction is then
proportional to the relative frequency of these pairs. For example, if
the thematic cow-grass match accounts for 30\% of collocations for this
triad (with cow-chicken making up the other 70\%), then our model
predicts, correspondingly, that 30\% of responses to the triad will be
grass, and the other 70\% chicken. We then use a mixed-effects
regression to evaluate how well each corpus collocate model predicts
participants' similarity judgments, across triads and languages.

\hypertarget{collocate-retrieval-and-coding}{%
\paragraph{Collocate retrieval and
coding}\label{collocate-retrieval-and-coding}}

For our English co-occurrence metric, we used the online interface of
the Corpus of Contemporary American English (Davies, 2008-) to retrieve
collocation counts. We recorded the raw count of times that any
cue-match pair (e.g., cow-grass or cow-chicken) co-occur in a window of
19 words, which is the maximum window size in the online interface, and
closest to the sentence co-occurrence metric in our VI corpus
collocation counts.

To determine Vietnamese co-occurrence, we used the raw frequency of
sentence co-occurrences from a subset of the Vietnamese corpus in the
Leipzig Corpora Collection (Goldhahn, Eckart, \& Quasthoff, 2012); this
corpus includes 70 million Vietnamese sentences, but our corpus data
comes from a 1 million sentence subset for which co-occurrence counts
are available for download. Vietnamese makes very frequent use of
compositional morphology but the written language uses spacing to
delineate syllable boundaries rather than word boundaries. Accordingly,
collocate searches returned instances of both target terms and many
morphologically related, but distinct, words. We included in our counts
any instances of the target term or close semantic neighbors containing
the same morpheme(s) as long as they entailed a likely literal reference
to the target term. For example, our search for collocates of the term
``gà'' (chicken) also returned ``gà mái,'' a distinct word for female
chickens. Despite being a different word, ``gà mái'' both includes the
morpheme for ``chicken'' and entails reference to a chicken.
Accordingly, instances of both ``gà'' and ``gà mái'' were included in
our collocate count for ``chicken.'' Some compounds do not meet this
criteria, and were excluded from collocate counts. For example ``trái
cây'' (tree.fruits) includes the same syllable as the word ``cây''
(tree), but refers to fruit that comes from trees, not the trees
themselves, and was therefore excluded from our collocate counts for
``tree.''

TODO; ADD INFO ABOUT MANDARIN CORPUS

\hypertarget{collocate-similarity-model}{%
\paragraph{Collocate similarity
model}\label{collocate-similarity-model}}

From the raw co-occurrence counts of each triad, we calculated the
thematic co-occurrence ratio as the number of thematic co-occurrences
over the sum of thematic and taxonomic co-occurrences. We did this for
both the English and Vietnamese corpus co-occurrence counts. In this
way, we obtained predictions for 73 of 105 triads from the Vietnamese
corpus and 104 of 105 triads from English. We therefore limited all
analyses reported here to the subset of triads for which our
corpus-based model can make meaningful predictions, meaning triads that
have at least one non-zero collocate count (either thematic or taxonomic
match). We replaced any remaining zero collocate counts with
\(\epsilon\) to account for sparsity in the corpus data. We then tested
whether these simple relative frequency models predict US and VN
responding.

\hypertarget{cosine-distance-of-word-vectors}{%
\subsubsection{Cosine distance of word
vectors}\label{cosine-distance-of-word-vectors}}

To give an intuition for our model, consider again the cow-grass-chicken
triad: we retrieved word vectors for ``cow'' and ``grass'', and
calculate the cosine distance between these vectors. Similarly, we
retrieved vectors for ``cow'' and ``chicken'' and calculate the cosine
distance between them. Our similarity prediction is then inversely
proportional to the cosine distance of these pairs. This is because a
larger cosine distance means the word vectors are further apart, and
thus the words are less similar. For example, if the cosine distance of
thematic cow-grass is 0.7 and the cosine distance of taxonomic
cow-chicken is 0.3, then our model predicts, correspondingly, that 30\%
of responses to the triad will be grass, and the other 70\% chicken. We
then use a mixed-effects regression to evaluate how well each corpus
model predicts participants' similarity judgments, across triads and
languages.

\hypertarget{collocate-retrieval}{%
\paragraph{Collocate retrieval}\label{collocate-retrieval}}

We use the fastText pre-trained models of English, Mandarin, and
Vietnamese in Grave et al. (2018). These models are trained on Common
Crawl and Wikipedia using We distribute pre-trained word vectors for 157
languages, trained on Common Crawl and Wikipedia using fastText. These
models were trained using a Continuous Bag of Words (CBOW) with
position-weights and a window of size 5. The models use character
n-grams of length 5 and 10 negative examples.From the aforementioned
models, we retrieve the word vectors (dimension 300) for each word we
are interested in.

\hypertarget{collocate-similarity-model-1}{%
\paragraph{Collocate similarity
model}\label{collocate-similarity-model-1}}

From the word vectors, we calculated the cosine distance between each
cue-thematic match (thematic cosine distance) and cue-taxonomic match
(taxonomic cosine distance), using the spatial.distance.cosine function
from the SciPy package (Virtanen et al., 2020). We then calculated the
thematic cosine distance proportion as thematic cosine distance over the
sum of taxonomic cosine distance and thematic cosine distance. We did
this for all three corpora. We were able to obtain predictions for all
triads in all languages.

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{do-we-extend-previous-work-reporting-a-preference-for-taxonomic-matching-in-the-us-and-thematic-matching-in-asia}{%
\subsection{1. Do we extend previous work reporting a preference for
taxonomic matching in the US and thematic matching in
Asia?}\label{do-we-extend-previous-work-reporting-a-preference-for-taxonomic-matching-in-the-us-and-thematic-matching-in-asia}}

The group means of proportion of thematic response in mainland China is
the highest (M = 0.65, SD = 0.12), followed by the groups means in
Vietnam (M = 0.6, SD = 0.11), which is slightly higher than that of the
US (M = 0.57, SD = 0.16).

\begin{CodeChunk}
\begin{figure}[tb]
\includegraphics{figs/unnamed-chunk-2-1} \caption[Proportion of thematic responses by country]{Proportion of thematic responses by country. Only US-China responding comparison shows a siginficant difference. We could not extend this to US-Vietnam responding comparison.}\label{fig:unnamed-chunk-2}
\end{figure}
\end{CodeChunk}

To test for cross-context differences in similarity judgments between
the countries, we ran a mixed-effects logistic regression predicting
triad responding (taxonomic or thematic) with country (US, China, or
Vietnam) as a fixed effect. As random effects, we included an intercept
per subject and one per triad, as well as by-triad random slopes for
country to account for variation in the country effect across triads. In
R syntax, the model is: response \textasciitilde{} country + (1
\textbar{} subject) + (country \textbar{} triad).

Overall, there is a significant effect of country on proportion of
thematic responses (\(\chi^2\)(2) = 15.75, p \textless{} .001). However,
this effect is driven by the difference between US and China responding
(\(\beta\) = -0.5, p \textless{} .001). There is no statistical
difference between the Vietnam and China responding (\(\beta\) = -0.25,
p = 0.066), and the US and Vietnam responding (\(\beta\) = 0.25, p =
0.095).

On this analysis, we do not find support that the US-China tendencies
toward taxonomic and thematic responding (respectively) extend to the
US-Vietnam comparison. Accordingly, we cannot speak to overall biases
toward thematic responding across Asian cultural contexts broadly, but
we do replicate the differences documented by Ji et al. (2004) between
the US and China. However, in our corpus model comparison, we do find
evidence for different, more fine-grained variation in similarity
judgments between the US and Vietnam.

\hypertarget{can-the-differences-in-similarity-judgments-between-english-mandarin-and-vietnamese-speakers-be-explained-by-variation-in-lexical-statistics}{%
\subsection{2. Can the differences in similarity judgments between
English, Mandarin and Vietnamese speakers be explained by variation in
lexical
statistics?}\label{can-the-differences-in-similarity-judgments-between-english-mandarin-and-vietnamese-speakers-be-explained-by-variation-in-lexical-statistics}}

\hypertarget{is-responding-in-each-cultural-context-predicted-by-the-corresponding-lexical-statistics-raw-co-occurrences}{%
\subsubsection{Is responding in each cultural context predicted by the
corresponding lexical statistics (raw
co-occurrences)?}\label{is-responding-in-each-cultural-context-predicted-by-the-corresponding-lexical-statistics-raw-co-occurrences}}

\hypertarget{raw-lexical-co-occurrences-1}{%
\paragraph{Raw lexical
co-occurrences}\label{raw-lexical-co-occurrences-1}}

To test whether variation in lexical co-occurrence can explain
differences in similarity judgments between US and Vietnam participants,
we compare logistic mixed-effects regression models fit to the thematic
responding data from each country separately. We first ask how well each
corpus model (English, Vietnamese, or Mandarin) predicts similarity
judgments by speakers of the corresponding language (US, Vietnam, or
China). To do this, we use a mixed-effects logistic regression to
predict triad responses (0=taxonomic or 1=thematic) with corpus
prediction (proportion thematic co-occurrence or cosine distance) as a
fixed effect and participant and triad as random effects.

We found that all corpora are significant predictors of all cultural
context responding.

For US responding: English (EN), Vietnamese (VI), and Mandarin (ZH)
corpus are all significant predictors. EN corpus: \(\beta\) = 2.01,
\(\chi^2\)(1) = 17.42, p \textless{} .001. VI corpus: \(\beta\) = 1.21,
\(\chi^2\)(1) = 11.1, p \textless{} .001. ZH corpus: \(\beta\) = 1.15,
\(\chi^2\)(1) = 6.38, p = 0.012.

For Vietnam responding: English (EN), Vietnamese (VI), and Mandarin (ZH)
corpus are all significant predictors. EN corpus: \(\beta\) = 1.73,
\(\chi^2\)(1) = 12.35, p \textless{} .001. VI corpus: \(\beta\) = 1.27,
\(\chi^2\)(1) = 12.83, p \textless{} .001. ZH corpus: \(\beta\) = 1.8,
\(\chi^2\)(1) = 18, p \textless{} .001.

For China responding: English (EN), Vietnamese (VI), and Mandarin (ZH)
corpus are all significant predictors. EN corpus: \(\beta\) = 1.21,
\(\chi^2\)(1) = 9.83, p = 0.002. VI corpus: \(\beta\) = 0.77,
\(\chi^2\)(1) = 7.44, p = 0.006. ZH corpus: \(\beta\) = 1.15,
\(\chi^2\)(1) = 13.28, p \textless{} .001.

This suggests a strong shared similarity signal across the languages.

\hypertarget{cosine-distances-of-fasttext-word-vectors}{%
\paragraph{Cosine distances of fastText word
vectors}\label{cosine-distances-of-fasttext-word-vectors}}

Similar to the results from the analysis with raw lexical
co-occurrences, we found that all corpora are significant predictors of
all cultural context responding.

For US responding: English (EN), Vietnamese (VI), and Mandarin (ZH)
corpus are significant predictors of US responding (EN-US model:
\(\beta\) = -8.64, \(\chi^2\)(1) = 30.44, p \textless{} .001; VI-US
model: \(\beta\) = -2.97, \(\chi^2\)(1) = 5.23, p = = 0.022; ZH-US
model: \(\beta\) = -6.96, \(\chi^2\)(1) = 18.08, p \textless{} .001).

For Vietnam (VN) responding: English (EN), Vietnamese (VI), and Mandarin
(ZH) corpus are significant predictors of VN responding (EN-VN model:
\(\beta\) = -5.33, \(\chi^2\)(1) = 9.39, p = 0.002; VI-VN model:
\(\beta\) = -3.46, \(\chi^2\)(1) = 6.64, p = = 0.01; ZH-VN model:
\(\beta\) = -6.37, \(\chi^2\)(1) = 13.93, p \textless{} .001).

For China (CN) responding: English (EN), Vietnamese (VI), and Mandarin
(ZH) corpus are significant predictors of CN responding (EN-CN model:
\(\beta\) = -6.18, \(\chi^2\)(1) = 25.34, p \textless{} .001; VI-CN
model: \(\beta\) = -2.44, \(\chi^2\)(1) = 5.83, p = = 0.016; ZH-CN
model: \(\beta\) = -7.36, \(\chi^2\)(1) = 37.45, p \textless{} .001).

\hypertarget{is-responding-in-each-cultural-context-best-predicted-by-the-corresponding-corpuss-lexical-statistics-raw-co-occurrences-as-opposed-to-the-other-two-corpora}{%
\subsubsection{\texorpdfstring{Is responding in each cultural context
\textbf{best} predicted by the corresponding corpus's lexical statistics
(raw co-occurrences), as opposed to the other two
corpora?}{Is responding in each cultural context best predicted by the corresponding corpus's lexical statistics (raw co-occurrences), as opposed to the other two corpora?}}\label{is-responding-in-each-cultural-context-best-predicted-by-the-corresponding-corpuss-lexical-statistics-raw-co-occurrences-as-opposed-to-the-other-two-corpora}}

Next, we directly compare the corpus models by including both as fixed
effects in three mixed-effect regressions (predicting US, Vietnam and
China responding) with the same random effects as above. In R syntax,
the model is: response \textasciitilde{} corpus\_English +
corpus\_Vietnamese + corpus\_Mandarin + (1\textbar triad) +
(1\textbar subject).

\hypertarget{raw-co-occurrences}{%
\paragraph{Raw co-occurrences}\label{raw-co-occurrences}}

When we included all corpora thematic cosine distance proportion as
predictors, all corpora are significant in predicting all cultural
context's responding.

For US responding: only English (EN) corpus is a significant predictor.
EN corpus: \(\beta\) = 1.62, \(\chi^2\)(1) = 4.59, p = 0.032. VI corpus:
\(\beta\) = 0.46, \(\chi^2\)(1) = 1.04, p = 0.307. ZH corpus: \(\beta\)
= -0.03, \(\chi^2\)(1) = 0, p = 0.962.

For Vietnam responding: only English (EN) and Mandarin (ZH) corpora are
significant predictors. EN corpus: \(\beta\) = -0.02, \(\chi^2\)(1) = 0,
p = 0.979. ZH corpus: \(\beta\) = 1.39, \(\chi^2\)(1) = 6.5, p =
0.011.VI corpus: \(\beta\) = 0.79, \(\chi^2\)(1) = 3.3, p = 0.069.

For China responding: only Mandarin (ZH) corpus is a significant
predictor. ZH corpus: \(\beta\) = 0.9, \(\chi^2\)(1) = 4.31, p = 0.038.
EN corpus: \(\beta\) = 0.21, \(\chi^2\)(1) = 0.13, p = 0.72. VI corpus:
\(\beta\) = 0.35, \(\chi^2\)(1) = 1.02, p = 0.312.

\begin{CodeChunk}
\begin{figure}[tb]
\includegraphics{figs/unnamed-chunk-4-1} \caption[Fixed effect sizes of each corpus when included as a predictor for China, US, and Vietnam responding, respectively]{Fixed effect sizes of each corpus when included as a predictor for China, US, and Vietnam responding, respectively. The English corpus is the best predictor for US response, and the Mandarin corpus is the best predictor for China response.}\label{fig:unnamed-chunk-4}
\end{figure}
\end{CodeChunk}

We observed some level of language specificity from this analysis. The
English corpus is the best predictor for US responding, and the Mandarin
corpus is the best predictor for China response. While this is not the
case with the Vietnamese corpus and the Vietnam responding, the
Vietnamese corpus is still a significant predictor for the Vietnam
responding.

However, we found that language specificity alone does not explain our
results. We used an ANOVA to compare the model with only the
corresponding corpus, and the model with all 3 corpora for each cultural
context. We found that in all three cases (US, China, Vietnam), adding
the other two corpora produces a significantly better fit than the
identical model without the additional corpora, and only the
corresponding corpus included as a predictor (US response: \(\chi^2\)(2)
= 1.04, p = 0.595; Vietnam response: \(\chi^2\)(2) = 8.84, p = 0.012;
China response: \(\chi^2\)(2) = 2.13, p = 0.345).

\_TODO: should we take this out?\_\_ We carried out an ANOVA model
comparison to compare our approach with previous studies that did not
include corpus information. Because Ji et al. (2004) only compared US
and China participants, we filtered our data to only include responding
data from these two countries. Our approach would be to compare a model
that only includes country (US or China) as a fixed effect with one that
also includes English and Chinese corpus data. Our previous model with
an intercept per subject and one per triad, as well as by-triad random
slopes for country to account for variation in the country effect across
triads fails to converge with the more complex model, so we include a
simpler random effect structure with an intercept per subject and one
per triad in both the basic and more complex model. We compare this
model with an identical model but including Chinese and English corpus
cosine distance proportion prediction. We found that adding English and
Chinese corpus data produces a significantly better fit than the
identical model without English and Chinese corpus data as predictors
(\(\chi^2\)(2) = 42.57, p = \textless{} .001. This suggests that
including corpus data would better model the cross-cultural differences
in similarity judgment in this study as well as similar studies.

\hypertarget{cosine-distances-of-fasttext-word-vectors-1}{%
\paragraph{Cosine distances of fastText word
vectors}\label{cosine-distances-of-fasttext-word-vectors-1}}

When we included all corpora thematic cosine distance proportion as
predictors, all corpora are significant in predicting all cultural
context's responding.

For US responding: English (EN), Vietnamese (VI), and Mandarin (ZH)
corpus are all significant predictors. EN corpus: \(\beta\) = -6.9,
\(\chi^2\)(1) = 17.06, p \textless{} .001. VI corpus: \(\beta\) = -2.18,
\(\chi^2\)(1) = 3.72, p = = 0.054. ZH corpus: \(\beta\) = -3.2,
\(\chi^2\)(1) = 3.59, p = = 0.058.

For Vietnam responding: English (EN), Vietnamese (VI), and Mandarin (ZH)
corpus are all significant predictors. EN corpus: \(\beta\) = -2.98,
\(\chi^2\)(1) = 2.58, p = = 0.108. VI corpus: \(\beta\) = -2.75,
\(\chi^2\)(1) = 4.84, p = = 0.028. ZH corpus: \(\beta\) = -4.39,
\(\chi^2\)(1) = 5.43, p = = 0.02.

For China responding: English (EN), Vietnamese (VI), and Mandarin (ZH)
corpus are all significant predictors. EN corpus: \(\beta\) = -3.52,
\(\chi^2\)(1) = 7.81, p = = 0.005. VI corpus: \(\beta\) = -1.62,
\(\chi^2\)(1) = 3.59, p = = 0.058. ZH corpus: \(\beta\) = -5.35,
\(\chi^2\)(1) = 17.28, p = \textless{} .001.

We observed some level of language specificity from this analysis. The
English corpus is the best predictor for US responding, and the Mandarin
corpus is the best predictor for China response. While this is not the
case with the Vietnamese corpus and the Vietnam responding, the
Vietnamese corpus is still a significant predictor for the Vietnam
responding.

\begin{CodeChunk}
\begin{figure}[tb]
\includegraphics{figs/unnamed-chunk-5-1} \caption[Fixed effect sizes of each corpus when included as a predictor for China, US, and Vietnam responding, respectively]{Fixed effect sizes of each corpus when included as a predictor for China, US, and Vietnam responding, respectively. The English corpus is the best predictor for US response, and the Mandarin corpus is the best predictor for China response.}\label{fig:unnamed-chunk-5}
\end{figure}
\end{CodeChunk}

However, we found that language specificity alone does not explain our
results. We used an ANOVA to compare the model with only the
corresponding corpus, and the model with all 3 corpora for each cultural
context. We found that in all three cases (US, China, Vietnam), adding
the other two corpora produces a significantly better fit than the
identical model without the additional corpora, and only the
corresponding corpus included as a predictor (US response: \(\chi^2\)(2)
= 7.95, p = = 0.019; Vietnam response: \(\chi^2\)(2) = 13.72, p = =
0.001; China response: \(\chi^2\)(2) = 10.83, p = NA).

\_TODO: should we take this out?\_\_ We carried out an ANOVA model
comparison to compare our approach with previous studies that did not
include corpus information. Because Ji et al. (2004) only compared US
and China participants, we filtered our data to only include responding
data from these two countries. Our approach would be to compare a model
that only includes country (US or China) as a fixed effect with one that
also includes English and Chinese corpus data. Our previous model with
an intercept per subject and one per triad, as well as by-triad random
slopes for country to account for variation in the country effect across
triads fails to converge with the more complex model, so we include a
simpler random effect structure with an intercept per subject and one
per triad in both the basic and more complex model. We compare this
model with an identical model but including Chinese and English corpus
cosine distance proportion prediction. We found that adding English and
Chinese corpus data produces a significantly better fit than the
identical model without English and Chinese corpus data as predictors
(\(\chi^2\)(2) = 42.57, p = \textless{} .001. This suggests that
including corpus data would better model the cross-cultural differences
in similarity judgment in this study as well as similar studies.

\hypertarget{does-similarity-reasoning-differ-across-cultures-only-the-input-to-it-or-both}{%
\subsection{3. Does similarity reasoning differ across cultures, only
the input to it, or
both?}\label{does-similarity-reasoning-differ-across-cultures-only-the-input-to-it-or-both}}

Does adding country and interaction term with the corresponding corpus
improves the model?

Adding country improves the model. Only country and interaction between
country and corresponding corpus's lexical co-occurrence are significant
predictors. Corresponding corpus's lexical co-occurrence is no longer a
significant predictor.

\hypertarget{how-general-are-the-cross-language-differences-in-similarity-judgments-we-observe-are-they-limited-to-taxonomic-thematic-contrasts-or-do-they-extend-to-other-cases}{%
\subsection{5. How general are the cross-language differences in
similarity judgments we observe? Are they limited to taxonomic-thematic
contrasts or do they extend to other
cases?}\label{how-general-are-the-cross-language-differences-in-similarity-judgments-we-observe-are-they-limited-to-taxonomic-thematic-contrasts-or-do-they-extend-to-other-cases}}

\begin{CodeChunk}
\begin{figure}[tb]
\includegraphics{figs/unnamed-chunk-8-1} \caption[Proportion of thematic responses by country]{Proportion of thematic responses by country. Only US-China responding comparison shows a siginficant difference. We could not extend this to US-Vietnam responding comparison.}\label{fig:unnamed-chunk-8}
\end{figure}
\end{CodeChunk}

No effect of country on filler responding.

\hypertarget{does-lexical-statistics-for-fillers-predict-responding-in-the-corresponding-cultural-context}{%
\subsubsection{Does lexical statistics for fillers predict responding in
the corresponding cultural
context?}\label{does-lexical-statistics-for-fillers-predict-responding-in-the-corresponding-cultural-context}}

\hypertarget{raw-co-occurrences-1}{%
\paragraph{Raw co-occurrences}\label{raw-co-occurrences-1}}

Yes, corpus raw co-occurrences predicts responding for both US and
Vietnamese. \emph{need to discuss with Shan to incorporate Mandarin due
to a lot of empty counts}

\hypertarget{cosine-distance}{%
\paragraph{Cosine distance}\label{cosine-distance}}

Corpus cosine similarities also predict responding for all cultures.

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

In this paper, we consider whether statistics of the language
environment can account for cross-cultural differences in a classic
similarity judgment paradigm, as an alternative to the view that members
of different cultures vary in their conception of similarity.

We first tested the generality of a cultural account which holds that
people from Western and East Asian cultures tend to conceive of
similarity in more taxonomic and thematic ways, respectively, and
respond accordingly in categorization tasks such as ours. While we
managed to replicate the previously documented contrast between English
speakers in the US and Mandarin Chinese speakers from East Asia
(mainland China, Taiwan, Hong Kong, and Singapore), we do not extend
this contrast to our sample of Vietnamese speakers in Vietnam and
English speakers in the US. This finding suggests some limitations on
the generality of this cultural account.

We did find some signatures of language specificity in our analysis,
such as the large positive correlation between similarity judgments of
each country and the respective corpus statistics, and how each corpus
statistics are good predictors for corresponding country's similarity
judgments. However, this is potentially due to the high correlation
between corpus statistics of English, Vietnamese and Mandarin. We find
even stronger evidence for consistency across the three groups, with
substantive overlapping predictions across the corpus models, highly
similar responding across the experiments, and a correspondingly high
fit in cross-language comparisons between models and data.

There are some suggestions that the current approach can predict
triad-specific cross-cultural effects. First of all, an ANOVA model
comparison showed that adding a random effect term for varying slope by
country and varying intercept by triad to the model produces a
significant better fit than the identical model without this random
effect term included as a predictor (\(\chi^2\)(6) = 7481.6, p
\textless{} .001)

Our findings raise additional questions for future work: if not
differences in taxonomic vs.~thematic responding, then what differences
drive the relativity effects previous studies have observed? To what
extent are the relativity effects driven by language, and to what extent
by culture? Ji et al. (2004) established that culture-aligned
differences in this paradigm exist, even when the test language is held
constant, concluding that ``it is culture (independent of the testing
language) that led to different grouping styles'' in their study. Our
data provide a cautionary note to this conclusion, suggesting that
semantic representations in bilinguals (see Francis (2005) for a review)
may have the potential to provide an offline account for cross-context
differences in similarity judgments, independent of test language.
However, there are still many open questions for this account. How do
semantic associations guide categorization? Can they explain
taxonomic-thematic differences of the type reported by Ji et al. (2004)
and others? Can we provide a more specific computational account than
the simple frequency model tested here?

Despite these caveats, our findings here demonstrate the plausibility of
an alternative perspective on cross-cultural accounts of language,
thought, and similarity in the case of taxonomic and thematic reasoning:
that it may be the input to similarity judgments, rather than the
evaluative process or the conceptualization of similarity that produces
variation in similarity reasoning across cultural and linguistic
contexts. We hope this work provides a foundation for further research
probing this question.

\newpage

\hypertarget{two-column-images}{%
\subsection{Two-column images}\label{two-column-images}}

You can read local images using png package for example and plot it like
a regular plot using grid.raster from the grid package. With this method
you have full control of the size of your image. \textbf{Note: Image
must be in .png file format for the readPNG function to work.}

You might want to display a wide figure across both columns. To do this,
you change the \texttt{fig.env} chunk option to \texttt{figure*}. To
align the image in the center of the page, set \texttt{fig.align} option
to \texttt{center}. To format the width of your caption text, you set
the \texttt{num.cols.cap} option to \texttt{2}.

\begin{CodeChunk}
\begin{figure*}[h]

{\centering \includegraphics{figs/2-col-image-1}

}

\caption[This image spans both columns]{This image spans both columns. And the caption text is limited to 0.8 of the width of the document.}\label{fig:2-col-image}
\end{figure*}
\end{CodeChunk}

\hypertarget{one-column-images}{%
\subsection{One-column images}\label{one-column-images}}

Single column is the default option, but if you want set it explicitly,
set \texttt{fig.env} to \texttt{figure}. Notice that the
\texttt{num.cols} option for the caption width is set to \texttt{1}.

\begin{CodeChunk}
\begin{figure}[H]

{\centering \includegraphics{figs/image-1}

}

\caption[One column image]{One column image.}\label{fig:image}
\end{figure}
\end{CodeChunk}

\hypertarget{r-plots}{%
\subsection{R Plots}\label{r-plots}}

You can use R chunks directly to plot graphs. And you can use latex
floats in the fig.pos chunk option to have more control over the
location of your plot on the page. For more information on latex
placement specifiers see
\textbf{\href{https://en.wikibooks.org/wiki/LaTeX/Floats,_Figures_and_Captions}{here}}

\begin{CodeChunk}
\begin{figure}[H]

{\centering \includegraphics{figs/plot-1}

}

\caption[R plot]{R plot}\label{fig:plot}
\end{figure}
\end{CodeChunk}

\hypertarget{tables}{%
\subsection{Tables}\label{tables}}

Number tables consecutively; place the table number and title (in 10
point) above the table with one line space above the caption and one
line space below it, as in Table 1. You may float tables to the top or
bottom of a column, set wide tables across both columns.

You can use the xtable function in the xtable package.

\begin{table}[H]
\centering
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std. Error & t value & Pr($>$$|$t$|$) \\ 
  \hline
(Intercept) & 0.02 & 0.10 & 0.2 & 0.86 \\ 
  x & 2.04 & 0.11 & 19.1 & 0.00 \\ 
   \hline
\end{tabular}
\caption{This table prints across one column.} 
\end{table}

\hypertarget{acknowledgements}{%
\section{Acknowledgements}\label{acknowledgements}}

Place acknowledgments (including funding information) in a section at
the end of the paper.

\hypertarget{references}{%
\section{References}\label{references}}

\setlength{\parindent}{-0.1in} 
\setlength{\leftskip}{0.125in}

\noindent

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-Chiu1972}{}}%
Chiu, L. (1972). A cross-cultural comparison of cognitive styles in
chinese and american children. \emph{International Journal of
Psychology}, \emph{7}(4), 235--242.
http://doi.org/\href{https://doi.org/doi:10.1080/00207597208246604}{doi:10.1080/00207597208246604}

\leavevmode\vadjust pre{\hypertarget{ref-Choi1999}{}}%
Choi, I., Nisbett, R. E., \& Norenzayan, A. (1999). Causal attribution
across cultures: Variation and universality. \emph{International Journal
of Psychology}, \emph{125}(1), 47--63.
http://doi.org/\href{https://doi.org/doi:10.1037/0033-2909.125.1.47}{doi:10.1037/0033-2909.125.1.47}

\leavevmode\vadjust pre{\hypertarget{ref-Chua2005}{}}%
Chua, H. F., Boland, J. E., \& Nisbett, R. E. (2005). Cultural variation
in eye movements during scene perception. \emph{Proceedings of the
National Academy of Sciences}, \emph{102}(35), 12629--12633.
http://doi.org/\href{https://doi.org/10.1073/pnas.0506162102}{10.1073/pnas.0506162102}

\leavevmode\vadjust pre{\hypertarget{ref-COCA}{}}%
Davies, M. (2008-2008-). The corpus of contemporary american english
(COCA). Retrieved from \url{https://www.english-corpora.org/coca/}

\leavevmode\vadjust pre{\hypertarget{ref-Francis2005}{}}%
Francis, W. S. (2005). \emph{Bilingual semantic and conceptual
representation}. Oxford University Press.

\leavevmode\vadjust pre{\hypertarget{ref-VICorpus}{}}%
Goldhahn, D., Eckart, T., \& Quasthoff, U. (2012). Building large
monolingual dictionaries at the leipzig corpora collection: From 100 to
200 languages. Retrieved from
\url{https://wortschatz.uni-leipzig.de/en/download/vietnamese}

\leavevmode\vadjust pre{\hypertarget{ref-Grave2018}{}}%
Grave, E., Bojanowski, P., Gupta, P., Joulin, A., \& Mikolov, T. (2018).
Learning word vectors for 157 languages. In \emph{Proceedings of the
international conference on language resources and evaluation (LREC
2018)}.

\leavevmode\vadjust pre{\hypertarget{ref-Griffiths2007}{}}%
Griffiths, T. L., Steyvers, M., \& Tenenbaum, J. B. (2007). Topics in
semantic representation. \emph{Psychological Review}, \emph{114}(2),
211--244.
http://doi.org/\href{https://doi.org/doi:10.1037/0033-295x.114.2.211}{doi:10.1037/0033-295x.114.2.211}

\leavevmode\vadjust pre{\hypertarget{ref-Hui2002}{}}%
Hui, W. (2002). Modernity and 'asia' in the study of chinese history. In
E. Fuchs \& B. Stuchteyi (Eds.), \emph{Across cultural borders:
Historiography in global perspective}. Rowman \& Littlefield.

\leavevmode\vadjust pre{\hypertarget{ref-Jatnika2019}{}}%
Jatnika, D., Bijaksana, M. A., \& Suryani, A. A. (2019). Word2Vec model
analysis for semantic similarities in english words. \emph{Procedia
Computer Science}, \emph{157}, 160--167.
http://doi.org/\url{https://doi.org/10.1016/j.procs.2019.08.153}

\leavevmode\vadjust pre{\hypertarget{ref-Ji2000}{}}%
Ji, L., Peng, K., \& Nisbett, R. E. (2000). Culture, control, and
perception of relationships in the environment. \emph{Journal of
Personality and Social Psychology}, \emph{78}(5), 943--955.
http://doi.org/\href{https://doi.org/doi:10.1037/0022-3514.78.5.943}{doi:10.1037/0022-3514.78.5.943}

\leavevmode\vadjust pre{\hypertarget{ref-Ji2004}{}}%
Ji, L., Zhang, Z., \& Nisbett, R. E. (2004). Is it culture or is it
language? Examination of language effects in cross-cultural research on
categorization. \emph{Journal of Personality and Social Psychology},
\emph{87}(1), 57--65.
http://doi.org/\href{https://doi.org/doi:10.1037/0022-3514.87.1.57}{doi:10.1037/0022-3514.87.1.57}

\leavevmode\vadjust pre{\hypertarget{ref-Liu2019}{}}%
Liu, N., Feng, C., Wu, S., Chan, A., \& Fulton, J. (2019). Automate RFP
response generation process using FastText word embeddings and soft
cosine measure. In \emph{Proceedings of the 2019 international
conference on artificial intelligence and computer science} (pp.
12--17).
http://doi.org/\href{https://doi.org/10.1145/3349341.3349362}{10.1145/3349341.3349362}

\leavevmode\vadjust pre{\hypertarget{ref-Markman1984}{}}%
Markman, E. M., \& Hutchinson, J. E. (1984). Children's sensitivity to
constraints on word meaning: Taxonomic versus thematic relations.
\emph{Cognitive Psychology}, \emph{16}(1), 1--27.
http://doi.org/\href{https://doi.org/doi:10.1016/0010-0285(84)90002-1}{doi:10.1016/0010-0285(84)90002-1}

\leavevmode\vadjust pre{\hypertarget{ref-Masuda2001}{}}%
Masuda, T., \& Nisbett, R. E. (2001). Attending holistically versus
analytically: Comparing the context sensitivity of japanese and
americans. \emph{Journal of Personality and Social Psychology},
\emph{81}(5), 922--934.
http://doi.org/\href{https://doi.org/doi:10.1037/0022-3514.81.5.922}{doi:10.1037/0022-3514.81.5.922}

\leavevmode\vadjust pre{\hypertarget{ref-Mikolov2018}{}}%
Mikolov, T., Grave, E., Bojanowski, P., Puhrsch, C., \& Joulin, A.
(2018). Advances in pre-training distributed word representations. In
\emph{Proceedings of the international conference on language resources
and evaluation (LREC 2018)}.

\leavevmode\vadjust pre{\hypertarget{ref-Nisbett2003}{}}%
Nisbett, R. E. (2003). \emph{The geography of thought: How asians and
westerners think differently \ldots{} and why}. New York: Free Press.

\leavevmode\vadjust pre{\hypertarget{ref-Norenzayan2002}{}}%
Norenzayan, A., Smith, E. E., Kim, B. J., \& Nisbett, R. E. (2002).
Cultural preferences for formal versus intuitive reasoning.
\emph{Cognitive Science}, \emph{26}(5), 653--684.
http://doi.org/\href{https://doi.org/doi:10.1207/s15516709cog2605_4}{doi:10.1207/s15516709cog2605\_4}

\leavevmode\vadjust pre{\hypertarget{ref-Rohde2006}{}}%
Rohde, D. L., Gonnerman, L. M., \& Plaut, D. C. (2006). An improved
model of semantic similarity based on lexical co‐occurrence.
\emph{Communications of the ACM}, \emph{8}, 627--633.

\leavevmode\vadjust pre{\hypertarget{ref-Thompson2020}{}}%
Thompson, R., B., \& Lupyan, G. (2020). Cultural influences on word
meanings revealed through large-scale semantic alignment. \emph{Nature
Human Behaviour Volume}, \emph{4}, 1029--1038.
http://doi.org/\url{https://doi.org/10.1038/s41562-020-0924-8}

\leavevmode\vadjust pre{\hypertarget{ref-2020SciPy}{}}%
Virtanen, P., Gommers, R., Oliphant, T. E., Haberland, M., Reddy, T.,
Cournapeau, D., \ldots{} SciPy 1.0 Contributors. (2020). {{SciPy} 1.0:
Fundamental Algorithms for Scientific Computing in Python}. \emph{Nature
Methods}, \emph{17}, 261--272.
http://doi.org/\href{https://doi.org/10.1038/s41592-019-0686-2}{10.1038/s41592-019-0686-2}

\end{CSLReferences}

\bibliographystyle{apacite}

\end{document}

### 2023-01-01 code/4_paper/manuscript/manuscript.Rmd
fixed manuscript

@@
 
-```{r add cosine linguistic model to Ji et al., include=FALSE, cache = T}
-fit.country = glmer(responses_theme ~ country + (1 | subject) + (1 | triad), 
-                           data = df %>% filter(country != "Vietnam"), 
-                           family = "binomial")
-
-fit.country_corpus = glmer(responses_theme ~ country + theme_cosine_prop_E + theme_cosine_prop_M + (1 | subject) + (1 | triad), 
-                           data = df %>% filter(country != "Vietnam"), 
-                           family = "binomial")
-
-fit.add_corpus <- anova(fit.country, fit.country_corpus, type = 3)
-
-```
-_TODO: should we take this out?__
-We carried out an ANOVA model comparison to compare our approach with previous studies that did not include corpus information.
-Because @Ji2004 only compared US and China participants, we filtered our data to only include responding data from these two countries.
-Our approach would be to compare a model that only includes country (US or China) as a fixed effect with one that also includes English and Chinese corpus data.
-Our previous model with an intercept per subject and one per triad, as well as by-triad random slopes for country to account for variation in the country effect across triads fails to converge with the more complex model, so we include a simpler random effect structure with an intercept per subject and one per triad in both the basic and more complex model.
-We compare this model with an identical model but including Chinese and English corpus cosine distance proportion prediction.
-We found that adding English and Chinese corpus data produces a significantly better fit than the identical model without English and Chinese corpus data as predictors ($\chi^2$(`r fit.add_corpus["fit.country_corpus", "Df"]`) = `r round(fit.add_corpus["fit.country_corpus", "Chisq"], 2)`, p = < .001.
-This suggests that including corpus data would better model the cross-cultural differences in similarity judgment in this study as well as similar studies.
-
 #### Cosine distances of fastText word vectors
@@
 
-```{r add linguistic model to Ji et al., include=FALSE}
+```{r add linguistic model to Ji et al., include=FALSE, eval = F}
+# this is probably similar to Q3
 fit.country = glmer(responses_theme ~ country + (1 | subject) + (1 | triad), 
@@
 fit.language_cos = glmer(responses_theme ~ theme_cosine_prop_corr_lang + (1 | subject) + (1 | triad), 
-          data = df %>% filter(!(triad %in% triads_omit)),  
+          data = df,  
           family="binomial")
@@
 fit.country_language_cos= glmer(responses_theme ~ theme_cosine_prop_corr_lang * country + (1 | subject) + (1 | triad), 
-          data = df %>% filter(!(triad %in% triads_omit)),  
+          data = df,  
           family="binomial")

### 2023-01-13 code/4_paper/manuscript/manuscript.Rmd
added ICC

@@
 library("effsize")
+library("irr")
 
@@
 \noindent
+
+# Appendix
+## 1. ICC of item variability and participant variability 
+```{r item variability, include = F}
+df.icc_item_full <- df_main_analysis %>% 
+  select(subject, triad, responses_theme) %>%
+  pivot_wider(names_from = subject, values_from = responses_theme)
+
+icc_item_full <- icc(df.icc_item_full %>% select(-triad), model = "twoway", type = "consistency", unit = "single")$value
+
+df.icc_item <- df_main_analysis %>% 
+  select(subject, triad, responses_theme, country) %>%
+  pivot_wider(names_from = subject, values_from = responses_theme)
+
+#unsure if type should be consistency or agreement
+df.icc_item_US <- df.icc_item %>% 
+  filter(country == "US") %>%
+  select_if(~ !any(is.na(.))) %>%
+  select(-country, -triad)
+
+icc_item_US <- icc(df.icc_item_US, model = "twoway", type = "consistency", unit = "single")$value
+
+#unsure if type should be consistency or agreement
+df.icc_item_VN <- df.icc_item %>% 
+  filter(country == "Vietnam") %>%
+  select_if(~ !any(is.na(.))) %>%
+  select(-country, -triad)
+
+icc_item_VN <- icc(df.icc_item_VN, model = "twoway", type = "consistency", unit = "single")$value
+
+#unsure if type should be consistency or agreement
+df.icc_item_CN <- df.icc_item %>% 
+  filter(country == "China") %>%
+  select_if(~ !any(is.na(.))) %>%
+  select(-country, -triad)
+
+icc_item_CN <- icc(df.icc_item_CN, model = "twoway", type = "consistency", unit = "single")$value
+```
+
+```{r participant variability, include = F}
+df.icc_ppt_full <- df_main_analysis %>% 
+  select(subject, triad, responses_theme) %>%
+  pivot_wider(names_from = triad, values_from = responses_theme)
+
+icc_ppt_full <- icc(df.icc_ppt_full %>% select(-subject), model = "twoway", type = "consistency", unit = "single")$value
+
+df.icc_ppt <- df_main_analysis %>% 
+  select(subject, triad, responses_theme, country) %>%
+  pivot_wider(names_from = triad, values_from = responses_theme)
+
+#unsure if type should be consistency or agreement
+df.icc_ppt_US <- df.icc_ppt %>% 
+  filter(country == "US") %>%
+  select(-country, -subject)
+
+icc_ppt_US <- icc(df.icc_ppt_US, model = "twoway", type = "consistency", unit = "single")$value
+
+#unsure if type should be consistency or agreement
+df.icc_ppt_VN <- df.icc_ppt %>% 
+  filter(country == "Vietnam") %>%
+  select(-country, -subject)
+
+icc_ppt_VN <- icc(df.icc_ppt_VN, model = "twoway", type = "consistency", unit = "single")$value
+
+#unsure if type should be consistency or agreement
+df.icc_ppt_CN <- df.icc_ppt %>% 
+  filter(country == "China") %>%
+  select(-country, -subject)
+
+icc_ppt_CN <- icc(df.icc_ppt_CN, model = "twoway", type = "consistency", unit = "single")$value
+```
+
+```{r}
+icc_tbl <- data.frame(
+  Country = c("US", "China", "Vietnam", "All"),
+  Item_Variability_ICC = c(icc_item_US, icc_item_CN, icc_item_VN, icc_item_full), 
+  Ppt_Variabiity_ICC = c(icc_ppt_US, icc_ppt_CN, icc_ppt_VN, icc_ppt_full)
+)
+kable(icc_tbl)
+```
+
+## 2. CCRR agreement
+```{r load CCRR data}
+df.ccrr <- read.csv("../../../data/replication/ccrr.csv") %>%
+  filter(task_name == "TD") %>%
+  select(subject, trial_info, resp) %>%
+  rename(triad = trial_info) %>%
+  mutate(response_theme = ifelse(resp == "FALSE", 1, 0)) %>%
+  select(subject, triad, response_theme) %>%
+  pivot_wider(names_from = subject, values_from = response_theme) %>%
+  select(-triad)
+
+df.ccrr %>%
+    dplyr::group_by(triad, subject) %>%
+    dplyr::summarise(n = dplyr::n(), .groups = "drop") %>%
+    dplyr::filter(n > 1L)
+
+icc(df.ccrr, model = "twoway", type = "consistency", unit = "single")
+```

### 2023-01-19 code/4_paper/manuscript/manuscript.Rmd
updated manuscript to add ICC

@@
 library("irr")
+require(agreement)
 
@@
 ## 1. ICC of item variability and participant variability
+
+```{r}
+US_agr <- agreement::dim_icc(df_main_analysis %>% filter(country == "US"),
+                             model = "2A",
+                             type = "agreement",
+                             unit = "average",
+                             object = triad,
+                             rater = subject,
+                             score = responses_theme,
+                             bootstrap = 0)
+
+CN_agr <- agreement::dim_icc(df_main_analysis %>% filter(country == "China"),
+                             model = "2A",
+                             type = "agreement",
+                             unit = "average",
+                             object = triad,
+                             rater = subject,
+                             score = responses_theme,
+                             bootstrap = 0)
+
+VN_agr <- agreement::dim_icc(df_main_analysis %>% filter(country == "Vietnam"),
+                             model = "2A",
+                             type = "agreement",
+                             unit = "average",
+                             object = triad,
+                             rater = subject,
+                             score = responses_theme,
+                             bootstrap = 0)
+
+iccs <- tibble(Sample = c("US","China", "Vietnam"),
+               `Intra-rater ICC` = c(US_agr$Intra_ICC,
+                                     CN_agr$Intra_ICC,
+                                     VN_agr$Intra_ICC),
+               `Inter-rater ICC` = c(US_agr$Inter_ICC,
+                                     CN_agr$Inter_ICC,
+                                     VN_agr$Inter_ICC))
+```
+
 ```{r item variability, include = F}
@@
 
-icc_item_US <- icc(df.icc_item_US, model = "twoway", type = "consistency", unit = "single")$value
+icc_item_US <- icc(df.icc_item_US, model = "twoway", type = "agreement", unit = "average")$value
 

### 2023-01-19 code/4_paper/manuscript/manuscript.Rmd
shorter intro
shortened/reorganized intro

--- 2023-01-13 code/4_paper/manuscript/manuscript.Rmd
@@
 Speakers of different languages judge similarity in this context differently, but why?
-One possibility is that cultures co-varying with these languages induce variation in conceptualizations of similarity.
-Specifically, East Asian cultures may promote reasoning about thematic similarity, by which cow and grass are more related whereas Western cultures may bias similarity judgements toward taxonomic relations, like cow-chicken.
+One possibility is that cultures co-varying with these languages induce differences in conceptualizations of similarity.
+Specifically, East Asian cultures may promote reasoning about thematic similarity, by which cow and grass are more related, whereas Western cultures may bias judgements toward taxonomic relations, like cow-chicken.
 This difference in notions of similarity is the consensus interpretation for cross-cultural variation in this paradigm.
-We consider, and provide evidence for, an alternative possibility, by which notions of similarity are equivalent across contexts, but the statistics of the environment vary.
-On this account, similarity judgements are guided by co-occurrence in experience, and observing or hearing about cows and grass or cows and chickens more often could induce preferences for the relevant grouping, and account for apparent differences in notions of similarity across contexts.
+We consider, and provide evidence for, an alternative possibility, by which notions of similarity are similar across contexts, but the statistics of the environment vary.
+On this account, similarity judgements are guided by co-occurrence in experience, and observing or hearing about cows and grass or cows and chickens more often could induce preferences for these groupings, and account in part for apparent differences in notions of similarity across contexts.
 
@@
 In contrast, thematic categorization is based on causal, spatial, and temporal relationships among objects [@Markman1984].
-To illustrate this point, if a participant is given the words “chicken” and “grass”, and asked which of those words are more closely related to the word “cow”, the pairing “chicken” - “cow” indicates a taxonomic match, whereas “grass” - “cow” indicates a thematic match.
-
-@Ji2004 found that preferences for taxonomic and thematic matches differ across cultures, even when controlling for testing language and fluency.
-Specifically, Chinese participants made more thematic matches than taxonomic, while the converse was true for European Americans.
-This difference held even for Chinese participants tested in English (rather than Mandarin), suggesting that culture has an effect on the categorization strategy independent of the test language.
-However, the study also found an effect of language within Chinese participants from mainland China (when tested both in China and in the US): their preference for thematic categorization was significantly lower when tested in English compared to Mandarin Chinese.
-This suggests that test language also influences categorization strategies.
+
+## Cross-cultural variation in similarity
+Preferences for taxonomic and thematic similarity vary across cultures.
+@Chiu1972 found that Chinese children (9-10 years old) are more likely to choose thematic matches in a picture triad task (shown, e.g., images of an ant, a bee, and honey) than their American counterparts.
+These cross-cultural differences are also observed in novel object categorization, with Chinese participants preferring to group by family resemblance across multiple features and Americans preferring a single-feature rule [@Norenzayan2002].
+<!-- Because differences in similarity preference persist with novel stimuli (as opposed to familiar items), this suggests that participants from different cultural backgrounds use different reasoning strategies when making similarity judgments.
+-->
+The authors link these differences to tendencies toward analytic processing in Western cultures, which emphasizes objects and their properties, and holistic processing in East Asian cultures, which emphasizes relationships between objects and their context (see also @Nisbett2003).
+In related work, East Asian participants show a higher level of sensitivity to context than their Western counterparts when reproducing drawings from memory [@Ji2000]; visually exploring naturalistic scenes [@Chua2005]; describing scenes [@Masuda2001]; and in explaining the causes of ambiguous behaviors [@Choi1999].
+
+@Ji2004 asked whether differences in analytic and holistic processing <!--they use that language, right?--> are driven by language, culture, or a combination of these.
+They presented Chinese and European American adults with a word triad task, and found a preference for thematic matching among Chinese participants compared to European Americans.
+They found that test language contributed to this difference, but did not fully explain it: Chinese participants showed a stronger thematic preference when tested in Mandarin, but still showed a thematic preference when tested in English.
 Ji et al.
-characterize these results as demonstrating that culture (independent of language) leads to different styles of reasoning about similarity, whereas language serves as a “tuning” mechanism operating within a culturally-specific style, by activating representations corresponding to the language being used.
-
-## Cross-cultural variation in similarity
-The view that culture drives differences in categorization style has been one favored by other non-linguistic studies that use taxonomic vs thematic categorization to probe similarity judgment.
-When shown pictorial triads that represent words (i.e.
-pictures of an ant, a bee, and honey), Chinese children (9-10 years old) scored higher on thematic categorization compared to American children of the same age range, and vice versa for taxonomic categorization [@Chiu1972].
-These cross-cultural differences in similarity judgment persist in novel object categorization, with Chinese participants preferring to group by family resemblance across multiple features and Americans preferring a single-feature rule [@Norenzayan2002].
-Since differences in categorization style persist with novel stimuli (as opposed to previously seen words or pictures of concepts), this suggests that participants from different cultural backgrounds are utilizing different reasoning strategies when making similarity judgments.
-The authors attribute these differences to tendencies toward analytic processing in Western cultures, which emphasizes objects and their properties and holistic processing in East Asian cultures, which emphasizes relationships between objects and their context.
-According to this framework, East Asians attend more to relationships between objects and context and reason more holistically, whereas Westerners attend more to objects and their properties, and reason analytically (ibid, see also @Nisbett2003).
-In related work, East Asian participants show a higher level of sensitivity to context than their Western counterparts when reproducing drawings from memory [@Ji2000]; visually exploring naturalistic scenes [@Chua2005]; describing scenes [@Masuda2001]; and in explaining the causes of ambiguous behaviors [@Choi1999].
-These cross-cultural differences in attention and analytic vs holistic processing are seen to map onto the cross-cultural differences in similarity judgment: because East Asian participants attend more to the context between objects and reason more holistically, it stands to reason that they would consider words that appear in the same context (i.e.
-thematically similar) to be more similar than taxonomically-similar words.
-
-This view ascribes cross-cultural differences in similarity judgment tasks to variation in the conceptualization of similarity itself.
+conclude that culture (independent of language) leads to different styles of reasoning about similarity, whereas language serves as a “tuning” mechanism operating within a culturally-specific style, by activating representations corresponding to the language being used.^[But note that this work did not include a manipulation to prevent participants from engaging in e.g., covert naming in a language other than the test language.]
+
+This view ascribes cross-cultural differences in similarity judgment to variation in the conceptualization of similarity itself.
 Alternatively, these judgments could be shaped by cross-cultural differences in the statistics of the environment, and accordingly the content of everyday experiences.
 Perhaps when confronted with the triad task, participants from all cultures follow the same process for reasoning about similarity, but rely on language or culture-specific inputs to this process.
-For example, it may be that Vietnamese participants are more likely to have knowledge of farming practices than Americans, and may associate cows and grass more strongly (as grass is the typical feed for cows in the small-scale family farming contexts common in Vietnam).
-Americans, on the other hand, may have strong associations between cows and chickens as a result of encountering them together in children’s books or petting zoo contexts.
-If we observe a difference in categorization between, say Vietnamese and US participants, it could be that members of both groups use the same procedure (considering similarity that is influenced by both taxonomic and thematic relations), but the inputs to this procedure differ between cultures, with Vietnamese participants exposed to more instances of “cow” and “grass” occurring together, compared to US participants.
-
-## Language as a proxy of variation in experience
+<!--For example, it may be that Vietnamese participants are more likely to have knowledge of farming practices than Americans, and may associate cows and grass more strongly (as grass is the typical feed for cows in the small-scale family farming contexts common in Vietnam).
+Americans, on the other hand, may have strong associations between cows and chickens as a result of encountering them together in children’s books or petting zoo contexts.--> If we observe a difference in categorization between East Asian and Western participants, it could be that members of both groups use the same procedure (considering similarity that is influenced by both taxonomic and thematic relations), but the inputs to this procedure differ between cultures, with East Asian participants exposed to more instances of thematic similarity than their Western counterparts.
+
+## Estimating variation in experience
 While co-occurrences in experience are difficult to measure, co-occurrence in language can provide a rough proxy--and indeed, language may afford many of the “experiences” that people have with infrequently encountered items, like cows or helicopters.
@@
 This is a generalizing assumption, and while no linguistic corpus can be expected to fully capture a culture, using this proxy as a model of culture provides a conservative test of the hypothesis that differences in the input, rather than the process, of reasoning produces cultural variation in this task.
-This means that if such a model does work -- if linguistic co-occurrence can predict cultural variation in this similarity task without building differences in the decision process into the model -- it is relatively strong evidence that language alone (perhaps as a more easily observed source of information on broader cultural and ecological variation) may account for these cross-cultural differences in reasoning.[^footnote]
-
-Indeed, previous work suggests that using lexical co-occurrence as a proxy can be useful in thinking about similarity judgments.
-Natural language processing tasks have found that lexical co-occurrence is a good predictor for performance in similarity judgment tasks.
+This means that if such a model does work -- if linguistic co-occurrence can predict cultural variation in this similarity task without building differences in the decision process into the model -- it is relatively strong evidence that language alone (perhaps as a more easily observed source of information on broader cultural and ecological variation) may account for these cross-cultural differences in reasoning.
+
+Indeed, previous work suggests that using lexical co-occurrence as a proxy can be useful in thinking about similarity reasoning.
+Natural language processing tasks have found that lexical co-occurrence is a good predictor for performance in similarity judgment.
 @Griffiths2007 showed that a model that takes word-document co-occurrence as input can be used to predict word association and the effects of semantic association on a variety of linguistic tasks.
-Additionally, lexical semantic models that are constructed using lexical co-occurrence (as opposed to annotated relations) have been shown to perform well on predicting human judgments about similarity between word pairs that are either thematically or taxonomically related [@Rohde2006].
-
-Our current study will be using 2 measures of lexical co-occurrence: 1) raw lexical co-occurrences and 2) cosined distances of fastText word vectors.
+Additionally, lexical semantic models that are constructed using lexical co-occurrence (as opposed to annotated relations) have been shown to perform well on predicting human judgments about similarity between word pairs that are thematically or taxonomically related [@Rohde2006].
+
+Our study uses two measures of lexical co-occurrence: 1) raw lexical co-occurrence and 2) cosined distances of fastText word vectors.
 fastText is a system that uses lexical co-occurrence information to generate a vector representing each word in its lexicon [@Mikolov2018].
+
+<!-- MOVE TO METHODS?
 fastText uses a continuous bag-of-words model, which takes into account a symmetric window of words surrounding the word in question and maximizes the log-likelihood of the probability of the word given its context.
@@
 However, models that use only lexical co-occurrence information (with or without a simple position weight system that gives more weight to words that are closer to the word in question) also perform well in similarity prediction tasks.
-For this study, due to the lack of large cleaned corpora for Mandarin and Vietnamese, we are leveraging fastText pre-trained models on the languages we are interested in @Grave2018.
-
-Systems like fastText and word2vec have been demonstrated to be good predictors for similarity judgments.
+For this study, due to the lack of large cleaned corpora for Mandarin and Vietnamese, we leverage fastText pre-trained models on the languages we are interested in @Grave2018.-->
+
+<!-- condense to 2 sentences --> Systems like fastText and word2vec have been demonstrated to be good predictors for similarity judgments.
 @Liu2019 showed that fastText performed well as the data for a system matching responses in a knowledge base by how similar they are to a customer’s query.
@@
 <!-- Additionally, outside of language, cross-cultural differences could come from a couple different mechanisms:  -->
-@Ji2004 suggest that the notion of similarity is what varies across cultural groups, but it is quite possible that similarity is regarded in the same way and it is actually the input to this similarity judgment that varies across culture contexts.
-It might be possible to gain traction on possible mechanisms by examining whether variation in similarity judgments co-varies with environmental statistics that differ across the cultural and linguistic contexts.
+@Ji2004 suggest that the notion of similarity is what varies across cultural groups, but it is possible that similarity is regarded in the same way and it is actually the input to this similarity judgment that varies across cultural contexts.
+It may be possible to gain traction on potential mechanisms by examining whether variation in similarity judgments co-vary with environmental statistics that differ across cultural and linguistic contexts.
 
@@
 Meanwhile, if we do see variation in responding trial-to-trial that tracks with lexical co-occurrence statistics (as a rough proxy combining both linguistic and cultural context), this suggests that cross-cultural notions of similarity might be similar, and it is environmental statistics that guide the differences in similarity judgments.
+
 To preview our results, we find that, while we do not see overall group differences (between the East Asian contexts and the US) in similarity, we do find language-specific co-occurrence can indeed explain cross-context differences in similarity judgments.
 In contrast to previous accounts, by which culture induces differing conceptions of similarity (varying between taxonomic and thematic), these findings provide an alternative, and more specific, account by which language may explain these cross-cultural differences without invoking variation in notions of similarity.
+
+There are several important limitations of our approach.
+While we discuss cross-cultural variability at the level of countries or larger world areas, these are not cultural monoliths.
+For convenience, we operationalize culture at the level of country, based on where participants were raised.
+It is an open question whether performance in our participant populations (of relatively young and well-educated adults) is representative of the broader country.
+This is especially true for societies with substantial ethnic and cultural variation such as the US.
+We expect that our data is likely to underestimate variation both within and between the countries we sample from.
+
+Language, culture, cognition, and individual experiences are intertwined in complex causal relationships: cultural features (farming) can lead to differences in individuals’ experiences (seeing cows and grass) and in turn these can influence language (talking more about cows and grass).
+But cultural features (a thematic orientation) could also more directly cause individuals to talk differently about the same experiences (mentioning what cows eat rather than what other animals cows are like).
+In this study, we measure language and its relation to cross-cultural differences in categorization, but these relations test only the plausibility of a language-based account; they cannot establish the direction of causality.
 
@@
 
-[^footnote]:While we discuss cross-cultural variability at the level of countries or larger world areas, these are not cultural monoliths.
-For convenience, we operationalize culture at the level of country, based on where participants were raised.
-It is an open question whether performance in our participant populations (of relatively young and well-educated adults) is representative of the broader country.
-This is especially true for societies with substantial ethnic and cultural variation such as the US.
-We expect that our data is likely to underestimate variation both within and between the countries we sample from.
-
 \newpage

### 2023-01-19 code/1_exclusions/1_exclusionsUS.Rmd
small changes based on Mike's feedback

--- 2022-12-14 code/1_exclusions/1_exclusionsUS.Rmd
@@
 ```{r}
+
+df.demog_metadata <- data.frame(ppts_finished = c(length(unique(df.ppts_finished_E$subject))),
+                      ppts_after_att_check_excl = c(length(unique(df.ppts_att_E$subject))),
+                      ppts_non_native_speaker = c(length(ppts_non_native_lang_E)), 
+                      ppts_vi_speaker_E = c(length(ppts_vi_speaker_E)), 
+                      ppts_zh_speaker_E = c(length(ppts_zh_speaker_E)), 
+                      ppts_lived_abroad_E = c(length(ppts_lived_abroad_E)), 
+                      ppts_oversea_exp_E = c(length(ppts_oversea_exp_E)),
+
+                      ppts_after_demog_excl = c(length(unique(df.resp_E$subject))))
+colnames(df.demog_metadata) <- c("Participants Finished", 
+                                 "Participants ")
+```
+
+```{r}
 write.csv(df.resp_E, "../../data/responding/dataUS_excl.csv")
+write.csv(df.demog_metadata, "../../data/responding/dataUS_excl_metadata.csv")
 ```

### 2023-01-19 code/4_paper/manuscript/manuscript.Rmd
small changes based on Mike's feedback

--- 2023-01-19 code/4_paper/manuscript/manuscript.Rmd
@@
 One possibility is that cultures co-varying with these languages induce variation in conceptualizations of similarity.
-Specifically, East Asian cultures may promote reasoning about thematic similarity, by which cow and grass are more related whereas Western cultures may bias similarity judgements toward taxonomic relations, like cow-chicken.
+Specifically, East Asian cultures may promote reasoning about thematic similarity, by which cow and grass are more related, whereas Western cultures may bias similarity judgements toward taxonomic relations, like cow-chicken.
 This difference in notions of similarity is the consensus interpretation for cross-cultural variation in this paradigm.
@@
 This is a generalizing assumption, and while no linguistic corpus can be expected to fully capture a culture, using this proxy as a model of culture provides a conservative test of the hypothesis that differences in the input, rather than the process, of reasoning produces cultural variation in this task.
-This means that if such a model does work -- if linguistic co-occurrence can predict cultural variation in this similarity task without building differences in the decision process into the model -- it is relatively strong evidence that language alone (perhaps as a more easily observed source of information on broader cultural and ecological variation) may account for these cross-cultural differences in reasoning.[^footnote]
+This means that if such a model does work -- if linguistic co-occurrence can predict cultural variation in this similarity task without building differences in the decision process into the model -- it is relatively strong evidence that language alone (perhaps as a more easily observed source of information on broader cultural and ecological variation) may account for these cross-cultural differences in reasoning.
+
+While we discuss cross-cultural variability at the level of countries or larger world areas, these are not cultural monoliths.
+For convenience, we operationalize culture at the level of country, based on where participants were raised.
+It is an open question whether performance in our participant populations (of relatively young and well-educated adults) is representative of the broader country.
+This is especially true for societies with substantial ethnic and cultural variation such as the US.
+We expect that our data is likely to underestimate variation both within and between the countries we sample from.
 
@@
 <!-- Additionally, outside of language, cross-cultural differences could come from a couple different mechanisms:  -->
-@Ji2004 suggest that the notion of similarity is what varies across cultural groups, but it is quite possible that similarity is regarded in the same way and it is actually the input to this similarity judgment that varies across culture contexts.
-It might be possible to gain traction on possible mechanisms by examining whether variation in similarity judgments co-varies with environmental statistics that differ across the cultural and linguistic contexts.
-
 In this study, we ask whether variation in lexical co-occurrence can account for the cross-context (culture and language) differences observed in how people evaluate similarity.
@@
 df <- read.csv("../../../data/data_USCNVN_ENZHVI.csv")
+#df <- read.csv("../../../data/data_USCNVN_ENZHVI_0623.csv")
 
@@
   pull(x)
+
+head(df)
 ```
@@
 The Vietnam sample included `r df.excl_VN$ppts_after_demog_excl` participants (`r df.gender_V %>% filter(gender == "Nam") %>% pull(n)`M, `r df.gender_V %>% filter(gender == "Nữ") %>% pull(n)`F, `r df.gender_V %>% filter(gender == "Từ chối trả lời") %>% pull(n)` other), with mean age = `r round(df.age_V$mean_age, 2)` (SD = `r round(df.age_V$sd_age, 2)`) and median age = `r df.age_V$median_age`.
-The China sample included `r df.excl_CN$ppts_after_demog_excl` participants (`r df.gender_M %>% filter(gender == "男性") %>% pull(n)`M, `r df.gender_M %>% filter(gender == "女性") %>% pull(n)`F, `r df.gender_M %>% filter(gender == "拒绝回答") %>% pull(n)` other), with mean age = `r round(df.age_M$mean_age, 2)` (SD = `r round(df.age_M$sd_age, 2)`) and median age = `r df.age_M$median_age`.
+The China sample included `r df.excl_CN$ppts_after_demog_excl` participants (`r df.gender_M %>% filter(gender == "男性") %>% pull(n)`M, `r df.gender_M %>% filter(gender == "女性") %>% pull(n)`F, `r df.gender_M %>% filter(gender == "拒绝回答") %>% pull(n)` other), with mean age = `r round(df.age_M$mean_age, 2)` (SD = `r round(df.age_M$sd_age, 2)`) and median age = `r df.age_M$median_age`.[^footnote]
+
+\footnote \smallfont A table summarizing number of participants lost at each round of exclusions is included in the Appendix.
 
 Notably, we lost a majority of our Vietnam participants (more than 60%) in the attention check exclusion.
-One reason we suspect why this might have happened is because our Vietnam participants are less familiar with research surveys and attention check questions, and thus might have thought too much about the attention check questions.
-We carried out an exploratory analysis where we used a less stringent attention check exclusion (covered in the final part of the Results & Analysis section).
+One reason we suspect why this might have happened is because our Vietnam participants are less familiar with research surveys and attention check questions, and thus might have thought too much about the attention check questions.[^footnote]
+
+\footnote \smallfont We carried out an exploratory analysis where we used a less stringent attention check exclusion (covered in the final part of the Results & Analysis section).
 To preview our findings for this analysis, we did not find any difference in significant results when compared with the main analysis.
@@
 
-TODO; ADD INFO ABOUT MANDARIN CORPUS
+Mandarin co-occurrence was collected using the online interface of the Chinese Lexical Association Database (Lin et al, 2019).
+Mandarin also makes frequent use of compositional morphology.
+To match the Vietnamese corpus statistics, we included in our counts any instances of the target term or close semantic neighbors containing the same morpheme(s) following the rule described above.
+These semantic neighbors were either suggested to us by the online interface (which gave search suggestions for words beginning with the target term as we typed them in) or suggested by a native speaker of Mandarin conducting the co-occurrence count data collection.
+For example, in getting the collocates of the term "門" (door), we also included "門兒" (also door, but is returned as a different word).
+Compounds that do not meet this criteria were excluded from collocate counts.
+For example "門牙" (door.tooth) refers to the front tooth even though it includes the same character as the target word "門" (door), so was therefore excluded from our collocate counts for "door".
 
@@
 ```
-The group means of proportion of thematic response in mainland China is the highest (M = `r round((df.country_sum %>% filter(country == "China"))$mean_theme_resp_percent, 2)`, SD = `r round((df.country_sum %>% filter(country == "China"))$sd_theme_resp_percent, 2)`), followed by the groups means in Vietnam (M = `r round((df.country_sum %>% filter(country == "Vietnam"))$mean_theme_resp_percent, 2)`, SD = `r round((df.country_sum %>% filter(country == "Vietnam"))$sd_theme_resp_percent, 2)`), which is slightly higher than that of the US (M = `r round((df.country_sum %>% filter(country == "US"))$mean_theme_resp_percent, 2)`, SD = `r round((df.country_sum %>% filter(country == "US"))$sd_theme_resp_percent, 2)`).
-
-```{r echo=FALSE, warning=FALSE, cache = TRUE, fig.cap="Proportion of thematic responses by country.
-Only US-China responding comparison shows a siginficant difference.
-We could not extend this to US-Vietnam responding comparison."}
+The group means of proportion of thematic response in mainland China is the highest (M = `r round((df.country_sum %>% filter(country == "China"))$mean_theme_resp_percent, 2)`, SD = `r round((df.country_sum %>% filter(country == "China"))$sd_theme_resp_percent, 2)`), followed by the groups means in Vietnam (M = `r round((df.country_sum %>% filter(country == "Vietnam"))$mean_theme_resp_percent, 2)`, SD = `r round((df.country_sum %>% filter(country == "Vietnam"))$sd_theme_resp_percent, 2)`), which is slightly higher than that of the US (M = `r round((df.country_sum %>% filter(country == "US"))$mean_theme_resp_percent, 2)`, SD = `r round((df.country_sum %>% filter(country == "US"))$sd_theme_resp_percent, 2)`) (Fig 1).
+
+```{r echo=FALSE, warning=FALSE, cache = TRUE, fig.cap="Proportion of thematic responses by country."}
 
@@
   labs(y = "Proportion Thematic Chosen", 
-       x = "Country", 
-       color = "Country") + 
-  scale_color_manual(values=c("#D63230", "#1C77C3", "#F39237"))
-```
-
-```{r correlation of country response, cache = TRUE, echo=FALSE, warning=FALSE}
-#US-China, US-Vietnam, China-Vietnam
-df.triad_country <- df %>%
-  group_by(triad, country) %>%
-  summarize(emp_theme_prop = mean(responses_theme))
-
-df.triad_country <- pivot_wider(data = df.triad_country, 
-                                names_from = country, 
-                                values_from = emp_theme_prop)
-plotUSCN = ggplot(data = df.triad_country,
-                  mapping = aes(x = US, 
-                                y = China, 
-                                label = triad)) +
-   geom_text() + 
-   geom_smooth(method = "lm") +
-   labs(x = "Proportion Thematic Chosen (US)", 
-        y = "Proportion Thematic Chosen (China)") + 
-   xlim(0, 1) + 
-   ylim(0, 1) + 
-  theme(axis.title = element_text(size=rel(0.75)))
-
-plotUSVN = ggplot(data = df.triad_country,
-                  mapping = aes(x = US, 
-                                y = Vietnam, 
-                                label = triad)) +
-   geom_text() + 
-   geom_smooth(method = "lm") +
-   labs(x = "Proportion Thematic Chosen (US)", 
-        y = "Proportion Thematic Chosen (Vietnam)") + 
-   xlim(0, 1) + 
-   ylim(0, 1)  + 
-  theme(axis.title = element_text(size=rel(0.75)))
-
-plotCNVN = ggplot(data = df.triad_country,
-                  mapping = aes(x = Vietnam,
-                                y = China, 
-                                label = triad)) +
-   geom_text() + 
-   geom_smooth(method = "lm") +
-   labs(x = "Proportion Thematic Chosen (Vietnam)", 
-        y = "Proportion Thematic Chosen (China)") + 
-   xlim(0, 1) + 
-   ylim(0, 1)  + 
-  theme(axis.title = element_text(size=rel(0.75)))
-
-corr.USCN = apa_print(cor.test(df.triad_country$US, 
-                  df.triad_country$China, na.rm=T))
-
-corr.USVN = apa_print(cor.test(df.triad_country$US, 
-                  df.triad_country$Vietnam, na.rm=T))
-
-corr.CNVN = apa_print(cor.test(df.triad_country$China, 
-                  df.triad_country$Vietnam, na.rm=T))
-```
-
-<!-- With a Pearson correlation test, we observed high correlations between thematic responding across all three countries.
-The proportion of US thematic responding is strongly correlated with thematic responding in China, `r corr.USCN$full_result`.
-The proportion of US thematic responding is strongly correlated with thematic responding in Vietnam, `r corr.USVN$full_result`.
-Likewise, the proportion of China thematic response is strongly correlated with thematic responding in Vietnam, `r corr.CNVN$full_result`.
-This points to a strong signal of universality across cultural contexts regarding similarity judgments.
--->
-
-```{r USCN effect size comparison, cache = TRUE, include=FALSE}
-USCN_cohen <- cohen.d(df.triad_country$China, df.triad_country$US)
+       x = "Country") + 
+  scale_color_manual(values=c("#D63230", "#1C77C3", "#F39237")) + 
+  theme(legend.position = "none")
 ```
@@
 #### Raw lexical co-occurrences
-```{r Pearson correlation between raw co-occurrences of corpora and responding, warning=FALSE, eval = F, cache = TRUE, include=FALSE}
-
-#raw co-occurrences
-df.triad_country_freq <- df %>%
-  filter(!(triad %in% triads_omit)) %>% # omit triads that do not have meaningful prediction (at least 1 non-zero prediction in both languages)
-  group_by(triad, country, theme_freq_prop_E, theme_freq_prop_V, theme_freq_prop_M) %>%  # not working 
-  summarize(emp_theme_prop = mean(responses_theme))
-df.triad_country_freq   #sanity
-
-df.triad_country_freq_E <- df.triad_country_freq %>%
-  filter(country == "US")
-
-#plotting English corpus against US responding data
-plotE = ggplot(data = df.triad_country_freq_E,
-        mapping = aes(x = emp_theme_prop,
-                     y = theme_freq_prop_E,
-                     label = triad)) +
-   geom_text() +
-   geom_smooth(method = "lm") +
-   labs(x = "Proportion Thematic Chosen (US)",
-        y = "Proportion Thematic Predicted (English)")
-plotE
-
-df.triad_country_freq_V <- df.triad_country_freq %>%
-  filter(country == "Vietnam")
-
-#plotting Vietnamese corpus against VN responding data
-plotV = ggplot(data = df.triad_country_freq_V,
-        mapping = aes(x = emp_theme_prop,
-                     y = theme_freq_prop_V,
-                     label = triad)) +
-   geom_text() +
-   geom_smooth(method = "lm") +
-   labs(x = "Proportion Thematic Chosen (Vietnam)",
-        y = "Proportion Thematic Predicted (Vietnamese)")
-plotV
-
-df.triad_country_freq_M <- df.triad_country_freq %>%
-  filter(country == "China")
-
-#plotting China corpus against CN responding data
-plotM = ggplot(data = df.triad_country_freq_M,
-        mapping = aes(x = emp_theme_prop,
-                     y = theme_freq_prop_M,
-                     label = triad)) +
-   geom_text() +
-   geom_smooth(method = "lm") +
-   labs(x = "Proportion Thematic Chosen (China)",
-        y = "Proportion Thematic Predicted (Chinese)")
-plotM
-
-#Pearson correlation between corpus and responding
-corr.E = apa_print(cor.test(df.triad_country_freq_E$emp_theme_prop,
-                  df.triad_country_freq_E$theme_freq_prop_E, na.rm=T))
-corr.E
-
-corr.V = apa_print(cor.test(df.triad_country_freq_V$emp_theme_prop,
-                  df.triad_country_freq_V$theme_freq_prop_V, na.rm=T))
-corr.V
-
-corr.M = apa_print(cor.test(df.triad_country_freq_M$emp_theme_prop,
-                  df.triad_country_freq_M$theme_freq_prop_M, na.rm=T))
-corr.M
-
-#Pearson correlation between EN and VI corpus
-corr.EV = apa_print(cor.test(df.triad_country_freq_V$theme_freq_prop_V,
-                   df.triad_country_freq_E$theme_freq_prop_E, na.rm=T))
-corr.EM = apa_print(cor.test(df.triad_country_freq_M$theme_freq_prop_M,
-                   df.triad_country_freq_E$theme_freq_prop_E, na.rm=T))
-corr.MV = apa_print(cor.test(df.triad_country_freq_V$theme_freq_prop_V,
-                   df.triad_country_freq_M$theme_freq_prop_M, na.rm=T))
-```
-
-```{r echo=FALSE, warning = F, eval = F, cache = TRUE, paged.print=FALSE, fig.cap ="Correlation between English corpus lexical co-occurrence and US responding, and Vietnamese corpus lexical co-occurrence and Vietnam responding."}
-plotE + plotV + plotM
-  plot_layout(ncol = 3)
-```
 
@@
 
-We found that all corpora are significant predictors of all cultural context responding.
 ```{r US responding predicted by each corpus model raw co-occurrences, warning=FALSE, include=F, cache = TRUE}
@@
 ```
-For US responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are all significant predictors.
-EN corpus: $\beta$ = `r round(fixef(fit.EN_US)["theme_freq_prop_E"], 2)`, $\chi^2$(`r fit.EN_US.anova["theme_freq_prop_E", "Df"]`) = `r round(fit.EN_US.anova["theme_freq_prop_E", "Chisq"], 2)`, p `r ifelse( fit.EN_US.anova["theme_freq_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.EN_US.anova["theme_freq_prop_E", "Pr(>Chisq)"], 3)), "< .001")`.
-VI corpus: $\beta$ = `r round(fixef(fit.VI_US)["theme_freq_prop_V"], 2)`, $\chi^2$(`r fit.VI_US.anova["theme_freq_prop_V", "Df"]`) = `r round(fit.VI_US.anova["theme_freq_prop_V", "Chisq"], 2)`, p `r ifelse( fit.VI_US.anova["theme_freq_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.VI_US.anova["theme_freq_prop_V", "Pr(>Chisq)"], 3)), "< .001")`.
-ZH corpus: $\beta$ = `r round(fixef(fit.ZH_US)["theme_freq_prop_M"], 2)`, $\chi^2$(`r fit.ZH_US.anova["theme_freq_prop_M", "Df"]`) = `r round(fit.ZH_US.anova["theme_freq_prop_M", "Chisq"], 2)`, p `r ifelse( fit.ZH_US.anova["theme_freq_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ZH_US.anova["theme_freq_prop_M", "Pr(>Chisq)"], 3)), "< .001")`.
 
@@
 ```
-For Vietnam responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are all significant predictors.
-EN corpus: $\beta$ = `r round(fixef(fit.EN_VN)["theme_freq_prop_E"], 2)`, $\chi^2$(`r fit.EN_VN.anova["theme_freq_prop_E", "Df"]`) = `r round(fit.EN_VN.anova["theme_freq_prop_E", "Chisq"], 2)`, p `r ifelse( fit.EN_VN.anova["theme_freq_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.EN_VN.anova["theme_freq_prop_E", "Pr(>Chisq)"], 3)), "< .001")`.
-VI corpus: $\beta$ = `r round(fixef(fit.VI_VN)["theme_freq_prop_V"], 2)`, $\chi^2$(`r fit.VI_VN.anova["theme_freq_prop_V", "Df"]`) = `r round(fit.VI_VN.anova["theme_freq_prop_V", "Chisq"], 2)`, p `r ifelse( fit.VI_VN.anova["theme_freq_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.VI_VN.anova["theme_freq_prop_V", "Pr(>Chisq)"], 3)), "< .001")`.
-ZH corpus: $\beta$ = `r round(fixef(fit.ZH_VN)["theme_freq_prop_M"], 2)`, $\chi^2$(`r fit.ZH_VN.anova["theme_freq_prop_M", "Df"]`) = `r round(fit.ZH_VN.anova["theme_freq_prop_M", "Chisq"], 2)`, p `r ifelse( fit.ZH_VN.anova["theme_freq_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ZH_VN.anova["theme_freq_prop_M", "Pr(>Chisq)"], 3)), "< .001")`.
 
@@
 
-For China responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are all significant predictors.
-EN corpus: $\beta$ = `r round(fixef(fit.EN_CN)["theme_freq_prop_E"], 2)`, $\chi^2$(`r fit.EN_CN.anova["theme_freq_prop_E", "Df"]`) = `r round(fit.EN_CN.anova["theme_freq_prop_E", "Chisq"], 2)`, p `r ifelse( fit.EN_CN.anova["theme_freq_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.EN_CN.anova["theme_freq_prop_E", "Pr(>Chisq)"], 3)), "< .001")`.
-VI corpus: $\beta$ = `r round(fixef(fit.VI_CN)["theme_freq_prop_V"], 2)`, $\chi^2$(`r fit.VI_CN.anova["theme_freq_prop_V", "Df"]`) = `r round(fit.VI_CN.anova["theme_freq_prop_V", "Chisq"], 2)`, p `r ifelse( fit.VI_CN.anova["theme_freq_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.VI_CN.anova["theme_freq_prop_V", "Pr(>Chisq)"], 3)), "< .001")`.
-ZH corpus: $\beta$ = `r round(fixef(fit.ZH_US)["theme_freq_prop_M"], 2)`, $\chi^2$(`r fit.ZH_CN.anova["theme_freq_prop_M", "Df"]`) = `r round(fit.ZH_CN.anova["theme_freq_prop_M", "Chisq"], 2)`, p `r ifelse( fit.ZH_CN.anova["theme_freq_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ZH_CN.anova["theme_freq_prop_M", "Pr(>Chisq)"], 3)), "< .001")`.
+```{r calculate range of beta statistics, warning=F, include=F}
+beta.single_corpus_freq <- c(
+  round(fixef(fit.EN_US)["theme_freq_prop_E"], 2),
+  round(fixef(fit.VI_US)["theme_freq_prop_V"], 2), 
+  round(fixef(fit.ZH_US)["theme_freq_prop_M"], 2),
+
+  round(fixef(fit.EN_CN)["theme_freq_prop_E"], 2),
+  round(fixef(fit.VI_CN)["theme_freq_prop_V"], 2), 
+  round(fixef(fit.ZH_CN)["theme_freq_prop_M"], 2),
+
+  round(fixef(fit.EN_VN)["theme_freq_prop_E"], 2),
+  round(fixef(fit.VI_VN)["theme_freq_prop_V"], 2), 
+  round(fixef(fit.ZH_VN)["theme_freq_prop_M"], 2)
+
+)
+```
+We found that all corpora are significant predictors of all cultural context responding, with p < 0.05 and $\beta$ from `r min(beta.single_corpus_freq)` - `r max(beta.single_corpus_freq)`.
+(For a full report, see Appendix.)
 
@@
 #### Cosine distances of fastText word vectors
-Similar to the results from the analysis with raw lexical co-occurrences, we found that all corpora are significant predictors of all cultural context responding.
 
@@
 ```
-For US responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are significant predictors of US responding (EN-US model: $\beta$ = `r round(fixef(fit.EN_US_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.EN_US_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.EN_US_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p `r ifelse( fit.EN_US_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.EN_US_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"], 3)), "< .001")`; VI-US model: $\beta$ = `r round(fixef(fit.VI_US_cos)["theme_cosine_prop_V"], 2)`, $\chi^2$(`r fit.VI_US_cos.anova["theme_cosine_prop_V", "Df"]`) = `r round(fit.VI_US_cos.anova["theme_cosine_prop_V", "Chisq"], 2)`, p = `r ifelse( fit.VI_US_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.VI_US_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"], 3)), "< .001")`; ZH-US model: $\beta$ = `r round(fixef(fit.ZH_US_cos)["theme_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ZH_US_cos.anova["theme_cosine_prop_M", "Df"]`) = `r round(fit.ZH_US_cos.anova["theme_cosine_prop_M", "Chisq"], 2)`, p `r ifelse( fit.ZH_US_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ZH_US_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"], 3)), "< .001")`).
 
@@
 
-For Vietnam (VN) responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are significant predictors of VN responding (EN-VN model: $\beta$ = `r round(fixef(fit.EN_VN_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.EN_VN_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.EN_VN_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p `r ifelse( fit.EN_VN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.EN_VN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"], 3)), "< .001")`; VI-VN model: $\beta$ = `r round(fixef(fit.VI_VN_cos)["theme_cosine_prop_V"], 2)`, $\chi^2$(`r fit.VI_VN_cos.anova["theme_cosine_prop_V", "Df"]`) = `r round(fit.VI_VN_cos.anova["theme_cosine_prop_V", "Chisq"], 2)`, p = `r ifelse( fit.VI_VN_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.VI_VN_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"], 3)), "< .001")`; ZH-VN model: $\beta$ = `r round(fixef(fit.ZH_VN_cos)["theme_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ZH_VN_cos.anova["theme_cosine_prop_M", "Df"]`) = `r round(fit.ZH_VN_cos.anova["theme_cosine_prop_M", "Chisq"], 2)`, p `r ifelse( fit.ZH_VN_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ZH_VN_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"], 3)), "< .001")`).
-
 ```{r CN responding predicted by each corpus model cosine differences, warning=FALSE, include=F}
@@
 
-For China (CN) responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are significant predictors of CN responding (EN-CN model: $\beta$ = `r round(fixef(fit.EN_CN_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.EN_CN_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.EN_CN_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p `r ifelse( fit.EN_CN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.EN_CN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"], 3)), "< .001")`; VI-CN model: $\beta$ = `r round(fixef(fit.VI_CN_cos)["theme_cosine_prop_V"], 2)`, $\chi^2$(`r fit.VI_CN_cos.anova["theme_cosine_prop_V", "Df"]`) = `r round(fit.VI_CN_cos.anova["theme_cosine_prop_V", "Chisq"], 2)`, p = `r ifelse( fit.VI_CN_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.VI_CN_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"], 3)), "< .001")`; ZH-CN model: $\beta$ = `r round(fixef(fit.ZH_CN_cos)["theme_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ZH_CN_cos.anova["theme_cosine_prop_M", "Df"]`) = `r round(fit.ZH_CN_cos.anova["theme_cosine_prop_M", "Chisq"], 2)`, p `r ifelse( fit.ZH_CN_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ZH_CN_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"], 3)), "< .001")`).
+```{r calculate range of beta statistics, warning=F, include=F}
+beta.single_corpus_cos <- c(
+  round(fixef(fit.EN_US_cos)["theme_cosine_prop_E"], 2),
+  round(fixef(fit.VI_US_cos)["theme_cosine_prop_V"], 2), 
+  round(fixef(fit.ZH_US_cos)["theme_cosine_prop_M"], 2),
+
+  round(fixef(fit.EN_CN_cos)["theme_cosine_prop_E"], 2),
+  round(fixef(fit.VI_CN_cos)["theme_cosine_prop_V"], 2), 
+  round(fixef(fit.ZH_CN_cos)["theme_cosine_prop_M"], 2),
+
+  round(fixef(fit.EN_VN_cos)["theme_cosine_prop_E"], 2),
+  round(fixef(fit.VI_VN_cos)["theme_cosine_prop_V"], 2), 
+  round(fixef(fit.ZH_VN_cos)["theme_cosine_prop_M"], 2),
+
+)
+```
+
+Similar to the results from the analysis with raw lexical co-occurrences, we found that all corpora are significant predictors of all cultural context responding, with p < 0.05 and $\beta$ from `r min(beta.single_corpus_cos)` - `r max(beta.single_corpus_cos)`.
+(For a full report, see Appendix.)
 
@@
 #### Raw co-occurrences
-When we included all corpora thematic cosine distance proportion as predictors, all corpora are significant in predicting all cultural context's responding.
 
@@
 ```
-For Vietnam responding: only English (EN) and Mandarin (ZH) corpora are significant predictors.
+For Vietnam responding: only Mandarin (ZH) corpus is a significant predictor.
 EN corpus: $\beta$ = `r round(fixef(fit.ENVIZH_VN)["theme_freq_prop_E"], 2)`, $\chi^2$(`r fit.ENVIZH_VN.anova["theme_freq_prop_E", "Df"]`) = `r round(fit.ENVIZH_VN.anova["theme_freq_prop_E", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_VN.anova["theme_freq_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_VN.anova["theme_freq_prop_E", "Pr(>Chisq)"], 3)), "< .001")`.
@@
 fit.ENVIZH_CN = glmer(responses_theme ~ 
-                      theme_freq_prop_V + theme_freq_prop_E + theme_freq_prop_M +
+                      theme_freq_prop_M + theme_freq_prop_E + theme_freq_prop_V +
                       (1 | subject) + (1 | triad), 
@@
 
-ggplot(data = df.USVNCN_coeffs_freq, 
+plot.coeffs_freq <- ggplot(data = df.USVNCN_coeffs_freq, 
        mapping = aes(x = country_value, y = coeff_value_freq, fill = corpus_value)) +
@@
   scale_x_discrete(labels=c("CN" = "China", "US" = "US", "VN" = "Vietnam")) + 
-  scale_fill_manual(values=c("#D63230", "#1C77C3", "#F39237"))
+  scale_fill_manual(values=c("#D63230", "#1C77C3", "#F39237")) + 
+  ggtitle('a')
 
@@
 We observed some level of language specificity from this analysis.
-The English corpus is the best predictor for US responding, and the Mandarin corpus is the best predictor for China response.
-While this is not the case with the Vietnamese corpus and the Vietnam responding, the Vietnamese corpus is still a significant predictor for the Vietnam responding.
-
-However, we found that language specificity alone does not explain our results.
+The English corpus is the only significant predictor for US responding, and the Mandarin corpus is the only significant predictor for China response.
+However, against our prediction, the Vietnamese corpus was not a significant predictor for Vietnam responding when other corpora were included.
+(Figure 2a).
+
+<!-- Nonetheless, we found that language specificity alone does not explain our results.
 We used an ANOVA to compare the model with only the corresponding corpus, and the model with all 3 corpora for each cultural context.
 We found that in all three cases (US, China, Vietnam), adding the other two corpora produces a significantly better fit than the identical model without the additional corpora, and only the corresponding corpus included as a predictor (US response: $\chi^2$(`r fit.US_freq_compare["fit.ENVIZH_US", "Df"]`) = `r round(fit.US_freq_compare["fit.ENVIZH_US", "Chisq"], 2)`, p `r ifelse( fit.US_freq_compare["fit.ENVIZH_US", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.US_freq_compare["fit.ENVIZH_US", "Pr(>Chisq)"], 3)), "< .001")`; Vietnam response: $\chi^2$(`r fit.VN_freq_compare["fit.ENVIZH_VN", "Df"]`) = `r round(fit.VN_freq_compare["fit.ENVIZH_VN", "Chisq"], 2)`, p `r ifelse( fit.VN_freq_compare["fit.ENVIZH_VN", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.VN_freq_compare["fit.ENVIZH_VN", "Pr(>Chisq)"], 3)), "< .001")`; China response: $\chi^2$(`r fit.CN_freq_compare["fit.ENVIZH_CN", "Df"]`) = `r round(fit.CN_freq_compare["fit.ENVIZH_CN", "Chisq"], 2)`, p `r ifelse( fit.CN_freq_compare["fit.ENVIZH_CN", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.CN_freq_compare["fit.ENVIZH_CN", "Pr(>Chisq)"], 3)), "< .001")`).
+-->
 
@@
 
-When we included all corpora thematic cosine distance proportion as predictors, all corpora are significant in predicting all cultural context's responding.
-
-For US responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are all significant predictors.
+For US responding: only English (EN) corpus is a significant predictor.
 EN corpus: $\beta$ = `r round(fixef(fit.ENVIZH_US_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.ENVIZH_US_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.ENVIZH_US_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_US_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_US_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"], 3)), "< .001")`.
@@
 
-For Vietnam responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are all significant predictors.
+For Vietnam responding: only Vietnamese (VI) and Mandarin (ZH) corpus are significant predictors.
 EN corpus: $\beta$ = `r round(fixef(fit.ENVIZH_VN_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.ENVIZH_VN_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p = `r ifelse( fit.ENVIZH_VN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"], 3)), "< .001")`.
@@
 
-For China responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are all significant predictors.
+For China responding: only Mandarin (ZH) and English (EN) corpus are significant predictors.
 EN corpus: $\beta$ = `r round(fixef(fit.ENVIZH_CN_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.ENVIZH_CN_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.ENVIZH_CN_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p = `r ifelse( fit.ENVIZH_CN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_CN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"], 3)), "< .001")`.
@@
 
-We observed some level of language specificity from this analysis.
-The English corpus is the best predictor for US responding, and the Mandarin corpus is the best predictor for China response.
-While this is not the case with the Vietnamese corpus and the Vietnam responding, the Vietnamese corpus is still a significant predictor for the Vietnam responding.
+Again, we observed some level of language specificity from this analysis.
+Each corpus is a significant predictor for responding in the corresponding cultural context.
+The English corpus is the best (and only) predictor for US responding, and the Mandarin corpus is the best predictor for China response.
+While this is not the case with the Vietnamese corpus and the Vietnam responding, the Vietnamese corpus is still a significant predictor for the Vietnam responding (Figure 2b).
 
@@
 
-ggplot(data = df.USVNCN_coeffs_cos, 
+plot.coeffs_cos <- ggplot(data = df.USVNCN_coeffs_cos, 
        mapping = aes(x = country_value, y = coeff_value_cos, fill = corpus_value)) +
@@
   scale_x_discrete(labels=c("CN" = "China", "US" = "US", "VN" = "Vietnam")) + 
-  scale_fill_manual(values=c("#D63230", "#1C77C3", "#F39237"))
-
+  scale_fill_manual(values=c("#D63230", "#1C77C3", "#F39237")) + 
+  ggtitle('b')
+```
+
+```{r echo=FALSE, warning=FALSE, cache = TRUE, fig.cap="Fixed effect sizes of each corpus when included as a predictor for China, US, and Vietnam responding, respectively (left: raw lexical co-occurrences, right: cosine similarity).
+The English corpus is the best predictor for US response, and the Mandarin corpus is the best predictor for China response."}
+plot.coeffs_freq + plot.coeffs_cos
 ```
@@
 ```
-_TODO: should we take this out?__
-We carried out an ANOVA model comparison to compare our approach with previous studies that did not include corpus information.
-Because @Ji2004 only compared US and China participants, we filtered our data to only include responding data from these two countries.
+
 Our approach would be to compare a model that only includes country (US or China) as a fixed effect with one that also includes English and Chinese corpus data.
@@
 
-## 5. How general are the cross-language differences in similarity judgments we observe? Are they limited to taxonomic-thematic contrasts or do they extend to other cases?
-
+## 4. How general are the cross-language differences in similarity judgments we observe? Are they limited to taxonomic-thematic contrasts or do they extend to other cases?
+
+We test whether using the same approach, we can also predict filler similarity judgements. 
 ```{r incorporate base freq for fillers}
@@
 
-```{r echo=FALSE, warning=FALSE, cache = TRUE, fig.cap="Proportion of thematic responses by country.
-Only US-China responding comparison shows a siginficant difference.
-We could not extend this to US-Vietnam responding comparison."}
+```{r echo=FALSE, warning=FALSE, cache = TRUE, fig.cap="Proportion of thematic responses by country."}
 
@@
 ``` 
-No effect of country on filler responding.
+No effect of country on filler responding (Figure 4).
 
@@
 First of all, an ANOVA model comparison showed that adding a random effect term for varying slope by country and varying intercept by triad to the model produces a significant better fit than the identical model without this random effect term included as a predictor ($\chi^2$(`r fit.no_triad_compare["fit.country", "Df"]`) = `r round(fit.no_triad_compare["fit.country", "Chisq"], 2)`, p `r ifelse( fit.no_triad_compare["fit.country", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.no_triad_compare["fit.country", "Pr(>Chisq)"], 3)), "< .001")`)
-
-<!-- Anecdotally, we show below some examples of triads that show contrasting difference in the magnitude of difference in thematic responses between countries.
-As a review, the overall result across all triads showed that there was significant difference between US and China responding, and no significant differences between US and Vietnam or China and Vietnam responding.
-However, we observed that for the triad "cow-grass-chicken," there were significant differences between US and China, and US and Vietnam responding.
-There was no significant difference between China and Vietnam responding.
-For the triad "spoon-sugar-fork," there were significant difference between China and US, and China and Vietnam responding, but no significant difference between US and Vietnam.
-For the triad "hair-comb-beard," there were no significant differences pairwise across the three cultural contexts.
-This suggests that there are triad-specific cross-cultural effects in play.
-Beyond emphasizing the importance of including triad predictors as a random effect, this finding suggests that, firstly, future similar studies need to report triads that are used, as the triads used can affect results (for example, if a study only includes triads where China and US responding are significantly different, it would be more likely to conclude that Chinese and US cultures hold different notions of similarity).
-Secondly, that future studies can look more deeply into which groups of triads are driving the US-China responding difference.
-For example, triads belonging to different semantic neighborhoods might be influencing cross-cultural responding in different ways.
--->
-
-```{r include=FALSE, eval = F, cache = TRUE}
-df.country_item <- df_main_analysis %>%
-  filter(triad == "hair")
-
-plot.hair <- ggplot(df.country_item,
-       mapping = aes(x = factor(country, levels=c("China", "US", "Vietnam")), 
-                     y = responses_theme, 
-                     color = factor(country, levels=c("China", "US", "Vietnam")))) +
-  geom_jitter(stat = "identity", alpha  = .5) +
-  labs(y = "Proportion Thematic Chosen (hair: beard / comb)",  
-       x = "Country", 
-       color = "Country") + 
-  stat_summary(fun.data = "mean_cl_boot", 
-               geom = "pointrange") + 
-  scale_y_continuous(limits=c(0.0, 1.0), oob = scales::squish) + 
-  scale_fill_manual(values=c("#D63230", "#1C77C3", "#F39237")) +  
-  scale_color_manual(values=c("#D63230", "#1C77C3", "#F39237"))  + 
-  theme(axis.title = element_text(size=rel(0.75)))
-```
-
-```{r include=FALSE, eval = F, cache = TRUE}
-df.country_item <- df_main_analysis %>%
-  filter(triad == "spoon2")
-
-plot.spoon2 <- ggplot(df.country_item,
-       mapping = aes(x = factor(country, levels=c("China", "US", "Vietnam")), 
-                     y = responses_theme, 
-                     color = factor(country, levels=c("China", "US", "Vietnam")))) +
-  geom_jitter(stat = "identity", alpha  = .5) +
-  labs(y = "Proportion Thematic Chosen (spoon: fork / sugar)",  
-       x = "Country", 
-       color = "Country") + 
-  stat_summary(fun.data = "mean_cl_boot", 
-               geom = "pointrange") + 
-  scale_y_continuous(limits=c(0.0, 1.0), oob = scales::squish) + 
-  scale_fill_manual(values=c("#D63230", "#1C77C3", "#F39237")) +  
-  scale_color_manual(values=c("#D63230", "#1C77C3", "#F39237")) + 
-  theme(legend.position = "none") + 
-  theme(axis.title = element_text(size=rel(0.75)))
-```
-
-```{r include = FALSE, eval = F, cache = TRUE}
-#show 1 triad
-
-df.country_item <- df_main_analysis %>%
-  filter(triad == "cow2")
-
-df.country_item_summ <- df %>%
-  group_by(triad, country) %>%
-  summarize(theme_resp_percent = mean(responses_theme, na.rm = T)) %>%
-  filter(triad == "cow2")
-
-plot.cow2 <- ggplot(df.country_item,
-       mapping = aes(x = factor(country, levels=c("China", "US", "Vietnam")), 
-                     y = responses_theme, 
-                     color = factor(country, levels=c("China", "US", "Vietnam")))) +
-  geom_jitter(stat = "identity", alpha  = .5) +
-  labs(y = "Proportion Thematic Chosen (cow: chicken / grass)",  
-       x = "Country", 
-       color = "Country") + 
-  stat_summary(fun.data = "mean_cl_boot", 
-               geom = "pointrange") + 
-  scale_y_continuous(limits=c(0.0, 1.0), oob = scales::squish) + 
-  scale_fill_manual(values=c("#D63230", "#1C77C3", "#F39237")) +  
-  scale_color_manual(values=c("#D63230", "#1C77C3", "#F39237")) + 
-  theme(legend.position = "none") + 
-  theme(axis.title = element_text(size=rel(0.75)))
-# 
-# +  
-#   geom_bar(data = df.country_item_summ, 
-#            mapping = aes(x = factor(country, levels=c("China", "US", "Vietnam")), 
-#                           y = theme_resp_percent, 
-#                          color = factor(country, levels=c("China", "US", "Vietnam"))), 
-#            stat='identity', alpha = .3, 
-#            fill=c("#D63230", "#1C77C3", "#F39237"))
-```
-
-```{r echo=FALSE, eval = F, warning = FALSE, cache = TRUE, fig.width=8, fig.cap="Anecdotal evidence of triad-specific effects.
-Cow-grass-chicken shows significant differences between US-China responding, and between US-Vietnam responding.
-Spoon-sugar-fork shows only a significant difference between US-China responding.
-Hair-comb-beard does not show any significant differences in pairwise comparisons across the three countries."}
-plot.cow2 + plot.spoon2 + plot.hair + 
-    plot_layout(ncol = 3)
-```
 
@@
 ```
+
+## 2. Supplemental for whether each corpus predicts similarity judgement in each cultural context
+### Lexical co-occurrence
+For US responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are all significant predictors.
+EN corpus: $\beta$ = `r round(fixef(fit.EN_US)["theme_freq_prop_E"], 2)`, $\chi^2$(`r fit.EN_US.anova["theme_freq_prop_E", "Df"]`) = `r round(fit.EN_US.anova["theme_freq_prop_E", "Chisq"], 2)`, p `r ifelse( fit.EN_US.anova["theme_freq_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.EN_US.anova["theme_freq_prop_E", "Pr(>Chisq)"], 3)), "< .001")`.
+VI corpus: $\beta$ = `r round(fixef(fit.VI_US)["theme_freq_prop_V"], 2)`, $\chi^2$(`r fit.VI_US.anova["theme_freq_prop_V", "Df"]`) = `r round(fit.VI_US.anova["theme_freq_prop_V", "Chisq"], 2)`, p `r ifelse( fit.VI_US.anova["theme_freq_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.VI_US.anova["theme_freq_prop_V", "Pr(>Chisq)"], 3)), "< .001")`.
+ZH corpus: $\beta$ = `r round(fixef(fit.ZH_US)["theme_freq_prop_M"], 2)`, $\chi^2$(`r fit.ZH_US.anova["theme_freq_prop_M", "Df"]`) = `r round(fit.ZH_US.anova["theme_freq_prop_M", "Chisq"], 2)`, p `r ifelse( fit.ZH_US.anova["theme_freq_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ZH_US.anova["theme_freq_prop_M", "Pr(>Chisq)"], 3)), "< .001")`.
+
+For Vietnam responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are all significant predictors.
+EN corpus: $\beta$ = `r round(fixef(fit.EN_VN)["theme_freq_prop_E"], 2)`, $\chi^2$(`r fit.EN_VN.anova["theme_freq_prop_E", "Df"]`) = `r round(fit.EN_VN.anova["theme_freq_prop_E", "Chisq"], 2)`, p `r ifelse( fit.EN_VN.anova["theme_freq_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.EN_VN.anova["theme_freq_prop_E", "Pr(>Chisq)"], 3)), "< .001")`.
+VI corpus: $\beta$ = `r round(fixef(fit.VI_VN)["theme_freq_prop_V"], 2)`, $\chi^2$(`r fit.VI_VN.anova["theme_freq_prop_V", "Df"]`) = `r round(fit.VI_VN.anova["theme_freq_prop_V", "Chisq"], 2)`, p `r ifelse( fit.VI_VN.anova["theme_freq_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.VI_VN.anova["theme_freq_prop_V", "Pr(>Chisq)"], 3)), "< .001")`.
+ZH corpus: $\beta$ = `r round(fixef(fit.ZH_VN)["theme_freq_prop_M"], 2)`, $\chi^2$(`r fit.ZH_VN.anova["theme_freq_prop_M", "Df"]`) = `r round(fit.ZH_VN.anova["theme_freq_prop_M", "Chisq"], 2)`, p `r ifelse( fit.ZH_VN.anova["theme_freq_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ZH_VN.anova["theme_freq_prop_M", "Pr(>Chisq)"], 3)), "< .001")`.
+
+For China responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are all significant predictors.
+EN corpus: $\beta$ = `r round(fixef(fit.EN_CN)["theme_freq_prop_E"], 2)`, $\chi^2$(`r fit.EN_CN.anova["theme_freq_prop_E", "Df"]`) = `r round(fit.EN_CN.anova["theme_freq_prop_E", "Chisq"], 2)`, p `r ifelse( fit.EN_CN.anova["theme_freq_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.EN_CN.anova["theme_freq_prop_E", "Pr(>Chisq)"], 3)), "< .001")`.
+VI corpus: $\beta$ = `r round(fixef(fit.VI_CN)["theme_freq_prop_V"], 2)`, $\chi^2$(`r fit.VI_CN.anova["theme_freq_prop_V", "Df"]`) = `r round(fit.VI_CN.anova["theme_freq_prop_V", "Chisq"], 2)`, p `r ifelse( fit.VI_CN.anova["theme_freq_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.VI_CN.anova["theme_freq_prop_V", "Pr(>Chisq)"], 3)), "< .001")`.
+ZH corpus: $\beta$ = `r round(fixef(fit.ZH_US)["theme_freq_prop_M"], 2)`, $\chi^2$(`r fit.ZH_CN.anova["theme_freq_prop_M", "Df"]`) = `r round(fit.ZH_CN.anova["theme_freq_prop_M", "Chisq"], 2)`, p `r ifelse( fit.ZH_CN.anova["theme_freq_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ZH_CN.anova["theme_freq_prop_M", "Pr(>Chisq)"], 3)), "< .001")`.
+
+### Cosine similarity 
+For US responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are significant predictors of US responding (EN-US model: $\beta$ = `r round(fixef(fit.EN_US_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.EN_US_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.EN_US_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p `r ifelse( fit.EN_US_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.EN_US_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"], 3)), "< .001")`; VI-US model: $\beta$ = `r round(fixef(fit.VI_US_cos)["theme_cosine_prop_V"], 2)`, $\chi^2$(`r fit.VI_US_cos.anova["theme_cosine_prop_V", "Df"]`) = `r round(fit.VI_US_cos.anova["theme_cosine_prop_V", "Chisq"], 2)`, p `r ifelse( fit.VI_US_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.VI_US_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"], 3)), "< .001")`; ZH-US model: $\beta$ = `r round(fixef(fit.ZH_US_cos)["theme_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ZH_US_cos.anova["theme_cosine_prop_M", "Df"]`) = `r round(fit.ZH_US_cos.anova["theme_cosine_prop_M", "Chisq"], 2)`, p `r ifelse( fit.ZH_US_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ZH_US_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"], 3)), "< .001")`).
+
+For Vietnam (VN) responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are significant predictors of VN responding (EN-VN model: $\beta$ = `r round(fixef(fit.EN_VN_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.EN_VN_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.EN_VN_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p `r ifelse( fit.EN_VN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.EN_VN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"], 3)), "< .001")`; VI-VN model: $\beta$ = `r round(fixef(fit.VI_VN_cos)["theme_cosine_prop_V"], 2)`, $\chi^2$(`r fit.VI_VN_cos.anova["theme_cosine_prop_V", "Df"]`) = `r round(fit.VI_VN_cos.anova["theme_cosine_prop_V", "Chisq"], 2)`, p `r ifelse( fit.VI_VN_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.VI_VN_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"], 3)), "< .001")`; ZH-VN model: $\beta$ = `r round(fixef(fit.ZH_VN_cos)["theme_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ZH_VN_cos.anova["theme_cosine_prop_M", "Df"]`) = `r round(fit.ZH_VN_cos.anova["theme_cosine_prop_M", "Chisq"], 2)`, p `r ifelse( fit.ZH_VN_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ZH_VN_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"], 3)), "< .001")`).
+
+For China (CN) responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are significant predictors of CN responding (EN-CN model: $\beta$ = `r round(fixef(fit.EN_CN_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.EN_CN_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.EN_CN_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p `r ifelse( fit.EN_CN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.EN_CN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"], 3)), "< .001")`; VI-CN model: $\beta$ = `r round(fixef(fit.VI_CN_cos)["theme_cosine_prop_V"], 2)`, $\chi^2$(`r fit.VI_CN_cos.anova["theme_cosine_prop_V", "Df"]`) = `r round(fit.VI_CN_cos.anova["theme_cosine_prop_V", "Chisq"], 2)`, p `r ifelse( fit.VI_CN_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.VI_CN_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"], 3)), "< .001")`; ZH-CN model: $\beta$ = `r round(fixef(fit.ZH_CN_cos)["theme_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ZH_CN_cos.anova["theme_cosine_prop_M", "Df"]`) = `r round(fit.ZH_CN_cos.anova["theme_cosine_prop_M", "Chisq"], 2)`, p `r ifelse( fit.ZH_CN_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ZH_CN_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"], 3)), "< .001")`).
 

### 2023-01-19 code/4_paper/manuscript/manuscript.Rmd
fixed merge

@@
 Speakers of different languages judge similarity in this context differently, but why?
-One possibility is that cultures co-varying with these languages induce variation in conceptualizations of similarity.
-Specifically, East Asian cultures may promote reasoning about thematic similarity, by which cow and grass are more related, whereas Western cultures may bias similarity judgements toward taxonomic relations, like cow-chicken.
+One possibility is that cultures co-varying with these languages induce differences in conceptualizations of similarity.
+Specifically, East Asian cultures may promote reasoning about thematic similarity, by which cow and grass are more related, whereas Western cultures may bias judgements toward taxonomic relations, like cow-chicken.
 This difference in notions of similarity is the consensus interpretation for cross-cultural variation in this paradigm.
-We consider, and provide evidence for, an alternative possibility, by which notions of similarity are equivalent across contexts, but the statistics of the environment vary.
-On this account, similarity judgements are guided by co-occurrence in experience, and observing or hearing about cows and grass or cows and chickens more often could induce preferences for the relevant grouping, and account for apparent differences in notions of similarity across contexts.
+We consider, and provide evidence for, an alternative possibility, by which notions of similarity are similar across contexts, but the statistics of the environment vary.
+On this account, similarity judgements are guided by co-occurrence in experience, and observing or hearing about cows and grass or cows and chickens more often could induce preferences for these groupings, and account in part for apparent differences in notions of similarity across contexts.
 
@@
 
-While we discuss cross-cultural variability at the level of countries or larger world areas, these are not cultural monoliths.
-For convenience, we operationalize culture at the level of country, based on where participants were raised.
-It is an open question whether performance in our participant populations (of relatively young and well-educated adults) is representative of the broader country.
-This is especially true for societies with substantial ethnic and cultural variation such as the US.
-We expect that our data is likely to underestimate variation both within and between the countries we sample from.
-
-Indeed, previous work suggests that using lexical co-occurrence as a proxy can be useful in thinking about similarity judgments.
-Natural language processing tasks have found that lexical co-occurrence is a good predictor for performance in similarity judgment tasks.
+Indeed, previous work suggests that using lexical co-occurrence as a proxy can be useful in thinking about similarity reasoning.
+Natural language processing tasks have found that lexical co-occurrence is a good predictor for performance in similarity judgment.
 @Griffiths2007 showed that a model that takes word-document co-occurrence as input can be used to predict word association and the effects of semantic association on a variety of linguistic tasks.
-Additionally, lexical semantic models that are constructed using lexical co-occurrence (as opposed to annotated relations) have been shown to perform well on predicting human judgments about similarity between word pairs that are either thematically or taxonomically related [@Rohde2006].
-
-Our current study will be using 2 measures of lexical co-occurrence: 1) raw lexical co-occurrences and 2) cosined distances of fastText word vectors.
+Additionally, lexical semantic models that are constructed using lexical co-occurrence (as opposed to annotated relations) have been shown to perform well on predicting human judgments about similarity between word pairs that are thematically or taxonomically related [@Rohde2006].
+
+Our study uses two measures of lexical co-occurrence: 1) raw lexical co-occurrence and 2) cosined distances of fastText word vectors.
 fastText is a system that uses lexical co-occurrence information to generate a vector representing each word in its lexicon [@Mikolov2018].
+
+<!-- MOVE TO METHODS?
 fastText uses a continuous bag-of-words model, which takes into account a symmetric window of words surrounding the word in question and maximizes the log-likelihood of the probability of the word given its context.
@@
 <!-- Additionally, outside of language, cross-cultural differences could come from a couple different mechanisms:  -->
+@Ji2004 suggest that the notion of similarity is what varies across cultural groups, but it is possible that similarity is regarded in the same way and it is actually the input to this similarity judgment that varies across cultural contexts.
+It may be possible to gain traction on potential mechanisms by examining whether variation in similarity judgments co-vary with environmental statistics that differ across cultural and linguistic contexts.
+
 In this study, we ask whether variation in lexical co-occurrence can account for the cross-context (culture and language) differences observed in how people evaluate similarity.

### 2023-01-20 code/1_exclusions/1_exclusionsCN.Rmd
cogsci paper exchange

--- 2022-12-14 code/1_exclusions/1_exclusionsCN.Rmd
@@
 
-df.ppts_not_finished_M <- df.resp_M %>% 
+df.ppts_not_finished_M <- df.resp_M %>% #3
   group_by(subject) %>%
@@
 
-df.ppts_att_M <- df.resp_M %>%
+df.ppts_att_M <- df.resp_M %>% #166
   filter(stim_type == "attention check") %>%
@@
   summarize(pass_att_check_percent = mean(pass_att_check)) %>%
-  filter(pass_att_check_percent >= 0.8)
+  filter(pass_att_check_percent == 1.0)
 
-df.resp_M <- df.resp_M %>%
+df.resp_M_aft_attn <- df.resp_M %>% #38841
   filter(subject %in% df.ppts_att_M$subject)
 
-ppts_resp_M <- unique(df.resp_M$subject)
+ppts_resp_M_aft_attn <- unique(df.resp_M$subject)
 ```
@@
 ppts_non_native_lang_M = unique(df.ppts_non_native_lang_M$subject) #3
-percent_dropped = length(intersect(ppts_non_native_lang_M, ppts_resp_M)) / length(ppts_resp_M)
+percent_dropped = length(intersect(ppts_non_native_lang_M, ppts_resp_M_aft_attn)) / length(ppts_resp_M_aft_attn)
 percent_dropped #0.01086
@@
 df.lang_sp_vi_M <- df.demog %>%
-  filter(demog_question == "lang_sp_vi" & demog_response > 4)
+  filter(demog_question == "lang_sp_vi" & as.numeric(demog_response) > 4)
 
 df.lang_ud_vi_M <- df.demog %>%
-  filter(demog_question == "lang_ud_vi" & demog_response > 4)
+  filter(demog_question == "lang_ud_vi" & as.numeric(demog_response) > 4)
 
@@
 ppts_vi_speaker_M = unique(df.lang_vi_M$subject) #1
-percent_dropped = length(intersect(ppts_vi_speaker_M, ppts_resp_M)) / length(ppts_resp_M)
+percent_dropped = length(intersect(ppts_vi_speaker_M, ppts_resp_M_aft_attn)) / length(ppts_resp_M_aft_attn)
 percent_dropped #0
@@
 df.lang_sp_en_M <- df.demog %>%
-  filter(demog_question == "lang_sp_en" & demog_response > 4)
+  filter(demog_question == "lang_sp_en" & as.numeric(demog_response) > 4)
 
 df.lang_ud_en_M <- df.demog %>%
-  filter(demog_question == "lang_ud_en" & demog_response > 4)
+  filter(demog_question == "lang_ud_en" & as.numeric(demog_response) > 4)
 
@@
 ppts_en_speaker_M = unique(df.lang_en_M$subject) #74
-percent_dropped = length(intersect(ppts_en_speaker_M, ppts_resp_M)) / length(ppts_resp_M)
+percent_dropped = length(intersect(ppts_en_speaker_M, ppts_resp_M_aft_attn)) / length(ppts_resp_M_aft_attn)
 percent_dropped #0.375 # do not use this criterion
@@
 ppts_lived_abroad_M = unique(df.lived_abroad_M$subject) #40
-percent_dropped = length(intersect(ppts_lived_abroad_M, ppts_resp_M)) / length(unique(df.resp_M$subject))
+percent_dropped = length(intersect(ppts_lived_abroad_M, ppts_resp_M_aft_attn)) / length(ppts_resp_M_aft_attn)
 percent_dropped #0.163043
@@
 ppts_oversea_exp_M = unique(df.oversea_exp_M$subject) #12
-percent_dropped = length(intersect(ppts_oversea_exp_M, ppts_resp_M)) / length(unique(df.resp_M$subject))
+percent_dropped = length(intersect(ppts_oversea_exp_M, ppts_resp_M_aft_attn)) / length(ppts_resp_M_aft_attn)
 percent_dropped #0.0434782
 
-df.resp_M <- df.resp_M %>%
+df.resp_M_aft_demog <- df.resp_M_aft_attn %>%
   filter(!(subject %in% ppts_non_native_lang_M),
@@
 
-length(unique(df.resp_M$subject)) #149
+length(unique(df.resp_M_aft_demog$subject)) #132
 ```
@@
 ```{r}
-write.csv(df.resp_M, "../../data/responding/dataCN_excl.csv")
+df.demog_metadata <- data.frame(
+  country = c("China"),
+  ppts_finished = c(length(unique(df.ppts_finished_M$subject))),
+  ppts_att_check_excl = c(length(unique(df.ppts_finished_M$subject)) - length(unique(df.ppts_att_M$subject))), 
+  ppts_after_att_check_excl = c(length(unique(df.ppts_att_M$subject))),
+  ppts_non_native_speaker = c(paste(length(ppts_non_native_lang_M),"*")), 
+  ppts_en_speaker = c(length(ppts_en_speaker_M)), 
+  ppts_vi_speaker = c(paste(length(ppts_vi_speaker_M),"*")),
+  ppts_zh_speaker = c("N/A"), 
+  ppts_lived_abroad = c(paste(length(ppts_lived_abroad_M),"*")), 
+  ppts_oversea_exp = c(paste(length(ppts_oversea_exp_M), "*")),
+  ppts_after_demog_excl = c(length(unique(df.resp_M_aft_demog$subject))))
 ```
+
+```{r}
+write.csv(df.resp_M_aft_demog, "../../data/responding/dataCN_excl.csv")
+write.csv(df.demog_metadata, "../../data/responding/dataCN_excl_metadata.csv")
+```

### 2023-01-20 code/1_exclusions/1_exclusionsUS.Rmd
cogsci paper exchange

--- 2022-12-14 code/1_exclusions/1_exclusionsUS.Rmd
@@
   summarize(pass_att_check_percent = mean(pass_att_check)) %>%
-  filter(pass_att_check_percent >= 0.8)
+  filter(pass_att_check_percent == 1.0)
 
-df.resp_E <- df.resp_E %>%
+df.resp_E_aft_attn <- df.resp_E %>%
   filter(subject %in% df.ppts_att_E$subject)
 
-ppts_resp_E <- unique(df.resp_E$subject)
+ppts_resp_E_aft_attn <- unique(df.resp_E_aft_attn$subject)
 ```
@@
   select(-X) %>%
-  filter(country == "US")
+  filter(country == "US") %>%
+  filter(subject %in% ppts_resp_E_aft_attn)
 ```
@@
 ppts_non_native_lang_E = unique(df.ppts_non_native_lang_E$subject)#20
-percent_dropped = length(intersect(ppts_non_native_lang_E, ppts_resp_E)) / length(ppts_resp_E)
-percent_dropped #0.104166
+percent_dropped = length(intersect(ppts_non_native_lang_E, ppts_resp_E_aft_attn)) / length(ppts_resp_E_aft_attn)
+percent_dropped #0.1034483
 
@@
 df.lang_sp_vi_E <- df.demog %>%
-  filter(demog_question == "lang_sp_vi" & demog_response > 4)
+  filter(demog_question == "lang_sp_vi" & as.numeric(demog_response) > 4)
 
 df.lang_ud_vi_E <- df.demog %>%
-  filter(demog_question == "lang_ud_vi" & demog_response > 4)
+  filter(demog_question == "lang_ud_vi" & as.numeric(demog_response) > 4)
 
@@
 ppts_vi_speaker_E = unique(df.lang_vi_E$subject) #2
-percent_dropped = length(intersect(ppts_vi_speaker_E, ppts_resp_E)) / length(ppts_resp_E)
-percent_dropped #0.01041666
+percent_dropped = length(intersect(ppts_vi_speaker_E, ppts_resp_E_aft_attn)) / length(ppts_resp_E_aft_attn)
+percent_dropped #0.01149425
 
 df.lang_sp_zh_E <- df.demog %>%
-  filter(demog_question == "lang_sp_zh" & demog_response > 4)
+  filter(demog_question == "lang_sp_zh" & as.numeric(demog_response) > 4)
 
 df.lang_ud_zh_E <- df.demog %>%
-  filter(demog_question == "lang_ud_zh" & demog_response > 4)
+  filter(demog_question == "lang_ud_zh" & as.numeric(demog_response) > 4)
 
@@
 ppts_zh_speaker_E = unique(df.lang_zh_E$subject) #30
-percent_dropped = length(intersect(ppts_zh_speaker_E, ppts_resp_E)) / length(ppts_resp_E)
-percent_dropped #0.15104
+percent_dropped = length(intersect(ppts_zh_speaker_E, ppts_resp_E_aft_attn)) / length(ppts_resp_E_aft_attn)
+percent_dropped #0.1436782
 
@@
 ppts_lived_abroad_E = unique(df.lived_abroad_E$subject) #36
-percent_dropped = length(intersect(ppts_lived_abroad_E, ppts_resp_E)) / length(unique(df.resp_E$subject))
-percent_dropped #0.171875
+percent_dropped = length(intersect(ppts_lived_abroad_E, ppts_resp_E_aft_attn)) / length(ppts_resp_E_aft_attn)
+percent_dropped #0.166667
 
@@
 ppts_oversea_exp_E = unique(df.oversea_exp_E$subject) #95
-percent_dropped = length(intersect(ppts_oversea_exp_E, ppts_resp_E)) / length(unique(df.resp_E$subject))
-percent_dropped #0.4739 # will not use this criterion
+percent_dropped = length(intersect(ppts_oversea_exp_E, ppts_resp_E_aft_attn)) / length(unique(df.resp_E_aft_attn$subject))
+percent_dropped #0.4425287 # will not use this criterion
 
-df.resp_E <- df.resp_E %>%
+df.resp_E_aft_demog <- df.resp_E_aft_attn %>%
   filter(!(subject %in% ppts_non_native_lang_E),
@@
 
-length(unique(df.resp_E$subject)) #124
+length(unique(df.resp_E_aft_demog$subject)) #124
+
 ```
@@
 ```{r}
-write.csv(df.resp_E, "../../data/responding/dataUS_excl.csv")
+df.demog_metadata <- data.frame(
+  country = c("US"),
+  ppts_finished = c(length(unique(df.ppts_finished_E$subject))),
+  ppts_att_check_excl = c(length(unique(df.ppts_finished_E$subject)) - length(unique(df.ppts_att_E$subject))), 
+  ppts_after_att_check_excl = c(length(unique(df.ppts_att_E$subject))),
+  ppts_non_native_speaker = c(paste(length(ppts_non_native_lang_E),"*")), 
+  ppts_en_speaker = c("N/A"),
+  ppts_vi_speaker = c(paste(length(ppts_vi_speaker_E),"*")), 
+  ppts_zh_speaker = c(paste(length(ppts_zh_speaker_E),"*")), 
+  ppts_lived_abroad = c(paste(length(ppts_lived_abroad_E),"*")), 
+  ppts_oversea_exp = c(length(ppts_oversea_exp_E)),
+  ppts_after_demog_excl = c(length(unique(df.resp_E_aft_demog$subject))))
+# colnames(df.demog_metadata) <- c("Participants Finished", 
+#                                  "Participants ")
 ```
+
+```{r}
+write.csv(df.resp_E_aft_demog, "../../data/responding/dataUS_excl.csv")
+write.csv(df.demog_metadata, "../../data/responding/dataUS_excl_metadata.csv")
+```

### 2023-01-20 code/1_exclusions/1_exclusionsVN.Rmd
cogsci paper exchange

@@
   summarize(pass_att_check_percent = mean(pass_att_check)) %>%
-  filter(pass_att_check_percent >= 0.8)
+  filter(pass_att_check_percent == 1.0)
 
-df.resp_V <- df.resp_V %>%
+df.resp_V_aft_attn <- df.resp_V %>%
   filter(subject %in% df.ppts_att_V$subject) #73
 
-ppts_resp_V <- unique(df.resp_V$subject) #137
+ppts_resp_V_aft_attn <- unique(df.resp_V$subject) #137
 ```
@@
 ppts_non_native_lang_V = unique(df.ppts_non_native_lang_V$subject)#2
-percent_dropped = length(intersect(ppts_non_native_lang_V, ppts_resp_V)) / length(ppts_resp_V)
-percent_dropped #0
+percent_dropped = length(intersect(ppts_non_native_lang_V, ppts_resp_V_aft_attn)) / length(ppts_resp_V_aft_attn)
+percent_dropped #0.01
 
@@
 df.lang_sp_en_V <- df.demog %>%
-  filter(demog_question == "lang_sp_en" & demog_response > 4)
+  filter(demog_question == "lang_sp_en" & as.numeric(demog_response) > 4)
 
 df.lang_ud_en_V <- df.demog %>%
-  filter(demog_question == "lang_ud_en" & demog_response > 4)
+  filter(demog_question == "lang_ud_en" & as.numeric(demog_response) > 4)
 
@@
 
-ppts_en_speaker_V = unique(df.lang_en_V$subject) #119
-percent_dropped = length(intersect(ppts_en_speaker_V, ppts_resp_V)) / length(ppts_resp_V)
+ppts_en_speaker_V = unique(df.lang_en_V$subject) #127
+percent_dropped = length(intersect(ppts_en_speaker_V, ppts_resp_V_aft_attn)) / length(ppts_resp_V_aft_attn)
 percent_dropped #0.6277 # do not use this criterion
@@
 df.lang_sp_zh_V <- df.demog %>%
-  filter(demog_question == "lang_sp_zh" & demog_response > 4)
+  filter(demog_question == "lang_sp_zh" & as.numeric(demog_response) > 4)
 
 df.lang_ud_zh_V <- df.demog %>%
-  filter(demog_question == "lang_ud_zh" & demog_response > 4)
+  filter(demog_question == "lang_ud_zh" & as.numeric(demog_response) > 4)
 
@@
 ppts_zh_speaker_V = unique(df.lang_zh_V$subject) #9
-percent_dropped = length(intersect(ppts_zh_speaker_V, ppts_resp_V)) / length(ppts_resp_V)
-percent_dropped #0.05839416
+percent_dropped = length(intersect(ppts_zh_speaker_V, ppts_resp_V_aft_attn)) / length(ppts_resp_V_aft_attn)
+percent_dropped #0.04522613
 
@@
 ppts_lived_abroad_V = unique(df.lived_abroad_V$subject) #18
-percent_dropped = length(intersect(ppts_lived_abroad_V, ppts_resp_V)) / length(unique(df.resp_V$subject))
+percent_dropped = length(intersect(ppts_lived_abroad_V, ppts_resp_V_aft_attn)) / length(ppts_resp_V_aft_attn)
 percent_dropped #0.05839416
@@
 df.oversea_exp_V <- df.demog %>%
-  filter(demog_question == "overseaexpnum" & demog_response == "Six or more experiences")
+  filter(demog_question == "overseaexpnum" & demog_response == "6 lần trở lên")
 
-ppts_oversea_exp_V = unique(df.oversea_exp_V$subject) #95
-percent_dropped = length(intersect(ppts_oversea_exp_V, ppts_resp_V)) / length(unique(df.resp_V$subject))
-percent_dropped #0.4739 # will not use this criterion
+ppts_oversea_exp_V = unique(df.oversea_exp_V$subject) #20
+percent_dropped = length(intersect(ppts_oversea_exp_V, ppts_resp_V_aft_attn)) / length(ppts_resp_V_aft_attn)
+percent_dropped #0.109
 
-df.resp_V <- df.resp_V %>%
+df.resp_V_aft_demog <- df.resp_V_aft_attn %>%
   filter(!(subject %in% ppts_non_native_lang_V),
-         !(subject %in% ppts_vi_speaker_V), 
          !(subject %in% ppts_zh_speaker_V),
-         !(subject %in% ppts_lived_abroad_V))
+         !(subject %in% ppts_lived_abroad_V), 
+         !(subject %in% ppts_oversea_exp_V))
 
-length(unique(df.resp_V$subject)) #124
+length(unique(df.resp_V_aft_demog$subject)) #110
 ```
@@
 ```{r}
-write.csv(df.resp_V, "../../data/responding/dataVN_excl.csv")
+df.demog_metadata <- data.frame(
+  country = c("Vietnam"),
+  ppts_finished = c(length(unique(df.ppts_finished_V$subject))),
+  ppts_att_check_excl = c(length(unique(df.ppts_finished_V$subject)) - length(unique(df.ppts_att_V$subject))), 
+  ppts_after_att_check_excl = c(length(unique(df.ppts_att_V$subject))),
+  ppts_non_native_speaker = c(paste(length(ppts_non_native_lang_V),"*")), 
+  ppts_en_speaker = c(paste(length(ppts_en_speaker_V))), 
+  ppts_vi_speaker = c("N/A"),
+  ppts_zh_speaker = c(paste(length(ppts_zh_speaker_V),"*")), 
+  ppts_lived_abroad = c(paste(length(ppts_lived_abroad_V),"*")), 
+  ppts_oversea_exp = c(paste(length(ppts_oversea_exp_V), "*")),
+  ppts_after_demog_excl = c(length(unique(df.resp_V_aft_demog$subject))))
 ```
+
+```{r}
+write.csv(df.resp_V_aft_demog, "../../data/responding/dataVN_excl.csv")
+write.csv(df.demog_metadata, "../../data/responding/dataVN_excl_metadata.csv")
+```

### 2023-01-20 code/1_exclusions_old/1_exclusionsCN.Rmd
cogsci paper exchange

@@
 
-df.resp_M <- df.resp_M %>%
+df.resp_M <- df.resp_M %>% #38841
   filter(subject %in% df.ppts_att_M$subject) 
@@
 
-df.ppts_non_native_lang_M <- df.resp_M %>%
+df.ppts_non_native_lang_M <- df.resp_M %>% #2
   select(subject, responses, variable_type) %>%
@@
 percent_dropped = length(ppts_non_native_lang_M) / length(unique(df.resp_M$subject))
-percent_dropped #0.01398601
+percent_dropped #0.012048
 
@@
 
-ppts_en_speaker_M = unique(df.lang_en_M$subject) #50
+ppts_en_speaker_M = unique(df.lang_en_M$subject) #66
 percent_dropped = length(ppts_en_speaker_M) / length(unique(df.resp_M$subject))
@@
 
-ppts_vi_speaker_M = unique(df.lang_vi_M$subject) #50
+ppts_vi_speaker_M = unique(df.lang_vi_M$subject) #0
 percent_dropped = length(ppts_vi_speaker_M) / length(unique(df.resp_M$subject))
@@
 
-ppts_lived_abroad_M = unique(df.lived_abroad_M$subject) #23
+ppts_lived_abroad_M = unique(df.lived_abroad_M$subject) #29
 percent_dropped = length(ppts_lived_abroad_M) / length(unique(df.resp_M$subject))
@@
 
-ppts_oversea_exp_M = unique(df.oversea_exp_M$subject) #0
+ppts_oversea_exp_M = unique(df.oversea_exp_M$subject) #8
 percent_dropped = length(ppts_oversea_exp_M) / length(unique(df.resp_M$subject))
@@
 
-length(unique(df.resp_M$subject)) 
+length(unique(df.resp_M$subject)) #132
 ```

### 2023-01-20 code/4_paper/manuscript/manuscript.Rmd
cogsci paper exchange

@@
   - \usepackage[utf8]{inputenc}
-  - \usepackage[T1, T5]{fontenc}
+  - \usepackage[T1, T2A, T5]{fontenc}
+  - \usepackage{kotex}
 
@@
 library("effsize")
+library("kableExtra")
 library("irr")
@@
 # set the default ggplot theme 
-theme_set(theme_classic())
+theme_set(theme_classic(base_size = 7))
 
@@
 
-Our study uses two measures of lexical co-occurrence: 1) raw lexical co-occurrence and 2) cosined distances of fastText word vectors.
+Our study uses cosine distances of fastText word vectors as a measure of lexical co-occurrence^[We also carried out our analysis using raw lexical co-occurrences and obtained similar results.].
 fastText is a system that uses lexical co-occurrence information to generate a vector representing each word in its lexicon [@Mikolov2018].
@@
 df <- read.csv("../../../data/data_USCNVN_ENZHVI.csv")
-#df <- read.csv("../../../data/data_USCNVN_ENZHVI_0623.csv")
 
@@
 ```{r get exclusions data, include = F, cache = T}
-df.excl_US <- read.csv("../../../data/responding/dataUS_excl_metadata.csv")
-df.excl_CN <- read.csv("../../../data/responding/dataCN_excl_metadata.csv")
-df.excl_VN <- read.csv("../../../data/responding/dataVN_excl_metadata.csv")
+df.excl_US <- read.csv("../../../data/responding/dataUS_excl_metadata.csv") %>%
+  select(-X)
+df.excl_CN <- read.csv("../../../data/responding/dataCN_excl_metadata.csv") %>%
+  select(-X)
+df.excl_VN <- read.csv("../../../data/responding/dataVN_excl_metadata.csv") %>%
+  select(-X)
 ```
@@
 The Vietnam sample included `r df.excl_VN$ppts_after_demog_excl` participants (`r df.gender_V %>% filter(gender == "Nam") %>% pull(n)`M, `r df.gender_V %>% filter(gender == "Nữ") %>% pull(n)`F, `r df.gender_V %>% filter(gender == "Từ chối trả lời") %>% pull(n)` other), with mean age = `r round(df.age_V$mean_age, 2)` (SD = `r round(df.age_V$sd_age, 2)`) and median age = `r df.age_V$median_age`.
-The China sample included `r df.excl_CN$ppts_after_demog_excl` participants (`r df.gender_M %>% filter(gender == "男性") %>% pull(n)`M, `r df.gender_M %>% filter(gender == "女性") %>% pull(n)`F, `r df.gender_M %>% filter(gender == "拒绝回答") %>% pull(n)` other), with mean age = `r round(df.age_M$mean_age, 2)` (SD = `r round(df.age_M$sd_age, 2)`) and median age = `r df.age_M$median_age`.[^footnote]
-
-\footnote \smallfont A table summarizing number of participants lost at each round of exclusions is included in the Appendix.
+The China sample included `r df.excl_CN$ppts_after_demog_excl` participants (`r df.gender_M %>% filter(gender == "男性") %>% pull(n)`M, `r df.gender_M %>% filter(gender == "女性") %>% pull(n)`F, `r df.gender_M %>% filter(gender == "拒绝回答") %>% pull(n)` other), with mean age = `r round(df.age_M$mean_age, 2)` (SD = `r round(df.age_M$sd_age, 2)`) and median age = `r df.age_M$median_age`.^[A table summarizing number of participants lost at each round of exclusions is included in the Appendix.]
 
 Notably, we lost a majority of our Vietnam participants (more than 60%) in the attention check exclusion.
-One reason we suspect why this might have happened is because our Vietnam participants are less familiar with research surveys and attention check questions, and thus might have thought too much about the attention check questions.[^footnote]
-
-\footnote \smallfont We carried out an exploratory analysis where we used a less stringent attention check exclusion (covered in the final part of the Results & Analysis section).
-To preview our findings for this analysis, we did not find any difference in significant results when compared with the main analysis.
+One reason we suspect why this might have happened is because our Vietnam participants are less familiar with research surveys and attention check questions, and thus might have thought too much about the attention check questions.^[We carried out an exploratory analysis where we used a less stringent attention check exclusion (covered in the final part of the Results & Analysis section).
+To preview our findings for this analysis, we did not find any difference in significant results when compared with the main analysis.]
 
@@
 For example, “cow,” “grass,” and “chicken,” where “cow” is the cue, “grass” is the thematic match, and “chicken” the taxonomic match.
-We included 105 such triads, a superset including triads pulled from supplemental information and in-text examples across the literature, and others that we adapted or created (see SI for the full list of stimuli and sources).
+We included 105 such triads, a superset including triads pulled from supplemental information and in-text examples across the literature, and others that we adapted or created <!--(see SI for the full list of stimuli and sources)-->.
 We selected triads on the basis of cultural familiarity in the US, Vietnam, and China.
@@
 The translations were then checked for accuracy after backtranslation to English by another fluent bilingual in each language who was naive to the original English versions.
+-->
 
@@
 ## Corpus model 
-Our general approach is to build a model of similarity that is based on collocation counts in each language.
-
-### Raw lexical co-occurrences
-To give an intuition for our model, consider the cow-grass-chicken triad: we counted how many times “cow” and “grass” co-occur within a window of text in each corpus, and compare this to how many times “cow” and “chicken” co-occur.
+<!-- Our general approach is to build a model of similarity that is based on collocation counts in each language.  -->
+
+<!-- ### Raw lexical co-occurrences -->
+<!-- To give an intuition for our model, consider the cow-grass-chicken triad: we counted how many times “cow” and “grass” co-occur within a window of text in each corpus, and compare this to how many times “cow” and “chicken” co-occur.
 Our similarity prediction is then proportional to the relative frequency of these pairs.
@@
 We then use a mixed-effects regression to evaluate how well each corpus collocate model predicts participants’ similarity judgments, across triads and languages.
-
-#### Collocate retrieval and coding
-For our English co-occurrence metric, we used the online interface of the Corpus of Contemporary American English [@COCA] to retrieve collocation counts.
+-->
+
+<!-- #### Collocate retrieval and coding -->
+<!-- For our English co-occurrence metric, we used the online interface of the Corpus of Contemporary American English [@COCA] to retrieve collocation counts.
 We recorded the raw count of times that any cue-match pair (e.g., cow-grass or cow-chicken) co-occur in a window of 19 words, which is the maximum window size in the online interface, and closest to the sentence co-occurrence metric in our VI corpus collocation counts.
-
-To determine Vietnamese co-occurrence, we used the raw frequency of sentence co-occurrences from a subset of the Vietnamese corpus in the Leipzig Corpora Collection [@VICorpus]; this corpus includes 70 million Vietnamese sentences, but our corpus data comes from a 1 million sentence subset for which co-occurrence counts are available for download.
+-->
+
+<!-- To determine Vietnamese co-occurrence, we used the raw frequency of sentence co-occurrences from a subset of the Vietnamese corpus in the Leipzig Corpora Collection [@VICorpus]; this corpus includes 70 million Vietnamese sentences, but our corpus data comes from a 1 million sentence subset for which co-occurrence counts are available for download.
 Vietnamese makes very frequent use of compositional morphology but the written language  uses spacing to delineate syllable boundaries rather than word boundaries.
@@
 Accordingly, instances of both “gà” and “gà mái” were included in our collocate count for “chicken.” Some compounds do not meet this criteria, and were excluded from collocate counts.
-For example “trái cây” (tree.fruits) includes the same syllable as the word “cây” (tree), but refers to fruit that comes from trees, not the trees themselves, and was therefore excluded from our collocate counts for “tree.”
-
-Mandarin co-occurrence was collected using the online interface of the Chinese Lexical Association Database (Lin et al, 2019).
+For example “trái cây” (tree.fruits) includes the same syllable as the word “cây” (tree), but refers to fruit that comes from trees, not the trees themselves, and was therefore excluded from our collocate counts for “tree.” -->
+
+<!-- Mandarin co-occurrence was collected using the online interface of the Chinese Lexical Association Database (Lin et al, 2019).
 Mandarin also makes frequent use of compositional morphology.
@@
 For example "門牙" (door.tooth) refers to the front tooth even though it includes the same character as the target word "門" (door), so was therefore excluded from our collocate counts for "door".
-
-#### Collocate similarity model
-From the raw co-occurrence counts of each triad, we calculated the thematic co-occurrence ratio as the number of thematic co-occurrences over the sum of thematic and taxonomic co-occurrences.
+-->
+
+<!-- #### Collocate similarity model -->
+<!-- From the raw co-occurrence counts of each triad, we calculated the thematic co-occurrence ratio as the number of thematic co-occurrences over the sum of thematic and taxonomic co-occurrences.
 We did this for both the English and Vietnamese corpus co-occurrence counts.
@@
 We then tested whether these simple relative frequency models predict US and VN responding.
-
-### Cosine distance of word vectors
+-->
+
+<!-- ### Cosine distance of word vectors -->
 To give an intuition for our model, consider again the cow-grass-chicken triad: we retrieved word vectors for "cow" and "grass", and calculate the cosine distance between these vectors.
@@
 
-#### Collocate retrieval
+#### Word vector retrieval
 We use the fastText pre-trained models of English, Mandarin, and Vietnamese in @Grave2018.
@@
 
-#### Collocate similarity model
+#### Similarity model
 From the word vectors, we calculated the cosine distance between each cue-thematic match (thematic cosine distance) and cue-taxonomic match (taxonomic cosine distance), using the spatial.distance.cosine function from the SciPy package [@2020SciPy].
@@
 
-```{r warning=FALSE, cache = TRUE, include=FALSE, paged.print=TRUE}
+```{r country, warning=FALSE, cache = TRUE, include=FALSE, paged.print=TRUE}
 df.country <- df %>%
@@
 ```
-The group means of proportion of thematic response in mainland China is the highest (M = `r round((df.country_sum %>% filter(country == "China"))$mean_theme_resp_percent, 2)`, SD = `r round((df.country_sum %>% filter(country == "China"))$sd_theme_resp_percent, 2)`), followed by the groups means in Vietnam (M = `r round((df.country_sum %>% filter(country == "Vietnam"))$mean_theme_resp_percent, 2)`, SD = `r round((df.country_sum %>% filter(country == "Vietnam"))$sd_theme_resp_percent, 2)`), which is slightly higher than that of the US (M = `r round((df.country_sum %>% filter(country == "US"))$mean_theme_resp_percent, 2)`, SD = `r round((df.country_sum %>% filter(country == "US"))$sd_theme_resp_percent, 2)`) (Fig 1).
-
-```{r echo=FALSE, warning=FALSE, cache = TRUE, fig.cap="Proportion of thematic responses by country."}
+The group means of proportion of thematic response in mainland China is the highest (M = `r round((df.country_sum %>% filter(country == "China"))$mean_theme_resp_percent, 2)`, SD = `r round((df.country_sum %>% filter(country == "China"))$sd_theme_resp_percent, 2)`), followed by the groups means in Vietnam (M = `r round((df.country_sum %>% filter(country == "Vietnam"))$mean_theme_resp_percent, 2)`, SD = `r round((df.country_sum %>% filter(country == "Vietnam"))$sd_theme_resp_percent, 2)`), which is slightly higher than that of the US (M = `r round((df.country_sum %>% filter(country == "US"))$mean_theme_resp_percent, 2)`, SD = `r round((df.country_sum %>% filter(country == "US"))$sd_theme_resp_percent, 2)`) (Figure 1).
+
+```{r echo=FALSE, warning=FALSE, cache = TRUE, fig.env="figure", fig.align = "center", fig.cap="Proportion of thematic responses by country."}
 
@@
 ## 2. Can the differences in similarity judgments between English, Mandarin and Vietnamese speakers be explained by variation in lexical statistics?
-### Is responding in each cultural context predicted by the corresponding lexical statistics (raw co-occurrences)? 
-#### Raw lexical co-occurrences
-
-To test whether variation in lexical co-occurrence can explain differences in similarity judgments between US and Vietnam participants, we compare logistic mixed-effects regression models fit to the thematic responding data from each country separately.
+### Is responding in each cultural context predicted by lexical statistics? 
+To test whether variation in lexical statistics can explain differences in similarity judgments between US and Vietnam participants, we compare logistic mixed-effects regression models fit to the thematic responding data from each country separately.
 We first ask how well each corpus model (English, Vietnamese, or Mandarin) predicts similarity judgments by speakers of the corresponding language (US, Vietnam, or China).
-To do this, we use a mixed-effects logistic regression to predict triad responses (0=taxonomic or 1=thematic) with corpus prediction (proportion thematic co-occurrence or cosine distance) as a fixed effect and participant and triad as random effects.
-
-```{r US responding predicted by each corpus model raw co-occurrences, warning=FALSE, include=F, cache = TRUE}
-# English 
-fit.EN_US = glmer(responses_theme ~ theme_freq_prop_E + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "US", !(triad %in% triads_omit)), 
-          family="binomial")
-summary(fit.EN_US)
-fit.EN_US.anova = Anova(fit.EN_US, type = 3)
-
-#Vietnamese
-fit.VI_US = glmer(responses_theme ~ theme_freq_prop_V + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "US", !(triad %in% triads_omit)), 
-          family="binomial")
-summary(fit.VI_US)
-fit.VI_US.anova = Anova(fit.VI_US, type = 3)
-
-#Mandarin
-fit.ZH_US = glmer(responses_theme ~ theme_freq_prop_M + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "US", !(triad %in% triads_omit)), 
-          family="binomial")
-summary(fit.ZH_US)
-fit.ZH_US.anova = Anova(fit.ZH_US, type = 3)
-```
-
-```{r VN responding predicted by each corpus model raw co-occurrences, warning=FALSE, include=F, cache = TRUE}
-# English 
-fit.EN_VN = glmer(responses_theme ~ theme_freq_prop_E + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "Vietnam", !(triad %in% triads_omit)), 
-          family="binomial")
-summary(fit.EN_VN)
-fit.EN_VN.anova = Anova(fit.EN_VN, type = 3)
-
-#Vietnamese
-fit.VI_VN = glmer(responses_theme ~ theme_freq_prop_V + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "Vietnam", !(triad %in% triads_omit)), 
-          family="binomial")
-summary(fit.VI_VN)
-fit.VI_VN.anova = Anova(fit.VI_VN, type = 3)
-
-#Mandarin
-fit.ZH_VN = glmer(responses_theme ~ theme_freq_prop_M + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "Vietnam", !(triad %in% triads_omit)), 
-          family="binomial")
-summary(fit.ZH_VN)
-fit.ZH_VN.anova = Anova(fit.ZH_VN, type = 3)
-```
-
-```{r CN responding predicted by each corpus model raw co-occurrences, warning=FALSE, include=F, cache = TRUE}
-#English
-fit.EN_CN = glmer(responses_theme ~ theme_freq_prop_E + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "China", !(triad %in% triads_omit)), 
-          family="binomial")
-summary(fit.EN_CN)
-fit.EN_CN.anova = Anova(fit.EN_CN, type = 3)
-
-#Vietnamese
-fit.VI_CN = glmer(responses_theme ~ theme_freq_prop_V + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "China", !(triad %in% triads_omit)), 
-          family="binomial")
-summary(fit.VI_CN)
-fit.VI_CN.anova = Anova(fit.VI_CN, type = 3)
-
-#Mandarin
-fit.ZH_CN = glmer(responses_theme ~ theme_freq_prop_M + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "China", !(triad %in% triads_omit)), 
-          family="binomial")
-summary(fit.ZH_CN)
-fit.ZH_CN.anova = Anova(fit.ZH_CN, type = 3)
-```
-
-```{r calculate range of beta statistics, warning=F, include=F}
-beta.single_corpus_freq <- c(
-  round(fixef(fit.EN_US)["theme_freq_prop_E"], 2),
-  round(fixef(fit.VI_US)["theme_freq_prop_V"], 2), 
-  round(fixef(fit.ZH_US)["theme_freq_prop_M"], 2),
-
-  round(fixef(fit.EN_CN)["theme_freq_prop_E"], 2),
-  round(fixef(fit.VI_CN)["theme_freq_prop_V"], 2), 
-  round(fixef(fit.ZH_CN)["theme_freq_prop_M"], 2),
-
-  round(fixef(fit.EN_VN)["theme_freq_prop_E"], 2),
-  round(fixef(fit.VI_VN)["theme_freq_prop_V"], 2), 
-  round(fixef(fit.ZH_VN)["theme_freq_prop_M"], 2)
-
-)
-```
-We found that all corpora are significant predictors of all cultural context responding, with p < 0.05 and $\beta$ from `r min(beta.single_corpus_freq)` - `r max(beta.single_corpus_freq)`.
-(For a full report, see Appendix.)
-
-This suggests a strong shared similarity signal across the languages.
-
-#### Cosine distances of fastText word vectors
+To do this, we use a mixed-effects logistic regression to predict triad responses (0=taxonomic or 1=thematic) with corpus prediction (proportion of cosine distance) as a fixed effect and participant and triad as random effects.
 
@@
 
-```{r calculate range of beta statistics, warning=F, include=F}
+```{r calculate range of beta statistics for cosine, warning=F, include=F}
 beta.single_corpus_cos <- c(
@@
   round(fixef(fit.VI_VN_cos)["theme_cosine_prop_V"], 2), 
-  round(fixef(fit.ZH_VN_cos)["theme_cosine_prop_M"], 2),
-
+  round(fixef(fit.ZH_VN_cos)["theme_cosine_prop_M"], 2)
 )
@@
 
-Similar to the results from the analysis with raw lexical co-occurrences, we found that all corpora are significant predictors of all cultural context responding, with p < 0.05 and $\beta$ from `r min(beta.single_corpus_cos)` - `r max(beta.single_corpus_cos)`.
+We found that all corpora are significant predictors of all cultural context responding, with p<0.05 and $\beta$ from `r min(beta.single_corpus_cos)` to `r max(beta.single_corpus_cos)`.
 (For a full report, see Appendix.)
 
-### Is responding in each cultural context __best__ predicted by the corresponding corpus's lexical statistics (raw co-occurrences), as opposed to the other two corpora?
+### Is responding in each cultural context best predicted by the corresponding corpus's lexical statistics, as opposed to the other two corpora?
 Next, we directly compare the corpus models by including both as fixed effects in three mixed-effect regressions (predicting US, Vietnam and China responding) with the same random effects as above.
@@
 
-#### Raw co-occurrences
-
-```{r Eng-Vie-Mand lexical co-occ predicting US, warning=FALSE, include=F, cache = TRUE}
-# ADDITION: adding theme_freq_prop_M, 
-#raw co-occurrences
-#linear mixed model with ALL corpora as predictors for each population.
-fit.ENVIZH_US = glmer(responses_theme ~ 
-                      theme_freq_prop_E + theme_freq_prop_V + theme_freq_prop_M +
-                      (1 | subject) + (1 | triad), 
-                    data = df %>% filter(country == "US", !(triad %in% triads_omit)),
-                    family="binomial")
-summary(fit.ENVIZH_US)
-fit.ENVIZH_US.anova = Anova(fit.ENVIZH_US, type = 3)
-fit.ENVIZH_US.anova
-```
-For US responding: only English (EN) corpus is a significant predictor.
-EN corpus: $\beta$ = `r round(fixef(fit.ENVIZH_US)["theme_freq_prop_E"], 2)`, $\chi^2$(`r fit.ENVIZH_US.anova["theme_freq_prop_E", "Df"]`) = `r round(fit.ENVIZH_US.anova["theme_freq_prop_E", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_US.anova["theme_freq_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_US.anova["theme_freq_prop_E", "Pr(>Chisq)"], 3)), "< .001")`.
-VI corpus: $\beta$ = `r round(fixef(fit.ENVIZH_US)["theme_freq_prop_V"], 2)`, $\chi^2$(`r fit.ENVIZH_US.anova["theme_freq_prop_V", "Df"]`) = `r round(fit.ENVIZH_US.anova["theme_freq_prop_V", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_US.anova["theme_freq_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_US.anova["theme_freq_prop_V", "Pr(>Chisq)"], 3)), "< .001")`.
-ZH corpus: $\beta$ = `r round(fixef(fit.ENVIZH_US)["theme_freq_prop_M"], 2)`, $\chi^2$(`r fit.ENVIZH_US.anova["theme_freq_prop_M", "Df"]`) = `r round(fit.ENVIZH_US.anova["theme_freq_prop_M", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_US.anova["theme_freq_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_US.anova["theme_freq_prop_M", "Pr(>Chisq)"], 3)), "< .001")`.
-
-```{r Eng-Vie-Mand lexical co-occ predicting VN, warning=FALSE, include=F, cache = TRUE}
-fit.ENVIZH_VN = glmer(responses_theme ~ 
-                      theme_freq_prop_V + theme_freq_prop_E + theme_freq_prop_M +
-                      (1 | subject) + (1 | triad), 
-                    data = df %>% filter(country == "Vietnam", !(triad %in% triads_omit)),
-                    family="binomial")
-summary(fit.ENVIZH_VN)
-fit.ENVIZH_VN.anova = Anova(fit.ENVIZH_VN, type = 3)
-fit.ENVIZH_VN.anova
-```
-For Vietnam responding: only Mandarin (ZH) corpus is a significant predictor.
-EN corpus: $\beta$ = `r round(fixef(fit.ENVIZH_VN)["theme_freq_prop_E"], 2)`, $\chi^2$(`r fit.ENVIZH_VN.anova["theme_freq_prop_E", "Df"]`) = `r round(fit.ENVIZH_VN.anova["theme_freq_prop_E", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_VN.anova["theme_freq_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_VN.anova["theme_freq_prop_E", "Pr(>Chisq)"], 3)), "< .001")`.
-ZH corpus: $\beta$ = `r round(fixef(fit.ENVIZH_VN)["theme_freq_prop_M"], 2)`, $\chi^2$(`r fit.ENVIZH_VN.anova["theme_freq_prop_M", "Df"]`) = `r round(fit.ENVIZH_VN.anova["theme_freq_prop_M", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_VN.anova["theme_freq_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_VN.anova["theme_freq_prop_M", "Pr(>Chisq)"], 3)), "< .001")`.VI corpus: $\beta$ = `r round(fixef(fit.ENVIZH_VN)["theme_freq_prop_V"], 2)`, $\chi^2$(`r fit.ENVIZH_VN.anova["theme_freq_prop_V", "Df"]`) = `r round(fit.ENVIZH_VN.anova["theme_freq_prop_V", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_VN.anova["theme_freq_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_VN.anova["theme_freq_prop_V", "Pr(>Chisq)"], 3)), "< .001")`.
-
-```{r Eng-Vie-Mand lexical co-occ predicting CN, warning=FALSE, include=F, cache = TRUE}
-fit.ENVIZH_CN = glmer(responses_theme ~ 
-                      theme_freq_prop_M + theme_freq_prop_E + theme_freq_prop_V +
-                      (1 | subject) + (1 | triad), 
-                    data = df %>% filter(country == "China", !(triad %in% triads_omit)),
-                    family="binomial")
-summary(fit.ENVIZH_CN)
-fit.ENVIZH_CN.anova = Anova(fit.ENVIZH_CN, type = 3)
-fit.ENVIZH_CN.anova
-```
-For China responding: only Mandarin (ZH) corpus is a significant predictor.
-ZH corpus: $\beta$ = `r round(fixef(fit.ENVIZH_CN)["theme_freq_prop_M"], 2)`, $\chi^2$(`r fit.ENVIZH_CN.anova["theme_freq_prop_M", "Df"]`) = `r round(fit.ENVIZH_CN.anova["theme_freq_prop_M", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_CN.anova["theme_freq_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_CN.anova["theme_freq_prop_M", "Pr(>Chisq)"], 3)), "< .001")`.
-EN corpus: $\beta$ = `r round(fixef(fit.ENVIZH_CN)["theme_freq_prop_E"], 2)`, $\chi^2$(`r fit.ENVIZH_CN.anova["theme_freq_prop_E", "Df"]`) = `r round(fit.ENVIZH_CN.anova["theme_freq_prop_E", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_CN.anova["theme_freq_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_CN.anova["theme_freq_prop_E", "Pr(>Chisq)"], 3)), "< .001")`.
-VI corpus: $\beta$ = `r round(fixef(fit.ENVIZH_CN)["theme_freq_prop_V"], 2)`, $\chi^2$(`r fit.ENVIZH_CN.anova["theme_freq_prop_V", "Df"]`) = `r round(fit.ENVIZH_CN.anova["theme_freq_prop_V", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_CN.anova["theme_freq_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_CN.anova["theme_freq_prop_V", "Pr(>Chisq)"], 3)), "< .001")`.
-
-```{r echo=FALSE, warning = FALSE, cache = TRUE, fig.cap = "Fixed effect sizes of each corpus when included as a predictor for China, US, and Vietnam responding, respectively.
-The English corpus is the best predictor for US response, and the Mandarin corpus is the best predictor for China response."}
-coeff_value_freq <- c(fixef(fit.ENVIZH_US)["theme_freq_prop_M"],
-                 fixef(fit.ENVIZH_US)["theme_freq_prop_E"], 
-                 fixef(fit.ENVIZH_US)["theme_freq_prop_V"],
-                 fixef(fit.ENVIZH_VN)["theme_freq_prop_M"],
-                 fixef(fit.ENVIZH_VN)["theme_freq_prop_E"],
-                 fixef(fit.ENVIZH_VN)["theme_freq_prop_V"], 
-                 fixef(fit.ENVIZH_CN)["theme_freq_prop_M"],
-                 fixef(fit.ENVIZH_CN)["theme_freq_prop_E"], 
-                 fixef(fit.ENVIZH_CN)["theme_freq_prop_V"])
-
-se_value_freq <- c(summary(fit.ENVIZH_US)$coef["theme_freq_prop_M", "Std. Error"], 
-              summary(fit.ENVIZH_US)$coef["theme_freq_prop_E", "Std. Error"],
-              summary(fit.ENVIZH_US)$coef["theme_freq_prop_V", "Std. Error"], 
-              summary(fit.ENVIZH_VN)$coef["theme_freq_prop_M", "Std. Error"], 
-              summary(fit.ENVIZH_VN)$coef["theme_freq_prop_E", "Std. Error"],
-              summary(fit.ENVIZH_VN)$coef["theme_freq_prop_V", "Std. Error"],
-              summary(fit.ENVIZH_CN)$coef["theme_freq_prop_M", "Std. Error"], 
-              summary(fit.ENVIZH_CN)$coef["theme_freq_prop_E", "Std. Error"],
-              summary(fit.ENVIZH_CN)$coef["theme_freq_prop_V", "Std. Error"])
-
-country_value <- c(rep("US", 3),
-                   rep("VN", 3),
-                   rep("CN", 3))
-
-corpus_value <- c(rep(c("ZH", "EN", "VI"), 3))
-
-df.USVNCN_coeffs_freq <- data.frame(country_value, corpus_value, coeff_value_freq, se_value_freq) %>%
-  mutate(corpus_value = factor(corpus_value, levels=c("ZH", "EN", "VI")))
-
-plot.coeffs_freq <- ggplot(data = df.USVNCN_coeffs_freq, 
-       mapping = aes(x = country_value, y = coeff_value_freq, fill = corpus_value)) +
-  geom_bar(position="dodge", stat="identity") +
-  geom_errorbar(aes(ymin= coeff_value_freq - se_value_freq, ymax = coeff_value_freq + se_value_freq), width=.2,
-                 position=position_dodge(.9)) +
-  labs(x = "Country", y = "Fixed effect size", fill = "Corpus") + 
-  scale_x_discrete(labels=c("CN" = "China", "US" = "US", "VN" = "Vietnam")) + 
-  scale_fill_manual(values=c("#D63230", "#1C77C3", "#F39237")) + 
-  ggtitle('a')
-
-```
-
-```{r freq model comparison, include=FALSE, cache = TRUE}
-fit.US_freq_compare = anova(fit.ENVIZH_US, fit.EN_US, type = 3)
-fit.VN_freq_compare = anova(fit.ENVIZH_VN, fit.VI_VN, type = 3)
-fit.CN_freq_compare = anova(fit.ENVIZH_CN, fit.ZH_CN, type = 3)
-```
-
-We observed some level of language specificity from this analysis.
-The English corpus is the only significant predictor for US responding, and the Mandarin corpus is the only significant predictor for China response.
-However, against our prediction, the Vietnamese corpus was not a significant predictor for Vietnam responding when other corpora were included.
-(Figure 2a).
-
-<!-- Nonetheless, we found that language specificity alone does not explain our results.
-We used an ANOVA to compare the model with only the corresponding corpus, and the model with all 3 corpora for each cultural context.
-We found that in all three cases (US, China, Vietnam), adding the other two corpora produces a significantly better fit than the identical model without the additional corpora, and only the corresponding corpus included as a predictor (US response: $\chi^2$(`r fit.US_freq_compare["fit.ENVIZH_US", "Df"]`) = `r round(fit.US_freq_compare["fit.ENVIZH_US", "Chisq"], 2)`, p `r ifelse( fit.US_freq_compare["fit.ENVIZH_US", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.US_freq_compare["fit.ENVIZH_US", "Pr(>Chisq)"], 3)), "< .001")`; Vietnam response: $\chi^2$(`r fit.VN_freq_compare["fit.ENVIZH_VN", "Df"]`) = `r round(fit.VN_freq_compare["fit.ENVIZH_VN", "Chisq"], 2)`, p `r ifelse( fit.VN_freq_compare["fit.ENVIZH_VN", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.VN_freq_compare["fit.ENVIZH_VN", "Pr(>Chisq)"], 3)), "< .001")`; China response: $\chi^2$(`r fit.CN_freq_compare["fit.ENVIZH_CN", "Df"]`) = `r round(fit.CN_freq_compare["fit.ENVIZH_CN", "Chisq"], 2)`, p `r ifelse( fit.CN_freq_compare["fit.ENVIZH_CN", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.CN_freq_compare["fit.ENVIZH_CN", "Pr(>Chisq)"], 3)), "< .001")`).
--->
-
-#### Cosine distances of fastText word vectors
-
 ```{r Eng-Vie-Mand cosine similarities predicting US-VN-CN, warning=FALSE, include=FALSE}
+df <- read.csv("../../../data/data_USCNVN_ENZHVI.csv")
+
 ## English/Vietnamese/Mandarin comparison
@@
 
-For US responding: only English (EN) corpus is a significant predictor.
+For US responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are all significant predictors.
 EN corpus: $\beta$ = `r round(fixef(fit.ENVIZH_US_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.ENVIZH_US_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.ENVIZH_US_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_US_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_US_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"], 3)), "< .001")`.
-VI corpus: $\beta$ = `r round(fixef(fit.ENVIZH_US_cos)["theme_cosine_prop_V"], 2)`, $\chi^2$(`r fit.ENVIZH_US_cos.anova["theme_cosine_prop_V", "Df"]`) = `r round(fit.ENVIZH_US_cos.anova["theme_cosine_prop_V", "Chisq"], 2)`, p = `r ifelse( fit.ENVIZH_US_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_US_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"], 3)), "< .001")`.
-ZH corpus: $\beta$ = `r round(fixef(fit.ENVIZH_US_cos)["theme_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ENVIZH_US_cos.anova["theme_cosine_prop_M", "Df"]`) = `r round(fit.ENVIZH_US_cos.anova["theme_cosine_prop_M", "Chisq"], 2)`, p = `r ifelse( fit.ENVIZH_US_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_US_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"], 3)), "< .001")`.
-
-For Vietnam responding: only Vietnamese (VI) and Mandarin (ZH) corpus are significant predictors.
-EN corpus: $\beta$ = `r round(fixef(fit.ENVIZH_VN_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.ENVIZH_VN_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p = `r ifelse( fit.ENVIZH_VN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"], 3)), "< .001")`.
-VI corpus: $\beta$ = `r round(fixef(fit.ENVIZH_VN_cos)["theme_cosine_prop_V"], 2)`, $\chi^2$(`r fit.ENVIZH_VN_cos.anova["theme_cosine_prop_V", "Df"]`) = `r round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_V", "Chisq"], 2)`, p = `r ifelse( fit.ENVIZH_VN_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"], 3)), "< .001")`.
-ZH corpus: $\beta$ = `r round(fixef(fit.ENVIZH_VN_cos)["theme_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ENVIZH_VN_cos.anova["theme_cosine_prop_M", "Df"]`) = `r round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_M", "Chisq"], 2)`, p = `r ifelse( fit.ENVIZH_VN_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"], 3)), "< .001")`.
-
-For China responding: only Mandarin (ZH) and English (EN) corpus are significant predictors.
-EN corpus: $\beta$ = `r round(fixef(fit.ENVIZH_CN_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.ENVIZH_CN_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.ENVIZH_CN_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p = `r ifelse( fit.ENVIZH_CN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_CN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"], 3)), "< .001")`.
-VI corpus: $\beta$ = `r round(fixef(fit.ENVIZH_CN_cos)["theme_cosine_prop_V"], 2)`, $\chi^2$(`r fit.ENVIZH_CN_cos.anova["theme_cosine_prop_V", "Df"]`) = `r round(fit.ENVIZH_CN_cos.anova["theme_cosine_prop_V", "Chisq"], 2)`, p = `r ifelse( fit.ENVIZH_CN_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_CN_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"], 3)), "< .001")`.
-ZH corpus: $\beta$ = `r round(fixef(fit.ENVIZH_CN_cos)["theme_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ENVIZH_CN_cos.anova["theme_cosine_prop_M", "Df"]`) = `r round(fit.ENVIZH_CN_cos.anova["theme_cosine_prop_M", "Chisq"], 2)`, p = `r ifelse( fit.ENVIZH_CN_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_CN_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"], 3)), "< .001")`.
-
-Again, we observed some level of language specificity from this analysis.
-Each corpus is a significant predictor for responding in the corresponding cultural context.
-The English corpus is the best (and only) predictor for US responding, and the Mandarin corpus is the best predictor for China response.
-While this is not the case with the Vietnamese corpus and the Vietnam responding, the Vietnamese corpus is still a significant predictor for the Vietnam responding (Figure 2b).
-
-```{r echo=FALSE, warning = FALSE, fig.cap = "Fixed effect sizes of each corpus when included as a predictor for China, US, and Vietnam responding, respectively.
-The English corpus is the best predictor for US response, and the Mandarin corpus is the best predictor for China response."}
+VI corpus: $\beta$ = `r round(fixef(fit.ENVIZH_US_cos)["theme_cosine_prop_V"], 2)`, $\chi^2$(`r fit.ENVIZH_US_cos.anova["theme_cosine_prop_V", "Df"]`) = `r round(fit.ENVIZH_US_cos.anova["theme_cosine_prop_V", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_US_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_US_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"], 3)), "< .001")`.
+ZH corpus: $\beta$ = `r round(fixef(fit.ENVIZH_US_cos)["theme_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ENVIZH_US_cos.anova["theme_cosine_prop_M", "Df"]`) = `r round(fit.ENVIZH_US_cos.anova["theme_cosine_prop_M", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_US_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_US_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"], 3)), "< .001")`.
+
+For Vietnam responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are all significant predictors.
+EN corpus: $\beta$ = `r round(fixef(fit.ENVIZH_VN_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.ENVIZH_VN_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_VN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"], 3)), "< .001")`.
+VI corpus: $\beta$ = `r round(fixef(fit.ENVIZH_VN_cos)["theme_cosine_prop_V"], 2)`, $\chi^2$(`r fit.ENVIZH_VN_cos.anova["theme_cosine_prop_V", "Df"]`) = `r round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_V", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_VN_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"], 3)), "< .001")`.
+ZH corpus: $\beta$ = `r round(fixef(fit.ENVIZH_VN_cos)["theme_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ENVIZH_VN_cos.anova["theme_cosine_prop_M", "Df"]`) = `r round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_M", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_VN_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"], 3)), "< .001")`.
+
+For China responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are all significant predictors.
+EN corpus: $\beta$ = `r round(fixef(fit.ENVIZH_CN_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.ENVIZH_CN_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.ENVIZH_CN_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_CN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_CN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"], 3)), "< .001")`.
+VI corpus: $\beta$ = `r round(fixef(fit.ENVIZH_CN_cos)["theme_cosine_prop_V"], 2)`, $\chi^2$(`r fit.ENVIZH_CN_cos.anova["theme_cosine_prop_V", "Df"]`) = `r round(fit.ENVIZH_CN_cos.anova["theme_cosine_prop_V", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_CN_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_CN_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"], 3)), "< .001")`.
+ZH corpus: $\beta$ = `r round(fixef(fit.ENVIZH_CN_cos)["theme_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ENVIZH_CN_cos.anova["theme_cosine_prop_M", "Df"]`) = `r round(fit.ENVIZH_CN_cos.anova["theme_cosine_prop_M", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_CN_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_CN_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"], 3)), "< .001")`.
+
+We observed some level of language specificity from this analysis.
+The English corpus is the best predictor for US responding, and the Mandarin corpus is the best predictor for China response.
+While this is not the case with the Vietnamese corpus and the Vietnam responding, the Vietnamese corpus is still a significant predictor for the Vietnam responding (Figure 2).
+
+```{r echo=FALSE, warning = FALSE}
 coeff_value_cos <- c(fixef(fit.ENVIZH_US_cos)["theme_cosine_prop_E"],
@@
 
-df.USVNCN_coeffs_cos <- data.frame(country_value, corpus_value, coeff_value_freq, se_value_freq) %>%
+df.USVNCN_coeffs_cos <- data.frame(country_value, corpus_value, coeff_value_cos, se_value_cos) %>%
   mutate(corpus_value = factor(corpus_value, levels=c("ZH", "EN", "VI")))
@@
   scale_x_discrete(labels=c("CN" = "China", "US" = "US", "VN" = "Vietnam")) + 
-  scale_fill_manual(values=c("#D63230", "#1C77C3", "#F39237")) + 
-  ggtitle('b')
-```
-
-```{r echo=FALSE, warning=FALSE, cache = TRUE, fig.cap="Fixed effect sizes of each corpus when included as a predictor for China, US, and Vietnam responding, respectively (left: raw lexical co-occurrences, right: cosine similarity).
+  scale_fill_manual(values=c("#D63230", "#1C77C3", "#F39237"))
+```
+
+```{r echo=FALSE, warning=FALSE, cache = TRUE, fig.env = "figure", fig.align = "center", set.cap.width=T, num.cols.cap=1, fig.cap="Fixed effect sizes of each corpus lexical statistics (cosine distance proportion) when included as a predictor for China, US, and Vietnam responding, respectively.
 The English corpus is the best predictor for US response, and the Mandarin corpus is the best predictor for China response."}
-plot.coeffs_freq + plot.coeffs_cos
+#plot.coeffs_freq + 
+  plot.coeffs_cos
 ```
@@
 We used an ANOVA to compare the model with only the corresponding corpus, and the model with all 3 corpora for each cultural context.
-We found that in all three cases (US, China, Vietnam), adding the other two corpora produces a significantly better fit than the identical model without the additional corpora, and only the corresponding corpus included as a predictor (US response: $\chi^2$(`r fit.US_cos_compare["fit.ENVIZH_US_cos", "Df"]`) = `r round(fit.US_cos_compare["fit.ENVIZH_US_cos", "Chisq"], 2)`, p = `r ifelse( fit.US_cos_compare["fit.ENVIZH_US_cos", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.US_cos_compare["fit.ENVIZH_US_cos", "Pr(>Chisq)"], 3)), "< .001")`; Vietnam response: $\chi^2$(`r fit.VN_cos_compare["fit.ENVIZH_VN_cos", "Df"]`) = `r round(fit.VN_cos_compare["fit.ENVIZH_VN_cos", "Chisq"], 2)`, p = `r ifelse( fit.VN_cos_compare["fit.ENVIZH_VN_cos", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.VN_cos_compare["fit.ENVIZH_VN_cos", "Pr(>Chisq)"], 3)), "< .001")`; China response: $\chi^2$(`r fit.CN_cos_compare["fit.ENVIZH_CN_cos", "Df"]`) = `r round(fit.CN_cos_compare["fit.ENVIZH_CN_cos", "Chisq"], 2)`, p = `r ifelse( fit.CN_cos_compare["fit.ENVIZH_VN_cos", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.CN_cos_compare["fit.ENVIZH_VN_cos", "Pr(>Chisq)"], 3)), "< .001")`).
-
-```{r add linguistic model to Ji et al., include=FALSE, eval = F}
-# this is probably similar to Q3
-fit.country = glmer(responses_theme ~ country + (1 | subject) + (1 | triad), 
-                           data = df %>% filter(country != "Vietnam"), 
-                           family = "binomial")
-
-fit.country_corpus = glmer(responses_theme ~ country + theme_cosine_prop_E + theme_cosine_prop_M + (1 | subject) + (1 | triad), 
-                           data = df %>% filter(country != "Vietnam"), 
-                           family = "binomial")
-
-fit.add_corpus <- anova(fit.country, fit.country_corpus, type = 3)
-
-```
-
-Our approach would be to compare a model that only includes country (US or China) as a fixed effect with one that also includes English and Chinese corpus data.
-Our previous model with an intercept per subject and one per triad, as well as by-triad random slopes for country to account for variation in the country effect across triads fails to converge with the more complex model, so we include a simpler random effect structure with an intercept per subject and one per triad in both the basic and more complex model.
-We compare this model with an identical model but including Chinese and English corpus cosine distance proportion prediction.
-We found that adding English and Chinese corpus data produces a significantly better fit than the identical model without English and Chinese corpus data as predictors ($\chi^2$(`r fit.add_corpus["fit.country_corpus", "Df"]`) = `r round(fit.add_corpus["fit.country_corpus", "Chisq"], 2)`, p = < .001.
-This suggests that including corpus data would better model the cross-cultural differences in similarity judgment in this study as well as similar studies.
+We found that in all three cases (US, China, Vietnam), adding the other two corpora produces a significantly better fit than the identical model without the additional corpora, and only the corresponding corpus included as a predictor (US response: $\chi^2$(`r fit.US_cos_compare["fit.ENVIZH_US_cos", "Df"]`) = `r round(fit.US_cos_compare["fit.ENVIZH_US_cos", "Chisq"], 2)`, p `r ifelse( fit.US_cos_compare["fit.ENVIZH_US_cos", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.US_cos_compare["fit.ENVIZH_US_cos", "Pr(>Chisq)"], 3)), "< .001")`; Vietnam response: $\chi^2$(`r fit.VN_cos_compare["fit.ENVIZH_VN_cos", "Df"]`) = `r round(fit.VN_cos_compare["fit.ENVIZH_VN_cos", "Chisq"], 2)`, p `r ifelse( fit.VN_cos_compare["fit.ENVIZH_VN_cos", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.VN_cos_compare["fit.ENVIZH_VN_cos", "Pr(>Chisq)"], 3)), "< .001")`; China response: $\chi^2$(`r fit.CN_cos_compare["fit.ENVIZH_CN_cos", "Df"]`) = `r round(fit.CN_cos_compare["fit.ENVIZH_CN_cos", "Chisq"], 2)`, p `r ifelse( fit.CN_cos_compare["fit.ENVIZH_VN_cos", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.CN_cos_compare["fit.ENVIZH_VN_cos", "Pr(>Chisq)"], 3)), "< .001")`).
 
 ## 3. Does similarity reasoning differ across cultures, only the input to it, or both?
-Does adding country and interaction term with the corresponding corpus improves the model?
-
-```{r, include = F}
+Our analysis shows that lexical statistics of each corpus is a significant predictor for similarity judgement in the corresponding cultural context, even without the addition of the other two corpora.
+Assuming that lexical statistics is a good proxy for environmental statistics, we take the above result as evidence that cross-cultural differences in input to the process of similarity judgement at least partially drives cross-cultural similarity judgement differences.
+However, it is still an open question whether the nature of similarity judgement (for e.g., the notion of similarity) itself differs across cultures and contributes to cross-cultural differences in similarity judgement responding.
+In an alternative hypothesis, the cross-cultural differences in similarity judgement observed is driven by not only the input, but also an interaction between cultural-specific nature of similarity judgement and input.
+To test this hypothesis, we operationalize cultural-specific nature of similarity judgement as country context, and input to similarity judgement as the corresponding corpus statistics.
+We then compare a model that includes country, corresponding corpus statistics and their interaction as fixed effects (R syntax: responses ~ corresponding_corpus * country + (1|triad) + (1|subject)) to a model with only the corresponding corpus statistics as the fixed effect (R syntax: responses ~ corresponding_corpus + (1|triad) + (1|subject))
+
+```{r add corresponding language, include = F}
 df <- df %>%
@@
 
-```{r country language interaction in raw co-occurrences, include = F}
-fit.language = glmer(responses_theme ~ theme_freq_prop_corr_lang + (1 | subject) + (1 | triad), 
-          data = df %>% filter(!(triad %in% triads_omit)),  
-          family="binomial")
-summary(fit.language)
-fit.language.anova = Anova(fit.language, type = 3)
-fit.language.anova
-
-fit.country_language = glmer(responses_theme ~ theme_freq_prop_corr_lang * country + (1 | subject) + (1 | triad), 
-          data = df %>% filter(!(triad %in% triads_omit)),  
-          family="binomial")
-summary(fit.country_language)
-fit.country_language.anova = Anova(fit.country_language, type = 3)
-fit.country_language.anova
-
-fit.country_language_compare = anova(fit.language, fit.country_language, type = 3)
-fit.country_language_compare
-```
+<!-- ```{r country language interaction in raw co-occurrences, include = F} -->
+<!-- fit.language = glmer(responses_theme ~ theme_freq_prop_corr_lang + (1 | subject) + (1 | triad),  -->
+<!--           data = df %>% filter(!(triad %in% triads_omit)),   -->
+<!--           family="binomial") -->
+<!-- summary(fit.language) -->
+<!-- fit.language.anova = Anova(fit.language, type = 3) -->
+<!-- fit.language.anova -->
+
+<!-- fit.country_language = glmer(responses_theme ~ theme_freq_prop_corr_lang * country + (1 | subject) + (1 | triad),  -->
+<!--           data = df %>% filter(!(triad %in% triads_omit)),   -->
+<!--           family="binomial") -->
+<!-- summary(fit.country_language) -->
+<!-- fit.country_language.anova = Anova(fit.country_language, type = 3) -->
+<!-- fit.country_language.anova -->
+
+<!-- fit.country_language_compare = anova(fit.language, fit.country_language, type = 3) -->
+<!-- fit.country_language_compare -->
+<!-- ``` -->
 
@@
 ```
-
-Adding country improves the model.
-Only country and interaction between country and corresponding corpus's lexical co-occurrence are significant predictors.
-Corresponding corpus's lexical co-occurrence is no longer a significant predictor.
+In the model containing only the corresponding corpus statistics, the corpus statistics is a significant predictor ($\beta$ = `r round(fixef(fit.language_cos)["theme_cosine_prop_corr_lang"], 2)`, $\chi^2$(`r fit.language_cos.anova["theme_cosine_prop_corr_lang", "Df"]`) = `r round(fit.language_cos.anova["theme_cosine_prop_corr_lang", "Chisq"], 2)`, p `r ifelse( fit.language_cos.anova["theme_cosine_prop_corr_lang", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.language_cos.anova["theme_cosine_prop_corr_lang", "Pr(>Chisq)"], 3)), "< .001")`).
+When adding country and interaction between country and corpus, both the corpus statistics ($\beta$ = `r round(fixef(fit.country_language_cos)["theme_cosine_prop_corr_lang"], 2)`, $\chi^2$(`r fit.country_language_cos.anova["theme_cosine_prop_corr_lang", "Df"]`) = `r round(fit.country_language_cos.anova["theme_cosine_prop_corr_lang", "Chisq"], 2)`, p `r ifelse( fit.country_language_cos.anova["theme_cosine_prop_corr_lang", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.country_language_cos.anova["theme_cosine_prop_corr_lang", "Pr(>Chisq)"], 3)), "< .001")`) and interaction between country and corpus ($\beta$ = `r round(fixef(fit.country_language_cos)["theme_cosine_prop_corr_lang:country"], 2)`, $\chi^2$(`r fit.country_language_cos.anova["theme_cosine_prop_corr_lang:country", "Df"]`) = `r round(fit.country_language_cos.anova["theme_cosine_prop_corr_lang:country", "Chisq"], 2)`, p `r ifelse( fit.country_language_cos.anova["theme_cosine_prop_corr_lang:country", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.country_language_cos.anova["theme_cosine_prop_corr_lang:country", "Pr(>Chisq)"], 3)), "< .001")`) are significant predictors.
+This suggests that there are cross-cultural differences in both input and nature of similarity judgement that drive differences in similarity judgement responding.
 
 ## 4. How general are the cross-language differences in similarity judgments we observe? Are they limited to taxonomic-thematic contrasts or do they extend to other cases?
-
-We test whether using the same approach, we can also predict filler similarity judgements. 
+Previous work using the triad task such as @Ji2004 has focused on contrasting taxonomic-thematic match preferences, driven by a theory of cross-cultural differences in notions of similarity.
+Meanwhile, our approach has shown that notions of similarity only has an effect on cross-cultural differences in similarity judgement when modulated by input, and that input as proxied by lexical statistics of the corresponding corpus by itself is a significant predictor for similarity judgement responding.
+Our approach using lexical statistics do not assume a taxonomic/thematic structure in the triads.
+Therefore, it should be possible to predict similarity judgements to triads that do not follow a taxonomic/thematic structure, such as our filler triads.
+If our approach is tractable, we should be able to repeat the above analyses to the filler triads, and find that lexical statistics of each corpus is a significant predictor for similarity judgements in filler triads of the corresponding cultural context.
+
 ```{r incorporate base freq for fillers}
@@
 
-```{r warning=FALSE, cache = TRUE, include = FALSE, paged.print=TRUE}
+```{r country summary filler, warning=FALSE, cache = TRUE, include = FALSE, paged.print=TRUE}
 df.country_filler <- df.filler %>%
@@
   summarize(word1_resp_percent = mean(responses_word1, na.rm = T))
-```
-
-```{r echo=FALSE, warning=FALSE, cache = TRUE, fig.cap="Proportion of thematic responses by country."}
-
+
+df.country_sum_filler <- df.country_filler %>%
+  group_by(country) %>%
+  summarize(mean_word1_resp_percent = mean(word1_resp_percent), 
+            sd_word1_resp_percent = sd(word1_resp_percent))
+```
+
+```{r echo=FALSE, warning=FALSE, cache = TRUE, fig.env="figure", fig.align = "center", fig.cap="Proportion of thematic responses by country."}
 #show violin plot
@@
   labs(y = "Proportion Word1 Chosen", 
-       x = "Country", 
-       color = "Country") + 
-  scale_color_manual(values=c("#D63230", "#1C77C3", "#F39237"))
-```
-
-```{r warning=FALSE, include = F, cache = TRUE, paged.print=TRUE}
+       x = "Country") + 
+  scale_color_manual(values=c("#D63230", "#1C77C3", "#F39237")) + 
+  theme(legend.position = "none")
+```
+
+```{r warning=FALSE, include = F, cache = TRUE, fig.env="figure", paged.print=TRUE}
 # df.country_sum <- df.country %>%
@@
 ``` 
-No effect of country on filler responding (Figure 4).
+For each filler triad, we randomly assigned one of the responding optiosn as 'Word1'.
+Running a mixed-effects logistic regression predict responding (Word1 or Word2) with structure equivalent to Analysis 1, we found no effect of country on filler responding (Figure 3).
 
 ### Does lexical statistics for fillers predict responding in the corresponding cultural context?
-
-#### Raw co-occurrences
-```{r US responding predicted by each corpus model raw co-occurrences for fillers, warning=FALSE,include = F}
-# English 
-fit.EN_US_filler = glmer(responses_word1 ~ word1_match_frequency_prop_E + (1 | subject) + (1 | cue), 
-          data = df.filler %>% filter(country == "US", 
-                               !(cue_id %in% fillers_omit)), 
-          family="binomial")
-summary(fit.EN_US_filler)
-fit.EN_US_filler.anova = Anova(fit.EN_US_filler, type = 3)
-
-fit.EN_US_filler.anova
-```
-
-```{r VN responding predicted by each corpus model raw co-occurrences for fillers, warning=FALSE, include = F}
-# Vietnamese
-fit.VI_VN_filler = glmer(responses_word1 ~ word1_match_frequency_prop_V + (1 | subject) + (1 | cue), 
-          data = df.filler %>% filter(country == "Vietnam", 
-                               !(cue_id %in% fillers_omit)), 
-          family="binomial")
-summary(fit.VI_VN_filler)
-fit.VI_VN_filler.anova = Anova(fit.VI_VN_filler, type = 3)
-
-fit.VI_VN_filler.anova
-```
-Yes, corpus raw co-occurrences predicts responding for both US and Vietnamese. *need to discuss with Shan to incorporate Mandarin due to a lot of empty counts*
-
-#### Cosine distance
+<!-- #### Raw co-occurrences -->
+<!-- ```{r US responding predicted by each corpus model raw co-occurrences for fillers, warning=FALSE,include = F} -->
+<!-- # English  -->
+<!-- fit.EN_US_filler = glmer(responses_word1 ~ word1_match_frequency_prop_E + (1 | subject) + (1 | cue),  -->
+<!--           data = df.filler %>% filter(country == "US",  -->
+<!--                                !(cue_id %in% fillers_omit)),  -->
+<!--           family="binomial") -->
+<!-- summary(fit.EN_US_filler) -->
+<!-- fit.EN_US_filler.anova = Anova(fit.EN_US_filler, type = 3) -->
+
+<!-- fit.EN_US_filler.anova -->
+<!-- ``` -->
+
+<!-- ```{r VN responding predicted by each corpus model raw co-occurrences for fillers, warning=FALSE, include = F} -->
+<!-- # Vietnamese -->
+<!-- fit.VI_VN_filler = glmer(responses_word1 ~ word1_match_frequency_prop_V + (1 | subject) + (1 | cue),  -->
+<!--           data = df.filler %>% filter(country == "Vietnam",  -->
+<!--                                !(cue_id %in% fillers_omit)),  -->
+<!--           family="binomial") -->
+<!-- summary(fit.VI_VN_filler) -->
+<!-- fit.VI_VN_filler.anova = Anova(fit.VI_VN_filler, type = 3) -->
+
+<!-- fit.VI_VN_filler.anova -->
+<!-- ``` -->
+<!-- Yes, corpus raw co-occurrences predicts responding for both US and Vietnamese. *need to discuss with Shan to incorporate Mandarin due to a lot of empty counts* -->
+
+<!-- #### Cosine distance -->
 ```{r US responding predicted by each corpus model cosine distances for fillers, warning=FALSE, include = F}
@@
 ```
-Corpus cosine similarities also predict responding for all cultures.
+
+```{r calculate range of beta statistics for cosine fillers, warning=F, include=F}
+beta.filler_single_corpus_cos <- c(
+  round(fixef(fit.EN_US_filler_cos)["word1_match_cosine_prop_E"], 2),
+  round(fixef(fit.ZH_CN_filler_cos)["word1_match_cosine_prop_M"], 2), 
+  round(fixef(fit.VI_VN_filler_cos)["word1_match_cosine_prop_V"], 2)
+)
+```
+Using the same mixed-effects logistic regression structure as Analysis 2, we predict responses (1=word1 or 0=word2) with corpus prediction (proportion of cosine distance) as a fixed effect and participant and triad as random effects.
+We found that in all cultural contexts, the correpsonding corpora is a significant predictor of responding, with p<0.05 and $\beta$ from `r min(beta.filler_single_corpus_cos)` to `r max(beta.filler_single_corpus_cos)`.
+(For a full report, see Appendix.)
 
@@
 We find even stronger evidence for consistency across the three groups, with substantive overlapping predictions across the corpus models, highly similar responding across the experiments, and a correspondingly high fit in cross-language comparisons between models and data.
-
-```{r include=FALSE, cache = TRUE}
-fit.country_no_triad <- glmer(responses_theme ~ country + (1 | subject), 
-                              data = df_main_analysis, 
-                              family = "binomial")
-
-fit.country = glmer(responses_theme ~ country + (1 | subject) + (country | triad), 
-                    data = df_main_analysis, 
-                    family = "binomial")
-summary(fit.country)
-
-fit.no_triad_compare <- anova(fit.country, fit.country_no_triad, type = 3)
-```
-
-There are some suggestions that the current approach can predict triad-specific cross-cultural effects.
-First of all, an ANOVA model comparison showed that adding a random effect term for varying slope by country and varying intercept by triad to the model produces a significant better fit than the identical model without this random effect term included as a predictor ($\chi^2$(`r fit.no_triad_compare["fit.country", "Df"]`) = `r round(fit.no_triad_compare["fit.country", "Chisq"], 2)`, p `r ifelse( fit.no_triad_compare["fit.country", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.no_triad_compare["fit.country", "Pr(>Chisq)"], 3)), "< .001")`)
 
@@
 
-\newpage
-
-## Two-column images
-
-You can read local images using png package for example and plot 
-it like a regular plot using grid.raster from the grid package. 
-With this method you have full control of the size of your image. **Note: Image must be in .png file format for the readPNG function to work.**
-
-You might want to display a wide figure across both columns.
-To do this, you change the `fig.env` chunk option to `figure*`.
-To align the image in the center of the page, set `fig.align` option to `center`.
-To format the width of your caption text, you set the `num.cols.cap` option to `2`.
-
-```{r 2-col-image, fig.env = "figure*", fig.pos = "h", fig.width=4, fig.height=2, fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "This image spans both columns.
-And the caption text is limited to 0.8 of the width of the document."}
-img <- png::readPNG("figs/walrus.png")
-grid::grid.raster(img)
-```
-
-## One-column images
-
-Single column is the default option, but if you want set it explicitly, set `fig.env` to `figure`. Notice that the `num.cols` option for the caption width is set to `1`.
-
-```{r image, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=2, fig.height=2, set.cap.width=T, num.cols.cap=1, fig.cap = "One column image."}
-img <- png::readPNG("figs/lab_logo_stanford.png")
-grid::grid.raster(img)
-```
-
-## R Plots
-
-You can use R chunks directly to plot graphs. And you can use latex floats in the
-fig.pos chunk option to have more control over the location of your plot on the page.
-For more information on latex placement specifiers see **[here](https://en.wikibooks.org/wiki/LaTeX/Floats,_Figures_and_Captions)**
-
-```{r plot, fig.env="figure", fig.pos = "H", fig.align = "center", fig.width=2, fig.height=2, fig.cap = "R plot" }
-x <- 0:100
-y <- 2 * (x + rnorm(length(x), sd = 3) + 3)
-
-ggplot2::ggplot(data = data.frame(x, y), 
-                aes(x = x, y = y)) + 
-  geom_point() + 
-  geom_smooth(method = "lm")
-```
-
-## Tables
-
-Number tables consecutively; place the table number and title (in
-10 point) above the table with one line space above the caption and
-one line space below it, as in Table 1. You may float
-tables to the top or bottom of a column, set wide tables across both
-columns.
-
-You can use the xtable function in the xtable package.
-
-```{r xtable, results="asis"}
-n <- 100
-x <- rnorm(n)
-y <- 2*x + rnorm(n)
-out <- lm(y ~ x)
-
-tab1 <- xtable::xtable(summary(out)$coef, digits=c(0, 2, 2, 1, 2), 
-                       caption = "This table prints across one column.")
-
-print(tab1, type="latex", comment = F, table.placement = "H")
-```
-
-# Acknowledgements
-
-Place acknowledgments (including funding information) in a section at
-the end of the paper.
-
-# References
-
-```{r}
-# References will be generated automatically by Pandoc and included here.
-# The following code is some latex to format the bibliography. Do not remove it.
-```
-
-\setlength{\parindent}{-0.1in} 
-\setlength{\leftskip}{0.125in}
-\noindent
-
 # Appendix
@@
 
-```{r}
+```{r xtable, results ="asis", fig.pos="H"}
 US_agr <- agreement::dim_icc(df_main_analysis %>% filter(country == "US"),
@@
                                      VN_agr$Inter_ICC))
-```
-
-```{r item variability, include = F}
-df.icc_item_full <- df_main_analysis %>% 
-  select(subject, triad, responses_theme) %>%
-  pivot_wider(names_from = subject, values_from = responses_theme)
-
-icc_item_full <- icc(df.icc_item_full %>% select(-triad), model = "twoway", type = "consistency", unit = "single")$value
-
-df.icc_item <- df_main_analysis %>% 
-  select(subject, triad, responses_theme, country) %>%
-  pivot_wider(names_from = subject, values_from = responses_theme)
-
-#unsure if type should be consistency or agreement
-df.icc_item_US <- df.icc_item %>% 
-  filter(country == "US") %>%
-  select_if(~ !any(is.na(.))) %>%
-  select(-country, -triad)
-
-icc_item_US <- icc(df.icc_item_US, model = "twoway", type = "agreement", unit = "average")$value
-
-#unsure if type should be consistency or agreement
-df.icc_item_VN <- df.icc_item %>% 
-  filter(country == "Vietnam") %>%
-  select_if(~ !any(is.na(.))) %>%
-  select(-country, -triad)
-
-icc_item_VN <- icc(df.icc_item_VN, model = "twoway", type = "consistency", unit = "single")$value
-
-#unsure if type should be consistency or agreement
-df.icc_item_CN <- df.icc_item %>% 
-  filter(country == "China") %>%
-  select_if(~ !any(is.na(.))) %>%
-  select(-country, -triad)
-
-icc_item_CN <- icc(df.icc_item_CN, model = "twoway", type = "consistency", unit = "single")$value
-```
-
-```{r participant variability, include = F}
-df.icc_ppt_full <- df_main_analysis %>% 
-  select(subject, triad, responses_theme) %>%
-  pivot_wider(names_from = triad, values_from = responses_theme)
-
-icc_ppt_full <- icc(df.icc_ppt_full %>% select(-subject), model = "twoway", type = "consistency", unit = "single")$value
-
-df.icc_ppt <- df_main_analysis %>% 
-  select(subject, triad, responses_theme, country) %>%
-  pivot_wider(names_from = triad, values_from = responses_theme)
-
-#unsure if type should be consistency or agreement
-df.icc_ppt_US <- df.icc_ppt %>% 
-  filter(country == "US") %>%
-  select(-country, -subject)
-
-icc_ppt_US <- icc(df.icc_ppt_US, model = "twoway", type = "consistency", unit = "single")$value
-
-#unsure if type should be consistency or agreement
-df.icc_ppt_VN <- df.icc_ppt %>% 
-  filter(country == "Vietnam") %>%
-  select(-country, -subject)
-
-icc_ppt_VN <- icc(df.icc_ppt_VN, model = "twoway", type = "consistency", unit = "single")$value
-
-#unsure if type should be consistency or agreement
-df.icc_ppt_CN <- df.icc_ppt %>% 
-  filter(country == "China") %>%
-  select(-country, -subject)
-
-icc_ppt_CN <- icc(df.icc_ppt_CN, model = "twoway", type = "consistency", unit = "single")$value
-```
+
+tab1 <- xtable::xtable(iccs, digits=2,
+                       caption = "ICCs for reliability within participants (intra-rater) and stimuli (inter-rater) for all cultural contexts.")
+
+print(tab1, type="latex", comment = F, include.rownames = FALSE)
+```
+
+## 2. Supplemental for whether each corpus predicts similarity judgement in each cultural context
+
+### Triads
+For US responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are significant predictors of US responding (EN-US model: $\beta$ = `r round(fixef(fit.EN_US_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.EN_US_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.EN_US_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p `r ifelse( fit.EN_US_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.EN_US_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"], 3)), "< .001")`; VI-US model: $\beta$ = `r round(fixef(fit.VI_US_cos)["theme_cosine_prop_V"], 2)`, $\chi^2$(`r fit.VI_US_cos.anova["theme_cosine_prop_V", "Df"]`) = `r round(fit.VI_US_cos.anova["theme_cosine_prop_V", "Chisq"], 2)`, p `r ifelse( fit.VI_US_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.VI_US_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"], 3)), "< .001")`; ZH-US model: $\beta$ = `r round(fixef(fit.ZH_US_cos)["theme_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ZH_US_cos.anova["theme_cosine_prop_M", "Df"]`) = `r round(fit.ZH_US_cos.anova["theme_cosine_prop_M", "Chisq"], 2)`, p `r ifelse( fit.ZH_US_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ZH_US_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"], 3)), "< .001")`).
+
+For Vietnam (VN) responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are significant predictors of VN responding (EN-VN model: $\beta$ = `r round(fixef(fit.EN_VN_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.EN_VN_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.EN_VN_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p `r ifelse( fit.EN_VN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.EN_VN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"], 3)), "< .001")`; VI-VN model: $\beta$ = `r round(fixef(fit.VI_VN_cos)["theme_cosine_prop_V"], 2)`, $\chi^2$(`r fit.VI_VN_cos.anova["theme_cosine_prop_V", "Df"]`) = `r round(fit.VI_VN_cos.anova["theme_cosine_prop_V", "Chisq"], 2)`, p `r ifelse( fit.VI_VN_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.VI_VN_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"], 3)), "< .001")`; ZH-VN model: $\beta$ = `r round(fixef(fit.ZH_VN_cos)["theme_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ZH_VN_cos.anova["theme_cosine_prop_M", "Df"]`) = `r round(fit.ZH_VN_cos.anova["theme_cosine_prop_M", "Chisq"], 2)`, p `r ifelse( fit.ZH_VN_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ZH_VN_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"], 3)), "< .001")`).
+
+For China (CN) responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are significant predictors of CN responding (EN-CN model: $\beta$ = `r round(fixef(fit.EN_CN_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.EN_CN_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.EN_CN_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p `r ifelse( fit.EN_CN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.EN_CN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"], 3)), "< .001")`; VI-CN model: $\beta$ = `r round(fixef(fit.VI_CN_cos)["theme_cosine_prop_V"], 2)`, $\chi^2$(`r fit.VI_CN_cos.anova["theme_cosine_prop_V", "Df"]`) = `r round(fit.VI_CN_cos.anova["theme_cosine_prop_V", "Chisq"], 2)`, p `r ifelse( fit.VI_CN_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.VI_CN_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"], 3)), "< .001")`; ZH-CN model: $\beta$ = `r round(fixef(fit.ZH_CN_cos)["theme_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ZH_CN_cos.anova["theme_cosine_prop_M", "Df"]`) = `r round(fit.ZH_CN_cos.anova["theme_cosine_prop_M", "Chisq"], 2)`, p `r ifelse( fit.ZH_CN_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ZH_CN_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"], 3)), "< .001")`).
+
+### Fillers
+English (EN) is a significant predictors of US responding ($\beta$ = `r round(fixef(fit.EN_US_filler_cos)["word1_match_cosine_prop_E"], 2)`, $\chi^2$(`r fit.EN_US_filler_cos.anova["word1_match_cosine_prop_E", "Df"]`) = `r round(fit.EN_US_filler_cos.anova["word1_match_cosine_prop_E", "Chisq"], 2)`, p `r ifelse( fit.EN_US_filler_cos.anova["word1_match_cosine_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.EN_US_filler_cos.anova["word1_match_cosine_prop_E", "Pr(>Chisq)"], 3)), "< .001")`).
+
+Vietnamese (VI) is a significant predictors of Vietnam responding ($\beta$ = `r round(fixef(fit.VI_VN_filler_cos)["word1_match_cosine_prop_V"], 2)`, $\chi^2$(`r fit.VI_VN_filler_cos.anova["word1_match_cosine_prop_V", "Df"]`) = `r round(fit.VI_VN_filler_cos.anova["word1_match_cosine_prop_V", "Chisq"], 2)`, p `r ifelse( fit.VI_VN_filler_cos.anova["word1_match_cosine_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.VI_VN_filler_cos.anova["word1_match_cosine_prop_V", "Pr(>Chisq)"], 3)), "< .001")`).
+
+Mandarin (ZH) is a significant predictors of China responding ($\beta$ = `r round(fixef(fit.ZH_CN_filler_cos)["word1_match_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ZH_CN_filler_cos.anova["word1_match_cosine_prop_M", "Df"]`) = `r round(fit.ZH_CN_filler_cos.anova["word1_match_cosine_prop_M", "Chisq"], 2)`, p `r ifelse( fit.ZH_CN_filler_cos.anova["word1_match_cosine_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ZH_CN_filler_cos.anova["word1_match_cosine_prop_M", "Pr(>Chisq)"], 3)), "< .001")`).
+
+## 3. Demographic Exclusion Statistics
+```{r results = "asis", fig.cap="Testing"}
+df.demog_excl <- cbind(t(df.excl_US), t(df.excl_CN))
+df.demog_excl <- cbind(df.demog_excl, t(df.excl_VN))
+
+rownames(df.demog_excl) <-
+  c("Country", "Ppts Finished", 
+    "Excluded", 
+    "After Exclusion", 
+    "Non-Native Speakers", "EN Speakers", 
+    "VI Speakers", "ZH Speakers", 
+    "Lived Abroad", "Overseas Experience", 
+    "After Exclusions")
+
+colnames(df.demog_excl) <- df.demog_excl[1,]
+df.demog_excl <- df.demog_excl[-1, ]
+
+kbl(df.demog_excl, align = "c") %>%
+  add_header_above(c(" " = 1, "Country" = 3)) %>%
+  pack_rows(index = c(" " = 1, "Attention Check Exclusions" = 2, "Demographics Exclusions" = 7))
+```
+
+\newpage
+
+# Acknowledgements
+
+Place acknowledgments (including funding information) in a section at
+the end of the paper.
+
+# References
 
 ```{r}
-icc_tbl <- data.frame(
-  Country = c("US", "China", "Vietnam", "All"),
-  Item_Variability_ICC = c(icc_item_US, icc_item_CN, icc_item_VN, icc_item_full), 
-  Ppt_Variabiity_ICC = c(icc_ppt_US, icc_ppt_CN, icc_ppt_VN, icc_ppt_full)
-)
-kable(icc_tbl)
-```
-
-## 2. Supplemental for whether each corpus predicts similarity judgement in each cultural context
-### Lexical co-occurrence
-For US responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are all significant predictors.
-EN corpus: $\beta$ = `r round(fixef(fit.EN_US)["theme_freq_prop_E"], 2)`, $\chi^2$(`r fit.EN_US.anova["theme_freq_prop_E", "Df"]`) = `r round(fit.EN_US.anova["theme_freq_prop_E", "Chisq"], 2)`, p `r ifelse( fit.EN_US.anova["theme_freq_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.EN_US.anova["theme_freq_prop_E", "Pr(>Chisq)"], 3)), "< .001")`.
-VI corpus: $\beta$ = `r round(fixef(fit.VI_US)["theme_freq_prop_V"], 2)`, $\chi^2$(`r fit.VI_US.anova["theme_freq_prop_V", "Df"]`) = `r round(fit.VI_US.anova["theme_freq_prop_V", "Chisq"], 2)`, p `r ifelse( fit.VI_US.anova["theme_freq_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.VI_US.anova["theme_freq_prop_V", "Pr(>Chisq)"], 3)), "< .001")`.
-ZH corpus: $\beta$ = `r round(fixef(fit.ZH_US)["theme_freq_prop_M"], 2)`, $\chi^2$(`r fit.ZH_US.anova["theme_freq_prop_M", "Df"]`) = `r round(fit.ZH_US.anova["theme_freq_prop_M", "Chisq"], 2)`, p `r ifelse( fit.ZH_US.anova["theme_freq_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ZH_US.anova["theme_freq_prop_M", "Pr(>Chisq)"], 3)), "< .001")`.
-
-For Vietnam responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are all significant predictors.
-EN corpus: $\beta$ = `r round(fixef(fit.EN_VN)["theme_freq_prop_E"], 2)`, $\chi^2$(`r fit.EN_VN.anova["theme_freq_prop_E", "Df"]`) = `r round(fit.EN_VN.anova["theme_freq_prop_E", "Chisq"], 2)`, p `r ifelse( fit.EN_VN.anova["theme_freq_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.EN_VN.anova["theme_freq_prop_E", "Pr(>Chisq)"], 3)), "< .001")`.
-VI corpus: $\beta$ = `r round(fixef(fit.VI_VN)["theme_freq_prop_V"], 2)`, $\chi^2$(`r fit.VI_VN.anova["theme_freq_prop_V", "Df"]`) = `r round(fit.VI_VN.anova["theme_freq_prop_V", "Chisq"], 2)`, p `r ifelse( fit.VI_VN.anova["theme_freq_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.VI_VN.anova["theme_freq_prop_V", "Pr(>Chisq)"], 3)), "< .001")`.
-ZH corpus: $\beta$ = `r round(fixef(fit.ZH_VN)["theme_freq_prop_M"], 2)`, $\chi^2$(`r fit.ZH_VN.anova["theme_freq_prop_M", "Df"]`) = `r round(fit.ZH_VN.anova["theme_freq_prop_M", "Chisq"], 2)`, p `r ifelse( fit.ZH_VN.anova["theme_freq_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ZH_VN.anova["theme_freq_prop_M", "Pr(>Chisq)"], 3)), "< .001")`.
-
-For China responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are all significant predictors.
-EN corpus: $\beta$ = `r round(fixef(fit.EN_CN)["theme_freq_prop_E"], 2)`, $\chi^2$(`r fit.EN_CN.anova["theme_freq_prop_E", "Df"]`) = `r round(fit.EN_CN.anova["theme_freq_prop_E", "Chisq"], 2)`, p `r ifelse( fit.EN_CN.anova["theme_freq_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.EN_CN.anova["theme_freq_prop_E", "Pr(>Chisq)"], 3)), "< .001")`.
-VI corpus: $\beta$ = `r round(fixef(fit.VI_CN)["theme_freq_prop_V"], 2)`, $\chi^2$(`r fit.VI_CN.anova["theme_freq_prop_V", "Df"]`) = `r round(fit.VI_CN.anova["theme_freq_prop_V", "Chisq"], 2)`, p `r ifelse( fit.VI_CN.anova["theme_freq_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.VI_CN.anova["theme_freq_prop_V", "Pr(>Chisq)"], 3)), "< .001")`.
-ZH corpus: $\beta$ = `r round(fixef(fit.ZH_US)["theme_freq_prop_M"], 2)`, $\chi^2$(`r fit.ZH_CN.anova["theme_freq_prop_M", "Df"]`) = `r round(fit.ZH_CN.anova["theme_freq_prop_M", "Chisq"], 2)`, p `r ifelse( fit.ZH_CN.anova["theme_freq_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ZH_CN.anova["theme_freq_prop_M", "Pr(>Chisq)"], 3)), "< .001")`.
-
-### Cosine similarity 
-For US responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are significant predictors of US responding (EN-US model: $\beta$ = `r round(fixef(fit.EN_US_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.EN_US_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.EN_US_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p `r ifelse( fit.EN_US_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.EN_US_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"], 3)), "< .001")`; VI-US model: $\beta$ = `r round(fixef(fit.VI_US_cos)["theme_cosine_prop_V"], 2)`, $\chi^2$(`r fit.VI_US_cos.anova["theme_cosine_prop_V", "Df"]`) = `r round(fit.VI_US_cos.anova["theme_cosine_prop_V", "Chisq"], 2)`, p `r ifelse( fit.VI_US_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.VI_US_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"], 3)), "< .001")`; ZH-US model: $\beta$ = `r round(fixef(fit.ZH_US_cos)["theme_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ZH_US_cos.anova["theme_cosine_prop_M", "Df"]`) = `r round(fit.ZH_US_cos.anova["theme_cosine_prop_M", "Chisq"], 2)`, p `r ifelse( fit.ZH_US_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ZH_US_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"], 3)), "< .001")`).
-
-For Vietnam (VN) responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are significant predictors of VN responding (EN-VN model: $\beta$ = `r round(fixef(fit.EN_VN_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.EN_VN_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.EN_VN_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p `r ifelse( fit.EN_VN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.EN_VN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"], 3)), "< .001")`; VI-VN model: $\beta$ = `r round(fixef(fit.VI_VN_cos)["theme_cosine_prop_V"], 2)`, $\chi^2$(`r fit.VI_VN_cos.anova["theme_cosine_prop_V", "Df"]`) = `r round(fit.VI_VN_cos.anova["theme_cosine_prop_V", "Chisq"], 2)`, p `r ifelse( fit.VI_VN_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.VI_VN_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"], 3)), "< .001")`; ZH-VN model: $\beta$ = `r round(fixef(fit.ZH_VN_cos)["theme_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ZH_VN_cos.anova["theme_cosine_prop_M", "Df"]`) = `r round(fit.ZH_VN_cos.anova["theme_cosine_prop_M", "Chisq"], 2)`, p `r ifelse( fit.ZH_VN_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ZH_VN_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"], 3)), "< .001")`).
-
-For China (CN) responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are significant predictors of CN responding (EN-CN model: $\beta$ = `r round(fixef(fit.EN_CN_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.EN_CN_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.EN_CN_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p `r ifelse( fit.EN_CN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.EN_CN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"], 3)), "< .001")`; VI-CN model: $\beta$ = `r round(fixef(fit.VI_CN_cos)["theme_cosine_prop_V"], 2)`, $\chi^2$(`r fit.VI_CN_cos.anova["theme_cosine_prop_V", "Df"]`) = `r round(fit.VI_CN_cos.anova["theme_cosine_prop_V", "Chisq"], 2)`, p `r ifelse( fit.VI_CN_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.VI_CN_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"], 3)), "< .001")`; ZH-CN model: $\beta$ = `r round(fixef(fit.ZH_CN_cos)["theme_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ZH_CN_cos.anova["theme_cosine_prop_M", "Df"]`) = `r round(fit.ZH_CN_cos.anova["theme_cosine_prop_M", "Chisq"], 2)`, p `r ifelse( fit.ZH_CN_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ZH_CN_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"], 3)), "< .001")`).
-
-## 2. CCRR agreement
-```{r load CCRR data}
-df.ccrr <- read.csv("../../../data/replication/ccrr.csv") %>%
-  filter(task_name == "TD") %>%
-  select(subject, trial_info, resp) %>%
-  rename(triad = trial_info) %>%
-  mutate(response_theme = ifelse(resp == "FALSE", 1, 0)) %>%
-  select(subject, triad, response_theme) %>%
-  pivot_wider(names_from = subject, values_from = response_theme) %>%
-  select(-triad)
-
-df.ccrr %>%
-    dplyr::group_by(triad, subject) %>%
-    dplyr::summarise(n = dplyr::n(), .groups = "drop") %>%
-    dplyr::filter(n > 1L)
-
-icc(df.ccrr, model = "twoway", type = "consistency", unit = "single")
-```
+# References will be generated automatically by Pandoc and included here.
+# The following code is some latex to format the bibliography. Do not remove it.
+```
+
+\setlength{\parindent}{-0.1in} 
+\setlength{\leftskip}{0.125in}
+\noindent
+
+\newpage

### 2023-01-20 code/4_paper/manuscript/manuscript.tex
cogsci paper exchange

@@
 \usepackage[utf8]{inputenc}
-\usepackage[T1, T5]{fontenc}
+\usepackage[T1, T2A, T5]{fontenc}
+\usepackage{kotex}
+\usepackage{booktabs}
+\usepackage{longtable}
+\usepackage{array}
+\usepackage{multirow}
+\usepackage{wrapfig}
+\usepackage{float}
+\usepackage{colortbl}
+\usepackage{pdflscape}
+\usepackage{tabu}
+\usepackage{threeparttable}
+\usepackage{threeparttablex}
+\usepackage[normalem]{ulem}
+\usepackage{makecell}
+\usepackage{xcolor}
 
@@
 why? One possibility is that cultures co-varying with these languages
-induce variation in conceptualizations of similarity. Specifically, East
-Asian cultures may promote reasoning about thematic similarity, by which
-cow and grass are more related whereas Western cultures may bias
-similarity judgements toward taxonomic relations, like cow-chicken. This
-difference in notions of similarity is the consensus interpretation for
+induce differences in conceptualizations of similarity. Specifically,
+East Asian cultures may promote reasoning about thematic similarity, by
+which cow and grass are more related, whereas Western cultures may bias
+judgements toward taxonomic relations, like cow-chicken. This difference
+in notions of similarity is the consensus interpretation for
 cross-cultural variation in this paradigm. We consider, and provide
 evidence for, an alternative possibility, by which notions of similarity
-are equivalent across contexts, but the statistics of the environment
-vary. On this account, similarity judgements are guided by co-occurrence
-in experience, and observing or hearing about cows and grass or cows and
-chickens more often could induce preferences for the relevant grouping,
-and account for apparent differences in notions of similarity across
+are similar across contexts, but the statistics of the environment vary.
+On this account, similarity judgements are guided by co-occurrence in
+experience, and observing or hearing about cows and grass or cows and
+chickens more often could induce preferences for these groupings, and
+account in part for apparent differences in notions of similarity across
 contexts.
@@
 categorization is based on causal, spatial, and temporal relationships
-among objects (Markman \& Hutchinson, 1984). To illustrate this point,
-if a participant is given the words ``chicken'' and ``grass'', and asked
-which of those words are more closely related to the word ``cow'', the
-pairing ``chicken'' - ``cow'' indicates a taxonomic match, whereas
-``grass'' - ``cow'' indicates a thematic match.
-
-Ji, Zhang, \& Nisbett (2004) found that preferences for taxonomic and
-thematic matches differ across cultures, even when controlling for
-testing language and fluency. Specifically, Chinese participants made
-more thematic matches than taxonomic, while the converse was true for
-European Americans. This difference held even for Chinese participants
-tested in English (rather than Mandarin), suggesting that culture has an
-effect on the categorization strategy independent of the test language.
-However, the study also found an effect of language within Chinese
-participants from mainland China (when tested both in China and in the
-US): their preference for thematic categorization was significantly
-lower when tested in English compared to Mandarin Chinese. This suggests
-that test language also influences categorization strategies. Ji et
-al.~characterize these results as demonstrating that culture
-(independent of language) leads to different styles of reasoning about
-similarity, whereas language serves as a ``tuning'' mechanism operating
-within a culturally-specific style, by activating representations
-corresponding to the language being used.
+among objects (Markman \& Hutchinson, 1984).
 
@@
 
-The view that culture drives differences in categorization style has
-been one favored by other non-linguistic studies that use taxonomic vs
-thematic categorization to probe similarity judgment. When shown
-pictorial triads that represent words (i.e.~pictures of an ant, a bee,
-and honey), Chinese children (9-10 years old) scored higher on thematic
-categorization compared to American children of the same age range, and
-vice versa for taxonomic categorization (Chiu, 1972). These
-cross-cultural differences in similarity judgment persist in novel
-object categorization, with Chinese participants preferring to group by
-family resemblance across multiple features and Americans preferring a
-single-feature rule (Norenzayan, Smith, Kim, \& Nisbett, 2002). Since
-differences in categorization style persist with novel stimuli (as
-opposed to previously seen words or pictures of concepts), this suggests
-that participants from different cultural backgrounds are utilizing
-different reasoning strategies when making similarity judgments. The
-authors attribute these differences to tendencies toward analytic
-processing in Western cultures, which emphasizes objects and their
-properties and holistic processing in East Asian cultures, which
-emphasizes relationships between objects and their context. According to
-this framework, East Asians attend more to relationships between objects
-and context and reason more holistically, whereas Westerners attend more
-to objects and their properties, and reason analytically (ibid, see also
-Nisbett (2003)). In related work, East Asian participants show a higher
-level of sensitivity to context than their Western counterparts when
-reproducing drawings from memory (Ji, Peng, \& Nisbett, 2000); visually
-exploring naturalistic scenes (Chua, Boland, \& Nisbett, 2005);
-describing scenes (Masuda \& Nisbett, 2001); and in explaining the
-causes of ambiguous behaviors (Choi, Nisbett, \& Norenzayan, 1999).
-These cross-cultural differences in attention and analytic vs holistic
-processing are seen to map onto the cross-cultural differences in
-similarity judgment: because East Asian participants attend more to the
-context between objects and reason more holistically, it stands to
-reason that they would consider words that appear in the same context
-(i.e.~thematically similar) to be more similar than
-taxonomically-similar words.
-
-This view ascribes cross-cultural differences in similarity judgment
-tasks to variation in the conceptualization of similarity itself.
-Alternatively, these judgments could be shaped by cross-cultural
-differences in the statistics of the environment, and accordingly the
-content of everyday experiences. Perhaps when confronted with the triad
-task, participants from all cultures follow the same process for
-reasoning about similarity, but rely on language or culture-specific
-inputs to this process. For example, it may be that Vietnamese
-participants are more likely to have knowledge of farming practices than
-Americans, and may associate cows and grass more strongly (as grass is
-the typical feed for cows in the small-scale family farming contexts
-common in Vietnam). Americans, on the other hand, may have strong
-associations between cows and chickens as a result of encountering them
-together in children's books or petting zoo contexts. If we observe a
-difference in categorization between, say Vietnamese and US
-participants, it could be that members of both groups use the same
-procedure (considering similarity that is influenced by both taxonomic
-and thematic relations), but the inputs to this procedure differ between
-cultures, with Vietnamese participants exposed to more instances of
-``cow'' and ``grass'' occurring together, compared to US participants.
-
-\hypertarget{language-as-a-proxy-of-variation-in-experience}{%
-\subsection{Language as a proxy of variation in
-experience}\label{language-as-a-proxy-of-variation-in-experience}}
+Preferences for taxonomic and thematic similarity vary across cultures.
+Chiu (1972) found that Chinese children (9-10 years old) are more likely
+to choose thematic matches in a picture triad task (shown, e.g., images
+of an ant, a bee, and honey) than their American counterparts. These
+cross-cultural differences are also observed in novel object
+categorization, with Chinese participants preferring to group by family
+resemblance across multiple features and Americans preferring a
+single-feature rule (Norenzayan, Smith, Kim, \& Nisbett, 2002). The
+authors link these differences to tendencies toward analytic processing
+in Western cultures, which emphasizes objects and their properties, and
+holistic processing in East Asian cultures, which emphasizes
+relationships between objects and their context (see also Nisbett
+(2003)). In related work, East Asian participants show a higher level of
+sensitivity to context than their Western counterparts when reproducing
+drawings from memory (Ji, Peng, \& Nisbett, 2000); visually exploring
+naturalistic scenes (Chua, Boland, \& Nisbett, 2005); describing scenes
+(Masuda \& Nisbett, 2001); and in explaining the causes of ambiguous
+behaviors (Choi, Nisbett, \& Norenzayan, 1999).
+
+Ji, Zhang, \& Nisbett (2004) asked whether differences in analytic and
+holistic processing are driven by language, culture, or a combination of
+these. They presented Chinese and European American adults with a word
+triad task, and found a preference for thematic matching among Chinese
+participants compared to European Americans. They found that test
+language contributed to this difference, but did not fully explain it:
+Chinese participants showed a stronger thematic preference when tested
+in Mandarin, but still showed a thematic preference when tested in
+English. Ji et al.~conclude that culture (independent of language) leads
+to different styles of reasoning about similarity, whereas language
+serves as a ``tuning'' mechanism operating within a culturally-specific
+style, by activating representations corresponding to the language being
+used.\footnote{But note that this work did not include a manipulation to
+  prevent participants from engaging in e.g., covert naming in a
+  language other than the test language.}
+
+This view ascribes cross-cultural differences in similarity judgment to
+variation in the conceptualization of similarity itself. Alternatively,
+these judgments could be shaped by cross-cultural differences in the
+statistics of the environment, and accordingly the content of everyday
+experiences. Perhaps when confronted with the triad task, participants
+from all cultures follow the same process for reasoning about
+similarity, but rely on language or culture-specific inputs to this
+process. If we observe a difference in categorization between East Asian
+and Western participants, it could be that members of both groups use
+the same procedure (considering similarity that is influenced by both
+taxonomic and thematic relations), but the inputs to this procedure
+differ between cultures, with East Asian participants exposed to more
+instances of thematic similarity than their Western counterparts.
+
+\hypertarget{estimating-variation-in-experience}{%
+\subsection{Estimating variation in
+experience}\label{estimating-variation-in-experience}}
 
@@
 cultural and ecological variation) may account for these cross-cultural
-differences in reasoning.\footnote{While we discuss cross-cultural
-  variability at the level of countries or larger world areas, these are
-  not cultural monoliths. For convenience, we operationalize culture at
-  the level of country, based on where participants were raised. It is
-  an open question whether performance in our participant populations
-  (of relatively young and well-educated adults) is representative of
-  the broader country. This is especially true for societies with
-  substantial ethnic and cultural variation such as the US. We expect
-  that our data is likely to underestimate variation both within and
-  between the countries we sample from.}
+differences in reasoning.
 
 Indeed, previous work suggests that using lexical co-occurrence as a
-proxy can be useful in thinking about similarity judgments. Natural
+proxy can be useful in thinking about similarity reasoning. Natural
 language processing tasks have found that lexical co-occurrence is a
-good predictor for performance in similarity judgment tasks. Griffiths,
+good predictor for performance in similarity judgment. Griffiths,
 Steyvers, \& Tenenbaum (2007) showed that a model that takes
@@
 relations) have been shown to perform well on predicting human judgments
-about similarity between word pairs that are either thematically or
+about similarity between word pairs that are thematically or
 taxonomically related (Rohde, Gonnerman, \& Plaut, 2006).
 
-Our current study will be using 2 measures of lexical co-occurrence: 1)
-raw lexical co-occurrences and 2) cosined distances of fastText word
-vectors. fastText is a system that uses lexical co-occurrence
-information to generate a vector representing each word in its lexicon
-(Mikolov, Grave, Bojanowski, Puhrsch, \& Joulin, 2018). fastText uses a
-continuous bag-of-words model, which takes into account a symmetric
-window of words surrounding the word in question and maximizes the
-log-likelihood of the probability of the word given its context.
-Calculating the cosine-similarity between word vectors from fastText
-gives us a score of how similar the contexts of these words are.
-Therefore, words that occur in the same context (high lexical
-co-occurrence) would have a larger cosine-similarity score.
-
-It must be noted that fastText supplements the lexical co-occurrence
-information by simultaneously training weight vectors for each position
-relative to the word in question, as well as adding sub-word information
-(bag-of-character n-gram vectors for each character forming the words).
-The similarity judgment prediction given by fastText may be more higher
-than a model using purely lexical co-occurrence information. However,
-models that use only lexical co-occurrence information (with or without
-a simple position weight system that gives more weight to words that are
-closer to the word in question) also perform well in similarity
-prediction tasks. For this study, due to the lack of large cleaned
-corpora for Mandarin and Vietnamese, we are leveraging fastText
-pre-trained models on the languages we are interested in Grave,
-Bojanowski, Gupta, Joulin, \& Mikolov (2018).
+Our study uses cosine distances of fastText word vectors as a measure of
+lexical co-occurrence\footnote{We also carried out our analysis using
+  raw lexical co-occurrences and obtained similar results.}. fastText is
+a system that uses lexical co-occurrence information to generate a
+vector representing each word in its lexicon (Mikolov, Grave,
+Bojanowski, Puhrsch, \& Joulin, 2018).
 
@@
 Ji et al. (2004) suggest that the notion of similarity is what varies
-across cultural groups, but it is quite possible that similarity is
-regarded in the same way and it is actually the input to this similarity
-judgment that varies across culture contexts. It might be possible to
-gain traction on possible mechanisms by examining whether variation in
-similarity judgments co-varies with environmental statistics that differ
-across the cultural and linguistic contexts.
+across cultural groups, but it is possible that similarity is regarded
+in the same way and it is actually the input to this similarity judgment
+that varies across cultural contexts. It may be possible to gain
+traction on potential mechanisms by examining whether variation in
+similarity judgments co-vary with environmental statistics that differ
+across cultural and linguistic contexts.
 
@@
 notions of similarity might be similar, and it is environmental
-statistics that guide the differences in similarity judgments. To
-preview our results, we find that, while we do not see overall group
+statistics that guide the differences in similarity judgments.
+
+To preview our results, we find that, while we do not see overall group
 differences (between the East Asian contexts and the US) in similarity,
@@
 notions of similarity.
+
+There are several important limitations of our approach. While we
+discuss cross-cultural variability at the level of countries or larger
+world areas, these are not cultural monoliths. For convenience, we
+operationalize culture at the level of country, based on where
+participants were raised. It is an open question whether performance in
+our participant populations (of relatively young and well-educated
+adults) is representative of the broader country. This is especially
+true for societies with substantial ethnic and cultural variation such
+as the US. We expect that our data is likely to underestimate variation
+both within and between the countries we sample from.
+
+Language, culture, cognition, and individual experiences are intertwined
+in complex causal relationships: cultural features (farming) can lead to
+differences in individuals' experiences (seeing cows and grass) and in
+turn these can influence language (talking more about cows and grass).
+But cultural features (a thematic orientation) could also more directly
+cause individuals to talk differently about the same experiences
+(mentioning what cows eat rather than what other animals cows are like).
+In this study, we measure language and its relation to cross-cultural
+differences in categorization, but these relations test only the
+plausibility of a language-based account; they cannot establish the
+direction of causality.
 
@@
 
-We excluded 8 US participants, 62 Vietnam participants, and 34 China
+We excluded 26 US participants, 123 Vietnam participants, and 34 China
 participants who did not answer all attention checks correctly. We
@@
 for a language if it would exclude 25\% or more of any one sample. In
-this round of exclusion, we excluded 68 US, 27 Vietnam participants, and
+this round of exclusion, we excluded 65 US, 19 Vietnam participants, and
 34 China participants. After these exclusions, the US sample included
-124 participants (30M, 89F, 3 non-binary, 2 other), with mean age =
-22.18 (SD = 8) and median age = 20. The Vietnam sample included 110
-participants (34M, 71F, 5 other), with mean age = 22.21 (SD = 5.81) and
+109 participants (27M, 78F, 3 non-binary, 1 other), with mean age = 22.4
+(SD = 8.49) and median age = 20. The Vietnam sample included 57
+participants (17M, 40F, other), with mean age = 22.21 (SD = 6.12) and
 median age = 21. The China sample included 132 participants (51M, 81F,
-other), with mean age = 23.27 (SD = 3.75) and median age = 23.
+other), with mean age = 23.27 (SD = 3.75) and median age =
+23.\footnote{A table summarizing number of participants lost at each
+  round of exclusions is included in the Appendix.}
 
@@
 research surveys and attention check questions, and thus might have
-thought too much about the attention check questions. We carried out an
-exploratory analysis where we used a less stringent attention check
-exclusion (covered in the final part of the Results \& Analysis
-section). To preview our findings for this analysis, we did not find any
-difference in significant results when compared with the main analysis.
+thought too much about the attention check questions.\footnote{We
+  carried out an exploratory analysis where we used a less stringent
+  attention check exclusion (covered in the final part of the Results \&
+  Analysis section). To preview our findings for this analysis, we did
+  not find any difference in significant results when compared with the
+  main analysis.}
 
@@
 from supplemental information and in-text examples across the
-literature, and others that we adapted or created (see SI for the full
-list of stimuli and sources). We selected triads on the basis of
-cultural familiarity in the US, Vietnam, and China. The triads were
-originally in English; they were translated to Vietnamese and Mandarin
-by a fluent bilingual speaker in each language. The translations were
-then checked for accuracy after backtranslation to English by another
-fluent bilingual in each language who was naive to the original English
-versions.
+literature, and others that we adapted or created . We selected triads
+on the basis of cultural familiarity in the US, Vietnam, and China. The
+triads were originally in English; they were translated to Vietnamese
+and Mandarin by a fluent bilingual speaker in each language. The
+translations were then checked for accuracy after backtranslation to
+English by another fluent bilingual in each language who was naive to
+the original English versions. --\textgreater{}
 
@@
 
-Our general approach is to build a model of similarity that is based on
-collocation counts in each language.
-
-\hypertarget{raw-lexical-co-occurrences}{%
-\subsubsection{Raw lexical
-co-occurrences}\label{raw-lexical-co-occurrences}}
-
-To give an intuition for our model, consider the cow-grass-chicken
-triad: we counted how many times ``cow'' and ``grass'' co-occur within a
-window of text in each corpus, and compare this to how many times
-``cow'' and ``chicken'' co-occur. Our similarity prediction is then
-proportional to the relative frequency of these pairs. For example, if
-the thematic cow-grass match accounts for 30\% of collocations for this
-triad (with cow-chicken making up the other 70\%), then our model
-predicts, correspondingly, that 30\% of responses to the triad will be
-grass, and the other 70\% chicken. We then use a mixed-effects
-regression to evaluate how well each corpus collocate model predicts
-participants' similarity judgments, across triads and languages.
-
-\hypertarget{collocate-retrieval-and-coding}{%
-\paragraph{Collocate retrieval and
-coding}\label{collocate-retrieval-and-coding}}
-
-For our English co-occurrence metric, we used the online interface of
-the Corpus of Contemporary American English (Davies, 2008-) to retrieve
-collocation counts. We recorded the raw count of times that any
-cue-match pair (e.g., cow-grass or cow-chicken) co-occur in a window of
-19 words, which is the maximum window size in the online interface, and
-closest to the sentence co-occurrence metric in our VI corpus
-collocation counts.
-
-To determine Vietnamese co-occurrence, we used the raw frequency of
-sentence co-occurrences from a subset of the Vietnamese corpus in the
-Leipzig Corpora Collection (Goldhahn, Eckart, \& Quasthoff, 2012); this
-corpus includes 70 million Vietnamese sentences, but our corpus data
-comes from a 1 million sentence subset for which co-occurrence counts
-are available for download. Vietnamese makes very frequent use of
-compositional morphology but the written language uses spacing to
-delineate syllable boundaries rather than word boundaries. Accordingly,
-collocate searches returned instances of both target terms and many
-morphologically related, but distinct, words. We included in our counts
-any instances of the target term or close semantic neighbors containing
-the same morpheme(s) as long as they entailed a likely literal reference
-to the target term. For example, our search for collocates of the term
-``gà'' (chicken) also returned ``gà mái,'' a distinct word for female
-chickens. Despite being a different word, ``gà mái'' both includes the
-morpheme for ``chicken'' and entails reference to a chicken.
-Accordingly, instances of both ``gà'' and ``gà mái'' were included in
-our collocate count for ``chicken.'' Some compounds do not meet this
-criteria, and were excluded from collocate counts. For example ``trái
-cây'' (tree.fruits) includes the same syllable as the word ``cây''
-(tree), but refers to fruit that comes from trees, not the trees
-themselves, and was therefore excluded from our collocate counts for
-``tree.''
-
-TODO; ADD INFO ABOUT MANDARIN CORPUS
-
-\hypertarget{collocate-similarity-model}{%
-\paragraph{Collocate similarity
-model}\label{collocate-similarity-model}}
-
-From the raw co-occurrence counts of each triad, we calculated the
-thematic co-occurrence ratio as the number of thematic co-occurrences
-over the sum of thematic and taxonomic co-occurrences. We did this for
-both the English and Vietnamese corpus co-occurrence counts. In this
-way, we obtained predictions for 73 of 105 triads from the Vietnamese
-corpus and 104 of 105 triads from English. We therefore limited all
-analyses reported here to the subset of triads for which our
-corpus-based model can make meaningful predictions, meaning triads that
-have at least one non-zero collocate count (either thematic or taxonomic
-match). We replaced any remaining zero collocate counts with
-\(\epsilon\) to account for sparsity in the corpus data. We then tested
-whether these simple relative frequency models predict US and VN
-responding.
-
-\hypertarget{cosine-distance-of-word-vectors}{%
-\subsubsection{Cosine distance of word
-vectors}\label{cosine-distance-of-word-vectors}}
-
 To give an intuition for our model, consider again the cow-grass-chicken
@@
 
-\hypertarget{collocate-retrieval}{%
-\paragraph{Collocate retrieval}\label{collocate-retrieval}}
+\hypertarget{word-vector-retrieval}{%
+\paragraph{Word vector retrieval}\label{word-vector-retrieval}}
 
 We use the fastText pre-trained models of English, Mandarin, and
-Vietnamese in Grave et al. (2018). These models are trained on Common
-Crawl and Wikipedia using We distribute pre-trained word vectors for 157
-languages, trained on Common Crawl and Wikipedia using fastText. These
-models were trained using a Continuous Bag of Words (CBOW) with
-position-weights and a window of size 5. The models use character
-n-grams of length 5 and 10 negative examples.From the aforementioned
-models, we retrieve the word vectors (dimension 300) for each word we
-are interested in.
-
-\hypertarget{collocate-similarity-model-1}{%
-\paragraph{Collocate similarity
-model}\label{collocate-similarity-model-1}}
+Vietnamese in Grave, Bojanowski, Gupta, Joulin, \& Mikolov (2018). These
+models are trained on Common Crawl and Wikipedia using We distribute
+pre-trained word vectors for 157 languages, trained on Common Crawl and
+Wikipedia using fastText. These models were trained using a Continuous
+Bag of Words (CBOW) with position-weights and a window of size 5. The
+models use character n-grams of length 5 and 10 negative examples.From
+the aforementioned models, we retrieve the word vectors (dimension 300)
+for each word we are interested in.
+
+\hypertarget{similarity-model}{%
+\paragraph{Similarity model}\label{similarity-model}}
 
@@
 the highest (M = 0.65, SD = 0.12), followed by the groups means in
-Vietnam (M = 0.6, SD = 0.11), which is slightly higher than that of the
-US (M = 0.57, SD = 0.16).
+Vietnam (M = 0.6, SD = 0.13), which is slightly higher than that of the
+US (M = 0.56, SD = 0.17) (Figure 1).
 
@@
 \begin{figure}[tb]
-\includegraphics{figs/unnamed-chunk-2-1} \caption[Proportion of thematic responses by country]{Proportion of thematic responses by country.
-Only US-China responding comparison shows a siginficant difference.
-We could not extend this to US-Vietnam responding comparison.}\label{fig:unnamed-chunk-2}
+
+{\centering \includegraphics{figs/unnamed-chunk-1-1}
+
+}
+
+\caption[Proportion of thematic responses by country]{Proportion of thematic responses by country.}\label{fig:unnamed-chunk-1}
 \end{figure}
@@
 Overall, there is a significant effect of country on proportion of
-thematic responses (\(\chi^2\)(2) = 15.75, p \textless{} .001). However,
+thematic responses (\(\chi^2\)(2) = 15.22, p \textless{} .001). However,
 this effect is driven by the difference between US and China responding
-(\(\beta\) = -0.5, p \textless{} .001). There is no statistical
+(\(\beta\) = -0.53, p \textless{} .001). There is no statistical
 difference between the Vietnam and China responding (\(\beta\) = -0.25,
-p = 0.066), and the US and Vietnam responding (\(\beta\) = 0.25, p =
-0.095).
+p = 0.137), and the US and Vietnam responding (\(\beta\) = 0.28, p =
+0.142).
 
@@
 
-\hypertarget{is-responding-in-each-cultural-context-predicted-by-the-corresponding-lexical-statistics-raw-co-occurrences}{%
-\subsubsection{Is responding in each cultural context predicted by the
-corresponding lexical statistics (raw
-co-occurrences)?}\label{is-responding-in-each-cultural-context-predicted-by-the-corresponding-lexical-statistics-raw-co-occurrences}}
-
-\hypertarget{raw-lexical-co-occurrences-1}{%
-\paragraph{Raw lexical
-co-occurrences}\label{raw-lexical-co-occurrences-1}}
-
-To test whether variation in lexical co-occurrence can explain
-differences in similarity judgments between US and Vietnam participants,
-we compare logistic mixed-effects regression models fit to the thematic
-responding data from each country separately. We first ask how well each
-corpus model (English, Vietnamese, or Mandarin) predicts similarity
-judgments by speakers of the corresponding language (US, Vietnam, or
-China). To do this, we use a mixed-effects logistic regression to
-predict triad responses (0=taxonomic or 1=thematic) with corpus
-prediction (proportion thematic co-occurrence or cosine distance) as a
-fixed effect and participant and triad as random effects.
+\hypertarget{is-responding-in-each-cultural-context-predicted-by-lexical-statistics}{%
+\subsubsection{Is responding in each cultural context predicted by
+lexical
+statistics?}\label{is-responding-in-each-cultural-context-predicted-by-lexical-statistics}}
+
+To test whether variation in lexical statistics can explain differences
+in similarity judgments between US and Vietnam participants, we compare
+logistic mixed-effects regression models fit to the thematic responding
+data from each country separately. We first ask how well each corpus
+model (English, Vietnamese, or Mandarin) predicts similarity judgments
+by speakers of the corresponding language (US, Vietnam, or China). To do
+this, we use a mixed-effects logistic regression to predict triad
+responses (0=taxonomic or 1=thematic) with corpus prediction (proportion
+of cosine distance) as a fixed effect and participant and triad as
+random effects.
 
 We found that all corpora are significant predictors of all cultural
-context responding.
-
-For US responding: English (EN), Vietnamese (VI), and Mandarin (ZH)
-corpus are all significant predictors. EN corpus: \(\beta\) = 2.01,
-\(\chi^2\)(1) = 17.42, p \textless{} .001. VI corpus: \(\beta\) = 1.21,
-\(\chi^2\)(1) = 11.1, p \textless{} .001. ZH corpus: \(\beta\) = 1.15,
-\(\chi^2\)(1) = 6.38, p = 0.012.
-
-For Vietnam responding: English (EN), Vietnamese (VI), and Mandarin (ZH)
-corpus are all significant predictors. EN corpus: \(\beta\) = 1.73,
-\(\chi^2\)(1) = 12.35, p \textless{} .001. VI corpus: \(\beta\) = 1.27,
-\(\chi^2\)(1) = 12.83, p \textless{} .001. ZH corpus: \(\beta\) = 1.8,
-\(\chi^2\)(1) = 18, p \textless{} .001.
-
-For China responding: English (EN), Vietnamese (VI), and Mandarin (ZH)
-corpus are all significant predictors. EN corpus: \(\beta\) = 1.21,
-\(\chi^2\)(1) = 9.83, p = 0.002. VI corpus: \(\beta\) = 0.77,
-\(\chi^2\)(1) = 7.44, p = 0.006. ZH corpus: \(\beta\) = 1.15,
-\(\chi^2\)(1) = 13.28, p \textless{} .001.
-
-This suggests a strong shared similarity signal across the languages.
-
-\hypertarget{cosine-distances-of-fasttext-word-vectors}{%
-\paragraph{Cosine distances of fastText word
-vectors}\label{cosine-distances-of-fasttext-word-vectors}}
-
-Similar to the results from the analysis with raw lexical
-co-occurrences, we found that all corpora are significant predictors of
-all cultural context responding.
-
-For US responding: English (EN), Vietnamese (VI), and Mandarin (ZH)
-corpus are significant predictors of US responding (EN-US model:
-\(\beta\) = -8.64, \(\chi^2\)(1) = 30.44, p \textless{} .001; VI-US
-model: \(\beta\) = -2.97, \(\chi^2\)(1) = 5.23, p = = 0.022; ZH-US
-model: \(\beta\) = -6.96, \(\chi^2\)(1) = 18.08, p \textless{} .001).
-
-For Vietnam (VN) responding: English (EN), Vietnamese (VI), and Mandarin
-(ZH) corpus are significant predictors of VN responding (EN-VN model:
-\(\beta\) = -5.33, \(\chi^2\)(1) = 9.39, p = 0.002; VI-VN model:
-\(\beta\) = -3.46, \(\chi^2\)(1) = 6.64, p = = 0.01; ZH-VN model:
-\(\beta\) = -6.37, \(\chi^2\)(1) = 13.93, p \textless{} .001).
-
-For China (CN) responding: English (EN), Vietnamese (VI), and Mandarin
-(ZH) corpus are significant predictors of CN responding (EN-CN model:
-\(\beta\) = -6.18, \(\chi^2\)(1) = 25.34, p \textless{} .001; VI-CN
-model: \(\beta\) = -2.44, \(\chi^2\)(1) = 5.83, p = = 0.016; ZH-CN
-model: \(\beta\) = -7.36, \(\chi^2\)(1) = 37.45, p \textless{} .001).
-
-\hypertarget{is-responding-in-each-cultural-context-best-predicted-by-the-corresponding-corpuss-lexical-statistics-raw-co-occurrences-as-opposed-to-the-other-two-corpora}{%
-\subsubsection{\texorpdfstring{Is responding in each cultural context
-\textbf{best} predicted by the corresponding corpus's lexical statistics
-(raw co-occurrences), as opposed to the other two
-corpora?}{Is responding in each cultural context best predicted by the corresponding corpus's lexical statistics (raw co-occurrences), as opposed to the other two corpora?}}\label{is-responding-in-each-cultural-context-best-predicted-by-the-corresponding-corpuss-lexical-statistics-raw-co-occurrences-as-opposed-to-the-other-two-corpora}}
+context responding, with p\textless0.05 and \(\beta\) from -9.05 to
+-2.44. (For a full report, see Appendix.)
+
+\hypertarget{is-responding-in-each-cultural-context-best-predicted-by-the-corresponding-corpuss-lexical-statistics-as-opposed-to-the-other-two-corpora}{%
+\subsubsection{Is responding in each cultural context best predicted by
+the corresponding corpus's lexical statistics, as opposed to the other
+two
+corpora?}\label{is-responding-in-each-cultural-context-best-predicted-by-the-corresponding-corpuss-lexical-statistics-as-opposed-to-the-other-two-corpora}}
 
@@
 
-\hypertarget{raw-co-occurrences}{%
-\paragraph{Raw co-occurrences}\label{raw-co-occurrences}}
-
-When we included all corpora thematic cosine distance proportion as
-predictors, all corpora are significant in predicting all cultural
-context's responding.
-
-For US responding: only English (EN) corpus is a significant predictor.
-EN corpus: \(\beta\) = 1.62, \(\chi^2\)(1) = 4.59, p = 0.032. VI corpus:
-\(\beta\) = 0.46, \(\chi^2\)(1) = 1.04, p = 0.307. ZH corpus: \(\beta\)
-= -0.03, \(\chi^2\)(1) = 0, p = 0.962.
-
-For Vietnam responding: only English (EN) and Mandarin (ZH) corpora are
-significant predictors. EN corpus: \(\beta\) = -0.02, \(\chi^2\)(1) = 0,
-p = 0.979. ZH corpus: \(\beta\) = 1.39, \(\chi^2\)(1) = 6.5, p =
-0.011.VI corpus: \(\beta\) = 0.79, \(\chi^2\)(1) = 3.3, p = 0.069.
-
-For China responding: only Mandarin (ZH) corpus is a significant
-predictor. ZH corpus: \(\beta\) = 0.9, \(\chi^2\)(1) = 4.31, p = 0.038.
-EN corpus: \(\beta\) = 0.21, \(\chi^2\)(1) = 0.13, p = 0.72. VI corpus:
-\(\beta\) = 0.35, \(\chi^2\)(1) = 1.02, p = 0.312.
-
-\begin{CodeChunk}
-\begin{figure}[tb]
-\includegraphics{figs/unnamed-chunk-4-1} \caption[Fixed effect sizes of each corpus when included as a predictor for China, US, and Vietnam responding, respectively]{Fixed effect sizes of each corpus when included as a predictor for China, US, and Vietnam responding, respectively.
-The English corpus is the best predictor for US response, and the Mandarin corpus is the best predictor for China response.}\label{fig:unnamed-chunk-4}
-\end{figure}
-\end{CodeChunk}
+For US responding: English (EN), Vietnamese (VI), and Mandarin (ZH)
+corpus are all significant predictors. EN corpus: \(\beta\) = -7.14,
+\(\chi^2\)(1) = 16.78, p \textless{} .001. VI corpus: \(\beta\) = -2.28,
+\(\chi^2\)(1) = 3.74, p = 0.053. ZH corpus: \(\beta\) = -3.53,
+\(\chi^2\)(1) = 3.99, p = 0.046.
+
+For Vietnam responding: English (EN), Vietnamese (VI), and Mandarin (ZH)
+corpus are all significant predictors. EN corpus: \(\beta\) = -4.25,
+\(\chi^2\)(1) = 3.87, p = 0.049. VI corpus: \(\beta\) = -2.98,
+\(\chi^2\)(1) = 4.17, p = 0.041. ZH corpus: \(\beta\) = -4.86,
+\(\chi^2\)(1) = 4.94, p = 0.026.
+
+For China responding: English (EN), Vietnamese (VI), and Mandarin (ZH)
+corpus are all significant predictors. EN corpus: \(\beta\) = -3.52,
+\(\chi^2\)(1) = 7.85, p = 0.005. VI corpus: \(\beta\) = -1.62,
+\(\chi^2\)(1) = 3.57, p = 0.059. ZH corpus: \(\beta\) = -5.35,
+\(\chi^2\)(1) = 17.19, p \textless{} .001.
 
@@
 Vietnamese corpus is still a significant predictor for the Vietnam
-responding.
+responding (Figure 2).
+
+\begin{CodeChunk}
+\begin{figure}[tb]
+
+{\centering \includegraphics{figs/unnamed-chunk-3-1}
+
+}
+
+\caption[Fixed effect sizes of each corpus lexical statistics (cosine distance proportion) when included as a predictor for China, US, and Vietnam responding, respectively]{Fixed effect sizes of each corpus lexical statistics (cosine distance proportion) when included as a predictor for China, US, and Vietnam responding, respectively.
+The English corpus is the best predictor for US response, and the Mandarin corpus is the best predictor for China response.}\label{fig:unnamed-chunk-3}
+\end{figure}
+\end{CodeChunk}
 
@@
 corresponding corpus included as a predictor (US response: \(\chi^2\)(2)
-= 1.04, p = 0.595; Vietnam response: \(\chi^2\)(2) = 8.84, p = 0.012;
-China response: \(\chi^2\)(2) = 2.13, p = 0.345).
-
-\_TODO: should we take this out?\_\_ We carried out an ANOVA model
-comparison to compare our approach with previous studies that did not
-include corpus information. Because Ji et al. (2004) only compared US
-and China participants, we filtered our data to only include responding
-data from these two countries. Our approach would be to compare a model
-that only includes country (US or China) as a fixed effect with one that
-also includes English and Chinese corpus data. Our previous model with
-an intercept per subject and one per triad, as well as by-triad random
-slopes for country to account for variation in the country effect across
-triads fails to converge with the more complex model, so we include a
-simpler random effect structure with an intercept per subject and one
-per triad in both the basic and more complex model. We compare this
-model with an identical model but including Chinese and English corpus
-cosine distance proportion prediction. We found that adding English and
-Chinese corpus data produces a significantly better fit than the
-identical model without English and Chinese corpus data as predictors
-(\(\chi^2\)(2) = 42.57, p = \textless{} .001. This suggests that
-including corpus data would better model the cross-cultural differences
-in similarity judgment in this study as well as similar studies.
-
-\hypertarget{cosine-distances-of-fasttext-word-vectors-1}{%
-\paragraph{Cosine distances of fastText word
-vectors}\label{cosine-distances-of-fasttext-word-vectors-1}}
-
-When we included all corpora thematic cosine distance proportion as
-predictors, all corpora are significant in predicting all cultural
-context's responding.
-
-For US responding: English (EN), Vietnamese (VI), and Mandarin (ZH)
-corpus are all significant predictors. EN corpus: \(\beta\) = -6.9,
-\(\chi^2\)(1) = 17.06, p \textless{} .001. VI corpus: \(\beta\) = -2.18,
-\(\chi^2\)(1) = 3.72, p = = 0.054. ZH corpus: \(\beta\) = -3.2,
-\(\chi^2\)(1) = 3.59, p = = 0.058.
-
-For Vietnam responding: English (EN), Vietnamese (VI), and Mandarin (ZH)
-corpus are all significant predictors. EN corpus: \(\beta\) = -2.98,
-\(\chi^2\)(1) = 2.58, p = = 0.108. VI corpus: \(\beta\) = -2.75,
-\(\chi^2\)(1) = 4.84, p = = 0.028. ZH corpus: \(\beta\) = -4.39,
-\(\chi^2\)(1) = 5.43, p = = 0.02.
-
-For China responding: English (EN), Vietnamese (VI), and Mandarin (ZH)
-corpus are all significant predictors. EN corpus: \(\beta\) = -3.52,
-\(\chi^2\)(1) = 7.81, p = = 0.005. VI corpus: \(\beta\) = -1.62,
-\(\chi^2\)(1) = 3.59, p = = 0.058. ZH corpus: \(\beta\) = -5.35,
-\(\chi^2\)(1) = 17.28, p = \textless{} .001.
-
-We observed some level of language specificity from this analysis. The
-English corpus is the best predictor for US responding, and the Mandarin
-corpus is the best predictor for China response. While this is not the
-case with the Vietnamese corpus and the Vietnam responding, the
-Vietnamese corpus is still a significant predictor for the Vietnam
-responding.
-
-\begin{CodeChunk}
-\begin{figure}[tb]
-\includegraphics{figs/unnamed-chunk-5-1} \caption[Fixed effect sizes of each corpus when included as a predictor for China, US, and Vietnam responding, respectively]{Fixed effect sizes of each corpus when included as a predictor for China, US, and Vietnam responding, respectively.
-The English corpus is the best predictor for US response, and the Mandarin corpus is the best predictor for China response.}\label{fig:unnamed-chunk-5}
-\end{figure}
-\end{CodeChunk}
-
-However, we found that language specificity alone does not explain our
-results. We used an ANOVA to compare the model with only the
-corresponding corpus, and the model with all 3 corpora for each cultural
-context. We found that in all three cases (US, China, Vietnam), adding
-the other two corpora produces a significantly better fit than the
-identical model without the additional corpora, and only the
-corresponding corpus included as a predictor (US response: \(\chi^2\)(2)
-= 7.95, p = = 0.019; Vietnam response: \(\chi^2\)(2) = 13.72, p = =
-0.001; China response: \(\chi^2\)(2) = 10.83, p = NA).
-
-\_TODO: should we take this out?\_\_ We carried out an ANOVA model
-comparison to compare our approach with previous studies that did not
-include corpus information. Because Ji et al. (2004) only compared US
-and China participants, we filtered our data to only include responding
-data from these two countries. Our approach would be to compare a model
-that only includes country (US or China) as a fixed effect with one that
-also includes English and Chinese corpus data. Our previous model with
-an intercept per subject and one per triad, as well as by-triad random
-slopes for country to account for variation in the country effect across
-triads fails to converge with the more complex model, so we include a
-simpler random effect structure with an intercept per subject and one
-per triad in both the basic and more complex model. We compare this
-model with an identical model but including Chinese and English corpus
-cosine distance proportion prediction. We found that adding English and
-Chinese corpus data produces a significantly better fit than the
-identical model without English and Chinese corpus data as predictors
-(\(\chi^2\)(2) = 42.57, p = \textless{} .001. This suggests that
-including corpus data would better model the cross-cultural differences
-in similarity judgment in this study as well as similar studies.
+= 8.42, p = 0.015; Vietnam response: \(\chi^2\)(2) = 15.21, p
+\textless{} .001; China response: \(\chi^2\)(2) = 10.83, p NA).
 
@@
 
-Does adding country and interaction term with the corresponding corpus
-improves the model?
-
-Adding country improves the model. Only country and interaction between
-country and corresponding corpus's lexical co-occurrence are significant
-predictors. Corresponding corpus's lexical co-occurrence is no longer a
-significant predictor.
+Our analysis shows that lexical statistics of each corpus is a
+significant predictor for similarity judgement in the corresponding
+cultural context, even without the addition of the other two corpora.
+Assuming that lexical statistics is a good proxy for environmental
+statistics, we take the above result as evidence that cross-cultural
+differences in input to the process of similarity judgement at least
+partially drives cross-cultural similarity judgement differences.
+However, it is still an open question whether the nature of similarity
+judgement (for e.g., the notion of similarity) itself differs across
+cultures and contributes to cross-cultural differences in similarity
+judgement responding. In an alternative hypothesis, the cross-cultural
+differences in similarity judgement observed is driven by not only the
+input, but also an interaction between cultural-specific nature of
+similarity judgement and input. To test this hypothesis, we
+operationalize cultural-specific nature of similarity judgement as
+country context, and input to similarity judgement as the corresponding
+corpus statistics. We then compare a model that includes country,
+corresponding corpus statistics and their interaction as fixed effects
+(R syntax: responses \textasciitilde{} corresponding\_corpus * country +
+(1\textbar triad) + (1\textbar subject)) to a model with only the
+corresponding corpus statistics as the fixed effect (R syntax: responses
+\textasciitilde{} corresponding\_corpus + (1\textbar triad) +
+(1\textbar subject))
+
+In the model containing only the corresponding corpus statistics, the
+corpus statistics is a significant predictor (\(\beta\) = -1.75,
+\(\chi^2\)(1) = 48.9, p \textless{} .001). When adding country and
+interaction between country and corpus, both the corpus statistics
+(\(\beta\) = -1.51, \(\chi^2\)(1) = 13.96, p \textless{} .001) and
+interaction between country and corpus (\(\beta\) = NA, \(\chi^2\)(2) =
+9.1, p = 0.011) are significant predictors. This suggests that there are
+cross-cultural differences in both input and nature of similarity
+judgement that drive differences in similarity judgement responding.
 
 \hypertarget{how-general-are-the-cross-language-differences-in-similarity-judgments-we-observe-are-they-limited-to-taxonomic-thematic-contrasts-or-do-they-extend-to-other-cases}{%
-\subsection{5. How general are the cross-language differences in
+\subsection{4. How general are the cross-language differences in
 similarity judgments we observe? Are they limited to taxonomic-thematic
@@
 
+Previous work using the triad task such as Ji et al. (2004) has focused
+on contrasting taxonomic-thematic match preferences, driven by a theory
+of cross-cultural differences in notions of similarity. Meanwhile, our
+approach has shown that notions of similarity only has an effect on
+cross-cultural differences in similarity judgement when modulated by
+input, and that input as proxied by lexical statistics of the
+corresponding corpus by itself is a significant predictor for similarity
+judgement responding. Our approach using lexical statistics do not
+assume a taxonomic/thematic structure in the triads. Therefore, it
+should be possible to predict similarity judgements to triads that do
+not follow a taxonomic/thematic structure, such as our filler triads. If
+our approach is tractable, we should be able to repeat the above
+analyses to the filler triads, and find that lexical statistics of each
+corpus is a significant predictor for similarity judgements in filler
+triads of the corresponding cultural context.
+
 \begin{CodeChunk}
 \begin{figure}[tb]
-\includegraphics{figs/unnamed-chunk-8-1} \caption[Proportion of thematic responses by country]{Proportion of thematic responses by country.
-Only US-China responding comparison shows a siginficant difference.
-We could not extend this to US-Vietnam responding comparison.}\label{fig:unnamed-chunk-8}
+
+{\centering \includegraphics{figs/unnamed-chunk-4-1}
+
+}
+
+\caption[Proportion of thematic responses by country]{Proportion of thematic responses by country.}\label{fig:unnamed-chunk-4}
 \end{figure}
@@
 
-No effect of country on filler responding.
+For each filler triad, we randomly assigned one of the responding
+optiosn as `Word1'. Running a mixed-effects logistic regression predict
+responding (Word1 or Word2) with structure equivalent to Analysis 1, we
+found no effect of country on filler responding (Figure 3).
 
@@
 
-\hypertarget{raw-co-occurrences-1}{%
-\paragraph{Raw co-occurrences}\label{raw-co-occurrences-1}}
-
-Yes, corpus raw co-occurrences predicts responding for both US and
-Vietnamese. \emph{need to discuss with Shan to incorporate Mandarin due
-to a lot of empty counts}
-
-\hypertarget{cosine-distance}{%
-\paragraph{Cosine distance}\label{cosine-distance}}
-
-Corpus cosine similarities also predict responding for all cultures.
+Using the same mixed-effects logistic regression structure as Analysis
+2, we predict responses (1=word1 or 0=word2) with corpus prediction
+(proportion of cosine distance) as a fixed effect and participant and
+triad as random effects. We found that in all cultural contexts, the
+correpsonding corpora is a significant predictor of responding, with
+p\textless0.05 and \(\beta\) from -9.59 to -3.05. (For a full report,
+see Appendix.)
 
@@
 fit in cross-language comparisons between models and data.
-
-There are some suggestions that the current approach can predict
-triad-specific cross-cultural effects. First of all, an ANOVA model
-comparison showed that adding a random effect term for varying slope by
-country and varying intercept by triad to the model produces a
-significant better fit than the identical model without this random
-effect term included as a predictor (\(\chi^2\)(6) = 7481.6, p
-\textless{} .001)
 
@@
 
+\hypertarget{appendix}{%
+\section{Appendix}\label{appendix}}
+
+\hypertarget{icc-of-item-variability-and-participant-variability}{%
+\subsection{1. ICC of item variability and participant
+variability}\label{icc-of-item-variability-and-participant-variability}}
+
+\begin{table}[ht]
+\centering
+\begin{tabular}{lrr}
+  \hline
+Sample & Intra-rater ICC & Inter-rater ICC \\ 
+  \hline
+US & 0.32 & 0.97 \\ 
+  China & 0.20 & 0.96 \\ 
+  Vietnam & 0.32 & 0.95 \\ 
+   \hline
+\end{tabular}
+\caption{ICCs for reliability within participants (intra-rater) and stimuli (inter-rater) for all cultural contexts.} 
+\end{table}
+
+\hypertarget{supplemental-for-whether-each-corpus-predicts-similarity-judgement-in-each-cultural-context}{%
+\subsection{2. Supplemental for whether each corpus predicts similarity
+judgement in each cultural
+context}\label{supplemental-for-whether-each-corpus-predicts-similarity-judgement-in-each-cultural-context}}
+
+\hypertarget{triads}{%
+\subsubsection{Triads}\label{triads}}
+
+For US responding: English (EN), Vietnamese (VI), and Mandarin (ZH)
+corpus are significant predictors of US responding (EN-US model:
+\(\beta\) = -9.05, \(\chi^2\)(1) = 31.28, p \textless{} .001; VI-US
+model: \(\beta\) = -3.13, \(\chi^2\)(1) = 5.1, p = 0.024; ZH-US model:
+\(\beta\) = -7.42, \(\chi^2\)(1) = 18.48, p \textless{} .001).
+
+For Vietnam (VN) responding: English (EN), Vietnamese (VI), and Mandarin
+(ZH) corpus are significant predictors of VN responding (EN-VN model:
+\(\beta\) = -6.86, \(\chi^2\)(1) = 11.71, p \textless{} .001; VI-VN
+model: \(\beta\) = -3.83, \(\chi^2\)(1) = 6.02, p = 0.014; ZH-VN model:
+\(\beta\) = -7.49, \(\chi^2\)(1) = 13.84, p \textless{} .001).
+
+For China (CN) responding: English (EN), Vietnamese (VI), and Mandarin
+(ZH) corpus are significant predictors of CN responding (EN-CN model:
+\(\beta\) = -6.18, \(\chi^2\)(1) = 25.39, p \textless{} .001; VI-CN
+model: \(\beta\) = -2.44, \(\chi^2\)(1) = 5.75, p = 0.017; ZH-CN model:
+\(\beta\) = -7.36, \(\chi^2\)(1) = 37.72, p \textless{} .001).
+
+\hypertarget{fillers}{%
+\subsubsection{Fillers}\label{fillers}}
+
+English (EN) is a significant predictors of US responding (\(\beta\) =
+-7.93, \(\chi^2\)(1) = 35.87, p \textless{} .001).
+
+Vietnamese (VI) is a significant predictors of Vietnam responding
+(\(\beta\) = -3.05, \(\chi^2\)(1) = 5.88, p = 0.015).
+
+Mandarin (ZH) is a significant predictors of China responding (\(\beta\)
+= -9.59, \(\chi^2\)(1) = 36.65, p \textless{} .001).
+
+\hypertarget{demographic-exclusion-statistics}{%
+\subsection{3. Demographic Exclusion
+Statistics}\label{demographic-exclusion-statistics}}
+
+\begin{tabular}[t]{l|c|c|c}
+\hline
+\multicolumn{1}{c|}{ } & \multicolumn{3}{c}{Country} \\
+\cline{2-4}
+  & US & China & Vietnam\\
+\hline
+Ppts Finished & 200 & 200 & 199\\
+\hline
+\multicolumn{4}{l}{\textbf{Attention Check Exclusions}}\\
+\hline
+\hspace{1em}Excluded & 26 & 34 & 123\\
+\hline
+\hspace{1em}After Exclusion & 174 & 166 & 76\\
+\hline
+\multicolumn{4}{l}{\textbf{Demographics Exclusions}}\\
+\hline
+\hspace{1em}Non-Native Speakers & 18 * & 3 * & 2 *\\
+\hline
+\hspace{1em}EN Speakers & N/A & 79 & 127\\
+\hline
+\hspace{1em}VI Speakers & 4 * & 1 * & N/A\\
+\hline
+\hspace{1em}ZH Speakers & 30 * & N/A & 9 *\\
+\hline
+\hspace{1em}Lived Abroad & 29 * & 40 * & 18 *\\
+\hline
+\hspace{1em}Overseas Experience & 77 & 12 * & 20 *\\
+\hline
+\hspace{1em}After Exclusions & 109 & 132 & 57\\
+\hline
+\end{tabular}
+
 \newpage
-
-\hypertarget{two-column-images}{%
-\subsection{Two-column images}\label{two-column-images}}
-
-You can read local images using png package for example and plot it like
-a regular plot using grid.raster from the grid package. With this method
-you have full control of the size of your image. \textbf{Note: Image
-must be in .png file format for the readPNG function to work.}
-
-You might want to display a wide figure across both columns. To do this,
-you change the \texttt{fig.env} chunk option to \texttt{figure*}. To
-align the image in the center of the page, set \texttt{fig.align} option
-to \texttt{center}. To format the width of your caption text, you set
-the \texttt{num.cols.cap} option to \texttt{2}.
-
-\begin{CodeChunk}
-\begin{figure*}[h]
-
-{\centering \includegraphics{figs/2-col-image-1}
-
-}
-
-\caption[This image spans both columns]{This image spans both columns. And the caption text is limited to 0.8 of the width of the document.}\label{fig:2-col-image}
-\end{figure*}
-\end{CodeChunk}
-
-\hypertarget{one-column-images}{%
-\subsection{One-column images}\label{one-column-images}}
-
-Single column is the default option, but if you want set it explicitly,
-set \texttt{fig.env} to \texttt{figure}. Notice that the
-\texttt{num.cols} option for the caption width is set to \texttt{1}.
-
-\begin{CodeChunk}
-\begin{figure}[H]
-
-{\centering \includegraphics{figs/image-1}
-
-}
-
-\caption[One column image]{One column image.}\label{fig:image}
-\end{figure}
-\end{CodeChunk}
-
-\hypertarget{r-plots}{%
-\subsection{R Plots}\label{r-plots}}
-
-You can use R chunks directly to plot graphs. And you can use latex
-floats in the fig.pos chunk option to have more control over the
-location of your plot on the page. For more information on latex
-placement specifiers see
-\textbf{\href{https://en.wikibooks.org/wiki/LaTeX/Floats,_Figures_and_Captions}{here}}
-
-\begin{CodeChunk}
-\begin{figure}[H]
-
-{\centering \includegraphics{figs/plot-1}
-
-}
-
-\caption[R plot]{R plot}\label{fig:plot}
-\end{figure}
-\end{CodeChunk}
-
-\hypertarget{tables}{%
-\subsection{Tables}\label{tables}}
-
-Number tables consecutively; place the table number and title (in 10
-point) above the table with one line space above the caption and one
-line space below it, as in Table 1. You may float tables to the top or
-bottom of a column, set wide tables across both columns.
-
-You can use the xtable function in the xtable package.
-
-\begin{table}[H]
-\centering
-\begin{tabular}{rrrrr}
-  \hline
- & Estimate & Std. Error & t value & Pr($>$$|$t$|$) \\ 
-  \hline
-(Intercept) & 0.02 & 0.10 & 0.2 & 0.86 \\ 
-  x & 2.04 & 0.11 & 19.1 & 0.00 \\ 
-   \hline
-\end{tabular}
-\caption{This table prints across one column.} 
-\end{table}
 
@@
 \noindent
+
+\newpage
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-COCA}{}}%
-Davies, M. (2008-2008-). The corpus of contemporary american english
-(COCA). Retrieved from \url{https://www.english-corpora.org/coca/}
-
 \leavevmode\vadjust pre{\hypertarget{ref-Francis2005}{}}%
@@
 representation}. Oxford University Press.
-
-\leavevmode\vadjust pre{\hypertarget{ref-VICorpus}{}}%
-Goldhahn, D., Eckart, T., \& Quasthoff, U. (2012). Building large
-monolingual dictionaries at the leipzig corpora collection: From 100 to
-200 languages. Retrieved from
-\url{https://wortschatz.uni-leipzig.de/en/download/vietnamese}
 

### 2023-01-20 code/4_paper/manuscript/manuscript_0119.Rmd
cogsci paper exchange

--- 2023-01-20 code/4_paper/manuscript/manuscript.Rmd
@@
 library("effsize")
-library("kableExtra")
 library("irr")
@@
 # set the default ggplot theme 
-theme_set(theme_classic(base_size = 7))
+theme_set(theme_classic())
 
@@
 ```{r get exclusions data, include = F, cache = T}
-df.excl_US <- read.csv("../../../data/responding/dataUS_excl_metadata.csv") %>%
-  select(-X)
-df.excl_CN <- read.csv("../../../data/responding/dataCN_excl_metadata.csv") %>%
-  select(-X)
-df.excl_VN <- read.csv("../../../data/responding/dataVN_excl_metadata.csv") %>%
-  select(-X)
+df.excl_US <- read.csv("../../../data/responding/dataUS_excl_metadata.csv")
+df.excl_CN <- read.csv("../../../data/responding/dataCN_excl_metadata.csv")
+df.excl_VN <- read.csv("../../../data/responding/dataVN_excl_metadata.csv")
 ```
@@
 
-```{r echo=FALSE, warning=FALSE, cache = TRUE, fig.env="figure", fig.align = "center", fig.cap="Proportion of thematic responses by country."}
+```{r echo=FALSE, warning=FALSE, cache = TRUE, fig.env="figure", fig.pos = "H", fig.align = "center", fig.width=2, fig.height=2, fig.cap="Proportion of thematic responses by country."}
 
@@
 
+<!-- #### Raw lexical co-occurrences -->
+
+<!-- To test whether variation in lexical co-occurrence can explain differences in similarity judgments between US and Vietnam participants, we compare logistic mixed-effects regression models fit to the thematic responding data from each country separately.
+We first ask how well each corpus model (English, Vietnamese, or Mandarin) predicts similarity judgments by speakers of the corresponding language (US, Vietnam, or China).
+To do this, we use a mixed-effects logistic regression to predict triad responses (0=taxonomic or 1=thematic) with corpus prediction (proportion thematic co-occurrence or cosine distance) as a fixed effect and participant and triad as random effects.
+-->
+
+<!-- ```{r US responding predicted by each corpus model raw co-occurrences, warning=FALSE, include=F, cache = TRUE} -->
+<!-- # English  -->
+<!-- fit.EN_US = glmer(responses_theme ~ theme_freq_prop_E + (1 | subject) + (1 | triad),  -->
+<!--           data = df %>% filter(country == "US", !(triad %in% triads_omit)),  -->
+<!--           family="binomial") -->
+<!-- summary(fit.EN_US) -->
+<!-- fit.EN_US.anova = Anova(fit.EN_US, type = 3) -->
+
+<!-- #Vietnamese -->
+<!-- fit.VI_US = glmer(responses_theme ~ theme_freq_prop_V + (1 | subject) + (1 | triad),  -->
+<!--           data = df %>% filter(country == "US", !(triad %in% triads_omit)),  -->
+<!--           family="binomial") -->
+<!-- summary(fit.VI_US) -->
+<!-- fit.VI_US.anova = Anova(fit.VI_US, type = 3) -->
+
+<!-- #Mandarin -->
+<!-- fit.ZH_US = glmer(responses_theme ~ theme_freq_prop_M + (1 | subject) + (1 | triad),  -->
+<!--           data = df %>% filter(country == "US", !(triad %in% triads_omit)),  -->
+<!--           family="binomial") -->
+<!-- summary(fit.ZH_US) -->
+<!-- fit.ZH_US.anova = Anova(fit.ZH_US, type = 3) -->
+<!-- ``` -->
+
+<!-- ```{r VN responding predicted by each corpus model raw co-occurrences, warning=FALSE, include=F, cache = TRUE} -->
+<!-- # English  -->
+<!-- fit.EN_VN = glmer(responses_theme ~ theme_freq_prop_E + (1 | subject) + (1 | triad),  -->
+<!--           data = df %>% filter(country == "Vietnam", !(triad %in% triads_omit)),  -->
+<!--           family="binomial") -->
+<!-- summary(fit.EN_VN) -->
+<!-- fit.EN_VN.anova = Anova(fit.EN_VN, type = 3) -->
+
+<!-- #Vietnamese -->
+<!-- fit.VI_VN = glmer(responses_theme ~ theme_freq_prop_V + (1 | subject) + (1 | triad),  -->
+<!--           data = df %>% filter(country == "Vietnam", !(triad %in% triads_omit)),  -->
+<!--           family="binomial") -->
+<!-- summary(fit.VI_VN) -->
+<!-- fit.VI_VN.anova = Anova(fit.VI_VN, type = 3) -->
+
+<!-- #Mandarin -->
+<!-- fit.ZH_VN = glmer(responses_theme ~ theme_freq_prop_M + (1 | subject) + (1 | triad),  -->
+<!--           data = df %>% filter(country == "Vietnam", !(triad %in% triads_omit)),  -->
+<!--           family="binomial") -->
+<!-- summary(fit.ZH_VN) -->
+<!-- fit.ZH_VN.anova = Anova(fit.ZH_VN, type = 3) -->
+<!-- ``` -->
+
+<!-- ```{r CN responding predicted by each corpus model raw co-occurrences, warning=FALSE, include=F, cache = TRUE} -->
+<!-- #English -->
+<!-- fit.EN_CN = glmer(responses_theme ~ theme_freq_prop_E + (1 | subject) + (1 | triad),  -->
+<!--           data = df %>% filter(country == "China", !(triad %in% triads_omit)),  -->
+<!--           family="binomial") -->
+<!-- summary(fit.EN_CN) -->
+<!-- fit.EN_CN.anova = Anova(fit.EN_CN, type = 3) -->
+
+<!-- #Vietnamese -->
+<!-- fit.VI_CN = glmer(responses_theme ~ theme_freq_prop_V + (1 | subject) + (1 | triad),  -->
+<!--           data = df %>% filter(country == "China", !(triad %in% triads_omit)),  -->
+<!--           family="binomial") -->
+<!-- summary(fit.VI_CN) -->
+<!-- fit.VI_CN.anova = Anova(fit.VI_CN, type = 3) -->
+
+<!-- #Mandarin -->
+<!-- fit.ZH_CN = glmer(responses_theme ~ theme_freq_prop_M + (1 | subject) + (1 | triad),  -->
+<!--           data = df %>% filter(country == "China", !(triad %in% triads_omit)),  -->
+<!--           family="binomial") -->
+<!-- summary(fit.ZH_CN) -->
+<!-- fit.ZH_CN.anova = Anova(fit.ZH_CN, type = 3) -->
+<!-- ``` -->
+
+<!-- ```{r calculate range of beta statistics for lexical cooc, warning=F, include=F} -->
+<!-- beta.single_corpus_freq <- c( -->
+<!--   round(fixef(fit.EN_US)["theme_freq_prop_E"], 2), -->
+<!--   round(fixef(fit.VI_US)["theme_freq_prop_V"], 2),  -->
+<!--   round(fixef(fit.ZH_US)["theme_freq_prop_M"], 2),  -->
+
+<!--   round(fixef(fit.EN_CN)["theme_freq_prop_E"], 2), -->
+<!--   round(fixef(fit.VI_CN)["theme_freq_prop_V"], 2),  -->
+<!--   round(fixef(fit.ZH_CN)["theme_freq_prop_M"], 2),  -->
+
+<!--   round(fixef(fit.EN_VN)["theme_freq_prop_E"], 2), -->
+<!--   round(fixef(fit.VI_VN)["theme_freq_prop_V"], 2),  -->
+<!--   round(fixef(fit.ZH_VN)["theme_freq_prop_M"], 2) -->
+
+<!-- ) -->
+<!-- ``` -->
+<!-- We found that all corpora are significant predictors of all cultural context responding, with p < 0.05 and $\beta$ from `r # min(beta.single_corpus_freq)` to `r #max(beta.single_corpus_freq)`.
+(For a full report, see Appendix.) -->
+
+<!-- This suggests a strong shared similarity signal across the languages. -->
+
+<!-- #### Cosine distances of fastText word vectors -->
+
 ```{r US responding predicted by each corpus model cosine differences, warning=FALSE, include=F}
@@
 
-### Is responding in each cultural context best predicted by the corresponding corpus's lexical statistics, as opposed to the other two corpora?
+### Is responding in each cultural context __best__ predicted by the corresponding corpus's lexical statistics, as opposed to the other two corpora?
 Next, we directly compare the corpus models by including both as fixed effects in three mixed-effect regressions (predicting US, Vietnam and China responding) with the same random effects as above.
 In R syntax, the model is: response ~ corpus_English + corpus_Vietnamese + corpus_Mandarin + (1|triad) + (1|subject).
+
+<!-- #### Raw co-occurrences  -->
+
+<!-- ```{r Eng-Vie-Mand lexical co-occ predicting US, warning=FALSE, include=F, cache = TRUE} -->
+<!-- # ADDITION: adding theme_freq_prop_M,  -->
+<!-- #raw co-occurrences -->
+<!-- #linear mixed model with ALL corpora as predictors for each population. -->
+<!-- fit.ENVIZH_US = glmer(responses_theme ~  -->
+<!--                       theme_freq_prop_E + theme_freq_prop_V + theme_freq_prop_M + -->
+<!--                       (1 | subject) + (1 | triad),  -->
+<!--                     data = df %>% filter(country == "US", !(triad %in% triads_omit)), -->
+<!--                     family="binomial") -->
+<!-- summary(fit.ENVIZH_US) -->
+<!-- fit.ENVIZH_US.anova = Anova(fit.ENVIZH_US, type = 3) -->
+<!-- fit.ENVIZH_US.anova -->
+<!-- ``` -->
+<!-- For US responding: only English (EN) corpus is a significant predictor.
+EN corpus: $\beta$ = `r round(fixef(fit.ENVIZH_US)["theme_freq_prop_E"], 2)`, $\chi^2$(`r fit.ENVIZH_US.anova["theme_freq_prop_E", "Df"]`) = `r round(fit.ENVIZH_US.anova["theme_freq_prop_E", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_US.anova["theme_freq_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_US.anova["theme_freq_prop_E", "Pr(>Chisq)"], 3)), "< .001")`.
+VI corpus: $\beta$ = `r round(fixef(fit.ENVIZH_US)["theme_freq_prop_V"], 2)`, $\chi^2$(`r fit.ENVIZH_US.anova["theme_freq_prop_V", "Df"]`) = `r round(fit.ENVIZH_US.anova["theme_freq_prop_V", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_US.anova["theme_freq_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_US.anova["theme_freq_prop_V", "Pr(>Chisq)"], 3)), "< .001")`.
+ZH corpus: $\beta$ = `r round(fixef(fit.ENVIZH_US)["theme_freq_prop_M"], 2)`, $\chi^2$(`r fit.ENVIZH_US.anova["theme_freq_prop_M", "Df"]`) = `r round(fit.ENVIZH_US.anova["theme_freq_prop_M", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_US.anova["theme_freq_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_US.anova["theme_freq_prop_M", "Pr(>Chisq)"], 3)), "< .001")`.
+-->
+
+<!-- ```{r Eng-Vie-Mand lexical co-occ predicting VN, warning=FALSE, include=F, cache = TRUE} -->
+<!-- fit.ENVIZH_VN = glmer(responses_theme ~  -->
+<!--                       theme_freq_prop_V + theme_freq_prop_E + theme_freq_prop_M + -->
+<!--                       (1 | subject) + (1 | triad),  -->
+<!--                     data = df %>% filter(country == "Vietnam", !(triad %in% triads_omit)), -->
+<!--                     family="binomial") -->
+<!-- summary(fit.ENVIZH_VN) -->
+<!-- fit.ENVIZH_VN.anova = Anova(fit.ENVIZH_VN, type = 3) -->
+<!-- fit.ENVIZH_VN.anova -->
+<!-- ``` -->
+<!-- For Vietnam responding: only Mandarin (ZH) corpus is a significant predictor.
+EN corpus: $\beta$ = `r round(fixef(fit.ENVIZH_VN)["theme_freq_prop_E"], 2)`, $\chi^2$(`r fit.ENVIZH_VN.anova["theme_freq_prop_E", "Df"]`) = `r round(fit.ENVIZH_VN.anova["theme_freq_prop_E", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_VN.anova["theme_freq_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_VN.anova["theme_freq_prop_E", "Pr(>Chisq)"], 3)), "< .001")`.
+ZH corpus: $\beta$ = `r round(fixef(fit.ENVIZH_VN)["theme_freq_prop_M"], 2)`, $\chi^2$(`r fit.ENVIZH_VN.anova["theme_freq_prop_M", "Df"]`) = `r round(fit.ENVIZH_VN.anova["theme_freq_prop_M", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_VN.anova["theme_freq_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_VN.anova["theme_freq_prop_M", "Pr(>Chisq)"], 3)), "< .001")`.VI corpus: $\beta$ = `r round(fixef(fit.ENVIZH_VN)["theme_freq_prop_V"], 2)`, $\chi^2$(`r fit.ENVIZH_VN.anova["theme_freq_prop_V", "Df"]`) = `r round(fit.ENVIZH_VN.anova["theme_freq_prop_V", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_VN.anova["theme_freq_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_VN.anova["theme_freq_prop_V", "Pr(>Chisq)"], 3)), "< .001")`.
+-->
+
+<!-- ```{r Eng-Vie-Mand lexical co-occ predicting CN, warning=FALSE, include=F, cache = TRUE} -->
+<!-- fit.ENVIZH_CN = glmer(responses_theme ~  -->
+<!--                       theme_freq_prop_M + theme_freq_prop_E + theme_freq_prop_V + -->
+<!--                       (1 | subject) + (1 | triad),  -->
+<!--                     data = df %>% filter(country == "China", !(triad %in% triads_omit)), -->
+<!--                     family="binomial") -->
+<!-- summary(fit.ENVIZH_CN) -->
+<!-- fit.ENVIZH_CN.anova = Anova(fit.ENVIZH_CN, type = 3) -->
+<!-- fit.ENVIZH_CN.anova -->
+<!-- ``` -->
+<!-- For China responding: only Mandarin (ZH) corpus is a significant predictor.
+ZH corpus: $\beta$ = `r round(fixef(fit.ENVIZH_CN)["theme_freq_prop_M"], 2)`, $\chi^2$(`r fit.ENVIZH_CN.anova["theme_freq_prop_M", "Df"]`) = `r round(fit.ENVIZH_CN.anova["theme_freq_prop_M", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_CN.anova["theme_freq_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_CN.anova["theme_freq_prop_M", "Pr(>Chisq)"], 3)), "< .001")`.
+EN corpus: $\beta$ = `r round(fixef(fit.ENVIZH_CN)["theme_freq_prop_E"], 2)`, $\chi^2$(`r fit.ENVIZH_CN.anova["theme_freq_prop_E", "Df"]`) = `r round(fit.ENVIZH_CN.anova["theme_freq_prop_E", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_CN.anova["theme_freq_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_CN.anova["theme_freq_prop_E", "Pr(>Chisq)"], 3)), "< .001")`.
+VI corpus: $\beta$ = `r round(fixef(fit.ENVIZH_CN)["theme_freq_prop_V"], 2)`, $\chi^2$(`r fit.ENVIZH_CN.anova["theme_freq_prop_V", "Df"]`) = `r round(fit.ENVIZH_CN.anova["theme_freq_prop_V", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_CN.anova["theme_freq_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_CN.anova["theme_freq_prop_V", "Pr(>Chisq)"], 3)), "< .001")`.
+-->
+
+<!-- ```{r echo=FALSE, warning = FALSE, cache = TRUE, fig.cap = "Fixed effect sizes of each corpus when included as a predictor for China, US, and Vietnam responding, respectively.
+The English corpus is the best predictor for US response, and the Mandarin corpus is the best predictor for China response."} -->
+<!-- coeff_value_freq <- c(fixef(fit.ENVIZH_US)["theme_freq_prop_M"], -->
+<!--                  fixef(fit.ENVIZH_US)["theme_freq_prop_E"],  -->
+<!--                  fixef(fit.ENVIZH_US)["theme_freq_prop_V"], -->
+<!--                  fixef(fit.ENVIZH_VN)["theme_freq_prop_M"], -->
+<!--                  fixef(fit.ENVIZH_VN)["theme_freq_prop_E"], -->
+<!--                  fixef(fit.ENVIZH_VN)["theme_freq_prop_V"],  -->
+<!--                  fixef(fit.ENVIZH_CN)["theme_freq_prop_M"], -->
+<!--                  fixef(fit.ENVIZH_CN)["theme_freq_prop_E"],  -->
+<!--                  fixef(fit.ENVIZH_CN)["theme_freq_prop_V"]) -->
+
+<!-- se_value_freq <- c(summary(fit.ENVIZH_US)$coef["theme_freq_prop_M", "Std. Error"],  -->
+<!--               summary(fit.ENVIZH_US)$coef["theme_freq_prop_E", "Std. Error"], -->
+<!--               summary(fit.ENVIZH_US)$coef["theme_freq_prop_V", "Std. Error"],  -->
+<!--               summary(fit.ENVIZH_VN)$coef["theme_freq_prop_M", "Std. Error"],  -->
+<!--               summary(fit.ENVIZH_VN)$coef["theme_freq_prop_E", "Std. Error"], -->
+<!--               summary(fit.ENVIZH_VN)$coef["theme_freq_prop_V", "Std. Error"], -->
+<!--               summary(fit.ENVIZH_CN)$coef["theme_freq_prop_M", "Std. Error"],  -->
+<!--               summary(fit.ENVIZH_CN)$coef["theme_freq_prop_E", "Std. Error"], -->
+<!--               summary(fit.ENVIZH_CN)$coef["theme_freq_prop_V", "Std. Error"]) -->
+
+<!-- country_value <- c(rep("US", 3), -->
+<!--                    rep("VN", 3), -->
+<!--                    rep("CN", 3)) -->
+
+<!-- corpus_value <- c(rep(c("ZH", "EN", "VI"), 3)) -->
+
+<!-- df.USVNCN_coeffs_freq <- data.frame(country_value, corpus_value, coeff_value_freq, se_value_freq) %>% -->
+<!--   mutate(corpus_value = factor(corpus_value, levels=c("ZH", "EN", "VI"))) -->
+
+<!-- plot.coeffs_freq <- ggplot(data = df.USVNCN_coeffs_freq,  -->
+<!--        mapping = aes(x = country_value, y = coeff_value_freq, fill = corpus_value)) + -->
+<!--   geom_bar(position="dodge", stat="identity") + -->
+<!--   geom_errorbar(aes(ymin= coeff_value_freq - se_value_freq, ymax = coeff_value_freq + se_value_freq), width=.2, -->
+<!--                  position=position_dodge(.9)) + -->
+<!--   labs(x = "Country", y = "Fixed effect size", fill = "Corpus") +  -->
+<!--   scale_x_discrete(labels=c("CN" = "China", "US" = "US", "VN" = "Vietnam")) +  -->
+<!--   scale_fill_manual(values=c("#D63230", "#1C77C3", "#F39237")) +  -->
+<!--   ggtitle('a') -->
+
+<!-- ``` -->
+
+<!-- ```{r freq model comparison, include=FALSE, cache = TRUE} -->
+<!-- fit.US_freq_compare = anova(fit.ENVIZH_US, fit.EN_US, type = 3) -->
+<!-- fit.VN_freq_compare = anova(fit.ENVIZH_VN, fit.VI_VN, type = 3) -->
+<!-- fit.CN_freq_compare = anova(fit.ENVIZH_CN, fit.ZH_CN, type = 3) -->
+<!-- ``` -->
+
+<!-- We observed some level of language specificity from this analysis.
+The English corpus is the only significant predictor for US responding, and the Mandarin corpus is the only significant predictor for China response.
+However, against our prediction, the Vietnamese corpus was not a significant predictor for Vietnam responding when other corpora were included.
+(Figure 2a).
+-->
+
+<!-- <!-- Nonetheless, we found that language specificity alone does not explain our results.
+We used an ANOVA to compare the model with only the corresponding corpus, and the model with all 3 corpora for each cultural context.
+We found that in all three cases (US, China, Vietnam), adding the other two corpora produces a significantly better fit than the identical model without the additional corpora, and only the corresponding corpus included as a predictor (US response: $\chi^2$(`r fit.US_freq_compare["fit.ENVIZH_US", "Df"]`) = `r round(fit.US_freq_compare["fit.ENVIZH_US", "Chisq"], 2)`, p `r ifelse( fit.US_freq_compare["fit.ENVIZH_US", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.US_freq_compare["fit.ENVIZH_US", "Pr(>Chisq)"], 3)), "< .001")`; Vietnam response: $\chi^2$(`r fit.VN_freq_compare["fit.ENVIZH_VN", "Df"]`) = `r round(fit.VN_freq_compare["fit.ENVIZH_VN", "Chisq"], 2)`, p `r ifelse( fit.VN_freq_compare["fit.ENVIZH_VN", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.VN_freq_compare["fit.ENVIZH_VN", "Pr(>Chisq)"], 3)), "< .001")`; China response: $\chi^2$(`r fit.CN_freq_compare["fit.ENVIZH_CN", "Df"]`) = `r round(fit.CN_freq_compare["fit.ENVIZH_CN", "Chisq"], 2)`, p `r ifelse( fit.CN_freq_compare["fit.ENVIZH_CN", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.CN_freq_compare["fit.ENVIZH_CN", "Pr(>Chisq)"], 3)), "< .001")`).
+-->
+
+#### Cosine distances of fastText word vectors
 
@@
   scale_x_discrete(labels=c("CN" = "China", "US" = "US", "VN" = "Vietnam")) + 
-  scale_fill_manual(values=c("#D63230", "#1C77C3", "#F39237"))
-```
-
-```{r echo=FALSE, warning=FALSE, cache = TRUE, fig.env = "figure", fig.align = "center", set.cap.width=T, num.cols.cap=1, fig.cap="Fixed effect sizes of each corpus lexical statistics (cosine distance proportion) when included as a predictor for China, US, and Vietnam responding, respectively.
+  scale_fill_manual(values=c("#D63230", "#1C77C3", "#F39237")) + 
+  ggtitle('b')
+```
+
+```{r echo=FALSE, warning=FALSE, cache = TRUE, fig.env = "figure", fig.pos = "h", fig.width=2, fig.height=2, fig.align = "center", set.cap.width=T, num.cols.cap=1, fig.cap="Fixed effect sizes of each corpus lexical statistics (cosine distance proportion) when included as a predictor for China, US, and Vietnam responding, respectively.
 The English corpus is the best predictor for US response, and the Mandarin corpus is the best predictor for China response."}
@@
 We found that in all three cases (US, China, Vietnam), adding the other two corpora produces a significantly better fit than the identical model without the additional corpora, and only the corresponding corpus included as a predictor (US response: $\chi^2$(`r fit.US_cos_compare["fit.ENVIZH_US_cos", "Df"]`) = `r round(fit.US_cos_compare["fit.ENVIZH_US_cos", "Chisq"], 2)`, p `r ifelse( fit.US_cos_compare["fit.ENVIZH_US_cos", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.US_cos_compare["fit.ENVIZH_US_cos", "Pr(>Chisq)"], 3)), "< .001")`; Vietnam response: $\chi^2$(`r fit.VN_cos_compare["fit.ENVIZH_VN_cos", "Df"]`) = `r round(fit.VN_cos_compare["fit.ENVIZH_VN_cos", "Chisq"], 2)`, p `r ifelse( fit.VN_cos_compare["fit.ENVIZH_VN_cos", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.VN_cos_compare["fit.ENVIZH_VN_cos", "Pr(>Chisq)"], 3)), "< .001")`; China response: $\chi^2$(`r fit.CN_cos_compare["fit.ENVIZH_CN_cos", "Df"]`) = `r round(fit.CN_cos_compare["fit.ENVIZH_CN_cos", "Chisq"], 2)`, p `r ifelse( fit.CN_cos_compare["fit.ENVIZH_VN_cos", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.CN_cos_compare["fit.ENVIZH_VN_cos", "Pr(>Chisq)"], 3)), "< .001")`).
+
+<!-- ```{r add linguistic model to Ji et al., include=FALSE} -->
+<!-- # this is probably similar to Q3 -->
+<!-- fit.country = glmer(responses_theme ~ country + (1 | subject) + (1 | triad),  -->
+<!--                            data = df %>% filter(country != "Vietnam"),  -->
+<!--                            family = "binomial") -->
+
+<!-- fit.country_corpus = glmer(responses_theme ~ country + theme_cosine_prop_E + theme_cosine_prop_M + (1 | subject) + (1 | triad),  -->
+<!--                            data = df %>% filter(country != "Vietnam"),  -->
+<!--                            family = "binomial") -->
+
+<!-- fit.add_corpus <- anova(fit.country, fit.country_corpus, type = 3) -->
+
+<!-- ``` -->
+
+<!-- Our approach would be to compare a model that only includes country (US or China) as a fixed effect with one that also includes English and Chinese corpus data.
+Our previous model with an intercept per subject and one per triad, as well as by-triad random slopes for country to account for variation in the country effect across triads fails to converge with the more complex model, so we include a simpler random effect structure with an intercept per subject and one per triad in both the basic and more complex model.
+We compare this model with an identical model but including Chinese and English corpus cosine distance proportion prediction.
+We found that adding English and Chinese corpus data produces a significantly better fit than the identical model without English and Chinese corpus data as predictors ($\chi^2$(`r fit.add_corpus["fit.country_corpus", "Df"]`) = `r round(fit.add_corpus["fit.country_corpus", "Chisq"], 2)`, p = < .001.
+This suggests that including corpus data would better model the cross-cultural differences in similarity judgment in this study as well as similar studies.
+-->
 
@@
 
-```{r echo=FALSE, warning=FALSE, cache = TRUE, fig.env="figure", fig.align = "center", fig.cap="Proportion of thematic responses by country."}
+```{r echo=FALSE, warning=FALSE, cache = TRUE, fig.env="figure", fig.pos = "H", fig.align = "center", fig.width=2, fig.height=2, fig.cap="Proportion of thematic responses by country."}
 #show violin plot
@@
   labs(y = "Proportion Word1 Chosen", 
-       x = "Country") + 
-  scale_color_manual(values=c("#D63230", "#1C77C3", "#F39237")) + 
-  theme(legend.position = "none")
-```
-
-```{r warning=FALSE, include = F, cache = TRUE, fig.env="figure", paged.print=TRUE}
+       x = "Country", 
+       color = "Country") + 
+  scale_color_manual(values=c("#D63230", "#1C77C3", "#F39237"))
+```
+
+```{r warning=FALSE, include = F, cache = TRUE, fig.env="figure", fig.width=2, fig.height=2, paged.print=TRUE}
 # df.country_sum <- df.country %>%
@@
 ### Does lexical statistics for fillers predict responding in the corresponding cultural context?
+Using the same model structure as Analysis 2 ()
 <!-- #### Raw co-occurrences -->
@@
 We find even stronger evidence for consistency across the three groups, with substantive overlapping predictions across the corpus models, highly similar responding across the experiments, and a correspondingly high fit in cross-language comparisons between models and data.
+
+<!-- ```{r include=FALSE, cache = TRUE} -->
+<!-- fit.country_no_triad <- glmer(responses_theme ~ country + (1 | subject),  -->
+<!--                               data = df_main_analysis,  -->
+<!--                               family = "binomial") -->
+
+<!-- fit.country = glmer(responses_theme ~ country + (1 | subject) + (country | triad),  -->
+<!--                     data = df_main_analysis,  -->
+<!--                     family = "binomial") -->
+<!-- summary(fit.country) -->
+
+<!-- fit.no_triad_compare <- anova(fit.country, fit.country_no_triad, type = 3) -->
+<!-- ``` -->
+
+<!-- There are some suggestions that the current approach can predict triad-specific cross-cultural effects.
+First of all, an ANOVA model comparison showed that adding a random effect term for varying slope by country and varying intercept by triad to the model produces a significant better fit than the identical model without this random effect term included as a predictor ($\chi^2$(`r fit.no_triad_compare["fit.country", "Df"]`) = `r round(fit.no_triad_compare["fit.country", "Chisq"], 2)`, p `r ifelse( fit.no_triad_compare["fit.country", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.no_triad_compare["fit.country", "Pr(>Chisq)"], 3)), "< .001")`) -->
 
@@
 
+\newpage
+
+# Acknowledgements
+
+Place acknowledgments (including funding information) in a section at
+the end of the paper.
+
+# References
+
+```{r}
+# References will be generated automatically by Pandoc and included here.
+# The following code is some latex to format the bibliography. Do not remove it.
+```
+
+\setlength{\parindent}{-0.1in} 
+\setlength{\leftskip}{0.125in}
+\noindent
+
+\newpage
+
 # Appendix
@@
 
-```{r xtable, results ="asis", fig.pos="H"}
+```{r xtable, results ="asis"}
 US_agr <- agreement::dim_icc(df_main_analysis %>% filter(country == "US"),
@@
 
-print(tab1, type="latex", comment = F, include.rownames = FALSE)
+print(tab1, type="latex", comment = F, table.placement = "t", include.rownames = FALSE)
 ```
@@
 ## 2. Supplemental for whether each corpus predicts similarity judgement in each cultural context
+<!-- ### Lexical co-occurrence -->
+<!-- For US responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are all significant predictors.
+EN corpus: $\beta$ = `r round(fixef(fit.EN_US)["theme_freq_prop_E"], 2)`, $\chi^2$(`r fit.EN_US.anova["theme_freq_prop_E", "Df"]`) = `r round(fit.EN_US.anova["theme_freq_prop_E", "Chisq"], 2)`, p `r ifelse( fit.EN_US.anova["theme_freq_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.EN_US.anova["theme_freq_prop_E", "Pr(>Chisq)"], 3)), "< .001")`.
+VI corpus: $\beta$ = `r round(fixef(fit.VI_US)["theme_freq_prop_V"], 2)`, $\chi^2$(`r fit.VI_US.anova["theme_freq_prop_V", "Df"]`) = `r round(fit.VI_US.anova["theme_freq_prop_V", "Chisq"], 2)`, p `r ifelse( fit.VI_US.anova["theme_freq_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.VI_US.anova["theme_freq_prop_V", "Pr(>Chisq)"], 3)), "< .001")`.
+ZH corpus: $\beta$ = `r round(fixef(fit.ZH_US)["theme_freq_prop_M"], 2)`, $\chi^2$(`r fit.ZH_US.anova["theme_freq_prop_M", "Df"]`) = `r round(fit.ZH_US.anova["theme_freq_prop_M", "Chisq"], 2)`, p `r ifelse( fit.ZH_US.anova["theme_freq_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ZH_US.anova["theme_freq_prop_M", "Pr(>Chisq)"], 3)), "< .001")`.
+-->
+
+<!-- For Vietnam responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are all significant predictors.
+EN corpus: $\beta$ = `r round(fixef(fit.EN_VN)["theme_freq_prop_E"], 2)`, $\chi^2$(`r fit.EN_VN.anova["theme_freq_prop_E", "Df"]`) = `r round(fit.EN_VN.anova["theme_freq_prop_E", "Chisq"], 2)`, p `r ifelse( fit.EN_VN.anova["theme_freq_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.EN_VN.anova["theme_freq_prop_E", "Pr(>Chisq)"], 3)), "< .001")`.
+VI corpus: $\beta$ = `r round(fixef(fit.VI_VN)["theme_freq_prop_V"], 2)`, $\chi^2$(`r fit.VI_VN.anova["theme_freq_prop_V", "Df"]`) = `r round(fit.VI_VN.anova["theme_freq_prop_V", "Chisq"], 2)`, p `r ifelse( fit.VI_VN.anova["theme_freq_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.VI_VN.anova["theme_freq_prop_V", "Pr(>Chisq)"], 3)), "< .001")`.
+ZH corpus: $\beta$ = `r round(fixef(fit.ZH_VN)["theme_freq_prop_M"], 2)`, $\chi^2$(`r fit.ZH_VN.anova["theme_freq_prop_M", "Df"]`) = `r round(fit.ZH_VN.anova["theme_freq_prop_M", "Chisq"], 2)`, p `r ifelse( fit.ZH_VN.anova["theme_freq_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ZH_VN.anova["theme_freq_prop_M", "Pr(>Chisq)"], 3)), "< .001")`.
+-->
+
+<!-- For China responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are all significant predictors.
+EN corpus: $\beta$ = `r round(fixef(fit.EN_CN)["theme_freq_prop_E"], 2)`, $\chi^2$(`r fit.EN_CN.anova["theme_freq_prop_E", "Df"]`) = `r round(fit.EN_CN.anova["theme_freq_prop_E", "Chisq"], 2)`, p `r ifelse( fit.EN_CN.anova["theme_freq_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.EN_CN.anova["theme_freq_prop_E", "Pr(>Chisq)"], 3)), "< .001")`.
+VI corpus: $\beta$ = `r round(fixef(fit.VI_CN)["theme_freq_prop_V"], 2)`, $\chi^2$(`r fit.VI_CN.anova["theme_freq_prop_V", "Df"]`) = `r round(fit.VI_CN.anova["theme_freq_prop_V", "Chisq"], 2)`, p `r ifelse( fit.VI_CN.anova["theme_freq_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.VI_CN.anova["theme_freq_prop_V", "Pr(>Chisq)"], 3)), "< .001")`.
+ZH corpus: $\beta$ = `r round(fixef(fit.ZH_US)["theme_freq_prop_M"], 2)`, $\chi^2$(`r fit.ZH_CN.anova["theme_freq_prop_M", "Df"]`) = `r round(fit.ZH_CN.anova["theme_freq_prop_M", "Chisq"], 2)`, p `r ifelse( fit.ZH_CN.anova["theme_freq_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ZH_CN.anova["theme_freq_prop_M", "Pr(>Chisq)"], 3)), "< .001")`.
+-->
 
@@
 Mandarin (ZH) is a significant predictors of China responding ($\beta$ = `r round(fixef(fit.ZH_CN_filler_cos)["word1_match_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ZH_CN_filler_cos.anova["word1_match_cosine_prop_M", "Df"]`) = `r round(fit.ZH_CN_filler_cos.anova["word1_match_cosine_prop_M", "Chisq"], 2)`, p `r ifelse( fit.ZH_CN_filler_cos.anova["word1_match_cosine_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ZH_CN_filler_cos.anova["word1_match_cosine_prop_M", "Pr(>Chisq)"], 3)), "< .001")`).
-
-## 3. Demographic Exclusion Statistics
-```{r results = "asis", fig.cap="Testing"}
-df.demog_excl <- cbind(t(df.excl_US), t(df.excl_CN))
-df.demog_excl <- cbind(df.demog_excl, t(df.excl_VN))
-
-rownames(df.demog_excl) <-
-  c("Country", "Ppts Finished", 
-    "Excluded", 
-    "After Exclusion", 
-    "Non-Native Speakers", "EN Speakers", 
-    "VI Speakers", "ZH Speakers", 
-    "Lived Abroad", "Overseas Experience", 
-    "After Exclusions")
-
-colnames(df.demog_excl) <- df.demog_excl[1,]
-df.demog_excl <- df.demog_excl[-1, ]
-
-kbl(df.demog_excl, align = "c") %>%
-  add_header_above(c(" " = 1, "Country" = 3)) %>%
-  pack_rows(index = c(" " = 1, "Attention Check Exclusions" = 2, "Demographics Exclusions" = 7))
-```
-
-\newpage
-
-# Acknowledgements
-
-Place acknowledgments (including funding information) in a section at
-the end of the paper.
-
-# References
-
-```{r}
-# References will be generated automatically by Pandoc and included here.
-# The following code is some latex to format the bibliography. Do not remove it.
-```
-
-\setlength{\parindent}{-0.1in} 
-\setlength{\leftskip}{0.125in}
-\noindent
-
-\newpage

### 2023-01-26 code/1_exclusions_exploratory/1_exclusionsCN.Rmd
changed analysis to exploratory version

--- 2022-12-14 code/1_exclusions/1_exclusionsCN.Rmd
@@
 
-df.resp_M <- df.resp_M %>%
+df.resp_M_aft_attn <- df.resp_M %>% #38841
   filter(subject %in% df.ppts_att_M$subject)
 
-ppts_resp_M <- unique(df.resp_M$subject)
+ppts_resp_M_aft_attn <- unique(df.resp_M$subject)
 ```
@@
 ppts_non_native_lang_M = unique(df.ppts_non_native_lang_M$subject) #3
-percent_dropped = length(intersect(ppts_non_native_lang_M, ppts_resp_M)) / length(ppts_resp_M)
-percent_dropped #0.01086
+percent_dropped = length(intersect(ppts_non_native_lang_M, ppts_resp_M_aft_attn)) / length(ppts_resp_M_aft_attn)
+percent_dropped #0.015
 
@@
 
-ppts_en_speaker_M = unique(df.lang_en_M$subject) #74
-percent_dropped = length(intersect(ppts_en_speaker_M, ppts_resp_M)) / length(ppts_resp_M)
-percent_dropped #0.375 # do not use this criterion
+ppts_en_speaker_M = unique(df.lang_en_M$subject) #79
+percent_dropped = length(intersect(ppts_en_speaker_M, ppts_resp_M_aft_attn)) / length(ppts_resp_M_aft_attn)
+percent_dropped #0.385 # do not use this criterion
 
@@
 ppts_lived_abroad_M = unique(df.lived_abroad_M$subject) #40
-percent_dropped = length(intersect(ppts_lived_abroad_M, ppts_resp_M)) / length(unique(df.resp_M$subject))
-percent_dropped #0.163043
+percent_dropped = length(intersect(ppts_lived_abroad_M, ppts_resp_M_aft_attn)) / length(ppts_resp_M_aft_attn)
+percent_dropped #0.185
 
@@
 ppts_oversea_exp_M = unique(df.oversea_exp_M$subject) #12
-percent_dropped = length(intersect(ppts_oversea_exp_M, ppts_resp_M)) / length(unique(df.resp_M$subject))
-percent_dropped #0.0434782
+percent_dropped = length(intersect(ppts_oversea_exp_M, ppts_resp_M_aft_attn)) / length(ppts_resp_M_aft_attn)
+percent_dropped #0.06
 
-df.resp_M <- df.resp_M %>%
+df.resp_M_aft_demog <- df.resp_M_aft_attn %>%
   filter(!(subject %in% ppts_non_native_lang_M),
@@
 
-length(unique(df.resp_M$subject)) #149
+length(unique(df.resp_M_aft_demog$subject)) #149
 ```
@@
 ```{r}
-write.csv(df.resp_M, "../../data/responding/dataCN_excl.csv")
+df.demog_metadata <- data.frame(
+  country = c("China"),
+  ppts_finished = c(length(unique(df.ppts_finished_M$subject))),
+  ppts_att_check_excl = c(length(unique(df.ppts_finished_M$subject)) - length(unique(df.ppts_att_M$subject))), 
+  ppts_after_att_check_excl = c(length(unique(df.ppts_att_M$subject))),
+  ppts_non_native_speaker = c(paste(length(ppts_non_native_lang_M),"*")), 
+  ppts_en_speaker = c(length(ppts_en_speaker_M)), 
+  ppts_vi_speaker = c(paste(length(ppts_vi_speaker_M),"*")),
+  ppts_zh_speaker = c("N/A"), 
+  ppts_lived_abroad = c(paste(length(ppts_lived_abroad_M),"*")), 
+  ppts_oversea_exp = c(paste(length(ppts_oversea_exp_M), "*")),
+  ppts_after_demog_excl = c(length(unique(df.resp_M_aft_demog$subject))))
 ```
+
+```{r}
+write.csv(df.resp_M_aft_demog, "../../data/responding/exploratory/dataCN_excl.csv")
+write.csv(df.demog_metadata, "../../data/responding/exploratory/dataCN_excl_metadata.csv")
+```

### 2023-01-26 code/1_exclusions_exploratory/1_exclusionsUS.Rmd
changed analysis to exploratory version

--- 2023-01-20 code/1_exclusions/1_exclusionsUS.Rmd
@@
 
-ppts_vi_speaker_E = unique(df.lang_vi_E$subject) #2
+ppts_vi_speaker_E = unique(df.lang_vi_E$subject) #4
 percent_dropped = length(intersect(ppts_vi_speaker_E, ppts_resp_E_aft_attn)) / length(ppts_resp_E_aft_attn)
-percent_dropped #0.01149425
+percent_dropped #0.02083333
 
@@
 
-ppts_zh_speaker_E = unique(df.lang_zh_E$subject) #30
+ppts_zh_speaker_E = unique(df.lang_zh_E$subject) #35
 percent_dropped = length(intersect(ppts_zh_speaker_E, ppts_resp_E_aft_attn)) / length(ppts_resp_E_aft_attn)
-percent_dropped #0.1436782
+percent_dropped #0.1822917
 
@@
 
-ppts_lived_abroad_E = unique(df.lived_abroad_E$subject) #36
+ppts_lived_abroad_E = unique(df.lived_abroad_E$subject) #33
 percent_dropped = length(intersect(ppts_lived_abroad_E, ppts_resp_E_aft_attn)) / length(ppts_resp_E_aft_attn)
-percent_dropped #0.166667
+percent_dropped #0.171875
 
@@
 
-ppts_oversea_exp_E = unique(df.oversea_exp_E$subject) #95
+ppts_oversea_exp_E = unique(df.oversea_exp_E$subject) #91
 percent_dropped = length(intersect(ppts_oversea_exp_E, ppts_resp_E_aft_attn)) / length(unique(df.resp_E_aft_attn$subject))
-percent_dropped #0.4425287 # will not use this criterion
+percent_dropped #0.4739583 # will not use this criterion
 
@@
 
-length(unique(df.resp_E_aft_demog$subject)) #124
+length(unique(df.resp_E_aft_demog$subject)) #119
 
@@
 ```{r}
-write.csv(df.resp_E_aft_demog, "../../data/responding/dataUS_excl.csv")
-write.csv(df.demog_metadata, "../../data/responding/dataUS_excl_metadata.csv")
+write.csv(df.resp_E_aft_demog, "../../data/responding/exploratory/dataUS_excl.csv")
+write.csv(df.demog_metadata, "../../data/responding/exploratory/dataUS_excl_metadata.csv")
 ```

### 2023-01-26 code/1_exclusions_exploratory/1_exclusionsVN.Rmd
changed analysis to exploratory version

@@
 
-df.resp_V <- df.resp_V %>%
+df.resp_V_aft_attn <- df.resp_V %>%
   filter(subject %in% df.ppts_att_V$subject) #73
 
-ppts_resp_V <- unique(df.resp_V$subject) #137
+ppts_resp_V_aft_attn <- unique(df.resp_V$subject) #137
 ```
@@
 ppts_non_native_lang_V = unique(df.ppts_non_native_lang_V$subject)#2
-percent_dropped = length(intersect(ppts_non_native_lang_V, ppts_resp_V)) / length(ppts_resp_V)
-percent_dropped #0
+percent_dropped = length(intersect(ppts_non_native_lang_V, ppts_resp_V_aft_attn)) / length(ppts_resp_V_aft_attn)
+percent_dropped #0.01005
 
@@
 
-ppts_en_speaker_V = unique(df.lang_en_V$subject) #119
-percent_dropped = length(intersect(ppts_en_speaker_V, ppts_resp_V)) / length(ppts_resp_V)
-percent_dropped #0.6277 # do not use this criterion
+ppts_en_speaker_V = unique(df.lang_en_V$subject) #127
+percent_dropped = length(intersect(ppts_en_speaker_V, ppts_resp_V_aft_attn)) / length(ppts_resp_V_aft_attn)
+percent_dropped #0.623156 # do not use this criterion
 
 df.lang_sp_zh_V <- df.demog %>%
-  filter(demog_question == "lang_sp_zh" & demog_response > 4)
+  filter(demog_question == "lang_sp_zh" & as.numeric(demog_response) > 4)
 
 df.lang_ud_zh_V <- df.demog %>%
-  filter(demog_question == "lang_ud_zh" & demog_response > 4)
+  filter(demog_question == "lang_ud_zh" & as.numeric(demog_response) > 4)
 
@@
 ppts_lived_abroad_V = unique(df.lived_abroad_V$subject) #18
-percent_dropped = length(intersect(ppts_lived_abroad_V, ppts_resp_V)) / length(unique(df.resp_V$subject))
-percent_dropped #0.05839416
+percent_dropped = length(intersect(ppts_lived_abroad_V, ppts_resp_V_aft_attn)) / length(ppts_resp_V_aft_attn)
+percent_dropped #0.08542714
 
@@
 
-ppts_oversea_exp_V = unique(df.oversea_exp_V$subject) #20
-percent_dropped = length(intersect(ppts_oversea_exp_V, ppts_resp_V)) / length(unique(df.resp_V$subject))
-percent_dropped #0.109
+ppts_oversea_exp_V = unique(df.oversea_exp_V$subject) #18
+percent_dropped = length(intersect(ppts_oversea_exp_V, ppts_resp_V_aft_attn)) / length(ppts_resp_V_aft_attn)
+percent_dropped #0.09547739
 
-df.resp_V <- df.resp_V %>%
+df.resp_V_aft_demog <- df.resp_V_aft_attn %>%
   filter(!(subject %in% ppts_non_native_lang_V),
@@
 
-length(unique(df.resp_V$subject)) #110
+length(unique(df.resp_V_aft_demog$subject)) #110
 ```
@@
 ```{r}
-df.demog_metadata <- data.frame(ppts_finished = c(length(unique(df.ppts_finished_V$subject))),
+df.demog_metadata <- data.frame(
+  country = c("Vietnam"),
+  ppts_finished = c(length(unique(df.ppts_finished_V$subject))),
+  ppts_att_check_excl = c(length(unique(df.ppts_finished_V$subject)) - length(unique(df.ppts_att_V$subject))), 
   ppts_after_att_check_excl = c(length(unique(df.ppts_att_V$subject))),
-                      ppts_after_demog_excl = c(length(unique(df.resp_V$subject))))
+  ppts_non_native_speaker = c(paste(length(ppts_non_native_lang_V),"*")), 
+  ppts_en_speaker = c(paste(length(ppts_en_speaker_V))), 
+  ppts_vi_speaker = c("N/A"),
+  ppts_zh_speaker = c(paste(length(ppts_zh_speaker_V),"*")), 
+  ppts_lived_abroad = c(paste(length(ppts_lived_abroad_V),"*")), 
+  ppts_oversea_exp = c(paste(length(ppts_oversea_exp_V), "*")),
+  ppts_after_demog_excl = c(length(unique(df.resp_V_aft_demog$subject))))
 ```
@@
 ```{r}
-write.csv(df.resp_V, "../../data/responding/dataVN_excl.csv")
-write.csv(df.demog_metadata, "../../data/responding/dataVN_excl_metadata.csv")
+write.csv(df.resp_V_aft_demog, "../../data/responding/exploratory/dataVN_excl.csv")
+write.csv(df.demog_metadata, "../../data/responding/exploratory/dataVN_excl_metadata.csv")
 ```

### 2023-01-26 code/2_combine/2_combine_exploratory.Rmd
changed analysis to exploratory version

--- 2022-09-28 code/2_combine/2_combine.Rmd
@@
 ```{r loading data E, warning=FALSE, include=F}
-df.resp_E <- read.csv("../../data/dataUS_excl.csv") %>%
+df.resp_E <- read.csv("../../data/responding/exploratory/dataUS_excl.csv") %>%
   select(-X)
@@
 ```{r loading data V, include=F}
-df.resp_V <- read.csv("../../data/dataVN_excl.csv") %>%
+df.resp_V <- read.csv("../../data/responding/exploratory/dataVN_excl.csv") %>%
   select(-X)
@@
 ```{r loading data M, warning=FALSE, include=F}
-df.resp_M <- read.csv("../../data/dataCN_excl.csv") %>%
+df.resp_M <- read.csv("../../data/responding/exploratory/dataCN_excl.csv") %>%
   select(-X)
@@
 df_main_analysis <- df #keep a copy of df in case exploratory analysis changes it
-write.csv(df_main_analysis, "../../data/data_USCNVN_ENZHVI.csv")
+write.csv(df_main_analysis, "../../data/data_USCNVN_ENZHVI_exploratory.csv", row.names = F)
+#write.csv(triads_omit, "../../data/triads_omit.csv", row.names = F)
 ```

### 2023-01-26 code/4_paper/manuscript/manuscript.Rmd
changed analysis to exploratory version

@@
 ---
-title: "Re-examining cross-cultural similarity judgements using lexical co-occurrence"
+title: "Re-examining cross-cultural similarity judgments using lexical co-occurrence"
 bibliography: library.bib
@@
 author-information: > 
-    \author{{\large \bf Morton Ann Gernsbacher (MAG@Macc.Wisc.Edu)} \\ Department of Psychology, 1202 W. Johnson Street \\ Madison, WI 53706 USA
-    \AND {\large \bf Sharon J.~Derry (SDJ@Macc.Wisc.Edu)} \\ Department of Educational Psychology, 1025 W. Johnson Street \\ Madison, WI 53706 USA}
+    \author{{\large \bf Khuyen N.
+Le (knl005@ucsd.edu)}$^{1\star}$, {\large \bf Alexandra Carstensen (abc@ucsd.edu)}$^{1\star}$, \\ {\large \bf Shan Gao (shangaocog@gmail.com)$^2$} {\large \bf Michael C.
+Frank (mcfrank@stanford.edu)$^3$},  \AND
+    $^1$Department of Psychology, UC San Diego, $^2$Department of Psychology, University of Chicago, \\ $^3$Department of Psychology, Stanford University
+    }
 
@@
 One possibility is that cultures co-varying with these languages induce differences in conceptualizations of similarity.
-Specifically, East Asian cultures may promote reasoning about thematic similarity, by which cow and grass are more related, whereas Western cultures may bias judgements toward taxonomic relations, like cow-chicken.
+Specifically, East Asian cultures may promote reasoning about thematic similarity, by which cow and grass are more related, whereas Western cultures may bias judgments toward taxonomic relations, like cow-chicken.
 This difference in notions of similarity is the consensus interpretation for cross-cultural variation in this paradigm.
 We consider, and provide evidence for, an alternative possibility, by which notions of similarity are similar across contexts, but the statistics of the environment vary.
-On this account, similarity judgements are guided by co-occurrence in experience, and observing or hearing about cows and grass or cows and chickens more often could induce preferences for these groupings, and account in part for apparent differences in notions of similarity across contexts.
+On this account, similarity judgments are guided by co-occurrence in experience, and observing or hearing about cows and grass or cows and chickens more often could induce preferences for these groupings, and account in part for apparent differences in notions of similarity across contexts.
 
@@
 library("lme4")
+library("emmeans")
 library("patchwork")
@@
 
-<!-- condense to 2 sentences --> Systems like fastText and word2vec have been demonstrated to be good predictors for similarity judgments.
-@Liu2019 showed that fastText performed well as the data for a system matching responses in a knowledge base by how similar they are to a customer’s query.
+<!-- condense to 2 sentences --> Word embeddings like fastText have been demonstrated to be good predictors for similarity judgments (@Liu2019, @Jatnika2019).
+fastText has also been shown to be sensitive towards cultural effects on word meanings: @Thompson2020 showed that the distribution of semantic meaning clusters generated by fastText trained on language-specific corpora correlates to the cultural, historical and geographical distances of such languages languages.
+This is a proof of concept for our use of fastText in different languages with varying levels of relatedness.
+<!-- @Liu2019 showed that fastText performed well as the data for a system matching responses in a knowledge base by how similar they are to a customer’s query.
 A study by @Jatnika2019 tested a word2vec model trained on the English wikipedia corpus against 353 word pairs labeled with similarity values based on human judgment.
 The word2vec model correlates moderately with human judgment.
-fastText has also been shown to be sensitive towards cultural effects on word meanings: @Thompson2020 applied fastText to language-specific Wikipedia corpus (among others) to generate a “semantic neighborhood” of 1010 meanings in different languages.
+-->
+<!-- @Thompson2020 applied fastText to language-specific Wikipedia corpus (among others) to generate a “semantic neighborhood” of 1010 meanings in different languages.
 The study showed that languages that are spoken by more similar cultures, more geographically proximate and/or historically related had more semantic neighborhoods that aligned.
-This is a proof of concept for our use of fastText in different languages with varying levels of relatedness.
+-->
 
@@
 
-To preview our results, we find that, while we do not see overall group differences (between the East Asian contexts and the US) in similarity, we do find language-specific co-occurrence can indeed explain cross-context differences in similarity judgments.
+To preview our results, we find that, while we do not find the predicted Eastern/Western contrast in notions of similarity in our Vietnam extension, we do find language-specific co-occurrence can indeed explain cross-context differences in similarity judgments.
 In contrast to previous accounts, by which culture induces differing conceptions of similarity (varying between taxonomic and thematic), these findings provide an alternative, and more specific, account by which language may explain these cross-cultural differences without invoking variation in notions of similarity.
@@
 ```{r get responding and demographic data, include = F}
-df <- read.csv("../../../data/data_USCNVN_ENZHVI.csv")
+#df <- read.csv("../../../data/data_USCNVN_ENZHVI.csv")
+df <- read.csv("../../../data/data_USCNVN_ENZHVI_exploratory.csv")
 
@@
 df.demog <- read.csv("../../../data/responding/data_demog.csv") %>%
-  filter(subject %in% unique(df$subject))
+  filter(subject %in% unique(df$subject)) %>%
+  select(-X)
 
@@
 ```{r get exclusions data, include = F, cache = T}
-df.excl_US <- read.csv("../../../data/responding/dataUS_excl_metadata.csv") %>%
+df.excl_US <- read.csv("../../../data/responding/exploratory/dataUS_excl_metadata.csv") %>%
   select(-X)
-df.excl_CN <- read.csv("../../../data/responding/dataCN_excl_metadata.csv") %>%
+df.excl_CN <- read.csv("../../../data/responding/exploratory/dataCN_excl_metadata.csv") %>%
   select(-X)
-df.excl_VN <- read.csv("../../../data/responding/dataVN_excl_metadata.csv") %>%
+df.excl_VN <- read.csv("../../../data/responding/exploratory/dataVN_excl_metadata.csv") %>%
   select(-X)
@@
 df.demog_E <- df.demog %>%
-  filter(country == "US")
+  filter(country == "US") %>%
+  filter(subject %in% unique(df$subject))
 
@@
 df.demog_M <- df.demog %>%
-  filter(country == "CN")
+  filter(country == "CN") %>%
+  filter(subject %in% unique(df$subject))
 
@@
 df.demog_V <- df.demog %>%
-  filter(country == "VN")
+  filter(country == "VN") %>%
+  filter(subject %in% unique(df$subject))
 
@@
 
-We excluded `r df.excl_US$ppts_finished - df.excl_US$ppts_after_att_check_excl` US participants, `r df.excl_VN$ppts_finished - df.excl_VN$ppts_after_att_check_excl` Vietnam participants, and `r df.excl_CN$ppts_finished - df.excl_CN$ppts_after_att_check_excl` China participants who did not answer all attention checks correctly.
+We excluded `r df.excl_US$ppts_finished - df.excl_US$ppts_after_att_check_excl` US participants, `r df.excl_VN$ppts_finished - df.excl_VN$ppts_after_att_check_excl` Vietnam participants, and `r df.excl_CN$ppts_finished - df.excl_CN$ppts_after_att_check_excl` China participants who did not answer 2 or more attention checks correctly.
 We followed 4 exclusion criteria that aim to retain only participants who are influenced by one culture: (1) non-native speakers of English and Vietnamese, respectively, (2) fluent in at least one of the other two study languages (Vietnamese for US participants, English for Vietnamese participants and Chinese participants), (3) have lived outside of the test country (US, Vietnam, or China) for more than two years, and (4) have significant international experience (more than 6 international experiences of 2 days or longer.) We did not use a particular criterion for a language if it would exclude 25% or more of any one sample.
@@
 Notably, we lost a majority of our Vietnam participants (more than 60%) in the attention check exclusion.
-One reason we suspect why this might have happened is because our Vietnam participants are less familiar with research surveys and attention check questions, and thus might have thought too much about the attention check questions.^[We carried out an exploratory analysis where we used a less stringent attention check exclusion (covered in the final part of the Results & Analysis section).
-To preview our findings for this analysis, we did not find any difference in significant results when compared with the main analysis.]
+One reason we suspect why this might have happened is because our Vietnam participants are less familiar with research surveys and attention check questions, and thus might have thought too much about the attention check questions.^[We carried out an exploratory analysis where we used a less stringent attention check exclusion, and did not find any difference in significant results when compared with the main analysis (see Appendix).]
 
@@
 
-We found that all corpora are significant predictors of all cultural context responding, with p<0.05 and $\beta$ from `r min(beta.single_corpus_cos)` to `r max(beta.single_corpus_cos)`.
+We found that all corpora are significant predictors of all cultural context responding, with p < 0.05 and $\beta$ from `r min(beta.single_corpus_cos)` to `r max(beta.single_corpus_cos)`.
 (For a full report, see Appendix.)
@@
 ```{r Eng-Vie-Mand cosine similarities predicting US-VN-CN, warning=FALSE, include=FALSE}
-df <- read.csv("../../../data/data_USCNVN_ENZHVI.csv")
 
@@
 We used an ANOVA to compare the model with only the corresponding corpus, and the model with all 3 corpora for each cultural context.
-We found that in all three cases (US, China, Vietnam), adding the other two corpora produces a significantly better fit than the identical model without the additional corpora, and only the corresponding corpus included as a predictor (US response: $\chi^2$(`r fit.US_cos_compare["fit.ENVIZH_US_cos", "Df"]`) = `r round(fit.US_cos_compare["fit.ENVIZH_US_cos", "Chisq"], 2)`, p `r ifelse( fit.US_cos_compare["fit.ENVIZH_US_cos", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.US_cos_compare["fit.ENVIZH_US_cos", "Pr(>Chisq)"], 3)), "< .001")`; Vietnam response: $\chi^2$(`r fit.VN_cos_compare["fit.ENVIZH_VN_cos", "Df"]`) = `r round(fit.VN_cos_compare["fit.ENVIZH_VN_cos", "Chisq"], 2)`, p `r ifelse( fit.VN_cos_compare["fit.ENVIZH_VN_cos", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.VN_cos_compare["fit.ENVIZH_VN_cos", "Pr(>Chisq)"], 3)), "< .001")`; China response: $\chi^2$(`r fit.CN_cos_compare["fit.ENVIZH_CN_cos", "Df"]`) = `r round(fit.CN_cos_compare["fit.ENVIZH_CN_cos", "Chisq"], 2)`, p `r ifelse( fit.CN_cos_compare["fit.ENVIZH_VN_cos", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.CN_cos_compare["fit.ENVIZH_VN_cos", "Pr(>Chisq)"], 3)), "< .001")`).
+We found that in all three cases (US, China, Vietnam), adding the other two corpora produces a significantly better fit than the identical model without the additional corpora, and only the corresponding corpus included as a predictor (US response: $\chi^2$(`r fit.US_cos_compare["fit.ENVIZH_US_cos", "Df"]`) = `r round(fit.US_cos_compare["fit.ENVIZH_US_cos", "Chisq"], 2)`, p `r ifelse( fit.US_cos_compare["fit.ENVIZH_US_cos", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.US_cos_compare["fit.ENVIZH_US_cos", "Pr(>Chisq)"], 3)), "< .001")`; Vietnam response: $\chi^2$(`r fit.VN_cos_compare["fit.ENVIZH_VN_cos", "Df"]`) = `r round(fit.VN_cos_compare["fit.ENVIZH_VN_cos", "Chisq"], 2)`, p `r ifelse( fit.VN_cos_compare["fit.ENVIZH_VN_cos", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.VN_cos_compare["fit.ENVIZH_VN_cos", "Pr(>Chisq)"], 3)), "< .001")`; China response: $\chi^2$(`r fit.CN_cos_compare["fit.ENVIZH_CN_cos", "Df"]`) = `r round(fit.CN_cos_compare["fit.ENVIZH_CN_cos", "Chisq"], 2)`, p `r ifelse( fit.CN_cos_compare["fit.ENVIZH_CN_cos", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.CN_cos_compare["fit.ENVIZH_CN_cos", "Pr(>Chisq)"], 3)), "< .001")`).
 
 ## 3. Does similarity reasoning differ across cultures, only the input to it, or both?
-Our analysis shows that lexical statistics of each corpus is a significant predictor for similarity judgement in the corresponding cultural context, even without the addition of the other two corpora.
-Assuming that lexical statistics is a good proxy for environmental statistics, we take the above result as evidence that cross-cultural differences in input to the process of similarity judgement at least partially drives cross-cultural similarity judgement differences.
-However, it is still an open question whether the nature of similarity judgement (for e.g., the notion of similarity) itself differs across cultures and contributes to cross-cultural differences in similarity judgement responding.
-In an alternative hypothesis, the cross-cultural differences in similarity judgement observed is driven by not only the input, but also an interaction between cultural-specific nature of similarity judgement and input.
-To test this hypothesis, we operationalize cultural-specific nature of similarity judgement as country context, and input to similarity judgement as the corresponding corpus statistics.
+Our analysis shows that lexical statistics of each corpus is a significant predictor for similarity judgment in the corresponding cultural context, even without the addition of the other two corpora.
+Assuming that lexical statistics is a good proxy for environmental statistics, we take the above result as evidence that cross-cultural differences in input to the process of similarity judgment at least partially drives cross-cultural similarity judgment differences.
+However, it is still an open question whether the nature of similarity judgment (for e.g., the notion of similarity) itself differs across cultures and contributes to cross-cultural differences in similarity judgment responding.
+In an alternative hypothesis, the cross-cultural differences in similarity judgment observed is driven by not only the input, but also an interaction between cultural-specific nature of similarity judgment and input.
+To test this hypothesis, we operationalize cultural-specific nature of similarity judgment as country context, and input to similarity judgment as the corresponding corpus statistics.
 We then compare a model that includes country, corresponding corpus statistics and their interaction as fixed effects (R syntax: responses ~ corresponding_corpus * country + (1|triad) + (1|subject)) to a model with only the corresponding corpus statistics as the fixed effect (R syntax: responses ~ corresponding_corpus + (1|triad) + (1|subject))
@@
 summary(fit.language_cos)
+fit.language_cos %>% joint_tests()
 fit.language_cos.anova = Anova(fit.language_cos, type = 3)
@@
 summary(fit.country_language_cos)
+fit_joint.country_language_cos <- fit.country_language_cos %>% 
+  joint_tests() %>%
+  remove_rownames() %>% 
+  column_to_rownames(var = "model term")
 fit.country_language_cos.anova = Anova(fit.country_language_cos, type = 3)
@@
 In the model containing only the corresponding corpus statistics, the corpus statistics is a significant predictor ($\beta$ = `r round(fixef(fit.language_cos)["theme_cosine_prop_corr_lang"], 2)`, $\chi^2$(`r fit.language_cos.anova["theme_cosine_prop_corr_lang", "Df"]`) = `r round(fit.language_cos.anova["theme_cosine_prop_corr_lang", "Chisq"], 2)`, p `r ifelse( fit.language_cos.anova["theme_cosine_prop_corr_lang", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.language_cos.anova["theme_cosine_prop_corr_lang", "Pr(>Chisq)"], 3)), "< .001")`).
-When adding country and interaction between country and corpus, both the corpus statistics ($\beta$ = `r round(fixef(fit.country_language_cos)["theme_cosine_prop_corr_lang"], 2)`, $\chi^2$(`r fit.country_language_cos.anova["theme_cosine_prop_corr_lang", "Df"]`) = `r round(fit.country_language_cos.anova["theme_cosine_prop_corr_lang", "Chisq"], 2)`, p `r ifelse( fit.country_language_cos.anova["theme_cosine_prop_corr_lang", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.country_language_cos.anova["theme_cosine_prop_corr_lang", "Pr(>Chisq)"], 3)), "< .001")`) and interaction between country and corpus ($\beta$ = `r round(fixef(fit.country_language_cos)["theme_cosine_prop_corr_lang:country"], 2)`, $\chi^2$(`r fit.country_language_cos.anova["theme_cosine_prop_corr_lang:country", "Df"]`) = `r round(fit.country_language_cos.anova["theme_cosine_prop_corr_lang:country", "Chisq"], 2)`, p `r ifelse( fit.country_language_cos.anova["theme_cosine_prop_corr_lang:country", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.country_language_cos.anova["theme_cosine_prop_corr_lang:country", "Pr(>Chisq)"], 3)), "< .001")`) are significant predictors.
-This suggests that there are cross-cultural differences in both input and nature of similarity judgement that drive differences in similarity judgement responding.
+When adding country and interaction between country and corpus, both the corpus statistics ($\beta$ = `r round(fixef(fit.country_language_cos)["theme_cosine_prop_corr_lang"], 2)`, $\chi^2$(`r fit.country_language_cos.anova["theme_cosine_prop_corr_lang", "Df"]`) = `r round(fit.country_language_cos.anova["theme_cosine_prop_corr_lang", "Chisq"], 2)`, p `r ifelse( fit.country_language_cos.anova["theme_cosine_prop_corr_lang", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.country_language_cos.anova["theme_cosine_prop_corr_lang", "Pr(>Chisq)"], 3)), "< .001")`) and interaction between country and corpus (F(`r fit_joint.country_language_cos["theme_cosine_prop_corr_lang:country", "df1"]`, `r fit_joint.country_language_cos["theme_cosine_prop_corr_lang:country", "df2"]`) = `r round(fit_joint.country_language_cos["theme_cosine_prop_corr_lang:country", "F.ratio"], 2)`, $\chi^2$(`r fit.country_language_cos.anova["theme_cosine_prop_corr_lang:country", "Df"]`) = `r round(fit.country_language_cos.anova["theme_cosine_prop_corr_lang:country", "Chisq"], 2)`, p `r ifelse( fit.country_language_cos.anova["theme_cosine_prop_corr_lang:country", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.country_language_cos.anova["theme_cosine_prop_corr_lang:country", "Pr(>Chisq)"], 3)), "< .001")`) are significant predictors.
+This suggests that there are cross-cultural differences in both input and nature of similarity judgment that drive differences in similarity judgment responding.
+We found no effects of country  (F(`r fit_joint.country_language_cos["country", "df1"]`, `r fit_joint.country_language_cos["country", "df2"]`) = `r round(fit_joint.country_language_cos["country", "F.ratio"], 2)`, $\chi^2$(`r fit.country_language_cos.anova["country", "Df"]`) = `r round(fit.country_language_cos.anova["country", "Chisq"], 2)`, p `r ifelse( fit.country_language_cos.anova["country", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.country_language_cos.anova["country", "Pr(>Chisq)"], 3)), "< .001")`).
 
@@
 Previous work using the triad task such as @Ji2004 has focused on contrasting taxonomic-thematic match preferences, driven by a theory of cross-cultural differences in notions of similarity.
-Meanwhile, our approach has shown that notions of similarity only has an effect on cross-cultural differences in similarity judgement when modulated by input, and that input as proxied by lexical statistics of the corresponding corpus by itself is a significant predictor for similarity judgement responding.
+Meanwhile, our approach has shown that notions of similarity only has an effect on cross-cultural differences in similarity judgment when modulated by input, and that input as proxied by lexical statistics of the corresponding corpus by itself is a significant predictor for similarity judgment responding.
 Our approach using lexical statistics do not assume a taxonomic/thematic structure in the triads.
-Therefore, it should be possible to predict similarity judgements to triads that do not follow a taxonomic/thematic structure, such as our filler triads.
-If our approach is tractable, we should be able to repeat the above analyses to the filler triads, and find that lexical statistics of each corpus is a significant predictor for similarity judgements in filler triads of the corresponding cultural context.
+Therefore, it should be possible to predict similarity judgments to triads that do not follow a taxonomic/thematic structure, such as our filler triads.
+If our approach is tractable, we should be able to repeat the above analyses to the filler triads, and find that lexical statistics of each corpus is a significant predictor for similarity judgments in filler triads of the corresponding cultural context.
 
@@
 
-```{r echo=FALSE, warning=FALSE, cache = TRUE, fig.env="figure", fig.align = "center", fig.cap="Proportion of thematic responses by country."}
+```{r echo=FALSE, warning=FALSE, cache = TRUE, fig.env="figure", fig.align = "center", fig.cap="Proportion of Word1 responses by country."}
 #show violin plot
@@
 In this paper, we consider whether statistics of the language environment can account for cross-cultural differences in a classic similarity judgment paradigm, as an alternative to the view that members of different cultures vary in their conception of similarity.
+We found that each corpus statistics is a good predictor for the corresponding country's similarity judgments.
+When corresponding corpus statistics, country and corpus-country interactions were included as fixed effects to predict similarity judgments, we found no effects of country, but both corpus statistics and corpus-country interaction are significant predictors.
+Our results provide evidence that cross-cultural differences in similarity judgment might not be driven by cross-cultural differences in conception of similarity alone, but rather by statistics to similarity judgment and its interaction with similarity conception.
+We also showed that corpus statistics predict similarity judgments for triads that do not have taxonomic/thematic structure.
 
@@
 
-We did find some signatures of language specificity in our analysis, such as the large positive correlation between similarity judgments of each country and the respective corpus statistics, and how each corpus statistics are good predictors for corresponding country's similarity judgments.
+We did find some signatures of language specificity in our analysis: each corpus statistics is a good predictor for the corresponding country's similarity judgments, even when other corpus statistics are included.
+However, we also find evidence for consistency across the three cultural groups: each corpus statistics is also a good predictor for the other two non-corresponding cultural contexts when included as the only predictor, and both English and Mandarin Chinese statistics are good predictors for their non-corresponding cultural contexts when all three corpora are included.
+
+When all cultural contexts are taken together, we found that both corresponding corpus statistics and an interaction between corpus and country are significant predictors for similarity judgments.
+This result suggests that in addition to input to similarity judgment, country-specific categorical differences in similarity judgment (for e.g., how each culture conceive of similarity) also predict cross-cultural differences in similarity judgment behavior while modulated by input.
+
+Even in triads with no taxonomic / thematic structure, each corpus statistics is still a good predictor of the corresponding country's similarity judgments.
+The ability of corpus statistics to predict similarity judgments in non-structured triads suggests that cross-cultural differences in similarity judgments should be construed in a more general and graded manner, as opposed to binary taxonomic/thematic match-preferring.
+
+<!-- such as the large positive correlation between similarity judgments of each country and the respective corpus statistics, and how each corpus statistics are good predictors for corresponding country's similarity judgments.
 However, this is potentially due to the high correlation between corpus statistics of English, Vietnamese and Mandarin.
 We find even stronger evidence for consistency across the three groups, with substantive overlapping predictions across the corpus models, highly similar responding across the experiments, and a correspondingly high fit in cross-language comparisons between models and data.
+-->
 
-Our findings raise additional questions for future work: if not differences in taxonomic vs.
-thematic responding, then what differences drive the relativity effects previous studies have observed?
-To what extent are the relativity effects driven by language, and to what extent by culture?
+Our findings raise additional questions for future work: <!--If not differences in taxonomic vs.
+thematic responding, then what differences drive the relativity effects previous studies have observed?--> To what extent are the relativity effects driven by language, and to what extent by culture?
 @Ji2004 established that culture-aligned differences in this paradigm exist, even when the test language is held constant, concluding that “it is culture (independent of the testing language) that led to different grouping styles” in their study.
@@
 ```
+An intraclass correlation coefficients (ICCs) analysis with a two-way, non-interactive model (following the standard taxonomy for ICCs from @McGraw1996) showed that, per cultural context, participants' judgments were variable across triads, while inter-rater agreement about specific triads was quite high (Table 1).
+This result suggests that each triad prompts taxonomic / thematic matching reliably within culture.
 
-## 2. Supplemental for whether each corpus predicts similarity judgement in each cultural context
+## 2. Supplemental for whether each corpus predicts similarity judgment in each cultural context
 
@@
 
-## 3. Demographic Exclusion Statistics
+## 3. Exclusion Statistics
 ```{r results = "asis", fig.cap="Testing"}

### 2023-01-26 code/4_paper/manuscript/manuscript.tex
changed analysis to exploratory version

@@
 
-\title{Re-examining cross-cultural similarity judgements using lexical
+\title{Re-examining cross-cultural similarity judgments using lexical
 co-occurrence}
@@
 
-\author{{\large \bf Morton Ann Gernsbacher (MAG@Macc.Wisc.Edu)} \\ Department of Psychology, 1202 W.
-Johnson Street \\ Madison, WI 53706 USA \AND {\large \bf Sharon J.~Derry (SDJ@Macc.Wisc.Edu)} \\ Department of Educational Psychology, 1025 W.
-Johnson Street \\ Madison, WI 53706 USA}
+\author{{\large \bf Khuyen N.
+Le (knl005@ucsd.edu)}$^{1\star}$, {\large \bf Alexandra Carstensen (abc@ucsd.edu)}$^{1\star}$, \\ {\large \bf Shan Gao (shangaocog@gmail.com)$^2$} {\large \bf Michael C.
+Frank (mcfrank@stanford.edu)$^3$},  \AND $^1$Department of Psychology, UC San Diego, $^2$Department of Psychology, University of Chicago, \\ $^3$Department of Psychology, Stanford University }
 
@@
 which cow and grass are more related, whereas Western cultures may bias
-judgements toward taxonomic relations, like cow-chicken. This difference
+judgments toward taxonomic relations, like cow-chicken. This difference
 in notions of similarity is the consensus interpretation for
@@
 are similar across contexts, but the statistics of the environment vary.
-On this account, similarity judgements are guided by co-occurrence in
+On this account, similarity judgments are guided by co-occurrence in
 experience, and observing or hearing about cows and grass or cows and
@@
 
-Systems like fastText and word2vec have been demonstrated to be good
-predictors for similarity judgments. Liu, Feng, Wu, Chan, \& Fulton
-(2019) showed that fastText performed well as the data for a system
-matching responses in a knowledge base by how similar they are to a
-customer's query. A study by Jatnika, Bijaksana, \& Suryani (2019)
-tested a word2vec model trained on the English wikipedia corpus against
-353 word pairs labeled with similarity values based on human judgment.
-The word2vec model correlates moderately with human judgment. fastText
-has also been shown to be sensitive towards cultural effects on word
-meanings: Thompson \& Lupyan (2020) applied fastText to
-language-specific Wikipedia corpus (among others) to generate a
-``semantic neighborhood'' of 1010 meanings in different languages. The
-study showed that languages that are spoken by more similar cultures,
-more geographically proximate and/or historically related had more
-semantic neighborhoods that aligned. This is a proof of concept for our
-use of fastText in different languages with varying levels of
+Word embeddings like fastText have been demonstrated to be good
+predictors for similarity judgments (Liu, Feng, Wu, Chan, \& Fulton
+(2019), Jatnika, Bijaksana, \& Suryani (2019)). fastText has also been
+shown to be sensitive towards cultural effects on word meanings:
+Thompson \& Lupyan (2020) showed that the distribution of semantic
+meaning clusters generated by fastText trained on language-specific
+corpora correlates to the cultural, historical and geographical
+distances of such languages languages. This is a proof of concept for
+our use of fastText in different languages with varying levels of
 relatedness.
@@
 
-To preview our results, we find that, while we do not see overall group
-differences (between the East Asian contexts and the US) in similarity,
-we do find language-specific co-occurrence can indeed explain
+To preview our results, we find that, while we do not find the predicted
+Eastern/Western contrast in notions of similarity in our Vietnam
+extension, we do find language-specific co-occurrence can indeed explain
 cross-context differences in similarity judgments. In contrast to
@@
 
-We excluded 26 US participants, 123 Vietnam participants, and 34 China
-participants who did not answer all attention checks correctly. We
+We excluded 8 US participants, 62 Vietnam participants, and 16 China
+participants who did not answer 2 or more attention checks correctly. We
 followed 4 exclusion criteria that aim to retain only participants who
@@
 for a language if it would exclude 25\% or more of any one sample. In
-this round of exclusion, we excluded 65 US, 19 Vietnam participants, and
-34 China participants. After these exclusions, the US sample included
-109 participants (27M, 78F, 3 non-binary, 1 other), with mean age = 22.4
-(SD = 8.49) and median age = 20. The Vietnam sample included 57
-participants (17M, 40F, other), with mean age = 22.21 (SD = 6.12) and
-median age = 21. The China sample included 132 participants (51M, 81F,
-other), with mean age = 23.27 (SD = 3.75) and median age =
-23.\footnote{A table summarizing number of participants lost at each
-  round of exclusions is included in the Appendix.}
+this round of exclusion, we excluded 73 US, 27 Vietnam participants, and
+35 China participants. After these exclusions, the US sample included
+119 participants (30M, 84F, 3 non-binary, 2 other), with mean age = 22.2
+(SD = 8.15) and median age = 20. The Vietnam sample included 110
+participants (34M, 71F, 5 other), with mean age = 22.21 (SD = 5.81) and
+median age = 21. The China sample included 149 participants (61M, 87F, 1
+other), with mean age = 23.1 (SD = 3.65) and median age = 23.\footnote{A
+  table summarizing number of participants lost at each round of
+  exclusions is included in the Appendix.}
 
@@
   carried out an exploratory analysis where we used a less stringent
-  attention check exclusion (covered in the final part of the Results \&
-  Analysis section). To preview our findings for this analysis, we did
-  not find any difference in significant results when compared with the
-  main analysis.}
+  attention check exclusion, and did not find any difference in
+  significant results when compared with the main analysis (see
+  Appendix).}
 
@@
 The group means of proportion of thematic response in mainland China is
-the highest (M = 0.65, SD = 0.12), followed by the groups means in
-Vietnam (M = 0.6, SD = 0.13), which is slightly higher than that of the
+the highest (M = 0.65, SD = 0.11), followed by the groups means in
+Vietnam (M = 0.6, SD = 0.11), which is slightly higher than that of the
 US (M = 0.56, SD = 0.17) (Figure 1).
@@
 Overall, there is a significant effect of country on proportion of
-thematic responses (\(\chi^2\)(2) = 15.22, p \textless{} .001). However,
+thematic responses (\(\chi^2\)(2) = 15.37, p \textless{} .001). However,
 this effect is driven by the difference between US and China responding
-(\(\beta\) = -0.53, p \textless{} .001). There is no statistical
-difference between the Vietnam and China responding (\(\beta\) = -0.25,
-p = 0.137), and the US and Vietnam responding (\(\beta\) = 0.28, p =
-0.142).
+(\(\beta\) = -0.48, p \textless{} .001). There is no statistical
+difference between the Vietnam and China responding (\(\beta\) = -0.22,
+p = 0.09), and the US and Vietnam responding (\(\beta\) = 0.26, p =
+0.086).
 
@@
 We found that all corpora are significant predictors of all cultural
-context responding, with p\textless0.05 and \(\beta\) from -9.05 to
--2.44. (For a full report, see Appendix.)
+context responding, with p \textless{} 0.05 and \(\beta\) from -8.69 to
+-2.4. (For a full report, see Appendix.)
 
@@
 For US responding: English (EN), Vietnamese (VI), and Mandarin (ZH)
-corpus are all significant predictors. EN corpus: \(\beta\) = -7.14,
-\(\chi^2\)(1) = 16.78, p \textless{} .001. VI corpus: \(\beta\) = -2.28,
-\(\chi^2\)(1) = 3.74, p = 0.053. ZH corpus: \(\beta\) = -3.53,
-\(\chi^2\)(1) = 3.99, p = 0.046.
+corpus are all significant predictors. EN corpus: \(\beta\) = -6.96,
+\(\chi^2\)(1) = 16.57, p \textless{} .001. VI corpus: \(\beta\) = -2.22,
+\(\chi^2\)(1) = 3.73, p = 0.054. ZH corpus: \(\beta\) = -3.18,
+\(\chi^2\)(1) = 3.37, p = 0.066.
 
 For Vietnam responding: English (EN), Vietnamese (VI), and Mandarin (ZH)
-corpus are all significant predictors. EN corpus: \(\beta\) = -4.25,
-\(\chi^2\)(1) = 3.87, p = 0.049. VI corpus: \(\beta\) = -2.98,
-\(\chi^2\)(1) = 4.17, p = 0.041. ZH corpus: \(\beta\) = -4.86,
-\(\chi^2\)(1) = 4.94, p = 0.026.
+corpus are all significant predictors. EN corpus: \(\beta\) = -2.98,
+\(\chi^2\)(1) = 2.58, p = 0.108. VI corpus: \(\beta\) = -2.75,
+\(\chi^2\)(1) = 4.84, p = 0.028. ZH corpus: \(\beta\) = -4.39,
+\(\chi^2\)(1) = 5.49, p = 0.019.
 
 For China responding: English (EN), Vietnamese (VI), and Mandarin (ZH)
-corpus are all significant predictors. EN corpus: \(\beta\) = -3.52,
-\(\chi^2\)(1) = 7.85, p = 0.005. VI corpus: \(\beta\) = -1.62,
-\(\chi^2\)(1) = 3.57, p = 0.059. ZH corpus: \(\beta\) = -5.35,
-\(\chi^2\)(1) = 17.19, p \textless{} .001.
+corpus are all significant predictors. EN corpus: \(\beta\) = -3.32,
+\(\chi^2\)(1) = 7.18, p = 0.007. VI corpus: \(\beta\) = -1.59,
+\(\chi^2\)(1) = 3.63, p = 0.057. ZH corpus: \(\beta\) = -5.31,
+\(\chi^2\)(1) = 17.69, p \textless{} .001.
 
@@
 corresponding corpus included as a predictor (US response: \(\chi^2\)(2)
-= 8.42, p = 0.015; Vietnam response: \(\chi^2\)(2) = 15.21, p
-\textless{} .001; China response: \(\chi^2\)(2) = 10.83, p NA).
+= 7.93, p = 0.019; Vietnam response: \(\chi^2\)(2) = 13.72, p = 0.001;
+China response: \(\chi^2\)(2) = 10.56, p = 0.005).
 
@@
 Our analysis shows that lexical statistics of each corpus is a
-significant predictor for similarity judgement in the corresponding
+significant predictor for similarity judgment in the corresponding
 cultural context, even without the addition of the other two corpora.
@@
 statistics, we take the above result as evidence that cross-cultural
-differences in input to the process of similarity judgement at least
-partially drives cross-cultural similarity judgement differences.
+differences in input to the process of similarity judgment at least
+partially drives cross-cultural similarity judgment differences.
 However, it is still an open question whether the nature of similarity
-judgement (for e.g., the notion of similarity) itself differs across
+judgment (for e.g., the notion of similarity) itself differs across
 cultures and contributes to cross-cultural differences in similarity
-judgement responding. In an alternative hypothesis, the cross-cultural
-differences in similarity judgement observed is driven by not only the
+judgment responding. In an alternative hypothesis, the cross-cultural
+differences in similarity judgment observed is driven by not only the
 input, but also an interaction between cultural-specific nature of
-similarity judgement and input. To test this hypothesis, we
-operationalize cultural-specific nature of similarity judgement as
-country context, and input to similarity judgement as the corresponding
+similarity judgment and input. To test this hypothesis, we
+operationalize cultural-specific nature of similarity judgment as
+country context, and input to similarity judgment as the corresponding
 corpus statistics. We then compare a model that includes country,
@@
 In the model containing only the corresponding corpus statistics, the
-corpus statistics is a significant predictor (\(\beta\) = -1.75,
-\(\chi^2\)(1) = 48.9, p \textless{} .001). When adding country and
+corpus statistics is a significant predictor (\(\beta\) = -1.79,
+\(\chi^2\)(1) = 75.58, p \textless{} .001). When adding country and
 interaction between country and corpus, both the corpus statistics
-(\(\beta\) = -1.51, \(\chi^2\)(1) = 13.96, p \textless{} .001) and
-interaction between country and corpus (\(\beta\) = NA, \(\chi^2\)(2) =
-9.1, p = 0.011) are significant predictors. This suggests that there are
-cross-cultural differences in both input and nature of similarity
-judgement that drive differences in similarity judgement responding.
+(\(\beta\) = -1.72, \(\chi^2\)(1) = 23.34, p \textless{} .001) and
+interaction between country and corpus (F(2, \ensuremath{\infty{}}) =
+6.66, \(\chi^2\)(2) = 13.33, p = 0.001) are significant predictors. This
+suggests that there are cross-cultural differences in both input and
+nature of similarity judgment that drive differences in similarity
+judgment responding. We found no effects of country (F(2,
+\ensuremath{\infty{}}) = 13.18, \(\chi^2\)(2) = 7.39, p = 0.025).
 
@@
 approach has shown that notions of similarity only has an effect on
-cross-cultural differences in similarity judgement when modulated by
+cross-cultural differences in similarity judgment when modulated by
 input, and that input as proxied by lexical statistics of the
 corresponding corpus by itself is a significant predictor for similarity
-judgement responding. Our approach using lexical statistics do not
-assume a taxonomic/thematic structure in the triads. Therefore, it
-should be possible to predict similarity judgements to triads that do
-not follow a taxonomic/thematic structure, such as our filler triads. If
-our approach is tractable, we should be able to repeat the above
-analyses to the filler triads, and find that lexical statistics of each
-corpus is a significant predictor for similarity judgements in filler
-triads of the corresponding cultural context.
+judgment responding. Our approach using lexical statistics do not assume
+a taxonomic/thematic structure in the triads. Therefore, it should be
+possible to predict similarity judgments to triads that do not follow a
+taxonomic/thematic structure, such as our filler triads. If our approach
+is tractable, we should be able to repeat the above analyses to the
+filler triads, and find that lexical statistics of each corpus is a
+significant predictor for similarity judgments in filler triads of the
+corresponding cultural context.
 
@@
 
-\caption[Proportion of thematic responses by country]{Proportion of thematic responses by country.}\label{fig:unnamed-chunk-4}
+\caption[Proportion of Word1 responses by country]{Proportion of Word1 responses by country.}\label{fig:unnamed-chunk-4}
 \end{figure}
@@
 correpsonding corpora is a significant predictor of responding, with
-p\textless0.05 and \(\beta\) from -9.59 to -3.05. (For a full report,
+p\textless0.05 and \(\beta\) from -9.59 to -3.14. (For a full report,
 see Appendix.)
@@
 similarity judgment paradigm, as an alternative to the view that members
-of different cultures vary in their conception of similarity.
+of different cultures vary in their conception of similarity. We found
+that each corpus statistics is a good predictor for the corresponding
+country's similarity judgments. When corresponding corpus statistics,
+country and corpus-country interactions were included as fixed effects
+to predict similarity judgments, we found no effects of country, but
+both corpus statistics and corpus-country interaction are significant
+predictors. Our results provide evidence that cross-cultural differences
+in similarity judgment might not be driven by cross-cultural differences
+in conception of similarity alone, but rather by statistics to
+similarity judgment and its interaction with similarity conception. We
+also showed that corpus statistics predict similarity judgments for
+triads that do not have taxonomic/thematic structure.
 
@@
 
-We did find some signatures of language specificity in our analysis,
-such as the large positive correlation between similarity judgments of
-each country and the respective corpus statistics, and how each corpus
-statistics are good predictors for corresponding country's similarity
-judgments. However, this is potentially due to the high correlation
-between corpus statistics of English, Vietnamese and Mandarin. We find
-even stronger evidence for consistency across the three groups, with
-substantive overlapping predictions across the corpus models, highly
-similar responding across the experiments, and a correspondingly high
-fit in cross-language comparisons between models and data.
+We did find some signatures of language specificity in our analysis:
+each corpus statistics is a good predictor for the corresponding
+country's similarity judgments, even when other corpus statistics are
+included. However, we also find evidence for consistency across the
+three cultural groups: each corpus statistics is also a good predictor
+for the other two non-corresponding cultural contexts when included as
+the only predictor, and both English and Mandarin Chinese statistics are
+good predictors for their non-corresponding cultural contexts when all
+three corpora are included.
 
-Our findings raise additional questions for future work: if not
-differences in taxonomic vs.~thematic responding, then what differences
-drive the relativity effects previous studies have observed? To what
-extent are the relativity effects driven by language, and to what extent
-by culture? Ji et al. (2004) established that culture-aligned
-differences in this paradigm exist, even when the test language is held
-constant, concluding that ``it is culture (independent of the testing
-language) that led to different grouping styles'' in their study. Our
-data provide a cautionary note to this conclusion, suggesting that
-semantic representations in bilinguals (see Francis (2005) for a review)
-may have the potential to provide an offline account for cross-context
+When all cultural contexts are taken together, we found that both
+corresponding corpus statistics and an interaction between corpus and
+country are significant predictors for similarity judgments. This result
+suggests that in addition to input to similarity judgment,
+country-specific categorical differences in similarity judgment (for
+e.g., how each culture conceive of similarity) also predict
+cross-cultural differences in similarity judgment behavior while
+modulated by input.
+
+Even in triads with no taxonomic / thematic structure, each corpus
+statistics is still a good predictor of the corresponding country's
+similarity judgments. The ability of corpus statistics to predict
+similarity judgments in non-structured triads suggests that
+cross-cultural differences in similarity judgments should be construed
+in a more general and graded manner, as opposed to binary
+taxonomic/thematic match-preferring.
+
+Our findings raise additional questions for future work: To what extent
+are the relativity effects driven by language, and to what extent by
+culture? Ji et al. (2004) established that culture-aligned differences
+in this paradigm exist, even when the test language is held constant,
+concluding that ``it is culture (independent of the testing language)
+that led to different grouping styles'' in their study. Our data provide
+a cautionary note to this conclusion, suggesting that semantic
+representations in bilinguals (see Francis (2005) for a review) may have
+the potential to provide an offline account for cross-context
 differences in similarity judgments, independent of test language.
@@
   \hline
-US & 0.32 & 0.97 \\ 
-  China & 0.20 & 0.96 \\ 
-  Vietnam & 0.32 & 0.95 \\ 
+US & 0.30 & 0.97 \\ 
+  China & 0.19 & 0.96 \\ 
+  Vietnam & 0.27 & 0.97 \\ 
    \hline
@@
 
-\hypertarget{supplemental-for-whether-each-corpus-predicts-similarity-judgement-in-each-cultural-context}{%
+An intraclass correlation coefficients (ICCs) analysis with a two-way,
+non-interactive model (following the standard taxonomy for ICCs from
+McGraw \& Wong (1996)) showed that, per cultural context, participants'
+judgments were variable across triads, while inter-rater agreement about
+specific triads was quite high (Table 1). This result suggests that each
+triad prompts taxonomic / thematic matching reliably within culture.
+
+\hypertarget{supplemental-for-whether-each-corpus-predicts-similarity-judgment-in-each-cultural-context}{%
 \subsection{2. Supplemental for whether each corpus predicts similarity
-judgement in each cultural
-context}\label{supplemental-for-whether-each-corpus-predicts-similarity-judgement-in-each-cultural-context}}
+judgment in each cultural
+context}\label{supplemental-for-whether-each-corpus-predicts-similarity-judgment-in-each-cultural-context}}
 
@@
 corpus are significant predictors of US responding (EN-US model:
-\(\beta\) = -9.05, \(\chi^2\)(1) = 31.28, p \textless{} .001; VI-US
-model: \(\beta\) = -3.13, \(\chi^2\)(1) = 5.1, p = 0.024; ZH-US model:
-\(\beta\) = -7.42, \(\chi^2\)(1) = 18.48, p \textless{} .001).
+\(\beta\) = -8.69, \(\chi^2\)(1) = 30.98, p \textless{} .001; VI-US
+model: \(\beta\) = -3.01, \(\chi^2\)(1) = 5.24, p = 0.022; ZH-US model:
+\(\beta\) = -6.97, \(\chi^2\)(1) = 17.62, p \textless{} .001).
 
@@
 (ZH) corpus are significant predictors of VN responding (EN-VN model:
-\(\beta\) = -6.86, \(\chi^2\)(1) = 11.71, p \textless{} .001; VI-VN
-model: \(\beta\) = -3.83, \(\chi^2\)(1) = 6.02, p = 0.014; ZH-VN model:
-\(\beta\) = -7.49, \(\chi^2\)(1) = 13.84, p \textless{} .001).
+\(\beta\) = -5.33, \(\chi^2\)(1) = 9.4, p = 0.002; VI-VN model:
+\(\beta\) = -3.46, \(\chi^2\)(1) = 6.8, p = 0.009; ZH-VN model:
+\(\beta\) = -6.37, \(\chi^2\)(1) = 13.84, p \textless{} .001).
 
@@
 (ZH) corpus are significant predictors of CN responding (EN-CN model:
-\(\beta\) = -6.18, \(\chi^2\)(1) = 25.39, p \textless{} .001; VI-CN
-model: \(\beta\) = -2.44, \(\chi^2\)(1) = 5.75, p = 0.017; ZH-CN model:
-\(\beta\) = -7.36, \(\chi^2\)(1) = 37.72, p \textless{} .001).
+\(\beta\) = -5.97, \(\chi^2\)(1) = 25.49, p \textless{} .001; VI-CN
+model: \(\beta\) = -2.4, \(\chi^2\)(1) = 5.91, p = 0.015; ZH-CN model:
+\(\beta\) = -7.22, \(\chi^2\)(1) = 39.24, p \textless{} .001).
 
@@
 English (EN) is a significant predictors of US responding (\(\beta\) =
--7.93, \(\chi^2\)(1) = 35.87, p \textless{} .001).
+-8.35, \(\chi^2\)(1) = 36.1, p \textless{} .001).
 
 Vietnamese (VI) is a significant predictors of Vietnam responding
-(\(\beta\) = -3.05, \(\chi^2\)(1) = 5.88, p = 0.015).
+(\(\beta\) = -3.14, \(\chi^2\)(1) = 4.65, p = 0.031).
 
@@
 
-\hypertarget{demographic-exclusion-statistics}{%
-\subsection{3. Demographic Exclusion
-Statistics}\label{demographic-exclusion-statistics}}
+\hypertarget{exclusion-statistics}{%
+\subsection{3. Exclusion Statistics}\label{exclusion-statistics}}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-McGraw1996}{}}%
+McGraw, K. O., \& Wong, S. P. (1996). Forming inferences about some
+intraclass correlation coefficients. \emph{Psychological Methods},
+\emph{1}(1), 30.
+
 \leavevmode\vadjust pre{\hypertarget{ref-Mikolov2018}{}}%

### 2023-01-31 code/4_paper/manuscript/SI.Rmd
manuscript edits

--- 2023-01-20 code/4_paper/manuscript/manuscript.Rmd
@@
 ---
-title: "Re-examining cross-cultural similarity judgements using lexical co-occurrence"
-bibliography: library.bib
-csl: apa6.csl
-document-params: "10pt, letterpaper"
-
-header-includes:
-  - \usepackage[utf8]{inputenc}
-  - \usepackage[T1, T2A, T5]{fontenc}
-  - \usepackage{kotex}
-
-author-information: > 
-    \author{{\large \bf Morton Ann Gernsbacher (MAG@Macc.Wisc.Edu)} \\ Department of Psychology, 1202 W. Johnson Street \\ Madison, WI 53706 USA
-    \AND {\large \bf Sharon J.~Derry (SDJ@Macc.Wisc.Edu)} \\ Department of Educational Psychology, 1025 W. Johnson Street \\ Madison, WI 53706 USA}
-
-abstract: >
- Is “cow” more closely related to “grass” or “chicken”?
-Speakers of different languages judge similarity in this context differently, but why?
-One possibility is that cultures co-varying with these languages induce differences in conceptualizations of similarity.
-Specifically, East Asian cultures may promote reasoning about thematic similarity, by which cow and grass are more related, whereas Western cultures may bias judgements toward taxonomic relations, like cow-chicken.
-This difference in notions of similarity is the consensus interpretation for cross-cultural variation in this paradigm.
-We consider, and provide evidence for, an alternative possibility, by which notions of similarity are similar across contexts, but the statistics of the environment vary.
-On this account, similarity judgements are guided by co-occurrence in experience, and observing or hearing about cows and grass or cows and chickens more often could induce preferences for these groupings, and account in part for apparent differences in notions of similarity across contexts.
-
-keywords: >
-    similarity; culture; language; semantics; lexical co-occurrence; variation
-
-output: cogsci2016::cogsci_paper
-#final-submission: \cogscifinalcopy
+title: "SI"
+output: html_document
+date: "2023-01-29"
 ---
 
-```{r global_options, include=FALSE}
-knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, 
-                      fig.pos = "tb", fig.path='figs/',
-                      echo=F, warning=F, cache=T, 
-                      message=F, sanitize = T)
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = TRUE)
 ```
 
-```{r, libraries, cache=F}
-library(png)
-library(grid)
-library(ggplot2)
-library(xtable)
+## R Markdown
+
+This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
+
+When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
+You can embed an R code chunk like this:
+
+```{r cars}
+summary(cars)
 ```
 
-```{r setup, include = FALSE, cache=F}
-library("papaja")
-library("knitr") # for knitting things
-library("tidyverse") # for all things tidyverse
-library("car")
-library("lme4")
-library("patchwork")
-library("effsize")
-library("kableExtra")
-library("irr")
-require(agreement)
+## Including Plots
 
-# # these options here change the formatting of how comments are rendered
-# opts_chunk$set(
-#   comment = "",
-#   results = "hold",
-#   fig.show = "hold")
+You can also embed plots, for example:
 
-# set the default ggplot theme 
-theme_set(theme_classic(base_size = 7))
-
-#r_refs("r-references.bib")
-#r_refs("references/packages.bib")
-
+```{r pressure, echo=FALSE}
+plot(pressure)
 ```
 
-```{r analysis-preferences, cache=F}
-# Seed for random number generation
-set.seed(42)
-knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
-```
+Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
+# Appendix
 
-# Introduction 
-By virtue of discrete words and grammatical features, language provides a categorical partition of our continuous experiences.
-By measuring the similarity between words (as commonly done with lexical co-occurrence models), it may be possible to model the shape of similarity space in order to capture cross-linguistic and cross-cultural variation and provide a more general answer to the question of how language influences our conception of the world.
-
-Taxonomic and thematic similarity provide a convenient entry point to broader debates about cross-linguistic and cross-cultural variation in notions of similarity.
-Taxonomic categorization is based on the similarity of attributes, for example, similar perceptual properties, like shared color or shape, among objects.
-In contrast, thematic categorization is based on causal, spatial, and temporal relationships among objects [@Markman1984].
-
-## Cross-cultural variation in similarity
-Preferences for taxonomic and thematic similarity vary across cultures.
-@Chiu1972 found that Chinese children (9-10 years old) are more likely to choose thematic matches in a picture triad task (shown, e.g., images of an ant, a bee, and honey) than their American counterparts.
-These cross-cultural differences are also observed in novel object categorization, with Chinese participants preferring to group by family resemblance across multiple features and Americans preferring a single-feature rule [@Norenzayan2002].
-<!-- Because differences in similarity preference persist with novel stimuli (as opposed to familiar items), this suggests that participants from different cultural backgrounds use different reasoning strategies when making similarity judgments.
--->
-The authors link these differences to tendencies toward analytic processing in Western cultures, which emphasizes objects and their properties, and holistic processing in East Asian cultures, which emphasizes relationships between objects and their context (see also @Nisbett2003).
-In related work, East Asian participants show a higher level of sensitivity to context than their Western counterparts when reproducing drawings from memory [@Ji2000]; visually exploring naturalistic scenes [@Chua2005]; describing scenes [@Masuda2001]; and in explaining the causes of ambiguous behaviors [@Choi1999].
-
-@Ji2004 asked whether differences in analytic and holistic processing <!--they use that language, right?--> are driven by language, culture, or a combination of these.
-They presented Chinese and European American adults with a word triad task, and found a preference for thematic matching among Chinese participants compared to European Americans.
-They found that test language contributed to this difference, but did not fully explain it: Chinese participants showed a stronger thematic preference when tested in Mandarin, but still showed a thematic preference when tested in English.
-Ji et al.
-conclude that culture (independent of language) leads to different styles of reasoning about similarity, whereas language serves as a “tuning” mechanism operating within a culturally-specific style, by activating representations corresponding to the language being used.^[But note that this work did not include a manipulation to prevent participants from engaging in e.g., covert naming in a language other than the test language.]
-
-This view ascribes cross-cultural differences in similarity judgment to variation in the conceptualization of similarity itself.
-Alternatively, these judgments could be shaped by cross-cultural differences in the statistics of the environment, and accordingly the content of everyday experiences.
-Perhaps when confronted with the triad task, participants from all cultures follow the same process for reasoning about similarity, but rely on language or culture-specific inputs to this process.
-<!--For example, it may be that Vietnamese participants are more likely to have knowledge of farming practices than Americans, and may associate cows and grass more strongly (as grass is the typical feed for cows in the small-scale family farming contexts common in Vietnam).
-Americans, on the other hand, may have strong associations between cows and chickens as a result of encountering them together in children’s books or petting zoo contexts.--> If we observe a difference in categorization between East Asian and Western participants, it could be that members of both groups use the same procedure (considering similarity that is influenced by both taxonomic and thematic relations), but the inputs to this procedure differ between cultures, with East Asian participants exposed to more instances of thematic similarity than their Western counterparts.
-
-## Estimating variation in experience
-While co-occurrences in experience are difficult to measure, co-occurrence in language can provide a rough proxy--and indeed, language may afford many of the “experiences” that people have with infrequently encountered items, like cows or helicopters.
-In this study, we use co-occurrence in language as a proxy of cultural experience.
-This is a generalizing assumption, and while no linguistic corpus can be expected to fully capture a culture, using this proxy as a model of culture provides a conservative test of the hypothesis that differences in the input, rather than the process, of reasoning produces cultural variation in this task.
-This means that if such a model does work -- if linguistic co-occurrence can predict cultural variation in this similarity task without building differences in the decision process into the model -- it is relatively strong evidence that language alone (perhaps as a more easily observed source of information on broader cultural and ecological variation) may account for these cross-cultural differences in reasoning.
-
-Indeed, previous work suggests that using lexical co-occurrence as a proxy can be useful in thinking about similarity reasoning.
-Natural language processing tasks have found that lexical co-occurrence is a good predictor for performance in similarity judgment.
-@Griffiths2007 showed that a model that takes word-document co-occurrence as input can be used to predict word association and the effects of semantic association on a variety of linguistic tasks.
-Additionally, lexical semantic models that are constructed using lexical co-occurrence (as opposed to annotated relations) have been shown to perform well on predicting human judgments about similarity between word pairs that are thematically or taxonomically related [@Rohde2006].
-
-Our study uses cosine distances of fastText word vectors as a measure of lexical co-occurrence^[We also carried out our analysis using raw lexical co-occurrences and obtained similar results.].
-fastText is a system that uses lexical co-occurrence information to generate a vector representing each word in its lexicon [@Mikolov2018].
-
-<!-- MOVE TO METHODS?
-fastText uses a continuous bag-of-words model, which takes into account a symmetric window of words surrounding the word in question and maximizes the log-likelihood of the probability of the word given its context.
-Calculating the cosine-similarity between word vectors from fastText gives us a score of how similar the contexts of these words are.
-Therefore, words that occur in the same context (high lexical co-occurrence) would have a larger cosine-similarity score.
-
-It must be noted that fastText supplements the lexical co-occurrence information by simultaneously training weight vectors for each position relative to the word in question, as well as adding sub-word information (bag-of-character n-gram vectors for each character forming the words).
-The similarity judgment prediction given by fastText may be more higher than a model using purely lexical co-occurrence information.
-However, models that use only lexical co-occurrence information (with or without a simple position weight system that gives more weight to words that are closer to the word in question) also perform well in similarity prediction tasks.
-For this study, due to the lack of large cleaned corpora for Mandarin and Vietnamese, we leverage fastText pre-trained models on the languages we are interested in @Grave2018.-->
-
-<!-- condense to 2 sentences --> Systems like fastText and word2vec have been demonstrated to be good predictors for similarity judgments.
-@Liu2019 showed that fastText performed well as the data for a system matching responses in a knowledge base by how similar they are to a customer’s query.
-A study by @Jatnika2019 tested a word2vec model trained on the English wikipedia corpus against 353 word pairs labeled with similarity values based on human judgment.
-The word2vec model correlates moderately with human judgment.
-fastText has also been shown to be sensitive towards cultural effects on word meanings: @Thompson2020 applied fastText to language-specific Wikipedia corpus (among others) to generate a “semantic neighborhood” of 1010 meanings in different languages.
-The study showed that languages that are spoken by more similar cultures, more geographically proximate and/or historically related had more semantic neighborhoods that aligned.
-This is a proof of concept for our use of fastText in different languages with varying levels of relatedness.
-
-## The present study
-<!-- @Ji2004 observed a difference in similarity judgment between Chinese and European Americans (the former preferred thematic matching the latter taxonomic).
-However, their evidence is not sufficient to conclude that it is culture that drives this difference, as their cross-cultural data is correlational.
-Furthermore, they have yet to rule out all mechanisms by which language could be relevant to the task.
-For example, their language manipulation (bilingual speakers from Mainland China making more taxonomic categorizations when tested in language) only points to an offline effect of language because it does not prevent participants from accessing linguistic representations.
-A stronger claim could have been made if verbal interference had been conducted, and if cross-cultural differences had remained.
-This would have been stronger in eliminating online effect of language as a potential cause for cross-cultural differences in similarity judgment.
--->
-
-<!-- Additionally, outside of language, cross-cultural differences could come from a couple different mechanisms:  -->
-@Ji2004 suggest that the notion of similarity is what varies across cultural groups, but it is possible that similarity is regarded in the same way and it is actually the input to this similarity judgment that varies across cultural contexts.
-It may be possible to gain traction on potential mechanisms by examining whether variation in similarity judgments co-vary with environmental statistics that differ across cultural and linguistic contexts.
-
-In this study, we ask whether variation in lexical co-occurrence can account for the cross-context (culture and language) differences observed in how people evaluate similarity.
-First, we attempt to replicate @Ji2004 by running a study comparing English speakers in the US and Mandarin speakers in mainland China.
-Second, we evaluate whether the differences observed between English and Mandarin speakers’ similarity judgments also extend to comparisons between English and Vietnamese, by running a similar study between English speakers in the US and Vietnamese speakers in Vietnam.
-Vietnam is a Southeast Asian country that borders China and is historically greatly influenced by Chinese culture [@Hui2002].
-Therefore, it serves as a suitable cultural context to investigate whether the claim made by @Ji2004 and previous studies, that Eastern and Western cultures have different notions of similarity, extends beyond mainland China.
-
-We then ask to what extent similarity judgments show cross-context differences that align with co-occurrence patterns in participants’ languages.
-We would only see a main effect of cultural context if differing notions of similarity drive these cross-cultural differences.
-Meanwhile, if we do see variation in responding trial-to-trial that tracks with lexical co-occurrence statistics (as a rough proxy combining both linguistic and cultural context), this suggests that cross-cultural notions of similarity might be similar, and it is environmental statistics that guide the differences in similarity judgments.
-
-To preview our results, we find that, while we do not see overall group differences (between the East Asian contexts and the US) in similarity, we do find language-specific co-occurrence can indeed explain cross-context differences in similarity judgments.
-In contrast to previous accounts, by which culture induces differing conceptions of similarity (varying between taxonomic and thematic), these findings provide an alternative, and more specific, account by which language may explain these cross-cultural differences without invoking variation in notions of similarity.
-
-There are several important limitations of our approach.
-While we discuss cross-cultural variability at the level of countries or larger world areas, these are not cultural monoliths.
-For convenience, we operationalize culture at the level of country, based on where participants were raised.
-It is an open question whether performance in our participant populations (of relatively young and well-educated adults) is representative of the broader country.
-This is especially true for societies with substantial ethnic and cultural variation such as the US.
-We expect that our data is likely to underestimate variation both within and between the countries we sample from.
-
-Language, culture, cognition, and individual experiences are intertwined in complex causal relationships: cultural features (farming) can lead to differences in individuals’ experiences (seeing cows and grass) and in turn these can influence language (talking more about cows and grass).
-But cultural features (a thematic orientation) could also more directly cause individuals to talk differently about the same experiences (mentioning what cows eat rather than what other animals cows are like).
-In this study, we measure language and its relation to cross-cultural differences in categorization, but these relations test only the plausibility of a language-based account; they cannot establish the direction of causality.
-
-# Methods 
-```{r get responding and demographic data, include = F}
-df <- read.csv("../../../data/data_USCNVN_ENZHVI.csv")
-
-df_main_analysis <- df
-df.demog <- read.csv("../../../data/responding/data_demog.csv") %>%
-  filter(subject %in% unique(df$subject))
-
-triads_omit <- read.csv("../../../data/triads_omit.csv") %>%
-  pull(x)
-
-head(df)
-```
-
-```{r get exclusions data, include = F, cache = T}
-df.excl_US <- read.csv("../../../data/responding/dataUS_excl_metadata.csv") %>%
-  select(-X)
-df.excl_CN <- read.csv("../../../data/responding/dataCN_excl_metadata.csv") %>%
-  select(-X)
-df.excl_VN <- read.csv("../../../data/responding/dataVN_excl_metadata.csv") %>%
-  select(-X)
-```
-
-```{r demog_E, include = F, cache = T}
-df.demog_E <- df.demog %>%
-  filter(country == "US")
-
-df.age_E <- df.demog_E %>%
-  filter(demog_question == "age") %>%
-  mutate(demog_response = as.numeric(demog_response)) %>%
-  summarize(mean_age = mean(demog_response), 
-            median_age = median(demog_response), 
-            sd_age = sd(demog_response))
-
-df.gender_E <- df.demog_E %>%
-  filter(demog_question == "gender") %>%
-  group_by(demog_response) %>%
-  rename(gender = demog_response) %>%
-  summarize(n=n())
-```
-
-```{r demog_M, include = F, cache = T}
-df.demog_M <- df.demog %>%
-  filter(country == "CN")
-
-df.age_M <- df.demog_M %>%
-  filter(demog_question == "age") %>%
-  mutate(demog_response = as.numeric(demog_response)) %>%
-  summarize(mean_age = mean(demog_response), 
-            median_age = median(demog_response), 
-            sd_age = sd(demog_response))
-
-df.gender_M <- df.demog_M %>%
-  filter(demog_question == "gender") %>%
-  group_by(demog_response) %>%
-  rename(gender = demog_response) %>%
-  summarize(n=n())
-```
-
-```{r demog_V, include = F, cache = T}
-df.demog_V <- df.demog %>%
-  filter(country == "VN")
-
-df.age_V <- df.demog_V %>%
-  filter(demog_question == "age") %>%
-  mutate(demog_response = as.numeric(demog_response)) %>%
-  summarize(mean_age = mean(demog_response), 
-            median_age = median(demog_response), 
-            sd_age = sd(demog_response))
-
-df.gender_V <- df.demog_V %>%
-  filter(demog_question == "gender") %>%
-  group_by(demog_response) %>%
-  rename(gender = demog_response) %>%
-  summarize(n=n())
-```
-
-## Participants
-We recruited `r df.excl_US$ppts_finished` participants from the US, `r df.excl_VN$ppts_finished` participants from Vietnam, and `r df.excl_CN$ppts_finished` participants from mainland China.
-US participants were recruited through snowball sampling seeded with Stanford student email lists, Vietnam participants were recruited through snowball sampling seeded with Vietnam-based student groups on Facebook, and mainland China participants were recruited through snowball sampling seeded with group chats on WeChat.
-US participants were compensated with $5 gift certificates (USD), VN participants received 50,000₫ (VND) in phone credit, and mainland China participants received 25CNY through WeChat credit transfer.
-
-We excluded `r df.excl_US$ppts_finished - df.excl_US$ppts_after_att_check_excl` US participants, `r df.excl_VN$ppts_finished - df.excl_VN$ppts_after_att_check_excl` Vietnam participants, and `r df.excl_CN$ppts_finished - df.excl_CN$ppts_after_att_check_excl` China participants who did not answer all attention checks correctly.
-We followed 4 exclusion criteria that aim to retain only participants who are influenced by one culture: (1) non-native speakers of English and Vietnamese, respectively, (2) fluent in at least one of the other two study languages (Vietnamese for US participants, English for Vietnamese participants and Chinese participants), (3) have lived outside of the test country (US, Vietnam, or China) for more than two years, and (4) have significant international experience (more than 6 international experiences of 2 days or longer.) We did not use a particular criterion for a language if it would exclude 25% or more of any one sample.
-In this round of exclusion, we excluded `r df.excl_US$ppts_after_att_check_excl - df.excl_US$ppts_after_demog_excl` US, `r df.excl_VN$ppts_after_att_check_excl - df.excl_VN$ppts_after_demog_excl` Vietnam participants, and `r df.excl_CN$ppts_after_att_check_excl - df.excl_CN$ppts_after_demog_excl` China participants.
-After these exclusions, the US sample included `r df.excl_US$ppts_after_demog_excl` participants (`r df.gender_E %>% filter(gender == "Male") %>% pull(n)`M, `r df.gender_E %>% filter(gender == "Female") %>% pull(n)`F, `r df.gender_E %>% filter(gender == "Non-binary") %>% pull(n)` non-binary, `r df.gender_E %>% filter(gender == "Decline to answer") %>% pull(n)` other), with mean age = `r round(df.age_E$mean_age, 2)` (SD = `r round(df.age_E$sd_age, 2)`) and median age = `r df.age_E$median_age`.
-The Vietnam sample included `r df.excl_VN$ppts_after_demog_excl` participants (`r df.gender_V %>% filter(gender == "Nam") %>% pull(n)`M, `r df.gender_V %>% filter(gender == "Nữ") %>% pull(n)`F, `r df.gender_V %>% filter(gender == "Từ chối trả lời") %>% pull(n)` other), with mean age = `r round(df.age_V$mean_age, 2)` (SD = `r round(df.age_V$sd_age, 2)`) and median age = `r df.age_V$median_age`.
-The China sample included `r df.excl_CN$ppts_after_demog_excl` participants (`r df.gender_M %>% filter(gender == "男性") %>% pull(n)`M, `r df.gender_M %>% filter(gender == "女性") %>% pull(n)`F, `r df.gender_M %>% filter(gender == "拒绝回答") %>% pull(n)` other), with mean age = `r round(df.age_M$mean_age, 2)` (SD = `r round(df.age_M$sd_age, 2)`) and median age = `r df.age_M$median_age`.^[A table summarizing number of participants lost at each round of exclusions is included in the Appendix.]
-
-Notably, we lost a majority of our Vietnam participants (more than 60%) in the attention check exclusion.
-One reason we suspect why this might have happened is because our Vietnam participants are less familiar with research surveys and attention check questions, and thus might have thought too much about the attention check questions.^[We carried out an exploratory analysis where we used a less stringent attention check exclusion (covered in the final part of the Results & Analysis section).
-To preview our findings for this analysis, we did not find any difference in significant results when compared with the main analysis.]
-
-## Stimuli
-We adapted stimuli from previous studies to create a set of test triads consisting of a cue, with one thematic and one taxonomic match option.
-For example, “cow,” “grass,” and “chicken,” where “cow” is the cue, “grass” is the thematic match, and “chicken” the taxonomic match.
-We included 105 such triads, a superset including triads pulled from supplemental information and in-text examples across the literature, and others that we adapted or created <!--(see SI for the full list of stimuli and sources)-->.
-We selected triads on the basis of cultural familiarity in the US, Vietnam, and China.
-The triads were originally in English; they were translated to Vietnamese and Mandarin by a fluent bilingual speaker in each language.
-The translations were then checked for accuracy after backtranslation to English by another fluent bilingual in each language who was naive to the original English versions.
--->
-
-Each participant completed all 105 triads in sets of 21 trials at a time (10 test triads, 10 filler triads, and 1 attention check per page), by selecting the match most related to the cue (“Which thing is most closely related to the bolded item?” or "Thứ nào liên quan nhất với thứ được in đậm?").
-The test triads were presented with 105 filler triads mixed in, to obscure the taxonomic-thematic two-answer forced choice structure of the test stimuli and reduce the likelihood that participants would become aware of the design.
-The filler triads were groups of three semantically related words, but where the match options were not distinguished by thematic vs.
-taxonomic similarity, e.g., cue “bird” with match options “lizard” and “toad.” Additionally, we included 10 attention check trials, which were formatted like the test and filler triads but included an instruction instead of a cue item, e.g., “Choose wife” with match options “wife” and “husband.” In total, each participant completed 210 similarity judgments and 10 attention check questions, with triads presented in randomized orders that varied between subjects.
-
-## Corpus model 
-<!-- Our general approach is to build a model of similarity that is based on collocation counts in each language.  -->
-
-<!-- ### Raw lexical co-occurrences -->
-<!-- To give an intuition for our model, consider the cow-grass-chicken triad: we counted how many times “cow” and “grass” co-occur within a window of text in each corpus, and compare this to how many times “cow” and “chicken” co-occur.
-Our similarity prediction is then proportional to the relative frequency of these pairs.
-For example, if the thematic cow-grass match accounts for 30% of collocations for this triad (with cow-chicken making up the other 70%), then our model predicts, correspondingly, that 30% of responses to the triad will be grass, and the other 70% chicken.
-We then use a mixed-effects regression to evaluate how well each corpus collocate model predicts participants’ similarity judgments, across triads and languages.
--->
-
-<!-- #### Collocate retrieval and coding -->
-<!-- For our English co-occurrence metric, we used the online interface of the Corpus of Contemporary American English [@COCA] to retrieve collocation counts.
-We recorded the raw count of times that any cue-match pair (e.g., cow-grass or cow-chicken) co-occur in a window of 19 words, which is the maximum window size in the online interface, and closest to the sentence co-occurrence metric in our VI corpus collocation counts.
--->
-
-<!-- To determine Vietnamese co-occurrence, we used the raw frequency of sentence co-occurrences from a subset of the Vietnamese corpus in the Leipzig Corpora Collection [@VICorpus]; this corpus includes 70 million Vietnamese sentences, but our corpus data comes from a 1 million sentence subset for which co-occurrence counts are available for download.
-Vietnamese makes very frequent use of compositional morphology but the written language  uses spacing to delineate syllable boundaries rather than word boundaries.
-Accordingly, collocate searches returned instances of both target terms and many morphologically related, but distinct, words.
-We included in our counts any instances of the target term or close semantic neighbors containing the same morpheme(s) as long as they entailed a likely literal reference to the target term.
-For example, our search for collocates of the term “gà” (chicken) also returned “gà mái,” a distinct word for female chickens.
-Despite being a different word, “gà mái” both includes the morpheme for “chicken” and entails reference to a chicken.
-Accordingly, instances of both “gà” and “gà mái” were included in our collocate count for “chicken.” Some compounds do not meet this criteria, and were excluded from collocate counts.
-For example “trái cây” (tree.fruits) includes the same syllable as the word “cây” (tree), but refers to fruit that comes from trees, not the trees themselves, and was therefore excluded from our collocate counts for “tree.” -->
-
-<!-- Mandarin co-occurrence was collected using the online interface of the Chinese Lexical Association Database (Lin et al, 2019).
-Mandarin also makes frequent use of compositional morphology.
-To match the Vietnamese corpus statistics, we included in our counts any instances of the target term or close semantic neighbors containing the same morpheme(s) following the rule described above.
-These semantic neighbors were either suggested to us by the online interface (which gave search suggestions for words beginning with the target term as we typed them in) or suggested by a native speaker of Mandarin conducting the co-occurrence count data collection.
-For example, in getting the collocates of the term "門" (door), we also included "門兒" (also door, but is returned as a different word).
-Compounds that do not meet this criteria were excluded from collocate counts.
-For example "門牙" (door.tooth) refers to the front tooth even though it includes the same character as the target word "門" (door), so was therefore excluded from our collocate counts for "door".
--->
-
-<!-- #### Collocate similarity model -->
-<!-- From the raw co-occurrence counts of each triad, we calculated the thematic co-occurrence ratio as the number of thematic co-occurrences over the sum of thematic and taxonomic co-occurrences.
-We did this for both the English and Vietnamese corpus co-occurrence counts.
-In this way, we obtained predictions for 73 of 105 triads from the Vietnamese corpus and 104 of 105 triads from English.
-We therefore limited all analyses reported here to the subset of triads for which our corpus-based model can make meaningful predictions, meaning triads that have at least one non-zero collocate count (either thematic or taxonomic match).
-We replaced any remaining zero collocate counts with $\epsilon$ to account for sparsity in the corpus data.
-We then tested whether these simple relative frequency models predict US and VN responding.
--->
-
-<!-- ### Cosine distance of word vectors -->
-To give an intuition for our model, consider again the cow-grass-chicken triad: we retrieved word vectors for "cow" and "grass", and calculate the cosine distance between these vectors.
-Similarly, we retrieved vectors for "cow" and "chicken" and calculate the cosine distance between them.
-Our similarity prediction is then inversely proportional to the cosine distance of these pairs.
-This is because a larger cosine distance means the word vectors are further apart, and thus the words are less similar.
-For example, if the cosine distance of thematic cow-grass is 0.7 and the cosine distance of taxonomic cow-chicken is 0.3, then our model predicts, correspondingly, that 30% of responses to the triad will be grass, and the other 70% chicken.
-We then use a mixed-effects regression to evaluate how well each corpus model predicts participants’ similarity judgments, across triads and languages.
-
-#### Word vector retrieval
-We use the fastText pre-trained models of English, Mandarin, and Vietnamese in @Grave2018.
-These models are trained on Common Crawl and Wikipedia using We distribute pre-trained word vectors for 157 languages, trained on Common Crawl and Wikipedia using fastText.
-These models were trained using a Continuous Bag of Words (CBOW) with position-weights and a window of size 5.
-The models use character n-grams of length 5 and 10  negative examples.From the aforementioned models, we retrieve the word vectors (dimension 300) for each word we are interested in.
-
-#### Similarity model
-From the word vectors, we calculated the cosine distance between each cue-thematic match (thematic cosine distance) and cue-taxonomic match (taxonomic cosine distance), using the spatial.distance.cosine function from the SciPy package [@2020SciPy].
-We then calculated the thematic cosine distance proportion as thematic cosine distance over the sum of taxonomic cosine distance and thematic cosine distance.
-We did this for all three corpora.
-We were able to obtain predictions for all triads in all languages.
-
-# Results
-
-## 1. Do we extend previous work reporting a preference for taxonomic matching in the US and thematic matching in Asia?
-
-```{r country, warning=FALSE, cache = TRUE, include=FALSE, paged.print=TRUE}
-df.country <- df %>%
-  group_by(subject, country) %>%
-  summarize(theme_resp_percent = mean(responses_theme, na.rm = T))
-
-df.country_sum <- df.country %>%
-  group_by(country) %>%
-  summarize(mean_theme_resp_percent = mean(theme_resp_percent), 
-            sd_theme_resp_percent = sd(theme_resp_percent))
-
-fit.country = glmer(responses_theme ~ country + (1 | subject) + (country | triad), 
-                    data = df, 
-                    family = "binomial")
-summary(fit.country) 
-fit.country.anova = Anova(fit.country, type=3)
-
-fit.country_EN_VN = glmer(responses_theme ~ country + (1 | subject) + (country | triad), 
-                    data = df %>% filter(country != "China"),
-                    family = "binomial")
-summary(fit.country_EN_VN) 
-```
-The group means of proportion of thematic response in mainland China is the highest (M = `r round((df.country_sum %>% filter(country == "China"))$mean_theme_resp_percent, 2)`, SD = `r round((df.country_sum %>% filter(country == "China"))$sd_theme_resp_percent, 2)`), followed by the groups means in Vietnam (M = `r round((df.country_sum %>% filter(country == "Vietnam"))$mean_theme_resp_percent, 2)`, SD = `r round((df.country_sum %>% filter(country == "Vietnam"))$sd_theme_resp_percent, 2)`), which is slightly higher than that of the US (M = `r round((df.country_sum %>% filter(country == "US"))$mean_theme_resp_percent, 2)`, SD = `r round((df.country_sum %>% filter(country == "US"))$sd_theme_resp_percent, 2)`) (Figure 1).
-
-```{r echo=FALSE, warning=FALSE, cache = TRUE, fig.env="figure", fig.align = "center", fig.cap="Proportion of thematic responses by country."}
-
-#show violin plot
-ggplot(df.country,
-       mapping = aes(x = factor(country, levels=c("China", "US", "Vietnam")), 
-                     y = theme_resp_percent, 
-                     color = factor(country, levels=c("China", "US", "Vietnam")))) +
-  geom_violin() +
-  geom_jitter(height = 0, 
-              alpha = 0.3) +  
-  stat_summary(fun.data = "mean_cl_boot", 
-               geom = "pointrange") + 
-  labs(y = "Proportion Thematic Chosen", 
-       x = "Country") + 
-  scale_color_manual(values=c("#D63230", "#1C77C3", "#F39237")) + 
-  theme(legend.position = "none")
-```
-
-To test for cross-context differences in similarity judgments between the countries, we ran a mixed-effects logistic regression predicting triad responding (taxonomic or thematic) with country (US, China, or Vietnam) as a fixed effect.
-As random effects, we included an intercept per subject and one per triad, as well as by-triad random slopes for country to account for variation in the country effect across triads.
-In R syntax, the model is: response ~ country + (1 | subject) + (country | triad).
-
-Overall, there is a significant effect of country on proportion of thematic responses ($\chi^2$(`r fit.country.anova["country", "Df"]`) = `r round(fit.country.anova["country", "Chisq"], 2)`, p `r ifelse( fit.country.anova["country", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.country.anova["country", "Pr(>Chisq)"], 3)), "< .001")`).
-However, this effect is driven by the difference between US and China responding ($\beta$ = `r round(fixef(fit.country)["countryUS"], 2)`, p `r ifelse(as.data.frame(summary(fit.country)[["coefficients"]])["countryUS", "Pr(>|z|)"] > 0.001, paste0("= ", round(as.data.frame(summary(fit.country)[["coefficients"]])["countryUS", "Pr(>|z|)"], 3)), "< .001")`).
-There is no statistical difference between the Vietnam and China responding ($\beta$ = `r round(fixef(fit.country)["countryVietnam"], 2)`, p `r ifelse(as.data.frame(summary(fit.country)[["coefficients"]])["countryVietnam", "Pr(>|z|)"] > 0.001, paste0("= ", round(as.data.frame(summary(fit.country)[["coefficients"]])["countryVietnam", "Pr(>|z|)"], 3)), "< .001")`), and the US and Vietnam responding ($\beta$ = `r round(fixef(fit.country_EN_VN)["countryVietnam"], 2)`, p `r ifelse(as.data.frame(summary(fit.country_EN_VN)[["coefficients"]])["countryVietnam", "Pr(>|z|)"] > 0.001, paste0("= ", round(as.data.frame(summary(fit.country_EN_VN)[["coefficients"]])["countryVietnam", "Pr(>|z|)"], 3)), "< .001")`).
-
-On this analysis, we do not find support that the US-China tendencies toward taxonomic and thematic responding (respectively) extend to the US-Vietnam comparison.
-Accordingly, we cannot speak to overall biases toward thematic responding across Asian cultural contexts broadly, but we do replicate the differences documented by @Ji2004 between the US and China.
-However, in our corpus model comparison, we do find evidence for different, more fine-grained variation in similarity judgments between the US and Vietnam.
-
-## 2. Can the differences in similarity judgments between English, Mandarin and Vietnamese speakers be explained by variation in lexical statistics?
-### Is responding in each cultural context predicted by lexical statistics? 
-To test whether variation in lexical statistics can explain differences in similarity judgments between US and Vietnam participants, we compare logistic mixed-effects regression models fit to the thematic responding data from each country separately.
-We first ask how well each corpus model (English, Vietnamese, or Mandarin) predicts similarity judgments by speakers of the corresponding language (US, Vietnam, or China).
-To do this, we use a mixed-effects logistic regression to predict triad responses (0=taxonomic or 1=thematic) with corpus prediction (proportion of cosine distance) as a fixed effect and participant and triad as random effects.
-
-```{r US responding predicted by each corpus model cosine differences, warning=FALSE, include=F}
-#English
-fit.EN_US_cos = glmer(responses_theme ~ theme_cosine_prop_E + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "US"), 
-          family="binomial")
-summary(fit.EN_US_cos)
-fit.EN_US_cos.anova = Anova(fit.EN_US_cos, type = 3)
-fit.EN_US_cos.anova
-
-#Vietnamese
-fit.VI_US_cos = glmer(responses_theme ~ theme_cosine_prop_V + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "US"), 
-          family="binomial")
-summary(fit.VI_US_cos)
-fit.VI_US_cos.anova = Anova(fit.VI_US_cos, type = 3)
-fit.VI_US_cos.anova
-
-#Mandarin
-fit.ZH_US_cos = glmer(responses_theme ~ theme_cosine_prop_M + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "US"), 
-          family="binomial")
-summary(fit.ZH_US_cos)
-fit.ZH_US_cos.anova = Anova(fit.ZH_US_cos, type = 3)
-fit.ZH_US_cos.anova
-```
-
-```{r VN responding predicted by each corpus model cosine differences, warning=FALSE, include=F}
-#English
-fit.EN_VN_cos = glmer(responses_theme ~ theme_cosine_prop_E + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "Vietnam"), 
-          family="binomial")
-summary(fit.EN_VN_cos)
-fit.EN_VN_cos.anova = Anova(fit.EN_VN_cos, type = 3)
-fit.EN_VN_cos.anova
-
-#Vietnamese
-fit.VI_VN_cos = glmer(responses_theme ~ theme_cosine_prop_V + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "Vietnam"), 
-          family="binomial")
-summary(fit.VI_VN_cos)
-fit.VI_VN_cos.anova = Anova(fit.VI_VN_cos, type = 3)
-fit.VI_VN_cos.anova
-
-#Mandarin
-fit.ZH_VN_cos = glmer(responses_theme ~ theme_cosine_prop_M + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "Vietnam"), 
-          family="binomial")
-summary(fit.ZH_VN_cos)
-fit.ZH_VN_cos.anova = Anova(fit.ZH_VN_cos, type = 3)
-fit.ZH_VN_cos.anova
-```
-
-```{r CN responding predicted by each corpus model cosine differences, warning=FALSE, include=F}
-## English
-fit.EN_CN_cos = glmer(responses_theme ~ theme_cosine_prop_E + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "China"), 
-          family="binomial")
-summary(fit.EN_CN_cos)
-fit.EN_CN_cos.anova = Anova(fit.EN_CN_cos, type = 3)
-fit.EN_CN_cos.anova
-
-#Vietnamese
-fit.VI_CN_cos = glmer(responses_theme ~ theme_cosine_prop_V + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "China"), 
-          family="binomial")
-summary(fit.VI_CN_cos)
-fit.VI_CN_cos.anova = Anova(fit.VI_CN_cos, type = 3)
-fit.VI_CN_cos.anova
-
-#Mandarin
-fit.ZH_CN_cos = glmer(responses_theme ~ theme_cosine_prop_M + (1 | subject) + (1 | triad), 
-          data = df %>% filter(country == "China"), 
-          family="binomial")
-summary(fit.ZH_CN_cos)
-fit.ZH_CN_cos.anova = Anova(fit.ZH_CN_cos, type = 3)
-fit.ZH_CN_cos.anova
-```
-
-```{r calculate range of beta statistics for cosine, warning=F, include=F}
-beta.single_corpus_cos <- c(
-  round(fixef(fit.EN_US_cos)["theme_cosine_prop_E"], 2),
-  round(fixef(fit.VI_US_cos)["theme_cosine_prop_V"], 2), 
-  round(fixef(fit.ZH_US_cos)["theme_cosine_prop_M"], 2),
-
-  round(fixef(fit.EN_CN_cos)["theme_cosine_prop_E"], 2),
-  round(fixef(fit.VI_CN_cos)["theme_cosine_prop_V"], 2), 
-  round(fixef(fit.ZH_CN_cos)["theme_cosine_prop_M"], 2),
-
-  round(fixef(fit.EN_VN_cos)["theme_cosine_prop_E"], 2),
-  round(fixef(fit.VI_VN_cos)["theme_cosine_prop_V"], 2), 
-  round(fixef(fit.ZH_VN_cos)["theme_cosine_prop_M"], 2)
-)
-```
-
-We found that all corpora are significant predictors of all cultural context responding, with p<0.05 and $\beta$ from `r min(beta.single_corpus_cos)` to `r max(beta.single_corpus_cos)`.
-(For a full report, see Appendix.)
-
-### Is responding in each cultural context best predicted by the corresponding corpus's lexical statistics, as opposed to the other two corpora?
-Next, we directly compare the corpus models by including both as fixed effects in three mixed-effect regressions (predicting US, Vietnam and China responding) with the same random effects as above.
-In R syntax, the model is: response ~ corpus_English + corpus_Vietnamese + corpus_Mandarin + (1|triad) + (1|subject).
-
-```{r Eng-Vie-Mand cosine similarities predicting US-VN-CN, warning=FALSE, include=FALSE}
-df <- read.csv("../../../data/data_USCNVN_ENZHVI.csv")
-
-## English/Vietnamese/Mandarin comparison
-fit.ENVIZH_US_cos = glmer(responses_theme ~ theme_cosine_prop_E + theme_cosine_prop_V + theme_cosine_prop_M +
-                      (1 | subject) + (1 | triad), 
-                    data = df %>% filter(country == "US"), 
-                    family="binomial")
-summary(fit.ENVIZH_US_cos)
-fit.ENVIZH_US_cos.anova = Anova(fit.ENVIZH_US_cos, type = 3)
-fit.ENVIZH_US_cos.anova
-
-fit.ENVIZH_VN_cos = glmer(responses_theme ~ theme_cosine_prop_V + theme_cosine_prop_E + theme_cosine_prop_M +
-                      (1 | subject) + (1 | triad), 
-                    data = df %>% filter(country == "Vietnam"), 
-                    family="binomial")
-summary(fit.ENVIZH_VN_cos)
-fit.ENVIZH_VN_cos.anova = Anova(fit.ENVIZH_VN_cos, type = 3)
-fit.ENVIZH_VN_cos.anova
-
-fit.ENVIZH_CN_cos = glmer(responses_theme ~ theme_cosine_prop_M + theme_cosine_prop_E + theme_cosine_prop_V +
-                      (1 | subject) + (1 | triad), 
-                    data = df %>% filter(country == "China"), 
-                    family="binomial")
-summary(fit.ENVIZH_CN_cos)
-fit.ENVIZH_CN_cos.anova = Anova(fit.ENVIZH_CN_cos, type = 3)
-fit.ENVIZH_CN_cos.anova
-```
-
-For US responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are all significant predictors.
-EN corpus: $\beta$ = `r round(fixef(fit.ENVIZH_US_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.ENVIZH_US_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.ENVIZH_US_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_US_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_US_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"], 3)), "< .001")`.
-VI corpus: $\beta$ = `r round(fixef(fit.ENVIZH_US_cos)["theme_cosine_prop_V"], 2)`, $\chi^2$(`r fit.ENVIZH_US_cos.anova["theme_cosine_prop_V", "Df"]`) = `r round(fit.ENVIZH_US_cos.anova["theme_cosine_prop_V", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_US_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_US_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"], 3)), "< .001")`.
-ZH corpus: $\beta$ = `r round(fixef(fit.ENVIZH_US_cos)["theme_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ENVIZH_US_cos.anova["theme_cosine_prop_M", "Df"]`) = `r round(fit.ENVIZH_US_cos.anova["theme_cosine_prop_M", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_US_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_US_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"], 3)), "< .001")`.
-
-For Vietnam responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are all significant predictors.
-EN corpus: $\beta$ = `r round(fixef(fit.ENVIZH_VN_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.ENVIZH_VN_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_VN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"], 3)), "< .001")`.
-VI corpus: $\beta$ = `r round(fixef(fit.ENVIZH_VN_cos)["theme_cosine_prop_V"], 2)`, $\chi^2$(`r fit.ENVIZH_VN_cos.anova["theme_cosine_prop_V", "Df"]`) = `r round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_V", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_VN_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"], 3)), "< .001")`.
-ZH corpus: $\beta$ = `r round(fixef(fit.ENVIZH_VN_cos)["theme_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ENVIZH_VN_cos.anova["theme_cosine_prop_M", "Df"]`) = `r round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_M", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_VN_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"], 3)), "< .001")`.
-
-For China responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are all significant predictors.
-EN corpus: $\beta$ = `r round(fixef(fit.ENVIZH_CN_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.ENVIZH_CN_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.ENVIZH_CN_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_CN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_CN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"], 3)), "< .001")`.
-VI corpus: $\beta$ = `r round(fixef(fit.ENVIZH_CN_cos)["theme_cosine_prop_V"], 2)`, $\chi^2$(`r fit.ENVIZH_CN_cos.anova["theme_cosine_prop_V", "Df"]`) = `r round(fit.ENVIZH_CN_cos.anova["theme_cosine_prop_V", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_CN_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_CN_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"], 3)), "< .001")`.
-ZH corpus: $\beta$ = `r round(fixef(fit.ENVIZH_CN_cos)["theme_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ENVIZH_CN_cos.anova["theme_cosine_prop_M", "Df"]`) = `r round(fit.ENVIZH_CN_cos.anova["theme_cosine_prop_M", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_CN_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_CN_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"], 3)), "< .001")`.
-
-We observed some level of language specificity from this analysis.
-The English corpus is the best predictor for US responding, and the Mandarin corpus is the best predictor for China response.
-While this is not the case with the Vietnamese corpus and the Vietnam responding, the Vietnamese corpus is still a significant predictor for the Vietnam responding (Figure 2).
-
-```{r echo=FALSE, warning = FALSE}
-coeff_value_cos <- c(fixef(fit.ENVIZH_US_cos)["theme_cosine_prop_E"],
-                 fixef(fit.ENVIZH_US_cos)["theme_cosine_prop_V"], 
-                 fixef(fit.ENVIZH_US_cos)["theme_cosine_prop_M"],
-                 fixef(fit.ENVIZH_VN_cos)["theme_cosine_prop_E"],
-                 fixef(fit.ENVIZH_VN_cos)["theme_cosine_prop_V"],
-                 fixef(fit.ENVIZH_VN_cos)["theme_cosine_prop_M"], 
-                 fixef(fit.ENVIZH_CN_cos)["theme_cosine_prop_E"],
-                 fixef(fit.ENVIZH_CN_cos)["theme_cosine_prop_V"], 
-                 fixef(fit.ENVIZH_CN_cos)["theme_cosine_prop_M"])
-
-se_value_cos <- c(summary(fit.ENVIZH_US_cos)$coef["theme_cosine_prop_E", "Std. Error"], 
-              summary(fit.ENVIZH_US_cos)$coef["theme_cosine_prop_V", "Std. Error"],
-              summary(fit.ENVIZH_US_cos)$coef["theme_cosine_prop_M", "Std. Error"], 
-              summary(fit.ENVIZH_VN_cos)$coef["theme_cosine_prop_E", "Std. Error"], 
-              summary(fit.ENVIZH_VN_cos)$coef["theme_cosine_prop_V", "Std. Error"],
-              summary(fit.ENVIZH_VN_cos)$coef["theme_cosine_prop_M", "Std. Error"],
-              summary(fit.ENVIZH_CN_cos)$coef["theme_cosine_prop_E", "Std. Error"], 
-              summary(fit.ENVIZH_CN_cos)$coef["theme_cosine_prop_V", "Std. Error"],
-              summary(fit.ENVIZH_CN_cos)$coef["theme_cosine_prop_M", "Std. Error"])
-
-country_value <- c(rep("US", 3),
-                   rep("VN", 3),
-                   rep("CN", 3))
-
-corpus_value <- c(rep(c("EN", "VI", "ZH"), 3))
-
-df.USVNCN_coeffs_cos <- data.frame(country_value, corpus_value, coeff_value_cos, se_value_cos) %>%
-  mutate(corpus_value = factor(corpus_value, levels=c("ZH", "EN", "VI")))
-
-plot.coeffs_cos <- ggplot(data = df.USVNCN_coeffs_cos, 
-       mapping = aes(x = country_value, y = coeff_value_cos, fill = corpus_value)) +
-  geom_bar(position="dodge", stat="identity") +
-  geom_errorbar(aes(ymin= coeff_value_cos - se_value_cos, ymax = coeff_value_cos + se_value_cos), width=.2,
-                 position=position_dodge(.9)) +
-  scale_y_reverse() + 
-  labs(x = "Country", y = "Fixed effect size", fill = "Corpus") + 
-  scale_x_discrete(labels=c("CN" = "China", "US" = "US", "VN" = "Vietnam")) + 
-  scale_fill_manual(values=c("#D63230", "#1C77C3", "#F39237"))
-```
-
-```{r echo=FALSE, warning=FALSE, cache = TRUE, fig.env = "figure", fig.align = "center", set.cap.width=T, num.cols.cap=1, fig.cap="Fixed effect sizes of each corpus lexical statistics (cosine distance proportion) when included as a predictor for China, US, and Vietnam responding, respectively.
-The English corpus is the best predictor for US response, and the Mandarin corpus is the best predictor for China response."}
-#plot.coeffs_freq + 
-  plot.coeffs_cos
-```
-
-```{r model comparison, include=FALSE}
-fit.US_cos_compare = anova(fit.ENVIZH_US_cos, fit.EN_US_cos, type = 3)
-fit.VN_cos_compare = anova(fit.ENVIZH_VN_cos, fit.VI_VN_cos, type = 3)
-fit.CN_cos_compare = anova(fit.ENVIZH_CN_cos, fit.ZH_CN_cos, type = 3)
-```
-
-However, we found that language specificity alone does not explain our results.
-We used an ANOVA to compare the model with only the corresponding corpus, and the model with all 3 corpora for each cultural context.
-We found that in all three cases (US, China, Vietnam), adding the other two corpora produces a significantly better fit than the identical model without the additional corpora, and only the corresponding corpus included as a predictor (US response: $\chi^2$(`r fit.US_cos_compare["fit.ENVIZH_US_cos", "Df"]`) = `r round(fit.US_cos_compare["fit.ENVIZH_US_cos", "Chisq"], 2)`, p `r ifelse( fit.US_cos_compare["fit.ENVIZH_US_cos", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.US_cos_compare["fit.ENVIZH_US_cos", "Pr(>Chisq)"], 3)), "< .001")`; Vietnam response: $\chi^2$(`r fit.VN_cos_compare["fit.ENVIZH_VN_cos", "Df"]`) = `r round(fit.VN_cos_compare["fit.ENVIZH_VN_cos", "Chisq"], 2)`, p `r ifelse( fit.VN_cos_compare["fit.ENVIZH_VN_cos", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.VN_cos_compare["fit.ENVIZH_VN_cos", "Pr(>Chisq)"], 3)), "< .001")`; China response: $\chi^2$(`r fit.CN_cos_compare["fit.ENVIZH_CN_cos", "Df"]`) = `r round(fit.CN_cos_compare["fit.ENVIZH_CN_cos", "Chisq"], 2)`, p `r ifelse( fit.CN_cos_compare["fit.ENVIZH_VN_cos", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.CN_cos_compare["fit.ENVIZH_VN_cos", "Pr(>Chisq)"], 3)), "< .001")`).
-
-## 3. Does similarity reasoning differ across cultures, only the input to it, or both?
-Our analysis shows that lexical statistics of each corpus is a significant predictor for similarity judgement in the corresponding cultural context, even without the addition of the other two corpora.
-Assuming that lexical statistics is a good proxy for environmental statistics, we take the above result as evidence that cross-cultural differences in input to the process of similarity judgement at least partially drives cross-cultural similarity judgement differences.
-However, it is still an open question whether the nature of similarity judgement (for e.g., the notion of similarity) itself differs across cultures and contributes to cross-cultural differences in similarity judgement responding.
-In an alternative hypothesis, the cross-cultural differences in similarity judgement observed is driven by not only the input, but also an interaction between cultural-specific nature of similarity judgement and input.
-To test this hypothesis, we operationalize cultural-specific nature of similarity judgement as country context, and input to similarity judgement as the corresponding corpus statistics.
-We then compare a model that includes country, corresponding corpus statistics and their interaction as fixed effects (R syntax: responses ~ corresponding_corpus * country + (1|triad) + (1|subject)) to a model with only the corresponding corpus statistics as the fixed effect (R syntax: responses ~ corresponding_corpus + (1|triad) + (1|subject))
-
-```{r add corresponding language, include = F}
-df <- df %>%
-  mutate(theme_freq_prop_corr_lang = case_when(
-    country == "US" ~ theme_freq_prop_E,
-    country == "China" ~ theme_freq_prop_M, 
-    country == "Vietnam" ~ theme_freq_prop_V)) %>% 
-    mutate(theme_cosine_prop_corr_lang = case_when(
-    country == "US" ~ theme_cosine_prop_E,
-    country == "China" ~ theme_cosine_prop_M, 
-    country == "Vietnam" ~ theme_cosine_prop_V))
-```
-
-<!-- ```{r country language interaction in raw co-occurrences, include = F} -->
-<!-- fit.language = glmer(responses_theme ~ theme_freq_prop_corr_lang + (1 | subject) + (1 | triad),  -->
-<!--           data = df %>% filter(!(triad %in% triads_omit)),   -->
-<!--           family="binomial") -->
-<!-- summary(fit.language) -->
-<!-- fit.language.anova = Anova(fit.language, type = 3) -->
-<!-- fit.language.anova -->
-
-<!-- fit.country_language = glmer(responses_theme ~ theme_freq_prop_corr_lang * country + (1 | subject) + (1 | triad),  -->
-<!--           data = df %>% filter(!(triad %in% triads_omit)),   -->
-<!--           family="binomial") -->
-<!-- summary(fit.country_language) -->
-<!-- fit.country_language.anova = Anova(fit.country_language, type = 3) -->
-<!-- fit.country_language.anova -->
-
-<!-- fit.country_language_compare = anova(fit.language, fit.country_language, type = 3) -->
-<!-- fit.country_language_compare -->
-<!-- ``` -->
-
-```{r country language interaction in cosine prop, include = F}
-fit.language_cos = glmer(responses_theme ~ theme_cosine_prop_corr_lang + (1 | subject) + (1 | triad), 
-          data = df,  
-          family="binomial")
-summary(fit.language_cos)
-fit.language_cos.anova = Anova(fit.language_cos, type = 3)
-fit.language_cos.anova
-
-fit.country_language_cos= glmer(responses_theme ~ theme_cosine_prop_corr_lang * country + (1 | subject) + (1 | triad), 
-          data = df,  
-          family="binomial")
-summary(fit.country_language_cos)
-fit.country_language_cos.anova = Anova(fit.country_language_cos, type = 3)
-fit.country_language_cos.anova
-
-fit.country_language_cos_compare = anova(fit.language_cos, fit.country_language_cos, type = 3)
-fit.country_language_cos_compare
-```
-In the model containing only the corresponding corpus statistics, the corpus statistics is a significant predictor ($\beta$ = `r round(fixef(fit.language_cos)["theme_cosine_prop_corr_lang"], 2)`, $\chi^2$(`r fit.language_cos.anova["theme_cosine_prop_corr_lang", "Df"]`) = `r round(fit.language_cos.anova["theme_cosine_prop_corr_lang", "Chisq"], 2)`, p `r ifelse( fit.language_cos.anova["theme_cosine_prop_corr_lang", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.language_cos.anova["theme_cosine_prop_corr_lang", "Pr(>Chisq)"], 3)), "< .001")`).
-When adding country and interaction between country and corpus, both the corpus statistics ($\beta$ = `r round(fixef(fit.country_language_cos)["theme_cosine_prop_corr_lang"], 2)`, $\chi^2$(`r fit.country_language_cos.anova["theme_cosine_prop_corr_lang", "Df"]`) = `r round(fit.country_language_cos.anova["theme_cosine_prop_corr_lang", "Chisq"], 2)`, p `r ifelse( fit.country_language_cos.anova["theme_cosine_prop_corr_lang", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.country_language_cos.anova["theme_cosine_prop_corr_lang", "Pr(>Chisq)"], 3)), "< .001")`) and interaction between country and corpus ($\beta$ = `r round(fixef(fit.country_language_cos)["theme_cosine_prop_corr_lang:country"], 2)`, $\chi^2$(`r fit.country_language_cos.anova["theme_cosine_prop_corr_lang:country", "Df"]`) = `r round(fit.country_language_cos.anova["theme_cosine_prop_corr_lang:country", "Chisq"], 2)`, p `r ifelse( fit.country_language_cos.anova["theme_cosine_prop_corr_lang:country", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.country_language_cos.anova["theme_cosine_prop_corr_lang:country", "Pr(>Chisq)"], 3)), "< .001")`) are significant predictors.
-This suggests that there are cross-cultural differences in both input and nature of similarity judgement that drive differences in similarity judgement responding.
-
-## 4. How general are the cross-language differences in similarity judgments we observe? Are they limited to taxonomic-thematic contrasts or do they extend to other cases?
-Previous work using the triad task such as @Ji2004 has focused on contrasting taxonomic-thematic match preferences, driven by a theory of cross-cultural differences in notions of similarity.
-Meanwhile, our approach has shown that notions of similarity only has an effect on cross-cultural differences in similarity judgement when modulated by input, and that input as proxied by lexical statistics of the corresponding corpus by itself is a significant predictor for similarity judgement responding.
-Our approach using lexical statistics do not assume a taxonomic/thematic structure in the triads.
-Therefore, it should be possible to predict similarity judgements to triads that do not follow a taxonomic/thematic structure, such as our filler triads.
-If our approach is tractable, we should be able to repeat the above analyses to the filler triads, and find that lexical statistics of each corpus is a significant predictor for similarity judgements in filler triads of the corresponding cultural context.
-
-```{r incorporate base freq for fillers}
-df.filler <- read.csv("../../../data/data_filler_USCNVN_ENZHVI.csv")
-fillers_omit <- read.csv("../../../data/fillers_omit.csv") %>%
-  pull(x)
-```
-
-```{r country summary filler, warning=FALSE, cache = TRUE, include = FALSE, paged.print=TRUE}
-df.country_filler <- df.filler %>%
-  group_by(subject, country) %>%
-  summarize(word1_resp_percent = mean(responses_word1, na.rm = T))
-
-df.country_sum_filler <- df.country_filler %>%
-  group_by(country) %>%
-  summarize(mean_word1_resp_percent = mean(word1_resp_percent), 
-            sd_word1_resp_percent = sd(word1_resp_percent))
-```
-
-```{r echo=FALSE, warning=FALSE, cache = TRUE, fig.env="figure", fig.align = "center", fig.cap="Proportion of thematic responses by country."}
-#show violin plot
-ggplot(df.country_filler,
-       mapping = aes(x = factor(country, levels=c("China", "US", "Vietnam")), 
-                     y = word1_resp_percent, 
-                     color = factor(country, levels=c("China", "US", "Vietnam")))) +
-  geom_violin() +
-  geom_jitter(height = 0, 
-              alpha = 0.3) +  
-  stat_summary(fun.data = "mean_cl_boot", 
-               geom = "pointrange") + 
-  labs(y = "Proportion Word1 Chosen", 
-       x = "Country") + 
-  scale_color_manual(values=c("#D63230", "#1C77C3", "#F39237")) + 
-  theme(legend.position = "none")
-```
-
-```{r warning=FALSE, include = F, cache = TRUE, fig.env="figure", paged.print=TRUE}
-# df.country_sum <- df.country %>%
-#   group_by(country) %>%
-#   summarize(mean_theme_resp_percent = mean(theme_resp_percent), 
-#             sd_theme_resp_percent = sd(theme_resp_percent))
-
-fit.country_filler = glmer(responses_word1 ~ country + (1 | subject) + (country | cue),
-                    data = df.filler, 
-                    family = "binomial")
-summary(fit.country_filler) 
-fit.country_filler.anova = Anova(fit.country_filler, type=3)
-fit.country_filler.anova
-``` 
-For each filler triad, we randomly assigned one of the responding optiosn as 'Word1'.
-Running a mixed-effects logistic regression predict responding (Word1 or Word2) with structure equivalent to Analysis 1, we found no effect of country on filler responding (Figure 3).
-
-### Does lexical statistics for fillers predict responding in the corresponding cultural context?
-<!-- #### Raw co-occurrences -->
-<!-- ```{r US responding predicted by each corpus model raw co-occurrences for fillers, warning=FALSE,include = F} -->
-<!-- # English  -->
-<!-- fit.EN_US_filler = glmer(responses_word1 ~ word1_match_frequency_prop_E + (1 | subject) + (1 | cue),  -->
-<!--           data = df.filler %>% filter(country == "US",  -->
-<!--                                !(cue_id %in% fillers_omit)),  -->
-<!--           family="binomial") -->
-<!-- summary(fit.EN_US_filler) -->
-<!-- fit.EN_US_filler.anova = Anova(fit.EN_US_filler, type = 3) -->
-
-<!-- fit.EN_US_filler.anova -->
-<!-- ``` -->
-
-<!-- ```{r VN responding predicted by each corpus model raw co-occurrences for fillers, warning=FALSE, include = F} -->
-<!-- # Vietnamese -->
-<!-- fit.VI_VN_filler = glmer(responses_word1 ~ word1_match_frequency_prop_V + (1 | subject) + (1 | cue),  -->
-<!--           data = df.filler %>% filter(country == "Vietnam",  -->
-<!--                                !(cue_id %in% fillers_omit)),  -->
-<!--           family="binomial") -->
-<!-- summary(fit.VI_VN_filler) -->
-<!-- fit.VI_VN_filler.anova = Anova(fit.VI_VN_filler, type = 3) -->
-
-<!-- fit.VI_VN_filler.anova -->
-<!-- ``` -->
-<!-- Yes, corpus raw co-occurrences predicts responding for both US and Vietnamese. *need to discuss with Shan to incorporate Mandarin due to a lot of empty counts* -->
-
-<!-- #### Cosine distance -->
-```{r US responding predicted by each corpus model cosine distances for fillers, warning=FALSE, include = F}
-# English 
-fit.EN_US_filler_cos = glmer(responses_word1 ~ word1_match_cosine_prop_E + (1 | subject) + (1 | cue), 
-          data = df.filler %>% filter(country == "US"), 
-          family="binomial")
-summary(fit.EN_US_filler_cos)
-fit.EN_US_filler_cos.anova = Anova(fit.EN_US_filler_cos, type = 3)
-
-fit.EN_US_filler_cos.anova
-```
-
-```{r VN responding predicted by each corpus model cosine distances for fillers, warning=FALSE, include = F}
-# Vietnamese
-fit.VI_VN_filler_cos = glmer(responses_word1 ~ word1_match_cosine_prop_V + (1 | subject) + (1 | cue), 
-          data = df.filler %>% filter(country == "Vietnam"), 
-          family="binomial")
-summary(fit.VI_VN_filler_cos)
-fit.VI_VN_filler_cos.anova = Anova(fit.VI_VN_filler_cos, type = 3)
-
-fit.VI_VN_filler_cos.anova
-```
-
-```{r CN responding predicted by each corpus model cosine distances for fillers, warning=FALSE, include = F}
-# Vietnamese
-fit.ZH_CN_filler_cos = glmer(responses_word1 ~ word1_match_cosine_prop_M + (1 | subject) + (1 | cue), 
-          data = df.filler %>% filter(country == "China"), 
-          family="binomial")
-summary(fit.ZH_CN_filler_cos)
-fit.ZH_CN_filler_cos.anova = Anova(fit.ZH_CN_filler_cos, type = 3)
-
-fit.ZH_CN_filler_cos.anova
-```
-
-```{r calculate range of beta statistics for cosine fillers, warning=F, include=F}
-beta.filler_single_corpus_cos <- c(
-  round(fixef(fit.EN_US_filler_cos)["word1_match_cosine_prop_E"], 2),
-  round(fixef(fit.ZH_CN_filler_cos)["word1_match_cosine_prop_M"], 2), 
-  round(fixef(fit.VI_VN_filler_cos)["word1_match_cosine_prop_V"], 2)
-)
-```
-Using the same mixed-effects logistic regression structure as Analysis 2, we predict responses (1=word1 or 0=word2) with corpus prediction (proportion of cosine distance) as a fixed effect and participant and triad as random effects.
-We found that in all cultural contexts, the correpsonding corpora is a significant predictor of responding, with p<0.05 and $\beta$ from `r min(beta.filler_single_corpus_cos)` to `r max(beta.filler_single_corpus_cos)`.
-(For a full report, see Appendix.)
-
-# Discussion
-In this paper, we consider whether statistics of the language environment can account for cross-cultural differences in a classic similarity judgment paradigm, as an alternative to the view that members of different cultures vary in their conception of similarity.
-
-We first tested the generality of a cultural account which holds that people from Western and East Asian cultures tend to conceive of similarity in more taxonomic and thematic ways, respectively, and respond accordingly in categorization tasks such as ours.
-While we managed to replicate the previously documented contrast between English speakers in the US and Mandarin Chinese speakers from East Asia (mainland China, Taiwan, Hong Kong, and Singapore), we do not extend this contrast to our sample of Vietnamese speakers in Vietnam and English speakers in the US.
-This finding suggests some limitations on the generality of this cultural account.
-
-We did find some signatures of language specificity in our analysis, such as the large positive correlation between similarity judgments of each country and the respective corpus statistics, and how each corpus statistics are good predictors for corresponding country's similarity judgments.
-However, this is potentially due to the high correlation between corpus statistics of English, Vietnamese and Mandarin.
-We find even stronger evidence for consistency across the three groups, with substantive overlapping predictions across the corpus models, highly similar responding across the experiments, and a correspondingly high fit in cross-language comparisons between models and data.
-
-Our findings raise additional questions for future work: if not differences in taxonomic vs.
-thematic responding, then what differences drive the relativity effects previous studies have observed?
-To what extent are the relativity effects driven by language, and to what extent by culture?
-@Ji2004 established that culture-aligned differences in this paradigm exist, even when the test language is held constant, concluding that “it is culture (independent of the testing language) that led to different grouping styles” in their study.
-Our data provide a cautionary note to this conclusion, suggesting that semantic representations in bilinguals (see @Francis2005 for a review) may have the potential to provide an offline account for cross-context differences in similarity judgments, independent of test language.
-However, there are still many open questions for this account.
-How do semantic associations guide categorization?
-Can they explain taxonomic-thematic differences of the type reported by @Ji2004 and others?
-Can we provide a more specific computational account than the simple frequency model tested here?
-
-Despite these caveats, our findings here demonstrate the plausibility of an alternative perspective on cross-cultural accounts of language, thought, and similarity in the case of taxonomic and thematic reasoning: that it may be the input to similarity judgments, rather than the evaluative process or the conceptualization of similarity that produces variation in similarity reasoning across cultural and linguistic contexts.
-We hope this work provides a foundation for further research probing this question.
-
-# Appendix
 ## 1. ICC of item variability and participant variability
@@
 
-## 2. Supplemental for whether each corpus predicts similarity judgement in each cultural context
+An intraclass correlation coefficients (ICCs) analysis with a two-way, non-interactive model (following the standard taxonomy for ICCs from @McGraw1996) showed that, per cultural context, participants' judgments were variable across triads, while inter-rater agreement about specific triads was quite high (Table 1).
+This result suggests that each triad prompts taxonomic / thematic matching reliably within culture.
+
+## 2. Supplemental for whether each corpus predicts similarity judgment in each cultural context
 
 ### Triads
+
 For US responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are significant predictors of US responding (EN-US model: $\beta$ = `r round(fixef(fit.EN_US_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.EN_US_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.EN_US_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p `r ifelse( fit.EN_US_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.EN_US_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"], 3)), "< .001")`; VI-US model: $\beta$ = `r round(fixef(fit.VI_US_cos)["theme_cosine_prop_V"], 2)`, $\chi^2$(`r fit.VI_US_cos.anova["theme_cosine_prop_V", "Df"]`) = `r round(fit.VI_US_cos.anova["theme_cosine_prop_V", "Chisq"], 2)`, p `r ifelse( fit.VI_US_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.VI_US_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"], 3)), "< .001")`; ZH-US model: $\beta$ = `r round(fixef(fit.ZH_US_cos)["theme_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ZH_US_cos.anova["theme_cosine_prop_M", "Df"]`) = `r round(fit.ZH_US_cos.anova["theme_cosine_prop_M", "Chisq"], 2)`, p `r ifelse( fit.ZH_US_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ZH_US_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"], 3)), "< .001")`).
@@
 ### Fillers
+
 English (EN) is a significant predictors of US responding ($\beta$ = `r round(fixef(fit.EN_US_filler_cos)["word1_match_cosine_prop_E"], 2)`, $\chi^2$(`r fit.EN_US_filler_cos.anova["word1_match_cosine_prop_E", "Df"]`) = `r round(fit.EN_US_filler_cos.anova["word1_match_cosine_prop_E", "Chisq"], 2)`, p `r ifelse( fit.EN_US_filler_cos.anova["word1_match_cosine_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.EN_US_filler_cos.anova["word1_match_cosine_prop_E", "Pr(>Chisq)"], 3)), "< .001")`).
@@
 
-## 3. Demographic Exclusion Statistics
+## 3. Exclusion Statistics
+
 ```{r results = "asis", fig.cap="Testing"}
@@
 \newpage
-
-# Acknowledgements
-
-Place acknowledgments (including funding information) in a section at
-the end of the paper.
-
-# References
-
-```{r}
-# References will be generated automatically by Pandoc and included here.
-# The following code is some latex to format the bibliography. Do not remove it.
-```
-
-\setlength{\parindent}{-0.1in} 
-\setlength{\leftskip}{0.125in}
-\noindent
-
-\newpage

### 2023-01-31 code/4_paper/manuscript/manuscript.Rmd
manuscript edits

@@
 # Introduction
-By virtue of discrete words and grammatical features, language provides a categorical partition of our continuous experiences.
-By measuring the similarity between words (as commonly done with lexical co-occurrence models), it may be possible to model the shape of similarity space in order to capture cross-linguistic and cross-cultural variation and provide a more general answer to the question of how language influences our conception of the world.
 
-Taxonomic and thematic similarity provide a convenient entry point to broader debates about cross-linguistic and cross-cultural variation in notions of similarity.
-Taxonomic categorization is based on the similarity of attributes, for example, similar perceptual properties, like shared color or shape, among objects.
-In contrast, thematic categorization is based on causal, spatial, and temporal relationships among objects [@Markman1984].
+<!-- By virtue of discrete words and grammatical features, language provides a categorical partition of our continuous experiences. -->
+
+<!-- By measuring the similarity between words (as commonly done with lexical co-occurrence models), it may be possible to model the shape of similarity space in order to capture cross-linguistic and cross-cultural variation and provide a more general answer to the question of how language influences our conception of the world.
+-->
+
+<!-- Taxonomic and thematic similarity provide a convenient entry point to broader debates about cross-linguistic and cross-cultural variation in notions of similarity. -->
+
+<!-- Taxonomic categorization is based on the similarity of attributes, for example, similar perceptual properties, like shared color or shape, among objects. -->
+
+<!-- In contrast, thematic categorization is based on causal, spatial, and temporal relationships among objects [@Markman1984]. -->
 
 ## Cross-cultural variation in similarity
-Preferences for taxonomic and thematic similarity vary across cultures.
-@Chiu1972 found that Chinese children (9-10 years old) are more likely to choose thematic matches in a picture triad task (shown, e.g., images of an ant, a bee, and honey) than their American counterparts.
-These cross-cultural differences are also observed in novel object categorization, with Chinese participants preferring to group by family resemblance across multiple features and Americans preferring a single-feature rule [@Norenzayan2002].
-<!-- Because differences in similarity preference persist with novel stimuli (as opposed to familiar items), this suggests that participants from different cultural backgrounds use different reasoning strategies when making similarity judgments.
--->
-The authors link these differences to tendencies toward analytic processing in Western cultures, which emphasizes objects and their properties, and holistic processing in East Asian cultures, which emphasizes relationships between objects and their context (see also @Nisbett2003).
-In related work, East Asian participants show a higher level of sensitivity to context than their Western counterparts when reproducing drawings from memory [@Ji2000]; visually exploring naturalistic scenes [@Chua2005]; describing scenes [@Masuda2001]; and in explaining the causes of ambiguous behaviors [@Choi1999].
 
-@Ji2004 asked whether differences in analytic and holistic processing <!--they use that language, right?--> are driven by language, culture, or a combination of these.
-They presented Chinese and European American adults with a word triad task, and found a preference for thematic matching among Chinese participants compared to European Americans.
-They found that test language contributed to this difference, but did not fully explain it: Chinese participants showed a stronger thematic preference when tested in Mandarin, but still showed a thematic preference when tested in English.
-Ji et al.
-conclude that culture (independent of language) leads to different styles of reasoning about similarity, whereas language serves as a “tuning” mechanism operating within a culturally-specific style, by activating representations corresponding to the language being used.^[But note that this work did not include a manipulation to prevent participants from engaging in e.g., covert naming in a language other than the test language.]
+The way we partition our continuous experiences of the world into categories, and which kind of similarity relationships we privilege to organize such partitions, vary across cultures.
+One way this cross-cultural difference has been observed is with a task comparing preference for taxonomic and thematic similarity between East Asian and Western participants.[^1]
+@Ji2004 found that in a word triad task (choose two out of three words that are more related to one another), Chinese participants preferred thematic matching more compared to European Americans.
+In a pictorial version of this task, @Chiu1972 found that Chinese children (9-10 years old) are also more likely to choose thematic matches compared to their American counterparts.
+This cross-cultural difference is also observed in novel object categorization, with Chinese participants preferring to group by family resemblance across multiple features and Americans preferring a single-feature rule [@Norenzayan2002].
 
-This view ascribes cross-cultural differences in similarity judgment to variation in the conceptualization of similarity itself.
-Alternatively, these judgments could be shaped by cross-cultural differences in the statistics of the environment, and accordingly the content of everyday experiences.
-Perhaps when confronted with the triad task, participants from all cultures follow the same process for reasoning about similarity, but rely on language or culture-specific inputs to this process.
-<!--For example, it may be that Vietnamese participants are more likely to have knowledge of farming practices than Americans, and may associate cows and grass more strongly (as grass is the typical feed for cows in the small-scale family farming contexts common in Vietnam).
-Americans, on the other hand, may have strong associations between cows and chickens as a result of encountering them together in children’s books or petting zoo contexts.--> If we observe a difference in categorization between East Asian and Western participants, it could be that members of both groups use the same procedure (considering similarity that is influenced by both taxonomic and thematic relations), but the inputs to this procedure differ between cultures, with East Asian participants exposed to more instances of thematic similarity than their Western counterparts.
+[^1]: Taxonomic categorization is based on the similarity of attributes, for example, similar perceptual properties, like shared color or shape, among objects.In contrast, thematic categorization is based on causal, spatial, and temporal relationships among objects [@Markman1984].
+
+Previous research has linked the observed difference in similarity judgment to related work showing tendencies toward analytic processing (emphasizing objects and their properties) in Western cultures and holistic processing in East Asian cultures (emphasizing relationships between objects and their context) (see also @Nisbett2003).
+Cross-cultural difference in similarity judgment is thus connected to well-documented work showing East Asian participants exhibiting a higher level of sensitivity to context than their Western counterparts when reproducing drawings from memory [@Ji2000]; visually exploring naturalistic scenes [@Chua2005]; describing scenes [@Masuda2001]; and in explaining the causes of ambiguous behaviors [@Choi1999].
+This view ascribes cross-cultural differences in similarity judgment to variation in how each culture (or group of culture, i.e.
+East Asian vs Western) **conceptualize** similarity -- with East Asians preferring thematic relations more than Westerners.
+
+Alternatively, these judgments could be shaped by cross-cultural differences in the **inputs** to similarity judgment, namely, the statistics of the environment, and accordingly the content of everyday experiences.
+Perhaps when faced with the triad task, participants from all cultures follow the same process for conceptualizing similarity, but rely on language or culture-specific inputs to this process.
+If we observe a difference in categorization between East Asian and Western participants, it could be that members of both groups use the same procedure (considering similarity that is influenced by both taxonomic and thematic relations), but the inputs to this procedure differ between cultures, with East Asian participants exposed to more instances of thematic similarity than their Western counterparts.
+We might also expect that both conceptualization and inputs of similarity play a role in driving cross-cultural differences -- East Asian participants may both be exposed to more instances of thematic similarity, and prefer to conceptualize similarity as thematic relations more so than Westerners.
 
 ## Estimating variation in experience
-While co-occurrences in experience are difficult to measure, co-occurrence in language can provide a rough proxy--and indeed, language may afford many of the “experiences” that people have with infrequently encountered items, like cows or helicopters.
-In this study, we use co-occurrence in language as a proxy of cultural experience.
-This is a generalizing assumption, and while no linguistic corpus can be expected to fully capture a culture, using this proxy as a model of culture provides a conservative test of the hypothesis that differences in the input, rather than the process, of reasoning produces cultural variation in this task.
-This means that if such a model does work -- if linguistic co-occurrence can predict cultural variation in this similarity task without building differences in the decision process into the model -- it is relatively strong evidence that language alone (perhaps as a more easily observed source of information on broader cultural and ecological variation) may account for these cross-cultural differences in reasoning.
 
-Indeed, previous work suggests that using lexical co-occurrence as a proxy can be useful in thinking about similarity reasoning.
-Natural language processing tasks have found that lexical co-occurrence is a good predictor for performance in similarity judgment.
-@Griffiths2007 showed that a model that takes word-document co-occurrence as input can be used to predict word association and the effects of semantic association on a variety of linguistic tasks.
-Additionally, lexical semantic models that are constructed using lexical co-occurrence (as opposed to annotated relations) have been shown to perform well on predicting human judgments about similarity between word pairs that are thematically or taxonomically related [@Rohde2006].
+To test alternative hypotheses involving variation of inputs to similarity judgment, we need a way to operationalize variation in exposure to thematic vs taxonomic relations.
+While this metric is difficult to directly measure, language statistics can provide a rough proxy.
+Language statistics is useful in that it is part of the inputs to everyday experiences (through spoken and written language), may afford many of the 'experiences' that people have with infrequently encountered items, like cows or helicopters, and provides accessible measures.
+Previous work also suggests that using language statistics (such as lexical co-occurrence or cosine distance of word embeddings) as a proxy can be a good predictor for similarity reasoning.
+@Griffiths2007 showed that a model trained on word-document co-occurrence can predict word association and the effects of semantic association on a variety of linguistic tasks.
+Lexical semantic models that are constructed using lexical co-occurrence (in comparison to annotated relations) have been shown to perform well on predicting human judgments about similarity between word pairs that are thematically or taxonomically related [@Rohde2006].
+Word embeddings like fastText have been demonstrated to be good predictors for similarity judgments (@Liu2019, @Jatnika2019).
 
-Our study uses cosine distances of fastText word vectors as a measure of lexical co-occurrence^[We also carried out our analysis using raw lexical co-occurrences and obtained similar results.].
+Our study uses cosine distances of fastText word vectors as a measure of lexical co-occurrence[^2].
 fastText is a system that uses lexical co-occurrence information to generate a vector representing each word in its lexicon [@Mikolov2018].
-
-<!-- MOVE TO METHODS?
-fastText uses a continuous bag-of-words model, which takes into account a symmetric window of words surrounding the word in question and maximizes the log-likelihood of the probability of the word given its context.
-Calculating the cosine-similarity between word vectors from fastText gives us a score of how similar the contexts of these words are.
-Therefore, words that occur in the same context (high lexical co-occurrence) would have a larger cosine-similarity score.
-
-It must be noted that fastText supplements the lexical co-occurrence information by simultaneously training weight vectors for each position relative to the word in question, as well as adding sub-word information (bag-of-character n-gram vectors for each character forming the words).
-The similarity judgment prediction given by fastText may be more higher than a model using purely lexical co-occurrence information.
-However, models that use only lexical co-occurrence information (with or without a simple position weight system that gives more weight to words that are closer to the word in question) also perform well in similarity prediction tasks.
-For this study, due to the lack of large cleaned corpora for Mandarin and Vietnamese, we leverage fastText pre-trained models on the languages we are interested in @Grave2018.-->
-
-<!-- condense to 2 sentences --> Word embeddings like fastText have been demonstrated to be good predictors for similarity judgments (@Liu2019, @Jatnika2019).
 fastText has also been shown to be sensitive towards cultural effects on word meanings: @Thompson2020 showed that the distribution of semantic meaning clusters generated by fastText trained on language-specific corpora correlates to the cultural, historical and geographical distances of such languages languages.
 This is a proof of concept for our use of fastText in different languages with varying levels of relatedness.
-<!-- @Liu2019 showed that fastText performed well as the data for a system matching responses in a knowledge base by how similar they are to a customer’s query.
-A study by @Jatnika2019 tested a word2vec model trained on the English wikipedia corpus against 353 word pairs labeled with similarity values based on human judgment.
-The word2vec model correlates moderately with human judgment.
--->
-<!-- @Thompson2020 applied fastText to language-specific Wikipedia corpus (among others) to generate a “semantic neighborhood” of 1010 meanings in different languages.
-The study showed that languages that are spoken by more similar cultures, more geographically proximate and/or historically related had more semantic neighborhoods that aligned.
--->
+
+[^2]: We also carried out our analysis using raw lexical co-occurrences and obtained similar results.
+
+We note that language statistics can incorporate both cultural-specific environmental statistics (the inputs of similarity judgment) and taxonomic/thematic preferences (the conceptualization of similarity).
+For example, cultural features (farming) can lead to differences in environmental statistics (seeing cows and grass) and in turn these can influence language (talking more about cows and grass).
+But cultural features (preferring thematic relations) could also more directly cause individuals to talk differently about the same experiences (mentioning what cows eat rather than what other animals cows are like).
+Therefore, our approach looks at the extent to which language statistics can predict cross-cultural differences in similarity judgment with the understanding that language statistics is a proxy for both inputs and conceptualization of similarity judgment[^3].
+
+[^3]: However, in Q3, we investigate whether differing culture-based conceptualization of similarity has unique contribution to cross-cultural variation of similarity jdugment.
 
 ## The present study
+
 <!-- @Ji2004 observed a difference in similarity judgment between Chinese and European Americans (the former preferred thematic matching the latter taxonomic).
@@
 <!-- Additionally, outside of language, cross-cultural differences could come from a couple different mechanisms:  -->
-@Ji2004 suggest that the notion of similarity is what varies across cultural groups, but it is possible that similarity is regarded in the same way and it is actually the input to this similarity judgment that varies across cultural contexts.
-It may be possible to gain traction on potential mechanisms by examining whether variation in similarity judgments co-vary with environmental statistics that differ across cultural and linguistic contexts.
 
-In this study, we ask whether variation in lexical co-occurrence can account for the cross-context (culture and language) differences observed in how people evaluate similarity.
-First, we attempt to replicate @Ji2004 by running a study comparing English speakers in the US and Mandarin speakers in mainland China.
-Second, we evaluate whether the differences observed between English and Mandarin speakers’ similarity judgments also extend to comparisons between English and Vietnamese, by running a similar study between English speakers in the US and Vietnamese speakers in Vietnam.
+```{=html}
+<!--@Ji2004 suggest that the notion of similarity is what varies across cultural groups, but it is possible that similarity is regarded in the same way and it is actually the input to this similarity judgment that varies across cultural contexts.
+It may be possible to gain traction on potential mechanisms by examining whether variation in similarity judgments co-vary with environmental statistics that differ across cultural and linguistic contexts.--
+```
+Our study tests the hypothesis that, rather than (or in addition to) the variation in conceptualization of similarity across cultural groups, variation in the input to similarity judgment (namely, environmental statistics as proxied by language statistics) can be used to predict cross-cultural differences observed in how people evaluate similarity.
+We note that our study is correlational and cannot make a causal claim about the relationship of environmental statistics to similarity judgment, but it may be possible to gain traction on potential mechanisms by examining whether variation in similarity judgments covary with environmental statistics that differ across cultural and linguistic contexts.
+Our specific research questions are as follows:
+
+Q1: Do we replicate @Ji2004 and extend the results to another East Asian culture, namely Vietnam?
 Vietnam is a Southeast Asian country that borders China and is historically greatly influenced by Chinese culture [@Hui2002].
@@
 
-We then ask to what extent similarity judgments show cross-context differences that align with co-occurrence patterns in participants’ languages.
-We would only see a main effect of cultural context if differing notions of similarity drive these cross-cultural differences.
-Meanwhile, if we do see variation in responding trial-to-trial that tracks with lexical co-occurrence statistics (as a rough proxy combining both linguistic and cultural context), this suggests that cross-cultural notions of similarity might be similar, and it is environmental statistics that guide the differences in similarity judgments.
+Q2: To what extent do cross-context environmental statistics (as proxied by language) align with variation in similarity judgment?
 
-To preview our results, we find that, while we do not find the predicted Eastern/Western contrast in notions of similarity in our Vietnam extension, we do find language-specific co-occurrence can indeed explain cross-context differences in similarity judgments.
-In contrast to previous accounts, by which culture induces differing conceptions of similarity (varying between taxonomic and thematic), these findings provide an alternative, and more specific, account by which language may explain these cross-cultural differences without invoking variation in notions of similarity.
+Q3: Is there evidence for a unique contribution from conceptualization of similarity?
 
-There are several important limitations of our approach.
-While we discuss cross-cultural variability at the level of countries or larger world areas, these are not cultural monoliths.
-For convenience, we operationalize culture at the level of country, based on where participants were raised.
-It is an open question whether performance in our participant populations (of relatively young and well-educated adults) is representative of the broader country.
-This is especially true for societies with substantial ethnic and cultural variation such as the US.
-We expect that our data is likely to underestimate variation both within and between the countries we sample from.
+Q4: Is language statistics viable as a standalone predictor, or is it simply measuring conceptualization of similarity in a different way?
 
-Language, culture, cognition, and individual experiences are intertwined in complex causal relationships: cultural features (farming) can lead to differences in individuals’ experiences (seeing cows and grass) and in turn these can influence language (talking more about cows and grass).
-But cultural features (a thematic orientation) could also more directly cause individuals to talk differently about the same experiences (mentioning what cows eat rather than what other animals cows are like).
-In this study, we measure language and its relation to cross-cultural differences in categorization, but these relations test only the plausibility of a language-based account; they cannot establish the direction of causality.
+To preview our results, we find that, while we do not find the predicted Eastern/Western contrast in conceptualization of similarity in our Vietnam extension, we do find that both language-specific statistics and cultural contexts are a good predictor for cross-cultural differences in similarity judgments.
+Language statistics are also a good predictor for filler items with no taxonomic/thematic structure.
+Our findings are in contrast to previous accounts, by which culture induces differing conceptions of similarity (varying between taxonomic and thematic).
+these findings provide an alternative, and more specific, account by which language may explain these cross-cultural differences without invoking variation in notions of similarity.
 
 # Methods
+
 ```{r get responding and demographic data, include = F}
@@
 ## Participants
+
 We recruited `r df.excl_US$ppts_finished` participants from the US, `r df.excl_VN$ppts_finished` participants from Vietnam, and `r df.excl_CN$ppts_finished` participants from mainland China.
 US participants were recruited through snowball sampling seeded with Stanford student email lists, Vietnam participants were recruited through snowball sampling seeded with Vietnam-based student groups on Facebook, and mainland China participants were recruited through snowball sampling seeded with group chats on WeChat.
-US participants were compensated with $5 gift certificates (USD), VN participants received 50,000₫ (VND) in phone credit, and mainland China participants received 25CNY through WeChat credit transfer.
+US participants were compensated with \$5 gift certificates (USD), VN participants received 50,000₫ (VND) in phone credit, and mainland China participants received 25CNY through WeChat credit transfer.
 
-We excluded `r df.excl_US$ppts_finished - df.excl_US$ppts_after_att_check_excl` US participants, `r df.excl_VN$ppts_finished - df.excl_VN$ppts_after_att_check_excl` Vietnam participants, and `r df.excl_CN$ppts_finished - df.excl_CN$ppts_after_att_check_excl` China participants who did not answer 2 or more attention checks correctly.
+We excluded `r df.excl_US$ppts_finished - df.excl_US$ppts_after_att_check_excl` US participants, `r df.excl_VN$ppts_finished - df.excl_VN$ppts_after_att_check_excl` Vietnam participants, and `r df.excl_CN$ppts_finished - df.excl_CN$ppts_after_att_check_excl` China participants who missed 2 or more attention checks.
 We followed 4 exclusion criteria that aim to retain only participants who are influenced by one culture: (1) non-native speakers of English and Vietnamese, respectively, (2) fluent in at least one of the other two study languages (Vietnamese for US participants, English for Vietnamese participants and Chinese participants), (3) have lived outside of the test country (US, Vietnam, or China) for more than two years, and (4) have significant international experience (more than 6 international experiences of 2 days or longer.) We did not use a particular criterion for a language if it would exclude 25% or more of any one sample.
@@
 The Vietnam sample included `r df.excl_VN$ppts_after_demog_excl` participants (`r df.gender_V %>% filter(gender == "Nam") %>% pull(n)`M, `r df.gender_V %>% filter(gender == "Nữ") %>% pull(n)`F, `r df.gender_V %>% filter(gender == "Từ chối trả lời") %>% pull(n)` other), with mean age = `r round(df.age_V$mean_age, 2)` (SD = `r round(df.age_V$sd_age, 2)`) and median age = `r df.age_V$median_age`.
-The China sample included `r df.excl_CN$ppts_after_demog_excl` participants (`r df.gender_M %>% filter(gender == "男性") %>% pull(n)`M, `r df.gender_M %>% filter(gender == "女性") %>% pull(n)`F, `r df.gender_M %>% filter(gender == "拒绝回答") %>% pull(n)` other), with mean age = `r round(df.age_M$mean_age, 2)` (SD = `r round(df.age_M$sd_age, 2)`) and median age = `r df.age_M$median_age`.^[A table summarizing number of participants lost at each round of exclusions is included in the Appendix.]
+The China sample included `r df.excl_CN$ppts_after_demog_excl` participants (`r df.gender_M %>% filter(gender == "男性") %>% pull(n)`M, `r df.gender_M %>% filter(gender == "女性") %>% pull(n)`F, `r df.gender_M %>% filter(gender == "拒绝回答") %>% pull(n)` other), with mean age = `r round(df.age_M$mean_age, 2)` (SD = `r round(df.age_M$sd_age, 2)`) and median age = `r df.age_M$median_age`.[^4]
 
-Notably, we lost a majority of our Vietnam participants (more than 60%) in the attention check exclusion.
-One reason we suspect why this might have happened is because our Vietnam participants are less familiar with research surveys and attention check questions, and thus might have thought too much about the attention check questions.^[We carried out an exploratory analysis where we used a less stringent attention check exclusion, and did not find any difference in significant results when compared with the main analysis (see Appendix).]
+[^4]: A table summarizing number of participants lost at each round of exclusions is included in the Supplementary Information.
 
-## Stimuli
+We preregistered a more stringent exclusion criterion where participants were excluded if they missed any attention checks.
+However, this led to a small sample size, especially for Vietnam context (US = 109, China = 132, Vietnam = 57).
+Our reported results with the less stringent exclusion criterion (detailed above) is largely not different from the results with the preregistered criterion.
+Any differences are noted in the Analysis section.
+
+## Stimuli Materials
+
 We adapted stimuli from previous studies to create a set of test triads consisting of a cue, with one thematic and one taxonomic match option.
-For example, “cow,” “grass,” and “chicken,” where “cow” is the cue, “grass” is the thematic match, and “chicken” the taxonomic match.
+For example, "cow," "grass," and "chicken," where "cow" is the cue, "grass" is the thematic match, and "chicken" the taxonomic match.
 We included 105 such triads, a superset including triads pulled from supplemental information and in-text examples across the literature, and others that we adapted or created <!--(see SI for the full list of stimuli and sources)-->.
@@
 The translations were then checked for accuracy after backtranslation to English by another fluent bilingual in each language who was naive to the original English versions.
--->
+All materials are included in the Supplementary Information.
 
-Each participant completed all 105 triads in sets of 21 trials at a time (10 test triads, 10 filler triads, and 1 attention check per page), by selecting the match most related to the cue (“Which thing is most closely related to the bolded item?” or "Thứ nào liên quan nhất với thứ được in đậm?").
+## Procedure
+
+Each participant completed all 105 triads in sets of 21 trials at a time (10 test triads, 10 filler triads, and 1 attention check per page), by selecting the match most related to the cue ("Which thing is most closely related to the bolded item?" and translated equivalents).
 The test triads were presented with 105 filler triads mixed in, to obscure the taxonomic-thematic two-answer forced choice structure of the test stimuli and reduce the likelihood that participants would become aware of the design.
 The filler triads were groups of three semantically related words, but where the match options were not distinguished by thematic vs.
-taxonomic similarity, e.g., cue “bird” with match options “lizard” and “toad.” Additionally, we included 10 attention check trials, which were formatted like the test and filler triads but included an instruction instead of a cue item, e.g., “Choose wife” with match options “wife” and “husband.” In total, each participant completed 210 similarity judgments and 10 attention check questions, with triads presented in randomized orders that varied between subjects.
+taxonomic similarity, e.g., cue "bird" with match options "lizard" and "toad." Additionally, we included 10 attention check trials, which were formatted like the test and filler triads but included an instruction instead of a cue item, e.g., "Choose wife" with match options "wife" and "husband." In total, each participant completed 210 similarity judgments and 10 attention check questions, with triads presented in randomized orders that varied between subjects.
 
 ## Corpus model
+
 <!-- Our general approach is to build a model of similarity that is based on collocation counts in each language.  -->
@@
 <!-- ### Raw lexical co-occurrences -->
+
 <!-- To give an intuition for our model, consider the cow-grass-chicken triad: we counted how many times “cow” and “grass” co-occur within a window of text in each corpus, and compare this to how many times “cow” and “chicken” co-occur.
@@
 <!-- #### Collocate retrieval and coding -->
+
 <!-- For our English co-occurrence metric, we used the online interface of the Corpus of Contemporary American English [@COCA] to retrieve collocation counts.
@@
 <!-- #### Collocate similarity model -->
+
 <!-- From the raw co-occurrence counts of each triad, we calculated the thematic co-occurrence ratio as the number of thematic co-occurrences over the sum of thematic and taxonomic co-occurrences.
@@
 <!-- ### Cosine distance of word vectors -->
-To give an intuition for our model, consider again the cow-grass-chicken triad: we retrieved word vectors for "cow" and "grass", and calculate the cosine distance between these vectors.
-Similarly, we retrieved vectors for "cow" and "chicken" and calculate the cosine distance between them.
-Our similarity prediction is then inversely proportional to the cosine distance of these pairs.
-This is because a larger cosine distance means the word vectors are further apart, and thus the words are less similar.
-For example, if the cosine distance of thematic cow-grass is 0.7 and the cosine distance of taxonomic cow-chicken is 0.3, then our model predicts, correspondingly, that 30% of responses to the triad will be grass, and the other 70% chicken.
-We then use a mixed-effects regression to evaluate how well each corpus model predicts participants’ similarity judgments, across triads and languages.
+
+Our general approach is to predict behavioral preferences in similarity judgment using relative similarity between word embeddings.
 
 #### Word vector retrieval
+
 We use the fastText pre-trained models of English, Mandarin, and Vietnamese in @Grave2018.
@@
 These models were trained using a Continuous Bag of Words (CBOW) with position-weights and a window of size 5.
-The models use character n-grams of length 5 and 10  negative examples.From the aforementioned models, we retrieve the word vectors (dimension 300) for each word we are interested in.
+The models use character n-grams of length 5 and 10 negative examples.
+From the aforementioned models, we retrieve the word vectors (dimension 300) for each word we are interested in.
 
 #### Similarity model
-From the word vectors, we calculated the cosine distance between each cue-thematic match (thematic cosine distance) and cue-taxonomic match (taxonomic cosine distance), using the spatial.distance.cosine function from the SciPy package [@2020SciPy].
+
+To give an intuition for our model, consider again the cow-grass-chicken triad: we retrieved word vectors for "cow" and "grass", and calculate the cosine distance between these vectors.
+Similarly, we retrieved vectors for "cow" and "chicken" and calculate the cosine distance between them.
+Our similarity prediction is then inversely proportional to the ratio of cosine distance of these pairs.
+This is because a larger cosine distance means the word vectors are further apart, and thus the words are less similar.
+For example, if the cosine distance of thematic cow-grass is 0.7 and the cosine distance of taxonomic cow-chicken is 0.3, then our model predicts, correspondingly, that 30% of responses to the triad will be grass, and the other 70% chicken.
+
+In practice, we calculated the cosine distance between each cue-thematic match (thematic cosine distance) and cue-taxonomic match (taxonomic cosine distance), using the spatial.distance.cosine function from the SciPy package [@2020SciPy].
 We then calculated the thematic cosine distance proportion as thematic cosine distance over the sum of taxonomic cosine distance and thematic cosine distance.
@@
 We were able to obtain predictions for all triads in all languages.
+We then use a mixed-effects regression to evaluate how well each corpus model predicts participants' similarity judgments, across triads and cultural contexts.
 
@@
 
-## 1. Do we extend previous work reporting a preference for taxonomic matching in the US and thematic matching in Asia?
+## 1. Replication of previous work and extension to a Vietnamese sample
 
@@
 ```
+
+Following previous work, we would expect participants from mainland China to prefer thematic matches more than US participants (to use the cow-grass-chicken triad: we would expect participants from mainland China to prefer the cow-grass match over the cow-chicken match to a larger extent compared to US participants).
+We would also expect that participants from Vietnam would pattern with China, and also show a significantly higher preference for thematic matches compare to US participants.
+
 The group means of proportion of thematic response in mainland China is the highest (M = `r round((df.country_sum %>% filter(country == "China"))$mean_theme_resp_percent, 2)`, SD = `r round((df.country_sum %>% filter(country == "China"))$sd_theme_resp_percent, 2)`), followed by the groups means in Vietnam (M = `r round((df.country_sum %>% filter(country == "Vietnam"))$mean_theme_resp_percent, 2)`, SD = `r round((df.country_sum %>% filter(country == "Vietnam"))$sd_theme_resp_percent, 2)`), which is slightly higher than that of the US (M = `r round((df.country_sum %>% filter(country == "US"))$mean_theme_resp_percent, 2)`, SD = `r round((df.country_sum %>% filter(country == "US"))$sd_theme_resp_percent, 2)`) (Figure 1).
@@
 As random effects, we included an intercept per subject and one per triad, as well as by-triad random slopes for country to account for variation in the country effect across triads.
-In R syntax, the model is: response ~ country + (1 | subject) + (country | triad).
 
@@
 
-## 2. Can the differences in similarity judgments between English, Mandarin and Vietnamese speakers be explained by variation in lexical statistics?
-### Is responding in each cultural context predicted by lexical statistics? 
-To test whether variation in lexical statistics can explain differences in similarity judgments between US and Vietnam participants, we compare logistic mixed-effects regression models fit to the thematic responding data from each country separately.
+## 2. Language statistics as a predictor for cross-cultural variation in similarity judgments
+
+### Single corpus model
+
+To test whether variation in language statistics can explain differences in similarity judgments between US and Vietnam participants, we compare logistic mixed-effects regression models fit to the thematic responding data from each country separately.
 We first ask how well each corpus model (English, Vietnamese, or Mandarin) predicts similarity judgments by speakers of the corresponding language (US, Vietnam, or China).
 To do this, we use a mixed-effects logistic regression to predict triad responses (0=taxonomic or 1=thematic) with corpus prediction (proportion of cosine distance) as a fixed effect and participant and triad as random effects.
+If environmental statistics (as proxied by language statistics) contribute to the differences in similarity judgments, we would expect each language corpus to be a good predictor for similarity judgment responding in its corresponding context.
 
@@
 
-We found that all corpora are significant predictors of all cultural context responding, with p < 0.05 and $\beta$ from `r min(beta.single_corpus_cos)` to `r max(beta.single_corpus_cos)`.
-(For a full report, see Appendix.)
+We found that all corpora are significant predictors of all cultural context responding, with p \< 0.05 and $\beta$ from `r min(beta.single_corpus_cos)` to `r max(beta.single_corpus_cos)`.
+(For a full report, see Supplementary Information.)
 
-### Is responding in each cultural context best predicted by the corresponding corpus's lexical statistics, as opposed to the other two corpora?
-Next, we directly compare the corpus models by including both as fixed effects in three mixed-effect regressions (predicting US, Vietnam and China responding) with the same random effects as above.
-In R syntax, the model is: response ~ corpus_English + corpus_Vietnamese + corpus_Mandarin + (1|triad) + (1|subject).
+While each corpus is a good predictor for its corresponding context, the fact that all corpora covary with all cultural contexts suggests that language is such a rich proxy of human experience that even using the wrong proxy (e.g.
+Mandarin for US responding) is informative.
+A single corpus model might therefore not be informative in culture-specific ways, but might only reflect consistency in experiences across cultures.
+
+### Multiple corpora model
+
+If language statistics is able to predict meaningful culture-specific variation in similarity judgment (rather than just consistency across cultures), we would expect each corpus to be the best predictor of its corresponding culture compared to the other two corpora.
+We directly compare the corpus models by including both as fixed effects in three mixed-effect regressions (predicting US, Vietnam and China responding) with the same random effects as above.
 
@@
 
-For US responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are all significant predictors.
+For US responding: only the English (EN) corpus is a significant predictor[^5].
 EN corpus: $\beta$ = `r round(fixef(fit.ENVIZH_US_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.ENVIZH_US_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.ENVIZH_US_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_US_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_US_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"], 3)), "< .001")`.
@@
 
-For Vietnam responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are all significant predictors.
+[^5]: With preregistered exclusion criterion: only the English (EN) and Mandarin (ZH) corpus are significant predictors.
+
+For Vietnam responding: only the Vietnamese (VI) and Mandarin (ZH) corpus are significant predictors[^6].
 EN corpus: $\beta$ = `r round(fixef(fit.ENVIZH_VN_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.ENVIZH_VN_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_VN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"], 3)), "< .001")`.
@@
 
-For China responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are all significant predictors.
+[^6]: With preregistered exclusion criterion: all three corpora are significant predictors.
+
+For China responding: only the Mandarin (ZH) and English (EN) corpus are significant predictors.
 EN corpus: $\beta$ = `r round(fixef(fit.ENVIZH_CN_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.ENVIZH_CN_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.ENVIZH_CN_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_CN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_CN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"], 3)), "< .001")`.
@@
 While this is not the case with the Vietnamese corpus and the Vietnam responding, the Vietnamese corpus is still a significant predictor for the Vietnam responding (Figure 2).
+These results strengthens our hypothesis that variation in inputs to similarity judgment (as proxied by language statistics) can predict cross-cultural variations of similarity judgment.
 
@@
 
-However, we found that language specificity alone does not explain our results.
-We used an ANOVA to compare the model with only the corresponding corpus, and the model with all 3 corpora for each cultural context.
-We found that in all three cases (US, China, Vietnam), adding the other two corpora produces a significantly better fit than the identical model without the additional corpora, and only the corresponding corpus included as a predictor (US response: $\chi^2$(`r fit.US_cos_compare["fit.ENVIZH_US_cos", "Df"]`) = `r round(fit.US_cos_compare["fit.ENVIZH_US_cos", "Chisq"], 2)`, p `r ifelse( fit.US_cos_compare["fit.ENVIZH_US_cos", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.US_cos_compare["fit.ENVIZH_US_cos", "Pr(>Chisq)"], 3)), "< .001")`; Vietnam response: $\chi^2$(`r fit.VN_cos_compare["fit.ENVIZH_VN_cos", "Df"]`) = `r round(fit.VN_cos_compare["fit.ENVIZH_VN_cos", "Chisq"], 2)`, p `r ifelse( fit.VN_cos_compare["fit.ENVIZH_VN_cos", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.VN_cos_compare["fit.ENVIZH_VN_cos", "Pr(>Chisq)"], 3)), "< .001")`; China response: $\chi^2$(`r fit.CN_cos_compare["fit.ENVIZH_CN_cos", "Df"]`) = `r round(fit.CN_cos_compare["fit.ENVIZH_CN_cos", "Chisq"], 2)`, p `r ifelse( fit.CN_cos_compare["fit.ENVIZH_CN_cos", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.CN_cos_compare["fit.ENVIZH_CN_cos", "Pr(>Chisq)"], 3)), "< .001")`).
+However, in all cultural contexts, adding the other two corpora produces a significantly better fit than the identical model without the additional corpora, and only the corresponding corpus included as a predictor (US response: $\chi^2$(`r fit.US_cos_compare["fit.ENVIZH_US_cos", "Df"]`) = `r round(fit.US_cos_compare["fit.ENVIZH_US_cos", "Chisq"], 2)`, p `r ifelse( fit.US_cos_compare["fit.ENVIZH_US_cos", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.US_cos_compare["fit.ENVIZH_US_cos", "Pr(>Chisq)"], 3)), "< .001")`; Vietnam response: $\chi^2$(`r fit.VN_cos_compare["fit.ENVIZH_VN_cos", "Df"]`) = `r round(fit.VN_cos_compare["fit.ENVIZH_VN_cos", "Chisq"], 2)`, p `r ifelse( fit.VN_cos_compare["fit.ENVIZH_VN_cos", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.VN_cos_compare["fit.ENVIZH_VN_cos", "Pr(>Chisq)"], 3)), "< .001")`; China response: $\chi^2$(`r fit.CN_cos_compare["fit.ENVIZH_CN_cos", "Df"]`) = `r round(fit.CN_cos_compare["fit.ENVIZH_CN_cos", "Chisq"], 2)`, p `r ifelse( fit.CN_cos_compare["fit.ENVIZH_CN_cos", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.CN_cos_compare["fit.ENVIZH_CN_cos", "Pr(>Chisq)"], 3)), "< .001")`).
+This analysis suggests that culture-specific inputs to similarity judgment (as proxied by language statistics) do not fully explain cross-cultural differences in similarity judgment.
 
-## 3. Does similarity reasoning differ across cultures, only the input to it, or both?
-Our analysis shows that lexical statistics of each corpus is a significant predictor for similarity judgment in the corresponding cultural context, even without the addition of the other two corpora.
-Assuming that lexical statistics is a good proxy for environmental statistics, we take the above result as evidence that cross-cultural differences in input to the process of similarity judgment at least partially drives cross-cultural similarity judgment differences.
-However, it is still an open question whether the nature of similarity judgment (for e.g., the notion of similarity) itself differs across cultures and contributes to cross-cultural differences in similarity judgment responding.
-In an alternative hypothesis, the cross-cultural differences in similarity judgment observed is driven by not only the input, but also an interaction between cultural-specific nature of similarity judgment and input.
-To test this hypothesis, we operationalize cultural-specific nature of similarity judgment as country context, and input to similarity judgment as the corresponding corpus statistics.
-We then compare a model that includes country, corresponding corpus statistics and their interaction as fixed effects (R syntax: responses ~ corresponding_corpus * country + (1|triad) + (1|subject)) to a model with only the corresponding corpus statistics as the fixed effect (R syntax: responses ~ corresponding_corpus + (1|triad) + (1|subject))
+## 3. Cultural context as a predictor for cross-cultural variation in similarity judgments
+
+Our above models tested whether language statistics is a good predictor for similarity judgment.
+As we noted above, language statistics can be a proxy of both inputs and conceptualization of similarity.
+However, it is still an open question whether conceptualization of similarity itself has a unique contribution to similarity judgment (beyond its influence on language statistics).
+To test this hypothesis, we operationalize cultural-specific conceptualization of similarity as country.
+We then compare a model that includes country, corresponding corpus statistics and their interaction as fixed effects to a model with only the corresponding corpus statistics as the fixed effect.
+If conceptualization of similarity has a unique contribution to similarity judgment, we should see that terms including country to be a significant predictor of responding.
 
@@
 <!-- ```{r country language interaction in raw co-occurrences, include = F} -->
+
 <!-- fit.language = glmer(responses_theme ~ theme_freq_prop_corr_lang + (1 | subject) + (1 | triad),  -->
+
 <!--           data = df %>% filter(!(triad %in% triads_omit)),   -->
+
 <!--           family="binomial") -->
+
 <!-- summary(fit.language) -->
+
 <!-- fit.language.anova = Anova(fit.language, type = 3) -->
+
 <!-- fit.language.anova -->
@@
 <!-- fit.country_language = glmer(responses_theme ~ theme_freq_prop_corr_lang * country + (1 | subject) + (1 | triad),  -->
+
 <!--           data = df %>% filter(!(triad %in% triads_omit)),   -->
+
 <!--           family="binomial") -->
+
 <!-- summary(fit.country_language) -->
+
 <!-- fit.country_language.anova = Anova(fit.country_language, type = 3) -->
+
 <!-- fit.country_language.anova -->
@@
 <!-- fit.country_language_compare = anova(fit.language, fit.country_language, type = 3) -->
+
 <!-- fit.country_language_compare -->
+
 <!-- ``` -->
@@
 ```
+
 In the model containing only the corresponding corpus statistics, the corpus statistics is a significant predictor ($\beta$ = `r round(fixef(fit.language_cos)["theme_cosine_prop_corr_lang"], 2)`, $\chi^2$(`r fit.language_cos.anova["theme_cosine_prop_corr_lang", "Df"]`) = `r round(fit.language_cos.anova["theme_cosine_prop_corr_lang", "Chisq"], 2)`, p `r ifelse( fit.language_cos.anova["theme_cosine_prop_corr_lang", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.language_cos.anova["theme_cosine_prop_corr_lang", "Pr(>Chisq)"], 3)), "< .001")`).
-When adding country and interaction between country and corpus, both the corpus statistics ($\beta$ = `r round(fixef(fit.country_language_cos)["theme_cosine_prop_corr_lang"], 2)`, $\chi^2$(`r fit.country_language_cos.anova["theme_cosine_prop_corr_lang", "Df"]`) = `r round(fit.country_language_cos.anova["theme_cosine_prop_corr_lang", "Chisq"], 2)`, p `r ifelse( fit.country_language_cos.anova["theme_cosine_prop_corr_lang", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.country_language_cos.anova["theme_cosine_prop_corr_lang", "Pr(>Chisq)"], 3)), "< .001")`) and interaction between country and corpus (F(`r fit_joint.country_language_cos["theme_cosine_prop_corr_lang:country", "df1"]`, `r fit_joint.country_language_cos["theme_cosine_prop_corr_lang:country", "df2"]`) = `r round(fit_joint.country_language_cos["theme_cosine_prop_corr_lang:country", "F.ratio"], 2)`, $\chi^2$(`r fit.country_language_cos.anova["theme_cosine_prop_corr_lang:country", "Df"]`) = `r round(fit.country_language_cos.anova["theme_cosine_prop_corr_lang:country", "Chisq"], 2)`, p `r ifelse( fit.country_language_cos.anova["theme_cosine_prop_corr_lang:country", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.country_language_cos.anova["theme_cosine_prop_corr_lang:country", "Pr(>Chisq)"], 3)), "< .001")`) are significant predictors.
-This suggests that there are cross-cultural differences in both input and nature of similarity judgment that drive differences in similarity judgment responding.
-We found no effects of country  (F(`r fit_joint.country_language_cos["country", "df1"]`, `r fit_joint.country_language_cos["country", "df2"]`) = `r round(fit_joint.country_language_cos["country", "F.ratio"], 2)`, $\chi^2$(`r fit.country_language_cos.anova["country", "Df"]`) = `r round(fit.country_language_cos.anova["country", "Chisq"], 2)`, p `r ifelse( fit.country_language_cos.anova["country", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.country_language_cos.anova["country", "Pr(>Chisq)"], 3)), "< .001")`).
+When adding country and interaction between country and corpus, corpus statistics ($\beta$ = `r round(fixef(fit.country_language_cos)["theme_cosine_prop_corr_lang"], 2)`, $\chi^2$(`r fit.country_language_cos.anova["theme_cosine_prop_corr_lang", "Df"]`) = `r round(fit.country_language_cos.anova["theme_cosine_prop_corr_lang", "Chisq"], 2)`, p `r ifelse( fit.country_language_cos.anova["theme_cosine_prop_corr_lang", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.country_language_cos.anova["theme_cosine_prop_corr_lang", "Pr(>Chisq)"], 3)), "< .001")`), country (F(`r fit_joint.country_language_cos["country", "df1"]`, `r fit_joint.country_language_cos["country", "df2"]`) = `r round(fit_joint.country_language_cos["country", "F.ratio"], 2)`, $\chi^2$(`r fit.country_language_cos.anova["country", "Df"]`) = `r round(fit.country_language_cos.anova["country", "Chisq"], 2)`, p `r ifelse( fit.country_language_cos.anova["country", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.country_language_cos.anova["country", "Pr(>Chisq)"], 3)), "< .001")`), and interaction between country and corpus (F(`r fit_joint.country_language_cos["theme_cosine_prop_corr_lang:country", "df1"]`, `r fit_joint.country_language_cos["theme_cosine_prop_corr_lang:country", "df2"]`) = `r round(fit_joint.country_language_cos["theme_cosine_prop_corr_lang:country", "F.ratio"], 2)`, $\chi^2$(`r fit.country_language_cos.anova["theme_cosine_prop_corr_lang:country", "Df"]`) = `r round(fit.country_language_cos.anova["theme_cosine_prop_corr_lang:country", "Chisq"], 2)`, p `r ifelse( fit.country_language_cos.anova["theme_cosine_prop_corr_lang:country", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.country_language_cos.anova["theme_cosine_prop_corr_lang:country", "Pr(>Chisq)"], 3)), "< .001")`), are significant predictors[^7].
+Including the country and country-corpus terms to the language-only model significantly its ability to explain variation in responding ($\chi^2$(`r fit.country_language_cos_compare["fit.country_language_cos", "Df"]`) = `r round(fit.country_language_cos_compare["fit.country_language_cos", "Chisq"], 2)`, p `r ifelse( fit.country_language_cos_compare["fit.country_language_cos", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.country_language_cos_compare["fit.country_language_cos", "Pr(>Chisq)"], 3)), "< .001")`).
+This result points to a unique contribution by culture-specific ways of conceptualizing similarity to similarity judgment that is not captured in language statistics.
 
-## 4. How general are the cross-language differences in similarity judgments we observe? Are they limited to taxonomic-thematic contrasts or do they extend to other cases?
-Previous work using the triad task such as @Ji2004 has focused on contrasting taxonomic-thematic match preferences, driven by a theory of cross-cultural differences in notions of similarity.
-Meanwhile, our approach has shown that notions of similarity only has an effect on cross-cultural differences in similarity judgment when modulated by input, and that input as proxied by lexical statistics of the corresponding corpus by itself is a significant predictor for similarity judgment responding.
-Our approach using lexical statistics do not assume a taxonomic/thematic structure in the triads.
-Therefore, it should be possible to predict similarity judgments to triads that do not follow a taxonomic/thematic structure, such as our filler triads.
-If our approach is tractable, we should be able to repeat the above analyses to the filler triads, and find that lexical statistics of each corpus is a significant predictor for similarity judgments in filler triads of the corresponding cultural context.
+[^7]: With preregistered exclusion criterion: only corpus statistics and interaction between country and corpus are significant predictors.
+
+## 4. Language statistics as a predictor for non-structured triad items
+
+A possible concern with our approach is that variation in language statistics (which we claim to be a proxy of both inputs and conceptualization of similarity) can be fully explained by variation in conceptualization of similarity (i.e.
+the difference in similarity measures between 'cow' and 'grass' versus 'cow' and 'chicken' in one corpus is solely driven by the corresponding culture's preference of thematic versus taxonomic categorization).
+Alternatively, language statistics may be measuring slight but pervasive differences in similarity driven by participants' different cultural contexts, rather than merely the type of similarity they generally prefer (thematic vs taxonomic relations).
+We address this concern by testing whether language statistics covary with similarity judgment of items with no taxonomic/thematic structures (filler items).
+If language statistics is only driven by conceptualization of similarity, we should not see an effect with such items, which have no structured similarity relations by which to make any predictions.
 
@@
   pull(x)
+
+df.filler <- df.filler %>%
+  mutate(word1_match_freq_prop_corr_lang = case_when(
+    country == "US" ~ word1_match_frequency_prop_E,
+    country == "China" ~ word1_match_frequency_prop_M, 
+    country == "Vietnam" ~ word1_match_frequency_prop_V)) %>% 
+    mutate(word1_match_cosine_prop_corr_lang = case_when(
+    country == "US" ~ word1_match_cosine_prop_E,
+    country == "China" ~ word1_match_cosine_prop_M, 
+    country == "Vietnam" ~ word1_match_cosine_prop_V))
+
+df.filler <- df.filler %>%
+  mutate(word1_match_freq_prop_corr_lang = ifelse(country == "US", 
+                                                  word1_match_frequency_prop_E, 
+                                                  ifelse(country == "China", 
+                                                         word1_match_frequency_prop_M, 
+                                                         word1_match_frequency_prop_V))) %>% 
+  mutate(word1_match_cosine_prop_corr_lang = ifelse(country == "US", 
+                                                  word1_match_cosine_prop_E, 
+                                                  ifelse(country == "China", 
+                                                         word1_match_cosine_prop_M, 
+                                                         word1_match_cosine_prop_V)))
+
+#NOT SURE WHY THIS DOESN'T WORK
+    #        case_when(
+    # country == "US" ~ word1_match_frequency_prop_E,
+    # country == "China" ~ word1_match_frequency_prop_M, 
+    # country == "Vietnam" ~ word1_match_frequency_prop_V)) %>% 
+    # mutate(word1_match_cosine_prop_corr_lang = case_when(
+    # country == "US" ~ word1_match_cosine_prop_E,
+    # country == "China" ~ word1_match_cosine_prop_M, 
+    # country == "Vietnam" ~ word1_match_cosine_prop_V))
 ```
@@
 
-```{r echo=FALSE, warning=FALSE, cache = TRUE, fig.env="figure", fig.align = "center", fig.cap="Proportion of Word1 responses by country."}
+```{r echo=FALSE, warning=FALSE, include = T, cache = TRUE, fig.env="figure", fig.align = "center", fig.cap="Proportion of Word1 responses by country."}
 #show violin plot
@@
 ```
-For each filler triad, we randomly assigned one of the responding optiosn as 'Word1'.
-Running a mixed-effects logistic regression predict responding (Word1 or Word2) with structure equivalent to Analysis 1, we found no effect of country on filler responding (Figure 3).
 
-### Does lexical statistics for fillers predict responding in the corresponding cultural context?
+For each filler triad, we randomly assigned one of the responding options as 'Word1'.
+Running a mixed-effects logistic regression to predict responding (Word1 or Word2) with country as the fixed effect and a random effect structure equivalent to Q1, we found no effect of country on filler responding ($\chi^2$(`r fit.country_filler.anova["country", "Df"]`) = `r round(fit.country_filler.anova["country", "Chisq"], 2)`, p `r ifelse( fit.country_filler.anova["country", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.country_filler.anova["country", "Pr(>Chisq)"], 3)), "< .001")`) (Figure 3).
+
 <!-- #### Raw co-occurrences -->
+
 <!-- ```{r US responding predicted by each corpus model raw co-occurrences for fillers, warning=FALSE,include = F} -->
+
 <!-- # English  -->
+
 <!-- fit.EN_US_filler = glmer(responses_word1 ~ word1_match_frequency_prop_E + (1 | subject) + (1 | cue),  -->
+
 <!--           data = df.filler %>% filter(country == "US",  -->
+
 <!--                                !(cue_id %in% fillers_omit)),  -->
+
 <!--           family="binomial") -->
+
 <!-- summary(fit.EN_US_filler) -->
+
 <!-- fit.EN_US_filler.anova = Anova(fit.EN_US_filler, type = 3) -->
@@
 <!-- fit.EN_US_filler.anova -->
+
 <!-- ``` -->
@@
 <!-- ```{r VN responding predicted by each corpus model raw co-occurrences for fillers, warning=FALSE, include = F} -->
+
 <!-- # Vietnamese -->
+
 <!-- fit.VI_VN_filler = glmer(responses_word1 ~ word1_match_frequency_prop_V + (1 | subject) + (1 | cue),  -->
+
 <!--           data = df.filler %>% filter(country == "Vietnam",  -->
+
 <!--                                !(cue_id %in% fillers_omit)),  -->
+
 <!--           family="binomial") -->
+
 <!-- summary(fit.VI_VN_filler) -->
+
 <!-- fit.VI_VN_filler.anova = Anova(fit.VI_VN_filler, type = 3) -->
@@
 <!-- fit.VI_VN_filler.anova -->
+
 <!-- ``` -->
+
 <!-- Yes, corpus raw co-occurrences predicts responding for both US and Vietnamese. *need to discuss with Shan to incorporate Mandarin due to a lot of empty counts* -->
@@
 <!-- #### Cosine distance -->
+
 ```{r US responding predicted by each corpus model cosine distances for fillers, warning=FALSE, include = F}
@@
 ```{r CN responding predicted by each corpus model cosine distances for fillers, warning=FALSE, include = F}
-# Vietnamese
+# Mandarin
 fit.ZH_CN_filler_cos = glmer(responses_word1 ~ word1_match_cosine_prop_M + (1 | subject) + (1 | cue), 
@@
 ```
-Using the same mixed-effects logistic regression structure as Analysis 2, we predict responses (1=word1 or 0=word2) with corpus prediction (proportion of cosine distance) as a fixed effect and participant and triad as random effects.
-We found that in all cultural contexts, the correpsonding corpora is a significant predictor of responding, with p<0.05 and $\beta$ from `r min(beta.filler_single_corpus_cos)` to `r max(beta.filler_single_corpus_cos)`.
-(For a full report, see Appendix.)
+
+Using the same mixed-effects logistic regression structure as Q2, we predict responses (1=word1 or 0=word2) of each cultural context with the corresponding corpus statistics as a fixed effect, and participant and triad as random effects.
+We found that in all cultural contexts, the corresponding corpus is a significant predictor of responding, with p \< 0.05 and $\beta$ from `r min(beta.filler_single_corpus_cos)` to `r max(beta.filler_single_corpus_cos)`.
+(For a full report, see Supplementary Information.)
+
+```{r combined filler and stimulus}
+df.triad_filler <- rbind(
+  df %>% mutate(response = responses_theme, 
+                cosine_prop_corr_lang = theme_cosine_prop_corr_lang, 
+                cue_id = triad, 
+                is_filler = 0) %>%
+          select(response, cosine_prop_corr_lang, is_filler,
+                 cue_id, country, subject), 
+  df.filler %>% mutate(response = responses_word1,
+                       cosine_prop_corr_lang = word1_match_cosine_prop_corr_lang,
+                       is_filler = 1) %>%
+                select(response, cosine_prop_corr_lang, is_filler,
+                       cue_id, country, subject)
+)
+
+fit.triad_filler = glmer(response ~ cosine_prop_corr_lang * is_filler + (1 | subject) + (1 | cue_id), 
+          data = df.triad_filler,
+          family="binomial")
+summary(fit.triad_filler)
+fit.triad_filler.anova = Anova(fit.triad_filler, type = 3)
+
+fit.triad_filler.anova
+```
 
 # Discussion
-In this paper, we consider whether statistics of the language environment can account for cross-cultural differences in a classic similarity judgment paradigm, as an alternative to the view that members of different cultures vary in their conception of similarity.
-We found that each corpus statistics is a good predictor for the corresponding country's similarity judgments.
-When corresponding corpus statistics, country and corpus-country interactions were included as fixed effects to predict similarity judgments, we found no effects of country, but both corpus statistics and corpus-country interaction are significant predictors.
-Our results provide evidence that cross-cultural differences in similarity judgment might not be driven by cross-cultural differences in conception of similarity alone, but rather by statistics to similarity judgment and its interaction with similarity conception.
-We also showed that corpus statistics predict similarity judgments for triads that do not have taxonomic/thematic structure.
 
-We first tested the generality of a cultural account which holds that people from Western and East Asian cultures tend to conceive of similarity in more taxonomic and thematic ways, respectively, and respond accordingly in categorization tasks such as ours.
+In this paper, we consider whether statistics of the environment (as proxied by language statistics) can account for cross-cultural differences in a classic similarity judgment paradigm, as an alternative to the view that members of different cultures vary in their conceptualization of similarity.
 While we managed to replicate the previously documented contrast between English speakers in the US and Mandarin Chinese speakers from East Asia (mainland China, Taiwan, Hong Kong, and Singapore), we do not extend this contrast to our sample of Vietnamese speakers in Vietnam and English speakers in the US.
-This finding suggests some limitations on the generality of this cultural account.
+This finding suggests some limitations on the generality of the cultural account.
+We found some support for the environmental statistics account: each corpus statistics is a good predictor for the corresponding country's similarity judgments, even when other corpus statistics are included, and even with triads without a taxonomic/thematic structure.
+However, we also found that culture-based conceptualization of similarity uniquely contributes to predicting similarity judgment when included in a model with corpus statistics.
+Overall, our results provide evidence that cross-cultural differences in similarity judgment might not be driven by cross-cultural differences in conception of similarity alone, but also by variation in inputs to similarity judgment.
 
-We did find some signatures of language specificity in our analysis: each corpus statistics is a good predictor for the corresponding country's similarity judgments, even when other corpus statistics are included.
-However, we also find evidence for consistency across the three cultural groups: each corpus statistics is also a good predictor for the other two non-corresponding cultural contexts when included as the only predictor, and both English and Mandarin Chinese statistics are good predictors for their non-corresponding cultural contexts when all three corpora are included.
+There are some important limitations of our approach.
+While we discuss cross-cultural variability at the level of countries or larger world areas, these are not cultural monoliths.
+For convenience, we operationalize culture at the level of country, based on where participants were raised.
+It is an open question whether performance in our participant populations (of relatively young and well-educated adults) is representative of the broader country.
+This is especially true for societies with substantial ethnic and cultural variation such as the US.
+We expect that our data is likely to underestimate variation both within and between the countries we sample from.
 
-When all cultural contexts are taken together, we found that both corresponding corpus statistics and an interaction between corpus and country are significant predictors for similarity judgments.
-This result suggests that in addition to input to similarity judgment, country-specific categorical differences in similarity judgment (for e.g., how each culture conceive of similarity) also predict cross-cultural differences in similarity judgment behavior while modulated by input.
-
-Even in triads with no taxonomic / thematic structure, each corpus statistics is still a good predictor of the corresponding country's similarity judgments.
-The ability of corpus statistics to predict similarity judgments in non-structured triads suggests that cross-cultural differences in similarity judgments should be construed in a more general and graded manner, as opposed to binary taxonomic/thematic match-preferring.
-
-<!-- such as the large positive correlation between similarity judgments of each country and the respective corpus statistics, and how each corpus statistics are good predictors for corresponding country's similarity judgments.
-However, this is potentially due to the high correlation between corpus statistics of English, Vietnamese and Mandarin.
-We find even stronger evidence for consistency across the three groups, with substantive overlapping predictions across the corpus models, highly similar responding across the experiments, and a correspondingly high fit in cross-language comparisons between models and data.
--->
+Additionally, language, culture, cognition, and individual experiences are intertwined in complex causal relationships.
+In this study, we measure language and its relation to cross-cultural differences in categorization, but these relations test only the plausibility of a language-based account; they cannot establish the direction of causality.
 
@@
 thematic responding, then what differences drive the relativity effects previous studies have observed?--> To what extent are the relativity effects driven by language, and to what extent by culture?
-@Ji2004 established that culture-aligned differences in this paradigm exist, even when the test language is held constant, concluding that “it is culture (independent of the testing language) that led to different grouping styles” in their study.
+@Ji2004 established that culture-aligned differences in this paradigm exist, even when the test language is held constant, concluding that "it is culture (independent of the testing language) that led to different grouping styles" in their study.
 Our data provide a cautionary note to this conclusion, suggesting that semantic representations in bilinguals (see @Francis2005 for a review) may have the potential to provide an offline account for cross-context differences in similarity judgments, independent of test language.
@@
 Can they explain taxonomic-thematic differences of the type reported by @Ji2004 and others?
-Can we provide a more specific computational account than the simple frequency model tested here?
+Can we provide a more specific computational account than the simple proportion-of-similarity model tested here?
 
@@
 
-# Appendix
-## 1. ICC of item variability and participant variability
-
-```{r xtable, results ="asis", fig.pos="H"}
-US_agr <- agreement::dim_icc(df_main_analysis %>% filter(country == "US"),
-                             model = "2A",
-                             type = "agreement",
-                             unit = "average",
-                             object = triad,
-                             rater = subject,
-                             score = responses_theme,
-                             bootstrap = 0)
-
-CN_agr <- agreement::dim_icc(df_main_analysis %>% filter(country == "China"),
-                             model = "2A",
-                             type = "agreement",
-                             unit = "average",
-                             object = triad,
-                             rater = subject,
-                             score = responses_theme,
-                             bootstrap = 0)
-
-VN_agr <- agreement::dim_icc(df_main_analysis %>% filter(country == "Vietnam"),
-                             model = "2A",
-                             type = "agreement",
-                             unit = "average",
-                             object = triad,
-                             rater = subject,
-                             score = responses_theme,
-                             bootstrap = 0)
-
-iccs <- tibble(Sample = c("US","China", "Vietnam"),
-               `Intra-rater ICC` = c(US_agr$Intra_ICC,
-                                     CN_agr$Intra_ICC,
-                                     VN_agr$Intra_ICC),
-               `Inter-rater ICC` = c(US_agr$Inter_ICC,
-                                     CN_agr$Inter_ICC,
-                                     VN_agr$Inter_ICC))
-
-tab1 <- xtable::xtable(iccs, digits=2,
-                       caption = "ICCs for reliability within participants (intra-rater) and stimuli (inter-rater) for all cultural contexts.")
-
-print(tab1, type="latex", comment = F, include.rownames = FALSE)
-```
-An intraclass correlation coefficients (ICCs) analysis with a two-way, non-interactive model (following the standard taxonomy for ICCs from @McGraw1996) showed that, per cultural context, participants' judgments were variable across triads, while inter-rater agreement about specific triads was quite high (Table 1).
-This result suggests that each triad prompts taxonomic / thematic matching reliably within culture.
-
-## 2. Supplemental for whether each corpus predicts similarity judgment in each cultural context
-
-### Triads
-For US responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are significant predictors of US responding (EN-US model: $\beta$ = `r round(fixef(fit.EN_US_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.EN_US_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.EN_US_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p `r ifelse( fit.EN_US_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.EN_US_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"], 3)), "< .001")`; VI-US model: $\beta$ = `r round(fixef(fit.VI_US_cos)["theme_cosine_prop_V"], 2)`, $\chi^2$(`r fit.VI_US_cos.anova["theme_cosine_prop_V", "Df"]`) = `r round(fit.VI_US_cos.anova["theme_cosine_prop_V", "Chisq"], 2)`, p `r ifelse( fit.VI_US_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.VI_US_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"], 3)), "< .001")`; ZH-US model: $\beta$ = `r round(fixef(fit.ZH_US_cos)["theme_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ZH_US_cos.anova["theme_cosine_prop_M", "Df"]`) = `r round(fit.ZH_US_cos.anova["theme_cosine_prop_M", "Chisq"], 2)`, p `r ifelse( fit.ZH_US_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ZH_US_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"], 3)), "< .001")`).
-
-For Vietnam (VN) responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are significant predictors of VN responding (EN-VN model: $\beta$ = `r round(fixef(fit.EN_VN_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.EN_VN_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.EN_VN_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p `r ifelse( fit.EN_VN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.EN_VN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"], 3)), "< .001")`; VI-VN model: $\beta$ = `r round(fixef(fit.VI_VN_cos)["theme_cosine_prop_V"], 2)`, $\chi^2$(`r fit.VI_VN_cos.anova["theme_cosine_prop_V", "Df"]`) = `r round(fit.VI_VN_cos.anova["theme_cosine_prop_V", "Chisq"], 2)`, p `r ifelse( fit.VI_VN_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.VI_VN_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"], 3)), "< .001")`; ZH-VN model: $\beta$ = `r round(fixef(fit.ZH_VN_cos)["theme_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ZH_VN_cos.anova["theme_cosine_prop_M", "Df"]`) = `r round(fit.ZH_VN_cos.anova["theme_cosine_prop_M", "Chisq"], 2)`, p `r ifelse( fit.ZH_VN_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ZH_VN_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"], 3)), "< .001")`).
-
-For China (CN) responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are significant predictors of CN responding (EN-CN model: $\beta$ = `r round(fixef(fit.EN_CN_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.EN_CN_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.EN_CN_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p `r ifelse( fit.EN_CN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.EN_CN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"], 3)), "< .001")`; VI-CN model: $\beta$ = `r round(fixef(fit.VI_CN_cos)["theme_cosine_prop_V"], 2)`, $\chi^2$(`r fit.VI_CN_cos.anova["theme_cosine_prop_V", "Df"]`) = `r round(fit.VI_CN_cos.anova["theme_cosine_prop_V", "Chisq"], 2)`, p `r ifelse( fit.VI_CN_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.VI_CN_cos.anova["theme_cosine_prop_V", "Pr(>Chisq)"], 3)), "< .001")`; ZH-CN model: $\beta$ = `r round(fixef(fit.ZH_CN_cos)["theme_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ZH_CN_cos.anova["theme_cosine_prop_M", "Df"]`) = `r round(fit.ZH_CN_cos.anova["theme_cosine_prop_M", "Chisq"], 2)`, p `r ifelse( fit.ZH_CN_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ZH_CN_cos.anova["theme_cosine_prop_M", "Pr(>Chisq)"], 3)), "< .001")`).
-
-### Fillers
-English (EN) is a significant predictors of US responding ($\beta$ = `r round(fixef(fit.EN_US_filler_cos)["word1_match_cosine_prop_E"], 2)`, $\chi^2$(`r fit.EN_US_filler_cos.anova["word1_match_cosine_prop_E", "Df"]`) = `r round(fit.EN_US_filler_cos.anova["word1_match_cosine_prop_E", "Chisq"], 2)`, p `r ifelse( fit.EN_US_filler_cos.anova["word1_match_cosine_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.EN_US_filler_cos.anova["word1_match_cosine_prop_E", "Pr(>Chisq)"], 3)), "< .001")`).
-
-Vietnamese (VI) is a significant predictors of Vietnam responding ($\beta$ = `r round(fixef(fit.VI_VN_filler_cos)["word1_match_cosine_prop_V"], 2)`, $\chi^2$(`r fit.VI_VN_filler_cos.anova["word1_match_cosine_prop_V", "Df"]`) = `r round(fit.VI_VN_filler_cos.anova["word1_match_cosine_prop_V", "Chisq"], 2)`, p `r ifelse( fit.VI_VN_filler_cos.anova["word1_match_cosine_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.VI_VN_filler_cos.anova["word1_match_cosine_prop_V", "Pr(>Chisq)"], 3)), "< .001")`).
-
-Mandarin (ZH) is a significant predictors of China responding ($\beta$ = `r round(fixef(fit.ZH_CN_filler_cos)["word1_match_cosine_prop_M"], 2)`, $\chi^2$(`r fit.ZH_CN_filler_cos.anova["word1_match_cosine_prop_M", "Df"]`) = `r round(fit.ZH_CN_filler_cos.anova["word1_match_cosine_prop_M", "Chisq"], 2)`, p `r ifelse( fit.ZH_CN_filler_cos.anova["word1_match_cosine_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ZH_CN_filler_cos.anova["word1_match_cosine_prop_M", "Pr(>Chisq)"], 3)), "< .001")`).
-
-## 3. Exclusion Statistics
-```{r results = "asis", fig.cap="Testing"}
-df.demog_excl <- cbind(t(df.excl_US), t(df.excl_CN))
-df.demog_excl <- cbind(df.demog_excl, t(df.excl_VN))
-
-rownames(df.demog_excl) <-
-  c("Country", "Ppts Finished", 
-    "Excluded", 
-    "After Exclusion", 
-    "Non-Native Speakers", "EN Speakers", 
-    "VI Speakers", "ZH Speakers", 
-    "Lived Abroad", "Overseas Experience", 
-    "After Exclusions")
-
-colnames(df.demog_excl) <- df.demog_excl[1,]
-df.demog_excl <- df.demog_excl[-1, ]
-
-kbl(df.demog_excl, align = "c") %>%
-  add_header_above(c(" " = 1, "Country" = 3)) %>%
-  pack_rows(index = c(" " = 1, "Attention Check Exclusions" = 2, "Demographics Exclusions" = 7))
-```
-
-\newpage
-
 # Acknowledgements
 
-Place acknowledgments (including funding information) in a section at
-the end of the paper.
+Place acknowledgments (including funding information) in a section at the end of the paper.
 
@@
 
+```{=tex}
 \setlength{\parindent}{-0.1in} 
 \setlength{\leftskip}{0.125in}
+```
 \noindent

### 2023-01-31 code/4_paper/manuscript/manuscript.tex
manuscript edits

@@
 
-By virtue of discrete words and grammatical features, language provides
-a categorical partition of our continuous experiences. By measuring the
-similarity between words (as commonly done with lexical co-occurrence
-models), it may be possible to model the shape of similarity space in
-order to capture cross-linguistic and cross-cultural variation and
-provide a more general answer to the question of how language influences
-our conception of the world.
-
-Taxonomic and thematic similarity provide a convenient entry point to
-broader debates about cross-linguistic and cross-cultural variation in
-notions of similarity. Taxonomic categorization is based on the
-similarity of attributes, for example, similar perceptual properties,
-like shared color or shape, among objects. In contrast, thematic
-categorization is based on causal, spatial, and temporal relationships
-among objects (Markman \& Hutchinson, 1984).
-
 \hypertarget{cross-cultural-variation-in-similarity}{%
@@
 
-Preferences for taxonomic and thematic similarity vary across cultures.
-Chiu (1972) found that Chinese children (9-10 years old) are more likely
-to choose thematic matches in a picture triad task (shown, e.g., images
-of an ant, a bee, and honey) than their American counterparts. These
-cross-cultural differences are also observed in novel object
-categorization, with Chinese participants preferring to group by family
-resemblance across multiple features and Americans preferring a
-single-feature rule (Norenzayan, Smith, Kim, \& Nisbett, 2002). The
-authors link these differences to tendencies toward analytic processing
-in Western cultures, which emphasizes objects and their properties, and
-holistic processing in East Asian cultures, which emphasizes
-relationships between objects and their context (see also Nisbett
-(2003)). In related work, East Asian participants show a higher level of
-sensitivity to context than their Western counterparts when reproducing
-drawings from memory (Ji, Peng, \& Nisbett, 2000); visually exploring
-naturalistic scenes (Chua, Boland, \& Nisbett, 2005); describing scenes
-(Masuda \& Nisbett, 2001); and in explaining the causes of ambiguous
-behaviors (Choi, Nisbett, \& Norenzayan, 1999).
+The way we partition our continuous experiences of the world into
+categories, and which kind of similarity relationships we privilege to
+organize such partitions, vary across cultures. One way this
+cross-cultural difference has been observed is with a task comparing
+preference for taxonomic and thematic similarity between East Asian and
+Western participants.\footnote{Taxonomic categorization is based on the
+  similarity of attributes, for example, similar perceptual properties,
+  like shared color or shape, among objects.In contrast, thematic
+  categorization is based on causal, spatial, and temporal relationships
+  among objects (Markman \& Hutchinson, 1984).} Ji, Zhang, \& Nisbett
+(2004) found that in a word triad task (choose two out of three words
+that are more related to one another), Chinese participants preferred
+thematic matching more compared to European Americans. In a pictorial
+version of this task, Chiu (1972) found that Chinese children (9-10
+years old) are also more likely to choose thematic matches compared to
+their American counterparts. This cross-cultural difference is also
+observed in novel object categorization, with Chinese participants
+preferring to group by family resemblance across multiple features and
+Americans preferring a single-feature rule (Norenzayan, Smith, Kim, \&
+Nisbett, 2002).
 
-Ji, Zhang, \& Nisbett (2004) asked whether differences in analytic and
-holistic processing are driven by language, culture, or a combination of
-these. They presented Chinese and European American adults with a word
-triad task, and found a preference for thematic matching among Chinese
-participants compared to European Americans. They found that test
-language contributed to this difference, but did not fully explain it:
-Chinese participants showed a stronger thematic preference when tested
-in Mandarin, but still showed a thematic preference when tested in
-English. Ji et al.~conclude that culture (independent of language) leads
-to different styles of reasoning about similarity, whereas language
-serves as a ``tuning'' mechanism operating within a culturally-specific
-style, by activating representations corresponding to the language being
-used.\footnote{But note that this work did not include a manipulation to
-  prevent participants from engaging in e.g., covert naming in a
-  language other than the test language.}
+Previous research has linked the observed difference in similarity
+judgment to related work showing tendencies toward analytic processing
+(emphasizing objects and their properties) in Western cultures and
+holistic processing in East Asian cultures (emphasizing relationships
+between objects and their context) (see also Nisbett (2003)).
+Cross-cultural difference in similarity judgment is thus connected to
+well-documented work showing East Asian participants exhibiting a higher
+level of sensitivity to context than their Western counterparts when
+reproducing drawings from memory (Ji, Peng, \& Nisbett, 2000); visually
+exploring naturalistic scenes (Chua, Boland, \& Nisbett, 2005);
+describing scenes (Masuda \& Nisbett, 2001); and in explaining the
+causes of ambiguous behaviors (Choi, Nisbett, \& Norenzayan, 1999). This
+view ascribes cross-cultural differences in similarity judgment to
+variation in how each culture (or group of culture, i.e.~East Asian vs
+Western) \textbf{conceptualize} similarity -- with East Asians
+preferring thematic relations more than Westerners.
 
-This view ascribes cross-cultural differences in similarity judgment to
-variation in the conceptualization of similarity itself. Alternatively,
-these judgments could be shaped by cross-cultural differences in the
+Alternatively, these judgments could be shaped by cross-cultural
+differences in the \textbf{inputs} to similarity judgment, namely, the
 statistics of the environment, and accordingly the content of everyday
-experiences. Perhaps when confronted with the triad task, participants
-from all cultures follow the same process for reasoning about
-similarity, but rely on language or culture-specific inputs to this
-process. If we observe a difference in categorization between East Asian
-and Western participants, it could be that members of both groups use
-the same procedure (considering similarity that is influenced by both
-taxonomic and thematic relations), but the inputs to this procedure
-differ between cultures, with East Asian participants exposed to more
-instances of thematic similarity than their Western counterparts.
+experiences. Perhaps when faced with the triad task, participants from
+all cultures follow the same process for conceptualizing similarity, but
+rely on language or culture-specific inputs to this process. If we
+observe a difference in categorization between East Asian and Western
+participants, it could be that members of both groups use the same
+procedure (considering similarity that is influenced by both taxonomic
+and thematic relations), but the inputs to this procedure differ between
+cultures, with East Asian participants exposed to more instances of
+thematic similarity than their Western counterparts. We might also
+expect that both conceptualization and inputs of similarity play a role
+in driving cross-cultural differences -- East Asian participants may
+both be exposed to more instances of thematic similarity, and prefer to
+conceptualize similarity as thematic relations more so than Westerners.
 
@@
 
-While co-occurrences in experience are difficult to measure,
-co-occurrence in language can provide a rough proxy--and indeed,
-language may afford many of the ``experiences'' that people have with
-infrequently encountered items, like cows or helicopters. In this study,
-we use co-occurrence in language as a proxy of cultural experience. This
-is a generalizing assumption, and while no linguistic corpus can be
-expected to fully capture a culture, using this proxy as a model of
-culture provides a conservative test of the hypothesis that differences
-in the input, rather than the process, of reasoning produces cultural
-variation in this task. This means that if such a model does work -- if
-linguistic co-occurrence can predict cultural variation in this
-similarity task without building differences in the decision process
-into the model -- it is relatively strong evidence that language alone
-(perhaps as a more easily observed source of information on broader
-cultural and ecological variation) may account for these cross-cultural
-differences in reasoning.
-
-Indeed, previous work suggests that using lexical co-occurrence as a
-proxy can be useful in thinking about similarity reasoning. Natural
-language processing tasks have found that lexical co-occurrence is a
-good predictor for performance in similarity judgment. Griffiths,
-Steyvers, \& Tenenbaum (2007) showed that a model that takes
-word-document co-occurrence as input can be used to predict word
-association and the effects of semantic association on a variety of
-linguistic tasks. Additionally, lexical semantic models that are
-constructed using lexical co-occurrence (as opposed to annotated
-relations) have been shown to perform well on predicting human judgments
-about similarity between word pairs that are thematically or
-taxonomically related (Rohde, Gonnerman, \& Plaut, 2006).
+To test alternative hypotheses involving variation of inputs to
+similarity judgment, we need a way to operationalize variation in
+exposure to thematic vs taxonomic relations. While this metric is
+difficult to directly measure, language statistics can provide a rough
+proxy. Language statistics is useful in that it is part of the inputs to
+everyday experiences (through spoken and written language), may afford
+many of the `experiences' that people have with infrequently encountered
+items, like cows or helicopters, and provides accessible measures.
+Previous work also suggests that using language statistics (such as
+lexical co-occurrence or cosine distance of word embeddings) as a proxy
+can be a good predictor for similarity reasoning. Griffiths, Steyvers,
+\& Tenenbaum (2007) showed that a model trained on word-document
+co-occurrence can predict word association and the effects of semantic
+association on a variety of linguistic tasks. Lexical semantic models
+that are constructed using lexical co-occurrence (in comparison to
+annotated relations) have been shown to perform well on predicting human
+judgments about similarity between word pairs that are thematically or
+taxonomically related (Rohde, Gonnerman, \& Plaut, 2006). Word
+embeddings like fastText have been demonstrated to be good predictors
+for similarity judgments (Liu, Feng, Wu, Chan, \& Fulton (2019),
+Jatnika, Bijaksana, \& Suryani (2019)).
 
@@
 vector representing each word in its lexicon (Mikolov, Grave,
-Bojanowski, Puhrsch, \& Joulin, 2018).
+Bojanowski, Puhrsch, \& Joulin, 2018). fastText has also been shown to
+be sensitive towards cultural effects on word meanings: Thompson \&
+Lupyan (2020) showed that the distribution of semantic meaning clusters
+generated by fastText trained on language-specific corpora correlates to
+the cultural, historical and geographical distances of such languages
+languages. This is a proof of concept for our use of fastText in
+different languages with varying levels of relatedness.
 
-Word embeddings like fastText have been demonstrated to be good
-predictors for similarity judgments (Liu, Feng, Wu, Chan, \& Fulton
-(2019), Jatnika, Bijaksana, \& Suryani (2019)). fastText has also been
-shown to be sensitive towards cultural effects on word meanings:
-Thompson \& Lupyan (2020) showed that the distribution of semantic
-meaning clusters generated by fastText trained on language-specific
-corpora correlates to the cultural, historical and geographical
-distances of such languages languages. This is a proof of concept for
-our use of fastText in different languages with varying levels of
-relatedness.
+We note that language statistics can incorporate both cultural-specific
+environmental statistics (the inputs of similarity judgment) and
+taxonomic/thematic preferences (the conceptualization of similarity).
+For example, cultural features (farming) can lead to differences in
+environmental statistics (seeing cows and grass) and in turn these can
+influence language (talking more about cows and grass). But cultural
+features (preferring thematic relations) could also more directly cause
+individuals to talk differently about the same experiences (mentioning
+what cows eat rather than what other animals cows are like). Therefore,
+our approach looks at the extent to which language statistics can
+predict cross-cultural differences in similarity judgment with the
+understanding that language statistics is a proxy for both inputs and
+conceptualization of similarity judgment\footnote{However, in Q3, we
+  investigate whether differing culture-based conceptualization of
+  similarity has unique contribution to cross-cultural variation of
+  similarity jdugment.}.
 
@@
 
-Ji et al. (2004) suggest that the notion of similarity is what varies
-across cultural groups, but it is possible that similarity is regarded
-in the same way and it is actually the input to this similarity judgment
-that varies across cultural contexts. It may be possible to gain
-traction on potential mechanisms by examining whether variation in
-similarity judgments co-vary with environmental statistics that differ
-across cultural and linguistic contexts.
+Our study tests the hypothesis that, rather than (or in addition to) the
+variation in conceptualization of similarity across cultural groups,
+variation in the input to similarity judgment (namely, environmental
+statistics as proxied by language statistics) can be used to predict
+cross-cultural differences observed in how people evaluate similarity.
+We note that our study is correlational and cannot make a causal claim
+about the relationship of environmental statistics to similarity
+judgment, but it may be possible to gain traction on potential
+mechanisms by examining whether variation in similarity judgments covary
+with environmental statistics that differ across cultural and linguistic
+contexts. Our specific research questions are as follows:~
 
-In this study, we ask whether variation in lexical co-occurrence can
-account for the cross-context (culture and language) differences
-observed in how people evaluate similarity. First, we attempt to
-replicate Ji et al. (2004) by running a study comparing English speakers
-in the US and Mandarin speakers in mainland China. Second, we evaluate
-whether the differences observed between English and Mandarin speakers'
-similarity judgments also extend to comparisons between English and
-Vietnamese, by running a similar study between English speakers in the
-US and Vietnamese speakers in Vietnam. Vietnam is a Southeast Asian
-country that borders China and is historically greatly influenced by
-Chinese culture (Hui, 2002). Therefore, it serves as a suitable cultural
-context to investigate whether the claim made by Ji et al. (2004) and
-previous studies, that Eastern and Western cultures have different
-notions of similarity, extends beyond mainland China.
+Q1: Do we replicate Ji et al. (2004) and extend the results to another
+East Asian culture, namely Vietnam? Vietnam is a Southeast Asian country
+that borders China and is historically greatly influenced by Chinese
+culture (Hui, 2002). Therefore, it serves as a suitable cultural context
+to investigate whether the claim made by Ji et al. (2004) and previous
+studies, that Eastern and Western cultures have different notions of
+similarity, extends beyond mainland China.
 
-We then ask to what extent similarity judgments show cross-context
-differences that align with co-occurrence patterns in participants'
-languages. We would only see a main effect of cultural context if
-differing notions of similarity drive these cross-cultural differences.
-Meanwhile, if we do see variation in responding trial-to-trial that
-tracks with lexical co-occurrence statistics (as a rough proxy combining
-both linguistic and cultural context), this suggests that cross-cultural
-notions of similarity might be similar, and it is environmental
-statistics that guide the differences in similarity judgments.
+Q2: To what extent do cross-context environmental statistics (as proxied
+by language) align with variation in similarity judgment?
+
+Q3: Is there evidence for a unique contribution from conceptualization
+of similarity?
+
+Q4: Is language statistics viable as a standalone predictor, or is it
+simply measuring conceptualization of similarity in a different way?~
 
 To preview our results, we find that, while we do not find the predicted
-Eastern/Western contrast in notions of similarity in our Vietnam
-extension, we do find language-specific co-occurrence can indeed explain
-cross-context differences in similarity judgments. In contrast to
-previous accounts, by which culture induces differing conceptions of
-similarity (varying between taxonomic and thematic), these findings
-provide an alternative, and more specific, account by which language may
-explain these cross-cultural differences without invoking variation in
-notions of similarity.
-
-There are several important limitations of our approach. While we
-discuss cross-cultural variability at the level of countries or larger
-world areas, these are not cultural monoliths. For convenience, we
-operationalize culture at the level of country, based on where
-participants were raised. It is an open question whether performance in
-our participant populations (of relatively young and well-educated
-adults) is representative of the broader country. This is especially
-true for societies with substantial ethnic and cultural variation such
-as the US. We expect that our data is likely to underestimate variation
-both within and between the countries we sample from.
-
-Language, culture, cognition, and individual experiences are intertwined
-in complex causal relationships: cultural features (farming) can lead to
-differences in individuals' experiences (seeing cows and grass) and in
-turn these can influence language (talking more about cows and grass).
-But cultural features (a thematic orientation) could also more directly
-cause individuals to talk differently about the same experiences
-(mentioning what cows eat rather than what other animals cows are like).
-In this study, we measure language and its relation to cross-cultural
-differences in categorization, but these relations test only the
-plausibility of a language-based account; they cannot establish the
-direction of causality.
+Eastern/Western contrast in conceptualization of similarity in our
+Vietnam extension, we do find that both language-specific statistics and
+cultural contexts are a good predictor for cross-cultural differences in
+similarity judgments. Language statistics are also a good predictor for
+filler items with no taxonomic/thematic structure. Our findings are in
+contrast to previous accounts, by which culture induces differing
+conceptions of similarity (varying between taxonomic and thematic).
+these findings provide an alternative, and more specific, account by
+which language may explain these cross-cultural differences without
+invoking variation in notions of similarity.
 
@@
 We excluded 8 US participants, 62 Vietnam participants, and 16 China
-participants who did not answer 2 or more attention checks correctly. We
-followed 4 exclusion criteria that aim to retain only participants who
-are influenced by one culture: (1) non-native speakers of English and
+participants who missed 2 or more attention checks. We followed 4
+exclusion criteria that aim to retain only participants who are
+influenced by one culture: (1) non-native speakers of English and
 Vietnamese, respectively, (2) fluent in at least one of the other two
@@
   table summarizing number of participants lost at each round of
-  exclusions is included in the Appendix.}
+  exclusions is included in the Supplementary Information.}
 
-Notably, we lost a majority of our Vietnam participants (more than 60\%)
-in the attention check exclusion. One reason we suspect why this might
-have happened is because our Vietnam participants are less familiar with
-research surveys and attention check questions, and thus might have
-thought too much about the attention check questions.\footnote{We
-  carried out an exploratory analysis where we used a less stringent
-  attention check exclusion, and did not find any difference in
-  significant results when compared with the main analysis (see
-  Appendix).}
+We preregistered a more stringent exclusion criterion where participants
+were excluded if they missed any attention checks. However, this led to
+a small sample size, especially for Vietnam context (US = 109, China =
+132, Vietnam = 57). Our reported results with the less stringent
+exclusion criterion (detailed above) is largely not different from the
+results with the preregistered criterion. Any differences are noted in
+the Analysis section.
 
-\hypertarget{stimuli}{%
-\subsection{Stimuli}\label{stimuli}}
+\hypertarget{stimuli-materials}{%
+\subsection{Stimuli Materials}\label{stimuli-materials}}
 
@@
 English by another fluent bilingual in each language who was naive to
-the original English versions. --\textgreater{}
+the original English versions. All materials are included in the
+Supplementary Information.
+
+\hypertarget{procedure}{%
+\subsection{Procedure}\label{procedure}}
 
@@
 selecting the match most related to the cue (``Which thing is most
-closely related to the bolded item?'' or ``Thứ nào liên quan nhất với
-thứ được in đậm?''). The test triads were presented with 105 filler
-triads mixed in, to obscure the taxonomic-thematic two-answer forced
-choice structure of the test stimuli and reduce the likelihood that
-participants would become aware of the design. The filler triads were
-groups of three semantically related words, but where the match options
-were not distinguished by thematic vs.~taxonomic similarity, e.g., cue
-``bird'' with match options ``lizard'' and ``toad.'' Additionally, we
-included 10 attention check trials, which were formatted like the test
-and filler triads but included an instruction instead of a cue item,
-e.g., ``Choose wife'' with match options ``wife'' and ``husband.'' In
-total, each participant completed 210 similarity judgments and 10
-attention check questions, with triads presented in randomized orders
-that varied between subjects.
+closely related to the bolded item?'' and translated equivalents). The
+test triads were presented with 105 filler triads mixed in, to obscure
+the taxonomic-thematic two-answer forced choice structure of the test
+stimuli and reduce the likelihood that participants would become aware
+of the design. The filler triads were groups of three semantically
+related words, but where the match options were not distinguished by
+thematic vs.~taxonomic similarity, e.g., cue ``bird'' with match options
+``lizard'' and ``toad.'' Additionally, we included 10 attention check
+trials, which were formatted like the test and filler triads but
+included an instruction instead of a cue item, e.g., ``Choose wife''
+with match options ``wife'' and ``husband.'' In total, each participant
+completed 210 similarity judgments and 10 attention check questions,
+with triads presented in randomized orders that varied between subjects.
 
@@
 
-To give an intuition for our model, consider again the cow-grass-chicken
-triad: we retrieved word vectors for ``cow'' and ``grass'', and
-calculate the cosine distance between these vectors. Similarly, we
-retrieved vectors for ``cow'' and ``chicken'' and calculate the cosine
-distance between them. Our similarity prediction is then inversely
-proportional to the cosine distance of these pairs. This is because a
-larger cosine distance means the word vectors are further apart, and
-thus the words are less similar. For example, if the cosine distance of
-thematic cow-grass is 0.7 and the cosine distance of taxonomic
-cow-chicken is 0.3, then our model predicts, correspondingly, that 30\%
-of responses to the triad will be grass, and the other 70\% chicken. We
-then use a mixed-effects regression to evaluate how well each corpus
-model predicts participants' similarity judgments, across triads and
-languages.
+Our general approach is to predict behavioral preferences in similarity
+judgment using relative similarity between word embeddings.
 
@@
 Bag of Words (CBOW) with position-weights and a window of size 5. The
-models use character n-grams of length 5 and 10 negative examples.From
+models use character n-grams of length 5 and 10 negative examples. From
 the aforementioned models, we retrieve the word vectors (dimension 300)
@@
 
-From the word vectors, we calculated the cosine distance between each
-cue-thematic match (thematic cosine distance) and cue-taxonomic match
-(taxonomic cosine distance), using the spatial.distance.cosine function
-from the SciPy package (Virtanen et al., 2020). We then calculated the
-thematic cosine distance proportion as thematic cosine distance over the
-sum of taxonomic cosine distance and thematic cosine distance. We did
-this for all three corpora. We were able to obtain predictions for all
-triads in all languages.
+To give an intuition for our model, consider again the cow-grass-chicken
+triad: we retrieved word vectors for ``cow'' and ``grass'', and
+calculate the cosine distance between these vectors. Similarly, we
+retrieved vectors for ``cow'' and ``chicken'' and calculate the cosine
+distance between them. Our similarity prediction is then inversely
+proportional to the ratio of cosine distance of these pairs. This is
+because a larger cosine distance means the word vectors are further
+apart, and thus the words are less similar. For example, if the cosine
+distance of thematic cow-grass is 0.7 and the cosine distance of
+taxonomic cow-chicken is 0.3, then our model predicts, correspondingly,
+that 30\% of responses to the triad will be grass, and the other 70\%
+chicken.
+
+In practice, we calculated the cosine distance between each cue-thematic
+match (thematic cosine distance) and cue-taxonomic match (taxonomic
+cosine distance), using the spatial.distance.cosine function from the
+SciPy package (Virtanen et al., 2020). We then calculated the thematic
+cosine distance proportion as thematic cosine distance over the sum of
+taxonomic cosine distance and thematic cosine distance. We did this for
+all three corpora. We were able to obtain predictions for all triads in
+all languages. We then use a mixed-effects regression to evaluate how
+well each corpus model predicts participants' similarity judgments,
+across triads and cultural contexts.
 
@@
 
-\hypertarget{do-we-extend-previous-work-reporting-a-preference-for-taxonomic-matching-in-the-us-and-thematic-matching-in-asia}{%
-\subsection{1. Do we extend previous work reporting a preference for
-taxonomic matching in the US and thematic matching in
-Asia?}\label{do-we-extend-previous-work-reporting-a-preference-for-taxonomic-matching-in-the-us-and-thematic-matching-in-asia}}
+\hypertarget{replication-of-previous-work-and-extension-to-a-vietnamese-sample}{%
+\subsection{1. Replication of previous work and extension to a
+Vietnamese
+sample}\label{replication-of-previous-work-and-extension-to-a-vietnamese-sample}}
+
+Following previous work, we would expect participants from mainland
+China to prefer thematic matches more than US participants (to use the
+cow-grass-chicken triad: we would expect participants from mainland
+China to prefer the cow-grass match over the cow-chicken match to a
+larger extent compared to US participants). We would also expect that
+participants from Vietnam would pattern with China, and also show a
+significantly higher preference for thematic matches compare to US
+participants.
 
@@
 per subject and one per triad, as well as by-triad random slopes for
-country to account for variation in the country effect across triads. In
-R syntax, the model is: response \textasciitilde{} country + (1
-\textbar{} subject) + (country \textbar{} triad).
+country to account for variation in the country effect across triads.
 
@@
 
-\hypertarget{can-the-differences-in-similarity-judgments-between-english-mandarin-and-vietnamese-speakers-be-explained-by-variation-in-lexical-statistics}{%
-\subsection{2. Can the differences in similarity judgments between
-English, Mandarin and Vietnamese speakers be explained by variation in
-lexical
-statistics?}\label{can-the-differences-in-similarity-judgments-between-english-mandarin-and-vietnamese-speakers-be-explained-by-variation-in-lexical-statistics}}
+\hypertarget{language-statistics-as-a-predictor-for-cross-cultural-variation-in-similarity-judgments}{%
+\subsection{2. Language statistics as a predictor for cross-cultural
+variation in similarity
+judgments}\label{language-statistics-as-a-predictor-for-cross-cultural-variation-in-similarity-judgments}}
 
-\hypertarget{is-responding-in-each-cultural-context-predicted-by-lexical-statistics}{%
-\subsubsection{Is responding in each cultural context predicted by
-lexical
-statistics?}\label{is-responding-in-each-cultural-context-predicted-by-lexical-statistics}}
+\hypertarget{single-corpus-model}{%
+\subsubsection{Single corpus model}\label{single-corpus-model}}
 
-To test whether variation in lexical statistics can explain differences
+To test whether variation in language statistics can explain differences
 in similarity judgments between US and Vietnam participants, we compare
@@
 of cosine distance) as a fixed effect and participant and triad as
-random effects.
+random effects. If environmental statistics (as proxied by language
+statistics) contribute to the differences in similarity judgments, we
+would expect each language corpus to be a good predictor for similarity
+judgment responding in its corresponding context.
 
@@
 context responding, with p \textless{} 0.05 and \(\beta\) from -8.69 to
--2.4. (For a full report, see Appendix.)
+-2.4. (For a full report, see Supplementary Information.)
 
-\hypertarget{is-responding-in-each-cultural-context-best-predicted-by-the-corresponding-corpuss-lexical-statistics-as-opposed-to-the-other-two-corpora}{%
-\subsubsection{Is responding in each cultural context best predicted by
-the corresponding corpus's lexical statistics, as opposed to the other
-two
-corpora?}\label{is-responding-in-each-cultural-context-best-predicted-by-the-corresponding-corpuss-lexical-statistics-as-opposed-to-the-other-two-corpora}}
+While each corpus is a good predictor for its corresponding context, the
+fact that all corpora covary with all cultural contexts suggests that
+language is such a rich proxy of human experience that even using the
+wrong proxy (e.g.~Mandarin for US responding) is informative. A single
+corpus model might therefore not be informative in culture-specific
+ways, but might only reflect consistency in experiences across cultures.
 
-Next, we directly compare the corpus models by including both as fixed
-effects in three mixed-effect regressions (predicting US, Vietnam and
-China responding) with the same random effects as above. In R syntax,
-the model is: response \textasciitilde{} corpus\_English +
-corpus\_Vietnamese + corpus\_Mandarin + (1\textbar triad) +
-(1\textbar subject).
+\hypertarget{multiple-corpora-model}{%
+\subsubsection{Multiple corpora model}\label{multiple-corpora-model}}
 
-For US responding: English (EN), Vietnamese (VI), and Mandarin (ZH)
-corpus are all significant predictors. EN corpus: \(\beta\) = -6.96,
-\(\chi^2\)(1) = 16.57, p \textless{} .001. VI corpus: \(\beta\) = -2.22,
-\(\chi^2\)(1) = 3.73, p = 0.054. ZH corpus: \(\beta\) = -3.18,
-\(\chi^2\)(1) = 3.37, p = 0.066.
+If language statistics is able to predict meaningful culture-specific
+variation in similarity judgment (rather than just consistency across
+cultures), we would expect each corpus to be the best predictor of its
+corresponding culture compared to the other two corpora. We directly
+compare the corpus models by including both as fixed effects in three
+mixed-effect regressions (predicting US, Vietnam and China responding)
+with the same random effects as above.
 
-For Vietnam responding: English (EN), Vietnamese (VI), and Mandarin (ZH)
-corpus are all significant predictors. EN corpus: \(\beta\) = -2.98,
-\(\chi^2\)(1) = 2.58, p = 0.108. VI corpus: \(\beta\) = -2.75,
-\(\chi^2\)(1) = 4.84, p = 0.028. ZH corpus: \(\beta\) = -4.39,
+For US responding: only the English (EN) corpus is a significant
+predictor\footnote{With preregistered exclusion criterion: only the
+  English (EN) and Mandarin (ZH) corpus are significant predictors.}. EN
+corpus: \(\beta\) = -6.96, \(\chi^2\)(1) = 16.57, p \textless{} .001. VI
+corpus: \(\beta\) = -2.22, \(\chi^2\)(1) = 3.73, p = 0.054. ZH corpus:
+\(\beta\) = -3.18, \(\chi^2\)(1) = 3.37, p = 0.066.
+
+For Vietnam responding: only the Vietnamese (VI) and Mandarin (ZH)
+corpus are significant predictors\footnote{With preregistered exclusion
+  criterion: all three corpora are significant predictors.}. EN corpus:
+\(\beta\) = -2.98, \(\chi^2\)(1) = 2.58, p = 0.108. VI corpus: \(\beta\)
+= -2.75, \(\chi^2\)(1) = 4.84, p = 0.028. ZH corpus: \(\beta\) = -4.39,
 \(\chi^2\)(1) = 5.49, p = 0.019.
 
-For China responding: English (EN), Vietnamese (VI), and Mandarin (ZH)
-corpus are all significant predictors. EN corpus: \(\beta\) = -3.32,
-\(\chi^2\)(1) = 7.18, p = 0.007. VI corpus: \(\beta\) = -1.59,
-\(\chi^2\)(1) = 3.63, p = 0.057. ZH corpus: \(\beta\) = -5.31,
-\(\chi^2\)(1) = 17.69, p \textless{} .001.
+For China responding: only the Mandarin (ZH) and English (EN) corpus are
+significant predictors. EN corpus: \(\beta\) = -3.32, \(\chi^2\)(1) =
+7.18, p = 0.007. VI corpus: \(\beta\) = -1.59, \(\chi^2\)(1) = 3.63, p =
+0.057. ZH corpus: \(\beta\) = -5.31, \(\chi^2\)(1) = 17.69, p
+\textless{} .001.
 
@@
 Vietnamese corpus is still a significant predictor for the Vietnam
-responding (Figure 2).
+responding (Figure 2). These results strengthens our hypothesis that
+variation in inputs to similarity judgment (as proxied by language
+statistics) can predict cross-cultural variations of similarity
+judgment.
 
@@
 
-However, we found that language specificity alone does not explain our
-results. We used an ANOVA to compare the model with only the
-corresponding corpus, and the model with all 3 corpora for each cultural
-context. We found that in all three cases (US, China, Vietnam), adding
-the other two corpora produces a significantly better fit than the
-identical model without the additional corpora, and only the
-corresponding corpus included as a predictor (US response: \(\chi^2\)(2)
-= 7.93, p = 0.019; Vietnam response: \(\chi^2\)(2) = 13.72, p = 0.001;
-China response: \(\chi^2\)(2) = 10.56, p = 0.005).
+However, in all cultural contexts, adding the other two corpora produces
+a significantly better fit than the identical model without the
+additional corpora, and only the corresponding corpus included as a
+predictor (US response: \(\chi^2\)(2) = 7.93, p = 0.019; Vietnam
+response: \(\chi^2\)(2) = 13.72, p = 0.001; China response:
+\(\chi^2\)(2) = 10.56, p = 0.005). This analysis suggests that
+culture-specific inputs to similarity judgment (as proxied by language
+statistics) do not fully explain cross-cultural differences in
+similarity judgment.
 
-\hypertarget{does-similarity-reasoning-differ-across-cultures-only-the-input-to-it-or-both}{%
-\subsection{3. Does similarity reasoning differ across cultures, only
-the input to it, or
-both?}\label{does-similarity-reasoning-differ-across-cultures-only-the-input-to-it-or-both}}
+\hypertarget{cultural-context-as-a-predictor-for-cross-cultural-variation-in-similarity-judgments}{%
+\subsection{3. Cultural context as a predictor for cross-cultural
+variation in similarity
+judgments}\label{cultural-context-as-a-predictor-for-cross-cultural-variation-in-similarity-judgments}}
 
-Our analysis shows that lexical statistics of each corpus is a
-significant predictor for similarity judgment in the corresponding
-cultural context, even without the addition of the other two corpora.
-Assuming that lexical statistics is a good proxy for environmental
-statistics, we take the above result as evidence that cross-cultural
-differences in input to the process of similarity judgment at least
-partially drives cross-cultural similarity judgment differences.
-However, it is still an open question whether the nature of similarity
-judgment (for e.g., the notion of similarity) itself differs across
-cultures and contributes to cross-cultural differences in similarity
-judgment responding. In an alternative hypothesis, the cross-cultural
-differences in similarity judgment observed is driven by not only the
-input, but also an interaction between cultural-specific nature of
-similarity judgment and input. To test this hypothesis, we
-operationalize cultural-specific nature of similarity judgment as
-country context, and input to similarity judgment as the corresponding
-corpus statistics. We then compare a model that includes country,
-corresponding corpus statistics and their interaction as fixed effects
-(R syntax: responses \textasciitilde{} corresponding\_corpus * country +
-(1\textbar triad) + (1\textbar subject)) to a model with only the
-corresponding corpus statistics as the fixed effect (R syntax: responses
-\textasciitilde{} corresponding\_corpus + (1\textbar triad) +
-(1\textbar subject))
+Our above models tested whether language statistics is a good predictor
+for similarity judgment. As we noted above, language statistics can be a
+proxy of both inputs and conceptualization of similarity. However, it is
+still an open question whether conceptualization of similarity itself
+has a unique contribution to similarity judgment (beyond its influence
+on language statistics). To test this hypothesis, we operationalize
+cultural-specific conceptualization of similarity as country. We then
+compare a model that includes country, corresponding corpus statistics
+and their interaction as fixed effects to a model with only the
+corresponding corpus statistics as the fixed effect. If
+conceptualization of similarity has a unique contribution to similarity
+judgment, we should see that terms including country to be a significant
+predictor of responding.
 
@@
 \(\chi^2\)(1) = 75.58, p \textless{} .001). When adding country and
-interaction between country and corpus, both the corpus statistics
-(\(\beta\) = -1.72, \(\chi^2\)(1) = 23.34, p \textless{} .001) and
+interaction between country and corpus, corpus statistics (\(\beta\) =
+-1.72, \(\chi^2\)(1) = 23.34, p \textless{} .001), country (F(2,
+\ensuremath{\infty{}}) = 13.18, \(\chi^2\)(2) = 7.39, p = 0.025), and
 interaction between country and corpus (F(2, \ensuremath{\infty{}}) =
-6.66, \(\chi^2\)(2) = 13.33, p = 0.001) are significant predictors. This
-suggests that there are cross-cultural differences in both input and
-nature of similarity judgment that drive differences in similarity
-judgment responding. We found no effects of country (F(2,
-\ensuremath{\infty{}}) = 13.18, \(\chi^2\)(2) = 7.39, p = 0.025).
+6.66, \(\chi^2\)(2) = 13.33, p = 0.001), are significant
+predictors\footnote{With preregistered exclusion criterion: only corpus
+  statistics and interaction between country and corpus are significant
+  predictors.}. Including the country and country-corpus terms to the
+language-only model significantly its ability to explain variation in
+responding (\(\chi^2\)(4) = 40.76, p \textless{} .001). This result
+points to a unique contribution by culture-specific ways of
+conceptualizing similarity to similarity judgment that is not captured
+in language statistics.
 
-\hypertarget{how-general-are-the-cross-language-differences-in-similarity-judgments-we-observe-are-they-limited-to-taxonomic-thematic-contrasts-or-do-they-extend-to-other-cases}{%
-\subsection{4. How general are the cross-language differences in
-similarity judgments we observe? Are they limited to taxonomic-thematic
-contrasts or do they extend to other
-cases?}\label{how-general-are-the-cross-language-differences-in-similarity-judgments-we-observe-are-they-limited-to-taxonomic-thematic-contrasts-or-do-they-extend-to-other-cases}}
+\hypertarget{language-statistics-as-a-predictor-for-non-structured-triad-items}{%
+\subsection{4. Language statistics as a predictor for non-structured
+triad
+items}\label{language-statistics-as-a-predictor-for-non-structured-triad-items}}
 
-Previous work using the triad task such as Ji et al. (2004) has focused
-on contrasting taxonomic-thematic match preferences, driven by a theory
-of cross-cultural differences in notions of similarity. Meanwhile, our
-approach has shown that notions of similarity only has an effect on
-cross-cultural differences in similarity judgment when modulated by
-input, and that input as proxied by lexical statistics of the
-corresponding corpus by itself is a significant predictor for similarity
-judgment responding. Our approach using lexical statistics do not assume
-a taxonomic/thematic structure in the triads. Therefore, it should be
-possible to predict similarity judgments to triads that do not follow a
-taxonomic/thematic structure, such as our filler triads. If our approach
-is tractable, we should be able to repeat the above analyses to the
-filler triads, and find that lexical statistics of each corpus is a
-significant predictor for similarity judgments in filler triads of the
-corresponding cultural context.
+A possible concern with our approach is that variation in language
+statistics (which we claim to be a proxy of both inputs and
+conceptualization of similarity) can be fully explained by variation in
+conceptualization of similarity (i.e.~the difference in similarity
+measures between `cow' and `grass' versus `cow' and `chicken' in one
+corpus is solely driven by the corresponding culture's preference of
+thematic versus taxonomic categorization). Alternatively, language
+statistics may be measuring slight but pervasive differences in
+similarity driven by participants' different cultural contexts, rather
+than merely the type of similarity they generally prefer (thematic vs
+taxonomic relations). We address this concern by testing whether
+language statistics covary with similarity judgment of items with no
+taxonomic/thematic structures (filler items). If language statistics is
+only driven by conceptualization of similarity, we should not see an
+effect with such items, which have no structured similarity relations by
+which to make any predictions.~
 
@@
 For each filler triad, we randomly assigned one of the responding
-optiosn as `Word1'. Running a mixed-effects logistic regression predict
-responding (Word1 or Word2) with structure equivalent to Analysis 1, we
-found no effect of country on filler responding (Figure 3).
+options as `Word1'. Running a mixed-effects logistic regression to
+predict responding (Word1 or Word2) with country as the fixed effect and
+a random effect structure equivalent to Q1, we found no effect of
+country on filler responding (\(\chi^2\)(2) = 0.74, p = 0.692) (Figure
+3).
 
-\hypertarget{does-lexical-statistics-for-fillers-predict-responding-in-the-corresponding-cultural-context}{%
-\subsubsection{Does lexical statistics for fillers predict responding in
-the corresponding cultural
-context?}\label{does-lexical-statistics-for-fillers-predict-responding-in-the-corresponding-cultural-context}}
-
-Using the same mixed-effects logistic regression structure as Analysis
-2, we predict responses (1=word1 or 0=word2) with corpus prediction
-(proportion of cosine distance) as a fixed effect and participant and
+Using the same mixed-effects logistic regression structure as Q2, we
+predict responses (1=word1 or 0=word2) of each cultural context with the
+corresponding corpus statistics as a fixed effect, and participant and
 triad as random effects. We found that in all cultural contexts, the
-correpsonding corpora is a significant predictor of responding, with
-p\textless0.05 and \(\beta\) from -9.59 to -3.14. (For a full report,
-see Appendix.)
+corresponding corpus is a significant predictor of responding, with p
+\textless{} 0.05 and \(\beta\) from -9.59 to -3.14. (For a full report,
+see Supplementary Information.)
 
@@
 
-In this paper, we consider whether statistics of the language
-environment can account for cross-cultural differences in a classic
-similarity judgment paradigm, as an alternative to the view that members
-of different cultures vary in their conception of similarity. We found
-that each corpus statistics is a good predictor for the corresponding
-country's similarity judgments. When corresponding corpus statistics,
-country and corpus-country interactions were included as fixed effects
-to predict similarity judgments, we found no effects of country, but
-both corpus statistics and corpus-country interaction are significant
-predictors. Our results provide evidence that cross-cultural differences
-in similarity judgment might not be driven by cross-cultural differences
-in conception of similarity alone, but rather by statistics to
-similarity judgment and its interaction with similarity conception. We
-also showed that corpus statistics predict similarity judgments for
-triads that do not have taxonomic/thematic structure.
-
-We first tested the generality of a cultural account which holds that
-people from Western and East Asian cultures tend to conceive of
-similarity in more taxonomic and thematic ways, respectively, and
-respond accordingly in categorization tasks such as ours. While we
-managed to replicate the previously documented contrast between English
-speakers in the US and Mandarin Chinese speakers from East Asia
-(mainland China, Taiwan, Hong Kong, and Singapore), we do not extend
-this contrast to our sample of Vietnamese speakers in Vietnam and
-English speakers in the US. This finding suggests some limitations on
-the generality of this cultural account.
-
-We did find some signatures of language specificity in our analysis:
+In this paper, we consider whether statistics of the environment (as
+proxied by langauge statistics) can account for cross-cultural
+differences in a classic similarity judgment paradigm, as an alternative
+to the view that members of different cultures vary in their
+conceptualization of similarity. While we managed to replicate the
+previously documented contrast between English speakers in the US and
+Mandarin Chinese speakers from East Asia (mainland China, Taiwan, Hong
+Kong, and Singapore), we do not extend this contrast to our sample of
+Vietnamese speakers in Vietnam and English speakers in the US. This
+finding suggests some limitations on the generality of the cultural
+account. We found some support for the environmental statistics account:
 each corpus statistics is a good predictor for the corresponding
 country's similarity judgments, even when other corpus statistics are
-included. However, we also find evidence for consistency across the
-three cultural groups: each corpus statistics is also a good predictor
-for the other two non-corresponding cultural contexts when included as
-the only predictor, and both English and Mandarin Chinese statistics are
-good predictors for their non-corresponding cultural contexts when all
-three corpora are included.
+included, and even with triads without a taxonomic/thematic structure.
+However, we also found that culture-based conceptualization of
+similarity uniquely contributes to predicting similarity judgment when
+included in a model with corpus statistics. Overall, our results provide
+evidence that cross-cultural differences in similarity judgment might
+not be driven by cross-cultural differences in conception of similarity
+alone, but also by variation in inputs to similarity judgment.
 
-When all cultural contexts are taken together, we found that both
-corresponding corpus statistics and an interaction between corpus and
-country are significant predictors for similarity judgments. This result
-suggests that in addition to input to similarity judgment,
-country-specific categorical differences in similarity judgment (for
-e.g., how each culture conceive of similarity) also predict
-cross-cultural differences in similarity judgment behavior while
-modulated by input.
+There are some important limitations of our approach. While we discuss
+cross-cultural variability at the level of countries or larger world
+areas, these are not cultural monoliths. For convenience, we
+operationalize culture at the level of country, based on where
+participants were raised. It is an open question whether performance in
+our participant populations (of relatively young and well-educated
+adults) is representative of the broader country. This is especially
+true for societies with substantial ethnic and cultural variation such
+as the US. We expect that our data is likely to underestimate variation
+both within and between the countries we sample from.
 
-Even in triads with no taxonomic / thematic structure, each corpus
-statistics is still a good predictor of the corresponding country's
-similarity judgments. The ability of corpus statistics to predict
-similarity judgments in non-structured triads suggests that
-cross-cultural differences in similarity judgments should be construed
-in a more general and graded manner, as opposed to binary
-taxonomic/thematic match-preferring.
+Additionally, language, culture, cognition, and individual experiences
+are intertwined in complex causal relationships. In this study, we
+measure language and its relation to cross-cultural differences in
+categorization, but these relations test only the plausibility of a
+language-based account; they cannot establish the direction of
+causality.
 
@@
 and others? Can we provide a more specific computational account than
-the simple frequency model tested here?
+the simple proportion-of-similarity model tested here?
 
@@
 probing this question.
-
-\hypertarget{appendix}{%
-\section{Appendix}\label{appendix}}
-
-\hypertarget{icc-of-item-variability-and-participant-variability}{%
-\subsection{1. ICC of item variability and participant
-variability}\label{icc-of-item-variability-and-participant-variability}}
-
-\begin{table}[ht]
-\centering
-\begin{tabular}{lrr}
-  \hline
-Sample & Intra-rater ICC & Inter-rater ICC \\ 
-  \hline
-US & 0.30 & 0.97 \\ 
-  China & 0.19 & 0.96 \\ 
-  Vietnam & 0.27 & 0.97 \\ 
-   \hline
-\end{tabular}
-\caption{ICCs for reliability within participants (intra-rater) and stimuli (inter-rater) for all cultural contexts.} 
-\end{table}
-
-An intraclass correlation coefficients (ICCs) analysis with a two-way,
-non-interactive model (following the standard taxonomy for ICCs from
-McGraw \& Wong (1996)) showed that, per cultural context, participants'
-judgments were variable across triads, while inter-rater agreement about
-specific triads was quite high (Table 1). This result suggests that each
-triad prompts taxonomic / thematic matching reliably within culture.
-
-\hypertarget{supplemental-for-whether-each-corpus-predicts-similarity-judgment-in-each-cultural-context}{%
-\subsection{2. Supplemental for whether each corpus predicts similarity
-judgment in each cultural
-context}\label{supplemental-for-whether-each-corpus-predicts-similarity-judgment-in-each-cultural-context}}
-
-\hypertarget{triads}{%
-\subsubsection{Triads}\label{triads}}
-
-For US responding: English (EN), Vietnamese (VI), and Mandarin (ZH)
-corpus are significant predictors of US responding (EN-US model:
-\(\beta\) = -8.69, \(\chi^2\)(1) = 30.98, p \textless{} .001; VI-US
-model: \(\beta\) = -3.01, \(\chi^2\)(1) = 5.24, p = 0.022; ZH-US model:
-\(\beta\) = -6.97, \(\chi^2\)(1) = 17.62, p \textless{} .001).
-
-For Vietnam (VN) responding: English (EN), Vietnamese (VI), and Mandarin
-(ZH) corpus are significant predictors of VN responding (EN-VN model:
-\(\beta\) = -5.33, \(\chi^2\)(1) = 9.4, p = 0.002; VI-VN model:
-\(\beta\) = -3.46, \(\chi^2\)(1) = 6.8, p = 0.009; ZH-VN model:
-\(\beta\) = -6.37, \(\chi^2\)(1) = 13.84, p \textless{} .001).
-
-For China (CN) responding: English (EN), Vietnamese (VI), and Mandarin
-(ZH) corpus are significant predictors of CN responding (EN-CN model:
-\(\beta\) = -5.97, \(\chi^2\)(1) = 25.49, p \textless{} .001; VI-CN
-model: \(\beta\) = -2.4, \(\chi^2\)(1) = 5.91, p = 0.015; ZH-CN model:
-\(\beta\) = -7.22, \(\chi^2\)(1) = 39.24, p \textless{} .001).
-
-\hypertarget{fillers}{%
-\subsubsection{Fillers}\label{fillers}}
-
-English (EN) is a significant predictors of US responding (\(\beta\) =
--8.35, \(\chi^2\)(1) = 36.1, p \textless{} .001).
-
-Vietnamese (VI) is a significant predictors of Vietnam responding
-(\(\beta\) = -3.14, \(\chi^2\)(1) = 4.65, p = 0.031).
-
-Mandarin (ZH) is a significant predictors of China responding (\(\beta\)
-= -9.59, \(\chi^2\)(1) = 36.65, p \textless{} .001).
-
-\hypertarget{exclusion-statistics}{%
-\subsection{3. Exclusion Statistics}\label{exclusion-statistics}}
-
-\begin{tabular}[t]{l|c|c|c}
-\hline
-\multicolumn{1}{c|}{ } & \multicolumn{3}{c}{Country} \\
-\cline{2-4}
-  & US & China & Vietnam\\
-\hline
-Ppts Finished & 200 & 200 & 199\\
-\hline
-\multicolumn{4}{l}{\textbf{Attention Check Exclusions}}\\
-\hline
-\hspace{1em}Excluded & 26 & 34 & 123\\
-\hline
-\hspace{1em}After Exclusion & 174 & 166 & 76\\
-\hline
-\multicolumn{4}{l}{\textbf{Demographics Exclusions}}\\
-\hline
-\hspace{1em}Non-Native Speakers & 18 * & 3 * & 2 *\\
-\hline
-\hspace{1em}EN Speakers & N/A & 79 & 127\\
-\hline
-\hspace{1em}VI Speakers & 4 * & 1 * & N/A\\
-\hline
-\hspace{1em}ZH Speakers & 30 * & N/A & 9 *\\
-\hline
-\hspace{1em}Lived Abroad & 29 * & 40 * & 18 *\\
-\hline
-\hspace{1em}Overseas Experience & 77 & 12 * & 20 *\\
-\hline
-\hspace{1em}After Exclusions & 109 & 132 & 57\\
-\hline
-\end{tabular}
-
-\newpage
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-McGraw1996}{}}%
-McGraw, K. O., \& Wong, S. P. (1996). Forming inferences about some
-intraclass correlation coefficients. \emph{Psychological Methods},
-\emph{1}(1), 30.
-
 \leavevmode\vadjust pre{\hypertarget{ref-Mikolov2018}{}}%

### 2023-01-31 code/4_paper/manuscript/manuscript.Rmd
manuscript edits

@@
 document-params: "10pt, letterpaper"
-
 header-includes:
@@
   - \usepackage{kotex}
-
 author-information: > 
@@
     }
-
 abstract: >
@@
 We consider, and provide evidence for, an alternative possibility, by which notions of similarity are similar across contexts, but the statistics of the environment vary.
-On this account, similarity judgments are guided by co-occurrence in experience, and observing or hearing about cows and grass or cows and chickens more often could induce preferences for these groupings, and account in part for apparent differences in notions of similarity across contexts.
+On this account, similarity judgments are guided by co-occurrence in experience, and hearing about cows and grass or cows and chickens more often could induce preferences for these groupings, and account in part for apparent differences in notions of similarity across contexts.
 
@@
 #final-submission: \cogscifinalcopy
+editor_options: 
+  markdown: 
+    wrap: sentence
 ---
@@
 require(agreement)
+library("report")
 
@@
 
-## Cross-cultural variation in similarity
-
-The way we partition our continuous experiences of the world into categories, and which kind of similarity relationships we privilege to organize such partitions, vary across cultures.
+We constantly partition our continuous experience of the world into categories, but the way we organize these partitions can vary across cultures.
 One way this cross-cultural difference has been observed is with a task comparing preference for taxonomic and thematic similarity between East Asian and Western participants.[^1]
@@
 
-Previous research has linked the observed difference in similarity judgment to related work showing tendencies toward analytic processing (emphasizing objects and their properties) in Western cultures and holistic processing in East Asian cultures (emphasizing relationships between objects and their context) (see also @Nisbett2003).
-Cross-cultural difference in similarity judgment is thus connected to well-documented work showing East Asian participants exhibiting a higher level of sensitivity to context than their Western counterparts when reproducing drawings from memory [@Ji2000]; visually exploring naturalistic scenes [@Chua2005]; describing scenes [@Masuda2001]; and in explaining the causes of ambiguous behaviors [@Choi1999].
+One hypothesis is that differences in similarity judgment is linked to the tendency to see more analytic processing in Western culture and more holistic processing in East Asian cultures [@Nisbett2003].
+On this hypothesis, since analytic processing emphasizes relationships between objects and their properties, it leads to taxonomic similarity judgments; in contrast, holistic processing emphasizes relations between objects and leads to thematic similarity judgments.
+Cross-cultural difference in similarity judgment is thus connected to work showing East Asian participants exhibiting a higher level of sensitivity to context than their Western counterparts when reproducing drawings from memory [@Ji2000]; visually exploring naturalistic scenes [@Chua2005]; describing scenes [@Masuda2001]; and in explaining the causes of ambiguous behaviors [@Choi1999].
 This view ascribes cross-cultural differences in similarity judgment to variation in how each culture (or group of culture, i.e.
-East Asian vs Western) **conceptualize** similarity -- with East Asians preferring thematic relations more than Westerners.
+East Asian vs Western) *conceptualize* similarity -- with East Asians preferring thematic relations more than Westerners.
 
-Alternatively, these judgments could be shaped by cross-cultural differences in the **inputs** to similarity judgment, namely, the statistics of the environment, and accordingly the content of everyday experiences.
+Alternatively, these judgments could be shaped by cross-cultural differences in the *inputs* to similarity judgment, namely, the statistics of the environment, and accordingly the content of everyday experiences.
 Perhaps when faced with the triad task, participants from all cultures follow the same process for conceptualizing similarity, but rely on language or culture-specific inputs to this process.
-If we observe a difference in categorization between East Asian and Western participants, it could be that members of both groups use the same procedure (considering similarity that is influenced by both taxonomic and thematic relations), but the inputs to this procedure differ between cultures, with East Asian participants exposed to more instances of thematic similarity than their Western counterparts.
+If we observe a difference in categorization between East Asian and Western participants, it could be that members of both groups use the same procedure (considering similarity that is influenced by both taxonomic and thematic relations), but the inputs to this procedure differ between cultures, with East Asian participants exposed to more support for thematic similarity in the language they hear in comparison to their Western counterparts.
 We might also expect that both conceptualization and inputs of similarity play a role in driving cross-cultural differences -- East Asian participants may both be exposed to more instances of thematic similarity, and prefer to conceptualize similarity as thematic relations more so than Westerners.
@@
 Previous work also suggests that using language statistics (such as lexical co-occurrence or cosine distance of word embeddings) as a proxy can be a good predictor for similarity reasoning.
-@Griffiths2007 showed that a model trained on word-document co-occurrence can predict word association and the effects of semantic association on a variety of linguistic tasks.
+A model trained on word-document co-occurrence can predict word association and the effects of semantic association on a variety of linguistic tasks [@Griffiths2007].
 Lexical semantic models that are constructed using lexical co-occurrence (in comparison to annotated relations) have been shown to perform well on predicting human judgments about similarity between word pairs that are thematically or taxonomically related [@Rohde2006].
-Word embeddings like fastText have been demonstrated to be good predictors for similarity judgments (@Liu2019, @Jatnika2019).
+Word embeddings like word2vec, gloVe, and fastText have been demonstrated to be good predictors for similarity judgments (@Liu2019, @Jatnika2019).
 
@@
 Our study tests the hypothesis that, rather than (or in addition to) the variation in conceptualization of similarity across cultural groups, variation in the input to similarity judgment (namely, environmental statistics as proxied by language statistics) can be used to predict cross-cultural differences observed in how people evaluate similarity.
+
+We measured taxonomic versus thematic categorization in a word triad task in three populations.
+Following @Ji2004, we conducted our study in the US and China.
+In addition, we collected data in Vietnam, Vietnam is a Southeast Asian country that borders China and is historically greatly influenced by Chinese culture [@Hui2002].
+Therefore, it serves as a suitable cultural context to investigate whether the claim made by @Ji2004 and previous studies, that Eastern and Western cultures have different notions of similarity, extends beyond mainland China.
+We then tested if fastText vectors from the corresponding corpus (English, Mandarin, and Vietnamese) are good predictors for similarity judgment in each cultural context.
+
 We note that our study is correlational and cannot make a causal claim about the relationship of environmental statistics to similarity judgment, but it may be possible to gain traction on potential mechanisms by examining whether variation in similarity judgments covary with environmental statistics that differ across cultural and linguistic contexts.
@@
 
-Q1: Do we replicate @Ji2004 and extend the results to another East Asian culture, namely Vietnam?
-Vietnam is a Southeast Asian country that borders China and is historically greatly influenced by Chinese culture [@Hui2002].
-Therefore, it serves as a suitable cultural context to investigate whether the claim made by @Ji2004 and previous studies, that Eastern and Western cultures have different notions of similarity, extends beyond mainland China.
+Q1: Do we replicate cross-cultural differences in thematic/taxonomic categorization between East Asian and Western cultures?
 
-Q2: To what extent do cross-context environmental statistics (as proxied by language) align with variation in similarity judgment?
+Q2: Are these cross-cultural differences related to differences in lexical co-occurrence?
 
@@
 
-Q4: Is language statistics viable as a standalone predictor, or is it simply measuring conceptualization of similarity in a different way?
+Q4: Is the relationship with co-occurrence specific to taxonomic/thematic items, or can co-occurrence structure predict other judgments?
 
-To preview our results, we find that, while we do not find the predicted Eastern/Western contrast in conceptualization of similarity in our Vietnam extension, we do find that both language-specific statistics and cultural contexts are a good predictor for cross-cultural differences in similarity judgments.
+To preview our results, we replicate US-China differences and find that Vietnamese judgments are intermediate between these two.
+Further, language-specific statistics are a good predictor for cross-cultural differences in similarity judgments.
 Language statistics are also a good predictor for filler items with no taxonomic/thematic structure.
 Our findings are in contrast to previous accounts, by which culture induces differing conceptions of similarity (varying between taxonomic and thematic).
-these findings provide an alternative, and more specific, account by which language may explain these cross-cultural differences without invoking variation in notions of similarity.
+these findings provide an alternative account by which language may explain these cross-cultural differences without invoking variation in notions of similarity.
 
@@
 fit.language_cos.anova
+#report(fit.language_cos)
 
@@
 df.filler <- df.filler %>%
-  mutate(word1_match_freq_prop_corr_lang = case_when(
-    country == "US" ~ word1_match_frequency_prop_E,
-    country == "China" ~ word1_match_frequency_prop_M, 
-    country == "Vietnam" ~ word1_match_frequency_prop_V)) %>% 
-    mutate(word1_match_cosine_prop_corr_lang = case_when(
-    country == "US" ~ word1_match_cosine_prop_E,
-    country == "China" ~ word1_match_cosine_prop_M, 
-    country == "Vietnam" ~ word1_match_cosine_prop_V))
-
-df.filler <- df.filler %>%
   mutate(word1_match_freq_prop_corr_lang = ifelse(country == "US", 
@@
 
-```{r echo=FALSE, warning=FALSE, include = T, cache = TRUE, fig.env="figure", fig.align = "center", fig.cap="Proportion of Word1 responses by country."}
+```{r echo=FALSE, warning=FALSE, include = F, cache = TRUE, fig.env="figure", fig.align = "center", fig.cap="Proportion of Word1 responses by country."}
 #show violin plot
@@
 For each filler triad, we randomly assigned one of the responding options as 'Word1'.
-Running a mixed-effects logistic regression to predict responding (Word1 or Word2) with country as the fixed effect and a random effect structure equivalent to Q1, we found no effect of country on filler responding ($\chi^2$(`r fit.country_filler.anova["country", "Df"]`) = `r round(fit.country_filler.anova["country", "Chisq"], 2)`, p `r ifelse( fit.country_filler.anova["country", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.country_filler.anova["country", "Pr(>Chisq)"], 3)), "< .001")`) (Figure 3).
+Running a mixed-effects logistic regression to predict responding (Word1 or Word2) with country as the fixed effect and a random effect structure equivalent to Q1, we found no effect of country on filler responding ($\chi^2$(`r fit.country_filler.anova["country", "Df"]`) = `r round(fit.country_filler.anova["country", "Chisq"], 2)`, p `r ifelse( fit.country_filler.anova["country", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.country_filler.anova["country", "Pr(>Chisq)"], 3)), "< .001")`).
 
@@
 
-```{r combined filler and stimulus}
+```{r filler corresponding cosine, warning = F, include = F}
+fit.filler = glmer(responses_word1 ~ word1_match_cosine_prop_corr_lang + (1 | subject) + (1 | cue_id), 
+          data = df.filler,
+          family="binomial")
+summary(fit.filler)
+fit.filler.anova = Anova(fit.filler, type = 3)
+
+fit.filler.anova
+#report(fit.filler)
+```
+
+```{r combined filler and stimulus, warning = F, include = F}
 df.triad_filler <- rbind(
@@
 In this paper, we consider whether statistics of the environment (as proxied by language statistics) can account for cross-cultural differences in a classic similarity judgment paradigm, as an alternative to the view that members of different cultures vary in their conceptualization of similarity.
-While we managed to replicate the previously documented contrast between English speakers in the US and Mandarin Chinese speakers from East Asia (mainland China, Taiwan, Hong Kong, and Singapore), we do not extend this contrast to our sample of Vietnamese speakers in Vietnam and English speakers in the US.
-This finding suggests some limitations on the generality of the cultural account.
+We replicated the previously documented contrast between English speakers in the US and Mandarin Chinese speakers from East Asia (mainland China, Taiwan, Hong Kong, and Singapore), with mainland China participants preferring thematic relations to a greater extent compared to US participants.
+Our sample of Vietnamese participants showed intermediate response but not significantly different from either Chinese or US participants.
+This finding suggests some limitations on the generality of the cultural account, which proposes that thematic/taxonomic similarity preference maps onto
 We found some support for the environmental statistics account: each corpus statistics is a good predictor for the corresponding country's similarity judgments, even when other corpus statistics are included, and even with triads without a taxonomic/thematic structure.
 However, we also found that culture-based conceptualization of similarity uniquely contributes to predicting similarity judgment when included in a model with corpus statistics.
-Overall, our results provide evidence that cross-cultural differences in similarity judgment might not be driven by cross-cultural differences in conception of similarity alone, but also by variation in inputs to similarity judgment.
+Overall, our results provide evidence that cross-cultural differences in similarity judgment are related to linguistic co-occurrence patterns (which also vary across cultures).
 
@@
 # Acknowledgements
-
-Place acknowledgments (including funding information) in a section at the end of the paper.
+BLINDED FOR PEER REVIEW.
 

### 2023-01-31 code/4_paper/manuscript/manuscript.tex
manuscript edits

@@
 On this account, similarity judgments are guided by co-occurrence in
-experience, and observing or hearing about cows and grass or cows and
-chickens more often could induce preferences for these groupings, and
-account in part for apparent differences in notions of similarity across
-contexts.
+experience, and hearing about cows and grass or cows and chickens more
+often could induce preferences for these groupings, and account in part
+for apparent differences in notions of similarity across contexts.
 
@@
 
-\hypertarget{cross-cultural-variation-in-similarity}{%
-\subsection{Cross-cultural variation in
-similarity}\label{cross-cultural-variation-in-similarity}}
+We constantly partition our continuous experience of the world into
+categories, but the way we organize these partitions can vary across
+cultures. One way this cross-cultural difference has been observed is
+with a task comparing preference for taxonomic and thematic similarity
+between East Asian and Western participants.\footnote{Taxonomic
+  categorization is based on the similarity of attributes, for example,
+  similar perceptual properties, like shared color or shape, among
+  objects.In contrast, thematic categorization is based on causal,
+  spatial, and temporal relationships among objects (Markman \&
+  Hutchinson, 1984).} Ji, Zhang, \& Nisbett (2004) found that in a word
+triad task (choose two out of three words that are more related to one
+another), Chinese participants preferred thematic matching more compared
+to European Americans. In a pictorial version of this task, Chiu (1972)
+found that Chinese children (9-10 years old) are also more likely to
+choose thematic matches compared to their American counterparts. This
+cross-cultural difference is also observed in novel object
+categorization, with Chinese participants preferring to group by family
+resemblance across multiple features and Americans preferring a
+single-feature rule (Norenzayan, Smith, Kim, \& Nisbett, 2002).
 
-The way we partition our continuous experiences of the world into
-categories, and which kind of similarity relationships we privilege to
-organize such partitions, vary across cultures. One way this
-cross-cultural difference has been observed is with a task comparing
-preference for taxonomic and thematic similarity between East Asian and
-Western participants.\footnote{Taxonomic categorization is based on the
-  similarity of attributes, for example, similar perceptual properties,
-  like shared color or shape, among objects.In contrast, thematic
-  categorization is based on causal, spatial, and temporal relationships
-  among objects (Markman \& Hutchinson, 1984).} Ji, Zhang, \& Nisbett
-(2004) found that in a word triad task (choose two out of three words
-that are more related to one another), Chinese participants preferred
-thematic matching more compared to European Americans. In a pictorial
-version of this task, Chiu (1972) found that Chinese children (9-10
-years old) are also more likely to choose thematic matches compared to
-their American counterparts. This cross-cultural difference is also
-observed in novel object categorization, with Chinese participants
-preferring to group by family resemblance across multiple features and
-Americans preferring a single-feature rule (Norenzayan, Smith, Kim, \&
-Nisbett, 2002).
-
-Previous research has linked the observed difference in similarity
-judgment to related work showing tendencies toward analytic processing
-(emphasizing objects and their properties) in Western cultures and
-holistic processing in East Asian cultures (emphasizing relationships
-between objects and their context) (see also Nisbett (2003)).
-Cross-cultural difference in similarity judgment is thus connected to
-well-documented work showing East Asian participants exhibiting a higher
-level of sensitivity to context than their Western counterparts when
-reproducing drawings from memory (Ji, Peng, \& Nisbett, 2000); visually
-exploring naturalistic scenes (Chua, Boland, \& Nisbett, 2005);
-describing scenes (Masuda \& Nisbett, 2001); and in explaining the
-causes of ambiguous behaviors (Choi, Nisbett, \& Norenzayan, 1999). This
-view ascribes cross-cultural differences in similarity judgment to
-variation in how each culture (or group of culture, i.e.~East Asian vs
-Western) \textbf{conceptualize} similarity -- with East Asians
-preferring thematic relations more than Westerners.
+One hypothesis is that differences in similarity judgment is linked to
+the tendency to see more analytic processing in Western culture and more
+holistic processing in East Asian cultures (Nisbett (2003)). On this
+hypothesis, since analytic processing emphasizes relationships between
+objects and their properties, it leads to taxonomic similarity
+judgments; in contrast, holistic processing emphasizes relations between
+objects and leads to thematic similarity judgments. Cross-cultural
+difference in similarity judgment is thus connected to work showing East
+Asian participants exhibiting a higher level of sensitivity to context
+than their Western counterparts when reproducing drawings from memory
+(Ji, Peng, \& Nisbett, 2000); visually exploring naturalistic scenes
+(Chua, Boland, \& Nisbett, 2005); describing scenes (Masuda \& Nisbett,
+2001); and in explaining the causes of ambiguous behaviors (Choi,
+Nisbett, \& Norenzayan, 1999). This view ascribes cross-cultural
+differences in similarity judgment to variation in how each culture (or
+group of culture, i.e.~East Asian vs Western) \emph{conceptualize}
+similarity -- with East Asians preferring thematic relations more than
+Westerners.
 
 Alternatively, these judgments could be shaped by cross-cultural
-differences in the \textbf{inputs} to similarity judgment, namely, the
+differences in the \emph{inputs} to similarity judgment, namely, the
 statistics of the environment, and accordingly the content of everyday
@@
 and thematic relations), but the inputs to this procedure differ between
-cultures, with East Asian participants exposed to more instances of
-thematic similarity than their Western counterparts. We might also
-expect that both conceptualization and inputs of similarity play a role
-in driving cross-cultural differences -- East Asian participants may
-both be exposed to more instances of thematic similarity, and prefer to
-conceptualize similarity as thematic relations more so than Westerners.
+cultures, with East Asian participants exposed to more support for
+thematic similarity in the language they hear in comparison to their
+Western counterparts. We might also expect that both conceptualization
+and inputs of similarity play a role in driving cross-cultural
+differences -- East Asian participants may both be exposed to more
+instances of thematic similarity, and prefer to conceptualize similarity
+as thematic relations more so than Westerners.
 
@@
 lexical co-occurrence or cosine distance of word embeddings) as a proxy
-can be a good predictor for similarity reasoning. Griffiths, Steyvers,
-\& Tenenbaum (2007) showed that a model trained on word-document
-co-occurrence can predict word association and the effects of semantic
-association on a variety of linguistic tasks. Lexical semantic models
-that are constructed using lexical co-occurrence (in comparison to
-annotated relations) have been shown to perform well on predicting human
-judgments about similarity between word pairs that are thematically or
+can be a good predictor for similarity reasoning. A model trained on
+word-document co-occurrence can predict word association and the effects
+of semantic association on a variety of linguistic tasks (Griffiths,
+Steyvers, \& Tenenbaum, 2007). Lexical semantic models that are
+constructed using lexical co-occurrence (in comparison to annotated
+relations) have been shown to perform well on predicting human judgments
+about similarity between word pairs that are thematically or
 taxonomically related (Rohde, Gonnerman, \& Plaut, 2006). Word
-embeddings like fastText have been demonstrated to be good predictors
-for similarity judgments (Liu, Feng, Wu, Chan, \& Fulton (2019),
-Jatnika, Bijaksana, \& Suryani (2019)).
+embeddings like word2vec, gloVe, and fastText have been demonstrated to
+be good predictors for similarity judgments (Liu, Feng, Wu, Chan, \&
+Fulton (2019), Jatnika, Bijaksana, \& Suryani (2019)).
 
@@
 cross-cultural differences observed in how people evaluate similarity.
+
+We measured taxonomic versus thematic categorization in a word triad
+task in three populations. Following Ji et al. (2004), we conducted our
+study in the US and China. In addition, we collected data in Vietnam,
+Vietnam is a Southeast Asian country that borders China and is
+historically greatly influenced by Chinese culture (Hui, 2002).
+Therefore, it serves as a suitable cultural context to investigate
+whether the claim made by Ji et al. (2004) and previous studies, that
+Eastern and Western cultures have different notions of similarity,
+extends beyond mainland China. We then tested if fastText vectors from
+the corresponding corpus (English, Mandarin, and Vietnamese) are good
+predictors for similarity judgment in each cultural context.
+
 We note that our study is correlational and cannot make a causal claim
@@
 
-Q1: Do we replicate Ji et al. (2004) and extend the results to another
-East Asian culture, namely Vietnam? Vietnam is a Southeast Asian country
-that borders China and is historically greatly influenced by Chinese
-culture (Hui, 2002). Therefore, it serves as a suitable cultural context
-to investigate whether the claim made by Ji et al. (2004) and previous
-studies, that Eastern and Western cultures have different notions of
-similarity, extends beyond mainland China.
+Q1: Do we replicate cross-cultural differences in thematic/taxonomic
+categorization between East Asian and Western cultures?
 
-Q2: To what extent do cross-context environmental statistics (as proxied
-by language) align with variation in similarity judgment?
+Q2: Are these cross-cultural differences related to differences in
+lexical co-occurrence?
 
@@
 
-Q4: Is language statistics viable as a standalone predictor, or is it
-simply measuring conceptualization of similarity in a different way?~
+Q4: Is the relationship with co-occurrence specific to
+taxonomic/thematic items, or can co-occurrence structure predict other
+judgments?~
 
-To preview our results, we find that, while we do not find the predicted
-Eastern/Western contrast in conceptualization of similarity in our
-Vietnam extension, we do find that both language-specific statistics and
-cultural contexts are a good predictor for cross-cultural differences in
-similarity judgments. Language statistics are also a good predictor for
-filler items with no taxonomic/thematic structure. Our findings are in
-contrast to previous accounts, by which culture induces differing
-conceptions of similarity (varying between taxonomic and thematic).
-these findings provide an alternative, and more specific, account by
-which language may explain these cross-cultural differences without
-invoking variation in notions of similarity.
+To preview our results, we replicate US-China differences and find that
+Vietnamese judgments are intermediate between these two. Further,
+language-specific statistics are a good predictor for cross-cultural
+differences in similarity judgments. Language statistics are also a good
+predictor for filler items with no taxonomic/thematic structure. Our
+findings are in contrast to previous accounts, by which culture induces
+differing conceptions of similarity (varying between taxonomic and
+thematic). these findings provide an alternative account by which
+language may explain these cross-cultural differences without invoking
+variation in notions of similarity.
 
@@
 
-\begin{CodeChunk}
-\begin{figure}[tb]
-
-{\centering \includegraphics{figs/unnamed-chunk-4-1}
-
-}
-
-\caption[Proportion of Word1 responses by country]{Proportion of Word1 responses by country.}\label{fig:unnamed-chunk-4}
-\end{figure}
-\end{CodeChunk}
-
 For each filler triad, we randomly assigned one of the responding
@@
 a random effect structure equivalent to Q1, we found no effect of
-country on filler responding (\(\chi^2\)(2) = 0.74, p = 0.692) (Figure
-3).
+country on filler responding (\(\chi^2\)(2) = 0.74, p = 0.692).
 
@@
 In this paper, we consider whether statistics of the environment (as
-proxied by langauge statistics) can account for cross-cultural
+proxied by language statistics) can account for cross-cultural
 differences in a classic similarity judgment paradigm, as an alternative
@@
 included in a model with corpus statistics. Overall, our results provide
-evidence that cross-cultural differences in similarity judgment might
-not be driven by cross-cultural differences in conception of similarity
-alone, but also by variation in inputs to similarity judgment.
+evidence that cross-cultural differences in similarity judgment are
+related to linguistic co-occurrence patterns (which also vary across
+cultures).
 
@@
 
-Place acknowledgments (including funding information) in a section at
-the end of the paper.
+BLINDED FOR PEER REVIEW.
 

### 2023-02-01 code/4_paper/manuscript/manuscript.Rmd
edited intro for clarity

@@
 keywords: >
-    similarity; culture; language; semantics; lexical co-occurrence; variation
+    similarity; culture; language; semantics; lexical co-occurrence; variation; US; China; Vietnam
 
@@
 
-We constantly partition our continuous experience of the world into categories, but the way we organize these partitions can vary across cultures.
-One way this cross-cultural difference has been observed is with a task comparing preference for taxonomic and thematic similarity between East Asian and Western participants.[^1]
-@Ji2004 found that in a word triad task (choose two out of three words that are more related to one another), Chinese participants preferred thematic matching more compared to European Americans.
-In a pictorial version of this task, @Chiu1972 found that Chinese children (9-10 years old) are also more likely to choose thematic matches compared to their American counterparts.
+<!-- We constantly partition our continuous experience of the world into categories, but the way we organize these partitions can vary across cultures.-->
+
+Many cognitive processes rely on similarity, from inference and generalization to analogy, mathematics, and science.
+There is substantial consistency in human similarity reasoning, but also systematic variation across cultural and linguistic contexts.
+In particular, there is considerable evidence showing that similarity reasoning in East Asian cultural contexts differs from that in Western cultures (e.g.
+@Nisbett2003b).
+<!-- Khuyen could you add this ref as Nisbett2003b?  https://www.pnas.org/doi/10.1073/pnas.1934527100-->
+For example, in a triad task comparing preferences for taxonomic and thematic similarity (choose two out of three words that are most related to one another), @Ji2004 found that Chinese participants preferred thematic matching to a greater extent than European Americans.
+In an image version of this task, Chinese children (9-10 years old) are also more likely to choose thematic matches compared to their American counterparts [@Chiu1972].
 This cross-cultural difference is also observed in novel object categorization, with Chinese participants preferring to group by family resemblance across multiple features and Americans preferring a single-feature rule [@Norenzayan2002].
+Across tasks, East Asian participants show a preference for thematic similarity based on causal, spatial, and temporal relationships while Western participants are more likely to make taxonomic matches based on the similarity of attributes, like shared color or shape, among objects [see @Markman1984 for a discussion of these types of similarity].
 
-[^1]: Taxonomic categorization is based on the similarity of attributes, for example, similar perceptual properties, like shared color or shape, among objects.In contrast, thematic categorization is based on causal, spatial, and temporal relationships among objects [@Markman1984].
+An influential perspective within cultural psychology links these differences in similarity judgment to tendencies toward analytic processing in Western cultures, and holistic processing in East Asian cultures [@Nisbett2003].
+Analytic processing emphasizes rule-like relationships predicated on objects and their properties and, correspondingly, taxonomic similarity, while holistic processing emphasizes relations between objects and their context and therefor, thematic similarity.
+In related work, East Asian participants show a higher level of sensitivity to context than their Western counterparts when reproducing drawings from memory [@Ji2000]; visually exploring naturalistic scenes [@Chua2005]; describing scenes [@Masuda2001]; and in explaining the causes of ambiguous behaviors [@Choi1999].
+The consensus interpretation in this literature ascribes cross-cultural differences in similarity judgment to variation in the *conceptualization* of similarity -- with people from East Asian cultures relying on a more thematic notion of similarity than Westerners.
 
-One hypothesis is that differences in similarity judgment is linked to the tendency to see more analytic processing in Western culture and more holistic processing in East Asian cultures [@Nisbett2003].
-On this hypothesis, since analytic processing emphasizes relationships between objects and their properties, it leads to taxonomic similarity judgments; in contrast, holistic processing emphasizes relations between objects and leads to thematic similarity judgments.
-Cross-cultural difference in similarity judgment is thus connected to work showing East Asian participants exhibiting a higher level of sensitivity to context than their Western counterparts when reproducing drawings from memory [@Ji2000]; visually exploring naturalistic scenes [@Chua2005]; describing scenes [@Masuda2001]; and in explaining the causes of ambiguous behaviors [@Choi1999].
-This view ascribes cross-cultural differences in similarity judgment to variation in how each culture (or group of culture, i.e.
-East Asian vs Western) *conceptualize* similarity -- with East Asians preferring thematic relations more than Westerners.
-
-Alternatively, these judgments could be shaped by cross-cultural differences in the *inputs* to similarity judgment, namely, the statistics of the environment, and accordingly the content of everyday experiences.
+Alternatively, these judgments could be shaped by cross-cultural differences in the *inputs* to similarity judgment, that is, the statistics of the environment, and the content of everyday experiences.
 Perhaps when faced with the triad task, participants from all cultures follow the same process for conceptualizing similarity, but rely on language or culture-specific inputs to this process.
 If we observe a difference in categorization between East Asian and Western participants, it could be that members of both groups use the same procedure (considering similarity that is influenced by both taxonomic and thematic relations), but the inputs to this procedure differ between cultures, with East Asian participants exposed to more support for thematic similarity in the language they hear in comparison to their Western counterparts.
-We might also expect that both conceptualization and inputs of similarity play a role in driving cross-cultural differences -- East Asian participants may both be exposed to more instances of thematic similarity, and prefer to conceptualize similarity as thematic relations more so than Westerners.
+We might also expect that both conceptualization of similarity and inputs from experience play a role in driving cross-cultural differences -- East Asian participants may be exposed to more instances of thematic similarity, and prefer to conceptualize similarity as thematic to a greater extent than Westerners.
 

### 2023-02-01 code/4_paper/manuscript/manuscript.Rmd
finished intro updates

@@
 
-Alternatively, these judgments could be shaped by cross-cultural differences in the *inputs* to similarity judgment, that is, the statistics of the environment, and the content of everyday experiences.
-Perhaps when faced with the triad task, participants from all cultures follow the same process for conceptualizing similarity, but rely on language or culture-specific inputs to this process.
-If we observe a difference in categorization between East Asian and Western participants, it could be that members of both groups use the same procedure (considering similarity that is influenced by both taxonomic and thematic relations), but the inputs to this procedure differ between cultures, with East Asian participants exposed to more support for thematic similarity in the language they hear in comparison to their Western counterparts.
-We might also expect that both conceptualization of similarity and inputs from experience play a role in driving cross-cultural differences -- East Asian participants may be exposed to more instances of thematic similarity, and prefer to conceptualize similarity as thematic to a greater extent than Westerners.
+Alternatively, these judgments could be shaped by cross-cultural differences in the *input* to similarity judgment, that is, the statistics of the environment, and the content of everyday experiences.
+Perhaps when faced with the triad task, participants from all cultures follow the same process for conceptualizing similarity, but rely on language or culture-specific input to this process.
+If we observe a difference in categorization between East Asian and Western participants, it could be that members of both groups use the same procedure (considering similarity that is influenced by both taxonomic and thematic relations), but the input to this procedure differ between cultures, with East Asian participants exposed to more support for thematic similarity in the language they hear in comparison to their Western counterparts.
+We might also expect that both conceptualization of similarity and input from experience play a role in driving cross-cultural differences -- East Asian participants may be exposed to more instances of thematic similarity, and prefer to conceptualize similarity as thematic to a greater extent than Westerners.
 
@@
 
-To test alternative hypotheses involving variation of inputs to similarity judgment, we need a way to operationalize variation in exposure to thematic vs taxonomic relations.
-While this metric is difficult to directly measure, language statistics can provide a rough proxy.
-Language statistics is useful in that it is part of the inputs to everyday experiences (through spoken and written language), may afford many of the 'experiences' that people have with infrequently encountered items, like cows or helicopters, and provides accessible measures.
-Previous work also suggests that using language statistics (such as lexical co-occurrence or cosine distance of word embeddings) as a proxy can be a good predictor for similarity reasoning.
-A model trained on word-document co-occurrence can predict word association and the effects of semantic association on a variety of linguistic tasks [@Griffiths2007].
-Lexical semantic models that are constructed using lexical co-occurrence (in comparison to annotated relations) have been shown to perform well on predicting human judgments about similarity between word pairs that are thematically or taxonomically related [@Rohde2006].
-Word embeddings like word2vec, gloVe, and fastText have been demonstrated to be good predictors for similarity judgments (@Liu2019, @Jatnika2019).
+To determine whether varied input to similarity judgments can in part explain cross-cultural differences, we need a way to operationalize variation in exposure to thematic and taxonomic relations.
+While exposure to types of similarity is difficult to measure, the statistics of language can provide a rough proxy.
+Language statistics are useful in that they are part of the input to everyday experience -- and indeed, may afford many of the 'experiences' that people have with infrequently encountered items, like cows or helicopters -- and they provide an accessible measure.
+Previous work also suggests that language statistics, such as lexical co-occurrence or cosine distance of word embeddings, can be good predictors of similarity reasoning.
+Semantic models that are constructed using lexical co-occurrence (in comparison to annotated relations) have been shown to perform well on predicting human judgments about similarity between word pairs that are thematically or taxonomically related [@Rohde2006].
+Relatedly, a model trained on word-document co-occurrence can predict word association and the effects of semantic association on a variety of linguistic tasks [@Griffiths2007].
+Word embeddings like word2vec, gloVe, and fastText have also been shown to be good predictors for similarity judgments (@Liu2019, @Jatnika2019).
 
@@
 fastText is a system that uses lexical co-occurrence information to generate a vector representing each word in its lexicon [@Mikolov2018].
-fastText has also been shown to be sensitive towards cultural effects on word meanings: @Thompson2020 showed that the distribution of semantic meaning clusters generated by fastText trained on language-specific corpora correlates to the cultural, historical and geographical distances of such languages languages.
-This is a proof of concept for our use of fastText in different languages with varying levels of relatedness.
+fastText has also been shown to be sensitive to cultural differences in word meanings: @Thompson2020 demonstrated that the distribution of semantic meaning clusters generated by fastText trained on language-specific corpora correlates with the cultural, historical, and geographical similarities of these languages.
+<!-- This proof of concept provides support for our use of fastText in comparing different languages with varying levels of relatedness.-->
 
@@
 
-We note that language statistics can incorporate both cultural-specific environmental statistics (the inputs of similarity judgment) and taxonomic/thematic preferences (the conceptualization of similarity).
-For example, cultural features (farming) can lead to differences in environmental statistics (seeing cows and grass) and in turn these can influence language (talking more about cows and grass).
-But cultural features (preferring thematic relations) could also more directly cause individuals to talk differently about the same experiences (mentioning what cows eat rather than what other animals cows are like).
-Therefore, our approach looks at the extent to which language statistics can predict cross-cultural differences in similarity judgment with the understanding that language statistics is a proxy for both inputs and conceptualization of similarity judgment[^3].
-
-[^3]: However, in Q3, we investigate whether differing culture-based conceptualization of similarity has unique contribution to cross-cultural variation of similarity jdugment.
+We note that language statistics may incorporate both cultural-specific environmental statistics, that is, the experiential *input* to similarity judgments, and culture-specific senses of similarity, the *conceptualization* of similarity.
+For example, cultural features (like farming) can lead to differences in environmental statistics (seeing cows and grass) and these can influence language (talking more about cows and grass).
+But other cultural features (like conceiving of similarity thematically) could also cause individuals to talk differently about the same experiences (mentioning what cows eat rather than what other animals cows are like).
+Acoordingly, our approach examines the extent to which language statistics can predict cross-cultural differences in similarity judgments with the understanding that language statistics are likely a proxy for both *input* to and *conceptualization* of similarity.
 
@@
 ```
-Our study tests the hypothesis that, rather than (or in addition to) the variation in conceptualization of similarity across cultural groups, variation in the input to similarity judgment (namely, environmental statistics as proxied by language statistics) can be used to predict cross-cultural differences observed in how people evaluate similarity.
+The present study tests whether the statistics of language can be used to predict cross-cultural differences in similarity judgments, and particularly, whether this approach provides additional insight beyond cross-cultural characterizations based on taxonomic vs thematic preferences.
 
-We measured taxonomic versus thematic categorization in a word triad task in three populations.
-Following @Ji2004, we conducted our study in the US and China.
-In addition, we collected data in Vietnam, Vietnam is a Southeast Asian country that borders China and is historically greatly influenced by Chinese culture [@Hui2002].
-Therefore, it serves as a suitable cultural context to investigate whether the claim made by @Ji2004 and previous studies, that Eastern and Western cultures have different notions of similarity, extends beyond mainland China.
-We then tested if fastText vectors from the corresponding corpus (English, Mandarin, and Vietnamese) are good predictors for similarity judgment in each cultural context.
+We measured taxonomic versus thematic similarity matching in a forced-choice word triad task in three populations.
+Following @Ji2004, we measured preferences in the US and China.
+In addition, we collected data in a novel context: Vietnam.
+Vietnam is a Southeast Asian country that borders China and has historically been greatly influenced by Chinese culture [@Hui2002].
+Therefore, it serves as a suitable cultural context to investigate whether the claim made by @Ji2004 and previous studies -- that Eastern and Western cultures have different notions of similarity -- extends beyond mainland China.
+In addition to these replication and extension questions, we tested whether fastText vectors from corpora corresponding to each language context (English, Mandarin, and Vietnamese) are good predictors for similarity judgments in each population.
 
-We note that our study is correlational and cannot make a causal claim about the relationship of environmental statistics to similarity judgment, but it may be possible to gain traction on potential mechanisms by examining whether variation in similarity judgments covary with environmental statistics that differ across cultural and linguistic contexts.
+This study is correlational and cannot evaluate causal relationships between environmental statistics and similarity judgments.
+However, this work can inform potential mechanisms by examining whether similarity judgments covary with environmental statistics that differ across these contexts.
 Our specific research questions are as follows:
 
-Q1: Do we replicate cross-cultural differences in thematic/taxonomic categorization between East Asian and Western cultures?
+1. Do we replicate cross-cultural differences in similarity judgments between East Asian and Western cultures?
 
-Q2: Are these cross-cultural differences related to differences in lexical co-occurrence?
+2. Are these cross-cultural differences related to differences in language?
 
-Q3: Is there evidence for a unique contribution from conceptualization of similarity?
+3. Is there evidence for a unique contribution from *conceptualization* of similarity?
 
-Q4: Is the relationship with co-occurrence specific to taxonomic/thematic items, or can co-occurrence structure predict other judgments?
+4. Is our language model specific to items with a taxonomic-thematic contrast, or can it predict similarity more generally?
 
 To preview our results, we replicate US-China differences and find that Vietnamese judgments are intermediate between these two.
-Further, language-specific statistics are a good predictor for cross-cultural differences in similarity judgments.
-Language statistics are also a good predictor for filler items with no taxonomic/thematic structure.
-Our findings are in contrast to previous accounts, by which culture induces differing conceptions of similarity (varying between taxonomic and thematic).
-these findings provide an alternative account by which language may explain these cross-cultural differences without invoking variation in notions of similarity.
+We find that language-specific statistics provide good predictions for cross-cultural differences in similarity judgments, and additionally, for more general similarity judgments that do not contrast taxonomic and thematic matches.
+Critically, the stimuli used to assess this more general case of similarity reasoning were constructed to be outside the scope of explanation for taxonomic-thematic accounts (for use as filler items).
+While the language model may succeed in taxonomic-thematic similarity predictions by picking up on differences in the *conceptualization* of similarity that are reflected in language data, this conceptualization account provides no prediction for these filler stimuli.
+Accordingly, these filler stimuli provide the strongest test of the language model, demonstrating that it can explain variation in similarity judgments beyond that explained by thematic or taxonomic conceptualizations of similarity.
+Taken together, our findings provide support for an alternative to previous accounts, on which differing cultures induce differing conceptions of similarity.
+They show that language can account for culture-specific variation in similarity reasoning, both for taxonomic-thematic judgments and for judgments not attributable to these senses of similarity.
+While these findings do not rule out contributions from differing senses of similarity, they show it is possible to explain cross-cultural differences in similarity judgments without invoking variation in notions of similarity, at least in some cases.
 

### 2023-02-01 code/4_paper/manuscript/manuscript.Rmd
manuscript edits

--- 2023-01-31 code/4_paper/manuscript/manuscript.Rmd
@@
     \author{{\large \bf Khuyen N.
-Le (knl005@ucsd.edu)}$^{1\star}$, {\large \bf Alexandra Carstensen (abc@ucsd.edu)}$^{1\star}$, \\ {\large \bf Shan Gao (shangaocog@gmail.com)$^2$} {\large \bf Michael C.
+Le (knl005@ucsd.edu)}$^{1}$, {\large \bf Alexandra Carstensen (abc@ucsd.edu)}$^{1}$, \\ {\large \bf Shan Gao (shangaocog@gmail.com)$^2$}, {\large \bf Michael C.
 Frank (mcfrank@stanford.edu)$^3$},  \AND
-    $^1$Department of Psychology, UC San Diego, $^2$Department of Psychology, University of Chicago, \\ $^3$Department of Psychology, Stanford University
+    $^1$Department of Psychology, University of California, San Diego, $^2$Department of Psychology, University of Chicago, \\ $^3$Department of Psychology, Stanford University
     }
@@
 library("report")
+library("MuMIn")
 
@@
 
-## Estimating variation in experience
+## Estimating variation in experience via language statistics
 
@@
 Lexical semantic models that are constructed using lexical co-occurrence (in comparison to annotated relations) have been shown to perform well on predicting human judgments about similarity between word pairs that are thematically or taxonomically related [@Rohde2006].
-Word embeddings like word2vec, gloVe, and fastText have been demonstrated to be good predictors for similarity judgments (@Liu2019, @Jatnika2019).
+Word embeddings like word2vec, gloVe, and fastText have been demonstrated to be good predictors for similarity judgments [@Liu2019; @Jatnika2019].
 
@@
 
-We note that language statistics can incorporate both cultural-specific environmental statistics (the inputs of similarity judgment) and taxonomic/thematic preferences (the conceptualization of similarity).
+We note that language statistics can incorporate both cultural-specific environmental statistics (the inputs of similarity judgment) and thematic/taxonomic preferences (the conceptualization of similarity).
 For example, cultural features (farming) can lead to differences in environmental statistics (seeing cows and grass) and in turn these can influence language (talking more about cows and grass).
@@
 
-Q4: Is the relationship with co-occurrence specific to taxonomic/thematic items, or can co-occurrence structure predict other judgments?
+Q4: Is the relationship with co-occurrence specific to thematic/taxonomic items, or can co-occurrence structure predict other judgments?
 
@@
 Further, language-specific statistics are a good predictor for cross-cultural differences in similarity judgments.
-Language statistics are also a good predictor for filler items with no taxonomic/thematic structure.
+Language statistics are also a good predictor for filler items with no thematic/taxonomic structure.
 Our findings are in contrast to previous accounts, by which culture induces differing conceptions of similarity (varying between taxonomic and thematic).
@@
 The translations were then checked for accuracy after backtranslation to English by another fluent bilingual in each language who was naive to the original English versions.
-All materials are included in the Supplementary Information.
+All materials are available at [BLINDED FOR REVIEW].
 
@@
 We then use a mixed-effects regression to evaluate how well each corpus model predicts participants' similarity judgments, across triads and cultural contexts.
+All analyses are available at [BLINDED FOR REVIEW].
 
-# Results
+# Results & Discussion
 
@@
 ggplot(df.country,
-       mapping = aes(x = factor(country, levels=c("China", "US", "Vietnam")), 
+       mapping = aes(x = factor(country, levels=c("China", "Vietnam", "US")), 
                      y = theme_resp_percent, 
-                     color = factor(country, levels=c("China", "US", "Vietnam")))) +
+                     color = factor(country, levels=c("China", "Vietnam", "US")))) +
   geom_violin() +
@@
        x = "Country") + 
-  scale_color_manual(values=c("#D63230", "#1C77C3", "#F39237")) + 
+  scale_color_manual(values=c("#D63230", "#F39237", "#1C77C3")) + 
   theme(legend.position = "none")
@@
 
-## 3. Cultural context as a predictor for cross-cultural variation in similarity judgments
+<!-- ## 3. Cultural context as a predictor for cross-cultural variation in similarity judgments -->
 
-Our above models tested whether language statistics is a good predictor for similarity judgment.
-As we noted above, language statistics can be a proxy of both inputs and conceptualization of similarity.
-However, it is still an open question whether conceptualization of similarity itself has a unique contribution to similarity judgment (beyond its influence on language statistics).
-To test this hypothesis, we operationalize cultural-specific conceptualization of similarity as country.
-We then compare a model that includes country, corresponding corpus statistics and their interaction as fixed effects to a model with only the corresponding corpus statistics as the fixed effect.
-If conceptualization of similarity has a unique contribution to similarity judgment, we should see that terms including country to be a significant predictor of responding.
+<!-- Our above models tested whether language statistics is a good predictor for similarity judgment. -->
+<!-- As we noted above, language statistics can be a proxy of both inputs and conceptualization of similarity. -->
+<!-- However, it is still an open question whether conceptualization of similarity itself has a unique contribution to similarity judgment (beyond its influence on language statistics). -->
+<!-- To test this hypothesis, we operationalize cultural-specific conceptualization of similarity as country. -->
+<!-- We then compare a model that includes country, corresponding corpus statistics and their interaction as fixed effects to a model with only the corresponding corpus statistics as the fixed effect.
+-->
+<!-- If conceptualization of similarity has a unique contribution to similarity judgment, we should see that terms including country to be a significant predictor of responding. -->
 
@@
 
-In the model containing only the corresponding corpus statistics, the corpus statistics is a significant predictor ($\beta$ = `r round(fixef(fit.language_cos)["theme_cosine_prop_corr_lang"], 2)`, $\chi^2$(`r fit.language_cos.anova["theme_cosine_prop_corr_lang", "Df"]`) = `r round(fit.language_cos.anova["theme_cosine_prop_corr_lang", "Chisq"], 2)`, p `r ifelse( fit.language_cos.anova["theme_cosine_prop_corr_lang", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.language_cos.anova["theme_cosine_prop_corr_lang", "Pr(>Chisq)"], 3)), "< .001")`).
+<!-- In the model containing only the corresponding corpus statistics, the corpus statistics is a significant predictor ($\beta$ = `r round(fixef(fit.language_cos)["theme_cosine_prop_corr_lang"], 2)`, $\chi^2$(`r fit.language_cos.anova["theme_cosine_prop_corr_lang", "Df"]`) = `r round(fit.language_cos.anova["theme_cosine_prop_corr_lang", "Chisq"], 2)`, p `r ifelse( fit.language_cos.anova["theme_cosine_prop_corr_lang", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.language_cos.anova["theme_cosine_prop_corr_lang", "Pr(>Chisq)"], 3)), "< .001")`).
 When adding country and interaction between country and corpus, corpus statistics ($\beta$ = `r round(fixef(fit.country_language_cos)["theme_cosine_prop_corr_lang"], 2)`, $\chi^2$(`r fit.country_language_cos.anova["theme_cosine_prop_corr_lang", "Df"]`) = `r round(fit.country_language_cos.anova["theme_cosine_prop_corr_lang", "Chisq"], 2)`, p `r ifelse( fit.country_language_cos.anova["theme_cosine_prop_corr_lang", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.country_language_cos.anova["theme_cosine_prop_corr_lang", "Pr(>Chisq)"], 3)), "< .001")`), country (F(`r fit_joint.country_language_cos["country", "df1"]`, `r fit_joint.country_language_cos["country", "df2"]`) = `r round(fit_joint.country_language_cos["country", "F.ratio"], 2)`, $\chi^2$(`r fit.country_language_cos.anova["country", "Df"]`) = `r round(fit.country_language_cos.anova["country", "Chisq"], 2)`, p `r ifelse( fit.country_language_cos.anova["country", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.country_language_cos.anova["country", "Pr(>Chisq)"], 3)), "< .001")`), and interaction between country and corpus (F(`r fit_joint.country_language_cos["theme_cosine_prop_corr_lang:country", "df1"]`, `r fit_joint.country_language_cos["theme_cosine_prop_corr_lang:country", "df2"]`) = `r round(fit_joint.country_language_cos["theme_cosine_prop_corr_lang:country", "F.ratio"], 2)`, $\chi^2$(`r fit.country_language_cos.anova["theme_cosine_prop_corr_lang:country", "Df"]`) = `r round(fit.country_language_cos.anova["theme_cosine_prop_corr_lang:country", "Chisq"], 2)`, p `r ifelse( fit.country_language_cos.anova["theme_cosine_prop_corr_lang:country", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.country_language_cos.anova["theme_cosine_prop_corr_lang:country", "Pr(>Chisq)"], 3)), "< .001")`), are significant predictors[^7].
@@
 This result points to a unique contribution by culture-specific ways of conceptualizing similarity to similarity judgment that is not captured in language statistics.
+-->
 
-[^7]: With preregistered exclusion criterion: only corpus statistics and interaction between country and corpus are significant predictors.
+<!-- [^7]: With preregistered exclusion criterion: only corpus statistics and interaction between country and corpus are significant predictors. -->
 
-## 4. Language statistics as a predictor for non-structured triad items
+## 3. Language statistics as a predictor for non-structured filler items
 
-A possible concern with our approach is that variation in language statistics (which we claim to be a proxy of both inputs and conceptualization of similarity) can be fully explained by variation in conceptualization of similarity (i.e.
-the difference in similarity measures between 'cow' and 'grass' versus 'cow' and 'chicken' in one corpus is solely driven by the corresponding culture's preference of thematic versus taxonomic categorization).
-Alternatively, language statistics may be measuring slight but pervasive differences in similarity driven by participants' different cultural contexts, rather than merely the type of similarity they generally prefer (thematic vs taxonomic relations).
-We address this concern by testing whether language statistics covary with similarity judgment of items with no taxonomic/thematic structures (filler items).
-If language statistics is only driven by conceptualization of similarity, we should not see an effect with such items, which have no structured similarity relations by which to make any predictions.
+A possible concern with our approach is that our models using language statistics in Q2 are only able to account for variation in thematic/taxonomic preference in similarity judgment because language statistics is picking up on differences in thematic/taxonomic preference in conceptualization of similarity.
+For example, perhaps "cow" and "grass" co-occurs more than "cow" and "chicken" in Mandarin because Chinese speakers prefer thematic relations, and thus talk about "cow" and "grass" together more often.
+Vice versa, English speakers preferring taxonomic relations would talk about "cow" and "chicken" together more often, hence driving higher lexical co-occurrence for "cow" and "chicken" in the English corpus.
+In other words, perhaps the language statistics models are merely measuring variation in thematic/taxonomic relation preference in conceptualization of similarity, only in a different way.
+If this is the case, language statistics should not be able to predict responding for filler items (such as whether "tomorrow" or "yesterday" is more related to "today") because these items do not have a thematic/taxonomic structure.
+Additionally, even when one option might be more related to the cue, such relationship is not systematic throughout the set of fillers.
+On the other hand, if language statistics capture similarity judgment in a more general sense (beyond thematic/taxonomic preference in conceptualization of similarity), it should also be a significant predictor for the non-structured filler items.
 
-```{r incorporate base freq for fillers}
+```{r incorporate base freq for fillers, warning = F, include = F}
 df.filler <- read.csv("../../../data/data_filler_USCNVN_ENZHVI.csv")
@@
 
-Using the same mixed-effects logistic regression structure as Q2, we predict responses (1=word1 or 0=word2) of each cultural context with the corresponding corpus statistics as a fixed effect, and participant and triad as random effects.
+Using the same mixed-effects logistic regression structure as the single corpus models in Q2, we predict responses (1=word1 or 0=word2) of each cultural context with the corresponding corpus statistics as a fixed effect, and participant and triad as random effects.
 We found that in all cultural contexts, the corresponding corpus is a significant predictor of responding, with p \< 0.05 and $\beta$ from `r min(beta.filler_single_corpus_cos)` to `r max(beta.filler_single_corpus_cos)`.
-(For a full report, see Supplementary Information.)
+(For a full report, see Supplementary Information.) These results show that the language statistics model is accounting for general similarity in addition to structured thematic/taxonomic similarity.
 
@@
 
-# Discussion
+To investigate whether language statistics predicts triads and filler items differently, we compare the variance in responding that can be accounted for by language statistics of the corresponding corpus in the two different types of items (structured triads versus non-structured filler items).
+Namely, we ran two mixed-effects logistic regression models that predict responding across cultural contexts (1=thematic or word1, 0=taxonomic or word2), with the corresponding corpus statistics (for e.g., cosine proportion from the English corpus for US responding) as a fixed effect and participant and item as random effects.
+Consistent with our results above, corresponding corpus is a significant predictor for responding to both triads and filler items (triads: $\beta$ = `r round(fixef(fit.language_cos)["theme_cosine_prop_corr_lang"], 2)`, $\chi^2$(`r fit.language_cos.anova["theme_cosine_prop_corr_lang", "Df"]`) = `r round(fit.language_cos.anova["theme_cosine_prop_corr_lang", "Chisq"], 2)`, p `r ifelse( fit.language_cos.anova["theme_cosine_prop_corr_lang", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.language_cos.anova["theme_cosine_prop_corr_lang", "Pr(>Chisq)"], 3)), "< .001")`, fillers: $\beta$ = `r round(fixef(fit.filler)["word1_match_cosine_prop_corr_lang"], 2)`, $\chi^2$(`r fit.filler.anova["word1_match_cosine_prop_corr_lang", "Df"]`) = `r round(fit.filler.anova["word1_match_cosine_prop_corr_lang", "Chisq"], 2)`, p `r ifelse(fit.filler.anova["word1_match_cosine_prop_corr_lang", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.filler.anova["word1_match_cosine_prop_corr_lang", "Pr(>Chisq)"], 3)), "< .001")`).
+Importantly, we found comparable conditional $R^2$ when corresponding corpus is used to predict only triad items ($R^2$ = `r round(as.data.frame(r.squaredGLMM(fit.language_cos))["theoretical", "R2c"], 2)`) and only filler items ($R^2$ = `r round(as.data.frame(r.squaredGLMM(fit.filler))["theoretical", "R2c"], 2)`), suggesting that culture-corresponding corpus statistics is able to explain the same amount of variance in the responding data for either triads or filler items.
+This result provides evidence for our view that language statistics is measuring general tendencies in similarity judgment, beyond preference for thematic/taxonomic relations.
+
+# General Discussion
 
@@
 Our sample of Vietnamese participants showed intermediate response but not significantly different from either Chinese or US participants.
-This finding suggests some limitations on the generality of the cultural account, which proposes that thematic/taxonomic similarity preference maps onto
-We found some support for the environmental statistics account: each corpus statistics is a good predictor for the corresponding country's similarity judgments, even when other corpus statistics are included, and even with triads without a taxonomic/thematic structure.
-However, we also found that culture-based conceptualization of similarity uniquely contributes to predicting similarity judgment when included in a model with corpus statistics.
+This finding suggests some limitations on the generality of the cultural account, which proposes that thematic/taxonomic similarity preference aligns with East Asian/Western tendency for holistic vs analytic processing.
+We found some support for the environmental statistics account: each corpus statistics is a good predictor for the corresponding country's similarity judgments, even when other corpus statistics are included, and even with triads without a thematic/taxonomic structure.
+<!-- However, we also found that culture-based conceptualization of similarity uniquely contributes to predicting similarity judgment when included in a model with corpus statistics. -->
 Overall, our results provide evidence that cross-cultural differences in similarity judgment are related to linguistic co-occurrence patterns (which also vary across cultures).
@@
 
-Our findings raise additional questions for future work: <!--If not differences in taxonomic vs.
-thematic responding, then what differences drive the relativity effects previous studies have observed?--> To what extent are the relativity effects driven by language, and to what extent by culture?
 @Ji2004 established that culture-aligned differences in this paradigm exist, even when the test language is held constant, concluding that "it is culture (independent of the testing language) that led to different grouping styles" in their study.
-Our data provide a cautionary note to this conclusion, suggesting that semantic representations in bilinguals (see @Francis2005 for a review) may have the potential to provide an offline account for cross-context differences in similarity judgments, independent of test language.
+Our data provide a cautionary note to this conclusion, suggesting that while cultural differences in similarity judgment exists, we might get better traction at modelling cross-cultural variation through environmental statistics such as lexical co-occurrences, rather than treating groups of cultures as monoliths (East Asian vs Western).
 However, there are still many open questions for this account.
-How do semantic associations guide categorization?
-Can they explain taxonomic-thematic differences of the type reported by @Ji2004 and others?
-Can we provide a more specific computational account than the simple proportion-of-similarity model tested here?
+Our operationalization of environmental statistics with lexical co-occurrence is a proxy of both language inputs and culture-specific conceptualization of similarity.
+The extent to which cross-cultural differences in similarity judgment are driven by language versus culture is still an open question.
+Future work should also aim to provide a more specific computational account of how lexical co-occurrence might guide categorization preference beyond the simple proportion-of-similarity model tested here, and investigate other individual- or triad-specific factors that might influence how environmental statistics affect similarity judgment.
 

### 2023-02-01 code/4_paper/manuscript/manuscript.tex
manuscript edits

@@
 \author{{\large \bf Khuyen N.
-Le (knl005@ucsd.edu)}$^{1\star}$, {\large \bf Alexandra Carstensen (abc@ucsd.edu)}$^{1\star}$, \\ {\large \bf Shan Gao (shangaocog@gmail.com)$^2$} {\large \bf Michael C.
-Frank (mcfrank@stanford.edu)$^3$},  \AND $^1$Department of Psychology, UC San Diego, $^2$Department of Psychology, University of Chicago, \\ $^3$Department of Psychology, Stanford University }
+Le (knl005@ucsd.edu)}$^{1}$, {\large \bf Alexandra Carstensen (abc@ucsd.edu)}$^{1}$, \\ {\large \bf Shan Gao (shangaocog@gmail.com)$^2$}, {\large \bf Michael C.
+Frank (mcfrank@stanford.edu)$^3$},  \AND $^1$Department of Psychology, University of California, San Diego, $^2$Department of Psychology, University of Chicago, \\ $^3$Department of Psychology, Stanford University }
 
@@
 the tendency to see more analytic processing in Western culture and more
-holistic processing in East Asian cultures (Nisbett (2003)). On this
+holistic processing in East Asian cultures (Nisbett, 2003). On this
 hypothesis, since analytic processing emphasizes relationships between
@@
 
-\hypertarget{estimating-variation-in-experience}{%
-\subsection{Estimating variation in
-experience}\label{estimating-variation-in-experience}}
+\hypertarget{estimating-variation-in-experience-via-language-statistics}{%
+\subsection{Estimating variation in experience via language
+statistics}\label{estimating-variation-in-experience-via-language-statistics}}
 
@@
 embeddings like word2vec, gloVe, and fastText have been demonstrated to
-be good predictors for similarity judgments (Liu, Feng, Wu, Chan, \&
-Fulton (2019), Jatnika, Bijaksana, \& Suryani (2019)).
+be good predictors for similarity judgments (Jatnika, Bijaksana, \&
+Suryani, 2019; Liu, Feng, Wu, Chan, \& Fulton, 2019).
 
@@
 environmental statistics (the inputs of similarity judgment) and
-taxonomic/thematic preferences (the conceptualization of similarity).
+thematic/taxonomic preferences (the conceptualization of similarity).
 For example, cultural features (farming) can lead to differences in
@@
 Q4: Is the relationship with co-occurrence specific to
-taxonomic/thematic items, or can co-occurrence structure predict other
+thematic/taxonomic items, or can co-occurrence structure predict other
 judgments?~
@@
 differences in similarity judgments. Language statistics are also a good
-predictor for filler items with no taxonomic/thematic structure. Our
+predictor for filler items with no thematic/taxonomic structure. Our
 findings are in contrast to previous accounts, by which culture induces
@@
 English by another fluent bilingual in each language who was naive to
-the original English versions. All materials are included in the
-Supplementary Information.
+the original English versions. All materials are available at {[}BLINDED
+FOR REVIEW{]}.
 
@@
 well each corpus model predicts participants' similarity judgments,
-across triads and cultural contexts.
+across triads and cultural contexts. All analyses are available at
+{[}BLINDED FOR REVIEW{]}.
 
-\hypertarget{results}{%
-\section{Results}\label{results}}
+\hypertarget{results-discussion}{%
+\section{Results \& Discussion}\label{results-discussion}}
 
@@
 
-\hypertarget{cultural-context-as-a-predictor-for-cross-cultural-variation-in-similarity-judgments}{%
-\subsection{3. Cultural context as a predictor for cross-cultural
-variation in similarity
-judgments}\label{cultural-context-as-a-predictor-for-cross-cultural-variation-in-similarity-judgments}}
+\hypertarget{language-statistics-as-a-predictor-for-non-structured-filler-items}{%
+\subsection{3. Language statistics as a predictor for non-structured
+filler
+items}\label{language-statistics-as-a-predictor-for-non-structured-filler-items}}
 
-Our above models tested whether language statistics is a good predictor
-for similarity judgment. As we noted above, language statistics can be a
-proxy of both inputs and conceptualization of similarity. However, it is
-still an open question whether conceptualization of similarity itself
-has a unique contribution to similarity judgment (beyond its influence
-on language statistics). To test this hypothesis, we operationalize
-cultural-specific conceptualization of similarity as country. We then
-compare a model that includes country, corresponding corpus statistics
-and their interaction as fixed effects to a model with only the
-corresponding corpus statistics as the fixed effect. If
-conceptualization of similarity has a unique contribution to similarity
-judgment, we should see that terms including country to be a significant
-predictor of responding.
-
-In the model containing only the corresponding corpus statistics, the
-corpus statistics is a significant predictor (\(\beta\) = -1.79,
-\(\chi^2\)(1) = 75.58, p \textless{} .001). When adding country and
-interaction between country and corpus, corpus statistics (\(\beta\) =
--1.72, \(\chi^2\)(1) = 23.34, p \textless{} .001), country (F(2,
-\ensuremath{\infty{}}) = 13.18, \(\chi^2\)(2) = 7.39, p = 0.025), and
-interaction between country and corpus (F(2, \ensuremath{\infty{}}) =
-6.66, \(\chi^2\)(2) = 13.33, p = 0.001), are significant
-predictors\footnote{With preregistered exclusion criterion: only corpus
-  statistics and interaction between country and corpus are significant
-  predictors.}. Including the country and country-corpus terms to the
-language-only model significantly its ability to explain variation in
-responding (\(\chi^2\)(4) = 40.76, p \textless{} .001). This result
-points to a unique contribution by culture-specific ways of
-conceptualizing similarity to similarity judgment that is not captured
-in language statistics.
-
-\hypertarget{language-statistics-as-a-predictor-for-non-structured-triad-items}{%
-\subsection{4. Language statistics as a predictor for non-structured
-triad
-items}\label{language-statistics-as-a-predictor-for-non-structured-triad-items}}
-
-A possible concern with our approach is that variation in language
-statistics (which we claim to be a proxy of both inputs and
-conceptualization of similarity) can be fully explained by variation in
-conceptualization of similarity (i.e.~the difference in similarity
-measures between `cow' and `grass' versus `cow' and `chicken' in one
-corpus is solely driven by the corresponding culture's preference of
-thematic versus taxonomic categorization). Alternatively, language
-statistics may be measuring slight but pervasive differences in
-similarity driven by participants' different cultural contexts, rather
-than merely the type of similarity they generally prefer (thematic vs
-taxonomic relations). We address this concern by testing whether
-language statistics covary with similarity judgment of items with no
-taxonomic/thematic structures (filler items). If language statistics is
-only driven by conceptualization of similarity, we should not see an
-effect with such items, which have no structured similarity relations by
-which to make any predictions.~
+A possible concern with our approach is that our models using language
+statistics in Q2 are only able to account for variation in
+thematic/taxonomic preference in similarity judgment because language
+statistics is picking up on differences in thematic/taxonomic preference
+in conceptualization of similarity. For example, perhaps ``cow'' and
+``grass'' co-occurs more than ``cow'' and ``chicken'' in Mandarin
+because Chinese speakers prefer thematic relations, and thus talk about
+``cow'' and ``grass'' together more often. Vice versa, English speakers
+preferring taxonomic relations would talk about ``cow'' and ``chicken''
+together more often, hence driving higher lexical co-occurrence for
+``cow'' and ``chicken'' in the English corpus. In other words, perhaps
+the language statistics models are merely measuring variation in
+thematic/taxonomic relation preference in conceptualization of
+similarity, only in a different way. If this is the case, language
+statistics should not be able to predict responding for filler items
+(such as whether ``tomorrow'' or ``yesterday'' is more related to
+``today'') because these items do not have a thematic/taxonomic
+structure. Additionally, even when one option might be more related to
+the cue, such relationship is not systematic throughout the set of
+fillers. On the other hand, if language statistics capture similarity
+judgment in a more general sense (beyond thematic/taxonomic preference
+in conceptualization of similarity), it should also be a significant
+predictor for the non-structured filler items.
 
@@
 
-Using the same mixed-effects logistic regression structure as Q2, we
-predict responses (1=word1 or 0=word2) of each cultural context with the
-corresponding corpus statistics as a fixed effect, and participant and
-triad as random effects. We found that in all cultural contexts, the
-corresponding corpus is a significant predictor of responding, with p
-\textless{} 0.05 and \(\beta\) from -9.59 to -3.14. (For a full report,
-see Supplementary Information.)
+Using the same mixed-effects logistic regression structure as the single
+corpus models in Q2, we predict responses (1=word1 or 0=word2) of each
+cultural context with the corresponding corpus statistics as a fixed
+effect, and participant and triad as random effects. We found that in
+all cultural contexts, the corresponding corpus is a significant
+predictor of responding, with p \textless{} 0.05 and \(\beta\) from
+-9.59 to -3.14. (For a full report, see Supplementary Information.)
+These results show that the language statistics model is accounting for
+general similarity in addition to structured thematic/taxonomic
+similarity.
 
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
+To investigate whether language statistics predicts triads and filler
+items differently, we compare the variance in responding that can be
+accounted for by language statistics of the corresponding corpus in the
+two different types of items (structured triads versus non-structured
+filler items). Namely, we ran two mixed-effects logistic regression
+models that predict responding across cultural contexts (1=thematic or
+word1, 0=taxonomic or word2), with the corresponding corpus statistics
+(for e.g., cosine proportion from the English corpus for US responding)
+as a fixed effect and participant and item as random effects. Consistent
+with our results above, corresponding corpus is a significant predictor
+for responding to both triads and filler items (triads: \(\beta\) =
+-1.79, \(\chi^2\)(1) = 75.58, p \textless{} .001, fillers: \(\beta\) =
+-2, \(\chi^2\)(1) = 70.89, p \textless{} .001). Importantly, we found
+comparable conditional \(R^2\) when corresponding corpus is used to
+predict only triad items (\(R^2\) = 0.3) and only filler items (\(R^2\)
+= 0.26), suggesting that culture-corresponding corpus statistics is able
+to explain the same amount of variance in the responding data for either
+triads or filler items. This result provides evidence for our view that
+language statistics is measuring general tendencies in similarity
+judgment, beyond preference for thematic/taxonomic relations.
+
+\hypertarget{general-discussion}{%
+\section{General Discussion}\label{general-discussion}}
 
@@
 to the view that members of different cultures vary in their
-conceptualization of similarity. While we managed to replicate the
-previously documented contrast between English speakers in the US and
-Mandarin Chinese speakers from East Asia (mainland China, Taiwan, Hong
-Kong, and Singapore), we do not extend this contrast to our sample of
-Vietnamese speakers in Vietnam and English speakers in the US. This
+conceptualization of similarity. We replicated the previously documented
+contrast between English speakers in the US and Mandarin Chinese
+speakers from East Asia (mainland China, Taiwan, Hong Kong, and
+Singapore), with mainland China participants preferring thematic
+relations to a greater extent compared to US participants. Our sample of
+Vietnamese participants showed intermediate response but not
+significantly different from either Chinese or US participants. This
 finding suggests some limitations on the generality of the cultural
-account. We found some support for the environmental statistics account:
-each corpus statistics is a good predictor for the corresponding
-country's similarity judgments, even when other corpus statistics are
-included, and even with triads without a taxonomic/thematic structure.
-However, we also found that culture-based conceptualization of
-similarity uniquely contributes to predicting similarity judgment when
-included in a model with corpus statistics. Overall, our results provide
-evidence that cross-cultural differences in similarity judgment are
-related to linguistic co-occurrence patterns (which also vary across
-cultures).
+account, which proposes that thematic/taxonomic similarity preference
+aligns with East Asian/Western tendency for holistic vs analytic
+processing. We found some support for the environmental statistics
+account: each corpus statistics is a good predictor for the
+corresponding country's similarity judgments, even when other corpus
+statistics are included, and even with triads without a
+thematic/taxonomic structure. Overall, our results provide evidence that
+cross-cultural differences in similarity judgment are related to
+linguistic co-occurrence patterns (which also vary across cultures).
 
@@
 
-Our findings raise additional questions for future work: To what extent
-are the relativity effects driven by language, and to what extent by
-culture? Ji et al. (2004) established that culture-aligned differences
-in this paradigm exist, even when the test language is held constant,
-concluding that ``it is culture (independent of the testing language)
-that led to different grouping styles'' in their study. Our data provide
-a cautionary note to this conclusion, suggesting that semantic
-representations in bilinguals (see Francis (2005) for a review) may have
-the potential to provide an offline account for cross-context
-differences in similarity judgments, independent of test language.
-However, there are still many open questions for this account. How do
-semantic associations guide categorization? Can they explain
-taxonomic-thematic differences of the type reported by Ji et al. (2004)
-and others? Can we provide a more specific computational account than
-the simple proportion-of-similarity model tested here?
+Ji et al. (2004) established that culture-aligned differences in this
+paradigm exist, even when the test language is held constant, concluding
+that ``it is culture (independent of the testing language) that led to
+different grouping styles'' in their study. Our data provide a
+cautionary note to this conclusion, suggesting that while cultural
+differences in similarity judgment exists, we might get better traction
+at modelling cross-cultural variation through environmental statistics
+such as lexical co-occurrences, rather than treating groups of cultures
+as monoliths (East Asian vs Western). However, there are still many open
+questions for this account. Our operationalization of environmental
+statistics with lexical co-occurrence is a proxy of both language inputs
+and culture-specific conceptualization of similarity. The extent to
+which cross-cultural differences in similarity judgment are driven by
+language versus culture is still an open question. Future work should
+also aim to provide a more specific computational account of how lexical
+co-occurrence might guide categorization preference beyond the simple
+proportion-of-similarity model tested here, and investigate other
+individual- or triad-specific factors that might influence how
+environmental statistics affect similarity judgment.
 
@@
 http://doi.org/\href{https://doi.org/10.1073/pnas.0506162102}{10.1073/pnas.0506162102}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Francis2005}{}}%
-Francis, W. S. (2005). \emph{Bilingual semantic and conceptual
-representation}. Oxford University Press.
 

### 2023-02-01 code/4_paper/manuscript/manuscript.Rmd

--- 2023-02-01 code/4_paper/manuscript/manuscript.Rmd
@@
 
-3. Is there evidence for a unique contribution from *conceptualization* of similarity?
-
-4. Is our language model specific to items with a taxonomic-thematic contrast, or can it predict similarity more generally?
+3. Is our language model specific to items with a taxonomic-thematic contrast, or can it predict similarity more generally?
 
@@
 We then use a mixed-effects regression to evaluate how well each corpus model predicts participants' similarity judgments, across triads and cultural contexts.
-
-# Results
+All analyses are available at [BLINDED FOR REVIEW].
+
+# Results & Discussion
 
@@
 
-## 3. Cultural context as a predictor for cross-cultural variation in similarity judgments
-
-Our above models tested whether language statistics is a good predictor for similarity judgment.
-As we noted above, language statistics can be a proxy of both inputs and conceptualization of similarity.
-However, it is still an open question whether conceptualization of similarity itself has a unique contribution to similarity judgment (beyond its influence on language statistics).
-To test this hypothesis, we operationalize cultural-specific conceptualization of similarity as country.
-We then compare a model that includes country, corresponding corpus statistics and their interaction as fixed effects to a model with only the corresponding corpus statistics as the fixed effect.
-If conceptualization of similarity has a unique contribution to similarity judgment, we should see that terms including country to be a significant predictor of responding.
+<!-- ## 3. Cultural context as a predictor for cross-cultural variation in similarity judgments -->
+
+<!-- Our above models tested whether language statistics is a good predictor for similarity judgment. -->
+<!-- As we noted above, language statistics can be a proxy of both inputs and conceptualization of similarity. -->
+<!-- However, it is still an open question whether conceptualization of similarity itself has a unique contribution to similarity judgment (beyond its influence on language statistics). -->
+<!-- To test this hypothesis, we operationalize cultural-specific conceptualization of similarity as country. -->
+<!-- We then compare a model that includes country, corresponding corpus statistics and their interaction as fixed effects to a model with only the corresponding corpus statistics as the fixed effect.
+-->
+<!-- If conceptualization of similarity has a unique contribution to similarity judgment, we should see that terms including country to be a significant predictor of responding. -->
 
@@
 This result points to a unique contribution by culture-specific ways of conceptualizing similarity to similarity judgment that is not captured in language statistics.
-
-[^7]: With preregistered exclusion criterion: only corpus statistics and interaction between country and corpus are significant predictors.
-
-## 4. Language statistics as a predictor for non-structured triad items
-
-A possible concern with our approach is that variation in language statistics (which we claim to be a proxy of both inputs and conceptualization of similarity) can be fully explained by variation in conceptualization of similarity (i.e.
-the difference in similarity measures between 'cow' and 'grass' versus 'cow' and 'chicken' in one corpus is solely driven by the corresponding culture's preference of thematic versus taxonomic categorization).
-Alternatively, language statistics may be measuring slight but pervasive differences in similarity driven by participants' different cultural contexts, rather than merely the type of similarity they generally prefer (thematic vs taxonomic relations).
-We address this concern by testing whether language statistics covary with similarity judgment of items with no taxonomic/thematic structures (filler items).
-If language statistics is only driven by conceptualization of similarity, we should not see an effect with such items, which have no structured similarity relations by which to make any predictions.
-
-```{r incorporate base freq for fillers}
+-->
+
+<!-- [^7]: With preregistered exclusion criterion: only corpus statistics and interaction between country and corpus are significant predictors. -->
+
+## 3. Language statistics as a predictor for non-structured filler items
+
+A possible concern with our approach is that our models using language statistics in Q2 are only able to account for variation in thematic/taxonomic preference in similarity judgment because language statistics is picking up on differences in thematic/taxonomic preference in conceptualization of similarity.
+For example, perhaps "cow" and "grass" co-occurs more than "cow" and "chicken" in Mandarin because Chinese speakers prefer thematic relations, and thus talk about "cow" and "grass" together more often.
+Vice versa, English speakers preferring taxonomic relations would talk about "cow" and "chicken" together more often, hence driving higher lexical co-occurrence for "cow" and "chicken" in the English corpus.
+In other words, perhaps the language statistics models are merely measuring variation in thematic/taxonomic relation preference in conceptualization of similarity, only in a different way.
+If this is the case, language statistics should not be able to predict responding for filler items (such as whether "tomorrow" or "yesterday" is more related to "today") because these items do not have a thematic/taxonomic structure.
+Additionally, even when one option might be more related to the cue, such relationship is not systematic throughout the set of fillers.
+On the other hand, if language statistics capture similarity judgment in a more general sense (beyond thematic/taxonomic preference in conceptualization of similarity), it should also be a significant predictor for the non-structured filler items.
+
+```{r incorporate base freq for fillers, warning = F, include = F}
 df.filler <- read.csv("../../../data/data_filler_USCNVN_ENZHVI.csv")

### 2023-02-01 code/4_paper/manuscript/manuscript.Rmd
manuscript edits

@@
 There is substantial consistency in human similarity reasoning, but also systematic variation across cultural and linguistic contexts.
-In particular, there is considerable evidence showing that similarity reasoning in East Asian cultural contexts differs from that in Western cultures (e.g.
-@Nisbett2003b).
-<!-- Khuyen could you add this ref as Nisbett2003b?  https://www.pnas.org/doi/10.1073/pnas.1934527100-->
+In particular, there is considerable evidence showing that similarity reasoning in East Asian cultural contexts differs from that in Western cultures [e.g.
+@Nisbett2003b].
 For example, in a triad task comparing preferences for taxonomic and thematic similarity (choose two out of three words that are most related to one another), @Ji2004 found that Chinese participants preferred thematic matching to a greater extent than European Americans.
@@
 Relatedly, a model trained on word-document co-occurrence can predict word association and the effects of semantic association on a variety of linguistic tasks [@Griffiths2007].
-Word embeddings like word2vec, gloVe, and fastText have also been shown to be good predictors for similarity judgments (@Liu2019, @Jatnika2019).
+Word embeddings like word2vec, gloVe, and fastText have also been shown to be good predictors for similarity judgments [@Liu2019, @Jatnika2019].
 

### 2023-02-01 code/4_paper/manuscript/manuscript.tex
manuscript edits

@@
 similarity; culture; language; semantics; lexical co-occurrence;
-variation
+variation; US; China; Vietnam
 \end{abstract}
@@
 
-We constantly partition our continuous experience of the world into
-categories, but the way we organize these partitions can vary across
-cultures. One way this cross-cultural difference has been observed is
-with a task comparing preference for taxonomic and thematic similarity
-between East Asian and Western participants.\footnote{Taxonomic
-  categorization is based on the similarity of attributes, for example,
-  similar perceptual properties, like shared color or shape, among
-  objects.In contrast, thematic categorization is based on causal,
-  spatial, and temporal relationships among objects (Markman \&
-  Hutchinson, 1984).} Ji, Zhang, \& Nisbett (2004) found that in a word
-triad task (choose two out of three words that are more related to one
-another), Chinese participants preferred thematic matching more compared
-to European Americans. In a pictorial version of this task, Chiu (1972)
-found that Chinese children (9-10 years old) are also more likely to
-choose thematic matches compared to their American counterparts. This
-cross-cultural difference is also observed in novel object
-categorization, with Chinese participants preferring to group by family
-resemblance across multiple features and Americans preferring a
-single-feature rule (Norenzayan, Smith, Kim, \& Nisbett, 2002).
+Many cognitive processes rely on similarity, from inference and
+generalization to analogy, mathematics, and science. There is
+substantial consistency in human similarity reasoning, but also
+systematic variation across cultural and linguistic contexts. In
+particular, there is considerable evidence showing that similarity
+reasoning in East Asian cultural contexts differs from that in Western
+cultures (e.g. Nisbett \& Masada, 2003). For example, in a triad task
+comparing preferences for taxonomic and thematic similarity (choose two
+out of three words that are most related to one another), Ji, Zhang, \&
+Nisbett (2004) found that Chinese participants preferred thematic
+matching to a greater extent than European Americans. In an image
+version of this task, Chinese children (9-10 years old) are also more
+likely to choose thematic matches compared to their American
+counterparts (Chiu, 1972). This cross-cultural difference is also
+observed in novel object categorization, with Chinese participants
+preferring to group by family resemblance across multiple features and
+Americans preferring a single-feature rule (Norenzayan, Smith, Kim, \&
+Nisbett, 2002). Across tasks, East Asian participants show a preference
+for thematic similarity based on causal, spatial, and temporal
+relationships while Western participants are more likely to make
+taxonomic matches based on the similarity of attributes, like shared
+color or shape, among objects (see Markman \& Hutchinson, 1984 for a
+discussion of these types of similarity).
 
-One hypothesis is that differences in similarity judgment is linked to
-the tendency to see more analytic processing in Western culture and more
-holistic processing in East Asian cultures (Nisbett, 2003). On this
-hypothesis, since analytic processing emphasizes relationships between
-objects and their properties, it leads to taxonomic similarity
-judgments; in contrast, holistic processing emphasizes relations between
-objects and leads to thematic similarity judgments. Cross-cultural
-difference in similarity judgment is thus connected to work showing East
-Asian participants exhibiting a higher level of sensitivity to context
-than their Western counterparts when reproducing drawings from memory
-(Ji, Peng, \& Nisbett, 2000); visually exploring naturalistic scenes
-(Chua, Boland, \& Nisbett, 2005); describing scenes (Masuda \& Nisbett,
-2001); and in explaining the causes of ambiguous behaviors (Choi,
-Nisbett, \& Norenzayan, 1999). This view ascribes cross-cultural
-differences in similarity judgment to variation in how each culture (or
-group of culture, i.e.~East Asian vs Western) \emph{conceptualize}
-similarity -- with East Asians preferring thematic relations more than
+An influential perspective within cultural psychology links these
+differences in similarity judgment to tendencies toward analytic
+processing in Western cultures, and holistic processing in East Asian
+cultures (Nisbett, 2003). Analytic processing emphasizes rule-like
+relationships predicated on objects and their properties and,
+correspondingly, taxonomic similarity, while holistic processing
+emphasizes relations between objects and their context and therefor,
+thematic similarity. In related work, East Asian participants show a
+higher level of sensitivity to context than their Western counterparts
+when reproducing drawings from memory (Ji, Peng, \& Nisbett, 2000);
+visually exploring naturalistic scenes (Chua, Boland, \& Nisbett, 2005);
+describing scenes (Masuda \& Nisbett, 2001); and in explaining the
+causes of ambiguous behaviors (Choi, Nisbett, \& Norenzayan, 1999). The
+consensus interpretation in this literature ascribes cross-cultural
+differences in similarity judgment to variation in the
+\emph{conceptualization} of similarity -- with people from East Asian
+cultures relying on a more thematic notion of similarity than
 Westerners.
@@
 Alternatively, these judgments could be shaped by cross-cultural
-differences in the \emph{inputs} to similarity judgment, namely, the
-statistics of the environment, and accordingly the content of everyday
-experiences. Perhaps when faced with the triad task, participants from
-all cultures follow the same process for conceptualizing similarity, but
-rely on language or culture-specific inputs to this process. If we
-observe a difference in categorization between East Asian and Western
+differences in the \emph{input} to similarity judgment, that is, the
+statistics of the environment, and the content of everyday experiences.
+Perhaps when faced with the triad task, participants from all cultures
+follow the same process for conceptualizing similarity, but rely on
+language or culture-specific input to this process. If we observe a
+difference in categorization between East Asian and Western
 participants, it could be that members of both groups use the same
 procedure (considering similarity that is influenced by both taxonomic
-and thematic relations), but the inputs to this procedure differ between
+and thematic relations), but the input to this procedure differ between
 cultures, with East Asian participants exposed to more support for
@@
 Western counterparts. We might also expect that both conceptualization
-and inputs of similarity play a role in driving cross-cultural
-differences -- East Asian participants may both be exposed to more
-instances of thematic similarity, and prefer to conceptualize similarity
-as thematic relations more so than Westerners.
+of similarity and input from experience play a role in driving
+cross-cultural differences -- East Asian participants may be exposed to
+more instances of thematic similarity, and prefer to conceptualize
+similarity as thematic to a greater extent than Westerners.
 
@@
 
-To test alternative hypotheses involving variation of inputs to
-similarity judgment, we need a way to operationalize variation in
-exposure to thematic vs taxonomic relations. While this metric is
-difficult to directly measure, language statistics can provide a rough
-proxy. Language statistics is useful in that it is part of the inputs to
-everyday experiences (through spoken and written language), may afford
-many of the `experiences' that people have with infrequently encountered
-items, like cows or helicopters, and provides accessible measures.
-Previous work also suggests that using language statistics (such as
-lexical co-occurrence or cosine distance of word embeddings) as a proxy
-can be a good predictor for similarity reasoning. A model trained on
-word-document co-occurrence can predict word association and the effects
-of semantic association on a variety of linguistic tasks (Griffiths,
-Steyvers, \& Tenenbaum, 2007). Lexical semantic models that are
-constructed using lexical co-occurrence (in comparison to annotated
-relations) have been shown to perform well on predicting human judgments
-about similarity between word pairs that are thematically or
-taxonomically related (Rohde, Gonnerman, \& Plaut, 2006). Word
-embeddings like word2vec, gloVe, and fastText have been demonstrated to
-be good predictors for similarity judgments (Jatnika, Bijaksana, \&
-Suryani, 2019; Liu, Feng, Wu, Chan, \& Fulton, 2019).
+To determine whether varied input to similarity judgments can in part
+explain cross-cultural differences, we need a way to operationalize
+variation in exposure to thematic and taxonomic relations. While
+exposure to types of similarity is difficult to measure, the statistics
+of language can provide a rough proxy. Language statistics are useful in
+that they are part of the input to everyday experience -- and indeed,
+may afford many of the `experiences' that people have with infrequently
+encountered items, like cows or helicopters -- and they provide an
+accessible measure. Previous work also suggests that language
+statistics, such as lexical co-occurrence or cosine distance of word
+embeddings, can be good predictors of similarity reasoning. Semantic
+models that are constructed using lexical co-occurrence (in comparison
+to annotated relations) have been shown to perform well on predicting
+human judgments about similarity between word pairs that are
+thematically or taxonomically related (Rohde, Gonnerman, \& Plaut,
+2006). Relatedly, a model trained on word-document co-occurrence can
+predict word association and the effects of semantic association on a
+variety of linguistic tasks (Griffiths, Steyvers, \& Tenenbaum, 2007).
+Word embeddings like word2vec, gloVe, and fastText have also been shown
+to be good predictors for similarity judgments Jatnika, Bijaksana, \&
+Suryani (2019).
 
@@
 Bojanowski, Puhrsch, \& Joulin, 2018). fastText has also been shown to
-be sensitive towards cultural effects on word meanings: Thompson \&
-Lupyan (2020) showed that the distribution of semantic meaning clusters
-generated by fastText trained on language-specific corpora correlates to
-the cultural, historical and geographical distances of such languages
-languages. This is a proof of concept for our use of fastText in
-different languages with varying levels of relatedness.
+be sensitive to cultural differences in word meanings: Thompson \&
+Lupyan (2020) demonstrated that the distribution of semantic meaning
+clusters generated by fastText trained on language-specific corpora
+correlates with the cultural, historical, and geographical similarities
+of these languages.
 
-We note that language statistics can incorporate both cultural-specific
-environmental statistics (the inputs of similarity judgment) and
-thematic/taxonomic preferences (the conceptualization of similarity).
-For example, cultural features (farming) can lead to differences in
-environmental statistics (seeing cows and grass) and in turn these can
-influence language (talking more about cows and grass). But cultural
-features (preferring thematic relations) could also more directly cause
-individuals to talk differently about the same experiences (mentioning
-what cows eat rather than what other animals cows are like). Therefore,
-our approach looks at the extent to which language statistics can
-predict cross-cultural differences in similarity judgment with the
-understanding that language statistics is a proxy for both inputs and
-conceptualization of similarity judgment\footnote{However, in Q3, we
-  investigate whether differing culture-based conceptualization of
-  similarity has unique contribution to cross-cultural variation of
-  similarity jdugment.}.
+We note that language statistics may incorporate both cultural-specific
+environmental statistics, that is, the experiential \emph{input} to
+similarity judgments, and culture-specific senses of similarity, the
+\emph{conceptualization} of similarity. For example, cultural features
+(like farming) can lead to differences in environmental statistics
+(seeing cows and grass) and these can influence language (talking more
+about cows and grass). But other cultural features (like conceiving of
+similarity thematically) could also cause individuals to talk
+differently about the same experiences (mentioning what cows eat rather
+than what other animals cows are like). Acoordingly, our approach
+examines the extent to which language statistics can predict
+cross-cultural differences in similarity judgments with the
+understanding that language statistics are likely a proxy for both
+\emph{input} to and \emph{conceptualization} of similarity.
 
@@
 
-Our study tests the hypothesis that, rather than (or in addition to) the
-variation in conceptualization of similarity across cultural groups,
-variation in the input to similarity judgment (namely, environmental
-statistics as proxied by language statistics) can be used to predict
-cross-cultural differences observed in how people evaluate similarity.
+The present study tests whether the statistics of language can be used
+to predict cross-cultural differences in similarity judgments, and
+particularly, whether this approach provides additional insight beyond
+cross-cultural characterizations based on taxonomic vs thematic
+preferences.
 
-We measured taxonomic versus thematic categorization in a word triad
-task in three populations. Following Ji et al. (2004), we conducted our
-study in the US and China. In addition, we collected data in Vietnam,
-Vietnam is a Southeast Asian country that borders China and is
-historically greatly influenced by Chinese culture (Hui, 2002).
-Therefore, it serves as a suitable cultural context to investigate
-whether the claim made by Ji et al. (2004) and previous studies, that
-Eastern and Western cultures have different notions of similarity,
-extends beyond mainland China. We then tested if fastText vectors from
-the corresponding corpus (English, Mandarin, and Vietnamese) are good
-predictors for similarity judgment in each cultural context.
+We measured taxonomic versus thematic similarity matching in a
+forced-choice word triad task in three populations. Following Ji et al.
+(2004), we measured preferences in the US and China. In addition, we
+collected data in a novel context: Vietnam. Vietnam is a Southeast Asian
+country that borders China and has historically been greatly influenced
+by Chinese culture (Hui, 2002). Therefore, it serves as a suitable
+cultural context to investigate whether the claim made by Ji et al.
+(2004) and previous studies -- that Eastern and Western cultures have
+different notions of similarity -- extends beyond mainland China. In
+addition to these replication and extension questions, we tested whether
+fastText vectors from corpora corresponding to each language context
+(English, Mandarin, and Vietnamese) are good predictors for similarity
+judgments in each population.
 
-We note that our study is correlational and cannot make a causal claim
-about the relationship of environmental statistics to similarity
-judgment, but it may be possible to gain traction on potential
-mechanisms by examining whether variation in similarity judgments covary
-with environmental statistics that differ across cultural and linguistic
+This study is correlational and cannot evaluate causal relationships
+between environmental statistics and similarity judgments. However, this
+work can inform potential mechanisms by examining whether similarity
+judgments covary with environmental statistics that differ across these
 contexts. Our specific research questions are as follows:~
 
-Q1: Do we replicate cross-cultural differences in thematic/taxonomic
-categorization between East Asian and Western cultures?
-
-Q2: Are these cross-cultural differences related to differences in
-lexical co-occurrence?
-
-Q3: Is there evidence for a unique contribution from conceptualization
-of similarity?
-
-Q4: Is the relationship with co-occurrence specific to
-thematic/taxonomic items, or can co-occurrence structure predict other
-judgments?~
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\item
+  Do we replicate cross-cultural differences in similarity judgments
+  between East Asian and Western cultures?
+\item
+  Are these cross-cultural differences related to differences in
+  language?
+\item
+  Is our language model specific to items with a taxonomic-thematic
+  contrast, or can it predict similarity more generally?~
+\end{enumerate}
 
 To preview our results, we replicate US-China differences and find that
-Vietnamese judgments are intermediate between these two. Further,
-language-specific statistics are a good predictor for cross-cultural
-differences in similarity judgments. Language statistics are also a good
-predictor for filler items with no thematic/taxonomic structure. Our
-findings are in contrast to previous accounts, by which culture induces
-differing conceptions of similarity (varying between taxonomic and
-thematic). these findings provide an alternative account by which
-language may explain these cross-cultural differences without invoking
-variation in notions of similarity.
+Vietnamese judgments are intermediate between these two. We find that
+language-specific statistics provide good predictions for cross-cultural
+differences in similarity judgments, and additionally, for more general
+similarity judgments that do not contrast taxonomic and thematic
+matches. Critically, the stimuli used to assess this more general case
+of similarity reasoning were constructed to be outside the scope of
+explanation for taxonomic-thematic accounts (for use as filler items).
+While the language model may succeed in taxonomic-thematic similarity
+predictions by picking up on differences in the \emph{conceptualization}
+of similarity that are reflected in language data, this
+conceptualization account provides no prediction for these filler
+stimuli. Accordingly, these filler stimuli provide the strongest test of
+the language model, demonstrating that it can explain variation in
+similarity judgments beyond that explained by thematic or taxonomic
+conceptualizations of similarity. Taken together, our findings provide
+support for an alternative to previous accounts, on which differing
+cultures induce differing conceptions of similarity. They show that
+language can account for culture-specific variation in similarity
+reasoning, both for taxonomic-thematic judgments and for judgments not
+attributable to these senses of similarity. While these findings do not
+rule out contributions from differing senses of similarity, they show it
+is possible to explain cross-cultural differences in similarity
+judgments without invoking variation in notions of similarity, at least
+in some cases.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Nisbett2003b}{}}%
+Nisbett, R. E., \& Masada, T. (2003). Culture and point of view.
+\emph{Proceedings of the National Academy of Sciences}, \emph{100}(19),
+11163--11170.
+http://doi.org/\href{https://doi.org/10.1073/pnas.1934527100}{10.1073/pnas.1934527100}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Norenzayan2002}{}}%

### 2023-02-01 code/4_paper/manuscript/manuscript.Rmd
make plots consistent

@@
 df.USVNCN_coeffs_cos <- data.frame(country_value, corpus_value, coeff_value_cos, se_value_cos) %>%
-  mutate(corpus_value = factor(corpus_value, levels=c("ZH", "EN", "VI")))
+  mutate(corpus_value = factor(corpus_value, levels=c("ZH", "VI", "EN")), 
+         country_value = factor(country_value, levels=c("CN", "VN", "US")))
 
@@
   labs(x = "Country", y = "Fixed effect size", fill = "Corpus") + 
-  scale_x_discrete(labels=c("CN" = "China", "US" = "US", "VN" = "Vietnam")) + 
-  scale_fill_manual(values=c("#D63230", "#1C77C3", "#F39237"))
-```
-
-```{r echo=FALSE, warning=FALSE, cache = TRUE, fig.env = "figure", fig.align = "center", set.cap.width=T, num.cols.cap=1, fig.cap="Fixed effect sizes of each corpus lexical statistics (cosine distance proportion) when included as a predictor for China, US, and Vietnam responding, respectively.
+  scale_x_discrete(labels=c("CN" = "China", "VN" = "Vietnam", "US" = "US")) + 
+  scale_fill_manual(values=c("#D63230", "#F39237", "#1C77C3"))
+```
+
+```{r coeffs_cos, echo=FALSE, warning=FALSE, cache = TRUE, fig.env = "figure", fig.align = "center", set.cap.width=T, num.cols.cap=1, fig.cap="Fixed effect sizes of each corpus lexical statistics (cosine distance proportion) when included as a predictor for China, Vietnam, and US responding, respectively.
 The English corpus is the best predictor for US response, and the Mandarin corpus is the best predictor for China response."}

### 2023-02-01 code/4_paper/manuscript/manuscript.tex
make plots consistent

@@
 
-{\centering \includegraphics{figs/unnamed-chunk-3-1}
+{\centering \includegraphics{figs/coeffs_cos-1}
 
@@
 
-\caption[Fixed effect sizes of each corpus lexical statistics (cosine distance proportion) when included as a predictor for China, US, and Vietnam responding, respectively]{Fixed effect sizes of each corpus lexical statistics (cosine distance proportion) when included as a predictor for China, US, and Vietnam responding, respectively.
-The English corpus is the best predictor for US response, and the Mandarin corpus is the best predictor for China response.}\label{fig:unnamed-chunk-3}
+\caption[Fixed effect sizes of each corpus lexical statistics (cosine distance proportion) when included as a predictor for China, Vietnam, and US responding, respectively]{Fixed effect sizes of each corpus lexical statistics (cosine distance proportion) when included as a predictor for China, Vietnam, and US responding, respectively.
+The English corpus is the best predictor for US response, and the Mandarin corpus is the best predictor for China response.}\label{fig:coeffs_cos}
 \end{figure}

### 2023-02-02 code/4_paper/manuscript/manuscript.Rmd
edited methods

@@
 
-We recruited `r df.excl_US$ppts_finished` participants from the US, `r df.excl_VN$ppts_finished` participants from Vietnam, and `r df.excl_CN$ppts_finished` participants from mainland China.
-US participants were recruited through snowball sampling seeded with Stanford student email lists, Vietnam participants were recruited through snowball sampling seeded with Vietnam-based student groups on Facebook, and mainland China participants were recruited through snowball sampling seeded with group chats on WeChat.
-US participants were compensated with \$5 gift certificates (USD), VN participants received 50,000₫ (VND) in phone credit, and mainland China participants received 25CNY through WeChat credit transfer.
-
-We excluded `r df.excl_US$ppts_finished - df.excl_US$ppts_after_att_check_excl` US participants, `r df.excl_VN$ppts_finished - df.excl_VN$ppts_after_att_check_excl` Vietnam participants, and `r df.excl_CN$ppts_finished - df.excl_CN$ppts_after_att_check_excl` China participants who missed 2 or more attention checks.
-We followed 4 exclusion criteria that aim to retain only participants who are influenced by one culture: (1) non-native speakers of English and Vietnamese, respectively, (2) fluent in at least one of the other two study languages (Vietnamese for US participants, English for Vietnamese participants and Chinese participants), (3) have lived outside of the test country (US, Vietnam, or China) for more than two years, and (4) have significant international experience (more than 6 international experiences of 2 days or longer.) We did not use a particular criterion for a language if it would exclude 25% or more of any one sample.
-In this round of exclusion, we excluded `r df.excl_US$ppts_after_att_check_excl - df.excl_US$ppts_after_demog_excl` US, `r df.excl_VN$ppts_after_att_check_excl - df.excl_VN$ppts_after_demog_excl` Vietnam participants, and `r df.excl_CN$ppts_after_att_check_excl - df.excl_CN$ppts_after_demog_excl` China participants.
-After these exclusions, the US sample included `r df.excl_US$ppts_after_demog_excl` participants (`r df.gender_E %>% filter(gender == "Male") %>% pull(n)`M, `r df.gender_E %>% filter(gender == "Female") %>% pull(n)`F, `r df.gender_E %>% filter(gender == "Non-binary") %>% pull(n)` non-binary, `r df.gender_E %>% filter(gender == "Decline to answer") %>% pull(n)` other), with mean age = `r round(df.age_E$mean_age, 2)` (SD = `r round(df.age_E$sd_age, 2)`) and median age = `r df.age_E$median_age`.
-The Vietnam sample included `r df.excl_VN$ppts_after_demog_excl` participants (`r df.gender_V %>% filter(gender == "Nam") %>% pull(n)`M, `r df.gender_V %>% filter(gender == "Nữ") %>% pull(n)`F, `r df.gender_V %>% filter(gender == "Từ chối trả lời") %>% pull(n)` other), with mean age = `r round(df.age_V$mean_age, 2)` (SD = `r round(df.age_V$sd_age, 2)`) and median age = `r df.age_V$median_age`.
-The China sample included `r df.excl_CN$ppts_after_demog_excl` participants (`r df.gender_M %>% filter(gender == "男性") %>% pull(n)`M, `r df.gender_M %>% filter(gender == "女性") %>% pull(n)`F, `r df.gender_M %>% filter(gender == "拒绝回答") %>% pull(n)` other), with mean age = `r round(df.age_M$mean_age, 2)` (SD = `r round(df.age_M$sd_age, 2)`) and median age = `r df.age_M$median_age`.[^4]
-
-[^4]: A table summarizing number of participants lost at each round of exclusions is included in the Supplementary Information.
-
-We preregistered a more stringent exclusion criterion where participants were excluded if they missed any attention checks.
-However, this led to a small sample size, especially for Vietnam context (US = 109, China = 132, Vietnam = 57).
-Our reported results with the less stringent exclusion criterion (detailed above) is largely not different from the results with the preregistered criterion.
-Any differences are noted in the Analysis section.
-
-## Stimuli Materials
-
-We adapted stimuli from previous studies to create a set of test triads consisting of a cue, with one thematic and one taxonomic match option.
+Data collection and analyses for this study were pre-registered, and the pre-registration is available at [blinded for peer review].
+We recruited `r df.excl_US$ppts_finished` participants from the US, `r df.excl_VN$ppts_finished` from Vietnam, and `r df.excl_CN$ppts_finished` from mainland China.
+All participants were recruited through snowball sampling, which, in the US was seeded with student email lists at a large university, in Vietnam (VN) with Vietnam-based student groups on Facebook, and in China (CN) with student groups on WeChat.
+US participants were compensated with \$5 gift certificates (USD), VN participants received 50,000₫ (VND) in phone credit, and CN participants received 25CNY through WeChat credit transfer.
+
+We excluded `r df.excl_US$ppts_finished - df.excl_US$ppts_after_att_check_excl` US participants, `r df.excl_VN$ppts_finished - df.excl_VN$ppts_after_att_check_excl` VN participants, and `r df.excl_CN$ppts_finished - df.excl_CN$ppts_after_att_check_excl` CN participants who missed two or more of the 10 attention check questions.
+
+In doing so, we deviated from our preregistered exclusion criterion, which used a more stringent policy, excluding participants who missed any of the 10 attention checks.
+This approach would have substantially reduced our sample size, disproportionately affecting the VN sample (resulting in a final sample of 109 US, 132 CN, and 57 VN participants).
+We report results with the less stringent exclusion criterion, but we performed analyses with both samples and found broadly similar results. Any differences are noted in the Analysis.
+
+We also applied four demographic exclusion criteria designed to reduce cross-cultural influences across our samples: we excluded participants who (1) were not native speakers of the test language (English, Vietnamese, or Mandarin Chinese), (2) were fluent in another one of the study languages, (3) had lived outside of the test country for more than two years, or (4) had significant international experience (more than 6 international experiences of 2 days or longer).
+Following our pre-registration, we dropped any exclusion criterion that would exclude 25% or more of any one population, but only for that population.
+Specifically, we did not exclude VN and CN participants who spoke English, or US participants with significant international experience.
+As a result of these demographic exclusions, we excluded `r df.excl_US$ppts_after_att_check_excl - df.excl_US$ppts_after_demog_excl` US, `r df.excl_VN$ppts_after_att_check_excl - df.excl_VN$ppts_after_demog_excl` VN, and `r df.excl_CN$ppts_after_att_check_excl - df.excl_CN$ppts_after_demog_excl` CN participants.
+The final US sample included `r df.excl_US$ppts_after_demog_excl` participants (`r df.gender_E %>% filter(gender == "Male") %>% pull(n)`M, `r df.gender_E %>% filter(gender == "Female") %>% pull(n)`F, `r df.gender_E %>% filter(gender == "Non-binary") %>% pull(n)` non-binary, `r df.gender_E %>% filter(gender == "Decline to answer") %>% pull(n)` other), with mean age = `r round(df.age_E$mean_age, 2)` (SD = `r round(df.age_E$sd_age, 2)`).
+Our VN sample included `r df.excl_VN$ppts_after_demog_excl` participants (`r df.gender_V %>% filter(gender == "Nam") %>% pull(n)`M, `r df.gender_V %>% filter(gender == "Nữ") %>% pull(n)`F, `r df.gender_V %>% filter(gender == "Từ chối trả lời") %>% pull(n)` other), with mean age = `r round(df.age_V$mean_age, 2)` (SD = `r round(df.age_V$sd_age, 2)`).
+And the CN sample included `r df.excl_CN$ppts_after_demog_excl` participants (`r df.gender_M %>% filter(gender == "男性") %>% pull(n)`M, `r df.gender_M %>% filter(gender == "女性") %>% pull(n)`F, `r df.gender_M %>% filter(gender == "拒绝回答") %>% pull(n)` other), with mean age = `r round(df.age_M$mean_age, 2)` (SD = `r round(df.age_M$sd_age, 2)`).[^4]
+
+[^4]: A table summarizing the number of participants omitted for each criterion is included in the Supplementary Information.
+
+## Materials
+
+All stimuli and scripts for the experiment and analysis are available at [BLINDED FOR REVIEW].
+We collected and adapted stimuli from previous studies to create test triads consisting of a cue with one thematic and one taxonomic match option.
 For example, "cow," "grass," and "chicken," where "cow" is the cue, "grass" is the thematic match, and "chicken" the taxonomic match.
 We included 105 such triads, a superset including triads pulled from supplemental information and in-text examples across the literature, and others that we adapted or created <!--(see SI for the full list of stimuli and sources)-->.
-We selected triads on the basis of cultural familiarity in the US, Vietnam, and China.
-The triads were originally in English; they were translated to Vietnamese and Mandarin by a fluent bilingual speaker in each language.
-The translations were then checked for accuracy after backtranslation to English by another fluent bilingual in each language who was naive to the original English versions.
-All materials are available at [BLINDED FOR REVIEW].
+We selected triads on the basis of cultural familiarity within the US, Vietnam, and China.
+The triads were translated from English to Vietnamese and Mandarin by fluent bilingual speakers of each language, and backtranslated to English by another fluent bilingual who was naive to the original English version.
+The backtranslations were checked against the original English to identify ambiguities in the translation, which were resolved through discussion and selection of alternative terms when relevant.
 
@@
 
-Each participant completed all 105 triads in sets of 21 trials at a time (10 test triads, 10 filler triads, and 1 attention check per page), by selecting the match most related to the cue ("Which thing is most closely related to the bolded item?" and translated equivalents).
+Each participant completed all 105 triads in blocks of 21 trials at a time (10 test triads, 10 filler triads, and 1 attention check per page), by selecting the match most related to the cue ("Which thing is most closely related to the bolded item?" and translated equivalents).
 The test triads were presented with 105 filler triads mixed in, to obscure the taxonomic-thematic two-answer forced choice structure of the test stimuli and reduce the likelihood that participants would become aware of the design.
 The filler triads were groups of three semantically related words, but where the match options were not distinguished by thematic vs.
-taxonomic similarity, e.g., cue "bird" with match options "lizard" and "toad." Additionally, we included 10 attention check trials, which were formatted like the test and filler triads but included an instruction instead of a cue item, e.g., "Choose wife" with match options "wife" and "husband." In total, each participant completed 210 similarity judgments and 10 attention check questions, with triads presented in randomized orders that varied between subjects.
+taxonomic similarity, for example, the cue "bird" with match options "lizard" and "toad." Additionally, we included 10 attention check trials, which were formatted similarly to the test and filler triads but included an instruction instead of a cue item, e.g., "Choose wife" with match options "wife" and "husband." In total, each participant completed 210 similarity judgments (105 test triads and 105 fillers) and 10 attention check questions, with all items presented in randomized orders that varied between subjects.
 
@@
 We use the fastText pre-trained models of English, Mandarin, and Vietnamese in @Grave2018.
-These models are trained on Common Crawl and Wikipedia using We distribute pre-trained word vectors for 157 languages, trained on Common Crawl and Wikipedia using fastText.
-These models were trained using a Continuous Bag of Words (CBOW) with position-weights and a window of size 5.
-The models use character n-grams of length 5 and 10 negative examples.
-From the aforementioned models, we retrieve the word vectors (dimension 300) for each word we are interested in.
+These models were trained on Common Crawl and Wikipedia using fastText and use character n-grams of length 5, and 10 negative examples.
+The training used a Continuous Bag of Words with position-weights and a window of size 5.
+From these models, we retrieve the word vectors (dimension 300) for each word in our triad and filler stimuli.
 
@@
 
-To give an intuition for our model, consider again the cow-grass-chicken triad: we retrieved word vectors for "cow" and "grass", and calculate the cosine distance between these vectors.
-Similarly, we retrieved vectors for "cow" and "chicken" and calculate the cosine distance between them.
-Our similarity prediction is then inversely proportional to the ratio of cosine distance of these pairs.
+To give an intuition for our model, consider again the cow: grass/chicken triad.
+We retrieved word vectors for "cow" and "grass", and calculated the cosine distance between these vectors.
+We did the same for "cow" and "chicken."
+Our similarity prediction is inversely proportional to the ratio of cosine distance of these pairs.
 This is because a larger cosine distance means the word vectors are further apart, and thus the words are less similar.
-For example, if the cosine distance of thematic cow-grass is 0.7 and the cosine distance of taxonomic cow-chicken is 0.3, then our model predicts, correspondingly, that 30% of responses to the triad will be grass, and the other 70% chicken.
-
-In practice, we calculated the cosine distance between each cue-thematic match (thematic cosine distance) and cue-taxonomic match (taxonomic cosine distance), using the spatial.distance.cosine function from the SciPy package [@2020SciPy].
+For example, if the cosine distance of thematic cow-grass is 0.7 and the cosine distance of taxonomic cow-chicken is 0.3 (the more similar of the two), then our model predicts, correspondingly, that 30% of responses to the triad will be grass, and the other 70% chicken.
+
+We calculated the cosine distance between each cue-thematic match (thematic cosine distance) and cue-taxonomic match (taxonomic cosine distance), using the spatial.distance.cosine function from the SciPy package in R [@2020SciPy].
 We then calculated the thematic cosine distance proportion as thematic cosine distance over the sum of taxonomic cosine distance and thematic cosine distance.
-We did this for all three corpora.
-We were able to obtain predictions for all triads in all languages.
-We then use a mixed-effects regression to evaluate how well each corpus model predicts participants' similarity judgments, across triads and cultural contexts.
-All analyses are available at [BLINDED FOR REVIEW].
+We followed this process for all three corpora, and were able to obtain predictions for all triads in all languages.
+Then, we used a mixed-effects regression to evaluate how well each corpus model predicts participants' similarity judgments, across triads and cultural contexts.
 

### 2023-02-02 code/4_paper/manuscript/manuscript.Rmd
mansucript changes
beginning of analysis

@@
 
-Following previous work, we would expect participants from mainland China to prefer thematic matches more than US participants (to use the cow-grass-chicken triad: we would expect participants from mainland China to prefer the cow-grass match over the cow-chicken match to a larger extent compared to US participants).
-We would also expect that participants from Vietnam would pattern with China, and also show a significantly higher preference for thematic matches compare to US participants.
-
-The group means of proportion of thematic response in mainland China is the highest (M = `r round((df.country_sum %>% filter(country == "China"))$mean_theme_resp_percent, 2)`, SD = `r round((df.country_sum %>% filter(country == "China"))$sd_theme_resp_percent, 2)`), followed by the groups means in Vietnam (M = `r round((df.country_sum %>% filter(country == "Vietnam"))$mean_theme_resp_percent, 2)`, SD = `r round((df.country_sum %>% filter(country == "Vietnam"))$sd_theme_resp_percent, 2)`), which is slightly higher than that of the US (M = `r round((df.country_sum %>% filter(country == "US"))$mean_theme_resp_percent, 2)`, SD = `r round((df.country_sum %>% filter(country == "US"))$sd_theme_resp_percent, 2)`) (Figure 1).
+In keeping with @Ji2004, we would expect participants from mainland China to prefer thematic matches more than US participants (e.g., to prefer the cow-grass match over cow-chicken to a greater extent than US participants).
+On the basis of the previous literate more broadly, we would also expect participants from Vietnam to pattern with China, showing a stronger preference for thematic matches than US participants.
+
+We observed the strongest preference for thematic matching in China (M = `r round((df.country_sum %>% filter(country == "China"))$mean_theme_resp_percent, 2)`, SD = `r round((df.country_sum %>% filter(country == "China"))$sd_theme_resp_percent, 2)`), followed by Vietnam (M = `r round((df.country_sum %>% filter(country == "Vietnam"))$mean_theme_resp_percent, 2)`, SD = `r round((df.country_sum %>% filter(country == "Vietnam"))$sd_theme_resp_percent, 2)`), and then the US (M = `r round((df.country_sum %>% filter(country == "US"))$mean_theme_resp_percent, 2)`, SD = `r round((df.country_sum %>% filter(country == "US"))$sd_theme_resp_percent, 2)`; see Figure 1).
 
@@
 
-To test for cross-context differences in similarity judgments between the countries, we ran a mixed-effects logistic regression predicting triad responding (taxonomic or thematic) with country (US, China, or Vietnam) as a fixed effect.
+To test for differences in similarity judgment between the countries, we ran a mixed-effects logistic regression predicting triad match (taxonomic or thematic) with country (US, China, or Vietnam) as a fixed effect.
 As random effects, we included an intercept per subject and one per triad, as well as by-triad random slopes for country to account for variation in the country effect across triads.
 
-Overall, there is a significant effect of country on proportion of thematic responses ($\chi^2$(`r fit.country.anova["country", "Df"]`) = `r round(fit.country.anova["country", "Chisq"], 2)`, p `r ifelse( fit.country.anova["country", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.country.anova["country", "Pr(>Chisq)"], 3)), "< .001")`).
-However, this effect is driven by the difference between US and China responding ($\beta$ = `r round(fixef(fit.country)["countryUS"], 2)`, p `r ifelse(as.data.frame(summary(fit.country)[["coefficients"]])["countryUS", "Pr(>|z|)"] > 0.001, paste0("= ", round(as.data.frame(summary(fit.country)[["coefficients"]])["countryUS", "Pr(>|z|)"], 3)), "< .001")`).
-There is no statistical difference between the Vietnam and China responding ($\beta$ = `r round(fixef(fit.country)["countryVietnam"], 2)`, p `r ifelse(as.data.frame(summary(fit.country)[["coefficients"]])["countryVietnam", "Pr(>|z|)"] > 0.001, paste0("= ", round(as.data.frame(summary(fit.country)[["coefficients"]])["countryVietnam", "Pr(>|z|)"], 3)), "< .001")`), and the US and Vietnam responding ($\beta$ = `r round(fixef(fit.country_EN_VN)["countryVietnam"], 2)`, p `r ifelse(as.data.frame(summary(fit.country_EN_VN)[["coefficients"]])["countryVietnam", "Pr(>|z|)"] > 0.001, paste0("= ", round(as.data.frame(summary(fit.country_EN_VN)[["coefficients"]])["countryVietnam", "Pr(>|z|)"], 3)), "< .001")`).
+We found a significant effect of country ($\chi^2$(`r fit.country.anova["country", "Df"]`) = `r round(fit.country.anova["country", "Chisq"], 2)`, p `r ifelse( fit.country.anova["country", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.country.anova["country", "Pr(>Chisq)"], 3)), "< .001")`), but this effect is driven by the difference between US and CN responding ($\beta$ = `r round(fixef(fit.country)["countryUS"], 2)`, p `r ifelse(as.data.frame(summary(fit.country)[["coefficients"]])["countryUS", "Pr(>|z|)"] > 0.001, paste0("= ", round(as.data.frame(summary(fit.country)[["coefficients"]])["countryUS", "Pr(>|z|)"], 3)), "< .001")`).
+There was no statistical difference between matching in Vietnam and China ($\beta$ = `r round(fixef(fit.country)["countryVietnam"], 2)`, p `r ifelse(as.data.frame(summary(fit.country)[["coefficients"]])["countryVietnam", "Pr(>|z|)"] > 0.001, paste0("= ", round(as.data.frame(summary(fit.country)[["coefficients"]])["countryVietnam", "Pr(>|z|)"], 3)), "< .001")`), or the US and Vietnam ($\beta$ = `r round(fixef(fit.country_EN_VN)["countryVietnam"], 2)`, p `r ifelse(as.data.frame(summary(fit.country_EN_VN)[["coefficients"]])["countryVietnam", "Pr(>|z|)"] > 0.001, paste0("= ", round(as.data.frame(summary(fit.country_EN_VN)[["coefficients"]])["countryVietnam", "Pr(>|z|)"], 3)), "< .001")`).
 

### 2023-02-02 code/4_paper/manuscript/manuscript.Rmd
mcf pass

@@
 ---
-title: "Re-examining cross-cultural similarity judgments using lexical co-occurrence"
+title: "Re-examining cross-cultural similarity judgments using language statistics"
 bibliography: library.bib
@@
 abstract: >
- Is “cow” more closely related to “grass” or “chicken”?
+ Is “cow” more closely related to “grass” or to “chicken”?
 Speakers of different languages judge similarity in this context differently, but why?
 One possibility is that cultures co-varying with these languages induce differences in conceptualizations of similarity.
-Specifically, East Asian cultures may promote reasoning about thematic similarity, by which cow and grass are more related, whereas Western cultures may bias judgments toward taxonomic relations, like cow-chicken.
-This difference in notions of similarity is the consensus interpretation for cross-cultural variation in this paradigm.
-We consider, and provide evidence for, an alternative possibility, by which notions of similarity are similar across contexts, but the statistics of the environment vary.
-On this account, similarity judgments are guided by co-occurrence in experience, and hearing about cows and grass or cows and chickens more often could induce preferences for these groupings, and account in part for apparent differences in notions of similarity across contexts.
+Specifically, East Asian cultures may promote reasoning about thematic similarity, by which cow and grass are more related, whereas Western cultures may bias judgments toward taxonomic relations, like cow and chicken.
+We measure similarity judgments across the US, China, and Vietnam and replicate US-China cultural differences with Vietnam intermediate.
+We also show that word embedding models (fastText models for each language) are related to judgments within each country, suggesting a possible alternative interpretation of cross cultural differences.
+Perhaps notions of similarity are similar across contexts, but the statistics of the linguistic environment vary.
 
@@
 
-Alternatively, these judgments could be shaped by cross-cultural differences in the *input* to similarity judgment, that is, the statistics of the environment, and the content of everyday experiences.
+Alternatively, these judgments could be shaped by cross-cultural differences in the *input* to similarity judgment, that is, the statistics of the linguistic and/or physical environment as manifest in everyday experiences.
 Perhaps when faced with the triad task, participants from all cultures follow the same process for conceptualizing similarity, but rely on language or culture-specific input to this process.
-If we observe a difference in categorization between East Asian and Western participants, it could be that members of both groups use the same procedure (considering similarity that is influenced by both taxonomic and thematic relations), but the input to this procedure differ between cultures, with East Asian participants exposed to more support for thematic similarity in the language they hear in comparison to their Western counterparts.
-We might also expect that both conceptualization of similarity and input from experience play a role in driving cross-cultural differences -- East Asian participants may be exposed to more instances of thematic similarity, and prefer to conceptualize similarity as thematic to a greater extent than Westerners.
+If we observe a difference in categorization between East Asian and Western participants, it could be that members of both groups use the same procedure (considering similarity that is influenced by both taxonomic and thematic relations), but that the input to this procedure differ between cultures, with East Asian participants exposed to more support for thematic similarity in their experience in comparison to their Western counterparts.
+<!-- We might also expect that both conceptualization of similarity and input from experience play a role in driving cross-cultural differences -- East Asian participants may be exposed to more instances of thematic similarity, and prefer to conceptualize similarity as thematic to a greater extent than Westerners.
+-->
 
@@
 To determine whether varied input to similarity judgments can in part explain cross-cultural differences, we need a way to operationalize variation in exposure to thematic and taxonomic relations.
-While exposure to types of similarity is difficult to measure, the statistics of language can provide a rough proxy.
-Language statistics are useful in that they are part of the input to everyday experience -- and indeed, may afford many of the 'experiences' that people have with infrequently encountered items, like cows or helicopters -- and they provide an accessible measure.
+While exposure to types of similarity in everyday experience is difficult to measure, the statistics of language can provide a rough proxy.
+Language statistics are useful in that they are part of the input to everyday experience -- and indeed, may afford many of the "experiences" that people have with infrequently encountered items, like cows or helicopters -- and they provide an accessible measure.
 Previous work also suggests that language statistics, such as lexical co-occurrence or cosine distance of word embeddings, can be good predictors of similarity reasoning.
@@
 Relatedly, a model trained on word-document co-occurrence can predict word association and the effects of semantic association on a variety of linguistic tasks [@Griffiths2007].
-Word embeddings like word2vec, gloVe, and fastText have also been shown to be good predictors for similarity judgments [@Liu2019, @Jatnika2019].
-
-Our study uses cosine distances of fastText word vectors as a measure of lexical co-occurrence[^2].
+Word embeddings like word2vec, gloVe, and fastText have also been shown to be good predictors for similarity judgments [@Liu2019, @Jatnika2019, @asr2018].
+
+Our study uses cosine distances of fastText word vectors as a measure of lexical co-occurrence.[^2]
 fastText is a system that uses lexical co-occurrence information to generate a vector representing each word in its lexicon [@Mikolov2018].
-fastText has also been shown to be sensitive to cultural differences in word meanings: @Thompson2020 demonstrated that the distribution of semantic meaning clusters generated by fastText trained on language-specific corpora correlates with the cultural, historical, and geographical similarities of these languages.
+Practically speaking, fastText vectors are available for many languages, and fastText has also been shown to be sensitive to cultural differences in word meanings: @Thompson2020 demonstrated that the distribution of semantic meaning clusters generated by fastText trained on language-specific corpora correlates with the cultural, historical, and geographical similarities of these languages.
 <!-- This proof of concept provides support for our use of fastText in comparing different languages with varying levels of relatedness.-->
@@
 
-We note that language statistics may incorporate both cultural-specific environmental statistics, that is, the experiential *input* to similarity judgments, and culture-specific senses of similarity, the *conceptualization* of similarity.
+Language statistics may incorporate both cultural-specific environmental statistics, that is, the experiential *input* to similarity judgments, and culture-specific senses of similarity, the *conceptualization* of similarity.
 For example, cultural features (like farming) can lead to differences in environmental statistics (seeing cows and grass) and these can influence language (talking more about cows and grass).
 But other cultural features (like conceiving of similarity thematically) could also cause individuals to talk differently about the same experiences (mentioning what cows eat rather than what other animals cows are like).
-Acoordingly, our approach examines the extent to which language statistics can predict cross-cultural differences in similarity judgments with the understanding that language statistics are likely a proxy for both *input* to and *conceptualization* of similarity.
+Accordingly, our approach examines the extent to which language statistics can predict cross-cultural differences in similarity judgments with the understanding that language statistics are likely a proxy for both *input* to and *conceptualization* of similarity.
 
@@
 ```
-The present study tests whether the statistics of language can be used to predict cross-cultural differences in similarity judgments, and particularly, whether this approach provides additional insight beyond cross-cultural characterizations based on taxonomic vs thematic preferences.
+
+<!-- The present study tests whether the statistics of language can be used to predict cross-cultural differences in similarity judgments, and particularly, whether this approach provides additional insight beyond cross-cultural characterizations based on taxonomic vs thematic preferences.
+-->
 
@@
 This study is correlational and cannot evaluate causal relationships between environmental statistics and similarity judgments.
-However, this work can inform potential mechanisms by examining whether similarity judgments covary with environmental statistics that differ across these contexts.
+However, this work can inform potential mechanisms by examining whether similarity judgments co-vary with environmental statistics that differ across these contexts.
+
 Our specific research questions are as follows:
@@
 While the language model may succeed in taxonomic-thematic similarity predictions by picking up on differences in the *conceptualization* of similarity that are reflected in language data, this conceptualization account provides no prediction for these filler stimuli.
-Accordingly, these filler stimuli provide the strongest test of the language model, demonstrating that it can explain variation in similarity judgments beyond that explained by thematic or taxonomic conceptualizations of similarity.
-Taken together, our findings provide support for an alternative to previous accounts, on which differing cultures induce differing conceptions of similarity.
-They show that language can account for culture-specific variation in similarity reasoning, both for taxonomic-thematic judgments and for judgments not attributable to these senses of similarity.
-While these findings do not rule out contributions from differing senses of similarity, they show it is possible to explain cross-cultural differences in similarity judgments without invoking variation in notions of similarity, at least in some cases.
+<!-- Accordingly, these filler stimuli provide the strongest test of the language model, demonstrating that it can explain variation in similarity judgments beyond that explained by thematic or taxonomic conceptualizations of similarity.
+-->
+
+Taken together, our findings provide support for an alternative to previous accounts on which differing cultures induce differing conceptions of similarity.
+On this alternative, language explains for culture-specific variation in similarity reasoning, both for taxonomic-thematic judgments and for judgments not attributable to these senses of similarity.
+While these findings do not rule out other cross-cultural factors, they show it is possible to explain some cross-cultural variation in similarity judgments purely from language statistics.
 
@@
 
-[^4]: A table summarizing the number of participants omitted for each criterion is included in the Supplementary Information.
+<!-- [^4]: A table summarizing the number of participants omitted for each criterion is included in the Supplementary Information. -->
 
@@
 We selected triads on the basis of cultural familiarity within the US, Vietnam, and China.
-The triads were translated from English to Vietnamese and Mandarin by fluent bilingual speakers of each language, and backtranslated to English by another fluent bilingual who was naive to the original English version.
-The backtranslations were checked against the original English to identify ambiguities in the translation, which were resolved through discussion and selection of alternative terms when relevant.
+The triads were translated from English to Vietnamese and Mandarin by fluent bilingual speakers of each language, and back-translated to English by another fluent bilingual who was naive to the original English version.
+The back-translations were checked against the original English to identify ambiguities in the translation, which were resolved through discussion and selection of alternative terms when relevant.
 
@@
 
-Our general approach is to predict behavioral preferences in similarity judgment using relative similarity between word embeddings.
+Our general approach is to predict behavioral preferences in similarity judgment using relative similarity between fastText word embeddings.
 
@@
 
-We calculated the cosine distance between each cue-thematic match (thematic cosine distance) and cue-taxonomic match (taxonomic cosine distance), using the spatial.distance.cosine function from the SciPy package in R [@2020SciPy].
+We calculated the cosine distance between each cue-thematic match (thematic cosine distance) and cue-taxonomic match (taxonomic cosine distance).
+<!-- , using the `spatial.distance.cosine` function from the SciPy package in R [@2020SciPy]. -->
 We then calculated the thematic cosine distance proportion as thematic cosine distance over the sum of taxonomic cosine distance and thematic cosine distance.
@@
 
-On this analysis, we do not find support that the US-China tendencies toward taxonomic and thematic responding (respectively) extend to the US-Vietnam comparison.
-Accordingly, we cannot speak to overall biases toward thematic responding across Asian cultural contexts broadly, but we do replicate the differences documented by @Ji2004 between the US and China.
-However, in our corpus model comparison, we do find evidence for different, more fine-grained variation in similarity judgments between the US and Vietnam.
+In sum, we replicated the differences documented by @Ji2004 between the US and China.
+We did not find that Vietnamese participants grouped particularly with Chinese participants, however.
+Instead they were intermediate between the two.
+Accordingly, we did not find strong support for the hypothesis that there are overall biases toward thematic responding across Asian cultural contexts broadly.
+<!-- However, in our corpus model comparison, we do find evidence for different, more fine-grained variation in similarity judgments between the US and Vietnam. -->
 
@@
 
+In our next analyses, we tested whether triad-level differences in judgments across countries could be predicted on the basis of language statistics.
+
 ### Single corpus model
 
-To test whether variation in language statistics can explain differences in similarity judgments between US and Vietnam participants, we compare logistic mixed-effects regression models fit to the thematic responding data from each country separately.
-We first ask how well each corpus model (English, Vietnamese, or Mandarin) predicts similarity judgments by speakers of the corresponding language (US, Vietnam, or China).
-To do this, we use a mixed-effects logistic regression to predict triad responses (0=taxonomic or 1=thematic) with corpus prediction (proportion of cosine distance) as a fixed effect and participant and triad as random effects.
-If environmental statistics (as proxied by language statistics) contribute to the differences in similarity judgments, we would expect each language corpus to be a good predictor for similarity judgment responding in its corresponding context.
+First, to test whether variation in language statistics can explain differences in similarity judgments, 
+<!-- we compare logistic mixed-effects regression models fit to the thematic responding data from each country separately. -->
+<!-- We first ask how well each corpus model (English, Vietnamese, or Mandarin) predicts similarity judgments by speakers of the corresponding language (US, Vietnam, or China). -->
+<!-- To do this,  -->
+we use a mixed-effects logistic regressions fit individually for each country.
+Our models predicted responses by individual participants to particular triads (0=taxonomic or 1=thematic) with fastText predictions (proportion of cosine distance) as a fixed effect and participant and triad as random effects.
+If language statistics, contribute to the differences in similarity judgments, we would expect each language corpus to be a good predictor for similarity judgment responding in its corresponding context.
 
@@
 
-We found that all corpora are significant predictors of all cultural context responding, with p \< 0.05 and $\beta$ from `r min(beta.single_corpus_cos)` to `r max(beta.single_corpus_cos)`.
-(For a full report, see Supplementary Information.)
-
-While each corpus is a good predictor for its corresponding context, the fact that all corpora covary with all cultural contexts suggests that language is such a rich proxy of human experience that even using the wrong proxy (e.g.
-Mandarin for US responding) is informative.
-A single corpus model might therefore not be informative in culture-specific ways, but might only reflect consistency in experiences across cultures.
-
-### Multiple corpora model
-
-If language statistics is able to predict meaningful culture-specific variation in similarity judgment (rather than just consistency across cultures), we would expect each corpus to be the best predictor of its corresponding culture compared to the other two corpora.
-We directly compare the corpus models by including both as fixed effects in three mixed-effect regressions (predicting US, Vietnam and China responding) with the same random effects as above.
+All corpora were significant predictors of all cultural context responding, with p \< 0.05 and $\beta$ from `r min(beta.single_corpus_cos)` to `r max(beta.single_corpus_cos)`.
+<!-- (For a full report, see Supplementary Information.) -->
+
+### Multi-corpus model
+
+If language statistics are able to predict meaningful culture-specific variation in similarity judgments (rather than just consistency across cultures), we would expect each corpus to be the best predictor of its corresponding culture compared to the other two corpora.
+We directly compared the corpus models by including all three corpus predictors as fixed effects in three mixed-effect regressions (predicting US, Vietnam and China responding) with the same random effects as above.
 
@@
 
-For US responding: only the English (EN) corpus is a significant predictor[^5].
+For US responding: only the English (EN) corpus was a significant predictor[^5].
 EN corpus: $\beta$ = `r round(fixef(fit.ENVIZH_US_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.ENVIZH_US_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.ENVIZH_US_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_US_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_US_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"], 3)), "< .001")`.
@@
 
-[^5]: With preregistered exclusion criterion: only the English (EN) and Mandarin (ZH) corpus are significant predictors.
-
-For Vietnam responding: only the Vietnamese (VI) and Mandarin (ZH) corpus are significant predictors[^6].
+[^5]: With the preregistered exclusion criterion, only the English (EN) and Mandarin (ZH) corpus were significant predictors.
+
+For Vietnam responding, only the Vietnamese (VI) and Mandarin (ZH) corpus were significant predictors[^6].
 EN corpus: $\beta$ = `r round(fixef(fit.ENVIZH_VN_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.ENVIZH_VN_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_VN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"], 3)), "< .001")`.
@@
 
-[^6]: With preregistered exclusion criterion: all three corpora are significant predictors.
-
-For China responding: only the Mandarin (ZH) and English (EN) corpus are significant predictors.
+[^6]: With the preregistered exclusion criterion, all three corpora were significant predictors.
+
+For China responding, only the Mandarin (ZH) and English (EN) corpus were significant predictors.
 EN corpus: $\beta$ = `r round(fixef(fit.ENVIZH_CN_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.ENVIZH_CN_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.ENVIZH_CN_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_CN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_CN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"], 3)), "< .001")`.
@@
 
-We observed some level of language specificity from this analysis.
-The English corpus is the best predictor for US responding, and the Mandarin corpus is the best predictor for China response.
-While this is not the case with the Vietnamese corpus and the Vietnam responding, the Vietnamese corpus is still a significant predictor for the Vietnam responding (Figure 2).
-These results strengthens our hypothesis that variation in inputs to similarity judgment (as proxied by language statistics) can predict cross-cultural variations of similarity judgment.
+We observed some language specificity in this analysis (Figure 2).
+The English corpus was the best predictor for US responding, and the Mandarin corpus was the best predictor for Chinese responding.
+While this is not the case with the Vietnamese corpus and the Vietnam responding, the Vietnamese corpus was still a significant predictor for the Vietnam responding.
+These results support our hypothesis that specific language statistics can predict cross-cultural variations of similarity judgment.
 
@@
 
-However, in all cultural contexts, adding the other two corpora produces a significantly better fit than the identical model without the additional corpora, and only the corresponding corpus included as a predictor (US response: $\chi^2$(`r fit.US_cos_compare["fit.ENVIZH_US_cos", "Df"]`) = `r round(fit.US_cos_compare["fit.ENVIZH_US_cos", "Chisq"], 2)`, p `r ifelse( fit.US_cos_compare["fit.ENVIZH_US_cos", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.US_cos_compare["fit.ENVIZH_US_cos", "Pr(>Chisq)"], 3)), "< .001")`; Vietnam response: $\chi^2$(`r fit.VN_cos_compare["fit.ENVIZH_VN_cos", "Df"]`) = `r round(fit.VN_cos_compare["fit.ENVIZH_VN_cos", "Chisq"], 2)`, p `r ifelse( fit.VN_cos_compare["fit.ENVIZH_VN_cos", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.VN_cos_compare["fit.ENVIZH_VN_cos", "Pr(>Chisq)"], 3)), "< .001")`; China response: $\chi^2$(`r fit.CN_cos_compare["fit.ENVIZH_CN_cos", "Df"]`) = `r round(fit.CN_cos_compare["fit.ENVIZH_CN_cos", "Chisq"], 2)`, p `r ifelse( fit.CN_cos_compare["fit.ENVIZH_CN_cos", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.CN_cos_compare["fit.ENVIZH_CN_cos", "Pr(>Chisq)"], 3)), "< .001")`).
-This analysis suggests that culture-specific inputs to similarity judgment (as proxied by language statistics) do not fully explain cross-cultural differences in similarity judgment.
+However, in all cultural contexts, adding the other two corpora produced a significantly better fit than the identical model with only the corresponding corpus included as a predictor (US response: $\chi^2$(`r fit.US_cos_compare["fit.ENVIZH_US_cos", "Df"]`) = `r round(fit.US_cos_compare["fit.ENVIZH_US_cos", "Chisq"], 2)`, p `r ifelse( fit.US_cos_compare["fit.ENVIZH_US_cos", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.US_cos_compare["fit.ENVIZH_US_cos", "Pr(>Chisq)"], 3)), "< .001")`; Vietnam response: $\chi^2$(`r fit.VN_cos_compare["fit.ENVIZH_VN_cos", "Df"]`) = `r round(fit.VN_cos_compare["fit.ENVIZH_VN_cos", "Chisq"], 2)`, p `r ifelse( fit.VN_cos_compare["fit.ENVIZH_VN_cos", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.VN_cos_compare["fit.ENVIZH_VN_cos", "Pr(>Chisq)"], 3)), "< .001")`; China response: $\chi^2$(`r fit.CN_cos_compare["fit.ENVIZH_CN_cos", "Df"]`) = `r round(fit.CN_cos_compare["fit.ENVIZH_CN_cos", "Chisq"], 2)`, p `r ifelse( fit.CN_cos_compare["fit.ENVIZH_CN_cos", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.CN_cos_compare["fit.ENVIZH_CN_cos", "Pr(>Chisq)"], 3)), "< .001")`).
+This analysis suggests that culture-specific inputs to similarity judgment (as proxied by language statistics) do not fully explain cross-cultural differences in similarity judgment, whether due to noise in the estimates of language statistics or true additional variance picked up by embeddings from other corpora.
 
@@
 
-A possible concern with our approach is that our models using language statistics in Q2 are only able to account for variation in thematic/taxonomic preference in similarity judgment because language statistics is picking up on differences in thematic/taxonomic preference in conceptualization of similarity.
-For example, perhaps "cow" and "grass" co-occurs more than "cow" and "chicken" in Mandarin because Chinese speakers prefer thematic relations, and thus talk about "cow" and "grass" together more often.
-Vice versa, English speakers preferring taxonomic relations would talk about "cow" and "chicken" together more often, hence driving higher lexical co-occurrence for "cow" and "chicken" in the English corpus.
-In other words, perhaps the language statistics models are merely measuring variation in thematic/taxonomic relation preference in conceptualization of similarity, only in a different way.
-If this is the case, language statistics should not be able to predict responding for filler items (such as whether "tomorrow" or "yesterday" is more related to "today") because these items do not have a thematic/taxonomic structure.
-Additionally, even when one option might be more related to the cue, such relationship is not systematic throughout the set of fillers.
-On the other hand, if language statistics capture similarity judgment in a more general sense (beyond thematic/taxonomic preference in conceptualization of similarity), it should also be a significant predictor for the non-structured filler items.
+One possible concern with our approach is that our models are only able to account for variation in  similarity judgment because the word embedding models pick up on cross-cultural differences in the conceptualization of similarity.
+Perhaps some aspect of the geometry of the embedding space specifically reflects these differences rather than capturing more item-specific patterns of co-occurrence.
+
+If this is the case, the embedding models should be less accurate at predicting responding for filler items (such as whether "tomorrow" or "yesterday" is more related to "today") because these items do not have a thematic/taxonomic structure.
+Additionally, even when one option might be more related to the cue, that relationship is not systematic throughout the set of fillers.
+On the other hand, if the embedding models capture similarity judgments more generally (beyond thematic/taxonomic preferences), they should predict judgments for the unstructured filler items as well as they do for our experimental items.
 
@@
 For each filler triad, we randomly assigned one of the responding options as 'Word1'.
-Running a mixed-effects logistic regression to predict responding (Word1 or Word2) with country as the fixed effect and a random effect structure equivalent to Q1, we found no effect of country on filler responding ($\chi^2$(`r fit.country_filler.anova["country", "Df"]`) = `r round(fit.country_filler.anova["country", "Chisq"], 2)`, p `r ifelse( fit.country_filler.anova["country", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.country_filler.anova["country", "Pr(>Chisq)"], 3)), "< .001")`).
+Running a mixed-effects logistic regression to predict responding (Word1 or Word2) with country as a fixed effect and a random effect structure as above Q1, we found no effect of country on filler responding ($\chi^2$(`r fit.country_filler.anova["country", "Df"]`) = `r round(fit.country_filler.anova["country", "Chisq"], 2)`, p `r ifelse( fit.country_filler.anova["country", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.country_filler.anova["country", "Pr(>Chisq)"], 3)), "< .001")`).
 
@@
 
-Using the same mixed-effects logistic regression structure as the single corpus models in Q2, we predict responses (1=word1 or 0=word2) of each cultural context with the corresponding corpus statistics as a fixed effect, and participant and triad as random effects.
-We found that in all cultural contexts, the corresponding corpus is a significant predictor of responding, with p \< 0.05 and $\beta$ from `r min(beta.filler_single_corpus_cos)` to `r max(beta.filler_single_corpus_cos)`.
-(For a full report, see Supplementary Information.) These results show that the language statistics model is accounting for general similarity in addition to structured thematic/taxonomic similarity.
+Using the same mixed-effects logistic regression structure as the single corpus models in Q2, we predicted responses (1=word1 or 0=word2) in each cultural context with the corresponding corpus predictor as a fixed effect, and participant and triad as random effects.
+In all cultural contexts, the corresponding corpus was a significant predictor of responding, with p \< 0.05 and $\beta$ from `r min(beta.filler_single_corpus_cos)` to `r max(beta.filler_single_corpus_cos)`.
+<!-- (For a full report, see Supplementary Information.)  -->
+These results show that the word embedding models predict general similarity in addition to structured thematic/taxonomic similarity.
 
@@
 
-To investigate whether language statistics predicts triads and filler items differently, we compare the variance in responding that can be accounted for by language statistics of the corresponding corpus in the two different types of items (structured triads versus non-structured filler items).
-Namely, we ran two mixed-effects logistic regression models that predict responding across cultural contexts (1=thematic or word1, 0=taxonomic or word2), with the corresponding corpus statistics (for e.g., cosine proportion from the English corpus for US responding) as a fixed effect and participant and item as random effects.
-Consistent with our results above, corresponding corpus is a significant predictor for responding to both triads and filler items (triads: $\beta$ = `r round(fixef(fit.language_cos)["theme_cosine_prop_corr_lang"], 2)`, $\chi^2$(`r fit.language_cos.anova["theme_cosine_prop_corr_lang", "Df"]`) = `r round(fit.language_cos.anova["theme_cosine_prop_corr_lang", "Chisq"], 2)`, p `r ifelse( fit.language_cos.anova["theme_cosine_prop_corr_lang", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.language_cos.anova["theme_cosine_prop_corr_lang", "Pr(>Chisq)"], 3)), "< .001")`, fillers: $\beta$ = `r round(fixef(fit.filler)["word1_match_cosine_prop_corr_lang"], 2)`, $\chi^2$(`r fit.filler.anova["word1_match_cosine_prop_corr_lang", "Df"]`) = `r round(fit.filler.anova["word1_match_cosine_prop_corr_lang", "Chisq"], 2)`, p `r ifelse(fit.filler.anova["word1_match_cosine_prop_corr_lang", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.filler.anova["word1_match_cosine_prop_corr_lang", "Pr(>Chisq)"], 3)), "< .001")`).
-Importantly, we found comparable conditional $R^2$ when corresponding corpus is used to predict only triad items ($R^2$ = `r round(as.data.frame(r.squaredGLMM(fit.language_cos))["theoretical", "R2c"], 2)`) and only filler items ($R^2$ = `r round(as.data.frame(r.squaredGLMM(fit.filler))["theoretical", "R2c"], 2)`), suggesting that culture-corresponding corpus statistics is able to explain the same amount of variance in the responding data for either triads or filler items.
-This result provides evidence for our view that language statistics is measuring general tendencies in similarity judgment, beyond preference for thematic/taxonomic relations.
+To investigate whether language statistics predict taxonomic/thematic triads and filler items differently, we compared the variance accounted for by the models of  the two different types of items.
+We ran two mixed-effects logistic regression models that predict responding across cultural contexts (1=thematic or word1, 0=taxonomic or word2), with the corresponding corpus predictor as a fixed effect and participant and item as random effects.
+Consistent with our results above, corresponding corpus was a significant predictor for responding to both triads and filler items (triads: $\beta$ = `r round(fixef(fit.language_cos)["theme_cosine_prop_corr_lang"], 2)`, $\chi^2$(`r fit.language_cos.anova["theme_cosine_prop_corr_lang", "Df"]`) = `r round(fit.language_cos.anova["theme_cosine_prop_corr_lang", "Chisq"], 2)`, p `r ifelse( fit.language_cos.anova["theme_cosine_prop_corr_lang", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.language_cos.anova["theme_cosine_prop_corr_lang", "Pr(>Chisq)"], 3)), "< .001")`, fillers: $\beta$ = `r round(fixef(fit.filler)["word1_match_cosine_prop_corr_lang"], 2)`, $\chi^2$(`r fit.filler.anova["word1_match_cosine_prop_corr_lang", "Df"]`) = `r round(fit.filler.anova["word1_match_cosine_prop_corr_lang", "Chisq"], 2)`, p `r ifelse(fit.filler.anova["word1_match_cosine_prop_corr_lang", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.filler.anova["word1_match_cosine_prop_corr_lang", "Pr(>Chisq)"], 3)), "< .001")`).
+Importantly, we found comparable conditional $R^2$ values when the corresponding corpus was used to predict only triad items ($R^2$ = `r round(as.data.frame(r.squaredGLMM(fit.language_cos))["theoretical", "R2c"], 2)`) and only filler items ($R^2$ = `r round(as.data.frame(r.squaredGLMM(fit.filler))["theoretical", "R2c"], 2)`).
+This result provides evidence for our view that word embeddings index general tendencies in similarity judgment, beyond a specific dimension of thematic/taxonomic relations.
 
@@
 
-In this paper, we consider whether statistics of the environment (as proxied by language statistics) can account for cross-cultural differences in a classic similarity judgment paradigm, as an alternative to the view that members of different cultures vary in their conceptualization of similarity.
-We replicated the previously documented contrast between English speakers in the US and Mandarin Chinese speakers from East Asia (mainland China, Taiwan, Hong Kong, and Singapore), with mainland China participants preferring thematic relations to a greater extent compared to US participants.
-Our sample of Vietnamese participants showed intermediate response but not significantly different from either Chinese or US participants.
+Do members of different cultures vary in their conceptualization of similarity? Cross-cultural differences in similarity judgment would seem to suggest this conclusion.
+In this paper, we consider whether statistics of the environment (as indexed by language statistics) can account for cross-cultural differences in a classic similarity judgment paradigm.
+We replicated the previously documented contrast between English speakers in the US and Mandarin Chinese speakers from East Asia (mainland China, Taiwan, Hong Kong, and Singapore): Chinese participants preferred thematic relations to a greater extent compared to US participants.
+Our sample of Vietnamese participants showed an intermediate preference but were not significantly different from either Chinese or US participants.
 This finding suggests some limitations on the generality of the cultural account, which proposes that thematic/taxonomic similarity preference aligns with East Asian/Western tendency for holistic vs analytic processing.
-We found some support for the environmental statistics account: each corpus statistics is a good predictor for the corresponding country's similarity judgments, even when other corpus statistics are included, and even with triads without a thematic/taxonomic structure.
+
+In contrast, we found some support for the environmental statistics account: word embeddings based on language specific corpora were a good predictor for the corresponding country's similarity judgments, even when other corpus statistics were included, and even with filler triads without a thematic/taxonomic structure.
 <!-- However, we also found that culture-based conceptualization of similarity uniquely contributes to predicting similarity judgment when included in a model with corpus statistics. -->
-Overall, our results provide evidence that cross-cultural differences in similarity judgment are related to linguistic co-occurrence patterns (which also vary across cultures).
+Overall, our results provide evidence that cross-cultural differences in similarity judgment are related to linguistic statistics patterns (which also vary across cultures).
 
@@
 @Ji2004 established that culture-aligned differences in this paradigm exist, even when the test language is held constant, concluding that "it is culture (independent of the testing language) that led to different grouping styles" in their study.
-Our data provide a cautionary note to this conclusion, suggesting that while cultural differences in similarity judgment exists, we might get better traction at modelling cross-cultural variation through environmental statistics such as lexical co-occurrences, rather than treating groups of cultures as monoliths (East Asian vs Western).
-However, there are still many open questions for this account.
-Our operationalization of environmental statistics with lexical co-occurrence is a proxy of both language inputs and culture-specific conceptualization of similarity.
-The extent to which cross-cultural differences in similarity judgment are driven by language versus culture is still an open question.
+Our data provide a cautionary note to this conclusion, suggesting that while cultural differences in similarity judgment exists, we might get better traction on modelling cross-cultural variation through environmental statistics such as lexical co-occurrences.
+
+There are still many open questions for this account, however.
+Our operationalization of environmental statistics with word embeddings likely captures both language inputs and culture-specific conceptualization of similarity.
+Further investigation of the semantic spaces captured by cross-cultural word embedding models is required.
 Future work should also aim to provide a more specific computational account of how lexical co-occurrence might guide categorization preference beyond the simple proportion-of-similarity model tested here, and investigate other individual- or triad-specific factors that might influence how environmental statistics affect similarity judgment.
 
-Despite these caveats, our findings here demonstrate the plausibility of an alternative perspective on cross-cultural accounts of language, thought, and similarity in the case of taxonomic and thematic reasoning: that it may be the input to similarity judgments, rather than the evaluative process or the conceptualization of similarity that produces variation in similarity reasoning across cultural and linguistic contexts.
+Despite these caveats, our findings here demonstrate the plausibility of an alternative perspective on cross-cultural accounts of similarity in the case of taxonomic and thematic reasoning.
+It may be the input to similarity judgments, rather than the evaluative process or the conceptualization of similarity that produces variation in similarity reasoning across cultural and linguistic contexts.
 We hope this work provides a foundation for further research probing this question.

### 2023-02-02 code/4_paper/manuscript/manuscript.tex
mcf pass

@@
 
-\title{Re-examining cross-cultural similarity judgments using lexical
-co-occurrence}
+\title{Re-examining cross-cultural similarity judgments using language
+statistics}
 
@@
 \begin{abstract}
-Is ``cow'' more closely related to ``grass'' or ``chicken''? Speakers of
-different languages judge similarity in this context differently, but
+Is ``cow'' more closely related to ``grass'' or to ``chicken''? Speakers
+of different languages judge similarity in this context differently, but
 why? One possibility is that cultures co-varying with these languages
@@
 which cow and grass are more related, whereas Western cultures may bias
-judgments toward taxonomic relations, like cow-chicken. This difference
-in notions of similarity is the consensus interpretation for
-cross-cultural variation in this paradigm. We consider, and provide
-evidence for, an alternative possibility, by which notions of similarity
-are similar across contexts, but the statistics of the environment vary.
-On this account, similarity judgments are guided by co-occurrence in
-experience, and hearing about cows and grass or cows and chickens more
-often could induce preferences for these groupings, and account in part
-for apparent differences in notions of similarity across contexts.
+judgments toward taxonomic relations, like cow and chicken. We measure
+similarity judgments across the US, China, and Vietnam and replicate
+US-China cultural differences with Vietnam intermediate. We also show
+that word embedding models (fastText models for each language) are
+related to judgments within each country, suggesting a possible
+alternative interpretation of cross cultural differences. Perhaps
+notions of similarity are similar across contexts, but the statistics of
+the linguistic environment vary.
 
@@
 differences in the \emph{input} to similarity judgment, that is, the
-statistics of the environment, and the content of everyday experiences.
-Perhaps when faced with the triad task, participants from all cultures
-follow the same process for conceptualizing similarity, but rely on
-language or culture-specific input to this process. If we observe a
-difference in categorization between East Asian and Western
-participants, it could be that members of both groups use the same
-procedure (considering similarity that is influenced by both taxonomic
-and thematic relations), but the input to this procedure differ between
-cultures, with East Asian participants exposed to more support for
-thematic similarity in the language they hear in comparison to their
-Western counterparts. We might also expect that both conceptualization
-of similarity and input from experience play a role in driving
-cross-cultural differences -- East Asian participants may be exposed to
-more instances of thematic similarity, and prefer to conceptualize
-similarity as thematic to a greater extent than Westerners.
+statistics of the linguistic and/or physical environment as manifest in
+everyday experiences. Perhaps when faced with the triad task,
+participants from all cultures follow the same process for
+conceptualizing similarity, but rely on language or culture-specific
+input to this process. If we observe a difference in categorization
+between East Asian and Western participants, it could be that members of
+both groups use the same procedure (considering similarity that is
+influenced by both taxonomic and thematic relations), but that the input
+to this procedure differ between cultures, with East Asian participants
+exposed to more support for thematic similarity in their experience in
+comparison to their Western counterparts.
 
@@
 variation in exposure to thematic and taxonomic relations. While
-exposure to types of similarity is difficult to measure, the statistics
-of language can provide a rough proxy. Language statistics are useful in
-that they are part of the input to everyday experience -- and indeed,
-may afford many of the `experiences' that people have with infrequently
-encountered items, like cows or helicopters -- and they provide an
-accessible measure. Previous work also suggests that language
-statistics, such as lexical co-occurrence or cosine distance of word
-embeddings, can be good predictors of similarity reasoning. Semantic
-models that are constructed using lexical co-occurrence (in comparison
-to annotated relations) have been shown to perform well on predicting
-human judgments about similarity between word pairs that are
-thematically or taxonomically related (Rohde, Gonnerman, \& Plaut,
-2006). Relatedly, a model trained on word-document co-occurrence can
-predict word association and the effects of semantic association on a
-variety of linguistic tasks (Griffiths, Steyvers, \& Tenenbaum, 2007).
-Word embeddings like word2vec, gloVe, and fastText have also been shown
-to be good predictors for similarity judgments Jatnika, Bijaksana, \&
-Suryani (2019).
+exposure to types of similarity in everyday experience is difficult to
+measure, the statistics of language can provide a rough proxy. Language
+statistics are useful in that they are part of the input to everyday
+experience -- and indeed, may afford many of the ``experiences'' that
+people have with infrequently encountered items, like cows or
+helicopters -- and they provide an accessible measure. Previous work
+also suggests that language statistics, such as lexical co-occurrence or
+cosine distance of word embeddings, can be good predictors of similarity
+reasoning. Semantic models that are constructed using lexical
+co-occurrence (in comparison to annotated relations) have been shown to
+perform well on predicting human judgments about similarity between word
+pairs that are thematically or taxonomically related (Rohde, Gonnerman,
+\& Plaut, 2006). Relatedly, a model trained on word-document
+co-occurrence can predict word association and the effects of semantic
+association on a variety of linguistic tasks (Griffiths, Steyvers, \&
+Tenenbaum, 2007). Word embeddings like word2vec, gloVe, and fastText
+have also been shown to be good predictors for similarity judgments Asr,
+Zinkov, \& Jones (2018).
 
 Our study uses cosine distances of fastText word vectors as a measure of
-lexical co-occurrence\footnote{We also carried out our analysis using
-  raw lexical co-occurrences and obtained similar results.}. fastText is
+lexical co-occurrence.\footnote{We also carried out our analysis using
+  raw lexical co-occurrences and obtained similar results.} fastText is
 a system that uses lexical co-occurrence information to generate a
 vector representing each word in its lexicon (Mikolov, Grave,
-Bojanowski, Puhrsch, \& Joulin, 2018). fastText has also been shown to
-be sensitive to cultural differences in word meanings: Thompson \&
-Lupyan (2020) demonstrated that the distribution of semantic meaning
+Bojanowski, Puhrsch, \& Joulin, 2018). Practically speaking, fastText
+vectors are available for many languages, and fastText has also been
+shown to be sensitive to cultural differences in word meanings: Thompson
+\& Lupyan (2020) demonstrated that the distribution of semantic meaning
 clusters generated by fastText trained on language-specific corpora
@@
 
-We note that language statistics may incorporate both cultural-specific
-environmental statistics, that is, the experiential \emph{input} to
-similarity judgments, and culture-specific senses of similarity, the
+Language statistics may incorporate both cultural-specific environmental
+statistics, that is, the experiential \emph{input} to similarity
+judgments, and culture-specific senses of similarity, the
 \emph{conceptualization} of similarity. For example, cultural features
@@
 differently about the same experiences (mentioning what cows eat rather
-than what other animals cows are like). Acoordingly, our approach
+than what other animals cows are like). Accordingly, our approach
 examines the extent to which language statistics can predict
@@
 \subsection{The present study}\label{the-present-study}}
-
-The present study tests whether the statistics of language can be used
-to predict cross-cultural differences in similarity judgments, and
-particularly, whether this approach provides additional insight beyond
-cross-cultural characterizations based on taxonomic vs thematic
-preferences.
 
@@
 work can inform potential mechanisms by examining whether similarity
-judgments covary with environmental statistics that differ across these
-contexts. Our specific research questions are as follows:~
+judgments co-vary with environmental statistics that differ across these
+contexts.
+
+Our specific research questions are as follows:
 
@@
   Is our language model specific to items with a taxonomic-thematic
-  contrast, or can it predict similarity more generally?~
+  contrast, or can it predict similarity more generally?
 \end{enumerate}
@@
 conceptualization account provides no prediction for these filler
-stimuli. Accordingly, these filler stimuli provide the strongest test of
-the language model, demonstrating that it can explain variation in
-similarity judgments beyond that explained by thematic or taxonomic
-conceptualizations of similarity. Taken together, our findings provide
-support for an alternative to previous accounts, on which differing
-cultures induce differing conceptions of similarity. They show that
-language can account for culture-specific variation in similarity
-reasoning, both for taxonomic-thematic judgments and for judgments not
-attributable to these senses of similarity. While these findings do not
-rule out contributions from differing senses of similarity, they show it
-is possible to explain cross-cultural differences in similarity
-judgments without invoking variation in notions of similarity, at least
-in some cases.
+stimuli.
+
+Taken together, our findings provide support for an alternative to
+previous accounts on which differing cultures induce differing
+conceptions of similarity. On this alternative, language explains for
+culture-specific variation in similarity reasoning, both for
+taxonomic-thematic judgments and for judgments not attributable to these
+senses of similarity. While these findings do not rule out other
+cross-cultural factors, they show it is possible to explain some
+cross-cultural variation in similarity judgments purely from language
+statistics.
 
@@
 
-We recruited 200 participants from the US, 199 participants from
-Vietnam, and 200 participants from mainland China. US participants were
-recruited through snowball sampling seeded with Stanford student email
-lists, Vietnam participants were recruited through snowball sampling
-seeded with Vietnam-based student groups on Facebook, and mainland China
-participants were recruited through snowball sampling seeded with group
-chats on WeChat. US participants were compensated with \$5 gift
-certificates (USD), VN participants received 50,000₫ (VND) in phone
-credit, and mainland China participants received 25CNY through WeChat
-credit transfer.
+Data collection and analyses for this study were pre-registered, and the
+pre-registration is available at {[}blinded for peer review{]}. We
+recruited 200 participants from the US, 199 from Vietnam, and 200 from
+mainland China. All participants were recruited through snowball
+sampling, which, in the US was seeded with student email lists at a
+large university, in Vietnam (VN) with Vietnam-based student groups on
+Facebook, and in China (CN) with student groups on WeChat. US
+participants were compensated with \$5 gift certificates (USD), VN
+participants received 50,000₫ (VND) in phone credit, and CN participants
+received 25CNY through WeChat credit transfer.
 
-We excluded 8 US participants, 62 Vietnam participants, and 16 China
-participants who missed 2 or more attention checks. We followed 4
-exclusion criteria that aim to retain only participants who are
-influenced by one culture: (1) non-native speakers of English and
-Vietnamese, respectively, (2) fluent in at least one of the other two
-study languages (Vietnamese for US participants, English for Vietnamese
-participants and Chinese participants), (3) have lived outside of the
-test country (US, Vietnam, or China) for more than two years, and (4)
-have significant international experience (more than 6 international
-experiences of 2 days or longer.) We did not use a particular criterion
-for a language if it would exclude 25\% or more of any one sample. In
-this round of exclusion, we excluded 73 US, 27 Vietnam participants, and
-35 China participants. After these exclusions, the US sample included
-119 participants (30M, 84F, 3 non-binary, 2 other), with mean age = 22.2
-(SD = 8.15) and median age = 20. The Vietnam sample included 110
-participants (34M, 71F, 5 other), with mean age = 22.21 (SD = 5.81) and
-median age = 21. The China sample included 149 participants (61M, 87F, 1
-other), with mean age = 23.1 (SD = 3.65) and median age = 23.\footnote{A
-  table summarizing number of participants lost at each round of
-  exclusions is included in the Supplementary Information.}
+We excluded 8 US participants, 62 VN participants, and 16 CN
+participants who missed two or more of the 10 attention check questions.
 
-We preregistered a more stringent exclusion criterion where participants
-were excluded if they missed any attention checks. However, this led to
-a small sample size, especially for Vietnam context (US = 109, China =
-132, Vietnam = 57). Our reported results with the less stringent
-exclusion criterion (detailed above) is largely not different from the
-results with the preregistered criterion. Any differences are noted in
-the Analysis section.
+In doing so, we deviated from our preregistered exclusion criterion,
+which used a more stringent policy, excluding participants who missed
+any of the 10 attention checks. This approach would have substantially
+reduced our sample size, disproportionately affecting the VN sample
+(resulting in a final sample of 109 US, 132 CN, and 57 VN participants).
+We report results with the less stringent exclusion criterion, but we
+performed analyses with both samples and found broadly similar results.
+Any differences are noted in the Analysis.
 
-\hypertarget{stimuli-materials}{%
-\subsection{Stimuli Materials}\label{stimuli-materials}}
+We also applied four demographic exclusion criteria designed to reduce
+cross-cultural influences across our samples: we excluded participants
+who (1) were not native speakers of the test language (English,
+Vietnamese, or Mandarin Chinese), (2) were fluent in another one of the
+study languages, (3) had lived outside of the test country for more than
+two years, or (4) had significant international experience (more than 6
+international experiences of 2 days or longer). Following our
+pre-registration, we dropped any exclusion criterion that would exclude
+25\% or more of any one population, but only for that population.
+Specifically, we did not exclude VN and CN participants who spoke
+English, or US participants with significant international experience.
+As a result of these demographic exclusions, we excluded 73 US, 27 VN,
+and 35 CN participants. The final US sample included 119 participants
+(30M, 84F, 3 non-binary, 2 other), with mean age = 22.2 (SD = 8.15). Our
+VN sample included 110 participants (34M, 71F, 5 other), with mean age =
+22.21 (SD = 5.81). And the CN sample included 149 participants (61M,
+87F, 1 other), with mean age = 23.1 (SD = 3.65).{[}\^{}4{]}
 
-We adapted stimuli from previous studies to create a set of test triads
-consisting of a cue, with one thematic and one taxonomic match option.
-For example, ``cow,'' ``grass,'' and ``chicken,'' where ``cow'' is the
-cue, ``grass'' is the thematic match, and ``chicken'' the taxonomic
-match. We included 105 such triads, a superset including triads pulled
-from supplemental information and in-text examples across the
-literature, and others that we adapted or created . We selected triads
-on the basis of cultural familiarity in the US, Vietnam, and China. The
-triads were originally in English; they were translated to Vietnamese
-and Mandarin by a fluent bilingual speaker in each language. The
-translations were then checked for accuracy after backtranslation to
-English by another fluent bilingual in each language who was naive to
-the original English versions. All materials are available at {[}BLINDED
-FOR REVIEW{]}.
+\hypertarget{materials}{%
+\subsection{Materials}\label{materials}}
+
+All stimuli and scripts for the experiment and analysis are available at
+{[}BLINDED FOR REVIEW{]}. We collected and adapted stimuli from previous
+studies to create test triads consisting of a cue with one thematic and
+one taxonomic match option. For example, ``cow,'' ``grass,'' and
+``chicken,'' where ``cow'' is the cue, ``grass'' is the thematic match,
+and ``chicken'' the taxonomic match. We included 105 such triads, a
+superset including triads pulled from supplemental information and
+in-text examples across the literature, and others that we adapted or
+created . We selected triads on the basis of cultural familiarity within
+the US, Vietnam, and China. The triads were translated from English to
+Vietnamese and Mandarin by fluent bilingual speakers of each language,
+and back-translated to English by another fluent bilingual who was naive
+to the original English version. The back-translations were checked
+against the original English to identify ambiguities in the translation,
+which were resolved through discussion and selection of alternative
+terms when relevant.
 
@@
 
-Each participant completed all 105 triads in sets of 21 trials at a time
-(10 test triads, 10 filler triads, and 1 attention check per page), by
-selecting the match most related to the cue (``Which thing is most
+Each participant completed all 105 triads in blocks of 21 trials at a
+time (10 test triads, 10 filler triads, and 1 attention check per page),
+by selecting the match most related to the cue (``Which thing is most
 closely related to the bolded item?'' and translated equivalents). The
@@
 related words, but where the match options were not distinguished by
-thematic vs.~taxonomic similarity, e.g., cue ``bird'' with match options
-``lizard'' and ``toad.'' Additionally, we included 10 attention check
-trials, which were formatted like the test and filler triads but
-included an instruction instead of a cue item, e.g., ``Choose wife''
-with match options ``wife'' and ``husband.'' In total, each participant
-completed 210 similarity judgments and 10 attention check questions,
-with triads presented in randomized orders that varied between subjects.
+thematic vs.~taxonomic similarity, for example, the cue ``bird'' with
+match options ``lizard'' and ``toad.'' Additionally, we included 10
+attention check trials, which were formatted similarly to the test and
+filler triads but included an instruction instead of a cue item, e.g.,
+``Choose wife'' with match options ``wife'' and ``husband.'' In total,
+each participant completed 210 similarity judgments (105 test triads and
+105 fillers) and 10 attention check questions, with all items presented
+in randomized orders that varied between subjects.
 
@@
 Our general approach is to predict behavioral preferences in similarity
-judgment using relative similarity between word embeddings.
+judgment using relative similarity between fastText word embeddings.
 
@@
 Vietnamese in Grave, Bojanowski, Gupta, Joulin, \& Mikolov (2018). These
-models are trained on Common Crawl and Wikipedia using We distribute
-pre-trained word vectors for 157 languages, trained on Common Crawl and
-Wikipedia using fastText. These models were trained using a Continuous
-Bag of Words (CBOW) with position-weights and a window of size 5. The
-models use character n-grams of length 5 and 10 negative examples. From
-the aforementioned models, we retrieve the word vectors (dimension 300)
-for each word we are interested in.
+models were trained on Common Crawl and Wikipedia using fastText and use
+character n-grams of length 5, and 10 negative examples. The training
+used a Continuous Bag of Words with position-weights and a window of
+size 5. From these models, we retrieve the word vectors (dimension 300)
+for each word in our triad and filler stimuli.
 
@@
 
-To give an intuition for our model, consider again the cow-grass-chicken
-triad: we retrieved word vectors for ``cow'' and ``grass'', and
-calculate the cosine distance between these vectors. Similarly, we
-retrieved vectors for ``cow'' and ``chicken'' and calculate the cosine
-distance between them. Our similarity prediction is then inversely
-proportional to the ratio of cosine distance of these pairs. This is
-because a larger cosine distance means the word vectors are further
-apart, and thus the words are less similar. For example, if the cosine
-distance of thematic cow-grass is 0.7 and the cosine distance of
-taxonomic cow-chicken is 0.3, then our model predicts, correspondingly,
-that 30\% of responses to the triad will be grass, and the other 70\%
-chicken.
+To give an intuition for our model, consider again the cow:
+grass/chicken triad. We retrieved word vectors for ``cow'' and
+``grass'', and calculated the cosine distance between these vectors. We
+did the same for ``cow'' and ``chicken.'' Our similarity prediction is
+inversely proportional to the ratio of cosine distance of these pairs.
+This is because a larger cosine distance means the word vectors are
+further apart, and thus the words are less similar. For example, if the
+cosine distance of thematic cow-grass is 0.7 and the cosine distance of
+taxonomic cow-chicken is 0.3 (the more similar of the two), then our
+model predicts, correspondingly, that 30\% of responses to the triad
+will be grass, and the other 70\% chicken.
 
-In practice, we calculated the cosine distance between each cue-thematic
-match (thematic cosine distance) and cue-taxonomic match (taxonomic
-cosine distance), using the spatial.distance.cosine function from the
-SciPy package (Virtanen et al., 2020). We then calculated the thematic
-cosine distance proportion as thematic cosine distance over the sum of
-taxonomic cosine distance and thematic cosine distance. We did this for
-all three corpora. We were able to obtain predictions for all triads in
-all languages. We then use a mixed-effects regression to evaluate how
-well each corpus model predicts participants' similarity judgments,
-across triads and cultural contexts. All analyses are available at
-{[}BLINDED FOR REVIEW{]}.
+We calculated the cosine distance between each cue-thematic match
+(thematic cosine distance) and cue-taxonomic match (taxonomic cosine
+distance). We then calculated the thematic cosine distance proportion as
+thematic cosine distance over the sum of taxonomic cosine distance and
+thematic cosine distance. We followed this process for all three
+corpora, and were able to obtain predictions for all triads in all
+languages. Then, we used a mixed-effects regression to evaluate how well
+each corpus model predicts participants' similarity judgments, across
+triads and cultural contexts.
 
@@
 
-Following previous work, we would expect participants from mainland
-China to prefer thematic matches more than US participants (to use the
-cow-grass-chicken triad: we would expect participants from mainland
-China to prefer the cow-grass match over the cow-chicken match to a
-larger extent compared to US participants). We would also expect that
-participants from Vietnam would pattern with China, and also show a
-significantly higher preference for thematic matches compare to US
+In keeping with Ji et al. (2004), we would expect participants from
+mainland China to prefer thematic matches more than US participants
+(e.g., to prefer the cow-grass match over cow-chicken to a greater
+extent than US participants). On the basis of the previous literate more
+broadly, we would also expect participants from Vietnam to pattern with
+China, showing a stronger preference for thematic matches than US
 participants.
 
-The group means of proportion of thematic response in mainland China is
-the highest (M = 0.65, SD = 0.11), followed by the groups means in
-Vietnam (M = 0.6, SD = 0.11), which is slightly higher than that of the
-US (M = 0.56, SD = 0.17) (Figure 1).
+We observed the strongest preference for thematic matching in China (M =
+0.65, SD = 0.11), followed by Vietnam (M = 0.6, SD = 0.11), and then the
+US (M = 0.56, SD = 0.17; see Figure 1).
 
@@
 
-To test for cross-context differences in similarity judgments between
-the countries, we ran a mixed-effects logistic regression predicting
-triad responding (taxonomic or thematic) with country (US, China, or
-Vietnam) as a fixed effect. As random effects, we included an intercept
-per subject and one per triad, as well as by-triad random slopes for
-country to account for variation in the country effect across triads.
+To test for differences in similarity judgment between the countries, we
+ran a mixed-effects logistic regression predicting triad match
+(taxonomic or thematic) with country (US, China, or Vietnam) as a fixed
+effect. As random effects, we included an intercept per subject and one
+per triad, as well as by-triad random slopes for country to account for
+variation in the country effect across triads.
 
-Overall, there is a significant effect of country on proportion of
-thematic responses (\(\chi^2\)(2) = 15.37, p \textless{} .001). However,
-this effect is driven by the difference between US and China responding
-(\(\beta\) = -0.48, p \textless{} .001). There is no statistical
-difference between the Vietnam and China responding (\(\beta\) = -0.22,
-p = 0.09), and the US and Vietnam responding (\(\beta\) = 0.26, p =
-0.086).
+We found a significant effect of country (\(\chi^2\)(2) = 15.37, p
+\textless{} .001), but this effect is driven by the difference between
+US and CN responding (\(\beta\) = -0.48, p \textless{} .001). There was
+no statistical difference between matching in Vietnam and China
+(\(\beta\) = -0.22, p = 0.09), or the US and Vietnam (\(\beta\) = 0.26,
+p = 0.086).
 
-On this analysis, we do not find support that the US-China tendencies
-toward taxonomic and thematic responding (respectively) extend to the
-US-Vietnam comparison. Accordingly, we cannot speak to overall biases
-toward thematic responding across Asian cultural contexts broadly, but
-we do replicate the differences documented by Ji et al. (2004) between
-the US and China. However, in our corpus model comparison, we do find
-evidence for different, more fine-grained variation in similarity
-judgments between the US and Vietnam.
+In sum, we replicated the differences documented by Ji et al. (2004)
+between the US and China. We did not find that Vietnamese participants
+grouped particularly with Chinese participants, however. Instead they
+were intermediate between the two. Accordingly, we did not find strong
+support for the hypothesis that there are overall biases toward thematic
+responding across Asian cultural contexts broadly.
 
@@
 
+In our next analyses, we tested whether triad-level differences in
+judgments across countries could be predicted on the basis of language
+statistics.
+
 \hypertarget{single-corpus-model}{%
@@
 
-To test whether variation in language statistics can explain differences
-in similarity judgments between US and Vietnam participants, we compare
-logistic mixed-effects regression models fit to the thematic responding
-data from each country separately. We first ask how well each corpus
-model (English, Vietnamese, or Mandarin) predicts similarity judgments
-by speakers of the corresponding language (US, Vietnam, or China). To do
-this, we use a mixed-effects logistic regression to predict triad
-responses (0=taxonomic or 1=thematic) with corpus prediction (proportion
-of cosine distance) as a fixed effect and participant and triad as
-random effects. If environmental statistics (as proxied by language
-statistics) contribute to the differences in similarity judgments, we
-would expect each language corpus to be a good predictor for similarity
-judgment responding in its corresponding context.
+First, to test whether variation in language statistics can explain
+differences in similarity judgments, we use a mixed-effects logistic
+regressions fit individually for each country. Our models predicted
+responses by individual participants to particular triads (0=taxonomic
+or 1=thematic) with fastText predictions (proportion of cosine distance)
+as a fixed effect and participant and triad as random effects. If
+language statistics, contribute to the differences in similarity
+judgments, we would expect each language corpus to be a good predictor
+for similarity judgment responding in its corresponding context.
 
-We found that all corpora are significant predictors of all cultural
-context responding, with p \textless{} 0.05 and \(\beta\) from -8.69 to
--2.4. (For a full report, see Supplementary Information.)
+All corpora were significant predictors of all cultural context
+responding, with p \textless{} 0.05 and \(\beta\) from -8.69 to -2.4.
 
-While each corpus is a good predictor for its corresponding context, the
-fact that all corpora covary with all cultural contexts suggests that
-language is such a rich proxy of human experience that even using the
-wrong proxy (e.g.~Mandarin for US responding) is informative. A single
-corpus model might therefore not be informative in culture-specific
-ways, but might only reflect consistency in experiences across cultures.
+\hypertarget{multi-corpus-model}{%
+\subsubsection{Multi-corpus model}\label{multi-corpus-model}}
 
-\hypertarget{multiple-corpora-model}{%
-\subsubsection{Multiple corpora model}\label{multiple-corpora-model}}
-
-If language statistics is able to predict meaningful culture-specific
-variation in similarity judgment (rather than just consistency across
+If language statistics are able to predict meaningful culture-specific
+variation in similarity judgments (rather than just consistency across
 cultures), we would expect each corpus to be the best predictor of its
 corresponding culture compared to the other two corpora. We directly
-compare the corpus models by including both as fixed effects in three
-mixed-effect regressions (predicting US, Vietnam and China responding)
-with the same random effects as above.
+compared the corpus models by including all three corpus predictors as
+fixed effects in three mixed-effect regressions (predicting US, Vietnam
+and China responding) with the same random effects as above.
 
-For US responding: only the English (EN) corpus is a significant
-predictor\footnote{With preregistered exclusion criterion: only the
-  English (EN) and Mandarin (ZH) corpus are significant predictors.}. EN
-corpus: \(\beta\) = -6.96, \(\chi^2\)(1) = 16.57, p \textless{} .001. VI
-corpus: \(\beta\) = -2.22, \(\chi^2\)(1) = 3.73, p = 0.054. ZH corpus:
-\(\beta\) = -3.18, \(\chi^2\)(1) = 3.37, p = 0.066.
+For US responding: only the English (EN) corpus was a significant
+predictor\footnote{With the preregistered exclusion criterion, only the
+  English (EN) and Mandarin (ZH) corpus were significant predictors.}.
+EN corpus: \(\beta\) = -6.96, \(\chi^2\)(1) = 16.57, p \textless{} .001.
+VI corpus: \(\beta\) = -2.22, \(\chi^2\)(1) = 3.73, p = 0.054. ZH
+corpus: \(\beta\) = -3.18, \(\chi^2\)(1) = 3.37, p = 0.066.
 
-For Vietnam responding: only the Vietnamese (VI) and Mandarin (ZH)
-corpus are significant predictors\footnote{With preregistered exclusion
-  criterion: all three corpora are significant predictors.}. EN corpus:
-\(\beta\) = -2.98, \(\chi^2\)(1) = 2.58, p = 0.108. VI corpus: \(\beta\)
-= -2.75, \(\chi^2\)(1) = 4.84, p = 0.028. ZH corpus: \(\beta\) = -4.39,
-\(\chi^2\)(1) = 5.49, p = 0.019.
+For Vietnam responding, only the Vietnamese (VI) and Mandarin (ZH)
+corpus were significant predictors\footnote{With the preregistered
+  exclusion criterion, all three corpora were significant predictors.}.
+EN corpus: \(\beta\) = -2.98, \(\chi^2\)(1) = 2.58, p = 0.108. VI
+corpus: \(\beta\) = -2.75, \(\chi^2\)(1) = 4.84, p = 0.028. ZH corpus:
+\(\beta\) = -4.39, \(\chi^2\)(1) = 5.49, p = 0.019.
 
-For China responding: only the Mandarin (ZH) and English (EN) corpus are
-significant predictors. EN corpus: \(\beta\) = -3.32, \(\chi^2\)(1) =
-7.18, p = 0.007. VI corpus: \(\beta\) = -1.59, \(\chi^2\)(1) = 3.63, p =
-0.057. ZH corpus: \(\beta\) = -5.31, \(\chi^2\)(1) = 17.69, p
+For China responding, only the Mandarin (ZH) and English (EN) corpus
+were significant predictors. EN corpus: \(\beta\) = -3.32, \(\chi^2\)(1)
+= 7.18, p = 0.007. VI corpus: \(\beta\) = -1.59, \(\chi^2\)(1) = 3.63, p
+= 0.057. ZH corpus: \(\beta\) = -5.31, \(\chi^2\)(1) = 17.69, p
 \textless{} .001.
 
-We observed some level of language specificity from this analysis. The
-English corpus is the best predictor for US responding, and the Mandarin
-corpus is the best predictor for China response. While this is not the
-case with the Vietnamese corpus and the Vietnam responding, the
-Vietnamese corpus is still a significant predictor for the Vietnam
-responding (Figure 2). These results strengthens our hypothesis that
-variation in inputs to similarity judgment (as proxied by language
-statistics) can predict cross-cultural variations of similarity
-judgment.
+We observed some language specificity in this analysis (Figure 2). The
+English corpus was the best predictor for US responding, and the
+Mandarin corpus was the best predictor for Chinese responding. While
+this is not the case with the Vietnamese corpus and the Vietnam
+responding, the Vietnamese corpus was still a significant predictor for
+the Vietnam responding. These results support our hypothesis that
+specific language statistics can predict cross-cultural variations of
+similarity judgment.
 
@@
 
-However, in all cultural contexts, adding the other two corpora produces
-a significantly better fit than the identical model without the
-additional corpora, and only the corresponding corpus included as a
-predictor (US response: \(\chi^2\)(2) = 7.93, p = 0.019; Vietnam
-response: \(\chi^2\)(2) = 13.72, p = 0.001; China response:
-\(\chi^2\)(2) = 10.56, p = 0.005). This analysis suggests that
-culture-specific inputs to similarity judgment (as proxied by language
-statistics) do not fully explain cross-cultural differences in
-similarity judgment.
+However, in all cultural contexts, adding the other two corpora produced
+a significantly better fit than the identical model with only the
+corresponding corpus included as a predictor (US response: \(\chi^2\)(2)
+= 7.93, p = 0.019; Vietnam response: \(\chi^2\)(2) = 13.72, p = 0.001;
+China response: \(\chi^2\)(2) = 10.56, p = 0.005). This analysis
+suggests that culture-specific inputs to similarity judgment (as proxied
+by language statistics) do not fully explain cross-cultural differences
+in similarity judgment, whether due to noise in the estimates of
+language statistics or true additional variance picked up by embeddings
+from other corpora.
 
@@
 
-A possible concern with our approach is that our models using language
-statistics in Q2 are only able to account for variation in
-thematic/taxonomic preference in similarity judgment because language
-statistics is picking up on differences in thematic/taxonomic preference
-in conceptualization of similarity. For example, perhaps ``cow'' and
-``grass'' co-occurs more than ``cow'' and ``chicken'' in Mandarin
-because Chinese speakers prefer thematic relations, and thus talk about
-``cow'' and ``grass'' together more often. Vice versa, English speakers
-preferring taxonomic relations would talk about ``cow'' and ``chicken''
-together more often, hence driving higher lexical co-occurrence for
-``cow'' and ``chicken'' in the English corpus. In other words, perhaps
-the language statistics models are merely measuring variation in
-thematic/taxonomic relation preference in conceptualization of
-similarity, only in a different way. If this is the case, language
-statistics should not be able to predict responding for filler items
-(such as whether ``tomorrow'' or ``yesterday'' is more related to
-``today'') because these items do not have a thematic/taxonomic
-structure. Additionally, even when one option might be more related to
-the cue, such relationship is not systematic throughout the set of
-fillers. On the other hand, if language statistics capture similarity
-judgment in a more general sense (beyond thematic/taxonomic preference
-in conceptualization of similarity), it should also be a significant
-predictor for the non-structured filler items.
+One possible concern with our approach is that our models are only able
+to account for variation in similarity judgment because the word
+embedding models pick up on cross-cultural differences in the
+conceptualization of similarity. Perhaps some aspect of the geometry of
+the embedding space specifically reflects these differences rather than
+capturing more item-specific patterns of co-occurrence.
+
+If this is the case, the embedding models should be less accurate at
+predicting responding for filler items (such as whether ``tomorrow'' or
+``yesterday'' is more related to ``today'') because these items do not
+have a thematic/taxonomic structure. Additionally, even when one option
+might be more related to the cue, that relationship is not systematic
+throughout the set of fillers. On the other hand, if the embedding
+models capture similarity judgments more generally (beyond
+thematic/taxonomic preferences), they should predict judgments for the
+unstructured filler items as well as they do for our experimental items.
 
@@
 options as `Word1'. Running a mixed-effects logistic regression to
-predict responding (Word1 or Word2) with country as the fixed effect and
-a random effect structure equivalent to Q1, we found no effect of
-country on filler responding (\(\chi^2\)(2) = 0.74, p = 0.692).
+predict responding (Word1 or Word2) with country as a fixed effect and a
+random effect structure as above Q1, we found no effect of country on
+filler responding (\(\chi^2\)(2) = 0.74, p = 0.692).
 
 Using the same mixed-effects logistic regression structure as the single
-corpus models in Q2, we predict responses (1=word1 or 0=word2) of each
-cultural context with the corresponding corpus statistics as a fixed
-effect, and participant and triad as random effects. We found that in
-all cultural contexts, the corresponding corpus is a significant
-predictor of responding, with p \textless{} 0.05 and \(\beta\) from
--9.59 to -3.14. (For a full report, see Supplementary Information.)
-These results show that the language statistics model is accounting for
-general similarity in addition to structured thematic/taxonomic
-similarity.
+corpus models in Q2, we predicted responses (1=word1 or 0=word2) in each
+cultural context with the corresponding corpus predictor as a fixed
+effect, and participant and triad as random effects. In all cultural
+contexts, the corresponding corpus was a significant predictor of
+responding, with p \textless{} 0.05 and \(\beta\) from -9.59 to -3.14.
+These results show that the word embedding models predict general
+similarity in addition to structured thematic/taxonomic similarity.
 
-To investigate whether language statistics predicts triads and filler
-items differently, we compare the variance in responding that can be
-accounted for by language statistics of the corresponding corpus in the
-two different types of items (structured triads versus non-structured
-filler items). Namely, we ran two mixed-effects logistic regression
-models that predict responding across cultural contexts (1=thematic or
-word1, 0=taxonomic or word2), with the corresponding corpus statistics
-(for e.g., cosine proportion from the English corpus for US responding)
-as a fixed effect and participant and item as random effects. Consistent
-with our results above, corresponding corpus is a significant predictor
-for responding to both triads and filler items (triads: \(\beta\) =
--1.79, \(\chi^2\)(1) = 75.58, p \textless{} .001, fillers: \(\beta\) =
--2, \(\chi^2\)(1) = 70.89, p \textless{} .001). Importantly, we found
-comparable conditional \(R^2\) when corresponding corpus is used to
-predict only triad items (\(R^2\) = 0.3) and only filler items (\(R^2\)
-= 0.26), suggesting that culture-corresponding corpus statistics is able
-to explain the same amount of variance in the responding data for either
-triads or filler items. This result provides evidence for our view that
-language statistics is measuring general tendencies in similarity
-judgment, beyond preference for thematic/taxonomic relations.
+To investigate whether language statistics predict taxonomic/thematic
+triads and filler items differently, we compared the variance accounted
+for by the models of the two different types of items. We ran two
+mixed-effects logistic regression models that predict responding across
+cultural contexts (1=thematic or word1, 0=taxonomic or word2), with the
+corresponding corpus predictor as a fixed effect and participant and
+item as random effects. Consistent with our results above, corresponding
+corpus was a significant predictor for responding to both triads and
+filler items (triads: \(\beta\) = -1.79, \(\chi^2\)(1) = 75.58, p
+\textless{} .001, fillers: \(\beta\) = -2, \(\chi^2\)(1) = 70.89, p
+\textless{} .001). Importantly, we found comparable conditional \(R^2\)
+values when the corresponding corpus was used to predict only triad
+items (\(R^2\) = 0.3) and only filler items (\(R^2\) = 0.26). This
+result provides evidence for our view that word embeddings index general
+tendencies in similarity judgment, beyond a specific dimension of
+thematic/taxonomic relations.
 
@@
 
-In this paper, we consider whether statistics of the environment (as
-proxied by language statistics) can account for cross-cultural
-differences in a classic similarity judgment paradigm, as an alternative
-to the view that members of different cultures vary in their
-conceptualization of similarity. We replicated the previously documented
-contrast between English speakers in the US and Mandarin Chinese
-speakers from East Asia (mainland China, Taiwan, Hong Kong, and
-Singapore), with mainland China participants preferring thematic
-relations to a greater extent compared to US participants. Our sample of
-Vietnamese participants showed intermediate response but not
-significantly different from either Chinese or US participants. This
-finding suggests some limitations on the generality of the cultural
-account, which proposes that thematic/taxonomic similarity preference
-aligns with East Asian/Western tendency for holistic vs analytic
-processing. We found some support for the environmental statistics
-account: each corpus statistics is a good predictor for the
-corresponding country's similarity judgments, even when other corpus
-statistics are included, and even with triads without a
-thematic/taxonomic structure. Overall, our results provide evidence that
-cross-cultural differences in similarity judgment are related to
-linguistic co-occurrence patterns (which also vary across cultures).
+Do members of different cultures vary in their conceptualization of
+similarity? Cross-cultural differences in similarity judgment would seem
+to suggest this conclusion. In this paper, we consider whether
+statistics of the environment (as indexed by language statistics) can
+account for cross-cultural differences in a classic similarity judgment
+paradigm. We replicated the previously documented contrast between
+English speakers in the US and Mandarin Chinese speakers from East Asia
+(mainland China, Taiwan, Hong Kong, and Singapore): Chinese participants
+preferred thematic relations to a greater extent compared to US
+participants. Our sample of Vietnamese participants showed an
+intermediate preference but were not significantly different from either
+Chinese or US participants. This finding suggests some limitations on
+the generality of the cultural account, which proposes that
+thematic/taxonomic similarity preference aligns with East Asian/Western
+tendency for holistic vs analytic processing.
+
+In contrast, we found some support for the environmental statistics
+account: word embeddings based on language specific corpora were a good
+predictor for the corresponding country's similarity judgments, even
+when other corpus statistics were included, and even with filler triads
+without a thematic/taxonomic structure. Overall, our results provide
+evidence that cross-cultural differences in similarity judgment are
+related to linguistic statistics patterns (which also vary across
+cultures).
 
@@
 differences in similarity judgment exists, we might get better traction
-at modelling cross-cultural variation through environmental statistics
-such as lexical co-occurrences, rather than treating groups of cultures
-as monoliths (East Asian vs Western). However, there are still many open
-questions for this account. Our operationalization of environmental
-statistics with lexical co-occurrence is a proxy of both language inputs
-and culture-specific conceptualization of similarity. The extent to
-which cross-cultural differences in similarity judgment are driven by
-language versus culture is still an open question. Future work should
-also aim to provide a more specific computational account of how lexical
-co-occurrence might guide categorization preference beyond the simple
-proportion-of-similarity model tested here, and investigate other
-individual- or triad-specific factors that might influence how
-environmental statistics affect similarity judgment.
+on modelling cross-cultural variation through environmental statistics
+such as lexical co-occurrences.
+
+There are still many open questions for this account, however. Our
+operationalization of environmental statistics with word embeddings
+likely captures both language inputs and culture-specific
+conceptualization of similarity. Further investigation of the semantic
+spaces captured by cross-cultural word embedding models is required.
+Future work should also aim to provide a more specific computational
+account of how lexical co-occurrence might guide categorization
+preference beyond the simple proportion-of-similarity model tested here,
+and investigate other individual- or triad-specific factors that might
+influence how environmental statistics affect similarity judgment.
 
 Despite these caveats, our findings here demonstrate the plausibility of
-an alternative perspective on cross-cultural accounts of language,
-thought, and similarity in the case of taxonomic and thematic reasoning:
-that it may be the input to similarity judgments, rather than the
-evaluative process or the conceptualization of similarity that produces
-variation in similarity reasoning across cultural and linguistic
-contexts. We hope this work provides a foundation for further research
-probing this question.
+an alternative perspective on cross-cultural accounts of similarity in
+the case of taxonomic and thematic reasoning. It may be the input to
+similarity judgments, rather than the evaluative process or the
+conceptualization of similarity that produces variation in similarity
+reasoning across cultural and linguistic contexts. We hope this work
+provides a foundation for further research probing this question.
 
@@
 \begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-asr2018}{}}%
+Asr, F. T., Zinkov, R., \& Jones, M. (2018). Querying word embeddings
+for similarity and relatedness. In \emph{Proceedings of the 2018
+conference of the north american chapter of the association for
+computational linguistics: Human language technologies, volume 1 (long
+papers)} (pp. 675--684).
+
 \leavevmode\vadjust pre{\hypertarget{ref-Chiu1972}{}}%
@@
 Nisbett, R. E. (2003). \emph{The geography of thought: How asians and
-westerners think differently \ldots{} and why}. New York: Free Press.
+westerners think differently {\ldots{}} and why}. New York: Free Press.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-2020SciPy}{}}%
-Virtanen, P., Gommers, R., Oliphant, T. E., Haberland, M., Reddy, T.,
-Cournapeau, D., \ldots{} SciPy 1.0 Contributors. (2020). {{SciPy} 1.0:
-Fundamental Algorithms for Scientific Computing in Python}. \emph{Nature
-Methods}, \emph{17}, 261--272.
-http://doi.org/\href{https://doi.org/10.1038/s41592-019-0686-2}{10.1038/s41592-019-0686-2}
-
 \end{CSLReferences}

### 2023-02-02 code/4_paper/manuscript/manuscript.Rmd
italics

@@
 In related work, East Asian participants show a higher level of sensitivity to context than their Western counterparts when reproducing drawings from memory [@Ji2000]; visually exploring naturalistic scenes [@Chua2005]; describing scenes [@Masuda2001]; and in explaining the causes of ambiguous behaviors [@Choi1999].
-The consensus interpretation in this literature ascribes cross-cultural differences in similarity judgment to variation in the *conceptualization* of similarity -- with people from East Asian cultures relying on a more thematic notion of similarity than Westerners.
+The consensus interpretation in this literature ascribes cross-cultural differences in similarity judgment to variation in the conceptualization of similarity -- with people from East Asian cultures relying on a more thematic notion of similarity than Westerners.
 
@@
 But other cultural features (like conceiving of similarity thematically) could also cause individuals to talk differently about the same experiences (mentioning what cows eat rather than what other animals cows are like).
-Accordingly, our approach examines the extent to which language statistics can predict cross-cultural differences in similarity judgments with the understanding that language statistics are likely a proxy for both *input* to and *conceptualization* of similarity.
+Accordingly, our approach examines the extent to which language statistics can predict cross-cultural differences in similarity judgments with the understanding that language statistics are likely a proxy for both input and conceptualization.
 
@@
 Critically, the stimuli used to assess this more general case of similarity reasoning were constructed to be outside the scope of explanation for taxonomic-thematic accounts (for use as filler items).
-While the language model may succeed in taxonomic-thematic similarity predictions by picking up on differences in the *conceptualization* of similarity that are reflected in language data, this conceptualization account provides no prediction for these filler stimuli.
+While the language model may succeed in taxonomic-thematic similarity predictions by picking up on differences in the conceptualization of similarity that are reflected in language data, this conceptualization account provides no prediction for these filler stimuli.
 <!-- Accordingly, these filler stimuli provide the strongest test of the language model, demonstrating that it can explain variation in similarity judgments beyond that explained by thematic or taxonomic conceptualizations of similarity.

### 2023-02-02 code/4_paper/manuscript/manuscript.Rmd
manuscript updates

--- 2023-02-02 code/4_paper/manuscript/manuscript.Rmd
@@
   - \usepackage{kotex}
+  - \usepackage{CJKutf8}
 author-information: > 
@@
 library("car")            
-library("lme4")
 library("emmeans")
@@
 library("MuMIn")
+library("lme4")
 
@@
 There is substantial consistency in human similarity reasoning, but also systematic variation across cultural and linguistic contexts.
-In particular, there is considerable evidence showing that similarity reasoning in East Asian cultural contexts differs from that in Western cultures [e.g.
-@Nisbett2003b].
+In particular, there is considerable evidence showing that similarity reasoning in East Asian cultural contexts differs from that in Western cultures [e.g. @Nisbett2003b].
 For example, in a triad task comparing preferences for taxonomic and thematic similarity (choose two out of three words that are most related to one another), @Ji2004 found that Chinese participants preferred thematic matching to a greater extent than European Americans.
@@
 An influential perspective within cultural psychology links these differences in similarity judgment to tendencies toward analytic processing in Western cultures, and holistic processing in East Asian cultures [@Nisbett2003].
-Analytic processing emphasizes rule-like relationships predicated on objects and their properties and, correspondingly, taxonomic similarity, while holistic processing emphasizes relations between objects and their context and therefor, thematic similarity.
+Analytic processing emphasizes rule-like relationships predicated on objects and their properties and, correspondingly, taxonomic similarity, while holistic processing emphasizes relations between objects and their context and therefore, thematic similarity.
 In related work, East Asian participants show a higher level of sensitivity to context than their Western counterparts when reproducing drawings from memory [@Ji2000]; visually exploring naturalistic scenes [@Chua2005]; describing scenes [@Masuda2001]; and in explaining the causes of ambiguous behaviors [@Choi1999].
@@
 
-Our study uses cosine distances of fastText word vectors as a measure of lexical co-occurrence[^2].
+Our study uses cosine distances of fastText word vectors as a measure of lexical co-occurrence[^1].
 fastText is a system that uses lexical co-occurrence information to generate a vector representing each word in its lexicon [@Mikolov2018].
@@
 
-[^2]: We also carried out our analysis using raw lexical co-occurrences and obtained similar results.
+[^1]: We also carried out our analysis using raw lexical co-occurrences and obtained similar results.
 
@@
 But other cultural features (like conceiving of similarity thematically) could also cause individuals to talk differently about the same experiences (mentioning what cows eat rather than what other animals cows are like).
-Acoordingly, our approach examines the extent to which language statistics can predict cross-cultural differences in similarity judgments with the understanding that language statistics are likely a proxy for both *input* to and *conceptualization* of similarity.
+Accordingly, our approach examines the extent to which language statistics can predict cross-cultural differences in similarity judgments with the understanding that language statistics are likely a proxy for both *input* to and *conceptualization* of similarity.
 
@@
 ```
-The present study tests whether the statistics of language can be used to predict cross-cultural differences in similarity judgments, and particularly, whether this approach provides additional insight beyond cross-cultural characterizations based on taxonomic vs thematic preferences.
-
-We measured taxonomic versus thematic similarity matching in a forced-choice word triad task in three populations.
+The present study tests whether the statistics of language can be used to predict cross-cultural differences in similarity judgments, and particularly, whether this approach provides additional insight beyond cross-cultural characterizations based on taxonomic vs.
+thematic preferences.
+
+We measured taxonomic vs. thematic similarity matching in a forced-choice word triad task in three populations.
 Following @Ji2004, we measured preferences in the US and China.
@@
 Data collection and analyses for this study were pre-registered, and the pre-registration is available at [blinded for peer review].
-We recruited `r df.excl_US$ppts_finished` participants from the US, `r df.excl_VN$ppts_finished` from Vietnam, and `r df.excl_CN$ppts_finished` from mainland China.
-All participants were recruited through snowball sampling, which, in the US was seeded with student email lists at a large university, in Vietnam (VN) with Vietnam-based student groups on Facebook, and in China (CN) with student groups on WeChat.
-US participants were compensated with \$5 gift certificates (USD), VN participants received 50,000₫ (VND) in phone credit, and CN participants received 25CNY through WeChat credit transfer.
-
-We excluded `r df.excl_US$ppts_finished - df.excl_US$ppts_after_att_check_excl` US participants, `r df.excl_VN$ppts_finished - df.excl_VN$ppts_after_att_check_excl` VN participants, and `r df.excl_CN$ppts_finished - df.excl_CN$ppts_after_att_check_excl` CN participants who missed two or more of the 10 attention check questions.
+We recruited `r df.excl_US$ppts_finished` participants from the US, `r df.excl_CN$ppts_finished` from mainland China, and `r df.excl_VN$ppts_finished` from Vietnam.
+All participants were recruited through snowball sampling, which, in the US was seeded with student email lists at a large university, in China (CN) with student groups on WeChat, and in Vietnam (VN) with Vietnam-based student groups on Facebook.
+US participants were compensated with \$5 gift certificates (USD), CN participants received 25CNY through WeChat credit transfer, and VN participants received 50,000₫ (VND) in phone credit,
+
+We excluded `r df.excl_US$ppts_finished - df.excl_US$ppts_after_att_check_excl` US participants, `r df.excl_CN$ppts_finished - df.excl_CN$ppts_after_att_check_excl` CN participants, and `r df.excl_VN$ppts_finished - df.excl_VN$ppts_after_att_check_excl` VN participants, who missed two or more of the 11 attention check questions.
 
@@
 This approach would have substantially reduced our sample size, disproportionately affecting the VN sample (resulting in a final sample of 109 US, 132 CN, and 57 VN participants).
-We report results with the less stringent exclusion criterion, but we performed analyses with both samples and found broadly similar results. Any differences are noted in the Analysis.
+We report results with the less stringent exclusion criterion, but we performed analyses with both samples and found broadly similar results.
+Any differences are noted in the Results & Discussion section.
 
@@
 Specifically, we did not exclude VN and CN participants who spoke English, or US participants with significant international experience.
-As a result of these demographic exclusions, we excluded `r df.excl_US$ppts_after_att_check_excl - df.excl_US$ppts_after_demog_excl` US, `r df.excl_VN$ppts_after_att_check_excl - df.excl_VN$ppts_after_demog_excl` VN, and `r df.excl_CN$ppts_after_att_check_excl - df.excl_CN$ppts_after_demog_excl` CN participants.
+As a result of these demographic exclusions, we excluded `r df.excl_US$ppts_after_att_check_excl - df.excl_US$ppts_after_demog_excl` US, `r df.excl_CN$ppts_after_att_check_excl - df.excl_CN$ppts_after_demog_excl` CN, and `r df.excl_VN$ppts_after_att_check_excl - df.excl_VN$ppts_after_demog_excl` VN participants.
 The final US sample included `r df.excl_US$ppts_after_demog_excl` participants (`r df.gender_E %>% filter(gender == "Male") %>% pull(n)`M, `r df.gender_E %>% filter(gender == "Female") %>% pull(n)`F, `r df.gender_E %>% filter(gender == "Non-binary") %>% pull(n)` non-binary, `r df.gender_E %>% filter(gender == "Decline to answer") %>% pull(n)` other), with mean age = `r round(df.age_E$mean_age, 2)` (SD = `r round(df.age_E$sd_age, 2)`).
-Our VN sample included `r df.excl_VN$ppts_after_demog_excl` participants (`r df.gender_V %>% filter(gender == "Nam") %>% pull(n)`M, `r df.gender_V %>% filter(gender == "Nữ") %>% pull(n)`F, `r df.gender_V %>% filter(gender == "Từ chối trả lời") %>% pull(n)` other), with mean age = `r round(df.age_V$mean_age, 2)` (SD = `r round(df.age_V$sd_age, 2)`).
-And the CN sample included `r df.excl_CN$ppts_after_demog_excl` participants (`r df.gender_M %>% filter(gender == "男性") %>% pull(n)`M, `r df.gender_M %>% filter(gender == "女性") %>% pull(n)`F, `r df.gender_M %>% filter(gender == "拒绝回答") %>% pull(n)` other), with mean age = `r round(df.age_M$mean_age, 2)` (SD = `r round(df.age_M$sd_age, 2)`).[^4]
-
-[^4]: A table summarizing the number of participants omitted for each criterion is included in the Supplementary Information.
+The CN sample included `r df.excl_CN$ppts_after_demog_excl` participants (`r df.gender_M %>% filter(gender == "男性") %>% pull(n)`M, `r df.gender_M %>% filter(gender == "女性") %>% pull(n)`F, `r df.gender_M %>% filter(gender == "拒绝回答") %>% pull(n)` other), with mean age = `r round(df.age_M$mean_age, 2)` (SD = `r round(df.age_M$sd_age, 2)`).
+And the VN sample included `r df.excl_VN$ppts_after_demog_excl` participants (`r df.gender_V %>% filter(gender == "Nam") %>% pull(n)`M, `r df.gender_V %>% filter(gender == "Nữ") %>% pull(n)`F, `r df.gender_V %>% filter(gender == "Từ chối trả lời") %>% pull(n)` other), with mean age = `r round(df.age_V$mean_age, 2)` (SD = `r round(df.age_V$sd_age, 2)`).[^2]
+
+[^2]: A table summarizing the number of participants omitted for each criterion is included in the Supplementary Information.
 
@@
 We included 105 such triads, a superset including triads pulled from supplemental information and in-text examples across the literature, and others that we adapted or created <!--(see SI for the full list of stimuli and sources)-->.
-We selected triads on the basis of cultural familiarity within the US, Vietnam, and China.
-The triads were translated from English to Vietnamese and Mandarin by fluent bilingual speakers of each language, and backtranslated to English by another fluent bilingual who was naive to the original English version.
+We selected triads on the basis of cultural familiarity within the US, China, and Vietnam.
+The triads were translated from English to Mandarin and Vietnamese by fluent bilingual speakers of each language, and backtranslated to English by another fluent bilingual who was naive to the original English version.
 The backtranslations were checked against the original English to identify ambiguities in the translation, which were resolved through discussion and selection of alternative terms when relevant.
@@
 ## Procedure
-
-Each participant completed all 105 triads in blocks of 21 trials at a time (10 test triads, 10 filler triads, and 1 attention check per page), by selecting the match most related to the cue ("Which thing is most closely related to the bolded item?" and translated equivalents).
+\begin{CJK*}{UTF8}{gbsn}
+Each participant completed all 105 triads in blocks of 21 trials at a time (10 test triads, 10 filler triads, and 1 attention check per page), by selecting the match most related to the cue (following Ji et al., 2004): "Which thing is most closely related to the bolded item?" / "哪个事物与加粗项关联最紧密?" / "Thứ nào liên quan nhất với thứ được in đậm?".
 The test triads were presented with 105 filler triads mixed in, to obscure the taxonomic-thematic two-answer forced choice structure of the test stimuli and reduce the likelihood that participants would become aware of the design.
 The filler triads were groups of three semantically related words, but where the match options were not distinguished by thematic vs.
-taxonomic similarity, for example, the cue "bird" with match options "lizard" and "toad." Additionally, we included 10 attention check trials, which were formatted similarly to the test and filler triads but included an instruction instead of a cue item, e.g., "Choose wife" with match options "wife" and "husband." In total, each participant completed 210 similarity judgments (105 test triads and 105 fillers) and 10 attention check questions, with all items presented in randomized orders that varied between subjects.
+taxonomic similarity, for example, the cue "bird" with match options "lizard" and "toad." Additionally, we included 11 attention check trials, which were formatted similarly to the test and filler triads but included an instruction instead of a cue item, e.g., "Choose wife" with match options "wife" and "husband." In total, each participant completed 210 similarity judgments (105 test triads and 105 fillers) and 11 attention check questions, with all items presented in randomized orders that varied between subjects.
+\end{CJK*}
 
@@
 We retrieved word vectors for "cow" and "grass", and calculated the cosine distance between these vectors.
-We did the same for "cow" and "chicken."
-Our similarity prediction is inversely proportional to the ratio of cosine distance of these pairs.
+We did the same for "cow" and "chicken." Our similarity prediction is inversely proportional to the ratio of cosine distance of these pairs.
 This is because a larger cosine distance means the word vectors are further apart, and thus the words are less similar.
@@
 
-In keeping with @Ji2004, we would expect participants from mainland China to prefer thematic matches more than US participants (e.g., to prefer the cow-grass match over cow-chicken to a greater extent than US participants).
-On the basis of the previous literate more broadly, we would also expect participants from Vietnam to pattern with China, showing a stronger preference for thematic matches than US participants.
-
-We observed the strongest preference for thematic matching in China (M = `r round((df.country_sum %>% filter(country == "China"))$mean_theme_resp_percent, 2)`, SD = `r round((df.country_sum %>% filter(country == "China"))$sd_theme_resp_percent, 2)`), followed by Vietnam (M = `r round((df.country_sum %>% filter(country == "Vietnam"))$mean_theme_resp_percent, 2)`, SD = `r round((df.country_sum %>% filter(country == "Vietnam"))$sd_theme_resp_percent, 2)`), and then the US (M = `r round((df.country_sum %>% filter(country == "US"))$mean_theme_resp_percent, 2)`, SD = `r round((df.country_sum %>% filter(country == "US"))$sd_theme_resp_percent, 2)`; see Figure 1).
+Following previous work, we would expect participants from mainland China to prefer thematic matches more than US participants (to use the cow-grass-chicken triad: we would expect participants from mainland China to prefer the cow-grass match over the cow-chicken match to a larger extent compared to US participants).
+We would also expect that participants from Vietnam would pattern with China, and also show a significantly higher preference for thematic matches compare to US participants.
+
+The group means of proportion of thematic response in mainland China is the highest (M = `r round((df.country_sum %>% filter(country == "China"))$mean_theme_resp_percent, 2)`, SD = `r round((df.country_sum %>% filter(country == "China"))$sd_theme_resp_percent, 2)`), followed by the groups means in Vietnam (M = `r round((df.country_sum %>% filter(country == "Vietnam"))$mean_theme_resp_percent, 2)`, SD = `r round((df.country_sum %>% filter(country == "Vietnam"))$sd_theme_resp_percent, 2)`), which is slightly higher than that of the US (M = `r round((df.country_sum %>% filter(country == "US"))$mean_theme_resp_percent, 2)`, SD = `r round((df.country_sum %>% filter(country == "US"))$sd_theme_resp_percent, 2)`) (Figure 1).
 
@@
 
-To test for differences in similarity judgment between the countries, we ran a mixed-effects logistic regression predicting triad match (taxonomic or thematic) with country (US, China, or Vietnam) as a fixed effect.
+To test for cross-context differences in similarity judgments between the countries, we ran a mixed-effects logistic regression predicting triad responding (taxonomic or thematic) with country (US, China, or Vietnam) as a fixed effect.
 As random effects, we included an intercept per subject and one per triad, as well as by-triad random slopes for country to account for variation in the country effect across triads.
 
-We found a significant effect of country ($\chi^2$(`r fit.country.anova["country", "Df"]`) = `r round(fit.country.anova["country", "Chisq"], 2)`, p `r ifelse( fit.country.anova["country", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.country.anova["country", "Pr(>Chisq)"], 3)), "< .001")`), but this effect is driven by the difference between US and CN responding ($\beta$ = `r round(fixef(fit.country)["countryUS"], 2)`, p `r ifelse(as.data.frame(summary(fit.country)[["coefficients"]])["countryUS", "Pr(>|z|)"] > 0.001, paste0("= ", round(as.data.frame(summary(fit.country)[["coefficients"]])["countryUS", "Pr(>|z|)"], 3)), "< .001")`).
-There was no statistical difference between matching in Vietnam and China ($\beta$ = `r round(fixef(fit.country)["countryVietnam"], 2)`, p `r ifelse(as.data.frame(summary(fit.country)[["coefficients"]])["countryVietnam", "Pr(>|z|)"] > 0.001, paste0("= ", round(as.data.frame(summary(fit.country)[["coefficients"]])["countryVietnam", "Pr(>|z|)"], 3)), "< .001")`), or the US and Vietnam ($\beta$ = `r round(fixef(fit.country_EN_VN)["countryVietnam"], 2)`, p `r ifelse(as.data.frame(summary(fit.country_EN_VN)[["coefficients"]])["countryVietnam", "Pr(>|z|)"] > 0.001, paste0("= ", round(as.data.frame(summary(fit.country_EN_VN)[["coefficients"]])["countryVietnam", "Pr(>|z|)"], 3)), "< .001")`).
+Overall, there is a significant effect of country on proportion of thematic responses ($\chi^2$(`r fit.country.anova["country", "Df"]`) = `r round(fit.country.anova["country", "Chisq"], 2)`, p `r ifelse( fit.country.anova["country", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.country.anova["country", "Pr(>Chisq)"], 3)), "< .001")`).
+However, this effect is driven by the difference between US and China responding ($\beta_{US}$ = `r round(fixef(fit.country)["countryUS"], 2)`, p `r ifelse(as.data.frame(summary(fit.country)[["coefficients"]])["countryUS", "Pr(>|z|)"] > 0.001, paste0("= ", round(as.data.frame(summary(fit.country)[["coefficients"]])["countryUS", "Pr(>|z|)"], 3)), "< .001")`).
+There is no statistical difference between the Vietnam and China responding ($\beta_{Vietnam}$ = `r round(fixef(fit.country)["countryVietnam"], 2)`, p `r ifelse(as.data.frame(summary(fit.country)[["coefficients"]])["countryVietnam", "Pr(>|z|)"] > 0.001, paste0("= ", round(as.data.frame(summary(fit.country)[["coefficients"]])["countryVietnam", "Pr(>|z|)"], 3)), "< .001")`), and the US and Vietnam responding ($\beta_{US}$ = `r round(fixef(fit.country_EN_VN)["countryVietnam"], 2)`, p `r ifelse(as.data.frame(summary(fit.country_EN_VN)[["coefficients"]])["countryVietnam", "Pr(>|z|)"] > 0.001, paste0("= ", round(as.data.frame(summary(fit.country_EN_VN)[["coefficients"]])["countryVietnam", "Pr(>|z|)"], 3)), "< .001")`).
 
@@
 
-For US responding: only the English (EN) corpus is a significant predictor[^5].
+For US responding: only the English (EN) corpus is a significant predictor[^3].
 EN corpus: $\beta$ = `r round(fixef(fit.ENVIZH_US_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.ENVIZH_US_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.ENVIZH_US_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_US_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_US_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"], 3)), "< .001")`.
@@
 
-[^5]: With preregistered exclusion criterion: only the English (EN) and Mandarin (ZH) corpus are significant predictors.
-
-For Vietnam responding: only the Vietnamese (VI) and Mandarin (ZH) corpus are significant predictors[^6].
+[^3]: With preregistered exclusion criterion: only the English (EN) and Mandarin (ZH) corpus are significant predictors.
+
+For Vietnam responding: only the Vietnamese (VI) and Mandarin (ZH) corpus are significant predictors[^4].
 EN corpus: $\beta$ = `r round(fixef(fit.ENVIZH_VN_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.ENVIZH_VN_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_VN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"], 3)), "< .001")`.
@@
 
-[^6]: With preregistered exclusion criterion: all three corpora are significant predictors.
+[^4]: With preregistered exclusion criterion: all three corpora are significant predictors.
 
@@
 <!-- Our above models tested whether language statistics is a good predictor for similarity judgment. -->
+
 <!-- As we noted above, language statistics can be a proxy of both inputs and conceptualization of similarity. -->
+
 <!-- However, it is still an open question whether conceptualization of similarity itself has a unique contribution to similarity judgment (beyond its influence on language statistics). -->
+
 <!-- To test this hypothesis, we operationalize cultural-specific conceptualization of similarity as country. -->
+
 <!-- We then compare a model that includes country, corresponding corpus statistics and their interaction as fixed effects to a model with only the corresponding corpus statistics as the fixed effect.
 -->
+
 <!-- If conceptualization of similarity has a unique contribution to similarity judgment, we should see that terms including country to be a significant predictor of responding. -->
@@
 
-To investigate whether language statistics predicts triads and filler items differently, we compare the variance in responding that can be accounted for by language statistics of the corresponding corpus in the two different types of items (structured triads versus non-structured filler items).
+To investigate whether language statistics predicts triads and filler items differently, we compare the variance in responding that can be accounted for by language statistics of the corresponding corpus in the two different types of items (structured triads vs.
+non-structured filler items).
 Namely, we ran two mixed-effects logistic regression models that predict responding across cultural contexts (1=thematic or word1, 0=taxonomic or word2), with the corresponding corpus statistics (for e.g., cosine proportion from the English corpus for US responding) as a fixed effect and participant and item as random effects.
@@
 Our sample of Vietnamese participants showed intermediate response but not significantly different from either Chinese or US participants.
-This finding suggests some limitations on the generality of the cultural account, which proposes that thematic/taxonomic similarity preference aligns with East Asian/Western tendency for holistic vs analytic processing.
+This finding suggests some limitations on the generality of the cultural account, which proposes that thematic/taxonomic similarity preference aligns with East Asian/Western tendency for holistic vs.
+analytic processing.
 We found some support for the environmental statistics account: each corpus statistics is a good predictor for the corresponding country's similarity judgments, even when other corpus statistics are included, and even with triads without a thematic/taxonomic structure.
-<!-- However, we also found that culture-based conceptualization of similarity uniquely contributes to predicting similarity judgment when included in a model with corpus statistics. -->
-Overall, our results provide evidence that cross-cultural differences in similarity judgment are related to linguistic co-occurrence patterns (which also vary across cultures).
+<!-- However, we also found that culture-based conceptualization of similarity uniquely contributes to predicting similarity judgment when included in a model with corpus statistics.
+--> Overall, our results provide evidence that cross-cultural differences in similarity judgment are related to linguistic co-occurrence patterns (which also vary across cultures).
 
@@
 @Ji2004 established that culture-aligned differences in this paradigm exist, even when the test language is held constant, concluding that "it is culture (independent of the testing language) that led to different grouping styles" in their study.
-Our data provide a cautionary note to this conclusion, suggesting that while cultural differences in similarity judgment exists, we might get better traction at modelling cross-cultural variation through environmental statistics such as lexical co-occurrences, rather than treating groups of cultures as monoliths (East Asian vs Western).
+Our data provide a cautionary note to this conclusion, suggesting that while cultural differences in similarity judgment exists, we might get better traction at modelling cross-cultural variation through environmental statistics such as lexical co-occurrences, rather than treating groups of cultures as monoliths (East Asian vs.
+Western).
 However, there are still many open questions for this account.
 Our operationalization of environmental statistics with lexical co-occurrence is a proxy of both language inputs and culture-specific conceptualization of similarity.
-The extent to which cross-cultural differences in similarity judgment are driven by language versus culture is still an open question.
+The extent to which cross-cultural differences in similarity judgment are driven by language vs. culture is still an open question.
 Future work should also aim to provide a more specific computational account of how lexical co-occurrence might guide categorization preference beyond the simple proportion-of-similarity model tested here, and investigate other individual- or triad-specific factors that might influence how environmental statistics affect similarity judgment.
@@
 # Acknowledgements
+
 BLINDED FOR PEER REVIEW.

### 2023-02-02 code/4_paper/manuscript/manuscript.tex
manuscript updates

--- 2023-02-01 code/4_paper/manuscript/manuscript.tex
@@
 \usepackage{kotex}
+\usepackage{CJKutf8}
 \usepackage{booktabs}
@@
 correspondingly, taxonomic similarity, while holistic processing
-emphasizes relations between objects and their context and therefor,
+emphasizes relations between objects and their context and therefore,
 thematic similarity. In related work, East Asian participants show a
@@
 particularly, whether this approach provides additional insight beyond
-cross-cultural characterizations based on taxonomic vs thematic
+cross-cultural characterizations based on taxonomic vs.~thematic
 preferences.
 
-We measured taxonomic versus thematic similarity matching in a
+We measured taxonomic vs.~thematic similarity matching in a
 forced-choice word triad task in three populations. Following Ji et al.
@@
 
-We recruited 200 participants from the US, 199 participants from
-Vietnam, and 200 participants from mainland China. US participants were
-recruited through snowball sampling seeded with Stanford student email
-lists, Vietnam participants were recruited through snowball sampling
-seeded with Vietnam-based student groups on Facebook, and mainland China
-participants were recruited through snowball sampling seeded with group
-chats on WeChat. US participants were compensated with \$5 gift
-certificates (USD), VN participants received 50,000₫ (VND) in phone
-credit, and mainland China participants received 25CNY through WeChat
-credit transfer.
+Data collection and analyses for this study were pre-registered, and the
+pre-registration is available at {[}blinded for peer review{]}. We
+recruited 200 participants from the US, 200 from mainland China, and 199
+from Vietnam. All participants were recruited through snowball sampling,
+which, in the US was seeded with student email lists at a large
+university, in China (CN) with student groups on WeChat, and in Vietnam
+(VN) with Vietnam-based student groups on Facebook. US participants were
+compensated with \$5 gift certificates (USD), CN participants received
+25CNY through WeChat credit transfer, and VN participants received
+50,000₫ (VND) in phone credit,
 
-We excluded 8 US participants, 62 Vietnam participants, and 16 China
-participants who missed 2 or more attention checks. We followed 4
-exclusion criteria that aim to retain only participants who are
-influenced by one culture: (1) non-native speakers of English and
-Vietnamese, respectively, (2) fluent in at least one of the other two
-study languages (Vietnamese for US participants, English for Vietnamese
-participants and Chinese participants), (3) have lived outside of the
-test country (US, Vietnam, or China) for more than two years, and (4)
-have significant international experience (more than 6 international
-experiences of 2 days or longer.) We did not use a particular criterion
-for a language if it would exclude 25\% or more of any one sample. In
-this round of exclusion, we excluded 73 US, 27 Vietnam participants, and
-35 China participants. After these exclusions, the US sample included
-119 participants (30M, 84F, 3 non-binary, 2 other), with mean age = 22.2
-(SD = 8.15) and median age = 20. The Vietnam sample included 110
-participants (34M, 71F, 5 other), with mean age = 22.21 (SD = 5.81) and
-median age = 21. The China sample included 149 participants (61M, 87F, 1
-other), with mean age = 23.1 (SD = 3.65) and median age = 23.\footnote{A
-  table summarizing number of participants lost at each round of
-  exclusions is included in the Supplementary Information.}
+We excluded 8 US participants, 16 CN participants, and 62 VN
+participants, who missed two or more of the 11 attention check
+questions.
 
-We preregistered a more stringent exclusion criterion where participants
-were excluded if they missed any attention checks. However, this led to
-a small sample size, especially for Vietnam context (US = 109, China =
-132, Vietnam = 57). Our reported results with the less stringent
-exclusion criterion (detailed above) is largely not different from the
-results with the preregistered criterion. Any differences are noted in
-the Analysis section.
+In doing so, we deviated from our preregistered exclusion criterion,
+which used a more stringent policy, excluding participants who missed
+any of the 10 attention checks. This approach would have substantially
+reduced our sample size, disproportionately affecting the VN sample
+(resulting in a final sample of 109 US, 132 CN, and 57 VN participants).
+We report results with the less stringent exclusion criterion, but we
+performed analyses with both samples and found broadly similar results.
+Any differences are noted in the Results \& Discussion section.
 
-\hypertarget{stimuli-materials}{%
-\subsection{Stimuli Materials}\label{stimuli-materials}}
+We also applied four demographic exclusion criteria designed to reduce
+cross-cultural influences across our samples: we excluded participants
+who (1) were not native speakers of the test language (English,
+Vietnamese, or Mandarin Chinese), (2) were fluent in another one of the
+study languages, (3) had lived outside of the test country for more than
+two years, or (4) had significant international experience (more than 6
+international experiences of 2 days or longer). Following our
+pre-registration, we dropped any exclusion criterion that would exclude
+25\% or more of any one population, but only for that population.
+Specifically, we did not exclude VN and CN participants who spoke
+English, or US participants with significant international experience.
+As a result of these demographic exclusions, we excluded 73 US, 35 CN,
+and 27 VN participants. The final US sample included 119 participants
+(30M, 84F, 3 non-binary, 2 other), with mean age = 22.2 (SD = 8.15). The
+CN sample included 149 participants (61M, 87F, 1 other), with mean age =
+23.1 (SD = 3.65). And the VN sample included 110 participants (34M, 71F,
+5 other), with mean age = 22.21 (SD = 5.81).\footnote{A table
+  summarizing the number of participants omitted for each criterion is
+  included in the Supplementary Information.}
 
-We adapted stimuli from previous studies to create a set of test triads
-consisting of a cue, with one thematic and one taxonomic match option.
-For example, ``cow,'' ``grass,'' and ``chicken,'' where ``cow'' is the
-cue, ``grass'' is the thematic match, and ``chicken'' the taxonomic
-match. We included 105 such triads, a superset including triads pulled
-from supplemental information and in-text examples across the
-literature, and others that we adapted or created . We selected triads
-on the basis of cultural familiarity in the US, Vietnam, and China. The
-triads were originally in English; they were translated to Vietnamese
-and Mandarin by a fluent bilingual speaker in each language. The
-translations were then checked for accuracy after backtranslation to
-English by another fluent bilingual in each language who was naive to
-the original English versions. All materials are available at {[}BLINDED
-FOR REVIEW{]}.
+\hypertarget{materials}{%
+\subsection{Materials}\label{materials}}
+
+All stimuli and scripts for the experiment and analysis are available at
+{[}BLINDED FOR REVIEW{]}. We collected and adapted stimuli from previous
+studies to create test triads consisting of a cue with one thematic and
+one taxonomic match option. For example, ``cow,'' ``grass,'' and
+``chicken,'' where ``cow'' is the cue, ``grass'' is the thematic match,
+and ``chicken'' the taxonomic match. We included 105 such triads, a
+superset including triads pulled from supplemental information and
+in-text examples across the literature, and others that we adapted or
+created . We selected triads on the basis of cultural familiarity within
+the US, China, and Vietnam. The triads were translated from English to
+Mandarin and Vietnamese by fluent bilingual speakers of each language,
+and backtranslated to English by another fluent bilingual who was naive
+to the original English version. The backtranslations were checked
+against the original English to identify ambiguities in the translation,
+which were resolved through discussion and selection of alternative
+terms when relevant.
 
@@
 
-Each participant completed all 105 triads in sets of 21 trials at a time
-(10 test triads, 10 filler triads, and 1 attention check per page), by
-selecting the match most related to the cue (``Which thing is most
-closely related to the bolded item?'' and translated equivalents). The
-test triads were presented with 105 filler triads mixed in, to obscure
-the taxonomic-thematic two-answer forced choice structure of the test
-stimuli and reduce the likelihood that participants would become aware
-of the design. The filler triads were groups of three semantically
-related words, but where the match options were not distinguished by
-thematic vs.~taxonomic similarity, e.g., cue ``bird'' with match options
-``lizard'' and ``toad.'' Additionally, we included 10 attention check
-trials, which were formatted like the test and filler triads but
-included an instruction instead of a cue item, e.g., ``Choose wife''
-with match options ``wife'' and ``husband.'' In total, each participant
-completed 210 similarity judgments and 10 attention check questions,
-with triads presented in randomized orders that varied between subjects.
+\begin{CJK*}{UTF8}{gbsn}
+Each participant completed all 105 triads in blocks of 21 trials at a time (10 test triads, 10 filler triads, and 1 attention check per page), by selecting the match most related to the cue (following Ji et al., 2004): "Which thing is most closely related to the bolded item?" / "哪个事物与加粗项关联最紧密?" / "Thứ nào liên quan nhất với thứ được in đậm?".
+The test triads were presented with 105 filler triads mixed in, to obscure the taxonomic-thematic two-answer forced choice structure of the test stimuli and reduce the likelihood that participants would become aware of the design.
+The filler triads were groups of three semantically related words, but where the match options were not distinguished by thematic vs.
+taxonomic similarity, for example, the cue "bird" with match options "lizard" and "toad." Additionally, we included 11 attention check trials, which were formatted similarly to the test and filler triads but included an instruction instead of a cue item, e.g., "Choose wife" with match options "wife" and "husband." In total, each participant completed 210 similarity judgments (105 test triads and 105 fillers) and 11 attention check questions, with all items presented in randomized orders that varied between subjects.
+\end{CJK*}
 
@@
 
-To give an intuition for our model, consider again the cow-grass-chicken
-triad: we retrieved word vectors for ``cow'' and ``grass'', and
-calculate the cosine distance between these vectors. Similarly, we
-retrieved vectors for ``cow'' and ``chicken'' and calculate the cosine
-distance between them. Our similarity prediction is then inversely
-proportional to the ratio of cosine distance of these pairs. This is
-because a larger cosine distance means the word vectors are further
-apart, and thus the words are less similar. For example, if the cosine
-distance of thematic cow-grass is 0.7 and the cosine distance of
-taxonomic cow-chicken is 0.3, then our model predicts, correspondingly,
-that 30\% of responses to the triad will be grass, and the other 70\%
-chicken.
+To give an intuition for our model, consider again the cow:
+grass/chicken triad. We retrieved word vectors for ``cow'' and
+``grass'', and calculated the cosine distance between these vectors. We
+did the same for ``cow'' and ``chicken.'' Our similarity prediction is
+inversely proportional to the ratio of cosine distance of these pairs.
+This is because a larger cosine distance means the word vectors are
+further apart, and thus the words are less similar. For example, if the
+cosine distance of thematic cow-grass is 0.7 and the cosine distance of
+taxonomic cow-chicken is 0.3 (the more similar of the two), then our
+model predicts, correspondingly, that 30\% of responses to the triad
+will be grass, and the other 70\% chicken.
 
-In practice, we calculated the cosine distance between each cue-thematic
-match (thematic cosine distance) and cue-taxonomic match (taxonomic
-cosine distance), using the spatial.distance.cosine function from the
-SciPy package (Virtanen et al., 2020). We then calculated the thematic
+We calculated the cosine distance between each cue-thematic match
+(thematic cosine distance) and cue-taxonomic match (taxonomic cosine
+distance), using the spatial.distance.cosine function from the SciPy
+package in R (Virtanen et al., 2020). We then calculated the thematic
 cosine distance proportion as thematic cosine distance over the sum of
-taxonomic cosine distance and thematic cosine distance. We did this for
-all three corpora. We were able to obtain predictions for all triads in
-all languages. We then use a mixed-effects regression to evaluate how
-well each corpus model predicts participants' similarity judgments,
-across triads and cultural contexts. All analyses are available at
-{[}BLINDED FOR REVIEW{]}.
+taxonomic cosine distance and thematic cosine distance. We followed this
+process for all three corpora, and were able to obtain predictions for
+all triads in all languages. Then, we used a mixed-effects regression to
+evaluate how well each corpus model predicts participants' similarity
+judgments, across triads and cultural contexts.
 
@@
 this effect is driven by the difference between US and China responding
-(\(\beta\) = -0.48, p \textless{} .001). There is no statistical
-difference between the Vietnam and China responding (\(\beta\) = -0.22,
-p = 0.09), and the US and Vietnam responding (\(\beta\) = 0.26, p =
-0.086).
+(\(\beta_{US}\) = -0.48, p \textless{} .001). There is no statistical
+difference between the Vietnam and China responding (\(\beta_{Vietnam}\)
+= -0.22, p = 0.09), and the US and Vietnam responding (\(\beta_{US}\) =
+0.26, p = 0.086).
 
@@
 accounted for by language statistics of the corresponding corpus in the
-two different types of items (structured triads versus non-structured
+two different types of items (structured triads vs.~non-structured
 filler items). Namely, we ran two mixed-effects logistic regression
@@
 account, which proposes that thematic/taxonomic similarity preference
-aligns with East Asian/Western tendency for holistic vs analytic
+aligns with East Asian/Western tendency for holistic vs.~analytic
 processing. We found some support for the environmental statistics
@@
 such as lexical co-occurrences, rather than treating groups of cultures
-as monoliths (East Asian vs Western). However, there are still many open
-questions for this account. Our operationalization of environmental
+as monoliths (East Asian vs.~Western). However, there are still many
+open questions for this account. Our operationalization of environmental
 statistics with lexical co-occurrence is a proxy of both language inputs
@@
 which cross-cultural differences in similarity judgment are driven by
-language versus culture is still an open question. Future work should
-also aim to provide a more specific computational account of how lexical
+language vs.~culture is still an open question. Future work should also
+aim to provide a more specific computational account of how lexical
 co-occurrence might guide categorization preference beyond the simple

### 2023-02-02 code/4_paper/manuscript/manuscript.Rmd

--- 2023-02-02 code/4_paper/manuscript/manuscript.Rmd
@@
 Specifically, we did not exclude VN and CN participants who spoke English, or US participants with significant international experience.
-As a result of these demographic exclusions, we excluded `r df.excl_US$ppts_after_att_check_excl - df.excl_US$ppts_after_demog_excl` US, `r df.excl_VN$ppts_after_att_check_excl - df.excl_VN$ppts_after_demog_excl` VN, and `r df.excl_CN$ppts_after_att_check_excl - df.excl_CN$ppts_after_demog_excl` CN participants.
+As a result of these demographic exclusions, we excluded `r df.excl_US$ppts_after_att_check_excl - df.excl_US$ppts_after_demog_excl` US, `r df.excl_CN$ppts_after_att_check_excl - df.excl_CN$ppts_after_demog_excl` CN, and `r df.excl_VN$ppts_after_att_check_excl - df.excl_VN$ppts_after_demog_excl` VN participants.
 The final US sample included `r df.excl_US$ppts_after_demog_excl` participants (`r df.gender_E %>% filter(gender == "Male") %>% pull(n)`M, `r df.gender_E %>% filter(gender == "Female") %>% pull(n)`F, `r df.gender_E %>% filter(gender == "Non-binary") %>% pull(n)` non-binary, `r df.gender_E %>% filter(gender == "Decline to answer") %>% pull(n)` other), with mean age = `r round(df.age_E$mean_age, 2)` (SD = `r round(df.age_E$sd_age, 2)`).
-Our VN sample included `r df.excl_VN$ppts_after_demog_excl` participants (`r df.gender_V %>% filter(gender == "Nam") %>% pull(n)`M, `r df.gender_V %>% filter(gender == "Nữ") %>% pull(n)`F, `r df.gender_V %>% filter(gender == "Từ chối trả lời") %>% pull(n)` other), with mean age = `r round(df.age_V$mean_age, 2)` (SD = `r round(df.age_V$sd_age, 2)`).
-And the CN sample included `r df.excl_CN$ppts_after_demog_excl` participants (`r df.gender_M %>% filter(gender == "男性") %>% pull(n)`M, `r df.gender_M %>% filter(gender == "女性") %>% pull(n)`F, `r df.gender_M %>% filter(gender == "拒绝回答") %>% pull(n)` other), with mean age = `r round(df.age_M$mean_age, 2)` (SD = `r round(df.age_M$sd_age, 2)`).[^4]
+The CN sample included `r df.excl_CN$ppts_after_demog_excl` participants (`r df.gender_M %>% filter(gender == "男性") %>% pull(n)`M, `r df.gender_M %>% filter(gender == "女性") %>% pull(n)`F, `r df.gender_M %>% filter(gender == "拒绝回答") %>% pull(n)` other), with mean age = `r round(df.age_M$mean_age, 2)` (SD = `r round(df.age_M$sd_age, 2)`).
+And the VN sample included `r df.excl_VN$ppts_after_demog_excl` participants (`r df.gender_V %>% filter(gender == "Nam") %>% pull(n)`M, `r df.gender_V %>% filter(gender == "Nữ") %>% pull(n)`F, `r df.gender_V %>% filter(gender == "Từ chối trả lời") %>% pull(n)` other), with mean age = `r round(df.age_V$mean_age, 2)` (SD = `r round(df.age_V$sd_age, 2)`).[^2]
 
@@
 In this study, we measure language and its relation to cross-cultural differences in categorization, but these relations test only the plausibility of a language-based account; they cannot establish the direction of causality.
+@Ji2004 established that culture-aligned differences in this paradigm exist, even when the test language is held constant, concluding that "it is culture (independent of the testing language) that led to different grouping styles" in their study.
+Our data provide a cautionary note to this conclusion, suggesting that while cultural differences in similarity judgment exists, we might get better traction on modelling cross-cultural variation through environmental statistics such as lexical co-occurrences.
 

### 2023-02-02 code/4_paper/manuscript/manuscript.Rmd
almost done!

@@
 
-Data collection and analyses for this study were pre-registered, and the pre-registration is available at [blinded for peer review].
+Data collection and analyses for this study were pre-registered, and the pre-registration is available at [blinded for review].
 We recruited `r df.excl_US$ppts_finished` participants from the US, `r df.excl_CN$ppts_finished` from mainland China, and `r df.excl_VN$ppts_finished` from Vietnam.
@@
 
-All stimuli and scripts for the experiment and analysis are available at [BLINDED FOR REVIEW].
+All stimuli and scripts for the experiment and analysis are available at [blinded for review].
 We collected and adapted stimuli from previous studies to create test triads consisting of a cue with one thematic and one taxonomic match option.
@@
 \begin{CJK*}{UTF8}{gbsn}
-Each participant completed all 105 triads in blocks of 21 trials at a time (10 test triads, 10 filler triads, and 1 attention check per page), by selecting the match most related to the cue (following Ji et al., 2004): "Which thing is most closely related to the bolded item?" / "哪个事物与加粗项关联最紧密?" / "Thứ nào liên quan nhất với thứ được in đậm?".
+Each participant completed all 105 triads in blocks of 21 trials at a time (10 test triads, 10 filler triads, and 1 attention check per page), by selecting the match most related to the cue.
+We elicited similarity match responses by asking "Which thing is most closely related to the bolded [cue] item?" In Mandarin Chinese, we used the phrasing for "most closely related" reported by Ji et al.
+(2004): "哪个事物与加粗项关联最紧密?" And in Vietnamese, we translated this as "Thứ nào liên quan nhất với thứ được in đậm?".
 The test triads were presented with 105 filler triads mixed in, to obscure the taxonomic-thematic two-answer forced choice structure of the test stimuli and reduce the likelihood that participants would become aware of the design.
@@
 In sum, we replicated the differences documented by @Ji2004 between the US and China.
-We did not find that Vietnamese participants grouped particularly with Chinese participants, however.
+However, we did not find that Vietnamese participants grouped particularly with Chinese participants.
 Instead they were intermediate between the two.
@@
 
-In our next analyses, we tested whether triad-level differences in judgments across countries could be predicted on the basis of language statistics.
+In our next analysis, we tested whether triad-level differences in judgments across countries could be predicted from language statistics.
 
@@
 <!-- To do this,  -->
-we use a mixed-effects logistic regressions fit individually for each country.
-Our models predicted responses by individual participants to particular triads (0=taxonomic or 1=thematic) with fastText predictions (proportion of cosine distance) as a fixed effect and participant and triad as random effects.
-If language statistics, contribute to the differences in similarity judgments, we would expect each language corpus to be a good predictor for similarity judgment responding in its corresponding context.
+we use a mixed-effects logistic regression fit individually for each country.
+Our models predicted responses by individual participants to particular triad (0=taxonomic or 1=thematic) with fastText predictions (proportion of cosine distance) as a fixed effect and participant and triad as random effects.
+If language statistics contribute to the differences in similarity judgments, we would expect each language corpus to be a good predictor for similarity judgments in the corresponding population.
 
@@
 If language statistics are able to predict meaningful culture-specific variation in similarity judgments (rather than just consistency across cultures), we would expect each corpus to be the best predictor of its corresponding culture compared to the other two corpora.
-We directly compared the corpus models by including all three corpus predictors as fixed effects in three mixed-effect regressions (predicting US, Vietnam and China responding) with the same random effects as above.
+We directly compared the corpus models by including all three corpus predictors as fixed effects in three mixed-effect regressions (predicting US, VN, and CN responding) with the same random effects as above.
 
@@
 
-[^5]: With the preregistered exclusion criterion, only the English (EN) and Mandarin (ZH) corpus were significant predictors.
-
-For Vietnam responding, only the Vietnamese (VI) and Mandarin (ZH) corpus were significant predictors[^6].
+[^5]: With the preregistered exclusion criteria, the English (EN) and Mandarin (ZH) corpora were significant predictors.
+
+For Vietnamese participants' responses, only the Vietnamese (VI) and Mandarin (ZH) corpora were significant predictors[^6].
 EN corpus: $\beta$ = `r round(fixef(fit.ENVIZH_VN_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.ENVIZH_VN_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_VN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"], 3)), "< .001")`.
@@
 
-[^6]: With the preregistered exclusion criterion, all three corpora were significant predictors.
-
-For China responding, only the Mandarin (ZH) and English (EN) corpus were significant predictors.
+[^6]: With the preregistered exclusion criteria, all three corpora were significant predictors.
+
+For responses by Chinese participants, only the Mandarin (ZH) and English (EN) corpus were significant predictors.
 EN corpus: $\beta$ = `r round(fixef(fit.ENVIZH_CN_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.ENVIZH_CN_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.ENVIZH_CN_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_CN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_CN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"], 3)), "< .001")`.
@@
 The English corpus was the best predictor for US responding, and the Mandarin corpus was the best predictor for Chinese responding.
-While this is not the case with the Vietnamese corpus and the Vietnam responding, the Vietnamese corpus was still a significant predictor for the Vietnam responding.
-These results support our hypothesis that specific language statistics can predict cross-cultural variations of similarity judgment.
+While this is not the case with the Vietnamese corpus and Vietnamese participants' responding, the Vietnamese corpus was still a significant predictor for this responding.
+These results support our hypothesis that specific language statistics can predict cross-cultural variation in similarity judgment.
 
@@
 
-However, in all cultural contexts, adding the other two corpora produced a significantly better fit than the identical model with only the corresponding corpus included as a predictor (US response: $\chi^2$(`r fit.US_cos_compare["fit.ENVIZH_US_cos", "Df"]`) = `r round(fit.US_cos_compare["fit.ENVIZH_US_cos", "Chisq"], 2)`, p `r ifelse( fit.US_cos_compare["fit.ENVIZH_US_cos", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.US_cos_compare["fit.ENVIZH_US_cos", "Pr(>Chisq)"], 3)), "< .001")`; Vietnam response: $\chi^2$(`r fit.VN_cos_compare["fit.ENVIZH_VN_cos", "Df"]`) = `r round(fit.VN_cos_compare["fit.ENVIZH_VN_cos", "Chisq"], 2)`, p `r ifelse( fit.VN_cos_compare["fit.ENVIZH_VN_cos", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.VN_cos_compare["fit.ENVIZH_VN_cos", "Pr(>Chisq)"], 3)), "< .001")`; China response: $\chi^2$(`r fit.CN_cos_compare["fit.ENVIZH_CN_cos", "Df"]`) = `r round(fit.CN_cos_compare["fit.ENVIZH_CN_cos", "Chisq"], 2)`, p `r ifelse( fit.CN_cos_compare["fit.ENVIZH_CN_cos", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.CN_cos_compare["fit.ENVIZH_CN_cos", "Pr(>Chisq)"], 3)), "< .001")`).
-This analysis suggests that culture-specific inputs to similarity judgment (as proxied by language statistics) do not fully explain cross-cultural differences in similarity judgment, whether due to noise in the estimates of language statistics or true additional variance picked up by embeddings from other corpora.
+However, in all cultural contexts, adding the other two corpora produced a significantly better fit than the identical model with only the corresponding corpus included as a predictor (US responses: $\chi^2$(`r fit.US_cos_compare["fit.ENVIZH_US_cos", "Df"]`) = `r round(fit.US_cos_compare["fit.ENVIZH_US_cos", "Chisq"], 2)`, p `r ifelse( fit.US_cos_compare["fit.ENVIZH_US_cos", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.US_cos_compare["fit.ENVIZH_US_cos", "Pr(>Chisq)"], 3)), "< .001")`; VN responses: $\chi^2$(`r fit.VN_cos_compare["fit.ENVIZH_VN_cos", "Df"]`) = `r round(fit.VN_cos_compare["fit.ENVIZH_VN_cos", "Chisq"], 2)`, p `r ifelse( fit.VN_cos_compare["fit.ENVIZH_VN_cos", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.VN_cos_compare["fit.ENVIZH_VN_cos", "Pr(>Chisq)"], 3)), "< .001")`; CN responses: $\chi^2$(`r fit.CN_cos_compare["fit.ENVIZH_CN_cos", "Df"]`) = `r round(fit.CN_cos_compare["fit.ENVIZH_CN_cos", "Chisq"], 2)`, p `r ifelse( fit.CN_cos_compare["fit.ENVIZH_CN_cos", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.CN_cos_compare["fit.ENVIZH_CN_cos", "Pr(>Chisq)"], 3)), "< .001")`).
+This analysis suggests that culture-specific input to similarity judgments (as proxied by language statistics) do not fully explain cross-cultural differences in similarity judgment, whether due to noise or sparsity in the estimates of language statistics or true additional variance picked up by embeddings from other corpora.
 
@@
 
-One possible concern with our approach is that our models are only able to account for variation in  similarity judgment because the word embedding models pick up on cross-cultural differences in the conceptualization of similarity.
+One possible concern with our approach is that our models are only able to account for variation in similarity judgments because the word embedding models pick up on cross-cultural differences in the conceptualization of similarity.
 Perhaps some aspect of the geometry of the embedding space specifically reflects these differences rather than capturing more item-specific patterns of co-occurrence.
@@
 Additionally, even when one option might be more related to the cue, that relationship is not systematic throughout the set of fillers.
-On the other hand, if the embedding models capture similarity judgments more generally (beyond thematic/taxonomic preferences), they should predict judgments for the unstructured filler items as well as they do for our experimental items.
+Alternatively, if the embedding models capture similarity judgments more generally (beyond thematic/taxonomic preferences), they should predict judgments for the unstructured filler items as well as they do for our experimental items.
 
@@
 For each filler triad, we randomly assigned one of the responding options as 'Word1'.
-Running a mixed-effects logistic regression to predict responding (Word1 or Word2) with country as a fixed effect and a random effect structure as above Q1, we found no effect of country on filler responding ($\chi^2$(`r fit.country_filler.anova["country", "Df"]`) = `r round(fit.country_filler.anova["country", "Chisq"], 2)`, p `r ifelse( fit.country_filler.anova["country", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.country_filler.anova["country", "Pr(>Chisq)"], 3)), "< .001")`).
+Running a mixed-effects logistic regression to predict responding (Word1 or Word2) with country as a fixed effect and a random effect structure as above in Question 1, we found no effect of country on filler responding ($\chi^2$(`r fit.country_filler.anova["country", "Df"]`) = `r round(fit.country_filler.anova["country", "Chisq"], 2)`, p `r ifelse( fit.country_filler.anova["country", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.country_filler.anova["country", "Pr(>Chisq)"], 3)), "< .001")`).
 
@@
 
-Using the same mixed-effects logistic regression structure as the single corpus models in Q2, we predicted responses (1=word1 or 0=word2) in each cultural context with the corresponding corpus predictor as a fixed effect, and participant and triad as random effects.
+Using the same mixed-effects logistic regression structure as the single corpus models in Question 2, we predicted responses (1=word1 or 0=word2) in each cultural context with the corresponding corpus predictor as a fixed effect, and participant and triad as random effects.
 In all cultural contexts, the corresponding corpus was a significant predictor of responding, with p \< 0.05 and $\beta$ from `r min(beta.filler_single_corpus_cos)` to `r max(beta.filler_single_corpus_cos)`.
@@
 We ran two mixed-effects logistic regression models that predict responding across cultural contexts (1=thematic or word1, 0=taxonomic or word2), with the corresponding corpus predictor as a fixed effect and participant and item as random effects.
-Consistent with our results above, corresponding corpus was a significant predictor for responding to both triads and filler items (triads: $\beta$ = `r round(fixef(fit.language_cos)["theme_cosine_prop_corr_lang"], 2)`, $\chi^2$(`r fit.language_cos.anova["theme_cosine_prop_corr_lang", "Df"]`) = `r round(fit.language_cos.anova["theme_cosine_prop_corr_lang", "Chisq"], 2)`, p `r ifelse( fit.language_cos.anova["theme_cosine_prop_corr_lang", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.language_cos.anova["theme_cosine_prop_corr_lang", "Pr(>Chisq)"], 3)), "< .001")`, fillers: $\beta$ = `r round(fixef(fit.filler)["word1_match_cosine_prop_corr_lang"], 2)`, $\chi^2$(`r fit.filler.anova["word1_match_cosine_prop_corr_lang", "Df"]`) = `r round(fit.filler.anova["word1_match_cosine_prop_corr_lang", "Chisq"], 2)`, p `r ifelse(fit.filler.anova["word1_match_cosine_prop_corr_lang", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.filler.anova["word1_match_cosine_prop_corr_lang", "Pr(>Chisq)"], 3)), "< .001")`).
+Consistent with our results above, the corresponding corpus was a significant predictor for responding to both triads and filler items (triads: $\beta$ = `r round(fixef(fit.language_cos)["theme_cosine_prop_corr_lang"], 2)`, $\chi^2$(`r fit.language_cos.anova["theme_cosine_prop_corr_lang", "Df"]`) = `r round(fit.language_cos.anova["theme_cosine_prop_corr_lang", "Chisq"], 2)`, p `r ifelse( fit.language_cos.anova["theme_cosine_prop_corr_lang", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.language_cos.anova["theme_cosine_prop_corr_lang", "Pr(>Chisq)"], 3)), "< .001")`, fillers: $\beta$ = `r round(fixef(fit.filler)["word1_match_cosine_prop_corr_lang"], 2)`, $\chi^2$(`r fit.filler.anova["word1_match_cosine_prop_corr_lang", "Df"]`) = `r round(fit.filler.anova["word1_match_cosine_prop_corr_lang", "Chisq"], 2)`, p `r ifelse(fit.filler.anova["word1_match_cosine_prop_corr_lang", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.filler.anova["word1_match_cosine_prop_corr_lang", "Pr(>Chisq)"], 3)), "< .001")`).
 Importantly, we found comparable conditional $R^2$ values when the corresponding corpus was used to predict only triad items ($R^2$ = `r round(as.data.frame(r.squaredGLMM(fit.language_cos))["theoretical", "R2c"], 2)`) and only filler items ($R^2$ = `r round(as.data.frame(r.squaredGLMM(fit.filler))["theoretical", "R2c"], 2)`).
@@
 Our sample of Vietnamese participants showed an intermediate preference but were not significantly different from either Chinese or US participants.
-This finding suggests some limitations on the generality of the cultural account, which proposes that thematic/taxonomic similarity preference aligns with East Asian/Western tendency for holistic vs analytic processing.
-
-In contrast, we found some support for the environmental statistics account: word embeddings based on language specific corpora were a good predictor for the corresponding country's similarity judgments, even when other corpus statistics were included, and even with filler triads without a thematic/taxonomic structure.
+This finding suggests some limitations on the generality of the cultural account, which proposes that thematic/taxonomic similarity preferences align with East Asian and Western tendencies toward holistic and analytic processing, respectively.
+
+In contrast, we found some support for the environmental statistics account: word embeddings based on language-specific corpora were a good predictor for the corresponding country's similarity judgments, even when other corpus statistics were included, and even for filler triads without a thematic/taxonomic structure.
 <!-- However, we also found that culture-based conceptualization of similarity uniquely contributes to predicting similarity judgment when included in a model with corpus statistics. -->
-Overall, our results provide evidence that cross-cultural differences in similarity judgment are related to linguistic statistics patterns (which also vary across cultures).
+Overall, our results provide evidence that cross-cultural differences in similarity judgments are related to patterns in linguistic statistics (which also vary across cultures).
 
@@
 While we discuss cross-cultural variability at the level of countries or larger world areas, these are not cultural monoliths.
-For convenience, we operationalize culture at the level of country, based on where participants were raised.
+For convenience, we operationalize culture at the level of country, based on where participants were raised and had lived for the large majority of their lives.
 It is an open question whether performance in our participant populations (of relatively young and well-educated adults) is representative of the broader country.
@@
 
-BLINDED FOR PEER REVIEW.
+Blinded for review.
 

### 2023-02-02 code/4_paper/manuscript/manuscript.Rmd
merging

--- 2023-02-02 code/4_paper/manuscript/manuscript.Rmd
@@
 In related work, East Asian participants show a higher level of sensitivity to context than their Western counterparts when reproducing drawings from memory [@Ji2000]; visually exploring naturalistic scenes [@Chua2005]; describing scenes [@Masuda2001]; and in explaining the causes of ambiguous behaviors [@Choi1999].
-The consensus interpretation in this literature ascribes cross-cultural differences in similarity judgment to variation in the conceptualization of similarity -- with people from East Asian cultures relying on a more thematic notion of similarity than Westerners.
+The consensus interpretation in this literature ascribes cross-cultural differences in similarity judgment to variation in the *conceptualization* of similarity -- with people from East Asian cultures relying on a more thematic notion of similarity than Westerners.
 
@@
 
-Our study uses cosine distances of fastText word vectors as a measure of lexical co-occurrence.[^2]
+Our study uses cosine distances of fastText word vectors as a measure of lexical co-occurrence.[^1]
 fastText is a system that uses lexical co-occurrence information to generate a vector representing each word in its lexicon [@Mikolov2018].
@@
 
-[^1]: We also carried out our analysis using raw lexical co-occurrences and obtained similar results.
+[^1]: With the preregistered exclusion criterion, all three corpora were significant predictors.
 
@@
 But other cultural features (like conceiving of similarity thematically) could also cause individuals to talk differently about the same experiences (mentioning what cows eat rather than what other animals cows are like).
-Accordingly, our approach examines the extent to which language statistics can predict cross-cultural differences in similarity judgments with the understanding that language statistics are likely a proxy for both input and conceptualization.
+Accordingly, our approach examines the extent to which language statistics can predict cross-cultural differences in similarity judgments with the understanding that language statistics are likely a proxy for both *input* to and *conceptualization* of similarity.
 
@@
 ```
-
 <!-- The present study tests whether the statistics of language can be used to predict cross-cultural differences in similarity judgments, and particularly, whether this approach provides additional insight beyond cross-cultural characterizations based on taxonomic vs thematic preferences.
@@
 The CN sample included `r df.excl_CN$ppts_after_demog_excl` participants (`r df.gender_M %>% filter(gender == "男性") %>% pull(n)`M, `r df.gender_M %>% filter(gender == "女性") %>% pull(n)`F, `r df.gender_M %>% filter(gender == "拒绝回答") %>% pull(n)` other), with mean age = `r round(df.age_M$mean_age, 2)` (SD = `r round(df.age_M$sd_age, 2)`).
-And the VN sample included `r df.excl_VN$ppts_after_demog_excl` participants (`r df.gender_V %>% filter(gender == "Nam") %>% pull(n)`M, `r df.gender_V %>% filter(gender == "Nữ") %>% pull(n)`F, `r df.gender_V %>% filter(gender == "Từ chối trả lời") %>% pull(n)` other), with mean age = `r round(df.age_V$mean_age, 2)` (SD = `r round(df.age_V$sd_age, 2)`).[^2]
+And the VN sample included `r df.excl_VN$ppts_after_demog_excl` participants (`r df.gender_V %>% filter(gender == "Nam") %>% pull(n)`M, `r df.gender_V %>% filter(gender == "Nữ") %>% pull(n)`F, `r df.gender_V %>% filter(gender == "Từ chối trả lời") %>% pull(n)` other), with mean age = `r round(df.age_V$mean_age, 2)` (SD = `r round(df.age_V$sd_age, 2)`).
 
@@
 ## Procedure
+
+```{=tex}
 \begin{CJK*}{UTF8}{gbsn}
@@
 \end{CJK*}
-
+```
 ## Corpus model
@@
 We calculated the cosine distance between each cue-thematic match (thematic cosine distance) and cue-taxonomic match (taxonomic cosine distance).
-<!-- , using the `spatial.distance.cosine` function from the SciPy package in R [@2020SciPy]. -->
-We then calculated the thematic cosine distance proportion as thematic cosine distance over the sum of taxonomic cosine distance and thematic cosine distance.
+<!-- , using the `spatial.distance.cosine` function from the SciPy package in R [@2020SciPy].
+--> We then calculated the thematic cosine distance proportion as thematic cosine distance over the sum of taxonomic cosine distance and thematic cosine distance.
 We followed this process for all three corpora, and were able to obtain predictions for all triads in all languages.
@@
 
-We found a significant effect of country ($\chi^2$(`r fit.country.anova["country", "Df"]`) = `r round(fit.country.anova["country", "Chisq"], 2)`, p `r ifelse( fit.country.anova["country", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.country.anova["country", "Pr(>Chisq)"], 3)), "< .001")`), but this effect is driven by the difference between US and CN responding ($\beta$ = `r round(fixef(fit.country)["countryUS"], 2)`, p `r ifelse(as.data.frame(summary(fit.country)[["coefficients"]])["countryUS", "Pr(>|z|)"] > 0.001, paste0("= ", round(as.data.frame(summary(fit.country)[["coefficients"]])["countryUS", "Pr(>|z|)"], 3)), "< .001")`).
-There was no statistical difference between matching in Vietnam and China ($\beta$ = `r round(fixef(fit.country)["countryVietnam"], 2)`, p `r ifelse(as.data.frame(summary(fit.country)[["coefficients"]])["countryVietnam", "Pr(>|z|)"] > 0.001, paste0("= ", round(as.data.frame(summary(fit.country)[["coefficients"]])["countryVietnam", "Pr(>|z|)"], 3)), "< .001")`), or the US and Vietnam ($\beta$ = `r round(fixef(fit.country_EN_VN)["countryVietnam"], 2)`, p `r ifelse(as.data.frame(summary(fit.country_EN_VN)[["coefficients"]])["countryVietnam", "Pr(>|z|)"] > 0.001, paste0("= ", round(as.data.frame(summary(fit.country_EN_VN)[["coefficients"]])["countryVietnam", "Pr(>|z|)"], 3)), "< .001")`).
+We found a significant effect of country ($\chi^2$(`r fit.country.anova["country", "Df"]`) = `r round(fit.country.anova["country", "Chisq"], 2)`, p `r ifelse( fit.country.anova["country", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.country.anova["country", "Pr(>Chisq)"], 3)), "< .001")`), but this effect is driven by the difference between US and CN responding ($\beta_{US}$ = `r round(fixef(fit.country)["countryUS"], 2)`, p `r ifelse(as.data.frame(summary(fit.country)[["coefficients"]])["countryUS", "Pr(>|z|)"] > 0.001, paste0("= ", round(as.data.frame(summary(fit.country)[["coefficients"]])["countryUS", "Pr(>|z|)"], 3)), "< .001")`).
+There was no statistical difference between matching in Vietnam and China ($\beta_{Vietnam}$ = `r round(fixef(fit.country)["countryVietnam"], 2)`, p `r ifelse(as.data.frame(summary(fit.country)[["coefficients"]])["countryVietnam", "Pr(>|z|)"] > 0.001, paste0("= ", round(as.data.frame(summary(fit.country)[["coefficients"]])["countryVietnam", "Pr(>|z|)"], 3)), "< .001")`), or the US and Vietnam ($\beta_{Vietnam}$ = `r round(fixef(fit.country_EN_VN)["countryVietnam"], 2)`, p `r ifelse(as.data.frame(summary(fit.country_EN_VN)[["coefficients"]])["countryVietnam", "Pr(>|z|)"] > 0.001, paste0("= ", round(as.data.frame(summary(fit.country_EN_VN)[["coefficients"]])["countryVietnam", "Pr(>|z|)"], 3)), "< .001")`).
 
@@
 
-First, to test whether variation in language statistics can explain differences in similarity judgments, 
-<!-- we compare logistic mixed-effects regression models fit to the thematic responding data from each country separately. -->
-<!-- We first ask how well each corpus model (English, Vietnamese, or Mandarin) predicts similarity judgments by speakers of the corresponding language (US, Vietnam, or China). -->
-<!-- To do this,  -->
-we use a mixed-effects logistic regressions fit individually for each country.
+First, to test whether variation in language statistics can explain differences in similarity judgments, <!-- we compare logistic mixed-effects regression models fit to the thematic responding data from each country separately.
+--> <!-- We first ask how well each corpus model (English, Vietnamese, or Mandarin) predicts similarity judgments by speakers of the corresponding language (US, Vietnam, or China).
+--> <!-- To do this,  --> we use a mixed-effects logistic regressions fit individually for each country.
 Our models predicted responses by individual participants to particular triads (0=taxonomic or 1=thematic) with fastText predictions (proportion of cosine distance) as a fixed effect and participant and triad as random effects.
@@
 
-For US responding: only the English (EN) corpus was a significant predictor[^5].
+For US responding: only the English (EN) corpus was a significant predictor[^2].
 EN corpus: $\beta$ = `r round(fixef(fit.ENVIZH_US_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.ENVIZH_US_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.ENVIZH_US_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_US_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_US_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"], 3)), "< .001")`.
@@
 
-[^5]: With the preregistered exclusion criterion, only the English (EN) and Mandarin (ZH) corpus were significant predictors.
-
-For Vietnam responding, only the Vietnamese (VI) and Mandarin (ZH) corpus were significant predictors[^6].
+[^2]: With the preregistered exclusion criterion, only the English (EN) and Mandarin (ZH) corpus were significant predictors.
+
+For Vietnam responding, only the Vietnamese (VI) and Mandarin (ZH) corpus were significant predictors[^3].
 EN corpus: $\beta$ = `r round(fixef(fit.ENVIZH_VN_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.ENVIZH_VN_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_VN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"], 3)), "< .001")`.
@@
 
-[^6]: With the preregistered exclusion criterion, all three corpora were significant predictors.
+[^3]: With the preregistered exclusion criterion, all three corpora were significant predictors.
 
@@
 In all cultural contexts, the corresponding corpus was a significant predictor of responding, with p \< 0.05 and $\beta$ from `r min(beta.filler_single_corpus_cos)` to `r max(beta.filler_single_corpus_cos)`.
-<!-- (For a full report, see Supplementary Information.)  -->
-These results show that the word embedding models predict general similarity in addition to structured thematic/taxonomic similarity.
+<!-- (For a full report, see Supplementary Information.)  --> These results show that the word embedding models predict general similarity in addition to structured thematic/taxonomic similarity.
 
@@
 In this study, we measure language and its relation to cross-cultural differences in categorization, but these relations test only the plausibility of a language-based account; they cannot establish the direction of causality.
-@Ji2004 established that culture-aligned differences in this paradigm exist, even when the test language is held constant, concluding that "it is culture (independent of the testing language) that led to different grouping styles" in their study.
-Our data provide a cautionary note to this conclusion, suggesting that while cultural differences in similarity judgment exists, we might get better traction on modelling cross-cultural variation through environmental statistics such as lexical co-occurrences.
 

### 2023-02-02 code/4_paper/manuscript/manuscript.tex
merging

--- 2023-02-02 code/4_paper/manuscript/manuscript.tex
@@
 Our study uses cosine distances of fastText word vectors as a measure of
-lexical co-occurrence.\footnote{We also carried out our analysis using
-  raw lexical co-occurrences and obtained similar results.} fastText is
+lexical co-occurrence.\footnote{With the preregistered exclusion
+  criterion, all three corpora were significant predictors.} fastText is
 a system that uses lexical co-occurrence information to generate a
@@
 While the language model may succeed in taxonomic-thematic similarity
-predictions by picking up on differences in the \emph{conceptualization}
-of similarity that are reflected in language data, this
-conceptualization account provides no prediction for these filler
-stimuli.
+predictions by picking up on differences in the conceptualization of
+similarity that are reflected in language data, this conceptualization
+account provides no prediction for these filler stimuli.
 
@@
 pre-registration is available at {[}blinded for peer review{]}. We
-recruited 200 participants from the US, 199 from Vietnam, and 200 from
-mainland China. All participants were recruited through snowball
-sampling, which, in the US was seeded with student email lists at a
-large university, in Vietnam (VN) with Vietnam-based student groups on
-Facebook, and in China (CN) with student groups on WeChat. US
-participants were compensated with \$5 gift certificates (USD), VN
-participants received 50,000₫ (VND) in phone credit, and CN participants
-received 25CNY through WeChat credit transfer.
+recruited 200 participants from the US, 200 from mainland China, and 199
+from Vietnam. All participants were recruited through snowball sampling,
+which, in the US was seeded with student email lists at a large
+university, in China (CN) with student groups on WeChat, and in Vietnam
+(VN) with Vietnam-based student groups on Facebook. US participants were
+compensated with \$5 gift certificates (USD), CN participants received
+25CNY through WeChat credit transfer, and VN participants received
+50,000₫ (VND) in phone credit,
 
-We excluded 8 US participants, 62 VN participants, and 16 CN
-participants who missed two or more of the 10 attention check questions.
+We excluded 8 US participants, 16 CN participants, and 62 VN
+participants, who missed two or more of the 11 attention check
+questions.
 
@@
 performed analyses with both samples and found broadly similar results.
-Any differences are noted in the Analysis.
+Any differences are noted in the Results \& Discussion section.
 
@@
 English, or US participants with significant international experience.
-As a result of these demographic exclusions, we excluded 73 US, 27 VN,
-and 35 CN participants. The final US sample included 119 participants
-(30M, 84F, 3 non-binary, 2 other), with mean age = 22.2 (SD = 8.15). Our
-VN sample included 110 participants (34M, 71F, 5 other), with mean age =
-22.21 (SD = 5.81). And the CN sample included 149 participants (61M,
-87F, 1 other), with mean age = 23.1 (SD = 3.65).{[}\^{}4{]}
+As a result of these demographic exclusions, we excluded 73 US, 35 CN,
+and 27 VN participants. The final US sample included 119 participants
+(30M, 84F, 3 non-binary, 2 other), with mean age = 22.2 (SD = 8.15). The
+CN sample included 149 participants (61M, 87F, 1 other), with mean age =
+23.1 (SD = 3.65). And the VN sample included 110 participants (34M, 71F,
+5 other), with mean age = 22.21 (SD = 5.81).
 
@@
 
-Each participant completed all 105 triads in blocks of 21 trials at a
-time (10 test triads, 10 filler triads, and 1 attention check per page),
-by selecting the match most related to the cue (``Which thing is most
-closely related to the bolded item?'' and translated equivalents). The
-test triads were presented with 105 filler triads mixed in, to obscure
-the taxonomic-thematic two-answer forced choice structure of the test
-stimuli and reduce the likelihood that participants would become aware
-of the design. The filler triads were groups of three semantically
-related words, but where the match options were not distinguished by
-thematic vs.~taxonomic similarity, for example, the cue ``bird'' with
-match options ``lizard'' and ``toad.'' Additionally, we included 10
-attention check trials, which were formatted similarly to the test and
-filler triads but included an instruction instead of a cue item, e.g.,
-``Choose wife'' with match options ``wife'' and ``husband.'' In total,
-each participant completed 210 similarity judgments (105 test triads and
-105 fillers) and 10 attention check questions, with all items presented
-in randomized orders that varied between subjects.
+\begin{CJK*}{UTF8}{gbsn}
+Each participant completed all 105 triads in blocks of 21 trials at a time (10 test triads, 10 filler triads, and 1 attention check per page), by selecting the match most related to the cue (following Ji et al., 2004): "Which thing is most closely related to the bolded item?" / "哪个事物与加粗项关联最紧密?" / "Thứ nào liên quan nhất với thứ được in đậm?".
+The test triads were presented with 105 filler triads mixed in, to obscure the taxonomic-thematic two-answer forced choice structure of the test stimuli and reduce the likelihood that participants would become aware of the design.
+The filler triads were groups of three semantically related words, but where the match options were not distinguished by thematic vs.
+taxonomic similarity, for example, the cue "bird" with match options "lizard" and "toad." Additionally, we included 11 attention check trials, which were formatted similarly to the test and filler triads but included an instruction instead of a cue item, e.g., "Choose wife" with match options "wife" and "husband." In total, each participant completed 210 similarity judgments (105 test triads and 105 fillers) and 11 attention check questions, with all items presented in randomized orders that varied between subjects.
+\end{CJK*}
 
@@
 \textless{} .001), but this effect is driven by the difference between
-US and CN responding (\(\beta\) = -0.48, p \textless{} .001). There was
-no statistical difference between matching in Vietnam and China
-(\(\beta\) = -0.22, p = 0.09), or the US and Vietnam (\(\beta\) = 0.26,
-p = 0.086).
+US and CN responding (\(\beta_{US}\) = -0.48, p \textless{} .001). There
+was no statistical difference between matching in Vietnam and China
+(\(\beta_{Vietnam}\) = -0.22, p = 0.09), or the US and Vietnam
+(\(\beta_{Vietnam}\) = 0.26, p = 0.086).
 

### 2023-02-02 code/4_paper/manuscript/manuscript.Rmd
small fixes

@@
 
-[^1]: With the preregistered exclusion criterion, all three corpora were significant predictors.
+[^1]: We also carried out our analysis using raw lexical cooccurrences
+and obtained similar results.
 
@@
 We elicited similarity match responses by asking "Which thing is most closely related to the bolded [cue] item?" In Mandarin Chinese, we used the phrasing for "most closely related" reported by Ji et al.
-(2004): "哪个事物与加粗项关联最紧密?" And in Vietnamese, we translated this as "Thứ nào liên quan nhất với thứ được in đậm?".
+(2004): "关联".
+And in Vietnamese, we translated this as "liên quan nhất".
 The test triads were presented with 105 filler triads mixed in, to obscure the taxonomic-thematic two-answer forced choice structure of the test stimuli and reduce the likelihood that participants would become aware of the design.
@@
 
-First, to test whether variation in language statistics can explain differences in similarity judgments, 
-<!-- we compare logistic mixed-effects regression models fit to the thematic responding data from each country separately. -->
-<!-- We first ask how well each corpus model (English, Vietnamese, or Mandarin) predicts similarity judgments by speakers of the corresponding language (US, Vietnam, or China). -->
-<!-- To do this,  -->
-we use a mixed-effects logistic regression fit individually for each country.
+First, to test whether variation in language statistics can explain differences in similarity judgments, <!-- we compare logistic mixed-effects regression models fit to the thematic responding data from each country separately.
+--> <!-- We first ask how well each corpus model (English, Vietnamese, or Mandarin) predicts similarity judgments by speakers of the corresponding language (US, Vietnam, or China).
+--> <!-- To do this,  --> we use a mixed-effects logistic regression fit individually for each country.
 Our models predicted responses by individual participants to particular triad (0=taxonomic or 1=thematic) with fastText predictions (proportion of cosine distance) as a fixed effect and participant and triad as random effects.
@@
 
-[^5]: With the preregistered exclusion criteria, the English (EN) and Mandarin (ZH) corpora were significant predictors.
-
-For Vietnamese participants' responses, only the Vietnamese (VI) and Mandarin (ZH) corpora were significant predictors[^6].
+[^2]: With the preregistered exclusion criterion, only the English
+(EN) and Mandarin (ZH) corpus were significant predictors.
+
+For Vietnamese participants' responses, only the Vietnamese (VI) and Mandarin (ZH) corpora were significant predictors[^3].
 EN corpus: $\beta$ = `r round(fixef(fit.ENVIZH_VN_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.ENVIZH_VN_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_VN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"], 3)), "< .001")`.
@@
 
-[^6]: With the preregistered exclusion criteria, all three corpora were significant predictors.
+[^3]: With the preregistered exclusion criteria, all three corpora were significant predictors.
 
@@
 
-Do members of different cultures vary in their conceptualization of similarity? Cross-cultural differences in similarity judgment would seem to suggest this conclusion.
+Do members of different cultures vary in their conceptualization of similarity?
+Cross-cultural differences in similarity judgment would seem to suggest this conclusion.
 In this paper, we consider whether statistics of the environment (as indexed by language statistics) can account for cross-cultural differences in a classic similarity judgment paradigm.
@@
 In contrast, we found some support for the environmental statistics account: word embeddings based on language-specific corpora were a good predictor for the corresponding country's similarity judgments, even when other corpus statistics were included, and even for filler triads without a thematic/taxonomic structure.
-<!-- However, we also found that culture-based conceptualization of similarity uniquely contributes to predicting similarity judgment when included in a model with corpus statistics. -->
-Overall, our results provide evidence that cross-cultural differences in similarity judgments are related to patterns in linguistic statistics (which also vary across cultures).
+<!-- However, we also found that culture-based conceptualization of similarity uniquely contributes to predicting similarity judgment when included in a model with corpus statistics.
+--> Overall, our results provide evidence that cross-cultural differences in similarity judgments are related to patterns in linguistic statistics (which also vary across cultures).
 

### 2023-02-02 code/4_paper/manuscript/manuscript.tex
small fixes

@@
 Data collection and analyses for this study were pre-registered, and the
-pre-registration is available at {[}blinded for peer review{]}. We
-recruited 200 participants from the US, 200 from mainland China, and 199
-from Vietnam. All participants were recruited through snowball sampling,
+pre-registration is available at {[}blinded for review{]}. We recruited
+200 participants from the US, 200 from mainland China, and 199 from
+Vietnam. All participants were recruited through snowball sampling,
 which, in the US was seeded with student email lists at a large
@@
 All stimuli and scripts for the experiment and analysis are available at
-{[}BLINDED FOR REVIEW{]}. We collected and adapted stimuli from previous
+{[}blinded for review{]}. We collected and adapted stimuli from previous
 studies to create test triads consisting of a cue with one thematic and
@@
 \begin{CJK*}{UTF8}{gbsn}
-Each participant completed all 105 triads in blocks of 21 trials at a time (10 test triads, 10 filler triads, and 1 attention check per page), by selecting the match most related to the cue (following Ji et al., 2004): "Which thing is most closely related to the bolded item?" / "哪个事物与加粗项关联最紧密?" / "Thứ nào liên quan nhất với thứ được in đậm?".
+Each participant completed all 105 triads in blocks of 21 trials at a time (10 test triads, 10 filler triads, and 1 attention check per page), by selecting the match most related to the cue.
+We elicited similarity match responses by asking "Which thing is most closely related to the bolded [cue] item?" In Mandarin Chinese, we used the phrasing for "most closely related" reported by Ji et al.
+(2004): "关联".
+And in Vietnamese, we translated this as "liên quan nhất".
 The test triads were presented with 105 filler triads mixed in, to obscure the taxonomic-thematic two-answer forced choice structure of the test stimuli and reduce the likelihood that participants would become aware of the design.
@@
 In sum, we replicated the differences documented by Ji et al. (2004)
-between the US and China. We did not find that Vietnamese participants
-grouped particularly with Chinese participants, however. Instead they
-were intermediate between the two. Accordingly, we did not find strong
-support for the hypothesis that there are overall biases toward thematic
-responding across Asian cultural contexts broadly.
+between the US and China. However, we did not find that Vietnamese
+participants grouped particularly with Chinese participants. Instead
+they were intermediate between the two. Accordingly, we did not find
+strong support for the hypothesis that there are overall biases toward
+thematic responding across Asian cultural contexts broadly.
 
@@
 
-In our next analyses, we tested whether triad-level differences in
-judgments across countries could be predicted on the basis of language
-statistics.
+In our next analysis, we tested whether triad-level differences in
+judgments across countries could be predicted from language statistics.
 
@@
 differences in similarity judgments, we use a mixed-effects logistic
-regressions fit individually for each country. Our models predicted
-responses by individual participants to particular triads (0=taxonomic
-or 1=thematic) with fastText predictions (proportion of cosine distance)
-as a fixed effect and participant and triad as random effects. If
-language statistics, contribute to the differences in similarity
-judgments, we would expect each language corpus to be a good predictor
-for similarity judgment responding in its corresponding context.
+regression fit individually for each country. Our models predicted
+responses by individual participants to particular triad (0=taxonomic or
+1=thematic) with fastText predictions (proportion of cosine distance) as
+a fixed effect and participant and triad as random effects. If language
+statistics contribute to the differences in similarity judgments, we
+would expect each language corpus to be a good predictor for similarity
+judgments in the corresponding population.
 
@@
 compared the corpus models by including all three corpus predictors as
-fixed effects in three mixed-effect regressions (predicting US, Vietnam
-and China responding) with the same random effects as above.
+fixed effects in three mixed-effect regressions (predicting US, VN, and
+CN responding) with the same random effects as above.
 
 For US responding: only the English (EN) corpus was a significant
-predictor\footnote{With the preregistered exclusion criterion, only the
-  English (EN) and Mandarin (ZH) corpus were significant predictors.}.
-EN corpus: \(\beta\) = -6.96, \(\chi^2\)(1) = 16.57, p \textless{} .001.
-VI corpus: \(\beta\) = -2.22, \(\chi^2\)(1) = 3.73, p = 0.054. ZH
-corpus: \(\beta\) = -3.18, \(\chi^2\)(1) = 3.37, p = 0.066.
+predictor{[}\^{}2{]}. EN corpus: \(\beta\) = -6.96, \(\chi^2\)(1) =
+16.57, p \textless{} .001. VI corpus: \(\beta\) = -2.22, \(\chi^2\)(1) =
+3.73, p = 0.054. ZH corpus: \(\beta\) = -3.18, \(\chi^2\)(1) = 3.37, p =
+0.066.
 
-For Vietnam responding, only the Vietnamese (VI) and Mandarin (ZH)
-corpus were significant predictors\footnote{With the preregistered
-  exclusion criterion, all three corpora were significant predictors.}.
-EN corpus: \(\beta\) = -2.98, \(\chi^2\)(1) = 2.58, p = 0.108. VI
-corpus: \(\beta\) = -2.75, \(\chi^2\)(1) = 4.84, p = 0.028. ZH corpus:
-\(\beta\) = -4.39, \(\chi^2\)(1) = 5.49, p = 0.019.
+For Vietnamese participants' responses, only the Vietnamese (VI) and
+Mandarin (ZH) corpora were significant predictors\footnote{With the
+  preregistered exclusion criteria, all three corpora were significant
+  predictors.}. EN corpus: \(\beta\) = -2.98, \(\chi^2\)(1) = 2.58, p =
+0.108. VI corpus: \(\beta\) = -2.75, \(\chi^2\)(1) = 4.84, p = 0.028. ZH
+corpus: \(\beta\) = -4.39, \(\chi^2\)(1) = 5.49, p = 0.019.
 
-For China responding, only the Mandarin (ZH) and English (EN) corpus
-were significant predictors. EN corpus: \(\beta\) = -3.32, \(\chi^2\)(1)
-= 7.18, p = 0.007. VI corpus: \(\beta\) = -1.59, \(\chi^2\)(1) = 3.63, p
-= 0.057. ZH corpus: \(\beta\) = -5.31, \(\chi^2\)(1) = 17.69, p
-\textless{} .001.
+For responses by Chinese participants, only the Mandarin (ZH) and
+English (EN) corpus were significant predictors. EN corpus: \(\beta\) =
+-3.32, \(\chi^2\)(1) = 7.18, p = 0.007. VI corpus: \(\beta\) = -1.59,
+\(\chi^2\)(1) = 3.63, p = 0.057. ZH corpus: \(\beta\) = -5.31,
+\(\chi^2\)(1) = 17.69, p \textless{} .001.
 
@@
 Mandarin corpus was the best predictor for Chinese responding. While
-this is not the case with the Vietnamese corpus and the Vietnam
-responding, the Vietnamese corpus was still a significant predictor for
-the Vietnam responding. These results support our hypothesis that
-specific language statistics can predict cross-cultural variations of
+this is not the case with the Vietnamese corpus and Vietnamese
+participants' responding, the Vietnamese corpus was still a significant
+predictor for this responding. These results support our hypothesis that
+specific language statistics can predict cross-cultural variation in
 similarity judgment.
@@
 a significantly better fit than the identical model with only the
-corresponding corpus included as a predictor (US response: \(\chi^2\)(2)
-= 7.93, p = 0.019; Vietnam response: \(\chi^2\)(2) = 13.72, p = 0.001;
-China response: \(\chi^2\)(2) = 10.56, p = 0.005). This analysis
-suggests that culture-specific inputs to similarity judgment (as proxied
+corresponding corpus included as a predictor (US responses:
+\(\chi^2\)(2) = 7.93, p = 0.019; VN responses: \(\chi^2\)(2) = 13.72, p
+= 0.001; CN responses: \(\chi^2\)(2) = 10.56, p = 0.005). This analysis
+suggests that culture-specific input to similarity judgments (as proxied
 by language statistics) do not fully explain cross-cultural differences
-in similarity judgment, whether due to noise in the estimates of
-language statistics or true additional variance picked up by embeddings
-from other corpora.
+in similarity judgment, whether due to noise or sparsity in the
+estimates of language statistics or true additional variance picked up
+by embeddings from other corpora.
 
@@
 One possible concern with our approach is that our models are only able
-to account for variation in similarity judgment because the word
+to account for variation in similarity judgments because the word
 embedding models pick up on cross-cultural differences in the
@@
 might be more related to the cue, that relationship is not systematic
-throughout the set of fillers. On the other hand, if the embedding
-models capture similarity judgments more generally (beyond
-thematic/taxonomic preferences), they should predict judgments for the
-unstructured filler items as well as they do for our experimental items.
+throughout the set of fillers. Alternatively, if the embedding models
+capture similarity judgments more generally (beyond thematic/taxonomic
+preferences), they should predict judgments for the unstructured filler
+items as well as they do for our experimental items.
 
@@
 predict responding (Word1 or Word2) with country as a fixed effect and a
-random effect structure as above Q1, we found no effect of country on
-filler responding (\(\chi^2\)(2) = 0.74, p = 0.692).
+random effect structure as above in Question 1, we found no effect of
+country on filler responding (\(\chi^2\)(2) = 0.74, p = 0.692).
 
 Using the same mixed-effects logistic regression structure as the single
-corpus models in Q2, we predicted responses (1=word1 or 0=word2) in each
-cultural context with the corresponding corpus predictor as a fixed
-effect, and participant and triad as random effects. In all cultural
-contexts, the corresponding corpus was a significant predictor of
-responding, with p \textless{} 0.05 and \(\beta\) from -9.59 to -3.14.
-These results show that the word embedding models predict general
+corpus models in Question 2, we predicted responses (1=word1 or 0=word2)
+in each cultural context with the corresponding corpus predictor as a
+fixed effect, and participant and triad as random effects. In all
+cultural contexts, the corresponding corpus was a significant predictor
+of responding, with p \textless{} 0.05 and \(\beta\) from -9.59 to
+-3.14. These results show that the word embedding models predict general
 similarity in addition to structured thematic/taxonomic similarity.
@@
 corresponding corpus predictor as a fixed effect and participant and
-item as random effects. Consistent with our results above, corresponding
-corpus was a significant predictor for responding to both triads and
-filler items (triads: \(\beta\) = -1.79, \(\chi^2\)(1) = 75.58, p
-\textless{} .001, fillers: \(\beta\) = -2, \(\chi^2\)(1) = 70.89, p
-\textless{} .001). Importantly, we found comparable conditional \(R^2\)
-values when the corresponding corpus was used to predict only triad
-items (\(R^2\) = 0.3) and only filler items (\(R^2\) = 0.26). This
+item as random effects. Consistent with our results above, the
+corresponding corpus was a significant predictor for responding to both
+triads and filler items (triads: \(\beta\) = -1.79, \(\chi^2\)(1) =
+75.58, p \textless{} .001, fillers: \(\beta\) = -2, \(\chi^2\)(1) =
+70.89, p \textless{} .001). Importantly, we found comparable conditional
+\(R^2\) values when the corresponding corpus was used to predict only
+triad items (\(R^2\) = 0.3) and only filler items (\(R^2\) = 0.26). This
 result provides evidence for our view that word embeddings index general
@@
 the generality of the cultural account, which proposes that
-thematic/taxonomic similarity preference aligns with East Asian/Western
-tendency for holistic vs analytic processing.
+thematic/taxonomic similarity preferences align with East Asian and
+Western tendencies toward holistic and analytic processing,
+respectively.
 
 In contrast, we found some support for the environmental statistics
-account: word embeddings based on language specific corpora were a good
+account: word embeddings based on language-specific corpora were a good
 predictor for the corresponding country's similarity judgments, even
-when other corpus statistics were included, and even with filler triads
+when other corpus statistics were included, and even for filler triads
 without a thematic/taxonomic structure. Overall, our results provide
-evidence that cross-cultural differences in similarity judgment are
-related to linguistic statistics patterns (which also vary across
+evidence that cross-cultural differences in similarity judgments are
+related to patterns in linguistic statistics (which also vary across
 cultures).
@@
 operationalize culture at the level of country, based on where
-participants were raised. It is an open question whether performance in
-our participant populations (of relatively young and well-educated
-adults) is representative of the broader country. This is especially
-true for societies with substantial ethnic and cultural variation such
-as the US. We expect that our data is likely to underestimate variation
-both within and between the countries we sample from.
+participants were raised and had lived for the large majority of their
+lives. It is an open question whether performance in our participant
+populations (of relatively young and well-educated adults) is
+representative of the broader country. This is especially true for
+societies with substantial ethnic and cultural variation such as the US.
+We expect that our data is likely to underestimate variation both within
+and between the countries we sample from.
 

### 2023-02-02 code/4_paper/manuscript/manuscript.tex
final pdf

@@
 Our study uses cosine distances of fastText word vectors as a measure of
-lexical co-occurrence.\footnote{With the preregistered exclusion
-  criterion, all three corpora were significant predictors.} fastText is
-a system that uses lexical co-occurrence information to generate a
-vector representing each word in its lexicon (Mikolov, Grave,
-Bojanowski, Puhrsch, \& Joulin, 2018). Practically speaking, fastText
-vectors are available for many languages, and fastText has also been
-shown to be sensitive to cultural differences in word meanings: Thompson
-\& Lupyan (2020) demonstrated that the distribution of semantic meaning
-clusters generated by fastText trained on language-specific corpora
-correlates with the cultural, historical, and geographical similarities
-of these languages.
+lexical co-occurrence.\footnote{We also carried out our analysis using
+  raw lexical cooccurrences and obtained similar results.} fastText is a
+system that uses lexical co-occurrence information to generate a vector
+representing each word in its lexicon (Mikolov, Grave, Bojanowski,
+Puhrsch, \& Joulin, 2018). Practically speaking, fastText vectors are
+available for many languages, and fastText has also been shown to be
+sensitive to cultural differences in word meanings: Thompson \& Lupyan
+(2020) demonstrated that the distribution of semantic meaning clusters
+generated by fastText trained on language-specific corpora correlates
+with the cultural, historical, and geographical similarities of these
+languages.
 
@@
 For US responding: only the English (EN) corpus was a significant
-predictor{[}\^{}2{]}. EN corpus: \(\beta\) = -6.96, \(\chi^2\)(1) =
-16.57, p \textless{} .001. VI corpus: \(\beta\) = -2.22, \(\chi^2\)(1) =
-3.73, p = 0.054. ZH corpus: \(\beta\) = -3.18, \(\chi^2\)(1) = 3.37, p =
-0.066.
+predictor\footnote{With the preregistered exclusion criterion, only the
+  English (EN) and Mandarin (ZH) corpus were significant predictors.}.
+EN corpus: \(\beta\) = -6.96, \(\chi^2\)(1) = 16.57, p \textless{} .001.
+VI corpus: \(\beta\) = -2.22, \(\chi^2\)(1) = 3.73, p = 0.054. ZH
+corpus: \(\beta\) = -3.18, \(\chi^2\)(1) = 3.37, p = 0.066.
 

### 2023-02-02 code/4_paper/manuscript/manuscript.Rmd
done!

--- 2023-02-02 code/4_paper/manuscript/manuscript.Rmd
@@
 Specifically, East Asian cultures may promote reasoning about thematic similarity, by which cow and grass are more related, whereas Western cultures may bias judgments toward taxonomic relations, like cow and chicken.
-We measure similarity judgments across the US, China, and Vietnam and replicate US-China cultural differences with Vietnam intermediate.
+We measure similarity judgments across the US, China, and Vietnam and replicate US-China differences, but do not find that responding in Vietnam patterns with China.
+Instead, similarity judgments in Vietnam are intermediate between the US and China.
 We also show that word embedding models (fastText models for each language) are related to judgments within each country, suggesting a possible alternative interpretation of cross cultural differences.
@@
 
-Our study uses cosine distances of fastText word vectors as a measure of lexical co-occurrence.[^1]
+Our study uses cosine distances of fastText word vectors as a measure of lexical co-occurrence.[^2]
 fastText is a system that uses lexical co-occurrence information to generate a vector representing each word in its lexicon [@Mikolov2018].
@@
 
-[^1]: With the preregistered exclusion criterion, all three corpora were significant predictors.
+[^1]: We also carried out our analysis using raw lexical co-occurrences and obtained similar results.
 
@@
 ```
+
 <!-- The present study tests whether the statistics of language can be used to predict cross-cultural differences in similarity judgments, and particularly, whether this approach provides additional insight beyond cross-cultural characterizations based on taxonomic vs thematic preferences.
@@
 The CN sample included `r df.excl_CN$ppts_after_demog_excl` participants (`r df.gender_M %>% filter(gender == "男性") %>% pull(n)`M, `r df.gender_M %>% filter(gender == "女性") %>% pull(n)`F, `r df.gender_M %>% filter(gender == "拒绝回答") %>% pull(n)` other), with mean age = `r round(df.age_M$mean_age, 2)` (SD = `r round(df.age_M$sd_age, 2)`).
-And the VN sample included `r df.excl_VN$ppts_after_demog_excl` participants (`r df.gender_V %>% filter(gender == "Nam") %>% pull(n)`M, `r df.gender_V %>% filter(gender == "Nữ") %>% pull(n)`F, `r df.gender_V %>% filter(gender == "Từ chối trả lời") %>% pull(n)` other), with mean age = `r round(df.age_V$mean_age, 2)` (SD = `r round(df.age_V$sd_age, 2)`).
+And the VN sample included `r df.excl_VN$ppts_after_demog_excl` participants (`r df.gender_V %>% filter(gender == "Nam") %>% pull(n)`M, `r df.gender_V %>% filter(gender == "Nữ") %>% pull(n)`F, `r df.gender_V %>% filter(gender == "Từ chối trả lời") %>% pull(n)` other), with mean age = `r round(df.age_V$mean_age, 2)` (SD = `r round(df.age_V$sd_age, 2)`).[^2]
 
@@
 ## Procedure
-
-```{=tex}
 \begin{CJK*}{UTF8}{gbsn}
@@
 \end{CJK*}
-```
+
 ## Corpus model
@@
 We calculated the cosine distance between each cue-thematic match (thematic cosine distance) and cue-taxonomic match (taxonomic cosine distance).
-<!-- , using the `spatial.distance.cosine` function from the SciPy package in R [@2020SciPy].
---> We then calculated the thematic cosine distance proportion as thematic cosine distance over the sum of taxonomic cosine distance and thematic cosine distance.
+<!-- , using the `spatial.distance.cosine` function from the SciPy package in R [@2020SciPy]. -->
+We then calculated the thematic cosine distance proportion as thematic cosine distance over the sum of taxonomic cosine distance and thematic cosine distance.
 We followed this process for all three corpora, and were able to obtain predictions for all triads in all languages.
@@
 
-We found a significant effect of country ($\chi^2$(`r fit.country.anova["country", "Df"]`) = `r round(fit.country.anova["country", "Chisq"], 2)`, p `r ifelse( fit.country.anova["country", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.country.anova["country", "Pr(>Chisq)"], 3)), "< .001")`), but this effect is driven by the difference between US and CN responding ($\beta_{US}$ = `r round(fixef(fit.country)["countryUS"], 2)`, p `r ifelse(as.data.frame(summary(fit.country)[["coefficients"]])["countryUS", "Pr(>|z|)"] > 0.001, paste0("= ", round(as.data.frame(summary(fit.country)[["coefficients"]])["countryUS", "Pr(>|z|)"], 3)), "< .001")`).
-There was no statistical difference between matching in Vietnam and China ($\beta_{Vietnam}$ = `r round(fixef(fit.country)["countryVietnam"], 2)`, p `r ifelse(as.data.frame(summary(fit.country)[["coefficients"]])["countryVietnam", "Pr(>|z|)"] > 0.001, paste0("= ", round(as.data.frame(summary(fit.country)[["coefficients"]])["countryVietnam", "Pr(>|z|)"], 3)), "< .001")`), or the US and Vietnam ($\beta_{Vietnam}$ = `r round(fixef(fit.country_EN_VN)["countryVietnam"], 2)`, p `r ifelse(as.data.frame(summary(fit.country_EN_VN)[["coefficients"]])["countryVietnam", "Pr(>|z|)"] > 0.001, paste0("= ", round(as.data.frame(summary(fit.country_EN_VN)[["coefficients"]])["countryVietnam", "Pr(>|z|)"], 3)), "< .001")`).
+We found a significant effect of country ($\chi^2$(`r fit.country.anova["country", "Df"]`) = `r round(fit.country.anova["country", "Chisq"], 2)`, p `r ifelse( fit.country.anova["country", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.country.anova["country", "Pr(>Chisq)"], 3)), "< .001")`), but this effect is driven by the difference between US and CN responding ($\beta$ = `r round(fixef(fit.country)["countryUS"], 2)`, p `r ifelse(as.data.frame(summary(fit.country)[["coefficients"]])["countryUS", "Pr(>|z|)"] > 0.001, paste0("= ", round(as.data.frame(summary(fit.country)[["coefficients"]])["countryUS", "Pr(>|z|)"], 3)), "< .001")`).
+There was no statistical difference between matching in Vietnam and China ($\beta$ = `r round(fixef(fit.country)["countryVietnam"], 2)`, p `r ifelse(as.data.frame(summary(fit.country)[["coefficients"]])["countryVietnam", "Pr(>|z|)"] > 0.001, paste0("= ", round(as.data.frame(summary(fit.country)[["coefficients"]])["countryVietnam", "Pr(>|z|)"], 3)), "< .001")`), or the US and Vietnam ($\beta$ = `r round(fixef(fit.country_EN_VN)["countryVietnam"], 2)`, p `r ifelse(as.data.frame(summary(fit.country_EN_VN)[["coefficients"]])["countryVietnam", "Pr(>|z|)"] > 0.001, paste0("= ", round(as.data.frame(summary(fit.country_EN_VN)[["coefficients"]])["countryVietnam", "Pr(>|z|)"], 3)), "< .001")`).
 
@@
 
-For US responding: only the English (EN) corpus was a significant predictor[^2].
+For US responding: only the English (EN) corpus was a significant predictor[^5].
 EN corpus: $\beta$ = `r round(fixef(fit.ENVIZH_US_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.ENVIZH_US_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.ENVIZH_US_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_US_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_US_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"], 3)), "< .001")`.
@@
 In all cultural contexts, the corresponding corpus was a significant predictor of responding, with p \< 0.05 and $\beta$ from `r min(beta.filler_single_corpus_cos)` to `r max(beta.filler_single_corpus_cos)`.
-<!-- (For a full report, see Supplementary Information.)  --> These results show that the word embedding models predict general similarity in addition to structured thematic/taxonomic similarity.
+<!-- (For a full report, see Supplementary Information.)  -->
+These results show that the word embedding models predict general similarity in addition to structured thematic/taxonomic similarity.
 
@@
 Additionally, language, culture, cognition, and individual experiences are intertwined in complex causal relationships.
-In this study, we measure language and its relation to cross-cultural differences in categorization, but these relations test only the plausibility of a language-based account; they cannot establish the direction of causality.
+In this study, we measure language and its relation to cross-cultural differences in similarity judgments, but these relations test only the plausibility of a language-based account; they cannot establish the direction of causality.
 
 @Ji2004 established that culture-aligned differences in this paradigm exist, even when the test language is held constant, concluding that "it is culture (independent of the testing language) that led to different grouping styles" in their study.
-Our data provide a cautionary note to this conclusion, suggesting that while cultural differences in similarity judgment exists, we might get better traction on modelling cross-cultural variation through environmental statistics such as lexical co-occurrences.
+Our data provide a cautionary note to this conclusion, suggesting that while cultural differences in similarity judgments exist, we might get better traction on modelling cross-cultural variation through environmental statistics such as lexical co-occurrence.
 
@@
 Further investigation of the semantic spaces captured by cross-cultural word embedding models is required.
-Future work should also aim to provide a more specific computational account of how lexical co-occurrence might guide categorization preference beyond the simple proportion-of-similarity model tested here, and investigate other individual- or triad-specific factors that might influence how environmental statistics affect similarity judgment.
+Future work should also aim to provide a more specific computational account of how lexical co-occurrence might guide categorization preference beyond the simple proportion-of-similarity model tested here, and investigate other person- or triad-specific factors that might influence how environmental statistics affect similarity judgments.
 

### 2023-02-02 code/4_paper/manuscript/manuscript.tex
final pdf

@@
 similarity judgments across the US, China, and Vietnam and replicate
-US-China cultural differences with Vietnam intermediate. We also show
-that word embedding models (fastText models for each language) are
-related to judgments within each country, suggesting a possible
-alternative interpretation of cross cultural differences. Perhaps
-notions of similarity are similar across contexts, but the statistics of
-the linguistic environment vary.
+US-China differences, but do not find that responding in Vietnam
+patterns with China. Instead, similarity judgments in Vietnam are
+intermediate between the US and China. We also show that word embedding
+models (fastText models for each language) are related to judgments
+within each country, suggesting a possible alternative interpretation of
+cross cultural differences. Perhaps notions of similarity are similar
+across contexts, but the statistics of the linguistic environment vary.
 
@@
 measure language and its relation to cross-cultural differences in
-categorization, but these relations test only the plausibility of a
-language-based account; they cannot establish the direction of
+similarity judgments, but these relations test only the plausibility of
+a language-based account; they cannot establish the direction of
 causality.
@@
 cautionary note to this conclusion, suggesting that while cultural
-differences in similarity judgment exists, we might get better traction
+differences in similarity judgments exist, we might get better traction
 on modelling cross-cultural variation through environmental statistics
-such as lexical co-occurrences.
+such as lexical co-occurrence.
 
@@
 preference beyond the simple proportion-of-similarity model tested here,
-and investigate other individual- or triad-specific factors that might
-influence how environmental statistics affect similarity judgment.
+and investigate other person- or triad-specific factors that might
+influence how environmental statistics affect similarity judgments.
 

### 2023-05-09 code/1_exclusions/1_exclusionsUS.Rmd
cogsci ready

@@
   ppts_after_demog_excl = c(length(unique(df.resp_E_aft_demog$subject))))
-# colnames(df.demog_metadata) <- c("Participants Finished", 
-#                                  "Participants ")
+# colnames(df.demog_metadata) <- c("Participants Finished", "Participants ")
 ```

### 2023-05-09 code/1_exclusions_exploratory/1_exclusionsCN.Rmd
cogsci ready

@@
   filter(subject %in% df.ppts_finished_M$subject)
+
+df.ppts_att_M <- df.resp_M %>%
+  filter(stim_type == "attention check") %>%
+  mutate(correct_response = strsplit(cue, "选择")) %>%
+  mutate(correct_response = sapply(correct_response, "[[", 2)) %>%
+  mutate(correct_response = str_replace_all(correct_response, "“", "")) %>%
+  mutate(correct_response = str_replace_all(correct_response, "”", "")) %>%
+  mutate(pass_att_check = ifelse(responses == correct_response, 1, 0)) %>%
+  group_by(subject) %>%
+  summarise(n_att_check_correct_M = sum(pass_att_check))
+
+ggplot(data = df.ppts_att_M, 
+       mapping = aes(x = n_att_check_correct_M)) + 
+  geom_bar()+ 
+  scale_x_discrete(limits=0:10, labels = 0:10)
 

### 2023-05-09 code/1_exclusions_exploratory/1_exclusionsUS.Rmd
cogsci ready

@@
   filter(subject %in% df.ppts_finished_E$subject)
+
+df.ppts_att_E <- df.resp_E %>%
+  filter(stim_type == "attention check") %>%
+  mutate(correct_response = strsplit(cue, "Choose ")) %>%
+  mutate(correct_response = sapply(correct_response, "[[", 2)) %>%
+  mutate(pass_att_check = ifelse(responses == correct_response, 1, 0)) %>%
+  group_by(subject) %>%
+  summarise(n_att_check_correct_E = sum(pass_att_check))
+
+ggplot(data = df.ppts_att_E, 
+       mapping = aes(x = n_att_check_correct_E)) + 
+  geom_bar()+ 
+  scale_x_discrete(limits=0:10, labels = 0:10)
 

### 2023-05-09 code/1_exclusions_exploratory/1_exclusionsVN.Rmd
cogsci ready

@@
   group_by(subject) %>%
+  summarise(n_att_check_correct_V = sum(pass_att_check))
+
+ggplot(data = df.ppts_att_V, 
+       mapping = aes(x = n_att_check_correct_V)) + 
+  geom_bar()+ 
+  scale_x_discrete(limits=0:10, labels = 0:10)
+
+df.ppts_att_V <- df.resp_V %>%
+  filter(stim_type == "attention check") %>%
+  mutate(correct_response = strsplit(cue, "Chọn ")) %>%
+  mutate(correct_response = sapply(correct_response, "[[", 2)) %>%
+  mutate(pass_att_check = ifelse(responses == correct_response, 1, 0)) %>%
+  group_by(subject) %>%
   summarize(pass_att_check_percent = mean(pass_att_check)) %>%
@@
 
-df.resp_V_aft_attn <- df.resp_V %>%
+df.ppts_att_E <- df.resp_E %>%
+  filter(stim_type == "attention check") %>%
+  mutate(correct_response = strsplit(cue, "Choose ")) %>%
+  mutate(correct_response = sapply(correct_response, "[[", 2)) %>%
+  mutate(pass_att_check = ifelse(responses == correct_response, 1, 0)) %>%
+  group_by(subject) %>%
+  summarise(n_att_check_correct = sum(pass_att_check))
+
+ggplot(data = df.ppts_att_E, 
+       mapping = aes(x = n_att_check_correct)) + 
+  geom_bar()+ 
+  scale_x_discrete(limits=0:10, labels = 0:10)df.resp_V_aft_attn <- df.resp_V %>%
   filter(subject %in% df.ppts_att_V$subject) #73

### 2023-05-09 code/4_paper/manuscript/manuscript.Rmd
cogsci ready

@@
 output: cogsci2016::cogsci_paper
-#final-submission: \cogscifinalcopy
+final-submission: \cogscifinalcopy
 editor_options: 
@@
 If we observe a difference in categorization between East Asian and Western participants, it could be that members of both groups use the same procedure (considering similarity that is influenced by both taxonomic and thematic relations), but that the input to this procedure differ between cultures, with East Asian participants exposed to more support for thematic similarity in their experience in comparison to their Western counterparts.
-<!-- We might also expect that both conceptualization of similarity and input from experience play a role in driving cross-cultural differences -- East Asian participants may be exposed to more instances of thematic similarity, and prefer to conceptualize similarity as thematic to a greater extent than Westerners.
+***Because this is a question about naturally-occurring differences in real-world reasoning contexts, it is difficult to address experimentally.
+In a controlled study, we could manipulate participants' input and determine whether differing inputs influence similarity judgments [e.g.
+@McDonald2001], but this would not address the actual sources of cross-cultural variation in similarity judgments.
+Here, we draw on real-world data to estimate variation across cultures.***<!-- We might also expect that both conceptualization of similarity and input from experience play a role in driving cross-cultural differences -- East Asian participants may be exposed to more instances of thematic similarity, and prefer to conceptualize similarity as thematic to a greater extent than Westerners.
 -->
@@
 
-[^1]: We also carried out our analysis using raw lexical cooccurrences
-and obtained similar results.
+[^1]: We also carried out our analysis using raw lexical cooccurrences and obtained similar results.
 
@@
 Vietnam is a Southeast Asian country that borders China and has historically been greatly influenced by Chinese culture [@Hui2002].
-Therefore, it serves as a suitable cultural context to investigate whether the claim made by @Ji2004 and previous studies -- that Eastern and Western cultures have different notions of similarity -- extends beyond mainland China.
+***We were unable to find cultural indices specifically on thematic/taxonomic reasoning, but Vietnam shows greater similarity to China than the US across the Hofstede dimensions of cultural comparison [-@hofstede] and is often cited for its similarity to more canonical exemplars of East Asian culture [@Woodside1998; @Hirschman1996; @Whitmore1984], for example, patterning with East Asian countries rather than Southeast Asian countries on a measure of family values [@Minkov2012].*** Therefore, Vietnam serves as a suitable cultural context to investigate whether the claim made by @Ji2004 and previous studies -- that Eastern and Western cultures have different notions of similarity -- extends beyond mainland China.
 In addition to these replication and extension questions, we tested whether fastText vectors from corpora corresponding to each language context (English, Mandarin, and Vietnamese) are good predictors for similarity judgments in each population.
@@
 
-We excluded `r df.excl_US$ppts_finished - df.excl_US$ppts_after_att_check_excl` US participants, `r df.excl_CN$ppts_finished - df.excl_CN$ppts_after_att_check_excl` CN participants, and `r df.excl_VN$ppts_finished - df.excl_VN$ppts_after_att_check_excl` VN participants, who missed two or more of the 11 attention check questions.
+***We excluded `r df.excl_US$ppts_finished - df.excl_US$ppts_after_att_check_excl` US participants (`r round((df.excl_US$ppts_finished - df.excl_US$ppts_after_att_check_excl) / df.excl_US$ppts_finished * 100, 2)`%), `r df.excl_CN$ppts_finished - df.excl_CN$ppts_after_att_check_excl` CN participants (`r round((df.excl_CN$ppts_finished - df.excl_CN$ppts_after_att_check_excl) / df.excl_CN$ppts_finished * 100, 2)`%), and `r df.excl_VN$ppts_finished - df.excl_VN$ppts_after_att_check_excl` VN participants (`r round((df.excl_VN$ppts_finished - df.excl_VN$ppts_after_att_check_excl) / df.excl_VN$ppts_finished * 100, 2)`%[^2]), who missed three or more of the 10 attention check questions.***
+
+[^2]: The high rate of exclusion within our Vietnamese sample may reflect some unfamiliarity with attention checks, which could have produced exploratory responding to these questions.
+    However, because exploratory responding to attention checks is indistinguishable from chance responding (from bots or inattentive participants), we did not analyze this data further.
 
@@
 We report results with the less stringent exclusion criterion, but we performed analyses with both samples and found broadly similar results.
-Any differences are noted in the Results & Discussion section.
+Any differences are noted ***with a footnote*** in the Results & Discussion section.
 
@@
 For example, "cow," "grass," and "chicken," where "cow" is the cue, "grass" is the thematic match, and "chicken" the taxonomic match.
-We included 105 such triads, a superset including triads pulled from supplemental information and in-text examples across the literature, and others that we adapted or created <!--(see SI for the full list of stimuli and sources)-->.
+We included 105 such triads, a superset including triads pulled from supplemental information and in-text examples across the literature, and others that we adapted or created<!--(see SI for the full list of stimuli and sources)-->.
 We selected triads on the basis of cultural familiarity within the US, Vietnam, and China.
@@
 The filler triads were groups of three semantically related words, but where the match options were not distinguished by thematic vs.
-taxonomic similarity, for example, the cue "bird" with match options "lizard" and "toad." Additionally, we included 11 attention check trials, which were formatted similarly to the test and filler triads but included an instruction instead of a cue item, e.g., "Choose wife" with match options "wife" and "husband." In total, each participant completed 210 similarity judgments (105 test triads and 105 fillers) and 11 attention check questions, with all items presented in randomized orders that varied between subjects.
+taxonomic similarity, for example, the cue "bird" with match options "lizard" and "toad." Additionally, we included 10 attention check trials, which were formatted similarly to the test and filler triads but included an instruction instead of a cue item, e.g., "Choose wife" with match options "wife" and "husband." In total, each participant completed 210 similarity judgments (105 test triads and 105 fillers) and 10 attention check questions, with all items presented in randomized orders that varied between subjects.
 \end{CJK*}
@@
 
+```{r method, fig.env = "figure", fig.asp = 0.5, fig.align='center', set.cap.width=T, num.cols.cap=1, strip.white=T, fig.cap = "Thematic response prediction based on cosine distance of the triad cow: grass/chicken."}
+img <- png::readPNG("figs/model.png")
+grid::grid.raster(img)
+```
+
 To give an intuition for our model, consider again the cow: grass/chicken triad.
 We retrieved word vectors for "cow" and "grass", and calculated the cosine distance between these vectors.
-We did the same for "cow" and "chicken." Our similarity prediction is inversely proportional to the ratio of cosine distance of these pairs.
+We did the same for "cow" and "chicken." Our similarity prediction is inversely proportional to the ratio of cosine distance of these pairs (Figure 1).
 This is because a larger cosine distance means the word vectors are further apart, and thus the words are less similar.
@@
 
-We observed the strongest preference for thematic matching in China (M = `r round((df.country_sum %>% filter(country == "China"))$mean_theme_resp_percent, 2)`, SD = `r round((df.country_sum %>% filter(country == "China"))$sd_theme_resp_percent, 2)`), followed by Vietnam (M = `r round((df.country_sum %>% filter(country == "Vietnam"))$mean_theme_resp_percent, 2)`, SD = `r round((df.country_sum %>% filter(country == "Vietnam"))$sd_theme_resp_percent, 2)`), and then the US (M = `r round((df.country_sum %>% filter(country == "US"))$mean_theme_resp_percent, 2)`, SD = `r round((df.country_sum %>% filter(country == "US"))$sd_theme_resp_percent, 2)`; see Figure 1).
+We observed the strongest preference for thematic matching in China (M = `r round((df.country_sum %>% filter(country == "China"))$mean_theme_resp_percent, 2)`, SD = `r round((df.country_sum %>% filter(country == "China"))$sd_theme_resp_percent, 2)`), followed by Vietnam (M = `r round((df.country_sum %>% filter(country == "Vietnam"))$mean_theme_resp_percent, 2)`, SD = `r round((df.country_sum %>% filter(country == "Vietnam"))$sd_theme_resp_percent, 2)`), and then the US (M = `r round((df.country_sum %>% filter(country == "US"))$mean_theme_resp_percent, 2)`, SD = `r round((df.country_sum %>% filter(country == "US"))$sd_theme_resp_percent, 2)`; see Figure 2).
 
@@
 
-For US responding: only the English (EN) corpus was a significant predictor[^2].
+For US responding: only the English (EN) corpus was a significant predictor[^3].
 EN corpus: $\beta$ = `r round(fixef(fit.ENVIZH_US_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.ENVIZH_US_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.ENVIZH_US_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_US_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_US_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"], 3)), "< .001")`.
@@
 
-[^2]: With the preregistered exclusion criterion, only the English
-(EN) and Mandarin (ZH) corpus were significant predictors.
-
-For Vietnamese participants' responses, only the Vietnamese (VI) and Mandarin (ZH) corpora were significant predictors[^3].
+[^3]: With the preregistered exclusion criterion, only the English (EN) and Mandarin (ZH) corpus were significant predictors.
+
+For Vietnamese participants' responses, only the Vietnamese (VI) and Mandarin (ZH) corpora were significant predictors[^4].
 EN corpus: $\beta$ = `r round(fixef(fit.ENVIZH_VN_cos)["theme_cosine_prop_E"], 2)`, $\chi^2$(`r fit.ENVIZH_VN_cos.anova["theme_cosine_prop_E", "Df"]`) = `r round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_E", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_VN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_VN_cos.anova["theme_cosine_prop_E", "Pr(>Chisq)"], 3)), "< .001")`.
@@
 
-[^3]: With the preregistered exclusion criteria, all three corpora were significant predictors.
+[^4]: With the preregistered exclusion criteria, all three corpora were significant predictors.
 
@@
 
-We observed some language specificity in this analysis (Figure 2).
+We observed some language specificity in this analysis (Figure 3).
 The English corpus was the best predictor for US responding, and the Mandarin corpus was the best predictor for Chinese responding.
@@
 
-df.USVNCN_coeffs_cos <- data.frame(country_value, corpus_value, coeff_value_cos, se_value_cos) %>%
+is_sig <- c(1, 0, 0, 
+            0, 1, 1, 
+            0, 0, 1)
+
+df.USVNCN_coeffs_cos <- data.frame(country_value, corpus_value, coeff_value_cos, se_value_cos, is_sig) %>%
   mutate(corpus_value = factor(corpus_value, levels=c("ZH", "VI", "EN")), 
@@
   scale_y_reverse() + 
+  ylim(0, -9) +
   labs(x = "Country", y = "Fixed effect size", fill = "Corpus") + 
   scale_x_discrete(labels=c("CN" = "China", "VN" = "Vietnam", "US" = "US")) + 
-  scale_fill_manual(values=c("#D63230", "#F39237", "#1C77C3"))
-```
-
-```{r coeffs_cos, echo=FALSE, warning=FALSE, cache = TRUE, fig.env = "figure", fig.align = "center", set.cap.width=T, num.cols.cap=1, fig.cap="Fixed effect sizes of each corpus lexical statistics (cosine distance proportion) when included as a predictor for China, Vietnam, and US responding, respectively.
+  scale_fill_manual(values=c("#D63230", "#F39237", "#1C77C3")) +
+  geom_text(aes(label = ifelse(is_sig, "*", "")), 
+            position = position_dodge(width = .9), vjust = -2.25, size = 20 / .pt)
+```
+
+```{r coeffs_cos, echo=FALSE, warning=FALSE, cache = FALSE, fig.env = "figure", fig.align = "center", set.cap.width=T, num.cols.cap=1, fig.cap="Fixed effect sizes of each corpus lexical statistics (cosine distance proportion) when included as a predictor for China, Vietnam, and US responding, respectively.
+Asterisks indicate corpora that are significant predictors.
 The English corpus is the best predictor for US response, and the Mandarin corpus is the best predictor for China response."}
@@
 However, in all cultural contexts, adding the other two corpora produced a significantly better fit than the identical model with only the corresponding corpus included as a predictor (US responses: $\chi^2$(`r fit.US_cos_compare["fit.ENVIZH_US_cos", "Df"]`) = `r round(fit.US_cos_compare["fit.ENVIZH_US_cos", "Chisq"], 2)`, p `r ifelse( fit.US_cos_compare["fit.ENVIZH_US_cos", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.US_cos_compare["fit.ENVIZH_US_cos", "Pr(>Chisq)"], 3)), "< .001")`; VN responses: $\chi^2$(`r fit.VN_cos_compare["fit.ENVIZH_VN_cos", "Df"]`) = `r round(fit.VN_cos_compare["fit.ENVIZH_VN_cos", "Chisq"], 2)`, p `r ifelse( fit.VN_cos_compare["fit.ENVIZH_VN_cos", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.VN_cos_compare["fit.ENVIZH_VN_cos", "Pr(>Chisq)"], 3)), "< .001")`; CN responses: $\chi^2$(`r fit.CN_cos_compare["fit.ENVIZH_CN_cos", "Df"]`) = `r round(fit.CN_cos_compare["fit.ENVIZH_CN_cos", "Chisq"], 2)`, p `r ifelse( fit.CN_cos_compare["fit.ENVIZH_CN_cos", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.CN_cos_compare["fit.ENVIZH_CN_cos", "Pr(>Chisq)"], 3)), "< .001")`).
-This analysis suggests that culture-specific input to similarity judgments (as proxied by language statistics) do not fully explain cross-cultural differences in similarity judgment, whether due to noise or sparsity in the estimates of language statistics or true additional variance picked up by embeddings from other corpora.
+***This analysis suggests that culture-specific input to similarity judgments (as proxied by language statistics) do not fully explain cross-cultural differences in similarity judgment.
+This could be due to noise or sparsity in the estimates of language statistics, so that adding additional corpora simply improves fit by expanding the effective size of the model corpus.
+Alternatively, it could be due to true additional cultural-specific variance picked up by embeddings from other corpora --- this is a question for future work.***
 
@@
 In contrast, we found some support for the environmental statistics account: word embeddings based on language-specific corpora were a good predictor for the corresponding country's similarity judgments, even when other corpus statistics were included, and even for filler triads without a thematic/taxonomic structure.
-<!-- However, we also found that culture-based conceptualization of similarity uniquely contributes to predicting similarity judgment when included in a model with corpus statistics.
+***This evidence is correlational and cannot evaluate causes of variation in similarity reasoning; indeed, it may be that cultural variation in similarity reasoning shapes the linguistic variation we measure, but we note that this account does not explain the fit to filler triads.***<!-- However, we also found that culture-based conceptualization of similarity uniquely contributes to predicting similarity judgment when included in a model with corpus statistics.
 --> Overall, our results provide evidence that cross-cultural differences in similarity judgments are related to patterns in linguistic statistics (which also vary across cultures).
@@
 Future work should also aim to provide a more specific computational account of how lexical co-occurrence might guide categorization preference beyond the simple proportion-of-similarity model tested here, and investigate other person- or triad-specific factors that might influence how environmental statistics affect similarity judgments.
+***This work should also investigate person- and item-specific factors, and characterize responses that are representative of each group compared to the others.***
 
@@
 
-Blinded for review.
+We are very grateful to Anjie Cao, Mai Nguyen, Victoria Yang, and Van Luong for their help with stimulus design and international participant recruitment.
+We also thank members of the Language and Cognition Lab for their feedback and helpful comments.
+This work was funded in part by NSF under grant SBE-2047581, by awards from the McDonnell Foundation and the Center for the Study of Language and Information at Stanford University supporting AC, and by the Vice Provost for Undergraduate Education Small Research Grant at Stanford University supporting KL.
 
@@
 \noindent
-
-\newpage

### 2023-05-09 code/4_paper/manuscript/manuscript.tex
cogsci ready

@@
 exposed to more support for thematic similarity in their experience in
-comparison to their Western counterparts.
+comparison to their Western counterparts. \textbf{\emph{Because this is
+a question about naturally-occurring differences in real-world reasoning
+contexts, it is difficult to address experimentally. In a controlled
+study, we could manipulate participants' input and determine whether
+differing inputs influence similarity judgments (e.g. McDonald \&
+Ramscar, 2001), but this would not address the actual sources of
+cross-cultural variation in similarity judgments. Here, we draw on
+real-world data to estimate variation across cultures.}}
 
@@
 country that borders China and has historically been greatly influenced
-by Chinese culture (Hui, 2002). Therefore, it serves as a suitable
-cultural context to investigate whether the claim made by Ji et al.
-(2004) and previous studies -- that Eastern and Western cultures have
-different notions of similarity -- extends beyond mainland China. In
-addition to these replication and extension questions, we tested whether
-fastText vectors from corpora corresponding to each language context
-(English, Mandarin, and Vietnamese) are good predictors for similarity
-judgments in each population.
+by Chinese culture (Hui, 2002). \textbf{\emph{We were unable to find
+cultural indices specifically on thematic/taxonomic reasoning, but
+Vietnam shows greater similarity to China than the US across the
+Hofstede dimensions of cultural comparison (2018) and is often cited for
+its similarity to more canonical exemplars of East Asian culture
+(Hirschman \& Loi, 1996; Whitmore, 1984; Woodside, 1998), for example,
+patterning with East Asian countries rather than Southeast Asian
+countries on a measure of family values (Minkov \& Hofstede, 2012).}}
+Therefore, Vietnam serves as a suitable cultural context to investigate
+whether the claim made by Ji et al. (2004) and previous studies -- that
+Eastern and Western cultures have different notions of similarity --
+extends beyond mainland China. In addition to these replication and
+extension questions, we tested whether fastText vectors from corpora
+corresponding to each language context (English, Mandarin, and
+Vietnamese) are good predictors for similarity judgments in each
+population.
 
@@
 
-We excluded 8 US participants, 16 CN participants, and 62 VN
-participants, who missed two or more of the 11 attention check
-questions.
+\textbf{\emph{We excluded 8 US participants (4\%), 16 CN participants
+(8\%), and 62 VN participants (31.16\%\footnote{The high rate of
+  exclusion within our Vietnamese sample may reflect some unfamiliarity
+  with attention checks, which could have produced exploratory
+  responding to these questions. However, because exploratory responding
+  to attention checks is indistinguishable from chance responding (from
+  bots or inattentive participants), we did not analyze this data
+  further.}), who missed three or more of the 10 attention check
+questions.}}
 
@@
 performed analyses with both samples and found broadly similar results.
-Any differences are noted in the Results \& Discussion section.
+Any differences are noted \textbf{\emph{with a footnote}} in the Results
+\& Discussion section.
 
@@
 
+\begin{CodeChunk}
+\begin{figure}[tb]
+
+{\centering \includegraphics{figs/method-1}
+
+}
+
+\caption[Thematic response prediction based on cosine distance of the triad cow]{Thematic response prediction based on cosine distance of the triad cow: grass/chicken.}\label{fig:method}
+\end{figure}
+\end{CodeChunk}
+
 To give an intuition for our model, consider again the cow:
@@
 did the same for ``cow'' and ``chicken.'' Our similarity prediction is
-inversely proportional to the ratio of cosine distance of these pairs.
-This is because a larger cosine distance means the word vectors are
-further apart, and thus the words are less similar. For example, if the
-cosine distance of thematic cow-grass is 0.7 and the cosine distance of
-taxonomic cow-chicken is 0.3 (the more similar of the two), then our
-model predicts, correspondingly, that 30\% of responses to the triad
-will be grass, and the other 70\% chicken.
+inversely proportional to the ratio of cosine distance of these pairs
+(Figure 1). This is because a larger cosine distance means the word
+vectors are further apart, and thus the words are less similar. For
+example, if the cosine distance of thematic cow-grass is 0.7 and the
+cosine distance of taxonomic cow-chicken is 0.3 (the more similar of the
+two), then our model predicts, correspondingly, that 30\% of responses
+to the triad will be grass, and the other 70\% chicken.
 
@@
 0.65, SD = 0.11), followed by Vietnam (M = 0.6, SD = 0.11), and then the
-US (M = 0.56, SD = 0.17; see Figure 1).
+US (M = 0.56, SD = 0.17; see Figure 2).
 
@@
 
-We observed some language specificity in this analysis (Figure 2). The
+We observed some language specificity in this analysis (Figure 3). The
 English corpus was the best predictor for US responding, and the
@@
 \caption[Fixed effect sizes of each corpus lexical statistics (cosine distance proportion) when included as a predictor for China, Vietnam, and US responding, respectively]{Fixed effect sizes of each corpus lexical statistics (cosine distance proportion) when included as a predictor for China, Vietnam, and US responding, respectively.
+Asterisks indicate corpora that are significant predictors.
 The English corpus is the best predictor for US response, and the Mandarin corpus is the best predictor for China response.}\label{fig:coeffs_cos}
@@
 \(\chi^2\)(2) = 7.93, p = 0.019; VN responses: \(\chi^2\)(2) = 13.72, p
-= 0.001; CN responses: \(\chi^2\)(2) = 10.56, p = 0.005). This analysis
-suggests that culture-specific input to similarity judgments (as proxied
-by language statistics) do not fully explain cross-cultural differences
-in similarity judgment, whether due to noise or sparsity in the
-estimates of language statistics or true additional variance picked up
-by embeddings from other corpora.
+= 0.001; CN responses: \(\chi^2\)(2) = 10.56, p = 0.005).
+\textbf{\emph{This analysis suggests that culture-specific input to
+similarity judgments (as proxied by language statistics) do not fully
+explain cross-cultural differences in similarity judgment. This could be
+due to noise or sparsity in the estimates of language statistics, so
+that adding additional corpora simply improves fit by expanding the
+effective size of the model corpus. Alternatively, it could be due to
+true additional cultural-specific variance picked up by embeddings from
+other corpora --- this is a question for future work.}}
 
@@
 when other corpus statistics were included, and even for filler triads
-without a thematic/taxonomic structure. Overall, our results provide
-evidence that cross-cultural differences in similarity judgments are
-related to patterns in linguistic statistics (which also vary across
-cultures).
+without a thematic/taxonomic structure. \textbf{\emph{This evidence is
+correlational and cannot evaluate causes of variation in similarity
+reasoning; indeed, it may be that cultural variation in similarity
+reasoning shapes the linguistic variation we measure, but we note that
+this account does not explain the fit to filler triads.}} Overall, our
+results provide evidence that cross-cultural differences in similarity
+judgments are related to patterns in linguistic statistics (which also
+vary across cultures).
 
@@
 influence how environmental statistics affect similarity judgments.
+\textbf{\emph{This work should also investigate person- and
+item-specific factors, and characterize responses that are
+representative of each group compared to the others.}}
 
@@
 \noindent
-
-\newpage
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-hofstede}{}}%
+{Country Comparison - Hofstede Insights}. (2018). \emph{Hofstede
+Insights}. Retrieved from
+\url{https://www.hofstede-insights.com/country-comparison-tool?countries=china\%2Cunited\%2Bstates\%2Cvietnam}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Grave2018}{}}%
@@
 http://doi.org/\href{https://doi.org/doi:10.1037/0033-295x.114.2.211}{doi:10.1037/0033-295x.114.2.211}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Hirschman1996}{}}%
+Hirschman, C., \& Loi, V. M. (1996). Family and household structure in
+vietnam: Some glimpses from a recent survey. \emph{Pacific Affairs},
+\emph{69}(2), 229--249. Retrieved from
+\url{http://www.jstor.org/stable/2760726}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-McDonald2001}{}}%
+McDonald, S., \& Ramscar, M. (2001). Testing the distributional
+hypothesis: The influence of context on judgements of semantic
+similarity. In.
+
 \leavevmode\vadjust pre{\hypertarget{ref-Mikolov2018}{}}%
@@
 and evaluation (LREC 2018)}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Minkov2012}{}}%
+Minkov, M., \& Hofstede, G. (2012). Is national culture a meaningful
+concept?: Cultural values delineate homogeneous national clusters of
+in-country regions. \emph{Cross-Cultural Research}, \emph{46}(2),
+133--159.
+http://doi.org/\href{https://doi.org/10.1177/1069397111427262}{10.1177/1069397111427262}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Whitmore1984}{}}%
+Whitmore, J. K. (1984). Social organization and confucian thought in
+vietnam. \emph{Journal of Southeast Asian Studies}, \emph{15}(2),
+296--306. Retrieved from \url{http://www.jstor.org/stable/20070597}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Woodside1998}{}}%
+Woodside, A. (1998). Territorial order and collective-identity tensions
+in confucian asia: China, vietnam, korea. \emph{Daedalus},
+\emph{127}(3), 191--220. Retrieved from
+\url{http://www.jstor.org/stable/20027512}
+
 \end{CSLReferences}

### 2023-05-09 experiment/demog/js/English-demog.js

@@ -1,0 +1,37 @@
+sub_ses = "<p>Imagine that this ladder pictures how the society is set up.</p><p>At the top of the ladder are the people who are the best off:</p><p>they have the most money, the highest amount of schooling, and the jobs that bring the most respect.</p><p>At the bottom are people who are the worst off:</p><p>they have the least money, little or no education, no job, or jobs that no one wants or respects.</p><p>Now think about your family. Please tell us where you think your family would be on this ladder.</p><p> Select the number corresponding to the rung that best represents where your family would be on this ladder：</p>"
+sub_ses_options = ["10", "9", "8", "7", "6", "5", "4", "3", "2", "1"]
+
+
+obj_ses = 'Please select your highest educational attainment:'
+obj_ses_options = ['8th grade/junior high or less', 'Some high school', 'High school graduate/GED', 'One or more years of college, no degree', 'Two-year college degree/vocational school', "Four-/Five-year college Bachelor's degree", 'At least some graduate school']
+
+
+ovs_exp = "How many overseas experiences do you have?"
+ovs_exp_options = ["No experiences", "One experience", "Two experiences", "Three to five experiences", "Six or more experiences"]
+
+
+resmobi_names = "<p>What cities/towns have you lived in since age 5?</p><p>Please list the name of the city/town you lived in at age 5 and all cities/towns that you have moved to since then,</p><p>including where you live now.</p><p>(Also include distinct villages and counties, but not different locations within the same city/town/village)</p>"
+resmobi_num = "<p>How many different cities/towns/villages have you lived in since age 5?</p><p>Count your responses from the previous question and enter the total here：</p>"
+
+
+lgfluency_preamble = "Language Fluency:"
+lgfleuncy_superq = "<p>On a scale from zero to ten, please select your level of proficiency</p><p>in speaking, understanding, and reading any</p><p>Chinese language or dialect from the scroll-down menus:</p>"
+sp = "Speaking"
+sp_placeholder = "select your level of proficiency in speaking"
+ud = "Understand Spoken Language"
+ud_placeholder = "select your level of proficiency in understanding spoken language"
+rd = "Reading"
+rd_placeholder = "select your level of proficiency in reading"
+opts = ["0", "1", "2", "3", "4", "5", "6", "7", "8", "9", "10"]
+
+
+uszipcode = "What are the first 3 digits of your zipcode?"
+
+
+ask_feedback = "Would you like to tell us anything about your experiences?"
+
+
+label_done = "Done!"
+
+
+

### 2023-05-09 experiment/demog/js/jspsych-demo-langfluency-CN.js

@@ -1,0 +1,173 @@
+/**
+ * jspsych-dropdown
+ * A plugin displaying multiple-choice questions. Choices are shown in dropdowns,
+ * using the Choices.js library. Supports selecting multiple choices for a question.
+ * Based on jspsych-survey-multi-choice:
+ * a jspsych plugin for multiple choice survey questions, by Shane Martin
+ */
+
+jsPsych.plugins['demo-langfluency-CN'] = (function () {
+	var plugin = {};
+
+	plugin.info = {
+		name: 'demo-langfluency-CN',
+		description: '',
+		parameters: {
+			preamble: {
+				type: jsPsych.plugins.parameterType.STRING,
+				description: 'Introductory text to display above all questions.',
+				default: ''
+			},
+			superq: {
+				type: jsPsych.plugins.parameterType.STRING,
+				description: 'A group name for the questions'
+			},
+			questions: {
+				type: jsPsych.plugins.parameterType.COMPLEX,
+				array: true,
+				nested: {
+					text: {
+						type: jsPsych.plugins.parameterType.STRING,
+						description: 'Question text'
+					},
+					allowMultipleSelections: {
+						type: jsPsych.plugins.parameterType.BOOL,
+						description: 'Whether to allow multiple choices to be selected',
+						default: false
+					},
+					required: {
+						type: jsPsych.plugins.parameterType.BOOL,
+						description: 'Whether an option must be selected for the question',
+						default: false
+					},
+					options: {
+						type: jsPsych.plugins.parameterType.STRING,
+						array: true,
+						description: 'An array of possible choices'
+					},
+					placeholder: {
+						type: jsPsych.plugins.parameterType.STRING,
+						description: 'Optional text to use as a placeholder'
+					}
+				}
+			}
+		}
+	}
+	plugin.trial = function (display_element, trial) {
+		var all_choice_objects = [];
+		var plugin_id_name = "jspsych-dropdown";
+		var _join = function (/*args*/) {
+			var arr = Array.prototype.slice.call(arguments, _join.length);
+			return arr.join(separator = '-');
+		}
+
+		// trial defaults
+		trial.preamble = typeof trial.preamble == 'undefined' ? '' : trial.preamble;
+		trial.superq = typeof trial.superq == 'undefined' ? '' : trial.superq;
+		trial.questions.forEach(function (question) {
+			question.required = question.required === true;
+			question.allowMultipleSelections = question.allowMultipleSelections === true;
+		});
+
+		// form element
[…]

### 2023-05-09 experiment/demog/js/jspsych-demo-langfluency.js

@@ -1,0 +1,173 @@
+/**
+ * jspsych-dropdown
+ * A plugin displaying multiple-choice questions. Choices are shown in dropdowns,
+ * using the Choices.js library. Supports selecting multiple choices for a question.
+ * Based on jspsych-survey-multi-choice:
+ * a jspsych plugin for multiple choice survey questions, by Shane Martin
+ */
+
+jsPsych.plugins['demo-langfluency'] = (function () {
+	var plugin = {};
+
+	plugin.info = {
+		name: 'demo-langfluency',
+		description: '',
+		parameters: {
+			preamble: {
+				type: jsPsych.plugins.parameterType.STRING,
+				description: 'Introductory text to display above all questions.',
+				default: ''
+			},
+			superq: {
+				type: jsPsych.plugins.parameterType.STRING,
+				description: 'A group name for the questions'
+			},
+			questions: {
+				type: jsPsych.plugins.parameterType.COMPLEX,
+				array: true,
+				nested: {
+					text: {
+						type: jsPsych.plugins.parameterType.STRING,
+						description: 'Question text'
+					},
+					allowMultipleSelections: {
+						type: jsPsych.plugins.parameterType.BOOL,
+						description: 'Whether to allow multiple choices to be selected',
+						default: false
+					},
+					required: {
+						type: jsPsych.plugins.parameterType.BOOL,
+						description: 'Whether an option must be selected for the question',
+						default: false
+					},
+					options: {
+						type: jsPsych.plugins.parameterType.STRING,
+						array: true,
+						description: 'An array of possible choices'
+					},
+					placeholder: {
+						type: jsPsych.plugins.parameterType.STRING,
+						description: 'Optional text to use as a placeholder'
+					}
+				}
+			}
+		}
+	}
+	plugin.trial = function (display_element, trial) {
+		var all_choice_objects = [];
+		var plugin_id_name = "jspsych-dropdown";
+		var _join = function (/*args*/) {
+			var arr = Array.prototype.slice.call(arguments, _join.length);
+			return arr.join(separator = '-');
+		}
+
+		// trial defaults
+		trial.preamble = typeof trial.preamble == 'undefined' ? '' : trial.preamble;
+		trial.superq = typeof trial.superq == 'undefined' ? '' : trial.superq;
+		trial.questions.forEach(function (question) {
+			question.required = question.required === true;
+			question.allowMultipleSelections = question.allowMultipleSelections === true;
+		});
+
+		// form element
[…]

### 2023-05-09 experiment/demog/js/jspsych-demo-objses.js

@@ -1,0 +1,199 @@
+/**
+ * jspsych-survey-multi-choice
+ * a jspsych plugin for multiple choice survey questions
+ *
+ * Shane Martin
+ *
+ * documentation: docs.jspsych.org
+ *
+ */
+
+
+jsPsych.plugins['demo-objses'] = (function() {
+  var plugin = {};
+
+  plugin.info = {
+    name: 'demo-objses',
+    description: '',
+    parameters: {
+      questions: {
+        type: jsPsych.plugins.parameterType.COMPLEX,
+        array: true,
+        pretty_name: 'Questions',
+        nested: {
+          prompt: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Prompt',
+            default: undefined,
+            description: 'The strings that will be associated with a group of options.'
+          },
+          options: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Options',
+            array: true,
+            default: undefined,
+            description: 'Displays options for an individual question.'
+          },
+          required: {
+            type: jsPsych.plugins.parameterType.BOOL,
+            pretty_name: 'Required',
+            default: false,
+            description: 'Subject will be required to pick an option for each question.'
+          },
+          horizontal: {
+            type: jsPsych.plugins.parameterType.BOOL,
+            pretty_name: 'Horizontal',
+            default: false,
+            description: 'If true, then questions are centered and options are displayed horizontally.'
+          },
+          name: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Question Name',
+            default: '',
+            description: 'Controls the name of data values associated with this question'
+          }
+        }
+      },
+      randomize_question_order: {
+        type: jsPsych.plugins.parameterType.BOOL,
+        pretty_name: 'Randomize Question Order',
+        default: false,
+        description: 'If true, the order of the questions will be randomized'
+      },
+      preamble: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Preamble',
+        default: null,
+        description: 'HTML formatted string to display at the top of the page above all the questions.'
+      },
+      button_label: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Button label',
+        default:  'Continue',
+        description: 'Label of the button.'
+      }
+    }
+  }
[…]

### 2023-05-09 experiment/demog/js/jspsych-demo-overseas.js

@@ -1,0 +1,199 @@
+/**
+ * jspsych-survey-multi-choice
+ * a jspsych plugin for multiple choice survey questions
+ *
+ * Shane Martin
+ *
+ * documentation: docs.jspsych.org
+ *
+ */
+
+
+jsPsych.plugins['demo-overseas'] = (function() {
+  var plugin = {};
+
+  plugin.info = {
+    name: 'demo-overseas',
+    description: '',
+    parameters: {
+      questions: {
+        type: jsPsych.plugins.parameterType.COMPLEX,
+        array: true,
+        pretty_name: 'Questions',
+        nested: {
+          prompt: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Prompt',
+            default: undefined,
+            description: 'The strings that will be associated with a group of options.'
+          },
+          options: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Options',
+            array: true,
+            default: undefined,
+            description: 'Displays options for an individual question.'
+          },
+          required: {
+            type: jsPsych.plugins.parameterType.BOOL,
+            pretty_name: 'Required',
+            default: false,
+            description: 'Subject will be required to pick an option for each question.'
+          },
+          horizontal: {
+            type: jsPsych.plugins.parameterType.BOOL,
+            pretty_name: 'Horizontal',
+            default: false,
+            description: 'If true, then questions are centered and options are displayed horizontally.'
+          },
+          name: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Question Name',
+            default: '',
+            description: 'Controls the name of data values associated with this question'
+          }
+        }
+      },
+      randomize_question_order: {
+        type: jsPsych.plugins.parameterType.BOOL,
+        pretty_name: 'Randomize Question Order',
+        default: false,
+        description: 'If true, the order of the questions will be randomized'
+      },
+      preamble: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Preamble',
+        default: null,
+        description: 'HTML formatted string to display at the top of the page above all the questions.'
+      },
+      button_label: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Button label',
+        default:  'Continue',
+        description: 'Label of the button.'
+      }
+    }
+  }
[…]

### 2023-05-09 experiment/demog/js/jspsych-demo-residentialmobi.js

@@ -1,0 +1,176 @@
+/**
+ * jspsych-survey-text
+ * a jspsych plugin for free response survey questions
+ *
+ * Josh de Leeuw
+ *
+ * documentation: docs.jspsych.org
+ *
+ */
+
+
+jsPsych.plugins['demo-residentialmobi'] = (function() {
+
+  var plugin = {};
+
+  plugin.info = {
+    name: 'demo-residentialmobi',
+    description: '',
+    parameters: {
+      questions: {
+        type: jsPsych.plugins.parameterType.COMPLEX,
+        array: true,
+        pretty_name: 'Questions',
+        default: undefined,
+        nested: {
+          prompt: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Prompt',
+            default: undefined,
+            description: 'Prompt for the subject to response'
+          },
+          placeholder: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Value',
+            default: "",
+            description: 'Placeholder text in the textfield.'
+          },
+          rows: {
+            type: jsPsych.plugins.parameterType.INT,
+            pretty_name: 'Rows',
+            default: 1,
+            description: 'The number of rows for the response text box.'
+          },
+          columns: {
+            type: jsPsych.plugins.parameterType.INT,
+            pretty_name: 'Columns',
+            default: 40,
+            description: 'The number of columns for the response text box.'
+          },
+          required: {
+            type: jsPsych.plugins.parameterType.BOOL,
+            pretty_name: 'Required',
+            default: false,
+            description: 'Require a response'
+          },
+          name: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Question Name',
+            default: '',
+            description: 'Controls the name of data values associated with this question'
+          }
+        }
+      },
+      preamble: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Preamble',
+        default: null,
+        description: 'HTML formatted string to display at the top of the page above all the questions.'
+      },
+      button_label: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Button label',
+        default:  'Continue',
+        description: 'The text that appears on the button to finish the trial.'
+      }
+    }
+  }
+
+  plugin.trial = function(display_element, trial) {
+
[…]

### 2023-05-09 experiment/demog/js/jspsych-demo-subses.js

@@ -1,0 +1,199 @@
+/**
+ * jspsych-survey-multi-choice
+ * a jspsych plugin for multiple choice survey questions
+ *
+ * Shane Martin
+ *
+ * documentation: docs.jspsych.org
+ *
+ */
+
+
+jsPsych.plugins['demo-subses'] = (function() {
+  var plugin = {};
+
+  plugin.info = {
+    name: 'demo-subses',
+    description: '',
+    parameters: {
+      questions: {
+        type: jsPsych.plugins.parameterType.COMPLEX,
+        array: true,
+        pretty_name: 'Questions',
+        nested: {
+          prompt: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Prompt',
+            default: undefined,
+            description: 'The strings that will be associated with a group of options.'
+          },
+          options: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Options',
+            array: true,
+            default: undefined,
+            description: 'Displays options for an individual question.'
+          },
+          required: {
+            type: jsPsych.plugins.parameterType.BOOL,
+            pretty_name: 'Required',
+            default: false,
+            description: 'Subject will be required to pick an option for each question.'
+          },
+          horizontal: {
+            type: jsPsych.plugins.parameterType.BOOL,
+            pretty_name: 'Horizontal',
+            default: false,
+            description: 'If true, then questions are centered and options are displayed horizontally.'
+          },
+          name: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Question Name',
+            default: '',
+            description: 'Controls the name of data values associated with this question'
+          }
+        }
+      },
+      randomize_question_order: {
+        type: jsPsych.plugins.parameterType.BOOL,
+        pretty_name: 'Randomize Question Order',
+        default: false,
+        description: 'If true, the order of the questions will be randomized'
+      },
+      preamble: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Preamble',
+        default: null,
+        description: 'HTML formatted string to display at the top of the page above all the questions.'
+      },
+      button_label: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Button label',
+        default:  'Continue',
+        description: 'Label of the button.'
+      }
+    }
+  }
[…]

### 2023-05-09 experiment/demog/js/jspsych-demo-uszipcode.js

@@ -1,0 +1,176 @@
+/**
+ * jspsych-survey-text
+ * a jspsych plugin for free response survey questions
+ *
+ * Josh de Leeuw
+ *
+ * documentation: docs.jspsych.org
+ *
+ */
+
+
+jsPsych.plugins['demo-uszipcode'] = (function() {
+
+  var plugin = {};
+
+  plugin.info = {
+    name: 'demo-uszipcode',
+    description: '',
+    parameters: {
+      questions: {
+        type: jsPsych.plugins.parameterType.COMPLEX,
+        array: true,
+        pretty_name: 'Questions',
+        default: undefined,
+        nested: {
+          prompt: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Prompt',
+            default: undefined,
+            description: 'Prompt for the subject to response'
+          },
+          placeholder: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Value',
+            default: "",
+            description: 'Placeholder text in the textfield.'
+          },
+          rows: {
+            type: jsPsych.plugins.parameterType.INT,
+            pretty_name: 'Rows',
+            default: 1,
+            description: 'The number of rows for the response text box.'
+          },
+          columns: {
+            type: jsPsych.plugins.parameterType.INT,
+            pretty_name: 'Columns',
+            default: 40,
+            description: 'The number of columns for the response text box.'
+          },
+          required: {
+            type: jsPsych.plugins.parameterType.BOOL,
+            pretty_name: 'Required',
+            default: false,
+            description: 'Require a response'
+          },
+          name: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Question Name',
+            default: '',
+            description: 'Controls the name of data values associated with this question'
+          }
+        }
+      },
+      preamble: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Preamble',
+        default: null,
+        description: 'HTML formatted string to display at the top of the page above all the questions.'
+      },
+      button_label: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Button label',
+        default:  'Continue',
+        description: 'The text that appears on the button to finish the trial.'
+      }
+    }
+  }
+
+  plugin.trial = function(display_element, trial) {
+
[…]

### 2023-05-09 experiment/demog/js/jspsych-feedback.js

@@ -1,0 +1,176 @@
+/**
+ * jspsych-survey-text
+ * a jspsych plugin for free response survey questions
+ *
+ * Josh de Leeuw
+ *
+ * documentation: docs.jspsych.org
+ *
+ */
+
+
+jsPsych.plugins['feedback'] = (function() {
+
+  var plugin = {};
+
+  plugin.info = {
+    name: 'feedback',
+    description: '',
+    parameters: {
+      questions: {
+        type: jsPsych.plugins.parameterType.COMPLEX,
+        array: true,
+        pretty_name: 'Questions',
+        default: undefined,
+        nested: {
+          prompt: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Prompt',
+            default: undefined,
+            description: 'Prompt for the subject to response'
+          },
+          placeholder: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Value',
+            default: "",
+            description: 'Placeholder text in the textfield.'
+          },
+          rows: {
+            type: jsPsych.plugins.parameterType.INT,
+            pretty_name: 'Rows',
+            default: 1,
+            description: 'The number of rows for the response text box.'
+          },
+          columns: {
+            type: jsPsych.plugins.parameterType.INT,
+            pretty_name: 'Columns',
+            default: 40,
+            description: 'The number of columns for the response text box.'
+          },
+          required: {
+            type: jsPsych.plugins.parameterType.BOOL,
+            pretty_name: 'Required',
+            default: false,
+            description: 'Require a response'
+          },
+          name: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Question Name',
+            default: '',
+            description: 'Controls the name of data values associated with this question'
+          }
+        }
+      },
+      preamble: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Preamble',
+        default: null,
+        description: 'HTML formatted string to display at the top of the page above all the questions.'
+      },
+      button_label: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Button label',
+        default:  'Continue',
+        description: 'The text that appears on the button to finish the trial.'
+      }
+    }
+  }
+
+  plugin.trial = function(display_element, trial) {
+
+    for (var i = 0; i < trial.questions.length; i++) {
[…]

### 2023-05-09 experiment/demog/js/jspsych-survey-multi-choice.js

@@ -1,0 +1,199 @@
+/**
+ * jspsych-survey-multi-choice
+ * a jspsych plugin for multiple choice survey questions
+ *
+ * Shane Martin
+ *
+ * documentation: docs.jspsych.org
+ *
+ */
+
+
+jsPsych.plugins['survey-multi-choice'] = (function() {
+  var plugin = {};
+
+  plugin.info = {
+    name: 'survey-multi-choice',
+    description: '',
+    parameters: {
+      questions: {
+        type: jsPsych.plugins.parameterType.COMPLEX,
+        array: true,
+        pretty_name: 'Questions',
+        nested: {
+          prompt: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Prompt',
+            default: undefined,
+            description: 'The strings that will be associated with a group of options.'
+          },
+          options: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Options',
+            array: true,
+            default: undefined,
+            description: 'Displays options for an individual question.'
+          },
+          required: {
+            type: jsPsych.plugins.parameterType.BOOL,
+            pretty_name: 'Required',
+            default: false,
+            description: 'Subject will be required to pick an option for each question.'
+          },
+          horizontal: {
+            type: jsPsych.plugins.parameterType.BOOL,
+            pretty_name: 'Horizontal',
+            default: false,
+            description: 'If true, then questions are centered and options are displayed horizontally.'
+          },
+          name: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Question Name',
+            default: '',
+            description: 'Controls the name of data values associated with this question'
+          }
+        }
+      },
+      randomize_question_order: {
+        type: jsPsych.plugins.parameterType.BOOL,
+        pretty_name: 'Randomize Question Order',
+        default: false,
+        description: 'If true, the order of the questions will be randomized'
+      },
+      preamble: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Preamble',
+        default: null,
+        description: 'HTML formatted string to display at the top of the page above all the questions.'
+      },
+      button_label: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Button label',
+        default:  'Continue',
+        description: 'Label of the button.'
+      }
+    }
[…]

### 2023-05-09 experiment/demog/js/jspsych-survey-text.js

@@ -1,0 +1,176 @@
+/**
+ * jspsych-survey-text
+ * a jspsych plugin for free response survey questions
+ *
+ * Josh de Leeuw
+ *
+ * documentation: docs.jspsych.org
+ *
+ */
+
+
+jsPsych.plugins['survey-text'] = (function() {
+
+  var plugin = {};
+
+  plugin.info = {
+    name: 'survey-text',
+    description: '',
+    parameters: {
+      questions: {
+        type: jsPsych.plugins.parameterType.COMPLEX,
+        array: true,
+        pretty_name: 'Questions',
+        default: undefined,
+        nested: {
+          prompt: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Prompt',
+            default: undefined,
+            description: 'Prompt for the subject to response'
+          },
+          placeholder: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Value',
+            default: "",
+            description: 'Placeholder text in the textfield.'
+          },
+          rows: {
+            type: jsPsych.plugins.parameterType.INT,
+            pretty_name: 'Rows',
+            default: 1,
+            description: 'The number of rows for the response text box.'
+          },
+          columns: {
+            type: jsPsych.plugins.parameterType.INT,
+            pretty_name: 'Columns',
+            default: 40,
+            description: 'The number of columns for the response text box.'
+          },
+          required: {
+            type: jsPsych.plugins.parameterType.BOOL,
+            pretty_name: 'Required',
+            default: false,
+            description: 'Require a response'
+          },
+          name: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Question Name',
+            default: '',
+            description: 'Controls the name of data values associated with this question'
+          }
+        }
+      },
+      preamble: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Preamble',
+        default: null,
+        description: 'HTML formatted string to display at the top of the page above all the questions.'
+      },
+      button_label: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Button label',
+        default:  'Continue',
+        description: 'The text that appears on the button to finish the trial.'
+      }
+    }
+  }
+
+  plugin.trial = function(display_element, trial) {
+
+    for (var i = 0; i < trial.questions.length; i++) {
[…]

### 2023-05-09 experiment/js/English.js

@@ -1,0 +1,141 @@
+// Stanford Consent
+first_page_instruction = ["<div class='w3-container' style='width: 600px; bottom-padding: 20px; text-align: left;'>" + 
+                "<div style='width: 600px; margin: 0 auto; text-align: center; background-color: #8C1516; padding: 20px 15px 10px 10px'>" +
+                "<img src='images/stanford.png' height='46' width='360' alt='Stanford University'></div>"+
+                "<center><p><strong>Stanford Language and Cognition Lab</strong></p></center>"+
+                "<p>In this study, you'll be asked to group things based on how related they are, and then answer some questions about yourself. It will take about 25 minutes.</p>" +
+                "<p class='block-text' id='legal'>Legal information: By answering the following questions, you are participating in a study being performed by cognitive scientists in the Stanford Department of Psychology. If you have questions about this research, please contact Alex Carstensen at <a href='mailto://abcarstensen@stanford.edu'>abcarstensen@stanford.edu</a>. You must be at least 18 years old to participate. Your participation in this research is voluntary. You may decline to answer any or all of the following questions. You may decline further participation, at any time, without adverse consequences. Your anonymity is assured; the researchers who have requested your participation will not receive any personal information about you.</p></div><p />" //,
+        ]
+
+//PARTICIPANT'S ID//
+
+prolific_ID_prompt = "Please enter your Participant ID below. If you do not have a Participant ID, check with Khuyen at khuyenle@stanford.edu before you proceed."
+
+prolific_ID_button = "Continue"
+
+participantIDtext1 =  "<p>Welcome to our study! Your Participant ID is</p><p><b>"
+participantIDtext2 =  "</b></p><p>Please make sure you save it somewhere secure so that you will be able to receive your compensation promptly.</p>"
+
+studyPaused = "Hello! Thank you for your interest in our study. Unfortunately, we have completed data collection for now. If we reopen the study, we will post it at this link, so feel free to try back in the future.<p></p>We hope you can participate next time!"
+
+
+//TASK//
+question_preamble = "Which thing is most closely related to the bolded item?"
+
+
+
+
+///////////////////////// demog questions /////////////////////////
+
[…]

### 2023-05-09 experiment/js/Mandarin-demog.js

@@ -1,0 +1,34 @@
+sub_ses = "<p>设想这把梯子反映了社会是如何构成的。</p><p>梯子的顶端是那些境况最优越的人：他们拥有最多的钱财，受过最多的教育，工作也最受人尊敬。</p><p>梯子的底端是那些境况最糟糕的人：他们只有最少的钱，极少或没有受过教育，没有工作，或者只有没人想干或没人尊敬的工作。</p><p>现在想想你的家庭。请告诉我们，你认为你的家庭在这个梯子上处于什么位置。</p><p>选择与最能代表你家庭所处位置的梯级相对应的数字：</p>"
+sub_ses_options = ["10", "9", "8", "7", "6", "5", "4", "3", "2", "1"]
+
+
+obj_ses = "请选择你的最高受教育程度："
+obj_ses_options = ["九年级/初中及以下", "上过一部分高中", "普通高中或职业高中毕业/高中等级学历", "一年或多年大学教育，无学位", "大专学历", "四年/五年制大学本科学位", "有过一些研究生经历"]  // how do we translate these into Chinese system?
+    
+
+ovs_exp = "你有多少海外经历？"
+ovs_exp_options = ["没有海外经历", "一段海外经历", "两段海外经历", "三到五段海外经历", "六段或更多海外经历"]
+
+
+resmobi_names = "<p>你从5岁起在哪些城市/城镇居住过？</p><p>请列出你在5岁时居住的城市/城镇名称，以及你在此后搬去过的所有城市/市镇名称，包括你现在居住的地方。</p><p>（可以清楚区分出来的村和县也算，但同一个城市/城镇/村里的不同地点不算）</p>"
+resmobi_num = "<p>你从5岁起在多少不同的城市/城镇/村居住过？</p><p>数一数你在上一题的回答有几个，把总数填在这里：</p>"
+
+
+lgfluency_preamble = "语言流利度："
+lgfleuncy_superq = "在0到10的范围内，请从下拉菜单中分别选择你在说、理解、阅读英语时的熟练程度"
+sp = "说"
+sp_placeholder = "选择你说英语的熟练程度"
+ud = "理解口语"
+ud_placeholder = "选择你理解口语的熟练程度"
+rd = "阅读"
+rd_placeholder = "选择你阅读的熟练程度"
+opts = ["0", "1", "2", "3", "4", "5", "6", "7", "8", "9", "10"]
+
+
[…]

### 2023-05-09 experiment/js/Mandarin.js

@@ -1,0 +1,138 @@
+//Stanford Consent
+first_page_instruction = ["<div class='w3-container' style='width: 600px; bottom-padding: 20px; text-align: left;'>" + 
+                "<div style='width: 600px; margin: 0 auto; text-align: center; background-color: #8C1516; padding: 20px 15px 10px 10px'>" +
+                "<img src='images/stanford.png' height='46' width='360' alt='Stanford University'></div>"+
+                "<center><p><strong>斯坦福语言与认知实验室</strong></p></center>"+
+                "<p>在这个实验中，你将会被邀请按事物的关联程度把它们分组，然后回答几个关于你自己的问题。这个实验大约需要25分钟。</p>" +
+                "<p class='block-text' id='legal'>法律信息：通过回答以下的问题，你将参与到一项由斯坦福大学心理系的认知科学家们开展的实验。如果你对本研究有任何问题的话，请联系Alex Carstensen （邮箱：<a href='mailto://abcarstensen@stanford.edu'>abcarstensen@stanford.edu</a>）。你必须要满十八岁才能参与本项实验。你的参与是完全自愿的。你可以拒绝回答以下任何一个、或所有的问题。你可以在任何时刻拒绝继续参与，并且不会带来不良后果。你的匿名性是被确保的；要求你参与实验的研究人员不会收到任何你的个人信息。</p></div><p />" //,     
+        ]
+
+
+//PARTICIPANT'S ID//
+//prolific stuff not used but put in so that code doesn't complain
+prolific_ID_prompt = "请在下方输入您的被试ID："
+
+prolific_ID_button = "继续"
+
+prolific_completion_code = "<p>感谢您的参与！请在微信上告知LangCog实验小助手，以便获得报酬有关的信息。</p>"
+
+
+participantIDtext1 = "<p>欢迎参加我们的实验！你的被试ID为</p><p><b>"
+participantIDtext2 = "</b></p><p>请确保将它存放在一个安全的地方，以便于你能即时收到报酬。</p>"
+
+
+studyPaused = "你好！感谢你对我们实验的兴趣。很遗憾，我们目前已经完成了数据收集。如果我们重启这一实验，我们将会在这个链接发布，你可以在日后返回尝试。<p></p>我们衷心希望你能在下次参与我们的实验！"
+
+//TASK//
+question_preamble = "哪个事物与加粗项关联最紧密？"
+
+
[…]

### 2023-05-09 experiment/js/Vietnamese.js

@@ -1,0 +1,163 @@
+// Stanford Consent
+first_page_instruction = ["<div class='w3-container' style='width: 600px; bottom-padding: 20px; text-align: left;'>" + 
+                "<div style='width: 600px; margin: 0 auto; text-align: center; background-color: #8C1516; padding: 20px 15px 10px 10px'>" +
+                "<img src='images/stanford.png' height='46' width='360' alt='Stanford University'></div>"+
+                "<center><p><strong>Phòng Nghiên cứu Ngôn ngữ và Nhận thức - Đại học Stanford</strong></p></center>"+
+                "<p>Trong nghiên cứu này, bạn sẽ được yêu cầu xếp các thứ theo mức độ liên quan của chúng. Sau đó, bạn sẽ trả lời một số câu hỏi về bản thân. Nghiên cứu này sẽ mất khoảng 25 phút." +
+                "<p class='block-text' id='legal'>Thông tin pháp lý: Khi trả lời những câu hỏi sau đây, bạn đang tham gia vào một nghiên cứu được thực hiện bởi các nhà khoa học nhận thức tại Khoa Tâm lý học, Đại học Stanford. Nếu bạn có thắc mắc nào về nghiên cứu này, vui lòng liên hệ với Alex Carstensen qua email <a href='mailto://abcarstensen@stanford.edu'>abcarstensen@stanford.edu</a>. Bạn phải ít nhất 18 tuổi để tham gia vào nghiên cứu này. Sự tham gia của bạn là tự nguyện. Bạn có thể từ chối trả lời bất kỳ hoặc tất cả các câu hỏi trong nghiên cứu. Bạn có thể từ chối tiếp tục tham gia nghiên cứu bất kỳ lúc nào mà không gây bất lợi gì cho bạn. Quyền bảo mật của bạn sẽ được đảm bảo; các nhà nghiên cứu sẽ không nhận được bất kỳ thông tin cá nhân nào của bạn.</p></div><p />" //,
+        ]
+
+//PARTICIPANT'S ID//
+
+prolific_ID_prompt = "Xin hãy nhập mã tham gia của bạn vào khung dưới đây. Nếu bạn không có mã tham gia, xin hãy kiểm tra với Khuyên tại email khuyenle@stanford.edu trước khi bạn tiếp tục."
+
[…]

### 2023-05-09 experiment/js/jspsych-RMTStest.js

@@ -1,0 +1,127 @@
+/**
+ * jsPsych plugin for RMTS test trial:
+ * accept two stimulus pairs, register choice between them
+ * Alex Carstensen
+ *
+ * documentation: docs.jspsych.org
+ */
+
+jsPsych.plugins.RMTStest = (function() {
+
+  var plugin = {};
+
+  jsPsych.pluginAPI.registerPreload('RMTStest', 'stimuli', 'image');
+
+  plugin.info = {
+    name: 'RMTStest',
+    description: 'Choose between two pairs of blocks',
+    parameters: {
+      samePair: {
+        type: jsPsych.plugins.parameterType.IMAGE,
+        pretty_name: 'Same Pair',
+        default: undefined,
+        array: true,
+        description: 'The pair of same objects to be displayed.'
+      },
+      diffPair: {
+        type: jsPsych.plugins.parameterType.IMAGE,
+        pretty_name: 'Different Pair',
+        default: undefined,
+        array: true,
+        description: 'The pair of different objects to be displayed.'
+      },
+      sameSide: {
+        type: jsPsych.plugins.parameterType.BOOL,
+        pretty_name: 'Same Side?',
+        default: undefined,
+        array: false,
+        description: 'The side (L/R) that the same pair should be displayed on.'
+      },
+      scene: {
+        type: jsPsych.plugins.parameterType.IMAGE,
+        pretty_name: 'scene',
+        default: 250,
+        description: 'contains background, box, and table'
+      },
+      prompt: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Prompt',
+        default: null,
+        description: 'Any content here will be displayed above stimulus.'
+      }
+    }
+  }
+
+  plugin.trial = function(display_element, trial) {
+
+    var startTime = (new Date()).getTime();
+    var responses = [];
+
+    if(trial.sameSide=="L") {
+      var left_side = trial.samePair;
+      var right_side = trial.diffPair;
+    } else {
+      var left_side = trial.diffPair;
+      var right_side = trial.samePair;
+    }
+    
+    display_element.innerHTML = '<div align="left">'+trial.prompt+'</div><br><div id="scene"> \
+                        <img src="'+left_side[0]+'" id="leftPair1"></img> \
+                        <img src="'+left_side[1]+'" id="leftPair2"></img> \
+                        <img src="img/tray.png" id="leftTray"></img> \
+                        <div id="leftTestButton"> </div> <div id="rightTestButton"> </div> \
[…]

### 2023-05-09 experiment/js/jspsych-RMTStrain.js

@@ -1,0 +1,160 @@
+/**
+ * jsPsych plugin for RMTS training trial:
+ * accept two stimuli, show them activating (or not) the machine 1x (by default) or n times (specified as numTriesPerPair)
+ * Alex Carstensen
+ *
+ * documentation: docs.jspsych.org
+ */
+
+jsPsych.plugins.RMTStrain = (function() {
+
+  var plugin = {};
+
+  jsPsych.pluginAPI.registerPreload('RMTStrain', 'stimuli', 'image');
+  //jsPsych.pluginAPI.registerPreload('RMTStrain', 'scene', 'audio');
+
+  plugin.info = {
+    name: 'RMTStrain',
+    description: '',
+    parameters: {
+      stimuli: {
+        type: jsPsych.plugins.parameterType.IMAGE,
+        pretty_name: 'Stimuli',
+        default: undefined,
+        array: true,
+        description: 'The two objects to be displayed.'
+      },
+      scene: {
+        type: jsPsych.plugins.parameterType.AUDIO,
+        pretty_name: 'scene',
+        default: 250,
+        description: 'contains background, box, box2 (flashing), song, and table'
+      },
+      numTriesPerPair: {
+        type: jsPsych.plugins.parameterType.INT,
+        pretty_name: 'Number of observations per pair',
+        default: 1,
+        description: 'Number of times each pair is put on the machine'
+      }
+    }
+  }
+
+  plugin.trial = function(display_element, trial) {
+
+    // setup audio stimulus
+    // var context = jsPsych.pluginAPI.audioContext();
+    // if(context !== null){
+    //   var source = context.createBufferSource();
+    //   source.buffer = jsPsych.pluginAPI.getAudioBuffer(trial.scene.song);
+    //   source.connect(context.destination);
+    // } else {
+    //   var audio = jsPsych.pluginAPI.getAudioBuffer(trial.scene.song);
+    //   //audio.currentTime = 0;
+    // }
+    var blicket = new Audio(trial.scene.song);
+    blicket.preload = "auto";
+
+    var reps = 0;
+    var startTime = (new Date()).getTime();
+    var animation_sequence = [];
+    var responses = [];
+    
+    var counter = 0; 
+    var flicker_state = 1;
+
+    display_element.innerHTML = '<div id="scene">\
+                        <img src="'+trial.stimuli[0]+'" id="leftObj"></img> \
+                        <img src="'+trial.stimuli[1]+'" id="rightObj"></img> \
[…]

### 2023-05-09 experiment/js/jspsych-attribution-Q1.js

@@ -1,0 +1,176 @@
+/**
+ * jspsych-survey-text
+ * a jspsych plugin for free response survey questions
+ *
+ * Josh de Leeuw
+ *
+ * documentation: docs.jspsych.org
+ *
+ */
+
+
+jsPsych.plugins['attribution-Q1'] = (function() {
+
+  var plugin = {};
+
+  plugin.info = {
+    name: 'attribution-Q1',
+    description: '',
+    parameters: {
+      questions: {
+        type: jsPsych.plugins.parameterType.COMPLEX,
+        array: true,
+        pretty_name: 'Questions',
+        default: undefined,
+        nested: {
+          prompt: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Prompt',
+            default: undefined,
+            description: 'Prompt for the subject to response'
+          },
+          placeholder: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Value',
+            default: "",
+            description: 'Placeholder text in the textfield.'
+          },
+          rows: {
+            type: jsPsych.plugins.parameterType.INT,
+            pretty_name: 'Rows',
+            default: 1,
+            description: 'The number of rows for the response text box.'
+          },
+          columns: {
+            type: jsPsych.plugins.parameterType.INT,
+            pretty_name: 'Columns',
+            default: 40,
+            description: 'The number of columns for the response text box.'
+          },
+          required: {
+            type: jsPsych.plugins.parameterType.BOOL,
+            pretty_name: 'Required',
+            default: false,
+            description: 'Require a response'
+          },
+          name: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Question Name',
+            default: '',
+            description: 'Controls the name of data values associated with this question'
+          }
+        }
+      },
+      preamble: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Preamble',
+        default: null,
+        description: 'HTML formatted string to display at the top of the page above all the questions.'
+      },
+      button_label: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Button label',
+        default:  'Continue',
+        description: 'The text that appears on the button to finish the trial.'
+      }
+    }
+  }
+
+  plugin.trial = function(display_element, trial) {
+
[…]

### 2023-05-09 experiment/js/jspsych-attribution-Q2.js

@@ -1,0 +1,176 @@
+/**
+ * jspsych-survey-text
+ * a jspsych plugin for free response survey questions
+ *
+ * Josh de Leeuw
+ *
+ * documentation: docs.jspsych.org
+ *
+ */
+
+
+jsPsych.plugins['attribution-Q2'] = (function() {
+
+  var plugin = {};
+
+  plugin.info = {
+    name: 'attribution-Q2',
+    description: '',
+    parameters: {
+      questions: {
+        type: jsPsych.plugins.parameterType.COMPLEX,
+        array: true,
+        pretty_name: 'Questions',
+        default: undefined,
+        nested: {
+          prompt: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Prompt',
+            default: undefined,
+            description: 'Prompt for the subject to response'
+          },
+          placeholder: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Value',
+            default: "",
+            description: 'Placeholder text in the textfield.'
+          },
+          rows: {
+            type: jsPsych.plugins.parameterType.INT,
+            pretty_name: 'Rows',
+            default: 1,
+            description: 'The number of rows for the response text box.'
+          },
+          columns: {
+            type: jsPsych.plugins.parameterType.INT,
+            pretty_name: 'Columns',
+            default: 40,
+            description: 'The number of columns for the response text box.'
+          },
+          required: {
+            type: jsPsych.plugins.parameterType.BOOL,
+            pretty_name: 'Required',
+            default: false,
+            description: 'Require a response'
+          },
+          name: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Question Name',
+            default: '',
+            description: 'Controls the name of data values associated with this question'
+          }
+        }
+      },
+      preamble: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Preamble',
+        default: null,
+        description: 'HTML formatted string to display at the top of the page above all the questions.'
+      },
+      button_label: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Button label',
+        default:  'Continue',
+        description: 'The text that appears on the button to finish the trial.'
+      }
+    }
+  }
+
+  plugin.trial = function(display_element, trial) {
+
[…]

### 2023-05-09 experiment/js/jspsych-circle-label.js

@@ -1,0 +1,177 @@
+/**
+ * jspsych-survey-text
+ * a jspsych plugin for free response survey questions
+ *
+ * Josh de Leeuw
+ *
+ * documentation: docs.jspsych.org
+ *
+ */
+
+
+jsPsych.plugins['circle-label'] = (function() {
+
+  var plugin = {};
+
+  plugin.info = {
+    name: 'circle-label',
+    description: '',
+    parameters: {
+      questions: {
+        type: jsPsych.plugins.parameterType.COMPLEX,
+        array: true,
+        pretty_name: 'Questions',
+        default: undefined,
+        nested: {
+          prompt: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Prompt',
+            default: undefined,
+            description: 'Prompt for the subject to response'
+          },
+          placeholder: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Value',
+            default: "",
+            description: 'Placeholder text in the textfield.'
+          },
+          rows: {
+            type: jsPsych.plugins.parameterType.INT,
+            pretty_name: 'Rows',
+            default: 1,
+            description: 'The number of rows for the response text box.'
+          },
+          columns: {
+            type: jsPsych.plugins.parameterType.INT,
+            pretty_name: 'Columns',
+            default: 40,
+            description: 'The number of columns for the response text box.'
+          },
+          required: {
+            type: jsPsych.plugins.parameterType.BOOL,
+            pretty_name: 'Required',
+            default: false,
+            description: 'Require a response'
+          },
+          name: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Question Name',
+            default: '',
+            description: 'Controls the name of data values associated with this question'
+          }
+        }
+      },
+      preamble: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Preamble',
+        default: null,
+        description: 'HTML formatted string to display at the top of the page above all the questions.'
+      },
+      button_label: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Button label',
+        default:  'Continue',
+        description: 'The text that appears on the button to finish the trial.'
+      }
+    }
+  }
+
+  plugin.trial = function(display_element, trial) {
+
[…]

### 2023-05-09 experiment/js/jspsych-demog-dropdown.js

@@ -1,0 +1,177 @@
+/**
+ * jspsych-dropdown
+ * A plugin displaying multiple-choice questions. Choices are shown in dropdowns,
+ * using the Choices.js library. Supports selecting multiple choices for a question.
+ * Based on jspsych-survey-multi-choice:
+ * a jspsych plugin for multiple choice survey questions, by Shane Martin
+ */
+
+jsPsych.plugins['demog-dropdown'] = (function () {
+	var plugin = {};
+
+	plugin.info = {
+		name: 'demog-dropdown',
+		description: '',
+		parameters: {
+			preamble: {
+				type: jsPsych.plugins.parameterType.STRING,
+				description: 'Introductory text to display above all questions.',
+				default: ''
+			},
+			superq: {
+				type: jsPsych.plugins.parameterType.STRING,
+				description: 'A group name for the questions'
+			},
+            button_label: {
+                type: jsPsych.plugins.parameterType.STRING,
+				description: 'label displayed on the button'
+            },
+			questions: {
+				type: jsPsych.plugins.parameterType.COMPLEX,
+				array: true,
+				nested: {
+					text: {
+						type: jsPsych.plugins.parameterType.STRING,
+						description: 'Question text'
+					},
+					allowMultipleSelections: {
+						type: jsPsych.plugins.parameterType.BOOL,
+						description: 'Whether to allow multiple choices to be selected',
+						default: false
+					},
+					required: {
+						type: jsPsych.plugins.parameterType.BOOL,
+						description: 'Whether an option must be selected for the question',
+						default: false
+					},
+					options: {
+						type: jsPsych.plugins.parameterType.STRING,
+						array: true,
+						description: 'An array of possible choices'
+					},
+					placeholder: {
+						type: jsPsych.plugins.parameterType.STRING,
+						description: 'Optional text to use as a placeholder'
+					}
+				}
+			}
+		}
+	}
+	plugin.trial = function (display_element, trial) {
+		var all_choice_objects = [];
+		var plugin_id_name = "jspsych-dropdown";
+		var _join = function (/*args*/) {
+			var arr = Array.prototype.slice.call(arguments, _join.length);
+			return arr.join(separator = '-');
+		}
+
+		// trial defaults
+		trial.preamble = typeof trial.preamble == 'undefined' ? '' : trial.preamble;
+		trial.superq = typeof trial.superq == 'undefined' ? '' : trial.superq;
+		trial.questions.forEach(function (question) {
+			question.required = question.required === true;
[…]

### 2023-05-09 experiment/js/jspsych-demog-free-response.js

@@ -1,0 +1,176 @@
+/**
+ * jspsych-survey-text
+ * a jspsych plugin for free response survey questions
+ *
+ * Josh de Leeuw
+ *
+ * documentation: docs.jspsych.org
+ *
+ */
+
+
+jsPsych.plugins['demog-free-response'] = (function() {
+
+  var plugin = {};
+
+  plugin.info = {
+    name: 'demog-free-response',
+    description: '',
+    parameters: {
+      questions: {
+        type: jsPsych.plugins.parameterType.COMPLEX,
+        array: true,
+        pretty_name: 'Questions',
+        default: undefined,
+        nested: {
+          prompt: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Prompt',
+            default: undefined,
+            description: 'Prompt for the subject to response'
+          },
+          placeholder: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Value',
+            default: "",
+            description: 'Placeholder text in the textfield.'
+          },
+          rows: {
+            type: jsPsych.plugins.parameterType.INT,
+            pretty_name: 'Rows',
+            default: 1,
+            description: 'The number of rows for the response text box.'
+          },
+          columns: {
+            type: jsPsych.plugins.parameterType.INT,
+            pretty_name: 'Columns',
+            default: 40,
+            description: 'The number of columns for the response text box.'
+          },
+          required: {
+            type: jsPsych.plugins.parameterType.BOOL,
+            pretty_name: 'Required',
+            default: false,
+            description: 'Require a response'
+          },
+          name: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Question Name',
+            default: '',
+            description: 'Controls the name of data values associated with this question'
+          }
+        }
+      },
+      preamble: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Preamble',
+        default: null,
+        description: 'HTML formatted string to display at the top of the page above all the questions.'
+      },
+      button_label: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Button label',
+        default:  'Continue',
+        description: 'The text that appears on the button to finish the trial.'
+      }
+    }
+  }
+
+  plugin.trial = function(display_element, trial) {
+
[…]

### 2023-05-09 experiment/js/jspsych-demog-multi-choice.js

@@ -1,0 +1,199 @@
+/**
+ * jspsych-survey-multi-choice
+ * a jspsych plugin for multiple choice survey questions
+ *
+ * Shane Martin
+ *
+ * documentation: docs.jspsych.org
+ *
+ */
+
+
+jsPsych.plugins['demog-multi-choice'] = (function() {
+  var plugin = {};
+
+  plugin.info = {
+    name: 'demog-multi-choice',
+    description: '',
+    parameters: {
+      questions: {
+        type: jsPsych.plugins.parameterType.COMPLEX,
+        array: true,
+        pretty_name: 'Questions',
+        nested: {
+          prompt: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Prompt',
+            default: undefined,
+            description: 'The strings that will be associated with a group of options.'
+          },
+          options: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Options',
+            array: true,
+            default: undefined,
+            description: 'Displays options for an individual question.'
+          },
+          required: {
+            type: jsPsych.plugins.parameterType.BOOL,
+            pretty_name: 'Required',
+            default: false,
+            description: 'Subject will be required to pick an option for each question.'
+          },
+          horizontal: {
+            type: jsPsych.plugins.parameterType.BOOL,
+            pretty_name: 'Horizontal',
+            default: false,
+            description: 'If true, then questions are centered and options are displayed horizontally.'
+          },
+          name: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Question Name',
+            default: '',
+            description: 'Controls the name of data values associated with this question'
+          }
+        }
+      },
+      randomize_question_order: {
+        type: jsPsych.plugins.parameterType.BOOL,
+        pretty_name: 'Randomize Question Order',
+        default: false,
+        description: 'If true, the order of the questions will be randomized'
+      },
+      preamble: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Preamble',
+        default: null,
+        description: 'HTML formatted string to display at the top of the page above all the questions.'
+      },
+      button_label: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Button label',
+        default:  'Continue',
+        description: 'Label of the button.'
+      }
+    }
[…]

### 2023-05-09 experiment/js/jspsych-demog-multi-select.js

@@ -1,0 +1,223 @@
+/**
+ * jspsych-survey-multi-select
+ * a jspsych plugin for multiple choice survey questions
+ *
+ * documentation: docs.jspsych.org
+ *
+ */
+
+
+jsPsych.plugins['demog-multi-select'] = (function() {
+  var plugin = {};
+
+  plugin.info = {
+    name: 'demog-multi-select',
+    description: '',
+    parameters: {
+      questions: {
+        type: jsPsych.plugins.parameterType.COMPLEX,
+        array: true,
+        pretty_name: 'Questions',
+        nested: {
+          prompt: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Prompt',
+            default: undefined,
+            description: 'The strings that will be associated with a group of options.'
+          },
+          options: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Options',
+            array: true,
+            default: undefined,
+            description: 'Displays options for an individual question.'
+          },
+          horizontal: {
+            type: jsPsych.plugins.parameterType.BOOL,
+            pretty_name: 'Horizontal',
+            default: false,
+            description: 'If true, then questions are centered and options are displayed horizontally.'
+          },
+          required: {
+            type: jsPsych.plugins.parameterType.BOOL,
+            pretty_name: 'Required',
+            default: false,
+            description: 'Subject will be required to pick at least one option for this question.'
+          },
+          name: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Question Name',
+            default: '',
+            description: 'Controls the name of data values associated with this question'
+          }
+        }
+      },
+      randomize_question_order: {
+        type: jsPsych.plugins.parameterType.BOOL,
+        pretty_name: 'Randomize Question Order',
+        default: false,
+        description: 'If true, the order of the questions will be randomized'
+      },
+      preamble: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Preamble',
+        default: null,
+        description: 'HTML formatted string to display at the top of the page above all the questions.'
+      },
+      button_label: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Button label',
+        default:  'Continue',
+        description: 'Label of the button.'
+      },
+      required_message: {
[…]

### 2023-05-09 experiment/js/jspsych-draw-circles-experiment.js

@@ -1,0 +1,59 @@
+
+
+
+jsPsych.plugins['draw-circles-experiment'] = (function(){
+
+  var plugin = {};
+
+  plugin.info = {
+    name: 'draw-circles-experiment',
+    parameters: {
+    }
+  }
+
+  plugin.trial = function(display_element, trial){
+     
+    
+      var canvas = this.__canvas = new fabric.Canvas('c', {
+    isDrawingMode: true
+  });
+
+      
+      
+      
+    
+      html = '<div '+
+      'id="jspsych-free-sort-arena" '+
+      'class="c" '+
+      'style="position: relative; up: 0%; left: 50%;transform: translateX(-50%);align: center;width:'+800+'px; height:'+800+'px; border:2px solid #444;"'+
+      '></div>'
+      
+      function Add() {
+    var rect = new fabric.Rect({
+      left: 100,
+      top: 50,
+      fill: 'yellow',
+      width: 200,
+      height: 100,
+      objectCaching: false,
+      stroke: 'lightgreen',
+      strokeWidth: 4,
+    });
+
+    canvas.add(rect);
+    canvas.setActiveObject(rect);
+  }
+
+display_element.innerHTML = html ;
+      
+      
+      
+    jsPsych.finishTrial();
+  }
+
+  return plugin;
+
+})();
+
+
+

### 2023-05-09 experiment/js/jspsych-draw-circles-practice.js

@@ -1,0 +1,382 @@
+/**
+ * jspsych-draw-circles
+ * plugin for creating and labeling circles of different sizes
+ * George Kachergis
+ *
+ * documentation: docs.jspsych.org
+ */
+
+
+jsPsych.plugins['draw-circles-practice'] = (function() {
+
+  var plugin = {};
+
+  plugin.info = {
+    name: 'draw-circles-practice',
+    description: 'Prompts participant to draw a series of labeled circles of varying size.',
+    parameters: {
+      circle_labels: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Circle labels',
+        default: undefined,
+        array: true,
+        description: 'Array of labels to apply to successively drawn circles.'
+      },
+      circle_diameter: {
+        type: jsPsych.plugins.parameterType.INT,
+        pretty_name: 'Circle diameter',
+        default: 100,
+        description: 'Starting diameter of new circles.'
+      },
+      sort_area_height: {
+        type: jsPsych.plugins.parameterType.INT,
+        pretty_name: 'Sort area height',
+        default: .8*window.innerHeight, //550,
+        description: 'The height of the container that subjects can move the stimuli in.'
+      },
+      sort_area_width: {
+        type: jsPsych.plugins.parameterType.INT,
+        pretty_name: 'Sort area width',
+        default: .9*window.innerWidth, //1024,
+        description: 'The width of the container that subjects can move the stimuli in.'
+      },
+      prompt: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Prompt',
+        default: null,
+        description: 'Provide a reminder about the action the subject is supposed to take.'
+      },
+      prompt_location: {
+        type: jsPsych.plugins.parameterType.SELECT,
+        pretty_name: 'Prompt location',
+        options: ['above','below'],
+        default: 'above',
+        description: 'Indicates whether to show prompt "above" or "below" the sorting area.'
+      },
+      button_label: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Button label',
+        default:  'Continue',
+        description: 'The text that appears on the button to continue to the next trial.'
+      }
+    }
+  }
+
[…]

### 2023-05-09 experiment/js/jspsych-draw-circles.js

@@ -1,0 +1,382 @@
+/**
+ * jspsych-draw-circles
+ * plugin for creating and labeling circles of different sizes
+ * George Kachergis
+ *
+ * documentation: docs.jspsych.org
+ */
+
+
+jsPsych.plugins['draw-circles'] = (function() {
+
+  var plugin = {};
+
+  plugin.info = {
+    name: 'draw-circles',
+    description: 'Prompts participant to draw a series of labeled circles of varying size.',
+    parameters: {
+      circle_labels: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Circle labels',
+        default: undefined,
+        array: true,
+        description: 'Array of labels to apply to successively drawn circles.'
+      },
+      circle_diameter: {
+        type: jsPsych.plugins.parameterType.INT,
+        pretty_name: 'Circle diameter',
+        default: 100,
+        description: 'Starting diameter of new circles.'
+      },
+      sort_area_height: {
+        type: jsPsych.plugins.parameterType.INT,
+        pretty_name: 'Sort area height',
+        default: .8*window.innerHeight, //550,
+        description: 'The height of the container that subjects can move the stimuli in.'
+      },
+      sort_area_width: {
+        type: jsPsych.plugins.parameterType.INT,
+        pretty_name: 'Sort area width',
+        default: .9*window.innerWidth, //1024,
+        description: 'The width of the container that subjects can move the stimuli in.'
+      },
+      prompt: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Prompt',
+        default: null,
+        description: 'Provide a reminder about the action the subject is supposed to take.'
+      },
+      prompt_location: {
+        type: jsPsych.plugins.parameterType.SELECT,
+        pretty_name: 'Prompt location',
+        options: ['above','below'],
+        default: 'above',
+        description: 'Indicates whether to show prompt "above" or "below" the sorting area.'
+      },
+      button_label: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Button label',
+        default:  'Continue',
+        description: 'The text that appears on the button to continue to the next trial.'
+      }
+    }
+  }
+
[…]

### 2023-05-09 experiment/js/jspsych-ebbinghaus-keyboard-practice.js

@@ -1,0 +1,332 @@
+/**
+ * jspsych-image-keyboard-response
+ * Josh de Leeuw
+ *
+ * plugin for displaying a stimulus and getting a keyboard response
+ *
+ * documentation: docs.jspsych.org
+ *
+ **/
+
+
+jsPsych.plugins["ebbinghaus-keyboard-practice"] = (function() {
+
+  var plugin = {};
+
+  jsPsych.pluginAPI.registerPreload('ebbinghaus-keyboard-practice', 'stimulus', 'image');
+
+  plugin.info = {
+    name: 'ebbinghaus-keyboard-practice',
+    description: '',
+    parameters: {
+      stimulus: {
+        type: jsPsych.plugins.parameterType.IMAGE,
+        pretty_name: 'Stimulus',
+        default: undefined,
+        description: 'The image to be displayed'
+      },
+      stimulus_height: {
+        type: jsPsych.plugins.parameterType.INT,
+        pretty_name: 'Image height',
+        default: 540,
+        description: 'Set the image height in pixels'
+      },
+      stimulus_width: {
+        type: jsPsych.plugins.parameterType.INT,
+        pretty_name: 'Image width',
+        default: 720,
+        description: 'Set the image width in pixels'
+      },
+      maintain_aspect_ratio: {
+        type: jsPsych.plugins.parameterType.BOOL,
+        pretty_name: 'Maintain aspect ratio',
+        default: true,
+        description: 'Maintain the aspect ratio after setting width or height'
+      },
+      choices: {
+        type: jsPsych.plugins.parameterType.KEYCODE,
+        array: true,
+        pretty_name: 'Choices',
+        default: jsPsych.ALL_KEYS,
+        description: 'The keys the subject is allowed to press to respond to the stimulus.'
+      },
+     correct_response: {
+        type: jsPsych.plugins.parameterType.INT, 
+        pretty_name: 'the correct repsonse for this trial', 
+          default: null, 
+          description: 'the button that participants should be pushing'
+      },
+     prompt: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Prompt',
+        default: null,
+        description: 'Any content here will be displayed below the stimulus.'
+      },
+      stimulus_duration: {
+        type: jsPsych.plugins.parameterType.INT,
+        pretty_name: 'Stimulus duration',
+        default: null,
+        description: 'How long to hide the stimulus.'
[…]

### 2023-05-09 experiment/js/jspsych-ebbinghaus-keyboard.js

@@ -1,0 +1,332 @@
+/**
+ * jspsych-image-keyboard-response
+ * Josh de Leeuw
+ *
+ * plugin for displaying a stimulus and getting a keyboard response
+ *
+ * documentation: docs.jspsych.org
+ *
+ **/
+
+
+jsPsych.plugins["ebbinghaus-keyboard"] = (function() {
+
+  var plugin = {};
+
+  jsPsych.pluginAPI.registerPreload('ebbinghaus-keyboard', 'stimulus', 'image');
+
+  plugin.info = {
+    name: 'image-keyboard-response',
+    description: '',
+    parameters: {
+      stimulus: {
+        type: jsPsych.plugins.parameterType.IMAGE,
+        pretty_name: 'Stimulus',
+        default: undefined,
+        description: 'The image to be displayed'
+      },
+      stimulus_height: {
+        type: jsPsych.plugins.parameterType.INT,
+        pretty_name: 'Image height',
+        default: 540,
+        description: 'Set the image height in pixels'
+      },
+      stimulus_width: {
+        type: jsPsych.plugins.parameterType.INT,
+        pretty_name: 'Image width',
+        default: 720,
+        description: 'Set the image width in pixels'
+      },
+      maintain_aspect_ratio: {
+        type: jsPsych.plugins.parameterType.BOOL,
+        pretty_name: 'Maintain aspect ratio',
+        default: true,
+        description: 'Maintain the aspect ratio after setting width or height'
+      },
+      choices: {
+        type: jsPsych.plugins.parameterType.KEYCODE,
+        array: true,
+        pretty_name: 'Choices',
+        default: jsPsych.ALL_KEYS,
+        description: 'The keys the subject is allowed to press to respond to the stimulus.'
+      },
+     correct_response: {
+        type: jsPsych.plugins.parameterType.INT, 
+        pretty_name: 'the correct repsonse for this trial', 
+          default: null, 
+          description: 'the button that participants should be pushing'
+      },
+     prompt: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Prompt',
+        default: null,
+        description: 'Any content here will be displayed below the stimulus.'
+      },
+      stimulus_duration: {
+        type: jsPsych.plugins.parameterType.INT,
+        pretty_name: 'Stimulus duration',
+        default: null,
+        description: 'How long to hide the stimulus.'
+      },
[…]

### 2023-05-09 experiment/js/jspsych-ebbinghaus.js

@@ -1,0 +1,327 @@
+/**
+ * jspsych-image-button-response
+ * Josh de Leeuw
+ *
+ * plugin for displaying a stimulus and getting a keyboard response
+ *
+ * documentation: docs.jspsych.org
+ *
+ **/
+
+jsPsych.plugins["ebbinghaus"] = (function() {
+
+  var plugin = {};
+
+  jsPsych.pluginAPI.registerPreload('ebbinghaus', 'stimulus', 'image');
+
+  plugin.info = {
+    name: 'ebbinghaus',
+    description: '',
+    parameters: {
+      stimulus: {
+        type: jsPsych.plugins.parameterType.IMAGE,
+        pretty_name: 'Stimulus',
+        default: undefined,
+        description: 'The image to be displayed'
+      },
+      choices: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Choices',
+        default: undefined,
+        array: true,
+        description: 'The labels for the buttons.'
+      },
+      button_html: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Button HTML',
+        default: '<button class="jspsych-btn">%choice%</button>',
+        array: true,
+        description: 'The html of the button. Can create own style.'
+      },
+      prompt: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Prompt',
+        default: null,
+        description: 'Any content here will be displayed under the button.'
+      },
+      stimulus_duration: {
+        type: jsPsych.plugins.parameterType.INT,
+        pretty_name: 'Stimulus duration',
+        default: null,
+        description: 'How long to hide the stimulus.'
+      },
+      trial_duration: {
+        type: jsPsych.plugins.parameterType.INT,
+        pretty_name: 'Trial duration',
+        default: null,
+        description: 'How long to show the trial.'
+      },
+      feedback_duration:  {
+          type: jsPsych.plugins.parameterType.INT, 
+          pretty_name: 'Feedback duration', 
+          default: null, 
+          description: 'How long to show the feedback'
+      },
+      margin_vertical: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Margin vertical',
+        default: '0px',
+        description: 'The vertical margin of the button.'
+      },
+      margin_horizontal: {
+        type: jsPsych.plugins.parameterType.STRING,
[…]

### 2023-05-09 experiment/js/jspsych-free-description-response-practice.js

@@ -1,0 +1,177 @@
+
+/**
+ * jspsych-survey-text
+ * a jspsych plugin for free response survey questions
+ *
+ * Josh de Leeuw
+ *
+ * documentation: docs.jspsych.org
+ *
+ */
+
+
+jsPsych.plugins['free-description-response-practice'] = (function() {
+
+  var plugin = {};
+
+  plugin.info = {
+    name: 'free-description-response-practice',
+    description: '',
+    parameters: {
+      questions: {
+        type: jsPsych.plugins.parameterType.COMPLEX,
+        array: true,
+        pretty_name: 'Questions',
+        default: undefined,
+        nested: {
+          prompt: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Prompt',
+            default: undefined,
+            description: 'Prompt for the subject to response'
+          },
+          placeholder: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Value',
+            default: "",
+            description: 'Placeholder text in the textfield.'
+          },
+          rows: {
+            type: jsPsych.plugins.parameterType.INT,
+            pretty_name: 'Rows',
+            default: 1,
+            description: 'The number of rows for the response text box.'
+          },
+          columns: {
+            type: jsPsych.plugins.parameterType.INT,
+            pretty_name: 'Columns',
+            default: 40,
+            description: 'The number of columns for the response text box.'
+          },
+          required: {
+            type: jsPsych.plugins.parameterType.BOOL,
+            pretty_name: 'Required',
+            default: false,
+            description: 'Require a response'
+          },
+          name: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Question Name',
+            default: '',
+            description: 'Controls the name of data values associated with this question'
+          }
+        }
+      },
+      preamble: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Preamble',
+        default: null,
+        description: 'HTML formatted string to display at the top of the page above all the questions.'
+      },
+      button_label: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Button label',
+        default:  'Continue',
+        description: 'The text that appears on the button to finish the trial.'
+      }
+    }
+  }
+
+  plugin.trial = function(display_element, trial) {
+
[…]

### 2023-05-09 experiment/js/jspsych-free-description-response.js

@@ -1,0 +1,177 @@
+
+/**
+ * jspsych-survey-text
+ * a jspsych plugin for free response survey questions
+ *
+ * Josh de Leeuw
+ *
+ * documentation: docs.jspsych.org
+ *
+ */
+
+
+jsPsych.plugins['free-description-response'] = (function() {
+
+  var plugin = {};
+
+  plugin.info = {
+    name: 'free-description-response',
+    description: '',
+    parameters: {
+      questions: {
+        type: jsPsych.plugins.parameterType.COMPLEX,
+        array: true,
+        pretty_name: 'Questions',
+        default: undefined,
+        nested: {
+          prompt: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Prompt',
+            default: undefined,
+            description: 'Prompt for the subject to response'
+          },
+          placeholder: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Value',
+            default: "",
+            description: 'Placeholder text in the textfield.'
+          },
+          rows: {
+            type: jsPsych.plugins.parameterType.INT,
+            pretty_name: 'Rows',
+            default: 1,
+            description: 'The number of rows for the response text box.'
+          },
+          columns: {
+            type: jsPsych.plugins.parameterType.INT,
+            pretty_name: 'Columns',
+            default: 40,
+            description: 'The number of columns for the response text box.'
+          },
+          required: {
+            type: jsPsych.plugins.parameterType.BOOL,
+            pretty_name: 'Required',
+            default: false,
+            description: 'Require a response'
+          },
+          name: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Question Name',
+            default: '',
+            description: 'Controls the name of data values associated with this question'
+          }
+        }
+      },
+      preamble: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Preamble',
+        default: null,
+        description: 'HTML formatted string to display at the top of the page above all the questions.'
+      },
+      button_label: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Button label',
+        default:  'Continue',
+        description: 'The text that appears on the button to finish the trial.'
+      }
+    }
+  }
+
+  plugin.trial = function(display_element, trial) {
+
[…]

### 2023-05-09 experiment/js/jspsych-funnel-debriefing-general.js

@@ -1,0 +1,176 @@
+/**
+ * jspsych-survey-text
+ * a jspsych plugin for free response survey questions
+ *
+ * Josh de Leeuw
+ *
+ * documentation: docs.jspsych.org
+ *
+ */
+
+
+jsPsych.plugins['funnel-debriefing-general'] = (function() {
+
+  var plugin = {};
+
+  plugin.info = {
+    name: 'funnel-debriefing-general',
+    description: '',
+    parameters: {
+      questions: {
+        type: jsPsych.plugins.parameterType.COMPLEX,
+        array: true,
+        pretty_name: 'Questions',
+        default: undefined,
+        nested: {
+          prompt: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Prompt',
+            default: undefined,
+            description: 'Prompt for the subject to response'
+          },
+          placeholder: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Value',
+            default: "",
+            description: 'Placeholder text in the textfield.'
+          },
+          rows: {
+            type: jsPsych.plugins.parameterType.INT,
+            pretty_name: 'Rows',
+            default: 1,
+            description: 'The number of rows for the response text box.'
+          },
+          columns: {
+            type: jsPsych.plugins.parameterType.INT,
+            pretty_name: 'Columns',
+            default: 40,
+            description: 'The number of columns for the response text box.'
+          },
+          required: {
+            type: jsPsych.plugins.parameterType.BOOL,
+            pretty_name: 'Required',
+            default: false,
+            description: 'Require a response'
+          },
+          name: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Question Name',
+            default: '',
+            description: 'Controls the name of data values associated with this question'
+          }
+        }
+      },
+      preamble: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Preamble',
+        default: null,
+        description: 'HTML formatted string to display at the top of the page above all the questions.'
+      },
+      button_label: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Button label',
+        default:  'Continue',
+        description: 'The text that appears on the button to finish the trial.'
+      }
+    }
+  }
+
+  plugin.trial = function(display_element, trial) {
+
[…]

### 2023-05-09 experiment/js/jspsych-funnel-debriefing-specific.js

@@ -1,0 +1,176 @@
+/**
+ * jspsych-survey-text
+ * a jspsych plugin for free response survey questions
+ *
+ * Josh de Leeuw
+ *
+ * documentation: docs.jspsych.org
+ *
+ */
+
+
+jsPsych.plugins['funnel-debriefing-specific'] = (function() {
+
+  var plugin = {};
+
+  plugin.info = {
+    name: 'funnel-debriefing-specific',
+    description: '',
+    parameters: {
+      questions: {
+        type: jsPsych.plugins.parameterType.COMPLEX,
+        array: true,
+        pretty_name: 'Questions',
+        default: undefined,
+        nested: {
+          prompt: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Prompt',
+            default: undefined,
+            description: 'Prompt for the subject to response'
+          },
+          placeholder: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Value',
+            default: "",
+            description: 'Placeholder text in the textfield.'
+          },
+          rows: {
+            type: jsPsych.plugins.parameterType.INT,
+            pretty_name: 'Rows',
+            default: 1,
+            description: 'The number of rows for the response text box.'
+          },
+          columns: {
+            type: jsPsych.plugins.parameterType.INT,
+            pretty_name: 'Columns',
+            default: 40,
+            description: 'The number of columns for the response text box.'
+          },
+          required: {
+            type: jsPsych.plugins.parameterType.BOOL,
+            pretty_name: 'Required',
+            default: false,
+            description: 'Require a response'
+          },
+          name: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Question Name',
+            default: '',
+            description: 'Controls the name of data values associated with this question'
+          }
+        }
+      },
+      preamble: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Preamble',
+        default: null,
+        description: 'HTML formatted string to display at the top of the page above all the questions.'
+      },
+      button_label: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Button label',
+        default:  'Continue',
+        description: 'The text that appears on the button to finish the trial.'
+      }
+    }
+  }
+
+  plugin.trial = function(display_element, trial) {
+
[…]

### 2023-05-09 experiment/js/jspsych-horizon-sticker-practice.js

@@ -1,0 +1,331 @@
+
+/**
+ * jspsych-free-sort
+ * plugin for drag-and-drop sorting of a collection of images
+ * Josh de Leeuw
+ *
+ * documentation: docs.jspsych.org
+ */
+
+
+jsPsych.plugins['horizon-sticker-practice'] = (function() {
+
+  var plugin = {};
+
+  jsPsych.pluginAPI.registerPreload('free-sort', 'stimuli', 'image');
+
+  plugin.info = {
+    name: 'horizon-sticker-practice',
+    description: '',
+    parameters: {
+      stimuli: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Stimuli',
+        default: undefined,
+        array: true,
+        description: 'Images to be displayed.'
+      },
+      stim_height: {
+        type: jsPsych.plugins.parameterType.INT,
+        pretty_name: 'Stimulus height',
+        default: 100,
+        description: 'Height of images in pixels.'
+      },
+      stim_width: {
+        type: jsPsych.plugins.parameterType.INT,
+        pretty_name: 'Stimulus width',
+        default: 100,
+        description: 'Width of images in pixels'
+      },
+      
+      horizon_height: {
+        type: jsPsych.plugins.parameterType.INT,
+        pretty_name: 'horizon height',
+        default: 5,
+        description: 'Height of horizon in pixels.'
+      },
+        
+      horizon_width: {
+        type: jsPsych.plugins.parameterType.INT,
+        pretty_name: 'horizon width',
+        default: 454,
+        description: 'width of horizon in pixels.'
+      },
+       
+      sort_area_height: {
+        type: jsPsych.plugins.parameterType.INT,
+        pretty_name: 'Sort area height',
+        default: 334.4,
+        description: 'The height of the container that subjects can move the stimuli in.'
+      },
+      sort_area_width: {
+        type: jsPsych.plugins.parameterType.INT,
+        pretty_name: 'Sort area width',
+        default: 451.4 ,
+        description: 'The width of the container that subjects can move the stimuli in.'
+      },
+      prompt: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Prompt',
+        default: null,
+        description: 'It can be used to provide a reminder about the action the subject is supposed to take.'
+      },
+      prompt_location: {
+        type: jsPsych.plugins.parameterType.SELECT,
+        pretty_name: 'Prompt location',
[…]

### 2023-05-09 experiment/js/jspsych-horizon-sticker.js

@@ -1,0 +1,461 @@
+
+/**
+ * jspsych-free-sort
+ * plugin for drag-and-drop sorting of a collection of images
+ * Josh de Leeuw
+ *
+ * documentation: docs.jspsych.org
+ */
+
+
+jsPsych.plugins['horizon-sticker'] = (function() {
+
+  var plugin = {};
+
+  jsPsych.pluginAPI.registerPreload('free-sort', 'stimuli', 'image');
+
+  plugin.info = {
+    name: 'horizon-sticker',
+    description: '',
+    parameters: {
+      stimuli: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Stimuli',
+        default: undefined,
+        array: true,
+        description: 'Images to be displayed.'
+      },
+      stim_height: {
+        type: jsPsych.plugins.parameterType.INT,
+        pretty_name: 'Stimulus height',
+        default: 100,
+        description: 'Height of images in pixels.'
+      },
+      stim_width: {
+        type: jsPsych.plugins.parameterType.INT,
+        pretty_name: 'Stimulus width',
+        default: 100,
+        description: 'Width of images in pixels'
+      },
+      
+      horizon_height: {
+        type: jsPsych.plugins.parameterType.INT,
+        pretty_name: 'horizon height',
+        default: 5,
+        description: 'Height of horizon in pixels.'
+      },
+        
+      horizon_width: {
+        type: jsPsych.plugins.parameterType.INT,
+        pretty_name: 'horizon width',
+        default: 454,
+        description: 'width of horizon in pixels.'
+      },
+       
+      sort_area_height: {
+        type: jsPsych.plugins.parameterType.INT,
+        pretty_name: 'Sort area height',
+        default: 334.4,
+        description: 'The height of the container that subjects can move the stimuli in.'
+      },
+      sort_area_width: {
+        type: jsPsych.plugins.parameterType.INT,
+        pretty_name: 'Sort area width',
+        default: 451.4 ,
+        description: 'The width of the container that subjects can move the stimuli in.'
+      },
+      prompt: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Prompt',
+        default: null,
+        description: 'It can be used to provide a reminder about the action the subject is supposed to take.'
+      },
+      prompt_location: {
+        type: jsPsych.plugins.parameterType.SELECT,
+        pretty_name: 'Prompt location',
+        options: ['above','below'],
+        default: 'above',
[…]

### 2023-05-09 experiment/js/jspsych-image-button-response.js

@@ -1,0 +1,259 @@
+/**
+ * jspsych-image-button-response
+ * Josh de Leeuw
+ *
+ * plugin for displaying a stimulus and getting a keyboard response
+ *
+ * documentation: docs.jspsych.org
+ *
+ **/
+
+jsPsych.plugins["image-button-response"] = (function() {
+
+  var plugin = {};
+
+  jsPsych.pluginAPI.registerPreload('image-button-response', 'stimulus', 'image');
+
+  plugin.info = {
+    name: 'image-button-response',
+    description: '',
+    parameters: {
+      stimulus: {
+        type: jsPsych.plugins.parameterType.IMAGE,
+        pretty_name: 'Stimulus',
+        default: undefined,
+        description: 'The image to be displayed'
+      },
+      choices: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Choices',
+        default: undefined,
+        array: true,
+        description: 'The labels for the buttons.'
+      },
+      button_html: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Button HTML',
+        default: '<button class="jspsych-btn">%choice%</button>',
+        array: true,
+        description: 'The html of the button. Can create own style.'
+      },
+      prompt: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Prompt',
+        default: null,
+        description: 'Any content here will be displayed under the button.'
+      },
+      stimulus_duration: {
+        type: jsPsych.plugins.parameterType.INT,
+        pretty_name: 'Stimulus duration',
+        default: null,
+        description: 'How long to hide the stimulus.'
+      },
+      trial_duration: {
+        type: jsPsych.plugins.parameterType.INT,
+        pretty_name: 'Trial duration',
+        default: null,
+        description: 'How long to show the trial.'
+      },
+      margin_vertical: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Margin vertical',
+        default: '0px',
+        description: 'The vertical margin of the button.'
+      },
+      margin_horizontal: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Margin horizontal',
+        default: '40px',
+        description: 'The horizontal margin of the button.'
+      },
+      response_ends_trial: {
+        type: jsPsych.plugins.parameterType.BOOL,
+        pretty_name: 'Response ends trial',
+        default: true,
[…]

### 2023-05-09 experiment/js/jspsych-konva-draw-circle-WORKING.js

@@ -1,0 +1,547 @@
+//TODO: alert needs to be variable in order for the language to work 
+
+
+jsPsych.plugins['konva-draw-circle'] = (function(){
+
+  var plugin = {};
+
+  plugin.info = {
+    name: 'konva-draw-circle',
+    parameters: {
+        
+        canvas_width: {
+            
+        type: jsPsych.plugins.parameterType.INT,
+        pretty_name: 'Sort area width',
+        default: .8*window.innerWidth, //550,
+        description: 'The height of the container that subjects can move the stimuli in.'
+            
+        },
+        canvas_height:{
+        
+        type: jsPsych.plugins.parameterType.INT,
+        pretty_name: 'Sort area height',
+        default: .8*window.innerHeight, //550,
+        description: 'The height of the container that subjects can move the stimuli in.'
+  
+        },
+        prompt:{
+        
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Prompt',
+        default: null,
+        description: 'Provide a reminder about the action the subject is supposed to take.'
+        
+        },
+        button_label:{
+            
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Button label',
+        default:  'Continue',
+        description: 'The text that appears on the button to continue to the next trial.'
+            
+        }
+        
+    }
+  }
+
+  plugin.trial = function(display_element, trial){
+      
+    var start_time = performance.now()
+    var html = ""
+    if (trial.prompt !== null){
+        html += trial.prompt
+    }
+    
+    html += '<body>' + 
+    '<div id="stage-parent">'+
+    '<div id="container1"></div>'+
+    '<div id="menu">'+
+    '<div>' + 
+    '<button id="delete-button">Delete</button>'+
+    '</div>'+
+    '</div>'
+      
+    display_element.innerHTML = html
+      
+      
+    display_element.innerHTML += '<p><button id="jspsych-draw-circles-done-btn" class="jspsych-btn">'+trial.button_label+'</button></p>';
+      
+// set up stage
+      
+    var stage = new Konva.Stage({container: 'container1', width: trial.canvas_width, height: trial.canvas_height});
+    var layer = new Konva.Layer({draggable: false});
+    stage.add(layer);
+      
+// important array to keep track of circles and labels       
+    var circles = []
+    var labels = []
+      
+
+// draw a background rect to catch events.
[…]

### 2023-05-09 experiment/js/jspsych-konva-draw-circle.js

@@ -1,0 +1,593 @@
+//TODO: alert needs to be variable in order for the language to work 
+
+
+jsPsych.plugins['konva-draw-circle'] = (function(){
+
+  var plugin = {};
+
+  plugin.info = {
+    name: 'konva-draw-circle',
+    parameters: {
+        
+        canvas_width: {
+            
+        type: jsPsych.plugins.parameterType.INT,
+        pretty_name: 'Sort area width',
+        default: 550, //550,
+        description: 'The height of the container that subjects can move the stimuli in.'
+            
+        },
+        canvas_height:{
+        
+        type: jsPsych.plugins.parameterType.INT,
+        pretty_name: 'Sort area height',
+        default: 550, //550,
+        description: 'The height of the container that subjects can move the stimuli in.'
+  
+        },
+        textbox_default:{
+        
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'textbox_default',
+        default: "Add label here",
+        description: 'text that prompts participants to input label'
+        
+        },
+        
+        delete_button:{
+        
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'delete_button',
+        default: "Delete",
+        description: 'label on delete button'
+        
+        },
+        
+        unlabeled_alert:{
+        
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'unlabeled_alert',
+        default: "",
+        description: 'alert text when the participants have not labeled all the drawn circles'
+        
+        },
+        no_circle_alert:{
+        
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'no_circle_alert',
+        default: "",
+        description: 'alert text when the participants have not drawn any circle'
+        
+        },
+        too_small_alert:{
+        
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'too_small_alert',
+        default: "",
+        description: 'alert text when the circle just drawn is too small'
+        
+        },
+        prompt:{
+        
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Prompt',
+        default: null,
+        description: 'Provide a reminder about the action the subject is supposed to take.'
+        
+        },
+        button_label:{
+            
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Button label',
[…]

### 2023-05-09 experiment/js/jspsych-pen-choice.js

@@ -1,0 +1,259 @@
+/**
+ * jspsych-image-button-response
+ * Josh de Leeuw
+ *
+ * plugin for displaying a stimulus and getting a keyboard response
+ *
+ * documentation: docs.jspsych.org
+ *
+ **/
+
+jsPsych.plugins["pen-choice"] = (function() {
+
+  var plugin = {};
+
+  jsPsych.pluginAPI.registerPreload('pen-choice', 'stimulus', 'image');
+
+  plugin.info = {
+    name: 'pen-choice',
+    description: '',
+    parameters: {
+      stimulus: {
+        type: jsPsych.plugins.parameterType.IMAGE,
+        pretty_name: 'Stimulus',
+        default: undefined,
+        description: 'The image to be displayed'
+      },
+      choices: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Choices',
+        default: undefined,
+        array: true,
+        description: 'The labels for the buttons.'
+      },
+      button_html: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Button HTML',
+        default: '<button class="jspsych-btn">%choice%</button>',
+        array: true,
+        description: 'The html of the button. Can create own style.'
+      },
+      prompt: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Prompt',
+        default: null,
+        description: 'Any content here will be displayed under the button.'
+      },
+      stimulus_duration: {
+        type: jsPsych.plugins.parameterType.INT,
+        pretty_name: 'Stimulus duration',
+        default: null,
+        description: 'How long to hide the stimulus.'
+      },
+      trial_duration: {
+        type: jsPsych.plugins.parameterType.INT,
+        pretty_name: 'Trial duration',
+        default: null,
+        description: 'How long to show the trial.'
+      },
+      margin_vertical: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Margin vertical',
+        default: '0px',
+        description: 'The vertical margin of the button.'
+      },
+      margin_horizontal: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Margin horizontal',
+        default: '40px',
+        description: 'The horizontal margin of the button.'
+      },
+      response_ends_trial: {
+        type: jsPsych.plugins.parameterType.BOOL,
+        pretty_name: 'Response ends trial',
+        default: true,
+        description: 'If true, then trial will end when user responds.'
+      },
[…]

### 2023-05-09 experiment/js/jspsych-prolific-ID.js

@@ -1,0 +1,176 @@
+/**
+ * jspsych-survey-text
+ * a jspsych plugin for free response survey questions
+ *
+ * Josh de Leeuw
+ *
+ * documentation: docs.jspsych.org
+ *
+ */
+
+
+jsPsych.plugins['prolific-id'] = (function() {
+
+  var plugin = {};
+
+  plugin.info = {
+    name: 'prolific-id',
+    description: '',
+    parameters: {
+      questions: {
+        type: jsPsych.plugins.parameterType.COMPLEX,
+        array: true,
+        pretty_name: 'Questions',
+        default: undefined,
+        nested: {
+          prompt: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Prompt',
+            default: undefined,
+            description: 'Prompt for the subject to response'
+          },
+          placeholder: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Value',
+            default: "",
+            description: 'Placeholder text in the textfield.'
+          },
+          rows: {
+            type: jsPsych.plugins.parameterType.INT,
+            pretty_name: 'Rows',
+            default: 1,
+            description: 'The number of rows for the response text box.'
+          },
+          columns: {
+            type: jsPsych.plugins.parameterType.INT,
+            pretty_name: 'Columns',
+            default: 40,
+            description: 'The number of columns for the response text box.'
+          },
+          required: {
+            type: jsPsych.plugins.parameterType.BOOL,
+            pretty_name: 'Required',
+            default: false,
+            description: 'Require a response'
+          },
+          name: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Question Name',
+            default: '',
+            description: 'Controls the name of data values associated with this question'
+          }
+        }
+      },
+      preamble: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Preamble',
+        default: null,
+        description: 'HTML formatted string to display at the top of the page above all the questions.'
+      },
+      button_label: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Button label',
+        default:  'Continue',
+        description: 'The text that appears on the button to finish the trial.'
+      }
+    }
+  }
+
+  plugin.trial = function(display_element, trial) {
+
+    for (var i = 0; i < trial.questions.length; i++) {
[…]

### 2023-05-09 experiment/js/jspsych-survey-multi-choice-C.js

@@ -1,0 +1,221 @@
+/**
+ * jspsych-survey-multi-choice
+ * a jspsych plugin for multiple choice survey questions
+ *
+ * Shane Martin
+ *
+ * documentation: docs.jspsych.org
+ *
+ */
+
+
+jsPsych.plugins['survey-multi-choice'] = (function() {
+  var plugin = {};
+
+  plugin.info = {
+    name: 'survey-multi-choice',
+    description: '',
+    parameters: {
+      questions: {
+        type: jsPsych.plugins.parameterType.COMPLEX,
+        array: true,
+        pretty_name: 'Questions',
+        nested: {
+          prompt: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Prompt',
+            default: undefined,
+            description: 'The strings that will be associated with a group of options.'
+          },
+          options: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Options',
+            array: true,
+            default: undefined,
+            description: 'Displays options for an individual question.'
+          },
+          required: {
+            type: jsPsych.plugins.parameterType.BOOL,
+            pretty_name: 'Required',
+            default: false,
+            description: 'Subject will be required to pick an option for each question.'
+          },
+          horizontal: {
+            type: jsPsych.plugins.parameterType.BOOL,
+            pretty_name: 'Horizontal',
+            default: false,
+            description: 'If true, then questions are centered and options are displayed horizontally.'
+          },
+          name: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Question Name',
+            default: '',
+            description: 'Controls the name of data values associated with this question'
+          },
+          timeout: {
+            type: jsPsych.plugins.parameterType.INT,
+            pretty_name: 'Timeout',
+            default: null,
+            description: 'Optional timeout (in seconds) if question is not answered'
+          }
+        }
+      },
+      randomize_question_order: {
+        type: jsPsych.plugins.parameterType.BOOL,
+        pretty_name: 'Randomize Question Order',
+        default: false,
+        description: 'If true, the order of the questions will be randomized'
+      },
+      preamble: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Preamble',
+        default: null,
[…]

### 2023-05-09 experiment/js/jspsych-survey-multi-choice.js

@@ -1,0 +1,221 @@
+/**
+ * jspsych-survey-multi-choice
+ * a jspsych plugin for multiple choice survey questions
+ *
+ * Shane Martin
+ *
+ * documentation: docs.jspsych.org
+ *
+ */
+
+
+jsPsych.plugins['survey-multi-choice'] = (function() {
+  var plugin = {};
+
+  plugin.info = {
+    name: 'survey-multi-choice',
+    description: '',
+    parameters: {
+      questions: {
+        type: jsPsych.plugins.parameterType.COMPLEX,
+        array: true,
+        pretty_name: 'Questions',
+        nested: {
+          prompt: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Prompt',
+            default: undefined,
+            description: 'The strings that will be associated with a group of options.'
+          },
+          options: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Options',
+            array: true,
+            default: undefined,
+            description: 'Displays options for an individual question.'
+          },
+          required: {
+            type: jsPsych.plugins.parameterType.BOOL,
+            pretty_name: 'Required',
+            default: false,
+            description: 'Subject will be required to pick an option for each question.'
+          },
+          horizontal: {
+            type: jsPsych.plugins.parameterType.BOOL,
+            pretty_name: 'Horizontal',
+            default: false,
+            description: 'If true, then questions are centered and options are displayed horizontally.'
+          },
+          name: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Question Name',
+            default: '',
+            description: 'Controls the name of data values associated with this question'
+          },
+          timeout: {
+            type: jsPsych.plugins.parameterType.INT,
+            pretty_name: 'Timeout',
+            default: null,
+            description: 'Optional timeout (in seconds) if question is not answered'
+          }
+        }
+      },
+      randomize_question_order: {
+        type: jsPsych.plugins.parameterType.BOOL,
+        pretty_name: 'Randomize Question Order',
+        default: false,
+        description: 'If true, the order of the questions will be randomized'
+      },
+      preamble: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Preamble',
+        default: null,
[…]

### 2023-05-09 experiment/js/jspsych-survey-multi-select.js

@@ -1,0 +1,223 @@
+/**
+ * jspsych-survey-multi-select
+ * a jspsych plugin for multiple choice survey questions
+ *
+ * documentation: docs.jspsych.org
+ *
+ */
+
+
+jsPsych.plugins['survey-multi-select'] = (function() {
+  var plugin = {};
+
+  plugin.info = {
+    name: 'survey-multi-select',
+    description: '',
+    parameters: {
+      questions: {
+        type: jsPsych.plugins.parameterType.COMPLEX,
+        array: true,
+        pretty_name: 'Questions',
+        nested: {
+          prompt: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Prompt',
+            default: undefined,
+            description: 'The strings that will be associated with a group of options.'
+          },
+          options: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Options',
+            array: true,
+            default: undefined,
+            description: 'Displays options for an individual question.'
+          },
+          horizontal: {
+            type: jsPsych.plugins.parameterType.BOOL,
+            pretty_name: 'Horizontal',
+            default: false,
+            description: 'If true, then questions are centered and options are displayed horizontally.'
+          },
+          required: {
+            type: jsPsych.plugins.parameterType.BOOL,
+            pretty_name: 'Required',
+            default: false,
+            description: 'Subject will be required to pick at least one option for this question.'
+          },
+          name: {
+            type: jsPsych.plugins.parameterType.STRING,
+            pretty_name: 'Question Name',
+            default: '',
+            description: 'Controls the name of data values associated with this question'
+          }
+        }
+      },
+      randomize_question_order: {
+        type: jsPsych.plugins.parameterType.BOOL,
+        pretty_name: 'Randomize Question Order',
+        default: false,
+        description: 'If true, the order of the questions will be randomized'
+      },
+      preamble: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Preamble',
+        default: null,
+        description: 'HTML formatted string to display at the top of the page above all the questions.'
+      },
+      button_label: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Button label',
+        default:  'Continue',
+        description: 'Label of the button.'
+      },
+      required_message: {
[…]

### 2023-05-09 experiment/js/jspsych-video-button-response.js

@@ -1,0 +1,288 @@
+/**
+ * jspsych-video-button-response
+ * Josh de Leeuw
+ *
+ * plugin for playing a video file and getting a button response
+ *
+ * documentation: docs.jspsych.org
+ *
+ **/
+
+jsPsych.plugins["video-button-response"] = (function() {
+
+  var plugin = {};
+
+  jsPsych.pluginAPI.registerPreload('video-button-response', 'stimulus', 'video');
+
+  plugin.info = {
+    name: 'video-button-response',
+    description: '',
+    parameters: {
+      sources: {
+        type: jsPsych.plugins.parameterType.VIDEO,
+        pretty_name: 'Video',
+        default: undefined,
+        description: 'The video file to play.'
+      },
+      choices: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Choices',
+        default: undefined,
+        array: true,
+        description: 'The labels for the buttons.'
+      },
+      button_html: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Button HTML',
+        default: '<button class="jspsych-btn">%choice%</button>',
+        array: true,
+        description: 'The html of the button. Can create own style.'
+      },
+      prompt: {
+        type: jsPsych.plugins.parameterType.STRING,
+        pretty_name: 'Prompt',
+        default: null,
+        description: 'Any content here will be displayed below the buttons.'
+      },
+      width: {
+        type: jsPsych.plugins.parameterType.INT,
+        pretty_name: 'Width',
+        default: '',
+        description: 'The width of the video in pixels.'
+      },
+      height: {
+        type: jsPsych.plugins.parameterType.INT,
+        pretty_name: 'Height',
+        default: '',
+        description: 'The height of the video display in pixels.'
+      },
+      autoplay: {
+        type: jsPsych.plugins.parameterType.BOOL,
+        pretty_name: 'Autoplay',
+        default: true,
+        description: 'If true, the video will begin playing as soon as it has loaded.'
+      },
+        
+      border: {
+        type: jsPsych.plugins.parameterType.BOOL,
+        pretty_name: 'Border',
+        default:true,
+        description: 'If true, the video will have border around it'   
+      },
+      controls: {
+        type: jsPsych.plugins.parameterType.BOOL,
+        pretty_name: 'Controls',
+        default: false,
+        description: 'If true, the subject will be able to pause the video or move the playback to any point in the video.'
[…]

### 2023-05-09 experiment/js/stim_E.js

@@ -1,0 +1,414 @@
+function shuffle(a) {
+        var j, x, i;
+        for (i = a.length - 1; i > 0; i--) {
+            j = Math.floor(Math.random() * (i + 1));
+            x = a[i];
+            a[i] = a[j];
+            a[j] = x;
+        }
+        return a;
+    }
+
+single_triads = shuffle([
+                        ["teacup", ["glass", "kettle"]], 
+                        ["beer", ["juice", "party"]],
+                        ["pigeon", ["duck", "nest"]], 
+                        ["ball", ["dice", "child"]], 
+                        ["boot", ["slipper", "foot"]], 
+                        ["hair", ["beard", "comb"]],
+                        ["bullet", ["arrow", "gun"]], 
+                        ["carrot", ["peas", "rabbit"]], 
+                        ["chair", ["stool", "desk"]],
+                        ["chalk", ["marker", "blackboard"]], 
+                        ["chimney", ["wall", "fire"]],
+                        ["squirrel", ["mouse", "acorn"]], 
+                        ["crayon", ["paintbrush", "drawing"]], 
+                        ["cup", ["saucer", "coffee"]],
+                        ["door", ["window", "key"]], 
+                        ["piano", ["flute", "song"]], 
+                        ["dust", ["ash", "broom"]],
+                        ["soccer", ["tennis", "goal"]], 
+                        ["kitchen", ["bedroom", "refrigerator"]], 
+                        ["knight", ["soldier", "armor"]], 
+                        ["gloves", ["shorts", "ski"]], 
+                        ["mouth", ["nose", "toothbrush"]],
+                        ["movie", ["cartoon", "director"]], 
+                        //["needle", ["pin", "sewing machine"]], 
+                        ["oyster", ["clam", "pearl"]], 
+                        ["mailman", ["firefighter", "package"]], 
+                        ["sink", ["bathtub", "soap"]], 
+                        ["spider", ["grasshopper", "web"]],
+                        ["sword", ["dagger", "pirate"]], 
+                        ["tent", ["cabin", "campfire"]], 
+                        ["towel", ["handkerchief", "shower"]], 
+                        ["train", ["bus", "tracks"]],
+                        ["peach", ["plum", "pit"]], 
[…]

### 2023-05-09 experiment/js/stim_M.js

@@ -1,0 +1,414 @@
+function shuffle(a) {
+        var j, x, i;
+        for (i = a.length - 1; i > 0; i--) {
+            j = Math.floor(Math.random() * (i + 1));
+            x = a[i];
+            a[i] = a[j];
+            a[j] = x;
+        }
+        return a;
+    }
+
+single_triads = shuffle([
+                        ["茶杯", ["玻璃杯", "水壶"]], 
+                        ["啤酒", ["果汁", "派对"]],
+                        ["鸽子", ["鸭", "鸟巢"]], 
+                        ["球", ["骰子", "儿童"]], 
+                        ["靴子", ["拖鞋", "脚"]], 
+                        ["头发", ["胡子", "梳子"]],
+                        ["子弹", ["箭", "手枪"]], 
+                        ["胡萝卜", ["豌豆", "兔子"]], 
+                        ["椅", ["凳", "桌"]],
+                        ["粉笔", ["马克笔", "黑板"]], 
+                        ["烟囱", ["墙", "火"]],
+                        ["松鼠", ["老鼠", "橡实"]], 
+                        ["蜡笔", ["油漆刷", "图画"]], 
+                        ["杯子", ["茶碟", "咖啡"]],
+                        ["门", ["窗户", "钥匙"]], 
+                        ["钢琴", ["长笛", "歌"]], 
+                        ["灰尘", ["灰烬", "扫帚"]],
+                        ["足球", ["网球", "球门"]], 
+                        ["厨房", ["卧室", "冰箱"]], 
+                        ["骑士", ["士兵", "盔甲"]], 
+                        ["手套", ["短裤", "滑雪"]], 
+                        ["嘴", ["鼻", "牙刷"]],
+                        ["电影", ["卡通片", "导演"]], 
+                        //["针", ["别针", "缝纫机"]], 
+                        ["蚌", ["蛤蜊", "珍珠"]], 
+                        ["快递员", ["消防员", "包裹"]], 
+                        ["洗脸盆", ["浴缸", "肥皂"]], 
+                        ["蜘蛛", ["蚱蜢", "网"]],
+                        ["弯刀", ["匕首", "海盗"]], 
+                        ["帐篷", ["小木屋", "篝火"]], 
+                        ["毛巾", ["手帕", "浴室"]], 
[…]

### 2023-05-09 experiment/js/stim_V.js

@@ -1,0 +1,414 @@
+function shuffle(a) {
+        var j, x, i;
+        for (i = a.length - 1; i > 0; i--) {
+            j = Math.floor(Math.random() * (i + 1));
+            x = a[i];
+            a[i] = a[j];
+            a[j] = x;
+        }
+        return a;
+    }
+
+single_triads = shuffle([
+                        ["cốc trà", ["ly", "ấm đun nước"]], 
+                        ["bia", ["nước ép", "tiệc"]],
+                        ["bồ câu", ["vịt", "tổ"]], 
+                        ["bóng", ["xúc xắc", "đứa trẻ"]], 
+                        ["ủng", ["dép", "bàn chân"]], 
+                        ["tóc", ["râu", "lược"]],
+                        ["đạn", ["mũi tên", "súng"]], 
+                        ["cà rốt", ["đậu", "thỏ"]], 
+                        ["ghế", ["ghế đẩu", "bàn"]],
+                        ["phấn", ["bút lông", "bảng đen"]], 
+                        ["ống khói", ["tường", "lửa"]],
+                        ["sóc", ["chuột", "hạt dẻ"]], 
+                        ["bút sáp", ["cọ", "tranh vẽ"]], 
+                        ["cốc", ["đĩa lót tách", "cà phê"]],
+                        ["cửa ra vào", ["cửa sổ", "chìa khoá"]], 
+                        ["đàn pi-a-nô", ["sáo", "bài hát"]], 
+                        ["bụi", ["tro", "chổi"]],
+                        ["bóng đá", ["quần vợt", "khung thành"]], 
+                        ["nhà bếp", ["phòng ngủ", "tủ lạnh"]], 
+                        ["hiệp sĩ", ["người lính", "áo giáp"]], 
+                        ["găng tay", ["quần đùi", "ván trượt tuyết"]], 
+                        ["miệng", ["mũi", "bàn chải đánh răng"]],
+                        ["phim", ["hoạt hình", "đạo diễn"]], 
+                        //["needle", ["pin", "sewing machine"]], 
+                        ["con trai", ["con sò", "ngọc trai"]], 
+                        ["người đưa thư", ["lính cứu hoả", "bưu kiện"]], 
+                        ["chậu rửa tay", ["bồn tắm", "xà phòng"]], 
[…]
